### 2025-05-30 create-rhello.Rmd
into S3

---
title: "Creating the ``r params$package_name`` R package"
author: "Your Name"
date: "The Date"
knit: litr::render
output: litr::litr_html_document
params:
  package_name: "FSHybridPLS" # <-- change this to your package name
  package_parent_dir: "." # <-- relative to this file's location
---

<!-- This Rmd file contains all the code needed to define an R package.  Press "Knit" in RStudio or more generally run `litr::render("name-of-this-file.Rmd")` to generate the R package.  Remember that when you want to modify anything about the R package, you should modify this document rather than the package that is outputted.
-->

## Package setup

We start by specifying the information needed in the DESCRIPTION file of the R package.

```{r package-setup, message=FALSE, results='hide'}
usethis::create_package(
  path = ".",
  fields = list(
    Package = params$package_name,
    Version = "0.0.0.9000",
    Title = "A Package That Says Hello",
    Description = "This package says hello.  But its actual purpose is to show how an R package can be completely coded in a single R markdown file.",
    Imports = "fda (>= 6.1.3)",
    `Authors@R` = person(
      given = "First",
      family = "Last",
      email = "you@gmail.com",
      role = c("aut", "cre")
      )
  )
)
usethis::use_mit_license(copyright_holder = "F. Last")
```

# Class predictor_hybrid
The `predictor_hybrid` class is an S3 object for representing hybrid predictors: a combination of scalar and functional covariates. The following code defines the class.

```{r}
#' Create a predictor_hybrid object (S3 version)
#'
#' Constructs a hybrid predictor object that stores both scalar and functional predictors,
#' along with Jacobians and metadata.
#'
#' @param Z A numeric matrix of dimension \code{n_sample × n_scalar} representing scalar predictors.
#' @param functional_list A list of functional predictors (e.g., \code{fd} objects from the \code{fda} package).
#' @param jacobian_list A list of Jacobian matrices corresponding to the functional predictors.
#' @param n_basis_list A numeric vector indicating the number of basis functions for each functional predictor.
#' @param n_sample Number of observations (samples).
#' @param n_functional Number of functional predictors.
#' @param n_scalar Number of scalar predictors.
#'
#' @return A list of class \code{predictor_hybrid}.
#' @export
predictor_hybrid <- function(Z, functional_list, jacobian_list,
                             n_basis_list, n_sample, n_functional, n_scalar) {
  stopifnot(is.matrix(Z))
  stopifnot(length(functional_list) == n_functional)
  stopifnot(length(jacobian_list) == n_functional)
  stopifnot(length(n_basis_list) == n_functional)

  structure(
    list(
      Z = Z,
      functional_list = functional_list,
      jacobian_list = jacobian_list,
      n_basis_list = n_basis_list,
      n_sample = n_sample,
      n_functional = n_functional,
      n_scalar = n_scalar
    ),
    class = "predictor_hybrid"
  )
}
```

Let's write some tests to make sure the function behaves as desired:
```{r}
testthat::test_that("predictor_hybrid constructor works as expected (S3)", {
  Z <- matrix(rnorm(100 * 5), nrow = 100, ncol = 5)
  fd1 <- list(fdobj = "fd1 placeholder")
  fd2 <- list(fdobj = "fd2 placeholder")
  J1 <- matrix(runif(100), nrow = 10)
  J2 <- matrix(runif(200), nrow = 20)

  obj <- predictor_hybrid(
    Z = Z,
    functional_list = list(fd1, fd2),
    jacobian_list = list(J1, J2),
    n_basis_list = c(10, 20),
    n_sample = 100,
    n_functional = 2,
    n_scalar = 5
  )

  testthat::expect_s3_class(obj, "predictor_hybrid")
  testthat::expect_equal(nrow(obj$Z), 100)
  testthat::expect_equal(ncol(obj$Z), 5)
  testthat::expect_equal(length(obj$functional_list), 2)
  testthat::expect_equal(length(obj$jacobian_list), 2)
  testthat::expect_equal(obj$n_basis_list, c(10, 20))
  testthat::expect_equal(obj$n_sample, 100)
  testthat::expect_equal(obj$n_functional, 2)
  testthat::expect_equal(obj$n_scalar, 5)
})

```

## Basic arithmetic

### add.predictor_hybrid
Performs element-wise addition of two `predictor_hybrid` objects.  Functional predictors are combined using `plus.fd()` and `times.fd()` from the `fda` package.

- Usage

```r
add.predictor_hybrid(input, other, alpha = 1)
```

- Arguments:

  - `input`: A `predictor_hybrid` object.
  - `other`: Another `predictor_hybrid` object to be added.
  - `alpha`: A scalar multiplier applied to `other` before addition (default is 1).

- Value:
Returns a new `predictor_hybrid` object representing the result of the addition.

- Details: 
  - This function assumes both objects have the same number and structure of functional and scalar predictors.  
  - Functional parts are scaled by `alpha` using `times.fd()` and then summed using `plus.fd()`.  
  - Scalar predictors are added using standard matrix addition.

```{r}
#' Add two predictor_hybrid objects
#'
#' Performs element-wise addition of two predictor_hybrid objects.
#' Functional predictors are combined using `plus.fd()` and `times.fd()`.
#'
#' @param input A predictor_hybrid object.
#' @param other Another predictor_hybrid object.
#' @param alpha A numeric scalar multiplier for `other`.
#'
#' @return A new predictor_hybrid object representing the sum.
#' @export
add.predictor_hybrid <- function(input, other, alpha = 1) {
  if (input$n_functional != other$n_functional || input$n_scalar != other$n_scalar) {
    stop("Mismatch in number of predictors.")
  }

  # Optionally check that functional bases are the same
  # if (!is_same_basis(input, other)) stop("Different functional bases.")

  new_functional_list <- vector("list", input$n_functional)
  for (i in seq_len(input$n_functional)) {
    new_functional_list[[i]] <- plus.fd(
      input$functional_list[[i]],
      times.fd(alpha, other$functional_list[[i]])
    )
  }

  new_Z <- input$Z + alpha * other$Z

  predictor_hybrid(
    Z = new_Z,
    functional_list = new_functional_list,
    jacobian_list = input$jacobian_list,  # Assumes identical structure
    n_basis_list = input$n_basis_list,
    n_sample = input$n_sample,
    n_functional = input$n_functional,
    n_scalar = input$n_scalar
  )
}

```

```{r}
testthat::test_that("add.predictor_hybrid works for matching predictors", {
  suppressPackageStartupMessages(library(fda))

  Z1 <- matrix(1, nrow = 3, ncol = 2)
  Z2 <- matrix(2, nrow = 3, ncol = 2)

  basis <- fda::create.bspline.basis(c(0, 1), 5)
  fd1 <- fda::fd(coef = matrix(1, 5, 3), basisobj = basis)
  fd2 <- fda::fd(coef = matrix(2, 5, 3), basisobj = basis)

  obj1 <- predictor_hybrid(Z1, list(fd1), list(matrix(0)), c(5), 3, 1, 2)
  obj2 <- predictor_hybrid(Z2, list(fd2), list(matrix(0)), c(5), 3, 1, 2)

  obj3 <- add.predictor_hybrid(obj1, obj2, alpha = 1)

  testthat::expect_s3_class(obj3, "predictor_hybrid")
  testthat::expect_equal(obj3$Z, matrix(3, nrow = 3, ncol = 2))

  expected_coef <- matrix(3, 5, 3)
  testthat::expect_equal(
    unname(coef(obj3$functional_list[[1]])),
    unname(expected_coef)
  )
})

```
### subtr.predictor_hybrid
Performs element-wise subtraction of two `predictor_hybrid` objects.   Internally uses `add.predictor_hybrid(input, other, alpha = -1)` to compute the result by negating the second operand.

- Usage

```r
subtr.predictor_hybrid(input, other, alpha = 1)
```

- Arguments:

  - `input`: A `predictor_hybrid` object.
  - `other`: Another `predictor_hybrid` object to be subtracted.
  - `alpha`: A scalar multiplier applied to `other` before subtraction (default is 1).

- Value:  
Returns a new `predictor_hybrid` object representing the result of the subtraction.

- Details:  
  - This function assumes both objects have the same number and structure of functional and scalar predictors.  
  - It performs subtraction by internally calling `add.predictor_hybrid()` with `-alpha`.  
  - Functional parts are scaled using `times.fd()` and subtracted via `plus.fd()` with a negated factor.  
  - Scalar predictors are subtracted using standard matrix arithmetic.

```{r}
#' Subtract two predictor_hybrid objects
#'
#' Performs element-wise subtraction of two `predictor_hybrid` objects.
#' Internally uses `add.predictor_hybrid(input, other, alpha = -1)`.
#'
#' @param input A `predictor_hybrid` object.
#' @param other Another `predictor_hybrid` object to subtract.
#' @param alpha A scalar multiplier applied to `other` before subtraction (default is 1).
#'
#' @return A new `predictor_hybrid` object representing the result of subtraction.
#' @export
subtr.predictor_hybrid <- function(input, other, alpha = 1) {
  add.predictor_hybrid(input, other, alpha = -alpha)
}

```
We skip the unit test for this function.

## Documenting the package and building

We finish by running commands that will document, build, and install the package.  It may also be a good idea to check the package from within this file.

```{r}
litr::document() # <-- use instead of devtools::document()
# devtools::build()
# devtools::install()
# devtools::check(document = FALSE)
```

### 2025-05-30 FSHybridPLS/R/add.predictor_hybrid.R

@@ -1,0 +1,42 @@
+# Generated from create-rhello.Rmd: do not edit by hand
+
+#' Add two predictor_hybrid objects
+#'
+#' Performs element-wise addition of two predictor_hybrid objects.
+#' Functional predictors are combined using `plus.fd()` and `times.fd()`.
+#'
+#' @param input A predictor_hybrid object.
+#' @param other Another predictor_hybrid object.
+#' @param alpha A numeric scalar multiplier for `other`.
+#'
+#' @return A new predictor_hybrid object representing the sum.
+#' @export
+add.predictor_hybrid <- function(input, other, alpha = 1) {
+  if (input$n_functional != other$n_functional || input$n_scalar != other$n_scalar) {
+    stop("Mismatch in number of predictors.")
+  }
+  
+  # Optionally check that functional bases are the same
+  # if (!is_same_basis(input, other)) stop("Different functional bases.")
+
+  new_functional_list <- vector("list", input$n_functional)
+  for (i in seq_len(input$n_functional)) {
+    new_functional_list[[i]] <- plus.fd(
+      input$functional_list[[i]],
+      times.fd(alpha, other$functional_list[[i]])
+    )
+  }
+  
+  new_Z <- input$Z + alpha * other$Z
+  
+  predictor_hybrid(
+    Z = new_Z,
+    functional_list = new_functional_list,
+    jacobian_list = input$jacobian_list,  # Assumes identical structure
+    n_basis_list = input$n_basis_list,
+    n_sample = input$n_sample,
+    n_functional = input$n_functional,
+    n_scalar = input$n_scalar
+  )
+}
+

### 2025-05-30 FSHybridPLS/R/predictor_hybrid.R

@@ -1,0 +1,37 @@
+# Generated from create-rhello.Rmd: do not edit by hand
+
+#' Create a predictor_hybrid object (S3 version)
+#'
+#' Constructs a hybrid predictor object that stores both scalar and functional predictors,
+#' along with Jacobians and metadata.
+#'
+#' @param Z A numeric matrix of dimension \code{n_sample × n_scalar} representing scalar predictors.
+#' @param functional_list A list of functional predictors (e.g., \code{fd} objects from the \code{fda} package).
+#' @param jacobian_list A list of Jacobian matrices corresponding to the functional predictors.
+#' @param n_basis_list A numeric vector indicating the number of basis functions for each functional predictor.
+#' @param n_sample Number of observations (samples).
+#' @param n_functional Number of functional predictors.
+#' @param n_scalar Number of scalar predictors.
+#'
+#' @return A list of class \code{predictor_hybrid}.
+#' @export
+predictor_hybrid <- function(Z, functional_list, jacobian_list,
+                             n_basis_list, n_sample, n_functional, n_scalar) {
+  stopifnot(is.matrix(Z))
+  stopifnot(length(functional_list) == n_functional)
+  stopifnot(length(jacobian_list) == n_functional)
+  stopifnot(length(n_basis_list) == n_functional)
+  
+  structure(
+    list(
+      Z = Z,
+      functional_list = functional_list,
+      jacobian_list = jacobian_list,
+      n_basis_list = n_basis_list,
+      n_sample = n_sample,
+      n_functional = n_functional,
+      n_scalar = n_scalar
+    ),
+    class = "predictor_hybrid"
+  )
+}

### 2025-05-30 FSHybridPLS/R/subtr.predictor_hybrid.R

@@ -1,0 +1,17 @@
+# Generated from create-rhello.Rmd: do not edit by hand
+
+#' Subtract two predictor_hybrid objects
+#'
+#' Performs element-wise subtraction of two `predictor_hybrid` objects.
+#' Internally uses `add.predictor_hybrid(input, other, alpha = -1)`.
+#'
+#' @param input A `predictor_hybrid` object.
+#' @param other Another `predictor_hybrid` object to subtract.
+#' @param alpha A scalar multiplier applied to `other` before subtraction (default is 1).
+#'
+#' @return A new `predictor_hybrid` object representing the result of subtraction.
+#' @export
+subtr.predictor_hybrid <- function(input, other, alpha = 1) {
+  add.predictor_hybrid(input, other, alpha = -alpha)
+}
+

### 2025-05-30 FSHybridPLS/tests/testthat.R

@@ -1,0 +1,12 @@
+# This file is part of the standard setup for testthat.
+# It is recommended that you do not modify it.
+#
+# Where should you do additional test configuration?
+# Learn more about the roles of various files in:
+# * https://r-pkgs.org/testing-design.html#sec-tests-files-overview
+# * https://testthat.r-lib.org/articles/special-files.html
+
+library(testthat)
+library(FSHybridPLS)
+
+test_check("FSHybridPLS")

### 2025-05-30 FSHybridPLS/tests/testthat/tests.R

@@ -1,0 +1,58 @@
+# Generated from create-rhello.Rmd: do not edit by hand  
+testthat::test_that("predictor_hybrid constructor works as expected (S3)", {
+  Z <- matrix(rnorm(100 * 5), nrow = 100, ncol = 5)
+  fd1 <- list(fdobj = "fd1 placeholder")
+  fd2 <- list(fdobj = "fd2 placeholder")
+  J1 <- matrix(runif(100), nrow = 10)
+  J2 <- matrix(runif(200), nrow = 20)
+  
+  obj <- predictor_hybrid(
+    Z = Z,
+    functional_list = list(fd1, fd2),
+    jacobian_list = list(J1, J2),
+    n_basis_list = c(10, 20),
+    n_sample = 100,
+    n_functional = 2,
+    n_scalar = 5
+  )
+  
+  testthat::expect_s3_class(obj, "predictor_hybrid")
+  testthat::expect_equal(nrow(obj$Z), 100)
+  testthat::expect_equal(ncol(obj$Z), 5)
+  testthat::expect_equal(length(obj$functional_list), 2)
+  testthat::expect_equal(length(obj$jacobian_list), 2)
+  testthat::expect_equal(obj$n_basis_list, c(10, 20))
+  testthat::expect_equal(obj$n_sample, 100)
+  testthat::expect_equal(obj$n_functional, 2)
+  testthat::expect_equal(obj$n_scalar, 5)
+})
+
+
+
+testthat::test_that("add.predictor_hybrid works for matching predictors", {
+  suppressPackageStartupMessages(library(fda))
+
+  Z1 <- matrix(1, nrow = 3, ncol = 2)
+  Z2 <- matrix(2, nrow = 3, ncol = 2)
+  
+  basis <- fda::create.bspline.basis(c(0, 1), 5)
+  fd1 <- fda::fd(coef = matrix(1, 5, 3), basisobj = basis)
+  fd2 <- fda::fd(coef = matrix(2, 5, 3), basisobj = basis)
+  
+  obj1 <- predictor_hybrid(Z1, list(fd1), list(matrix(0)), c(5), 3, 1, 2)
+  obj2 <- predictor_hybrid(Z2, list(fd2), list(matrix(0)), c(5), 3, 1, 2)
+  
+  obj3 <- add.predictor_hybrid(obj1, obj2, alpha = 1)
+  
+  testthat::expect_s3_class(obj3, "predictor_hybrid")
[…]

### 2025-05-30 create-rhello.Rmd
scalar multiple

@@
 
+### scalar_mul.predictor_hybrid
+Multiplies all components of a `predictor_hybrid` object by a scalar.
+Functional components are scaled using `times.fd()` from the `fda` package, and scalar predictors are multiplied directly using matrix operations.
+
+- Usage
+
+```r
+scalar_mul.predictor_hybrid(input, scalar)
+```
+
+- Arguments:
+
+  - `input`: A `predictor_hybrid` object.
+  - `scalar`: A numeric value used to scale both scalar and functional components.
+
+- Value:  
+Returns a new `predictor_hybrid` object with all components scaled by `scalar`.
+
+- Details:  
+  - Functional predictors are scaled using `times.fd(scalar, fd_obj)` for each element.  
+  - Scalar predictors (the matrix `Z`) are scaled elementwise using matrix multiplication.
+
+```{r}
+#' Multiply a predictor_hybrid object by a scalar
+#'
+#' Performs scalar multiplication of both scalar and functional components 
+#' of a `predictor_hybrid` object. Functional predictors are scaled using 
+#' `times.fd()` from the `fda` package.
+#'
+#' @param input A `predictor_hybrid` object.
+#' @param scalar A numeric value to multiply all components by.
+#'
+#' @return A new `predictor_hybrid` object scaled by `scalar`.
+#' @export
+scalar_mul.predictor_hybrid <- function(input, scalar) {
+  new_functional_list <- lapply(
+    input$functional_list,
+    function(fd_obj) times.fd(scalar, fd_obj)
+  )
+
+  new_Z <- scalar * input$Z
+
+  predictor_hybrid(
+    Z = new_Z,
+    functional_list = new_functional_list,
+    jacobian_list = input$jacobian_list,
+    n_basis_list = input$n_basis_list,
+    n_sample = input$n_sample,
+    n_functional = input$n_functional,
+    n_scalar = input$n_scalar
+  )
+}
+```
+
+Here is a test code with two functional predictors:
+```{r}
+testthat::test_that("scalar_mul.predictor_hybrid works with two functional predictors", {
+  suppressPackageStartupMessages(library(fda))
+
+  # Scalar matrix
+  Z <- matrix(2, nrow = 3, ncol = 2)
+
+  # Create a shared basis for both functional predictors
+  basis <- create.bspline.basis(c(0, 1), 5)
+
+  # Two identical fd objects
+  fd1 <- fd(coef = matrix(2, 5, 3), basisobj = basis)
+  fd2 <- fd(coef = matrix(2, 5, 3), basisobj = basis)
+
+  # Construct predictor_hybrid object
+  obj <- predictor_hybrid(
+    Z = Z,
+    functional_list = list(fd1, fd2),
+    jacobian_list = list(matrix(0), matrix(0)),
+    n_basis_list = c(5, 5),
+    n_sample = 3,
+    n_functional = 2,
+    n_scalar = 2
+  )
+
+  # Perform scalar multiplication
+  scaled <- scalar_mul.predictor_hybrid(obj, 4)
+
+  testthat::expect_s3_class(scaled, "predictor_hybrid")
+
+  # Scalar part should be scaled
+  testthat::expect_equal(scaled$Z, Z * 4)
+
+  # Each functional part should be scaled
+  expected_coef <- matrix(8, 5, 3)  # 2 * 4
+  for (fd_scaled in scaled$functional_list) {
+    testthat::expect_equal(
+      unname(coef(fd_scaled)),
+      unname(expected_coef)
+    )
+  }
+})
+```
+
 ## Documenting the package and building

### 2025-05-30 FSHybridPLS/R/scalar_mul.predictor_hybrid.R

@@ -1,0 +1,31 @@
+# Generated from create-rhello.Rmd: do not edit by hand
+
+#' Multiply a predictor_hybrid object by a scalar
+#'
+#' Performs scalar multiplication of both scalar and functional components 
+#' of a `predictor_hybrid` object. Functional predictors are scaled using 
+#' `times.fd()` from the `fda` package.
+#'
+#' @param input A `predictor_hybrid` object.
+#' @param scalar A numeric value to multiply all components by.
+#'
+#' @return A new `predictor_hybrid` object scaled by `scalar`.
+#' @export
+scalar_mul.predictor_hybrid <- function(input, scalar) {
+  new_functional_list <- lapply(
+    input$functional_list,
+    function(fd_obj) times.fd(scalar, fd_obj)
+  )
+  
+  new_Z <- scalar * input$Z
+  
+  predictor_hybrid(
+    Z = new_Z,
+    functional_list = new_functional_list,
+    jacobian_list = input$jacobian_list,
+    n_basis_list = input$n_basis_list,
+    n_sample = input$n_sample,
+    n_functional = input$n_functional,
+    n_scalar = input$n_scalar
+  )
+}

### 2025-05-30 FSHybridPLS/tests/testthat/tests.R

@@ -56,3 +56,45 @@ testthat::test_that("add.predictor_hybrid works for matching predictors", {
 
 
 
+testthat::test_that("scalar_mul.predictor_hybrid works with two functional predictors", {
+  suppressPackageStartupMessages(library(fda))
+  
+  # Scalar matrix
+  Z <- matrix(2, nrow = 3, ncol = 2)
+  
+  # Create a shared basis for both functional predictors
+  basis <- create.bspline.basis(c(0, 1), 5)
+  
+  # Two identical fd objects
+  fd1 <- fd(coef = matrix(2, 5, 3), basisobj = basis)
+  fd2 <- fd(coef = matrix(2, 5, 3), basisobj = basis)
+  
+  # Construct predictor_hybrid object
+  obj <- predictor_hybrid(
+    Z = Z,
+    functional_list = list(fd1, fd2),
+    jacobian_list = list(matrix(0), matrix(0)),
+    n_basis_list = c(5, 5),
+    n_sample = 3,
+    n_functional = 2,
+    n_scalar = 2
+  )
+  
+  # Perform scalar multiplication
+  scaled <- scalar_mul.predictor_hybrid(obj, 4)
+  
+  testthat::expect_s3_class(scaled, "predictor_hybrid")
+  
+  # Scalar part should be scaled
+  testthat::expect_equal(scaled$Z, Z * 4)
+  
+  # Each functional part should be scaled
+  expected_coef <- matrix(8, 5, 3)  # 2 * 4
+  for (fd_scaled in scaled$functional_list) {
+    testthat::expect_equal(
+      unname(coef(fd_scaled)),
+      unname(expected_coef)
+    )
+  }
+})
+

### 2025-05-30 create-rhello.Rmd
got to know that class constructer is redundant

@@
 # Class predictor_hybrid
-The `predictor_hybrid` class is an S3 object for representing hybrid predictors: a combination of scalar and functional covariates. The following code defines the class.
+- Let $\{X^{(k)}\}_{k=1, \ldots, K}$ be a collection of random functions defined on unit hypercube domains $\mathcal{T}_k := [0,1]^{d_k}$ ($d_k \in \mathbb{N})$; i.e., $X^{(k)}: \mathcal{T}_k \rightarrow \mathbb{R}$.
+
+- Assume that each $X^{(k)}$ is in $L^2(\mathcal{T}_k)$, a Hilbert space of square integrable functions with respect to Lebesgue measure $dt_k$ on $\mathcal{T}_k$.
+
+- Write  $X=(X^{(1)}, \ldots, X^{(K)})$ as a multivariate functional object that belongs to $\mathcal{F} = L^2(\mathcal{T}_1) \times \cdots \times L^2(\mathcal{T}_K)$---a cartesian product of individual $L^2(\mathcal{T}_k)$ spaces.
+
+- We can also express the functional object $X$ evaluated on the multi-dimensional argument $\mathbf{t} = (t_1, \ldots, t_k)^\top \in \mathcal{T} = \mathcal{T}_1 \times \cdots \times \mathcal{T}_K$ as a $K$-dimensional vector $X(\mathbf{t})=(X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top$.
+
+- **Our strategy is to formulate a hybrid random object**, $\mathbf{W} = (X, \mathbf{Z})$, which combines $X$ and $p$-dimensional scalar covariate $\mathbf{Z}$ into an ordered pair belonging to $\mathcal{H} = \mathcal{F} \times \mathbb{R}^p$.
+
+- An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}[\mathbf{t}] = (X(\mathbf{t}), \mathbf{Z})^\top$, with $X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $\mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.
+
+- The hybrid object forms a Hilbert space, characterized by well-defined addition, scalar multiplication, and inner product operations.
+
+- The `predictor_hybrid` class is an S3 object designed to represent this structure.
+
+- We implement Hilbert space operations for this class, and our algorithm is built on these foundational operations.
+
+The class definition is a simple list that contains a matrix and a collection of \code{fd} objects from the \code{fda} package, along with the necessary metadata.
 
@@
 ```
+### inprod.predictor_hybrid
+The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)}) $ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as $\langle f_1, f_2\rangle_\mathcal{F} =  \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)}\rangle_{L^2} = \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k$ with norm $\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k)^2 dt_k\}^{1/2}$.
+
+Computes the inner product between two `predictor_hybrid` objects.Both scalar and functional components are included.
+
+  We define the inner product between any two hybrid objects, $\mathbf{h}_1 = (f_1, \mathbf{v}_1)$ and $\mathbf{h}_2 = (f_2, \mathbf{v}_2)$, as
+$$
+    \langle \mathbf{h}_1, \mathbf{h}_2\rangle_{\mathcal{H}} = \langle f_1, f_2\rangle_\mathcal{F} + w \langle  \mathbf{v_1}, \mathbf{v_2} \rangle = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k + \omega \sum \limits_{r=1}^p v_{1r}v_{2r},
+$$
+with norm $\Vert \cdot \Vert_\mathcal{H} = \langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
+$\omega$ is a positive weight that needs to be pre-specified or estimated.
+It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}).
+Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$.
+The results remain valid for any positive weights.
+- Usage
+
+```r
+inprod.predictor_hybrid(xi_1, xi_2)
+```
+
+- Arguments:
+
+  - `xi_1`: A `predictor_hybrid` object.
+  - `xi_2`: Another `predictor_hybrid` object.
+
+- Value:  
+A numeric matrix of inner products (or a scalar if both inputs are single observations).
+
+- Details:  
+  - Functional components are summed using `inprod()` from the `fda` package.  
+  - Scalar components are handled via matrix multiplication.  
+  - Returns a scalar if both `xi_1` and `xi_2` are single-sample predictors.
+```{r}
+#' Inner product between two predictor_hybrid objects (with broadcasting)
+#'
+#' Computes the inner product between two `predictor_hybrid` objects,
+#' including both functional and scalar components. Supports broadcasting
+#' when one of the inputs has a single observation. If only one input is given,
+#' the inner product is computed with itself.
+#'
+#' @param xi_1 A `predictor_hybrid` object.
+#' @param xi_2 Another `predictor_hybrid` object. If missing, defaults to `xi_1`.
+#'
+#' @return A numeric matrix of inner products (or a scalar if both inputs have one row).
+#' @export
+inprod.predictor_hybrid <- function(xi_1, xi_2 = NULL) {
+  if (is.null(xi_2)) xi_2 <- xi_1
+
+  # Optional: Check for basis compatibility
+  # if (!is_same_basis(xi_1, xi_2)) stop("Functional predictors must share the same basis.")
+
+  n1 <- xi_1$n_sample
+  n2 <- xi_2$n_sample
+
+  # Compute sum of pairwise functional inner products
+  inprod_functional <- Reduce(`+`,
+    Map(function(f1, f2) fda::inprod(f1, f2),
+        xi_1$functional_list, xi_2$functional_list)
+  )
+
+  # Broadcast-aware scalar component
+  Z1 <- if (n1 == 1) matrix(xi_1$Z, nrow = 1) else xi_1$Z
+  Z2 <- if (n2 == 1) matrix(xi_2$Z, nrow = 1) else xi_2$Z
+  inprod_scalar <- Z1 %*% t(Z2)
+
+  result <- inprod_functional + inprod_scalar
+
+  if (n1 == 1 && n2 == 1) as.numeric(result) else result
+}
+
+```
+
+```{r}
+testthat::test_that("inprod.predictor_hybrid works with broadcasting and self-inner product", {
+  suppressPackageStartupMessages(library(fda))
+
+  basis <- create.bspline.basis(c(0, 1), 5)
+  coef_val <- function(val) matrix(val, 5, 3)
+
+  # Define functional objects
+  fd_1 <- fd(coef = coef_val(1), basisobj = basis)
+  fd_2 <- fd(coef = coef_val(2), basisobj = basis)
+
+  # Define scalar matrices
+  Z1 <- matrix(c(1, 2), nrow = 1)         # 1 × 2
+  Z2 <- matrix(c(3, 4), nrow = 1)         # 1 × 2
+  Z_many <- matrix(rep(c(1, 2), 3), nrow = 3, byrow = TRUE)  # 3 × 2
+
+  # (1, 1)
+  x1 <- predictor_hybrid(Z1, list(fd_1, fd_1), list(matrix(0), matrix(0)), c(5, 5), 1, 2, 2)
+  x2 <- predictor_hybrid(Z2, list(fd_2, fd_2), list(matrix(0), matrix(0)), c(5, 5), 1, 2, 2)
+  val_scalar <- inprod.predictor_hybrid(x1, x2)
+
+  testthat::expect_type(val_scalar, "double")
+  testthat::expect_length(val_scalar, 1)
+
+  # Expected functional inner product: 2 fds × sum(1 * 2) = 2 × (5×3) = 30
+  expected_functional <- 2 * sum(1 * 2) * 15  # 5 × 3 = 15 elements
+  expected_scalar <- sum(Z1 * Z2)            # 1*3 + 2*4 = 11
+  testthat::expect_equal(val_scalar, expected_functional + expected_scalar)
+
+  # (n, 1) broadcasting
+  x3 <- predictor_hybrid(Z_many, list(fd_1, fd_1), list(matrix(0), matrix(0)), c(5, 5), 3, 2, 2)
+  mat_3_1 <- inprod.predictor_hybrid(x3, x2)
+  testthat::expect_equal(dim(mat_3_1), c(3, 1))
+  testthat::expect_equal(as.numeric(mat_3_1), rep(val_scalar, 3))
+
+  # (1, m) broadcasting
+  x4 <- predictor_hybrid(Z_many, list(fd_2, fd_2), list(matrix(0), matrix(0)), c(5, 5), 3, 2, 2)
+  mat_1_3 <- inprod.predictor_hybrid(x1, x4)
+  testthat::expect_equal(dim(mat_1_3), c(1, 3))
+  testthat::expect_equal(as.numeric(mat_1_3), rep(val_scalar, 3))
+
+  # (n, m)
+  mat_3_3 <- inprod.predictor_hybrid(x3, x4)
+  testthat::expect_equal(dim(mat_3_3), c(3, 3))
+  testthat::expect_true(all(as.numeric(mat_3_3) == val_scalar))
+
+  # shorthand inprod(x) ≡ inprod(x, x)
+  self_inner <- inprod.predictor_hybrid(x1)
+  testthat::expect_equal(
+    self_inner,
+    inprod.predictor_hybrid(x1, x1)
+  )
+})
+
+```
+
+# helper functions
+
+### is_same_basis
+```{r}
+#' @export
+is_same_basis <- function(input, other) {
+  all(
+    length(input$functional_list) == length(other$functional_list),
+    all(
+      mapply(function(fd1, fd2) fda::is.eqbasis(fd1$basis, fd2$basis),
+             input$functional_list, other$functional_list)
+    )
+  )
+}
+```
 

### 2025-05-30 FSHybridPLS/R/inprod.predictor_hybrid.R

@@ -1,0 +1,39 @@
+# Generated from create-rhello.Rmd: do not edit by hand
+
+#' Inner product between two predictor_hybrid objects (with broadcasting)
+#'
+#' Computes the inner product between two `predictor_hybrid` objects,
+#' including both functional and scalar components. Supports broadcasting
+#' when one of the inputs has a single observation. If only one input is given,
+#' the inner product is computed with itself.
+#'
+#' @param xi_1 A `predictor_hybrid` object.
+#' @param xi_2 Another `predictor_hybrid` object. If missing, defaults to `xi_1`.
+#'
+#' @return A numeric matrix of inner products (or a scalar if both inputs have one row).
+#' @export
+inprod.predictor_hybrid <- function(xi_1, xi_2 = NULL) {
+  if (is.null(xi_2)) xi_2 <- xi_1
+  
+  # Optional: Check for basis compatibility
+  # if (!is_same_basis(xi_1, xi_2)) stop("Functional predictors must share the same basis.")
+
+  n1 <- xi_1$n_sample
+  n2 <- xi_2$n_sample
+
+  # Compute sum of pairwise functional inner products
+  inprod_functional <- Reduce(`+`,
+    Map(function(f1, f2) fda::inprod(f1, f2),
+        xi_1$functional_list, xi_2$functional_list)
+  )
+
+  # Broadcast-aware scalar component
+  Z1 <- if (n1 == 1) matrix(xi_1$Z, nrow = 1) else xi_1$Z
+  Z2 <- if (n2 == 1) matrix(xi_2$Z, nrow = 1) else xi_2$Z
+  inprod_scalar <- Z1 %*% t(Z2)
+
+  result <- inprod_functional + inprod_scalar
+
+  if (n1 == 1 && n2 == 1) as.numeric(result) else result
+}
+

### 2025-05-30 FSHybridPLS/tests/testthat/tests.R

@@ -98,3 +98,57 @@ testthat::test_that("scalar_mul.predictor_hybrid works with two functional predi
   }
 })
 
+testthat::test_that("inprod.predictor_hybrid works with broadcasting and self-inner product", {
+  suppressPackageStartupMessages(library(fda))
+  
+  basis <- create.bspline.basis(c(0, 1), 5)
+  coef_val <- function(val) matrix(val, 5, 3)
+
+  # Define functional objects
+  fd_1 <- fd(coef = coef_val(1), basisobj = basis)
+  fd_2 <- fd(coef = coef_val(2), basisobj = basis)
+
+  # Define scalar matrices
+  Z1 <- matrix(c(1, 2), nrow = 1)         # 1 × 2
+  Z2 <- matrix(c(3, 4), nrow = 1)         # 1 × 2
+  Z_many <- matrix(rep(c(1, 2), 3), nrow = 3, byrow = TRUE)  # 3 × 2
+
+  # (1, 1)
+  x1 <- predictor_hybrid(Z1, list(fd_1, fd_1), list(matrix(0), matrix(0)), c(5, 5), 1, 2, 2)
+  x2 <- predictor_hybrid(Z2, list(fd_2, fd_2), list(matrix(0), matrix(0)), c(5, 5), 1, 2, 2)
+  val_scalar <- inprod.predictor_hybrid(x1, x2)
+
+  testthat::expect_type(val_scalar, "double")
+  testthat::expect_length(val_scalar, 1)
+
+  # Expected functional inner product: 2 fds × sum(1 * 2) = 2 × (5×3) = 30
+  expected_functional <- 2 * sum(1 * 2) * 15  # 5 × 3 = 15 elements
+  expected_scalar <- sum(Z1 * Z2)            # 1*3 + 2*4 = 11
+  testthat::expect_equal(val_scalar, expected_functional + expected_scalar)
+
+  # (n, 1) broadcasting
+  x3 <- predictor_hybrid(Z_many, list(fd_1, fd_1), list(matrix(0), matrix(0)), c(5, 5), 3, 2, 2)
+  mat_3_1 <- inprod.predictor_hybrid(x3, x2)
+  testthat::expect_equal(dim(mat_3_1), c(3, 1))
+  testthat::expect_equal(as.numeric(mat_3_1), rep(val_scalar, 3))
+
+  # (1, m) broadcasting
[…]

### 2025-05-30 create-rhello.Rmd
re-defined the class and operations, right before inprod

@@
 ```{r}
-#' Create a predictor_hybrid object (S3 version)
+#' Create a predictor_hybrid object (S3 version, automatic basis size and Gram matrix)
 #'
 #' Constructs a hybrid predictor object that stores both scalar and functional predictors,
-#' along with Jacobians and metadata.
+#' and automatically computes Gram matrices (inner products of basis functions).
 #'
@@
 #' @param functional_list A list of functional predictors (e.g., \code{fd} objects from the \code{fda} package).
-#' @param jacobian_list A list of Jacobian matrices corresponding to the functional predictors.
-#' @param n_basis_list A numeric vector indicating the number of basis functions for each functional predictor.
-#' @param n_sample Number of observations (samples).
-#' @param n_functional Number of functional predictors.
-#' @param n_scalar Number of scalar predictors.
 #'
-#' @return A list of class \code{predictor_hybrid}.
+#' @return An object of class \code{predictor_hybrid}, containing scalar and functional data with Gram matrices.
 #' @export
-predictor_hybrid <- function(Z, functional_list, jacobian_list,
-                             n_basis_list, n_sample, n_functional, n_scalar) {
-  stopifnot(is.matrix(Z))
-  stopifnot(length(functional_list) == n_functional)
-  stopifnot(length(jacobian_list) == n_functional)
-  stopifnot(length(n_basis_list) == n_functional)
+predictor_hybrid <- function(Z, functional_list) {
+  stopifnot(is.matrix(Z), is.numeric(Z))
+  stopifnot(is.list(functional_list))
+
+  n_sample <- nrow(Z)
+  n_scalar <- ncol(Z)
+  n_functional <- length(functional_list)
+
+  gram_list <- vector("list", n_functional)
+  n_basis_list <- numeric(n_functional)
+
+  for (i in seq_len(n_functional)) {
+    fd_i <- functional_list[[i]]
+    stopifnot(inherits(fd_i, "fd"))
+
+    n_fd_sample <- ncol(coef(fd_i))
+    if (n_fd_sample != n_sample) {
+      stop(sprintf("Functional predictor %d has %d replicates, but Z has %d rows.",
+                   i, n_fd_sample, n_sample))
+    }
+
+    basis_i <- fd_i$basis
+    gram_list[[i]] <- compute_gram_matrix(basis_i)
+    n_basis_list[i] <- basis_i$nbasis
+  }
 
@@
       functional_list = functional_list,
-      jacobian_list = jacobian_list,
+      gram_list = gram_list,
       n_basis_list = n_basis_list,
@@
 }
+
 ```
@@
 ```{r}
-testthat::test_that("predictor_hybrid constructor works as expected (S3)", {
+testthat::test_that("predictor_hybrid constructor works as expected (S3, updated)", {
+  library(fda)
+
+  # Create scalar matrix
   Z <- matrix(rnorm(100 * 5), nrow = 100, ncol = 5)
-  fd1 <- list(fdobj = "fd1 placeholder")
-  fd2 <- list(fdobj = "fd2 placeholder")
-  J1 <- matrix(runif(100), nrow = 10)
-  J2 <- matrix(runif(200), nrow = 20)
 
-  obj <- predictor_hybrid(
-    Z = Z,
-    functional_list = list(fd1, fd2),
-    jacobian_list = list(J1, J2),
-    n_basis_list = c(10, 20),
-    n_sample = 100,
-    n_functional = 2,
-    n_scalar = 5
-  )
+  # Create two fd objects with 100 replications
+  basis1 <- create.bspline.basis(c(0, 1), nbasis = 10)
+  basis2 <- create.bspline.basis(c(0, 1), nbasis = 20)
 
+  coef1 <- matrix(rnorm(10 * 100), nrow = 10)  # 10 basis × 100 samples
+  coef2 <- matrix(rnorm(20 * 100), nrow = 20)  # 20 basis × 100 samples
+
+  fd1 <- fd(coef = coef1, basisobj = basis1)
+  fd2 <- fd(coef = coef2, basisobj = basis2)
+
+  # Construct object
+  obj <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
+
+  # Assertions
   testthat::expect_s3_class(obj, "predictor_hybrid")
@@
   testthat::expect_equal(length(obj$functional_list), 2)
-  testthat::expect_equal(length(obj$jacobian_list), 2)
   testthat::expect_equal(obj$n_basis_list, c(10, 20))
@@
   testthat::expect_equal(obj$n_scalar, 5)
+  testthat::expect_equal(dim(obj$gram_list[[1]]), c(10, 10))
+  testthat::expect_equal(dim(obj$gram_list[[2]]), c(20, 20))
 })
-
 ```
@@
 ```{r}
-#' Add two predictor_hybrid objects
-#'
-#' Performs element-wise addition of two predictor_hybrid objects.
-#' Functional predictors are combined using `plus.fd()` and `times.fd()`.
-#'
-#' @param input A predictor_hybrid object.
-#' @param other Another predictor_hybrid object.
-#' @param alpha A numeric scalar multiplier for `other`.
-#'
-#' @return A new predictor_hybrid object representing the sum.
-#' @export
 add.predictor_hybrid <- function(input, other, alpha = 1) {
-  if (input$n_functional != other$n_functional || input$n_scalar != other$n_scalar) {
-    stop("Mismatch in number of predictors.")
+  if (!inherits(input, "predictor_hybrid") || !inherits(other, "predictor_hybrid")) {
+    stop("Both arguments must be of class 'predictor_hybrid'.")
   }
 
-  # Optionally check that functional bases are the same
-  # if (!is_same_basis(input, other)) stop("Different functional bases.")
+  if (input$n_functional != other$n_functional || input$n_scalar != other$n_scalar) {
+    stop("Mismatch in number of functional or scalar predictors.")
+  }
 
-  new_functional_list <- vector("list", input$n_functional)
+  # Check broadcasting compatibility
+  n1 <- input$n_sample
+  n2 <- other$n_sample
+  if (n1 != n2 && !(n1 == 1 || n2 == 1)) {
+    stop("Sample sizes are incompatible for broadcasting.")
+  }
+
+  # Safe access to is.eqbasis()
+  is_eqbasis <- getFromNamespace("is.eqbasis", "fda")
+
   for (i in seq_len(input$n_functional)) {
-    new_functional_list[[i]] <- plus.fd(
-      input$functional_list[[i]],
-      times.fd(alpha, other$functional_list[[i]])
+    if (!is_eqbasis(input$functional_list[[i]]$basis, other$functional_list[[i]]$basis)) {
+      stop("Functional predictors must have the same basis.")
+    }
+  }
+
+  # Broadcast if needed
+  broadcast <- function(obj, n_target) {
+    if (obj$n_sample == n_target) return(obj)
+    obj$Z <- matrix(rep(obj$Z, each = n_target), nrow = n_target, byrow = TRUE)
+    obj$functional_list <- lapply(obj$functional_list, function(fd_obj) {
+      fd(coef = matrix(rep(coef(fd_obj), n_target), nrow = nrow(coef(fd_obj))),
+         basisobj = fd_obj$basis)
+    })
+    obj$n_sample <- n_target
+    obj
+  }
+
+  # Determine output sample size
+  n_out <- max(n1, n2)
+  input <- broadcast(input, n_out)
+  other <- broadcast(other, n_out)
+
+  # Combine functional predictors
+  new_functional_list <- Map(
+    function(f1, f2) plus.fd(f1, times.fd(alpha, f2)),
+    input$functional_list,
+    other$functional_list
+  )
+
+  # Combine scalar predictors
+  new_Z <- input$Z + alpha * other$Z
+
+  # Construct new object
+  predictor_hybrid(Z = new_Z, functional_list = new_functional_list)
+}
+```
+
+Here are the unit tests:
+| Case                    | Description                         | Expected Outcome |
+| ----------------------- | ----------------------------------- | ---------------- |
+| ✅ Same sample size      | Functional and scalar values summed | Pass             |
+| ✅ Broadcast one → many  | One-sample input broadcasted        | Pass             |
+| ✅ Broadcast many ← one  | One-sample other broadcasted        | Pass             |
+| ❌ Basis mismatch        | Different functional basis          | Error            |
+| ❌ Irregular sample size | Neither matches nor is singleton    | Error            |
+| ❌ Different dimensions  | Functional or scalar count mismatch | Error            |
+```{r}
+testthat::test_that("add.predictor_hybrid handles broadcasting and basis compatibility", {
+  suppressPackageStartupMessages(library(fda))
+
+  # Create shared B-spline basis
+  basis <- create.bspline.basis(c(0, 1), nbasis = 5)
+
+  # Helper to generate a valid coefficient matrix
+  coef_mat <- function(val, n_sample, basis_obj) {
+    nbasis <- basis_obj$nbasis
+    matrix(val, nrow = nbasis, ncol = n_sample)
+  }
+
+  # Helper to create a list of fd objects (2 functional predictors)
+  fd_list <- function(val, n_sample, basis_obj = basis) {
+    list(
+      fd(coef = coef_mat(val, n_sample, basis_obj), basisobj = basis_obj),
+      fd(coef = coef_mat(val, n_sample, basis_obj), basisobj = basis_obj)
     )
@@
 
-  new_Z <- input$Z + alpha * other$Z
+  # Scalar predictors
+  Z1 <- matrix(1, nrow = 1, ncol = 2)
+  Z3 <- matrix(3, nrow = 3, ncol = 2)
 
-  predictor_hybrid(
-    Z = new_Z,
-    functional_list = new_functional_list,
-    jacobian_list = input$jacobian_list,  # Assumes identical structure
-    n_basis_list = input$n_basis_list,
-    n_sample = input$n_sample,
-    n_functional = input$n_functional,
-    n_scalar = input$n_scalar
-  )
+  # Functional predictors (same basis)
+  F1 <- fd_list(1, 1)
+  F3 <- fd_list(3, 3)
+
+  # Create predictor_hybrid objects
+  x1 <- predictor_hybrid(Z1, F1)  # 1 sample
+  x3 <- predictor_hybrid(Z3, F3)  # 3 samples
+
+  # Broadcast x1 to match x3
+  result <- add.predictor_hybrid(x1, x3, alpha = 1)
+
+  # Check metadata
+  testthat::expect_s3_class(result, "predictor_hybrid")
+  testthat::expect_equal(result$n_sample, 3)
+  testthat::expect_equal(result$n_scalar, 2)
+  testthat::expect_equal(result$n_functional, 2)
+
+  # Check scalar component
+  expected_Z <- matrix(4, nrow = 3, ncol = 2)  # 1 + 3 = 4
+  testthat::expect_equal(result$Z, expected_Z)
+
+  # Check functional component
+  for (fd_out in result$functional_list) {
+    testthat::expect_equal(unname(coef(fd_out)), matrix(4, nrow = 5, ncol = 3))
   }
 
-```
+  # Test symmetry: broadcasting x3 + x1
+  result2 <- add.predictor_hybrid(x3, x1, alpha = 1)
+  testthat::expect_equal(result2$Z, expected_Z)
+  for (fd_out in result2$functional_list) {
+    testthat::expect_equal(unname(coef(fd_out)), matrix(4, nrow = 5, ncol = 3))
+  }
 
-```{r}
-testthat::test_that("add.predictor_hybrid works for matching predictors", {
-  suppressPackageStartupMessages(library(fda))
+  # Incompatible sample sizes (should fail)
+  x_bad <- predictor_hybrid(matrix(1, 2, 2), fd_list(1, 2))
+  testthat::expect_error(add.predictor_hybrid(x3, x_bad), "incompatible for broadcasting")
 
-  Z1 <- matrix(1, nrow = 3, ncol = 2)
-  Z2 <- matrix(2, nrow = 3, ncol = 2)
-
-  basis <- fda::create.bspline.basis(c(0, 1), 5)
-  fd1 <- fda::fd(coef = matrix(1, 5, 3), basisobj = basis)
-  fd2 <- fda::fd(coef = matrix(2, 5, 3), basisobj = basis)
-
-  obj1 <- predictor_hybrid(Z1, list(fd1), list(matrix(0)), c(5), 3, 1, 2)
-  obj2 <- predictor_hybrid(Z2, list(fd2), list(matrix(0)), c(5), 3, 1, 2)
-
-  obj3 <- add.predictor_hybrid(obj1, obj2, alpha = 1)
-
-  testthat::expect_s3_class(obj3, "predictor_hybrid")
-  testthat::expect_equal(obj3$Z, matrix(3, nrow = 3, ncol = 2))
-
-  expected_coef <- matrix(3, 5, 3)
-  testthat::expect_equal(
-    unname(coef(obj3$functional_list[[1]])),
-    unname(expected_coef)
-  )
+  # Incompatible functional basis (should fail)
+  bad_basis <- create.bspline.basis(c(0, 1), nbasis = 6)
+  bad_fd <- fd_list(2, 3, bad_basis)
+  x_basis_mismatch <- predictor_hybrid(Z3, bad_fd)
+  testthat::expect_error(add.predictor_hybrid(x3, x_basis_mismatch), "same basis")
 })
@@
 #'
-#' Performs scalar multiplication of both scalar and functional components 
+#' Performs scalar multiplication on both the scalar and functional components
 #' of a `predictor_hybrid` object. Functional predictors are scaled using 
@@
 scalar_mul.predictor_hybrid <- function(input, scalar) {
-  new_functional_list <- lapply(
-    input$functional_list,
-    function(fd_obj) times.fd(scalar, fd_obj)
-  )
+  if (!inherits(input, "predictor_hybrid")) {
+    stop("Input must be of class 'predictor_hybrid'.")
+  }
+  if (!is.numeric(scalar) || length(scalar) != 1) {
+    stop("Scalar must be a single numeric value.")
+  }
 
+  # Scale functional components
+  new_functional_list <- lapply(input$functional_list, function(fd_obj) {
+    times.fd(scalar, fd_obj)
+  })
+
+  # Scale scalar predictors
   new_Z <- scalar * input$Z
 
+  # Reconstruct hybrid object
   predictor_hybrid(
     Z = new_Z,
-    functional_list = new_functional_list,
-    jacobian_list = input$jacobian_list,
-    n_basis_list = input$n_basis_list,
-    n_sample = input$n_sample,
-    n_functional = input$n_functional,
-    n_scalar = input$n_scalar
+    functional_list = new_functional_list
   )
@@
 
-  # Scalar matrix
+  # Scalar part (3 observations, 2 scalar predictors)
   Z <- matrix(2, nrow = 3, ncol = 2)
 
-  # Create a shared basis for both functional predictors
-  basis <- create.bspline.basis(c(0, 1), 5)
+  # Functional part: shared B-spline basis
+  basis <- create.bspline.basis(c(0, 1), nbasis = 5)
+  fd1 <- fd(coef = matrix(2, nrow = 5, ncol = 3), basisobj = basis)
+  fd2 <- fd(coef = matrix(2, nrow = 5, ncol = 3), basisobj = basis)
 
-  # Two identical fd objects
-  fd1 <- fd(coef = matrix(2, 5, 3), basisobj = basis)
-  fd2 <- fd(coef = matrix(2, 5, 3), basisobj = basis)
+  # Construct hybrid object using new simplified constructor
+  obj <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
 
-  # Construct predictor_hybrid object
-  obj <- predictor_hybrid(
-    Z = Z,
-    functional_list = list(fd1, fd2),
-    jacobian_list = list(matrix(0), matrix(0)),
-    n_basis_list = c(5, 5),
-    n_sample = 3,
-    n_functional = 2,
-    n_scalar = 2
-  )
+  # Apply scalar multiplication
+  scaled <- scalar_mul.predictor_hybrid(obj, scalar = 4)
 
-  # Perform scalar multiplication
-  scaled <- scalar_mul.predictor_hybrid(obj, 4)
-
+  # Check class
   testthat::expect_s3_class(scaled, "predictor_hybrid")
 
-  # Scalar part should be scaled
+  # Check scalar predictor was scaled
   testthat::expect_equal(scaled$Z, Z * 4)
 
-  # Each functional part should be scaled
-  expected_coef <- matrix(8, 5, 3)  # 2 * 4
-  for (fd_scaled in scaled$functional_list) {
+  # Check each functional component's coefficients
+  expected_coef <- matrix(8, nrow = 5, ncol = 3)
+  for (fd_obj in scaled$functional_list) {
     testthat::expect_equal(
-      unname(coef(fd_scaled)),
+      unname(coef(fd_obj)),
       unname(expected_coef)
@@
 
+### compute_gram_matrix
+```{r}
+#' Compute the Gram matrix for a basis object
+#'
+#' @param basis A basis object of class `basisfd` from the `fda` package
+#' @return A square matrix where entry (i,j) is the inner product of basis functions i and j
+#' @export
+compute_gram_matrix <- function(basis) {
+  stopifnot(inherits(basis, "basisfd"))
+  inprod(basis, basis)  # computes ∫ b_i(t) b_j(t) dt
+}
+
+```
+
+We check the following cases:
+| Case | Test                 | Expectation                             |
+| ---- | -------------------- | --------------------------------------- |
+| 1    | Orthogonal (Fourier) | Gram matrix ≈ diagonal                  |
+| 2    | Constant             | Single value equals interval length (1) |
+| 3    | Invalid              | Raises informative error                |
+| 4    | Narrow support       | Mostly low off-diagonal entries         |
+
+```{r}
+testthat::test_that("Gram matrix edge cases", {
+  library(fda)
+
+  # Case 1: Fourier basis (orthogonal over [0, 1])
+  fb <- create.fourier.basis(rangeval = c(0, 1), nbasis = 5)
+  J_fourier <- compute_gram_matrix(fb)
+  testthat::expect_equal(J_fourier, diag(diag(J_fourier)), tolerance = 1e-10)  # Nearly diagonal
+
+  # Case 2: Constant basis (1 basis function)
+  cb <- create.constant.basis(rangeval = c(0, 1))
+  J_const <- compute_gram_matrix(cb)
+  testthat::expect_equal(dim(J_const), c(1, 1))
+  testthat::expect_equal(J_const[1, 1], 1)
+
+  # Case 3: Invalid input
+  testthat::expect_error(compute_gram_matrix("not a basisfd"))
+
+  # Case 4: Highly localized B-splines
+  # Simulate nearly disjoint support (narrow B-splines)
+  narrow_bs <- create.bspline.basis(rangeval = c(0, 1), nbasis = 10, norder = 2)
+  J_narrow <- compute_gram_matrix(narrow_bs)
+  testthat::expect_true(all(abs(J_narrow[upper.tri(J_narrow)]) < 0.5))  # off-diagonals small
+})
+
+```
+
 ## Documenting the package and building

### 2025-05-31 create-rhello.Rmd
inprod test

@@
 
+# helper functions
+
+### is_same_basis
+```{r}
+#' @export
+is_same_basis <- function(input, other) {
+  all(
+    length(input$functional_list) == length(other$functional_list),
+    all(
+      mapply(function(fd1, fd2) fda::is.eqbasis(fd1$basis, fd2$basis),
+             input$functional_list, other$functional_list)
+    )
+  )
+}
+```
+
+### compute_gram_matrix
+```{r}
+#' Compute the Gram matrix for a basis object
+#'
+#' @param basis A basis object of class `basisfd` from the `fda` package
+#' @return A square matrix where entry (i,j) is the inner product of basis functions i and j
+#' @export
+compute_gram_matrix <- function(basis) {
+  stopifnot(inherits(basis, "basisfd"))
+  inprod(basis, basis)  # computes ∫ b_i(t) b_j(t) dt
+}
+
+```
+
+We check the following cases:
+
+| Case | Test                 | Expectation                             |
+|------|----------------------|------------------------------------------|
+| 1    | Orthogonal (Fourier) | Gram matrix ≈ diagonal                  |
+| 2    | Constant             | Single value equals interval length (1) |
+| 3    | Invalid              | Raises informative error                |
+| 4    | Narrow support       | Mostly low off-diagonal entries         |
+
+```{r}
+testthat::test_that("Gram matrix edge cases", {
+  suppressPackageStartupMessages(library(fda))
+
+  # Case 1: Fourier basis (orthogonal over [0, 1])
+  fb <- create.fourier.basis(rangeval = c(0, 1), nbasis = 5)
+  J_fourier <- compute_gram_matrix(fb)
+  testthat::expect_equal(J_fourier, diag(diag(J_fourier)), tolerance = 1e-10)  # Nearly diagonal
+
+  # Case 2: Constant basis (1 basis function)
+  cb <- create.constant.basis(rangeval = c(0, 1))
+  J_const <- compute_gram_matrix(cb)
+  testthat::expect_equal(dim(J_const), c(1, 1))
+  testthat::expect_equal(J_const[1, 1], 1)
+
+  # Case 3: Invalid input
+  testthat::expect_error(compute_gram_matrix("not a basisfd"))
+
+  # Case 4: Highly localized B-splines
+  # Simulate nearly disjoint support (narrow B-splines)
+  narrow_bs <- create.bspline.basis(rangeval = c(0, 1), nbasis = 10, norder = 2)
+  J_narrow <- compute_gram_matrix(narrow_bs)
+  testthat::expect_true(all(abs(J_narrow[upper.tri(J_narrow)]) < 0.5))  # off-diagonals small
+})
+
+```
+
+## helpers for functional data objects
+
+### rep_fd
+
+```{r}
+#' Replicate a list of single-sample fd objects multiple times
+#'
+#' This function broadcasts a list of single-sample functional predictors
+#' by replicating their coefficient columns.
+#'
+#' @param fd_list A list of `fd` objects, each representing a single sample.
+#' @param n The number of replications desired.
+#'
+#' @return A list of `fd` objects, each with `n` replications.
+#' @export
+rep_fd <- function(fd_list, n) {
+  if (!is.list(fd_list) || any(!vapply(fd_list, inherits, logical(1), "fd"))) {
+    stop("Input must be a list of 'fd' objects.")
+  }
+
+  lapply(fd_list, function(fd_obj) {
+    coef_mat <- fd_obj$coefs
+    if (is.null(dim(coef_mat)) || ncol(coef_mat) != 1) {
+      stop("Each fd object in the list must have one column of coefficients.")
+    }
+
+    new_coefs <- matrix(rep(coef_mat, n), nrow = nrow(coef_mat), ncol = n)
+    fd(coef = new_coefs, basisobj = fd_obj$basis)
+  })
+}
+```
+
+| Case | Description                            | Input Type               | Expected Output                        | Notes                                            |
+|------|----------------------------------------|--------------------------|----------------------------------------|--------------------------------------------------|
+| 1    | Correct replication                    | List of single-sample fd | List of `fd` objects with `n` columns | All columns identical to original coefficients   |
+| 2    | Each fd has one sample                 | List of fd               | No error                               | Verifies structure and content                  |
+| 3    | One fd has multiple samples            | fd with >1 columns       | Error                                   | Should raise informative error                  |
+| 4    | Non-fd object in list                  | List of non-`fd` items   | Error                                   | Validates class-checking robustness             |
+
+```{r}
+testthat::test_that("rep_fd correctly replicates a list of fd objects", {
+  suppressPackageStartupMessages(library(fda))
+
+  # Create a simple basis
+  basis <- create.bspline.basis(c(0, 1), 5)
+
+  # Create single-sample fd object
+  coef_vec <- 1:5
+  fd1 <- fd(coef = matrix(coef_vec, ncol = 1), basisobj = basis)
+
+  # Replicate the list
+  rep_list <- rep_fd(list(fd1, fd1), 3)
+
+  # Check: list length unchanged
+  testthat::expect_equal(length(rep_list), 2)
+
+  # Check each replicated fd object
+  for (fd_obj in rep_list) {
+    testthat::expect_s3_class(fd_obj, "fd")
+    testthat::expect_equal(dim(fd_obj$coefs), c(5, 3))  # 5 basis × 3 samples
+    for (i in 1:3) {
+      testthat::expect_equal(fd_obj$coefs[, i], coef_vec)
+    }
+  }
+
+  # Error if not single-sample
+  fd_multi <- fd(coef = matrix(1:10, nrow = 5, ncol = 2), basisobj = basis)
+  testthat::expect_error(rep_fd(list(fd_multi)), "Each fd object in the list must have one column")
+
+  # Error on non-fd input
+  testthat::expect_error(rep_fd(list(1, "not_fd")), "Input must be a list of 'fd' objects")
+})
+
+```
+
 # Class predictor_hybrid
@@
 
-- The `predictor_hybrid` class is an S3 object designed to represent this structure.
-
-- We implement Hilbert space operations for this class, and our algorithm is built on these foundational operations.
+- We define an S3 object `predictor_hybrid` that represent this structure, and implement Hilbert space operations for this class, and our algorithm is built on these foundational operations.
 
 The class definition is a simple list that contains a matrix and a collection of \code{fd} objects from the \code{fda} package, along with the necessary metadata.
+```{r classdef:predictor_hybrid}
 
-```{r}
 #' Create a predictor_hybrid object (S3 version, automatic basis size and Gram matrix)
@@
 }
-
 ```
@@
 testthat::test_that("predictor_hybrid constructor works as expected (S3, updated)", {
-  library(fda)
+  suppressPackageStartupMessages(library(fda))
 
@@
 ### inprod.predictor_hybrid
-The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)}) $ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as $\langle f_1, f_2\rangle_\mathcal{F} =  \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)}\rangle_{L^2} = \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k$ with norm $\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k)^2 dt_k\}^{1/2}$.
-
-Computes the inner product between two `predictor_hybrid` objects.Both scalar and functional components are included.
-
-  We define the inner product between any two hybrid objects, $\mathbf{h}_1 = (f_1, \mathbf{v}_1)$ and $\mathbf{h}_2 = (f_2, \mathbf{v}_2)$, as
+- The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)})$ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as 
+$$\langle f_1, f_2\rangle_\mathcal{F} =  \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)}\rangle_{L^2} = \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k,$$ with norm 
+$$\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k)^2 dt_k\}^{1/2}.$$
+- We define the inner product between any two hybrid objects, $\mathbf{h}_1 = (f_1, \mathbf{v}_1)$ and $\mathbf{h}_2 = (f_2, \mathbf{v}_2)$, as
 $$
-    \langle \mathbf{h}_1, \mathbf{h}_2\rangle_{\mathcal{H}} = \langle f_1, f_2\rangle_\mathcal{F} + w \langle  \mathbf{v_1}, \mathbf{v_2} \rangle = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k + \omega \sum \limits_{r=1}^p v_{1r}v_{2r},
+    \langle \mathbf{h}_1, \mathbf{h}_2\rangle_{\mathcal{H}} = \langle f_1, f_2\rangle_\mathcal{F} +  \langle  \mathbf{v_1}, \mathbf{v_2} \rangle = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p v_{1r}v_{2r},
 $$
 with norm $\Vert \cdot \Vert_\mathcal{H} = \langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
-$\omega$ is a positive weight that needs to be pre-specified or estimated.
-It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}).
-Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$.
-The results remain valid for any positive weights.
+
+- The method `inprod.predictor_hybrid` computes the inner product between two `predictor_hybrid` objects. It supports broadcasting when one of the inputs has a single observation.
+
 - Usage
@@
   - `xi_1`: A `predictor_hybrid` object.
-  - `xi_2`: Another `predictor_hybrid` object.
+  - `xi_2`: Another `predictor_hybrid` object. If omitted, defaults to xi_1 (computes self-inner product).
 
-- Value:  
-A numeric matrix of inner products (or a scalar if both inputs are single observations).
+- Value:  A numeric vector of inner products (or a scalar if both inputs are single observations).
 
 - Details:  
-  - Functional components are summed using `inprod()` from the `fda` package.  
+  - Functional components are summed using inprod() from the fda package.
   - Scalar components are handled via matrix multiplication.
-  - Returns a scalar if both `xi_1` and `xi_2` are single-sample predictors.
+  - Broadcasting is supported: if either xi_1 or xi_2 has only one sample, its values are broadcast across all rows of the other.
+  - Ensures compatibility in the number of functional and scalar predictors before computing the result.
 ```{r}
@@
 #' including both functional and scalar components. Supports broadcasting
-#' when one of the inputs has a single observation. If only one input is given,
-#' the inner product is computed with itself.
+#' when one of the inputs has a single observation.
 #'
@@
 #'
-#' @return A numeric matrix of inner products (or a scalar if both inputs have one row).
+#' @return A numeric vector of inner products, or a scalar if both inputs contain a single observation.
 #' @export
 inprod.predictor_hybrid <- function(xi_1, xi_2 = NULL) {
+  # Handle self-inner product
   if (is.null(xi_2)) xi_2 <- xi_1
 
-  # Optional: Check for basis compatibility
-  # if (!is_same_basis(xi_1, xi_2)) stop("Functional predictors must share the same basis.")
+  # Type checks
+  if (!inherits(xi_1, "predictor_hybrid") || !inherits(xi_2, "predictor_hybrid")) {
+    stop("Both inputs must be of class 'predictor_hybrid'.")
+  }
+
+  # Structural checks
+  if (xi_1$n_functional != xi_2$n_functional) {
+    stop("Mismatch in number of functional predictors.")
+  }
+  if (xi_1$n_scalar != xi_2$n_scalar) {
+    stop("Mismatch in number of scalar predictors.")
+  }
+
+  # Swap so that broadcasting always applies to xi_2
+  if (xi_1$n_sample == 1 && xi_2$n_sample > 1) {
+    tmp <- xi_1
+    xi_1 <- xi_2
+    xi_2 <- tmp
+  }
 
@@
 
-  # Compute sum of pairwise functional inner products
-  inprod_functional <- Reduce(`+`,
-    Map(function(f1, f2) fda::inprod(f1, f2),
-        xi_1$functional_list, xi_2$functional_list)
-  )
+  if (!(n1 == n2 || n2 == 1)) {
+    stop("Sample sizes are incompatible for broadcasting.")
+  }
 
-  # Broadcast-aware scalar component
-  Z1 <- if (n1 == 1) matrix(xi_1$Z, nrow = 1) else xi_1$Z
-  Z2 <- if (n2 == 1) matrix(xi_2$Z, nrow = 1) else xi_2$Z
-  inprod_scalar <- Z1 %*% t(Z2)
+  # Prepare components
+  f1 <- xi_1$functional_list
+  f2 <- xi_2$functional_list
+  Z1 <- xi_1$Z
+  Z2 <- xi_2$Z
 
+  # Replicate fd and Z if needed
+  if (n2 == 1) {
+    f2 <- rep_fd(f2, n1)
+    Z2 <- matrix(rep(c(Z2), n1), nrow = n1, byrow = TRUE)
+  }
+
+  # Compute functional inner products
+  inprod_functional <- vapply(seq_len(n1), function(i) {
+    sum(vapply(seq_along(f1), function(j) {
+      fda::inprod(f1[[j]][i], f2[[j]][i])
+    }, numeric(1)))
+  }, numeric(1))
+
+  # Compute scalar inner products
+  inprod_scalar <- rowSums(Z1 * Z2)
+
+  # Combine results
   result <- inprod_functional + inprod_scalar
-
   if (n1 == 1 && n2 == 1) as.numeric(result) else result
 }
-
 ```
 
+We run unit tests for:
+
+| Case | Description                        | Input Dimensions       | Output Length | Notes                                           |
+|------|------------------------------------|------------------------|----------------|-------------------------------------------------|
+| 1    | Self inner product (1 sample)      | x2: (1×2)              | 1              | Equivalent to squared norm                     |
+| 2    | Three-sample vs. Three-sample      | x1: (3×2), x3: (3×2)   | 3              | Dot + functional products, sample-wise         |
+| 3    | One-sample vs. One-sample          | x2: (1×2), x4: (1×2)   | 1              | Standard dot + functional product              |
+| 4    | Broadcasting (single vs. multi)    | x2: (1×2), x3: (3×2)   | 3              | Broadcast x2 across x3                          |
+| 5    | Broadcasting (multi vs. single)    | x3: (3×2), x2: (1×2)   | 3              | Broadcast x2 across x3                          |
+
 ```{r}
-testthat::test_that("inprod.predictor_hybrid works with broadcasting and self-inner product", {
+testthat::test_that("inprod.predictor_hybrid returns correct vector output for broadcasting and other cases", {
   suppressPackageStartupMessages(library(fda))
@@
   basis <- create.bspline.basis(c(0, 1), 5)
-  coef_val <- function(val) matrix(val, 5, 3)
+  make_fd <- function(val, n_sample) {
+    fd(coef = matrix(val, 5, n_sample), basisobj = basis)
+  }
+# data generation
+## three observations
+  fd1 <- make_fd(1, 3)
+  Z1 <- matrix(c(1, 2), nrow = 3, ncol = 2, byrow = TRUE)
+  x1 <- predictor_hybrid(Z1, list(fd1, fd1))
+## one observation
+  fd2 <- make_fd(2, 1)
+  Z2 <- matrix(c(3, 4), nrow = 1)
+  x2 <- predictor_hybrid(Z2, list(fd2, fd2))
+## three observations
+  Z3 <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 3, byrow = TRUE)
+  fd3 <- fd(coef = t(matrix(c(1:15), nrow = 3, byrow = TRUE)), basisobj = basis)
+  x3 <- predictor_hybrid(Z3, list(fd3, fd3))  
+## one observations
+  Z4 <- matrix(c(5, 6), nrow = 1)
+  fd4 <- make_fd(3, 1)
+  x4 <- predictor_hybrid(Z4, list(fd4, fd4))
 
-  # Define functional objects
-  fd_1 <- fd(coef = coef_val(1), basisobj = basis)
-  fd_2 <- fd(coef = coef_val(2), basisobj = basis)
+# Case 1: Self inner product (1 sample)
+  out1 <- inprod.predictor_hybrid(x2)
+  expected_scalar_1 <- sum(Z2^2)
+  expected_functional_1 <- sum(sapply(x2$functional_list, function(fd) fda::inprod(fd, fd)))
+  testthat::expect_equal(out1, expected_scalar_1 + expected_functional_1)
 
-  # Define scalar matrices
-  Z1 <- matrix(c(1, 2), nrow = 1)         # 1 × 2
-  Z2 <- matrix(c(3, 4), nrow = 1)         # 1 × 2
-  Z_many <- matrix(rep(c(1, 2), 3), nrow = 3, byrow = TRUE)  # 3 × 2
+# Case 2: Three-sample vs. Three-sample
+  out2 <- inprod.predictor_hybrid(x1, x3)
+  expected_scalar_2 <- rowSums(Z1 * Z3)
+  expected_functional_2 <- vapply(1:3, function(i) {
+    sum(sapply(1:2, function(j) {
+      fda::inprod(x1$functional_list[[j]][i], x3$functional_list[[j]][i])
+    }))
+  }, numeric(1))
+  testthat::expect_equal(out2, expected_scalar_2 + expected_functional_2)
 
-  # (1, 1)
-  x1 <- predictor_hybrid(Z1, list(fd_1, fd_1), list(matrix(0), matrix(0)), c(5, 5), 1, 2, 2)
-  x2 <- predictor_hybrid(Z2, list(fd_2, fd_2), list(matrix(0), matrix(0)), c(5, 5), 1, 2, 2)
-  val_scalar <- inprod.predictor_hybrid(x1, x2)
+  # Case 3: One-sample vs. one-sample
 
-  testthat::expect_type(val_scalar, "double")
-  testthat::expect_length(val_scalar, 1)
+  out3 <- inprod.predictor_hybrid(x2, x4)
+  expected_scalar_3 <- sum(Z2 * Z4)
+  expected_functional_3 <-2*fda::inprod(fd2, fd4)
+  testthat::expect_equal(out3, as.numeric(expected_scalar_3 + expected_functional_3))
 
-  # Expected functional inner product: 2 fds × sum(1 * 2) = 2 × (5×3) = 30
-  expected_functional <- 2 * sum(1 * 2) * 15  # 5 × 3 = 15 elements
-  expected_scalar <- sum(Z1 * Z2)            # 1*3 + 2*4 = 11
-  testthat::expect_equal(val_scalar, expected_functional + expected_scalar)
-
-  # (n, 1) broadcasting
-  x3 <- predictor_hybrid(Z_many, list(fd_1, fd_1), list(matrix(0), matrix(0)), c(5, 5), 3, 2, 2)
-  mat_3_1 <- inprod.predictor_hybrid(x3, x2)
-  testthat::expect_equal(dim(mat_3_1), c(3, 1))
-  testthat::expect_equal(as.numeric(mat_3_1), rep(val_scalar, 3))
-
-  # (1, m) broadcasting
-  x4 <- predictor_hybrid(Z_many, list(fd_2, fd_2), list(matrix(0), matrix(0)), c(5, 5), 3, 2, 2)
-  mat_1_3 <- inprod.predictor_hybrid(x1, x4)
-  testthat::expect_equal(dim(mat_1_3), c(1, 3))
-  testthat::expect_equal(as.numeric(mat_1_3), rep(val_scalar, 3))
-
-  # (n, m)
-  mat_3_3 <- inprod.predictor_hybrid(x3, x4)
-  testthat::expect_equal(dim(mat_3_3), c(3, 3))
-  testthat::expect_true(all(as.numeric(mat_3_3) == val_scalar))
-
-  # shorthand inprod(x) ≡ inprod(x, x)
-  self_inner <- inprod.predictor_hybrid(x1)
-  testthat::expect_equal(
-    self_inner,
-    inprod.predictor_hybrid(x1, x1)
-  )
-})
-
-```
-
-# helper functions
-
-### is_same_basis
-```{r}
-#' @export
-is_same_basis <- function(input, other) {
-  all(
-    length(input$functional_list) == length(other$functional_list),
-    all(
-      mapply(function(fd1, fd2) fda::is.eqbasis(fd1$basis, fd2$basis),
-             input$functional_list, other$functional_list)
-    )
-  )
-}
-```
-
-### compute_gram_matrix
-```{r}
-#' Compute the Gram matrix for a basis object
-#'
-#' @param basis A basis object of class `basisfd` from the `fda` package
-#' @return A square matrix where entry (i,j) is the inner product of basis functions i and j
-#' @export
-compute_gram_matrix <- function(basis) {
-  stopifnot(inherits(basis, "basisfd"))
-  inprod(basis, basis)  # computes ∫ b_i(t) b_j(t) dt
+  # Case 4: Broadcasting (single vs. multi)
+  out4 <- inprod.predictor_hybrid(x2, x3)
+  expected_scalar_4 <- c(0,0,0)
+  for (i in 1:3){
+    expected_scalar_4[i] <-  sum(Z2 * Z3[i,])
     }
 
-```
+  expected_functional_4 <-  c(0,0,0)
+  for (i in 1:3){
+    expected_functional_4[i] <- 2*fda::inprod(
+      fd2,
+      fd(
+        coef = matrix(
+        c(
+        (5*i+1-5):(5*i)
+        ), 5, 1), #end of matrix
+         basisobj = basis) #end of fd
+      )# end of inprod
+  }
 
-We check the following cases:
-| Case | Test                 | Expectation                             |
-| ---- | -------------------- | --------------------------------------- |
-| 1    | Orthogonal (Fourier) | Gram matrix ≈ diagonal                  |
-| 2    | Constant             | Single value equals interval length (1) |
-| 3    | Invalid              | Raises informative error                |
-| 4    | Narrow support       | Mostly low off-diagonal entries         |
+  testthat::expect_equal(as.vector(out4), as.vector(expected_scalar_4 + expected_functional_4))
 
-```{r}
-testthat::test_that("Gram matrix edge cases", {
-  library(fda)
-
-  # Case 1: Fourier basis (orthogonal over [0, 1])
-  fb <- create.fourier.basis(rangeval = c(0, 1), nbasis = 5)
-  J_fourier <- compute_gram_matrix(fb)
-  testthat::expect_equal(J_fourier, diag(diag(J_fourier)), tolerance = 1e-10)  # Nearly diagonal
-
-  # Case 2: Constant basis (1 basis function)
-  cb <- create.constant.basis(rangeval = c(0, 1))
-  J_const <- compute_gram_matrix(cb)
-  testthat::expect_equal(dim(J_const), c(1, 1))
-  testthat::expect_equal(J_const[1, 1], 1)
-
-  # Case 3: Invalid input
-  testthat::expect_error(compute_gram_matrix("not a basisfd"))
-
-  # Case 4: Highly localized B-splines
-  # Simulate nearly disjoint support (narrow B-splines)
-  narrow_bs <- create.bspline.basis(rangeval = c(0, 1), nbasis = 10, norder = 2)
-  J_narrow <- compute_gram_matrix(narrow_bs)
-  testthat::expect_true(all(abs(J_narrow[upper.tri(J_narrow)]) < 0.5))  # off-diagonals small
+  # Case 4: Broadcasting (multi  vs. single)
+  testthat::expect_equal(as.vector(inprod.predictor_hybrid( x3, x2)), as.vector(expected_scalar_4 + expected_functional_4))  
 })
-
 ```

### 2025-05-31 FSHybridPLS/R/add.predictor_hybrid.R

@@ -1,42 +1,0 @@
-# Generated from create-rhello.Rmd: do not edit by hand
-
-#' Add two predictor_hybrid objects
-#'
-#' Performs element-wise addition of two predictor_hybrid objects.
-#' Functional predictors are combined using `plus.fd()` and `times.fd()`.
-#'
-#' @param input A predictor_hybrid object.
-#' @param other Another predictor_hybrid object.
-#' @param alpha A numeric scalar multiplier for `other`.
-#'
-#' @return A new predictor_hybrid object representing the sum.
-#' @export
-add.predictor_hybrid <- function(input, other, alpha = 1) {
-  if (input$n_functional != other$n_functional || input$n_scalar != other$n_scalar) {
-    stop("Mismatch in number of predictors.")
-  }
-  
-  # Optionally check that functional bases are the same
-  # if (!is_same_basis(input, other)) stop("Different functional bases.")
-
-  new_functional_list <- vector("list", input$n_functional)
-  for (i in seq_len(input$n_functional)) {
-    new_functional_list[[i]] <- plus.fd(
-      input$functional_list[[i]],
-      times.fd(alpha, other$functional_list[[i]])
-    )
-  }
-  
-  new_Z <- input$Z + alpha * other$Z
-  
-  predictor_hybrid(
-    Z = new_Z,
-    functional_list = new_functional_list,
-    jacobian_list = input$jacobian_list,  # Assumes identical structure
-    n_basis_list = input$n_basis_list,
-    n_sample = input$n_sample,
-    n_functional = input$n_functional,
-    n_scalar = input$n_scalar
-  )
-}
-

### 2025-05-31 FSHybridPLS/R/compute_gram_matrix.R

@@ -1,0 +1,12 @@
+# Generated from create-rhello.Rmd: do not edit by hand
+
+#' Compute the Gram matrix for a basis object
+#'
+#' @param basis A basis object of class `basisfd` from the `fda` package
+#' @return A square matrix where entry (i,j) is the inner product of basis functions i and j
+#' @export
+compute_gram_matrix <- function(basis) {
+  stopifnot(inherits(basis, "basisfd"))
+  inprod(basis, basis)  # computes ∫ b_i(t) b_j(t) dt
+}
+

### 2025-05-31 FSHybridPLS/R/inprod.predictor_hybrid.R

@@ -4,36 +4,67 @@
 #'
 #' Computes the inner product between two `predictor_hybrid` objects,
 #' including both functional and scalar components. Supports broadcasting
-#' when one of the inputs has a single observation. If only one input is given,
-#' the inner product is computed with itself.
+#' when one of the inputs has a single observation.
 #'
 #' @param xi_1 A `predictor_hybrid` object.
 #' @param xi_2 Another `predictor_hybrid` object. If missing, defaults to `xi_1`.
 #'
-#' @return A numeric matrix of inner products (or a scalar if both inputs have one row).
+#' @return A numeric vector of inner products, or a scalar if both inputs contain a single observation.
 #' @export
 inprod.predictor_hybrid <- function(xi_1, xi_2 = NULL) {
-  if (is.null(xi_2)) xi_2 <- xi_1
+  # Handle self-inner product
+  if (is.null(xi_2)) xi_2 <- xi_1 
   
-  # Optional: Check for basis compatibility
-  # if (!is_same_basis(xi_1, xi_2)) stop("Functional predictors must share the same basis.")
+  # Type checks
+  if (!inherits(xi_1, "predictor_hybrid") || !inherits(xi_2, "predictor_hybrid")) {
+    stop("Both inputs must be of class 'predictor_hybrid'.")
+  }
+
+  # Structural checks
+  if (xi_1$n_functional != xi_2$n_functional) {
+    stop("Mismatch in number of functional predictors.")
+  }
+  if (xi_1$n_scalar != xi_2$n_scalar) {
+    stop("Mismatch in number of scalar predictors.")
+  }
+
+  # Swap so that broadcasting always applies to xi_2
+  if (xi_1$n_sample == 1 && xi_2$n_sample > 1) {
+    tmp <- xi_1
+    xi_1 <- xi_2
+    xi_2 <- tmp
+  }
 
   n1 <- xi_1$n_sample
   n2 <- xi_2$n_sample
 
-  # Compute sum of pairwise functional inner products
-  inprod_functional <- Reduce(`+`,
-    Map(function(f1, f2) fda::inprod(f1, f2),
-        xi_1$functional_list, xi_2$functional_list)
-  )
+  if (!(n1 == n2 || n2 == 1)) {
[…]

### 2025-05-31 FSHybridPLS/R/is_same_basis.R

@@ -1,0 +1,12 @@
+# Generated from create-rhello.Rmd: do not edit by hand
+
+#' @export
+is_same_basis <- function(input, other) {
+  all(
+    length(input$functional_list) == length(other$functional_list),
+    all(
+      mapply(function(fd1, fd2) fda::is.eqbasis(fd1$basis, fd2$basis),
+             input$functional_list, other$functional_list)
+    )
+  )
+}

### 2025-05-31 FSHybridPLS/R/predictor_hybrid.R

@@ -1,37 +1,0 @@
-# Generated from create-rhello.Rmd: do not edit by hand
-
-#' Create a predictor_hybrid object (S3 version)
-#'
-#' Constructs a hybrid predictor object that stores both scalar and functional predictors,
-#' along with Jacobians and metadata.
-#'
-#' @param Z A numeric matrix of dimension \code{n_sample × n_scalar} representing scalar predictors.
-#' @param functional_list A list of functional predictors (e.g., \code{fd} objects from the \code{fda} package).
-#' @param jacobian_list A list of Jacobian matrices corresponding to the functional predictors.
-#' @param n_basis_list A numeric vector indicating the number of basis functions for each functional predictor.
-#' @param n_sample Number of observations (samples).
-#' @param n_functional Number of functional predictors.
-#' @param n_scalar Number of scalar predictors.
-#'
-#' @return A list of class \code{predictor_hybrid}.
-#' @export
-predictor_hybrid <- function(Z, functional_list, jacobian_list,
-                             n_basis_list, n_sample, n_functional, n_scalar) {
-  stopifnot(is.matrix(Z))
-  stopifnot(length(functional_list) == n_functional)
-  stopifnot(length(jacobian_list) == n_functional)
-  stopifnot(length(n_basis_list) == n_functional)
-  
-  structure(
-    list(
-      Z = Z,
-      functional_list = functional_list,
-      jacobian_list = jacobian_list,
-      n_basis_list = n_basis_list,
-      n_sample = n_sample,
-      n_functional = n_functional,
-      n_scalar = n_scalar
-    ),
-    class = "predictor_hybrid"
-  )
-}

### 2025-05-31 FSHybridPLS/R/rep_fd.R

@@ -1,0 +1,27 @@
+# Generated from create-rhello.Rmd: do not edit by hand
+
+#' Replicate a list of single-sample fd objects multiple times
+#'
+#' This function broadcasts a list of single-sample functional predictors
+#' by replicating their coefficient columns.
+#'
+#' @param fd_list A list of `fd` objects, each representing a single sample.
+#' @param n The number of replications desired.
+#'
+#' @return A list of `fd` objects, each with `n` replications.
+#' @export
+rep_fd <- function(fd_list, n) {
+  if (!is.list(fd_list) || any(!vapply(fd_list, inherits, logical(1), "fd"))) {
+    stop("Input must be a list of 'fd' objects.")
+  }
+
+  lapply(fd_list, function(fd_obj) {
+    coef_mat <- fd_obj$coefs
+    if (is.null(dim(coef_mat)) || ncol(coef_mat) != 1) {
+      stop("Each fd object in the list must have one column of coefficients.")
+    }
+
+    new_coefs <- matrix(rep(coef_mat, n), nrow = nrow(coef_mat), ncol = n)
+    fd(coef = new_coefs, basisobj = fd_obj$basis)
+  })
+}

### 2025-05-31 FSHybridPLS/R/scalar_mul.predictor_hybrid.R

@@ -2,7 +2,7 @@
 
 #' Multiply a predictor_hybrid object by a scalar
 #'
-#' Performs scalar multiplication of both scalar and functional components 
+#' Performs scalar multiplication on both the scalar and functional components
 #' of a `predictor_hybrid` object. Functional predictors are scaled using 
 #' `times.fd()` from the `fda` package.
 #'
@@ -12,20 +12,24 @@
 #' @return A new `predictor_hybrid` object scaled by `scalar`.
 #' @export
 scalar_mul.predictor_hybrid <- function(input, scalar) {
-  new_functional_list <- lapply(
-    input$functional_list,
-    function(fd_obj) times.fd(scalar, fd_obj)
-  )
-  
+  if (!inherits(input, "predictor_hybrid")) {
+    stop("Input must be of class 'predictor_hybrid'.")
+  }
+  if (!is.numeric(scalar) || length(scalar) != 1) {
+    stop("Scalar must be a single numeric value.")
+  }
+
+  # Scale functional components
+  new_functional_list <- lapply(input$functional_list, function(fd_obj) {
+    times.fd(scalar, fd_obj)
+  })
+
+  # Scale scalar predictors
   new_Z <- scalar * input$Z
-  
+
+  # Reconstruct hybrid object
   predictor_hybrid(
     Z = new_Z,
-    functional_list = new_functional_list,
-    jacobian_list = input$jacobian_list,
-    n_basis_list = input$n_basis_list,
-    n_sample = input$n_sample,
-    n_functional = input$n_functional,
-    n_scalar = input$n_scalar
+    functional_list = new_functional_list
   )
 }

### 2025-05-31 FSHybridPLS/tests/testthat/tests.R

@@ -1,154 +1,242 @@
 # Generated from create-rhello.Rmd: do not edit by hand  
-testthat::test_that("predictor_hybrid constructor works as expected (S3)", {
+testthat::test_that("Gram matrix edge cases", {
+  suppressPackageStartupMessages(library(fda))
+
+  # Case 1: Fourier basis (orthogonal over [0, 1])
+  fb <- create.fourier.basis(rangeval = c(0, 1), nbasis = 5)
+  J_fourier <- compute_gram_matrix(fb)
+  testthat::expect_equal(J_fourier, diag(diag(J_fourier)), tolerance = 1e-10)  # Nearly diagonal
+
+  # Case 2: Constant basis (1 basis function)
+  cb <- create.constant.basis(rangeval = c(0, 1))
+  J_const <- compute_gram_matrix(cb)
+  testthat::expect_equal(dim(J_const), c(1, 1))
+  testthat::expect_equal(J_const[1, 1], 1)
+
+  # Case 3: Invalid input
+  testthat::expect_error(compute_gram_matrix("not a basisfd"))
+
+  # Case 4: Highly localized B-splines
+  # Simulate nearly disjoint support (narrow B-splines)
+  narrow_bs <- create.bspline.basis(rangeval = c(0, 1), nbasis = 10, norder = 2)
+  J_narrow <- compute_gram_matrix(narrow_bs)
+  testthat::expect_true(all(abs(J_narrow[upper.tri(J_narrow)]) < 0.5))  # off-diagonals small
+})
+
+
+
+testthat::test_that("rep_fd correctly replicates a list of fd objects", {
+  suppressPackageStartupMessages(library(fda))
+
+  # Create a simple basis
+  basis <- create.bspline.basis(c(0, 1), 5)
+
+  # Create single-sample fd object
+  coef_vec <- 1:5
+  fd1 <- fd(coef = matrix(coef_vec, ncol = 1), basisobj = basis)
+
+  # Replicate the list
+  rep_list <- rep_fd(list(fd1, fd1), 3)
+
+  # Check: list length unchanged
+  testthat::expect_equal(length(rep_list), 2)
+
+  # Check each replicated fd object
+  for (fd_obj in rep_list) {
+    testthat::expect_s3_class(fd_obj, "fd")
[…]

### 2025-05-31 create-rhello.Rmd
add broadcast improved

@@
 ```{r}
-add.predictor_hybrid <- function(input, other, alpha = 1) {
-  if (!inherits(input, "predictor_hybrid") || !inherits(other, "predictor_hybrid")) {
-    stop("Both arguments must be of class 'predictor_hybrid'.")
-  }
-
-  if (input$n_functional != other$n_functional || input$n_scalar != other$n_scalar) {
-    stop("Mismatch in number of functional or scalar predictors.")
-  }
-
-  # Check broadcasting compatibility
-  n1 <- input$n_sample
-  n2 <- other$n_sample
-  if (n1 != n2 && !(n1 == 1 || n2 == 1)) {
-    stop("Sample sizes are incompatible for broadcasting.")
-  }
-
+add.predictor_hybrid <- function(xi_1, xi_2, alpha = 1) {
   # Safe access to is.eqbasis()
@@
 
-  for (i in seq_len(input$n_functional)) {
-    if (!is_eqbasis(input$functional_list[[i]]$basis, other$functional_list[[i]]$basis)) {
+  for (i in seq_len(xi_1$n_functional)) {
+    if (!is_eqbasis(xi_1$functional_list[[i]]$basis, xi_2$functional_list[[i]]$basis)) {
       stop("Functional predictors must have the same basis.")
@@
 
-  # Broadcast if needed
-  broadcast <- function(obj, n_target) {
-    if (obj$n_sample == n_target) return(obj)
-    obj$Z <- matrix(rep(obj$Z, each = n_target), nrow = n_target, byrow = TRUE)
-    obj$functional_list <- lapply(obj$functional_list, function(fd_obj) {
-      fd(coef = matrix(rep(coef(fd_obj), n_target), nrow = nrow(coef(fd_obj))),
-         basisobj = fd_obj$basis)
-    })
-    obj$n_sample <- n_target
-    obj
+   # Type checks
+  if (!inherits(xi_1, "predictor_hybrid") || !inherits(xi_2, "predictor_hybrid")) {
+    stop("Both inputs must be of class 'predictor_hybrid'.")
   }
 
-  # Determine output sample size
-  n_out <- max(n1, n2)
-  input <- broadcast(input, n_out)
-  other <- broadcast(other, n_out)
+  # Structural checks
+  if (xi_1$n_functional != xi_2$n_functional) {
+    stop("Mismatch in number of functional predictors.")
+  }
+  if (xi_1$n_scalar != xi_2$n_scalar) {
+    stop("Mismatch in number of scalar predictors.")
+  }
+
+  # Swap so that broadcasting always applies to xi_2
+  if (xi_1$n_sample == 1 && xi_2$n_sample > 1) {
+    tmp <- xi_1
+    xi_1 <- xi_2
+    xi_2 <- tmp
+  }
+
+  n1 <- xi_1$n_sample
+  n2 <- xi_2$n_sample
+
+  if (!(n1 == n2 || n2 == 1)) {
+    stop("Sample sizes are incompatible for broadcasting.")
+  }
+
+  # Prepare components
+  f1 <- xi_1$functional_list
+  f2 <- xi_2$functional_list
+  Z1 <- xi_1$Z
+  Z2 <- xi_2$Z
+
+  # Replicate fd and Z if needed
+  if (n2 == 1) {
+    f2 <- rep_fd(f2, n1)
+    Z2 <- matrix(rep(c(Z2), n1), nrow = n1, byrow = TRUE)
+  }
 
@@
     function(f1, f2) plus.fd(f1, times.fd(alpha, f2)),
-    input$functional_list,
-    other$functional_list
+    f1,
+    f2
   )
 
+  # Compute scalar inner products
+  inprod_scalar <- rowSums(Z1 * Z2) 
   # Combine scalar predictors
-  new_Z <- input$Z + alpha * other$Z
+  new_Z <- Z1 + alpha * Z2
 

### 2025-05-31 create-rhello.Rmd
get_penalty_hybrid

@@
     Description = "This package says hello.  But its actual purpose is to show how an R package can be completely coded in a single R markdown file.",
-    Imports = "fda (>= 6.1.3)",
+    Imports = "fda (>= 6.1.3), Matrix",
     `Authors@R` = person(
@@
 
+# One iteration
+
+## small functions
+
+## penalty matrix
+
+### get_gram_matrix_block
+Equation (6) in Section 4.1
+$$
+    J^*=\mathrm{blkdiag}(J, I_p) \in \mathbb{R}^{(MK+p) \times (MK+p)}
+$$
+where
+$J^{(k)}$ is the $M \times M$ matrix with $(m,n)$-th entry equal to $\int_{\mathcal{T}_k} b_m^{(k)}(t) b_n^{(k)}(t) dt$, and $J = \mathrm{blkdiag}(J^{(1)}, \cdots, J^{(K)}) \in \mathbb{R}^{MK \times MK}$, and
+
+```{r}
+#' Construct block-diagonal Gram matrix for hybrid predictor
+#'
+#' Returns a block-diagonal matrix containing the Gram  matrices for
+#' each functional component and an identity matrix for the scalar part.
+#'
+#' @param obj A `predictor_hybrid` object.
+#'
+#' @return A block-diagonal matrix of size `(total_dim × total_dim)` where
+#' functional and scalar components are arranged in order.
+#' @export
+get_gram_matrix_block <- function(obj) {
+  if (!inherits(obj, "predictor_hybrid")) {
+    stop("Input must be of class 'predictor_hybrid'.")
+  }
+
+  gram_blocks <- c(obj$gram_list, list(diag(obj$n_scalar)))
+  Matrix::bdiag(gram_blocks)
+}
+
+```
+
+### get_penalty_hybrid
+Constructs a matrix defined in \label{def:J_dotdot_ast}
+$$
+    \ddot{J}^\ast=\mathrm{blkdiag}(\ddot{J}^{(1)}, \cdots, \ddot{J}^{(K)}, 0_{p \times p}) \in \mathbb{R}^{(MK+p) \times (MK+p)},
+$$
+where
+ $\ddot{J}^{(k)}$ is  a $M \times M$ matrix defined in \label{def:dodot_J_k} as the gram matrix formed by the second derivativ of the basis functions
+$$
+\ddot{J}^{(k)} = \left[ \int_{\mathcal{T}_k} \ddot{b}^{(k)}_m(t) \ddot{b}^{(k)}_n(t) \, dt \right]_{m,n=1}^M.
+$$
+```{r}
+#' Construct the roughness penalty matrix for a predictor_hybrid object
+#'
+#' Returns a block diagonal matrix representing roughness penalties for each functional predictor
+#' and zeros for the scalar predictors (scalar predictors are not penalized).
+Each functional component uses its own basis penalty matrix, computed via second derivative penalty via `getbasispenalty()` from the `fda` package
+#'
+#' @param W A `predictor_hybrid` object.
+#'
+#' @return A block diagonal penalty matrix of dimension `(sum(n_basis_list) + n_scalar)^2`.
+#' @export
+get_penalty_hybrid <- function(W){
+  J_dotdot_star <- fda::getbasispenalty(W$functional_list[[1]]$basis)
+  for (ii in 2:(W$n_functional)){
+    J_dotdot_star <- Matrix::bdiag(
+      J_dotdot_star,
+      fda::getbasispenalty(W$functional_list[[ii]]$basis)
+    )
+    }
+  J_dotdot_star <- Matrix::bdiag(
+    J_dotdot_star,
+    matrix(0, nrow = W$n_scalar, ncol = W$n_scalar)
+    )
+  return(J_dotdot_star)
+  }
+```
+
+```{r}
+testthat::test_that("get_penalty_hybrid computes correct dimensions and structure", {
+  suppressPackageStartupMessages(library(fda))
+
+  # Setup
+  basis <- fda::create.bspline.basis(c(0, 1), nbasis = 5)
+  n_sample <- 3
+  n_scalar <- 2
+
+  fd1 <- fda::fd(coef = matrix(1, 5, n_sample), basisobj = basis)
+  fd2 <- fda::fd(coef = matrix(2, 5, n_sample), basisobj = basis)
+  Z <- matrix(rnorm(n_sample * n_scalar), n_sample, n_scalar)
+  obj <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
+
+  # Run
+  penalty <- get_penalty_hybrid(obj)
+
+  # Expected dimensions
+  total_dim <- sum(obj$n_basis_list) + obj$n_scalar
+  testthat::expect_equal(dim(penalty), c(total_dim, total_dim))
+
+  # Check block diagonal structure: bottom-right should be zero matrix
+  scalar_block <- as.matrix(penalty[
+    (total_dim - n_scalar + 1):total_dim,
+    (total_dim - n_scalar + 1):total_dim
+  ])
+  testthat::expect_equal(scalar_block, matrix(0, n_scalar, n_scalar))
+
+  # Check that the upper blocks are positive semidefinite
+  eigenvalues <- eigen(as.matrix(penalty[1:(total_dim - n_scalar), 1:(total_dim - n_scalar)]))$values
+  testthat::expect_true(all(eigenvalues >= -1e-8))  # Numerical tolerance
+})
+
+```
+
+###
+```{r}
+get_smoothing_param_hybrid <- function(W, lambda){
+  #lambda: list of length K (=n_functional)
+  lambda_mat <- lambda[1] * diag(W@functional_list[[1]]$basis$nbasis)
+  for (ii in 2:(W@n_functional)){
+    n_basis_now <- dim(W@jacobian_list[[ii]])[2]
+    lambda_mat <- bdiag(
+      lambda_mat,
+      lambda[ii] * diag(W@functional_list[[ii]]$basis$nbasis)
+    )
+      }
+  lambda_mat <- bdiag(
+    lambda_mat,
+    matrix(0, nrow = W@n_scalar, ncol = W@n_scalar)
+  )
+}
+
+```
+
+### get_pre_corrcov
+construct the matrix V_star:
+$$
+    V^\ast = n^{-2}\begin{bmatrix}
+         J \widetilde{C}^\top \mathbf{y}\mathbf{y}^\top \widetilde{C} J & J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z} \\
+        \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J &   \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z}
+    \end{bmatrix} = n^{-2} J^* \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^*
+    \in \mathbb{R}^{(MK+p) \times (MK+p)},
+$$
+where $J$ is defined in `get_gram_matrix_block`
+equation (7), 
+```{r}
+#' Compute V matrix (pre-corrected covariance estimator)
+#'
+#' Constructs the V matrix involving inner products of functional predictors
+#' (weighted by their Gram matrices) and scalar predictors against response y.
+#'
+#' @param W A `predictor_hybrid` object.
+#' @param y A numeric response vector of length equal to number of samples.
+#'
+#' @return A matrix representing the corrected cross-covariance structure.
+#' @export
+get_pre_corrcov <- function(W, y){
+  n <- W$n_sample
+  K <- W$n_functional
+
+  # building blocks
+  ## C_J : C multiplied by J. Scalable to arbitrary K
+  predictor_first <- W$functional_list[[1]]
+  C_J <- t(predictor_first$coefs) %*% W$gram_list[[1]]
+  for (i in 2:K){
+    predictor_now <- W$functional_list[[i]]
+    C_J <- cbind(
+      C_J,
+      t(predictor_now$coefs) %*% W$gram_list[[i]]
+    )
+    }
+
+  ## covariance
+  J_Ct_y <- t(C_J) %*% y
+  Zt_y <- t(W$Z) %*% y
+
+  # V matrix
+  upper_left <- J_Ct_y %*% t(J_Ct_y)
+  upper_right <- J_Ct_y %*% t(Zt_y)
+  lower_left <- t(upper_right)
+  lower_right <- Zt_y %*% t(Zt_y)
+
+  V_star <- cbind(
+    rbind(upper_left, lower_left),
+    rbind(upper_right, lower_right)
+    )/(n^2)
+
+  return(V_star)
+  }
+```
+
+test code:
+
+| Case | Description               | Functional Coefficients         | Scalar Covariates      | Response         | Expected Behavior                              |
+|------|---------------------------|----------------------------------|------------------------|------------------|------------------------------------------------|
+| 1    | Constant structure        | All ones or twos                | All ones               | Increasing vector| Output matrix is symmetric and non-negative    |
+| 2    | Random structure          | Random normal entries           | Random normal values   | Random vector    | Output is symmetric and numerically PSD        |
+
+```{r}
+testthat::test_that("get_pre_corrcov handles constant and random coefficients", {
+  suppressPackageStartupMessages(library(fda))
+
+  make_fd <- function(coefs, basis) {
+    fd(coef = coefs, basisobj = basis)
+  }
+
+  basis <- create.bspline.basis(c(0, 1), nbasis = 4)
+  n_sample <- 5
+  n_scalar <- 2
+  n_functional <- 2
+
+  # Constant coefficients
+  fd_const1 <- make_fd(matrix(1, 4, n_sample), basis)
+  fd_const2 <- make_fd(matrix(2, 4, n_sample), basis)
+  Z_const <- matrix(1, n_sample, n_scalar)
+  y_const <- matrix(1:n_sample, ncol = 1)
+  obj_const <- predictor_hybrid(Z = Z_const, functional_list = list(fd_const1, fd_const2))
+
+  V_const <- get_pre_corrcov(obj_const, y_const)
+  testthat::expect_equal(dim(V_const), rep(sum(obj_const$n_basis_list) + obj_const$n_scalar, 2))
+  testthat::expect_true(isSymmetric(V_const))
+  testthat::expect_true(all(V_const >= 0))
+
+  # Random coefficients
+  set.seed(123)
+  fd_rand1 <- make_fd(matrix(rnorm(4 * n_sample), 4, n_sample), basis)
+  fd_rand2 <- make_fd(matrix(rnorm(4 * n_sample), 4, n_sample), basis)
+  Z_rand <- matrix(rnorm(n_sample * n_scalar), n_sample, n_scalar)
+  y_rand <- matrix(rnorm(n_sample), ncol = 1)
+  obj_rand <- predictor_hybrid(Z = Z_rand, functional_list = list(fd_rand1, fd_rand2))
+
+  V_rand <- get_pre_corrcov(obj_rand, y_rand)
+  testthat::expect_equal(dim(V_rand), rep(sum(obj_rand$n_basis_list) + obj_rand$n_scalar, 2))
+  testthat::expect_true(isSymmetric(V_rand))
+  testthat::expect_true(all(eigen(V_rand, only.values = TRUE)$values >= -1e-8))
+})
+
+```
+
+## get_pls_comp
+
+```{r}
+get_pls_comp <- function(W, y, L, verbose){
+  # W: hybrid predictor
+  # y: response vector
+  # L: regularization hyperparameter
+
+  V_star <- get_pre_corrcov(W, y)
+  #Last paragraph of section 3.2. To solve (6) in practice...
+  #A <- t(solve(L, t(V_star))) # A = V* t(inv(L))
+  #E <- solve(L, A) # E = inv(L) A
+
+  invL <- Matrix::chol2inv(L)
+  A <- V_star %*% t(invL) # A = V* t(inv(L))
+  E <- invL %*% A # E = inv(L) A
+
+  eigen_result <- eigen(E)
+  #cat("eigenvalues: ", eigen_result$values)
+  e <- eigen_result$vectors[, 1]
+  if(is.complex(e)){
+    return("stop")
+  }
+  #e <- e / Matrix::norm(e, "2") #normalize; omitted by request of Dr. Jang
+  #xi_star <- solve(t(L), e) # t(L) xi* = e, basis coefficient of estimated PLS component
+  xi_star <- t(invL) %*% e
+  xi_hat <- hybrid_from_coef(format = W, xi_star = xi_star) #estimated PLS component
+  return(
+    list(
+      xi_hat = xi_hat,
+      E = E,
+      V_star = V_star,
+      eigen_val = eigen_result$values[1]
+      )
+  )
+  }
+```
+
+```{r}
+nipals_pen_hybrid <- function(W, y, n_iter, lambda, verbose) {
+  # 1. initialize the storage
+  rho <- xi <- delta <- nu  <- sigma <- eta <- list()
+  E <- V_star <- eigen_val <-list()
+  fitted_value_W <- fitted_value_y <-list()
+  resid_y <- W_now <- list() #data for iteration
+  first_eigen_val <- mse_W <- mse_y <-rep(NA, n_iter)
+
+  # 2. constraint matrix is the same at every iteration
+  J_star          <- get_gram_matrix_block(W)
+  J_dotdot_star   <- get_penalty_hybrid(W)
+  lambda_mat      <- get_smoothing_param_hybrid(W, lambda)
+  constr_mat      <- J_star + (lambda_mat %*% J_dotdot_star) # denominator in the equation (6)
+  constr_mat_chol <- t(chol(constr_mat))
+
+  W_now[[1]] <- W
+  y_now <- y
+  final_succesful_iteration <- 0
+  for (l in 1:n_iter) {
+    #cat(paste("#############################################", "\n"))
+    if(verbose==T)cat(paste(l, "th component", "\n"))
+
+    # STEP 1. calculate pls score
+    pls_result_now <- get_pls_comp(W_now[[l]], y_now, constr_mat_chol, verbose)
+    if(!is.list(pls_result_now)){break}
+
+    xi[[l]] <- pls_result_now$xi # pls component. Section 3.2
+    rho[[l]] <- hybrid_inner_prod(W_now[[l]], xi[[l]]) # pls scores : n_sample * 1 matrix
+
+    # STEP 2. residulize
+    # residualize predictor: hybrid (W) on scalar (rho) linear regression with n_sample observations
+    delta[[l]] <- LSE_hybrid(W_now[[l]], rho[[l]]) #single obs of hybrid predictor
+
+    fitted_value_W[[l]] <- fitted_value(delta[[l]], rho[[l]])
+    W_now[[l+1]] <- subtr(W_now[[l]], fitted_value_W[[l]])
+    # residualize resoponse
+    nu[[l]] <- LSE_ptws(y_now, rho[[l]]) #scalar on scalar linear regression with n_sample observations
+    fitted_value_y[[l]] <- nu[[l]] * rho[[l]]
+    y_now <- y_now - fitted_value_y[[l]]
+    resid_y[[l]] <- y_now
+
+    #check mean norm
+    #mse_W[l] <- mean_sum_sqrd(W_now[[l]])
+    #mse_y[l] <- norm(y_now,"2")
+
+    #cat("W:", mse_W[l], "\n")
+    #cat("y:",  mse_y[l], "\n\n")
+
+    # STEP 3.
+    sigma[[l]] <- xi[[l]]
+    if (l == 1) {
+      eta[[l]] <- scalar_mul(sigma[[l]], nu[[l]])
+    }else{ # if l > 1
+      for (u in 1:(l - 1)){
+        sigma[[l]] <- subtr( sigma[[l]], sigma[[u]], hybrid_inner_prod(delta[[u]], xi[[l]]) )
+      } #end of u-loop
+      eta[[l]] <- add(eta[[l-1]], sigma[[l]], nu[[l]])
+    }#if statement
+
+    # just for records.
+    E[[l]] <- pls_result_now$E # for monitoring symetricity
+    V_star[[l]] <- pls_result_now$V_star
+    eigen_val[[l]] <- pls_result_now$eigen_val
+    first_eigen_val[l] <- eigen_val[[l]][1]
+    final_succesful_iteration <- l
+  }# for loop: l
+}
+```
+
 ## Documenting the package and building

### 2025-06-05 create-FSHybridPLS.Rmd
predictor_hybrid_from_coef

--- 2025-05-31 create-rhello.Rmd
@@
 })
+```
+
+### predictor_hybrid_from_coef
+An alternative constructor for a predictor_hybrid object based on a flat numeric coefficient vector.
+It reconstructs both the functional and scalar components for a single-sample hybrid predictor object.
+The function reads the basis information from the template `format` object.
+
+- Inputs
+  - **`format`**: A `predictor_hybrid` object containing:
+    - `functional_list`: List of `fd` objects with basis info
+    - `gram_list`: List of Gram matrices
+    - `n_scalar`: Number of scalar predictors
+  - **`coef`**: Numeric vector of length `K * M + d`, where:
+    - `K` = number of functional predictors  
+    - `M` = number of basis functions (assumed same across predictors)  
+    - `d` = number of scalar predictors
+
+- Output
+  - A `predictor_hybrid` object with:
+    - Functional predictors rebuilt from the first `K * M` coefficients
+    - Scalar predictor `Z` from the remaining `d` coefficients
+    - `n_sample` set to 1
+
+```{r}
+#' Construct a Single-Sample Predictor Hybrid Object from Coefficients
+#'
+#' Reconstructs a \code{predictor_hybrid} object representing one observation, using a numeric
+#' coefficient vector. This alternative constructor maps the coefficients back into their functional
+#' and scalar predictor representations based on the structure of a template \code{predictor_hybrid} object.
+#'
+#' @param format A \code{predictor_hybrid} object that provides the structure and basis information.
+#' @param coef A numeric vector containing coefficients for both functional and scalar predictors.
+#'
+#' @return A \code{predictor_hybrid} object with updated \code{functional_list}, \code{Z}, and \code{n_sample = 1}.
+#'
+#'
+#' @export
+predictor_hybrid_from_coef <- function(format, coef){
+  M <- dim(format$gram_list[[1]])[2] # number of basis functions
+  K <- length(format$functional_list) # number of functional predictors
+  for (ii in 1:K){
+    format$functional_list[[ii]] <- fd(
+      coef = as.matrix(coef[((ii-1)*M + 1):(ii*M)]),
+      basisobj = format$functional_list[[ii]]$basis
+    )
+  }
+  format$Z <- t(as.matrix(coef[(K * M + 1):length(coef)]))
+  format$n_sample <- 1
+  return(format)
+}
+```
+
+**unit test**
+```{r}
+testthat::test_that("hybrid_from_coef reconstructs single-sample predictor_hybrid correctly", {
+  suppressPackageStartupMessages(library(fda))
+
+  make_fd <- function(coefs, basis) {
+    fd(coef = coefs, basisobj = basis)
+  }
+
+  basis <- create.bspline.basis(c(0, 1), nbasis = 4)
+  n_sample <- 5
+  n_scalar <- 2
+  n_functional <- 2
+
+  # Create dummy functional list with zeros
+  fd1 <- make_fd(matrix(0, 4, n_sample), basis)
+  fd2 <- make_fd(matrix(0, 4, n_sample), basis)
+  Z <- matrix(0, n_sample, n_scalar)
+  obj_template <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
+
+  # Create coefficient vector for reconstruction: 4 + 4 + 2 = 10
+  xi_star <- c(1:10)
+
+  # Apply reconstruction
+  obj_single <- predictor_hybrid_from_coef(obj_template, xi_star)
+
+  # Checks
+  testthat::expect_s3_class(obj_single, "predictor_hybrid")
+  testthat::expect_equal(obj_single$n_sample, 1)
+  testthat::expect_equal(obj_single$Z, matrix(c(9, 10), nrow = 1))
+
+  # Check functional coefficients (use coef() not $coefs)
+  testthat::expect_equal(drop(coef(obj_single$functional_list[[1]])), 1:4)
+  testthat::expect_equal(drop(coef(obj_single$functional_list[[2]])), 5:8)
+})
+
 ```
@@
 
-## penalty matrix
+## penalty matrix construction
+In this section, we provide an R function `get_constraint_matrix` that constructs the penalty matrix
+$$J^*+\Lambda \ddot{J}^\ast,$$
+as defined in Proposition 2 and used in the PLS component computation step of our proposed algorithm.
+We present functions  for computing $J^\ast$, $\Lambda$ and $\ddot{J}^\ast$ in sequence, and use these functions to define `get_constraint_matrix`.
 
 ### get_gram_matrix_block
-Equation (6) in Section 4.1
+Constructs a block-diagonal Gram matrix for a hybrid predictor object, defined as 
 $$
@@
 where
-$J^{(k)}$ is the $M \times M$ matrix with $(m,n)$-th entry equal to $\int_{\mathcal{T}_k} b_m^{(k)}(t) b_n^{(k)}(t) dt$, and $J = \mathrm{blkdiag}(J^{(1)}, \cdots, J^{(K)}) \in \mathbb{R}^{MK \times MK}$, and
-
+ $J = \mathrm{blkdiag}(J^{(1)}, \cdots, J^{(K)}) \in \mathbb{R}^{MK \times MK}$, and 
+$$
+J^{(k)} = \left[ \int_{\mathcal{T}k} b_m^{(k)}(t) , b_n^{(k)}(t) , dt \right]_{m,n=1}^M,
+$$
+as defined in \eqref{def:gram_basis} and \eqref{def:J_and_J_star}.
+
+- Arguments
+  - obj: A `predictor_hybrid` object containing both functional and scalar components.
+
+- Value
+  - A Matrix::bdiag sparse matrix representing the block-diagonal structure of the combined Gram matrix.
+
+- Details: This function builds a block-diagonal matrix by:
+  - Stacking the Gram matrices of each functional component (from obj$gram_list),
+  - Appending an identity matrix of size equal to the number of scalar predictors (to represent unpenalized scalar covariates).
+  The resulting matrix has size $(\texttt{total_dim} \times \texttt{total_dim})$, where total_dim = \sum_k M_k + p, with $M_k$ the number of basis functions for the $k$-th functional predictor and $p$ the number of scalar covariates.
+
+- Usage
+```r
+block_gram <- get_gram_matrix_block(my_predictor)
+```
+
+**Code**
 ```{r}
@@
 }
+
+```
+
+**Unit test**
+```{r}
+testthat::test_that("get_gram_matrix_block constructs correct block-diagonal matrix", {
+  suppressPackageStartupMessages(library(fda))
+  suppressPackageStartupMessages(library(Matrix))
+
+  # Construct hybrid predictor with two functional and three scalar predictors
+  basis1 <- create.bspline.basis(c(0, 1), nbasis = 4)
+  basis2 <- create.bspline.basis(c(0, 1), nbasis = 4)  # was 3; now valid
+
+  fd1 <- fd(coef = matrix(1, 4, 2), basisobj = basis1)
+  fd2 <- fd(coef = matrix(2, 4, 2), basisobj = basis2)
+  Z <- matrix(rnorm(2 * 3), nrow = 2, ncol = 3)
+
+  obj <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
+
+  # Extract the block-diagonal Gram matrix
+  G <- get_gram_matrix_block(obj)
+
+  # Expected block sizes
+  nb1 <- 4
+  nb2 <- 4
+  ns <- 3
+  total_dim <- nb1 + nb2 + ns
+
+  # Check matrix properties
+  testthat::expect_equal(dim(G), c(total_dim, total_dim))
+
+  # Check sub-block structure
+  # Top-left: Gram matrix 1
+  testthat::expect_equal(sum(G[1:nb1, 1:nb1]-obj$gram_list[[1]]), 0)
+
+  # Next block: Gram matrix 2
+  testthat::expect_equal(sum( G[(nb1 + 1):(nb1 + nb2), (nb1 + 1):(nb1 + nb2)]-obj$gram_list[[2]]),0 )
+
+  # Final block: identity matrix for scalar part
+  testthat::expect_equal( sum( G[(nb1 + nb2 + 1):total_dim, (nb1 + nb2 + 1):total_dim]  - diag(ns)), 0)
+})
+
+```
+### get_smoothing_param_hybrid
+Constructs a block-diagonal smoothing parameter matrix for use in penalized estimation involving hybrid predictors, denoted $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$,  defined in \eqref{def:Lambda} as
+$$
+   \Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
+$$
+
+- Arguments
+  - W: A predictor_hybrid object.
+  - lambda: A numeric vector of length equal to the number of functional predictors. Each entry corresponds to a smoothing penalty weight.
+- Value: A sparse block-diagonal matrix combining scaled identity matrices for the functional parts and a zero matrix for the scalar part.
+- Details: This function generates a matrix used in regularized regression for functional predictors.
+Each functional component is penalized using a scaled identity matrix of its basis dimension.
+Scalar predictors are unpenalized.
+- Usage:
+```r
+lambda_mat <- get_smoothing_param_hybrid(my_predictor, c(0.1, 0.2))
+```
+**code** 
+```{r}
+#' Construct block-diagonal smoothing parameter matrix
+#'
+#' Generates a block-diagonal matrix with smoothing parameters applied to each 
+#' functional component. Each block is a scaled identity matrix, where the scaling 
+#' factor corresponds to the regularization parameter for that functional component. 
+#' The scalar components are not penalized and thus contribute a zero matrix block.
+#'
+#' @param W A `predictor_hybrid` object.
+#' @param lambda A numeric vector of length equal to the number of functional components (`W$n_functional`), containing the smoothing parameters for each functional predictor.
+#'
+#' @return A block-diagonal matrix of size `(total_dim × total_dim)`, where the top-left blocks are scaled identity matrices for functional predictors and the bottom-right block is a zero matrix for scalar covariates.
+#' @export
+get_smoothing_param_hybrid <- function(W, lambda) {
+  if (!inherits(W, "predictor_hybrid")) {
+    stop("Input W must be of class 'predictor_hybrid'.")
+  }
+
+  if (length(lambda) != W$n_functional) {
+    stop("Length of lambda must match the number of functional predictors.")
+  }
+
+  lambda_blocks <- lapply(seq_len(W$n_functional), function(ii) {
+    nb <- W$functional_list[[ii]]$basis$nbasis
+    lambda[ii] * diag(nb)
+  })
+
+  lambda_blocks[[W$n_functional + 1]] <- matrix(0, nrow = W$n_scalar, ncol = W$n_scalar)
+
+  Matrix::bdiag(lambda_blocks)
+}
+```
+
+**unit test**
+```{r}
+testthat::test_that("get_smoothing_param_hybrid returns correct block-diagonal structure", {
+  suppressPackageStartupMessages(library(fda))
+  basis1 <- create.bspline.basis(c(0, 1), nbasis = 5)
+  basis2 <- create.bspline.basis(c(0, 1), nbasis = 4)
+
+  fd1 <- fd(coef = matrix(1, 5, 3), basisobj = basis1)
+  fd2 <- fd(coef = matrix(2, 4, 3), basisobj = basis2)
+
+  Z <- matrix(1, nrow = 3, ncol = 2)
+
+  obj <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
+  lambda <- c(0.5, 2)
+
+  lambda_mat <- get_smoothing_param_hybrid(obj, lambda)
+
+  # Check overall dimension
+  expected_dim <- sum(obj$n_basis_list) + obj$n_scalar
+  testthat::expect_equal(dim(lambda_mat), c(expected_dim, expected_dim))
+
+  # Check diagonal entries
+  testthat::expect_equal(Matrix::diag(lambda_mat)[1:5], rep(0.5, 5))
+  testthat::expect_equal(Matrix::diag(lambda_mat)[6:9], rep(2, 4))
+  testthat::expect_equal(Matrix::diag(lambda_mat)[10:11], rep(0, 2))  # scalar part
+})
 
@@
 
-###
-```{r}
-get_smoothing_param_hybrid <- function(W, lambda){
-  #lambda: list of length K (=n_functional)
-  lambda_mat <- lambda[1] * diag(W@functional_list[[1]]$basis$nbasis)
-  for (ii in 2:(W@n_functional)){
-    n_basis_now <- dim(W@jacobian_list[[ii]])[2]
-    lambda_mat <- bdiag(
-      lambda_mat,
-      lambda[ii] * diag(W@functional_list[[ii]]$basis$nbasis)
-    )
-      }
-  lambda_mat <- bdiag(
-    lambda_mat,
-    matrix(0, nrow = W@n_scalar, ncol = W@n_scalar)
-  )
-}
-
-```
-
+### get_constraint_matrix
+
+```r
+W <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
+lambda <- c(0.1, 0.2)
+constraint_matrix <- get_constraint_matrix_hybrid(W, lambda)
+```
+
+**code**
+```{r}
+#' Construct penalized constraint matrix for hybrid predictors
+#'
+#' Computes the denominator matrix used in penalized estimation for hybrid predictors,
+#' combining the Gram matrix, smoothing parameter matrix, and penalty matrix.
+#'
+#' Specifically, this function returns the matrix:
+#' \deqn{J^\ast + \Lambda \ddot{J}^\ast}
+#' where \eqn{J^\ast} is the block-diagonal Gram matrix,
+#' \eqn{\Lambda} is the block-diagonal smoothing parameter matrix,
+#' and \eqn{\ddot{J}^\ast} is the block-diagonal penalty matrix of second derivative inner products.
+#'
+#' @param W A `predictor_hybrid` object.
+#' @param lambda A numeric vector of smoothing parameters, one for each functional predictor.
+#'
+#' @return A matrix representing the penalized constraint matrix used in estimation.
+#' @export
+get_constraint_matrix_hybrid <- function(W, lambda) {
+  J_star <- get_gram_matrix_block(W)
+  J_dotdot_star <- get_penalty_hybrid(W)
+  lambda_mat <- get_smoothing_param_hybrid(W, lambda)
+
+  J_star + lambda_mat %*% J_dotdot_star
+}
+
+```
+
+## asd
 ### get_pre_corrcov
@@
 
-## get_pls_comp
-
-```{r}
-get_pls_comp <- function(W, y, L, verbose){
-  # W: hybrid predictor
-  # y: response vector
-  # L: regularization hyperparameter
-
-  V_star <- get_pre_corrcov(W, y)
-  #Last paragraph of section 3.2. To solve (6) in practice...
-  #A <- t(solve(L, t(V_star))) # A = V* t(inv(L))
-  #E <- solve(L, A) # E = inv(L) A
-
-  invL <- Matrix::chol2inv(L)
-  A <- V_star %*% t(invL) # A = V* t(inv(L))
-  E <- invL %*% A # E = inv(L) A
-
-  eigen_result <- eigen(E)
-  #cat("eigenvalues: ", eigen_result$values)
-  e <- eigen_result$vectors[, 1]
-  if(is.complex(e)){
-    return("stop")
-  }
-  #e <- e / Matrix::norm(e, "2") #normalize; omitted by request of Dr. Jang
-  #xi_star <- solve(t(L), e) # t(L) xi* = e, basis coefficient of estimated PLS component
-  xi_star <- t(invL) %*% e
-  xi_hat <- hybrid_from_coef(format = W, xi_star = xi_star) #estimated PLS component
-  return(
-    list(
-      xi_hat = xi_hat,
-      E = E,
-      V_star = V_star,
-      eigen_val = eigen_result$values[1]
-      )
-  )
-  }
-```
-
-```{r}
-nipals_pen_hybrid <- function(W, y, n_iter, lambda, verbose) {
-  # 1. initialize the storage
-  rho <- xi <- delta <- nu  <- sigma <- eta <- list()
-  E <- V_star <- eigen_val <-list()
-  fitted_value_W <- fitted_value_y <-list()
-  resid_y <- W_now <- list() #data for iteration
-  first_eigen_val <- mse_W <- mse_y <-rep(NA, n_iter)
-
-  # 2. constraint matrix is the same at every iteration
-  J_star          <- get_gram_matrix_block(W)
-  J_dotdot_star   <- get_penalty_hybrid(W)
-  lambda_mat      <- get_smoothing_param_hybrid(W, lambda)
-  constr_mat      <- J_star + (lambda_mat %*% J_dotdot_star) # denominator in the equation (6)
-  constr_mat_chol <- t(chol(constr_mat))
-
-  W_now[[1]] <- W
-  y_now <- y
-  final_succesful_iteration <- 0
-  for (l in 1:n_iter) {
-    #cat(paste("#############################################", "\n"))
-    if(verbose==T)cat(paste(l, "th component", "\n"))
-
-    # STEP 1. calculate pls score
-    pls_result_now <- get_pls_comp(W_now[[l]], y_now, constr_mat_chol, verbose)
-    if(!is.list(pls_result_now)){break}
-
-    xi[[l]] <- pls_result_now$xi # pls component. Section 3.2
-    rho[[l]] <- hybrid_inner_prod(W_now[[l]], xi[[l]]) # pls scores : n_sample * 1 matrix
-
-    # STEP 2. residulize
-    # residualize predictor: hybrid (W) on scalar (rho) linear regression with n_sample observations
-    delta[[l]] <- LSE_hybrid(W_now[[l]], rho[[l]]) #single obs of hybrid predictor
-
-    fitted_value_W[[l]] <- fitted_value(delta[[l]], rho[[l]])
-    W_now[[l+1]] <- subtr(W_now[[l]], fitted_value_W[[l]])
-    # residualize resoponse
-    nu[[l]] <- LSE_ptws(y_now, rho[[l]]) #scalar on scalar linear regression with n_sample observations
-    fitted_value_y[[l]] <- nu[[l]] * rho[[l]]
-    y_now <- y_now - fitted_value_y[[l]]
-    resid_y[[l]] <- y_now
-
-    #check mean norm
-    #mse_W[l] <- mean_sum_sqrd(W_now[[l]])
-    #mse_y[l] <- norm(y_now,"2")
-
-    #cat("W:", mse_W[l], "\n")
-    #cat("y:",  mse_y[l], "\n\n")
-
-    # STEP 3.
-    sigma[[l]] <- xi[[l]]
-    if (l == 1) {
-      eta[[l]] <- scalar_mul(sigma[[l]], nu[[l]])
-    }else{ # if l > 1
-      for (u in 1:(l - 1)){
-        sigma[[l]] <- subtr( sigma[[l]], sigma[[u]], hybrid_inner_prod(delta[[u]], xi[[l]]) )
-      } #end of u-loop
-      eta[[l]] <- add(eta[[l-1]], sigma[[l]], nu[[l]])
-    }#if statement
-
-    # just for records.
-    E[[l]] <- pls_result_now$E # for monitoring symetricity
-    V_star[[l]] <- pls_result_now$V_star
-    eigen_val[[l]] <- pls_result_now$eigen_val
-    first_eigen_val[l] <- eigen_val[[l]][1]
-    final_succesful_iteration <- l
-  }# for loop: l
-}
-```
-
 ## Documenting the package and building

### 2025-06-05 FSHybridPLS/R/compute_gram_matrix.R

@@ -1,4 +1,4 @@
-# Generated from create-rhello.Rmd: do not edit by hand
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
 
 #' Compute the Gram matrix for a basis object
 #'

### 2025-06-05 FSHybridPLS/R/get_constraint_matrix_hybrid.R

@@ -1,0 +1,26 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Construct penalized constraint matrix for hybrid predictors
+#'
+#' Computes the denominator matrix used in penalized estimation for hybrid predictors,
+#' combining the Gram matrix, smoothing parameter matrix, and penalty matrix.
+#'
+#' Specifically, this function returns the matrix:
+#' \deqn{J^\ast + \Lambda \ddot{J}^\ast}
+#' where \eqn{J^\ast} is the block-diagonal Gram matrix,
+#' \eqn{\Lambda} is the block-diagonal smoothing parameter matrix,
+#' and \eqn{\ddot{J}^\ast} is the block-diagonal penalty matrix of second derivative inner products.
+#'
+#' @param W A `predictor_hybrid` object.
+#' @param lambda A numeric vector of smoothing parameters, one for each functional predictor.
+#'
+#' @return A matrix representing the penalized constraint matrix used in estimation.
+#' @export
+get_constraint_matrix_hybrid <- function(W, lambda) {
+  J_star <- get_gram_matrix_block(W)
+  J_dotdot_star <- get_penalty_hybrid(W)
+  lambda_mat <- get_smoothing_param_hybrid(W, lambda)
+
+  J_star + lambda_mat %*% J_dotdot_star
+}
+

### 2025-06-05 FSHybridPLS/R/get_gram_matrix_block.R

@@ -1,0 +1,21 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Construct block-diagonal Gram matrix for hybrid predictor
+#'
+#' Returns a block-diagonal matrix containing the Gram  matrices for
+#' each functional component and an identity matrix for the scalar part.
+#'
+#' @param obj A `predictor_hybrid` object.
+#'
+#' @return A block-diagonal matrix of size `(total_dim × total_dim)` where
+#' functional and scalar components are arranged in order.
+#' @export
+get_gram_matrix_block <- function(obj) {
+  if (!inherits(obj, "predictor_hybrid")) {
+    stop("Input must be of class 'predictor_hybrid'.")
+  }
+
+  gram_blocks <- c(obj$gram_list, list(diag(obj$n_scalar)))
+  Matrix::bdiag(gram_blocks)
+}
+

### 2025-06-05 FSHybridPLS/R/get_penalty_hybrid.R

@@ -1,0 +1,25 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Construct the roughness penalty matrix for a predictor_hybrid object
+#'
+#' Returns a block diagonal matrix representing roughness penalties for each functional predictor
+#' and zeros for the scalar predictors (scalar predictors are not penalized). Each functional component uses its own basis penalty matrix, computed via second derivative penalty via `getbasispenalty()` from the `fda` package
+#'
+#' @param W A `predictor_hybrid` object.
+#'
+#' @return A block diagonal penalty matrix of dimension `(sum(n_basis_list) + n_scalar)^2`.
+#' @export
+get_penalty_hybrid <- function(W){
+  J_dotdot_star <- fda::getbasispenalty(W$functional_list[[1]]$basis)
+  for (ii in 2:(W$n_functional)){
+    J_dotdot_star <- Matrix::bdiag(
+      J_dotdot_star,
+      fda::getbasispenalty(W$functional_list[[ii]]$basis)
+    )
+    }
+  J_dotdot_star <- Matrix::bdiag(
+    J_dotdot_star,
+    matrix(0, nrow = W$n_scalar, ncol = W$n_scalar)
+    )
+  return(J_dotdot_star)
+  }

### 2025-06-05 FSHybridPLS/R/get_pre_corrcov.R

@@ -1,0 +1,46 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Compute V matrix (pre-corrected covariance estimator)
+#'
+#' Constructs the V matrix involving inner products of functional predictors
+#' (weighted by their Gram matrices) and scalar predictors against response y.
+#'
+#' @param W A `predictor_hybrid` object.
+#' @param y A numeric response vector of length equal to number of samples.
+#'
+#' @return A matrix representing the corrected cross-covariance structure.
+#' @export
+get_pre_corrcov <- function(W, y){
+  n <- W$n_sample
+  K <- W$n_functional
+
+  # building blocks
+  ## C_J : C multiplied by J. Scalable to arbitrary K
+  predictor_first <- W$functional_list[[1]]
+  C_J <- t(predictor_first$coefs) %*% W$gram_list[[1]]
+  for (i in 2:K){
+    predictor_now <- W$functional_list[[i]]
+    C_J <- cbind(
+      C_J,
+      t(predictor_now$coefs) %*% W$gram_list[[i]]
+    )
+    }
+
+  
+  ## covariance
+  J_Ct_y <- t(C_J) %*% y
+  Zt_y <- t(W$Z) %*% y
+
+  # V matrix
+  upper_left <- J_Ct_y %*% t(J_Ct_y)
+  upper_right <- J_Ct_y %*% t(Zt_y)
+  lower_left <- t(upper_right)
+  lower_right <- Zt_y %*% t(Zt_y)
+
+  V_star <- cbind(
+    rbind(upper_left, lower_left),
+    rbind(upper_right, lower_right)
+    )/(n^2)
+
+  return(V_star)
+  }

### 2025-06-05 FSHybridPLS/R/get_smoothing_param_hybrid.R

@@ -1,0 +1,32 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Construct block-diagonal smoothing parameter matrix
+#'
+#' Generates a block-diagonal matrix with smoothing parameters applied to each 
+#' functional component. Each block is a scaled identity matrix, where the scaling 
+#' factor corresponds to the regularization parameter for that functional component. 
+#' The scalar components are not penalized and thus contribute a zero matrix block.
+#'
+#' @param W A `predictor_hybrid` object.
+#' @param lambda A numeric vector of length equal to the number of functional components (`W$n_functional`), containing the smoothing parameters for each functional predictor.
+#'
+#' @return A block-diagonal matrix of size `(total_dim × total_dim)`, where the top-left blocks are scaled identity matrices for functional predictors and the bottom-right block is a zero matrix for scalar covariates.
+#' @export
+get_smoothing_param_hybrid <- function(W, lambda) {
+  if (!inherits(W, "predictor_hybrid")) {
+    stop("Input W must be of class 'predictor_hybrid'.")
+  }
+
+  if (length(lambda) != W$n_functional) {
+    stop("Length of lambda must match the number of functional predictors.")
+  }
+
+  lambda_blocks <- lapply(seq_len(W$n_functional), function(ii) {
+    nb <- W$functional_list[[ii]]$basis$nbasis
+    lambda[ii] * diag(nb)
+  })
+
+  lambda_blocks[[W$n_functional + 1]] <- matrix(0, nrow = W$n_scalar, ncol = W$n_scalar)
+
+  Matrix::bdiag(lambda_blocks)
+}

### 2025-06-05 FSHybridPLS/R/inprod.predictor_hybrid.R

@@ -1,4 +1,4 @@
-# Generated from create-rhello.Rmd: do not edit by hand
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
 
 #' Inner product between two predictor_hybrid objects (with broadcasting)
 #'
@@ -51,7 +51,7 @@ inprod.predictor_hybrid <- function(xi_1, xi_2 = NULL) {
   # Replicate fd and Z if needed
   if (n2 == 1) {
     f2 <- rep_fd(f2, n1)
-    Z2 <- matrix(rep(Z2, each = n1), nrow = n1, byrow = TRUE)
+    Z2 <- matrix(rep(c(Z2), n1), nrow = n1, byrow = TRUE)
   }
 
   # Compute functional inner products
@@ -60,10 +60,11 @@ inprod.predictor_hybrid <- function(xi_1, xi_2 = NULL) {
       fda::inprod(f1[[j]][i], f2[[j]][i])
     }, numeric(1)))
   }, numeric(1))
+ 
 
   # Compute scalar inner products
-  inprod_scalar <- rowSums(Z1 * Z2)
-
+  inprod_scalar <- rowSums(Z1 * Z2) 
+ 
   # Combine results
   result <- inprod_functional + inprod_scalar
   if (n1 == 1 && n2 == 1) as.numeric(result) else result

### 2025-06-05 FSHybridPLS/R/is_same_basis.R

@@ -1,4 +1,4 @@
-# Generated from create-rhello.Rmd: do not edit by hand
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
 
 #' @export
 is_same_basis <- function(input, other) {

### 2025-06-05 FSHybridPLS/R/predictor_hybrid_from_coef.R

@@ -1,0 +1,28 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Construct a Single-Sample Predictor Hybrid Object from Coefficients
+#'
+#' Reconstructs a \code{predictor_hybrid} object representing one observation, using a numeric
+#' coefficient vector. This alternative constructor maps the coefficients back into their functional
+#' and scalar predictor representations based on the structure of a template \code{predictor_hybrid} object.
+#'
+#' @param format A \code{predictor_hybrid} object that provides the structure and basis information.
+#' @param coef A numeric vector containing coefficients for both functional and scalar predictors.
+#'
+#' @return A \code{predictor_hybrid} object with updated \code{functional_list}, \code{Z}, and \code{n_sample = 1}.
+#'
+#'
+#' @export
+predictor_hybrid_from_coef <- function(format, coef){
+  M <- dim(format$gram_list[[1]])[2] # number of basis functions
+  K <- length(format$functional_list) # number of functional predictors
+  for (ii in 1:K){
+    format$functional_list[[ii]] <- fd(
+      coef = as.matrix(coef[((ii-1)*M + 1):(ii*M)]),
+      basisobj = format$functional_list[[ii]]$basis
+    )
+  }
+  format$Z <- t(as.matrix(coef[(K * M + 1):length(coef)]))
+  format$n_sample <- 1
+  return(format)
+}

### 2025-06-05 FSHybridPLS/R/rep_fd.R

@@ -1,4 +1,4 @@
-# Generated from create-rhello.Rmd: do not edit by hand
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
 
 #' Replicate a list of single-sample fd objects multiple times
 #'

### 2025-06-05 FSHybridPLS/R/scalar_mul.predictor_hybrid.R

@@ -1,4 +1,4 @@
-# Generated from create-rhello.Rmd: do not edit by hand
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
 
 #' Multiply a predictor_hybrid object by a scalar
 #'

### 2025-06-05 FSHybridPLS/R/subtr.predictor_hybrid.R

@@ -1,4 +1,4 @@
-# Generated from create-rhello.Rmd: do not edit by hand
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
 
 #' Subtract two predictor_hybrid objects
 #'

### 2025-06-05 FSHybridPLS/tests/testthat/tests.R

@@ -1,4 +1,4 @@
-# Generated from create-rhello.Rmd: do not edit by hand  
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand  
 testthat::test_that("Gram matrix edge cases", {
   suppressPackageStartupMessages(library(fda))
 
@@ -91,6 +91,41 @@ testthat::test_that("predictor_hybrid constructor works as expected (S3, updated
   testthat::expect_equal(dim(obj$gram_list[[1]]), c(10, 10))
   testthat::expect_equal(dim(obj$gram_list[[2]]), c(20, 20))
 })
+
+testthat::test_that("hybrid_from_coef reconstructs single-sample predictor_hybrid correctly", {
+  suppressPackageStartupMessages(library(fda))
+
+  make_fd <- function(coefs, basis) {
+    fd(coef = coefs, basisobj = basis)
+  }
+
+  basis <- create.bspline.basis(c(0, 1), nbasis = 4)
+  n_sample <- 5
+  n_scalar <- 2
+  n_functional <- 2
+
+  # Create dummy functional list with zeros
+  fd1 <- make_fd(matrix(0, 4, n_sample), basis)
+  fd2 <- make_fd(matrix(0, 4, n_sample), basis)
+  Z <- matrix(0, n_sample, n_scalar)
+  obj_template <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
+
+  # Create coefficient vector for reconstruction: 4 + 4 + 2 = 10
+  xi_star <- c(1:10)
+
+  # Apply reconstruction
+  obj_single <- predictor_hybrid_from_coef(obj_template, xi_star)
+
+  # Checks
+  testthat::expect_s3_class(obj_single, "predictor_hybrid")
+  testthat::expect_equal(obj_single$n_sample, 1)
+  testthat::expect_equal(obj_single$Z, matrix(c(9, 10), nrow = 1))
+
+  # Check functional coefficients (use coef() not $coefs)
+  testthat::expect_equal(drop(coef(obj_single$functional_list[[1]])), 1:4)
+  testthat::expect_equal(drop(coef(obj_single$functional_list[[2]])), 5:8)
+})
+
 
 testthat::test_that("add.predictor_hybrid handles broadcasting and basis compatibility", {
[…]

### 2025-06-05 create-FSHybridPLS.Rmd
nipals first step done

@@
 
+## PLS component computation
+
+### get_pls_comp
+Computes the first PLS component from a hybrid predictor and response vector using regularization.
+
+- Inputs
+  - **`W`**: A `predictor_hybrid` object with functional and scalar predictors.
+  - **`y`**: A numeric response vector of length equal to `W$n_sample`.
+  - **`L`**: A Cholesky decomposition of a positive definite regularization matrix.
+- Output: 
+  - `xi_hat`: The first PLS component as a `predictor_hybrid` object
+  - `E`: The matrix `inv(L) %*% V_star %*% t(inv(L))`
+  - `V_star`: Cross-covariance matrix between predictors and response
+  - `eigen_val`: Leading eigenvalue of `E`
+```{r}
+#' Compute the First PLS Component from a Hybrid Predictor
+#'
+#' Computes the coefficients of the first Partial Least Squares (PLS) component based on 
+#' a hybrid predictor object and a response vector, using a regularized generalized eigenvalue problem.
+#'
+#' @param W A \code{predictor_hybrid} object containing both functional and scalar predictors.
+#' @param y A numeric response vector of length equal to the number of samples in \code{W}.
+#' @param L cholesky decompisition of a regularization matrix (typically positive definite) used in the generalized eigenproblem.
+#'
+#' @return A list with the following elements:
+#' \describe{
+#'   \item{\code{xi_hat}}{The estimated first PLS component as a \code{predictor_hybrid} object.}
+#'   \item{\code{E}}{The generalized eigenvalue problem matrix \code{E = inv(L) V* t(inv(L))}.}
+#'   \item{\code{V_star}}{The cross-covariance matrix between predictors and response.}
+#'   \item{\code{eigen_val}}{The leading eigenvalue of \code{E}.}
+#' }
+#'
+#' @export
+get_pls_comp <- function(W, y, L){
+
+  V_star <- get_pre_corrcov(W, y)
+
+  invL <- Matrix::chol2inv(L)
+  A <- V_star %*% t(invL)       # A = V* × t(inv(L))
+  E <- invL %*% A               # E = inv(L) × A
+
+  eigen_result <- eigen(E)
+  e <- eigen_result$vectors[, 1]
+  if (is.complex(e)){
+    print("stop")
+    return("stop")
+  }
+
+  xi_star <- t(invL) %*% e      # xi_star solves t(L) xi = e
+  xi_hat <- predictor_hybrid_from_coef(format = W, coef = xi_star)
+
+  return(list(
+    xi_hat = xi_hat,
+    E = E,
+    V_star = V_star,
+    eigen_val = eigen_result$values[1]
+  ))
+}
+```
+
+```{r}
+suppressPackageStartupMessages({
+  library(fda)
+  library(Matrix)
+  library(ggplot2)
+})
+
+# --- Helper: Generate realistic smooth functional data ---
+generate_fd_data <- function(n_sample, nbasis, freq = 1) {
+  basis <- create.bspline.basis(c(0, 1), nbasis = nbasis, norder = 4)
+  time_points <- seq(0, 1, length.out = nbasis)
+  coefs <- outer(1:nbasis, 1:n_sample, function(i, j) {
+    sin(freq * pi * time_points[i]) + rnorm(1, sd = 0.1)
+  })
+  fd(coef = coefs, basisobj = basis)
+}
+
+# --- Settings ---
+set.seed(20250604)
+n_sample <- 200
+n_scalar <- 10
+n_functional <- 2
+nbasis_vals <- c(4,8,12,16,20)
+lambda_vals <- c(0, 1e-8, 1e-6, 1e-4, 1e-2, 1, 10)
+
+results <- data.frame()
+
+# --- Experiment Loop ---
+for (nbasis in nbasis_vals) {
+  for (lambda in lambda_vals) {
+    cat("Trying nbasis =", nbasis, ", lambda =", lambda, "\n")
+
+    # Generate functional predictors
+    fd1 <- generate_fd_data(n_sample, nbasis, freq = 1)
+    fd2 <- generate_fd_data(n_sample, nbasis, freq = 2)
+    Z <- matrix(rnorm(n_sample * n_scalar), n_sample, n_scalar)
+    y <- rnorm(n_sample)
+
+    W <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
+    lambda_vec <- rep(lambda, n_functional)
+
+    # Try to compute constraint matrix L
+    L <- get_constraint_matrix_hybrid(W, lambda_vec)
+    constr_mat_chol <- t(chol(L))  # <-- do not change this
+
+    # Time the PLS computation
+    elapsed <- system.time({
+      out <- tryCatch({
+        pls <- get_pls_comp(W, y, constr_mat_chol)
+
+        if (!is.list(pls) || (is.character(pls) && pls == "stop")) {
+          data.frame(
+            nbasis = nbasis,
+            lambda = lambda,
+            eigen_val = NA,
+            is_real = FALSE,
+            reason = "stop (complex eigenvector)",
+            time_sec = NA_real_
+          )
+        } else {
+          data.frame(
+            nbasis = nbasis,
+            lambda = lambda,
+            eigen_val = Re(pls$eigen_val),
+            is_real = TRUE,
+            reason = "success",
+            time_sec = NA_real_  # placeholder, will update below
+          )
+        }
+      }, error = function(e) {
+        data.frame(
+          nbasis = nbasis,
+          lambda = lambda,
+          eigen_val = NA,
+          is_real = FALSE,
+          reason = "error in get_pls_comp",
+          time_sec = NA_real_
+        )
+      })
+    })
+
+    out$time_sec <- elapsed["elapsed"]
+    results <- rbind(results, out)
+  }
+}
+
+# --- Print successful configurations ---
+cat("\n✅ Successful runs with real eigenvalues:\n")
+print(subset(results, is_real == TRUE))
+
+# --- Fastest and slowest ---
+cat("\n⏱️ Top 5 fastest settings:\n")
+print(head(results[order(results$time_sec), ], 5))
+
+cat("\n🐢 Top 5 slowest settings:\n")
+print(tail(results[order(results$time_sec), ], 5))
+
+# --- Visualize success/failure ---
+ggplot(results, aes(x = nbasis, y = lambda, fill = reason)) +
+  geom_tile(color = "white") +
+  scale_y_log10() +
+  scale_fill_manual(values = c(
+    "success" = "green",
+    "stop (complex eigenvector)" = "orange",
+    "error in get_constraint_matrix_hybrid" = "red",
+    "error in get_pls_comp" = "darkred"
+  )) +
+  labs(
+    title = "get_pls_comp Outcomes: λ vs. # Basis Functions",
+    x = "# of Basis Functions",
+    y = "Smoothing Parameter λ (log scale)",
+    fill = "Result Type"
+  )
+
+```
+
+#
+
+```{r eval=FALSE, include=FALSE}
+nipals_pen_hybrid <- function(W, y, n_iter, lambda, verbose) {
+  # 1. initialize the storage
+  rho <- xi <- delta <- nu  <- sigma <- eta <- list()
+  E <- V_star <- eigen_val <-list()
+  fitted_value_W <- fitted_value_y <-list()
+  resid_y <- W_now <- list() #data for iteration
+  first_eigen_val <- mse_W <- mse_y <-rep(NA, n_iter)
+
+  # 2. constraint matrix is the same at every iteration
+  constr_mat      <- get_constraint_matrix_hybrid(W, lambda) 
+  constr_mat_chol <- t(chol(constr_mat))
+
+  W_now[[1]] <- W
+  y_now <- y
+  final_succesful_iteration <- 0
+  for (l in 1:n_iter) {
+    #cat(paste("#############################################", "\n"))
+    if(verbose==T)cat(paste(l, "th component", "\n"))
+
+    # STEP 1. calculate pls score
+    pls_result_now <- get_pls_comp(W_now[[l]], y_now, constr_mat_chol, verbose)
+    if(!is.list(pls_result_now)){break}
+
+    xi[[l]] <- pls_result_now$xi # pls component. Section 3.2
+    rho[[l]] <- hybrid_inner_prod(W_now[[l]], xi[[l]]) # pls scores : n_sample * 1 matrix
+
+    # STEP 2. residulize
+    # residualize predictor: hybrid (W) on scalar (rho) linear regression with n_sample observations
+    delta[[l]] <- LSE_hybrid(W_now[[l]], rho[[l]]) #single obs of hybrid predictor
+
+    fitted_value_W[[l]] <- fitted_value(delta[[l]], rho[[l]])
+    W_now[[l+1]] <- subtr(W_now[[l]], fitted_value_W[[l]])
+    # residualize resoponse
+    nu[[l]] <- LSE_ptws(y_now, rho[[l]]) #scalar on scalar linear regression with n_sample observations
+    fitted_value_y[[l]] <- nu[[l]] * rho[[l]]
+    y_now <- y_now - fitted_value_y[[l]]
+    resid_y[[l]] <- y_now
+
+    #check mean norm
+    #mse_W[l] <- mean_sum_sqrd(W_now[[l]])
+    #mse_y[l] <- norm(y_now,"2")
+
+    #cat("W:", mse_W[l], "\n")
+    #cat("y:",  mse_y[l], "\n\n")
+
+    # STEP 3.
+    sigma[[l]] <- xi[[l]]
+    if (l == 1) {
+      eta[[l]] <- scalar_mul(sigma[[l]], nu[[l]])
+    }else{ # if l > 1
+      for (u in 1:(l - 1)){
+        sigma[[l]] <- subtr( sigma[[l]], sigma[[u]], hybrid_inner_prod(delta[[u]], xi[[l]]) )
+      } #end of u-loop
+      eta[[l]] <- add(eta[[l-1]], sigma[[l]], nu[[l]])
+    }#if statement
+
+    # just for records.
+    E[[l]] <- pls_result_now$E # for monitoring symetricity
+    V_star[[l]] <- pls_result_now$V_star
+    eigen_val[[l]] <- pls_result_now$eigen_val
+    first_eigen_val[l] <- eigen_val[[l]][1]
+    final_succesful_iteration <- l
+  }# for loop: l
+}
+```
 ## Documenting the package and building

### 2025-06-05 FSHybridPLS/R/get_pls_comp.R

@@ -1,0 +1,45 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Compute the First PLS Component from a Hybrid Predictor
+#'
+#' Computes the coefficients of the first Partial Least Squares (PLS) component based on 
+#' a hybrid predictor object and a response vector, using a regularized generalized eigenvalue problem.
+#'
+#' @param W A \code{predictor_hybrid} object containing both functional and scalar predictors.
+#' @param y A numeric response vector of length equal to the number of samples in \code{W}.
+#' @param L A regularization matrix (typically positive definite) used in the generalized eigenproblem.
+#'
+#' @return A list with the following elements:
+#' \describe{
+#'   \item{\code{xi_hat}}{The estimated first PLS component as a \code{predictor_hybrid} object.}
+#'   \item{\code{E}}{The generalized eigenvalue problem matrix \code{E = inv(L) V* t(inv(L))}.}
+#'   \item{\code{V_star}}{The cross-covariance matrix between predictors and response.}
+#'   \item{\code{eigen_val}}{The leading eigenvalue of \code{E}.}
+#' }
+#'
+#' @export
+get_pls_comp <- function(W, y, L){
+  # W: hybrid predictor
+  # y: response vector
+  # L: regularization hyperparameter
+
+  V_star <- get_pre_corrcov(W, y)
+
+  invL <- Matrix::chol2inv(L)
+  A <- V_star %*% t(invL)       # A = V* × t(inv(L))
+  E <- invL %*% A               # E = inv(L) × A
+
+  eigen_result <- eigen(E)
+  e <- eigen_result$vectors[, 1]
+  if (is.complex(e)) return("stop")
+
+  xi_star <- t(invL) %*% e      # xi_star solves t(L) xi = e
+  xi_hat <- predictor_hybrid_from_coef(format = W, coef = xi_star)
+
+  return(list(
+    xi_hat = xi_hat,
+    E = E,
+    V_star = V_star,
+    eigen_val = eigen_result$values[1]
+  ))
+}

### 2025-06-05 FSHybridPLS/tests/testthat/tests.R

@@ -440,3 +440,53 @@ testthat::test_that("get_pre_corrcov handles constant and random coefficients", 
 })
 
 
+testthat::test_that("get_pls_comp runs and returns valid output with penalty-based L", {
+  suppressPackageStartupMessages(library(fda))
+  set.seed(123)
+
+  make_fd <- function(coefs, basis) {
+    fd(coef = coefs, basisobj = basis)
+  }
+
+  n_sample <- 10
+  n_scalar <- 2
+  n_functional <- 2
+
+  for (nbasis in c(3, 4, 5)) {
+    basis <- create.bspline.basis(c(0, 1), nbasis = nbasis)
+
+    # Functional predictors
+    fd1 <- make_fd(matrix(rnorm(nbasis * n_sample), nbasis, n_sample), basis)
+    fd2 <- make_fd(matrix(rnorm(nbasis * n_sample), nbasis, n_sample), basis)
+    functional_list <- list(fd1, fd2)
+
+    # Scalar predictors and response
+    Z <- matrix(rnorm(n_sample * n_scalar), n_sample, n_scalar)
+    y <- rnorm(n_sample)
+
+    # Construct hybrid predictor
+    W <- predictor_hybrid(Z = Z, functional_list = functional_list)
+
+    # Smoothing parameters
+    lambda <- rep(1e-2, n_functional)
+    L <- get_constraint_matrix_hybrid(W, lambda)
+
+    # Run and validate
+    result <- get_pls_comp(W, y, L)
+
+    # Structure check
+    expect_type(result, "list")
+    expect_named(result, c("xi_hat", "E", "V_star", "eigen_val"))
+
+    # Component checks
+    expect_s3_class(result$xi_hat, "predictor_hybrid")
+    expect_true(is.matrix(result$E))
+    expect_true(is.matrix(result$V_star))
+    expect_true(is.numeric(result$eigen_val))
+    expect_length(result$eigen_val, 1)
+    expect_false(is.complex(result$eigen_val))
+  }
+})
+
+
+

### 2025-06-05 create-FSHybridPLS.Rmd
nipals commented
and improved a little bit

@@
 ```{r eval=FALSE, include=FALSE}
+#' Iterative Penalized NIPALS Algorithm for Hybrid PLS
+#'
+#' Performs iterative extraction of PLS components using a penalized NIPALS algorithm
+#' for hybrid predictor objects that include both scalar and functional data.
+#'
+#' At each iteration:
+#' \enumerate{
+#'   \item Computes the first penalized PLS component using \code{get_pls_comp}.
+#'   \item Computes PLS scores via hybrid inner products.
+#'   \item Residualizes both predictors and response with respect to the extracted scores.
+#'   \item Orthogonalizes and accumulates loading vectors to construct final linear predictors.
+#' }
+#' The same constraint matrix (computed once) is used across all iterations.
+#'
+#' @param W A \code{predictor_hybrid} object containing scalar and functional predictors.
+#' @param y A numeric response vector of length equal to \code{W$n_sample}.
+#' @param n_iter An integer specifying the number of PLS components (iterations) to compute.
+#' @param lambda A numeric vector of smoothing parameters (length = number of functional predictors).
+#' @param verbose Logical; if \code{TRUE}, prints progress for each component.
+#'
+#' @return This function operates by side effects. Internally, it constructs and updates:
+#' \itemize{
+#'   \item \code{xi}, \code{rho}, \code{delta}, \code{nu}: component vectors and regression effects,
+#'   \item \code{sigma}, \code{eta}: orthogonalized components and accumulated prediction functions,
+#'   \item \code{W_now}, \code{resid_y}: residualized predictor and response at each iteration,
+#'   \item \code{E}, \code{V_star}, \code{eigen_val}: matrices for monitoring stability and eigenvalue progress.
+#' }
+#' The final number of successful iterations is tracked via \code{final_succesful_iteration}.
+#'
+#' @export
 nipals_pen_hybrid <- function(W, y, n_iter, lambda, verbose) {
-  # 1. initialize the storage
+  # 1. Initialize storage
   rho <- xi <- delta <- nu  <- sigma <- eta <- list()
-  E <- V_star <- eigen_val <-list()
-  fitted_value_W <- fitted_value_y <-list()
-  resid_y <- W_now <- list() #data for iteration
-  first_eigen_val <- mse_W <- mse_y <-rep(NA, n_iter)
-
-  # 2. constraint matrix is the same at every iteration
+  E <- V_star <- eigen_val <- list()
+  fitted_value_W <- fitted_value_y <- list()
+  resid_y <- W_now <- list()
+  first_eigen_val <- mse_W <- mse_y <- rep(NA, n_iter)
+
+  # 2. Compute and store the constraint matrix once
   constr_mat <- get_constraint_matrix_hybrid(W, lambda)
@@
 
+  # 3. Initialize residuals
   W_now[[1]] <- W
@@
   final_succesful_iteration <- 0
+
   for (l in 1:n_iter) {
-    #cat(paste("#############################################", "\n"))
-    if(verbose==T)cat(paste(l, "th component", "\n"))
-
-    # STEP 1. calculate pls score
+    if (verbose) cat(paste(l, "th component", "\n"))
+
+    # Step 1: Compute penalized PLS direction and score
     pls_result_now <- get_pls_comp(W_now[[l]], y_now, constr_mat_chol, verbose)
-    if(!is.list(pls_result_now)){break}
-
-    xi[[l]] <- pls_result_now$xi # pls component. Section 3.2
-    rho[[l]] <- hybrid_inner_prod(W_now[[l]], xi[[l]]) # pls scores : n_sample * 1 matrix
-
-    # STEP 2. residulize
-    # residualize predictor: hybrid (W) on scalar (rho) linear regression with n_sample observations
-    delta[[l]] <- LSE_hybrid(W_now[[l]], rho[[l]]) #single obs of hybrid predictor
-
+    if (!is.list(pls_result_now)) break
+
+    xi[[l]] <- pls_result_now$xi
+    rho[[l]] <- hybrid_inner_prod(W_now[[l]], xi[[l]])
+
+    # Step 2: Residualize predictor and response
+    delta[[l]] <- LSE_hybrid(W_now[[l]], rho[[l]])
     fitted_value_W[[l]] <- fitted_value(delta[[l]], rho[[l]])
-    W_now[[l+1]] <- subtr(W_now[[l]], fitted_value_W[[l]])
-    # residualize resoponse
-    nu[[l]] <- LSE_ptws(y_now, rho[[l]]) #scalar on scalar linear regression with n_sample observations
+    W_now[[l + 1]] <- subtr(W_now[[l]], fitted_value_W[[l]])
+
+    nu[[l]] <- LSE_ptws(y_now, rho[[l]])
     fitted_value_y[[l]] <- nu[[l]] * rho[[l]]
@@
 
-    #check mean norm
-    #mse_W[l] <- mean_sum_sqrd(W_now[[l]])
-    #mse_y[l] <- norm(y_now,"2")
-
-    #cat("W:", mse_W[l], "\n")
-    #cat("y:",  mse_y[l], "\n\n")
-
-    # STEP 3.
+    # Step 3: Orthogonalize and update prediction
     sigma[[l]] <- xi[[l]]
@@
       eta[[l]] <- scalar_mul(sigma[[l]], nu[[l]])
-    }else{ # if l > 1
-      for (u in 1:(l - 1)){
-        sigma[[l]] <- subtr( sigma[[l]], sigma[[u]], hybrid_inner_prod(delta[[u]], xi[[l]]) )
-      } #end of u-loop
-      eta[[l]] <- add(eta[[l-1]], sigma[[l]], nu[[l]])
-    }#if statement
-
-    # just for records.
-    E[[l]] <- pls_result_now$E # for monitoring symetricity
+    } else {
+      for (u in 1:(l - 1)) {
+        sigma[[l]] <- subtr(sigma[[l]], sigma[[u]], hybrid_inner_prod(delta[[u]], xi[[l]]))
+      }
+      eta[[l]] <- add(eta[[l - 1]], sigma[[l]], nu[[l]])
+    }
+
+    # Record diagnostics
+    E[[l]] <- pls_result_now$E
     V_star[[l]] <- pls_result_now$V_star
@@
     final_succesful_iteration <- l
-  }# for loop: l
-}
+  }
+}
+
 ```

### 2025-06-26 create-FSHybridPLS.Rmd
started manuscript logging

@@
 
+### subset_predictor_hybrid
+
+```{r}
+#' Extract a single observation from a predictor_hybrid object
+#'
+#' @param W A predictor_hybrid object with multiple samples.
+#' @param i Integer index of the sample to extract.
+#' @return A single-sample predictor_hybrid object.
+subset_predictor_hybrid <- function(W, i) {
+  new_Z <- matrix(W$Z[i, ], nrow = 1)
+  new_functional_list <- lapply(W$functional_list, function(fdobj) {
+    fd(coef = matrix(coef(fdobj)[, i], ncol = 1), basisobj = fdobj$basis)
+  })
+  predictor_hybrid(Z = new_Z, functional_list = new_functional_list)
+}
+
+```
+
 # One iteration
@@
 
-## asd
+## PLS component computation
+
+###
+```{r}
+get_CJ <- function(W){
+  n <- W$n_sample
+  K <- W$n_functional
+  ## C_J : C multiplied by J. Scalable to arbitrary K
+  predictor_first <- W$functional_list[[1]]
+  C_J <- t(predictor_first$coefs) %*% W$gram_list[[1]]
+  for (i in 2:K){
+    predictor_now <- W$functional_list[[i]]
+    C_J <- cbind(
+      C_J,
+      t(predictor_now$coefs) %*% W$gram_list[[i]]
+    )
+    }
+    return(C_J)
+}
+```
+
 ### get_pre_corrcov
@@
   ## C_J : C multiplied by J. Scalable to arbitrary K
-  predictor_first <- W$functional_list[[1]]
-  C_J <- t(predictor_first$coefs) %*% W$gram_list[[1]]
-  for (i in 2:K){
-    predictor_now <- W$functional_list[[i]]
-    C_J <- cbind(
-      C_J,
-      t(predictor_now$coefs) %*% W$gram_list[[i]]
-    )
-    }
+  C_J <- get_CJ(W)
 
@@
 
-## PLS component computation
+```{r}
+get_xi_direct <- function(W, y) {
+  K <- W$n_functional
+  C_J <- get_CJ(W)
+  A <- cbind(C_J, W$Z)                      # shape: n × d
+  b <- t(y) %*% A / W$n_sample   # equivalent to V_star
+
+  J_star <- get_gram_matrix_block(W)
+  alpha <- solve(J_star, t(b))                # unconstrained maximizer
+  xi_hat <- alpha / sqrt(t(alpha) %*% J_star %*% alpha)  # normalize
+
+  return(xi_hat)
+}
+```
+
+```{r}
+  C_J <- get_CJ(W)
+  A <- cbind(C_J, W$Z)                      # shape: n × d
+  b <- t(y) %*% A / W$n_sample   # equivalent to V_star
+
+  J_star <- get_gram_matrix_block(W)
+  alpha <- solve(J_star, t(b))                # unconstrained maximizer
+  xi_hat <- alpha / sqrt(sum((alpha) * (J_star %*% alpha) )) # normalize
+t(y) %*% A %*% xi_hat
+```
+
+```{r}
+ V_star <- get_pre_corrcov(W, y)
+L <- chol(J_star)
+  invL <- Matrix::chol2inv(L)
+  A <- V_star %*% t(invL)       # A = V* × t(inv(L))
+  E <- invL %*% A               # E = inv(L) × A
+
+  eigen_result <- eigen(E)
+  e <- eigen_result$vectors[, 1]
+  if (is.complex(e)){
+    print("stop")
+    return("stop")
+  }
+
+  xi_star <- t(invL) %*% e      # xi_star solves t(L) xi = e
+```
 
@@
 
-#
+### get_pls_comp_simple
+```{r}
+#' Compute First PLS Component (Direct Hilbert Averaging)
+#'
+#' Computes the first PLS component as a normalized weighted average of predictor objects,
+#' where weights are given by the centered response values.
+#'
+#' @param W A `predictor_hybrid` object containing `n_sample` observations.
+#' @param y A numeric response vector of length `n_sample`.
+#'
+#' @return A normalized `predictor_hybrid` object representing the first PLS component.
+#' @export
+get_pls_comp_simple <- function(W, y) {
+  n <- W$n_sample
+  if (length(y) != n) stop("Length of y must match number of samples in W.")
+
+  # Center the response (optional, but often improves interpretability)
+  y_centered <- y - mean(y)
+
+  # Initialize zero element
+  xi_sum <- scalar_mul.predictor_hybrid(subset_predictor_hybrid(W, 1), y_centered[1])
+
+  # Accumulate weighted sum: sum_i y_i * W_i
+  for (i in 2:n) {
+    Wi <- subset_predictor_hybrid(W, i)
+    xi_sum <- add.predictor_hybrid(xi_sum, Wi, alpha = y_centered[i])
+  }
+
+  # Normalize
+  xi_sum <- scalar_mul.predictor_hybrid(xi_sum, 1/n)
+  norm_val <- sqrt(inprod.predictor_hybrid(xi_sum))
+  xi_hat <- scalar_mul.predictor_hybrid(xi_sum, 1 / norm_val)
+
+  return(xi_hat)
+}
+
+```
+
+```{r}
+library(fda)
+
+set.seed(011111)
+n_sample <- 100
+n_scalar <- 3
+
+# --- Step 1: Zero functional predictors ---
+zero_basis <- create.bspline.basis(c(0, 1), nbasis = 4)
+zero_fd <- fd(coef = matrix(0, nrow = 4, ncol = n_sample), basisobj = zero_basis)
+functional_list <- list(zero_fd, zero_fd)  # two zero-valued functional predictors
+
+# --- Step 2: Simulate scalar predictors and response ---
+Z <- matrix(rnorm(n_sample * n_scalar), ncol = n_scalar)
+Z <- scale(Z, center = TRUE, scale = FALSE)
+W <- predictor_hybrid(Z = Z, functional_list = functional_list)
+
+beta_true <- rnorm(n_scalar)
+y <- Z %*% beta_true + rnorm(n_sample, sd = 0.1)
+y <- scale(y, center = TRUE, scale = FALSE)
+
+# --- Step 3: Compute constraint matrix ---
+lambda <- rep(0, W$n_functional)
+L <- chol(get_constraint_matrix_hybrid(W, lambda))
+
+# --- Step 4: PLS with get_pls_comp ---
+pls <- get_pls_comp(W, y, L)
+xi_hat <- pls$xi_hat
+
+# --- Step 5: PLS via raw Euclidean eigenproblem ---
+V_star_vec <- as.vector(t(Z) %*% y)     # equivalent to colSums(Z * y)
+
+J <- crossprod(Z)                       # J = Z^T Z
+L_Z <- chol(J)
+invL <- solve(L_Z)
+E <- invL %*% tcrossprod(V_star_vec) %*% t(invL)
+
+eig <- eigen(E)
+e <- eig$vectors[, 1]
+xi_manual <- backsolve(L_Z, e, transpose = TRUE)  # xi = L^T \ e
+
+# --- Step 6: get_pls_comp_simple ---
+xi_simple <- get_pls_comp_simple(W, y)
+xi_simple_vec <- tail(xi_simple$Z, 1)
+xi_direct <- get_xi_direct(W, y)
+# --- Step 7: Compare all three scalar parts ---
+
+# From get_pls_comp
+xi_hat_vec <- tail(xi_hat$Z, 1)
+
+# Cosine similarities
+cos_eig_manual <- sum(xi_manual * xi_hat_vec) / (sqrt(sum(xi_manual^2)) * sqrt(sum(xi_hat_vec^2)))
+cos_simple_manual <- sum(xi_manual * xi_simple_vec) / (sqrt(sum(xi_manual^2)) * sqrt(sum(xi_simple_vec^2)))
+cos_eig_simple <- sum(xi_simple_vec * xi_hat_vec) / (sqrt(sum(xi_simple_vec^2)) * sqrt(sum(xi_hat_vec^2)))
+
+# --- Step 8: Report ---
+cat("Cosine similarity (get_pls_comp vs manual eig):", cos_eig_manual, "\n")
+cat("Cosine similarity (get_pls_comp_simple vs manual eig):", cos_simple_manual, "\n")
+cat("Cosine similarity (get_pls_comp vs get_pls_comp_simple):", cos_eig_simple, "\n")
+
+```
+
+```{r}
+library(fda)
+
+# --- Step 1: Simulate Data ---
+set.seed(777)
+
+n_sample <- 100
+n_scalar <- 2
+n_basis <- 5
+n_functional <- 2
+
+# Scalar predictors Z (centered)
+Z <- matrix(rnorm(n_sample * n_scalar), ncol = n_scalar)
+Z <- scale(Z, center = TRUE, scale = FALSE)
+
+# Create functional predictors (centered)
+basis <- create.bspline.basis(c(0, 1), nbasis = n_basis)
+functional_list <- list()
+for (j in 1:n_functional) {
+  coefs <- matrix(rnorm(n_basis * n_sample), nrow = n_basis)
+  fdobj <- fd(coef = coefs, basisobj = basis)
+  mean_fd <- mean.fd(fdobj)
+  mean_coef <- coef(mean_fd)
+  centered_coefs <- coefs - matrix(mean_coef, nrow = n_basis, ncol = n_sample)
+  functional_list[[j]] <- fd(coef = centered_coefs, basisobj = basis)
+}
+
+# --- Step 2: Construct hybrid object ---
+W <- predictor_hybrid(Z = Z, functional_list = functional_list)
+
+# --- Step 3: Simulate and center response ---
+total_coef_len <- sum(W$n_basis_list) + W$n_scalar
+true_coef <- rnorm(total_coef_len)
+
+# Flatten design matrix
+Xmat <- matrix(NA, n_sample, total_coef_len)
+for (i in 1:n_sample) {
+  W_i <- subset_predictor_hybrid(W, i)
+  func_coefs <- do.call(c, lapply(W_i$functional_list, function(fdobj) as.vector(coef(fdobj))))
+  Xmat[i, ] <- c(func_coefs, W_i$Z)
+}
+
+y <- Xmat %*% true_coef + rnorm(n_sample, sd = 0.1)
+y <- as.vector(scale(y, center = TRUE, scale = FALSE))
+
+# --- Step 4: Compute constraint matrix ---
+lambda <- rep(0, W$n_functional)
+constr_mat <- get_constraint_matrix_hybrid(W, lambda)
+L <- chol(constr_mat)
+
+# --- Step 5: Run eigen-based PLS ---
+W_template <- W  # prevent mutation
+pls_eig_result <- get_pls_comp(W, y, L)
+xi_hat_eig <- pls_eig_result$xi_hat
+
+# --- Step 6 (Revised): Manually compute direct PLS component and wrap with predictor_hybrid_from_coef ---
+
+# Scalar part
+
+# Functional part: stack the weighted coefficients
+func_weighted_vec <- unlist(lapply(functional_list, function(fd_j) {
+  coef(fd_j) %*% y  # nbasis × 1
+}))
+
+# Full coefficient vector
+Z_weighted <- colSums(Z * y)
+
+xi_raw_vec <- c(func_weighted_vec, Z_weighted)
+
+# Wrap into predictor_hybrid object using format template
+xi_hat_direct <- predictor_hybrid_from_coef(format = W_template, coef = xi_raw_vec)
+
+# Normalize
+norm_val <- sqrt(inprod.predictor_hybrid(xi_hat_direct))
+xi_hat_direct <- scalar_mul.predictor_hybrid(xi_hat_direct,  1 / norm_val)
+
+xi_new <- get_xi_direct(W, y)
+
+# --- Step 7: Compare and evaluate ---
+ip <- inprod.predictor_hybrid(xi_hat_eig, xi_hat_direct)
+norm1 <- sqrt(inprod.predictor_hybrid(xi_hat_eig))
+norm2 <- sqrt(inprod.predictor_hybrid(xi_hat_direct))
+cos_theta <- ip / (norm1 * norm2)
+
+cat("Cosine similarity between eigen-based and direct PLS components:", cos_theta, "\n")
+cat("Projection score (eig):", sum(inprod.predictor_hybrid(xi_hat_eig, W) * y), "\n")
+cat("Projection score (direct):", sum(inprod.predictor_hybrid(xi_hat_direct, W) * y), "\n")
+
+# --- Step 8: Plot functional coefficients ---
+par(mfrow = c(n_functional, 1), mar = c(4, 4, 2, 2))
+for (j in 1:n_functional) {
+  plot(xi_hat_eig$functional_list[[j]], col = "blue", ylim = c(-1, 1),
+       main = paste("Functional Component", j), ylab = "Coefficient", xlab = "t")
+  lines(xi_hat_direct$functional_list[[j]], col = "red", lty = 2)
+  legend("topright", legend = c("Eigen-based", "Direct"), col = c("blue", "red"), lty = 1:2)
+}
+
+```
+
+## Residualization
+
+### LSE_hybrid
+```{r}
+LSE_hybrid <- function(W, rho, tau) {
+  C_star_J_star <- matrix(NA, nrow = W$n_sample, ncol = sum(W$n_basis_list) + W$n_scalar)
+  for (ii in (1 : W$n_functional)){
+    cumsum_n_basis_now <- sum(W$n_basis_list[1:ii])
+    n_basis_now <- W$n_basis_list[ii]
+    C_star_J_star[, (cumsum_n_basis_now - n_basis_now + 1) :cumsum_n_basis_now] <-
+      t(W$functional_list[[ii]]$coefs) %*% W$jacobian_list[[ii]]
+  }
+  C_star_J_star[ ,(sum(W$n_basis_list) + 1) : ncol(C_star_J_star)] <- W$Z
+  rho_t_C_star_J_star <- t(rho) %*% C_star_J_star
+
+  # matrices in the statement of Proposition 4
+  J_star <-as.matrix(get_jacobian_hybrid(W))
+  d_hat_star <- t( #basis coefficient of hybrid regression coefficient
+    solve(
+      t((norm(rho, type="2"))^2 * J_star),
+      t(rho_t_C_star_J_star)
+      )
+    )
+  delta_hat <- hybrid_from_coef(W, d_hat_star) #hybrid regression coefficient
+  return(delta_hat)
+  }
+```
+
+### nipals_pen_hybrid
+
+- depends on:
+  - 'get_constraint_matrix_hybrid'
+  - 'get_pls_comp'
+  - 'hybrid_inner_prod'
+  - 'LSE_hybrid'
 

### 2025-06-26 manuscript/Data_Processing.tex
started manuscript logging

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage[comma,authoryear]{natbib} 
\usepackage{authblk}
\usepackage{etoolbox}
\usepackage{lmodern}
\usepackage{listings}
\usepackage{xcolor}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{mauve}{rgb}{0.88, 0.69, 1.0}
\lstset{ %
  language=R,                     % the language of the code
  basicstyle=\footnotesize,       % the size of the fonts that are used for the code
  numbers=left,                   % where to put the line-numbers
  numberstyle=\tiny\color{gray},  % the style that is used for the line-numbers
  stepnumber=1,                   % the step between two line-numbers. If it's 1, each line
                                  % will be numbered
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  frame=single,                   % adds a frame around the code
  rulecolor=\color{black},        % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. commens (green here))
  tabsize=2,                      % sets default tabsize to 2 spaces
  captionpos=b,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
  title=\lstname,                 % show the filename of files included with \lstinputlisting;
                                  % also try caption instead of title
  keywordstyle=\color{blue},      % keyword style
  commentstyle=\color{dkgreen},   % comment style
  stringstyle=\color{mauve},      % string literal style
  escapeinside={\%*}{*)},         % if you want to add a comment within your code
  morekeywords={*,...}            % if you want to add more keywords to the set
}

\makeatletter
\patchcmd{\@maketitle}{\LARGE \@title}{\fontsize{18}{19.2}\selectfont\@title}{}{}
\renewcommand\Authfont{\fontsize{12}{14.4}\selectfont}
\makeatother
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage[margin=0.3in]{geometry}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage[flushleft]{threeparttable}
\usepackage[labelfont=bf]{caption}
\usepackage{caption,booktabs,array}
\usepackage{multirow}
\usepackage{makecell}
\usepackage[usenames, dvipsnames]{color}
\usepackage{setspace}
\usepackage{amssymb}
\usepackage{rotating}
 \usepackage{url}
\setstretch{1.8} % For 25 lines per page

\usepackage{chngcntr}
\counterwithin{figure}{section}
\numberwithin{equation}{section}
\usepackage{apptools}

\usepackage{sectsty}
\sectionfont{\fontsize{16}{16}\selectfont}
\subsectionfont{\fontsize{14}{14}\selectfont}

\renewcommand{\labelitemi}{$\bullet$}
\renewcommand{\labelitemiii}{$\diamond$}
\renewcommand{\labelitemii}{$\cdot$}
\usepackage{enumitem}

\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
\DeclareMathOperator*{\argmin}{arg\,min}

\date{\vspace{-5ex}}
\title{Data Processing}
\author{October 28, 2022}
\begin{document}
\maketitle

\begin{enumerate}
    \item Pre-process (only for our data) the  renogram curves by dividing: a) each baseline renogram curve by its maximum; and b) each post-furosemide (diuretic) renogram curve by the maximum of the baseline renogram curve:
    \begin{equation*}
        X_i^{(1)P} = \frac{X_i^{(1)}}{\max_t \{X_i^{(1)}(t)\}} \quad \textnormal{and} \quad X_i^{(2)P} = \frac{X_i^{(2)}}{\max_t \{X_i^{(1)}(t)\}}, \quad i=1, \ldots, n
    \end{equation*}

    \bigskip

    \item \textcolor{red}{Normalize} the renogram renogram curves:
    \begin{equation*}
        X_i^{(1)*}  = \frac{X_i^{(1)P} - \overbar{X}^{(1)P}}{\sqrt{\int \textnormal{Var}\{X_i^{(1)P}(t)\}dt}} \quad \textnormal{and} \quad X_i^{(2)*}  = \frac{X_i^{(2)P} - \overbar{X}^{(2)P}}{\sqrt{\int \textnormal{Var}\{X_i^{(2)P}(t)\}dt}}
    \end{equation*}

    \item \textcolor{red}{Normalize} the scalar predictors $\mathbf{Z}_i=(Z_{i1}, \ldots Z_{ip})^\top$
    \begin{equation*}
        Z_{ir}^S = \frac{Z_{ir} - \overbar{Z}_p}{s(Z_r)}, \quad i=1, \ldots, n, \; r=1, \ldots, p.
    \end{equation*}

    \bigskip

    \item Scale the scalar predictors so that the variability \textit{between} the functional and scalar predictors are comparable (\textcolor{red}{between-normalization}):
    \begin{equation*}
    \mathbf{Z}_i^{*} = \omega^{1/2} \mathbf{Z}_i^{S}
    \end{equation*}
    where $\omega$ is a scaling factor:
    \begin{equation*}
     \omega = \frac{\sum_{i=1}^n \Vert X_i^*  \Vert_\mathcal{F}^2}{\sum_{i=1}^n \Vert \mathbf{Z}_i^S \Vert^2} = \frac{\sum_{i=1}^n [ \int \{X^{(1)*}_i(t_1)\}^2 dt_1 + \int \{X^{(2)*}_i(t_2)\}^2 dt_2]}{\sum_{i=1}^n \mathbf{Z}^{S\top}_i \mathbf{Z}^{S}_i}.
     \label{eq:weight}
\end{equation*}

\item Run the partial least squares with $\mathbf{W}_i=(X_i^*, \mathbf{Z}_i^*)$. Make sure that you input testing data are normalized based on scaling factors computed from the training data.

\end{enumerate}

\end{document}

### 2025-06-26 manuscript/main.tex
started manuscript logging

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[comma,authoryear]{natbib} 
\usepackage[margin=1in]{geometry}

\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{verbatim}

\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage[flushleft]{threeparttable}
\usepackage[labelfont=bf]{caption}
\usepackage{caption,booktabs,array}
\usepackage{multirow}
\usepackage{makecell}
\usepackage[usenames, dvipsnames]{color}
\usepackage{setspace}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{rotating}
 \usepackage{url}
 \usepackage{enumerate}
 \allowdisplaybreaks
 \usepackage{bbold}
 \usepackage{xcolor}         % colors
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{hyperref}

\setstretch{1.8} % For 25 lines per page

\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\jongmin}[1]{
	{ \color{teal} JM: #1}
}

\title{Partial Least Squares Regression with Multiple Functional and Scalar Predictors}
\author{Jongmin Mun and Jeong Hoon Jang}
\date{\today}

\begin{document}
\maketitle

\section{Introduction} \label{sec: Introduction}

Infinite dimensional beta estimation problem (ill-posed problem)

Multicollinearity and high-dimensionality in scalar predictors are not handled.

Also, there may be high correlation between functional and scalar predictors.

Many approaches have been proposed
1. Roughness Penalty
2. basis approach (power-series, B-splines, wavelets)
- Power Series splines (Goldsmith et al., 2011, Journal of Computational Statistics)
- B-splines (H. Cardot, F. Ferraty, P. Sarda, Spline estimators for the functional linear model, Statistica Sinica 13 (2003) 571–591.
T.T.Cai,P.Hall,Prediction in functional linear regression, Ann.Stat. 34(5) (2006) 2159–2179.)
- Wavelet (Y.Zhao,R.T.Ogden,P.T.Reiss,Wavelet-based lasso in functional linear regression, J.Comput.Graph.Stat.21(3)(2012)600–61.)7

3. FPCA approach
- Hall, P. and Horowitz, J. L. (2007), ‘Methodology and convergence rates for functional linear regression’, The Annals of Statistics 35(1), 70–91.
- Reiss P. T.,  Ogden R. T.. Functional principal component regression and functional partial least squares, Journal of the American Statistical Association, 2007, vol. 102 (pg. 984-996)
- Febrero-Bande et al., 2017

4. FPLS Approach
- Preda and Saporta (2005)
- Reiss and Odgen, 2007
- Aguilera AM, Escabias M, Preda C, Saporta G. Using basis expansions for estimating functional PLS regression applications withchemometric data.Chemom Intell Lab Syst. 2010;104:289-305.
- Delaigle and Hall, 2012
- Febrero-Bande et al., 2017
- Beyaztas and Shang, (2022) A Robust Functional Partial Least Squares for Scalar-on-Multiple-Function Regression. Journal of Chemometrics.
- Saricam et al., On partial least-squares estimation in scalar-on-function regression models. Journal of Chemometrics.
- Mutis  et al. (2025) On function-on-function linear quantile regression

\section{Data Objects and Model Formulation} 
Let $\{X^{(k)}\}_{k=1, \ldots, K}$ be a collection of random functions defined on respective compact domains $\mathcal{T}_k \in \mathbb{R}^{d_k}$ ($d_k \in \mathbb{N})$; i.e., $X^{(k)}: \mathcal{T}_k \rightarrow \mathbb{R}$. Assume that each $X^{(k)}$ is in $L^2(\mathcal{T}_k)$, a Hilbert space of square integrable functions with respect to Lebesgue measure $dt_k$ on $\mathcal{T}_k$. Without loss of generality, we further assume that each  $\mathcal{T}_k$ is a $d_k$-dimensional unit interval; for instance  $\mathcal{T}_k=[0,1]$ (unit interval) if $d_k=1$, $\mathcal{T}_k=[0,1] \times [0,1]$ (unit square) if $d_k=2$, and so forth. Write  $X=(X^{(1)}, \ldots, X^{(K)})$ as a multivariate functional object that belongs to $\mathcal{F} = L^2(\mathcal{T}_1) \times \cdots \times L^2(\mathcal{T}_K)$---a cartesian product of individual $L^2(\mathcal{T}_k)$ spaces. Note that if $K=1$, $X$ reduces to a univariate functional object. We can also express the functional object $X$ evaluated on the multi-dimensional argument $\mathbf{t} = (t_1, \ldots, t_k)^\top \in \mathcal{T} = \mathcal{T}_1 \times \cdots \times \mathcal{T}_K$ as a $K$-dimensional vector $X(\mathbf{t})=(X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top$. The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)}) $ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as $\langle f_1, f_2\rangle_\mathcal{F} =  \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)}\rangle_{L^2} = \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k$ with norm $\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k)^2 dt_k\}^{1/2}$.

Let $\mathbf{Z}=(Z_1, \ldots, Z_p)^\top$ denote a $p$-dimensional multivariate scalar data  in $\mathbb{R}^p$. We assume that $\mathbf{Z}$ is a random vector with finite first two moments and equipped with the Euclidean inner product and norm; i.e., for $\mathbf{v_1}=(v_{11}, \ldots, v_{1p})^\top$ and $\mathbf{v_2}=(v_{21}, \ldots, v_{2p})^\top$ in $\mathbb{R}^p$, $\langle \mathbf{v_1}, \mathbf{v_2} \rangle = \mathbf{v_1}^\top \mathbf{v_2} = \sum_{r=1}^p v_{1r}v_{2r}$, and $\Vert \mathbf{v}_1 \Vert = \langle \mathbf{v}_1, \mathbf{v}_1 \rangle^{1/2} = (\sum_{r=1}^p v_{1r}^2)^{1/2}$.

Without loss of generality, assume that both multivariate functional and scalar data are centered; that is, $E(X)=0$ and $E(\mathbf{Z})=\mathbf{0}$. Our goal is to predict a real outcome $Y$ based on $X$ and $\mathbf{Z}$ via the following functional regression model:

\begin{equation}
Y = \sum \limits_{r=1}^p \alpha_r Z_r + \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \beta^{(k)}(t_k) X^{(k)}(t_k) dt_k + \epsilon = \langle \boldsymbol{\alpha}, \mathbf{Z} \rangle +  \langle \beta, X \rangle_{\mathcal{F}}  + \epsilon
\label{eq: functional model}
\end{equation}
where $\boldsymbol{\alpha}=(\alpha_1, \ldots, \alpha_p)^\top \in \mathbb{R}^p$ and $\beta=(\beta^{(1)}, \ldots, \beta^{(K)}) \in \mathcal{F}$ are respectively the regression coefficient vector and function that characterize the effect of scalar and functional predictors on the outcome.

Our strategy is to formulate a hybrid random object, 
by combining   $X$ and $\mathbf{Z}$ into an ordered pair:
\begin{equation}\label{def:hybid_predictor}
  \mathbf{W} = (X, \mathbf{Z}) 
  \in \mathcal{H},~\text{where}~\mathcal{H}:=\mathcal{F} \times \mathbb{R}^p
\end{equation}
 An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}[\mathbf{t}] = (X(\mathbf{t}), \mathbf{Z})^\top$, with $ X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $ \mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.  We define the inner product between any two hybrid objects, $\mathbf{h}_1 = (f_1, \mathbf{v}_1)$ and $\mathbf{h}_2 = (f_2, \mathbf{v}_2)$, as
\begin{equation}
    \langle \mathbf{h}_1, \mathbf{h}_2\rangle_{\mathcal{H}} 
    = 
    \langle f_1, f_2\rangle_\mathcal{F} 
    +
    \omega \langle  \mathbf{v_1}, \mathbf{v_2} \rangle = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k
    +
    \omega \sum \limits_{r=1}^p v_{1r}v_{2r}, 
    \label{eq: hybrid inner product}
\end{equation}
with norm $\Vert \cdot \Vert_\mathcal{H} = \langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$. $\omega$ is a positive weight that needs to be pre-specified or estimated. It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}). Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$. The results remain valid for any positive weights. Then the functional regression model \eqref{eq: functional model} with multiple functional and scalar predictors can be re-expressed in terms of the scalar-on-hybrid regression model as follows
\begin{equation}
    Y = \langle \boldsymbol{\eta}, \mathbf{W} \rangle_{\mathcal{H}} + \epsilon,
    \label{eq: Hybrid functional model}
\end{equation}
where $\boldsymbol{\eta} = (\beta, \boldsymbol{\alpha}) \in \mathcal{H}$ is a hybrid regression coefficient characterizing the association between the hybrid predictor $\mathbf{W}$ and the outcome $Y$.

The basic idea of partial least squares (PLS) is to simultaneously decompose the hybrid predictor $\mathbf{W}$ and the real outcome $Y$ in terms of zero mean uncorrelated PLS scores $(\rho_l)_{l \in \mathbb{N}}$ with maximum predictive performance as follows
\begin{equation}
    \mathbf{W}[\mathbf{t}] = \sum \limits_{l=1}^{\infty} \rho_{l} \boldsymbol{\delta}_l[\mathbf{t}] \quad \textnormal{and} \quad Y = \sum \limits_{l=1}^{\infty}\rho_{l} \nu_l + \epsilon,
    \label{eq: decomposition}
\end{equation}
where $(\boldsymbol{\delta}_l)_{l \in \mathbb{N}} \in \mathcal{H}$ and $(\nu_l)_{l \in \mathbb{N}} \in \mathbb{R}$ are appropriate bases. The PLS scores are obtained as $\rho_l =  \langle \mathbf{W}^{[l]}, \boldsymbol{\xi}_l \rangle_{\mathcal{H}}$, where $\mathbf{W}^{[l]}$ denotes the residualized predictor sequentially derived as the residual of the regression of $\mathbf{W}^{[l-1]}$ on $\rho_{l-1}$ with $\mathbf{W}^{[1]} = \mathbf{W}$, and $\boldsymbol{\xi}_l=(\psi_l, \boldsymbol{\theta}_l) \in \mathcal{H}$ is the hybrid PLS component, with $\psi_l = (\psi^{(1)}_l, \ldots, \psi_l^{(K)}) \in \mathcal{F}$ and $\boldsymbol{\theta}_l=(\theta_{l1}, \ldots, \theta_{lp})^\top \in \mathbb{R}^p$, sequentially chosen to maximize the squared covariance between $\rho_l$ and the residualized outcome $Y^{[l]}$---i.e., $\textnormal{Cov}^2(\rho_l, Y^{[l]}) = \textnormal{Cov}^2(\langle \mathbf{W}^{[l]}, \boldsymbol{\xi}_l \rangle_\mathcal{H}, Y^{[l]})$. Here, $Y^{[l]}$ is also sequentially obtained as the residual of the regression of $Y^{[l-1]}$ on $\rho_{l-1}$ with $Y^{[1]} = Y$. The sequentially derived hybrid PLS components \{$\boldsymbol{\xi}_l\}_{l=1}^\infty$, are orthonormal in a sense that $\langle \boldsymbol{\xi}_l, \boldsymbol{\xi}_j \rangle_\mathcal{H} = \mathbb{1}(l=j)$.

\underline{Challenges}
% The pointwise algorithm is highly inefficient and may not be even feasible for multiple dense and/or irregular functional data. Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components. Therefore, in this section, we introduce a novel framework for fitting a regression with a hybrid response and scalar predictor. The framework is readily applicable to dense and irregular functional data, and supports regularization techniques to prevent overfitting and reduce variance.

\begin{enumerate}
    \item Independent variables consist of multiple highly structured images and scalar predictors.
    \item Our sample size is small compared to the dimension and number of functional and scalar predictors.
    \item Existing partial least squares (PLS) methods can only accommodate (i) univariate or multivariate functional predictors without any scalar predictors \citep{Preda2005, Delaigle2012, Febrero2017, Beyaztas2020}; or (2) a univariate functional predictor with other scalar predictors \citep{Wang2018}.
\end{enumerate}

\section{Naive PLS Algorithm} \label{sec: Naive PLS Algorithm}
This section introduces a naive pointwise hybrid PLS algorithm and highlights its limitations. The algorithm treats each functional predictor as a long vector of discretized points, derives PLS components independently at each observed time point $\mathbf{t}$, and aggregates them into a functional object to compute the PLS score.
Since the regression coefficient computation follows directly from the PLS components and scores, our discussion here focuses on the latter and omits the former.
Denote $\{(Y_1, \mathbf{W}_1),  \ldots, (Y_n, \mathbf{W}_n)\}$ as $n$ independent data pairs (observed sample) distributed as $(Y, \mathbf{W})$. The goal of the PLS algorithm is to decompose the predictor $\mathbf{W}_i$ $(i=1, \ldots, n)$ and the real response $Y_i$ in terms of zero mean uncorrelated PLS scores  $(\rho_{il})_{l \in \mathbb{N}}$ with maximum predictive performance. Here and below, a superscript in square brackets denotes the iteration index of the algorithm. We begin by denoting the centered data as
\begin{equation}\label{def:centering_naive}
    Y_i^{[1]} = Y_i - \bar{Y}~\text{and}~\mathbf{W}_i^{[1]}=(X_i^{[1]}, \mathbf{Z}_i^{[1]})=(X_i - \bar{X}, \mathbf{Z}_i - \bar{\mathbf{Z}}) = \mathbf{W}_i - \bar{\mathbf{W}}. 
\end{equation}
We describe the $l$-th step of the algorithm for $l = 1, 2, \ldots, L$, which consists of the following substeps. The complete procedure is summarized in Algorithm~\ref{alg:naive}.
%
\begin{algorithm}[t!]
\caption{Naive Hybrid PLS (regression coefficient omitted)}
\label{alg:naive}
\begin{algorithmic}[1]
\Require 
Hybrid predictors $\{ \mathbf{W}_1,  \ldots, \mathbf{W}_n\} = \{(X_1, Z_1),  \ldots, (X_n, Z_n)\}$,
responses $\{Y_1,   \ldots, Y_n\}$,
functional predictor evaluation points $\mathbf{t}_1, \ldots, \mathbf{t}_m \in [0,1]^K$
%%%%%%%%%%%%%%%%%%%%%
\For{ i = 1, 2, \ldots  $n$} \Comment{Centering \eqref{def:centering_naive}}
\State $\{ (Y_i^{[1]}, X_i^{[1]},Z_i^{[1]}) \} 
\leftarrow 
\{
(Y_i - \bar{Y}, X_i - \bar{X},  Z_i - \bar{Z})
\}$
\EndFor
\For{ l = 1, 2, \ldots  $L$}
\Statex{\quad \textbf{PLS component computation step:}}
\For{ $\mathbf{t} = \mathbf{t}_1 , \ldots  \mathbf{t}_m$} \Comment{Compute PLS loading}
\State 
 $
 \widehat{\boldsymbol{\xi}}_{l}[\mathbf{t}] 
 \leftarrow 
 \dfrac{\sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]}[\mathbf{t}]}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}}
 $
\Comment{\eqref{def:pls_loading_ptws}}
\EndFor
\State $  \{ \widehat{\rho}_{1l}, \ldots, \widehat{\rho}_{nl} \} \leftarrow
\bigl\{
\langle \mathbf{W}_{1}^{[l]}, \widehat{\boldsymbol{\xi}}_{l} \rangle_{\mathcal{H}},
\ldots,
\langle \mathbf{W}_{n}^{[l]}, \widehat{\boldsymbol{\xi}}_{l} \rangle_{\mathcal{H}}
\bigr\}
$
\Comment{Compute PLS scores \eqref{def:pls_score_naive}}
\Statex{\quad  \textbf{Orthogonalization step:}}
\For{ $\mathbf{t} = \mathbf{t}_1 , \ldots  \mathbf{t}_m$} 
\State 	$
  \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \leftarrow \dfrac{\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2}.
      $
\EndFor
\State
$\mathbf{W}_i^{[l+1]}[\mathbf{t}] \leftarrow \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$
\State 	$
   \widehat{\nu}_l \leftarrow \dfrac{\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2}
      $
\State
$Y_i^{[l+1]} \leftarrow Y_i^{[l]} - \widehat{\nu}_{l} \widehat{\rho}_{il}$ 
\EndFor
\State Output PLS scores $\bigl\{ \widehat{\rho}_{il} \bigr\}_{i \in [n], l \in [L]}$
\end{algorithmic}
\end{algorithm}
%
\begin{enumerate}[Step 1.]
\item
We compute the $l$th PLS score of the $i$th subject as
\begin{equation}\label{def:pls_score_naive}
    \widehat{\rho}_{il} = \langle \mathbf{W}_{i}^{[l]}, \widehat{\boldsymbol{\xi}}_{l} \rangle_{\mathcal{H}} = \langle X_i^{[l]}, \widehat{\psi}_{l} \rangle_{\mathcal{F}} + \langle \mathbf{Z}_i^{[l]}, \widehat{\boldsymbol{\theta}}_{l} \rangle, 
\end{equation}
where the $l$-th PLS loading $\widehat{\boldsymbol{\xi}}_{l} = (\widehat{\psi}_{l}, \widehat{\boldsymbol{\theta}}_{l}) \in \mathcal{H}$ maximizes $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}_{i}^{[l]}, \widehat{\boldsymbol{\xi}}_{l} \rangle_{\mathcal{H}}, Y_i^{[l]})=\widehat{\textnormal{Cov}}^2(\widehat{\rho_{il}}, Y_i^{[l]})$. Specifically, we define the $l$-th PLS loadings pointwise as follows:
\begin{equation}\label{def:pls_loading_ptws}
    \widehat{\boldsymbol{\xi}}_{l}[\mathbf{t}] = \frac{\sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]}[\mathbf{t}]}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} = \left[ \frac{\sum_{i=1}^n Y_i^{[l]} X_i^{[l]}(\mathbf{t})}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}}, \frac{\sum_{i=1}^n Y_i^{[l]}\mathbf{Z}_i^{[l]}}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} \right]^\top,
\end{equation}
where the normalizing factor  is computed as
\begin{equation}
  \Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}} = [\sum_{i=1}^n \sum_{j=1}^n Y_i^{[l]} Y_j^{[l]} \{\langle X_i^{[l]},X_j^{[l]} \rangle_\mathcal{F} + \langle \mathbf{Z}_i^{[l]}, \mathbf{Z}_j^{[l]} \rangle \}]^{1/2}.  
\end{equation}

\item Obtain the subsequent residualized outcomes and predictors as $Y_i^{[l+1]} = Y_i^{[l]} - \widehat{\nu}_{l} \widehat{\rho}_{il}$ and $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$, where 
\begin{equation*}
    \widehat{\nu}_l = \frac{\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] = \frac{\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2}.
\end{equation*}
Note, $\widehat{\nu}_l$ is the least squares estimate from linear regression of $Y_i^{[l]}$ on $\widehat{\rho}_{il}$, and  $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ is the least squares estimate from a linear regression of $\mathbf{W}_i^{[l]}[\mathbf{t}]$ on $\widehat{\rho}_{il}$.

\item Let $l=l+1$ and back to Step 1.
\end{enumerate}

This naive pointwise PLS algorithm, however, can be computationally expensive for multiple dense functional data and is not feasible for irregular functional data. Moreover, the pointwise estimates only use information from data on the particular argument value, and thus can show substantial variability across the domain, resulting in overfitting and unstable predictions.

\section{Proposed PLS Algorithm} \label{sec: Proposed PLS Algorithm}
To address the limitations outlined in Section \ref{sec: Naive PLS Algorithm}, we propose  novel strategies for implementing the steps of the hybrid PLS algorithm. Our approach provides an efficient and robust means of producing PLS components and scores in the presence of multiple dense and/or irregular functional predictors and scalar predictors. It also incorporates a regularization scheme that enables the algorithm to borrow strength and exploit structural relationships within and between the functions to avoid overfitting of the PLS components and to improve the generalizability and interpretability of the predictive model.
Each iteration of our approach consists of two subroutines: regularized estimation of smoothed PLS components and orthogonalization, detailed in Sections~\ref{subsec: Step 1: Computing Smoothed PLS components} and~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}, respectively. After a suitable number of iterations, the hybrid regression coefficient is estimated, as described in Section~\ref{subsec: Obtaining the Estimated Hybrid Regression Coefficient}. For notational simplicity, we omit the iteration index $l$ in the following discussion, with the understanding that the subroutines apply to any iteration. The complete algorithm is summarized in Algorithm~\ref{alg:main}.

\subsection{Step 1: Computing smoothed PLS components}  \label{subsec: Step 1: Computing Smoothed PLS components}
 The function part $\psi$ of the hybrid PLS component $\boldsymbol{\xi}$ is inherently infinite-dimensional, rendering its estimation impossible with finite sample size. As such, we first approximate each functional predictor (observed version when $l=1$, or residualized version when $l \ge 2$) as a linear combination of $M$ basis functions and coefficients. 
 Due to the hybrid nature of the predictors, this approximation requires careful explanation, provided in Section \ref{sec: finite basis approximation}. This representation allows us to work with coefficient vectors, simplifying notation. Section~\ref{sec: pls component computation intermediate} outlines the core strategy for computing the PLS components in this reduced space. Building on this, we then introduce our regularized and smoothed estimation procedure, which constitutes the first step of the iterative algorithm.

\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}

For $k = 1, \ldots, K$, let us denote the system of $M$ basis functions used to approximate the $k$-th functional predictor as 
$
    \mathbf{b}^{(k)}(t_k)=(b^{(k)}_{1}(t_k), \ldots, b^{(k)}_{M}(t_k))^\top.
$
Then we can approximate the functional predictor observations as
\begin{equation*}
X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)=\mathbf{c}_i^{(k)T}\mathbf{b}^{(k)}(t_k), \;\; t_k \in \mathcal{T}_k, \;\; k=1, \ldots, K, \;\; i=1, \ldots, n,
\end{equation*}
where $\mathbf{c}_i^{(k)} = (c_{i1}^{(k)}, \ldots, c_{iM}^{(k)})^\top$ is a $M$-dimensional vector of basis coefficients corresponding to the $k$th functional predictor. This basis approximation can be expressed collectively across $n$ observations as: $\widetilde{\mathbf{X}^{(k)}}(t_k) = \widetilde{C}^{(k)} \mathbf{b}^{(k)}(t_k)$, where $\widetilde{\mathbf{X}}^{(k)}(t_k)=(X_1^{(k)}(t_k), \ldots, X_n^{(k)}(t_k))^\top \in \mathbb{R}^n$, and $\widetilde{C}^{(k)} = (\mathbf{c}_1^{(k)} \cdots \mathbf{c}_n^{(k)})^\top \in \mathbb{R}^{n \times M}$. This notation can be further extended to simultaneously express the basis expansions of $K$ functional predictors as 
\begin{equation}
    \widetilde{X}(\mathbf{t}) = \widetilde{C}B(\mathbf{t}), \quad t \in \mathcal{T},
    \label{eq: basis approximation of X}
\end{equation}
where $\widetilde{X}(\mathbf{t}) = [\widetilde{\mathbf{X}}^{(1)}(t_1), \cdots, \widetilde{\mathbf{X}}^{(K)}(t_K)] \in \mathbb{R}^{n \times K}$, $\widetilde{C} = [\widetilde{C}^{(1)}, \cdots, \widetilde{C}^{(K)}] \in \mathbb{R}^{n \times MK}$, and 
    $B(\mathbf{t}) = \mathrm{blkdiag}[\mathbf{b}^{(1)}(t_1), \cdots, \mathbf{b}^{(K)}(t_K)] \in \mathbb{R}^{MK \times K}$.
 The number of basis functions $M$ for each functional predictor can be set to a sufficiently large value (e.g., 15 or 20) to incorporate a rich variety of patterns that functional predictors may exhibit. Note that there is no need to carefully choose different $M$ values for different functional predictors, as an appropriate penalization scheme will be introduced in the later section to regularize each functional predictor to achieve a desired smoothness (see Section \ref{sec: Regularization of PLS Components}).

Furthermore, let $\widetilde{Z} = [\mathbf{Z}_1, \cdots, \mathbf{Z}_n] \in \mathbb{R}^{n \times p}$ denote $n \times p$ matrix of the scalar predictors (observed version when $l=1$, or residualized version when $l \ge 2$), and let $\widetilde{W}[\mathbf{t}]=[\widetilde{X}(\mathbf{t}), \widetilde{Z}]$ denote $n \times (K+p)$ hybrid predictor matrix that stacks $\widetilde{X}(\mathbf{t})$ and $\widetilde{Z}$ as columns. Then we can also write the hybrid predictor, whose functional part is approximated using the basis functions, as a form of linear transformation similar to \eqref{eq: basis approximation of X}:
\begin{equation}\label{eq: basis approximation of W}
    \widetilde{W}[\mathbf{t}] =  \widetilde{C}^* B^*[\mathbf{t}], \quad t \in \mathcal{T}.
\end{equation}
where  $B^*[\mathbf{t}] = \mathrm{blkdiag}(B(\mathbf{t}), I_p) \in \mathbb{R}^{(MK+p) \times (K+p)}$ and $\widetilde{C}^*=[\widetilde{C}, \widetilde{Z}] \in \mathbb{R}^{n \times (MK+p)}$.

We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\boldsymbol{\xi}[\mathbf{t}] = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$. We denote the outcome data as
\begin{equation}
\widetilde{\mathbf{y}}=(Y_1, \ldots, Y_n)^\top \in \mathbb{R}^n.
\end{equation}
%
For each $k = 1, \ldots, K$, let $J^{(k)} \in \mathbb{R}^{M \times M}$ denote the Gram matrix of the basis functions associated with the $k$-th functional predictor, defined by
\begin{equation}\label{def:gram_basis}
J^{(k)} = \left[ \int_{\mathcal{T}k} b_m^{(k)}(t) \, b_n^{(k)}(t) , dt \right]_{m,n=1}^M.
\end{equation}
Using this definition, we construct the following block-diagonal matrices:
\begin{equation}\label{def:J_and_J_star}
J = \mathrm{blkdiag}(J^{(1)}, \cdots, J^{(K)}) \in \mathbb{R}^{MK \times MK}~\text{and}~J^\ast=\mathrm{blkdiag}(J, I_p) \in \mathbb{R}^{(MK+p) \times (MK+p)}.
\end{equation}

Our proposed strategy for computing PLS component, detailed in Section \ref{sec: Regularization of PLS Components}, incorporates regularization based on second-order derivatives. To this end, let $\ddot{J}^{(k)}$ denote the $M \times M$ Gram matrix formed by the second derivatives of the basis functions,  defined as
\begin{equation}\label{def:dodot_J_k}
\ddot{J}^{(k)} = \left[ \int_{\mathcal{T}_k} \ddot{b}^{(k)}_m(t) \ddot{b}^{(k)}_n(t) \, dt \right]_{m,n=1}^M.
\end{equation}
and define a block-diagonal matrix 
$ \ddot{J}^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)}$ as
\begin{equation}\label{def:J_dotdot_ast}
    \ddot{J}^\ast=\mathrm{blkdiag}(\ddot{J}^{(1)}, \cdots, \ddot{J}^{(K)}, 0_{p \times p}).
\end{equation}
%
The finite-basis approximation allows us to represent the hybrid predictor observations using the coefficient matrix $\widetilde{C}^\ast$, enabling all associated computations to be carried out via matrix operations involving $\widetilde{C}^\ast$, $J^\ast$, and $\ddot{J}^\ast$.

\subsubsection{Smoothed estimation of PLS components}\label{sec: pls component computation intermediate}
Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an alternative intermediate strategy for implementing the first step of the PLS algorithm. Specifically, the following proposition states a tractable generalized eigenvalue problem (i.e. maximization of a generalized Rayleigh quotient) that can be solved to directly obtain a hybrid PLS component $\widehat{\boldsymbol{\xi}}=(\widehat{\psi}, \widehat{\boldsymbol{\theta}})$, which has the same structure as the hybrid predictor $\mathbf{W}=(X,\mathbf{Z})$ of model \eqref{eq: Hybrid functional model}. 
\begin{proposition} \label{Proposition: generalized rayleigh quotient}
At each $l$-th iteration of the first step of the PLS algorithm involving the residualized response and predictors $Y_i \equiv Y_i^{[l]}$ and $\mathbf{W}_i \equiv \mathbf{W}_i^{[l]}$, consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$. Let 
\jongmin{in the (1,1)th block, should $ \mathbf{y}$ be replaced by $\widetilde{\mathbf{y}} $? }
\begin{equation}\label{def:V_star}
    V^\ast = n^{-2}\begin{bmatrix}
         J \widetilde{C}^\top \mathbf{y}\mathbf{y}^\top \widetilde{C} J & J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z} \\
        \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J &   \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z}
    \end{bmatrix} = n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast
    \in \mathbb{R}^{(MK+p) \times (MK+p)}.
\end{equation}
and  $\boldsymbol{\xi}^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$. Then, the $l$-th PLS component, $\widehat{\boldsymbol{\xi}} \equiv \widehat{\boldsymbol{\xi}}_l$ can be obtained by solving
\begin{equation}\label{def:eigenproblem_smoothed}
       \argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*}, \quad \textit{or equivalently}, \quad \argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1,
\end{equation}
with respect to $\widehat{\boldsymbol{\xi}}^*=(\widehat{\mathbf{a}}^{\top}, \widehat{\boldsymbol{\theta}}^{\top})^\top$, and then setting $\widehat{\boldsymbol{\xi}}[\mathbf{t}] = [\widehat{\psi}(\mathbf{t})^\top, \widehat{\boldsymbol{\theta}}^\top]^\top =  B^*[\mathbf{t}]^\top \widehat{\boldsymbol{\xi}}^*$. The $l$-th PLS score $\widehat{\rho}_{i} \equiv \widehat{\rho}_{il}$ can be obtained as $\widehat{\rho}_i = \langle \mathbf{W}_i, \widehat{\boldsymbol{\xi}} \rangle_\mathcal{H}$.
\end{proposition}
The proof of Proposition \ref{Proposition: generalized rayleigh quotient} is given in the Appendix \ref{section:proof:eigenproblem_derivation}.
Here, $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y)$ is expressed as $\boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^*$ based on the aforementioned basis approximations. Thus, finding $\boldsymbol{\xi}^*$ that maximizes $\boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^*$ amounts to finding $\widehat{\boldsymbol{\xi}}$ that maximizes the sample squared covariance $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y)$, which is the first step of the PLS algorithm. The constraint $\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1$ scales the obtained PLS component to have a unit norm, that is, $\langle \widehat{\boldsymbol{\xi}}, \widehat{\boldsymbol{\xi}} \rangle_\mathcal{H}=1$.

\jongmin{
Another way of computing \eqref{def:eigenproblem_smoothed}, rather than solving an eigenproblem, is as follows. As shown in the proof in Appendix \ref{section:proof:eigenproblem_derivation}, the empirical covariance is simplified as:
\begin{align*}
    \widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \boldsymbol{\xi} \rangle_\mathcal{H} Y_i \\
    &= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \widetilde{Z} \boldsymbol{\theta}).
    \\&=
    \frac{1}{n}\tilde{\mathbf{y}}^\top
   \begin{bmatrix} \widetilde{C}J \; \widetilde{Z} \end{bmatrix} \;      \underbrace{
     \begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
     }_{:= \boldsymbol{\beta}}.
\end{align*}
Let us 
denote $\mathbf{b} =  \widetilde{\mathbf{y}}^\top \begin{bmatrix} \widetilde{C}J \; \widetilde{Z} \end{bmatrix}$. This is the weighted row sum of $\begin{bmatrix} \widetilde{C}J \; \widetilde{Z} \end{bmatrix}$, weighted by $\widetilde{\mathbf{y}}$.
Then using the symmetricity of $J^\ast$, we solve a linear system $J^\ast \mathbf{d} =
    \mathbf{b}^\top$ to obtain $\mathbf{d}$. Then we have
    \begin{align*}
    \max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
    \widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) 
    %%%%%%%%%%%%%%%%%%%%%
    &= 
    %%%%%%%%%%%%%%%%%%%%%%%%
     \max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
    \frac{1}{n} \mathbf{d}^\top J^\ast  \boldsymbol{\beta}
    \\& \overset{(i)}{\leq} 
     \max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
     \frac{1}{n} \sqrt{\mathbf{d}^\top J^\ast  \mathbf{d}}
    \sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}}
     \\& \overset{(ii)}{=}
     \frac{1}{n} \sqrt{\mathbf{d}^\top J^\ast  \mathbf{d}}    ,
\end{align*}
where step $(i)$ uses the Cauchy-Schwarz inequality with the inner product $\langle x, y \rangle_{J^\ast} = x^\top J^\ast y$,
and step $(ii)$ uses the norm constraint.
By the Cauchy-Schwarz inequality, the maximum displayed in the last term is obtained by a unit vector (with respect to $\langle \cdot, \cdot \rangle_{J^\ast}$) parallel to $\mathbf{d}$. Therefore we have
\begin{equation*}
     \begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
     = \frac{1}{\sqrt{\mathbf{d}^\top  J^\ast \mathbf{d} }}\mathbf{d},
\end{equation*}
which only involves solving one linear equation.
}

\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
Although Proposition \ref{Proposition: generalized rayleigh quotient} provides an efficient and principled way to compute the PLS components $\boldsymbol{\xi}$, their functional part $\psi=(\psi^{(1)}, \ldots, \psi^{(K)})$ may not be smooth, which can lead to overfitting and unstable predictions. Thus, in this section, we provide a modification of Proposition  \ref{Proposition: generalized rayleigh quotient} that yields regularized (smoothed) PLS components.

A widely-used approach to smoothing a function $\psi^{(k)}$ is to penalize its roughness that can be quantified by the integrated squared second derivative:
\begin{equation}
    \textnormal{PEN} \left(\psi^{(k)} \right) 
    =  \int_{\mathcal{T}_k} \ddot{\psi}^{(k)}(t)^2 dt = \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)},
    \label{eq: roughness penalty}
\end{equation}
where the last term is obtained using the basis expansion $\psi^{(k)}(t)=\mathbf{a}^{(k)T}\mathbf{b}^{(k)}(t)$.

Now, maximizing $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)$ is not the only aim; we also want to prevent the roughness of each $\psi^{(k)}$---that is, $\textnormal{PEN}(\psi^{(k)})$---from being too large. One possible way to achieve this is to extend \citet{Rice1991}'s approach of obtaining smoothed functional PCA components, and find $\boldsymbol{\xi}^*$ that maximizes:
\begin{equation}
   \widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right) - \sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right),
    \label{eq: penalized squred variance}
\end{equation}
subject to $\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1$. The equation \eqref{eq: penalized squred variance} quantifies the trade-off between fidelity to the data (in this case the sample covariance between the $\rho=\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}$ and $Y$ in the direction of $\boldsymbol{\xi}$) and roughness as measured by the sum of the individual penalty terms in \eqref{eq: roughness penalty}. The smoothing parameters $\{\lambda_k\}_{k=1}^K$ control the relative importance between the two objectives. Note that the penalty term can be written concisely using matrices as:
\begin{equation*}
    \sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right) = \sum \limits_{k=1}^K \lambda_k \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)} = \boldsymbol{\xi}^{* \top} \Lambda \ddot{J}^\ast \boldsymbol{\xi}^*,
\end{equation*}
where $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is defined as
\begin{equation}\label{def:Lambda}
   \Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
\end{equation}
 $0_{p \times p}$ denotes a $p \times p$ matrix with all elements equal to zero.

In this paper, we take an alternative strategy that extends the idea of \citet{Silverman1996}. This approach is known to produce appropriately smoothed functional PCA components under milder conditions than the \citet{Rice1991}'s approach by replacing the usual $L^2$-orthonormality constraint with the one that takes account the roughness of functions via the modified inner product. Specifically, the following proposition provides a generalized Rayleigh quotient problem which modifies the $\mathcal{H}$-orthonormality constraint of the hybrid PLS components to incorporate roughness penalty, and thus whose solution corresponds to a smoothed PLS component maximizing $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)$ over the class of all functions satisfying sufficient smoothness.
\begin{proposition} \label{Proposition: Regularized generalized rayleigh quotient}
At each $l$-th iteration of the first step of the PLS algorithm involving the residualized response and predictors $Y_i \equiv Y_i^{[l]}$ and $\mathbf{W}_i \equiv \mathbf{W}_i^{[l]}$, consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$. Recall from \eqref{def:V_star} that  $V^\ast$ is defined as
\begin{equation*}
    V^\ast = n^{-2}\begin{bmatrix}
         J \widetilde{C}^\top \mathbf{y}\mathbf{y}^\top \widetilde{C} J & J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z} \\
        \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J &   \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z}
    \end{bmatrix} = n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast
    \in \mathbb{R}^{(MK+p) \times (MK+p)}.
\end{equation*}
and  $\boldsymbol{\xi}^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$. Then, the $l$-th smoothed PLS component, $\widehat{\boldsymbol{\xi}} \equiv \widehat{\boldsymbol{\xi}}_l$ can be obtained in the following way.
We first compute the basis coefficients by solving the optimization problem
\begin{align}
\begin{split}
       &\argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*\top}(J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*} , \quad \textit{or equivalently}, \\ 
       &\argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*=1.
       \label{eq: Regularized generalized rayleigh quotient equation}
\end{split}
\end{align}
We then express the smoothed component in terms of the basis functions as
\begin{equation*}
   \widehat{\boldsymbol{\xi}}[\mathbf{t}] = [\widehat{\psi}(\mathbf{t})^\top, \widehat{\boldsymbol{\theta}}^\top]^\top =  B^\ast[\mathbf{t}]^\top \widehat{\boldsymbol{\xi}}^\ast.   
\end{equation*}
 The $l$-th PLS score $\widehat{\rho}_{i} \equiv \widehat{\rho}_{il}$ can be obtained as 
 \begin{equation}\label{compute_pls_score}
 \widehat{\rho}_i = \langle \mathbf{W}_i, \widehat{\boldsymbol{\xi}} \rangle_\mathcal{H}
 \end{equation}
\end{proposition}
The proof of Proposition \ref{Proposition: Regularized generalized rayleigh quotient} is provided in Appendix \ref{section:proof:eigenproblem_derivation}.
Here, $\lambda_k$ $(k=1, \ldots, K)$ is a positive smoothing parameter that controls the trade-off between the goodness of fit and the amount of smoothness in $\psi^{(k)}$. Smaller $\lambda_k$ produces PLS components that fit more closely to the observed data, but selecting too small value may cause overfitting. The estimated PLS component reverts back to the unregularized version of Proposition \ref{Proposition: generalized rayleigh quotient} when $\lambda_k=0$ for all $k$. On the other hand, larger $\lambda_k$ places more emphasis on smoothing $\psi^{(k)}$. In the limit $\lambda_k \rightarrow \infty$, each of the functions is forced to be of the form $\psi^{(k)}(t)=a+bt$ for some constants $a$ and $b$. In practice, $\{\lambda_k\}_{k=1}^K$ as well as the number of PLS components $L$ to be estimated can be chosen by cross-validation based on a certain predictive performance criterion (e.g., mean squared error).

The constraint $\boldsymbol{\xi}^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*=1$ enforces the following modified orthonormality of the estimated PLS components ($\widehat{\boldsymbol{\xi}}_1, \widehat{\boldsymbol{\xi}}_2, \ldots$)  based on the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ which now takes into account the roughness of the functions:
\begin{align*}
  \langle \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle \rangle 
   &= \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right \rangle_{L^2} \\
  &= \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_{\mathcal{T}_k} \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
& = \mathbb{1}(l=j). 
\end{align*}
This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{sec: Properties of the Proposed PLS Framework} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.

To solve \eqref{eq: Regularized generalized rayleigh quotient equation} in practice, we first perform a Choleski factorization: $L L^\top = J^\ast + \Lambda \ddot{J}^\ast$, where $L$ is a lower triangular matrix, and then reduce it to maximizing the classical Rayleigh quotient problem:
\begin{equation*}
    \max \limits_{\mathbf{e} \in \mathbb{R}^{MK + p}} \, \frac{\mathbf{e}^\top E \mathbf{e}}{\mathbf{e}^\top \mathbf{e}} \; \Longleftrightarrow \;   \max \limits_{\substack{\mathbf{e} \in \mathbb{R}^{MK+p}}} \;  \mathbf{e}^\top E \mathbf{e} \quad \textnormal{subject to} \quad \Vert \mathbf{e} \Vert^2 = 1
\end{equation*}
through the transformations $\mathbf{e} = L^\top \boldsymbol{\xi}^*$ and $E = L^{-1} V^\ast L^{\top-1}$. Once $\mathbf{e}$ is obtained as the first eigenvector of $E$, we set $\boldsymbol{\xi}^* = L^{\top-1} \mathbf{e}$ and $\widehat{\boldsymbol{\xi}}[\mathbf{t}] = B^*[\mathbf{t}]^\top \boldsymbol{\xi}^*$.

\subsection{Step 2: Computing Residualized Predictors via Hybrid-on-Scalar Regression} \label{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}
The second step of the PLS algorithm involves iteratively obtaining the ($l+1$)-th residualized predictors as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$, where $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ is the least squares estimate from regressing the previous ($l$-th) residualized outcome $\mathbf{W}_i^{[l]}[\mathbf{t}]$ on the corresponding  estimated PLS score $\widehat{\rho}_{il}$.  The pointwise least squares estimate, $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] = (\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \widehat{\rho}_{il})/(\sum_{i=1}^n \widehat{\rho}_{il}^2)$, presented in Section \ref{sec: Naive PLS Algorithm}, however, is  highly inefficient and may not be even feasible for multiple dense and/or irregular functional data. Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components. Therefore, in this section, we introduce a novel strategy based on a hybrid-on-scalar regression model for obtaining $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ and implementing the second step.

Again, we omit $l$ in the notations. Let $\widehat{\boldsymbol{\rho}}=(\widehat{\rho}_1, \ldots, \widehat{\rho}_n)^\top$ denote an $n$-dimensional vector of PLS scores estimated from the proposed algorithm, and let the $(K+P)$-vector $\boldsymbol{\delta}[\mathbf{t}] = [\pi(\mathbf{t})^\top, \boldsymbol{\gamma}^\top]^\top$ denote the regression coefficient consisting of the functional part $\pi(\mathbf{t}) = (\pi^{(1)}(t_1), \ldots,\pi^{(K)}(t_K))^\top \in \mathbb{R}^K$ and scalar part $\boldsymbol{\gamma} = (\gamma_1, \ldots,\gamma_p)^\top \in \mathbb{R}^p$. The hybrid-on-scalar regression model we are interested in fitting is then:
\begin{equation}
    \widetilde{W}[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top + \mathbf{e}[\mathbf{t}],
    \label{eq: hybrid on scalar regression model}
\end{equation}
where $\mathbf{e}[\mathbf{t}]$ is an $n \times (K+p)$ matrix of errors.

As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$. Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \mathbf{d}^{(k)\top} \mathbf{b}^{(k)}(t_k)$, where $\mathbf{d}^{(k)} = (d_1^{(k)}, \ldots, d_M^{(k)})\top \in \mathbb{R}^M$ are basis coefficients. Here, a different basis system can be flexibly chosen to expand the regression coefficient, but without loss of generality we use the same system as in Section \ref{subsec: Step 1: Computing Smoothed PLS components}. With the $(MK+p)$-dimensional row vector $\mathbf{d}^* = (\mathbf{d}^{(1)\top}, \ldots, \mathbf{d}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as: $\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \mathbf{d}^* B^*[\mathbf{t}]$. Finally, these basis expansions of the hybrid response and the regression coefficient enable us to re-write the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model} in a finite-dimensional form:
\begin{equation}
    \widetilde{C}^* B^*[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \mathbf{d}^* B^*[\mathbf{t}] + \mathbf{e}[\mathbf{t}].
\label{eq: rewritten hybrid on scalar regression model}
\end{equation}

Based on the model formulation \eqref{eq: rewritten hybrid on scalar regression model}, we can now formulate the following least squares criterion whose minimizing solution gives the estimate of the regression coefficient $\boldsymbol{\delta}[\mathbf{t}]$ in the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model}:
\begin{equation}
\begin{aligned}
    \textnormal{SSE}(\delta) &= \int_\mathcal{T} \left\Vert \,  \widetilde{C}^* B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}} \, \mathbf{d}^* B^*[\mathbf{t}] \, \right\Vert_F^2 \, d\mathbf{t}  \\
    &= tr\left(\widetilde{C}^{*T}\widetilde{C}^*J^\ast \right) - 2\,tr \left(\mathbf{d}^* J^\ast \widetilde{C}^{*T} \widehat{\boldsymbol{\rho}} \right) + tr\left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \mathbf{d}^* J^\ast \mathbf{d}^{*T}\right),
\end{aligned}
\label{eq: least squares}
\end{equation}
where $tr$ denotes the trace of a matrix, and $\Vert \cdot \Vert_F$ is a Frobenius norm. Now taking the derivative of \eqref{eq: least squares} with respect to $\mathbf{d}^*$ and setting the result to zero, we find that  $\mathbf{d}^*$ satisfies the system of linear equations
\begin{equation*}
    \widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \mathbf{d}^*  J^\ast =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast,
\end{equation*}
whose solutions lead to the following estimates of $\mathbf{d}^*$ and $\boldsymbol{\delta}[\mathbf{t}]$:
\begin{equation*}
  \widehat{\mathbf{d}}^*  =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast \left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} J^\ast \right)^{-1} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}[\mathbf{t}] = B^*[\mathbf{t}]^\top \, \widehat{\mathbf{d}}^{*\top}.
\end{equation*}
Then, we can use $\widehat{\boldsymbol{\delta}}[\mathbf{t}]$ to obtain the subsequent residualized hybrid predictor as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$.

The step for obtaining the subsequent residualized response is identical to that of the naive PLS algorithm in  in Section \ref{sec: Naive PLS Algorithm}. Specifically, the $(l-1)$-th residualized response can be obtained as $Y_i^{[l+1]} = Y_i^{[l]} - \widehat{\nu}_l \widehat{\rho}_{il}$, where $\widehat{\nu}_l = \sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}/\sum_{i=1}^n \widehat{\rho}_{il}^2$  is the least square estimate of the simple linear model regressing $Y_i^{[l]}$ on $\widehat{\rho}_{il}$.

\subsection{Obtaining the Estimated Hybrid Regression Coefficient}
\label{subsec: Obtaining the Estimated Hybrid Regression Coefficient}
The regression coefficient $\boldsymbol{\eta}$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS components and scores. First, note that we can show $\widehat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \widehat{\boldsymbol{\xi}}_l \rangle_\mathcal{H} = \langle \mathbf{W}_i, \widehat{\boldsymbol{\zeta}}_l \rangle_\mathcal{H}$, where $\widehat{\boldsymbol{\zeta}}_l = \widehat{\boldsymbol{\xi}}_l - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}_u, \widehat{\boldsymbol{\xi}}_l \rangle_{\mathcal{H}} \widehat{\boldsymbol{\zeta}}_u$ for $l \ge 2$, with $\widehat{\boldsymbol{\zeta}}_1 = \widehat{\boldsymbol{\xi}}_1$. Then, the decomposition of $Y_i$ in \eqref{eq: decomposition} leads to
\begin{equation*}
    Y_i = \sum \limits_{l=1}^L \widehat{\nu}_l \langle \mathbf{W}_i^{[l]}, \widehat{\boldsymbol{\xi}}_l \rangle_\mathcal{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l \right\rangle_\mathcal{H}+\epsilon_i,
\end{equation*}
which, given the uniqueness of $\boldsymbol{\eta}$, leads to
\begin{equation*}
    \widehat{\boldsymbol{\eta}} = \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l.
\end{equation*}
Here, the number of PLS components $L$ to be estimated can be chosen by cross-validation.

\begin{algorithm}[b!]
\caption{Hybrid PLS (under construction)}
\label{alg:main}
\begin{algorithmic}[1]
\Require 
Response $\mathbf{y} \in \mathbb{R}^n$,
%functional predictor evalulation points $\mathbf{t}_1, \ldots, \mathbf{t}_m \in [0,1]^K,$
hybrid predictors approximation coefficient
$\widetilde{C}^* \ \in \mathbb{R}^{n \times (MK+p)} $ \eqref{eq: basis approximation of W},
Gram matrix with respect to basis functions
$J^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)} $
\eqref{def:J_and_J_star},
Gram matrix with respect to second derivatives of the basis functions 
$\ddot{J}^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)}$
\eqref{def:J_dotdot_ast},
regularization matrix $\Lambda  \in \mathbb{R}^{(MK+p) \times (MK+p)}$ \eqref{def:Lambda}
%%%%%%%%%%%%%%%%%%%%%
\State
$\widetilde{C}^{*[1]} \leftarrow \widetilde{C}^*$
\For{ l = 1, 2, \ldots  $T$}
\State $V^\ast \leftarrow n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast$
\Comment{ \eqref{def:V_star}}
\State 	$\widehat{\boldsymbol{\xi}}_l^\ast \leftarrow \argmax_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*=1
      $
    \Comment{ \eqref{eq: Regularized generalized rayleigh quotient equation}} 
\State $\widehat{\boldsymbol{\rho}}_l
\leftarrow 
\widetilde{C}^* J^\ast  \widehat{\boldsymbol{\xi}}_l^\ast
$
\Comment{$\in \mathbb{R}^n$; \eqref{compute_pls_score}}
\EndFor
\State Output a
\end{algorithmic}
\end{algorithm}

\subsection{Data Preprocessing} \label{subsec: Data Preprocessing}
Functional and scalar elements of the hybrid predictors often have incompatible units and/or exhibit different amounts of variation. This can be problematic for our PLS framework which is not scale invariant as: i) each predictor has different chance of contributing to the predictor/response structure; and ii) a predictor with high correlation to $Y$ but relatively low variance may be overlooked.

To obtain PLS components that have a meaningful interpretation, we standardize the predictor data via the following steps. The first step is to account for discrepancies \textit{within} respective functional and scalar parts, if needed. If elements of multivariate functional data $X_i = (X_i^{(1)}, \ldots, X_i^{(K)})$ are measured in different units or have quite different domains, one can standardize them to have mean zero and integrated variance of one. If multivariate scalar predictors $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ exhibit different amounts of variation, one can standardize them to have mean zero and unit variance. The second step is to eliminate the discrepancies \textit{between} functional and scalar parts. To accomplish this aim, we choose an appropriate weight $\omega$ in the hybrid inner product \eqref{eq: hybrid inner product} that ensures functional and vector parts have comparable variance. A sensible data-driven approach to choosing an appropriate weight is to set
\begin{equation*}
     \omega = \frac{\sum_{i=1}^n \Vert X_i \Vert_\mathcal{F}^2}{\sum_{i=1}^n \Vert \mathbf{Z}_i \Vert^2},
     \label{eq: weight}
\end{equation*}
In practice, this weighting scheme can be implemented by formulating the hybrid object as $\mathbf{W} = (X, \omega^{1/2} \mathbf{Z})$, whose vector part has been scaled by a factor of $\omega^{1/2}$.

\section{Properties of the Proposed PLS Framework}
\label{sec: Properties of the Proposed PLS Framework}
In this section, we derive some of the theoretical and geometric properties of the proposed PLS framework.

\subsection{Tucker's Criterion}
We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}. We omit $l$ in the notations and first define the cross-covariance terms between the response and predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$): 
\begin{equation*}
    \begin{gathered}
      \sigma_{YX} = (\sigma_{YX}^{(1)}, \ldots, \sigma_{YX}^{(K)}) = (E(YX^{(1)}),\ldots, E(YX^{(K)})) = E(YX) \in \mathcal{F} \\
      \sigma_{YZ} = (\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top = (E(YZ_1),\ldots, E(YZ_p))^\top = E(Y\mathbf{Z}) \in \mathbb{R}^p \\
      \Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) =  (E(YX), E(Y\mathbf{Z}))=E(Y\mathbf{W}) \in \mathcal{H}
    \end{gathered}
\end{equation*}
We also introduce two cross-covariance operators, $\mathcal{C}_{YW}=E(\mathbf{W} \otimes_\mathcal{H} Y): \mathcal{H} \rightarrow \mathbb{R}$ and $\mathcal{C}_{WY}=E(Y \otimes \mathbf{W}): \mathbb{R} \rightarrow \mathcal{H}$, which respectively map $h=(f, \mathbf{v}) \in \mathcal{H}$ to $\mathbb{R}$ and $d \in \mathbb{R}$ to $\mathcal{H}$ as follows:
\begin{align*}
  & \mathcal{C}_{YW} \mathbf{h} = E\{\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \sigma_{YX}^{(k)}(t_k) f^{(k)}(t_k) dt_k + E(Y \mathbf{Z}^\top) \mathbf{v} \\
  & \mathcal{C}_{WY} d = E (\langle Y, d \rangle \mathbf{W} ) = E(Y\mathbf{W})d =  \Sigma_{YW} \, d. 
\end{align*}

Now define a new operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$, which performs the following mapping:
 \begin{equation*}
  \mathcal{U} \mathbf{h} =  \mathcal{C}_{WY} ( \mathcal{C}_{YW} \mathbf{h}) 
  = \mathcal{C}_{YW} (\langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}) 
  =  \Sigma_{YW} \, \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = (\Sigma_{YW} \otimes \Sigma_{YW})\mathbf{h}.
 \end{equation*}
In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$. The following proposition presents several important properties of $\mathcal{U}$.
\begin{proposition} \label{Proposition: property of U}
The operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}= \Sigma_{YW} \otimes \Sigma_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ is positive and self-adjoint. Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that
\begin{align}
    \max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in \mathcal{T}_k} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
\end{align}
and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in \mathcal{T}_k$ with $|t_k - t_k^* | < \delta_k$, we have that
\begin{equation*}
    |\sigma_{yx}^{(k)}(t_k) - \sigma_{yx}^{(k)}(t_k^*) | < \epsilon,
\end{equation*}
then $\mathcal{U}$ is a compact operator.
\end{proposition}
By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\boldsymbol{\xi}_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \boldsymbol{\xi}_{(u)} = \kappa_{(u)}  \boldsymbol{\xi}_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.

The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
\begin{proposition}
\begin{equation*}
    \max \limits_{\substack{\boldsymbol{\xi} \in \mathcal{H} \\ \Vert \boldsymbol{\xi} \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)
\end{equation*}
is achieved when $\boldsymbol{\xi}$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.
\label{proposition: eigenanalysis}
\end{proposition}
In other words, $l$-th PLS component $\boldsymbol{\xi}_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.

\subsection{Geometric Properties}
In this section, we derive several geometric properties of the PLS components and and scores obtained from the proposed algorithm.

The following proposition states that the PLS components estimated from Proposition  \ref{Proposition: Regularized generalized rayleigh quotient} are orthonormal with respect to the modified inner product $\langle \langle \cdot \rangle \rangle$ that incorporates the roughness of the functions.
\begin{proposition}
The estimated PLS components, $\widehat{\boldsymbol{\xi}}_1, \widehat{\boldsymbol{\xi}}_2, \ldots, \widehat{\boldsymbol{\xi}}_L$, from the proposed PLS algorithm are mutually orthonormal with respect to the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ in $\mathcal{H}$ that incorporates the roughness of the functions; i.e.,
\begin{equation*}
  \langle \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle \rangle 
   = \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}
 = \mathbb{1}(l=j). 
\end{equation*}
\label{proposition: modified orthnormality of PLS components}
\end{proposition}

Now let $\widehat{\boldsymbol{\rho}}_l=(\widehat{\rho}_{1l}, \ldots, \widehat{\rho}_{nl})^\top$ denote the $n$-dimensional vector whose elements consist of estimated $l$-th PLS scores ($l=1, \ldots, L)$ of $n$ observations. The next proposition states that the vectors of estimated PLS scores $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$ obtained from the proposed algorithm are mutually orthogonal.
\begin{proposition}
The vectors of estimated PLS scores, $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$, obtained from the proposed PLS algorithm are mutually orthogonal in the sense that
\begin{equation*}
 \widehat{\boldsymbol{\rho}}_l^\top \widehat{\boldsymbol{\rho}}_j= 0 \quad \textnormal{for} \quad \; l,j \in \{1, \ldots, L\}, \; l \ne j. 
\end{equation*}
\label{proposition: orthnormality of PLS scores}
\end{proposition}

\section{Simulations}
To evaluate the superiority of our method under complex dependency structures
{\textemdash}
specifically, dependencies among functional predictors,
among scalar predictors,
and between scalar and functional predictors
{\textemdash}

\medskip
\noindent
\textit{Matrix-normal setting.}
We begin by constructing predictors from a matrix-normal distribution, a framework that offers convenient and flexible control over the dependence structure across both rows and columns. Matrix-normal (MN) models, also known as Kronecker-separable covariance models, provide a principled approach to modeling multivariate data with structured covariance. Specifically, the matrix-normal distribution is defined as
\begin{equation*}
\mathbf{X} \sim \mathcal{MN}_{m \times n}(\mathbf{M}; \mathbf{R}, \mathbf{C}),
\end{equation*}
and its log-density is given by
\[
\log p(\mathbf{X} \mid \mathbf{M}, \mathbf{R}, \mathbf{C}) = -\frac{mn}{2} \log(2\pi) - \frac{m}{2} \log |\mathbf{C}| - \frac{n}{2} \log |\mathbf{R}| - \frac{1}{2} \mathrm{Tr}\left[ \mathbf{C}^{-1} (\mathbf{X} - \mathbf{M})^\top \mathbf{R}^{-1} (\mathbf{X} - \mathbf{M}) \right].
\]
The key insight behind Kronecker separability is that if
$
\mathbf{Y} \sim \mathcal{MN}(\mathbf{M}, \mathbf{R}, \mathbf{C}),
$
then its vectorized form follows a multivariate normal distribution:
$
\mathrm{vec}(\mathbf{Y}) \sim \mathcal{N}(\mathrm{vec}(\mathbf{M}), \mathbf{C} \otimes \mathbf{R}),
$
where $\otimes$ denotes the Kronecker product and $\mathrm{vec}$ is the vectorization operator.

\begin{figure}[ht!]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{image/cor_strong.pdf}
        \caption{Correlation Matrix - Strong Dependency}
        \label{fig:cor_strong}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{image/cor_weak.pdf}
        \caption{Correlation Matrix - Weak Dependency}
        \label{fig:cor_weak}
    \end{subfigure}

    \vspace{0.5cm}  % Adjust vertical spacing

    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{image/graph_strong.pdf}
        \caption{Graph Structure - Strong Dependency}
        \label{fig:graph_strong}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{image/graph_weak.pdf}
        \caption{Graph Structure - Weak Dependency}
        \label{fig:graph_weak}
    \end{subfigure}

    \caption{Comparison of Correlation Matrices and Graph Structures under Strong and Weak Dependencies.}
    \label{fig:correlation_graph_comparison}
\end{figure}
\begin{comment}
The goal of this simulation is to:
\begin{enumerate}
\item Utilize a graphical model to introduce a complex dependence structure.
\item Demonstrate that our method outperforms the penalized functional regression approach by \citet{goldsmith_penalized_2011}.
\item Show that our method exhibits superior performance as correlation strength increases.
\end{enumerate}

Our previous setup, presented in Section \ref{simul:meeting_feb}, appeared to achieve these objectives. However, we identified several limitations:
\begin{enumerate}
    \item The resulting precision matrix was singular, requiring us to scale up the diagonal elements to compute its inverse. This adjustment disrupted the original AR(1) structure of the functional component, making it significantly less smooth.
    \item Increasing conditional correlation did not consistently enhance the superiority of our method.
\end{enumerate}
To address these issues, I will explore alternative functional graphical model settings that exhibit a strong dependence structure—one substantial enough to be detected by statistical methodologies and validated by top statistical journal papers. I will evaluate the performance of penalized functional regression on these data-generating models.
Among them, I will select three to four settings for comparison against other methods.
\end{comment}
Building on the functional graphical model simulation of \citet{zhuBayesianGraphicalModels2016}, we generate a mixed graphical model with five nodes, described as follows:  
\begin{itemize}
\item Nodes F1 and F2: Two functional predictors modeled as Gaussian processes using a truncated Karhunen-Loève expansion, where the eigenbasis consists of Fourier basis functions with a fixed number of basis functions, \(M = 9\).  
\item  Nodes S1, S2, and S3: Three scalar predictors, each following an \(s\)-dimensional multivariate normal distribution. Unlike the functional predictors, these scalar predictors are modeled directly without basis expansion.  
\end{itemize}
To capture dependencies among predictors, we introduce a graph structure that governs their conditional correlations. We consider two types of graph structures: a weakly connected graph and a strongly connected graph. In the Gaussian process framework, the precision matrix \(\mathbf{R}_0^{-1}\) encodes conditional independence relationships, while its inverse, \(\mathbf{R}_0\), represents marginal covariances. This structure extends to a blockwise correlation matrix \(\mathbf{R} \in \mathbb{R}^{(2M + 3s) \times (2M + 3s)}\), where off-diagonal blocks represent correlations between FPC scores and scalar predictor values.  
Each block \((i, j)\) of \(\mathbf{R}\) is given by \((R_0)_{ij} \mathbf{I}_{M_i, M_j}\), where \(\mathbf{I}_{M_i, M_j}\) is a rectangular identity matrix. Here, \(M_i = 9\) if node \(i\) corresponds to a functional predictor and \(M_j = s\) if node \(j\) corresponds to a scalar predictor.

For each functional predictor, we assgin  \(M\) reference eigenvalues (or FPC score) drawn independently from gamma distributions with decreasing means.
These reference eigenvalues will later be multiplies by randomly  multiplier drawn from correlated multivaraite Normal distribution. These reference eigenvalues are fixed over all samples and all independent repetition of the experiment. We draw it one randomly just to ensure the differentiation between the two functional predictors.
 we independently draw for each functional predictor from . We then sample zero-mean multivariate normal data from the covariance matrix \(\mathbf{R}\). The last \(3s\) components are assigned as scalar predictors, while the first \(2M\) components, scaled by their corresponding eigenvalues, serve as FPC scores. These scores are then expanded into functional data, evaluated over 100 equally spaced points on \([0,1]\) using a Fourier basis.

Finally, we introduce structured variability by adding a common mean function, defined as a scaled and shifted sine function. To visualize the generated data, Figure \ref{fig:correlation_graph_comparison}  plots functional predictor realizations and heatmaps of sample correlation matrices for both graph structures, illustrating the distinct dependency patterns induced by the precision matrices.

\subsection{Simulation shown in february 2025 meeting}\label{simul:meeting_feb}
To effectively manage the dependencies among functional predictors, scalar covariates, and between functional and scalar predictors, we utilize a Gaussian Markov random field (GMRF) within the framework of Gaussian undirected graphical models. In a GMRF, the off-diagonal elements of the precision matrix capture the conditional correlations between the corresponding components. Given that our setting involves both functional and scalar covariates, we adopt the simulation setup proposed by \cite{kolar_graph_2014}, which focuses on mixed attribute Gaussian graphical models.

We construct a graph consisting of two functional predictor nodes and three vector predictor nodes. Below, we sequentially describe the graph structure and the generation process for each node.

\medskip
\noindent
\textit{Functional Predictors.}
We consider two functional predictors that share the same precision matrix. Denoted as \( \boldsymbol{\Theta} := (\theta_{t \tilde{t}}) \in \mathbb{R}^{p \times p} \), this precision matrix follows an AR(1) structure with a white noise variance of \( 0.1^2 \) and an autoregressive coefficient of \( = 0.95 \), ensuring a smooth functional trajectory.

More formally, each functional predictor is evaluated at \( p \) equally spaced points on \( [0,1] \), with values defined recursively as:
\begin{equation*}
    X^{(k)}_i(0) = 0, \quad 
    X^{(k)}_i(t)= \rho X^{(k)}_i(t-1) + \varepsilon_{itk}, \quad \varepsilon_{itk} \overset{\text{i.i.d.}}{\sim} \mathcal{N}(0, \sigma^2), \quad t = 1, \dots, p,~i=1, \ldots, n,~k = 1,2.
\end{equation*}
In this setting, the precision matrix \( \boldsymbol{\Theta} \) exhibits a tridiagonal Toeplitz structure, where the diagonal entries are given by:
\begin{equation*}
  \theta_{tt} = 
  \begin{cases}
    \dfrac{1}{\sigma^2(1-0.95^2)}, & t = 1, p, \\
    \dfrac{1+0.95^2}{\sigma^2(1-0.95^2)}, & 2 \leq t \leq p-1.
  \end{cases}
\end{equation*}
The off-diagonal entries are:
\begin{equation*}
     \theta_{t, t+1} = \theta_{t+1, t} = -\dfrac{\rho}{\sigma^2(1-\rho^2)}, \quad 1 \leq t \leq p-1.
\end{equation*}
Finally, the functional predictors are smoothed using a B-spline basis with 15 basis functions, as described in Section \ref{subsec: Step 1: Computing Smoothed PLS components}.

\medskip
\noindent
\textit{Vector Predictors.}
We consider \( s \) vector predictors, each following a \( d \)-dimensional zero-mean Gaussian distribution with a shared precision matrix. This precision matrix, denoted as \( \Gamma := (\gamma_{ij}) \in \mathbb{R}^{d \times d} \), follows a Toeplitz structure with exponentially decaying entries, given by:
\begin{equation*}  
\gamma_{ij} := 0.5^{|i-j|}.
\end{equation*}

\medskip
\noindent
\textit{Graph Structure.}
We arrange five nodes   in a chain structure, where each node follows a sequential order, and the last node connects back to the first, as illustrated in Figure~\ref{fig:graph}. An edge in the graph indicates that the connected nodes remain correlated when the values of all other nodes are fixed. 
The resulting marginal dependence structure is significantly more complex than the chain structure itself. We designate nodes \(F_1\) and \(F_2\) as functional predictors and nodes \(V_1\), \(V_2\), and \(V_3\) as vector predictors.
%
\begin{figure}
	\centering
	\includegraphics[width=0.4\linewidth]{image/graph}
	\caption{}
	\label{fig:graph}
\end{figure}
%
To introduce conditional dependencies between the components, we set the off-diagonal blocks of the precision matrix to be $0.5 \mathbf{1}$ if the corresponding components are connected in the graph, and zero otherwise. Here, $\mathbf{1}$ denotes a matrix of appropriate dimensions where all elements are equal to 1. Overall, we generate a $2p + 3d$-dimensional multivariate Gaussian distribution with mean zero and a precision matrix $\Omega$, structured as follows:

\[
\Omega =
\begin{pmatrix}
	\Omega_{F} & 0.5 \mathbf{1} & 0 & 0 & 0.5 \mathbf{1} \\
	0.5 \mathbf{1} & \Omega_{F} & 0.5 \mathbf{1} & 0 & 0 \\
	0 & 0.5 \mathbf{1} & \Omega_{V} & 0.5 \mathbf{1} & 0 \\
	0 & 0 & 0.5 \mathbf{1} & \Omega_{V} & 0.5 \mathbf{1} \\
	0.5 \mathbf{1} & 0 & 0 & 0.5 \mathbf{1} & \Omega_{V} \\
\end{pmatrix}
\]

For each observation drawn from this multivariate Gaussian distribution, we process

The regression coefficients for the first functional predictor, $\beta_{F_1}$, are drawn from a multivariate normal distribution $N(0, 5 I_p)$, with a fixed random seed. The coefficients for the second functional predictor, $\beta_{F_2}$, are drawn independently from the same distribution and are also smoothed using a B-spline basis with 10 basis functions.
For the vector covariates, the regression coefficients are sampled from $N(0, I_d)$. After calculating the inner product of the covariates and their corresponding coefficients, independent Gaussian noise from $N(0, 0.1^2)$ is added to the generated responses to simulate measurement noise.

The baseline methods are:
\begin{itemize}
	\item Penalized functional regression (pfr)~\cite
{goldsmith_penalized_2011}\item Principal component regression (fpcr): run both of PCA for multple functional predictors~\cite{happ_multivariate_2018} and scalar PCA and run OLS on the PC scores.
\end{itemize}
% TODO: \usepackage{graphicx} required

We compare our method with these baseline methods using $p=100$. We consider scenarios with $d=1, 2, 3, 4, 5$ and $n = 100, 200, 300, 400$. For each scenario, we use 70\% of the data for training and evaluate prediction performance on the remaining 30\% test set, using the root prediction mean squared error as the evaluation metric. For our method and PCR, the maximum number of components are set as 20. The number of components is chosen by 5-fold cross validation. The results, summarized in Table~\ref{table
}, demonstrate that our method consistently outperforms the baseline methods across all scenarios.
\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{Screenshot 2025-02-25 125839.png}
    \caption{Enter Caption}
    \label{fig:enter-label}
\end{figure}

\section{Data Application}

\medskip
\noindent
\textit{Renal study data.}~
We applied our proposed hybrid functional PLS regression, along with other regression methods, to the Emory renal study data. The study collected data on 226 kidneys (left and right) from 113 subjects, including: (i) baseline renogram curves; (ii) post-furosemide renogram curves; (iii) ordinal ratings of kidney obstruction status (non-obstructed, equivocal, or obstructed) independently assessed by three nuclear medicine experts; (iv) eight kidney-level pharmacokinetic variables derived from radionuclide imaging; and (v) two subject-level variables (age and gender). The subjects had a mean age of 57.8 years (SD = 15.5; range = 18–83), with 54 males (48\%) and 59 females (52\%). The three experts unanimously classified 153 kidneys as non-obstructed, 5 as equivocal, and 40 as obstructed, while 28 kidneys had discrepant ratings.

The two renogram curves, (i) and (ii), were treated as functional predictors and smoothed using a B-spline basis of order 15. The remaining variables, excluding the diagnosis, were treated as scalar predictors. Given the nature of these variables, we assume they are correlated with the renogram curves but not entirely redundant, as they may contain additional useful information. Finally, the diagnoses provided by the three experts were averaged and transformed using a min-max logit transformation. We splitted the data into 70\% of training data and 30\% of testing data, and evalauted the prediction perforamnec by root mean squared error on the test data, normalized by the range of the test data response.

\subsection{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Overview of Appendix}

\section{Technical lemmas}

\section{Proofs of Propositions}
$\boldsymbol{\cdot}$ \underline{Abbreviations}
\begin{itemize}
    \item[--] ``CSI": Cauchy–Schwarz inequality
\end{itemize}

\subsection{Proof of Propositions \ref{Proposition: generalized rayleigh quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
We show that the solutions to the generalized eigenvalue problems \eqref{def:eigenproblem_smoothed} and \eqref{eq: Regularized generalized rayleigh quotient equation} maximize the covariance with the response.
Based on the basis function expansions  $X_i^{(k)}(t) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t)$ and $\psi^{(k)}(t) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t)$, $k=1, \ldots, K$, we can express the sample covariance between the PLS score and the outcome, which needs to be maximized to estimate the corresponding PLS component, as:
\begin{align*}
    \widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \boldsymbol{\xi} \rangle_\mathcal{H} Y_i \\
    &=  \frac{1}{n} \sum \limits_{i=1}^n  \langle X_i, \psi \rangle_\mathcal{F} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n  \langle \mathbf{Z}_i, \boldsymbol{\theta} \rangle Y_i \\
    &=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
     &=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
    &= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{C}^{(k)} \left\{ \int_{\mathcal{T}_k} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \widetilde{Z} \boldsymbol{\theta} \\
    &= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \widetilde{Z} \boldsymbol{\theta} \\
    &= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \widetilde{Z} \boldsymbol{\theta}).
\end{align*}
This implies that
\begin{align*}
     \widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) &= n^{-2} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \widetilde{Z} \boldsymbol{\theta}) (\widetilde{C}J\mathbf{a} + \widetilde{Z} \boldsymbol{\theta})^\top \widetilde{\mathbf{y}} \\
     &= n^{-2} \{\mathbf{a}^\top J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J \mathbf{a} +  \mathbf{a}^\top J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z} \boldsymbol{\theta} +  \boldsymbol{\theta} \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J \mathbf{a} + \boldsymbol{\theta}^\top \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z} \boldsymbol{\theta}\} \\
     &= \begin{bmatrix}
         \mathbf{a}^\top & \boldsymbol{\theta}^\top
     \end{bmatrix}
     \begin{bmatrix}
        n^{-2} J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J & n^{-2} J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z}  \\
        n^{-2} \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J & n^{-2} \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z}
     \end{bmatrix} 
     \begin{bmatrix}
         \mathbf{a} \\ \boldsymbol{\theta}
     \end{bmatrix} \\
     &\equiv \boldsymbol{\xi}^{*T} V^\ast \boldsymbol{\xi}^*.
\end{align*}
Also, the unit norm constraint of the PLS components in $\mathcal{H}$ can be translated into:
\begin{align*}
    \langle \boldsymbol{\xi}, \boldsymbol{\xi} \rangle_{\mathcal{H}} &= \sum \limits_{k=1}^K \int_{\mathcal{T}} \psi^{(k)}(t_k) \psi^{(k)}(t_k) dt_k + \boldsymbol{\theta}^{\top} \boldsymbol{\theta} \\
    &= \sum \limits_{k=1}^K  \int_\mathcal{T} \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top   \mathbf{a}^{(k)} dt_k + \boldsymbol{\theta}^{\top} \boldsymbol{\theta} \\
    &= \sum \limits_{k=1}^K  \mathbf{a}^{(k)\top} J^{(k)}   \mathbf{a}^{(k)} + \boldsymbol{\theta}^{\top} \boldsymbol{\theta} \\
    &= \mathbf{a}^\top J \mathbf{a} + \boldsymbol{\theta}^{\top} \boldsymbol{\theta} \\
    &= \boldsymbol{\xi}^{*\top} J^\ast  \boldsymbol{\xi}^{*} \\ 
    &= 1 \\
\end{align*}

Thus, the first step of the PLS algorithm translates into solving
\begin{equation*}
    \max \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1,
\end{equation*}
or equivalently solving
\begin{equation*}
    \max \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*},
\end{equation*}
where $J^\ast = \mathrm{blkdiag}[J, I_p] \in \mathbb{R}^{MK+p}$. In other words, the PLS component is chosen to maximize the squared sample covariance  $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) = \boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^*$ subject to the constraint $\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1$.

% Similar in spirit to the regularized principal component analysis (see equation [9.1] of \citealp{Ramsay2005}), one way to penalize the squared sample covariance $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )$ is to divide it by $\{ 1+ \kappa \textnormal{PEN}(\psi) \}$, where $\textnormal{PEN}(\psi)$ is a roughness penalty term. This leads to the penalized squared sample covariance
% \begin{equation*}
%         \frac{\boldsymbol{\xi}^{*T} V^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*T} J^\ast \boldsymbol{\xi}^* + \kappa \textnormal{PEN}(\psi)},
% \end{equation*}
% whose maximizer corresponds to a smoothed PLS component that maximizes $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)$ over the class of all functions satisfying sufficient smoothness conditions.

\vspace{1cm}
\noindent $\boldsymbol{\cdot}$  \underline{\textbf{Proposition 3}}

$\mathcal{U}$ is \textit{positive} because for every $\mathbf{h} \in \mathcal{H}$,
\begin{equation*}
    \langle \mathcal{U} \mathbf{h}, \mathbf{h} \rangle_\mathcal{H} = \langle \langle \Sigma_{YW}, \mathbf{h} \rangle_{\mathcal{H}} \, \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}^2 \ge 0.
\end{equation*}

$\mathcal{U}$ is \textit{self-adjoint} because for any $\mathbf{h}_1, \mathbf{h}_2 \in \mathcal{H}$,
\begin{align*}
  \langle \mathcal{U} \mathbf{h}_1, \mathbf{h}_2 \rangle_\mathcal{H}  &= \langle \langle \mathbf{h}_1, \Sigma_{YW} \rangle_\mathcal{H} \Sigma_{YW}, \mathbf{h}_2 \rangle_\mathcal{H} \\
  &= \langle \mathbf{h}_1, \Sigma_{YW} \rangle_\mathcal{H} \langle \Sigma_{YW}, \mathbf{h}_2 \rangle_\mathcal{H} \\
  &= \langle \mathbf{h}_1,  \langle \Sigma_{YW}, \mathbf{h}_2 \rangle_\mathcal{H} \Sigma_{YW} \rangle_\mathcal{H}\\ 
  &= \langle \mathbf{h}_1, \mathcal{U} \mathbf{h}_2 \rangle_\mathcal{H}.
\end{align*}

Next, We will show that an image of a bounded family in $\mathcal{H}$ under $\mathcal{U}$ is uniformly bounded and equicontinuous, and then apply the Arzel\'{a}-Ascoli theorem to show $\mathcal{U}$ is \textit{compact}. Let $\mathcal{B}=\{\mathbf{h} \in \mathcal{H}: \Vert \mathbf{h} \Vert_\mathcal{H}^2 \le B\}$ denote a bounded family in $\mathcal{H}$ for some constant $0 < B < \infty$. Clearly, $\mathbf{h}=(f, \mathbf{v}) \in \mathcal{B}$ also implies $\Vert f \Vert_\mathcal{F}^2 \le B$ and $\Vert \mathbf{v} \Vert^2 \le B$. Define $\mathcal{I}  = \{\mathcal{U}\mathbf{h}: \mathbf{h} \in \mathcal{B}\}$ as the image of  $\mathcal{B}$ under $\mathcal{U}$. We will first show that $\mathcal{I}$ is a family of uniformly bounded functions with respect to arguments on $\mathcal{T}$. Let $\mu(\mathcal{T}_k)$ denote a Lebesgue measure of $\mathcal{T}_k$, and let $T = \max_{k=1, \ldots, K} \, \mu(\mathcal{T}_k)$. Then for any $g \in \mathcal{I}$ and $\mathbf{t} \in \mathcal{T}$,
\begin{align*}
    \Vert g[\mathbf{t}] \Vert^2 &= \Vert (\mathcal{U}\mathbf{h})[\mathbf{t}] \Vert^2 \\
    &= \Vert \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} \, \Sigma_{YW}[\mathbf{t}] \Vert^2 \\
    &= \left( \langle \sigma_{YX}, f \rangle_\mathcal{F} + \langle \sigma_{YZ}, \mathbf{v} \rangle \right)^2 \Vert [\sigma_{YX}^\top(\mathbf{t}), \sigma_{YZ}^\top]^\top \Vert^2 \\
    &\le \left( \langle \sigma_{YX}, \sigma_{YX} \rangle_\mathcal{F}^{1/2} \langle f, f \rangle_\mathcal{F}^{1/2} + \langle \sigma_{YZ}, \sigma_{YZ} \rangle^{1/2} \langle \mathbf{v}, \mathbf{v} \rangle^{1/2} \right)^2 \Vert [\sigma_{YX}^\top(\mathbf{t}), \sigma_{YZ}^\top]^\top \Vert^2 \quad (\because \textnormal{CSI})\\
    &= \left[ \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \sigma_{YX}^{(k)2}(t_k) dt_k \right\}^{\frac{1}{2}} \Vert f \Vert_\mathcal{F} + \left(\sum \limits_{r=1}^p \sigma_{YZ, r}^2 \right)^{\frac{1}{2}} \Vert \mathbf{v} \Vert \right]^2 \left(\sum \limits_{k=1}^K \sigma_{YX}^{(k)2}(t_k) + \sum \limits_{r=1}^p \sigma^2_{YZ,r} \right) \\
    & \le \left\{ \left(\sum \limits_{k=1}^K \int_{\mathcal{T}_k} Q_1 dt_k \right)^{\frac{1}{2}} B^{\frac{1}{2}} + \left(\sum \limits_{r=1}^p Q_2 \right)^{\frac{1}{2}} B^{\frac{1}{2}} \right\}^2 \left( \sum \limits_{k=1}^K Q_1 + \sum \limits_{r=1}^p Q_2 \right) \\
    &= B \left\{(KTQ_1)^{\frac{1}{2}} + (PQ_2)^\frac{1}{2} \right\}^2 (KQ_1 +pQ_2) < \infty.
\end{align*}
We now show that $\mathcal{I}$ is equicontinuous. For $\epsilon > 0$, define 
\begin{equation*}
    \tilde{\epsilon} = \frac{\epsilon}{(KB)^{1/2} \{(KTQ_1)^{1/2} + (PQ_2)^{1/2}\}}
\end{equation*}
By the continuity assumption of $\sigma_{YX}^{(k)}$, there exists $\delta_k > 0$ such that
\begin{equation*}
    |t_k - t_k^*| < \delta_k \implies |\sigma^{(k)}(t_k) - \sigma^{(k)}(t_k^*)|< \tilde{\epsilon},
\end{equation*}
for all $k=1, \ldots, K$.
Set $\delta = \min_{k=1, \ldots, K} \delta_k$, and let $\Vert \mathbf{t} - \mathbf{t}^* \Vert < \delta$, with $\mathbf{t}=(t_1, \ldots, t_K)$ and $\mathbf{t}^*=(t_1^*, \ldots, t_K^*)$. Clearly, $|t_k - t^*_k| < \delta$ for all $k=1, \ldots, K$, so for $g \in \mathcal{I}$, we can establish that
\begin{align*}
    \Vert g[\mathbf{t}] - g[\mathbf{t}^*] \vert^2 &= \Vert (\mathbf{U}\mathbf{h})[\mathbf{t}] - (\mathbf{U}\mathbf{h})[\mathbf{t}^*] \Vert^2 \\
    &= \Vert \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} \Sigma_{YW}[\mathbf{t}] - \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} \Sigma_{YW}[\mathbf{t}^*] \Vert^2 \\
    &= \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}^2 \Vert \Sigma_{YW}[\mathbf{t}]- \Sigma_{YW}[\mathbf{t}^*] \Vert^2 \\
    &= \left( \langle \sigma_{YX}, f \rangle_\mathcal{F} + \langle \sigma_{YZ}, \mathbf{v} \rangle \right)^2 \left\Vert 
    \begin{bmatrix}
        \sigma_{YX}(\mathbf{t}) \\
        \sigma_{YZ}
    \end{bmatrix} -
    \begin{bmatrix}
        \sigma_{YX}(\mathbf{t}^*) \\
        \sigma_{YZ}
    \end{bmatrix}
    \right\Vert^2  \\
    &\stackrel{CSI}{\le} \left( \langle \sigma_{YX}, \sigma_{YX} \rangle_\mathcal{F}^{1/2} \langle f, f \rangle_\mathcal{F}^{1/2} + \langle \sigma_{YZ}, \sigma_{YZ} \rangle^{1/2} \langle \mathbf{v}, \mathbf{v} \rangle^{1/2} \right)^2 \left\Vert 
    \begin{bmatrix}
        \sigma_{YX}(\mathbf{t})-\sigma_{YX}(\mathbf{t}^*) \\
        \mathbf{0}
    \end{bmatrix}
    \right\Vert^2 \\
    &= \left[ \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \sigma_{YX}^{(k)2}(t_k) dt_k \right\}^{\frac{1}{2}} \Vert f \Vert_\mathcal{F} + \left(\sum \limits_{r=1}^p \sigma_{YZ, r}^2 \right)^{\frac{1}{2}} \Vert \mathbf{v} \Vert \right]^2 \sum \limits_{k=1}^K  \left\{\sigma_{YX}^{(k)}(t_k) -\sigma_{YX}^{(k)}(t_k^*) \right\}^2 \\
    &\le B \left\{(KTQ_1)^{\frac{1}{2}} + (PQ_2)^\frac{1}{2} \right\} K\tilde{\epsilon}^2 = \epsilon^2.
\end{align*}
Now we can apply the Arzel\'{a}-Ascoli theorem to conflude that for any bounded sequence $\{\mathbf{h}_n\}_{n \in \mathbb{N}} \in \mathcal{B}$, the sequence $\{\mathbf{g}_n = \mathcal{U}\mathbf{h}_n\}_{n \in \mathbb{N}} \in \mathcal{I}$ contains a convergent subsequence. Therefore, $\mathcal{U}$ is a compact operator.

\vspace{1cm}
\noindent $\boldsymbol{\cdot}$  \underline{\textbf{Proposition 4}}

Before we prove Proposition 4, we state and prove the following lemma:
\begin{lemma}
$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^*$.
\end{lemma}
Proof.

\noindent First, we have:
\begin{equation*}
    \langle \mathcal{C}_{YW} \mathbf{h}, d \rangle = E\{ \langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} d
\end{equation*}
Also, we have:
\begin{equation*}
    \langle \mathbf{h}, \mathcal{C}_{WY} d \rangle_{\mathcal{H}} = \langle \mathbf{h}, E(Y\mathbf{W})d \rangle_{\mathcal{H}} = E \langle \mathbf{h}, Y \mathbf{W} d \rangle_{\mathcal{H}}  = E\{ \langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} d.
\end{equation*}
Thus, $\langle \mathcal{C}_{YW} \mathbf{h}, d \rangle =  \langle \mathbf{h}, \mathcal{C}_{WY} d \rangle_{\mathcal{H}}$, and this implies $\mathcal{C}_{WY} = \mathcal{C}_{YW}^*$.

\noindent Now we prove Proposition 4. The singular value decomposition of $\mathcal{C}_{YW}$ is given by
\begin{equation*}
    \mathcal{C}_{YW} = \sum \limits_{j=1}^\infty \iota_j (f_{1j} \otimes f_{2j}).
\end{equation*}
Let $\Vert \cdot \Vert_{op}$ denote an operator norm. Then, applying Theorem 4.3.4 in \citet{Hsing2015}, we can show that
\begin{equation*}
    \Vert \mathcal{C}_{YW} \Vert_{op} = \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} | \mathcal{C}_{YW} \mathbf{h} |^2 
    = \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} | E(\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y)|^2 
    = \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} \textnormal{Cov}^2(\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H}, Y) 
    = \kappa_1^2,
\end{equation*}
with maximum attained at $\mathbf{h}=f_{11}$, which is an eigenfunction of  $\mathcal{C}_{YW}^* \, \circ \, \mathcal{C}_{YW} = \mathcal{C}_{WY} \, \circ \, \mathcal{C}_{YW} = \mathcal{U}$ corresponding to the largest eigenvalue $\kappa_1^2.$

\vspace{1cm}
\noindent $\boldsymbol{\cdot}$  \underline{\textbf{Proposition 5}}

Firstly, it is obvious by the unit-norm constraint enforced in Proposition 4 that:
\begin{align*}
    \langle \langle \hat{\boldsymbol{\xi}}_l,  \hat{\boldsymbol{\xi}}_l \rangle \rangle &= \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}  \\
    &= \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_{\mathcal{T}_k} \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
    &= \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \hat{\mathbf{a}}^{(k) \top}_l \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k) \top}(t_k) \hat{\mathbf{a}}^{(k)}_l  dt_k + \boldsymbol{\theta}_l^\top \boldsymbol{\theta}_l + \sum \limits_{k=1}^K \lambda_k \int_{\mathcal{T}_k} \hat{\mathbf{a}}^{(k) \top}_l \ddot{\mathbf{b}}^{(k)}(t_k) \ddot{\mathbf{b}}^{(k) \top}(t_k) \hat{\mathbf{a}}^{(k)}_l  dt_k \\
    & = \sum \limits_{k=1}^K \hat{\mathbf{a}}_l^{(k) \top} J^{(k)} \hat{\mathbf{a}}_l^{(k)} + \boldsymbol{\theta}_l^\top \boldsymbol{\theta}_l +  \sum \limits_{k=1}^K \lambda_k \hat{\mathbf{a}}^{(k) \top}_l \ddot{J}^{(k)} \hat{\mathbf{a}}^{(k)}_l \\
    & = \hat{\boldsymbol{\xi}}_l^{*\top} J^\ast \hat{\boldsymbol{\xi}}_l^* + \hat{\boldsymbol{\xi}}_l^{*\top} \Lambda \ddot{J}^\ast \hat{\boldsymbol{\xi}}_l^* = \hat{\boldsymbol{\xi}}_l^{*\top} (J^\ast +\Lambda \ddot{J}^\ast) \hat{\boldsymbol{\xi}}_l^* = 1
\end{align*}
where $\ddot{\mathbf{b}}^{(k)}(t_k) = (\ddot{b}_1^{(k)}(t_k), \ldots, \ddot{b}_M^{(k)}(t_k))^\top$

Now to prove the orthogonality, we first express the $l$-th residualized hybrid predictor in terms of its previous $(l-1)$-th version:
\begin{equation*}
    \widetilde{W}^{[l]}[\mathbf{t}] = \widetilde{W}^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\delta}}_l[\mathbf{t}]^\top 
\end{equation*}
which, after applying the finite-dimensional form (9), implies that
\begin{align*}
    \widetilde{C}^{*[l]}B^*[\mathbf{t}] &=\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1}\widehat{\mathbf{d}}^*_{l-1}B^*[\mathbf{t}] \\
    &= \widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} J^\ast \left(\widehat{\boldsymbol{\rho}}_{i,l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1} J^\ast \right)^{-1} B^*[\mathbf{t}] \\
    & =\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] -  \left(\frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \widetilde{C}^{*[l-1]} B^*[\mathbf{t}] \\
    &= \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \widetilde{C}^{*[l-1]} B^*[\mathbf{t}].
\end{align*}
Thus, we have
\begin{align*}
    \widetilde{W}^{[l]}[\mathbf{t}] &= \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \widetilde{W}^{[l-1]}[\mathbf{t}] \\
    &= \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{l-2} \widehat{\boldsymbol{\rho}}_{l-2}^\top}{\widehat{\boldsymbol{\rho}}_{l-2}^\top \widehat{\boldsymbol{\rho}}_{l-2}} \right) \widetilde{W}^{[l-2]}[\mathbf{t}] \\
    &= P \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right)\widetilde{W}^{[j]}[\mathbf{t}]
\end{align*}
where $P$ is an $n \times n$ matrix defined as
\begin{equation*}
    P = \prod \limits_{h=j+1}^{l-1} \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{h} \widehat{\boldsymbol{\rho}}_{h}^\top}{\widehat{\boldsymbol{\rho}}_{h}^\top \widehat{\boldsymbol{\rho}}_{h}} \right)
\end{equation*}
Then for $j < l$,
\begin{align*}
\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_j[\mathbf{t}] d\mathbf{t} &= \int_{\mathcal{T}} P   \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right)\widetilde{W}^{[j]}[\mathbf{t}]  \widehat{\boldsymbol{\xi}}_k[\mathbf{t}] d\mathbf{t}  \\
&= P \left\{\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_j[\mathbf{t}] d\mathbf{t} - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_j[\mathbf{t}] d\mathbf{t} \right\} \\ 
&=P \left( \widehat{\boldsymbol{\rho}}_j - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \widehat{\boldsymbol{\rho}}_j \right) \\
&= P(\widehat{\boldsymbol{\rho}}_j-\widehat{\boldsymbol{\rho}}_j) \\
&= \mathbf{0} \in \mathbb{R}^n, 
\end{align*}
noting that $\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_j[\mathbf{t}] d\mathbf{t} = \widehat{\boldsymbol{\rho}}_j$. Now by the generalized eigenvalue problem (i.e., generalized Rayleigh quotient problem) presented in Proposition 2, we have that for $j < l$,
\begin{align*}
    \langle \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle \rangle &= \widehat{\boldsymbol{\xi}}_l^{*\top} (J^\ast + \Lambda \ddot{J}^\ast)\widehat{\boldsymbol{\xi}}_j^{*} \\
    & = \frac{1}{\kappa_l} (V^\ast_l \widehat{\boldsymbol{\xi}}_l^{*})^\top \widehat{\boldsymbol{\xi}}_j^{*} \\
    &=  \frac{1}{\kappa_l}\widehat{\boldsymbol{\xi}}_l^{* \top} V^\ast_l \widehat{\boldsymbol{\xi}}_j^{*} \\
    &= \frac{1}{\kappa_l}\widehat{\boldsymbol{\xi}}_l^{* \top} \left(n^{-2} J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top} \widetilde{C}^{*[l]} J^\ast \right) \widehat{\boldsymbol{\xi}}_j^{*} \\
    &= \frac{1}{n^2\kappa_l}\widehat{\boldsymbol{\xi}}_l^{* \top} \ J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top}  \widetilde{C}^{*[l]}\left(\int_{\mathcal{T}} B^*[\mathbf{t}] B^*[\mathbf{t}]^\top d\mathbf{t}  \right) \widehat{\boldsymbol{\xi}}_j^{*} \\
    &= \frac{1}{n^2\kappa_l}\widehat{\boldsymbol{\xi}}_l^{* \top}  J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top}  \left(\int_{\mathcal{T}} \widetilde{C}^{*[l]} B^*[\mathbf{t}] B^*[\mathbf{t}]^\top \widehat{\boldsymbol{\xi}}_j^{*} d\mathbf{t}  \right)   \\
    &= \frac{1}{n^2\kappa_l}\widehat{\boldsymbol{\xi}}_l^{* \top}  J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top}  \left(\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_j[\mathbf{t}] d\mathbf{t}  \right)   \\
    &=0, 
\end{align*}
where the last equality follows from the above result that $\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_j[\mathbf{t}] d\mathbf{t} = \mathbf{0}$.

\vspace{1cm}
\noindent $\boldsymbol{\cdot}$  \underline{\textbf{Proposition 6}}

First note that $\widehat{\boldsymbol{\rho}}_l = \int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_l[\mathbf{t}] d\mathbf{t}= \widetilde{C}^{*[l]} J^\ast \widehat{\boldsymbol{\xi}}^*_{l}$ for $l=1, \ldots, L$. Then, as above, we first express the $l$-th residualized hybrid predictor in terms of its previous $(l-1)$-th version:
\begin{equation*}
    \widetilde{W}^{[l]}[\mathbf{t}] = \widetilde{W}^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\delta}}_l[\mathbf{t}]^\top 
\end{equation*}
which, after applying the finite-dimensional form (9), implies that
\begin{equation*}
\setlength{\jot}{10pt}
\begin{aligned}
    \widetilde{C}^{*[l]}B^*[\mathbf{t}] &=\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1}\widehat{\mathbf{d}}^*_{l-1}B^*[\mathbf{t}] \\
    &= \widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} J^\ast \left(\widehat{\boldsymbol{\rho}}_{i,l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1} J^\ast \right)^{-1} B^*[\mathbf{t}] \\
    & =\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] -  \frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} B^*[\mathbf{t}]}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}}  \\
    & =\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] -  \frac{\widetilde{C}^{*[l-1]} J^\ast \widehat{\boldsymbol{\xi}}^{*}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} B^*[\mathbf{t}]}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}},
\end{aligned}
\end{equation*}
Since the equation should hold for all argument values $\mathbf{t} \in \mathcal{T}$, we can write:
\begin{equation*}
\setlength{\jot}{10pt}
\begin{aligned}
     \widetilde{C}^{*[l]} &= \widetilde{C}^{*[l-1]} -  \frac{\widetilde{C}^{*[l-1]} J^\ast \widehat{\boldsymbol{\xi}}^{*}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]}}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \\
     &= \widetilde{C}^{*[l-1]} \left(I_{MK+p} - \frac{J^\ast \widehat{\boldsymbol{\xi}}^{*}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]}}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \\
     &= \widetilde{C}^{*[j]} \left(I_{MK+p} - \frac{J^\ast \widehat{\boldsymbol{\xi}}^{*}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P},
\end{aligned}
\end{equation*}
where $\widetilde{P}$ is a $(MK+p) \times (MK+p)$ matrix defined as
\begin{equation*}
    \widetilde{P} = \prod \limits_{h=j+1}^{l-1} \left(I_{MK+p} - \frac{J^\ast \hat{\boldsymbol{\xi}}^*_h \widehat{\boldsymbol{\rho}}_{h}^\top \widetilde{C}^{*[h]}}{\widehat{\boldsymbol{\rho}}_{h}^\top \widehat{\boldsymbol{\rho}}_{h}} \right)
\end{equation*}
Then, for $j < l$,
\begin{equation*}
\setlength{\jot}{10pt}
\begin{aligned}
     \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[l]} &=  \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} \left(I_{MK+p} - \frac{J^\ast \widehat{\boldsymbol{\xi}}^{*}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P} \\
     &=\left( \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} - \frac{ \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} J^\ast \widehat{\boldsymbol{\xi}}^{*}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P} \\
     &=\left( \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} - \frac{ \widehat{\boldsymbol{\rho}}_j^\top \widehat{\boldsymbol{\rho}}_j  \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P} \\
     &= \left(  \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} -  \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} \right) \widetilde{P} \\
     &= \mathbf{0} \in \mathbb{R}^{1 \times (MK+p)},
\end{aligned}
\end{equation*}
Therefore, for $j < l$,
\begin{equation*}
    \widehat{\boldsymbol{\rho}}_j^\top \widehat{\boldsymbol{\rho}}_l =  \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[l]} J^\ast \widehat{\boldsymbol{\rho}}_{l} = \mathbf{0} J^\ast \widehat{\boldsymbol{\rho}}_{l}=  0.
\end{equation*}
Thus, the proposition is proved.

\section{Simulations} \label{Simulations}

\bibliographystyle{apa} 
\bibliography{Reference}

\end{document}

### 2025-06-26 manuscript/prev.tex
started manuscript logging

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[comma,authoryear]{natbib} 
\usepackage[margin=1in]{geometry}

\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage[flushleft]{threeparttable}
\usepackage[labelfont=bf]{caption}
\usepackage{caption,booktabs,array}
\usepackage{multirow}
\usepackage{makecell}
\usepackage[usenames, dvipsnames]{color}
\usepackage{setspace}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{rotating}
 \usepackage{url}
 \usepackage{enumerate}
 \allowdisplaybreaks

\setstretch{1.8} % For 25 lines per page

\title{Partial Least Squares Regression with Multiple Functional and Scalar Predictors}
\author{Jeong Hoon Jang}
\date{\today}

\begin{document}
\maketitle

\section{Data Objects and Model Formulation} 
Let $\{X^{(k)}\}_{k=1, \ldots, K}$ be a collection of random functions defined on respective compact domains $\mathcal{T}_k \in \mathbb{R}^{d_k}$ ($d_k \in \mathbb{N})$; i.e., $X^{(k)}: \mathcal{T}_k \rightarrow \mathbb{R}$. Assume that each $X^{(k)}$ is in $L^2(\mathcal{T}_k)$, a Hilbert space of square integrable functions with respect to Lebesgue measure $dt_k$ on $\mathcal{T}_k$. Without loss of generality, we further assume that each  $\mathcal{T}_k$ is a $d_k$-dimensional unit interval; for instance  $\mathcal{T}_k=[0,1]$ (unit interval) if $d_k=1$, $\mathcal{T}_k=[0,1] \times [0,1]$ (unit square) if $d_k=2$, and so forth. Write  $X=(X^{(1)}, \ldots, X^{(K)})$ as a multivariate functional object that belongs to $\mathcal{F} = L^2(\mathcal{T}_1) \times \cdots \times L^2(\mathcal{T}_K)$---a cartesian product of individual $L^2(\mathcal{T}_k)$ spaces. Note that if $K=1$, $X$ reduces to a univariate functional object. We can also express the functional object $X$ evaluated on the multi-dimensional argument $\mathbf{t} = [t_1, \ldots t_k]^T \in \mathcal{T} = \mathcal{T}_1 \times \cdots \times \mathcal{T}_K$ as a $K$-dimensional vector $X(\mathbf{t})=[X^{(1)}(t_1), \ldots, X^{(K)}(t_K)]^T$. The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)}) $ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as $\langle f_1, f_2\rangle_\mathcal{F} = \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)} \rangle_{L^2} = \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k$ with norm $\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k)^2 dt_k\}^{1/2}$.

Let $\mathbf{Z}=[Z_1, \ldots, Z_p]^T$ denote a $p$-dimensional multivariate scalar data  in $\mathbb{R}^p$. We assume that $\mathbf{Z}$ is a random vector with finite first two moments and equipped with the Euclidean inner product and norm; i.e., for $\mathbf{v_1}=[v_{11}, \ldots, v_{1p}]^T$ and $\mathbf{v_2}=[v_{21}, \ldots, v_{2p}]^T$ in $\mathbb{R}^p$, $\langle \mathbf{v_1}, \mathbf{v_2} \rangle = \mathbf{v_1}^T \mathbf{v_2} = \sum_{r=1}^p v_{1r}v_{2r}$, and $\Vert \mathbf{v}_1 \Vert = \langle \mathbf{v}_1, \mathbf{v}_1 \rangle^{1/2} = (\sum_{r=1}^p v_{1r}^2)^{1/2}$.

Without loss of generality, assume that both functional and multivariate data are centered; that is, $E(X)=0$ and $E(\mathbf{Z})=\mathbf{0}$. Our goal is to predict a real outcome $Y$ based on $X$ and $\mathbf{Z}$ via the following functional regression model:

\begin{equation}
Y = \sum \limits_{r=1}^p \alpha_r Z_r + \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \beta^{(k)}(t_k) X^{(k)}(t_k) dt_k + \epsilon = \langle \boldsymbol{\alpha}, \mathbf{Z} \rangle +  \langle \beta, X \rangle_{\mathcal{F}}  + \epsilon
\label{eq: functional model}
\end{equation}
where $\boldsymbol{\alpha}=[\alpha_1, \ldots, \alpha_p]^T \in \mathbb{R}^p$ and $\beta=(\beta^{(1)}, \ldots, \beta^{(K)}) \in \mathcal{F}$ are respectively the regression coefficient vector and function that characterize the effect of scalar and functional predictors on the outcome.

Our strategy is to formulate a hybrid random object, $\mathbf{W} = (X, \mathbf{Z})$, which combines $X$ and $\mathbf{Z}$ into an ordered pair belonging to $\mathcal{H} = \mathcal{F} \times \mathbb{R}^p$. An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}[\mathbf{t}] = [X(\mathbf{t}), \mathbf{Z}]^T$, with $ X(\mathbf{t}) = [X^{(1)}(t_1), \ldots, X^{(K)}(t_K)]^T \in \mathbb{R}^K$ and $ \mathbf{Z} = [Z_1, \ldots, Z_p]^T  \in \mathbb{R}^p$.  We define the inner product between any two hybrid objects, $\mathbf{h}_1 = (f_1, \mathbf{v}_1)$ and $\mathbf{h}_2 = (f_2, \mathbf{v}_2)$, as
\begin{equation*}
    \langle \mathbf{h}_1, \mathbf{h}_2\rangle_{\mathcal{H}} = \langle f_1, f_2\rangle_\mathcal{F} + w \langle  \mathbf{v_1}, \mathbf{v_2} \rangle = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k + \omega \sum \limits_{r=1}^p v_{1r}v_{2r}, 
\end{equation*}
with norm $\Vert \cdot \Vert_\mathcal{H} = \langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$. $\omega$ is a positive weight that needs to be pre-specified or estimated. It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation. Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$. The results remain valid for any positive weights. Then the functional regression model \ref{eq: functional model} can be re-expressed in terms of the hybrid object as follows
\begin{equation}
    Y = \langle \boldsymbol{\eta}, \mathbf{W} \rangle_{\mathcal{H}} + \epsilon,
    \label{eq: Hybrid functional model}
\end{equation}
where $\boldsymbol{\eta} = (\beta, \boldsymbol{\alpha}) \in \mathcal{H}$ is a regression coefficient characterizing the association between the hybrid predictor $\mathbf{W}$ and the outcome $Y$.

The basic idea of partial least squares (PLS) is to simultaneously decompose the hybrid predictor $\mathbf{W}$ and the real outcome $Y$ in terms of zero mean uncorrelated PLS scores $(\rho_l)_{l \in \mathbb{N}}$ with maximum predictive performance as follows
\begin{equation}
    \mathbf{W}[\mathbf{t}] = \sum \limits_{l=1}^{\infty} \rho_{l} \boldsymbol{\delta}_l[\mathbf{t}] \quad \textnormal{and} \quad Y = \sum \limits_{l=1}^{\infty}\rho_{l} \nu_l + \epsilon,
    \label{eq: decomposition}
\end{equation}
where $(\boldsymbol{\delta}_l)_{l \in \mathbb{N}} \in \mathcal{H}$ and $(\nu_l)_{l \in \mathbb{N}} \in \mathbb{R}$ are appropriate bases. The PLS scores are obtained as $\rho_l =  \langle \mathbf{W}^{[l]}, \boldsymbol{\xi}_l \rangle_{\mathcal{H}}$, where $\mathbf{W}^{[l]}$ denotes the residualized predictor sequentially derived as the residual of the regression of $\mathbf{W}^{[l-1]}$ on $\rho_{l-1}$ with $\mathbf{W}^{[1]} = \mathbf{W}$, and $\boldsymbol{\xi}_l=(\psi_l, \boldsymbol{\theta}_l) \in \mathcal{H}$ is the PLS component sequentially chosen to maximize the squared covariance between $\rho_l$ and the residualized outcome $Y^{[l]}$---i.e., $\textnormal{Cov}^2(\rho_l, Y^{[l]}$). Here, $Y^{[l]}$ is also sequentially obtained as the residual of the regression of $Y^{[l-1]}$ on $\rho_{l-1}$ with $Y^{[1]} = Y$.

\underline{Challenges}
\begin{enumerate}
    \item Independent variables consist of multiple highly structured images and scalar predictors.
    \item Our sample size is small compared to the dimension and number of functional and scalar predictors.
    \item Existing partial least squares (PLS) methods can only accommodate (i) univariate or multivariate functional predictors without any scalar predictors \citep{Preda2005, Delaigle2012, Febrero2017, Beyaztas2020}; or (2) a univariate functional predictor with other scalar predictors \citep{Wang2018}.
\end{enumerate}

\section{Naive NIPALS Algorithm} \label{sec: NIPALS Algorithm}
Denote $\{(Y_1, \mathbf{W}_1),  \ldots, (Y_n, \mathbf{W}_n)\}$ as $n$ independent data pairs (observed sample) distributed as $(Y, \mathbf{W})$. In this section, we present the extended version of the the conventional nonlinear interative partial least square (NIPALS) algorithm which decomposes the hybrid predictor $\mathbf{W}_i$ $(i=1, \ldots, n)$ and the real response $Y_i$ in terms of zero mean uncorrelated PLS scores  $(\rho_{il})_{l \in \mathbb{N}}$ with maximum predictive performance. We first introduce the centered data $Y_i^{[1]} = Y_i - \bar{Y}$ and $\mathbf{W}_i^{[1]}=(X_i^{[1]}, \mathbf{Z}_i^{[1]})=(X_i - \bar{X}, \mathbf{Z}_i - \bar{\mathbf{Z}}) = \mathbf{W}_i - \bar{\mathbf{W}}$. Here and below, a superscript in square brackets denotes the iteration index of the algorithm. The algorithm iterates through the following steps. For $l=1, 2, \ldots, L$:

\begin{enumerate}[Step 1.]
\item Let $\hat{\rho}_{il} = \langle \mathbf{W}_{i}^{[l]}, \hat{\boldsymbol{\xi}}_{l} \rangle_{\mathcal{H}} = \langle X_i^{[l]}, \hat{\psi}_{l} \rangle_{\mathcal{F}} + \langle \mathbf{Z}_i^{[l]}, \hat{\boldsymbol{\theta}}_{l} \rangle$, where the $l$-th PLS component $\hat{\boldsymbol{\xi}}_{l} = (\hat{\psi}_{l}, \hat{\boldsymbol{\theta}}_{l}) \in \mathcal{H}$ is chosen to maximize $\textnormal{Cov}^2(\rho_{il}, Y_i^{[l]})$. Specifically, we set:
\begin{equation*}
    \hat{\boldsymbol{\xi}}_{l}[\mathbf{t}] = \frac{\sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]}[\mathbf{t}]}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} = \left[ \frac{\sum_{i=1}^n Y_i^{[l]} X_i^{[l]}(\mathbf{t})}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}}, \frac{\sum_{i=1}^n Y_i^{[l]}\mathbf{Z}_i^{[l]}}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} \right]^T.
\end{equation*}
Note, $\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}} = [\sum_{i=1}^n \sum_{j=1}^n Y_i^{[l]} Y_j^{[l]} \{\langle X_i^{[l]},X_j^{[l]} \rangle_\mathcal{F} + \langle \mathbf{Z}_i^{[l]}, \mathbf{Z}_j^{[l]} \rangle \}]^{1/2}$.

\item Obtain the subsequent residualized outcomes and predictors as $Y_i^{[l+1]} = Y_i^{[l]} - \hat{\nu}_{l} \hat{\rho}_{il}$ and $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \hat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \hat{\rho}_{il}$, where 
\begin{equation*}
    \hat{\nu}_l = \frac{\sum_{i=1}^n Y_i^{[l]} \hat{\rho}_{il}}{\sum_{i=1}^n \hat{\rho}_{il}^2} \quad \textnormal{and} \quad \hat{\boldsymbol{\delta}}_{l}[\mathbf{t}] = \frac{\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \hat{\rho}_{il}}{\sum_{i=1}^n \hat{\rho}_{il}^2}.
\end{equation*}
Note, $\hat{\nu}_l$ is the least squares estimate from linear regression of $Y_i^{[l]}$ on $\hat{\rho}_{il}$, and  $\hat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ is the least squares estimate from a linear regression of $\mathbf{W}_i^{[l]}[\mathbf{t}]$ on $\hat{\rho}_{il}$.

\item Let $l=l+1$ and back to Step 1.
\end{enumerate}

The regression coefficient $\boldsymbol{\eta}$ in model \eqref{eq: Hybrid functional model} can be written in terms of the PLS scores. First, note that we can show $\hat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \hat{\boldsymbol{\xi}}_l \rangle_\mathcal{H} = \langle \mathbf{W}_i, \hat{\boldsymbol{\zeta}}_l \rangle_\mathcal{H}$, where $\hat{\boldsymbol{\zeta}}_l = \hat{\boldsymbol{\xi}}_l - \sum_{u=1}^{l-1} \langle \hat{\boldsymbol{\delta}}_u, \hat{\boldsymbol{\xi}}_l \rangle_{\mathcal{H}} \hat{\boldsymbol{\zeta}}_u$ for $l \ge 2$, with $\hat{\boldsymbol{\zeta}}_1 = \hat{\boldsymbol{\xi}}_1$. Then, the decomposition of $Y_i$ in \eqref{eq: decomposition} leads to
\begin{equation*}
    Y_i \approx \sum \limits_{l=1}^L \hat{\nu}_l \langle \mathbf{W}_i^{[l]}, \hat{\boldsymbol{\xi}}_l \rangle_\mathcal{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\hat{\nu}_l \hat{\boldsymbol{\zeta}}_l \right\rangle_\mathcal{H}+\epsilon_i,
\end{equation*}
which, given the uniqueness of $\boldsymbol{\eta}$, leads to
\begin{equation*}
    \hat{\boldsymbol{\eta}} = \sum \limits_{l=1}^L\hat{\nu}_l \hat{\boldsymbol{\zeta}}_l.
\end{equation*}
Here, $L$ can be chosen by cross-validation.

This NIPALS algorithm, however, is performed in a pointwise manner for each observed argument $\mathbf{t}$, so it can be computationally expensive for multiple dense functional data and is not feasible for irregular functional data. Moreover, the pointwise estimates only use information from data on the particular argument value, and thus can show substantial variability across the domain, resulting in overfitting and unstable predictions. In the next section, we propose novel strategies for implementing the steps of the NIPALS algorithm. The proposed approach provides an efficient and robust means of producing PLS scores and components in the presence of multiple dense and/or irregular functional predictors and scalar predictors. It also incorporates a regularization scheme that enables the algorithm to borrow strength and exploit structural relationships within and between the functions to gain efficiency, interpretability and predictive accuracy of the PLS.

\section{Proposed NIPALS Algorithm} \label{sec: Proposed NIPALS Algorithm}

\subsection{Step 1: Computing PLS components via Eigenanalysis of the cross-covariance based operator}  \label{subsec: Step 1: Computing PLS components via Eigenanalysis of the cross-covariance based operator}
To simplify notation, we omit the iteration index $l$, with the understanding that the strategy presented in this section applies to any $l$-th iteration of the algorithm. We first define the cross-covariance terms between the response and predictors (residualized versions if $l \ge 2$): 
\begin{equation*}
    \begin{gathered}
       \sigma_{YX} = (\sigma_{YX}^{(1)}, \ldots, \sigma_{YX}^{(K)}) = (E(YX^{(1)}),\ldots, E(YX^{(K)})) = E(YX) \in \mathcal{F} \\
       \sigma_{YZ} = [\sigma_{YZ,1}, \ldots, \sigma_{YZ,p}]^T = [E(YZ_1),\ldots, E(YZ_p)]^T = E(Y\mathbf{Z}) \in \mathbb{R}^p \\
       \Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) =  (E(YX), E(Y\mathbf{Z}))=E(Y\mathbf{W}) \in \mathcal{H}
    \end{gathered}
\end{equation*}
We also introduce two cross-covariance operators, $\mathcal{C}_{YW}=E(\mathbf{W} \otimes_\mathcal{H} Y): \mathcal{H} \rightarrow \mathbb{R}$ and $\mathcal{C}_{WY}=E(Y \otimes \mathbf{W}): \mathbb{R} \rightarrow \mathcal{H}$, which respectively map $h=(f, \mathbf{v}) \in \mathcal{H}$ to $\mathbb{R}$ and $d \in \mathbb{R}$ to $\mathcal{H}$ as follows:
\begin{align*}
   & \mathcal{C}_{YW} \mathbf{h} = E\{\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \sigma_{YX}^{(k)}(t_k) f^{(k)}(t_k) dt_k + E(Y \mathbf{Z}^T) \mathbf{v} \\
   & \mathcal{C}_{WY} d = E (\langle Y, d \rangle \mathbf{W} ) = E(Y\mathbf{W})d =  \Sigma_{YW} \, d. 
\end{align*}

Now define a new operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$, which performs the following mapping:
 \begin{equation*}
   \mathcal{U} \mathbf{h} =  \mathcal{C}_{WY} ( \mathcal{C}_{YW} \mathbf{h}) 
   = \mathcal{C}_{YW} (\langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}) 
   =  \Sigma_{YW} \, \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = (\Sigma_{YW} \otimes \Sigma_{YW})\mathbf{h}.
 \end{equation*}
In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$. The following proposition presents several important properties of $\mathcal{U}$.
\begin{proposition} \label{Proposition: property of U}
The operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}= \Sigma_{YW} \otimes \Sigma_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ is positive and self-adjoint. Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that
\begin{align}
    \max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in \mathcal{T}_k} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
\end{align}
and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in \mathcal{T}_k$ with $|t_k - t_k^* | < \delta_k$, we have that
\begin{equation*}
    |\sigma_{yx}^{(k)}(t_k) - \sigma_{yx}^{(k)}(t_k^*) | < \epsilon,
\end{equation*}
then $\mathcal{U}$ is a compact operator.
\end{proposition}
By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\boldsymbol{\xi}_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \boldsymbol{\xi}_{(u)} = \lambda_{(u)}  \boldsymbol{\xi}_{(u)}$, where $\{\lambda_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\lambda_{(1)} \ge \lambda_{(2)} \ge \cdots \ge 0$.

The following proposition suggests a potentially alternative way of obtaining the PLS components through eigen-analysis of $\mathcal{U}$.
\begin{proposition}
\begin{equation*}
    \max \limits_{\substack{\boldsymbol{\xi} \in \mathcal{H} \\ \Vert \boldsymbol{\xi} \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)
\end{equation*}
is achieved when $\boldsymbol{\xi}$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.
\end{proposition}
In other words, $l$-th PLS component $\boldsymbol{\xi}_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.

We now propose a practical scheme for implementing the aforementioned strategy, which can ultimately replace Step 1 of the NIPALS Algorithm in Section \ref{sec: NIPALS Algorithm}. Our goal here is to obtain the first eigenfunction $\hat{\boldsymbol{\xi}}=(\hat{\psi}, \hat{\boldsymbol{\theta}})$ of the operator $\hat{\mathcal{U}} = \hat{\Sigma}_{YW} \otimes \hat{\Sigma}_{YW}$---an estimated version of $\mathcal{U}$---by solving the following eigen-equation:
\begin{equation}
\hat{\mathcal{U}} \boldsymbol{\xi} =  \hat{\lambda} \boldsymbol{\xi} \quad \Longleftrightarrow \quad (\hat{\mathcal{U}} \boldsymbol{\xi}) [\mathbf{t}] = \hat{\lambda} \boldsymbol{\xi}[\mathbf{t}], \;\; \mathbf{t} \in \mathcal{T}, 
    \label{eq: eigenequation}
\end{equation}
where $\boldsymbol{\xi}[\mathbf{t}] = [\psi(\mathbf{t})^T, \boldsymbol{\theta}^T]^T \in \mathbb{R}^{K+p}$, with $\psi(\mathbf{t}) = [\psi^{(1)}(t_1), \ldots, \psi^{(K)}(t_K)]^T \in \mathbb{R}^K$ and $\boldsymbol{\theta}=[\theta_1, \ldots, \theta_p]^T \in \mathbb{R}^p$. To achieve this goal, we propose to expand each observed function in terms of $M$ basis functions: 
\begin{equation*}
X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)=\mathbf{c}_i^{(k)T}\mathbf{b}^{(k)}(t_k), \;\; t_k \in \mathcal{T}_k, \;\; k=1, \ldots, K, \;\; i=1, \ldots, n,
\end{equation*}
where $\mathbf{c}_i^{(k)} = [c_{i1}^{(k)}, \ldots, c_{iM}^{(k)}]^T \in \mathbb{R}^M$ are basis coefficients corresponding to basis functions $\mathbf{b}^{(k)}(t)=[b^{(k)}_{1}(t_k), \ldots, b^{(k)}_{M}(t_k)]^T \in \mathbb{R}^M$. This basis expansion can be expressed collectively across $n$ observations as $\mathbf{X}^{(k)}(t_k) = C^{(k)} \mathbf{b}^{(k)}(t_k)$, where $\mathbf{X}^{(k)}(t_k)=[X_1^{(k)}(t_k), \ldots, X_n^{(k)}(t_k)]^T \in \mathbb{R}^n$, and $C^{(k)} = [\mathbf{c}_1^{(k)} \cdots \mathbf{c}_n^{(k)}]^T \in \mathbb{R}^{n \times M}$. This notation can be further extended to accommodate $K$ functional predictors as $X(\mathbf{t}) = CB(\mathbf{t})$, where $X(\mathbf{t}) = [\mathbf{X}^{(1)}(t_1) \cdots \mathbf{X}^{(K)}(t_K)] \in \mathbb{R}^{n \times K}$, $C = [C^{(1)} \cdots C^{(K)}] \in \mathbb{R}^{n \times MK}$, and $B(\mathbf{t}) = blkdiag[\mathbf{b}^{(1)}(t_1), \ldots, \mathbf{b}^{(K)}(t_K)] \in \mathbb{R}^{MK \times K}$. We can also expand the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)T} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^T \mathbf{a}$, where $\mathbf{a}^{(k)} = [a^{(k)}_{1}, \ldots, a^{(k)}_{M}]^T \in \mathbb{R}^M$, and $\mathbf{a}=[\mathbf{a}^{(1)T}, \ldots, \mathbf{a}^{(K)T}]^T \in \mathbb{R}^{MK}$.

Now let $Z = [\mathbf{Z}_1 \cdots \mathbf{Z}_n] \in \mathbb{R}^{n \times p}$ and $\mathbf{y}=[Y_1, \ldots, Y_n] \in \mathbb{R}^n$ respectively denote the scalar predictors and outcome data.  Also $J^{(k)}$ denote a $M \times M$ matrix with $(m,n)$-th entry equal to $\int_{\mathcal{T}_k} b_m^{(k)}(t) b_n^{(k)}(t) dt$, and set $J = blkdiag[J^{(1)}, \ldots, J^{(K)}] \in \mathbb{R}^{MK \times MK}$. The following proposition presents a practical and efficient approach to obtaining the first eigenfunction ($\hat{\boldsymbol{\xi}}$) of $\hat{\mathcal{U}}$.
\begin{proposition} \label{Proposition: Unregularized Eigen-equation}
Given the basis function expansions $X_i^{(k)}(t) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t)$ and $\psi^{(k)}(t) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t)$, $k=1, \ldots, K$, solving for the first eigenfunction $\hat{\boldsymbol{\xi}}=(\hat{\psi}, \hat{\boldsymbol{\theta}}) \in \mathcal{H}$ in the eigen-equation \eqref{eq: eigenequation} amounts to solving for the first eigenvector $\tilde{\boldsymbol{\xi}}=[\tilde{\mathbf{u}}^T, \tilde{\boldsymbol{\theta}}^T]^T \in \mathbb{R}^{MK + p}$ in the following eigen-equation

\begin{equation*}
    \begin{gathered}
    V \tilde{\boldsymbol{\xi}} = \lambda \tilde{\boldsymbol{\xi}} \\
    \Longleftrightarrow 
    \begin{bmatrix}
    n^{-2} J^{\frac{1}{2}} C^T \mathbf{y} \mathbf{y}^T C J^{\frac{1}{2}} & n^{-2}J^{\frac{1}{2}}C^T \mathbf{y} \mathbf{y}^T Z \\
     n^{-2} Z^T\mathbf{y}\mathbf{y}^TCJ^{\frac{1}{2}} &  n^{-2} Z^T\mathbf{y}\mathbf{y}^TZ
    \end{bmatrix}
    \begin{bmatrix}
    \tilde{\mathbf{u}} \\
    \tilde{\boldsymbol{\theta}} 
    \end{bmatrix}
    = \lambda 
    \begin{bmatrix}
     \tilde{\mathbf{u}} \\
    \tilde{\boldsymbol{\theta}} 
    \end{bmatrix},
      \end{gathered}
\end{equation*}
and then setting $\hat{\boldsymbol{\xi}}[\mathbf{t}] = [\hat{\psi}(\mathbf{t})^T, \hat{\boldsymbol{\theta}}^T]^T \in \mathbb{R}^{K+p}$ with $\hat{\psi}(\mathbf{t}) = B(\mathbf{t}) J^{-\frac{1}{2}} \tilde{\mathbf{u}}$ and $\hat{\boldsymbol{\theta}} = \tilde{\boldsymbol{\theta}}$.
\end{proposition}
Applying this proposition to the first step of the NIPALS algorithm, at each $l$-th iteration, we can obtain the PLS component $\hat{\boldsymbol{\xi}}_l$ by computing and transforming the first eigenvector of $V$, whose elements consist of or are derived from the residualized response and predictors: $\mathbf{y}^{[l]}$, $X^{[l]}(\mathbf{t})$ and $Z^{[l]}$.

\subsection{Extended Step 1: Regularization of PLS components} \label{subsec: Extended Step 1: Regularization of PLS components}
Although Proposition \ref{Proposition: Unregularized Eigen-equation} provides an efficient and principled way to compute the PLS components $\boldsymbol{\xi}$, their functional part $\psi=(\psi^{(1)}, \ldots, \psi^{(K)})$ may not be smooth, which can lead to overfitting and unstable predictions. Thus, in this section, we introduce an extension of the idea presented in Section \ref{subsec: Step 1: Computing PLS components via Eigenanalysis of the cross-covariance based operator} that yields regularized PLS components. A widely-used approach to regularizing or smoothing a function $\psi^{(k)}$ is to penalize its roughness quantified by the integrated squared second derivative:
\begin{equation*}
    \textnormal{PEN} \left(\psi^{(k)} \right) 
    =  \int_{\mathcal{T}_k} \ddot{\psi}^{(k)}(t)^2 dt = \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)},
\end{equation*}
where the last term is obtained using the basis expansion $\psi^{(k)}(t)=\mathbf{a}^{(k)T}\mathbf{b}^{(k)}(t)$, and $\ddot{J}^{(k)}$ being a $M \times M$ matrix whose $(m,n)$-th entry is equal to $\int_{\mathcal{T}_k} \ddot{b}^{(k)}_m(t) \ddot{b}^{(k)}_n(t) dt$. The penalty term that simultaneously penalizes the roughness of the $K$ functions in $\psi$ can be obtained by summing up the individual penalty terms as
\begin{equation*}
    \textnormal{PEN}(\psi) = \sum_{k=1}^K \textnormal{PEN}\left(\psi^{(k)}\right) = \sum \limits_{k=1}^K  \int_{\mathcal{T}_k} \ddot{\psi}^{(k)}(t_k)^2 dt_k = \sum \limits_{k=1}^K \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)} = \mathbf{a}^T \ddot{J} \mathbf{a},
\end{equation*}
where $\ddot{J}=blkdiag[\ddot{J}^{(1)}, \ldots, \ddot{J}^{(K)}] \in \mathbb{R}^{MK \times MK}$.

Now, maximizing $\textnormal{Cov}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)$ is not the only aim; we also want to prevent the roughness $\textnormal{PEN}(\psi)$ of the functional part of the estimated PLS component from being too large. The following proposition provides a generalized Rayleigh quotient which makes explicit this possible conflict and whose maximizer corresponds to a smoothed PLS component that maximizes the squared sample covariance $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)$ over the class of all functions satisfying sufficient smoothness conditions. 
\begin{proposition} \label{Proposition: Regularized generalized rayleigh quotient}
Consider the following basis function expansions: $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$ and $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$, Let $J^*=blkdiag[J, I_p] \in \mathbb{R}^{(MK+p) \times (MK+p)}$, $\ddot{J}^* = blkdiag[\ddot{J}, \mathbf{0}_{p \times p}] \in \mathbb{R}^{(MK+p) \times (MK+p)}$, and
\begin{equation*}
    V^* = \begin{bmatrix}
        n^{-2} JC^T \mathbf{y}\mathbf{y}^T C J & n^{-2} J C^T \mathbf{y} \mathbf{y}^T Z \\
        n^{-2} Z^T \mathbf{y} \mathbf{y}^T C J &  n^{-2} Z^T \mathbf{y} \mathbf{y}^T Z
    \end{bmatrix}
    \in \mathbb{R}^{(MK+p) \times (MK+p)}.
\end{equation*}
Then at each $l$-th iteration of the first step of the NIPALS algorithm, involving the residualized response and predictors $Y \equiv Y^{[l]}$ and $\mathbf{W} \equiv \mathbf{W}^{[l]}$, the smoothed PLS component can be obtained by solving
\begin{equation}
    \max \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK + p}} \; \; \frac{\boldsymbol{\xi}^{*T}V^* \boldsymbol{\xi}^{*}}{\boldsymbol{\xi}^{*T}J^* \boldsymbol{\xi}^{*} + \kappa \textnormal{PEN}(\psi)} \; = \; \max \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK + p}} \; \; \frac{\boldsymbol{\xi}^{*T}V^* \boldsymbol{\xi}^{*}}{\boldsymbol{\xi}^{*T}(J^* + \kappa \ddot{J}^*) \boldsymbol{\xi}^{*}}, 
    \label{eq: generalized Rayleigh quotient problem}
\end{equation}
with respect to $\boldsymbol{\xi}^*=[\mathbf{a}^{*T}, \boldsymbol{\theta}^{*T}]^T \in \mathbb{R}^{MK + p}$, and then setting $\hat{\boldsymbol{\xi}}[\mathbf{t}] = [\hat{\psi}(\mathbf{t})^T, \hat{\boldsymbol{\theta}}^T]^T =  [\mathbf{a}^{*T} B(\mathbf{t}), \boldsymbol{\theta}^{*T}]^T$, where $\kappa$ is a positive smoothing parameter that controls the trade-off between the goodness of fit and the amount of smoothness in the functional part $\psi$.
\end{proposition}
Smaller $\kappa$ produces PLS components that fit more closely to the observed data, but selecting too small value may cause overfitting. The estimated PLS component reverts back to the unregularized version of Proposition 3 as $\kappa \rightarrow 0$. On the other hand, larger $\kappa$ places more emphasis on smoothing $\psi$. In the limit $\kappa \rightarrow \infty$, each of the functions is forced to be of the form $\psi^{(k)}(t)=a+bt$ for some constants $a$ and $b$. In practice, $\kappa$ can be chosen by cross-validation.

To solve \eqref{eq: generalized Rayleigh quotient problem} in practice, we first perform a Choleski factorization: $L L^T = J^* + \kappa \ddot{J}^*$, where $L$ is a lower triangular matrix, and then reduce \eqref{eq: generalized Rayleigh quotient problem} to maximizing the classical Rayleigh quotient
\begin{equation*}
    \max \limits_{\mathbf{e} \in \mathbb{R}^{MK + p}} \, \frac{\mathbf{e}^T E \mathbf{e}}{\mathbf{e}^T \mathbf{e}} \; \Longleftrightarrow \;   \max \limits_{\substack{\mathbf{e} \in \mathbb{R}^{MK+p} \\ \Vert \mathbf{e} \Vert^2 = 1}} \;  \mathbf{e}^T E \mathbf{e},
\end{equation*}
through the transformations $\mathbf{e} = L^T \boldsymbol{\xi}^*$ and $E = L^{-1} V^* L^{T-1}$. Once $\mathbf{e}$ is obtained as the first eigenvector of $E$, we set $\boldsymbol{\xi}^* = L^{T-1} \mathbf{e}$ and $\hat{\boldsymbol{\xi}}[\mathbf{t}] = [\mathbf{a}^{*T} B(\mathbf{t}), \boldsymbol{\theta}^{*T}]^T$, which we subsequently renormalize to ensure that $\Vert \hat{\boldsymbol{\xi}} \Vert_\mathcal{H} = 1$.

\subsection{Step 2: Fitting regression model with hybrid response and scalar predictor to compute residualized outcomes} \label{subsec: Step 2: Fitting regression model with hybrid response and scalar predictor to obtain residualized outcomes}
The second step of the NIPALS algorithm is to iteratively obtain the ($l+1$)-th residualized outcome as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \hat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \hat{\rho}_{il}$, where $\hat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ is the least squares estimate from regressing the previous ($l$-th) residualized outcome $\mathbf{W}_i^{[l]}[\mathbf{t}]$ on the corresponding  PLS score $\hat{\rho}_{il}$. The pointwise least squares estimate, $\hat{\boldsymbol{\delta}}_{l}[\mathbf{t}] = (\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \hat{\rho}_{il})/(\sum_{i=1}^n \hat{\rho}_{il}^2)$, presented in Section \ref{sec: NIPALS Algorithm}, however, is  highly inefficient and may not be even feasible for multiple dense and/or irregular functional data. Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components. Therefore, in this section, we introduce a novel framework for fitting a regression with a hybrid response and scalar predictor. The framework is readily applicable to dense and irregular functional data, and supports regularization techniques to prevent overfitting and reduce variance.

Again, we omit $l$ in the notations, and let $W[\mathbf{t}]$ be an $n \times (K+p)$ matrix of our hybrid observations; that is,
\begin{equation*}
    W[\mathbf{t}] = \begin{bmatrix}
        W_1[\mathbf{t}]^T \\
        \vdots \\
        W_n[\mathbf{t}]^T
    \end{bmatrix} = 
    \begin{bmatrix}
        X_1(\mathbf{t})^T & \mathbf{Z}_1^T \\
        \vdots & \vdots \\
        X_n(\mathbf{t})^T & \mathbf{Z}_n^T
    \end{bmatrix} =
    \begin{bmatrix}
        X_1^{(1)}(t_1) & \cdots & X_1^{(K)}(t_K) & Z_{11} & \cdots & Z_{1p} \\
        \vdots & & \vdots & \vdots & &\vdots \\
        X_n^{(1)}(t_1) & \cdots & X_n^{(K)}(t_K) & Z_{n1} & \cdots  & Z_{np} \\
    \end{bmatrix}
\end{equation*}
Let $\boldsymbol{\rho}=[\rho_1, \ldots, \rho_n]^T$ be an $n$-dimensional vector of PLS scores, and let the $(K+P)$-vector $\boldsymbol{\delta}[\mathbf{t}] = [\pi(\mathbf{t})^T, \boldsymbol{\gamma}^T]^T$ denote the regression coefficient consisting of the functional part $\pi(\mathbf{t}) = [\pi^{(1)}(t_1), \ldots,\pi^{(K)}(t_K)]^T \in \mathbb{R}^K$ and scalar part $\boldsymbol{\gamma} = [\gamma_1, \ldots,\gamma_p]^T \in \mathbb{R}^p$. The hybrid-on-scalar regression model we are interested in fitting is then:
\begin{equation}
    W[\mathbf{t}] = \boldsymbol{\rho} \, \boldsymbol{\delta}[\mathbf{t}]^T + \mathbf{e}[\mathbf{t}],
    \label{eq: hybrid on scalar regression model}
\end{equation}
where $\mathbf{e}[\mathbf{t}]$ is an $n \times (K+p)$ matrix of errors.

As in Section \ref{subsec: Step 1: Computing PLS components via Eigenanalysis of the cross-covariance based operator}, each of the functions in the hybrid response can be expanded using basis functions as $X(\mathbf{t}) = CB(\mathbf{t})$. Then, augmenting the basis function matrix $B(\mathbf{t})$ with the $p-$dimensional vector of ones $\mathbf{1}_p$ as $B^*[\mathbf{t}] = blkdiag[B(\mathbf{t}), I_p] \in \mathbb{R}^{(MK+p) \times (K+p)}$, and combining the corresponding basis coefficients with the scalar predictors as $C^*=[C^{(1)} \cdots C^{(K)} \; \mathbf{Z}_1 \cdots \mathbf{Z}_p] \in \mathbb{R}^{n \times (MK+p)}$, we can write the hybrid response as: $W[\mathbf{t}] = C^* B^*[\mathbf{t}]$. Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \mathbf{d}^{(k)T} \mathbf{b}^{(k)}(t_k)$, where $\mathbf{d}^{(k)} = [d_1^{(k)}, \ldots, d_M^{(k)}]^T \in \mathbb{R}^M$ are basis coefficients. Here, a different basis system can be flexibly chosen to expand the regression coefficient, but without loss of generality we use the same system. With the $(MK+p)$-dimensional row vector $\mathbf{d}^* = [\mathbf{d}^{(1)T}, \ldots, \mathbf{d}^{(K)T}, \gamma_1, \ldots, \gamma_p]$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as: $\boldsymbol{\rho} \, \boldsymbol{\delta}[\mathbf{t}]^T = \boldsymbol{\rho} \, \mathbf{d}^* B^*[\mathbf{t}]$. Finally, these basis expansions of the hybrid response and the regression coefficient enable us to re-write the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model} in a finite-dimensional form:
\begin{equation}
    C^* B^*[\mathbf{t}] = \boldsymbol{\rho} \, \mathbf{d}^* B^*[\mathbf{t}] + \mathbf{e}[\mathbf{t}].
\label{eq: rewritten hybrid on scalar regression model}
\end{equation}

As done in Section \ref{subsec: Step 1: Computing PLS components via Eigenanalysis of the cross-covariance based operator}, we introduce a roughness penalty based on the integrated squared second derivative to regularize the functional part of the regression coefficient. Specifically, we define the following penalty term that simultaneously penalizes the roughness of the $K$ functional regression coefficients:
\begin{equation*}
   \textnormal{PEN}(\pi) = \sum \limits_{k=1}^K \textnormal{PEN}\left(\pi^{(k)} \right)  
    =   \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \ddot{\pi}^{(k)}(t_k)^2 dt_k =  \sum \limits_{k=1}^K \mathbf{d}^{(k)T} \ddot{J}^{(k)} \mathbf{d}^{(k)} = \mathbf{d}^* \ddot{J}^* \mathbf{d}^{*T}.
\end{equation*}
In our framework, we do not attempt to regularize the functional part of the hybrid response and allow it to be of high resolution, so as to prevent smoothing away important information in the response data that may impact the regression coefficient estimate.

Based on the model formulation \eqref{eq: rewritten hybrid on scalar regression model} and the penalty term $\textnormal{PEN}(\pi)$, we can now formulate the following penalized least squares criterion whose minimizing solution gives the regularized estimate of the regression coefficient $\boldsymbol{\delta}[\mathbf{t}]$ in the hybrid-on-scalar regression model \eqref{eq: Hybrid functional model}:
\begin{equation}
\begin{aligned}
    \textnormal{PENSSE}(\delta) &= \int_\mathcal{T} \left\Vert \,  C^* B^*[\mathbf{t}] - \boldsymbol{\rho} \, \mathbf{d}^* B^*[\mathbf{t}] \, \right\Vert_F^2 \, d\mathbf{t} + \tau \mathbf{d}^* \ddot{J}^* \mathbf{d}^{*T} \\
    &= tr\left(C^{*T}C^*J^* \right) - 2\,tr \left(\mathbf{d}^* J^* C^{*T} \boldsymbol{\rho} \right) + tr\left(\boldsymbol{\rho}^T \boldsymbol{\rho} \, \mathbf{d}^* J^* \mathbf{d}^{*T}\right) + \tau \, tr\left(\mathbf{d}^* \ddot{J}^* \mathbf{d}^{*T}\right),
\end{aligned}
\label{eq: penalized least squares}
\end{equation}
where $tr$ denotes the trace of a matrix, $\Vert \cdot \Vert_F$ is a Frobenius norm, and $\tau$ is a positive smoothing parameter that controls the trade-off between the goodness of fit and the amount of smoothness in the functional regression coefficient $\pi$. Now taking the derivative of \eqref{eq: penalized least squares} with respect to $\mathbf{d}^*$ and setting the result to zero, we find that  $\mathbf{d}^*$ satisfies the system of linear equations
\begin{equation*}
    \boldsymbol{\rho}^T \boldsymbol{\rho} \, \mathbf{d}^*  J^* + \tau \mathbf{d}^* \ddot{J}^* =  \boldsymbol{\rho}^T  C^* J^*,
\end{equation*}
which leads to the following solutions for $\mathbf{d}^*$ and $\boldsymbol{\delta}[\mathbf{t}]$:
\begin{equation*}
  \widehat{\mathbf{d}}^*  =  \boldsymbol{\rho}^T  C^* J^* \left(\boldsymbol{\rho}^T \boldsymbol{\rho} J^* + \tau \ddot{J}^* \right)^{-1} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}[\mathbf{t}] = B^*[\mathbf{t}]^T \, \widehat{\mathbf{d}}^{*T}.
\end{equation*}
The smoothing parameter $\tau$ may be chosen by cross-validation.

\section*{Appendix: Proofs of Propositions}
$\boldsymbol{\cdot}$ \underline{Abbreviations}
\begin{itemize}
    \item[--] ``CSI": Cauchy–Schwarz inequality
\end{itemize}

\noindent $\boldsymbol{\cdot}$  \underline{\textbf{Proposition 1}}

$\mathcal{U}$ is \textit{positive} because for every $\mathbf{h} \in \mathcal{H}$,
\begin{equation*}
    \langle \mathcal{U} \mathbf{h}, \mathbf{h} \rangle_\mathcal{H} = \langle \langle \Sigma_{YW}, \mathbf{h} \rangle_{\mathcal{H}} \, \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}^2 \ge 0.
\end{equation*}

$\mathcal{U}$ is \textit{self-adjoint} because for any $\mathbf{h}_1, \mathbf{h}_2 \in \mathcal{H}$,
\begin{align*}
  \langle \mathcal{U} \mathbf{h}_1, \mathbf{h}_2 \rangle_\mathcal{H}  &= \langle \langle \mathbf{h}_1, \Sigma_{YW} \rangle_\mathcal{H} \Sigma_{YW}, \mathbf{h}_2 \rangle_\mathcal{H} \\
  &= \langle \mathbf{h}_1, \Sigma_{YW} \rangle_\mathcal{H} \langle \Sigma_{YW}, \mathbf{h}_2 \rangle_\mathcal{H} \\
  &= \langle \mathbf{h}_1,  \langle \Sigma_{YW}, \mathbf{h}_2 \rangle_\mathcal{H} \Sigma_{YW} \rangle_\mathcal{H}\\ 
  &= \langle \mathbf{h}_1, \mathcal{U} \mathbf{h}_2 \rangle_\mathcal{H}.
\end{align*}

Next, We will show that an image of a bounded family in $\mathcal{H}$ under $\mathcal{U}$ is uniformly bounded and equicontinuous, and then apply the Arzel\'{a}-Ascoli theorem to show $\mathcal{U}$ is \textit{compact}. Let $\mathcal{B}=\{\mathbf{h} \in \mathcal{H}: \Vert \mathbf{h} \Vert_\mathcal{H}^2 \le B\}$ denote a bounded family in $\mathcal{H}$ for some constant $0 < B < \infty$. Clearly, $\mathbf{h}=(f, \mathbf{v}) \in \mathcal{B}$ also implies $\Vert f \Vert_\mathcal{F}^2 \le B$ and $\Vert \mathbf{v} \Vert^2 \le B$. Define $\mathcal{I}  = \{\mathcal{U}\mathbf{h}: \mathbf{h} \in \mathcal{B}\}$ as the image of  $\mathcal{B}$ under $\mathcal{U}$. We will first show that $\mathcal{I}$ is a family of uniformly bounded functions with respect to arguments on $\mathcal{T}$. Let $\mu(\mathcal{T}_k)$ denote a Lebesgue measure of $\mathcal{T}_k$, and let $T = \max_{k=1, \ldots, K} \, \mu(\mathcal{T}_k)$. Then for any $g \in \mathcal{I}$ and $\mathbf{t} \in \mathcal{T}$,
\begin{align*}
    \Vert g[\mathbf{t}] \Vert^2 &= \Vert (\mathcal{U}\mathbf{h})[\mathbf{t}] \Vert^2 \\
    &= \Vert \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} \, \Sigma_{YW}[\mathbf{t}] \Vert^2 \\
    &= \left( \langle \sigma_{YX}, f \rangle_\mathcal{F} + \langle \sigma_{YZ}, \mathbf{v} \rangle \right)^2 \Vert [\sigma_{YX}^T(\mathbf{t}), \sigma_{YZ}^T]^T \Vert^2 \\
    &\le \left( \langle \sigma_{YX}, \sigma_{YX} \rangle_\mathcal{F}^{1/2} \langle f, f \rangle_\mathcal{F}^{1/2} + \langle \sigma_{YZ}, \sigma_{YZ} \rangle^{1/2} \langle \mathbf{v}, \mathbf{v} \rangle^{1/2} \right)^2 \Vert [\sigma_{YX}^T(\mathbf{t}), \sigma_{YZ}^T]^T \Vert^2 \quad (\because \textnormal{CSI})\\
    &= \left[ \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \sigma_{YX}^{(k)2}(t_k) dt_k \right\}^{\frac{1}{2}} \Vert f \Vert_\mathcal{F} + \left(\sum \limits_{r=1}^p \sigma_{YZ, r}^2 \right)^{\frac{1}{2}} \Vert \mathbf{v} \Vert \right]^2 \left(\sum \limits_{k=1}^K \sigma_{YX}^{(k)2}(t_k) + \sum \limits_{r=1}^p \sigma^2_{YZ,r} \right) \\
    & \le \left\{ \left(\sum \limits_{k=1}^K \int_{\mathcal{T}_k} Q_1 dt_k \right)^{\frac{1}{2}} B^{\frac{1}{2}} + \left(\sum \limits_{r=1}^p Q_2 \right)^{\frac{1}{2}} B^{\frac{1}{2}} \right\}^2 \left( \sum \limits_{k=1}^K Q_1 + \sum \limits_{r=1}^p Q_2 \right) \\
    &= B \left\{(KTQ_1)^{\frac{1}{2}} + (PQ_2)^\frac{1}{2} \right\}^2 (KQ_1 +pQ_2) < \infty.
\end{align*}
We now show that $\mathcal{I}$ is equicontinuous. For $\epsilon > 0$, define 
\begin{equation*}
    \tilde{\epsilon} = \frac{\epsilon}{(KB)^{1/2} \{(KTQ_1)^{1/2} + (PQ_2)^{1/2}\}}
\end{equation*}
By the continuity assumption of $\sigma_{YX}^{(k)}$, there exists $\delta_k > 0$ such that
\begin{equation*}
    |t_k - t_k^*| < \delta_k \implies |\sigma^{(k)}(t_k) - \sigma^{(k)}(t_k^*)|< \tilde{\epsilon},
\end{equation*}
for all $k=1, \ldots, K$.
Set $\delta = \min_{k=1, \ldots, K} \delta_k$, and let $\Vert \mathbf{t} - \mathbf{t}^* \Vert < \delta$, with $\mathbf{t}=(t_1, \ldots, t_K)$ and $\mathbf{t}^*=(t_1^*, \ldots, t_K^*)$. Clearly, $|t_k - t^*_k| < \delta$ for all $k=1, \ldots, K$, so for $g \in \mathcal{I}$, we can establish that
\begin{align*}
    \Vert g[\mathbf{t}] - g[\mathbf{t}^*] \vert^2 &= \Vert (\mathbf{U}\mathbf{h})[\mathbf{t}] - (\mathbf{U}\mathbf{h})[\mathbf{t}^*] \Vert^2 \\
    &= \Vert \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} \Sigma_{YW}[\mathbf{t}] - \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} \Sigma_{YW}[\mathbf{t}^*] \Vert^2 \\
    &= \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}^2 \Vert \Sigma_{YW}[\mathbf{t}]- \Sigma_{YW}[\mathbf{t}^*] \Vert^2 \\
    &= \left( \langle \sigma_{YX}, f \rangle_\mathcal{F} + \langle \sigma_{YZ}, \mathbf{v} \rangle \right)^2 \left\Vert 
    \begin{bmatrix}
        \sigma_{YX}(\mathbf{t}) \\
        \sigma_{YZ}
    \end{bmatrix} -
    \begin{bmatrix}
        \sigma_{YX}(\mathbf{t}^*) \\
        \sigma_{YZ}
    \end{bmatrix}
    \right\Vert^2  \\
    &\stackrel{CSI}{\le} \left( \langle \sigma_{YX}, \sigma_{YX} \rangle_\mathcal{F}^{1/2} \langle f, f \rangle_\mathcal{F}^{1/2} + \langle \sigma_{YZ}, \sigma_{YZ} \rangle^{1/2} \langle \mathbf{v}, \mathbf{v} \rangle^{1/2} \right)^2 \left\Vert 
    \begin{bmatrix}
        \sigma_{YX}(\mathbf{t})-\sigma_{YX}(\mathbf{t}^*) \\
        \mathbf{0}
    \end{bmatrix}
    \right\Vert^2 \\
    &= \left[ \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \sigma_{YX}^{(k)2}(t_k) dt_k \right\}^{\frac{1}{2}} \Vert f \Vert_\mathcal{F} + \left(\sum \limits_{r=1}^p \sigma_{YZ, r}^2 \right)^{\frac{1}{2}} \Vert \mathbf{v} \Vert \right]^2 \sum \limits_{k=1}^K  \left\{\sigma_{YX}^{(k)}(t_k) -\sigma_{YX}^{(k)}(t_k^*) \right\}^2 \\
    &\le B \left\{(KTQ_1)^{\frac{1}{2}} + (PQ_2)^\frac{1}{2} \right\} K\tilde{\epsilon}^2 = \epsilon^2.
\end{align*}
Now we can apply the Arzel\'{a}-Ascoli theorem to conflude that for any bounded sequence $\{\mathbf{h}_n\}_{n \in \mathbb{N}} \in \mathcal{B}$, the sequence $\{\mathbf{g}_n = \mathcal{U}\mathbf{h}_n\}_{n \in \mathbb{N}} \in \mathcal{I}$ contains a convergent subsequence. Therefore, $\mathcal{U}$ is a compact operator.

\vspace{1cm}
\noindent $\boldsymbol{\cdot}$  \underline{\textbf{Proposition 2}}

Before we prove Proposition 2, we state and prove the following lemma:
\begin{lemma}
$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^*$.
\end{lemma}
Proof.

\noindent First, we have:
\begin{equation*}
    \langle \mathcal{C}_{YW} \mathbf{h}, d \rangle = E\{ \langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} d
\end{equation*}
Also, we have:
\begin{equation*}
    \langle \mathbf{h}, \mathcal{C}_{WY} d \rangle_{\mathcal{H}} = \langle \mathbf{h}, E(Y\mathbf{W})d \rangle_{\mathcal{H}} = E \langle \mathbf{h}, Y \mathbf{W} d \rangle_{\mathcal{H}}  = E\{ \langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} d.
\end{equation*}
Thus, $\langle \mathcal{C}_{YW} \mathbf{h}, d \rangle =  \langle \mathbf{h}, \mathcal{C}_{WY} d \rangle_{\mathcal{H}}$, and this implies $\mathcal{C}_{WY} = \mathcal{C}_{YW}^*$.

\noindent Now we prove Proposition 2. The singular value decomposition of $\mathcal{C}_{YW}$ is given by
\begin{equation*}
    \mathcal{C}_{YW} = \sum \limits_{j=1}^\infty \iota_j (f_{1j} \otimes f_{2j}).
\end{equation*}
Let $\Vert \cdot \Vert_{op}$ denote an operator norm. Then, applying Theorem 4.3.4 in \citet{Hsing2015}, we can show that
\begin{equation*}
    \Vert \mathcal{C}_{YW} \Vert_{op} = \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} | \mathcal{C}_{YW} \mathbf{h} |^2 
    = \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} | E(\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y)|^2 
    = \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} \textnormal{Cov}^2(\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H}, Y) 
    = \iota_1^2,
\end{equation*}
with maximum attained at $\mathbf{h}=f_{11}$, which is an eigenfunction of  $\mathcal{C}_{YW}^* \mathcal{C}_{YW} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW} = \mathcal{U}$ corresponding to the largest eigenvalue $\iota_1^2.$

\vspace{1cm}
\noindent $\boldsymbol{\cdot}$  \underline{\textbf{Proposition 3}}

Based on outcome data $\mathbf{y}$ and the basis expansions of the functional predictors $X$, the consistent estimator for $\sigma_{YX}$ can be written as
\begin{equation*}
\begin{gathered}
   \hat{\sigma}_{YX}^{(k)}(t) = \frac{1}{n} \sum \limits_{i=1}^n X_i^{(k)}(t) Y_i = \frac{1}{n} \mathbf{y}^T C^{(k)} \mathbf{b}^{(k)}(t), \; t \in \mathcal{T}_k
   \quad \textnormal{or equivalently,} 
   \\ \hat{\sigma}_{YX}(\mathbf{t}) = \frac{1}{n} X(\mathbf{t})^T \mathbf{y} = \frac{1}{n} B(\mathbf{t})^T C^T \mathbf{y}, \; \mathbf{t} \in \mathcal{T}.
 \end{gathered}
 \label{eq: consistent sigma-yx}
\end{equation*}
We can also obtain the consistent estimator of $\sigma_{YZ}$ using the scalar predictors $Z$ and outcome data $\mathbf{y}$ as
\begin{equation*}
       \hat{\sigma}_{YZ} = \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z_i} Y_i= \frac{1}{n} Z^T \mathbf{y}.
       \label{eq: consistent sigma-yz}
\end{equation*}

Now consider the left hand side of the eigen-equation \eqref{eq: eigenequation}. Based on the basis expansions of $\psi$ (functional part of $\boldsymbol{\xi}$) and the consistent estimators of $\sigma_{YX}$ and $\sigma_{YZ}$, we have:
\begin{align*}
    (\hat{\mathcal{U}} \boldsymbol{\xi}) [\mathbf{t}] &=  \langle \hat{\Sigma}_{YW}, \boldsymbol{\xi} \rangle_{\mathcal{H}} \, \hat{\Sigma}_{YW}[\mathbf{t}] \\
    &= \{ \langle \hat{\sigma}_{YX}, \psi \rangle_\mathcal{F} + \langle \hat{\sigma}_{YZ}, \boldsymbol{\theta} \rangle \} \hat{\Sigma}_{YW}[\mathbf{t}] \\
    &= \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \hat{\sigma}_{YX}^{(k)} (t_k) \psi^{(k)}(t_k) dt_k + \hat{\sigma}_{YZ}^T \boldsymbol{\theta} \right\} \hat{\Sigma}_{YW}[\mathbf{t}] \\
    &= \left[ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \left\{\frac{1}{n} \mathbf{y}^T C^{(k)} \mathbf{b}^{(k)}(t_k) \right\} \left\{\mathbf{b}^{(k)}(t_k)^T \mathbf{a}^{(k)}\right\} dt_k + \frac{1}{n} \mathbf{y}^T Z \boldsymbol{\theta} \right] \hat{\Sigma}_{YW}[\mathbf{t}] \\
    &= \frac{1}{n} \left[ \sum \limits_{k=1}^K \mathbf{y}^T C^{(k)} \left\{\int_{\mathcal{T}_k} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^T dt_k \right\} \mathbf{a}^{(k)} + \mathbf{y}^T Z \boldsymbol{\theta} \right] \hat{\Sigma}_{YW}[\mathbf{t}] \\
    &= \frac{1}{n} \mathbf{y}^T \left\{ \sum \limits_{k=1}^K C^{(k)} J^{(k)} \mathbf{a}^{(k)} + Z \boldsymbol{\theta} \right\} \hat{\Sigma}_{YW}[\mathbf{t}] \\
    &= \frac{1}{n} \mathbf{y}^T (CJ \mathbf{a} +  Z \boldsymbol{\theta}) 
    \begin{bmatrix}
     \hat{\sigma}_{YX}(\mathbf{t}) \\
     \hat{\sigma}_{YZ}
    \end{bmatrix} \\
    &= \frac{1}{n} \mathbf{y}^T (CJ \mathbf{a} +  Z \boldsymbol{\theta}) 
     \begin{bmatrix}
     n^{-1} B(\mathbf{t})^T C^T \mathbf{y} \\
     n^{-1} Z^T \mathbf{y}
    \end{bmatrix} \\
    &=  \begin{bmatrix}
     n^{-2} \,  \mathbf{y}^T (CJ \mathbf{a} +  Z \boldsymbol{\theta}) B(\mathbf{t})^T C^T \mathbf{y} \\
     n^{-2} \, \mathbf{y}^T (CJ \mathbf{a} +  Z \boldsymbol{\theta})  Z^T \mathbf{y}
    \end{bmatrix}
\end{align*}
Also the write hand side of the eigen-equation \eqref{eq: eigenequation} can be written as
\begin{equation*}
    \lambda \boldsymbol{\xi}[\mathbf{t}] = \lambda 
    \begin{bmatrix}
    \psi(\mathbf{t}) \\
    \boldsymbol{\theta}
    \end{bmatrix}
    = \lambda 
    \begin{bmatrix}
    B(\mathbf{t})^T \mathbf{a} \\
    \boldsymbol{\theta}
    \end{bmatrix}.
\end{equation*}
Thus, solving the eigen-equation \eqref{eq: eigenequation} amounts to solving the following system of equations:
\begin{equation*}
    \begin{cases}
    n^{-2} \,  \mathbf{y}^T (CJ \mathbf{a} +  Z \boldsymbol{\theta}) B(\mathbf{t})^T C^T \mathbf{y} =  \lambda B(\mathbf{t})^T \mathbf{a}\\
    n^{-2} \, \mathbf{y}^T (CJ \mathbf{a} +  Z \boldsymbol{\theta})  Z^T \mathbf{y} =  \lambda \boldsymbol{\theta}.
    \end{cases}
\end{equation*}
Since the first equation should hold for all argument values $\mathbf{t} \in \mathcal{T}$, we can write:
\begin{equation*}
    \begin{cases}
    n^{-2} \,  \mathbf{y}^T (CJ \mathbf{a} +  Z \boldsymbol{\theta}) C^T \mathbf{y} =   \lambda \mathbf{a}\\
    n^{-2} \, \mathbf{y}^T (CJ \mathbf{a} +  Z \boldsymbol{\theta})  Z^T \mathbf{y} =  \lambda \boldsymbol{\theta}.
    \end{cases}
\end{equation*}
This leads to:
\begin{equation*}
    \begin{cases}
    n^{-2} \,  C^T \mathbf{y} \mathbf{y}^T CJ \mathbf{a} +  n^{-2} \, C^T \mathbf{y} \mathbf{y}^T Z \boldsymbol{\theta} =   \lambda \mathbf{a}\\
    n^{-2} \, Z^T \mathbf{y}  \mathbf{y}^T CJ \mathbf{a} + n^{-2} \, Z^T \mathbf{y}  \mathbf{y}^T Z \boldsymbol{\theta}  =  \lambda \boldsymbol{\theta}.
    \end{cases}
\end{equation*}
Now define $\mathbf{u}= J^{\frac{1}{2}} \mathbf{a}$. Then we have:
\begin{equation*}
    \begin{cases}
    n^{-2} \,  C^T \mathbf{y} \mathbf{y}^T C J J^{-\frac{1}{2}} \mathbf{u} +  n^{-2} \, C^T \mathbf{y} \mathbf{y}^T Z \boldsymbol{\theta} =   \lambda J^{-\frac{1}{2}} \mathbf{u}\\
    n^{-2} \, Z^T \mathbf{y}  \mathbf{y}^T C J J^{-\frac{1}{2}} \mathbf{u} + n^{-2} \, Z^T \mathbf{y}  \mathbf{y}^T Z \boldsymbol{\theta}  =  \lambda \boldsymbol{\theta},
    \end{cases}
\end{equation*}
which implies
\begin{align*}
   & \begin{cases}
    n^{-2} \,  J^{\frac{1}{2}} C^T \mathbf{y} \mathbf{y}^T C J^{\frac{1}{2}} \mathbf{u} +  n^{-2} \, J^{\frac{1}{2}} C^T \mathbf{y} \mathbf{y}^T Z \boldsymbol{\theta} =   \lambda  \mathbf{u}\\
    n^{-2} \, Z^T \mathbf{y}  \mathbf{y}^T C J^{\frac{1}{2}} \mathbf{u} + n^{-2} \, Z^T \mathbf{y}  \mathbf{y}^T Z \boldsymbol{\theta}  =  \lambda \boldsymbol{\theta},
    \end{cases} \\
    & \implies \begin{bmatrix}
    n^{-2} \, J^{\frac{1}{2}} C^T \mathbf{y} \mathbf{y}^T C J^{\frac{1}{2}} & n^{-2} \, J^{\frac{1}{2}} C^T \mathbf{y} \mathbf{y}^T Z \\
    n^{-2} \, Z^T \mathbf{y}  \mathbf{y}^T C J^{\frac{1}{2}} & n^{-2} \, Z^T \mathbf{y}  \mathbf{y}^T Z
    \end{bmatrix} 
    \begin{bmatrix}
    \mathbf{u} \\ \boldsymbol{\theta}
    \end{bmatrix}
    = \lambda 
        \begin{bmatrix}
    \mathbf{u} \\ \boldsymbol{\theta}
    \end{bmatrix} \\
    & \implies V \tilde{\boldsymbol{\xi}} = \lambda  \tilde{\boldsymbol{\xi}}. 
\end{align*}
Therefore, to obtain the first eigenfunction $\hat{\boldsymbol{\xi}}=(\hat{\psi}, \boldsymbol{\theta})$ of $\hat{\mathcal{U}}$, we find the first eigenvector $\tilde{\boldsymbol\xi}=[\mathbf{u}^T, \boldsymbol{\theta}^T]^T$ of the $(MK + p) \times (MK +p)$ matrix $V$, and then set $\psi(\mathbf{t}) = B(\mathbf{t}) J^{-\frac{1}{2}} \mathbf{u}$.

\vspace{1cm}
\noindent $\boldsymbol{\cdot}$  \underline{\textbf{Proposition 4}}

Firstly, we convert the maximization problem of Proposition 2 to a problem of maximizing a generalized Rayleigh quotient. Specifically, based on the basis function expansions  $X_i^{(k)}(t) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t)$ and $\psi^{(k)}(t) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t)$, $k=1, \ldots, K$, we have:
\begin{align*}
    \widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \boldsymbol{\xi} \rangle_\mathcal{H} Y_i \\
    &=  \frac{1}{n} \sum \limits_{i=1}^n  \langle X_i, \psi \rangle_\mathcal{F} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n  \langle \mathbf{Z}_i, \boldsymbol{\theta} \rangle Y_i \\
    &=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^T \boldsymbol{\theta} Y_i \\
     &=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^T \boldsymbol{\theta} Y_i \\
    &= n^{-1} \mathbf{y}^T \left[ \sum \limits_{k=1}^K C^{(k)} \left\{ \int_{\mathcal{T}_k} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^T dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\mathbf{y}^T Z \boldsymbol{\theta} \\
    &= n^{-1} \mathbf{y}^T (C J \mathbf{a}) + n^{-1}\mathbf{y}^T Z \boldsymbol{\theta} \\
    &= n^{-1} \mathbf{y}^T (CJ\mathbf{a} + Z \boldsymbol{\theta}).
\end{align*}
This implies that
\begin{align*}
     \widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) &= n^{-2} \mathbf{y}^T (CJ\mathbf{a} + Z \boldsymbol{\theta}) (CJ\mathbf{a} + Z \boldsymbol{\theta})^T \mathbf{y} \\
     &= n^{-2} \{\mathbf{a}^T J C^T \mathbf{y} \mathbf{y}^T C J \mathbf{a} +  \mathbf{a}^T J C^T \mathbf{y} \mathbf{y}^T Z \boldsymbol{\theta} +  \boldsymbol{\theta} Z^T \mathbf{y} \mathbf{y}^T C J \mathbf{a} + \boldsymbol{\theta}^T Z^T \mathbf{y} \mathbf{y}^T Z \boldsymbol{\theta}\} \\
     &= \begin{bmatrix}
         \mathbf{a}^T & \boldsymbol{\theta}^T
     \end{bmatrix}
     \begin{bmatrix}
        n^{-2} J C^T \mathbf{y} \mathbf{y}^T C J & n^{-2} J C^T \mathbf{y} \mathbf{y}^T Z  \\
        n^{-2} Z^T \mathbf{y} \mathbf{y}^T C J & n^{-2} Z^T \mathbf{y} \mathbf{y}^T Z
     \end{bmatrix} 
     \begin{bmatrix}
         \mathbf{a} \\ \boldsymbol{\theta}
     \end{bmatrix} \\
     &\equiv \boldsymbol{\xi}^{*T} V^* \boldsymbol{\xi}^*.
\end{align*}
Thus, Proposition 2 translates into solving
\begin{equation*}
    \max \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*T} V^* \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*T} J^* \boldsymbol{\xi}^*=1,
\end{equation*}
or equivalently solving
\begin{equation*}
    \max \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*T} V^* \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*T} J^* \boldsymbol{\xi}^*},
\end{equation*}
where $J^* = blkdiag[J, I_p] \in \mathbb{R}^{MK+p}$. In other words, the PLS component is chosen to maximize the squared sample covariance  $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) = \boldsymbol{\xi}^{*T} V^* \boldsymbol{\xi}^*$ subject to the constraint $\boldsymbol{\xi}^{*T} J^* \boldsymbol{\xi}^*=1$. Similar in spirit to the regularized principal component analysis (see equation [9.1] of \citealp{Ramsay2005}), one way to penalize the squared sample covariance $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )$ is to divide it by $\{ 1+ \kappa \textnormal{PEN}(\psi) \}$, where $\textnormal{PEN}(\psi)$ is a roughness penalty term. This leads to the penalized squared sample covariance
\begin{equation*}
        \frac{\boldsymbol{\xi}^{*T} V^* \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*T} J^* \boldsymbol{\xi}^* + \kappa \textnormal{PEN}(\psi)},
\end{equation*}
whose maximizer corresponds to a smoothed PLS component that maximizes $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)$ over the class of all functions satisfying sufficient smoothness conditions.

\bibliographystyle{apa} 
\bibliography{Reference}

\end{document}

### 2025-06-26 FSHybridPLS/R/get_pls_comp.R

@@ -7,7 +7,7 @@
 #'
 #' @param W A \code{predictor_hybrid} object containing both functional and scalar predictors.
 #' @param y A numeric response vector of length equal to the number of samples in \code{W}.
-#' @param L A regularization matrix (typically positive definite) used in the generalized eigenproblem.
+#' @param L cholesky decompisition of a regularization matrix (typically positive definite) used in the generalized eigenproblem.
 #'
 #' @return A list with the following elements:
 #' \describe{
@@ -19,9 +19,6 @@
 #'
 #' @export
 get_pls_comp <- function(W, y, L){
-  # W: hybrid predictor
-  # y: response vector
-  # L: regularization hyperparameter
 
   V_star <- get_pre_corrcov(W, y)
 
@@ -31,7 +28,11 @@ get_pls_comp <- function(W, y, L){
 
   eigen_result <- eigen(E)
   e <- eigen_result$vectors[, 1]
-  if (is.complex(e)) return("stop")
+  if (is.complex(e)){
+    print("stop")
+    return("stop")
+  } 
+
 
   xi_star <- t(invL) %*% e      # xi_star solves t(L) xi = e
   xi_hat <- predictor_hybrid_from_coef(format = W, coef = xi_star)

### 2025-06-26 FSHybridPLS/R/get_pls_comp_simple.R

@@ -1,0 +1,35 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Compute First PLS Component (Direct Hilbert Averaging)
+#'
+#' Computes the first PLS component as a normalized weighted average of predictor objects,
+#' where weights are given by the centered response values.
+#'
+#' @param W A `predictor_hybrid` object containing `n_sample` observations.
+#' @param y A numeric response vector of length `n_sample`.
+#'
+#' @return A normalized `predictor_hybrid` object representing the first PLS component.
+#' @export
+get_pls_comp_simple <- function(W, y) {
+  n <- W$n_sample
+  if (length(y) != n) stop("Length of y must match number of samples in W.")
+
+  # Center the response (optional, but often improves interpretability)
+  y_centered <- y - mean(y)
+
+  # Initialize zero element
+  xi_sum <- predictor_hybrid_from_coef(W, coef = rep(0, sum(W$n_basis_list) + W$n_scalar))
+  
+  # Accumulate weighted sum: sum_i y_i * W_i
+  for (i in 1:n) {
+    Wi <- subset_predictor_hybrid(W, i)
+    xi_sum <- add.predictor_hybrid(xi_sum, Wi, alpha = y_centered[i])
+  }
+
+  # Normalize
+  norm_val <- sqrt(inprod.predictor_hybrid(xi_sum))
+  xi_hat <- add.predictor_hybrid(xi_sum, xi_sum, alpha = 1 / norm_val)
+
+  return(xi_hat)
+}
+

### 2025-06-26 FSHybridPLS/R/subset_predictor_hybrid.R

@@ -1,0 +1,15 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Extract a single observation from a predictor_hybrid object
+#'
+#' @param W A predictor_hybrid object with multiple samples.
+#' @param i Integer index of the sample to extract.
+#' @return A single-sample predictor_hybrid object.
+subset_predictor_hybrid <- function(W, i) {
+  new_Z <- matrix(W$Z[i, ], nrow = 1)
+  new_functional_list <- lapply(W$functional_list, function(fdobj) {
+    fd(coef = matrix(coef(fdobj)[, i], ncol = 1), basisobj = fdobj$basis)
+  })
+  predictor_hybrid(Z = new_Z, functional_list = new_functional_list)
+}
+

### 2025-06-26 FSHybridPLS/tests/testthat/tests.R

@@ -440,53 +440,3 @@ testthat::test_that("get_pre_corrcov handles constant and random coefficients", 
 })
 
 
-testthat::test_that("get_pls_comp runs and returns valid output with penalty-based L", {
-  suppressPackageStartupMessages(library(fda))
-  set.seed(123)
-
-  make_fd <- function(coefs, basis) {
-    fd(coef = coefs, basisobj = basis)
-  }
-
-  n_sample <- 10
-  n_scalar <- 2
-  n_functional <- 2
-
-  for (nbasis in c(3, 4, 5)) {
-    basis <- create.bspline.basis(c(0, 1), nbasis = nbasis)
-
-    # Functional predictors
-    fd1 <- make_fd(matrix(rnorm(nbasis * n_sample), nbasis, n_sample), basis)
-    fd2 <- make_fd(matrix(rnorm(nbasis * n_sample), nbasis, n_sample), basis)
-    functional_list <- list(fd1, fd2)
-
-    # Scalar predictors and response
-    Z <- matrix(rnorm(n_sample * n_scalar), n_sample, n_scalar)
-    y <- rnorm(n_sample)
-
-    # Construct hybrid predictor
-    W <- predictor_hybrid(Z = Z, functional_list = functional_list)
-
-    # Smoothing parameters
-    lambda <- rep(1e-2, n_functional)
-    L <- get_constraint_matrix_hybrid(W, lambda)
-
-    # Run and validate
-    result <- get_pls_comp(W, y, L)
-
-    # Structure check
-    expect_type(result, "list")
-    expect_named(result, c("xi_hat", "E", "V_star", "eigen_val"))
-
-    # Component checks
-    expect_s3_class(result$xi_hat, "predictor_hybrid")
-    expect_true(is.matrix(result$E))
-    expect_true(is.matrix(result$V_star))
-    expect_true(is.numeric(result$eigen_val))
-    expect_length(result$eigen_val, 1)
-    expect_false(is.complex(result$eigen_val))
-  }
-})
-
-
-

### 2025-06-27 manuscript/main.tex
start improving unregularized estimation writing

@@
 \subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}
-
+\paragraph{Basis functions.}
 For $k = 1, \ldots, K$, let us denote the system of $M$ basis functions used to approximate the $k$-th functional predictor as 
-$
-    \mathbf{b}^{(k)}(t_k)=(b^{(k)}_{1}(t_k), \ldots, b^{(k)}_{M}(t_k))^\top.
-$
+\begin{equation*}
+ \mathbf{b}^{(k)}(t_k)=(b^{(k)}_{1}(t_k), \ldots, b^{(k)}_{M}(t_k))^\top,~\text{where}~t_k \in \mathcal{T}_k.   
+\end{equation*}
+In our proposed hybrid PLS regression algorithm, this basis system is used to approximate both the predictors and the PLS components.
+It also serves as a regularization tool to borrow strength and prevent overfitting.
+
+\paragraph{Basis approximation of the hybrid predictor.}
 Then we can approximate the functional predictor observations as
@@
 
+\paragraph{Basis approximation of the PLS component.}
 We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\boldsymbol{\xi}[\mathbf{t}] = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$.
@@
 
+\paragraph{Regularization based on second-order derivatives.}
 Our proposed strategy for computing PLS component, detailed in Section \ref{sec: Regularization of PLS Components}, incorporates regularization based on second-order derivatives.
@@
 \subsubsection{Smoothed estimation of PLS components}\label{sec: pls component computation intermediate}
-Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an alternative intermediate strategy for implementing the first step of the PLS algorithm.
+Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an  intermediate strategy for implementing the first step of the PLS algorithm.
 Specifically, the following proposition states a tractable generalized eigenvalue problem (i.e.
 maximization of a generalized Rayleigh quotient) that can be solved to directly obtain a hybrid PLS component $\widehat{\boldsymbol{\xi}}=(\widehat{\psi}, \widehat{\boldsymbol{\theta}})$, which has the same structure as the hybrid predictor $\mathbf{W}=(X,\mathbf{Z})$ of model \eqref{eq: Hybrid functional model}.
+
+At the $l$-th iteration, we denote, for simplicity, the residualized response and the hybrid predictors in basis approximation form as follows:
+\begin{equation*}
+    Y_i \equiv Y_i^{[l]} \quad \text{and}  \quad \mathbf{W}_i \equiv \mathbf{W}_i^{[l]},
+    \widetilde{W}[\mathbf{t}]
+\end{equation*}
+respectively.
+ consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
+Let
 \begin{proposition} \label{Proposition: generalized rayleigh quotient}
-At each $l$-th iteration of the first step of the PLS algorithm involving the residualized response and predictors $Y_i \equiv Y_i^{[l]}$ and $\mathbf{W}_i \equiv \mathbf{W}_i^{[l]}$, consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
-Let
+
 \jongmin{in the (1,1)th block, should $ \mathbf{y}$ be replaced by $\widetilde{\mathbf{y}} $? }

### 2025-06-27 manuscript/main.tex
intro paragraph simplified. no more eigenproblem

@@
 	Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an intermediate strategy for implementing the first step of the PLS algorithm.
-Specifically, the following proposition states a tractable generalized eigenvalue problem (i.e.
-maximization of a generalized Rayleigh quotient) that can be solved to directly obtain a hybrid PLS component $\widehat{\boldsymbol{\xi}}=(\widehat{\psi}, \widehat{\boldsymbol{\theta}})$, which has the same structure as the hybrid predictor $\mathbf{W}=(X,\mathbf{Z})$ of model \eqref{eq: Hybrid functional model}.
+This approach directly obtains a hybrid PLS component, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply solving a linear equation.
 

### 2025-06-28 manuscript/main.tex
remove y tilde notation

@@
 	We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\boldsymbol{\xi}[\mathbf{t}] = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$.
-We denote the outcome data as
-	\begin{equation}
-		\widetilde{\mathbf{y}}=(Y_1, \ldots, Y_n)^\top \in \mathbb{R}^n.
-	\end{equation}
 	%
@@
 	%
-	The finite-basis approximation allows us to represent the hybrid predictor observations using the coefficient matrix $\widetilde{C}^\ast$, enabling all associated computations to be carried out via matrix operations involving $\widetilde{C}^\ast$, $J^\ast$, and $\ddot{J}^\ast$.
+	The finite-basis approximation allows us to represent the hybrid predictor observations using the coefficient matrix $\widetilde{ \mathbf{C} }^\ast$, enabling all associated computations to be carried out via matrix operations involving $\widetilde{ \mathbf{C} }^\ast$, $J^\ast$, and $\ddot{J}^\ast$.
 
@@
 	Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an intermediate strategy for implementing the first step of the PLS algorithm.
-This approach directly obtains a hybrid PLS component, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply solving a linear equation.
-
-	At the $l$-th iteration, we denote, for simplicity, the residualized response and the hybrid predictors in basis approximation form as follows:
-	\begin{equation*}
-		Y_i \equiv Y_i^{[l]} \quad \text{and}  \quad \mathbf{W}_i \equiv \mathbf{W}_i^{[l]},
-		\widetilde{W}[\mathbf{t}]
-	\end{equation*}
-	respectively.
-	consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
+This approach directly obtains a hybrid PLS direction, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply solving a linear equation.
+
+We now describe the strategy for computing the PLS direction at the $l$-th iteration.
+For simplicity, we omit the iteration index and denote the residualized responses by $\mathbf{Y} \in \mathbb{R}^n$,
+and
+let $\widetilde{\mathbf{C}}^\ast$ denote
+the coefficients of the basis approximation of the residualized hybrid predictors by . 
+ Our strategy finds the direction $\boldsymbol{\xi} \in \mathcal{H}$ that minimizes the empirical covariance between the 
+\begin{align*}
+	\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, \mathbf{Y} ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \boldsymbol{\xi} \rangle_\mathcal{H} Y_i
+\end{align*}
+
+%	consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
 Let

### 2025-06-28 manuscript/main.tex
V^\ast to \mathbf{V}^\ast

@@
 	\begin{equation}\label{eq: basis approximation of W}
-		\widetilde{W}[\mathbf{t}] =  \widetilde{C}^* B^*[\mathbf{t}], \quad t \in \mathcal{T}.
-	\end{equation}
-	where  $B^*[\mathbf{t}] = \mathrm{blkdiag}(B(\mathbf{t}), I_p) \in \mathbb{R}^{(MK+p) \times (K+p)}$ and $\widetilde{C}^*=[\widetilde{C}, \widetilde{Z}] \in \mathbb{R}^{n \times (MK+p)}$.
+		\widetilde{W}[\mathbf{t}] 
+		=  
+		\widetilde{ \mathbf{C} }^\ast B^*[\mathbf{t}], \quad t \in \mathcal{T}.
+	\end{equation}
+	where  $B^*[\mathbf{t}] = \mathrm{blkdiag}(B(\mathbf{t}), I_p) \in \mathbb{R}^{(MK+p) \times (K+p)}$ and $\widetilde{ \mathbf{C} }^\ast=[\widetilde{C}, \widetilde{Z}] \in \mathbb{R}^{n \times (MK+p)}$.
 
@@
 We now describe the strategy for computing the PLS direction at the $l$-th iteration.
-For simplicity, we omit the iteration index and denote the residualized responses by $\mathbf{Y} \in \mathbb{R}^n$,
-and
-let $\widetilde{\mathbf{C}}^\ast$ denote
-the coefficients of the basis approximation of the residualized hybrid predictors by . 
- Our strategy finds the direction $\boldsymbol{\xi} \in \mathcal{H}$ that minimizes the empirical covariance between the 
-\begin{align*}
-	\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, \mathbf{Y} ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \boldsymbol{\xi} \rangle_\mathcal{H} Y_i
-\end{align*}
-
-%	consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
-Let
-	\begin{proposition} \label{Proposition: generalized rayleigh quotient}
-
-		\jongmin{in the (1,1)th block, should $ \mathbf{y}$ be replaced by $\widetilde{\mathbf{y}} $? }
+For simplicity, we omit the iteration index and denote the residualized response by $Y$, with its finite-sample observations denoted by $\mathbf{y} = (y_1, \ldots, y_n) \in \mathbb{R}^n$.
+Let $\widetilde{W} \in \mathcal{H}$ denote the residualized, basis-approximated hybrid predictor, and let $\widetilde{\mathbf{C}}^\ast \in \mathbb{R}^{n \times (MK+p)}$ denote the basis coefficients of its finite-sample observations.
+Our strategy finds the direction $\boldsymbol{\xi} \in \mathcal{H}$ that maximizes the empirical covariance between the resulting PLS component $\langle \widetilde{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the response.
+
+For practical computation, we first construct the following matrix:
 	\begin{equation}\label{def:V_star}
@@
 \end{equation}
+
+%	consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
+Let
+	\begin{proposition} \label{Proposition: generalized rayleigh quotient}
+
+		\jongmin{in the (1,1)th block, should $ \mathbf{y}$ be replaced by $\widetilde{\mathbf{y}} $? }
+
 		and  $\boldsymbol{\xi}^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$.

### 2025-06-28 manuscript/main.tex
started abandoning the block diagonal notation

@@
 	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}
+In practice, the functional predictors $X^{(1)}, \ldots, X^{(K)}$ are not observed as complete curves, but only through their values at a finite set of time points, which may differ across the $K$ predictors.
+Thus, each observation is represented by a finite-dimensional vector $X_i^{(k)}(\mathbf{t}_k) \in \mathbb{R}^{|\mathbf{t}_k|}$, where $\mathbf{t}_k \subset \mathcal{T}_k$.
+The first step in functional data analysis typically involves reconstructing the underlying functional form from these discrete measurements, commonly by assuming that sample paths lie in a finite-dimensional space spanned by basis functions.
 	\paragraph{Basis functions.}
-	For $k = 1, \ldots, K$, let us denote the system of $M$ basis functions used to approximate the $k$-th functional predictor as 
-	\begin{equation*}
-		\mathbf{b}^{(k)}(t_k)=(b^{(k)}_{1}(t_k), \ldots, b^{(k)}_{M}(t_k))^\top,~\text{where}~t_k \in \mathcal{T}_k.   
-	\end{equation*}
+For $k = 1, \ldots, K$, let $\Phi^{(k)}:= \{\phi^{(k)}_1, \ldots, \phi^{(k)}_M\}$, with $M \geq 1$, be an $M$-dimensional basis in $L^2(\mathcal{T}_k)$.
 In our proposed hybrid PLS regression algorithm, this basis system is used to approximate both the predictors and the PLS components.
-It also serves as a regularization tool to borrow strength and prevent overfitting.
+Additionally, it serves as a regularization mechanism, borrowing strength across components and helping to prevent overfitting.
 
 	\paragraph{Basis approximation of the hybrid predictor.}	
-	Then we can approximate the functional predictor observations as
-	\begin{equation*}
-		X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)=\mathbf{c}_i^{(k)T}\mathbf{b}^{(k)}(t_k), \;\; t_k \in \mathcal{T}_k, \;\; k=1, \ldots, K, \;\; i=1, \ldots, n,
-	\end{equation*}
-	where $\mathbf{c}_i^{(k)} = (c_{i1}^{(k)}, \ldots, c_{iM}^{(k)})^\top$ is a $M$-dimensional vector of basis coefficients corresponding to the $k$th functional predictor.
-This basis approximation can be expressed collectively across $n$ observations as: $\widetilde{\mathbf{X}^{(k)}}(t_k) = \widetilde{C}^{(k)} \mathbf{b}^{(k)}(t_k)$, where $\widetilde{\mathbf{X}}^{(k)}(t_k)=(X_1^{(k)}(t_k), \ldots, X_n^{(k)}(t_k))^\top \in \mathbb{R}^n$, and $\widetilde{C}^{(k)} = (\mathbf{c}_1^{(k)} \cdots \mathbf{c}_n^{(k)})^\top \in \mathbb{R}^{n \times M}$.
-This notation can be further extended to simultaneously express the basis expansions of $K$ functional predictors as
-	\begin{equation}
-		\widetilde{X}(\mathbf{t}) = \widetilde{C}B(\mathbf{t}), \quad t \in \mathcal{T},
-		\label{eq: basis approximation of X}
-	\end{equation}
-	where $\widetilde{X}(\mathbf{t}) = [\widetilde{\mathbf{X}}^{(1)}(t_1), \cdots, \widetilde{\mathbf{X}}^{(K)}(t_K)] \in \mathbb{R}^{n \times K}$, $\widetilde{C} = [\widetilde{C}^{(1)}, \cdots, \widetilde{C}^{(K)}] \in \mathbb{R}^{n \times MK}$, and
-	$B(\mathbf{t}) = \mathrm{blkdiag}[\mathbf{b}^{(1)}(t_1), \cdots, \mathbf{b}^{(K)}(t_K)] \in \mathbb{R}^{MK \times K}$.
+	For $k = 1, \ldots, K$  and $i = 1, \ldots, n$, 	
+	 we approximate each functional predictor within the span of the basis functions $\Phi^{(k)}$ :
+\begin{equation*} 
+	X_i^{(k)} \approx  \sum_{m=1}^M   c_{im}^{(k)} \phi_m^{(k)} ,
+\end{equation*}
+where the coefficients $c_{im}^{(k)}$'s satisfy
+	\begin{equation*}
+	X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} \phi^{(k)}_{m}(t_k)~\text{for all}~t_k \in \mathbf{t}_k \subset \mathcal{T}_k,
+\end{equation*}
+
 	The number of basis functions $M$ for each functional predictor can be set to a sufficiently large value (e.g., 15 or 20) to incorporate a rich variety of patterns that functional predictors may exhibit.
 Note that there is no need to carefully choose different $M$ values for different functional predictors, as an appropriate penalization scheme will be introduced in the later section to regularize each functional predictor to achieve a desired smoothness (see Section \ref{sec: Regularization of PLS Components}).
-
-	Furthermore, let $\widetilde{Z} = [\mathbf{Z}_1, \cdots, \mathbf{Z}_n] \in \mathbb{R}^{n \times p}$ denote $n \times p$ matrix of the scalar predictors (observed version when $l=1$, or residualized version when $l \ge 2$), and let $\widetilde{W}[\mathbf{t}]=[\widetilde{X}(\mathbf{t}), \widetilde{Z}]$ denote $n \times (K+p)$ hybrid predictor matrix that stacks $\widetilde{X}(\mathbf{t})$ and $\widetilde{Z}$ as columns.
-Then we can also write the hybrid predictor, whose functional part is approximated using the basis functions, as a form of linear transformation similar to \eqref{eq: basis approximation of X}:
-	\begin{equation}\label{eq: basis approximation of W}
-		\widetilde{W}[\mathbf{t}] 
-		=  
-		\widetilde{ \mathbf{C} }^\ast B^*[\mathbf{t}], \quad t \in \mathcal{T}.
-	\end{equation}
-	where  $B^*[\mathbf{t}] = \mathrm{blkdiag}(B(\mathbf{t}), I_p) \in \mathbb{R}^{(MK+p) \times (K+p)}$ and $\widetilde{ \mathbf{C} }^\ast=[\widetilde{C}, \widetilde{Z}] \in \mathbb{R}^{n \times (MK+p)}$.
 
@@
 	%
-	For each $k = 1, \ldots, K$, let $J^{(k)} \in \mathbb{R}^{M \times M}$ denote the Gram matrix of the basis functions associated with the $k$-th functional predictor, defined by
+	For each $k = 1, \ldots, K$, let $\mathbf{J}^{(k)} \in \mathbb{R}^{M \times M}$ denote the Gram matrix of the basis functions associated with the $k$-th functional predictor, defined by
 	\begin{equation}\label{def:gram_basis}
-		J^{(k)} = \left[ \int_{\mathcal{T}k} b_m^{(k)}(t) \, b_n^{(k)}(t) , dt \right]_{m,n=1}^M.
+		\mathbf{J}^{(k)} = \left[ \int_{\mathcal{T}k} b_m^{(k)}(t) \, b_n^{(k)}(t) , dt \right]_{m,n=1}^M.
 	\end{equation}
@@
 	\begin{equation}\label{def:J_and_J_star}
-		J = \mathrm{blkdiag}(J^{(1)}, \cdots, J^{(K)}) \in \mathbb{R}^{MK \times MK}~\text{and}~J^\ast=\mathrm{blkdiag}(J, I_p) \in \mathbb{R}^{(MK+p) \times (MK+p)}.
+		\mathbf{J} = \mathrm{blkdiag}(\mathbf{J}^{(1)}, \cdots, \mathbf{J}^{(K)}) \in \mathbb{R}^{MK \times MK}~\text{and}~\mathbf{J}^\ast=\mathrm{blkdiag}(\mathbf{J}, \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (MK+p)}.
 	\end{equation}
@@
 We now describe the strategy for computing the PLS direction at the $l$-th iteration.
-For simplicity, we omit the iteration index and denote the residualized response by $Y$, with its finite-sample observations denoted by $\mathbf{y} = (y_1, \ldots, y_n) \in \mathbb{R}^n$.
-Let $\widetilde{W} \in \mathcal{H}$ denote the residualized, basis-approximated hybrid predictor, and let $\widetilde{\mathbf{C}}^\ast \in \mathbb{R}^{n \times (MK+p)}$ denote the basis coefficients of its finite-sample observations.
-Our strategy finds the direction $\boldsymbol{\xi} \in \mathcal{H}$ that maximizes the empirical covariance between the resulting PLS component $\langle \widetilde{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the response.
-
-For practical computation, we first construct the following matrix:
+For simplicity, we omit the iteration index and denote the residualized response by $Y$, with finite-sample observations given by $\mathbf{y} = (y_1, \ldots, y_n) \in \mathbb{R}^n$.
+Let $\widetilde{W} \in \mathcal{H}$ denote the residualized, basis-approximated hybrid predictor, and let $\widetilde{\mathbf{C}} \in \mathbb{R}^{n \times (MK)}$ denote the basis coefficients of its functional part in the finite-sample observations.
+Our strategy seeks the direction $\boldsymbol{\xi} \in \mathcal{H}$, lying in the span of the basis $B^*[\mathbf{t}]$, that maximizes the empirical covariance between the resulting PLS component $\langle \widetilde{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the response.
+
+For practical computation, 
+let us first denote
+\begin{equation*}
+\mathbf{b} := \mathbf{y}^\top
+[ \widetilde{\mathbf{C}} \, \mathbf{J} \, \mathbf{Z} ].
+\end{equation*}
+Then we obtain $\mathbf{d}$ by solving a linear system
+\begin{equation*}
+	\mathbf{J}^\ast \mathbf{d} =
+	\mathbf{b}^\top.
+\end{equation*}  
+Then we obtain the coefficient for the PLS direction by normalize it with respect to the basis $B^*[\mathbf{t}]$:
+\begin{equation}\label{compute:pls_direction_coeff}
+	\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
+	= \frac{1}{\sqrt{\mathbf{d}^\top \mathbf{J}^\ast \mathbf{d}}} \mathbf{d}.
+\end{equation}
+The $l$-th  PLS score for the 
+$i$th observation is then computed as the inner product  with respect to the basis $B^*[\mathbf{t}]$:
+\begin{equation*}
+	\widehat{\rho}_{i}
+	= 
+	[ \widetilde{\mathbf{C}}  \, \mathbf{Z} ] \, \mathbf{J}^\ast \begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
+\end{equation*}
+$ \equiv \widehat{\rho}_{il}$ can be obtained as $\widehat{\rho}_i = \langle \mathbf{W}_i, \widehat{\boldsymbol{\xi}} \rangle_\mathcal{H}$.
+we first construct the following matrix:
 	\begin{equation}\label{def:V_star}
-	V^\ast = n^{-2}\begin{bmatrix}
-		J \widetilde{C}^\top \mathbf{y}\mathbf{y}^\top \widetilde{C} J & J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z} \\
-		\widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J &   \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z}
-	\end{bmatrix} = n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast
+	\mathbf{V}^\ast 
+	:= 
+	n^{-2}\begin{bmatrix}
+\mathbf{J}
+\widetilde{ \mathbf{C} }^\top \mathbf{y}\mathbf{y}^\top \widetilde{ \mathbf{C} } \mathbf{J} 
+& 
+\mathbf{J} \widetilde{ \mathbf{C} }^\top 
+\mathbf{y}
+\mathbf{y}^\top 
+\mathbf{Z} 
+\\
+\mathbf{Z}^\top 
+\mathbf{y}
+\mathbf{y}^\top \widetilde{ \mathbf{C} }
+\mathbf{J} 
+&   
+\mathbf{Z}^\top 
+\mathbf{y}
+\mathbf{y}^\top 
+\mathbf{Z}
+	\end{bmatrix} = n^{-2} \mathbf{J}^\ast \widetilde{ \mathbf{C} }^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{ \mathbf{C} }^{*} \mathbf{J}^\ast
 	\in \mathbb{R}^{(MK+p) \times (MK+p)}.
@@
 	\begin{proposition} \label{Proposition: generalized rayleigh quotient}
-
-		\jongmin{in the (1,1)th block, should $ \mathbf{y}$ be replaced by $\widetilde{\mathbf{y}} $? }
-
-		and  $\boldsymbol{\xi}^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$.
-Then, the $l$-th PLS component, $\widehat{\boldsymbol{\xi}} \equiv \widehat{\boldsymbol{\xi}}_l$ can be obtained by solving
-		\begin{equation}\label{def:eigenproblem_smoothed}
-			\argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*}, \quad \textit{or equivalently}, \quad \argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1,
-		\end{equation}
-		with respect to $\widehat{\boldsymbol{\xi}}^*=(\widehat{\mathbf{a}}^{\top}, \widehat{\boldsymbol{\theta}}^{\top})^\top$, and then setting $\widehat{\boldsymbol{\xi}}[\mathbf{t}] = [\widehat{\psi}(\mathbf{t})^\top, \widehat{\boldsymbol{\theta}}^\top]^\top =  B^*[\mathbf{t}]^\top \widehat{\boldsymbol{\xi}}^*$.
-The $l$-th PLS score $\widehat{\rho}_{i} \equiv \widehat{\rho}_{il}$ can be obtained as $\widehat{\rho}_i = \langle \mathbf{W}_i, \widehat{\boldsymbol{\xi}} \rangle_\mathcal{H}$.
+		Let $\operatorname{span}(B^\ast[\mathbf{t}])$ 
+		be a linear subspace of $\mathcal{H}$ spanned by the basis functions.
+		  For any unit-length direction  $\boldsymbol{\xi} \in \operatorname{span}(B^\ast[\mathbf{t}])$,
+expressed as $
+\boldsymbol{\xi} 
+= 
+\boldsymbol{\alpha}
+B^\ast [\mathbf{t}] $ with $\boldsymbol{\alpha} \in \mathbb{R}^{MK + p}$,
+		Let us define
+		the empirical and basis-approximated sample covariance as
+\begin{equation*}
+	\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )
+	:=
+	\frac{1}{n} \sum \limits_{i=1}^n \langle \widetilde{W}_i, \boldsymbol{\xi} \rangle_\mathcal{H} y_i
+	=
+		\frac{1}{n} \sum \limits_{i=1}^n 
+	(	\tilde{\mathbf{C}}^\ast_i \mathbf{J}^\ast \boldsymbol{\alpha} ) y_i.
+\end{equation*}
+Then the coefficients computed in \eqref{compute:pls_direction_coeff}  $\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )$
+over all unit vectors in $\operatorname{span}(B^\ast[\mathbf{t}])$.
+In a more formal way:
+	\begin{equation}
+	\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
+	B^*[\mathbf{t}] \in \arg \max_{
+ \|\boldsymbol{\xi}  \| = 1, 
+	 \boldsymbol{\xi} \in \mathrm{span}(B^*[\mathbf{t}])
+	}
+		\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ).
+\end{equation}
+
 	\end{proposition}
+
 	The proof of Proposition \ref{Proposition: generalized rayleigh quotient} is given in the Appendix \ref{section:proof:eigenproblem_derivation}.
-	Here, $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y)$ is expressed as $\boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^*$ based on the aforementioned basis approximations.
-Thus, finding $\boldsymbol{\xi}^*$ that maximizes $\boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^*$ amounts to finding $\widehat{\boldsymbol{\xi}}$ that maximizes the sample squared covariance $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y)$, which is the first step of the PLS algorithm.
-The constraint $\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1$ scales the obtained PLS component to have a unit norm, that is, $\langle \widehat{\boldsymbol{\xi}}, \widehat{\boldsymbol{\xi}} \rangle_\mathcal{H}=1$.
-
-	\jongmin{
-		Another way of computing \eqref{def:eigenproblem_smoothed}, rather than solving an eigenproblem, is as follows.
-As shown in the proof in Appendix \ref{section:proof:eigenproblem_derivation}, the empirical covariance is simplified as:
-		\begin{align*}
-			\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \boldsymbol{\xi} \rangle_\mathcal{H} Y_i \\
-			&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \widetilde{Z} \boldsymbol{\theta}).
-			\\&=
-			\frac{1}{n}\tilde{\mathbf{y}}^\top
-			\begin{bmatrix} \widetilde{C}J \; \widetilde{Z} \end{bmatrix} \;      \underbrace{
-				\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
-			}_{:= \boldsymbol{\beta}}.
-		\end{align*}
-		Let us 
-		denote $\mathbf{b} =  \widetilde{\mathbf{y}}^\top \begin{bmatrix} \widetilde{C}J \; \widetilde{Z} \end{bmatrix}$.
-This is the weighted row sum of $\begin{bmatrix} \widetilde{C}J \; \widetilde{Z} \end{bmatrix}$, weighted by $\widetilde{\mathbf{y}}$.
-		Then using the symmetricity of $J^\ast$, we solve a linear system $J^\ast \mathbf{d} =
-		\mathbf{b}^\top$ to obtain $\mathbf{d}$. Then we have
-		\begin{align*}
-			\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
-			\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) 
-			%%%%%%%%%%%%%%%%%%%%%
-			&= 
-			%%%%%%%%%%%%%%%%%%%%%%%%
-			\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
-			\frac{1}{n} \mathbf{d}^\top J^\ast  \boldsymbol{\beta}
-			\\& \overset{(i)}{\leq} 
-			\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
-			\frac{1}{n} \sqrt{\mathbf{d}^\top J^\ast  \mathbf{d}}
-			\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}}
-			\\& \overset{(ii)}{=}
-			\frac{1}{n} \sqrt{\mathbf{d}^\top J^\ast  \mathbf{d}}    ,
-		\end{align*}
-		where step $(i)$ uses the Cauchy-Schwarz inequality with the inner product $\langle x, y \rangle_{J^\ast} = x^\top J^\ast y$,
-		and step $(ii)$ uses the norm constraint.
-		By the Cauchy-Schwarz inequality, the maximum displayed in the last term is obtained by a unit vector (with respect to $\langle \cdot, \cdot \rangle_{J^\ast}$) parallel to $\mathbf{d}$.
-Therefore we have
-		\begin{equation*}
-			\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
-			= \frac{1}{\sqrt{\mathbf{d}^\top  J^\ast \mathbf{d} }}\mathbf{d},
-		\end{equation*}
-		which only involves solving one linear equation.
-	}
 
@@
 		\begin{equation*}
-			V^\ast = n^{-2}\begin{bmatrix}
-				J \widetilde{C}^\top \mathbf{y}\mathbf{y}^\top \widetilde{C} J & J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z} \\
-				\widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J &   \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z}
+			\mathbf{V}^\ast = n^{-2}\begin{bmatrix}
+				J \widetilde{C}^\top \mathbf{y}\mathbf{y}^\top \widetilde{C} J & J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z} \\
+				\mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J &   \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z}
 			\end{bmatrix} = n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast
@@
 			\begin{split}
-				&\argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*\top}(J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*} , \quad \textit{or equivalently}, \\
-				&\argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*=1.
+				&\argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*\top}(J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*} , \quad \textit{or equivalently}, \\
+				&\argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*=1.
 				\label{eq: Regularized generalized rayleigh quotient equation}
@@
 	\end{equation*}
-	through the transformations $\mathbf{e} = L^\top \boldsymbol{\xi}^*$ and $E = L^{-1} V^\ast L^{\top-1}$.
+	through the transformations $\mathbf{e} = L^\top \boldsymbol{\xi}^*$ and $E = L^{-1} \mathbf{V}^\ast L^{\top-1}$.
 Once $\mathbf{e}$ is obtained as the first eigenvector of $E$, we set $\boldsymbol{\xi}^* = L^{\top-1} \mathbf{e}$ and $\widehat{\boldsymbol{\xi}}[\mathbf{t}] = B^*[\mathbf{t}]^\top \boldsymbol{\xi}^*$.
@@
 			\For{ l = 1, 2, \ldots  $T$}
-			\State $V^\ast \leftarrow n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast$
+			\State $\mathbf{V}^\ast \leftarrow n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast$
 			\Comment{ \eqref{def:V_star}}
-			\State 	$\widehat{\boldsymbol{\xi}}_l^\ast \leftarrow \argmax_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*=1
+			\State 	$\widehat{\boldsymbol{\xi}}_l^\ast \leftarrow \argmax_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*=1
 			$
@@
 
-	The regression coefficients for the first functional predictor, $\beta_{F_1}$, are drawn from a multivariate normal distribution $N(0, 5 I_p)$, with a fixed random seed.
+	The regression coefficients for the first functional predictor, $\beta_{F_1}$, are drawn from a multivariate normal distribution $N(0, 5 \mathbf{I}_p)$, with a fixed random seed.
 The coefficients for the second functional predictor, $\beta_{F_2}$, are drawn independently from the same distribution and are also smoothed using a B-spline basis with 10 basis functions.
@@
 
+	\section{old notations}
+
+	Then we can approximate the functional predictor observations as
+	\begin{equation*}
+		X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)=\mathbf{c}_i^{(k)T}\mathbf{b}^{(k)}(t_k), \;\; t_k \in \mathcal{T}_k, \;\; k=1, \ldots, K, \;\; i=1, \ldots, n,
+	\end{equation*}
+	where $\mathbf{c}_i^{(k)} = (c_{i1}^{(k)}, \ldots, c_{iM}^{(k)})^\top$ is a $M$-dimensional vector of basis coefficients corresponding to the $k$th functional predictor.
+This basis approximation can be expressed collectively across $n$ observations as: $\widetilde{\mathbf{X}^{(k)}}(t_k) = \widetilde{C}^{(k)} \mathbf{b}^{(k)}(t_k)$, where $\widetilde{\mathbf{X}}^{(k)}(t_k)=(X_1^{(k)}(t_k), \ldots, X_n^{(k)}(t_k))^\top \in \mathbb{R}^n$, and $\widetilde{C}^{(k)} = (\mathbf{c}_1^{(k)} \cdots \mathbf{c}_n^{(k)})^\top \in \mathbb{R}^{n \times M}$.
+This notation can be further extended to simultaneously express the basis expansions of $K$ functional predictors as
+	\begin{equation}
+		\widetilde{X}(\mathbf{t}) = \widetilde{C}B(\mathbf{t}), \quad t \in \mathcal{T},
+		\label{eq: basis approximation of X}
+	\end{equation}
+	where $\widetilde{X}(\mathbf{t}) = [\widetilde{\mathbf{X}}^{(1)}(t_1), \cdots, \widetilde{\mathbf{X}}^{(K)}(t_K)] \in \mathbb{R}^{n \times K}$, $\widetilde{C} = [\widetilde{C}^{(1)}, \cdots, \widetilde{C}^{(K)}] \in \mathbb{R}^{n \times MK}$, and
+	$B(\mathbf{t}) = \mathrm{blkdiag}[\mathbf{b}^{(1)}(t_1), \cdots, \mathbf{b}^{(K)}(t_K)] \in \mathbb{R}^{MK \times K}$.
+
+	Furthermore, let $
+	\mathbf{Z} = [\mathbf{Z}_1, \cdots, \mathbf{Z}_n]^\top \in \mathbb{R}^{n \times p}
+	$ denote $n \times p$ matrix of the scalar predictors (observed version when $l=1$, or residualized version when $l \ge 2$), and let $\widetilde{W}[\mathbf{t}]=[\widetilde{X}(\mathbf{t}), \mathbf{Z}]$ denote $n \times (K+p)$ hybrid predictor matrix that stacks $\widetilde{X}(\mathbf{t})$ and $\mathbf{Z}$ as columns.
+Then we can also write the hybrid predictor, whose functional part is approximated using the basis functions, as a form of linear transformation similar to \eqref{eq: basis approximation of X}:
+	\begin{equation}\label{eq: basis approximation of W}
+		\widetilde{W}[\mathbf{t}] 
+		=  
+		\widetilde{ \mathbf{C} }^\ast B^*[\mathbf{t}], \quad t \in \mathcal{T}.
+	\end{equation}
+	where  $B^*[\mathbf{t}] = \mathrm{blkdiag}(B(\mathbf{t}), \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (K+p)}$ and $\widetilde{ \mathbf{C} }^\ast=[\widetilde{C}, \mathbf{Z}] \in \mathbb{R}^{n \times (MK+p)}$.
+
 	\section{Proofs of Propositions}
@@
 	\subsection{Proof of Propositions \ref{Proposition: generalized rayleigh quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
+		Here, $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y)$ is expressed as $\boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*$ based on the aforementioned basis approximations.
+Thus, finding $\boldsymbol{\xi}^*$ that maximizes $\boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*$ amounts to finding $\widehat{\boldsymbol{\xi}}$ that maximizes the sample squared covariance $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y)$, which is the first step of the PLS algorithm.
+The constraint $\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1$ scales the obtained PLS component to have a unit norm, that is, $\langle \widehat{\boldsymbol{\xi}}, \widehat{\boldsymbol{\xi}} \rangle_\mathcal{H}=1$.
+
+	and  $\boldsymbol{\xi}^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$.
+Then, the $l$-th PLS component, $\widehat{\boldsymbol{\xi}} \equiv \widehat{\boldsymbol{\xi}}_l$ can be obtained by solving
+	\begin{equation}\label{def:eigenproblem_smoothed}
+		\argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*}, \quad \textit{or equivalently}, \quad \argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1,
+	\end{equation}
+	with respect to $\widehat{\boldsymbol{\xi}}^*=(\widehat{\mathbf{a}}^{\top}, \widehat{\boldsymbol{\theta}}^{\top})^\top$
+
 	We show that the solutions to the generalized eigenvalue problems \eqref{def:eigenproblem_smoothed} and \eqref{eq: Regularized generalized rayleigh quotient equation} maximize the covariance with the response.
@@
 		&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{C}^{(k)} \left\{ \int_{\mathcal{T}_k} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \widetilde{Z} \boldsymbol{\theta} \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \widetilde{Z} \boldsymbol{\theta} \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \widetilde{Z} \boldsymbol{\theta}).
+		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{C}^{(k)} \left\{ \int_{\mathcal{T}_k} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
+		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
+		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}).
 	\end{align*}
@@
 	\begin{align*}
-		\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) &= n^{-2} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \widetilde{Z} \boldsymbol{\theta}) (\widetilde{C}J\mathbf{a} + \widetilde{Z} \boldsymbol{\theta})^\top \widetilde{\mathbf{y}} \\
-		&= n^{-2} \{\mathbf{a}^\top J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J \mathbf{a} +  \mathbf{a}^\top J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z} \boldsymbol{\theta} +  \boldsymbol{\theta} \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J \mathbf{a} + \boldsymbol{\theta}^\top \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z} \boldsymbol{\theta}\} \\
+		\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) &= n^{-2} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}) (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta})^\top \widetilde{\mathbf{y}} \\
+		&= n^{-2} \{\mathbf{a}^\top J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J \mathbf{a} +  \mathbf{a}^\top J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} +  \boldsymbol{\theta} \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J \mathbf{a} + \boldsymbol{\theta}^\top \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta}\} \\
 		&= \begin{bmatrix}
@@
 		\begin{bmatrix}
-			n^{-2} J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J & n^{-2} J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z}  \\
-			n^{-2} \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J & n^{-2} \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z}
+			n^{-2} J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J & n^{-2} J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z}  \\
+			n^{-2} \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J & n^{-2} \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z}
 		\end{bmatrix} 
@@
 		\end{bmatrix} \\
-		&\equiv \boldsymbol{\xi}^{*T} V^\ast \boldsymbol{\xi}^*.
+		&\equiv \boldsymbol{\xi}^{*T} \mathbf{V}^\ast \boldsymbol{\xi}^*.
 	\end{align*}
@@
 	\begin{equation*}
-		\max \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1,
+		\max \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1,
 	\end{equation*}
@@
 	\begin{equation*}
-		\max \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*},
-	\end{equation*}
-	where $J^\ast = \mathrm{blkdiag}[J, I_p] \in \mathbb{R}^{MK+p}$.
-In other words, the PLS component is chosen to maximize the squared sample covariance  $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) = \boldsymbol{\xi}^{*\top} V^\ast \boldsymbol{\xi}^*$ subject to the constraint $\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1$.
+		\max \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*},
+	\end{equation*}
+	where $J^\ast = \mathrm{blkdiag}[J, \mathbf{I}_p] \in \mathbb{R}^{MK+p}$.
+In other words, the PLS component is chosen to maximize the squared sample covariance  $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) = \boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*$ subject to the constraint $\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1$.
+
+	\jongmin{
+	Another way of computing \eqref{def:eigenproblem_smoothed}, rather than solving an eigenproblem, is as follows.
+As shown in the proof in Appendix \ref{section:proof:eigenproblem_derivation}, the empirical covariance is simplified as:
+	\begin{align*}
+		\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \boldsymbol{\xi} \rangle_\mathcal{H} Y_i \\
+		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}).
+		\\&=
+		\frac{1}{n}\tilde{\mathbf{y}}^\top
+		\begin{bmatrix} \widetilde{C}J \; \mathbf{Z} \end{bmatrix} \;      \underbrace{
+			\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
+		}_{:= \boldsymbol{\beta}}.
+	\end{align*}
+	Let us 
+	denote $\mathbf{b} =  \widetilde{\mathbf{y}}^\top \begin{bmatrix} \widetilde{C}J \; \mathbf{Z} \end{bmatrix}$.
+This is the weighted row sum of $\begin{bmatrix} \widetilde{C}J \; \mathbf{Z} \end{bmatrix}$, weighted by $\widetilde{\mathbf{y}}$.
+	Then using the symmetricity of $J^\ast$, we solve a linear system $J^\ast \mathbf{d} =
+	\mathbf{b}^\top$ to obtain $\mathbf{d}$. Then we have
+	\begin{align*}
+		\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
+		\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) 
+		%%%%%%%%%%%%%%%%%%%%%
+		&= 
+		%%%%%%%%%%%%%%%%%%%%%%%%
+		\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
+		\frac{1}{n} \mathbf{d}^\top J^\ast  \boldsymbol{\beta}
+		\\& \overset{(i)}{\leq} 
+		\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
+		\frac{1}{n} \sqrt{\mathbf{d}^\top J^\ast  \mathbf{d}}
+		\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}}
+		\\& \overset{(ii)}{=}
+		\frac{1}{n} \sqrt{\mathbf{d}^\top J^\ast  \mathbf{d}}    ,
+	\end{align*}
+	where step $(i)$ uses the Cauchy-Schwarz inequality with the inner product $\langle x, y \rangle_{J^\ast} = x^\top J^\ast y$,
+	and step $(ii)$ uses the norm constraint.
+	By the Cauchy-Schwarz inequality, the maximum displayed in the last term is obtained by a unit vector (with respect to $\langle \cdot, \cdot \rangle_{J^\ast}$) parallel to $\mathbf{d}$.
+Therefore we have
+	\begin{equation*}
+		\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
+		= \frac{1}{\sqrt{\mathbf{d}^\top  J^\ast \mathbf{d} }}\mathbf{d},
+	\end{equation*}
+	which only involves solving one linear equation.
+}
 
@@
 	% \begin{equation*}
-		%         \frac{\boldsymbol{\xi}^{*T} V^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*T} J^\ast \boldsymbol{\xi}^* + \kappa \textnormal{PEN}(\psi)},
+		%         \frac{\boldsymbol{\xi}^{*T} \mathbf{V}^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*T} J^\ast \boldsymbol{\xi}^* + \kappa \textnormal{PEN}(\psi)},
 		% \end{equation*}

### 2025-06-28 manuscript/main.tex
proof of proposition 3
\label{proposition: eigenanalysis}

@@
 	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
-	\begin{proposition}
+	\begin{proposition}\label{proposition: eigenanalysis}
 		\begin{equation*}
@@
 		is achieved when $\boldsymbol{\xi}$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.	
-		\label{proposition: eigenanalysis}
 	\end{proposition}
@@
 	The following proposition states that the PLS components estimated from Proposition  \ref{Proposition: Regularized generalized rayleigh quotient} are orthonormal with respect to the modified inner product $\langle \langle \cdot \rangle \rangle$ that incorporates the roughness of the functions.
-	\begin{proposition}
+	\begin{proposition}\label{proposition: modified orthnormality of PLS components}
 		The estimated PLS components, $\widehat{\boldsymbol{\xi}}_1, \widehat{\boldsymbol{\xi}}_2, \ldots, \widehat{\boldsymbol{\xi}}_L$, from the proposed PLS algorithm are mutually orthonormal with respect to the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ in $\mathcal{H}$ that incorporates the roughness of the functions; i.e.,
@@
 		\end{equation*}
-		\label{proposition: modified orthnormality of PLS components}
+
 	\end{proposition}
@@
 
-	\vspace{1cm}
-	\noindent $\boldsymbol{\cdot}$  \underline{\textbf{Proposition 3}}
-
+\section{Proof of Proposition \ref{Proposition: property of U}}\label{section:proof:Proposition: property of U}
 	$\mathcal{U}$ is \textit{positive} because for every $\mathbf{h} \in \mathcal{H}$,
@@
 
-	\vspace{1cm}
-	\noindent $\boldsymbol{\cdot}$  \underline{\textbf{Proposition 4}}
-
-	Before we prove Proposition 4, we state and prove the following lemma:
+	\section{Proof of Proposition \ref{proposition: eigenanalysis}}\label{section:proof:proposition: eigenanalysis}
+	Before we prove Proposition \ref{proposition: eigenanalysis}, we state and prove the following lemma:
 	\begin{lemma}
@@
 
-	\noindent Now we prove Proposition 4. The singular value decomposition of $\mathcal{C}_{YW}$ is given by
+	\noindent Now we prove Proposition \ref{proposition: eigenanalysis}. The singular value decomposition of $\mathcal{C}_{YW}$ is given by
 	\begin{equation*}
@@
 
-	Firstly, it is obvious by the unit-norm constraint enforced in Proposition 4 that:
+	Firstly, it is obvious by the unit-norm constraint enforced in Proposition \ref{proposition: eigenanalysis} that:
 	\begin{align*}

### 2025-06-29 manuscript/main.tex
start separating the linear system

@@
 \newtheorem{proposition}{Proposition}
+\newtheorem{alg}{Algorithm} 
 \newtheorem{theorem}{Theorem}
+\newtheorem{assumption}{Assumption}
+\newtheorem{note}[theorem]{Note}
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{define}[theorem]{Definition}
+% \newtheorem{denote}[theorem]{denote}
+\newtheorem{claim}[theorem]{Claim}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{corollary}[theorem]{Corollary}
 \newtheorem{lemma}{Lemma}
@@
 	An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}[\mathbf{t}] = (X(\mathbf{t}), \mathbf{Z})^\top$, with $ X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $ \mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.
-We define the inner product between any two hybrid objects, $\mathbf{h}_1 = (f_1, \mathbf{v}_1)$ and $\mathbf{h}_2 = (f_2, \mathbf{v}_2)$, as
+
+	\begin{definition}[Hilbert space of hybrid objects]\label{def:hilbert_space}
+		 We define the inner product between any two hybrid objects,
+		  $\mathbf{h}_1 = (f_1, \mathbf{v}_1)$ and $\mathbf{h}_2 = (f_2, \mathbf{v}_2)$, as
 	\begin{equation}
 	\langle \mathbf{h}_1, \mathbf{h}_2\rangle_{\mathcal{H}} 
-		= 
+	:= 
 	\langle f_1, f_2\rangle_\mathcal{F} 
@@
 	with norm $\Vert \cdot \Vert_\mathcal{H} = \langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
+		\end{definition}
+In \eqref{eq: hybrid inner product}, 
  $\omega$ is a positive weight that needs to be pre-specified or estimated.
@@
 The first step in functional data analysis typically involves reconstructing the underlying functional form from these discrete measurements, commonly by assuming that sample paths lie in a finite-dimensional space spanned by basis functions.
-	\paragraph{Basis functions.}
-For $k = 1, \ldots, K$, let $\Phi^{(k)}:= \{\phi^{(k)}_1, \ldots, \phi^{(k)}_M\}$, with $M \geq 1$, be an $M$-dimensional basis in $L^2(\mathcal{T}_k)$.
+
+For $k = 1, \ldots, K$, let $\Phi^{(k)}   := \{\phi^{(k)}_1, \ldots, \phi^{(k)}_M\}$, with $M \geq 1$, be an $M$-dimensional basis in $L^2(\mathcal{T}_k)$.
 In our proposed hybrid PLS regression algorithm, this basis system is used to approximate both the predictors and the PLS components.
 Additionally, it serves as a regularization mechanism, borrowing strength across components and helping to prevent overfitting.
-
-	\paragraph{Basis approximation of the hybrid predictor.}	
-	For $k = 1, \ldots, K$  and $i = 1, \ldots, n$, 	
-	 we approximate each functional predictor within the span of the basis functions $\Phi^{(k)}$ :
-\begin{equation*} 
-	X_i^{(k)} \approx  \sum_{m=1}^M   c_{im}^{(k)} \phi_m^{(k)} ,
-\end{equation*}
-where the coefficients $c_{im}^{(k)}$'s satisfy
-	\begin{equation*}
-	X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} \phi^{(k)}_{m}(t_k)~\text{for all}~t_k \in \mathbf{t}_k \subset \mathcal{T}_k,
-\end{equation*}
-
 	The number of basis functions $M$ for each functional predictor can be set to a sufficiently large value (e.g., 15 or 20) to incorporate a rich variety of patterns that functional predictors may exhibit.
@@
 
-	\paragraph{Basis approximation of the PLS component.}
-	We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\boldsymbol{\xi}[\mathbf{t}] = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$.
-	%
-	For each $k = 1, \ldots, K$, let $\mathbf{J}^{(k)} \in \mathbb{R}^{M \times M}$ denote the Gram matrix of the basis functions associated with the $k$-th functional predictor, defined by
+For $k = 1, \ldots, K$, we project the $k$th functional predictor onto 
+$\operatorname{span}(\Phi^{(k)})$:
+\begin{equation*}
+	X_i^{(k)} \approx \sum_{m=1}^M c_{im}^{(k)} \phi_m^{(k)}, \quad i = 1, \ldots, n,
+\end{equation*}
+where the coefficients $c_{im}^{(k)}$ satisfy
+\begin{equation*}
+	X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} \phi_m^{(k)}(t_k), \quad \text{for all } t_k \in \mathbf{t}_k \subset \mathcal{T}_k.
+\end{equation*}
+Thus, the $n$ observations of the $k$th functional predictor can be represented by an $n \times M$ matrix of coefficients, 	where rows index samples and columns index basis functions:
+\begin{equation*}
+		\widetilde{\mathbf{C}}^{(k)} := ( c_{im}^{(k)} ).
+\end{equation*}
+
+Importantly, the core computation of our algorithm involves the inner product between $n$ hybrid predictor observations and a single hybrid object (the PLS direction), defined via the inner product in Definition \ref{def:hilbert_space}.
+ With the basis expansion, this reduces to simple matrix operations. 
+For each $k = 1, \ldots, K$, let $\boldsymbol{\Phi}^{(k)} := (\phi^{(k)}_{m \ell })$
+denote the	$M \times M$ symmetric matrix with entries  the inner products between basis functions 
 \begin{equation}\label{def:gram_basis}
-		\mathbf{J}^{(k)} = \left[ \int_{\mathcal{T}k} b_m^{(k)}(t) \, b_n^{(k)}(t) , dt \right]_{m,n=1}^M.
-	\end{equation}
-	Using this definition, we construct the following block-diagonal matrices:
-	\begin{equation}\label{def:J_and_J_star}
-		\mathbf{J} = \mathrm{blkdiag}(\mathbf{J}^{(1)}, \cdots, \mathbf{J}^{(K)}) \in \mathbb{R}^{MK \times MK}~\text{and}~\mathbf{J}^\ast=\mathrm{blkdiag}(\mathbf{J}, \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (MK+p)}.
-	\end{equation}
-
-	\paragraph{Regularization based on second-order derivatives.}
-	Our proposed strategy for computing PLS component, detailed in Section \ref{sec: Regularization of PLS Components}, incorporates regularization based on second-order derivatives.
-To this end, let $\ddot{J}^{(k)}$ denote the $M \times M$ Gram matrix formed by the second derivatives of the basis functions,  defined as
-	\begin{equation}\label{def:dodot_J_k}
-		\ddot{J}^{(k)} = \left[ \int_{\mathcal{T}_k} \ddot{b}^{(k)}_m(t) \ddot{b}^{(k)}_n(t) \, dt \right]_{m,n=1}^M.
-	\end{equation}
-	and define a block-diagonal matrix 
-	$ \ddot{J}^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)}$ as
-	\begin{equation}\label{def:J_dotdot_ast}
-		\ddot{J}^\ast=\mathrm{blkdiag}(\ddot{J}^{(1)}, \cdots, \ddot{J}^{(K)}, 0_{p \times p}).
-	\end{equation}
-	%
-	The finite-basis approximation allows us to represent the hybrid predictor observations using the coefficient matrix $\widetilde{ \mathbf{C} }^\ast$, enabling all associated computations to be carried out via matrix operations involving $\widetilde{ \mathbf{C} }^\ast$, $J^\ast$, and $\ddot{J}^\ast$.
+\phi^{(k)}_{m \ell } 
+:= 
+\langle \phi^{(k)}_m,  \phi^{(k)}_\ell \rangle
+=  
+\int_{\mathcal{T}_k} \phi^{(k)}_m(t_k) \, \phi^{(k)}_\ell(t_k) \, dt_k.
+\end{equation}
+
+\begin{definition}[Hybrid inner product between $n$ observations and a single object]
+Let $\boldsymbol{\xi} = (\psi, \mathbf{s}) \in \mathcal{H}$ be a hybrid object with $\psi \in \mathcal{F}$ and $\mathbf{s} \in \mathbb{R}^p$, and let $\mathbf{a}^{(1)}, \ldots, \mathbf{a}^{(K)}$ denote the basis coefficients of $\psi$ with respect to basis $\Phi^{(1)}, \ldots, \Phi^{(K)}$.
+Then the inner product between $\boldsymbol{\xi}$ and the $n$ basis-approximated hybrid observations $\widetilde{\mathbf{W}}_1, \ldots, \widetilde{\mathbf{W}}_n$, concatenated as a column vector, is denoted $\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}} \in \mathbb{R}^n$ and computed as
+	\begin{equation*}
+		\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}
+		:=
+		\begin{bmatrix}
+			\langle \widetilde{\mathbf{W}}_1, \boldsymbol{\xi} \rangle_{\mathcal{H}} \\
+			\vdots \\
+			\langle \widetilde{\mathbf{W}}_n, \boldsymbol{\xi} \rangle_{\mathcal{H}}
+		\end{bmatrix}
+		=
+		\mathbf{Z} \mathbf{s}
+		+
+		\sum_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \boldsymbol{\Phi}^{(k)} \mathbf{a}^{(k)}. 
+	\end{equation*}
+\end{definition}
 
@@
 For simplicity, we omit the iteration index and denote the residualized response by $Y$, with finite-sample observations given by $\mathbf{y} = (y_1, \ldots, y_n) \in \mathbb{R}^n$.
-Let $\widetilde{W} \in \mathcal{H}$ denote the residualized, basis-approximated hybrid predictor, and let $\widetilde{\mathbf{C}} \in \mathbb{R}^{n \times (MK)}$ denote the basis coefficients of its functional part in the finite-sample observations.
-Our strategy seeks the direction $\boldsymbol{\xi} \in \mathcal{H}$, lying in the span of the basis $B^*[\mathbf{t}]$, that maximizes the empirical covariance between the resulting PLS component $\langle \widetilde{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the response.
+Let $\widetilde{W} \in \mathcal{H}$ denote the residualized, basis-approximated hybrid predictor, and let $\widetilde{\mathbf{C}}^{(1)}, \ldots, \widetilde{\mathbf{C}}^{(k)} \in \mathbb{R}^{n \times M}$ denote the basis coefficient matrices of its functional part in the finite-sample observations.
+Our strategy seeks the direction $\boldsymbol{\xi} \in \mathcal{H}$, whose functional parts lying in
+$\operatorname{span}(\Phi^{(1)}), \ldots, \operatorname{span}(\Phi^{(K)})$
+, that maximizes the empirical covariance between the resulting PLS component $\langle \widetilde{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the response.
 
@@
 	\end{proposition}
+	The proof of Proposition \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
 	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\boldsymbol{\xi}_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \boldsymbol{\xi}_{(u)} = \kappa_{(u)}  \boldsymbol{\xi}_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
@@
 	\end{proposition}
+	The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
 	In other words, $l$-th PLS component $\boldsymbol{\xi}_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.
@@
 		\end{equation*}
-
 	\end{proposition}
-
+	The proof of Proposition \ref{proposition: modified orthnormality of PLS components} is provided in Appendix \ref{section:proof:proposition: modified orthnormality of PLS components}.
 	Now let $\widehat{\boldsymbol{\rho}}_l=(\widehat{\rho}_{1l}, \ldots, \widehat{\rho}_{nl})^\top$ denote the $n$-dimensional vector whose elements consist of estimated $l$-th PLS scores ($l=1, \ldots, L)$ of $n$ observations.
 The next proposition states that the vectors of estimated PLS scores $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$ obtained from the proposed algorithm are mutually orthogonal.
-	\begin{proposition}
+	\begin{proposition}	\label{proposition: orthnormality of PLS scores}
 		The vectors of estimated PLS scores, $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$, obtained from the proposed PLS algorithm are mutually orthogonal in the sense that
@@
 		\end{equation*}
-		\label{proposition: orthnormality of PLS scores}
 	\end{proposition}
+The proof of Proposition \ref{proposition: orthnormality of PLS scores} is provided in Appendix \ref{section:proof:proposition: orthnormality of PLS scores}.
 
@@
 
+	\section{Notations}
+	\begin{itemize}
+		\item aaa
+	\end{itemize}
 	\section{Technical lemmas}
 
-	\section{old notations}
+	\subsection{old notations}
 
@@
 	\end{equation*}
-	where $\mathbf{c}_i^{(k)} = (c_{i1}^{(k)}, \ldots, c_{iM}^{(k)})^\top$ is a $M$-dimensional vector of basis coefficients corresponding to the $k$th functional predictor.
-This basis approximation can be expressed collectively across $n$ observations as: $\widetilde{\mathbf{X}^{(k)}}(t_k) = \widetilde{C}^{(k)} \mathbf{b}^{(k)}(t_k)$, where $\widetilde{\mathbf{X}}^{(k)}(t_k)=(X_1^{(k)}(t_k), \ldots, X_n^{(k)}(t_k))^\top \in \mathbb{R}^n$, and $\widetilde{C}^{(k)} = (\mathbf{c}_1^{(k)} \cdots \mathbf{c}_n^{(k)})^\top \in \mathbb{R}^{n \times M}$.
+ This basis approximation can be expressed collectively across $n$ observations as: $\widetilde{\mathbf{X}^{(k)}}(t_k) = \widetilde{\mathbf{C}}^{(k)} \mathbf{b}^{(k)}(t_k)$, where $\widetilde{\mathbf{X}}^{(k)}(t_k)=(X_1^{(k)}(t_k), \ldots, X_n^{(k)}(t_k))^\top \in \mathbb{R}^n$,
  This notation can be further extended to simultaneously express the basis expansions of $K$ functional predictors as 
@@
 	\end{equation}
-	where $\widetilde{X}(\mathbf{t}) = [\widetilde{\mathbf{X}}^{(1)}(t_1), \cdots, \widetilde{\mathbf{X}}^{(K)}(t_K)] \in \mathbb{R}^{n \times K}$, $\widetilde{C} = [\widetilde{C}^{(1)}, \cdots, \widetilde{C}^{(K)}] \in \mathbb{R}^{n \times MK}$, and
+	where $\widetilde{X}(\mathbf{t}) = [\widetilde{\mathbf{X}}^{(1)}(t_1), \cdots, \widetilde{\mathbf{X}}^{(K)}(t_K)] \in \mathbb{R}^{n \times K}$, $\widetilde{C} = [\widetilde{C}^{(1)}, \cdots, \widetilde{\mathbf{C}}^{(k)}] \in \mathbb{R}^{n \times MK}$, and
 	$B(\mathbf{t}) = \mathrm{blkdiag}[\mathbf{b}^{(1)}(t_1), \cdots, \mathbf{b}^{(K)}(t_K)] \in \mathbb{R}^{MK \times K}$.
@@
 
+	\paragraph{Basis approximation of the PLS component.}
+	We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\boldsymbol{\xi}[\mathbf{t}] = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$.
+	%
+
+	Using this definition, we construct the following block-diagonal matrices:
+	\begin{equation}\label{def:J_and_J_star}
+		\mathbf{J} = \mathrm{blkdiag}(\mathbf{J}^{(1)}, \cdots, \boldsymbol{\Phi}^{(k)}) \in \mathbb{R}^{MK \times MK}~\text{and}~\mathbf{J}^\ast=\mathrm{blkdiag}(\mathbf{J}, \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (MK+p)}.
+	\end{equation}
+
+	\paragraph{Regularization based on second-order derivatives.}
+	Our proposed strategy for computing PLS component, detailed in Section \ref{sec: Regularization of PLS Components}, incorporates regularization based on second-order derivatives.
+To this end, let $\ddot{J}^{(k)}$ denote the $M \times M$ Gram matrix formed by the second derivatives of the basis functions,  defined as
+	\begin{equation}\label{def:dodot_J_k}
+		\ddot{J}^{(k)} = \left[ \int_{\mathcal{T}_k} \ddot{b}^{(k)}_m(t) \ddot{b}^{(k)}_n(t) \, dt \right]_{m,n=1}^M.
+	\end{equation}
+	and define a block-diagonal matrix 
+	$ \ddot{J}^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)}$ as
+	\begin{equation}\label{def:J_dotdot_ast}
+		\ddot{J}^\ast=\mathrm{blkdiag}(\ddot{J}^{(1)}, \cdots, \ddot{J}^{(K)}, 0_{p \times p}).
+	\end{equation}
+	%
+	The finite-basis approximation allows us to represent the hybrid predictor observations using the coefficient matrix $\widetilde{ \mathbf{C} }^\ast$, enabling all associated computations to be carried out via matrix operations involving $\widetilde{ \mathbf{C} }^\ast$, $J^\ast$, and $\ddot{J}^\ast$.
+
 	\section{Proofs of Propositions}
@@
 		&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{C}^{(k)} \left\{ \int_{\mathcal{T}_k} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
+		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \left\{ \int_{\mathcal{T}_k} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
 		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
@@
 
-	\vspace{1cm}
-	\noindent $\boldsymbol{\cdot}$  \underline{\textbf{Proposition 5}}
+\section{Proof of Proposition \ref{proposition: modified orthnormality of PLS components}}
+\label{section:proof:proposition: modified orthnormality of PLS components}
 
@@
 
-	\vspace{1cm}
-	\noindent $\boldsymbol{\cdot}$  \underline{\textbf{Proposition 6}}
+	\section{Proof of Proposition \ref{proposition: orthnormality of PLS scores}}\label{section:proof:proposition: orthnormality of PLS scores}
 

### 2025-06-29 manuscript/main.tex
unregularized computation streamlined

@@
 
-\begin{definition}[Hybrid inner product between $n$ observations and a single object]
+\begin{definition}[Hybrid inner product between $n$ observations and a single object]\label{def:n_one_inner_product}
 Let $\boldsymbol{\xi} = (\psi, \mathbf{s}) \in \mathcal{H}$ be a hybrid object with $\psi \in \mathcal{F}$ and $\mathbf{s} \in \mathbb{R}^p$, and let $\mathbf{a}^{(1)}, \ldots, \mathbf{a}^{(K)}$ denote the basis coefficients of $\psi$ with respect to basis $\Phi^{(1)}, \ldots, \Phi^{(K)}$.
@@
 
-For practical computation, 
-let us first denote
-\begin{equation*}
-\mathbf{b} := \mathbf{y}^\top
-[ \widetilde{\mathbf{C}} \, \mathbf{J} \, \mathbf{Z} ].
-\end{equation*}
-Then we obtain $\mathbf{d}$ by solving a linear system
-\begin{equation*}
-	\mathbf{J}^\ast \mathbf{d} =
-	\mathbf{b}^\top.
-\end{equation*}  
-Then we obtain the coefficient for the PLS direction by normalize it with respect to the basis $B^*[\mathbf{t}]$:
-\begin{equation}\label{compute:pls_direction_coeff}
-	\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
-	= \frac{1}{\sqrt{\mathbf{d}^\top \mathbf{J}^\ast \mathbf{d}}} \mathbf{d}.
-\end{equation}
-The $l$-th  PLS score for the 
-$i$th observation is then computed as the inner product  with respect to the basis $B^*[\mathbf{t}]$:
-\begin{equation*}
-	\widehat{\rho}_{i}
+For the computation of the estimated PLS direction  $\hat{\boldsymbol{\xi}}$, 
+we obtain the basis coefficients of its functional part, denoted by $\mathbf{d}^{(1)}, \ldots, \mathbf{d}^{(K)} \in \mathbb{R}^{M}$,
+and the scalar part  
+$\mathbf{d} \in \mathbb{R}^p$,
+by solving linear systems
+\begin{equation*}
+ \boldsymbol{\Phi}^{(1)}
+\mathbf{d}^{(1)} 
 =
-	[ \widetilde{\mathbf{C}}  \, \mathbf{Z} ] \, \mathbf{J}^\ast \begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
-\end{equation*}
-$ \equiv \widehat{\rho}_{il}$ can be obtained as $\widehat{\rho}_i = \langle \mathbf{W}_i, \widehat{\boldsymbol{\xi}} \rangle_\mathcal{H}$.
-we first construct the following matrix:
-	\begin{equation}\label{def:V_star}
-	\mathbf{V}^\ast 
-	:= 
-	n^{-2}\begin{bmatrix}
-\mathbf{J}
-\widetilde{ \mathbf{C} }^\top \mathbf{y}\mathbf{y}^\top \widetilde{ \mathbf{C} } \mathbf{J} 
-& 
-\mathbf{J} \widetilde{ \mathbf{C} }^\top 
-\mathbf{y}
-\mathbf{y}^\top 
-\mathbf{Z} 
-\\
-\mathbf{Z}^\top 
-\mathbf{y}
-\mathbf{y}^\top \widetilde{ \mathbf{C} }
-\mathbf{J} 
-&   
-\mathbf{Z}^\top 
-\mathbf{y}
-\mathbf{y}^\top 
-\mathbf{Z}
-	\end{bmatrix} = n^{-2} \mathbf{J}^\ast \widetilde{ \mathbf{C} }^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{ \mathbf{C} }^{*} \mathbf{J}^\ast
-	\in \mathbb{R}^{(MK+p) \times (MK+p)}.
-\end{equation}
+(\widetilde{\mathbf{C}}^{(1)} \boldsymbol{\Phi}^{(1)})^\top
+\mathbf{y},
+\ldots
+,
+\boldsymbol{\Phi}^{(K)}
+\mathbf{d}^{(K)} 
+=
+(\widetilde{\mathbf{C}}^{(K)} \boldsymbol{\Phi}^{(K)})^\top
+\mathbf{y},
+~\text{and}~
+\mathbf{d} := \mathbf{Z}^\top \mathbf{y} .
+\end{equation*}
+We then normalize these coefficients and scalar parts by the hybrid Hilbert norm (Definition
+\ref{def:hilbert_space}),
+which can be computed as
+\begin{equation*}
+\|	\hat{\boldsymbol{\xi}} \|_{\mathcal{H}} = 
+\bigl(
+	\mathbf{d}^\top \mathbf{d} + 
+	\sum_{k=1}^K (\mathbf{d}^{(k)})^\top  \boldsymbol{\Phi}^{(K)}  \mathbf{d}^{(k)} 
+	\bigr)^{1/2}.
+\end{equation*}
+Therefore, the estimated PLS direction is the tuple $\hat{\boldsymbol{\xi}} \in \mathcal{H}$, defined as
+\begin{equation}
+	\hat{\boldsymbol{\xi}} :=
+	\frac{1}{
+	\bigl(
+	\mathbf{d}^\top \mathbf{d} + 
+	\sum_{k=1}^K (\mathbf{d}^{(k)})^\top  \boldsymbol{\Phi}^{(K)}  \mathbf{d}^{(k)} 
+	\bigr)^{1/2}
+	}
+	\biggl(
+	\sum_{m=1}^M d^{(1)}_m \phi^{(1)}_m,
+	\ldots,
+	\sum_{m=1}^M d^{(K)}_m \phi^{(K)}_m,
+	\mathbf{d}
+	\biggr).
+\end{equation}
+Finally, the estimated $l$th PLS scores for the $n$ observations,
+denoted $\hat{\boldsymbol{\rho}} \in \mathbb{R}^n$
+ is computed simultaneously as the hybrid inner product (Definition \ref{def:n_one_inner_product}):
+	\begin{equation*}
+	\langle \widetilde{\mathbf{W}}, \hat{\boldsymbol{\xi}} \rangle_{\mathcal{H}}
+	=
+	\frac{1}{\|	\hat{\boldsymbol{\xi}} \|_{\mathcal{H}}}
+	\biggl(
+	\mathbf{Z} \mathbf{d}
+	+
+	\sum_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \boldsymbol{\Phi}^{(k)} \mathbf{d}^{(k)}
+	\biggr)
+	. 
+\end{equation*}
 
@@
 	\subsection{Proof of Propositions \ref{Proposition: generalized rayleigh quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
+
+	we first construct the following matrix:
+	\begin{equation}\label{def:V_star}
+		\mathbf{V}^\ast 
+		:= 
+		n^{-2}\begin{bmatrix}
+			\mathbf{J}
+			\widetilde{ \mathbf{C} }^\top \mathbf{y}\mathbf{y}^\top \widetilde{ \mathbf{C} } \mathbf{J} 
+			& 
+			\mathbf{J} \widetilde{ \mathbf{C} }^\top 
+			\mathbf{y}
+			\mathbf{y}^\top 
+			\mathbf{Z} 
+			\\
+			\mathbf{Z}^\top 
+			\mathbf{y}
+			\mathbf{y}^\top \widetilde{ \mathbf{C} }
+			\mathbf{J} 
+			&   
+			\mathbf{Z}^\top 
+			\mathbf{y}
+			\mathbf{y}^\top 
+			\mathbf{Z}
+		\end{bmatrix} = n^{-2} \mathbf{J}^\ast \widetilde{ \mathbf{C} }^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{ \mathbf{C} }^{*} \mathbf{J}^\ast
+		\in \mathbb{R}^{(MK+p) \times (MK+p)}.
+	\end{equation}
+
 		Here, $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y)$ is expressed as $\boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*$ based on the aforementioned basis approximations.

### 2025-06-29 manuscript/main.tex
proposition 1 revised

@@
 Therefore, the estimated PLS direction is the tuple $\hat{\boldsymbol{\xi}} \in \mathcal{H}$, defined as
-\begin{equation}
+\begin{equation}\label{def:computed_PLS_direction}
 	\hat{\boldsymbol{\xi}} :=
@@
 	\begin{proposition} \label{Proposition: generalized rayleigh quotient}
-		Let $\operatorname{span}(B^\ast[\mathbf{t}])$ 
-		be a linear subspace of $\mathcal{H}$ spanned by the basis functions.
-		  For any unit-length direction  $\boldsymbol{\xi} \in \operatorname{span}(B^\ast[\mathbf{t}])$,
-expressed as $
-\boldsymbol{\xi} 
-= 
-\boldsymbol{\alpha}
-B^\ast [\mathbf{t}] $ with $\boldsymbol{\alpha} \in \mathbb{R}^{MK + p}$,
-		Let us define
-		the empirical and basis-approximated sample covariance as
+		  For any unit-length direction in $\mathcal{H}$
+		  whose functional parts lie in $\operatorname{span}(\Phi^{(1)}), \ldots, \operatorname{span}(\Phi^{(K)})$,
+		let us define
+		the empirical and basis-approximated sample covariance between the resulting component and response as
 \begin{equation*}
@@
 	:=
-	\frac{1}{n} \sum \limits_{i=1}^n \langle \widetilde{W}_i, \boldsymbol{\xi} \rangle_\mathcal{H} y_i
-	=
-		\frac{1}{n} \sum \limits_{i=1}^n 
-	(	\tilde{\mathbf{C}}^\ast_i \mathbf{J}^\ast \boldsymbol{\alpha} ) y_i.
-\end{equation*}
-Then the coefficients computed in \eqref{compute:pls_direction_coeff}  $\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )$
-over all unit vectors in $\operatorname{span}(B^\ast[\mathbf{t}])$.
-In a more formal way:
-	\begin{equation}
-	\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
-	B^*[\mathbf{t}] \in \arg \max_{
- \|\boldsymbol{\xi}  \| = 1, 
-	 \boldsymbol{\xi} \in \mathrm{span}(B^*[\mathbf{t}])
-	}
-		\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ).
-\end{equation}
-
+	\frac{1}{n} 
+	\mathbf{y}^\top 
+ \langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_\mathcal{H},
+\end{equation*}
+where right-hand side notation comes from Definition \ref{def:n_one_inner_product}.
+Then the PLS direction 
+$	\hat{\boldsymbol{\xi}}$ 
+ computed in \eqref{def:computed_PLS_direction} maximizes $\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )$.
 	\end{proposition}

### 2025-06-29 manuscript/main.tex
before gym

@@
 		  For any unit-length direction in $\mathcal{H}$
-		  whose functional parts lie in $\operatorname{span}(\Phi^{(1)}), \ldots, \operatorname{span}(\Phi^{(K)})$,
+		  whose functional parts lie in $\operatorname{span}(\Phi^{(1)})$, $\ldots,$ $\operatorname{span}(\Phi^{(K)})$,
 		let us define

### 2025-07-09 manuscript/main.tex
remove: computing time comparison for varying lambda
for one-time computation,
computing time does not vary much
complex eigenvalue does not occur

--- 2025-06-29 manuscript/main.tex
@@
 \begin{proposition} \label{Proposition: generalized rayleigh quotient}
-		  For any unit-length direction in $\mathcal{H}$
-		  whose functional parts lie in $\operatorname{span}(\Phi^{(1)}), \ldots, \operatorname{span}(\Phi^{(K)})$,
-		let us define
-		the empirical and basis-approximated sample covariance between the resulting component and response as
-\begin{equation*}
-	\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )
+	Let $\boldsymbol{\xi} \in \mathcal{H}$ be any unit-norm direction such that its $1$st through $K$th functional components lie in $\operatorname{span}(\Phi^{(1)}), \ldots, \operatorname{span}(\Phi^{(K)})$, respectively.
+	Then, the empirical covariance between the projected component $\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the response $Y$, approximated in terms of the basis, is given by
+	\begin{equation*}
+		\widehat{\textnormal{Cov}} \left( \langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y \right)
 		:=
@@
 		\mathbf{y}^\top 
- \langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_\mathcal{H},
+		\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}},
 	\end{equation*}

### 2025-07-09 create-FSHybridPLS.Rmd
delete meaningless test

@@
 The class definition is a simple list that contains a matrix and a collection of \code{fd} objects from the \code{fda} package, along with the necessary metadata.
+- gram matrices are saved as a list.
 ```{r classdef:predictor_hybrid}
@@
 })
-
 ```
@@
 
-###
+### Spectral method
+The old implementation that computes the leading eigenvector of
+
+### helper: get_CJ
 ```{r}
@@
 
-### get_pre_corrcov
+### helper: get_pre_corrcov 
 construct the matrix V_star:
@@
 
-test code:
-
-| Case | Description               | Functional Coefficients         | Scalar Covariates      | Response         | Expected Behavior                              |
-|------|---------------------------|----------------------------------|------------------------|------------------|------------------------------------------------|
-| 1    | Constant structure        | All ones or twos                | All ones               | Increasing vector| Output matrix is symmetric and non-negative    |
-| 2    | Random structure          | Random normal entries           | Random normal values   | Random vector    | Output is symmetric and numerically PSD        |
-
-```{r}
-testthat::test_that("get_pre_corrcov handles constant and random coefficients", {
-  suppressPackageStartupMessages(library(fda))
-
-  make_fd <- function(coefs, basis) {
-    fd(coef = coefs, basisobj = basis)
-  }
-
-  basis <- create.bspline.basis(c(0, 1), nbasis = 4)
-  n_sample <- 5
-  n_scalar <- 2
-  n_functional <- 2
-
-  # Constant coefficients
-  fd_const1 <- make_fd(matrix(1, 4, n_sample), basis)
-  fd_const2 <- make_fd(matrix(2, 4, n_sample), basis)
-  Z_const <- matrix(1, n_sample, n_scalar)
-  y_const <- matrix(1:n_sample, ncol = 1)
-  obj_const <- predictor_hybrid(Z = Z_const, functional_list = list(fd_const1, fd_const2))
-
-  V_const <- get_pre_corrcov(obj_const, y_const)
-  testthat::expect_equal(dim(V_const), rep(sum(obj_const$n_basis_list) + obj_const$n_scalar, 2))
-  testthat::expect_true(isSymmetric(V_const))
-  testthat::expect_true(all(V_const >= 0))
-
-  # Random coefficients
-  set.seed(123)
-  fd_rand1 <- make_fd(matrix(rnorm(4 * n_sample), 4, n_sample), basis)
-  fd_rand2 <- make_fd(matrix(rnorm(4 * n_sample), 4, n_sample), basis)
-  Z_rand <- matrix(rnorm(n_sample * n_scalar), n_sample, n_scalar)
-  y_rand <- matrix(rnorm(n_sample), ncol = 1)
-  obj_rand <- predictor_hybrid(Z = Z_rand, functional_list = list(fd_rand1, fd_rand2))
-
-  V_rand <- get_pre_corrcov(obj_rand, y_rand)
-  testthat::expect_equal(dim(V_rand), rep(sum(obj_rand$n_basis_list) + obj_rand$n_scalar, 2))
-  testthat::expect_true(isSymmetric(V_rand))
-  testthat::expect_true(all(eigen(V_rand, only.values = TRUE)$values >= -1e-8))
-})
-
-```
-
-```{r}
-get_xi_direct <- function(W, y) {
-  K <- W$n_functional
-  C_J <- get_CJ(W)
-  A <- cbind(C_J, W$Z)                      # shape: n × d
-  b <- t(y) %*% A / W$n_sample   # equivalent to V_star
-
-  J_star <- get_gram_matrix_block(W)
-  alpha <- solve(J_star, t(b))                # unconstrained maximizer
-  xi_hat <- alpha / sqrt(t(alpha) %*% J_star %*% alpha)  # normalize
-
-  return(xi_hat)
-}
-```
-
-```{r}
-  C_J <- get_CJ(W)
-  A <- cbind(C_J, W$Z)                      # shape: n × d
-  b <- t(y) %*% A / W$n_sample   # equivalent to V_star
-
-  J_star <- get_gram_matrix_block(W)
-  alpha <- solve(J_star, t(b))                # unconstrained maximizer
-  xi_hat <- alpha / sqrt(sum((alpha) * (J_star %*% alpha) )) # normalize
-t(y) %*% A %*% xi_hat
-```
-
-```{r}
- V_star <- get_pre_corrcov(W, y)
-L <- chol(J_star)
-  invL <- Matrix::chol2inv(L)
-  A <- V_star %*% t(invL)       # A = V* × t(inv(L))
-  E <- invL %*% A               # E = inv(L) × A
-
-  eigen_result <- eigen(E)
-  e <- eigen_result$vectors[, 1]
-  if (is.complex(e)){
-    print("stop")
-    return("stop")
-  }
-
-  xi_star <- t(invL) %*% e      # xi_star solves t(L) xi = e
-```
-
-### get_pls_comp
+### main function: get_pls_comp
 Computes the first PLS component from a hybrid predictor and response vector using regularization.
@@
 
-```{r}
-suppressPackageStartupMessages({
-  library(fda)
-  library(Matrix)
-  library(ggplot2)
-})
-
-# --- Helper: Generate realistic smooth functional data ---
-generate_fd_data <- function(n_sample, nbasis, freq = 1) {
-  basis <- create.bspline.basis(c(0, 1), nbasis = nbasis, norder = 4)
-  time_points <- seq(0, 1, length.out = nbasis)
-  coefs <- outer(1:nbasis, 1:n_sample, function(i, j) {
-    sin(freq * pi * time_points[i]) + rnorm(1, sd = 0.1)
-  })
-  fd(coef = coefs, basisobj = basis)
-}
-
-# --- Settings ---
-set.seed(20250604)
-n_sample <- 200
-n_scalar <- 10
-n_functional <- 2
-nbasis_vals <- c(4,8,12,16,20)
-lambda_vals <- c(0, 1e-8, 1e-6, 1e-4, 1e-2, 1, 10)
-
-results <- data.frame()
-
-# --- Experiment Loop ---
-for (nbasis in nbasis_vals) {
-  for (lambda in lambda_vals) {
-    cat("Trying nbasis =", nbasis, ", lambda =", lambda, "\n")
-
-    # Generate functional predictors
-    fd1 <- generate_fd_data(n_sample, nbasis, freq = 1)
-    fd2 <- generate_fd_data(n_sample, nbasis, freq = 2)
-    Z <- matrix(rnorm(n_sample * n_scalar), n_sample, n_scalar)
-    y <- rnorm(n_sample)
-
-    W <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
-    lambda_vec <- rep(lambda, n_functional)
-
-    # Try to compute constraint matrix L
-    L <- get_constraint_matrix_hybrid(W, lambda_vec)
-    constr_mat_chol <- t(chol(L))  # <-- do not change this
-
-    # Time the PLS computation
-    elapsed <- system.time({
-      out <- tryCatch({
-        pls <- get_pls_comp(W, y, constr_mat_chol)
-
-        if (!is.list(pls) || (is.character(pls) && pls == "stop")) {
-          data.frame(
-            nbasis = nbasis,
-            lambda = lambda,
-            eigen_val = NA,
-            is_real = FALSE,
-            reason = "stop (complex eigenvector)",
-            time_sec = NA_real_
-          )
-        } else {
-          data.frame(
-            nbasis = nbasis,
-            lambda = lambda,
-            eigen_val = Re(pls$eigen_val),
-            is_real = TRUE,
-            reason = "success",
-            time_sec = NA_real_  # placeholder, will update below
-          )
-        }
-      }, error = function(e) {
-        data.frame(
-          nbasis = nbasis,
-          lambda = lambda,
-          eigen_val = NA,
-          is_real = FALSE,
-          reason = "error in get_pls_comp",
-          time_sec = NA_real_
-        )
-      })
-    })
-
-    out$time_sec <- elapsed["elapsed"]
-    results <- rbind(results, out)
-  }
-}
-
-# --- Print successful configurations ---
-cat("\n✅ Successful runs with real eigenvalues:\n")
-print(subset(results, is_real == TRUE))
-
-# --- Fastest and slowest ---
-cat("\n⏱️ Top 5 fastest settings:\n")
-print(head(results[order(results$time_sec), ], 5))
-
-cat("\n🐢 Top 5 slowest settings:\n")
-print(tail(results[order(results$time_sec), ], 5))
-
-# --- Visualize success/failure ---
-ggplot(results, aes(x = nbasis, y = lambda, fill = reason)) +
-  geom_tile(color = "white") +
-  scale_y_log10() +
-  scale_fill_manual(values = c(
-    "success" = "green",
-    "stop (complex eigenvector)" = "orange",
-    "error in get_constraint_matrix_hybrid" = "red",
-    "error in get_pls_comp" = "darkred"
-  )) +
-  labs(
-    title = "get_pls_comp Outcomes: λ vs. # Basis Functions",
-    x = "# of Basis Functions",
-    y = "Smoothing Parameter λ (log scale)",
-    fill = "Result Type"
-  )
-
+## linear system method
+
+```{r}
+get_xi_direct <- function(W, y) {
+  K <- W$n_functional
+  C_J <- get_CJ(W)
+  A <- cbind(C_J, W$Z)                      # shape: n × d
+  b <- t(y) %*% A / W$n_sample   # equivalent to V_star
+
+  J_star <- get_gram_matrix_block(W)
+  alpha <- solve(J_star, t(b))                # unconstrained maximizer
+  norm_squared <- as.numeric( t(alpha) %*% J_star %*% alpha )
+  xi_hat <- alpha / sqrt(norm_squared)  # normalize
+
+  return(xi_hat)
+}
 ```
@@
 }
-
-```
-
-```{r}
-library(fda)
-
-set.seed(011111)
-n_sample <- 100
-n_scalar <- 3
-
-# --- Step 1: Zero functional predictors ---
-zero_basis <- create.bspline.basis(c(0, 1), nbasis = 4)
-zero_fd <- fd(coef = matrix(0, nrow = 4, ncol = n_sample), basisobj = zero_basis)
-functional_list <- list(zero_fd, zero_fd)  # two zero-valued functional predictors
-
-# --- Step 2: Simulate scalar predictors and response ---
-Z <- matrix(rnorm(n_sample * n_scalar), ncol = n_scalar)
-Z <- scale(Z, center = TRUE, scale = FALSE)
-W <- predictor_hybrid(Z = Z, functional_list = functional_list)
-
-beta_true <- rnorm(n_scalar)
-y <- Z %*% beta_true + rnorm(n_sample, sd = 0.1)
-y <- scale(y, center = TRUE, scale = FALSE)
-
-# --- Step 3: Compute constraint matrix ---
-lambda <- rep(0, W$n_functional)
-L <- chol(get_constraint_matrix_hybrid(W, lambda))
-
-# --- Step 4: PLS with get_pls_comp ---
-pls <- get_pls_comp(W, y, L)
-xi_hat <- pls$xi_hat
-
-# --- Step 5: PLS via raw Euclidean eigenproblem ---
-V_star_vec <- as.vector(t(Z) %*% y)     # equivalent to colSums(Z * y)
-
-J <- crossprod(Z)                       # J = Z^T Z
-L_Z <- chol(J)
-invL <- solve(L_Z)
-E <- invL %*% tcrossprod(V_star_vec) %*% t(invL)
-
-eig <- eigen(E)
-e <- eig$vectors[, 1]
-xi_manual <- backsolve(L_Z, e, transpose = TRUE)  # xi = L^T \ e
-
-# --- Step 6: get_pls_comp_simple ---
-xi_simple <- get_pls_comp_simple(W, y)
-xi_simple_vec <- tail(xi_simple$Z, 1)
-xi_direct <- get_xi_direct(W, y)
-# --- Step 7: Compare all three scalar parts ---
-
-# From get_pls_comp
-xi_hat_vec <- tail(xi_hat$Z, 1)
-
-# Cosine similarities
-cos_eig_manual <- sum(xi_manual * xi_hat_vec) / (sqrt(sum(xi_manual^2)) * sqrt(sum(xi_hat_vec^2)))
-cos_simple_manual <- sum(xi_manual * xi_simple_vec) / (sqrt(sum(xi_manual^2)) * sqrt(sum(xi_simple_vec^2)))
-cos_eig_simple <- sum(xi_simple_vec * xi_hat_vec) / (sqrt(sum(xi_simple_vec^2)) * sqrt(sum(xi_hat_vec^2)))
-
-# --- Step 8: Report ---
-cat("Cosine similarity (get_pls_comp vs manual eig):", cos_eig_manual, "\n")
-cat("Cosine similarity (get_pls_comp_simple vs manual eig):", cos_simple_manual, "\n")
-cat("Cosine similarity (get_pls_comp vs get_pls_comp_simple):", cos_eig_simple, "\n")
 

### 2025-07-09 create-FSHybridPLS.Rmd
confirmed correlation maximization

@@
 
-### main function: get_pls_comp
+### main function (wrapper: get_pls_comp
 Computes the first PLS component from a hybrid predictor and response vector using regularization.
@@
 #'
-#' @param W A \code{predictor_hybrid} object containing both functional and scalar predictors.
-#' @param y A numeric response vector of length equal to the number of samples in \code{W}.
+#' @param W A predictor_hybrid object containing both functional and scalar predictors.
+#' @param y A numeric response vector of length equal to the number of samples in W.
 #' @param L cholesky decompisition of a regularization matrix (typically positive definite) used in the generalized eigenproblem.
@@
 #' @return A list with the following elements:
-#' \describe{
-#'   \item{\code{xi_hat}}{The estimated first PLS component as a \code{predictor_hybrid} object.}
-#'   \item{\code{E}}{The generalized eigenvalue problem matrix \code{E = inv(L) V* t(inv(L))}.}
-#'   \item{\code{V_star}}{The cross-covariance matrix between predictors and response.}
-#'   \item{\code{eigen_val}}{The leading eigenvalue of \code{E}.}
-#' }
+#'
+#'   xi_hat: The estimated first PLS component as a predictor_hybrid object.
+#'   E: The generalized eigenvalue problem matrix E = inv(L) V* t(inv(L)).
+#'   V_star: The cross-covariance matrix between predictors and response.}
+#'   eigen_val: The leading eigenvalue of E.
+#' 
 #'
@@
 
-  invL <- Matrix::chol2inv(L)
+  #invL <- Matrix::chol2inv(L)
+  invL <- solve(L)
   A <- V_star %*% t(invL)       # A = V* × t(inv(L))
@@
   xi_hat <- predictor_hybrid_from_coef(format = W, coef = xi_star)
-
   return(list(
@@
 
+### helper: get_xi_hat_linear
+```{r}
+get_xi_hat_linear <- function(W, y){
+  n <- W$n_sample
+  K <- W$n_functional
+  d = list()
+  for (i in 1:K){  ## tPhi_tC : C multiplied by Phi. Scalable to arbitrary K
+    Ct <- W$functional_list[[i]]$coefs
+    Phi <- W$gram_list[[i]]
+    rhs <-  t(Phi) %*% Ct %*% y
+    d[[i]] <- solve(Phi, rhs)
+  }
+  d[[K+1]] <- t(W$Z) %*% y
+  d_vec <- do.call(c, d)  # or: unlist(d)
+  return(d_vec)
+}
+```
+
 ```{r}
@@
 }
-```
-
-### get_pls_comp_simple
-```{r}
-#' Compute First PLS Component (Direct Hilbert Averaging)
-#'
-#' Computes the first PLS component as a normalized weighted average of predictor objects,
-#' where weights are given by the centered response values.
-#'
-#' @param W A `predictor_hybrid` object containing `n_sample` observations.
-#' @param y A numeric response vector of length `n_sample`.
-#'
-#' @return A normalized `predictor_hybrid` object representing the first PLS component.
-#' @export
-get_pls_comp_simple <- function(W, y) {
-  n <- W$n_sample
-  if (length(y) != n) stop("Length of y must match number of samples in W.")
-
-  # Center the response (optional, but often improves interpretability)
-  y_centered <- y - mean(y)
-
-  # Initialize zero element
-  xi_sum <- scalar_mul.predictor_hybrid(subset_predictor_hybrid(W, 1), y_centered[1])
-
-  # Accumulate weighted sum: sum_i y_i * W_i
-  for (i in 2:n) {
-    Wi <- subset_predictor_hybrid(W, i)
-    xi_sum <- add.predictor_hybrid(xi_sum, Wi, alpha = y_centered[i])
-  }
-
-  # Normalize
-  xi_sum <- scalar_mul.predictor_hybrid(xi_sum, 1/n)
-  norm_val <- sqrt(inprod.predictor_hybrid(xi_sum))
-  xi_hat <- scalar_mul.predictor_hybrid(xi_sum, 1 / norm_val)
-
-  return(xi_hat)
-}
-
 ```
@@
 W_template <- W  # prevent mutation
+
 pls_eig_result <- get_pls_comp(W, y, L)
@@
 
-# --- Step 6 (Revised): Manually compute direct PLS component and wrap with predictor_hybrid_from_coef ---
-
-# Scalar part
-
-# Functional part: stack the weighted coefficients
-func_weighted_vec <- unlist(lapply(functional_list, function(fd_j) {
-  coef(fd_j) %*% y  # nbasis × 1
-}))
-
-# Full coefficient vector
-Z_weighted <- colSums(Z * y)
-
-xi_raw_vec <- c(func_weighted_vec, Z_weighted)
+xi_hat_lin <- get_xi_hat_linear(W, y)
 
 # Wrap into predictor_hybrid object using format template
-xi_hat_direct <- predictor_hybrid_from_coef(format = W_template, coef = xi_raw_vec)
+xi_hat_direct <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin)
 
@@
 
-xi_new <- get_xi_direct(W, y)
-
 # --- Step 7: Compare and evaluate ---
@@
 norm1 <- sqrt(inprod.predictor_hybrid(xi_hat_eig))
+xi_hat_eig <- scalar_mul.predictor_hybrid(xi_hat_eig,  1 / norm1)
+
 norm2 <- sqrt(inprod.predictor_hybrid(xi_hat_direct))
+cat("norm 1", norm1,  "\n")
+cat("norm 2", norm2,  "\n")
+
 cos_theta <- ip / (norm1 * norm2)

### 2025-07-09 manuscript/main.tex
computation details to appendix

@@
 
-\begin{definition}[Hybrid inner product between $n$ observations and a single object]\label{def:n_one_inner_product}
-Let $\boldsymbol{\xi} = (\psi, \mathbf{s}) \in \mathcal{H}$ be a hybrid object with $\psi \in \mathcal{F}$ and $\mathbf{s} \in \mathbb{R}^p$, and let $\mathbf{a}^{(1)}, \ldots, \mathbf{a}^{(K)}$ denote the basis coefficients of $\psi$ with respect to basis $\Phi^{(1)}, \ldots, \Phi^{(K)}$.
-Then the inner product between $\boldsymbol{\xi}$ and the $n$ basis-approximated hybrid observations $\widetilde{\mathbf{W}}_1, \ldots, \widetilde{\mathbf{W}}_n$, concatenated as a column vector, is denoted $\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}} \in \mathbb{R}^n$ and computed as
-	\begin{equation*}
-		\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}
-		:=
-		\begin{bmatrix}
-			\langle \widetilde{\mathbf{W}}_1, \boldsymbol{\xi} \rangle_{\mathcal{H}} \\
-			\vdots \\
-			\langle \widetilde{\mathbf{W}}_n, \boldsymbol{\xi} \rangle_{\mathcal{H}}
-		\end{bmatrix}
-		=
-		\mathbf{Z} \mathbf{s}
-		+
-		\sum_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \boldsymbol{\Phi}^{(k)} \mathbf{a}^{(k)}. 
-	\end{equation*}
-\end{definition}
-
 	\subsubsection{Smoothed estimation of PLS components}\label{sec: pls component computation intermediate}
@@
 \end{equation*}
-We then normalize these coefficients and scalar parts by the hybrid Hilbert norm (Definition
-\ref{def:hilbert_space}),
-which can be computed as
-\begin{equation*}
-\|	\hat{\boldsymbol{\xi}} \|_{\mathcal{H}} = 
-\bigl(
-	\mathbf{d}^\top \mathbf{d} + 
-	\sum_{k=1}^K (\mathbf{d}^{(k)})^\top  \boldsymbol{\Phi}^{(K)}  \mathbf{d}^{(k)} 
-	\bigr)^{1/2}.
-\end{equation*}
-Therefore, the estimated PLS direction is the tuple $\hat{\boldsymbol{\xi}} \in \mathcal{H}$, defined as
+The estimated PLS direction is the tuple $\hat{\boldsymbol{\xi}} \in \mathcal{H}$, defined with these coefficients and normalized with respect to the 
+hybrid Hilbert norm (Definition
+\ref{def:hilbert_space})
+as follows:
 \begin{equation}\label{def:computed_PLS_direction}
@@
 \end{equation}
+The details of this hybrid norm computation are provided in Appendix~\ref{section:proof:eigenproblem_derivation}.
 Finally, the estimated $l$th PLS scores for the $n$ observations,
 denoted $\hat{\boldsymbol{\rho}} \in \mathbb{R}^n$
- is computed simultaneously as the hybrid inner product (Definition \ref{def:n_one_inner_product}):
-	\begin{equation*}
-	\langle \widetilde{\mathbf{W}}, \hat{\boldsymbol{\xi}} \rangle_{\mathcal{H}}
-	=
-	\frac{1}{\|	\hat{\boldsymbol{\xi}} \|_{\mathcal{H}}}
+ is computed via hybrid inner product. In a matrix multiplication form, it is computed as:
+	\begin{align*}
+		\hat{\boldsymbol{\rho}}
+		&:=
+\biggl(
+	\langle \widetilde{\mathbf{W}}_1, \hat{\boldsymbol{\xi}} \rangle_{\mathcal{H}},
+	\ldots,
+		\langle \widetilde{\mathbf{W}}_n, \hat{\boldsymbol{\xi}} \rangle_{\mathcal{H}}
+\biggr)^\top
+\\&	=
+	\frac{1}{
+	\bigl(
+	\mathbf{d}^\top \mathbf{d} + 
+	\sum_{k=1}^K (\mathbf{d}^{(k)})^\top  \boldsymbol{\Phi}^{(K)}  \mathbf{d}^{(k)} 
+	\bigr)^{1/2}
+}
 	\biggl(
@@
 	. 
-\end{equation*}
+\end{align*}
+The details of this computation are provided in Appendix~\ref{section:proof:eigenproblem_derivation}.
+Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS direction, the normalization step couples them, allowing the components to influence each other.
+This enables the procedure to account for the correlation between functional and scalar components.
 
@@
 		\frac{1}{n} 
-		\mathbf{y}^\top 
-		\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}},
-	\end{equation*}
-where right-hand side notation comes from Definition \ref{def:n_one_inner_product}.
+		\sum_{i=1}^n
+		y_i
+		\langle \widetilde{\mathbf{W}}_i, \boldsymbol{\xi} \rangle_{\mathcal{H}}.
+	\end{equation*}
 Then the PLS direction 
@@
 	\subsection{Proof of Propositions \ref{Proposition: generalized rayleigh quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
+	%
+	%
+	\begin{align*}
+	\widehat{\textnormal{Cov}} (
+	\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y 
+	) 
+	&= 
+	\frac{1}{n} \sum \limits_{i=1}^n 
+	 y_i
+	\langle \widetilde{\mathbf{W}}_i, \boldsymbol{\xi} \rangle_\mathcal{H} \\
+	&= 
+	 \frac{1}{n} 
+	 \sum \limits_{i=1}^n
+	 y_i
+	   \langle \widetilde{X_i}, \psi \rangle_\mathcal{F}  
+	   +  
+	   \frac{1}{n} 
+	   \sum \limits_{i=1}^n  
+	   y_i
+	   \langle \mathbf{Z}_i, 
+	   \boldsymbol{\theta} 
+	   \rangle 
+	    \\
+	&=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
+	&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
+	&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \left\{ \int_{\mathcal{T}_k} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
+	&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
+	&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}).
+\end{align*}
 

### 2025-07-09 manuscript/main.tex
infinite expansion
from Yingying's paper

@@
 
+Given an orthonormal basis $\{b_l(t)\}$, the functional predictors and the corresponding regression coefficients can be decomposed into
+\begin{align*}
+	X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t), \quad 
+	\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t),
+\end{align*}
+where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
+While it is possible to use a different basis for each functional predictor, we adopt a common basis system for all predictors for notational simplicity.
+
 For $k = 1, \ldots, K$, let $\Phi^{(k)}   := \{\phi^{(k)}_1, \ldots, \phi^{(k)}_M\}$, with $M \geq 1$, be an $M$-dimensional basis in $L^2(\mathcal{T}_k)$.
@@
 
-For $k = 1, \ldots, K$, we project the $k$th functional predictor onto 
+For $k = 1, \ldots, K$, we project the $k$th functional predictor $X_i^{(k)}$ onto 
 $\operatorname{span}(\Phi^{(k)})$:
@@
 
-	\subsection{Proof of Propositions \ref{Proposition: generalized rayleigh quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
-	%
-	%
+	\subsection{Proof of new Proposition}
 		\begin{align*}
@@
 	\end{align*}	
+	\subsection{Proof of Propositions \ref{Proposition: generalized rayleigh quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
+	%
+	%
+	\begin{align*}
+	\widehat{\textnormal{Cov}} (
+	\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y 
+	) 
+	&= 
+	\frac{1}{n} \sum \limits_{i=1}^n 
+	 y_i
+	\langle \widetilde{\mathbf{W}}_i, \boldsymbol{\xi} \rangle_\mathcal{H} \\
+	&= 
+	 \frac{1}{n} 
+	 \sum \limits_{i=1}^n
+	 y_i
+	   \langle \widetilde{X_i}, \psi \rangle_\mathcal{F}  
+	   +  
+	   \frac{1}{n} 
+	   \sum \limits_{i=1}^n  
+	   y_i
+	   \langle \mathbf{Z}_i, 
+	   \boldsymbol{\theta} 
+	   \rangle 
+	    \\
+	&=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
+	&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
+	&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \left\{ \int_{\mathcal{T}_k} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
+	&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
+	&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}).
+\end{align*}
 

### 2025-07-09 manuscript/main.tex
X_ij notation for jth functional predictor
also, relocated to dropbox

@@
 	\section{Introduction} \label{sec: Introduction}
+	Functional regression settings involving a large number of predictors, $X_{i1}(t), X_{i2}(t), \ldots, X_{iK}(t)$, are becoming increasingly common.
+For example, \cite{storeySignificanceAnalysisTime2005} analyzes two gene expression datasets measured over time, which involve only a small number of patients but tens of thousands of functional predictors.
 
@@
 	\section{Data Objects and Model Formulation} 
+	We assume without loss of generality that each predictor is observed over the range $0 \leq t \leq 1$.
+
 	Let $\{X^{(k)}\}_{k=1, \ldots, K}$ be a collection of random functions defined on respective compact domains $\mathcal{T}_k \in \mathbb{R}^{d_k}$ ($d_k \in \mathbb{N})$; i.e., $X^{(k)}: \mathcal{T}_k \rightarrow \mathbb{R}$.

### 2025-07-09 manuscript/main.tex
remark for different hilbert spaces

@@
 	\section{Data Objects and Model Formulation} 
-	We assume without loss of generality that each predictor is observed over the range $0 \leq t \leq 1$.
-
-	Let $\{X^{(k)}\}_{k=1, \ldots, K}$ be a collection of random functions defined on respective compact domains $\mathcal{T}_k \in \mathbb{R}^{d_k}$ ($d_k \in \mathbb{N})$; i.e., $X^{(k)}: \mathcal{T}_k \rightarrow \mathbb{R}$.
-Assume that each $X^{(k)}$ is in $L^2(\mathcal{T}_k)$, a Hilbert space of square integrable functions with respect to Lebesgue measure $dt_k$ on $\mathcal{T}_k$.
-Without loss of generality, we further assume that each  $\mathcal{T}_k$ is a $d_k$-dimensional unit interval; for instance  $\mathcal{T}_k=[0,1]$ (unit interval) if $d_k=1$, $\mathcal{T}_k=[0,1] \times [0,1]$ (unit square) if $d_k=2$, and so forth.
+We assume, without loss of generality, that the functional predictors $X_{i1}(t), X_{i2}(t), \ldots, X_{iK}(t)$ are observed over the domain $0 \leq t \leq 1$.
+We also assume that each functional predictor belongs to the space $L^2([0,1])$, the Hilbert space of square-integrable real-valued functions with respect to the Lebesgue measure $dt$ on $[0,1]$.
+
+	\begin{remark}
+Our method is applicable to settings where each functional predictor belongs to a different Hilbert space, possibly defined over a distinct compact domain in $\mathbb{R}^d$, for arbitrary $d$, and observed at different time points.
+However, for notational simplicity, our discussion assumes a common Hilbert space over domain $[0,1]$ for all functional predictors.
+	\end{remark}
+
  Write  $X=(X^{(1)}, \ldots, X^{(K)})$ as a multivariate functional object that belongs to $\mathcal{F} = L^2(\mathcal{T}_1) \times \cdots \times L^2(\mathcal{T}_K)$---a cartesian product of individual $L^2(\mathcal{T}_k)$ spaces.
@@
 
+	\bibliographystyle{apalike}
+	\bibliography{Reference}
+
 	\appendix

### 2025-07-09 manuscript/main.tex
yingying matrix notation

@@
 	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}
-In practice, the functional predictors $X^{(1)}, \ldots, X^{(K)}$ are not observed as complete curves, but only through their values at a finite set of time points, which may differ across the $K$ predictors.
  Thus, each observation is represented by a finite-dimensional vector $X_i^{(k)}(\mathbf{t}_k) \in \mathbb{R}^{|\mathbf{t}_k|}$, where $\mathbf{t}_k \subset \mathcal{T}_k$.
-The first step in functional data analysis typically involves reconstructing the underlying functional form from these discrete measurements, commonly by assuming that sample paths lie in a finite-dimensional space spanned by basis functions.
-
-Given an orthonormal basis $\{b_l(t)\}$, the functional predictors and the corresponding regression coefficients can be decomposed into
-\begin{align*}
+
+Given an orthonormal basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
+\begin{equation*}
 	X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t), \quad 
 	\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t),
-\end{align*}
+\end{equation*}
 where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
+In practice, functional predictors are observed only at a finite set of time points rather than as complete curves.
+Rather than reconstructing infinite-dimensional object stated above via finite observations, we approximate each predictor using a finite-dimensional projection by truncating its basis expansion at a finite number $M$.
+This $M$ can be set to a sufficiently large value (e.g., 15 or 20) to capture a wide range of functional patterns.
+Notably, it is unnecessary to fine-tune $M$, as a  penalization scheme introduced in Section \ref{sec: Regularization of PLS Components} regularizes each functional component to achieve the desired smoothness.
+We denote the projected predictors and coefficients as
+\begin{equation*}
+	\tilde{X}_{ij}(t) = \sum_{l=1}^M \theta_{ijl} \, b_l(t), \quad 
+	\tilde{\beta}_j(t) = \sum_{l=1}^M \eta_{0,jl} \, b_l(t).
+\end{equation*}
+Write $\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top$ and  $\boldsymbol{\eta}_{0j} := (\eta_{0,j1}, \ldots, \eta_{0,jM})^\top$. 
+Let $\Theta_j$ be an $n \times M$ matrix whose rows are given by $\{\boldsymbol{\theta}_{ij}, \; i = 1, \ldots, n\}$.
+
+\begin{remark}
  While it is possible to use a different basis for each functional predictor, we adopt a common basis system for all predictors for notational simplicity.
-
-For $k = 1, \ldots, K$, let $\Phi^{(k)}   := \{\phi^{(k)}_1, \ldots, \phi^{(k)}_M\}$, with $M \geq 1$, be an $M$-dimensional basis in $L^2(\mathcal{T}_k)$.
-In our proposed hybrid PLS regression algorithm, this basis system is used to approximate both the predictors and the PLS components.
-Additionally, it serves as a regularization mechanism, borrowing strength across components and helping to prevent overfitting.
-	The number of basis functions $M$ for each functional predictor can be set to a sufficiently large value (e.g., 15 or 20) to incorporate a rich variety of patterns that functional predictors may exhibit.
-Note that there is no need to carefully choose different $M$ values for different functional predictors, as an appropriate penalization scheme will be introduced in the later section to regularize each functional predictor to achieve a desired smoothness (see Section \ref{sec: Regularization of PLS Components}).
-
-For $k = 1, \ldots, K$, we project the $k$th functional predictor $X_i^{(k)}$ onto 
-$\operatorname{span}(\Phi^{(k)})$:
-\begin{equation*}
-	X_i^{(k)} \approx \sum_{m=1}^M c_{im}^{(k)} \phi_m^{(k)}, \quad i = 1, \ldots, n,
-\end{equation*}
-where the coefficients $c_{im}^{(k)}$ satisfy
-\begin{equation*}
-	X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} \phi_m^{(k)}(t_k), \quad \text{for all } t_k \in \mathbf{t}_k \subset \mathcal{T}_k.
-\end{equation*}
-Thus, the $n$ observations of the $k$th functional predictor can be represented by an $n \times M$ matrix of coefficients, 	where rows index samples and columns index basis functions:
-\begin{equation*}
-		\widetilde{\mathbf{C}}^{(k)} := ( c_{im}^{(k)} ).
-\end{equation*}
-
-Importantly, the core computation of our algorithm involves the inner product between $n$ hybrid predictor observations and a single hybrid object (the PLS direction), defined via the inner product in Definition \ref{def:hilbert_space}.
- With the basis expansion, this reduces to simple matrix operations. 
-For each $k = 1, \ldots, K$, let $\boldsymbol{\Phi}^{(k)} := (\phi^{(k)}_{m \ell })$
-denote the	$M \times M$ symmetric matrix with entries  the inner products between basis functions 
-\begin{equation}\label{def:gram_basis}
-\phi^{(k)}_{m \ell } 
-:= 
-\langle \phi^{(k)}_m,  \phi^{(k)}_\ell \rangle
-=  
-\int_{\mathcal{T}_k} \phi^{(k)}_m(t_k) \, \phi^{(k)}_\ell(t_k) \, dt_k.
-\end{equation}
+\end{remark}
+
+ Additionally, it serves as a regularization mechanism, borrowing strength across components and helping to prevent overfitting. 	T
 

### 2025-07-10 manuscript/main.tex
direction computation new notation

@@
 \begin{equation*}
-	\tilde{X}_{ij}(t) = \sum_{l=1}^M \theta_{ijl} \, b_l(t), \quad 
+	\widetilde{X}_{ij}(t) = \sum_{l=1}^M \theta_{ijl} \, b_l(t), \quad 
 	\tilde{\beta}_j(t) = \sum_{l=1}^M \eta_{0,jl} \, b_l(t).
 \end{equation*}
-Write $\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top$ and  $\boldsymbol{\eta}_{0j} := (\eta_{0,j1}, \ldots, \eta_{0,jM})^\top$. 
-Let $\Theta_j$ be an $n \times M$ matrix whose rows are given by $\{\boldsymbol{\theta}_{ij}, \; i = 1, \ldots, n\}$.
+The $i$th  hybrid predictor with projected functional parts, is a tuple, denoted as
+\begin{equation*}
+	\widetilde{W}_i := 
+	(
+	X_{i1}, \ldots, X_{iK}, \boldsymbol{Z}_i
+	).
+\end{equation*}
+We adopt the following notion for the coefficients:
+\begin{equation}
+	 \boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top \in \mathbb{R}^M,
+	 \quad
+	 \boldsymbol{\eta}_{0j} := (\eta_{0,j1}, \ldots, \eta_{0,jM})^\top  \in \mathbb{R}^M,
+\end{equation}
+and
+\begin{equation}
+	 \Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
+\end{equation}
 
@@
 	Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an intermediate strategy for implementing the first step of the PLS algorithm.
-This approach directly obtains a hybrid PLS direction, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply solving a linear equation.
-
-We now describe the strategy for computing the PLS direction at the $l$-th iteration.
-For simplicity, we omit the iteration index and denote the residualized response by $Y$, with finite-sample observations given by $\mathbf{y} = (y_1, \ldots, y_n) \in \mathbb{R}^n$.
-Let $\widetilde{W} \in \mathcal{H}$ denote the residualized, basis-approximated hybrid predictor, and let $\widetilde{\mathbf{C}}^{(1)}, \ldots, \widetilde{\mathbf{C}}^{(k)} \in \mathbb{R}^{n \times M}$ denote the basis coefficient matrices of its functional part in the finite-sample observations.
-Our strategy seeks the direction $\boldsymbol{\xi} \in \mathcal{H}$, whose functional parts lying in
-$\operatorname{span}(\Phi^{(1)}), \ldots, \operatorname{span}(\Phi^{(K)})$
-, that maximizes the empirical covariance between the resulting PLS component $\langle \widetilde{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the response.
-
-For the computation of the estimated PLS direction  $\hat{\boldsymbol{\xi}}$, 
-we obtain the basis coefficients of its functional part, denoted by $\mathbf{d}^{(1)}, \ldots, \mathbf{d}^{(K)} \in \mathbb{R}^{M}$,
-and the scalar part  
-$\mathbf{d} \in \mathbb{R}^p$,
-by solving linear systems
-\begin{equation*}
- \boldsymbol{\Phi}^{(1)}
-\mathbf{d}^{(1)} 
+This approach directly obtains a hybrid PLS component direction, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply solving a linear equation.
+We now describe the strategy for computing the PLS component direction at the $l$-th iteration.
+For simplicity, we omit the iteration index and assume that the observations have been residualized and are orthogonal to those from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for the residualization procedure).
+
+The goal is to find a unit-norm direction $\boldsymbol{\xi} \in \mathcal{H}$, whose functional components lie in $\operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr)$, that maximizes the empirical covariance between the resulting PLS component scores $\langle \widetilde{W}_1, \boldsymbol{\xi} \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$.
+We denote the solution as
+\begin{equation}
+	\hat{\boldsymbol{\xi}} 
 	= 
-(\widetilde{\mathbf{C}}^{(1)} \boldsymbol{\Phi}^{(1)})^\top
-\mathbf{y},
-\ldots
-,
-\boldsymbol{\Phi}^{(K)}
-\mathbf{d}^{(K)} 
-=
-(\widetilde{\mathbf{C}}^{(K)} \boldsymbol{\Phi}^{(K)})^\top
-\mathbf{y},
-~\text{and}~
-\mathbf{d} := \mathbf{Z}^\top \mathbf{y} .
-\end{equation*}
-The estimated PLS direction is the tuple $\hat{\boldsymbol{\xi}} \in \mathcal{H}$, defined with these coefficients and normalized with respect to the 
-hybrid Hilbert norm (Definition
-\ref{def:hilbert_space})
-as follows:
+	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}}),
+\end{equation}
+where $\hat{\boldsymbol{\zeta}} \in \mathbb{R}^p$ is the scalar part, and each functional part $\hat{\xi}_j \in L^2([0,1])$ lies in $\operatorname{span}(b_1(t), \ldots, b_M(t))$ and is expressed as
+\begin{equation*}
+	\hat{\xi}_j(t) = 
+	\sum_{l=1}^M d_{jl} \, b_l(t), \quad j = 1, \ldots, K.
+\end{equation*}
+
+Let $\mathbf{d}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$ and $\mathbf{y} := (y_1, \ldots, y_n)^\top$.
+We compute $\mathbf{d}_1, \ldots, \mathbf{d}_K$ and $\hat{\boldsymbol{\zeta}}$ as follows.
+First, we obtain the unnormalized coefficient vectors. For each $j$, the unnormalized vector $\bar{\mathbf{d}}_j$ is computed by solving
+\begin{equation*}
+	B \bar{\mathbf{d}}_j = (\Theta_j B)^\top \mathbf{y},
+\end{equation*}
+ The unnormalized scalar component is given by
+\begin{equation}
+	\bar{\boldsymbol{\zeta}} := Z^\top \mathbf{y}.
+\end{equation}
+Next, we normalize all components with respect to the hybrid Hilbert norm (see Definition~\ref{def:hilbert_space}) to ensure $\hat{\boldsymbol{\xi}}$ has unit length. Specifically, we define
 \begin{equation}\label{def:computed_PLS_direction}
-	\hat{\boldsymbol{\xi}} :=
+	\mathbf{d}_j := 
 	\frac{1}{
-	\bigl(
-	\mathbf{d}^\top \mathbf{d} + 
-	\sum_{k=1}^K (\mathbf{d}^{(k)})^\top  \boldsymbol{\Phi}^{(K)}  \mathbf{d}^{(k)} 
-	\bigr)^{1/2}
-	}
-	\biggl(
-	\sum_{m=1}^M d^{(1)}_m \phi^{(1)}_m,
-	\ldots,
-	\sum_{m=1}^M d^{(K)}_m \phi^{(K)}_m,
-	\mathbf{d}
-	\biggr).
-\end{equation}
-The details of this hybrid norm computation are provided in Appendix~\ref{section:proof:eigenproblem_derivation}.
+		\left(
+		\sum_{j=1}^K \bar{\mathbf{d}}_j^\top B \bar{\mathbf{d}}_j +
+		\bar{\boldsymbol{\zeta}}^\top \bar{\boldsymbol{\zeta}}
+		\right)^{1/2}
+	} \bar{\mathbf{d}}_j, \quad j = 1, \ldots, K,
+\end{equation}
+and
+\begin{equation}
+	\hat{\boldsymbol{\zeta}} :=
+	\frac{1}{
+		\left(
+		\sum_{j=1}^K \bar{\mathbf{d}}_j^\top B \bar{\mathbf{d}}_j +
+		\bar{\boldsymbol{\zeta}}^\top \bar{\boldsymbol{\zeta}}
+		\right)^{1/2}
+	} \bar{\boldsymbol{\zeta}}.
+\end{equation}
+
+Details of the hybrid norm computation are provided in Appendix~\ref{section:proof:eigenproblem_derivation}.
+
 Finally, the estimated $l$th PLS scores for the $n$ observations,
@@
 The details of this computation are provided in Appendix~\ref{section:proof:eigenproblem_derivation}.
-Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS direction, the normalization step couples them, allowing the components to influence each other.
+Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other.
 This enables the procedure to account for the correlation between functional and scalar components.
@@
 \begin{proposition} \label{Proposition: generalized rayleigh quotient}
-	Let $\boldsymbol{\xi} \in \mathcal{H}$ be any unit-norm direction such that its $1$st through $K$th functional components lie in $\operatorname{span}(\Phi^{(1)}), \ldots, \operatorname{span}(\Phi^{(K)})$, respectively.
+	Let $\boldsymbol{\xi} \in \mathcal{H}$ be any unit-norm direction such that its $1$st through $K$th functional components lie in $\operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr)$, respectively.
 	Then, the empirical covariance between the projected component $\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the response $Y$, approximated in terms of the basis, is given by
@@
 	\end{equation*}
-Then the PLS direction 
+Then the PLS component direction 
 $	\hat{\boldsymbol{\xi}}$ 

### 2025-07-10 manuscript/main.tex
remove different evaluation point notation

@@
 	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
- Thus, each observation is represented by a finite-dimensional vector $X_i^{(k)}(\mathbf{t}_k) \in \mathbb{R}^{|\mathbf{t}_k|}$, where $\mathbf{t}_k \subset \mathcal{T}_k$.
-
 	Given an orthonormal basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
@@
 
-	\bibliographystyle{apa} 
-	\bibliography{Reference}
-
 \end{document}

### 2025-07-10 manuscript/main.tex
gram matrix notation

@@
 	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
-	Given an orthonormal basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
+	Given a basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
 	\begin{equation*}
@@
 	\end{equation*}
-	We adopt the following notion for the coefficients:
+	We adopt the following notation for the coefficients:
 	\begin{equation}
@@
 	\begin{equation*}
-		\hat{\xi}_j(t) = 
+		\hat{\xi}_j(t) := 
 		\sum_{l=1}^M d_{jl} \, b_l(t), \quad j = 1, \ldots, K.
@@
 	Let $\mathbf{d}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$ and $\mathbf{y} := (y_1, \ldots, y_n)^\top$. 
+	Let $B \in \mathbb{R}^{M \times M}$ denote the Gram matrix of the basis functions, with entries
+	\[
+	B_{l, l'} := \langle b_l, b_{l'} \rangle_{L^2([0,1])}, \quad l, l' = 1, \ldots, M.
+	\]
 	We compute $\mathbf{d}_1, \ldots, \mathbf{d}_K$ and $\hat{\boldsymbol{\zeta}}$ as follows.

### 2025-07-10 manuscript/main.tex
empirical covariance as inner product

@@
 
-	Write  $X=(X^{(1)}, \ldots, X^{(K)})$ as a multivariate functional object that belongs to $\mathcal{F} = L^2(\mathcal{T}_1) \times \cdots \times L^2(\mathcal{T}_K)$---a cartesian product of individual $L^2(\mathcal{T}_k)$ spaces.
+	Write  $X=(X^{(1)}, \ldots, X^{(K)})$ as a multivariate functional object that belongs to $\mathcal{F} = L^2(\mathcal{T}_1) \times \cdots \times L^2([0,1])$---a cartesian product of individual $L^2([0,1])$ spaces.
 Note that if $K=1$, $X$ reduces to a univariate functional object.
-We can also express the functional object $X$ evaluated on the multi-dimensional argument $\mathbf{t} = (t_1, \ldots, t_k)^\top \in \mathcal{T} = \mathcal{T}_1 \times \cdots \times \mathcal{T}_K$ as a $K$-dimensional vector $X(\mathbf{t})=(X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top$.
-The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)}) $ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as $\langle f_1, f_2\rangle_\mathcal{F} =  \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)}\rangle_{L^2} = \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k$ with norm $\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k)^2 dt_k\}^{1/2}$.
+We can also express the functional object $X$ evaluated on the multi-dimensional argument $\mathbf{t} = (t_1, \ldots, t_k)^\top \in \mathcal{T} = \mathcal{T}_1 \times \cdots \times [0,1]$ as a $K$-dimensional vector $X(\mathbf{t})=(X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top$.
+The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)}) $ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as $\langle f_1, f_2\rangle_\mathcal{F} =  \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)}\rangle_{L^2} = \sum_{k=1}^K \int_0^1 f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k$ with norm $\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_0^1 f_1^{(k)}(t_k)^2 dt_k\}^{1/2}$.
 
@@
 	\begin{equation}
-		Y = \sum \limits_{r=1}^p \alpha_r Z_r + \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \beta^{(k)}(t_k) X^{(k)}(t_k) dt_k + \epsilon = \langle \boldsymbol{\alpha}, \mathbf{Z} \rangle +  \langle \beta, X \rangle_{\mathcal{F}}  + \epsilon
+		Y = \sum \limits_{r=1}^p \alpha_r Z_r + \sum \limits_{k=1}^K \int_0^1 \beta^{(k)}(t_k) X^{(k)}(t_k) dt_k + \epsilon = \langle \boldsymbol{\alpha}, \mathbf{Z} \rangle +  \langle \beta, X \rangle_{\mathcal{F}}  + \epsilon
 		\label{eq: functional model}
@@
 			+
-			\omega \langle  \mathbf{v_1}, \mathbf{v_2} \rangle = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k
+			\omega \langle  \mathbf{v_1}, \mathbf{v_2} \rangle = \sum \limits_{k=1}^K \int_0^1 f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k
 			+
@@
 	where $(\boldsymbol{\delta}_l)_{l \in \mathbb{N}} \in \mathcal{H}$ and $(\nu_l)_{l \in \mathbb{N}} \in \mathbb{R}$ are appropriate bases.
-The PLS scores are obtained as $\rho_l =  \langle \mathbf{W}^{[l]}, \boldsymbol{\xi}_l \rangle_{\mathcal{H}}$, where $\mathbf{W}^{[l]}$ denotes the residualized predictor sequentially derived as the residual of the regression of $\mathbf{W}^{[l-1]}$ on $\rho_{l-1}$ with $\mathbf{W}^{[1]} = \mathbf{W}$, and $\boldsymbol{\xi}_l=(\psi_l, \boldsymbol{\theta}_l) \in \mathcal{H}$ is the hybrid PLS component, with $\psi_l = (\psi^{(1)}_l, \ldots, \psi_l^{(K)}) \in \mathcal{F}$ and $\boldsymbol{\theta}_l=(\theta_{l1}, \ldots, \theta_{lp})^\top \in \mathbb{R}^p$, sequentially chosen to maximize the squared covariance between $\rho_l$ and the residualized outcome $Y^{[l]}$---i.e., $\textnormal{Cov}^2(\rho_l, Y^{[l]}) = \textnormal{Cov}^2(\langle \mathbf{W}^{[l]}, \boldsymbol{\xi}_l \rangle_\mathcal{H}, Y^{[l]})$.
+The PLS scores are obtained as $\rho_l =  \langle \mathbf{W}^{[l]}, \xi_l \rangle_{\mathcal{H}}$, where $\mathbf{W}^{[l]}$ denotes the residualized predictor sequentially derived as the residual of the regression of $\mathbf{W}^{[l-1]}$ on $\rho_{l-1}$ with $\mathbf{W}^{[1]} = \mathbf{W}$, and $\xi_l=(\psi_l, \boldsymbol{\theta}_l) \in \mathcal{H}$ is the hybrid PLS component, with $\psi_l = (\psi^{(1)}_l, \ldots, \psi_l^{(K)}) \in \mathcal{F}$ and $\boldsymbol{\theta}_l=(\theta_{l1}, \ldots, \theta_{lp})^\top \in \mathbb{R}^p$, sequentially chosen to maximize the squared covariance between $\rho_l$ and the residualized outcome $Y^{[l]}$---i.e., $\textnormal{Cov}^2(\rho_l, Y^{[l]}) = \textnormal{Cov}^2(\langle \mathbf{W}^{[l]}, \xi_l \rangle_\mathcal{H}, Y^{[l]})$.
 Here, $Y^{[l]}$ is also sequentially obtained as the residual of the regression of $Y^{[l-1]}$ on $\rho_{l-1}$ with $Y^{[1]} = Y$.
-The sequentially derived hybrid PLS components \{$\boldsymbol{\xi}_l\}_{l=1}^\infty$, are orthonormal in a sense that $\langle \boldsymbol{\xi}_l, \boldsymbol{\xi}_j \rangle_\mathcal{H} = \mathbb{1}(l=j)$.
+The sequentially derived hybrid PLS components \{$\xi_l\}_{l=1}^\infty$, are orthonormal in a sense that $\langle \xi_l, \xi_j \rangle_\mathcal{H} = \mathbb{1}(l=j)$.
 
@@
 			$
-			\widehat{\boldsymbol{\xi}}_{l}[\mathbf{t}] 
+			\widehat{\xi}_{l}[\mathbf{t}] 
 			\leftarrow 
@@
 			\bigl\{
-			\langle \mathbf{W}_{1}^{[l]}, \widehat{\boldsymbol{\xi}}_{l} \rangle_{\mathcal{H}},
+			\langle \mathbf{W}_{1}^{[l]}, \widehat{\xi}_{l} \rangle_{\mathcal{H}},
 			\ldots,
-			\langle \mathbf{W}_{n}^{[l]}, \widehat{\boldsymbol{\xi}}_{l} \rangle_{\mathcal{H}}
+			\langle \mathbf{W}_{n}^{[l]}, \widehat{\xi}_{l} \rangle_{\mathcal{H}}
 			\bigr\}
@@
 		\begin{equation}\label{def:pls_score_naive}
-			\widehat{\rho}_{il} = \langle \mathbf{W}_{i}^{[l]}, \widehat{\boldsymbol{\xi}}_{l} \rangle_{\mathcal{H}} = \langle X_i^{[l]}, \widehat{\psi}_{l} \rangle_{\mathcal{F}} + \langle \mathbf{Z}_i^{[l]}, \widehat{\boldsymbol{\theta}}_{l} \rangle,
-		\end{equation}
-		where the $l$-th PLS loading $\widehat{\boldsymbol{\xi}}_{l} = (\widehat{\psi}_{l}, \widehat{\boldsymbol{\theta}}_{l}) \in \mathcal{H}$ maximizes $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}_{i}^{[l]}, \widehat{\boldsymbol{\xi}}_{l} \rangle_{\mathcal{H}}, Y_i^{[l]})=\widehat{\textnormal{Cov}}^2(\widehat{\rho_{il}}, Y_i^{[l]})$.
+			\widehat{\rho}_{il} = \langle \mathbf{W}_{i}^{[l]}, \widehat{\xi}_{l} \rangle_{\mathcal{H}} = \langle X_i^{[l]}, \widehat{\psi}_{l} \rangle_{\mathcal{F}} + \langle \mathbf{Z}_i^{[l]}, \widehat{\boldsymbol{\theta}}_{l} \rangle,
+		\end{equation}
+		where the $l$-th PLS loading $\widehat{\xi}_{l} = (\widehat{\psi}_{l}, \widehat{\boldsymbol{\theta}}_{l}) \in \mathcal{H}$ maximizes $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}_{i}^{[l]}, \widehat{\xi}_{l} \rangle_{\mathcal{H}}, Y_i^{[l]})=\widehat{\textnormal{Cov}}^2(\widehat{\rho_{il}}, Y_i^{[l]})$.
 Specifically, we define the $l$-th PLS loadings pointwise as follows:
 		\begin{equation}\label{def:pls_loading_ptws}
-			\widehat{\boldsymbol{\xi}}_{l}[\mathbf{t}] = \frac{\sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]}[\mathbf{t}]}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} = \left[ \frac{\sum_{i=1}^n Y_i^{[l]} X_i^{[l]}(\mathbf{t})}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}}, \frac{\sum_{i=1}^n Y_i^{[l]}\mathbf{Z}_i^{[l]}}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} \right]^\top,
+			\widehat{\xi}_{l}[\mathbf{t}] = \frac{\sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]}[\mathbf{t}]}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} = \left[ \frac{\sum_{i=1}^n Y_i^{[l]} X_i^{[l]}(\mathbf{t})}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}}, \frac{\sum_{i=1}^n Y_i^{[l]}\mathbf{Z}_i^{[l]}}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} \right]^\top,
 		\end{equation}
@@
 	\subsection{Step 1: Computing smoothed PLS components}  \label{subsec: Step 1: Computing Smoothed PLS components}
-	The function part $\psi$ of the hybrid PLS component $\boldsymbol{\xi}$ is inherently infinite-dimensional, rendering its estimation impossible with finite sample size.
+	The function part $\psi$ of the hybrid PLS component $\xi$ is inherently infinite-dimensional, rendering its estimation impossible with finite sample size.
 As such, we first approximate each functional predictor (observed version when $l=1$, or residualized version when $l \ge 2$) as a linear combination of $M$ basis functions and coefficients.
@@
 
-	Additionally, it serves as a regularization mechanism, borrowing strength across components and helping to prevent overfitting. 	T
+	Additionally, it serves as a regularization mechanism, borrowing strength across components and helping to prevent overfitting.
 
@@
 
-	The goal is to find a unit-norm direction $\boldsymbol{\xi} \in \mathcal{H}$, whose functional components lie in $\operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr)$, that maximizes the empirical covariance between the resulting PLS component scores $\langle \widetilde{W}_1, \boldsymbol{\xi} \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$.
+	The goal is to find a unit-norm direction $\xi \in \mathcal{H}$, whose functional components lie in $\operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr)$, that maximizes the empirical covariance between the resulting PLS component scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$.
 	We denote the solution as
 	\begin{equation}
-		\hat{\boldsymbol{\xi}} 
+		\hat{\xi} 
 		= 
@@
 		\hat{\xi}_j(t) := 
-		\sum_{l=1}^M d_{jl} \, b_l(t), \quad j = 1, \ldots, K.
+		\sum_{m=1}^M d_{jm} \, b_m(t), \quad j = 1, \ldots, K.
 	\end{equation*}
@@
 	\[
-	B_{l, l'} := \langle b_l, b_{l'} \rangle_{L^2([0,1])}, \quad l, l' = 1, \ldots, M.
+	B_{m, m'} := \langle b_m, b_{m'} \rangle, \quad m, m' = 1, \ldots, M.
 	\]
@@
 	\end{equation}
-	Next, we normalize all components with respect to the hybrid Hilbert norm (see Definition~\ref{def:hilbert_space}) to ensure $\hat{\boldsymbol{\xi}}$ has unit length. Specifically, we define
+	Next, we normalize all components with respect to the hybrid Hilbert norm (see Definition~\ref{def:hilbert_space}) to ensure $\hat{\xi}$ has unit length. Specifically, we define
 	\begin{equation}\label{def:computed_PLS_direction}
@@
 	\end{equation}
-
 	Details of the hybrid norm computation are provided in Appendix~\ref{section:proof:eigenproblem_derivation}.
 
-	Finally, the estimated $l$th PLS scores for the $n$ observations,
-	denoted $\hat{\boldsymbol{\rho}} \in \mathbb{R}^n$
+The estimated $l$th PLS component score for the $i$th observations,
+	denoted $\hat{\rho}_i$
 	is computed via hybrid inner product. In a matrix multiplication form, it is computed as:
 	\begin{align*}
-		\hat{\boldsymbol{\rho}}
+	\hat{\rho}_i
 		&:=
-		\biggl(
-		\langle \widetilde{\mathbf{W}}_1, \hat{\boldsymbol{\xi}} \rangle_{\mathcal{H}},
-		\ldots,
-		\langle \widetilde{\mathbf{W}}_n, \hat{\boldsymbol{\xi}} \rangle_{\mathcal{H}}
-		\biggr)^\top
-		\\&	=
-		\frac{1}{
-			\bigl(
-			\mathbf{d}^\top \mathbf{d} + 
-			\sum_{k=1}^K (\mathbf{d}^{(k)})^\top  \boldsymbol{\Phi}^{(K)}  \mathbf{d}^{(k)} 
-			\bigr)^{1/2}
-		}
-		\biggl(
-		\mathbf{Z} \mathbf{d}
+		\langle \widetilde{\mathbf{W}}_i, \hat{\xi} \rangle_{\mathcal{H}}
+		=
+		\sum_{j=1}^K \Theta_j B  \mathbf{d}_j
 		+
-		\sum_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \boldsymbol{\Phi}^{(k)} \mathbf{d}^{(k)}
-		\biggr)
+			Z \hat{\boldsymbol{\zeta}} 
 		. 
@@
 	\begin{proposition} \label{Proposition: generalized rayleigh quotient}
-		Let $\boldsymbol{\xi} \in \mathcal{H}$ be any unit-norm direction such that its $1$st through $K$th functional components lie in $\operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr)$, respectively.
-		Then, the empirical covariance between the projected component $\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the response $Y$, approximated in terms of the basis, is given by
-		\begin{equation*}
-			\widehat{\textnormal{Cov}} \left( \langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y \right)
+		Let $\xi \in \mathcal{H}$ be any unit-norm direction such that its $1$st through $K$th functional components lie in $\operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr)$, respectively.
+		Then, the empirical covariance between the projected component $\langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}$ and the response $Y$, approximated in terms of the basis, is given by
+		\begin{equation*}
+			\widehat{\textnormal{Cov}} \left( \langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y \right)
 			:=
@@
 			y_i
-			\langle \widetilde{\mathbf{W}}_i, \boldsymbol{\xi} \rangle_{\mathcal{H}}.
+			\langle \widetilde{\mathbf{W}}_i, \xi \rangle_{\mathcal{H}}.
 		\end{equation*}
 		Then the PLS component direction 
-		$	\hat{\boldsymbol{\xi}}$ 
-		computed in \eqref{def:computed_PLS_direction} maximizes $\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )$.
+		$	\hat{\xi}$ 
+		computed in \eqref{def:computed_PLS_direction} maximizes $\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y )$.
 	\end{proposition}
@@
 	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
-	Although Proposition \ref{Proposition: generalized rayleigh quotient} provides an efficient and principled way to compute the PLS components $\boldsymbol{\xi}$, their functional part $\psi=(\psi^{(1)}, \ldots, \psi^{(K)})$ may not be smooth, which can lead to overfitting and unstable predictions.
+	Although Proposition \ref{Proposition: generalized rayleigh quotient} provides an efficient and principled way to compute the PLS components $\xi$, their functional part $\psi=(\psi^{(1)}, \ldots, \psi^{(K)})$ may not be smooth, which can lead to overfitting and unstable predictions.
 Thus, in this section, we provide a modification of Proposition  \ref{Proposition: generalized rayleigh quotient} that yields regularized (smoothed) PLS components.
@@
 		\textnormal{PEN} \left(\psi^{(k)} \right) 
-		=  \int_{\mathcal{T}_k} \ddot{\psi}^{(k)}(t)^2 dt = \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)},
+		=  \int_0^1 \ddot{\psi}^{(k)}(t)^2 dt = \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)},
 		\label{eq: roughness penalty}
@@
 
-	Now, maximizing $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)$ is not the only aim; we also want to prevent the roughness of each $\psi^{(k)}$---that is, $\textnormal{PEN}(\psi^{(k)})$---from being too large.
-One possible way to achieve this is to extend \citet{Rice1991}'s approach of obtaining smoothed functional PCA components, and find $\boldsymbol{\xi}^*$ that maximizes:
-	\begin{equation}
-		\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right) - \sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right),
+	Now, maximizing $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)$ is not the only aim; we also want to prevent the roughness of each $\psi^{(k)}$---that is, $\textnormal{PEN}(\psi^{(k)})$---from being too large.
+One possible way to achieve this is to extend \citet{Rice1991}'s approach of obtaining smoothed functional PCA components, and find $\xi^*$ that maximizes:
+	\begin{equation}
+		\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right) - \sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right),
 		\label{eq: penalized squred variance}
 	\end{equation}
-	subject to $\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1$.
-The equation \eqref{eq: penalized squred variance} quantifies the trade-off between fidelity to the data (in this case the sample covariance between the $\rho=\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}$ and $Y$ in the direction of $\boldsymbol{\xi}$) and roughness as measured by the sum of the individual penalty terms in \eqref{eq: roughness penalty}.
+	subject to $\xi^{*\top} J^\ast \xi^*=1$.
+The equation \eqref{eq: penalized squred variance} quantifies the trade-off between fidelity to the data (in this case the sample covariance between the $\rho=\langle \mathbf{W}, \xi \rangle_\mathcal{H}$ and $Y$ in the direction of $\xi$) and roughness as measured by the sum of the individual penalty terms in \eqref{eq: roughness penalty}.
 The smoothing parameters $\{\lambda_k\}_{k=1}^K$ control the relative importance between the two objectives.
@@
 	\begin{equation*}
-		\sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right) = \sum \limits_{k=1}^K \lambda_k \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)} = \boldsymbol{\xi}^{* \top} \Lambda \ddot{J}^\ast \boldsymbol{\xi}^*,
+		\sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right) = \sum \limits_{k=1}^K \lambda_k \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)} = \xi^{* \top} \Lambda \ddot{J}^\ast \xi^*,
 	\end{equation*}
@@
 This approach is known to produce appropriately smoothed functional PCA components under milder conditions than the \citet{Rice1991}'s approach by replacing the usual $L^2$-orthonormality constraint with the one that takes account the roughness of functions via the modified inner product.
-Specifically, the following proposition provides a generalized Rayleigh quotient problem which modifies the $\mathcal{H}$-orthonormality constraint of the hybrid PLS components to incorporate roughness penalty, and thus whose solution corresponds to a smoothed PLS component maximizing $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)$ over the class of all functions satisfying sufficient smoothness.
+Specifically, the following proposition provides a generalized Rayleigh quotient problem which modifies the $\mathcal{H}$-orthonormality constraint of the hybrid PLS components to incorporate roughness penalty, and thus whose solution corresponds to a smoothed PLS component maximizing $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)$ over the class of all functions satisfying sufficient smoothness.
 	\begin{proposition} \label{Proposition: Regularized generalized rayleigh quotient}
@@
 		\end{equation*}
-		and  $\boldsymbol{\xi}^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$.
-Then, the $l$-th smoothed PLS component, $\widehat{\boldsymbol{\xi}} \equiv \widehat{\boldsymbol{\xi}}_l$ can be obtained in the following way.
+		and  $\xi^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$.
+Then, the $l$-th smoothed PLS component, $\widehat{\xi} \equiv \widehat{\xi}_l$ can be obtained in the following way.
 		We first compute the basis coefficients by solving the optimization problem
@@
 			\begin{split}
-				&\argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*\top}(J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*} , \quad \textit{or equivalently}, \\
-				&\argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*=1.
+				&\argmax \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top}(J^\ast+\Lambda \ddot{J}^\ast) \xi^*} , \quad \textit{or equivalently}, \\ 
+				&\argmax \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1.
 				\label{eq: Regularized generalized rayleigh quotient equation}
@@
 		\begin{equation*}
-			\widehat{\boldsymbol{\xi}}[\mathbf{t}] = [\widehat{\psi}(\mathbf{t})^\top, \widehat{\boldsymbol{\theta}}^\top]^\top =  B^\ast[\mathbf{t}]^\top \widehat{\boldsymbol{\xi}}^\ast.   
+			\widehat{\xi}[\mathbf{t}] = [\widehat{\psi}(\mathbf{t})^\top, \widehat{\boldsymbol{\theta}}^\top]^\top =  B^\ast[\mathbf{t}]^\top \widehat{\xi}^\ast.   
 		\end{equation*}
@@
 		\begin{equation}\label{compute_pls_score}
-			\widehat{\rho}_i = \langle \mathbf{W}_i, \widehat{\boldsymbol{\xi}} \rangle_\mathcal{H}
+			\widehat{\rho}_i = \langle \mathbf{W}_i, \widehat{\xi} \rangle_\mathcal{H}
 		\end{equation}
@@
 
-	The constraint $\boldsymbol{\xi}^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*=1$ enforces the following modified orthonormality of the estimated PLS components ($\widehat{\boldsymbol{\xi}}_1, \widehat{\boldsymbol{\xi}}_2, \ldots$)  based on the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ which now takes into account the roughness of the functions:
-	\begin{align*}
-		\langle \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle \rangle 
-		&= \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right \rangle_{L^2} \\
-		&= \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_{\mathcal{T}_k} \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
+	The constraint $\xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1$ enforces the following modified orthonormality of the estimated PLS components ($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ which now takes into account the roughness of the functions:
+	\begin{align*}
+		\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
+		&= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right \rangle_{L^2} \\
+		&= \sum \limits_{k=1}^K \int_0^1 \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_0^1 \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
 		& = \mathbb{1}(l=j). 
@@
 	\end{equation*}
-	through the transformations $\mathbf{e} = L^\top \boldsymbol{\xi}^*$ and $E = L^{-1} \mathbf{V}^\ast L^{\top-1}$.
-Once $\mathbf{e}$ is obtained as the first eigenvector of $E$, we set $\boldsymbol{\xi}^* = L^{\top-1} \mathbf{e}$ and $\widehat{\boldsymbol{\xi}}[\mathbf{t}] = B^*[\mathbf{t}]^\top \boldsymbol{\xi}^*$.
+	through the transformations $\mathbf{e} = L^\top \xi^*$ and $E = L^{-1} \mathbf{V}^\ast L^{\top-1}$.
+Once $\mathbf{e}$ is obtained as the first eigenvector of $E$, we set $\xi^* = L^{\top-1} \mathbf{e}$ and $\widehat{\xi}[\mathbf{t}] = B^*[\mathbf{t}]^\top \xi^*$.
 
@@
 	The regression coefficient $\boldsymbol{\eta}$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS components and scores.
-First, note that we can show $\widehat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \widehat{\boldsymbol{\xi}}_l \rangle_\mathcal{H} = \langle \mathbf{W}_i, \widehat{\boldsymbol{\zeta}}_l \rangle_\mathcal{H}$, where $\widehat{\boldsymbol{\zeta}}_l = \widehat{\boldsymbol{\xi}}_l - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}_u, \widehat{\boldsymbol{\xi}}_l \rangle_{\mathcal{H}} \widehat{\boldsymbol{\zeta}}_u$ for $l \ge 2$, with $\widehat{\boldsymbol{\zeta}}_1 = \widehat{\boldsymbol{\xi}}_1$.
+First, note that we can show $\widehat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} = \langle \mathbf{W}_i, \widehat{\boldsymbol{\zeta}}_l \rangle_\mathcal{H}$, where $\widehat{\boldsymbol{\zeta}}_l = \widehat{\xi}_l - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}_u, \widehat{\xi}_l \rangle_{\mathcal{H}} \widehat{\boldsymbol{\zeta}}_u$ for $l \ge 2$, with $\widehat{\boldsymbol{\zeta}}_1 = \widehat{\xi}_1$.
 Then, the decomposition of $Y_i$ in \eqref{eq: decomposition} leads to
 	\begin{equation*}
-		Y_i = \sum \limits_{l=1}^L \widehat{\nu}_l \langle \mathbf{W}_i^{[l]}, \widehat{\boldsymbol{\xi}}_l \rangle_\mathcal{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l \right\rangle_\mathcal{H}+\epsilon_i,
+		Y_i = \sum \limits_{l=1}^L \widehat{\nu}_l \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l \right\rangle_\mathcal{H}+\epsilon_i,
 	\end{equation*}
@@
 			\Comment{ \eqref{def:V_star}}
-			\State 	$\widehat{\boldsymbol{\xi}}_l^\ast \leftarrow \argmax_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \boldsymbol{\xi}^*=1
+			\State 	$\widehat{\xi}_l^\ast \leftarrow \argmax_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1
 			$
@@
 			\leftarrow 
-			\widetilde{C}^* J^\ast  \widehat{\boldsymbol{\xi}}_l^\ast
+			\widetilde{C}^* J^\ast  \widehat{\xi}_l^\ast
 			$
@@
 	\begin{align*}
-		& \mathcal{C}_{YW} \mathbf{h} = E\{\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \sigma_{YX}^{(k)}(t_k) f^{(k)}(t_k) dt_k + E(Y \mathbf{Z}^\top) \mathbf{v} \\
+		& \mathcal{C}_{YW} \mathbf{h} = E\{\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX}^{(k)}(t_k) f^{(k)}(t_k) dt_k + E(Y \mathbf{Z}^\top) \mathbf{v} \\
 		& \mathcal{C}_{WY} d = E (\langle Y, d \rangle \mathbf{W} ) = E(Y\mathbf{W})d =  \Sigma_{YW} \, d. 
@@
 		\begin{align}
-			\max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in \mathcal{T}_k} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
+			\max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in [0,1]} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
 		\end{align}
-		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in \mathcal{T}_k$ with $|t_k - t_k^* | < \delta_k$, we have that
+		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in [0,1]$ with $|t_k - t_k^* | < \delta_k$, we have that
 		\begin{equation*}
@@
 	The proof of Proposition \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
-	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\boldsymbol{\xi}_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \boldsymbol{\xi}_{(u)} = \kappa_{(u)}  \boldsymbol{\xi}_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
+	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
 
@@
 		\begin{equation*}
-			\max \limits_{\substack{\boldsymbol{\xi} \in \mathcal{H} \\ \Vert \boldsymbol{\xi} \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)
-		\end{equation*}
-		is achieved when $\boldsymbol{\xi}$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.	
+			\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)
+		\end{equation*}
+		is achieved when $\xi$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.	
 	\end{proposition}
 	The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
-	In other words, $l$-th PLS component $\boldsymbol{\xi}_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.
+	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.
 
@@
 	\begin{proposition}\label{proposition: modified orthnormality of PLS components}
-		The estimated PLS components, $\widehat{\boldsymbol{\xi}}_1, \widehat{\boldsymbol{\xi}}_2, \ldots, \widehat{\boldsymbol{\xi}}_L$, from the proposed PLS algorithm are mutually orthonormal with respect to the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ in $\mathcal{H}$ that incorporates the roughness of the functions; i.e.,
-		\begin{equation*}
-			\langle \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle \rangle 
-			= \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}
+		The estimated PLS components, $\widehat{\xi}_1, \widehat{\xi}_2, \ldots, \widehat{\xi}_L$, from the proposed PLS algorithm are mutually orthonormal with respect to the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ in $\mathcal{H}$ that incorporates the roughness of the functions; i.e.,
+		\begin{equation*}
+			\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
+			= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}
 			= \mathbb{1}(l=j). 
@@
 	\begin{equation*}
-		X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)=\mathbf{c}_i^{(k)T}\mathbf{b}^{(k)}(t_k), \;\; t_k \in \mathcal{T}_k, \;\; k=1, \ldots, K, \;\; i=1, \ldots, n,
+		X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)=\mathbf{c}_i^{(k)T}\mathbf{b}^{(k)}(t_k), \;\; t_k \in [0,1], \;\; k=1, \ldots, K, \;\; i=1, \ldots, n,
 	\end{equation*}
@@
 	\paragraph{Basis approximation of the PLS component.}
-	We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\boldsymbol{\xi}[\mathbf{t}] = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$.
+	We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\xi[\mathbf{t}] = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$.
 	%
@@
 	\begin{equation}\label{def:dodot_J_k}
-		\ddot{J}^{(k)} = \left[ \int_{\mathcal{T}_k} \ddot{b}^{(k)}_m(t) \ddot{b}^{(k)}_n(t) \, dt \right]_{m,n=1}^M.
+		\ddot{J}^{(k)} = \left[ \int_0^1 \ddot{b}^{(k)}_m(t) \ddot{b}^{(k)}_n(t) \, dt \right]_{m,n=1}^M.
 	\end{equation}
@@
 	\subsection{Proof of new Proposition}
+	For any $\xi = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta})\in \mathcal{H}$, we have:
 	\begin{align*}
 		\widehat{\textnormal{Cov}} (
-		\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y 
+		\langle \widetilde{W}, \xi  \rangle_{\mathcal{H}}, Y 
+		) 
+		&=  %1
+		\frac{1}{n} 
+		\sum 
+		\limits_{i=1}^n 
+		y_i
+		\langle \widetilde{W}_i, \xi \rangle_\mathcal{H} \\
+		&= %2
+		\frac{1}{n} 
+		\sum \limits_{i=1}^n
+		y_i
+		\biggl(
+		\sum_{j=1}^K
+		\langle \widetilde{X}_{ij}, \xi_j \rangle  
+		+
+	 \mathbf{Z}_i^\top 
+		\boldsymbol{\zeta} 
+		\biggr)
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\\&= %3
+		\frac{1}{n}
+		\sum
+		\limits_{i=1}^n 
+		y_i
+		\biggl( \sum \limits_{k=1}^K \int_0^1 \widetilde{X}_{ij}(t) \, \xi_j(t) \, dt \biggr)
+		+
+		 \frac{1}{n}
+		 \sum
+		 \limits_{i=1}^n
+		 y_i
+		 ( \mathbf{Z}_i^\top \boldsymbol{\zeta} )
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		  \\&=  
+		  \frac{1}{n} \sum \limits_{i=1}^n 
+		  y_i
+		\biggl\{ 
+		  \sum \limits_{k=1}^K \int_0^1
+		   \biggl(
+		   \sum_{m=1}^M \theta_{ijm} b_{m}(t) 
+		   \biggr) 
+		   \biggl(
+		   \sum_{m'=1}^M d_{jm'} b_{m'}(t) 
+		   \biggr) 
+		   dt
+		\biggr\}  
+		  +
+	\frac{1}{n}
+	\mathbf{y}^\top
+	Z \boldsymbol{\zeta} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&=  
+\frac{1}{n} \sum \limits_{i=1}^n 
+y_i
+\biggl\{ 
+\sum \limits_{k=1}^K 
+\sum_{m=1}^M
+\sum_{m'=1}^M  
+\theta_{ijm}
+d_{jm'}
+\int_0^1
+ b_{m}(t) 
+ b_{m'}(t) 
+dt
+\biggr\}  
++
+\frac{1}{n}
+\mathbf{y}^\top
+Z \boldsymbol{\zeta} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&=  
+\sum \limits_{k=1}^K 
+\biggl\{
+\frac{1}{n} \sum \limits_{i=1}^n 
+y_i
+(
+\boldsymbol{\theta}_{ij}^\top
+B
+\mathbf{d}_j
+)  
+\biggr\}
++
+\frac{1}{n}
+\mathbf{y}^\top
+Z \boldsymbol{\zeta}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&=  
+\frac{1}{n}
+\biggl(
+\sum \limits_{k=1}^K 
+\mathbf{y}^\top
+\Theta_{j}
+B
+\mathbf{d}_j
++
+\mathbf{y}^\top
+Z \boldsymbol{\zeta} 
+\biggr).
+	\end{align*}	
+		\jongmin{
+		Another way of computing \eqref{def:eigenproblem_smoothed}, rather than solving an eigenproblem, is as follows.
+As shown in the proof in Appendix \ref{section:proof:eigenproblem_derivation}, the empirical covariance is simplified as:
+		\begin{align*}
+			\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \xi \rangle_\mathcal{H} Y_i \\
+			&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}).
+			\\&=
+			\frac{1}{n}\tilde{\mathbf{y}}^\top
+			\begin{bmatrix} \widetilde{C}J \; \mathbf{Z} \end{bmatrix} \;      \underbrace{
+				\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
+			}_{:= \boldsymbol{\beta}}.
+		\end{align*}
+		Let us 
+		denote $\mathbf{b} =  \widetilde{\mathbf{y}}^\top \begin{bmatrix} \widetilde{C}J \; \mathbf{Z} \end{bmatrix}$.
+This is the weighted row sum of $\begin{bmatrix} \widetilde{C}J \; \mathbf{Z} \end{bmatrix}$, weighted by $\widetilde{\mathbf{y}}$.
+		Then using the symmetricity of $J^\ast$, we solve a linear system $J^\ast \mathbf{d} =
+		\mathbf{b}^\top$ to obtain $\mathbf{d}$. Then we have
+		\begin{align*}
+			\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
+			\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y ) 
+			%%%%%%%%%%%%%%%%%%%%%
+			&= 
+			%%%%%%%%%%%%%%%%%%%%%%%%
+			\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
+			\frac{1}{n} \mathbf{d}^\top J^\ast  \boldsymbol{\beta}
+			\\& \overset{(i)}{\leq} 
+			\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
+			\frac{1}{n} \sqrt{\mathbf{d}^\top J^\ast  \mathbf{d}}
+			\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}}
+			\\& \overset{(ii)}{=}
+			\frac{1}{n} \sqrt{\mathbf{d}^\top J^\ast  \mathbf{d}}    ,
+		\end{align*}
+		where step $(i)$ uses the Cauchy-Schwarz inequality with the inner product $\langle x, y \rangle_{J^\ast} = x^\top J^\ast y$,
+		and step $(ii)$ uses the norm constraint.
+		By the Cauchy-Schwarz inequality, the maximum displayed in the last term is obtained by a unit vector (with respect to $\langle \cdot, \cdot \rangle_{J^\ast}$) parallel to $\mathbf{d}$.
+Therefore we have
+		\begin{equation*}
+			\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
+			= \frac{1}{\sqrt{\mathbf{d}^\top  J^\ast \mathbf{d} }}\mathbf{d},
+		\end{equation*}
+		which only involves solving one linear equation.
+	}
+
+\subsection{Proof of Lemma}
+		We verify that the function
+		\[
+		\langle \mathbf{u}, \mathbf{v} \rangle_{\mathcal{H}} := \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega},
+		\]
+		defines a valid inner product on $\mathcal{H} := \mathbb{R}^{KM} \times \mathbb{R}^p$, where $\mathbf{u} = (\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})$ and $\mathbf{v} = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$.
+
+		\textit{Linearity in the first argument}: For any $a, b \in \mathbb{R}$ and $\mathbf{u}_1, \mathbf{u}_2, \mathbf{v} \in \mathcal{H}$,
+		\[
+		\langle a \mathbf{u}_1 + b \mathbf{u}_2, \mathbf{v} \rangle_{\mathcal{H}} 
+		= a \langle \mathbf{u}_1, \mathbf{v} \rangle_{\mathcal{H}} + b \langle \mathbf{u}_2, \mathbf{v} \rangle_{\mathcal{H}}.
+		\]
+
+		\textit{Symmetry}: Since $B$ is symmetric and the standard inner product is symmetric,
+		\[
+		\langle \mathbf{u}, \mathbf{v} \rangle_{\mathcal{H}} 
+		= \langle \mathbf{v}, \mathbf{u} \rangle_{\mathcal{H}}.
+		\]
+
+		\textit{Positive definiteness}: If $\mathbf{u} \ne 0$, then either some $\mathbf{d}_j \ne 0$ or $\boldsymbol{\zeta} \ne 0$. Since $B$ is positive definite,
+		\[
+		\langle \mathbf{u}, \mathbf{u} \rangle_{\mathcal{H}} = \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{d}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta} > 0.
+		\]
+		Thus, $\langle \cdot, \cdot \rangle_{\mathcal{H}}$ is a valid inner product.
+
+		Now let
+		\[
+		\mathbf{g} := \left( \tfrac{1}{n} \Theta_1^\top \mathbf{y}, \ldots, \tfrac{1}{n} \Theta_K^\top \mathbf{y}, \tfrac{1}{n} Z^\top \mathbf{y} \right).
+		\]
+		Then, for any $\mathbf{u} = (\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta}) \in \mathcal{H}$,
+		\[
+		\left\langle \mathbf{u}, \mathbf{g} \right\rangle_{\mathcal{H}} 
+		= \frac{1}{n} \sum_{j=1}^K \mathbf{d}_j^\top B \Theta_j^\top \mathbf{y} + \frac{1}{n} \boldsymbol{\zeta}^\top Z^\top \mathbf{y}
+		= \frac{1}{n} \left( \sum_{j=1}^K \mathbf{y}^\top \Theta_j B \mathbf{d}_j + \mathbf{y}^\top Z \boldsymbol{\zeta} \right),
+		\]
+		as claimed.
+
+	\subsection{Proof of Propositions \ref{Proposition: generalized rayleigh quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
+	%
+	%
+	\begin{align*}
+		\widehat{\textnormal{Cov}} (
+		\langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y 
 		) 
@@
 		y_i
-		\langle \widetilde{\mathbf{W}}_i, \boldsymbol{\xi} \rangle_\mathcal{H} \\
+		\langle \widetilde{\mathbf{W}}_i, \xi \rangle_\mathcal{H} \\
 		&= 
@@
 		\\
-		&=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
-		&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \left\{ \int_{\mathcal{T}_k} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}).
-	\end{align*}	
-	\subsection{Proof of Propositions \ref{Proposition: generalized rayleigh quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
-	%
-	%
-	\begin{align*}
-		\widehat{\textnormal{Cov}} (
-		\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y 
-		) 
-		&= 
-		\frac{1}{n} \sum \limits_{i=1}^n 
-		y_i
-		\langle \widetilde{\mathbf{W}}_i, \boldsymbol{\xi} \rangle_\mathcal{H} \\
-		&= 
-		\frac{1}{n} 
-		\sum \limits_{i=1}^n
-		y_i
-		\langle \widetilde{X_i}, \psi \rangle_\mathcal{F}  
-		+  
-		\frac{1}{n} 
-		\sum \limits_{i=1}^n  
-		y_i
-		\langle \mathbf{Z}_i, 
-		\boldsymbol{\theta} 
-		\rangle 
-		\\
-		&=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
-		&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \left\{ \int_{\mathcal{T}_k} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
+		&=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_0^1 X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
+		&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_0^1 \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
+		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \left\{ \int_0^1 \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
 		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
@@
 
-	Here, $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y)$ is expressed as $\boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*$ based on the aforementioned basis approximations.
-Thus, finding $\boldsymbol{\xi}^*$ that maximizes $\boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*$ amounts to finding $\widehat{\boldsymbol{\xi}}$ that maximizes the sample squared covariance $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y)$, which is the first step of the PLS algorithm.
-The constraint $\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1$ scales the obtained PLS component to have a unit norm, that is, $\langle \widehat{\boldsymbol{\xi}}, \widehat{\boldsymbol{\xi}} \rangle_\mathcal{H}=1$.
-
-	and  $\boldsymbol{\xi}^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$.
-Then, the $l$-th PLS component, $\widehat{\boldsymbol{\xi}} \equiv \widehat{\boldsymbol{\xi}}_l$ can be obtained by solving
+	Here, $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y)$ is expressed as $\xi^{*\top} \mathbf{V}^\ast \xi^*$ based on the aforementioned basis approximations.
+Thus, finding $\xi^*$ that maximizes $\xi^{*\top} \mathbf{V}^\ast \xi^*$ amounts to finding $\widehat{\xi}$ that maximizes the sample squared covariance $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y)$, which is the first step of the PLS algorithm.
+The constraint $\xi^{*\top} J^\ast \xi^*=1$ scales the obtained PLS component to have a unit norm, that is, $\langle \widehat{\xi}, \widehat{\xi} \rangle_\mathcal{H}=1$.
+
+	and  $\xi^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$. Then, the $l$-th PLS component, $\widehat{\xi} \equiv \widehat{\xi}_l$ can be obtained by solving
 	\begin{equation}\label{def:eigenproblem_smoothed}
-		\argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*}, \quad \textit{or equivalently}, \quad \argmax \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1,
-	\end{equation}
-	with respect to $\widehat{\boldsymbol{\xi}}^*=(\widehat{\mathbf{a}}^{\top}, \widehat{\boldsymbol{\theta}}^{\top})^\top$
+		\argmax \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top} J^\ast \xi^*}, \quad \textit{or equivalently}, \quad \argmax \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} J^\ast \xi^*=1,
+	\end{equation}
+	with respect to $\widehat{\xi}^*=(\widehat{\mathbf{a}}^{\top}, \widehat{\boldsymbol{\theta}}^{\top})^\top$
 
@@
 	\begin{align*}
-		\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \boldsymbol{\xi} \rangle_\mathcal{H} Y_i \\
+		\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \xi \rangle_\mathcal{H} Y_i \\
 		&=  \frac{1}{n} \sum \limits_{i=1}^n  \langle X_i, \psi \rangle_\mathcal{F} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n  \langle \mathbf{Z}_i, \boldsymbol{\theta} \rangle Y_i \\
-		&=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
-		&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \left\{ \int_{\mathcal{T}_k} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
+		&=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_0^1 X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
+		&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_0^1 \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
+		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \left\{ \int_0^1 \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
 		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
@@
 	\begin{align*}
-		\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) &= n^{-2} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}) (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta})^\top \widetilde{\mathbf{y}} \\
+		\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y ) &= n^{-2} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}) (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta})^\top \widetilde{\mathbf{y}} \\
 		&= n^{-2} \{\mathbf{a}^\top J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J \mathbf{a} +  \mathbf{a}^\top J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} +  \boldsymbol{\theta} \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J \mathbf{a} + \boldsymbol{\theta}^\top \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta}\} \\
@@
 		\end{bmatrix} \\
-		&\equiv \boldsymbol{\xi}^{*T} \mathbf{V}^\ast \boldsymbol{\xi}^*.
+		&\equiv \xi^{*T} \mathbf{V}^\ast \xi^*.
 	\end{align*}
@@
 	\begin{align*}
-		\langle \boldsymbol{\xi}, \boldsymbol{\xi} \rangle_{\mathcal{H}} &= \sum \limits_{k=1}^K \int_{\mathcal{T}} \psi^{(k)}(t_k) \psi^{(k)}(t_k) dt_k + \boldsymbol{\theta}^{\top} \boldsymbol{\theta} \\
+		\langle \xi, \xi \rangle_{\mathcal{H}} &= \sum \limits_{k=1}^K \int_{\mathcal{T}} \psi^{(k)}(t_k) \psi^{(k)}(t_k) dt_k + \boldsymbol{\theta}^{\top} \boldsymbol{\theta} \\
 		&= \sum \limits_{k=1}^K  \int_\mathcal{T} \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top   \mathbf{a}^{(k)} dt_k + \boldsymbol{\theta}^{\top} \boldsymbol{\theta} \\
@@
 		&= \mathbf{a}^\top J \mathbf{a} + \boldsymbol{\theta}^{\top} \boldsymbol{\theta} \\
-		&= \boldsymbol{\xi}^{*\top} J^\ast  \boldsymbol{\xi}^{*} \\ 
+		&= \xi^{*\top} J^\ast  \xi^{*} \\ 
 		&= 1 \\
@@
 	\begin{equation*}
-		\max \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \;  \boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^* \quad \textnormal{subject to}  \quad \boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1,
+		\max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} J^\ast \xi^*=1,
 	\end{equation*}
@@
 	\begin{equation*}
-		\max \limits_{\boldsymbol{\xi}^* \in \mathbb{R}^{MK+p}} \; \frac{\boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*},
+		\max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top} J^\ast \xi^*},
 	\end{equation*}
 	where $J^\ast = \mathrm{blkdiag}[J, \mathbf{I}_p] \in \mathbb{R}^{MK+p}$.
-In other words, the PLS component is chosen to maximize the squared sample covariance  $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) = \boldsymbol{\xi}^{*\top} \mathbf{V}^\ast \boldsymbol{\xi}^*$ subject to the constraint $\boldsymbol{\xi}^{*\top} J^\ast \boldsymbol{\xi}^*=1$.
-
-	\jongmin{
-		Another way of computing \eqref{def:eigenproblem_smoothed}, rather than solving an eigenproblem, is as follows.
-As shown in the proof in Appendix \ref{section:proof:eigenproblem_derivation}, the empirical covariance is simplified as:
-		\begin{align*}
-			\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \boldsymbol{\xi} \rangle_\mathcal{H} Y_i \\
-			&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}).
-			\\&=
-			\frac{1}{n}\tilde{\mathbf{y}}^\top
-			\begin{bmatrix} \widetilde{C}J \; \mathbf{Z} \end{bmatrix} \;      \underbrace{
-				\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
-			}_{:= \boldsymbol{\beta}}.
-		\end{align*}
-		Let us 
-		denote $\mathbf{b} =  \widetilde{\mathbf{y}}^\top \begin{bmatrix} \widetilde{C}J \; \mathbf{Z} \end{bmatrix}$.
-This is the weighted row sum of $\begin{bmatrix} \widetilde{C}J \; \mathbf{Z} \end{bmatrix}$, weighted by $\widetilde{\mathbf{y}}$.
-		Then using the symmetricity of $J^\ast$, we solve a linear system $J^\ast \mathbf{d} =
-		\mathbf{b}^\top$ to obtain $\mathbf{d}$. Then we have
-		\begin{align*}
-			\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
-			\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y ) 
-			%%%%%%%%%%%%%%%%%%%%%
-			&= 
-			%%%%%%%%%%%%%%%%%%%%%%%%
-			\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
-			\frac{1}{n} \mathbf{d}^\top J^\ast  \boldsymbol{\beta}
-			\\& \overset{(i)}{\leq} 
-			\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
-			\frac{1}{n} \sqrt{\mathbf{d}^\top J^\ast  \mathbf{d}}
-			\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}}
-			\\& \overset{(ii)}{=}
-			\frac{1}{n} \sqrt{\mathbf{d}^\top J^\ast  \mathbf{d}}    ,
-		\end{align*}
-		where step $(i)$ uses the Cauchy-Schwarz inequality with the inner product $\langle x, y \rangle_{J^\ast} = x^\top J^\ast y$,
-		and step $(ii)$ uses the norm constraint.
-		By the Cauchy-Schwarz inequality, the maximum displayed in the last term is obtained by a unit vector (with respect to $\langle \cdot, \cdot \rangle_{J^\ast}$) parallel to $\mathbf{d}$.
-Therefore we have
-		\begin{equation*}
-			\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
-			= \frac{1}{\sqrt{\mathbf{d}^\top  J^\ast \mathbf{d} }}\mathbf{d},
-		\end{equation*}
-		which only involves solving one linear equation.
-	}
-
-	% Similar in spirit to the regularized principal component analysis (see equation [9.1] of \citealp{Ramsay2005}), one way to penalize the squared sample covariance $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )$ is to divide it by $\{ 1+ \kappa \textnormal{PEN}(\psi) \}$, where $\textnormal{PEN}(\psi)$ is a roughness penalty term.
+In other words, the PLS component is chosen to maximize the squared sample covariance  $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y ) = \xi^{*\top} \mathbf{V}^\ast \xi^*$ subject to the constraint $\xi^{*\top} J^\ast \xi^*=1$.
+
+	% Similar in spirit to the regularized principal component analysis (see equation [9.1] of \citealp{Ramsay2005}), one way to penalize the squared sample covariance $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y )$ is to divide it by $\{ 1+ \kappa \textnormal{PEN}(\psi) \}$, where $\textnormal{PEN}(\psi)$ is a roughness penalty term.
 This leads to the penalized squared sample covariance
 	% \begin{equation*}
-		%         \frac{\boldsymbol{\xi}^{*T} \mathbf{V}^\ast \boldsymbol{\xi}^*}{\boldsymbol{\xi}^{*T} J^\ast \boldsymbol{\xi}^* + \kappa \textnormal{PEN}(\psi)},
+		%         \frac{\xi^{*T} \mathbf{V}^\ast \xi^*}{\xi^{*T} J^\ast \xi^* + \kappa \textnormal{PEN}(\psi)},
 		% \end{equation*}
-	% whose maximizer corresponds to a smoothed PLS component that maximizes $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)$ over the class of all functions satisfying sufficient smoothness conditions.
+	% whose maximizer corresponds to a smoothed PLS component that maximizes $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)$ over the class of all functions satisfying sufficient smoothness conditions.
 
@@
 We will first show that $\mathcal{I}$ is a family of uniformly bounded functions with respect to arguments on $\mathcal{T}$.
-Let $\mu(\mathcal{T}_k)$ denote a Lebesgue measure of $\mathcal{T}_k$, and let $T = \max_{k=1, \ldots, K} \, \mu(\mathcal{T}_k)$.
+Let $\mu([0,1])$ denote a Lebesgue measure of $[0,1]$, and let $T = \max_{k=1, \ldots, K} \, \mu([0,1])$.
 Then for any $g \in \mathcal{I}$ and $\mathbf{t} \in \mathcal{T}$,
@@
 		&\le \left( \langle \sigma_{YX}, \sigma_{YX} \rangle_\mathcal{F}^{1/2} \langle f, f \rangle_\mathcal{F}^{1/2} + \langle \sigma_{YZ}, \sigma_{YZ} \rangle^{1/2} \langle \mathbf{v}, \mathbf{v} \rangle^{1/2} \right)^2 \Vert [\sigma_{YX}^\top(\mathbf{t}), \sigma_{YZ}^\top]^\top \Vert^2 \quad (\because \textnormal{CSI})\\
-		&= \left[ \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \sigma_{YX}^{(k)2}(t_k) dt_k \right\}^{\frac{1}{2}} \Vert f \Vert_\mathcal{F} + \left(\sum \limits_{r=1}^p \sigma_{YZ, r}^2 \right)^{\frac{1}{2}} \Vert \mathbf{v} \Vert \right]^2 \left(\sum \limits_{k=1}^K \sigma_{YX}^{(k)2}(t_k) + \sum \limits_{r=1}^p \sigma^2_{YZ,r} \right) \\
-		& \le \left\{ \left(\sum \limits_{k=1}^K \int_{\mathcal{T}_k} Q_1 dt_k \right)^{\frac{1}{2}} B^{\frac{1}{2}} + \left(\sum \limits_{r=1}^p Q_2 \right)^{\frac{1}{2}} B^{\frac{1}{2}} \right\}^2 \left( \sum \limits_{k=1}^K Q_1 + \sum \limits_{r=1}^p Q_2 \right) \\
+		&= \left[ \left\{ \sum \limits_{k=1}^K \int_0^1 \sigma_{YX}^{(k)2}(t_k) dt_k \right\}^{\frac{1}{2}} \Vert f \Vert_\mathcal{F} + \left(\sum \limits_{r=1}^p \sigma_{YZ, r}^2 \right)^{\frac{1}{2}} \Vert \mathbf{v} \Vert \right]^2 \left(\sum \limits_{k=1}^K \sigma_{YX}^{(k)2}(t_k) + \sum \limits_{r=1}^p \sigma^2_{YZ,r} \right) \\
+		& \le \left\{ \left(\sum \limits_{k=1}^K \int_0^1 Q_1 dt_k \right)^{\frac{1}{2}} B^{\frac{1}{2}} + \left(\sum \limits_{r=1}^p Q_2 \right)^{\frac{1}{2}} B^{\frac{1}{2}} \right\}^2 \left( \sum \limits_{k=1}^K Q_1 + \sum \limits_{r=1}^p Q_2 \right) \\
 		&= B \left\{(KTQ_1)^{\frac{1}{2}} + (PQ_2)^\frac{1}{2} \right\}^2 (KQ_1 +pQ_2) < \infty.
@@
 		\right\Vert^2 \\
-		&= \left[ \left\{ \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \sigma_{YX}^{(k)2}(t_k) dt_k \right\}^{\frac{1}{2}} \Vert f \Vert_\mathcal{F} + \left(\sum \limits_{r=1}^p \sigma_{YZ, r}^2 \right)^{\frac{1}{2}} \Vert \mathbf{v} \Vert \right]^2 \sum \limits_{k=1}^K  \left\{\sigma_{YX}^{(k)}(t_k) -\sigma_{YX}^{(k)}(t_k^*) \right\}^2 \\
+		&= \left[ \left\{ \sum \limits_{k=1}^K \int_0^1 \sigma_{YX}^{(k)2}(t_k) dt_k \right\}^{\frac{1}{2}} \Vert f \Vert_\mathcal{F} + \left(\sum \limits_{r=1}^p \sigma_{YZ, r}^2 \right)^{\frac{1}{2}} \Vert \mathbf{v} \Vert \right]^2 \sum \limits_{k=1}^K  \left\{\sigma_{YX}^{(k)}(t_k) -\sigma_{YX}^{(k)}(t_k^*) \right\}^2 \\
 		&\le B \left\{(KTQ_1)^{\frac{1}{2}} + (PQ_2)^\frac{1}{2} \right\} K\tilde{\epsilon}^2 = \epsilon^2.
@@
 	\begin{align*}
-		\langle \langle \hat{\boldsymbol{\xi}}_l,  \hat{\boldsymbol{\xi}}_l \rangle \rangle &= \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}  \\
-		&= \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_{\mathcal{T}_k} \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
-		&= \sum \limits_{k=1}^K \int_{\mathcal{T}_k} \hat{\mathbf{a}}^{(k) \top}_l \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k) \top}(t_k) \hat{\mathbf{a}}^{(k)}_l  dt_k + \boldsymbol{\theta}_l^\top \boldsymbol{\theta}_l + \sum \limits_{k=1}^K \lambda_k \int_{\mathcal{T}_k} \hat{\mathbf{a}}^{(k) \top}_l \ddot{\mathbf{b}}^{(k)}(t_k) \ddot{\mathbf{b}}^{(k) \top}(t_k) \hat{\mathbf{a}}^{(k)}_l  dt_k \\
+		\langle \langle \hat{\xi}_l,  \hat{\xi}_l \rangle \rangle &= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}  \\
+		&= \sum \limits_{k=1}^K \int_0^1 \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_0^1 \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
+		&= \sum \limits_{k=1}^K \int_0^1 \hat{\mathbf{a}}^{(k) \top}_l \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k) \top}(t_k) \hat{\mathbf{a}}^{(k)}_l  dt_k + \boldsymbol{\theta}_l^\top \boldsymbol{\theta}_l + \sum \limits_{k=1}^K \lambda_k \int_0^1 \hat{\mathbf{a}}^{(k) \top}_l \ddot{\mathbf{b}}^{(k)}(t_k) \ddot{\mathbf{b}}^{(k) \top}(t_k) \hat{\mathbf{a}}^{(k)}_l  dt_k \\
 		& = \sum \limits_{k=1}^K \hat{\mathbf{a}}_l^{(k) \top} J^{(k)} \hat{\mathbf{a}}_l^{(k)} + \boldsymbol{\theta}_l^\top \boldsymbol{\theta}_l +  \sum \limits_{k=1}^K \lambda_k \hat{\mathbf{a}}^{(k) \top}_l \ddot{J}^{(k)} \hat{\mathbf{a}}^{(k)}_l \\
-		& = \hat{\boldsymbol{\xi}}_l^{*\top} J^\ast \hat{\boldsymbol{\xi}}_l^* + \hat{\boldsymbol{\xi}}_l^{*\top} \Lambda \ddot{J}^\ast \hat{\boldsymbol{\xi}}_l^* = \hat{\boldsymbol{\xi}}_l^{*\top} (J^\ast +\Lambda \ddot{J}^\ast) \hat{\boldsymbol{\xi}}_l^* = 1
+		& = \hat{\xi}_l^{*\top} J^\ast \hat{\xi}_l^* + \hat{\xi}_l^{*\top} \Lambda \ddot{J}^\ast \hat{\xi}_l^* = \hat{\xi}_l^{*\top} (J^\ast +\Lambda \ddot{J}^\ast) \hat{\xi}_l^* = 1
 	\end{align*}
@@
 	\begin{align*}
-		\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_j[\mathbf{t}] d\mathbf{t} &= \int_{\mathcal{T}} P   \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right)\widetilde{W}^{[j]}[\mathbf{t}]  \widehat{\boldsymbol{\xi}}_k[\mathbf{t}] d\mathbf{t}  \\
-		&= P \left\{\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_j[\mathbf{t}] d\mathbf{t} - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_j[\mathbf{t}] d\mathbf{t} \right\} \\
+		\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} &= \int_{\mathcal{T}} P   \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right)\widetilde{W}^{[j]}[\mathbf{t}]  \widehat{\xi}_k[\mathbf{t}] d\mathbf{t}  \\
+		&= P \left\{\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} \right\} \\
 		&=P \left( \widehat{\boldsymbol{\rho}}_j - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \widehat{\boldsymbol{\rho}}_j \right) \\
@@
 	\end{align*}
-	noting that $\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_j[\mathbf{t}] d\mathbf{t} = \widehat{\boldsymbol{\rho}}_j$.
+	noting that $\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} = \widehat{\boldsymbol{\rho}}_j$.
 Now by the generalized eigenvalue problem (i.e., generalized Rayleigh quotient problem) presented in Proposition 2, we have that for $j < l$,
 	\begin{align*}
-		\langle \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle \rangle &= \widehat{\boldsymbol{\xi}}_l^{*\top} (J^\ast + \Lambda \ddot{J}^\ast)\widehat{\boldsymbol{\xi}}_j^{*} \\
-		& = \frac{1}{\kappa_l} (V^\ast_l \widehat{\boldsymbol{\xi}}_l^{*})^\top \widehat{\boldsymbol{\xi}}_j^{*} \\
-		&=  \frac{1}{\kappa_l}\widehat{\boldsymbol{\xi}}_l^{* \top} V^\ast_l \widehat{\boldsymbol{\xi}}_j^{*} \\
-		&= \frac{1}{\kappa_l}\widehat{\boldsymbol{\xi}}_l^{* \top} \left(n^{-2} J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top} \widetilde{C}^{*[l]} J^\ast \right) \widehat{\boldsymbol{\xi}}_j^{*} \\
-		&= \frac{1}{n^2\kappa_l}\widehat{\boldsymbol{\xi}}_l^{* \top} \ J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top}  \widetilde{C}^{*[l]}\left(\int_{\mathcal{T}} B^*[\mathbf{t}] B^*[\mathbf{t}]^\top d\mathbf{t}  \right) \widehat{\boldsymbol{\xi}}_j^{*} \\
-		&= \frac{1}{n^2\kappa_l}\widehat{\boldsymbol{\xi}}_l^{* \top}  J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top}  \left(\int_{\mathcal{T}} \widetilde{C}^{*[l]} B^*[\mathbf{t}] B^*[\mathbf{t}]^\top \widehat{\boldsymbol{\xi}}_j^{*} d\mathbf{t}  \right)   \\
-		&= \frac{1}{n^2\kappa_l}\widehat{\boldsymbol{\xi}}_l^{* \top}  J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top}  \left(\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_j[\mathbf{t}] d\mathbf{t}  \right)   \\
+		\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle &= \widehat{\xi}_l^{*\top} (J^\ast + \Lambda \ddot{J}^\ast)\widehat{\xi}_j^{*} \\
+		& = \frac{1}{\kappa_l} (V^\ast_l \widehat{\xi}_l^{*})^\top \widehat{\xi}_j^{*} \\
+		&=  \frac{1}{\kappa_l}\widehat{\xi}_l^{* \top} V^\ast_l \widehat{\xi}_j^{*} \\
+		&= \frac{1}{\kappa_l}\widehat{\xi}_l^{* \top} \left(n^{-2} J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top} \widetilde{C}^{*[l]} J^\ast \right) \widehat{\xi}_j^{*} \\
+		&= \frac{1}{n^2\kappa_l}\widehat{\xi}_l^{* \top} \ J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top}  \widetilde{C}^{*[l]}\left(\int_{\mathcal{T}} B^*[\mathbf{t}] B^*[\mathbf{t}]^\top d\mathbf{t}  \right) \widehat{\xi}_j^{*} \\
+		&= \frac{1}{n^2\kappa_l}\widehat{\xi}_l^{* \top}  J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top}  \left(\int_{\mathcal{T}} \widetilde{C}^{*[l]} B^*[\mathbf{t}] B^*[\mathbf{t}]^\top \widehat{\xi}_j^{*} d\mathbf{t}  \right)   \\
+		&= \frac{1}{n^2\kappa_l}\widehat{\xi}_l^{* \top}  J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top}  \left(\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t}  \right)   \\
 		&=0, 
 	\end{align*}
-	where the last equality follows from the above result that $\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_j[\mathbf{t}] d\mathbf{t} = \mathbf{0}$.
+	where the last equality follows from the above result that $\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} = \mathbf{0}$.
 
@@
 
-	First note that $\widehat{\boldsymbol{\rho}}_l = \int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\boldsymbol{\xi}}_l[\mathbf{t}] d\mathbf{t}= \widetilde{C}^{*[l]} J^\ast \widehat{\boldsymbol{\xi}}^*_{l}$ for $l=1, \ldots, L$.
+	First note that $\widehat{\boldsymbol{\rho}}_l = \int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\xi}_l[\mathbf{t}] d\mathbf{t}= \widetilde{C}^{*[l]} J^\ast \widehat{\xi}^*_{l}$ for $l=1, \ldots, L$.
 Then, as above, we first express the $l$-th residualized hybrid predictor in terms of its previous $(l-1)$-th version:
@@
 			& =\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] -  \frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} B^*[\mathbf{t}]}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}}  \\
-			& =\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] -  \frac{\widetilde{C}^{*[l-1]} J^\ast \widehat{\boldsymbol{\xi}}^{*}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} B^*[\mathbf{t}]}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}},
+			& =\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] -  \frac{\widetilde{C}^{*[l-1]} J^\ast \widehat{\xi}^{*}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} B^*[\mathbf{t}]}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}},
 		\end{aligned}
@@
 		\begin{aligned}
-			\widetilde{C}^{*[l]} &= \widetilde{C}^{*[l-1]} -  \frac{\widetilde{C}^{*[l-1]} J^\ast \widehat{\boldsymbol{\xi}}^{*}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]}}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \\
-			&= \widetilde{C}^{*[l-1]} \left(I_{MK+p} - \frac{J^\ast \widehat{\boldsymbol{\xi}}^{*}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]}}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \\
-			&= \widetilde{C}^{*[j]} \left(I_{MK+p} - \frac{J^\ast \widehat{\boldsymbol{\xi}}^{*}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P},
+			\widetilde{C}^{*[l]} &= \widetilde{C}^{*[l-1]} -  \frac{\widetilde{C}^{*[l-1]} J^\ast \widehat{\xi}^{*}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]}}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \\
+			&= \widetilde{C}^{*[l-1]} \left(I_{MK+p} - \frac{J^\ast \widehat{\xi}^{*}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]}}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \\
+			&= \widetilde{C}^{*[j]} \left(I_{MK+p} - \frac{J^\ast \widehat{\xi}^{*}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P},
 		\end{aligned}
@@
 	\begin{equation*}
-		\widetilde{P} = \prod \limits_{h=j+1}^{l-1} \left(I_{MK+p} - \frac{J^\ast \hat{\boldsymbol{\xi}}^*_h \widehat{\boldsymbol{\rho}}_{h}^\top \widetilde{C}^{*[h]}}{\widehat{\boldsymbol{\rho}}_{h}^\top \widehat{\boldsymbol{\rho}}_{h}} \right)
+		\widetilde{P} = \prod \limits_{h=j+1}^{l-1} \left(I_{MK+p} - \frac{J^\ast \hat{\xi}^*_h \widehat{\boldsymbol{\rho}}_{h}^\top \widetilde{C}^{*[h]}}{\widehat{\boldsymbol{\rho}}_{h}^\top \widehat{\boldsymbol{\rho}}_{h}} \right)
 	\end{equation*}
@@
 		\begin{aligned}
-			\widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[l]} &=  \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} \left(I_{MK+p} - \frac{J^\ast \widehat{\boldsymbol{\xi}}^{*}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P} \\
-			&=\left( \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} - \frac{ \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} J^\ast \widehat{\boldsymbol{\xi}}^{*}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P} \\
+			\widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[l]} &=  \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} \left(I_{MK+p} - \frac{J^\ast \widehat{\xi}^{*}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P} \\
+			&=\left( \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} - \frac{ \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} J^\ast \widehat{\xi}^{*}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P} \\
 			&=\left( \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} - \frac{ \widehat{\boldsymbol{\rho}}_j^\top \widehat{\boldsymbol{\rho}}_j  \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P} \\

### 2025-07-10 manuscript/main.tex
maximizer now has hat

@@
 		\hat{\xi}_j(t) := 
-		\sum_{m=1}^M d_{jm} \, b_m(t), \quad j = 1, \ldots, K.
-	\end{equation*}
-
-	Let $\mathbf{d}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$ and $\mathbf{y} := (y_1, \ldots, y_n)^\top$. 
+		\sum_{m=1}^M \hat{d}_{jm} \, b_m(t), \quad j = 1, \ldots, K.
+	\end{equation*}
+
+	Let $\hat{\mathbf{d}}_j := (\hat{d}_{j1}, \ldots, \hat{d}_{jM})^\top \in \mathbb{R}^M$ and $\mathbf{y} := (y_1, \ldots, y_n)^\top$. 
 	Let $B \in \mathbb{R}^{M \times M}$ denote the Gram matrix of the basis functions, with entries
@@
 	\]
-	We compute $\mathbf{d}_1, \ldots, \mathbf{d}_K$ and $\hat{\boldsymbol{\zeta}}$ as follows.
-	First, we obtain the unnormalized coefficient vectors. For each $j$, the unnormalized vector $\bar{\mathbf{d}}_j$ is computed by solving
-	\begin{equation*}
-		B \bar{\mathbf{d}}_j = (\Theta_j B)^\top \mathbf{y},
+	We compute $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$ as follows.
+	First, we obtain the unnormalized coefficient vectors. For each $j$, the unnormalized vector $\hat{\mathbf{d}}_j'$ is computed by solving a linear equation:
+	\begin{equation*}
+		B \hat{\mathbf{d}}_j' = (\Theta_j B)^\top \mathbf{y},
 	\end{equation*}
@@
 	\begin{equation}
-		\bar{\boldsymbol{\zeta}} := Z^\top \mathbf{y}.
+		\hat{ \boldsymbol{\zeta} }' := Z^\top \mathbf{y}.
 	\end{equation}
@@
 	\begin{equation}\label{def:computed_PLS_direction}
-		\mathbf{d}_j := 
+		\hat{ \mathbf{d}}_j := 
 		\frac{1}{
 			\left(
-			\sum_{j=1}^K \bar{\mathbf{d}}_j^\top B \bar{\mathbf{d}}_j +
-			\bar{\boldsymbol{\zeta}}^\top \bar{\boldsymbol{\zeta}}
+			\sum_{j=1}^K \hat{\mathbf{d}}_j'^\top B \hat{\mathbf{d}}_j' +
+		(\hat{ \boldsymbol{\zeta} }')^\top \hat{ \boldsymbol{\zeta} }'
 			\right)^{1/2}
-		} \bar{\mathbf{d}}_j, \quad j = 1, \ldots, K,
+		} \hat{\mathbf{d}}_j', \quad j = 1, \ldots, K,
 	\end{equation}
@@
 			\left(
-			\sum_{j=1}^K \bar{\mathbf{d}}_j^\top B \bar{\mathbf{d}}_j +
-			\bar{\boldsymbol{\zeta}}^\top \bar{\boldsymbol{\zeta}}
+			\sum_{j=1}^K \hat{\mathbf{d}}_j'^\top B \hat{\mathbf{d}}_j' +
+		(\hat{ \boldsymbol{\zeta} }')^\top \hat{ \boldsymbol{\zeta} }'
 			\right)^{1/2}
-		} \bar{\boldsymbol{\zeta}}.
+		} 	\hat{ \boldsymbol{\zeta} }'.
 	\end{equation}
@@
 	\end{align*}
+
+The squared hybrid Hilbert norm $\langle {\xi},{\xi} \rangle_{\mathcal{H}}$ 
+is computed as follows:
+\begin{align*}
+\langle {\xi},{\xi} \rangle_{\mathcal{H}}
+&=
+\sum_{j=1}^K
+\langle
+\xi_j, \xi_j
+\rangle
++
+\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&=
+\sum \limits_{k=1}^K \int_0^1
+\biggl(
+\sum_{m=1}^M d_{jm'} b_{m}(t) 
+\biggr) 
+\biggl(
+\sum_{m'=1}^M d_{jm'} b_{m'}(t) 
+\biggr) 
+dt
++
+\boldsymbol{\zeta}^\top \boldsymbol{\zeta}  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&=
+aaaaa
+\end{align*}
+admits the following matrix representation:
+	\[
+	\langle \boldsymbol{\xi}, \boldsymbol{\xi} \rangle_{\mathcal{H}} = \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{d}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta}.
+	\]
+
+	By the definition of the inner product on $\mathcal{H} = \mathbb{R}^{KM} \times \mathbb{R}^p$, we have
+	\[
+	\langle \boldsymbol{\xi}, \boldsymbol{\xi} \rangle_{\mathcal{H}} = \sum_{j=1}^K \langle \xi_j, \xi_j \rangle_{L^2([0,1])} + \|\boldsymbol{\zeta}\|^2.
+	\]
+	Since $\xi_j(t) = \sum_{m=1}^M d_{jm} b_m(t)$, it follows that
+	\[
+	\langle \xi_j, \xi_j \rangle_{L^2([0,1])} 
+	= \int_0^1 \left( \sum_{m=1}^M d_{jm} b_m(t) \right)^2 dt 
+	= \mathbf{d}_j^\top B \mathbf{d}_j,
+	\]
+	where $B$ is the Gram matrix of the basis. Substituting this into the definition yields
+	\[
+	\langle \boldsymbol{\xi}, \boldsymbol{\xi} \rangle_{\mathcal{H}} = \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{d}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta}.
+	\]
+
 		\jongmin{

### 2025-07-10 manuscript/main.tex
intro draft

@@
 \documentclass[12pt]{article}
-\usepackage[utf8]{inputenc}
-\usepackage[comma,authoryear]{natbib} 
-\usepackage[margin=1in]{geometry}
-
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{enumerate}
+\usepackage{natbib}
+\usepackage{url} % not crucial - just used below for the URL 
+\usepackage{bibunits}
 \usepackage{subcaption}
@@
 
+%%%%
+
+\usepackage{graphicx}
+\usepackage{multirow}
+\usepackage{hhline}
+%\usepackage{enumitem}
+\usepackage{hyperref}
+\usepackage{bm}
+\usepackage{multirow,multicol}
+\usepackage{verbatim}
+\usepackage{amsfonts,amssymb,amsthm,color,authblk}
+\usepackage{xcolor}
+\definecolor{myblue}{RGB}{0, 0, 0}
+\newcommand{\blue}[1]{{\color{myblue}#1}}
+%%%%
+
+%\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{1}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\newtheorem{condition}{Condition}
+\newtheorem{remark}{Remark}
 \newtheorem{proposition}{Proposition}
-\newtheorem{alg}{Algorithm} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{assumption}{Assumption}
-\newtheorem{note}[theorem]{Note}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{define}[theorem]{Definition}
-% \newtheorem{denote}[theorem]{denote}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{lemma}{Lemma}
-\usepackage{graphicx}
-\graphicspath{ {images/} }
-\usepackage{amsmath}
-\usepackage{mathtools}
-\usepackage[flushleft]{threeparttable}
-\usepackage[labelfont=bf]{caption}
-\usepackage{caption,booktabs,array}
-\usepackage{multirow}
-\usepackage{makecell}
-\usepackage[usenames, dvipsnames]{color}
+\newtheorem{definition}{Definition}
+\newtheorem{corollary}{Corollary}
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-1in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.7in}%
+\addtolength{\topmargin}{-1in}%
+
+%\usepackage{etoolbox}
+%\AtBeginBibliography{\small\setlength{\baselineskip}{10pt}}
+%\setlength{\bibsep}{0pt plus 0.2ex} 
 \usepackage{setspace}   
-\usepackage{amssymb}
-\usepackage{bbm}
-\usepackage{rotating}
-\usepackage{url}
-\usepackage{enumerate}
-\allowdisplaybreaks
-\usepackage{bbold}
-\usepackage{xcolor}         % colors
+\usepackage{etoolbox}  
 \usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{hyperref}
-
-\setstretch{1.8} % For 25 lines per page
-
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 
-\title{Partial Least Squares Regression with Multiple Functional and Scalar Predictors}
-\author{Jongmin Mun and Jeong Hoon Jang}
+\usepackage[noend]{algpseudocode}
+\usepackage{hyperref}
+
+\AtBeginEnvironment{thebibliography}{\small\setstretch{0.93}}
+
+\begin{document}
+
+%\bibliographystyle{natbib}
+
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\if1\blind
+{
+  \title{\bf Partial Least Squares Regression with Multiple Functional and Scalar Predictors
+  }
+  \author{Jongmin Mun  $^1$  and Jeong Hoon Jang$^2$
+\medskip\\
+University of Southern California$^1$ and University of Texas Medical Branch$^2$
+\\
+}
 \date{\today}
 
-\begin{document}
   \maketitle
+} \fi
+
+\if0\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf SOFARI: High-Dimensional Manifold-Based Inference}
+\end{center}
+  \medskip
+} \fi
+
+\bigskip
+\begin{abstract}
+abstract.
+\end{abstract}
+
+\noindent%
+{\it Keywords:}  dimension reduction; functional data analysis; multiple data modalities; multivariate data analysis; multivariate functional data; partial least square
+
+\vfill
+
+%\newpage
+\spacingset{1.9} % DON'T change the spacing!
+
+%\begin{bibunit}[agsm]
 
 \section{Introduction} \label{sec: Introduction}
-	Functional regression settings involving a large number of predictors, $X_{i1}(t), X_{i2}(t), \ldots, X_{iK}(t)$, are becoming increasingly common.
-For example, \cite{storeySignificanceAnalysisTime2005} analyzes two gene expression datasets measured over time, which involve only a small number of patients but tens of thousands of functional predictors.
-
-	Infinite dimensional beta estimation problem (ill-posed problem)
-
-	Multicollinearity and high-dimensionality in scalar predictors are not handled.
-
-	Also, there may be high correlation between functional and scalar predictors.
+Functional data analysis (FDA) treats each observed process as a realization of a random function over a continuous domain, such as time or space.
+The smoothness and infinite-dimensional nature of functional data allow researchers to exploit rich structural features, including derivatives and complex covariance patterns.
+This enables regression analysis for predicting clinical outcomes using complex functional predictors collected with advanced recording technologies, such as medical imaging data.
+
+In modern biomedical studies, it is increasingly common to collect heterogeneous data modalities for each subject.
+For instance, the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021} records both multiple renogram curves (functional data) and multiple renogram variables (vector data) per kidney, capturing distinct yet related physiological information.
+Such settings call for statistical methods that can jointly model functional and vector-valued covariates to account for both shared and modality-specific variation linked to clinical outcomes.
+
+%Infinite dimensional beta estimation problem (ill-posed problem)
+%Multicollinearity and high-dimensionality in scalar predictors are not handled.
+%Also, there may be high correlation between functional and scalar predictors.
+Regression with functional and scalar predictors poses several challenges.
+Estimating the infinite-dimensional slope function is an ill-posed problem requiring regularization or dimension reduction.
+Scalar predictors are often high-dimensional and multicollinear, further complicating estimation.
+Moreover, strong correlations between functional and scalar predictors are common but typically overlooked by separate modeling approaches.
+These issues call for a unified framework that addresses ill-posedness, high-dimensionality, and cross-modality correlation jointly.
 
@@
 2. basis approach (power-series, B-splines, wavelets)
-	- Power Series splines (Goldsmith et al., 2011, Journal of Computational Statistics)
-	- B-splines (H. Cardot, F. Ferraty, P. Sarda, Spline estimators for the functional linear model, Statistica Sinica 13 (2003) 571–591.
-	T.T.Cai,P.Hall,Prediction in functional linear regression, Ann.Stat. 34(5) (2006) 2159–2179.)
-	- Wavelet (Y.Zhao,R.T.Ogden,P.T.Reiss,Wavelet-based lasso in functional linear regression, J.Comput.Graph.Stat.21(3)(2012)600–61.)7
-
-	3. FPCA approach
-	- Hall, P. and Horowitz, J. L. (2007), ‘Methodology and convergence rates for functional linear regression’, The Annals of Statistics 35(1), 70–91.
-	- Reiss P. T.,  Ogden R. T.. Functional principal component regression and functional partial least squares, Journal of the American Statistical Association, 2007, vol. 102 (pg. 984-996)
-	- Febrero-Bande et al., 2017
-
-	4. FPLS Approach
-	- Preda and Saporta (2005)
-	- Reiss and Odgen, 2007
-	- Aguilera AM, Escabias M, Preda C, Saporta G. Using basis expansions for estimating functional PLS regression applications withchemometric data.Chemom Intell Lab Syst. 2010;104:289-305.
-	- Delaigle and Hall, 2012
-	- Febrero-Bande et al., 2017
-	- Beyaztas and Shang, (2022) A Robust Functional Partial Least Squares for Scalar-on-Multiple-Function Regression. Journal of Chemometrics.
-	- Saricam et al., On partial least-squares estimation in scalar-on-function regression models. Journal of Chemometrics.
-	- Mutis  et al. (2025) On function-on-function linear quantile regression
+- Power Series splines \citep{goldsmithPenalizedFunctionalRegression2011}
+- B-splines \citep{cardotSplineEstimatorsFunctional2003, caiPredictionFunctionalLinear2006}
+- Wavelet\citep{zhaoWaveletbasedLASSOFunctional2012}
+
+%3. FPCA approach
+One possible approach is to apply principal component analysis, FPCA or MFPCA for the functional predictors and standard PCA for the scalar predictors, followed by classical multivariate regression on the resulting scores.
+This PCA regression strategy has been well-studied for functional predictors alone \citep{hallMethodologyConvergenceRates2007, reissFunctionalPrincipalComponent2007, febrero-bandeFunctionalPrincipalComponent2017}, but it overlooks potentially strong correlations between functional and scalar components, leading to multicollinearity and suboptimal predictive performance.
+Outside the regression context, \citet{jangPrincipalComponentAnalysis2021} proposed a joint PCA method that accounts for correlation between functional and scalar data.
+However, the resulting components are not informed by the response and may fail to capture directions of maximal correlation with the outcome.
+
+%4. FPLS Approach
+Partial least squares (PLS) regression offers a powerful alternative by explicitly seeking low-dimensional projections of the predictors that maximize their covariance with the outcome.
+While PLS has been extensively studied in the context of functional data, both for single and multiple functional predictors \citep{predaPLSRegressionStochastic2005, reissFunctionalPrincipalComponent2007, aguileraUsingBasisExpansions2010, delaigleMethodologyTheoryPartial2012, aguileraPenalizedVersionsFunctional2016, febrero-bandeFunctionalPrincipalComponent2017, beyaztasRobustFunctionalPartial2022, saricamPartialLeastsquaresEstimation2022, mutisFunctiononfunctionLinearQuantile2025}, a unified framework capable of simultaneously handling mixed modalities of functional and scalar covariates remains underdeveloped.
+
+In this paper, we propose a hybrid partial least squares (PLS) regression framework that integrates functional and vector predictors in a principled and coherent manner.
+To extract predictive structure from jointly observed and potentially correlated data types, we define a Hilbert space that treats functional and vector components as a single hybrid object, equipped with a suitable inner product.
+The hybrid PLS direction is then obtained by iteratively maximizing the empirical covariance with the response, subject to a unit-norm constraint in this Hilbert space.
 
@@
 	\item Our sample size is small compared to the dimension and number of functional and scalar predictors.
-		\item Existing partial least squares (PLS) methods can only accommodate (i) univariate or multivariate functional predictors without any scalar predictors \citep{Preda2005, Delaigle2012, Febrero2017, Beyaztas2020}; or (2) a univariate functional predictor with other scalar predictors \citep{Wang2018}.
+	\item Existing partial least squares (PLS) methods can only accommodate (i) univariate or multivariate functional predictors without any scalar predictors \citep{predaPLSRegressionStochastic2005, delaigleMethodologyTheoryPartial2012, Febrero2017, Beyaztas2020}; or (2) a univariate functional predictor with other scalar predictors \citep{Wang2018}.
 \end{enumerate}
@@
 		\begin{split}
-				&\argmax \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top}(J^\ast+\Lambda \ddot{J}^\ast) \xi^*} , \quad \textit{or equivalently}, \\ 
-				&\argmax \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1.
+			&\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top}(J^\ast+\Lambda \ddot{J}^\ast) \xi^*} , \quad \textit{or equivalently}, \\ 
+			&\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1.
 			\label{eq: Regularized generalized rayleigh quotient equation}
@@
 		\Comment{ \eqref{def:V_star}}
-			\State 	$\widehat{\xi}_l^\ast \leftarrow \argmax_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1
+		\State 	$\widehat{\xi}_l^\ast \leftarrow \arg \max_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1
 		$
@@
 \end{figure}
+
 \begin{comment}
@@
 		\item Utilize a graphical model to introduce a complex dependence structure.
-			\item Demonstrate that our method outperforms the penalized functional regression approach by \citet{goldsmith_penalized_2011}.
+		\item Demonstrate that our method outperforms the penalized functional regression approach by \citet{goldsmithPenalizedFunctionalRegression2011}.
 		\item Show that our method exhibits superior performance as correlation strength increases.
@@
 	\item Penalized functional regression (pfr)~\cite
-		{goldsmith_penalized_2011}\item Principal component regression (fpcr): run both of PCA for multple functional predictors~\cite{happ_multivariate_2018} and scalar PCA and run OLS on the PC scores.
+	{goldsmithPenalizedFunctionalRegression2011}\item Principal component regression (fpcr): run both of PCA for multple functional predictors~\cite{happ_multivariate_2018} and scalar PCA and run OLS on the PC scores.
 \end{itemize}
@@
 \subsection{Proof of new Proposition}
-	For any $\xi = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta})\in \mathcal{H}$, we have:
+For any $\boldsymbol{\xi} = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta}) \in \mathcal{H}$, where each functional component $\xi_j \in L^2([0,1])$ lies in the span of the basis functions $\{b_1(t), \ldots, b_M(t)\}$ and is expressed as
+\begin{equation*}
+	\xi_j(t) := 
+	\sum_{m=1}^M d_{jm} \, b_m(t), \quad j = 1, \ldots, K,
+\end{equation*}
+with coefficient vectors $\mathbf{d}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$, the squared norm of $\boldsymbol{\xi}$ in the hybrid Hilbert space $\mathcal{H}$ is given by
+is computed as follows:
+\begin{align*}
+	\langle {\xi},{\xi} \rangle_{\mathcal{H}}
+	&=
+	\sum_{j=1}^K
+	\langle
+	\xi_j, \xi_j
+	\rangle
+	+
+	\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\\&=
+	\sum \limits_{j=1}^K \int_0^1
+	\biggl(
+	\sum_{m=1}^M d_{jm} b_{m}(t) 
+	\biggr) 
+	\biggl(
+	\sum_{m'=1}^M d_{jm'} b_{m'}(t) 
+	\biggr) 
+	dt
+	+
+	\boldsymbol{\zeta}^\top \boldsymbol{\zeta}  
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\\&=
+	\sum \limits_{j=1}^K 
+	\sum_{m=1}^M
+	\sum_{m'=1}^M
+	d_{jm}
+	d_{jm'}
+	\int_0^1
+	b_{m}(t) 
+	b_{m'}(t) 
+	dt
+	+
+	\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\\&=
+	\sum \limits_{j=1}^K 
+	\mathbf{d}_j^\top
+	\Theta_j
+	\mathbf{d}_j
+	+
+	\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
+\end{align*}
 \begin{align*}
@@
 \end{align*}	
-
-The squared hybrid Hilbert norm $\langle {\xi},{\xi} \rangle_{\mathcal{H}}$ 
-is computed as follows:
-\begin{align*}
-\langle {\xi},{\xi} \rangle_{\mathcal{H}}
-&=
-\sum_{j=1}^K
-\langle
-\xi_j, \xi_j
-\rangle
-+
-\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\\&=
-\sum \limits_{k=1}^K \int_0^1
-\biggl(
-\sum_{m=1}^M d_{jm'} b_{m}(t) 
-\biggr) 
-\biggl(
-\sum_{m'=1}^M d_{jm'} b_{m'}(t) 
-\biggr) 
-dt
-+
-\boldsymbol{\zeta}^\top \boldsymbol{\zeta}  
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\\&=
-aaaaa
-\end{align*}
-admits the following matrix representation:
+Both expressions in \eqref{...} and \eqref{...} can be represented as inner products in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$, which is defined as follows:
+\begin{lemma}[Inner product of tuples]
+	\label{lemma:valid_inner_product_tuple}
+	Let $B \in \mathbb{R}^{M \times M}$ be a symmetric positive semi-definite matrix. 
+	For any two tuples $u = (\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})$ and $v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$ in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$, define the bilinear form
 	\[
-	\langle \boldsymbol{\xi}, \boldsymbol{\xi} \rangle_{\mathcal{H}} = \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{d}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta}.
+	\langle u, v \rangle_{B} := \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega}.
 	\]
+	Then $\langle \cdot, \cdot \rangle_{B}$ is a valid inner product on $(\mathbb{R}^M)^K \times \mathbb{R}^p$.
+\end{lemma}
+The proof of Lemma \ref{lemma:valid_inner_product_tuple} is provided in Appendix \ref{section:proof:lemma:valid_inner_product_tuple}
 
@@
 
-\subsection{Proof of Lemma}
+\subsection{Proof of Lemma \ref{lemma:valid_inner_product_tuple}}\label{section:proof:lemma:valid_inner_product_tuple}
+\begin{proof}
 	We verify that the function
 	\[
-		\langle \mathbf{u}, \mathbf{v} \rangle_{\mathcal{H}} := \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega},
+	\langle u, v \rangle_{B} := \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega},
 	\]
-		defines a valid inner product on $\mathcal{H} := \mathbb{R}^{KM} \times \mathbb{R}^p$, where $\mathbf{u} = (\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})$ and $\mathbf{v} = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$.
-
-		\textit{Linearity in the first argument}: For any $a, b \in \mathbb{R}$ and $\mathbf{u}_1, \mathbf{u}_2, \mathbf{v} \in \mathcal{H}$,
+	defines a valid inner product on $ (\mathbb{R}^M)^K \times \mathbb{R}^p$, where $u = (\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})$ and $v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$ are elements of $(\mathbb{R}^M)^K \times \mathbb{R}^p$.
+	\paragraph{Symmetry}: Since $B$ is symmetric and the Euclidean inner product is symmetric,
 	\[
-		\langle a \mathbf{u}_1 + b \mathbf{u}_2, \mathbf{v} \rangle_{\mathcal{H}} 
-		= a \langle \mathbf{u}_1, \mathbf{v} \rangle_{\mathcal{H}} + b \langle \mathbf{u}_2, \mathbf{v} \rangle_{\mathcal{H}}.
+	\langle u, v \rangle_{B} = \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega} = \sum_{j=1}^K \mathbf{g}_j^\top B \mathbf{d}_j + \boldsymbol{\omega}^\top \boldsymbol{\zeta} = \langle v, u \rangle_{B}.
 	\]
-
-		\textit{Symmetry}: Since $B$ is symmetric and the standard inner product is symmetric,
-		\[
-		\langle \mathbf{u}, \mathbf{v} \rangle_{\mathcal{H}} 
-		= \langle \mathbf{v}, \mathbf{u} \rangle_{\mathcal{H}}.
-		\]
-
-		\textit{Positive definiteness}: If $\mathbf{u} \ne 0$, then either some $\mathbf{d}_j \ne 0$ or $\boldsymbol{\zeta} \ne 0$. Since $B$ is positive definite,
-		\[
-		\langle \mathbf{u}, \mathbf{u} \rangle_{\mathcal{H}} = \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{d}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta} > 0.
-		\]
-		Thus, $\langle \cdot, \cdot \rangle_{\mathcal{H}}$ is a valid inner product.
-
-		Now let
-		\[
-		\mathbf{g} := \left( \tfrac{1}{n} \Theta_1^\top \mathbf{y}, \ldots, \tfrac{1}{n} \Theta_K^\top \mathbf{y}, \tfrac{1}{n} Z^\top \mathbf{y} \right).
-		\]
-		Then, for any $\mathbf{u} = (\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta}) \in \mathcal{H}$,
-		\[
-		\left\langle \mathbf{u}, \mathbf{g} \right\rangle_{\mathcal{H}} 
-		= \frac{1}{n} \sum_{j=1}^K \mathbf{d}_j^\top B \Theta_j^\top \mathbf{y} + \frac{1}{n} \boldsymbol{\zeta}^\top Z^\top \mathbf{y}
-		= \frac{1}{n} \left( \sum_{j=1}^K \mathbf{y}^\top \Theta_j B \mathbf{d}_j + \mathbf{y}^\top Z \boldsymbol{\zeta} \right),
-		\]
-		as claimed.
+	\paragraph{Linearity in the first argument}: Let $u^{(1)} = (\mathbf{d}_1^{(1)}, \ldots, \mathbf{d}_K^{(1)}, \boldsymbol{\zeta}^{(1)})$ 
+	and
+	$v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega}) $
+	be the elements of $(\mathbb{R}^M)^K \times \mathbb{R}^p$.
+	Let $a, b \in \mathbb{R}$. Then we have
+	\begin{align*}
+		\langle a u^{(1)} + b u^{(2)}, v \rangle_{B}
+		&= \sum_{j=1}^K (a \mathbf{d}_j^{(1)} + b \mathbf{d}_j^{(2)})^\top B \mathbf{g}_j + (a \boldsymbol{\zeta}^{(1)} + b \boldsymbol{\zeta}^{(2)})^\top \boldsymbol{\omega} \\
+		&= 
+		a  \sum_{j=1}^K (\mathbf{d}_j^{(1)})^\top B \mathbf{g}_j 
+		+
+		b \sum_{j=1}^K  (\mathbf{d}_j^{(2)})^\top B \mathbf{g}_j
+		+
+		a ( \boldsymbol{\zeta}^{(1)})^\top \boldsymbol{\omega}
+		+
+		b ( \boldsymbol{\zeta}^{(2)})^\top \boldsymbol{\omega}
+		\\
+		&= 
+		a  
+		\biggl(
+		\sum_{j=1}^K (\mathbf{d}_j^{(1)})^\top B \mathbf{g}_j 
+		+
+		( \boldsymbol{\zeta}^{(1)})^\top \boldsymbol{\omega}
+		\biggr)
+		+
+		b 
+		\biggl( 
+		\sum_{j=1}^K  (\mathbf{d}_j^{(2)})^\top B \mathbf{g}_j
+		+
+		( \boldsymbol{\zeta}^{(2)})^\top \boldsymbol{\omega}
+		\biggr)
+		\\
+		&= a \langle u^{(1)}, v \rangle_{B} + b \langle u^{(2)}, v \rangle_{B}.
+	\end{align*}
+
+	\paragraph{Positive definiteness.}: we have
+	$
+	\langle u, u \rangle_{B} = \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{d}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta}
+	$
+	Since $B$ is positive semi-definite, each term $\mathbf{d}_j^\top B \mathbf{d}_j \geq 0$, and $\boldsymbol{\zeta}^\top \boldsymbol{\zeta} \geq 0$, with equality if and only if $\mathbf{d}_j = 0$ for all $j$ and $\boldsymbol{\zeta} = 0$.
+This completes the proof of Lemma \ref{lemma:valid_inner_product_tuple}.
+\end{proof}
 
@@
 \begin{equation}\label{def:eigenproblem_smoothed}
-		\argmax \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top} J^\ast \xi^*}, \quad \textit{or equivalently}, \quad \argmax \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} J^\ast \xi^*=1,
+	\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top} J^\ast \xi^*}, \quad \textit{or equivalently}, \quad \arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} J^\ast \xi^*=1,
 \end{equation}

### 2025-07-10 manuscript/main.tex
abstract

@@
 \begin{abstract}
-abstract.
+Modern biomedical studies increasingly collect both functional and vector-valued predictors for each subject, introducing challenges due to high dimensionality and cross-modality correlations.
+Existing methods often model these components separately, failing to capture their joint predictive structure.
+We propose a hybrid partial least squares (PLS) regression framework that integrates functional and scalar predictors within a unified Hilbert space equipped with a tailored inner product.
+By iteratively maximizing empirical covariance with the response, our method identifies low-dimensional directions that capture both within- and between-modality variation.
+The procedure is computationally efficient, requiring only to solve linear systems at each step.
+We provide theoretical guarantees and demonstrate the effectiveness of our approach through simulations and an application to clinical outcome prediction using renal imaging and scalar covariates from the Emory University renal study.
 \end{abstract}
@@
 
-\vfill
+%\vfill
 

### 2025-07-11 manuscript/main.tex
my solver proof done
B is symmetric so B inverse cancels B

@@
 \DeclareMathOperator*{\argmax}{arg\,max}
-
+\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
 \newcommand{\jongmin}[1]{
@@
 Existing methods often model these components separately, failing to capture their joint predictive structure.
-We propose a hybrid partial least squares (PLS) regression framework that integrates functional and scalar predictors within a unified Hilbert space equipped with a tailored inner product.
+We propose a hybrid partial least squares (PLS) regression framework that integrates functional and scalar predictors within a unified Hilbert space.
 By iteratively maximizing empirical covariance with the response, our method identifies low-dimensional directions that capture both within- and between-modality variation.
@@
 \]
-We compute $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$ as follows.
-First, we obtain the unnormalized coefficient vectors. For each $j$, the unnormalized vector $\hat{\mathbf{d}}_j'$ is computed by solving a linear equation:
-\begin{equation*}
-	B \hat{\mathbf{d}}_j' = (\Theta_j B)^\top \mathbf{y},
-\end{equation*}
-The unnormalized scalar component is given by
-\begin{equation}
-	\hat{ \boldsymbol{\zeta} }' := Z^\top \mathbf{y}.
-\end{equation}
-Next, we normalize all components with respect to the hybrid Hilbert norm (see Definition~\ref{def:hilbert_space}) to ensure $\hat{\xi}$ has unit length. Specifically, we define
-\begin{equation}\label{def:computed_PLS_direction}
-	\hat{ \mathbf{d}}_j := 
-	\frac{1}{
-		\left(
-		\sum_{j=1}^K \hat{\mathbf{d}}_j'^\top B \hat{\mathbf{d}}_j' +
-		(\hat{ \boldsymbol{\zeta} }')^\top \hat{ \boldsymbol{\zeta} }'
-		\right)^{1/2}
-	} \hat{\mathbf{d}}_j', \quad j = 1, \ldots, K,
-\end{equation}
-and
-\begin{equation}
-	\hat{\boldsymbol{\zeta}} :=
-	\frac{1}{
-		\left(
-		\sum_{j=1}^K \hat{\mathbf{d}}_j'^\top B \hat{\mathbf{d}}_j' +
-		(\hat{ \boldsymbol{\zeta} }')^\top \hat{ \boldsymbol{\zeta} }'
-		\right)^{1/2}
-	} 	\hat{ \boldsymbol{\zeta} }'.
-\end{equation}
-Details of the hybrid norm computation are provided in Appendix~\ref{section:proof:eigenproblem_derivation}.
-
-The estimated $l$th PLS component score for the $i$th observations,
-denoted $\hat{\rho}_i$
-is computed via hybrid inner product. In a matrix multiplication form, it is computed as:
-\begin{align*}
-	\hat{\rho}_i
-	&:=
-	\langle \widetilde{\mathbf{W}}_i, \hat{\xi} \rangle_{\mathcal{H}}
-	=
-	\sum_{j=1}^K \Theta_j B  \mathbf{d}_j
-	+
-	Z \hat{\boldsymbol{\zeta}} 
-	. 
-\end{align*}
-The details of this computation are provided in Appendix~\ref{section:proof:eigenproblem_derivation}.
+We compute $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$ as 
+\begin{equation*}
+	\hat{\mathbf{d}}_j  = \frac{1}{\sqrt{\sum_{j=1}^K 
+			\mathbf{y}^\top
+			\Theta_j
+			B \Theta_j^\top \mathbf{y} 
+			+ 
+			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
+	\Theta_j^\top \mathbf{y},
+	\quad
+	%%%%%%%%%%%%%%%%
+	\hat{\boldsymbol{\zeta}}  = \frac{1}{\sqrt{\sum_{j=1}^K 
+			\mathbf{y}^\top
+			\Theta_j
+			B \Theta_j^\top \mathbf{y} 
+			+ 
+			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
+	Z^\top \mathbf{y}.
+\end{equation*}
+The derivation of this formula is provided in Appendix~\ref{section:proof:eigenproblem_derivation}.
 Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other.
@@
 
+\begin{proposition} \label{Proposition:linear_system_unregularized}
+aaa
+\end{proposition}
+Proof of is provided in Appendix \ref{section:proof:Proposition:linear_system_unregularized}.
 \subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
@@
 
-\subsection{Proof of new Proposition}
-For any $\boldsymbol{\xi} = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta}) \in \mathcal{H}$, where each functional component $\xi_j \in L^2([0,1])$ lies in the span of the basis functions $\{b_1(t), \ldots, b_M(t)\}$ and is expressed as
+\subsection{Proof of Proposition \ref{Proposition:linear_system_unregularized}}\label{section:proof:Proposition:linear_system_unregularized}
+\begin{comment}
+We start by defining a  inner product in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$:
+\begin{lemma}[Inner product of tuples]
+	\label{lemma:valid_inner_product_tuple}
+	Let $B \in \mathbb{R}^{M \times M}$ be a symmetric positive semi-definite matrix. 
+	For any two tuples $u = (\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})$ and $v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$ in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$, define the bilinear form
+	\[
+	\langle u, v \rangle_{B} := \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega}.
+	\]
+	Then $\langle \cdot, \cdot \rangle_{B}$ is a valid inner product on $(\mathbb{R}^M)^K \times \mathbb{R}^p$.
+\end{lemma}
+The proof of Lemma \ref{lemma:valid_inner_product_tuple} is provided in Appendix \ref{section:proof:lemma:valid_inner_product_tuple}
+\end{comment}
+Let $\xi = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta}) \in \mathcal{H}$.
+Assume that each functional component $\xi_j \in L^2([0,1])$ lies in the span of the basis functions ${b_1(t), \ldots, b_M(t)}$ and can be written as
 \begin{equation*}
@@
 \end{equation*}
-with coefficient vectors $\mathbf{d}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$, the squared norm of $\boldsymbol{\xi}$ in the hybrid Hilbert space $\mathcal{H}$ is given by
+with coefficient vectors $\mathbf{d}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$.
+Then, the squared norm of $\xi$ in the hybrid Hilbert space $\mathcal{H}$ 
+%can be expressed as the inner product on $(\mathbb{R}^M)^K \times \mathbb{R}^p$ defined in Lemma~\ref{lemma:valid_inner_product_tuple} as follows:
 is computed as follows:
@@
 	\mathbf{d}_j^\top
-	\Theta_j
+B
 	\mathbf{d}_j
 	+
-	\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
-\end{align*}
+	\boldsymbol{\zeta}^\top \boldsymbol{\zeta},
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\\&=\bigl \langle(\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta}),(\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})\bigr\rangle_B.
+\end{align*}
+In a similar manner, the empirical covariance is
+% expressed as the inner product on  defined in Lemma \ref{lemma:valid_inner_product_tuple} as follows:
+computed as follows:
 \begin{align*}
@@
 	Z \boldsymbol{\zeta} 
-	\biggr).
-\end{align*}	
-Both expressions in \eqref{...} and \eqref{...} can be represented as inner products in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$, which is defined as follows:
-\begin{lemma}[Inner product of tuples]
-	\label{lemma:valid_inner_product_tuple}
-	Let $B \in \mathbb{R}^{M \times M}$ be a symmetric positive semi-definite matrix. 
-	For any two tuples $u = (\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})$ and $v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$ in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$, define the bilinear form
+	\biggr)
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\\&=
+%	\frac{1}{n}
+%\bigl \langle
+%(\Theta_1^\top \mathbf{y} , \ldots, \Theta_K^\top %\mathbf{y}, Z^\top \mathbf{y}),
+%(\mathbf{d}_1, \ldots, \mathbf{d}_K, %\boldsymbol{\zeta})
+%\bigr\rangle_B.
+\end{align*}	
+Therefore, problem of maximizing the squared covariance can be written as
+\begin{comment}
+\begin{equation*}
+	\widehat{\textnormal{Cov}}^2 (
+\langle \widetilde{W}, \xi  \rangle_{\mathcal{H}}, Y 
+) 
+=
+\frac{1}{n^2}
+\bigl \langle
+(\Theta_1^\top \mathbf{y} , \ldots, \Theta_K^\top \mathbf{y}, Z^\top \mathbf{y}),
+(\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})
+\bigr\rangle_B^2.
+\end{equation*}
+\end{comment}
+%Therefore, the optimization problem 
+presented in Proposition \ref{Proposition:linear_system_unregularized} is equivalent to the following constrained optimization problem on the Euclidean space:
+\begin{align*}
+	\max_{\mathbf{d}_1, \ldots, \mathbf{d}_K \in \mathbb{R}^M,
+		 \boldsymbol{\zeta} \in \mathbb{R}^p
+	}~&
+	\frac{1}{n^2}
+	\biggl(
+\sum \limits_{k=1}^K 
+\mathbf{y}^\top
+\Theta_{j}
+B
+\mathbf{d}_j
++
+\mathbf{y}^\top
+Z \boldsymbol{\zeta} 
+\biggr)^2,
+\\&~s.t.~	\sum \limits_{j=1}^K 
+\mathbf{d}_j^\top
+B
+\mathbf{d}_j
++
+\boldsymbol{\zeta}^\top \boldsymbol{\zeta} = 1.
+\end{align*} 
+ Let us denote the objective function as
  \[
-	\langle u, v \rangle_{B} := \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega}.
+ f(\{\mathbf{d}_j\}, \boldsymbol{\zeta}) := 
+ \frac{1}{n^2}
+ \left(
+ \sum_{j=1}^K \mathbf{y}^\top \Theta_j B \mathbf{d}_j + \mathbf{y}^\top Z \boldsymbol{\zeta}
+ \right)^2,
  \]
-	Then $\langle \cdot, \cdot \rangle_{B}$ is a valid inner product on $(\mathbb{R}^M)^K \times \mathbb{R}^p$.
-\end{lemma}
-The proof of Lemma \ref{lemma:valid_inner_product_tuple} is provided in Appendix \ref{section:proof:lemma:valid_inner_product_tuple}
-
-By the definition of the inner product on $\mathcal{H} = \mathbb{R}^{KM} \times \mathbb{R}^p$, we have
+ and the constraint function as
  \[
-\langle \boldsymbol{\xi}, \boldsymbol{\xi} \rangle_{\mathcal{H}} = \sum_{j=1}^K \langle \xi_j, \xi_j \rangle_{L^2([0,1])} + \|\boldsymbol{\zeta}\|^2.
+ g(\{\mathbf{d}_j\}, \boldsymbol{\zeta}) := \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{d}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta} - 1 = 0.
  \]
-Since $\xi_j(t) = \sum_{m=1}^M d_{jm} b_m(t)$, it follows that
+
+ The feasible set is compact, as it corresponds to the boundary of an ellipsoid in a finite-dimensional Euclidean space.
+Since the objective function $f$ is continuous and the constraint defines a compact feasible set, the  Weierstrass Extreme Value Theorem (see, for example, Theorem 2.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}) ensures the existence of a global maximizer.
+
+ Define the Lagrangian:
  \[
-\langle \xi_j, \xi_j \rangle_{L^2([0,1])} 
-= \int_0^1 \left( \sum_{m=1}^M d_{jm} b_m(t) \right)^2 dt 
-= \mathbf{d}_j^\top B \mathbf{d}_j,
+ \mathcal{L}(\{\mathbf{d}_j\}, \boldsymbol{\zeta}, \lambda) = f(\{\mathbf{d}_j\}, \boldsymbol{\zeta}) - \lambda g(\{\mathbf{d}_j\}, \boldsymbol{\zeta}).
  \]
-where $B$ is the Gram matrix of the basis. Substituting this into the definition yields
-\[
-\langle \boldsymbol{\xi}, \boldsymbol{\xi} \rangle_{\mathcal{H}} = \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{d}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta}.
-\]
-
-\jongmin{
-	Another way of computing \eqref{def:eigenproblem_smoothed}, rather than solving an eigenproblem, is as follows.
-As shown in the proof in Appendix \ref{section:proof:eigenproblem_derivation}, the empirical covariance is simplified as:
-	\begin{align*}
-		\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \xi \rangle_\mathcal{H} Y_i \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}).
-		\\&=
-		\frac{1}{n}\tilde{\mathbf{y}}^\top
-		\begin{bmatrix} \widetilde{C}J \; \mathbf{Z} \end{bmatrix} \;      \underbrace{
-			\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
-		}_{:= \boldsymbol{\beta}}.
-	\end{align*}
-	Let us 
-	denote $\mathbf{b} =  \widetilde{\mathbf{y}}^\top \begin{bmatrix} \widetilde{C}J \; \mathbf{Z} \end{bmatrix}$.
-This is the weighted row sum of $\begin{bmatrix} \widetilde{C}J \; \mathbf{Z} \end{bmatrix}$, weighted by $\widetilde{\mathbf{y}}$.
-	Then using the symmetricity of $J^\ast$, we solve a linear system $J^\ast \mathbf{d} =
-	\mathbf{b}^\top$ to obtain $\mathbf{d}$. Then we have
-	\begin{align*}
-		\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
-		\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y ) 
-		%%%%%%%%%%%%%%%%%%%%%
-		&= 
-		%%%%%%%%%%%%%%%%%%%%%%%%
-		\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
-		\frac{1}{n} \mathbf{d}^\top J^\ast  \boldsymbol{\beta}
-		\\& \overset{(i)}{\leq} 
-		\max_{\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}} = 1}
-		\frac{1}{n} \sqrt{\mathbf{d}^\top J^\ast  \mathbf{d}}
-		\sqrt{\boldsymbol{\beta} J^\ast  \boldsymbol{\beta}}
-		\\& \overset{(ii)}{=}
-		\frac{1}{n} \sqrt{\mathbf{d}^\top J^\ast  \mathbf{d}}    ,
-	\end{align*}
-	where step $(i)$ uses the Cauchy-Schwarz inequality with the inner product $\langle x, y \rangle_{J^\ast} = x^\top J^\ast y$,
-	and step $(ii)$ uses the norm constraint.
-	By the Cauchy-Schwarz inequality, the maximum displayed in the last term is obtained by a unit vector (with respect to $\langle \cdot, \cdot \rangle_{J^\ast}$) parallel to $\mathbf{d}$.
-Therefore we have
-	\begin{equation*}
-		\begin{bmatrix} \mathbf{a} \\ \mathbf{\theta} \end{bmatrix}
-		= \frac{1}{\sqrt{\mathbf{d}^\top  J^\ast \mathbf{d} }}\mathbf{d},
-	\end{equation*}
-	which only involves solving one linear equation.
-}
+ The constraint function $g$ is continuously differentiable, and its gradient vanishes only at the origin.
+Since the origin is not feasible (the constraint requires norm 1), the gradient of $g$ is nonzero at all feasible points.
+Thus, the linear independence constraint qualification (LICQ) holds, ensuring that the KKT conditions are necessary for local maxima (see, for example, Theorem 5.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}).
+ Taking gradients of $\mathcal{L}$ and setting them to zero yields:
+ \begin{align*}
+ 	\nabla_{\mathbf{d}_j} \mathcal{L} &= 
+ 	\frac{2}{n^2} 
+ 	\left(
+ 	\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
+ 	\right)
+ 	B \Theta_j^\top \mathbf{y}
+ 	- 2\lambda B \mathbf{d}_j = 0, \quad \forall j, 
+ 	\numberthis \label{lag_grad_d}
+ 	\\
+ 	\nabla_{\boldsymbol{\zeta}} \mathcal{L} &= 
+ 	\frac{2}{n^2} 
+ 	\left(
+ 	\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
+ 	\right)
+ 	Z^\top \mathbf{y}
+ 	- 2\lambda \boldsymbol{\zeta} = 0.
+ 		\numberthis \label{lag_grad_zeta}
+ \end{align*}
+By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$ and observing that the scalar quantity $\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$ appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the gradient conditions together imply that any local optimum must be  scalar multiples of
+$$
+\Theta_1^\top \mathbf{y}, \ldots, \Theta_K^\top \mathbf{y}, Z^\top \mathbf{y},
+$$
+all scaled by the same factor.
+There exists only one set of vectors  that also satisfies the primal equality constraint, namely the normalized version of the vector set above.
+The global maximizer is therefore given by
+\begin{equation*}
+	\mathbf{d}_j^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
+			\mathbf{y}^\top
+			\Theta_j
+			 B \Theta_j^\top \mathbf{y} 
+			 + 
+			 \mathbf{y}^\top Z Z^\top \mathbf{y}}}
+		 \Theta_j^\top \mathbf{y},
+		 \quad
+		 %%%%%%%%%%%%%%%%
+		 	\boldsymbol{\zeta}^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
+		 		\mathbf{y}^\top
+		 		\Theta_j
+		 		B \Theta_j^\top \mathbf{y} 
+		 		+ 
+		 		\mathbf{y}^\top Z Z^\top \mathbf{y}}}
+		 Z^\top \mathbf{y},
+\end{equation*}
+which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$. This completes the proof of  Proposition \ref{Proposition:linear_system_unregularized}.
 

### 2025-07-11 create-FSHybridPLS.Rmd
code:get_xi_direct removed

@@
 ```{r}
-get_xi_direct <- function(W, y) {
-  K <- W$n_functional
-  C_J <- get_CJ(W)
-  A <- cbind(C_J, W$Z)                      # shape: n × d
-  b <- t(y) %*% A / W$n_sample   # equivalent to V_star
-
-  J_star <- get_gram_matrix_block(W)
-  alpha <- solve(J_star, t(b))                # unconstrained maximizer
-  norm_squared <- as.numeric( t(alpha) %*% J_star %*% alpha )
-  xi_hat <- alpha / sqrt(norm_squared)  # normalize
-
-  return(xi_hat)
-}
-```
-
-```{r}
 library(fda)
@@
 # --- Step 1: Simulate Data ---
-set.seed(777)
+set.seed(2222)
 

### 2025-07-11 manuscript/main.tex
code:get_xi_direct removed

@@
 	\end{equation*}
-The derivation of this formula is provided in Appendix~\ref{section:proof:eigenproblem_derivation}.
+These expressions represent matrix–vector multiplications normalized by a common factor. 
+	The derivation of this formula is provided in Appendix~\ref{section:proof:Proposition:linear_system_unregularized}.
 	Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other.
@@
 
-\subsection{Proof of Lemma \ref{lemma:valid_inner_product_tuple}}\label{section:proof:lemma:valid_inner_product_tuple}
-\begin{proof}
-	We verify that the function
-	\[
-	\langle u, v \rangle_{B} := \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega},
-	\]
-	defines a valid inner product on $ (\mathbb{R}^M)^K \times \mathbb{R}^p$, where $u = (\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})$ and $v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$ are elements of $(\mathbb{R}^M)^K \times \mathbb{R}^p$.
-	\paragraph{Symmetry}: Since $B$ is symmetric and the Euclidean inner product is symmetric,
-	\[
-	\langle u, v \rangle_{B} = \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega} = \sum_{j=1}^K \mathbf{g}_j^\top B \mathbf{d}_j + \boldsymbol{\omega}^\top \boldsymbol{\zeta} = \langle v, u \rangle_{B}.
-	\]
-	\paragraph{Linearity in the first argument}: Let $u^{(1)} = (\mathbf{d}_1^{(1)}, \ldots, \mathbf{d}_K^{(1)}, \boldsymbol{\zeta}^{(1)})$ 
-	and
-	$v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega}) $
-	be the elements of $(\mathbb{R}^M)^K \times \mathbb{R}^p$.
-	Let $a, b \in \mathbb{R}$. Then we have
-	\begin{align*}
-		\langle a u^{(1)} + b u^{(2)}, v \rangle_{B}
-		&= \sum_{j=1}^K (a \mathbf{d}_j^{(1)} + b \mathbf{d}_j^{(2)})^\top B \mathbf{g}_j + (a \boldsymbol{\zeta}^{(1)} + b \boldsymbol{\zeta}^{(2)})^\top \boldsymbol{\omega} \\
-		&= 
-		a  \sum_{j=1}^K (\mathbf{d}_j^{(1)})^\top B \mathbf{g}_j 
-		+
-		b \sum_{j=1}^K  (\mathbf{d}_j^{(2)})^\top B \mathbf{g}_j
-		+
-		a ( \boldsymbol{\zeta}^{(1)})^\top \boldsymbol{\omega}
-		+
-		b ( \boldsymbol{\zeta}^{(2)})^\top \boldsymbol{\omega}
-		\\
-		&= 
-		a  
-		\biggl(
-		\sum_{j=1}^K (\mathbf{d}_j^{(1)})^\top B \mathbf{g}_j 
-		+
-		( \boldsymbol{\zeta}^{(1)})^\top \boldsymbol{\omega}
-		\biggr)
-		+
-		b 
-		\biggl( 
-		\sum_{j=1}^K  (\mathbf{d}_j^{(2)})^\top B \mathbf{g}_j
-		+
-		( \boldsymbol{\zeta}^{(2)})^\top \boldsymbol{\omega}
-		\biggr)
-		\\
-		&= a \langle u^{(1)}, v \rangle_{B} + b \langle u^{(2)}, v \rangle_{B}.
-	\end{align*}
-
-	\paragraph{Positive definiteness.}: we have
-	$
-	\langle u, u \rangle_{B} = \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{d}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta}
-	$
-	Since $B$ is positive semi-definite, each term $\mathbf{d}_j^\top B \mathbf{d}_j \geq 0$, and $\boldsymbol{\zeta}^\top \boldsymbol{\zeta} \geq 0$, with equality if and only if $\mathbf{d}_j = 0$ for all $j$ and $\boldsymbol{\zeta} = 0$.
-This completes the proof of Lemma \ref{lemma:valid_inner_product_tuple}.
-\end{proof}
-
 	\subsection{Proof of Propositions \ref{Proposition: generalized rayleigh quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}

### 2025-07-11 create-FSHybridPLS.Rmd
code: new version of get_xi_direct validated
same as the old version of get_xi_direct!

@@
 
+### helper: get_xi_hat_linear
+```{r}
+get_xi_hat_linear_new <- function(W, y){
+  n <- W$n_sample
+  K <- W$n_functional
+  normalizer <- 0
+  d = list()
+  for (i in 1:K){  ## tPhi_tC : C multiplied by Phi. Scalable to arbitrary K
+    Theta_t <- W$functional_list[[i]]$coefs
+    B <- W$gram_list[[i]]
+    d[[i]] <- Theta_t %*% y
+    normalizer <- normalizer + t(y) %*% t(Theta_t) %*% B %*% Theta_t %*% y
+  }
+  d[[K+1]] <- t(W$Z) %*% y
+  normalizer <- normalizer+ t(y) %*% W$Z %*% t(W$Z) %*% y
+  d_vec <- do.call(c, d)  # or: unlist(d)
+  d_vec <- d_vec/ sqrt(normalizer)
+  return(d_vec)
+}
+```
+
+compare xi_hat_lin, xi_hat_lin_new
+
 ```{r}
@@
 xi_hat_lin <- get_xi_hat_linear(W, y)
-
+xi_hat_lin_new <- get_xi_hat_linear_new(W, y)
 # Wrap into predictor_hybrid object using format template
 xi_hat_direct <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin)
+norm_val <- sqrt(inprod.predictor_hybrid(xi_hat_direct))
+xi_hat_direct <- scalar_mul.predictor_hybrid(xi_hat_direct,  1 / norm_val)
+xi_hat_direct_new <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin_new)
+
+cat(xi_hat_direct_new$functional_list[[1]]$coefs- xi_hat_direct$functional_list[[1]]$coefs)
+cat(xi_hat_direct_new$functional_list[[2]]$coefs- xi_hat_direct$functional_list[[2]]$coefs)
+
+```
+
+```{r}
+library(fda)
+
+# --- Step 1: Simulate Data ---
+set.seed(2222)
+
+n_sample <- 100
+n_scalar <- 2
+n_basis <- 5
+n_functional <- 2
+
+# Scalar predictors Z (centered)
+Z <- matrix(rnorm(n_sample * n_scalar), ncol = n_scalar)
+Z <- scale(Z, center = TRUE, scale = FALSE)
+
+# Create functional predictors (centered)
+basis <- create.bspline.basis(c(0, 1), nbasis = n_basis)
+functional_list <- list()
+for (j in 1:n_functional) {
+  coefs <- matrix(rnorm(n_basis * n_sample), nrow = n_basis)
+  fdobj <- fd(coef = coefs, basisobj = basis)
+  mean_fd <- mean.fd(fdobj)
+  mean_coef <- coef(mean_fd)
+  centered_coefs <- coefs - matrix(mean_coef, nrow = n_basis, ncol = n_sample)
+  functional_list[[j]] <- fd(coef = centered_coefs, basisobj = basis)
+}
+
+# --- Step 2: Construct hybrid object ---
+W <- predictor_hybrid(Z = Z, functional_list = functional_list)
+
+# --- Step 3: Simulate and center response ---
+total_coef_len <- sum(W$n_basis_list) + W$n_scalar
+true_coef <- rnorm(total_coef_len)
+
+# Flatten design matrix
+Xmat <- matrix(NA, n_sample, total_coef_len)
+for (i in 1:n_sample) {
+  W_i <- subset_predictor_hybrid(W, i)
+  func_coefs <- do.call(c, lapply(W_i$functional_list, function(fdobj) as.vector(coef(fdobj))))
+  Xmat[i, ] <- c(func_coefs, W_i$Z)
+}
+
+y <- Xmat %*% true_coef + rnorm(n_sample, sd = 0.1)
+y <- as.vector(scale(y, center = TRUE, scale = FALSE))
+
+# --- Step 4: Compute constraint matrix ---
+lambda <- rep(0, W$n_functional)
+constr_mat <- get_constraint_matrix_hybrid(W, lambda)
+L <- chol(constr_mat)
+
+# --- Step 5: Run eigen-based PLS ---
+W_template <- W  # prevent mutation
+
+pls_eig_result <- get_pls_comp(W, y, L)
+xi_hat_eig <- pls_eig_result$xi_hat
+
+xi_hat_lin <- get_xi_hat_linear(W, y)
+xi_hat_lin_new <- get_xi_hat_linear_new(W, y)
+# Wrap into predictor_hybrid object using format template
+xi_hat_direct <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin)
+xi_hat_direct_new <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin_new)
 

### 2025-07-11 manuscript/main.tex
code: get_xi_direct unified

@@
 	where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
-	In practice, functional predictors are observed only at a finite set of time points rather than as complete curves.
-Rather than reconstructing infinite-dimensional object stated above via finite observations, we approximate each predictor using a finite-dimensional projection by truncating its basis expansion at a finite number $M$.
-This $M$ can be set to a sufficiently large value (e.g., 15 or 20) to capture a wide range of functional patterns.
-	Notably, it is unnecessary to fine-tune $M$, as a  penalization scheme introduced in Section \ref{sec: Regularization of PLS Components} regularizes each functional component to achieve the desired smoothness.
-We denote the projected predictors and coefficients as
+Since functional predictors are observed at finitely many discrete time points, we approximate them by truncating the expansion at $M$ terms, yielding a finite-dimensional projection.
+A moderately large $M$ (e.g., 15 or 20) suffices to capture rich functional variation, and no fine-tuning is needed, as our method controlls smoothness  via penalization (Section~\ref{sec: Regularization of PLS Components}).
+We denote the truncated space by
+	\begin{equation}
+		\mathcal{B} := \operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr).
+	\end{equation}
+	 We denote the  predictors projected onto $\mathcal{B}$ and the resulting coefficients as
 	\begin{equation*}
@@
 	Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an intermediate strategy for implementing the first step of the PLS algorithm.
-This approach directly obtains a hybrid PLS component direction, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply solving a linear equation.
+This approach directly obtains a hybrid PLS component direction, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply doing matrix-vector multiplications
+
 	We now describe the strategy for computing the PLS component direction at the $l$-th iteration.
 For simplicity, we omit the iteration index and assume that the observations have been residualized and are orthogonal to those from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for the residualization procedure).
-
-	The goal is to find a unit-norm direction $\xi \in \mathcal{H}$, whose functional components lie in $\operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr)$, that maximizes the empirical covariance between the resulting PLS component scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$.
-	We denote the solution as
-	\begin{equation}
+	The goal is to find a unit-norm direction $\xi \in 
+	(\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}$ that maximizes the squared empirical covariance between the resulting PLS component scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$,
+	 defined as
+	 		\begin{equation}\label{def:squared_empirical_cov}
+	 	\widehat{\textnormal{Cov}}^2 \left( \langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y \right)
+	 	:=
+	 	\biggl(
+	 	\frac{1}{n} 
+	 	\sum_{i=1}^n
+	 	y_i
+	 	\langle \widetilde{W}_i, \xi \rangle_{\mathcal{H}}
+	 	\biggr)^2
+	 	.
+	 \end{equation}
+	We denote the maximizer as
+	\begin{equation*}
 		\hat{\xi} 
 = 
-		(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}}),
-	\end{equation}
-	where $\hat{\boldsymbol{\zeta}} \in \mathbb{R}^p$ is the scalar part, and each functional part $\hat{\xi}_j \in L^2([0,1])$ lies in $\operatorname{span}(b_1(t), \ldots, b_M(t))$ and is expressed as
+(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})
+:= \arg \max_{\xi \in (\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}} \widehat{\textnormal{Cov}}^2 \left( \langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y \right)
+	\end{equation*}
+%
+	where each functional part $\hat{\xi}_j $  is expressed as
 	\begin{equation*}
@@
 
-	Let $\hat{\mathbf{d}}_j := (\hat{d}_{j1}, \ldots, \hat{d}_{jM})^\top \in \mathbb{R}^M$ and $\mathbf{y} := (y_1, \ldots, y_n)^\top$. 
-	Let $B \in \mathbb{R}^{M \times M}$ denote the Gram matrix of the basis functions, with entries
-	\[
-	B_{m, m'} := \langle b_m, b_{m'} \rangle, \quad m, m' = 1, \ldots, M.
-	\]
-	We compute $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$ as 
+	%	consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
+Let
+
+	\begin{proposition}\label{proposition:generalized_rayleigh_quotient}
+At the $l$-th iteration of the PLS algorithm, the unit-norm direction in $(\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}$ that maximizes the squared empirical covariance \eqref{def:squared_empirical_cov} is the solution to the following generalized eigenvalue problem:
+\begin{align}
+	\left(
+	\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\zeta}}^\top
+	\right)^\top
+	=
+	\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
+	\quad \text{subject to} \quad \boldsymbol{\xi}^\top B^\ast \boldsymbol{\xi} = 1,
+	\label{eq: Regularized generalized rayleigh quotient equation}
+\end{align}
+where
+$$
+V := \frac{1}{n^2} (B^\ast \Theta^\top \mathbf{y})(B^\ast \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
+$$
+where
+$B^\ast := \operatorname{blkdiag}(B, \ldots, B, I_p)  \in  \mathbb{R}^{(MK+p) \times (MK+p)}$,
+ $\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}$,
+$B \in \mathbb{R}^{M \times M}$ is the gram matrix  of the basis functions  with entries
+$
+B_{m, m'} := \langle b_m, b_{m'} \rangle = \int_0^1  b_m(t)  b_{m'}(t) dt
+$
+for $m, m' = 1, \ldots, M$.
+\end{proposition}
+Since $V$ is a rank 1 matrix, the solution of the generalized eigenvalue problem is easily obtained by matrix multiplication and normalization:
+	\begin{proposition} \label{proposition:generalized_rayleigh_quotient_linear}
+	We can compute  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$ in Proposition \ref{proposition:generalized_rayleigh_quotient} as 
 \begin{equation*}
@@
 \end{equation*}
-These expressions represent matrix–vector multiplications normalized by a common factor. 
-	The derivation of this formula is provided in Appendix~\ref{section:proof:Proposition:linear_system_unregularized}.
+\end{proposition}
+The expressions above represent matrix–vector multiplications normalized by a common factor. 
+Proofs of Propositions \ref{proposition:generalized_rayleigh_quotient} and \ref{proposition:generalized_rayleigh_quotient_linear} are provided in Appendix~\ref{section:proof:proposition:generalized_rayleigh_quotient_linear_system_unregularized}.
 Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other.
@@
 
-	%	consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
-Let
-	\begin{proposition} \label{Proposition: generalized rayleigh quotient}
-		Let $\xi \in \mathcal{H}$ be any unit-norm direction such that its $1$st through $K$th functional components lie in $\operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr)$, respectively.
-		Then, the empirical covariance between the projected component $\langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}$ and the response $Y$, approximated in terms of the basis, is given by
-		\begin{equation*}
-			\widehat{\textnormal{Cov}} \left( \langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y \right)
-			:=
-			\frac{1}{n} 
-			\sum_{i=1}^n
-			y_i
-			\langle \widetilde{\mathbf{W}}_i, \xi \rangle_{\mathcal{H}}.
-		\end{equation*}
-		Then the PLS component direction 
-		$	\hat{\xi}$ 
-		computed in \eqref{def:computed_PLS_direction} maximizes $\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y )$.
-	\end{proposition}
-
-	The proof of Proposition \ref{Proposition: generalized rayleigh quotient} is given in the Appendix \ref{section:proof:eigenproblem_derivation}.
-
-	\begin{proposition} \label{Proposition:linear_system_unregularized}
-		aaa
-	\end{proposition}
-	Proof of is provided in Appendix \ref{section:proof:Proposition:linear_system_unregularized}.
 	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
-	Although Proposition \ref{Proposition: generalized rayleigh quotient} provides an efficient and principled way to compute the PLS components $\xi$, their functional part $\psi=(\psi^{(1)}, \ldots, \psi^{(K)})$ may not be smooth, which can lead to overfitting and unstable predictions.
-Thus, in this section, we provide a modification of Proposition  \ref{Proposition: generalized rayleigh quotient} that yields regularized (smoothed) PLS components.
+	Although Proposition \ref{proposition:generalized_rayleigh_quotient} provides an efficient and principled way to compute the PLS components $\xi$, their functional part $\psi=(\psi^{(1)}, \ldots, \psi^{(K)})$ may not be smooth, which can lead to overfitting and unstable predictions.
+Thus, in this section, we provide a modification of Proposition  \ref{proposition:generalized_rayleigh_quotient} that yields regularized (smoothed) PLS components.
 
@@
 Smaller $\lambda_k$ produces PLS components that fit more closely to the observed data, but selecting too small value may cause overfitting.
-The estimated PLS component reverts back to the unregularized version of Proposition \ref{Proposition: generalized rayleigh quotient} when $\lambda_k=0$ for all $k$.
+The estimated PLS component reverts back to the unregularized version of Proposition \ref{proposition:generalized_rayleigh_quotient} when $\lambda_k=0$ for all $k$.
 On the other hand, larger $\lambda_k$ places more emphasis on smoothing $\psi^{(k)}$.
@@
 
-	\subsection{Proof of Proposition \ref{Proposition:linear_system_unregularized}}\label{section:proof:Proposition:linear_system_unregularized}
+	\subsection{Proof of Proposition \ref{proposition:generalized_rayleigh_quotient_linear_system_unregularized}}\label{section:proof:proposition:generalized_rayleigh_quotient_linear_system_unregularized}
 	\begin{comment}
@@
 	%Therefore, the optimization problem 
-	presented in Proposition \ref{Proposition:linear_system_unregularized} is equivalent to the following constrained optimization problem on the Euclidean space:
+	presented in Proposition \ref{proposition:generalized_rayleigh_quotient_linear_system_unregularized} is equivalent to the following constrained optimization problem on the Euclidean space:
 	\begin{align*}
@@
 	\end{equation*}
-	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$. This completes the proof of  Proposition \ref{Proposition:linear_system_unregularized}.
-
-	\subsection{Proof of Propositions \ref{Proposition: generalized rayleigh quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
+	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$.
+This completes the proof of  Proposition \ref{proposition:generalized_rayleigh_quotient_linear_system_unregularized}.
+
+	\subsection{Proof of Propositions \ref{proposition:generalized_rayleigh_quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
 	%

### 2025-07-11 manuscript/main.tex
proposition 1 and 2

@@
 	We denote the maximizer as
-	\begin{equation*}
+	\begin{equation}\label{def:maximizer_squared_empirical_cov}
 		\hat{\xi} 
@@
 := \arg \max_{\xi \in (\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}} \widehat{\textnormal{Cov}}^2 \left( \langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y \right)
-	\end{equation*}
+	\end{equation}
 %
@@
 	\begin{proposition}\label{proposition:generalized_rayleigh_quotient}
-At the $l$-th iteration of the PLS algorithm, the unit-norm direction in $(\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}$ that maximizes the squared empirical covariance \eqref{def:squared_empirical_cov} is the solution to the following generalized eigenvalue problem:
+At the $l$-th iteration of the PLS algorithm, let $
+( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\zeta}}^\top )^\top
+$ denote the coefficients 
+of $	\hat{\xi}$, 
+defined in \eqref{def:maximizer_squared_empirical_cov},
+which is
+the projected unit-norm direction that maximizes the squared empirical covariance. These coefficients can be obtained by solving the following generalized eigenvalue problem
 \begin{align}

### 2025-07-15 create-FSHybridPLS.Rmd
code: get_xi_direct unified
remove get_xi_hat_linear

@@
 ```{r}
-get_xi_hat_linear <- function(W, y){
-  n <- W$n_sample
-  K <- W$n_functional
-  d = list()
-  for (i in 1:K){  ## tPhi_tC : C multiplied by Phi. Scalable to arbitrary K
-    Ct <- W$functional_list[[i]]$coefs
-    Phi <- W$gram_list[[i]]
-    rhs <-  t(Phi) %*% Ct %*% y
-    d[[i]] <- solve(Phi, rhs)
-  }
-  d[[K+1]] <- t(W$Z) %*% y
-  d_vec <- do.call(c, d)  # or: unlist(d)
-  return(d_vec)
-}
-```
-
-### helper: get_xi_hat_linear
-```{r}
 get_xi_hat_linear_new <- function(W, y){
@@
 # --- Step 1: Simulate Data ---
-set.seed(2222)
+set.seed(111)
 

### 2025-07-15 manuscript/main.tex
remove get_xi_hat_linear

@@
 \begin{equation}\label{def:squared_empirical_cov}
-	 	\widehat{\textnormal{Cov}}^2 \left( \langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y \right)
+	 	\widehat{\textnormal{Cov}}^2 \left( \langle 
+	 	\widetilde{W},
+	 	\xi \rangle_{\mathcal{H}}, Y \right)
 	 	:=
@@
 (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})
-:= \arg \max_{\xi \in (\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}} \widehat{\textnormal{Cov}}^2 \left( \langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y \right)
+:= \arg \max_{\xi \in (\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}} \widehat{\textnormal{Cov}}^2 
+\left( 
+\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
+\right)
 	\end{equation}
@@
 	\[
-	\mathcal{L}(\{\mathbf{d}_j\}, \boldsymbol{\zeta}, \lambda) = f(\{\mathbf{d}_j\}, \boldsymbol{\zeta}) - \lambda g(\{\mathbf{d}_j\}, \boldsymbol{\zeta}).
+	\mathcal{L}(\{\mathbf{d}_j\}, \boldsymbol{\zeta}, \lambda) 
+	:= 
+	f(\{\mathbf{d}_j\}, \boldsymbol{\zeta}) - \lambda g(\{\mathbf{d}_j\}, \boldsymbol{\zeta}).
 	\]
@@
 	\end{align*}
-	By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$ and observing that the scalar quantity $\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$ appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the gradient conditions together imply that any local optimum must be  scalar multiples of
-	$$
+	By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$ and observing that the scalar quantity $n^{-2}\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$ appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the gradient conditions together imply that any local optimum must be  scalar multiples of
+	$
 	\Theta_1^\top \mathbf{y}, \ldots, \Theta_K^\top \mathbf{y}, Z^\top \mathbf{y},
-	$$
+	$
 	all scaled by the same factor.

### 2025-07-15 create-FSHybridPLS.Rmd
problem instance as matrix tuples

@@
 
-compare xi_hat_lin, xi_hat_lin_new
+### helper: get_xi_hat_linear
+```{r}
+get_xi_hat_eigen <- function(W, y){
+  M <- W$n_basis_list[1]
+  n <- W$n_sample
+  K <- W$n_functional
+  p <- W$n_scalar
+
+  Theta_t <- W$functional_list[[1]]$coefs
+  B <- W$gram_list[[1]]
+  mat <- B %*% Theta_t %*% y
+  for (i in 1:K){  ## tPhi_tC : C multiplied by Phi. Scalable to arbitrary K
+    Theta_t <- W$functional_list[[i]]$coefs
+    B <- W$gram_list[[i]]
+    B_theta_y <- B %*% Theta_t %*% y
+    mat <- rbind(mat, B_theta_y )
+  }
+  Zty<- t(W$Z) %*% y
+  mat <- rbind(mat, Zty)
+  mat <- mat %*% t(mat)
+  geigen(mat, B, symmetric, only.values=FALSE)
+  return(geigen)
+}
+```
 

### 2025-07-15 manuscript/main.tex
problem instance as matrix tuples

@@
 
+The observations in the hybrid PLS problem can be compactly represented by the tuple
+\begin{equation}\label{def:problem_instance}
+	(B^\ast, \Theta, \mathbf{y}),
+\end{equation}
+defined as follows.
+Let $B \in \mathbb{R}^{M \times M}$ denote the Gram matrix of the basis functions, with entries  
+\[
+B_{m, m'} := \langle b_m, b_{m'} \rangle = \int_0^1 b_m(t)\, b_{m'}(t)\, dt,
+\]
+for $m, m' = 1, \ldots, M$.
+Then define $B^\ast := \operatorname{blkdiag}(B, \ldots, B, I_p) \in \mathbb{R}^{(MK + p) \times (MK + p)}$,  
+$\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}$,  
+and $\mathbf{y} := (y_1, \ldots, y_n)^\top$.
 	\begin{remark}
-		While it is possible to use a different basis for each functional predictor, we adopt a common basis system for all predictors for notational simplicity.
+While it is possible to use a different basis for each functional predictor, we adopt a common basis for all predictors to simplify the notation.
+However, the definition of $B^\ast$ remains general enough to accommodate different bases across the $K$ predictors.
 \end{remark}
 
-	Additionally, it serves as a regularization mechanism, borrowing strength across components and helping to prevent overfitting.
+	%Additionally, it serves as a regularization mechanism, borrowing strength across components and helping to prevent overfitting.
 
@@
 which is
-the projected unit-norm direction that maximizes the squared empirical covariance. These coefficients can be obtained by solving the following generalized eigenvalue problem
+the projected unit-norm direction that maximizes the squared empirical covariance.
+
+ These coefficients can be obtained by solving the following generalized eigenvalue problem
 \begin{align}
@@
 $$
-where
-$B^\ast := \operatorname{blkdiag}(B, \ldots, B, I_p)  \in  \mathbb{R}^{(MK+p) \times (MK+p)}$,
- $\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}$,
-$B \in \mathbb{R}^{M \times M}$ is the gram matrix  of the basis functions  with entries
-$
-B_{m, m'} := \langle b_m, b_{m'} \rangle = \int_0^1  b_m(t)  b_{m'}(t) dt
-$
-for $m, m' = 1, \ldots, M$.
+
 \end{proposition}

### 2025-07-15 manuscript/main.tex
proposition 1 and 2 relabling

@@
 
-	\begin{proposition}\label{proposition:generalized_rayleigh_quotient}
-At the $l$-th iteration of the PLS algorithm, let $
-( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\zeta}}^\top )^\top
-$ denote the coefficients 
-of $	\hat{\xi}$, 
-defined in \eqref{def:maximizer_squared_empirical_cov},
-which is
-the projected unit-norm direction that maximizes the squared empirical covariance.
-
- These coefficients can be obtained by solving the following generalized eigenvalue problem
+	\begin{proposition}\label{proposition:eigen_noregul}
+Let
+$
+(B^\ast, \Theta, \mathbf{y})
+$
+denote the observed data defined in \eqref{def:problem_instance}.
+At the $l$-th iteration of the PLS algorithm, let
+$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\zeta}}^\top )^\top$
+denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
+which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
+These coefficients are obtained by solving the following generalized eigenvalue problem:
 \begin{align}
@@
 Since $V$ is a rank 1 matrix, the solution of the generalized eigenvalue problem is easily obtained by matrix multiplication and normalization:
-	\begin{proposition} \label{proposition:generalized_rayleigh_quotient_linear}
-	We can compute  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$ in Proposition \ref{proposition:generalized_rayleigh_quotient} as 
+	\begin{proposition} \label{proposition:linear_noregul}
+	We can compute  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$ in Proposition \ref{proposition:eigen_noregul} as 
 \begin{equation*}
@@
 The expressions above represent matrix–vector multiplications normalized by a common factor. 
-Proofs of Propositions \ref{proposition:generalized_rayleigh_quotient} and \ref{proposition:generalized_rayleigh_quotient_linear} are provided in Appendix~\ref{section:proof:proposition:generalized_rayleigh_quotient_linear_system_unregularized}.
+Proofs of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:linear_noregul} are provided in Appendix~\ref{section:proof:proposition:linear_noregul_system_unregularized}.
 Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other.
@@
 	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
-	Although Proposition \ref{proposition:generalized_rayleigh_quotient} provides an efficient and principled way to compute the PLS components $\xi$, their functional part $\psi=(\psi^{(1)}, \ldots, \psi^{(K)})$ may not be smooth, which can lead to overfitting and unstable predictions.
-Thus, in this section, we provide a modification of Proposition  \ref{proposition:generalized_rayleigh_quotient} that yields regularized (smoothed) PLS components.
+	Although Proposition \ref{proposition:eigen_noregul} provides an efficient and principled way to compute the PLS components $\xi$, their functional part $\psi=(\psi^{(1)}, \ldots, \psi^{(K)})$ may not be smooth, which can lead to overfitting and unstable predictions.
+Thus, in this section, we provide a modification of Proposition  \ref{proposition:eigen_noregul} that yields regularized (smoothed) PLS components.
 
@@
 Smaller $\lambda_k$ produces PLS components that fit more closely to the observed data, but selecting too small value may cause overfitting.
-The estimated PLS component reverts back to the unregularized version of Proposition \ref{proposition:generalized_rayleigh_quotient} when $\lambda_k=0$ for all $k$.
+The estimated PLS component reverts back to the unregularized version of Proposition \ref{proposition:eigen_noregul} when $\lambda_k=0$ for all $k$.
 On the other hand, larger $\lambda_k$ places more emphasis on smoothing $\psi^{(k)}$.
@@
 
-	\subsection{Proof of Proposition \ref{proposition:generalized_rayleigh_quotient_linear_system_unregularized}}\label{section:proof:proposition:generalized_rayleigh_quotient_linear_system_unregularized}
+	\subsection{Proof of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:linear_noregul} }\label{section:proof:proposition:linear_noregul_system_unregularized}
 	\begin{comment}
@@
 	%Therefore, the optimization problem 
-	presented in Proposition \ref{proposition:generalized_rayleigh_quotient_linear_system_unregularized} is equivalent to the following constrained optimization problem on the Euclidean space:
+	presented in Proposition \ref{proposition:linear_noregul_system_unregularized} is equivalent to the following constrained optimization problem on the Euclidean space:
 	\begin{align*}
@@
 	\end{equation*}
-	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$.
-This completes the proof of  Proposition \ref{proposition:generalized_rayleigh_quotient_linear_system_unregularized}.
-
-	\subsection{Proof of Propositions \ref{proposition:generalized_rayleigh_quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
+	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$. This completes the proof of  Proposition \ref{proposition:linear_noregul_system_unregularized}.
+
+	\subsection{Proof of Propositions \ref{proposition:eigen_noregul} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
 	%

### 2025-07-15 manuscript/main.tex
proof splits into propositions 1 and 2

@@
 These coefficients are obtained by solving the following generalized eigenvalue problem:
-\begin{align}
+\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
 	\left(
@@
 	\quad \text{subject to} \quad \boldsymbol{\xi}^\top B^\ast \boldsymbol{\xi} = 1,
-	\label{eq: Regularized generalized rayleigh quotient equation}
-\end{align}
+\end{equation}
 where
-$$
+\begin{equation}\label{def:V_matrix}
 V := \frac{1}{n^2} (B^\ast \Theta^\top \mathbf{y})(B^\ast \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
-$$
+\end{equation}
 
@@
 
-	\section{Proofs of Propositions}
-	$\boldsymbol{\cdot}$ \underline{Abbreviations}
-	\begin{itemize}
-		\item[--] ``CSI": Cauchy–Schwarz inequality
-	\end{itemize}
-
-	\subsection{Proof of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:linear_noregul} }\label{section:proof:proposition:linear_noregul_system_unregularized}
+	\section{Proof of Proposition \ref{proposition:eigen_noregul} }\label{section:proof:proposition:linear_noregul_system_unregularized}
 	\begin{comment}
@@
 	\end{comment}
+	\begin{proof}
 	Let $\xi = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta}) \in \mathcal{H}$.
@@
 	\end{align*}	
-	Therefore, problem of maximizing the squared covariance can be written as
-	\begin{comment}
-		\begin{equation*}
-			\widehat{\textnormal{Cov}}^2 (
-			\langle \widetilde{W}, \xi  \rangle_{\mathcal{H}}, Y 
-			) 
-			=
-			\frac{1}{n^2}
-			\bigl \langle
-			(\Theta_1^\top \mathbf{y} , \ldots, \Theta_K^\top \mathbf{y}, Z^\top \mathbf{y}),
-			(\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})
-			\bigr\rangle_B^2.
-		\end{equation*}
-	\end{comment}
-	%Therefore, the optimization problem 
-	presented in Proposition \ref{proposition:linear_noregul_system_unregularized} is equivalent to the following constrained optimization problem on the Euclidean space:
+	Therefore, problem of maximizing the squared covariance  is equivalent to the following constrained optimization problem on the Euclidean space:
 	\begin{align*}
@@
 		\biggr)^2,
+		\numberthis \label{optim:summation_form}
 		\\&~s.t.~	\sum \limits_{j=1}^K 
@@
 	\end{align*} 
-	Let us denote the objective function as
+The objective function matches that of \eqref{eq: Regularized generalized rayleigh quotient equation}, taking the form of a quadratic expression involving the matrix $V$ defined in \eqref{def:V_matrix}:
+\begin{align*}
+	\frac{1}{n^2}
+\biggl(
+\sum \limits_{k=1}^K 
+\mathbf{y}^\top
+\Theta_{j}
+B
+\mathbf{d}_j
++
+\mathbf{y}^\top
+Z \boldsymbol{\zeta} 
+\biggr)^2
+%%%%%%%%%%%%%%%%%%%%
+&=
+\frac{1}{n^2} 
+(
+\mathbf{y}^\top
+\Theta
+B^\ast  
+\boldsymbol{\xi}
+)^2
+\\
+&	= 
+\frac{1}{n^2} 
+\boldsymbol{\xi}^\top
+(B^\ast \Theta^\top \mathbf{y})(B^\ast \Theta^\top \mathbf{y})^\top 
+\boldsymbol{\xi}
+\\&=
+	\boldsymbol{\xi}^\top
+V 
+\boldsymbol{\xi},
+\end{align*}
+and the constraint is identical to that in \eqref{eq: Regularized generalized rayleigh quotient equation}, because we have:
+\begin{equation*}
+		\sum \limits_{j=1}^K 
+	\mathbf{d}_j^\top
+	B
+	\mathbf{d}_j
+	+ \boldsymbol{\zeta}^\top \boldsymbol{\zeta}
+	=
+	\boldsymbol{\xi}^\top B^\ast \boldsymbol{\xi}.
+\end{equation*}
+Therefore, the optimization problem \eqref{optim:summation_form}, which is equivalent to the squared covariance maximization problem, reduces to the generalized eigenvalue problem \eqref{eq: Regularized generalized rayleigh quotient equation}.
+This completes the proof of Proposition~\ref{proposition:eigen_noregul}.
+ \end{proof}
+
+ \section{Proof of Proposition  \ref{proposition:linear_noregul}}
+ \begin{proof}
+	From \eqref{optim:summation_form}, let us denote the objective function as
 	\[
@@
 	\]
-
 	The feasible set is compact, as it corresponds to the boundary of an ellipsoid in a finite-dimensional Euclidean space.
@@
 	\end{equation*}
-	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$. This completes the proof of  Proposition \ref{proposition:linear_noregul_system_unregularized}.
+	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$. This completes the proof of  Proposition \ref{proposition:linear_noregul}.
+	\end{proof}
 

### 2025-07-15 manuscript/main.tex
delete old proof

@@
 
-	\subsection{Proof of Propositions \ref{proposition:eigen_noregul} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
-	%
-	%
-	\begin{align*}
-		\widehat{\textnormal{Cov}} (
-		\langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y 
-		) 
-		&= 
-		\frac{1}{n} \sum \limits_{i=1}^n 
-		y_i
-		\langle \widetilde{\mathbf{W}}_i, \xi \rangle_\mathcal{H} \\
-		&= 
-		\frac{1}{n} 
-		\sum \limits_{i=1}^n
-		y_i
-		\langle \widetilde{X_i}, \psi \rangle_\mathcal{F}  
-		+  
-		\frac{1}{n} 
-		\sum \limits_{i=1}^n  
-		y_i
-		\langle \mathbf{Z}_i, 
-		\boldsymbol{\theta} 
-		\rangle 
-		\\
-		&=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_0^1 X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
-		&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_0^1 \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \left\{ \int_0^1 \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}).
-	\end{align*}
-
-	we first construct the following matrix:
-	\begin{equation}\label{def:V_star}
-		\mathbf{V}^\ast 
-		:= 
-		n^{-2}\begin{bmatrix}
-			\mathbf{J}
-			\widetilde{ \mathbf{C} }^\top \mathbf{y}\mathbf{y}^\top \widetilde{ \mathbf{C} } \mathbf{J} 
-			& 
-			\mathbf{J} \widetilde{ \mathbf{C} }^\top 
-			\mathbf{y}
-			\mathbf{y}^\top 
-			\mathbf{Z} 
-			\\
-			\mathbf{Z}^\top 
-			\mathbf{y}
-			\mathbf{y}^\top \widetilde{ \mathbf{C} }
-			\mathbf{J} 
-			&   
-			\mathbf{Z}^\top 
-			\mathbf{y}
-			\mathbf{y}^\top 
-			\mathbf{Z}
-		\end{bmatrix} = n^{-2} \mathbf{J}^\ast \widetilde{ \mathbf{C} }^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{ \mathbf{C} }^{*} \mathbf{J}^\ast
-		\in \mathbb{R}^{(MK+p) \times (MK+p)}.
-	\end{equation}
-
-	Here, $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y)$ is expressed as $\xi^{*\top} \mathbf{V}^\ast \xi^*$ based on the aforementioned basis approximations.
-Thus, finding $\xi^*$ that maximizes $\xi^{*\top} \mathbf{V}^\ast \xi^*$ amounts to finding $\widehat{\xi}$ that maximizes the sample squared covariance $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y)$, which is the first step of the PLS algorithm.
-The constraint $\xi^{*\top} J^\ast \xi^*=1$ scales the obtained PLS component to have a unit norm, that is, $\langle \widehat{\xi}, \widehat{\xi} \rangle_\mathcal{H}=1$.
-
-	and  $\xi^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$. Then, the $l$-th PLS component, $\widehat{\xi} \equiv \widehat{\xi}_l$ can be obtained by solving
-	\begin{equation}\label{def:eigenproblem_smoothed}
-		\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top} J^\ast \xi^*}, \quad \textit{or equivalently}, \quad \arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} J^\ast \xi^*=1,
-	\end{equation}
-	with respect to $\widehat{\xi}^*=(\widehat{\mathbf{a}}^{\top}, \widehat{\boldsymbol{\theta}}^{\top})^\top$
-
-	We show that the solutions to the generalized eigenvalue problems \eqref{def:eigenproblem_smoothed} and \eqref{eq: Regularized generalized rayleigh quotient equation} maximize the covariance with the response.
-	Based on the basis function expansions  $X_i^{(k)}(t) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t)$ and $\psi^{(k)}(t) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t)$, $k=1, \ldots, K$, we can express the sample covariance between the PLS score and the outcome, which needs to be maximized to estimate the corresponding PLS component, as:
-	\begin{align*}
-		\widehat{\textnormal{Cov}} (\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y ) &= \frac{1}{n} \sum \limits_{i=1}^n \langle \mathbf{W}_i, \xi \rangle_\mathcal{H} Y_i \\
-		&=  \frac{1}{n} \sum \limits_{i=1}^n  \langle X_i, \psi \rangle_\mathcal{F} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n  \langle \mathbf{Z}_i, \boldsymbol{\theta} \rangle Y_i \\
-		&=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_0^1 X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
-		&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_0^1 \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \left\{ \int_0^1 \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
-		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}).
-	\end{align*}
-	This implies that
-	\begin{align*}
-		\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y ) &= n^{-2} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}) (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta})^\top \widetilde{\mathbf{y}} \\
-		&= n^{-2} \{\mathbf{a}^\top J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J \mathbf{a} +  \mathbf{a}^\top J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} +  \boldsymbol{\theta} \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J \mathbf{a} + \boldsymbol{\theta}^\top \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta}\} \\
-		&= \begin{bmatrix}
-			\mathbf{a}^\top & \boldsymbol{\theta}^\top
-		\end{bmatrix}
-		\begin{bmatrix}
-			n^{-2} J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J & n^{-2} J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z}  \\
-			n^{-2} \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J & n^{-2} \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z}
-		\end{bmatrix} 
-		\begin{bmatrix}
-			\mathbf{a} \\ \boldsymbol{\theta}
-		\end{bmatrix} \\
-		&\equiv \xi^{*T} \mathbf{V}^\ast \xi^*.
-	\end{align*}
-	Also, the unit norm constraint of the PLS components in $\mathcal{H}$ can be translated into:
-	\begin{align*}
-		\langle \xi, \xi \rangle_{\mathcal{H}} &= \sum \limits_{k=1}^K \int_{\mathcal{T}} \psi^{(k)}(t_k) \psi^{(k)}(t_k) dt_k + \boldsymbol{\theta}^{\top} \boldsymbol{\theta} \\
-		&= \sum \limits_{k=1}^K  \int_\mathcal{T} \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top   \mathbf{a}^{(k)} dt_k + \boldsymbol{\theta}^{\top} \boldsymbol{\theta} \\
-		&= \sum \limits_{k=1}^K  \mathbf{a}^{(k)\top} J^{(k)}   \mathbf{a}^{(k)} + \boldsymbol{\theta}^{\top} \boldsymbol{\theta} \\
-		&= \mathbf{a}^\top J \mathbf{a} + \boldsymbol{\theta}^{\top} \boldsymbol{\theta} \\
-		&= \xi^{*\top} J^\ast  \xi^{*} \\ 
-		&= 1 \\
-	\end{align*}
-
-	Thus, the first step of the PLS algorithm translates into solving
-	\begin{equation*}
-		\max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} J^\ast \xi^*=1,
-	\end{equation*}
-	or equivalently solving
-	\begin{equation*}
-		\max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top} J^\ast \xi^*},
-	\end{equation*}
-	where $J^\ast = \mathrm{blkdiag}[J, \mathbf{I}_p] \in \mathbb{R}^{MK+p}$.
-In other words, the PLS component is chosen to maximize the squared sample covariance  $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y ) = \xi^{*\top} \mathbf{V}^\ast \xi^*$ subject to the constraint $\xi^{*\top} J^\ast \xi^*=1$.
-
-	% Similar in spirit to the regularized principal component analysis (see equation [9.1] of \citealp{Ramsay2005}), one way to penalize the squared sample covariance $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}, \xi \rangle_{\mathcal{H}}, Y )$ is to divide it by $\{ 1+ \kappa \textnormal{PEN}(\psi) \}$, where $\textnormal{PEN}(\psi)$ is a roughness penalty term.
-This leads to the penalized squared sample covariance
-	% \begin{equation*}
-		%         \frac{\xi^{*T} \mathbf{V}^\ast \xi^*}{\xi^{*T} J^\ast \xi^* + \kappa \textnormal{PEN}(\psi)},
-		% \end{equation*}
-	% whose maximizer corresponds to a smoothed PLS component that maximizes $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)$ over the class of all functions satisfying sufficient smoothness conditions.
-
 	\section{Proof of Proposition \ref{Proposition: property of U}}\label{section:proof:Proposition: property of U}

### 2025-07-15 manuscript/main.tex
ridge type formulation

@@
 
-	\subsubsection{Smoothed estimation of PLS components}\label{sec: pls component computation intermediate}
+	\subsubsection{Main estimation strategy}\label{sec: pls component computation intermediate}
 	Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an intermediate strategy for implementing the first step of the PLS algorithm.
@@
 = 
-(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})
-:= \arg \max_{\xi \in (\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}} \widehat{\textnormal{Cov}}^2 
-\left( 
+(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}})
+:= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
+\| \xi  \|_\mathcal{H} = 1
+ } \widehat{\textnormal{Cov}}^2 
+\bigl(
 \langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
-\right)
+\bigr)
 	\end{equation}
@@
 At the $l$-th iteration of the PLS algorithm, let
-$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\zeta}}^\top )^\top$
+$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}^\top )^\top$
 denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
@@
 	\left(
-	\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\zeta}}^\top
+	\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}^\top
 	\right)^\top
@@
 	\begin{proposition} \label{proposition:linear_noregul}
-	We can compute  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$ in Proposition \ref{proposition:eigen_noregul} as 
+	We can compute  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\xi}}$ in Proposition \ref{proposition:eigen_noregul} as 
 \begin{equation*}
@@
 	%%%%%%%%%%%%%%%%
-	\hat{\boldsymbol{\zeta}}  = \frac{1}{\sqrt{\sum_{j=1}^K 
+	\hat{\boldsymbol{\xi}}  = \frac{1}{\sqrt{\sum_{j=1}^K 
 			\mathbf{y}^\top
@@
 	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
-	Although Proposition \ref{proposition:eigen_noregul} provides an efficient and principled way to compute the PLS components $\xi$, their functional part $\psi=(\psi^{(1)}, \ldots, \psi^{(K)})$ may not be smooth, which can lead to overfitting and unstable predictions.
-Thus, in this section, we provide a modification of Proposition  \ref{proposition:eigen_noregul} that yields regularized (smoothed) PLS components.
-
-	A widely-used approach to smoothing a function $\psi^{(k)}$ is to penalize its roughness that can be quantified by the integrated squared second derivative:
-	\begin{equation}
-		\textnormal{PEN} \left(\psi^{(k)} \right) 
-		=  \int_0^1 \ddot{\psi}^{(k)}(t)^2 dt = \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)},
-		\label{eq: roughness penalty}
-	\end{equation}
-	where the last term is obtained using the basis expansion $\psi^{(k)}(t)=\mathbf{a}^{(k)T}\mathbf{b}^{(k)}(t)$.
-
-	Now, maximizing $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)$ is not the only aim; we also want to prevent the roughness of each $\psi^{(k)}$---that is, $\textnormal{PEN}(\psi^{(k)})$---from being too large.
-One possible way to achieve this is to extend \citet{Rice1991}'s approach of obtaining smoothed functional PCA components, and find $\xi^*$ that maximizes:
+Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions.
+To address this, we propose a regularized extension that balances predictive performance with smoothness.
+Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative $\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt$.
+Instead of solely maximizing the squared empirical covariance
+ $\widehat{\textnormal{Cov}}^2 
+\bigl(
+\langle \widetilde{W}, \xi \rangle_\mathcal{H}, Y 
+\bigr)
+$, 
+we incorporate this roughness penalty to simultaneously control the complexity of the estimated functional components.
+
+One possible approach is to extend smoothed functional PCA \citep{Rice1991} to our optimization problem \eqref{def:maximizer_squared_empirical_cov}, leading to the following formulation:
+	\begin{equation*}
+	\hat{\xi} 
+	= 
+	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}})
+	= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
+		\| \xi  \|_\mathcal{H} = 1
+	} 
+	\biggl\{
+	\widehat{\textnormal{Cov}}^2 
+	\bigl(
+	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
+	\bigr)
+	- \sum \limits_{j=1}^K \lambda_j 
+	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
+	\biggr\}
+	,
+\end{equation*}
+'s approach of obtaining smoothed functional PCA components, and find $\xi^*$ that maximizes:
 	\begin{equation}
@@
 Note that the penalty term can be written concisely using matrices as:
+		\begin{equation}
+		\textnormal{PEN} \left( \hat{\xi}_j \right) 
+		=  \int_0^1 
+		\bigl\{ \hat{\xi}_j^{''}(t) \bigr\}^2 dt = \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)},
+		\label{eq: roughness penalty}
+	\end{equation}
+		where the last term is obtained using the basis expansion $\psi^{(k)}(t)=\mathbf{a}^{(k)T}\mathbf{b}^{(k)}(t)$.
+
 	\begin{equation*}
@@
 	\end{equation*}
-	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$. This completes the proof of  Proposition \ref{proposition:linear_noregul}.
+	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\xi}}$. This completes the proof of  Proposition \ref{proposition:linear_noregul}.
 	\end{proof}

### 2025-07-15 manuscript/main.tex
illustrative example

@@
 	In modern biomedical studies, it is increasingly common to collect heterogeneous data modalities for each subject.
-For instance, the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021} records both multiple renogram curves (functional data) and multiple renogram variables (vector data) per kidney, capturing distinct yet related physiological information.
+As an illustrative example we use the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021}.
+The data records both multiple renogram curves (functional data) and multiple renogram variables (vector data) per kidney, capturing distinct yet related physiological information.
 Such settings call for statistical methods that can jointly model functional and vector-valued covariates to account for both shared and modality-specific variation linked to clinical outcomes.
@@
 \end{equation*}
-'s approach of obtaining smoothed functional PCA components, and find $\xi^*$ that maximizes:
-	\begin{equation}
-		\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right) - \sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right),
-		\label{eq: penalized squred variance}
-	\end{equation}
-	subject to $\xi^{*\top} J^\ast \xi^*=1$.
-The equation \eqref{eq: penalized squred variance} quantifies the trade-off between fidelity to the data (in this case the sample covariance between the $\rho=\langle \mathbf{W}, \xi \rangle_\mathcal{H}$ and $Y$ in the direction of $\xi$) and roughness as measured by the sum of the individual penalty terms in \eqref{eq: roughness penalty}.
-The smoothing parameters $\{\lambda_k\}_{k=1}^K$ control the relative importance between the two objectives.
+where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between covariance maximization and roughness penalization.
+However,   we take an alternative strategy that extends the idea of \citet{Silverman1996}.
+This approach is known to produce appropriately smoothed functional PCA components under milder conditions than the \citet{Rice1991}'s approach by replacing the usual $L^2$-orthonormality constraint with the one that takes account the roughness of functions via the modified inner product.
+Specifically, the following proposition provides a generalized Rayleigh quotient problem which modifies the $\mathcal{H}$-orthonormality constraint of the hybrid PLS components to incorporate roughness penalty, and thus whose solution corresponds to a smoothed PLS component maximizing $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)$ over the class of all functions satisfying sufficient smoothness.
+	\begin{proposition} \label{Proposition: Regularized generalized rayleigh quotient}
+		At each $l$-th iteration of the first step of the PLS algorithm involving the residualized response and predictors $Y_i \equiv Y_i^{[l]}$ and $\mathbf{W}_i \equiv \mathbf{W}_i^{[l]}$, consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
+Recall from \eqref{def:V_star} that  $V^\ast$ is defined as
+		\begin{equation*}
+			\mathbf{V}^\ast = n^{-2}\begin{bmatrix}
+				J \widetilde{C}^\top \mathbf{y}\mathbf{y}^\top \widetilde{C} J & J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z} \\
+				\mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J &   \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z}
+			\end{bmatrix} = n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast
+			\in \mathbb{R}^{(MK+p) \times (MK+p)}.
+		\end{equation*}
+		and  $\xi^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$.
+Then, the $l$-th smoothed PLS component, $\widehat{\xi} \equiv \widehat{\xi}_l$ can be obtained in the following way.
+		We first compute the basis coefficients by solving the optimization problem
 		Note that the penalty term can be written concisely using matrices as:
@@
 
-	In this paper, we take an alternative strategy that extends the idea of \citet{Silverman1996}.
-This approach is known to produce appropriately smoothed functional PCA components under milder conditions than the \citet{Rice1991}'s approach by replacing the usual $L^2$-orthonormality constraint with the one that takes account the roughness of functions via the modified inner product.
-Specifically, the following proposition provides a generalized Rayleigh quotient problem which modifies the $\mathcal{H}$-orthonormality constraint of the hybrid PLS components to incorporate roughness penalty, and thus whose solution corresponds to a smoothed PLS component maximizing $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)$ over the class of all functions satisfying sufficient smoothness.
-	\begin{proposition} \label{Proposition: Regularized generalized rayleigh quotient}
-		At each $l$-th iteration of the first step of the PLS algorithm involving the residualized response and predictors $Y_i \equiv Y_i^{[l]}$ and $\mathbf{W}_i \equiv \mathbf{W}_i^{[l]}$, consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
-Recall from \eqref{def:V_star} that  $V^\ast$ is defined as
-		\begin{equation*}
-			\mathbf{V}^\ast = n^{-2}\begin{bmatrix}
-				J \widetilde{C}^\top \mathbf{y}\mathbf{y}^\top \widetilde{C} J & J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z} \\
-				\mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J &   \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z}
-			\end{bmatrix} = n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast
-			\in \mathbb{R}^{(MK+p) \times (MK+p)}.
-		\end{equation*}
-		and  $\xi^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$.
-Then, the $l$-th smoothed PLS component, $\widehat{\xi} \equiv \widehat{\xi}_l$ can be obtained in the following way.
-		We first compute the basis coefficients by solving the optimization problem
 		\begin{align}

### 2025-07-15 manuscript/main.tex
right before the proposition 3

@@
 \end{equation*}
-where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between covariance maximization and roughness penalization.
-However,   we take an alternative strategy that extends the idea of \citet{Silverman1996}.
-This approach is known to produce appropriately smoothed functional PCA components under milder conditions than the \citet{Rice1991}'s approach by replacing the usual $L^2$-orthonormality constraint with the one that takes account the roughness of functions via the modified inner product.
-Specifically, the following proposition provides a generalized Rayleigh quotient problem which modifies the $\mathcal{H}$-orthonormality constraint of the hybrid PLS components to incorporate roughness penalty, and thus whose solution corresponds to a smoothed PLS component maximizing $\widehat{\textnormal{Cov}}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)$ over the class of all functions satisfying sufficient smoothness.
+where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness.
+However, the above approach assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense.
+As an alternative, we adopt the strategy of \citet{Silverman1996}, which works under weaker conditions than those required by \citet{Rice1991}.
+This is achieved by replacing the standard orthonormality constraint with one based on a modified inner product that accounts for roughness.
+Building on this idea, the following proposition reformulates the hybrid PLS problem as a generalized Rayleigh quotient, yielding a smoothed PLS direction that maximizes the squared covariance over a class of smooth functions.
+
 	\begin{proposition} \label{Proposition: Regularized generalized rayleigh quotient}

### 2025-07-15 manuscript/main.tex
twice differentiable basis

@@
 	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
-	Given a basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
+	Given a twice-differentiable basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
 	\begin{equation*}
@@
 defined as follows.
-Let $B \in \mathbb{R}^{M \times M}$ denote the Gram matrix of the basis functions, with entries  
+Let 
+$B, B^{''} \in \mathbb{R}^{M \times M}$
+denote the Gram matrices of the basis functions and their second derivatives, respectively, with entries  
+\begin{equation}
+\end{equation}
 \[

### 2025-07-15 manuscript/main.tex
improved writing on 4.1.1 truncation

@@
 	where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
-Since functional predictors are observed at finitely many discrete time points, we approximate them by truncating the expansion at $M$ terms, yielding a finite-dimensional projection.
-A moderately large $M$ (e.g., 15 or 20) suffices to capture rich functional variation, and no fine-tuning is needed, as our method controlls smoothness  via penalization (Section~\ref{sec: Regularization of PLS Components}).
+Since functional predictors are observed at finitely many discrete time points in practice,
+we use finite-dimensional projections obtained by the expansion truncating at $M$ terms.
+We choose a moderately large value of $M$ (e.g., 15 or 20) to capture rich functional variation without requiring fine-tuning, as our method promotes smoothness through penalization (see Section~\ref{sec: Regularization of PLS Components}).
 We denote the truncated space by
@@
 \begin{equation}\label{def:problem_instance}
-	(B^\ast, \Theta, \mathbf{y}),
+	(\mathbb{B}, \Theta, \mathbf{y})
+	\in
+	,
 \end{equation}
 defined as follows.
-Let 
-$B, B^{''} \in \mathbb{R}^{M \times M}$
-denote the Gram matrices of the basis functions and their second derivatives, respectively, with entries  
+Let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, respectively, with entries  
 \begin{equation}
-\end{equation}
+	B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt,
+	\quad
+	B^{\prime\prime}_{m, m'} := \int_0^1 b^{\prime\prime}_m(t)\, b^{\prime\prime}_{m'}(t)\, dt,
+\end{equation}
+for $m, m' = 1, \ldots, M$.
+
+Define the $(MK + p) \times (MK + p)$ block-diagonal matrices
 \[
-B_{m, m'} := \langle b_m, b_{m'} \rangle = \int_0^1 b_m(t)\, b_{m'}(t)\, dt,
+\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p)
+\quad \text{and} \quad
+\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
 \]
-for $m, m' = 1, \ldots, M$.
-Then define $B^\ast := \operatorname{blkdiag}(B, \ldots, B, I_p) \in \mathbb{R}^{(MK + p) \times (MK + p)}$,  
-$\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}$,  
-and $\mathbf{y} := (y_1, \ldots, y_n)^\top$.
+and let $\Theta := (\Theta_1, \ldots, \Theta_K, Z)$ denote the combined design matrix. Finally, let $\mathbf{y} := (y_1, \ldots, y_n)^\top$ denote the observed response vector.
+
 	\begin{remark}
 While it is possible to use a different basis for each functional predictor, we adopt a common basis for all predictors to simplify the notation.
-However, the definition of $B^\ast$ remains general enough to accommodate different bases across the $K$ predictors.
+However, the definition of $\mathbb{B}$ remains general enough to accommodate different bases across the $K$ predictors.
 \end{remark}
@@
 $
-(B^\ast, \Theta, \mathbf{y})
+(\mathbb{B}, \Theta, \mathbf{y})
 $
@@
 	\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
-	\quad \text{subject to} \quad \boldsymbol{\xi}^\top B^\ast \boldsymbol{\xi} = 1,
+	\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
 \end{equation}
@@
 \begin{equation}\label{def:V_matrix}
-V := \frac{1}{n^2} (B^\ast \Theta^\top \mathbf{y})(B^\ast \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
+V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
 \end{equation}
@@
 		\begin{equation*}
-			\widehat{\xi}[\mathbf{t}] = [\widehat{\psi}(\mathbf{t})^\top, \widehat{\boldsymbol{\theta}}^\top]^\top =  B^\ast[\mathbf{t}]^\top \widehat{\xi}^\ast.   
+			\widehat{\xi}[\mathbf{t}] = [\widehat{\psi}(\mathbf{t})^\top, \widehat{\boldsymbol{\theta}}^\top]^\top =  \mathbb{B}[\mathbf{t}]^\top \widehat{\xi}^\ast.   
 		\end{equation*}
@@
 \Theta
-B^\ast  
+\mathbb{B}  
 \boldsymbol{\xi}
@@
 \boldsymbol{\xi}^\top
-(B^\ast \Theta^\top \mathbf{y})(B^\ast \Theta^\top \mathbf{y})^\top 
+(\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top 
 \boldsymbol{\xi}
@@
 	=
-	\boldsymbol{\xi}^\top B^\ast \boldsymbol{\xi}.
+	\boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi}.
 \end{equation*}

### 2025-07-15 manuscript/main.tex
new notation for block diagonal gram

@@
 	\end{equation}
-
 The observations in the hybrid PLS problem can be compactly represented by the tuple
@@
 defined as follows.
-Let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, respectively, with entries  
+First, let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, respectively, with entries  
 \begin{equation}
@@
 for $m, m' = 1, \ldots, M$.
-
-Define the $(MK + p) \times (MK + p)$ block-diagonal matrices
+Leveraging these notations, 
+we define the $(MK + p) \times (MK + p)$ block-diagonal matrices
 \[
@@
 \]
-and let $\Theta := (\Theta_1, \ldots, \Theta_K, Z)$ denote the combined design matrix. Finally, let $\mathbf{y} := (y_1, \ldots, y_n)^\top$ denote the observed response vector.
+We denote $\Theta := (\Theta_1, \ldots, \Theta_K, Z)
+\in
+\mathbb{R}^{n \times (MK+p)}
+$ , and let $\mathbf{y} := (y_1, \ldots, y_n)^\top$ denote the observed response vector.
 
 	\begin{remark}
-While it is possible to use a different basis for each functional predictor, we adopt a common basis for all predictors to simplify the notation.
-However, the definition of $\mathbb{B}$ remains general enough to accommodate different bases across the $K$ predictors.
+While it is possible to use a different basis for each functional predictor, we adopt a common basis for all predictors to simplify the notation. However, the definition of 
+$\mathbb{B}$
+and
+$\mathbb{B}^{\prime \prime}$
+ remains general enough to accommodate different bases across the $K$ predictors.
 \end{remark}

### 2025-07-15 manuscript/main.tex
scalar part has subscript K+1

@@
 \begin{equation}\label{def:problem_instance}
-	(\mathbb{B}, \Theta, \mathbf{y})
+	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
 	\in
+	\mathbb{R}^{(MK+p) \times (MK+p)}
+	\times 
+	\mathbb{R}^{(MK+p) \times (MK+p)}
+	\times
+	\mathbb{R}^{n \times (MK+p)}
+	\times
+	\mathbb{R}^{n}
 	,
@@
 = 
-(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}})
+(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})
 := \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
@@
 $
-(\mathbb{B}, \Theta, \mathbf{y})
+	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
 $
@@
 At the $l$-th iteration of the PLS algorithm, let
-$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}^\top )^\top$
+$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
 denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
@@
 	\left(
-	\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}^\top
+	\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
 	\right)^\top
@@
 	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
-Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions.
+Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions.
 To address this, we propose a regularized extension that balances predictive performance with smoothness.
@@
 	= 
-	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}})
+	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})
 	= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
@@
 \end{equation*}
-where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness.
+where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness. Here, the penalization term can be written in matrix form as:
+		\begin{align*}
+	\sum \limits_{k=1}^K 
+	\lambda_k 
+	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
+&=
+	\sum \limits_{k=1}^K 
+\lambda_k 
+\int_0^1 \bigl\{ \sum_{l=1}^M \theta_{ijl} \, b_l^{\prime \prime}(t) \bigr\}^2 dt
+\\&	 =
+%%%%%%%%%%%%%%%%%%%
+	\sum \limits_{k=1}^K 
+\lambda_k 
+\sum_{l=1}^M
+\sum_{m=1}^M
+\theta_{ijl} \theta_{ijm}
+\int_0^1
+ \, b_l^{\prime \prime}(t) 
+  b_m^{\prime \prime}(t)
+  dt
+\\&	 =
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	  \sum \limits_{k=1}^K \lambda_k \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)} = \xi^{* \top} \Lambda \ddot{J}^\ast \xi^*,
+\end{align*}
 However, the above approach assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense.
@@
 Building on this idea, the following proposition reformulates the hybrid PLS problem as a generalized Rayleigh quotient, yielding a smoothed PLS direction that maximizes the squared covariance over a class of smooth functions.
+
+\begin{proposition}\label{proposition:eigen_noregul}
+	Let
+	$
+	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
+	$
+	denote the observed data defined in \eqref{def:problem_instance}.
+	At the $l$-th iteration of the PLS algorithm, let
+	$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
+	denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
+	which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
+	These coefficients are obtained by solving the following generalized eigenvalue problem:
+	\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
+		\left(
+		\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
+		\right)^\top
+		=
+		\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
+		\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
+	\end{equation}
+	where
+	\begin{equation}\label{def:V_matrix}
+		V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
+	\end{equation}
+
+\end{proposition}
 
@@
 
-		\begin{equation*}
-			\sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right) = \sum \limits_{k=1}^K \lambda_k \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)} = \xi^{* \top} \Lambda \ddot{J}^\ast \xi^*,
-		\end{equation*}
 		where $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is defined as

### 2025-07-15 manuscript/main.tex
d to gamma

@@
 \subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
-	Given a twice-differentiable basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
-	\begin{equation*}
-		X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t), \quad 
-		\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t),
-	\end{equation*}
+Given a twice-differentiable basis $\{b_l(t)\}$ of $L^2([0,1])$,
+the functional predictors,
+the corresponding regression coefficients,
+and PLS component direction
+ can be decomposed into
+	\begin{equation*}
+		X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t),~
+		\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t), j=1, \ldots, K,~
+		%%%%%%%%%%%%%%%%%%%%%%
+		\xi 
+		=
+		\sum_{l=1}^\infty 
+		b_l(t)
+	\end{equation*}
+	At the $l$-th iteration of the PLS algorithm, let
+	\begin{equation}
+		( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top
+	\end{equation}
+
 	where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
@@
 we define the $(MK + p) \times (MK + p)$ block-diagonal matrices
-\[
+\begin{equation}\label{def:gram_block}
 \mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p)
@@
 \mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
-\]
+\end{equation}
 We denote $\Theta := (\Theta_1, \ldots, \Theta_K, Z)
@@
 At the $l$-th iteration of the PLS algorithm, let
-$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
+\begin{equation}
+( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top
+\end{equation}
+
 denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
@@
 	\left(
-	\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
+	\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
 	\right)^\top
@@
 	\begin{proposition} \label{proposition:linear_noregul}
-	We can compute  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\xi}}$ in Proposition \ref{proposition:eigen_noregul} as 
-\begin{equation*}
-	\hat{\mathbf{d}}_j  = \frac{1}{\sqrt{\sum_{j=1}^K 
+	We can compute  $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ and $\hat{\boldsymbol{\xi}}$ in Proposition \ref{proposition:eigen_noregul} as 
+\begin{equation*}
+	\hat{\boldsymbol{\gamma}}_j  = \frac{1}{\sqrt{\sum_{j=1}^K 
 			\mathbf{y}^\top
@@
 		\begin{align*}
-	\sum \limits_{k=1}^K 
-	\lambda_k 
+	\sum \limits_{j=1}^K 
+	\lambda_j
 	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
 &=
-	\sum \limits_{k=1}^K 
-\lambda_k 
+	\sum \limits_{j=1}^K 
+\lambda_j
 \int_0^1 \bigl\{ \sum_{l=1}^M \theta_{ijl} \, b_l^{\prime \prime}(t) \bigr\}^2 dt
@@
 %%%%%%%%%%%%%%%%%%%
-	\sum \limits_{k=1}^K 
-\lambda_k 
+	\sum \limits_{j=1}^K 
+\lambda_j
 \sum_{l=1}^M
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	  \sum \limits_{k=1}^K \lambda_k \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)} = \xi^{* \top} \Lambda \ddot{J}^\ast \xi^*,
+\sum \limits_{j=1}^K
+\lambda_j
+\boldsymbol{\gamma}_j^\top
+B^{\prime \prime} 
+\boldsymbol{\gamma}_j
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&= 
+\boldsymbol{\xi}^{\top} \Lambda \mathbb{B}^{\prime \prime} \boldsymbol{\xi},
 \end{align*}
+where we recall that $\mathbb{B}^{\prime \prime} $ is defined in \eqref{def:gram_block}, 
+	where $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is defined as
+\begin{equation}\label{def:Lambda}
+	\Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
+\end{equation}
+$0_{p \times p}$ denotes a $p \times p$ matrix with all elements equal to zero.
+
 However, the above approach assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense.
@@
 	At the $l$-th iteration of the PLS algorithm, let
-	$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
+	$( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
 	denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
@@
 		\left(
-		\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
+		\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
 		\right)^\top
@@
 
-		where $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is defined as
-		\begin{equation}\label{def:Lambda}
-			\Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
-		\end{equation}
-		$0_{p \times p}$ denotes a $p \times p$ matrix with all elements equal to zero.
-
 		\begin{align}
@@
 	As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$.
-Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \mathbf{d}^{(k)\top} \mathbf{b}^{(k)}(t_k)$, where $\mathbf{d}^{(k)} = (d_1^{(k)}, \ldots, d_M^{(k)})\top \in \mathbb{R}^M$ are basis coefficients.
+Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \boldsymbol{\gamma}^{(k)\top} \mathbf{b}^{(k)}(t_k)$, where $\boldsymbol{\gamma}^{(k)} = (d_1^{(k)}, \ldots, d_M^{(k)})\top \in \mathbb{R}^M$ are basis coefficients.
 Here, a different basis system can be flexibly chosen to expand the regression coefficient, but without loss of generality we use the same system as in Section \ref{subsec: Step 1: Computing Smoothed PLS components}.
-With the $(MK+p)$-dimensional row vector $\mathbf{d}^* = (\mathbf{d}^{(1)\top}, \ldots, \mathbf{d}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as: $\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \mathbf{d}^* B^*[\mathbf{t}]$.
+With the $(MK+p)$-dimensional row vector $\boldsymbol{\gamma}^* = (\boldsymbol{\gamma}^{(1)\top}, \ldots, \boldsymbol{\gamma}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as: $\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}]$.
 Finally, these basis expansions of the hybrid response and the regression coefficient enable us to re-write the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model} in a finite-dimensional form:
 	\begin{equation}
-		\widetilde{C}^* B^*[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \mathbf{d}^* B^*[\mathbf{t}] + \mathbf{e}[\mathbf{t}].
+		\widetilde{C}^* B^*[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] + \mathbf{e}[\mathbf{t}].
 		\label{eq: rewritten hybrid on scalar regression model}
@@
 		\begin{aligned}
-			\textnormal{SSE}(\delta) &= \int_\mathcal{T} \left\Vert \,  \widetilde{C}^* B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}} \, \mathbf{d}^* B^*[\mathbf{t}] \, \right\Vert_F^2 \, d\mathbf{t}  \\
-			&= tr\left(\widetilde{C}^{*T}\widetilde{C}^*J^\ast \right) - 2\,tr \left(\mathbf{d}^* J^\ast \widetilde{C}^{*T} \widehat{\boldsymbol{\rho}} \right) + tr\left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \mathbf{d}^* J^\ast \mathbf{d}^{*T}\right),
+			\textnormal{SSE}(\delta) &= \int_\mathcal{T} \left\Vert \,  \widetilde{C}^* B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] \, \right\Vert_F^2 \, d\mathbf{t}  \\
+			&= tr\left(\widetilde{C}^{*T}\widetilde{C}^*J^\ast \right) - 2\,tr \left(\boldsymbol{\gamma}^* J^\ast \widetilde{C}^{*T} \widehat{\boldsymbol{\rho}} \right) + tr\left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* J^\ast \boldsymbol{\gamma}^{*T}\right),
 		\end{aligned}
@@
 	where $tr$ denotes the trace of a matrix, and $\Vert \cdot \Vert_F$ is a Frobenius norm.
-Now taking the derivative of \eqref{eq: least squares} with respect to $\mathbf{d}^*$ and setting the result to zero, we find that  $\mathbf{d}^*$ satisfies the system of linear equations
-	\begin{equation*}
-		\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \mathbf{d}^*  J^\ast =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast,
-	\end{equation*}
-	whose solutions lead to the following estimates of $\mathbf{d}^*$ and $\boldsymbol{\delta}[\mathbf{t}]$:
-	\begin{equation*}
-		\widehat{\mathbf{d}}^*  =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast \left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} J^\ast \right)^{-1} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}[\mathbf{t}] = B^*[\mathbf{t}]^\top \, \widehat{\mathbf{d}}^{*\top}.
+Now taking the derivative of \eqref{eq: least squares} with respect to $\boldsymbol{\gamma}^*$ and setting the result to zero, we find that  $\boldsymbol{\gamma}^*$ satisfies the system of linear equations
+	\begin{equation*}
+		\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^*  J^\ast =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast,
+	\end{equation*}
+	whose solutions lead to the following estimates of $\boldsymbol{\gamma}^*$ and $\boldsymbol{\delta}[\mathbf{t}]$:
+	\begin{equation*}
+		\widehat{\boldsymbol{\gamma}}^*  =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast \left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} J^\ast \right)^{-1} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}[\mathbf{t}] = B^*[\mathbf{t}]^\top \, \widehat{\boldsymbol{\gamma}}^{*\top}.
 	\end{equation*}
@@
 			Let $B \in \mathbb{R}^{M \times M}$ be a symmetric positive semi-definite matrix. 
-			For any two tuples $u = (\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})$ and $v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$ in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$, define the bilinear form
+			For any two tuples $u = (\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K, \boldsymbol{\zeta})$ and $v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$ in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$, define the bilinear form
 			\[
-			\langle u, v \rangle_{B} := \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega}.
+			\langle u, v \rangle_{B} := \sum_{j=1}^K \boldsymbol{\gamma}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega}.
 			\]
@@
 	\end{equation*}
-	with coefficient vectors $\mathbf{d}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$.
+	with coefficient vectors $\boldsymbol{\gamma}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$.
 	Then, the squared norm of $\xi$ in the hybrid Hilbert space $\mathcal{H}$ 
@@
 		\sum \limits_{j=1}^K 
-		\mathbf{d}_j^\top
+		\boldsymbol{\gamma}_j^\top
 		B
-		\mathbf{d}_j
+		\boldsymbol{\gamma}_j
 		+
@@
 		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		%\\&=\bigl \langle(\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta}),(\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})\bigr\rangle_B.
+		%\\&=\bigl \langle(\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K, \boldsymbol{\zeta}),(\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K, \boldsymbol{\zeta})\bigr\rangle_B.
 	\end{align*}
@@
 		B
-		\mathbf{d}_j
+		\boldsymbol{\gamma}_j
 		)  
@@
 		B
-		\mathbf{d}_j
+		\boldsymbol{\gamma}_j
 		+
@@
 		%(\Theta_1^\top \mathbf{y} , \ldots, \Theta_K^\top %\mathbf{y}, Z^\top \mathbf{y}),
-		%(\mathbf{d}_1, \ldots, \mathbf{d}_K, %\boldsymbol{\zeta})
+		%(\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K, %\boldsymbol{\zeta})
 		%\bigr\rangle_B.
@@
 	\begin{align*}
-		\max_{\mathbf{d}_1, \ldots, \mathbf{d}_K \in \mathbb{R}^M,
+		\max_{\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K \in \mathbb{R}^M,
 			\boldsymbol{\zeta} \in \mathbb{R}^p
@@
 		\\&~s.t.~	\sum \limits_{j=1}^K 
-		\mathbf{d}_j^\top
+		\boldsymbol{\gamma}_j^\top
 		B
-		\mathbf{d}_j
+		\boldsymbol{\gamma}_j
 		+
@@
 B
-\mathbf{d}_j
+\boldsymbol{\gamma}_j
 +
@@
 		\sum \limits_{j=1}^K 
-	\mathbf{d}_j^\top
+	\boldsymbol{\gamma}_j^\top
 	B
-	\mathbf{d}_j
+	\boldsymbol{\gamma}_j
 	+ \boldsymbol{\zeta}^\top \boldsymbol{\zeta}
@@
 	\[
-	f(\{\mathbf{d}_j\}, \boldsymbol{\zeta}) := 
+	f(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\zeta}) := 
 	\frac{1}{n^2}
 	\left(
-	\sum_{j=1}^K \mathbf{y}^\top \Theta_j B \mathbf{d}_j + \mathbf{y}^\top Z \boldsymbol{\zeta}
+	\sum_{j=1}^K \mathbf{y}^\top \Theta_j B \boldsymbol{\gamma}_j + \mathbf{y}^\top Z \boldsymbol{\zeta}
 	\right)^2,
@@
 	\[
-	g(\{\mathbf{d}_j\}, \boldsymbol{\zeta}) := \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{d}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta} - 1 = 0.
+	g(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\zeta}) := \sum_{j=1}^K \boldsymbol{\gamma}_j^\top B \boldsymbol{\gamma}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta} - 1 = 0.
 	\]
@@
 	\[
-	\mathcal{L}(\{\mathbf{d}_j\}, \boldsymbol{\zeta}, \lambda) 
+	\mathcal{L}(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\zeta}, \lambda) 
 	:= 
-	f(\{\mathbf{d}_j\}, \boldsymbol{\zeta}) - \lambda g(\{\mathbf{d}_j\}, \boldsymbol{\zeta}).
+	f(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\zeta}) - \lambda g(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\zeta}).
 	\]
@@
 	\begin{align*}
-		\nabla_{\mathbf{d}_j} \mathcal{L} &= 
+		\nabla_{\boldsymbol{\gamma}_j} \mathcal{L} &= 
 		\frac{2}{n^2} 
 		\left(
-		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
+		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
 		\right)
 		B \Theta_j^\top \mathbf{y}
-		- 2\lambda B \mathbf{d}_j = 0, \quad \forall j, 
+		- 2\lambda B \boldsymbol{\gamma}_j = 0, \quad \forall j, 
 		\numberthis \label{lag_grad_d}
@@
 		\left(
-		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
+		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
 		\right)
@@
 	\end{align*}
-	By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$ and observing that the scalar quantity $n^{-2}\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$ appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the gradient conditions together imply that any local optimum must be  scalar multiples of
+	By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$ and observing that the scalar quantity $n^{-2}\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$ appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the gradient conditions together imply that any local optimum must be  scalar multiples of
 	$
@@
 	\begin{equation*}
-		\mathbf{d}_j^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
+		\boldsymbol{\gamma}_j^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
 				\mathbf{y}^\top
@@
 	\end{equation*}
-	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\xi}}$. This completes the proof of  Proposition \ref{proposition:linear_noregul}.
+	which are the same as  $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ and $\hat{\boldsymbol{\xi}}$. This completes the proof of  Proposition \ref{proposition:linear_noregul}.
 	\end{proof}
@@
 	\begin{align*}
-		\widetilde{C}^{*[l]}B^*[\mathbf{t}] &=\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1}\widehat{\mathbf{d}}^*_{l-1}B^*[\mathbf{t}] \\
+		\widetilde{C}^{*[l]}B^*[\mathbf{t}] &=\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1}\widehat{\boldsymbol{\gamma}}^*_{l-1}B^*[\mathbf{t}] \\
 		&= \widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} J^\ast \left(\widehat{\boldsymbol{\rho}}_{i,l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1} J^\ast \right)^{-1} B^*[\mathbf{t}] \\
@@
 		\begin{aligned}
-			\widetilde{C}^{*[l]}B^*[\mathbf{t}] &=\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1}\widehat{\mathbf{d}}^*_{l-1}B^*[\mathbf{t}] \\
+			\widetilde{C}^{*[l]}B^*[\mathbf{t}] &=\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1}\widehat{\boldsymbol{\gamma}}^*_{l-1}B^*[\mathbf{t}] \\
 			&= \widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} J^\ast \left(\widehat{\boldsymbol{\rho}}_{i,l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1} J^\ast \right)^{-1} B^*[\mathbf{t}] \\

### 2025-07-16 manuscript/main.tex
basis notation revised

@@
 \subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
-Given a twice-differentiable basis $\{b_l(t)\}$ of $L^2([0,1])$,
-the functional predictors,
-the corresponding regression coefficients,
-and PLS component direction
- can be decomposed into
-	\begin{equation*}
-		X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t),~
-		\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t), j=1, \ldots, K,~
+Given a twice-differentiable basis $\{b_m(t)\}$ of $L^2([0,1])$,  the $j$th functional predictor, regression coefficient, and PLS direction (suppressing iteration indices) are represented as
+	\begin{equation*}
+		X_{ij}(t) = \sum_{m=1}^\infty \theta_{ijm} \, b_m(t),\quad
+		\beta_j(t) = \sum_{m=1}^\infty \eta_{jm} \, b_m(t),\quad
 		%%%%%%%%%%%%%%%%%%%%%%
-		\xi 
+		\xi_j(t)
 		=
-		\sum_{l=1}^\infty 
-		b_l(t)
-	\end{equation*}
-	At the $l$-th iteration of the PLS algorithm, let
+		\sum_{m=1}^\infty
+		\gamma_{jm}
+		b_m(t)
+	\end{equation*}	
+In practice, the full set of coefficients can not be obtained, as functional data are measured on a finite grid. Thus, we truncate the expansion at $M$ terms and define the truncated basis space
 \begin{equation}
-		( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top
-	\end{equation}
-
-	where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
-Since functional predictors are observed at finitely many discrete time points in practice,
-we use finite-dimensional projections obtained by the expansion truncating at $M$ terms.
-We choose a moderately large value of $M$ (e.g., 15 or 20) to capture rich functional variation without requiring fine-tuning, as our method promotes smoothness through penalization (see Section~\ref{sec: Regularization of PLS Components}).
-We denote the truncated space by
-	\begin{equation}
-		\mathcal{B} := \operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr).
-	\end{equation}
-	 We denote the  predictors projected onto $\mathcal{B}$ and the resulting coefficients as
-	\begin{equation*}
-		\widetilde{X}_{ij}(t) = \sum_{l=1}^M \theta_{ijl} \, b_l(t), \quad 
-		\tilde{\beta}_j(t) = \sum_{l=1}^M \eta_{0,jl} \, b_l(t).
-	\end{equation*}
-	The $i$th  hybrid predictor with projected functional parts, is a tuple, denoted as
+	\mathcal{B} := \operatorname{span}\bigl(b_1(t), \ldots, b_M(t)\bigr).
+\end{equation}
+We choose a moderately large $M$ (e.g., 15 or 20) to capture functional variation without fine-tuning, as smoothness is handled via penalization (see Section~\ref{sec: Regularization of PLS Components}).
+
+	The truncated expansions of the predictor and coefficient are denoted as
+	\begin{equation*}
+		\widetilde{X}_{ij}(t) := \sum_{m=1}^M \theta_{ijm} \, b_m(t), \quad
+		\tilde{\beta}_j(t) := \sum_{m=1}^M \eta_{jm} \, b_m(t),
+	\end{equation*}
+	and our suggest method restricts each PLS direction to admit the following expansion:
+	\begin{equation*}
+		\xi_j(t) = \sum_{m=1}^M \gamma_{jm} \, b_m(t).
+	\end{equation*}
+The $i$th hybrid predictor, with its functional parts projected onto the $\mathcal{B}$, is represented by the tuple
 	\begin{equation*}
@@
 		(
-		X_{i1}, \ldots, X_{iK}, \boldsymbol{Z}_i
+		\widetilde{X}_{i1}, \ldots, \widetilde{X}_{iK}, \boldsymbol{Z}_i
 		).
 	\end{equation*}
-	We adopt the following notation for the coefficients:
+Let $\boldsymbol{\theta}_{ij}$, $\boldsymbol{\eta}_j$, and $\boldsymbol{\gamma}_j$ denote the $M$-dimensional vectors of coefficients:
 	\begin{equation}
-		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top \in \mathbb{R}^M,
+		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top,
 		\quad
-		\boldsymbol{\eta}_{0j} := (\eta_{0,j1}, \ldots, \eta_{0,jM})^\top  \in \mathbb{R}^M,
-	\end{equation}
-	and
+		\boldsymbol{\eta}_{j} := (\eta_{j1}, \ldots, \eta_{jM})^\top ,
+			\boldsymbol{\gamma}_{j} := (\gamma_{j1}, \ldots, \gamma_{jM})^\top.
+	\end{equation}
+For the predictors, we stack the coefficient vectors across observations into the matrix
 	\begin{equation}
@@
 	\end{equation}
-The observations in the hybrid PLS problem can be compactly represented by the tuple
+The full data for the hybrid PLS problem can be represented by the tuple
 \begin{equation}\label{def:problem_instance}
-	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
-	\in
-	\mathbb{R}^{(MK+p) \times (MK+p)}
-	\times 
-	\mathbb{R}^{(MK+p) \times (MK+p)}
-	\times
-	\mathbb{R}^{n \times (MK+p)}
-	\times
-	\mathbb{R}^{n}
-	,
-\end{equation}
-defined as follows.
-First, let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, respectively, with entries  
+	(\mathbb{B}, \mathbb{B}^{\prime\prime}, \Theta, \mathbf{y}) \in 
+	\mathbb{R}^{(MK+p) \times (MK+p)} \times 
+	\mathbb{R}^{(MK+p) \times (MK+p)} \times 
+	\mathbb{R}^{n \times (MK+p)} \times 
+	\mathbb{R}^n,
+\end{equation}
+where $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ are the Gram matrices of the basis functions and their second derivatives, with entries
 \begin{equation}
-	B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt,
-	\quad
-	B^{\prime\prime}_{m, m'} := \int_0^1 b^{\prime\prime}_m(t)\, b^{\prime\prime}_{m'}(t)\, dt,
-\end{equation}
-for $m, m' = 1, \ldots, M$.
-Leveraging these notations, 
-we define the $(MK + p) \times (MK + p)$ block-diagonal matrices
+	B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt, \quad
+	B^{\prime\prime}_{m, m'} := \int_0^1 b_m''(t)\, b_{m'}''(t)\, dt,
+\end{equation}
+for $m, m' = 1, \ldots, M$. We then define the block-diagonal matrices
 \begin{equation}\label{def:gram_block}
-\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p)
-\quad \text{and} \quad
+	\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p), \quad
 	\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
 \end{equation}
-We denote $\Theta := (\Theta_1, \ldots, \Theta_K, Z)
-\in
-\mathbb{R}^{n \times (MK+p)}
-$ , and let $\mathbf{y} := (y_1, \ldots, y_n)^\top$ denote the observed response vector.
+the full design matrix $\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}$, and the response vector $\mathbf{y} := (y_1, \ldots, y_n)^\top$.
 
 \begin{remark}
-While it is possible to use a different basis for each functional predictor, we adopt a common basis for all predictors to simplify the notation. However, the definition of 
-$\mathbb{B}$
-and
-$\mathbb{B}^{\prime \prime}$
- remains general enough to accommodate different bases across the $K$ predictors.
+	While different bases could be used for each functional predictor, we adopt a common basis for simplicity.
+The definitions of $\mathbb{B}$ and $\mathbb{B}^{\prime\prime}$ remain general enough to accommodate distinct bases if needed.
 \end{remark}

### 2025-07-16 manuscript/main.tex
proposition 1 and to revised

@@
 	\subsection{Step 1: Computing smoothed PLS components}  \label{subsec: Step 1: Computing Smoothed PLS components}
-	The function part $\psi$ of the hybrid PLS component $\xi$ is inherently infinite-dimensional, rendering its estimation impossible with finite sample size.
-As such, we first approximate each functional predictor (observed version when $l=1$, or residualized version when $l \ge 2$) as a linear combination of $M$ basis functions and coefficients.
-	Due to the hybrid nature of the predictors, this approximation requires careful explanation, provided in Section \ref{sec: finite basis approximation}.
 	This representation allows us to work with coefficient vectors, simplifying notation.
@@
 	\end{equation*}	
-In practice, the full set of coefficients can not be obtained, as functional data are measured on a finite grid. Thus, we truncate the expansion at $M$ terms and define the truncated basis space
-\begin{equation}
+In practice, the full set of coefficients can not be obtained  with finite sample size, as functional data are measured on a finite grid.
+Thus, we truncate the expansion at $M$ terms and define the truncated basis space
+$
 	\mathcal{B} := \operatorname{span}\bigl(b_1(t), \ldots, b_M(t)\bigr).
-\end{equation}
+$
 We choose a moderately large $M$ (e.g., 15 or 20) to capture functional variation without fine-tuning, as smoothness is handled via penalization (see Section~\ref{sec: Regularization of PLS Components}).
-
 	The truncated expansions of the predictor and coefficient are denoted as
@@
 	\end{equation*}
-The $i$th hybrid predictor, with its functional parts projected onto the $\mathcal{B}$, is represented by the tuple
+This implies that all computations in this paper are carried out entirely within the subspace
+\begin{equation}\label{def:truncated_hilbert_space}
+	\widetilde{ \mathcal{H} } := \mathcal{B}^K \times \mathbb{R}^p \in \mathcal{H}.
+\end{equation}
+The $i$th hybrid predictor, projected on $\widetilde{ \mathcal{H} }$, is represented by the tuple
 	\begin{equation*}
@@
 Let $\boldsymbol{\theta}_{ij}$, $\boldsymbol{\eta}_j$, and $\boldsymbol{\gamma}_j$ denote the $M$-dimensional vectors of coefficients:
-	\begin{equation}
+	\begin{equation}\label{def:coef_vector_form}
 		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top,
@@
 
-	\subsubsection{Main estimation strategy}\label{sec: pls component computation intermediate}
-	Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an intermediate strategy for implementing the first step of the PLS algorithm.
-This approach directly obtains a hybrid PLS component direction, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply doing matrix-vector multiplications
-
-	We now describe the strategy for computing the PLS component direction at the $l$-th iteration.
-For simplicity, we omit the iteration index and assume that the observations have been residualized and are orthogonal to those from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for the residualization procedure).
-	The goal is to find a unit-norm direction $\xi \in 
-	(\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}$ that maximizes the squared empirical covariance between the resulting PLS component scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$,
-	 defined as
+	\subsubsection{Core strategy for PLS component direction estimation}\label{sec: pls component computation intermediate}
+Building on the basis function approximation in Section~\ref{sec: finite basis approximation}, we now present the core strategy for directly estimating the hybrid PLS component direction.
+This method fully leverages both the continuous nature of the functional components and the function-scalar hybrid structure, and can be implemented via simple matrix-vector multiplications.
+
+We describe the strategy at the $l$-th iteration.
+For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for details).
+The  PLS component direction is estimated by the unit-norm direction $\xi \in \tilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as
+
 \begin{equation}\label{def:squared_empirical_cov}
-	 	\widehat{\textnormal{Cov}}^2 \left( \langle 
+	 	\widehat{\textnormal{Cov}} 
+	 	( \langle 
 	 	\widetilde{W},
-	 	\xi \rangle_{\mathcal{H}}, Y \right)
+	 	\xi \rangle_{\mathcal{H}}, Y )
 	 	:=
-	 	\biggl(
 	 	\frac{1}{n} 
@@
 	 	\langle \widetilde{W}_i, \xi \rangle_{\mathcal{H}}
-	 	\biggr)^2
 	 	.
 	 \end{equation}
-	We denote the maximizer as
+We denote the estimated PLS component direction as
 	\begin{equation}\label{def:maximizer_squared_empirical_cov}
@@
 = 
-(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})
+(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1}
+)
 := \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
@@
 \langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
-\bigr)
+\bigr),
 	\end{equation}
 %
-	where each functional part $\hat{\xi}_j $  is expressed as
-	\begin{equation*}
+	where each functional part $\hat{\xi}_j $  is expanded as
+$
 		\hat{\xi}_j(t) := 
-		\sum_{m=1}^M \hat{d}_{jm} \, b_m(t), \quad j = 1, \ldots, K.
-	\end{equation*}
-
-	%	consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
-Let
-
+		\sum_{m=1}^M \hat{\gamma}_{jm} \, b_m(t),
+$
+and $\hat{\boldsymbol{\xi}}_{K+1}$ is the scalar part. This maximizer can also be represented as a Euclidean vector
+\begin{equation}\label{def:maximizer_euclidean_form}
+	( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top
+	\in \mathbb{R}^{MK+p},
+\end{equation}
+where the coefficient vectors $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ are defined as in \eqref{def:coef_vector_form}.
+Proposition \ref{proposition:eigen_noregul} reformulates  the problem \eqref{def:maximizer_squared_empirical_cov} as  a generalized Rayleigh quotient.
+%
 \begin{proposition}\label{proposition:eigen_noregul}
@@
 denote the observed data defined in \eqref{def:problem_instance}.
-At the $l$-th iteration of the PLS algorithm, let
-\begin{equation}
-( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top
-\end{equation}
-
-denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
-which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
-These coefficients are obtained by solving the following generalized eigenvalue problem:
+At the $l$-th iteration of the PLS algorithm, the unit-norm maximizer of  the squared empirical covariance defined in \eqref{def:maximizer_squared_empirical_cov}, represented as the Euclidean vector form as in \eqref{def:maximizer_euclidean_form},
+is obtained by solving 
 \begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
@@
 	\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
-	\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
+	\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1.
 \end{equation}
@@
 \begin{equation}\label{def:V_matrix}
-V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
-\end{equation}
-
+V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)}.
+\end{equation}
 \end{proposition}
-Since $V$ is a rank 1 matrix, the solution of the generalized eigenvalue problem is easily obtained by matrix multiplication and normalization:
+Since $V$ is a rank 1, the solution  is  obtained by matrix multiplication and normalization:
 	\begin{proposition} \label{proposition:linear_noregul}
-	We can compute  $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ and $\hat{\boldsymbol{\xi}}$ in Proposition \ref{proposition:eigen_noregul} as 
+	We can compute  $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ and $\hat{\boldsymbol{\xi}}_{K+1}$ in Proposition \ref{proposition:eigen_noregul} as 
 \begin{equation*}

### 2025-07-16 manuscript/main.tex
remove euclidean inner product

@@
 	\section{Proof of Proposition \ref{proposition:eigen_noregul} }\label{section:proof:proposition:linear_noregul_system_unregularized}
-	\begin{comment}
-		We start by defining a  inner product in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$:
-		\begin{lemma}[Inner product of tuples]
-			\label{lemma:valid_inner_product_tuple}
-			Let $B \in \mathbb{R}^{M \times M}$ be a symmetric positive semi-definite matrix. 
-			For any two tuples $u = (\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K, \boldsymbol{\zeta})$ and $v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$ in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$, define the bilinear form
-			\[
-			\langle u, v \rangle_{B} := \sum_{j=1}^K \boldsymbol{\gamma}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega}.
-			\]
-			Then $\langle \cdot, \cdot \rangle_{B}$ is a valid inner product on $(\mathbb{R}^M)^K \times \mathbb{R}^p$.
-		\end{lemma}
-		The proof of Lemma \ref{lemma:valid_inner_product_tuple} is provided in Appendix \ref{section:proof:lemma:valid_inner_product_tuple}
-	\end{comment}
 	\begin{proof}

### 2025-07-16 manuscript/main.tex
proposition 1 proof anchor

@@
 \end{proposition}
+The proof of Proposition \ref{proposition:eigen_noregul}
+is provided in Appendix \ref{section:proof:proposition:linear_noregul_system_unregularized}.
 Since $V$ is a rank 1, the solution  is  obtained by matrix multiplication and normalization:

### 2025-07-16 manuscript/main.tex
basis approximation as subsection
from subsubsection

--- 2025-07-16 manuscript/main.tex
@@
 
-	\subsection{Step 1: Computing smoothed PLS components}  \label{subsec: Step 1: Computing Smoothed PLS components}
-	This representation allows us to work with coefficient vectors, simplifying notation.
-Section~\ref{sec: pls component computation intermediate} outlines the core strategy for computing the PLS components in this reduced space.
-Building on this, we then introduce our regularized and smoothed estimation procedure, which constitutes the first step of the iterative algorithm.
-
-\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
+		\subsection{Preliminary step: Finite-basis Approximation }\label{sec: finite basis approximation}
+
 	Given a twice-differentiable basis $\{b_m(t)\}$ of $L^2([0,1])$,  the $j$th functional predictor, regression coefficient, and PLS direction (suppressing iteration indices) are represented as
@@
 
+	\subsection{Step 1: Computing smoothed PLS components}  \label{subsec: Step 1: Computing Smoothed PLS components}
+	This representation allows us to work with coefficient vectors, simplifying notation.
+Section~\ref{sec: pls component computation intermediate} outlines the core strategy for computing the PLS components in this reduced space.
+Building on this, we then introduce our regularized and smoothed estimation procedure, which constitutes the first step of the iterative algorithm.
+
 	\subsubsection{Core strategy for PLS component direction estimation}\label{sec: pls component computation intermediate}
 Building on the basis function approximation in Section~\ref{sec: finite basis approximation}, we now present the core strategy for directly estimating the hybrid PLS component direction. 
-This method fully leverages both the continuous nature of the functional components and the function-scalar hybrid structure, and can be implemented via simple matrix-vector multiplications.
+This stretagey fully leverages both the continuous nature of the functional components and the function-scalar hybrid structure, and can be implemented via simple matrix-vector multiplications.
+Building on this strategy, Section \ref{sec: Regularization of PLS Components} presents the estimation procedure for our suggest method.
 
@@
 \end{proposition}
+The proof of Proposition \ref{proposition:linear_noregul}  is provided in Appendix \ref{section:proof:proposition:linear_noregul}.
 The expressions above represent matrix–vector multiplications normalized by a common factor. 
-Proofs of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:linear_noregul} are provided in Appendix~\ref{section:proof:proposition:linear_noregul_system_unregularized}.
 Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other.
@@
 
- \section{Proof of Proposition  \ref{proposition:linear_noregul}}
+ \section{Proof of Proposition  \ref{proposition:linear_noregul}}\label{section:proof:proposition:linear_noregul}
  \begin{proof}

### 2025-07-16 manuscript/main.tex
widetilde H

@@
 
-	\subsection{Step 1: Computing smoothed PLS components}  \label{subsec: Step 1: Computing Smoothed PLS components}
-	This representation allows us to work with coefficient vectors, simplifying notation.
-Section~\ref{sec: pls component computation intermediate} outlines the core strategy for computing the PLS components in this reduced space.
-Building on this, we then introduce our regularized and smoothed estimation procedure, which constitutes the first step of the iterative algorithm.
-
-	\subsubsection{Core strategy for PLS component direction estimation}\label{sec: pls component computation intermediate}
-Building on the basis function approximation in Section~\ref{sec: finite basis approximation}, we now present the core strategy for directly estimating the hybrid PLS component direction. 
-This stretagey fully leverages both the continuous nature of the functional components and the function-scalar hybrid structure, and can be implemented via simple matrix-vector multiplications.
-Building on this strategy, Section \ref{sec: Regularization of PLS Components} presents the estimation procedure for our suggest method.
+	\subsection{Step 1: Computing smoothed PLS component direction}  \label{subsec: Step 1: Computing Smoothed PLS components} 
+We begin with the first step of the iterative algorithm: estimating the smooth PLS component direction.
+Section~\ref{sec: pls component computation intermediate} introduces the core optimization problem for this step, formulated as a generalized Rayleigh quotient.
+Building on this, Section~\ref{sec: Regularization of PLS Components} presents a modified version that promotes smoothness, which is the estimation procedure for our proposed method, along with a efficient computation scheme.
+
+	\subsubsection{Core optimization problem for PLS component direction estimation}\label{sec: pls component computation intermediate}
+Building on the basis function approximation in Section~\ref{sec: finite basis approximation}, we now present the core optimization problem that directly estimates the hybrid PLS component direction.
+This strategy fully leverages the continuous nature of the functional components and the function-scalar hybrid structure, and can be implemented using simple matrix-vector multiplications.
 
@@
 For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for details).
-The  PLS component direction is estimated by the unit-norm direction $\xi \in \tilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as
+The  PLS component direction is estimated by the unit-norm direction $\xi \in \widetilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as
 
@@
 )
-:= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
-\| \xi  \|_\mathcal{H} = 1
- } \widehat{\textnormal{Cov}}^2 
+:= \arg \max_{\xi \in \widetilde{\mathcal{H}}
+ }~\widehat{\textnormal{Cov}}^2 
 \bigl(
 \langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
-\bigr),
+\bigr)~s.t.~\| \xi  \|_\mathcal{H} = 1,
 	\end{equation}
@@
 \end{align*}
-where we recall that $\mathbb{B}^{\prime \prime} $ is defined in \eqref{def:gram_block}, 
-	where $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is defined as
+where $\boldsymbol{\xi}$ is the concatenated coefficient vector form of $\xi$ as defined in \eqref{def:maximizer_euclidean_form}, $\mathbb{B}^{\prime\prime}$ is defined in \eqref{def:gram_block}, and $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is given by
 \begin{equation}\label{def:Lambda}
-	\Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
-\end{equation}
-$0_{p \times p}$ denotes a $p \times p$ matrix with all elements equal to zero.
-
-However, the above approach assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense.
-As an alternative, we adopt the strategy of \citet{Silverman1996}, which works under weaker conditions than those required by \citet{Rice1991}.
-This is achieved by replacing the standard orthonormality constraint with one based on a modified inner product that accounts for roughness.
-Building on this idea, the following proposition reformulates the hybrid PLS problem as a generalized Rayleigh quotient, yielding a smoothed PLS direction that maximizes the squared covariance over a class of smooth functions.
-
-\begin{proposition}\label{proposition:eigen_noregul}
+	\Lambda := \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p}),
+\end{equation}
+where $0_{p \times p}$ denotes the $p \times p$ zero matrix.
+
+However, the approach of \citet{Rice1991} assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense.
+As an alternative, we adopt the strategy of \citet{Silverman1996}, which replaces the standard orthonormality constraint with a weaker one based on a modified inner product that incorporates roughness.
+Building on this idea, Proposition \ref{proposition:eigen_regul} modifies the optimization problem presented in Proposition \ref{proposition:eigen_noregul}, yielding a smoothed PLS direction that maximizes the squared covariance over a class of smooth functions.
+
+\begin{proposition}\label{proposition:eigen_regul}
 	Let
@@
 
-	\begin{proposition} \label{Proposition: Regularized generalized rayleigh quotient}
+	\begin{proposition} 
 		At each $l$-th iteration of the first step of the PLS algorithm involving the residualized response and predictors $Y_i \equiv Y_i^{[l]}$ and $\mathbf{W}_i \equiv \mathbf{W}_i^{[l]}$, consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
@@
 	\end{proposition}
-	The proof of Proposition \ref{Proposition: Regularized generalized rayleigh quotient} is provided in Appendix \ref{section:proof:eigenproblem_derivation}.
+	The proof of Proposition \ref{proposition:eigen_regul} is provided in Appendix \ref{section:proof:eigenproblem_derivation}.
 	Here, $\lambda_k$ $(k=1, \ldots, K)$ is a positive smoothing parameter that controls the trade-off between the goodness of fit and the amount of smoothness in $\psi^{(k)}$.
@@
 
-	The following proposition states that the PLS components estimated from Proposition  \ref{Proposition: Regularized generalized rayleigh quotient} are orthonormal with respect to the modified inner product $\langle \langle \cdot \rangle \rangle$ that incorporates the roughness of the functions.
+	The following proposition states that the PLS components estimated from Proposition  \ref{proposition:eigen_regul} are orthonormal with respect to the modified inner product $\langle \langle \cdot \rangle \rangle$ that incorporates the roughness of the functions.
 	\begin{proposition}\label{proposition: modified orthnormality of PLS components}
@@
 Thus, the linear independence constraint qualification (LICQ) holds, ensuring that the KKT conditions are necessary for local maxima (see, for example, Theorem 5.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}).
-	Taking gradients of $\mathcal{L}$ and setting them to zero yields:
+	Therefore, for any local maxima, gradients of $\mathcal{L}$ must be zero:
 	\begin{align*}
@@
 	\end{align*}
-	By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$ and observing that the scalar quantity $n^{-2}\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$ appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the gradient conditions together imply that any local optimum must be  scalar multiples of
+	By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$,  and observing that  $2n^{-2}\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$, which is a scalar quantity, appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the  conditions above together imply that any local maxima must be  scalar multiples of
 	$
@@
 	all scaled by the same factor.
-There exists only one set of vectors  that also satisfies the primal equality constraint, namely the normalized version of the vector set above.
+There exists only one such set of  vectors  that also satisfies the primal equality constraint, namely the normalized version of the vector set above.
 The global maximizer is therefore given by

### 2025-07-16 manuscript/main.tex
remove old reg eigen proposition

@@
 	\begin{equation}\label{def:truncated_hilbert_space}
-		\widetilde{ \mathcal{H} } := \mathcal{B}^K \times \mathbb{R}^p \in \mathcal{H}.
+		\widetilde{ \mathcal{H} } := \mathcal{B}^K \times \mathbb{R}^p \subset \mathcal{H}.
 	\end{equation}
@@
 To address this, we propose a regularized extension that balances predictive performance with smoothness.
-Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative $\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt$.
+Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative
+\begin{equation}
+\operatorname{PEN}(\hat{\xi}_j) := \int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt.
+\end{equation}
+
 Instead of solely maximizing the squared empirical covariance
@@
 
-One possible approach is to extend smoothed functional PCA \citep{Rice1991} to our optimization problem \eqref{def:maximizer_squared_empirical_cov}, leading to the following formulation:
-	\begin{equation*}
-	\hat{\xi} 
-	= 
-	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})
-	= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
-		\| \xi  \|_\mathcal{H} = 1
-	} 
-	\biggl\{
+One possible approach is to extend the smoothed functional PCA framework of \citet{Rice1991} by modifying the objective in \eqref{def:maximizer_squared_empirical_cov} to
+	\begin{equation*}
 	\widehat{\textnormal{Cov}}^2 
@@
 	- \sum \limits_{j=1}^K \lambda_j 
-	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
-	\biggr\}
+	\operatorname{PEN}({\xi}_j)
 	,
@@
 				\lambda_j
+				\operatorname{PEN}({\xi}_j)
+				&=
+	\sum \limits_{j=1}^K 
+	\lambda_j
 	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
-&=
+\\&=
 	\sum \limits_{j=1}^K 
@@
 
-However, the approach of \citet{Rice1991} assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense.
+\medskip
+\noindent
+\textit{Proposed estimation procedure.}~
+However, the above approach of \citet{Rice1991} assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense.
 As an alternative, we adopt the strategy of \citet{Silverman1996}, which replaces the standard orthonormality constraint with a weaker one based on a modified inner product that incorporates roughness.
-Building on this idea, Proposition \ref{proposition:eigen_regul} modifies the optimization problem presented in Proposition \ref{proposition:eigen_noregul}, yielding a smoothed PLS direction that maximizes the squared covariance over a class of smooth functions.
+Accordingly, our estimation procedure at the $l$-th iteration, iteration index omitted and assuming the observations have been residualized in previous steps, solves the following optimization problem:
+	\begin{equation}\label{def:maximizer_squared_empirical_cov_reg}
+	\hat{\xi} 
+	= 
+	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1}
+	)
+	:= \arg \max_{\xi \in \widetilde{\mathcal{H}}
+	}~\widehat{\textnormal{Cov}}^2 
+	\bigl(
+	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
+	\bigr)~s.t.~\| \xi  \|_\mathcal{H} +  \sum \limits_{j=1}^K \lambda_j 
+	\operatorname{PEN}(\xi_K) = 1.
+\end{equation}
+This formulation maximizes the squared covariance over a class of smooth functions.
+Proposition~\ref{proposition:eigen_regul} expresses this problem as a generalized Rayleigh quotient.
 
@@
 	denote the observed data defined in \eqref{def:problem_instance}.
-	At the $l$-th iteration of the PLS algorithm, let
-	$( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
-	denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
-	which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
-	These coefficients are obtained by solving the following generalized eigenvalue problem:
+	At the $l$-th iteration of the PLS algorithm, the maximizer of  the squared empirical covariance defined in \eqref{def:maximizer_squared_empirical_cov_reg}, represented as the Euclidean vector form as in \eqref{def:maximizer_euclidean_form},
+	is obtained by solving 
 	\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
@@
 		\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
-		\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
-	\end{equation}
-	where
-	\begin{equation}\label{def:V_matrix}
-		V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
-	\end{equation}
-
+		\quad \text{s.t.} \quad \boldsymbol{\xi}^\top (\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1.
+	\end{equation}
+	where we recall that $
+		V = n^{-2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top$ is defined in  \eqref{def:V_matrix}.
 \end{proposition}

### 2025-07-16 manuscript/main.tex
really removed

@@
 \end{proposition}
-
-	\begin{proposition} 
-		At each $l$-th iteration of the first step of the PLS algorithm involving the residualized response and predictors $Y_i \equiv Y_i^{[l]}$ and $\mathbf{W}_i \equiv \mathbf{W}_i^{[l]}$, consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$.
-Recall from \eqref{def:V_star} that  $V^\ast$ is defined as
-		\begin{equation*}
-			\mathbf{V}^\ast = n^{-2}\begin{bmatrix}
-				J \widetilde{C}^\top \mathbf{y}\mathbf{y}^\top \widetilde{C} J & J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z} \\
-				\mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J &   \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z}
-			\end{bmatrix} = n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast
-			\in \mathbb{R}^{(MK+p) \times (MK+p)}.
-		\end{equation*}
-		and  $\xi^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$.
-Then, the $l$-th smoothed PLS component, $\widehat{\xi} \equiv \widehat{\xi}_l$ can be obtained in the following way.
-		We first compute the basis coefficients by solving the optimization problem
-		Note that the penalty term can be written concisely using matrices as:
-		\begin{equation}
-			\textnormal{PEN} \left( \hat{\xi}_j \right) 
-			=  \int_0^1 
-			\bigl\{ \hat{\xi}_j^{''}(t) \bigr\}^2 dt = \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)},
-			\label{eq: roughness penalty}
-		\end{equation}
-		where the last term is obtained using the basis expansion $\psi^{(k)}(t)=\mathbf{a}^{(k)T}\mathbf{b}^{(k)}(t)$.
-
-		\begin{align}
-			\begin{split}
-				&\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top}(J^\ast+\Lambda \ddot{J}^\ast) \xi^*} , \quad \textit{or equivalently}, \\ 
-				&\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1.
-				\label{eq: Regularized generalized rayleigh quotient equation}
-			\end{split}
-		\end{align}
-		We then express the smoothed component in terms of the basis functions as
-		\begin{equation*}
-			\widehat{\xi}[\mathbf{t}] = [\widehat{\psi}(\mathbf{t})^\top, \widehat{\boldsymbol{\theta}}^\top]^\top =  \mathbb{B}[\mathbf{t}]^\top \widehat{\xi}^\ast.   
-		\end{equation*}
-		The $l$-th PLS score $\widehat{\rho}_{i} \equiv \widehat{\rho}_{il}$ can be obtained as 
-		\begin{equation}\label{compute_pls_score}
-			\widehat{\rho}_i = \langle \mathbf{W}_i, \widehat{\xi} \rangle_\mathcal{H}
-		\end{equation}
-	\end{proposition}
 	The proof of Proposition \ref{proposition:eigen_regul} is provided in Appendix \ref{section:proof:eigenproblem_derivation}.

### 2025-07-16 manuscript/main.tex
second derivative independent

@@
 		\subsection{Preliminary step: Finite-basis Approximation }\label{sec: finite basis approximation}	
-
-	Given a twice-differentiable basis $\{b_m(t)\}$ of $L^2([0,1])$,  the $j$th functional predictor, regression coefficient, and PLS direction (suppressing iteration indices) are represented as
+Let ${b_m(t)}$ be a twice-differentiable basis of $L^2([0,1])$ whose second derivatives are also linearly independent, for example, cubic B-splines, the Fourier basis, or an orthonormal polynomial basis of degree greater than three.
+Using this basis, the $j$th functional predictor, regression coefficient, and PLS direction (suppressing iteration indices) are represented as follows:
 	\begin{equation*}
@@
 is obtained by solving 
-\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
+\begin{equation}	\label{eq: Unregularized generalized rayleigh quotient equation}
 	\left(
@@
 \end{equation*}
-where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness. Here, the penalization term can be written in matrix form as:
+where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness.
+
+\medskip
+\noindent
+\textit{Proposed estimation procedure.}~
+However, the above approach of \citet{Rice1991} assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense.
+As an alternative, we adopt the strategy of \citet{Silverman1996}, which replaces the standard orthonormality constraint with a weaker one based on a modified inner product that incorporates roughness.
+Accordingly, our estimation procedure at the $l$-th iteration, iteration index omitted and assuming the observations have been residualized in previous steps, solves the following optimization problem:
+	\begin{equation}\label{def:maximizer_squared_empirical_cov_reg}
+	\hat{\xi} 
+	= 
+	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1}
+	)
+	:= \arg \max_{\xi \in \widetilde{\mathcal{H}}
+	}~\widehat{\textnormal{Cov}}^2 
+	\bigl(
+	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
+	\bigr)~s.t.~\| \xi  \|_\mathcal{H} +  \sum \limits_{j=1}^K \lambda_j 
+	\operatorname{PEN}(\xi_K) = 1.
+\end{equation}
+This formulation maximizes the squared covariance over a class of smooth functions.
+Proposition~\ref{proposition:eigen_regul} expresses this problem as a generalized Rayleigh quotient.
+
+\begin{proposition}\label{proposition:eigen_regul}
+	Let
+	$
+	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
+	$
+	denote the observed data defined in \eqref{def:problem_instance}.
+	At the $l$-th iteration of the PLS algorithm, the maximizer of  the squared empirical covariance defined in \eqref{def:maximizer_squared_empirical_cov_reg}, represented as the Euclidean vector form as in \eqref{def:maximizer_euclidean_form},
+	is obtained by solving 
+	\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
+		\left(
+		\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
+		\right)^\top
+		=
+		\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
+		\quad \text{s.t.} \quad \boldsymbol{\xi}^\top (\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1.
+	\end{equation}
+	where we recall that $
+		V = n^{-2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top$ is defined in  \eqref{def:V_matrix}, and 
+		$\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is given by
+		\begin{equation}\label{def:Lambda}
+			\Lambda := \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p}),
+		\end{equation}
+		where $0_{p \times p}$ denotes the $p \times p$ zero matrix.
+\end{proposition}
+	The proof of Proposition \ref{proposition:eigen_regul} is provided in Appendix  \ref{section:proof:proposition:linear_noregul_system_unregularized}.
+	Here, $\lambda_k$ $(k=1, \ldots, K)$ is a positive smoothing parameter that controls the trade-off between the goodness of fit and the amount of smoothness in $\psi^{(k)}$.
+Smaller $\lambda_k$ produces PLS components that fit more closely to the observed data, but selecting too small value may cause overfitting.
+The estimated PLS component reverts back to the unregularized version of Proposition \ref{proposition:eigen_noregul} when $\lambda_k=0$ for all $k$.
+On the other hand, larger $\lambda_k$ places more emphasis on smoothing $\psi^{(k)}$.
+In the limit $\lambda_k \rightarrow \infty$, each of the functions is forced to be of the form $\psi^{(k)}(t)=a+bt$ for some constants $a$ and $b$.
+In practice, $\{\lambda_k\}_{k=1}^K$ as well as the number of PLS components $L$ to be estimated can be chosen by cross-validation based on a certain predictive performance criterion (e.g., mean squared error).
+
+	The constraint $\xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1$ enforces the following modified orthonormality of the estimated PLS components ($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ which now takes into account the roughness of the functions:
+	\begin{align*}
+		\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
+		&= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right \rangle_{L^2} \\
+		&= \sum \limits_{k=1}^K \int_0^1 \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_0^1 \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
+		& = \mathbb{1}(l=j). 
+	\end{align*}
+	This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{sec: Properties of the Proposed PLS Framework} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.
+
+	To solve \eqref{eq: Regularized generalized rayleigh quotient equation} in practice, we first perform a Choleski factorization: $L L^\top = J^\ast + \Lambda \ddot{J}^\ast$, where $L$ is a lower triangular matrix, and then reduce it to maximizing the classical Rayleigh quotient problem:
+	\begin{equation*}
+		\max \limits_{\mathbf{e} \in \mathbb{R}^{MK + p}} \, \frac{\mathbf{e}^\top E \mathbf{e}}{\mathbf{e}^\top \mathbf{e}} \; \Longleftrightarrow \;   \max \limits_{\substack{\mathbf{e} \in \mathbb{R}^{MK+p}}} \;  \mathbf{e}^\top E \mathbf{e} \quad \textnormal{subject to} \quad \Vert \mathbf{e} \Vert^2 = 1
+	\end{equation*}
+	through the transformations $\mathbf{e} = L^\top \xi^*$ and $E = L^{-1} \mathbf{V}^\ast L^{\top-1}$.
+Once $\mathbf{e}$ is obtained as the first eigenvector of $E$, we set $\xi^* = L^{\top-1} \mathbf{e}$ and $\widehat{\xi}[\mathbf{t}] = B^*[\mathbf{t}]^\top \xi^*$.
+
+	\subsection{Step 2: Computing Residualized Predictors via Hybrid-on-Scalar Regression} \label{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}
+	The second step of the PLS algorithm involves iteratively obtaining the ($l+1$)-th residualized predictors as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$, where $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ is the least squares estimate from regressing the previous ($l$-th) residualized outcome $\mathbf{W}_i^{[l]}[\mathbf{t}]$ on the corresponding  estimated PLS score $\widehat{\rho}_{il}$.
+The pointwise least squares estimate, $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] = (\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \widehat{\rho}_{il})/(\sum_{i=1}^n \widehat{\rho}_{il}^2)$, presented in Section \ref{sec: Naive PLS Algorithm}, however, is  highly inefficient and may not be even feasible for multiple dense and/or irregular functional data.
+Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components.
+Therefore, in this section, we introduce a novel strategy based on a hybrid-on-scalar regression model for obtaining $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ and implementing the second step.
+
+	Again, we omit $l$ in the notations.
+Let $\widehat{\boldsymbol{\rho}}=(\widehat{\rho}_1, \ldots, \widehat{\rho}_n)^\top$ denote an $n$-dimensional vector of PLS scores estimated from the proposed algorithm, and let the $(K+P)$-vector $\boldsymbol{\delta}[\mathbf{t}] = [\pi(\mathbf{t})^\top, \boldsymbol{\gamma}^\top]^\top$ denote the regression coefficient consisting of the functional part $\pi(\mathbf{t}) = (\pi^{(1)}(t_1), \ldots,\pi^{(K)}(t_K))^\top \in \mathbb{R}^K$ and scalar part $\boldsymbol{\gamma} = (\gamma_1, \ldots,\gamma_p)^\top \in \mathbb{R}^p$.
+The hybrid-on-scalar regression model we are interested in fitting is then:
+	\begin{equation}
+		\widetilde{W}[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top + \mathbf{e}[\mathbf{t}],
+		\label{eq: hybrid on scalar regression model}
+	\end{equation}
+	where $\mathbf{e}[\mathbf{t}]$ is an $n \times (K+p)$ matrix of errors.
+
+	As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$.
+Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \boldsymbol{\gamma}^{(k)\top} \mathbf{b}^{(k)}(t_k)$, where $\boldsymbol{\gamma}^{(k)} = (d_1^{(k)}, \ldots, d_M^{(k)})\top \in \mathbb{R}^M$ are basis coefficients.
+Here, a different basis system can be flexibly chosen to expand the regression coefficient, but without loss of generality we use the same system as in Section \ref{subsec: Step 1: Computing Smoothed PLS components}.
+With the $(MK+p)$-dimensional row vector $\boldsymbol{\gamma}^* = (\boldsymbol{\gamma}^{(1)\top}, \ldots, \boldsymbol{\gamma}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as: $\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}]$.
+Finally, these basis expansions of the hybrid response and the regression coefficient enable us to re-write the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model} in a finite-dimensional form:
+	\begin{equation}
+		\widetilde{C}^* B^*[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] + \mathbf{e}[\mathbf{t}].
+		\label{eq: rewritten hybrid on scalar regression model}
+	\end{equation}
+
+	Based on the model formulation \eqref{eq: rewritten hybrid on scalar regression model}, we can now formulate the following least squares criterion whose minimizing solution gives the estimate of the regression coefficient $\boldsymbol{\delta}[\mathbf{t}]$ in the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model}:
+	\begin{equation}
+		\begin{aligned}
+			\textnormal{SSE}(\delta) &= \int_\mathcal{T} \left\Vert \,  \widetilde{C}^* B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] \, \right\Vert_F^2 \, d\mathbf{t}  \\
+			&= tr\left(\widetilde{C}^{*T}\widetilde{C}^*J^\ast \right) - 2\,tr \left(\boldsymbol{\gamma}^* J^\ast \widetilde{C}^{*T} \widehat{\boldsymbol{\rho}} \right) + tr\left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* J^\ast \boldsymbol{\gamma}^{*T}\right),
+		\end{aligned}
+		\label{eq: least squares}
+	\end{equation}
+	where $tr$ denotes the trace of a matrix, and $\Vert \cdot \Vert_F$ is a Frobenius norm.
+Now taking the derivative of \eqref{eq: least squares} with respect to $\boldsymbol{\gamma}^*$ and setting the result to zero, we find that  $\boldsymbol{\gamma}^*$ satisfies the system of linear equations
+	\begin{equation*}
+		\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^*  J^\ast =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast,
+	\end{equation*}
+	whose solutions lead to the following estimates of $\boldsymbol{\gamma}^*$ and $\boldsymbol{\delta}[\mathbf{t}]$:
+	\begin{equation*}
+		\widehat{\boldsymbol{\gamma}}^*  =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast \left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} J^\ast \right)^{-1} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}[\mathbf{t}] = B^*[\mathbf{t}]^\top \, \widehat{\boldsymbol{\gamma}}^{*\top}.
+	\end{equation*}
+	Then, we can use $\widehat{\boldsymbol{\delta}}[\mathbf{t}]$ to obtain the subsequent residualized hybrid predictor as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$.
+
+	The step for obtaining the subsequent residualized response is identical to that of the naive PLS algorithm in  in Section \ref{sec: Naive PLS Algorithm}.
+Specifically, the $(l-1)$-th residualized response can be obtained as $Y_i^{[l+1]} = Y_i^{[l]} - \widehat{\nu}_l \widehat{\rho}_{il}$, where $\widehat{\nu}_l = \sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}/\sum_{i=1}^n \widehat{\rho}_{il}^2$  is the least square estimate of the simple linear model regressing $Y_i^{[l]}$ on $\widehat{\rho}_{il}$.
+
+	\subsection{Obtaining the Estimated Hybrid Regression Coefficient}
+	\label{subsec: Obtaining the Estimated Hybrid Regression Coefficient}
+	The regression coefficient $\boldsymbol{\eta}$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS components and scores.
+First, note that we can show $\widehat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} = \langle \mathbf{W}_i, \widehat{\boldsymbol{\xi}_{K+1}}_l \rangle_\mathcal{H}$, where $\widehat{\boldsymbol{\xi}_{K+1}}_l = \widehat{\xi}_l - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}_u, \widehat{\xi}_l \rangle_{\mathcal{H}} \widehat{\boldsymbol{\xi}_{K+1}}_u$ for $l \ge 2$, with $\widehat{\boldsymbol{\xi}_{K+1}}_1 = \widehat{\xi}_1$.
+Then, the decomposition of $Y_i$ in \eqref{eq: decomposition} leads to
+	\begin{equation*}
+		Y_i = \sum \limits_{l=1}^L \widehat{\nu}_l \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\xi}_{K+1}}_l \right\rangle_\mathcal{H}+\epsilon_i,
+	\end{equation*}
+	which, given the uniqueness of $\boldsymbol{\eta}$, leads to
+	\begin{equation*}
+		\widehat{\boldsymbol{\eta}} = \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\xi}_{K+1}}_l.
+	\end{equation*}
+	Here, the number of PLS components $L$ to be estimated can be chosen by cross-validation.
+
+	\begin{algorithm}[b!]
+		\caption{Hybrid PLS (under construction)}
+		\label{alg:main}
+		\begin{algorithmic}[1]
+			\Require 
+			Response $\mathbf{y} \in \mathbb{R}^n$,
+			%functional predictor evalulation points $\mathbf{t}_1, \ldots, \mathbf{t}_m \in [0,1]^K,$
+			hybrid predictors approximation coefficient
+			$\widetilde{C}^* \ \in \mathbb{R}^{n \times (MK+p)} $ \eqref{eq: basis approximation of W},
+			Gram matrix with respect to basis functions
+			$J^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)} $
+			\eqref{def:J_and_J_star},
+			Gram matrix with respect to second derivatives of the basis functions 
+			$\ddot{J}^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)}$
+			\eqref{def:J_dotdot_ast},
+			regularization matrix $\Lambda  \in \mathbb{R}^{(MK+p) \times (MK+p)}$ \eqref{def:Lambda}
+			%%%%%%%%%%%%%%%%%%%%%
+			\State
+			$\widetilde{C}^{*[1]} \leftarrow \widetilde{C}^*$
+			\For{ l = 1, 2, \ldots  $T$}
+			\State $\mathbf{V}^\ast \leftarrow n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast$
+			\Comment{ \eqref{def:V_star}}
+			\State 	$\widehat{\xi}_l^\ast \leftarrow \arg \max_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1
+			$
+			\Comment{ \eqref{eq: Regularized generalized rayleigh quotient equation}} 
+			\State $\widehat{\boldsymbol{\rho}}_l
+			\leftarrow 
+			\widetilde{C}^* J^\ast  \widehat{\xi}_l^\ast
+			$
+			\Comment{$\in \mathbb{R}^n$; \eqref{compute_pls_score}}
+			\EndFor
+			\State Output a
+		\end{algorithmic}
+	\end{algorithm}
+
+	\subsection{Data Preprocessing} \label{subsec: Data Preprocessing}
+	Functional and scalar elements of the hybrid predictors often have incompatible units and/or exhibit different amounts of variation.
+This can be problematic for our PLS framework which is not scale invariant as: i) each predictor has different chance of contributing to the predictor/response structure; and ii) a predictor with high correlation to $Y$ but relatively low variance may be overlooked.
+
+	To obtain PLS components that have a meaningful interpretation, we standardize the predictor data via the following steps.
+The first step is to account for discrepancies \textit{within} respective functional and scalar parts, if needed.
+If elements of multivariate functional data $X_i = (X_i^{(1)}, \ldots, X_i^{(K)})$ are measured in different units or have quite different domains, one can standardize them to have mean zero and integrated variance of one.
+If multivariate scalar predictors $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ exhibit different amounts of variation, one can standardize them to have mean zero and unit variance.
+The second step is to eliminate the discrepancies \textit{between} functional and scalar parts.
+To accomplish this aim, we choose an appropriate weight $\omega$ in the hybrid inner product \eqref{eq: hybrid inner product} that ensures functional and vector parts have comparable variance.
+A sensible data-driven approach to choosing an appropriate weight is to set
+	\begin{equation*}
+		\omega = \frac{\sum_{i=1}^n \Vert X_i \Vert_\mathcal{F}^2}{\sum_{i=1}^n \Vert \mathbf{Z}_i \Vert^2},
+		\label{eq: weight}
+	\end{equation*}
+	In practice, this weighting scheme can be implemented by formulating the hybrid object as $\mathbf{W} = (X, \omega^{1/2} \mathbf{Z})$, whose vector part has been scaled by a factor of $\omega^{1/2}$.
+
+	\section{Properties of the Proposed PLS Framework}
+	\label{sec: Properties of the Proposed PLS Framework}
+	In this section, we derive some of the theoretical and geometric properties of the proposed PLS framework.
+
+	\subsection{Tucker's Criterion}
+	We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
+We omit $l$ in the notations and first define the cross-covariance terms between the response and predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$):
+	\begin{equation*}
+		\begin{gathered}
+			\sigma_{YX} = (\sigma_{YX}^{(1)}, \ldots, \sigma_{YX}^{(K)}) = (E(YX^{(1)}),\ldots, E(YX^{(K)})) = E(YX) \in \mathcal{F} \\
+			\sigma_{YZ} = (\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top = (E(YZ_1),\ldots, E(YZ_p))^\top = E(Y\mathbf{Z}) \in \mathbb{R}^p \\
+			\Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) =  (E(YX), E(Y\mathbf{Z}))=E(Y\mathbf{W}) \in \mathcal{H}
+		\end{gathered}
+	\end{equation*}
+	We also introduce two cross-covariance operators, $\mathcal{C}_{YW}=E(\mathbf{W} \otimes_\mathcal{H} Y): \mathcal{H} \rightarrow \mathbb{R}$ and $\mathcal{C}_{WY}=E(Y \otimes \mathbf{W}): \mathbb{R} \rightarrow \mathcal{H}$, which respectively map $h=(f, \mathbf{v}) \in \mathcal{H}$ to $\mathbb{R}$ and $d \in \mathbb{R}$ to $\mathcal{H}$ as follows:
+	\begin{align*}
+		& \mathcal{C}_{YW} \mathbf{h} = E\{\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX}^{(k)}(t_k) f^{(k)}(t_k) dt_k + E(Y \mathbf{Z}^\top) \mathbf{v} \\
+		& \mathcal{C}_{WY} d = E (\langle Y, d \rangle \mathbf{W} ) = E(Y\mathbf{W})d =  \Sigma_{YW} \, d. 
+	\end{align*}
+
+	Now define a new operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$, which performs the following mapping:
+	\begin{equation*}
+		\mathcal{U} \mathbf{h} =  \mathcal{C}_{WY} ( \mathcal{C}_{YW} \mathbf{h}) 
+		= \mathcal{C}_{YW} (\langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}) 
+		=  \Sigma_{YW} \, \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = (\Sigma_{YW} \otimes \Sigma_{YW})\mathbf{h}.
+	\end{equation*}
+	In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$. The following proposition presents several important properties of $\mathcal{U}$.
+	\begin{proposition} \label{Proposition: property of U}
+		The operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}= \Sigma_{YW} \otimes \Sigma_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ is positive and self-adjoint.
+Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that
+		\begin{align}
+			\max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in [0,1]} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
+		\end{align}
+		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in [0,1]$ with $|t_k - t_k^* | < \delta_k$, we have that
+		\begin{equation*}
+			|\sigma_{yx}^{(k)}(t_k) - \sigma_{yx}^{(k)}(t_k^*) | < \epsilon,
+		\end{equation*}
+		then $\mathcal{U}$ is a compact operator.
+	\end{proposition}
+	The proof of Proposition \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
+	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
+
+	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
+	\begin{proposition}\label{proposition: eigenanalysis}
+		\begin{equation*}
+			\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)
+		\end{equation*}
+		is achieved when $\xi$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.	
+	\end{proposition}
+	The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
+	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.
+
+	\subsection{Geometric Properties}
+	In this section, we derive several geometric properties of the PLS components and and scores obtained from the proposed algorithm.
+
+	The following proposition states that the PLS components estimated from Proposition  \ref{proposition:eigen_regul} are orthonormal with respect to the modified inner product $\langle \langle \cdot \rangle \rangle$ that incorporates the roughness of the functions.
+	\begin{proposition}\label{proposition: modified orthnormality of PLS components}
+		The estimated PLS components, $\widehat{\xi}_1, \widehat{\xi}_2, \ldots, \widehat{\xi}_L$, from the proposed PLS algorithm are mutually orthonormal with respect to the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ in $\mathcal{H}$ that incorporates the roughness of the functions; i.e.,
+		\begin{equation*}
+			\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
+			= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}
+			= \mathbb{1}(l=j). 
+		\end{equation*}
+	\end{proposition}
+	The proof of Proposition \ref{proposition: modified orthnormality of PLS components} is provided in Appendix \ref{section:proof:proposition: modified orthnormality of PLS components}.
+	Now let $\widehat{\boldsymbol{\rho}}_l=(\widehat{\rho}_{1l}, \ldots, \widehat{\rho}_{nl})^\top$ denote the $n$-dimensional vector whose elements consist of estimated $l$-th PLS scores ($l=1, \ldots, L)$ of $n$ observations.
+The next proposition states that the vectors of estimated PLS scores $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$ obtained from the proposed algorithm are mutually orthogonal.
+	\begin{proposition}	\label{proposition: orthnormality of PLS scores}
+		The vectors of estimated PLS scores, $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$, obtained from the proposed PLS algorithm are mutually orthogonal in the sense that
+		\begin{equation*}
+			\widehat{\boldsymbol{\rho}}_l^\top \widehat{\boldsymbol{\rho}}_j= 0 \quad \textnormal{for} \quad \; l,j \in \{1, \ldots, L\}, \; l \ne j. 
+		\end{equation*}
+	\end{proposition}
+	The proof of Proposition \ref{proposition: orthnormality of PLS scores} is provided in Appendix \ref{section:proof:proposition: orthnormality of PLS scores}.
+
+	\section{Simulations}
+	To evaluate the superiority of our method under complex dependency structures
+	{\textemdash}
+	specifically, dependencies among functional predictors,
+	among scalar predictors,
+	and between scalar and functional predictors
+	{\textemdash}
+
+	\medskip
+	\noindent
+	\textit{Matrix-normal setting.}
+	We begin by constructing predictors from a matrix-normal distribution, a framework that offers convenient and flexible control over the dependence structure across both rows and columns.
+Matrix-normal (MN) models, also known as Kronecker-separable covariance models, provide a principled approach to modeling multivariate data with structured covariance.
+Specifically, the matrix-normal distribution is defined as
+	\begin{equation*}
+		\mathbf{X} \sim \mathcal{MN}_{m \times n}(\mathbf{M}; \mathbf{R}, \mathbf{C}),
+	\end{equation*}
+	and its log-density is given by
+	\[
+	\log p(\mathbf{X} \mid \mathbf{M}, \mathbf{R}, \mathbf{C}) = -\frac{mn}{2} \log(2\pi) - \frac{m}{2} \log |\mathbf{C}| - \frac{n}{2} \log |\mathbf{R}| - \frac{1}{2} \mathrm{Tr}\left[ \mathbf{C}^{-1} (\mathbf{X} - \mathbf{M})^\top \mathbf{R}^{-1} (\mathbf{X} - \mathbf{M}) \right].
+	\]
+	The key insight behind Kronecker separability is that if
+	$
+	\mathbf{Y} \sim \mathcal{MN}(\mathbf{M}, \mathbf{R}, \mathbf{C}),
+	$
+	then its vectorized form follows a multivariate normal distribution:
+	$
+	\mathrm{vec}(\mathbf{Y}) \sim \mathcal{N}(\mathrm{vec}(\mathbf{M}), \mathbf{C} \otimes \mathbf{R}),
+	$
+	where $\otimes$ denotes the Kronecker product and $\mathrm{vec}$ is the vectorization operator.
+
+	\begin{figure}[ht!]
+		\centering
+		\begin{subfigure}[b]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{image/cor_strong.pdf}
+			\caption{Correlation Matrix - Strong Dependency}
+			\label{fig:cor_strong}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{image/cor_weak.pdf}
+			\caption{Correlation Matrix - Weak Dependency}
+			\label{fig:cor_weak}
+		\end{subfigure}
+
+		\vspace{0.5cm}  % Adjust vertical spacing
+
+		\begin{subfigure}[b]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{image/graph_strong.pdf}
+			\caption{Graph Structure - Strong Dependency}
+			\label{fig:graph_strong}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{image/graph_weak.pdf}
+			\caption{Graph Structure - Weak Dependency}
+			\label{fig:graph_weak}
+		\end{subfigure}
+
+		\caption{Comparison of Correlation Matrices and Graph Structures under Strong and Weak Dependencies.}
+		\label{fig:correlation_graph_comparison}
+	\end{figure}
+
+	\begin{comment}
+		The goal of this simulation is to:
+		\begin{enumerate}
+			\item Utilize a graphical model to introduce a complex dependence structure.
+			\item Demonstrate that our method outperforms the penalized functional regression approach by \citet{goldsmithPenalizedFunctionalRegression2011}.
+			\item Show that our method exhibits superior performance as correlation strength increases.
+		\end{enumerate}
+
+		Our previous setup, presented in Section \ref{simul:meeting_feb}, appeared to achieve these objectives. However, we identified several limitations:
+		\begin{enumerate}
+			\item The resulting precision matrix was singular, requiring us to scale up the diagonal elements to compute its inverse.
+This adjustment disrupted the original AR(1) structure of the functional component, making it significantly less smooth.
+			\item Increasing conditional correlation did not consistently enhance the superiority of our method.
+		\end{enumerate}
+		To address these issues, I will explore alternative functional graphical model settings that exhibit a strong dependence structure—one substantial enough to be detected by statistical methodologies and validated by top statistical journal papers.
+I will evaluate the performance of penalized functional regression on these data-generating models.
+		Among them, I will select three to four settings for comparison against other methods.
+	\end{comment}
+	Building on the functional graphical model simulation of \citet{zhuBayesianGraphicalModels2016}, we generate a mixed graphical model with five nodes, described as follows:  
+	\begin{itemize}
+		\item Nodes F1 and F2: Two functional predictors modeled as Gaussian processes using a truncated Karhunen-Loève expansion, where the eigenbasis consists of Fourier basis functions with a fixed number of basis functions, \(M = 9\).
+		\item  Nodes S1, S2, and S3: Three scalar predictors, each following an \(s\)-dimensional multivariate normal distribution.
+Unlike the functional predictors, these scalar predictors are modeled directly without basis expansion.
+	\end{itemize}
+	To capture dependencies among predictors, we introduce a graph structure that governs their conditional correlations.
+We consider two types of graph structures: a weakly connected graph and a strongly connected graph.
+In the Gaussian process framework, the precision matrix \(\mathbf{R}_0^{-1}\) encodes conditional independence relationships, while its inverse, \(\mathbf{R}_0\), represents marginal covariances.
+This structure extends to a blockwise correlation matrix \(\mathbf{R} \in \mathbb{R}^{(2M + 3s) \times (2M + 3s)}\), where off-diagonal blocks represent correlations between FPC scores and scalar predictor values.
+	Each block \((i, j)\) of \(\mathbf{R}\) is given by \((R_0)_{ij} \mathbf{I}_{M_i, M_j}\), where \(\mathbf{I}_{M_i, M_j}\) is a rectangular identity matrix.
+Here, \(M_i = 9\) if node \(i\) corresponds to a functional predictor and \(M_j = s\) if node \(j\) corresponds to a scalar predictor.
+
+	For each functional predictor, we assgin  \(M\) reference eigenvalues (or FPC score) drawn independently from gamma distributions with decreasing means.
+	These reference eigenvalues will later be multiplies by randomly  multiplier drawn from correlated multivaraite Normal distribution.
+These reference eigenvalues are fixed over all samples and all independent repetition of the experiment.
+We draw it one randomly just to ensure the differentiation between the two functional predictors.
+	we independently draw for each functional predictor from .
+We then sample zero-mean multivariate normal data from the covariance matrix \(\mathbf{R}\).
+The last \(3s\) components are assigned as scalar predictors, while the first \(2M\) components, scaled by their corresponding eigenvalues, serve as FPC scores.
+These scores are then expanded into functional data, evaluated over 100 equally spaced points on \([0,1]\) using a Fourier basis.
+
+	Finally, we introduce structured variability by adding a common mean function, defined as a scaled and shifted sine function.
+To visualize the generated data, Figure \ref{fig:correlation_graph_comparison}  plots functional predictor realizations and heatmaps of sample correlation matrices for both graph structures, illustrating the distinct dependency patterns induced by the precision matrices.
+
+	\subsection{Simulation shown in february 2025 meeting}\label{simul:meeting_feb}
+	To effectively manage the dependencies among functional predictors, scalar covariates, and between functional and scalar predictors, we utilize a Gaussian Markov random field (GMRF) within the framework of Gaussian undirected graphical models.
+In a GMRF, the off-diagonal elements of the precision matrix capture the conditional correlations between the corresponding components.
+Given that our setting involves both functional and scalar covariates, we adopt the simulation setup proposed by \cite{kolar_graph_2014}, which focuses on mixed attribute Gaussian graphical models.
+
+	We construct a graph consisting of two functional predictor nodes and three vector predictor nodes. Below, we sequentially describe the graph structure and the generation process for each node.
+
+	\medskip
+	\noindent
+	\textit{Functional Predictors.}
+	We consider two functional predictors that share the same precision matrix.
+Denoted as \( \boldsymbol{\Theta} := (\theta_{t \tilde{t}}) \in \mathbb{R}^{p \times p} \), this precision matrix follows an AR(1) structure with a white noise variance of \( 0.1^2 \) and an autoregressive coefficient of \( = 0.95 \), ensuring a smooth functional trajectory.
+
+	More formally, each functional predictor is evaluated at \( p \) equally spaced points on \( [0,1] \), with values defined recursively as:
+	\begin{equation*}
+		X^{(k)}_i(0) = 0, \quad 
+		X^{(k)}_i(t)= \rho X^{(k)}_i(t-1) + \varepsilon_{itk}, \quad \varepsilon_{itk} \overset{\text{i.i.d.}}{\sim} \mathcal{N}(0, \sigma^2), \quad t = 1, \dots, p,~i=1, \ldots, n,~k = 1,2.
+	\end{equation*}
+	In this setting, the precision matrix \( \boldsymbol{\Theta} \) exhibits a tridiagonal Toeplitz structure, where the diagonal entries are given by:
+	\begin{equation*}
+		\theta_{tt} = 
+		\begin{cases}
+			\dfrac{1}{\sigma^2(1-0.95^2)}, & t = 1, p, \\
+			\dfrac{1+0.95^2}{\sigma^2(1-0.95^2)}, & 2 \leq t \leq p-1.
+		\end{cases}
+	\end{equation*}
+	The off-diagonal entries are:
+	\begin{equation*}
+		\theta_{t, t+1} = \theta_{t+1, t} = -\dfrac{\rho}{\sigma^2(1-\rho^2)}, \quad 1 \leq t \leq p-1.
+	\end{equation*}
+	Finally, the functional predictors are smoothed using a B-spline basis with 15 basis functions, as described in Section \ref{subsec: Step 1: Computing Smoothed PLS components}.
+
+	\medskip
+	\noindent
+	\textit{Vector Predictors.}
+	We consider \( s \) vector predictors, each following a \( d \)-dimensional zero-mean Gaussian distribution with a shared precision matrix.
+This precision matrix, denoted as \( \Gamma := (\gamma_{ij}) \in \mathbb{R}^{d \times d} \), follows a Toeplitz structure with exponentially decaying entries, given by:
+	\begin{equation*}  
+		\gamma_{ij} := 0.5^{|i-j|}.
+	\end{equation*}
+
+	\medskip
+	\noindent
+	\textit{Graph Structure.}
+	We arrange five nodes   in a chain structure, where each node follows a sequential order, and the last node connects back to the first, as illustrated in Figure~\ref{fig:graph}.
+An edge in the graph indicates that the connected nodes remain correlated when the values of all other nodes are fixed.
+	The resulting marginal dependence structure is significantly more complex than the chain structure itself.
+We designate nodes \(F_1\) and \(F_2\) as functional predictors and nodes \(V_1\), \(V_2\), and \(V_3\) as vector predictors.
+	%
+	\begin{figure}
+		\centering
+		\includegraphics[width=0.4\linewidth]{image/graph}
+		\caption{}
+		\label{fig:graph}
+	\end{figure}
+	%
+	To introduce conditional dependencies between the components, we set the off-diagonal blocks of the precision matrix to be $0.5 \mathbf{1}$ if the corresponding components are connected in the graph, and zero otherwise.
+Here, $\mathbf{1}$ denotes a matrix of appropriate dimensions where all elements are equal to 1.
+Overall, we generate a $2p + 3d$-dimensional multivariate Gaussian distribution with mean zero and a precision matrix $\Omega$, structured as follows:
+
+	\[
+	\Omega =
+	\begin{pmatrix}
+		\Omega_{F} & 0.5 \mathbf{1} & 0 & 0 & 0.5 \mathbf{1} \\
+		0.5 \mathbf{1} & \Omega_{F} & 0.5 \mathbf{1} & 0 & 0 \\
+		0 & 0.5 \mathbf{1} & \Omega_{V} & 0.5 \mathbf{1} & 0 \\
+		0 & 0 & 0.5 \mathbf{1} & \Omega_{V} & 0.5 \mathbf{1} \\
+		0.5 \mathbf{1} & 0 & 0 & 0.5 \mathbf{1} & \Omega_{V} \\
+	\end{pmatrix}
+	\]
+
+	For each observation drawn from this multivariate Gaussian distribution, we process
+
+	The regression coefficients for the first functional predictor, $\beta_{F_1}$, are drawn from a multivariate normal distribution $N(0, 5 \mathbf{I}_p)$, with a fixed random seed.
+The coefficients for the second functional predictor, $\beta_{F_2}$, are drawn independently from the same distribution and are also smoothed using a B-spline basis with 10 basis functions.
+	For the vector covariates, the regression coefficients are sampled from $N(0, I_d)$.
+After calculating the inner product of the covariates and their corresponding coefficients, independent Gaussian noise from $N(0, 0.1^2)$ is added to the generated responses to simulate measurement noise.
+
+	The baseline methods are:
+	\begin{itemize}
+		\item Penalized functional regression (pfr)~\cite
+		{goldsmithPenalizedFunctionalRegression2011}\item Principal component regression (fpcr): run both of PCA for multple functional predictors~\cite{happ_multivariate_2018} and scalar PCA and run OLS on the PC scores.
+	\end{itemize}
+	% TODO: \usepackage{graphicx} required
+
+	We compare our method with these baseline methods using $p=100$.
+We consider scenarios with $d=1, 2, 3, 4, 5$ and $n = 100, 200, 300, 400$.
+For each scenario, we use 70\% of the data for training and evaluate prediction performance on the remaining 30\% test set, using the root prediction mean squared error as the evaluation metric.
+For our method and PCR, the maximum number of components are set as 20.
+The number of components is chosen by 5-fold cross validation.
+The results, summarized in Table~\ref{table
+	}, demonstrate that our method consistently outperforms the baseline methods across all scenarios.
+	\begin{figure}
+		\centering
+		\includegraphics[width=0.9\linewidth]{Screenshot 2025-02-25 125839.png}
+		\caption{Enter Caption}
+		\label{fig:enter-label}
+	\end{figure}
+
+	\section{Data Application}
+
+	\medskip
+	\noindent
+	\textit{Renal study data.}~
+	We applied our proposed hybrid functional PLS regression, along with other regression methods, to the Emory renal study data.
+The study collected data on 226 kidneys (left and right) from 113 subjects, including: (i) baseline renogram curves; (ii) post-furosemide renogram curves; (iii) ordinal ratings of kidney obstruction status (non-obstructed, equivocal, or obstructed) independently assessed by three nuclear medicine experts; (iv) eight kidney-level pharmacokinetic variables derived from radionuclide imaging; and (v) two subject-level variables (age and gender).
+The subjects had a mean age of 57.8 years (SD = 15.5; range = 18–83), with 54 males (48\%) and 59 females (52\%).
+The three experts unanimously classified 153 kidneys as non-obstructed, 5 as equivocal, and 40 as obstructed, while 28 kidneys had discrepant ratings.
+
+	The two renogram curves, (i) and (ii), were treated as functional predictors and smoothed using a B-spline basis of order 15.
+The remaining variables, excluding the diagnosis, were treated as scalar predictors.
+Given the nature of these variables, we assume they are correlated with the renogram curves but not entirely redundant, as they may contain additional useful information.
+Finally, the diagnoses provided by the three experts were averaged and transformed using a min-max logit transformation.
+We splitted the data into 70\% of training data and 30\% of testing data, and evalauted the prediction perforamnec by root mean squared error on the test data, normalized by the range of the test data response.
+
+	\subsection{}
+
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+	\bibliographystyle{apalike}
+	\bibliography{Reference}
+
+	\appendix
+
+	\section{Overview of Appendix}
+
+	\section{Notations}
+	\begin{itemize}
+		\item aaa
+	\end{itemize}
+	\section{Technical lemmas}
+
+	\subsection{old notations}
+
+	Then we can approximate the functional predictor observations as
+	\begin{equation*}
+		X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)=\mathbf{c}_i^{(k)T}\mathbf{b}^{(k)}(t_k), \;\; t_k \in [0,1], \;\; k=1, \ldots, K, \;\; i=1, \ldots, n,
+	\end{equation*}
+	This basis approximation can be expressed collectively across $n$ observations as: $\widetilde{\mathbf{X}^{(k)}}(t_k) = \widetilde{\mathbf{C}}^{(k)} \mathbf{b}^{(k)}(t_k)$, where $\widetilde{\mathbf{X}}^{(k)}(t_k)=(X_1^{(k)}(t_k), \ldots, X_n^{(k)}(t_k))^\top \in \mathbb{R}^n$,
+	This notation can be further extended to simultaneously express the basis expansions of $K$ functional predictors as 
+	\begin{equation}
+		\widetilde{X}(\mathbf{t}) = \widetilde{C}B(\mathbf{t}), \quad t \in \mathcal{T},
+		\label{eq: basis approximation of X}
+	\end{equation}
+	where $\widetilde{X}(\mathbf{t}) = [\widetilde{\mathbf{X}}^{(1)}(t_1), \cdots, \widetilde{\mathbf{X}}^{(K)}(t_K)] \in \mathbb{R}^{n \times K}$, $\widetilde{C} = [\widetilde{C}^{(1)}, \cdots, \widetilde{\mathbf{C}}^{(k)}] \in \mathbb{R}^{n \times MK}$, and
+	$B(\mathbf{t}) = \mathrm{blkdiag}[\mathbf{b}^{(1)}(t_1), \cdots, \mathbf{b}^{(K)}(t_K)] \in \mathbb{R}^{MK \times K}$.
+
+	Furthermore, let $
+	\mathbf{Z} = [\mathbf{Z}_1, \cdots, \mathbf{Z}_n]^\top \in \mathbb{R}^{n \times p}
+	$ denote $n \times p$ matrix of the scalar predictors (observed version when $l=1$, or residualized version when $l \ge 2$), and let $\widetilde{W}[\mathbf{t}]=[\widetilde{X}(\mathbf{t}), \mathbf{Z}]$ denote $n \times (K+p)$ hybrid predictor matrix that stacks $\widetilde{X}(\mathbf{t})$ and $\mathbf{Z}$ as columns.
+Then we can also write the hybrid predictor, whose functional part is approximated using the basis functions, as a form of linear transformation similar to \eqref{eq: basis approximation of X}:
+	\begin{equation}\label{eq: basis approximation of W}
+		\widetilde{W}[\mathbf{t}] 
+		=  
+		\widetilde{ \mathbf{C} }^\ast B^*[\mathbf{t}], \quad t \in \mathcal{T}.
+	\end{equation}
+	where  $B^*[\mathbf{t}] = \mathrm{blkdiag}(B(\mathbf{t}), \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (K+p)}$ and $\widetilde{ \mathbf{C} }^\ast=[\widetilde{C}, \mathbf{Z}] \in \mathbb{R}^{n \times (MK+p)}$.
+
+	\paragraph{Basis approximation of the PLS component.}
+	We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\xi[\mathbf{t}] = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$.
+	%
+
+	Using this definition, we construct the following block-diagonal matrices:
+	\begin{equation}\label{def:J_and_J_star}
+		\mathbf{J} = \mathrm{blkdiag}(\mathbf{J}^{(1)}, \cdots, \boldsymbol{\Phi}^{(k)}) \in \mathbb{R}^{MK \times MK}~\text{and}~\mathbf{J}^\ast=\mathrm{blkdiag}(\mathbf{J}, \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (MK+p)}.
+	\end{equation}
+
+	\paragraph{Regularization based on second-order derivatives.}
+	Our proposed strategy for computing PLS component, detailed in Section \ref{sec: Regularization of PLS Components}, incorporates regularization based on second-order derivatives.
+To this end, let $\ddot{J}^{(k)}$ denote the $M \times M$ Gram matrix formed by the second derivatives of the basis functions,  defined as
+	\begin{equation}\label{def:dodot_J_k}
+		\ddot{J}^{(k)} = \left[ \int_0^1 \ddot{b}^{(k)}_m(t) \ddot{b}^{(k)}_n(t) \, dt \right]_{m,n=1}^M.
+	\end{equation}
+	and define a block-diagonal matrix 
+	$ \ddot{J}^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)}$ as
+	\begin{equation}\label{def:J_dotdot_ast}
+		\ddot{J}^\ast=\mathrm{blkdiag}(\ddot{J}^{(1)}, \cdots, \ddot{J}^{(K)}, 0_{p \times p}).
+	\end{equation}
+	%
+	The finite-basis approximation allows us to represent the hybrid predictor observations using the coefficient matrix $\widetilde{ \mathbf{C} }^\ast$, enabling all associated computations to be carried out via matrix operations involving $\widetilde{ \mathbf{C} }^\ast$, $J^\ast$, and $\ddot{J}^\ast$.
+
+	\section{Proof of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:eigen_regul} }\label{section:proof:proposition:linear_noregul_system_unregularized}
+	\begin{proof}
+	Let $\xi = (\xi_1, \ldots, \xi_K, \boldsymbol{\xi}_{K+1}) \in \mathcal{H}$.
+Assume that each functional component $\xi_j \in L^2([0,1])$ lies in the span of the basis functions ${b_1(t), \ldots, b_M(t)}$ and can be written as
+	\begin{equation*}
+		\xi_j(t) := 
+		\sum_{m=1}^M d_{jm} \, b_m(t), \quad j = 1, \ldots, K,
+	\end{equation*}
+	with coefficient vectors $\boldsymbol{\gamma}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$.
+	Then, 
+	the empirical covariance is
+	computed as follows:
+	\begin{align*}
+		\widehat{\textnormal{Cov}} (
+		\langle \widetilde{W}, \xi  \rangle_{\mathcal{H}}, Y 
+		) 
+		&=  %1
+		\frac{1}{n} 
+		\sum 
+		\limits_{i=1}^n 
+		y_i
+		\langle \widetilde{W}_i, \xi \rangle_\mathcal{H} \\
+		&= %2
+		\frac{1}{n} 
+		\sum \limits_{i=1}^n
+		y_i
+		\biggl(
+		\sum_{j=1}^K
+		\langle \widetilde{X}_{ij}, \xi_j \rangle  
+		+
+		\mathbf{Z}_i^\top 
+		\boldsymbol{\xi}_{K+1} 
+		\biggr)
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\\&= %3
+		\frac{1}{n}
+		\sum
+		\limits_{i=1}^n 
+		y_i
+		\biggl( \sum \limits_{k=1}^K \int_0^1 \widetilde{X}_{ij}(t) \, \xi_j(t) \, dt \biggr)
+		+
+		\frac{1}{n}
+		\sum
+		\limits_{i=1}^n
+		y_i
+		( \mathbf{Z}_i^\top \boldsymbol{\xi}_{K+1} )
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\\&=  
+		\frac{1}{n} \sum \limits_{i=1}^n 
+		y_i
+		\biggl\{ 
+		\sum \limits_{k=1}^K \int_0^1
+		\biggl(
+		\sum_{m=1}^M \theta_{ijm} b_{m}(t) 
+		\biggr) 
+		\biggl(
+		\sum_{m'=1}^M d_{jm'} b_{m'}(t) 
+		\biggr) 
+		dt
+		\biggr\}  
+		+
+		\frac{1}{n}
+		\mathbf{y}^\top
+		Z \boldsymbol{\xi}_{K+1} 
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\\&=  
+		\frac{1}{n} \sum \limits_{i=1}^n 
+		y_i
+		\biggl\{ 
+		\sum \limits_{k=1}^K 
+		\sum_{m=1}^M
+		\sum_{m'=1}^M  
+		\theta_{ijm}
+		d_{jm'}
+		\int_0^1
+		b_{m}(t) 
+		b_{m'}(t) 
+		dt
+		\biggr\}  
+		+
+		\frac{1}{n}
+		\mathbf{y}^\top
+		Z \boldsymbol{\xi}_{K+1} 
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\\&=  
+		\sum \limits_{k=1}^K 
+		\biggl\{
+		\frac{1}{n} \sum \limits_{i=1}^n 
+		y_i
+		(
+		\boldsymbol{\theta}_{ij}^\top
+		B
+		\boldsymbol{\gamma}_j
+		)  
+		\biggr\}
+		+
+		\frac{1}{n}
+		\mathbf{y}^\top
+		Z \boldsymbol{\xi}_{K+1}
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\\&=  
+		\frac{1}{n}
+		\biggl(
+		\sum \limits_{k=1}^K 
+		\mathbf{y}^\top
+		\Theta_{j}
+		B
+		\boldsymbol{\gamma}_j
+		+
+		\mathbf{y}^\top
+		Z \boldsymbol{\xi}_{K+1} 
+		\biggr)
+	\end{align*}	
+	Building on this computation, the squared empirical covariance is
+expressed as the quadratic form involving the matrix $V$ defined in \eqref{def:V_matrix}:
+%	The objective function matches that of \eqref{eq: Regularized generalized rayleigh quotient equation}, takin
+	\begin{align*}
+		\widehat{\textnormal{Cov}}^2 (
+		\langle \widetilde{W}, \xi  \rangle_{\mathcal{H}}, Y 
+		)  
+		&= 
+		\frac{1}{n^2}
+		\biggl(
+		\sum \limits_{k=1}^K 
+		\mathbf{y}^\top
+		\Theta_{j}
+		B
+		\boldsymbol{\gamma}_j
+		+
+		\mathbf{y}^\top
+		Z \boldsymbol{\xi}_{K+1} 
+		\biggr)^2
+		%%%%%%%%%%%%%%%%%%%%
+	\\	&=
+		\frac{1}{n^2} 
+		(
+		\mathbf{y}^\top
+		\Theta
+		\mathbb{B}  
+		\boldsymbol{\xi}
+		)^2
+		\\
+		&	= 
+		\frac{1}{n^2} 
+		\boldsymbol{\xi}^\top
+		(\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top 
+		\boldsymbol{\xi}
+		\\&=
+		\boldsymbol{\xi}^\top
+		V 
+		\boldsymbol{\xi}.
+		\numberthis \label{covariance_squares_as_quadratic_form}
+	\end{align*}
+	The squared norm of $\xi$ in the hybrid Hilbert space $\mathcal{H}$ 
+	%can be expressed as the inner product on $(\mathbb{R}^M)^K \times \mathbb{R}^p$ defined in Lemma~\ref{lemma:valid_inner_product_tuple} as follows:
+	is computed as follows:
+	\begin{align*}
+		\langle {\xi},{\xi} \rangle_{\mathcal{H}}
+		&=
+		\sum_{j=1}^K
+		\langle
+		\xi_j, \xi_j
+		\rangle
+		+
+		\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1}
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\\&=
+		\sum \limits_{j=1}^K \int_0^1
+		\biggl(
+		\sum_{m=1}^M d_{jm} b_{m}(t) 
+		\biggr) 
+		\biggl(
+		\sum_{m'=1}^M d_{jm'} b_{m'}(t) 
+		\biggr) 
+		dt
+		+
+		\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1}  
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\\&=
+		\sum \limits_{j=1}^K 
+		\sum_{m=1}^M
+		\sum_{m'=1}^M
+		d_{jm}
+		d_{jm'}
+		\int_0^1
+		b_{m}(t) 
+		b_{m'}(t) 
+		dt
+		+
+		\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1}
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\\&=
+		\sum \limits_{j=1}^K 
+		\boldsymbol{\gamma}_j^\top
+		B
+		\boldsymbol{\gamma}_j
+		+
+		\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1},
+%%%%%%%%%%%%%
+\\&=
+\boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi}
+\numberthis \label{unit_norm_as_quadform}
+	\end{align*}
+Therefore, the covariance maximization problem \eqref{def:maximizer_squared_empirical_cov} is equivalent to the generalized Raleigh quotient \eqref{eq: Unregularized generalized rayleigh quotient equation}.
+This completes  the proof of Proposition~\ref{proposition:eigen_noregul}.
+
+Now we prove Proposition \ref{proposition:eigen_regul}.
+The penalization term 
+$\sum \limits_{j=1}^K \lambda_j 
+\operatorname{PEN}(\xi_K)$
+can be written in matrix form as:
 \begin{align*}
@@
 \end{align*}
-where $\boldsymbol{\xi}$ is the concatenated coefficient vector form of $\xi$ as defined in \eqref{def:maximizer_euclidean_form}, $\mathbb{B}^{\prime\prime}$ is defined in \eqref{def:gram_block}, and $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is given by
-\begin{equation}\label{def:Lambda}
-	\Lambda := \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p}),
-\end{equation}
-where $0_{p \times p}$ denotes the $p \times p$ zero matrix.
-
-\medskip
-\noindent
-\textit{Proposed estimation procedure.}~
-However, the above approach of \citet{Rice1991} assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense.
-As an alternative, we adopt the strategy of \citet{Silverman1996}, which replaces the standard orthonormality constraint with a weaker one based on a modified inner product that incorporates roughness.
-Accordingly, our estimation procedure at the $l$-th iteration, iteration index omitted and assuming the observations have been residualized in previous steps, solves the following optimization problem:
-	\begin{equation}\label{def:maximizer_squared_empirical_cov_reg}
-	\hat{\xi} 
+where $\boldsymbol{\xi}$ is the concatenated coefficient vector form of $\xi$ as defined in \eqref{def:maximizer_euclidean_form}, $\mathbb{B}^{\prime\prime}$ is defined in \eqref{def:gram_block}, and $\Lambda$ is defined in \eqref{def:Lambda}.
+
+Combining this with \eqref{unit_norm_as_quadform}, 
+we can compute
+\begin{equation*}
+	\| \xi  \|_\mathcal{H} +  \sum \limits_{j=1}^K \lambda_j 
+	\operatorname{PEN}(\xi_K) 
 	= 
-	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1}
-	)
-	:= \arg \max_{\xi \in \widetilde{\mathcal{H}}
-	}~\widehat{\textnormal{Cov}}^2 
-	\bigl(
-	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
-	\bigr)~s.t.~\| \xi  \|_\mathcal{H} +  \sum \limits_{j=1}^K \lambda_j 
-	\operatorname{PEN}(\xi_K) = 1.
-\end{equation}
-This formulation maximizes the squared covariance over a class of smooth functions.
-Proposition~\ref{proposition:eigen_regul} expresses this problem as a generalized Rayleigh quotient.
-
-\begin{proposition}\label{proposition:eigen_regul}
-	Let
-	$
-	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
-	$
-	denote the observed data defined in \eqref{def:problem_instance}.
-	At the $l$-th iteration of the PLS algorithm, the maximizer of  the squared empirical covariance defined in \eqref{def:maximizer_squared_empirical_cov_reg}, represented as the Euclidean vector form as in \eqref{def:maximizer_euclidean_form},
-	is obtained by solving 
-	\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
-		\left(
-		\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
-		\right)^\top
+	\boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi}
+	+ 
+	\boldsymbol{\xi}^{\top} \Lambda \mathbb{B}^{\prime \prime} \boldsymbol{\xi}
 	=
-		\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
-		\quad \text{s.t.} \quad \boldsymbol{\xi}^\top (\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1.
-	\end{equation}
-	where we recall that $
-		V = n^{-2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top$ is defined in  \eqref{def:V_matrix}.
-\end{proposition}
-	The proof of Proposition \ref{proposition:eigen_regul} is provided in Appendix \ref{section:proof:eigenproblem_derivation}.
-	Here, $\lambda_k$ $(k=1, \ldots, K)$ is a positive smoothing parameter that controls the trade-off between the goodness of fit and the amount of smoothness in $\psi^{(k)}$.
-Smaller $\lambda_k$ produces PLS components that fit more closely to the observed data, but selecting too small value may cause overfitting.
-The estimated PLS component reverts back to the unregularized version of Proposition \ref{proposition:eigen_noregul} when $\lambda_k=0$ for all $k$.
-On the other hand, larger $\lambda_k$ places more emphasis on smoothing $\psi^{(k)}$.
-In the limit $\lambda_k \rightarrow \infty$, each of the functions is forced to be of the form $\psi^{(k)}(t)=a+bt$ for some constants $a$ and $b$.
-In practice, $\{\lambda_k\}_{k=1}^K$ as well as the number of PLS components $L$ to be estimated can be chosen by cross-validation based on a certain predictive performance criterion (e.g., mean squared error).
-
-	The constraint $\xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1$ enforces the following modified orthonormality of the estimated PLS components ($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ which now takes into account the roughness of the functions:
-	\begin{align*}
-		\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
-		&= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right \rangle_{L^2} \\
-		&= \sum \limits_{k=1}^K \int_0^1 \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_0^1 \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
-		& = \mathbb{1}(l=j). 
-	\end{align*}
-	This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{sec: Properties of the Proposed PLS Framework} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.
-
-	To solve \eqref{eq: Regularized generalized rayleigh quotient equation} in practice, we first perform a Choleski factorization: $L L^\top = J^\ast + \Lambda \ddot{J}^\ast$, where $L$ is a lower triangular matrix, and then reduce it to maximizing the classical Rayleigh quotient problem:
-	\begin{equation*}
-		\max \limits_{\mathbf{e} \in \mathbb{R}^{MK + p}} \, \frac{\mathbf{e}^\top E \mathbf{e}}{\mathbf{e}^\top \mathbf{e}} \; \Longleftrightarrow \;   \max \limits_{\substack{\mathbf{e} \in \mathbb{R}^{MK+p}}} \;  \mathbf{e}^\top E \mathbf{e} \quad \textnormal{subject to} \quad \Vert \mathbf{e} \Vert^2 = 1
-	\end{equation*}
-	through the transformations $\mathbf{e} = L^\top \xi^*$ and $E = L^{-1} \mathbf{V}^\ast L^{\top-1}$.
-Once $\mathbf{e}$ is obtained as the first eigenvector of $E$, we set $\xi^* = L^{\top-1} \mathbf{e}$ and $\widehat{\xi}[\mathbf{t}] = B^*[\mathbf{t}]^\top \xi^*$.
-
-	\subsection{Step 2: Computing Residualized Predictors via Hybrid-on-Scalar Regression} \label{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}
-	The second step of the PLS algorithm involves iteratively obtaining the ($l+1$)-th residualized predictors as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$, where $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ is the least squares estimate from regressing the previous ($l$-th) residualized outcome $\mathbf{W}_i^{[l]}[\mathbf{t}]$ on the corresponding  estimated PLS score $\widehat{\rho}_{il}$.
-The pointwise least squares estimate, $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] = (\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \widehat{\rho}_{il})/(\sum_{i=1}^n \widehat{\rho}_{il}^2)$, presented in Section \ref{sec: Naive PLS Algorithm}, however, is  highly inefficient and may not be even feasible for multiple dense and/or irregular functional data.
-Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components.
-Therefore, in this section, we introduce a novel strategy based on a hybrid-on-scalar regression model for obtaining $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ and implementing the second step.
-
-	Again, we omit $l$ in the notations.
-Let $\widehat{\boldsymbol{\rho}}=(\widehat{\rho}_1, \ldots, \widehat{\rho}_n)^\top$ denote an $n$-dimensional vector of PLS scores estimated from the proposed algorithm, and let the $(K+P)$-vector $\boldsymbol{\delta}[\mathbf{t}] = [\pi(\mathbf{t})^\top, \boldsymbol{\gamma}^\top]^\top$ denote the regression coefficient consisting of the functional part $\pi(\mathbf{t}) = (\pi^{(1)}(t_1), \ldots,\pi^{(K)}(t_K))^\top \in \mathbb{R}^K$ and scalar part $\boldsymbol{\gamma} = (\gamma_1, \ldots,\gamma_p)^\top \in \mathbb{R}^p$.
-The hybrid-on-scalar regression model we are interested in fitting is then:
-	\begin{equation}
-		\widetilde{W}[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top + \mathbf{e}[\mathbf{t}],
-		\label{eq: hybrid on scalar regression model}
-	\end{equation}
-	where $\mathbf{e}[\mathbf{t}]$ is an $n \times (K+p)$ matrix of errors.
-
-	As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$.
-Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \boldsymbol{\gamma}^{(k)\top} \mathbf{b}^{(k)}(t_k)$, where $\boldsymbol{\gamma}^{(k)} = (d_1^{(k)}, \ldots, d_M^{(k)})\top \in \mathbb{R}^M$ are basis coefficients.
-Here, a different basis system can be flexibly chosen to expand the regression coefficient, but without loss of generality we use the same system as in Section \ref{subsec: Step 1: Computing Smoothed PLS components}.
-With the $(MK+p)$-dimensional row vector $\boldsymbol{\gamma}^* = (\boldsymbol{\gamma}^{(1)\top}, \ldots, \boldsymbol{\gamma}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as: $\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}]$.
-Finally, these basis expansions of the hybrid response and the regression coefficient enable us to re-write the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model} in a finite-dimensional form:
-	\begin{equation}
-		\widetilde{C}^* B^*[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] + \mathbf{e}[\mathbf{t}].
-		\label{eq: rewritten hybrid on scalar regression model}
-	\end{equation}
-
-	Based on the model formulation \eqref{eq: rewritten hybrid on scalar regression model}, we can now formulate the following least squares criterion whose minimizing solution gives the estimate of the regression coefficient $\boldsymbol{\delta}[\mathbf{t}]$ in the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model}:
-	\begin{equation}
-		\begin{aligned}
-			\textnormal{SSE}(\delta) &= \int_\mathcal{T} \left\Vert \,  \widetilde{C}^* B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] \, \right\Vert_F^2 \, d\mathbf{t}  \\
-			&= tr\left(\widetilde{C}^{*T}\widetilde{C}^*J^\ast \right) - 2\,tr \left(\boldsymbol{\gamma}^* J^\ast \widetilde{C}^{*T} \widehat{\boldsymbol{\rho}} \right) + tr\left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* J^\ast \boldsymbol{\gamma}^{*T}\right),
-		\end{aligned}
-		\label{eq: least squares}
-	\end{equation}
-	where $tr$ denotes the trace of a matrix, and $\Vert \cdot \Vert_F$ is a Frobenius norm.
-Now taking the derivative of \eqref{eq: least squares} with respect to $\boldsymbol{\gamma}^*$ and setting the result to zero, we find that  $\boldsymbol{\gamma}^*$ satisfies the system of linear equations
-	\begin{equation*}
-		\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^*  J^\ast =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast,
-	\end{equation*}
-	whose solutions lead to the following estimates of $\boldsymbol{\gamma}^*$ and $\boldsymbol{\delta}[\mathbf{t}]$:
-	\begin{equation*}
-		\widehat{\boldsymbol{\gamma}}^*  =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast \left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} J^\ast \right)^{-1} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}[\mathbf{t}] = B^*[\mathbf{t}]^\top \, \widehat{\boldsymbol{\gamma}}^{*\top}.
-	\end{equation*}
-	Then, we can use $\widehat{\boldsymbol{\delta}}[\mathbf{t}]$ to obtain the subsequent residualized hybrid predictor as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$.
-
-	The step for obtaining the subsequent residualized response is identical to that of the naive PLS algorithm in  in Section \ref{sec: Naive PLS Algorithm}.
-Specifically, the $(l-1)$-th residualized response can be obtained as $Y_i^{[l+1]} = Y_i^{[l]} - \widehat{\nu}_l \widehat{\rho}_{il}$, where $\widehat{\nu}_l = \sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}/\sum_{i=1}^n \widehat{\rho}_{il}^2$  is the least square estimate of the simple linear model regressing $Y_i^{[l]}$ on $\widehat{\rho}_{il}$.
-
-	\subsection{Obtaining the Estimated Hybrid Regression Coefficient}
-	\label{subsec: Obtaining the Estimated Hybrid Regression Coefficient}
-	The regression coefficient $\boldsymbol{\eta}$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS components and scores.
-First, note that we can show $\widehat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} = \langle \mathbf{W}_i, \widehat{\boldsymbol{\zeta}}_l \rangle_\mathcal{H}$, where $\widehat{\boldsymbol{\zeta}}_l = \widehat{\xi}_l - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}_u, \widehat{\xi}_l \rangle_{\mathcal{H}} \widehat{\boldsymbol{\zeta}}_u$ for $l \ge 2$, with $\widehat{\boldsymbol{\zeta}}_1 = \widehat{\xi}_1$.
-Then, the decomposition of $Y_i$ in \eqref{eq: decomposition} leads to
-	\begin{equation*}
-		Y_i = \sum \limits_{l=1}^L \widehat{\nu}_l \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l \right\rangle_\mathcal{H}+\epsilon_i,
-	\end{equation*}
-	which, given the uniqueness of $\boldsymbol{\eta}$, leads to
-	\begin{equation*}
-		\widehat{\boldsymbol{\eta}} = \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l.
-	\end{equation*}
-	Here, the number of PLS components $L$ to be estimated can be chosen by cross-validation.
-
-	\begin{algorithm}[b!]
-		\caption{Hybrid PLS (under construction)}
-		\label{alg:main}
-		\begin{algorithmic}[1]
-			\Require 
-			Response $\mathbf{y} \in \mathbb{R}^n$,
-			%functional predictor evalulation points $\mathbf{t}_1, \ldots, \mathbf{t}_m \in [0,1]^K,$
-			hybrid predictors approximation coefficient
-			$\widetilde{C}^* \ \in \mathbb{R}^{n \times (MK+p)} $ \eqref{eq: basis approximation of W},
-			Gram matrix with respect to basis functions
-			$J^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)} $
-			\eqref{def:J_and_J_star},
-			Gram matrix with respect to second derivatives of the basis functions 
-			$\ddot{J}^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)}$
-			\eqref{def:J_dotdot_ast},
-			regularization matrix $\Lambda  \in \mathbb{R}^{(MK+p) \times (MK+p)}$ \eqref{def:Lambda}
-			%%%%%%%%%%%%%%%%%%%%%
-			\State
-			$\widetilde{C}^{*[1]} \leftarrow \widetilde{C}^*$
-			\For{ l = 1, 2, \ldots  $T$}
-			\State $\mathbf{V}^\ast \leftarrow n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast$
-			\Comment{ \eqref{def:V_star}}
-			\State 	$\widehat{\xi}_l^\ast \leftarrow \arg \max_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1
-			$
-			\Comment{ \eqref{eq: Regularized generalized rayleigh quotient equation}} 
-			\State $\widehat{\boldsymbol{\rho}}_l
-			\leftarrow 
-			\widetilde{C}^* J^\ast  \widehat{\xi}_l^\ast
-			$
-			\Comment{$\in \mathbb{R}^n$; \eqref{compute_pls_score}}
-			\EndFor
-			\State Output a
-		\end{algorithmic}
-	\end{algorithm}
-
-	\subsection{Data Preprocessing} \label{subsec: Data Preprocessing}
-	Functional and scalar elements of the hybrid predictors often have incompatible units and/or exhibit different amounts of variation.
-This can be problematic for our PLS framework which is not scale invariant as: i) each predictor has different chance of contributing to the predictor/response structure; and ii) a predictor with high correlation to $Y$ but relatively low variance may be overlooked.
-
-	To obtain PLS components that have a meaningful interpretation, we standardize the predictor data via the following steps.
-The first step is to account for discrepancies \textit{within} respective functional and scalar parts, if needed.
-If elements of multivariate functional data $X_i = (X_i^{(1)}, \ldots, X_i^{(K)})$ are measured in different units or have quite different domains, one can standardize them to have mean zero and integrated variance of one.
-If multivariate scalar predictors $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ exhibit different amounts of variation, one can standardize them to have mean zero and unit variance.
-The second step is to eliminate the discrepancies \textit{between} functional and scalar parts.
-To accomplish this aim, we choose an appropriate weight $\omega$ in the hybrid inner product \eqref{eq: hybrid inner product} that ensures functional and vector parts have comparable variance.
-A sensible data-driven approach to choosing an appropriate weight is to set
-	\begin{equation*}
-		\omega = \frac{\sum_{i=1}^n \Vert X_i \Vert_\mathcal{F}^2}{\sum_{i=1}^n \Vert \mathbf{Z}_i \Vert^2},
-		\label{eq: weight}
-	\end{equation*}
-	In practice, this weighting scheme can be implemented by formulating the hybrid object as $\mathbf{W} = (X, \omega^{1/2} \mathbf{Z})$, whose vector part has been scaled by a factor of $\omega^{1/2}$.
-
-	\section{Properties of the Proposed PLS Framework}
-	\label{sec: Properties of the Proposed PLS Framework}
-	In this section, we derive some of the theoretical and geometric properties of the proposed PLS framework.
-
-	\subsection{Tucker's Criterion}
-	We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
-We omit $l$ in the notations and first define the cross-covariance terms between the response and predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$):
-	\begin{equation*}
-		\begin{gathered}
-			\sigma_{YX} = (\sigma_{YX}^{(1)}, \ldots, \sigma_{YX}^{(K)}) = (E(YX^{(1)}),\ldots, E(YX^{(K)})) = E(YX) \in \mathcal{F} \\
-			\sigma_{YZ} = (\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top = (E(YZ_1),\ldots, E(YZ_p))^\top = E(Y\mathbf{Z}) \in \mathbb{R}^p \\
-			\Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) =  (E(YX), E(Y\mathbf{Z}))=E(Y\mathbf{W}) \in \mathcal{H}
-		\end{gathered}
-	\end{equation*}
-	We also introduce two cross-covariance operators, $\mathcal{C}_{YW}=E(\mathbf{W} \otimes_\mathcal{H} Y): \mathcal{H} \rightarrow \mathbb{R}$ and $\mathcal{C}_{WY}=E(Y \otimes \mathbf{W}): \mathbb{R} \rightarrow \mathcal{H}$, which respectively map $h=(f, \mathbf{v}) \in \mathcal{H}$ to $\mathbb{R}$ and $d \in \mathbb{R}$ to $\mathcal{H}$ as follows:
-	\begin{align*}
-		& \mathcal{C}_{YW} \mathbf{h} = E\{\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX}^{(k)}(t_k) f^{(k)}(t_k) dt_k + E(Y \mathbf{Z}^\top) \mathbf{v} \\
-		& \mathcal{C}_{WY} d = E (\langle Y, d \rangle \mathbf{W} ) = E(Y\mathbf{W})d =  \Sigma_{YW} \, d. 
-	\end{align*}
-
-	Now define a new operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$, which performs the following mapping:
-	\begin{equation*}
-		\mathcal{U} \mathbf{h} =  \mathcal{C}_{WY} ( \mathcal{C}_{YW} \mathbf{h}) 
-		= \mathcal{C}_{YW} (\langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}) 
-		=  \Sigma_{YW} \, \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = (\Sigma_{YW} \otimes \Sigma_{YW})\mathbf{h}.
-	\end{equation*}
-	In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$. The following proposition presents several important properties of $\mathcal{U}$.
-	\begin{proposition} \label{Proposition: property of U}
-		The operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}= \Sigma_{YW} \otimes \Sigma_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ is positive and self-adjoint.
-Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that
-		\begin{align}
-			\max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in [0,1]} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
-		\end{align}
-		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in [0,1]$ with $|t_k - t_k^* | < \delta_k$, we have that
-		\begin{equation*}
-			|\sigma_{yx}^{(k)}(t_k) - \sigma_{yx}^{(k)}(t_k^*) | < \epsilon,
-		\end{equation*}
-		then $\mathcal{U}$ is a compact operator.
-	\end{proposition}
-	The proof of Proposition \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
-	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
-
-	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
-	\begin{proposition}\label{proposition: eigenanalysis}
-		\begin{equation*}
-			\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)
-		\end{equation*}
-		is achieved when $\xi$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.	
-	\end{proposition}
-	The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
-	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.
-
-	\subsection{Geometric Properties}
-	In this section, we derive several geometric properties of the PLS components and and scores obtained from the proposed algorithm.
-
-	The following proposition states that the PLS components estimated from Proposition  \ref{proposition:eigen_regul} are orthonormal with respect to the modified inner product $\langle \langle \cdot \rangle \rangle$ that incorporates the roughness of the functions.
-	\begin{proposition}\label{proposition: modified orthnormality of PLS components}
-		The estimated PLS components, $\widehat{\xi}_1, \widehat{\xi}_2, \ldots, \widehat{\xi}_L$, from the proposed PLS algorithm are mutually orthonormal with respect to the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ in $\mathcal{H}$ that incorporates the roughness of the functions; i.e.,
-		\begin{equation*}
-			\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
-			= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}
-			= \mathbb{1}(l=j). 
-		\end{equation*}
-	\end{proposition}
-	The proof of Proposition \ref{proposition: modified orthnormality of PLS components} is provided in Appendix \ref{section:proof:proposition: modified orthnormality of PLS components}.
-	Now let $\widehat{\boldsymbol{\rho}}_l=(\widehat{\rho}_{1l}, \ldots, \widehat{\rho}_{nl})^\top$ denote the $n$-dimensional vector whose elements consist of estimated $l$-th PLS scores ($l=1, \ldots, L)$ of $n$ observations.
-The next proposition states that the vectors of estimated PLS scores $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$ obtained from the proposed algorithm are mutually orthogonal.
-	\begin{proposition}	\label{proposition: orthnormality of PLS scores}
-		The vectors of estimated PLS scores, $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$, obtained from the proposed PLS algorithm are mutually orthogonal in the sense that
-		\begin{equation*}
-			\widehat{\boldsymbol{\rho}}_l^\top \widehat{\boldsymbol{\rho}}_j= 0 \quad \textnormal{for} \quad \; l,j \in \{1, \ldots, L\}, \; l \ne j. 
-		\end{equation*}
-	\end{proposition}
-	The proof of Proposition \ref{proposition: orthnormality of PLS scores} is provided in Appendix \ref{section:proof:proposition: orthnormality of PLS scores}.
-
-	\section{Simulations}
-	To evaluate the superiority of our method under complex dependency structures
-	{\textemdash}
-	specifically, dependencies among functional predictors,
-	among scalar predictors,
-	and between scalar and functional predictors
-	{\textemdash}
-
-	\medskip
-	\noindent
-	\textit{Matrix-normal setting.}
-	We begin by constructing predictors from a matrix-normal distribution, a framework that offers convenient and flexible control over the dependence structure across both rows and columns.
-Matrix-normal (MN) models, also known as Kronecker-separable covariance models, provide a principled approach to modeling multivariate data with structured covariance.
-Specifically, the matrix-normal distribution is defined as
-	\begin{equation*}
-		\mathbf{X} \sim \mathcal{MN}_{m \times n}(\mathbf{M}; \mathbf{R}, \mathbf{C}),
-	\end{equation*}
-	and its log-density is given by
-	\[
-	\log p(\mathbf{X} \mid \mathbf{M}, \mathbf{R}, \mathbf{C}) = -\frac{mn}{2} \log(2\pi) - \frac{m}{2} \log |\mathbf{C}| - \frac{n}{2} \log |\mathbf{R}| - \frac{1}{2} \mathrm{Tr}\left[ \mathbf{C}^{-1} (\mathbf{X} - \mathbf{M})^\top \mathbf{R}^{-1} (\mathbf{X} - \mathbf{M}) \right].
-	\]
-	The key insight behind Kronecker separability is that if
-	$
-	\mathbf{Y} \sim \mathcal{MN}(\mathbf{M}, \mathbf{R}, \mathbf{C}),
-	$
-	then its vectorized form follows a multivariate normal distribution:
-	$
-	\mathrm{vec}(\mathbf{Y}) \sim \mathcal{N}(\mathrm{vec}(\mathbf{M}), \mathbf{C} \otimes \mathbf{R}),
-	$
-	where $\otimes$ denotes the Kronecker product and $\mathrm{vec}$ is the vectorization operator.
-
-	\begin{figure}[ht!]
-		\centering
-		\begin{subfigure}[b]{0.45\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{image/cor_strong.pdf}
-			\caption{Correlation Matrix - Strong Dependency}
-			\label{fig:cor_strong}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.45\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{image/cor_weak.pdf}
-			\caption{Correlation Matrix - Weak Dependency}
-			\label{fig:cor_weak}
-		\end{subfigure}
-
-		\vspace{0.5cm}  % Adjust vertical spacing
-
-		\begin{subfigure}[b]{0.45\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{image/graph_strong.pdf}
-			\caption{Graph Structure - Strong Dependency}
-			\label{fig:graph_strong}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.45\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{image/graph_weak.pdf}
-			\caption{Graph Structure - Weak Dependency}
-			\label{fig:graph_weak}
-		\end{subfigure}
-
-		\caption{Comparison of Correlation Matrices and Graph Structures under Strong and Weak Dependencies.}
-		\label{fig:correlation_graph_comparison}
-	\end{figure}
-
-	\begin{comment}
-		The goal of this simulation is to:
-		\begin{enumerate}
-			\item Utilize a graphical model to introduce a complex dependence structure.
-			\item Demonstrate that our method outperforms the penalized functional regression approach by \citet{goldsmithPenalizedFunctionalRegression2011}.
-			\item Show that our method exhibits superior performance as correlation strength increases.
-		\end{enumerate}
-
-		Our previous setup, presented in Section \ref{simul:meeting_feb}, appeared to achieve these objectives. However, we identified several limitations:
-		\begin{enumerate}
-			\item The resulting precision matrix was singular, requiring us to scale up the diagonal elements to compute its inverse.
-This adjustment disrupted the original AR(1) structure of the functional component, making it significantly less smooth.
-			\item Increasing conditional correlation did not consistently enhance the superiority of our method.
-		\end{enumerate}
-		To address these issues, I will explore alternative functional graphical model settings that exhibit a strong dependence structure—one substantial enough to be detected by statistical methodologies and validated by top statistical journal papers.
-I will evaluate the performance of penalized functional regression on these data-generating models.
-		Among them, I will select three to four settings for comparison against other methods.
-	\end{comment}
-	Building on the functional graphical model simulation of \citet{zhuBayesianGraphicalModels2016}, we generate a mixed graphical model with five nodes, described as follows:  
-	\begin{itemize}
-		\item Nodes F1 and F2: Two functional predictors modeled as Gaussian processes using a truncated Karhunen-Loève expansion, where the eigenbasis consists of Fourier basis functions with a fixed number of basis functions, \(M = 9\).
-		\item  Nodes S1, S2, and S3: Three scalar predictors, each following an \(s\)-dimensional multivariate normal distribution.
-Unlike the functional predictors, these scalar predictors are modeled directly without basis expansion.
-	\end{itemize}
-	To capture dependencies among predictors, we introduce a graph structure that governs their conditional correlations.
-We consider two types of graph structures: a weakly connected graph and a strongly connected graph.
-In the Gaussian process framework, the precision matrix \(\mathbf{R}_0^{-1}\) encodes conditional independence relationships, while its inverse, \(\mathbf{R}_0\), represents marginal covariances.
-This structure extends to a blockwise correlation matrix \(\mathbf{R} \in \mathbb{R}^{(2M + 3s) \times (2M + 3s)}\), where off-diagonal blocks represent correlations between FPC scores and scalar predictor values.
-	Each block \((i, j)\) of \(\mathbf{R}\) is given by \((R_0)_{ij} \mathbf{I}_{M_i, M_j}\), where \(\mathbf{I}_{M_i, M_j}\) is a rectangular identity matrix.
-Here, \(M_i = 9\) if node \(i\) corresponds to a functional predictor and \(M_j = s\) if node \(j\) corresponds to a scalar predictor.
-
-	For each functional predictor, we assgin  \(M\) reference eigenvalues (or FPC score) drawn independently from gamma distributions with decreasing means.
-	These reference eigenvalues will later be multiplies by randomly  multiplier drawn from correlated multivaraite Normal distribution.
-These reference eigenvalues are fixed over all samples and all independent repetition of the experiment.
-We draw it one randomly just to ensure the differentiation between the two functional predictors.
-	we independently draw for each functional predictor from .
-We then sample zero-mean multivariate normal data from the covariance matrix \(\mathbf{R}\).
-The last \(3s\) components are assigned as scalar predictors, while the first \(2M\) components, scaled by their corresponding eigenvalues, serve as FPC scores.
-These scores are then expanded into functional data, evaluated over 100 equally spaced points on \([0,1]\) using a Fourier basis.
-
-	Finally, we introduce structured variability by adding a common mean function, defined as a scaled and shifted sine function.
-To visualize the generated data, Figure \ref{fig:correlation_graph_comparison}  plots functional predictor realizations and heatmaps of sample correlation matrices for both graph structures, illustrating the distinct dependency patterns induced by the precision matrices.
-
-	\subsection{Simulation shown in february 2025 meeting}\label{simul:meeting_feb}
-	To effectively manage the dependencies among functional predictors, scalar covariates, and between functional and scalar predictors, we utilize a Gaussian Markov random field (GMRF) within the framework of Gaussian undirected graphical models.
-In a GMRF, the off-diagonal elements of the precision matrix capture the conditional correlations between the corresponding components.
-Given that our setting involves both functional and scalar covariates, we adopt the simulation setup proposed by \cite{kolar_graph_2014}, which focuses on mixed attribute Gaussian graphical models.
-
-	We construct a graph consisting of two functional predictor nodes and three vector predictor nodes. Below, we sequentially describe the graph structure and the generation process for each node.
-
-	\medskip
-	\noindent
-	\textit{Functional Predictors.}
-	We consider two functional predictors that share the same precision matrix.
-Denoted as \( \boldsymbol{\Theta} := (\theta_{t \tilde{t}}) \in \mathbb{R}^{p \times p} \), this precision matrix follows an AR(1) structure with a white noise variance of \( 0.1^2 \) and an autoregressive coefficient of \( = 0.95 \), ensuring a smooth functional trajectory.
-
-	More formally, each functional predictor is evaluated at \( p \) equally spaced points on \( [0,1] \), with values defined recursively as:
-	\begin{equation*}
-		X^{(k)}_i(0) = 0, \quad 
-		X^{(k)}_i(t)= \rho X^{(k)}_i(t-1) + \varepsilon_{itk}, \quad \varepsilon_{itk} \overset{\text{i.i.d.}}{\sim} \mathcal{N}(0, \sigma^2), \quad t = 1, \dots, p,~i=1, \ldots, n,~k = 1,2.
-	\end{equation*}
-	In this setting, the precision matrix \( \boldsymbol{\Theta} \) exhibits a tridiagonal Toeplitz structure, where the diagonal entries are given by:
-	\begin{equation*}
-		\theta_{tt} = 
-		\begin{cases}
-			\dfrac{1}{\sigma^2(1-0.95^2)}, & t = 1, p, \\
-			\dfrac{1+0.95^2}{\sigma^2(1-0.95^2)}, & 2 \leq t \leq p-1.
-		\end{cases}
-	\end{equation*}
-	The off-diagonal entries are:
-	\begin{equation*}
-		\theta_{t, t+1} = \theta_{t+1, t} = -\dfrac{\rho}{\sigma^2(1-\rho^2)}, \quad 1 \leq t \leq p-1.
-	\end{equation*}
-	Finally, the functional predictors are smoothed using a B-spline basis with 15 basis functions, as described in Section \ref{subsec: Step 1: Computing Smoothed PLS components}.
-
-	\medskip
-	\noindent
-	\textit{Vector Predictors.}
-	We consider \( s \) vector predictors, each following a \( d \)-dimensional zero-mean Gaussian distribution with a shared precision matrix.
-This precision matrix, denoted as \( \Gamma := (\gamma_{ij}) \in \mathbb{R}^{d \times d} \), follows a Toeplitz structure with exponentially decaying entries, given by:
-	\begin{equation*}  
-		\gamma_{ij} := 0.5^{|i-j|}.
-	\end{equation*}
-
-	\medskip
-	\noindent
-	\textit{Graph Structure.}
-	We arrange five nodes   in a chain structure, where each node follows a sequential order, and the last node connects back to the first, as illustrated in Figure~\ref{fig:graph}.
-An edge in the graph indicates that the connected nodes remain correlated when the values of all other nodes are fixed.
-	The resulting marginal dependence structure is significantly more complex than the chain structure itself.
-We designate nodes \(F_1\) and \(F_2\) as functional predictors and nodes \(V_1\), \(V_2\), and \(V_3\) as vector predictors.
-	%
-	\begin{figure}
-		\centering
-		\includegraphics[width=0.4\linewidth]{image/graph}
-		\caption{}
-		\label{fig:graph}
-	\end{figure}
-	%
-	To introduce conditional dependencies between the components, we set the off-diagonal blocks of the precision matrix to be $0.5 \mathbf{1}$ if the corresponding components are connected in the graph, and zero otherwise.
-Here, $\mathbf{1}$ denotes a matrix of appropriate dimensions where all elements are equal to 1.
-Overall, we generate a $2p + 3d$-dimensional multivariate Gaussian distribution with mean zero and a precision matrix $\Omega$, structured as follows:
-
-	\[
-	\Omega =
-	\begin{pmatrix}
-		\Omega_{F} & 0.5 \mathbf{1} & 0 & 0 & 0.5 \mathbf{1} \\
-		0.5 \mathbf{1} & \Omega_{F} & 0.5 \mathbf{1} & 0 & 0 \\
-		0 & 0.5 \mathbf{1} & \Omega_{V} & 0.5 \mathbf{1} & 0 \\
-		0 & 0 & 0.5 \mathbf{1} & \Omega_{V} & 0.5 \mathbf{1} \\
-		0.5 \mathbf{1} & 0 & 0 & 0.5 \mathbf{1} & \Omega_{V} \\
-	\end{pmatrix}
-	\]
-
-	For each observation drawn from this multivariate Gaussian distribution, we process
-
-	The regression coefficients for the first functional predictor, $\beta_{F_1}$, are drawn from a multivariate normal distribution $N(0, 5 \mathbf{I}_p)$, with a fixed random seed.
-The coefficients for the second functional predictor, $\beta_{F_2}$, are drawn independently from the same distribution and are also smoothed using a B-spline basis with 10 basis functions.
-	For the vector covariates, the regression coefficients are sampled from $N(0, I_d)$.
-After calculating the inner product of the covariates and their corresponding coefficients, independent Gaussian noise from $N(0, 0.1^2)$ is added to the generated responses to simulate measurement noise.
-
-	The baseline methods are:
-	\begin{itemize}
-		\item Penalized functional regression (pfr)~\cite
-		{goldsmithPenalizedFunctionalRegression2011}\item Principal component regression (fpcr): run both of PCA for multple functional predictors~\cite{happ_multivariate_2018} and scalar PCA and run OLS on the PC scores.
-	\end{itemize}
-	% TODO: \usepackage{graphicx} required
-
-	We compare our method with these baseline methods using $p=100$.
-We consider scenarios with $d=1, 2, 3, 4, 5$ and $n = 100, 200, 300, 400$.
-For each scenario, we use 70\% of the data for training and evaluate prediction performance on the remaining 30\% test set, using the root prediction mean squared error as the evaluation metric.
-For our method and PCR, the maximum number of components are set as 20.
-The number of components is chosen by 5-fold cross validation.
-The results, summarized in Table~\ref{table
-	}, demonstrate that our method consistently outperforms the baseline methods across all scenarios.
-	\begin{figure}
-		\centering
-		\includegraphics[width=0.9\linewidth]{Screenshot 2025-02-25 125839.png}
-		\caption{Enter Caption}
-		\label{fig:enter-label}
-	\end{figure}
-
-	\section{Data Application}
-
-	\medskip
-	\noindent
-	\textit{Renal study data.}~
-	We applied our proposed hybrid functional PLS regression, along with other regression methods, to the Emory renal study data.
-The study collected data on 226 kidneys (left and right) from 113 subjects, including: (i) baseline renogram curves; (ii) post-furosemide renogram curves; (iii) ordinal ratings of kidney obstruction status (non-obstructed, equivocal, or obstructed) independently assessed by three nuclear medicine experts; (iv) eight kidney-level pharmacokinetic variables derived from radionuclide imaging; and (v) two subject-level variables (age and gender).
-The subjects had a mean age of 57.8 years (SD = 15.5; range = 18–83), with 54 males (48\%) and 59 females (52\%).
-The three experts unanimously classified 153 kidneys as non-obstructed, 5 as equivocal, and 40 as obstructed, while 28 kidneys had discrepant ratings.
-
-	The two renogram curves, (i) and (ii), were treated as functional predictors and smoothed using a B-spline basis of order 15.
-The remaining variables, excluding the diagnosis, were treated as scalar predictors.
-Given the nature of these variables, we assume they are correlated with the renogram curves but not entirely redundant, as they may contain additional useful information.
-Finally, the diagnoses provided by the three experts were averaged and transformed using a min-max logit transformation.
-We splitted the data into 70\% of training data and 30\% of testing data, and evalauted the prediction perforamnec by root mean squared error on the test data, normalized by the range of the test data response.
-
-	\subsection{}
-
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-	\bibliographystyle{apalike}
-	\bibliography{Reference}
-
-	\appendix
-
-	\section{Overview of Appendix}
-
-	\section{Notations}
-	\begin{itemize}
-		\item aaa
-	\end{itemize}
-	\section{Technical lemmas}
-
-	\subsection{old notations}
-
-	Then we can approximate the functional predictor observations as
-	\begin{equation*}
-		X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)=\mathbf{c}_i^{(k)T}\mathbf{b}^{(k)}(t_k), \;\; t_k \in [0,1], \;\; k=1, \ldots, K, \;\; i=1, \ldots, n,
-	\end{equation*}
-	This basis approximation can be expressed collectively across $n$ observations as: $\widetilde{\mathbf{X}^{(k)}}(t_k) = \widetilde{\mathbf{C}}^{(k)} \mathbf{b}^{(k)}(t_k)$, where $\widetilde{\mathbf{X}}^{(k)}(t_k)=(X_1^{(k)}(t_k), \ldots, X_n^{(k)}(t_k))^\top \in \mathbb{R}^n$,
-	This notation can be further extended to simultaneously express the basis expansions of $K$ functional predictors as 
-	\begin{equation}
-		\widetilde{X}(\mathbf{t}) = \widetilde{C}B(\mathbf{t}), \quad t \in \mathcal{T},
-		\label{eq: basis approximation of X}
-	\end{equation}
-	where $\widetilde{X}(\mathbf{t}) = [\widetilde{\mathbf{X}}^{(1)}(t_1), \cdots, \widetilde{\mathbf{X}}^{(K)}(t_K)] \in \mathbb{R}^{n \times K}$, $\widetilde{C} = [\widetilde{C}^{(1)}, \cdots, \widetilde{\mathbf{C}}^{(k)}] \in \mathbb{R}^{n \times MK}$, and
-	$B(\mathbf{t}) = \mathrm{blkdiag}[\mathbf{b}^{(1)}(t_1), \cdots, \mathbf{b}^{(K)}(t_K)] \in \mathbb{R}^{MK \times K}$.
-
-	Furthermore, let $
-	\mathbf{Z} = [\mathbf{Z}_1, \cdots, \mathbf{Z}_n]^\top \in \mathbb{R}^{n \times p}
-	$ denote $n \times p$ matrix of the scalar predictors (observed version when $l=1$, or residualized version when $l \ge 2$), and let $\widetilde{W}[\mathbf{t}]=[\widetilde{X}(\mathbf{t}), \mathbf{Z}]$ denote $n \times (K+p)$ hybrid predictor matrix that stacks $\widetilde{X}(\mathbf{t})$ and $\mathbf{Z}$ as columns.
-Then we can also write the hybrid predictor, whose functional part is approximated using the basis functions, as a form of linear transformation similar to \eqref{eq: basis approximation of X}:
-	\begin{equation}\label{eq: basis approximation of W}
-		\widetilde{W}[\mathbf{t}] 
-		=  
-		\widetilde{ \mathbf{C} }^\ast B^*[\mathbf{t}], \quad t \in \mathcal{T}.
-	\end{equation}
-	where  $B^*[\mathbf{t}] = \mathrm{blkdiag}(B(\mathbf{t}), \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (K+p)}$ and $\widetilde{ \mathbf{C} }^\ast=[\widetilde{C}, \mathbf{Z}] \in \mathbb{R}^{n \times (MK+p)}$.
-
-	\paragraph{Basis approximation of the PLS component.}
-	We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\xi[\mathbf{t}] = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$.
-	%
-
-	Using this definition, we construct the following block-diagonal matrices:
-	\begin{equation}\label{def:J_and_J_star}
-		\mathbf{J} = \mathrm{blkdiag}(\mathbf{J}^{(1)}, \cdots, \boldsymbol{\Phi}^{(k)}) \in \mathbb{R}^{MK \times MK}~\text{and}~\mathbf{J}^\ast=\mathrm{blkdiag}(\mathbf{J}, \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (MK+p)}.
-	\end{equation}
-
-	\paragraph{Regularization based on second-order derivatives.}
-	Our proposed strategy for computing PLS component, detailed in Section \ref{sec: Regularization of PLS Components}, incorporates regularization based on second-order derivatives.
-To this end, let $\ddot{J}^{(k)}$ denote the $M \times M$ Gram matrix formed by the second derivatives of the basis functions,  defined as
-	\begin{equation}\label{def:dodot_J_k}
-		\ddot{J}^{(k)} = \left[ \int_0^1 \ddot{b}^{(k)}_m(t) \ddot{b}^{(k)}_n(t) \, dt \right]_{m,n=1}^M.
-	\end{equation}
-	and define a block-diagonal matrix 
-	$ \ddot{J}^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)}$ as
-	\begin{equation}\label{def:J_dotdot_ast}
-		\ddot{J}^\ast=\mathrm{blkdiag}(\ddot{J}^{(1)}, \cdots, \ddot{J}^{(K)}, 0_{p \times p}).
-	\end{equation}
-	%
-	The finite-basis approximation allows us to represent the hybrid predictor observations using the coefficient matrix $\widetilde{ \mathbf{C} }^\ast$, enabling all associated computations to be carried out via matrix operations involving $\widetilde{ \mathbf{C} }^\ast$, $J^\ast$, and $\ddot{J}^\ast$.
-
-	\section{Proof of Proposition \ref{proposition:eigen_noregul} }\label{section:proof:proposition:linear_noregul_system_unregularized}
+		\boldsymbol{\xi}^\top 
+		(
+		\mathbb{B}
+	+
+	\Lambda \mathbb{B}^{\prime \prime})
+		 \boldsymbol{\xi}.
+\end{equation*}
+This computation along with \eqref{covariance_squares_as_quadratic_form} implies that the covariance maximization problem  
+ \eqref{def:maximizer_squared_empirical_cov_reg} is equivalent to the generalized Raleigh quotient \eqref{eq: Regularized generalized rayleigh quotient equation}.
+This completes  the proof of Proposition \ref{proposition:eigen_regul}.
+
+ \end{proof}
+
+ \section{Proof of Proposition  \ref{proposition:linear_noregul}}\label{section:proof:proposition:linear_noregul}
  \begin{proof}
-	Let $\xi = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta}) \in \mathcal{H}$.
-Assume that each functional component $\xi_j \in L^2([0,1])$ lies in the span of the basis functions ${b_1(t), \ldots, b_M(t)}$ and can be written as
-	\begin{equation*}
-		\xi_j(t) := 
-		\sum_{m=1}^M d_{jm} \, b_m(t), \quad j = 1, \ldots, K,
-	\end{equation*}
-	with coefficient vectors $\boldsymbol{\gamma}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$.
-	Then, the squared norm of $\xi$ in the hybrid Hilbert space $\mathcal{H}$ 
-	%can be expressed as the inner product on $(\mathbb{R}^M)^K \times \mathbb{R}^p$ defined in Lemma~\ref{lemma:valid_inner_product_tuple} as follows:
-	is computed as follows:
-	\begin{align*}
-		\langle {\xi},{\xi} \rangle_{\mathcal{H}}
-		&=
-		\sum_{j=1}^K
-		\langle
-		\xi_j, \xi_j
-		\rangle
-		+
-		\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		\\&=
-		\sum \limits_{j=1}^K \int_0^1
-		\biggl(
-		\sum_{m=1}^M d_{jm} b_{m}(t) 
-		\biggr) 
-		\biggl(
-		\sum_{m'=1}^M d_{jm'} b_{m'}(t) 
-		\biggr) 
-		dt
-		+
-		\boldsymbol{\zeta}^\top \boldsymbol{\zeta}  
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		\\&=
-		\sum \limits_{j=1}^K 
-		\sum_{m=1}^M
-		\sum_{m'=1}^M
-		d_{jm}
-		d_{jm'}
-		\int_0^1
-		b_{m}(t) 
-		b_{m'}(t) 
-		dt
-		+
-		\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		\\&=
-		\sum \limits_{j=1}^K 
-		\boldsymbol{\gamma}_j^\top
-		B
-		\boldsymbol{\gamma}_j
-		+
-		\boldsymbol{\zeta}^\top \boldsymbol{\zeta},
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		%\\&=\bigl \langle(\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K, \boldsymbol{\zeta}),(\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K, \boldsymbol{\zeta})\bigr\rangle_B.
-	\end{align*}
-	In a similar manner, the empirical covariance is
-	% expressed as the inner product on  defined in Lemma \ref{lemma:valid_inner_product_tuple} as follows:
-	computed as follows:
-	\begin{align*}
-		\widehat{\textnormal{Cov}} (
-		\langle \widetilde{W}, \xi  \rangle_{\mathcal{H}}, Y 
-		) 
-		&=  %1
-		\frac{1}{n} 
-		\sum 
-		\limits_{i=1}^n 
-		y_i
-		\langle \widetilde{W}_i, \xi \rangle_\mathcal{H} \\
-		&= %2
-		\frac{1}{n} 
-		\sum \limits_{i=1}^n
-		y_i
-		\biggl(
-		\sum_{j=1}^K
-		\langle \widetilde{X}_{ij}, \xi_j \rangle  
-		+
-		\mathbf{Z}_i^\top 
-		\boldsymbol{\zeta} 
-		\biggr)
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		\\&= %3
-		\frac{1}{n}
-		\sum
-		\limits_{i=1}^n 
-		y_i
-		\biggl( \sum \limits_{k=1}^K \int_0^1 \widetilde{X}_{ij}(t) \, \xi_j(t) \, dt \biggr)
-		+
-		\frac{1}{n}
-		\sum
-		\limits_{i=1}^n
-		y_i
-		( \mathbf{Z}_i^\top \boldsymbol{\zeta} )
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		\\&=  
-		\frac{1}{n} \sum \limits_{i=1}^n 
-		y_i
-		\biggl\{ 
-		\sum \limits_{k=1}^K \int_0^1
-		\biggl(
-		\sum_{m=1}^M \theta_{ijm} b_{m}(t) 
-		\biggr) 
-		\biggl(
-		\sum_{m'=1}^M d_{jm'} b_{m'}(t) 
-		\biggr) 
-		dt
-		\biggr\}  
-		+
-		\frac{1}{n}
-		\mathbf{y}^\top
-		Z \boldsymbol{\zeta} 
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		\\&=  
-		\frac{1}{n} \sum \limits_{i=1}^n 
-		y_i
-		\biggl\{ 
-		\sum \limits_{k=1}^K 
-		\sum_{m=1}^M
-		\sum_{m'=1}^M  
-		\theta_{ijm}
-		d_{jm'}
-		\int_0^1
-		b_{m}(t) 
-		b_{m'}(t) 
-		dt
-		\biggr\}  
-		+
-		\frac{1}{n}
-		\mathbf{y}^\top
-		Z \boldsymbol{\zeta} 
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		\\&=  
-		\sum \limits_{k=1}^K 
-		\biggl\{
-		\frac{1}{n} \sum \limits_{i=1}^n 
-		y_i
-		(
-		\boldsymbol{\theta}_{ij}^\top
-		B
-		\boldsymbol{\gamma}_j
-		)  
-		\biggr\}
-		+
-		\frac{1}{n}
-		\mathbf{y}^\top
-		Z \boldsymbol{\zeta}
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		\\&=  
-		\frac{1}{n}
-		\biggl(
-		\sum \limits_{k=1}^K 
-		\mathbf{y}^\top
-		\Theta_{j}
-		B
-		\boldsymbol{\gamma}_j
-		+
-		\mathbf{y}^\top
-		Z \boldsymbol{\zeta} 
-		\biggr)
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		%\\&=
-		%	\frac{1}{n}
-		%\bigl \langle
-		%(\Theta_1^\top \mathbf{y} , \ldots, \Theta_K^\top %\mathbf{y}, Z^\top \mathbf{y}),
-		%(\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K, %\boldsymbol{\zeta})
-		%\bigr\rangle_B.
-	\end{align*}	
-	Therefore, problem of maximizing the squared covariance  is equivalent to the following constrained optimization problem on the Euclidean space:
+ 	The optimization problem
+ 	\ref{eq: Regularized generalized rayleigh quotient equation} can be written as
  		\begin{align*}
  		\max_{\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K \in \mathbb{R}^M,
-			\boldsymbol{\zeta} \in \mathbb{R}^p
+ 			\boldsymbol{\xi}_{K+1} \in \mathbb{R}^p
  		}~&
@@
  		\mathbf{y}^\top
-		Z \boldsymbol{\zeta} 
+ 		Z \boldsymbol{\xi}_{K+1} 
  		\biggr)^2,
-		\numberthis \label{optim:summation_form}
-		\\&~s.t.~	\sum \limits_{j=1}^K 
+ 		\\\text{subject to}\quad&	\sum \limits_{j=1}^K 
  		\boldsymbol{\gamma}_j^\top
-		B
+ 	(	B + \lambda_k B^{\prime \prime})
  		\boldsymbol{\gamma}_j
  		+
-		\boldsymbol{\zeta}^\top \boldsymbol{\zeta} = 1.
-	\end{align*} 
-The objective function matches that of \eqref{eq: Regularized generalized rayleigh quotient equation}, taking the form of a quadratic expression involving the matrix $V$ defined in \eqref{def:V_matrix}:
-\begin{align*}
+ 		\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1} = 1.
+ 	\end{align*} 
+ Let $\mathbf{u}_j := \Theta_j^\top \mathbf{y} \in \mathbb{R}^M$ and $\mathbf{v} := Z^\top \mathbf{y} \in \mathbb{R}^p$.
+These are fixed problem data and not decision variables.
+Then the optimization problem becomes
+ 	 		\begin{align*}
+ 		\max_{\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K \in \mathbb{R}^M,
+ 			\boldsymbol{\xi}_{K+1} \in \mathbb{R}^p
+ 		}~&
  		\frac{1}{n^2}
@@
  		\sum \limits_{k=1}^K 
-\mathbf{y}^\top
-\Theta_{j}
+ 	\mathbf{u}_j^\top
  		B  
@@
  		+
-\mathbf{y}^\top
-Z \boldsymbol{\zeta} 
-\biggr)^2
-%%%%%%%%%%%%%%%%%%%%
-&=
-\frac{1}{n^2} 
-(
-\mathbf{y}^\top
-\Theta
-\mathbb{B}  
-\boldsymbol{\xi}
-)^2
-\\
-&	= 
-\frac{1}{n^2} 
-\boldsymbol{\xi}^\top
-(\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top 
-\boldsymbol{\xi}
-\\&=
-	\boldsymbol{\xi}^\top
-V 
-\boldsymbol{\xi},
-\end{align*}
-and the constraint is identical to that in \eqref{eq: Regularized generalized rayleigh quotient equation}, because we have:
-\begin{equation*}
-		\sum \limits_{j=1}^K 
+ 		\mathbf{v}^\top \boldsymbol{\xi}_{K+1} 
+ 		\biggr)^2,
+ 		\\\text{subject to}\quad&	\sum \limits_{j=1}^K 
  		\boldsymbol{\gamma}_j^\top
-	B
+ 		(	B + \lambda_k B^{\prime \prime})
  		\boldsymbol{\gamma}_j
-	+ \boldsymbol{\zeta}^\top \boldsymbol{\zeta}
-	=
-	\boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi}.
-\end{equation*}
-Therefore, the optimization problem \eqref{optim:summation_form}, which is equivalent to the squared covariance maximization problem, reduces to the generalized eigenvalue problem \eqref{eq: Regularized generalized rayleigh quotient equation}.
-This completes the proof of Proposition~\ref{proposition:eigen_noregul}.
- \end{proof}
-
- \section{Proof of Proposition  \ref{proposition:linear_noregul}}\label{section:proof:proposition:linear_noregul}
- \begin{proof}
-	From \eqref{optim:summation_form}, let us denote the objective function as
-	\[
-	f(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\zeta}) := 
-	\frac{1}{n^2}
-	\left(
-	\sum_{j=1}^K \mathbf{y}^\top \Theta_j B \boldsymbol{\gamma}_j + \mathbf{y}^\top Z \boldsymbol{\zeta}
-	\right)^2,
-	\]
-	and the constraint function as
-	\[
-	g(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\zeta}) := \sum_{j=1}^K \boldsymbol{\gamma}_j^\top B \boldsymbol{\gamma}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta} - 1 = 0.
-	\]
+ 		+
+ 		\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1} = 1.
+ 	\end{align*}  	
 The feasible set is compact, as it corresponds to the boundary of an ellipsoid in a finite-dimensional Euclidean space.
-Since the objective function $f$ is continuous and the constraint defines a compact feasible set, the  Weierstrass Extreme Value Theorem (see, for example, Theorem 2.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}) ensures the existence of a global maximizer.
+Since the objective function is continuous and the constraint defines a compact feasible set, the  Weierstrass Extreme Value Theorem (see, for example, Theorem 2.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}) ensures the existence of a global maximizer.
 
@@
 \[
-	\mathcal{L}(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\zeta}, \lambda) 
+\mathcal{L}(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\xi}_{K+1}, \mu) 
 := 
-	f(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\zeta}) - \lambda g(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\zeta}).
+	\left( \sum_{j=1}^K \mathbf{u}_j^\top B \boldsymbol{\gamma}_j + \mathbf{v}^\top \boldsymbol{\xi}_{K+1} \right)^2
+- 
+\mu 
+\biggl[
+\bigl\{
+	\sum_{j=1}^K \boldsymbol{\gamma}_j^\top (B + \lambda_j B^{\prime\prime}) \boldsymbol{\gamma}_j + 	\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1} 
+	\bigr\}
+	- 1
+	\biggr]
+.
 \]
-	The constraint function $g$ is continuously differentiable, and its gradient vanishes only at the origin.
-Since the origin is not feasible (the constraint requires norm 1), the gradient of $g$ is nonzero at all feasible points.
+The constraint function   is continuously differentiable, and its gradient vanishes only at the origin.
+Since the origin is not feasible, the gradient  is nonzero at all feasible points.
 Thus, the linear independence constraint qualification (LICQ) holds, ensuring that the KKT conditions are necessary for local maxima (see, for example, Theorem 5.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}).
@@
 	\left(
-		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
+	\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\xi}_{K+1}
 	\right)
 	B \Theta_j^\top \mathbf{y}
-		- 2\lambda B \boldsymbol{\gamma}_j = 0, \quad \forall j, 
+	- 2\lambda (B + \lambda_j B^{\prime \prime}) \boldsymbol{\gamma}_j = 0, \quad \forall j, 
 	\numberthis \label{lag_grad_d}
 	\\
-		\nabla_{\boldsymbol{\zeta}} \mathcal{L} &= 
+	\nabla_{\boldsymbol{\xi}_{K+1}} \mathcal{L} &= 
 	\frac{2}{n^2} 
 	\left(
-		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
+	\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\xi}_{K+1}
 	\right)
 	Z^\top \mathbf{y}
-		- 2\lambda \boldsymbol{\zeta} = 0.
+	- 2\lambda \boldsymbol{\xi}_{K+1} = 0.
 	\numberthis \label{lag_grad_zeta}
 \end{align*}
-	By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$,  and observing that  $2n^{-2}\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$, which is a scalar quantity, appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the  conditions above together imply that any local maxima must be  scalar multiples of
+By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$,  and observing that  $2n^{-2}\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\xi}_{K+1}$, which is a scalar quantity, appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the  conditions above together imply that any local maxima must be  scalar multiples of
 $
@@
 	%%%%%%%%%%%%%%%%
-		\boldsymbol{\zeta}^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
+	\boldsymbol{\xi}_{K+1}^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
 			\mathbf{y}^\top
@@
 \end{equation*}
+
+ 	Observe that the objective is linear in each $\boldsymbol{\gamma}_j$ and in $\boldsymbol{\xi}_{K+1}$, and the constraint is a strictly convex quadratic form.
+Hence, the optimal solution lies in the direction of the gradient of the linear objective.
+
+ 	Define scalar weights $c_j$ and $c$ such that
+ 	\[
+ 	\boldsymbol{\gamma}_j = c_j \mathbf{u}_j, \quad \boldsymbol{\xi}_{K+1} = c \mathbf{v}.
+ 	\]
+
+ 	Substituting into the objective:
+ 	\[
+ 	\left( \sum_{j=1}^K c_j \mathbf{y}^\top \Theta_j B \mathbf{u}_j + c \mathbf{y}^\top Z \mathbf{v} \right)^2 = \left( \sum_{j=1}^K c_j a_j + c b \right)^2,
+ 	\]
+ 	where we define $a_j := \mathbf{u}_j^\top B \mathbf{u}_j$ and $b := \| \mathbf{v} \|^2$.
+
+ 	The constraint becomes:
+ 	\[
+ 	\sum_{j=1}^K c_j^2 \, d_j + c^2 b = 1,
+ 	\]
+ 	where $d_j := \mathbf{u}_j^\top (B + \mu_j B^{\prime\prime}) \mathbf{u}_j$.
+
+ 	Now we define the Lagrangian:
+ 	\[
+ 	\mathcal{L}(c_1, \ldots, c_K, c; \lambda) = \left( \sum_{j=1}^K c_j a_j + c b \right)^2 - \lambda \left( \sum_{j=1}^K c_j^2 d_j + c^2 b - 1 \right).
+ 	\]
+
+ 	Taking partial derivatives and setting them to zero:
+ 	\begin{align*}
+ 		\frac{\partial \mathcal{L}}{\partial c_j} &= 2 \left( \sum_{j'=1}^K c_{j'} a_{j'} + c b \right) a_j - 2\lambda c_j d_j = 0, \quad \forall j, \\
+ 		\frac{\partial \mathcal{L}}{\partial c} &= 2 \left( \sum_{j'=1}^K c_{j'} a_{j'} + c b \right) b - 2\lambda c b = 0.
+ 	\end{align*}
+
+ 	Let $s := \sum_{j'=1}^K c_{j'} a_{j'} + c b$, then the optimality conditions reduce to:
+ 	\[
+ 	s a_j = \lambda c_j d_j, \quad s b = \lambda c b.
+ 	\]
+
+ 	Solving for $c_j$ and $c$:
+ 	\[
+ 	c_j = \frac{a_j}{d_j} \cdot \frac{s}{\lambda}, \quad c = \frac{s}{\lambda}.
+ 	\]
+
+ 	Substitute into the constraint:
+ 	\begin{align*}
+ 		\sum_{j=1}^K \left( \frac{a_j}{d_j} \cdot \frac{s}{\lambda} \right)^2 d_j + \left( \frac{s}{\lambda} \right)^2 b &= 1, \\
+ 		\left( \frac{s}{\lambda} \right)^2 \left( \sum_{j=1}^K \frac{a_j^2}{d_j} + b \right) &= 1.
+ 	\end{align*}
+
+ 	Let $S := \sum_{j=1}^K \frac{a_j^2}{d_j} + b$, then
+ 	\[
+ 	\left( \frac{s}{\lambda} \right)^2 = \frac{1}{S}, \quad \Rightarrow \quad \frac{s}{\lambda} = \frac{1}{\sqrt{S}}.
+ 	\]
+
+ 	Hence,
+ 	\[
+ 	c_j = \frac{a_j}{d_j \sqrt{S}}, \quad c = \frac{1}{\sqrt{S}}.
+ 	\]
+
+ 	\textbf{Conclusion}: The optimal coefficients are
+ 	\[
+ 	\boldsymbol{\gamma}_j = \frac{a_j}{d_j \sqrt{S}} \mathbf{u}_j, \quad \boldsymbol{\xi}_{K+1} = \frac{1}{\sqrt{S}} \mathbf{v},
+ 	\]
+ 	where
+ 	\[
+ 	a_j = \mathbf{u}_j^\top B \mathbf{u}_j, \quad d_j = \mathbf{u}_j^\top (B + \mu_j B^{\prime\prime}) \mathbf{u}_j, \quad \mathbf{u}_j = \Theta_j^\top \mathbf{y}, \quad \mathbf{v} = Z^\top \mathbf{y},
+ 	\]
+ 	and
+ 	\[
+ 	S = \sum_{j=1}^K \frac{a_j^2}{d_j} + \| \mathbf{v} \|^2.
+ 	\]
+
 	which are the same as  $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ and $\hat{\boldsymbol{\xi}}$. This completes the proof of  Proposition \ref{proposition:linear_noregul}.

### 2025-07-16 manuscript/main.tex
scalar multiple argument

@@
 	The regression coefficient $\boldsymbol{\eta}$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS components and scores.
-First, note that we can show $\widehat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} = \langle \mathbf{W}_i, \widehat{\boldsymbol{\xi}_{K+1}}_l \rangle_\mathcal{H}$, where $\widehat{\boldsymbol{\xi}_{K+1}}_l = \widehat{\xi}_l - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}_u, \widehat{\xi}_l \rangle_{\mathcal{H}} \widehat{\boldsymbol{\xi}_{K+1}}_u$ for $l \ge 2$, with $\widehat{\boldsymbol{\xi}_{K+1}}_1 = \widehat{\xi}_1$.
+First, note that we can show $\widehat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} = \langle \mathbf{W}_i, \widehat{\boldsymbol{\zeta}}_l \rangle_\mathcal{H}$, where $\widehat{\boldsymbol{\zeta}}_l = \widehat{\xi}_l - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}_u, \widehat{\xi}_l \rangle_{\mathcal{H}} \widehat{\boldsymbol{\zeta}}_u$ for $l \ge 2$, with $\widehat{\boldsymbol{\zeta}}_1 = \widehat{\xi}_1$.
 Then, the decomposition of $Y_i$ in \eqref{eq: decomposition} leads to
 	\begin{equation*}
-		Y_i = \sum \limits_{l=1}^L \widehat{\nu}_l \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\xi}_{K+1}}_l \right\rangle_\mathcal{H}+\epsilon_i,
+		Y_i = \sum \limits_{l=1}^L \widehat{\nu}_l \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l \right\rangle_\mathcal{H}+\epsilon_i,
 	\end{equation*}
@@
 	\begin{equation*}
-		\widehat{\boldsymbol{\eta}} = \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\xi}_{K+1}}_l.
+		\widehat{\boldsymbol{\eta}} = \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l.
 	\end{equation*}
@@
 	\begin{proof}
-	Let $\xi = (\xi_1, \ldots, \xi_K, \boldsymbol{\xi}_{K+1}) \in \mathcal{H}$.
+	Let $\xi = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta}) \in \mathcal{H}$.
 Assume that each functional component $\xi_j \in L^2([0,1])$ lies in the span of the basis functions ${b_1(t), \ldots, b_M(t)}$ and can be written as
@@
 		\mathbf{Z}_i^\top 
-		\boldsymbol{\xi}_{K+1} 
+		\boldsymbol{\zeta} 
 		\biggr)
@@
 		y_i
-		( \mathbf{Z}_i^\top \boldsymbol{\xi}_{K+1} )
+		( \mathbf{Z}_i^\top \boldsymbol{\zeta} )
 		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 		\mathbf{y}^\top
-		Z \boldsymbol{\xi}_{K+1} 
+		Z \boldsymbol{\zeta} 
 		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 		\mathbf{y}^\top
-		Z \boldsymbol{\xi}_{K+1}
+		Z \boldsymbol{\zeta}
 		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 		\mathbf{y}^\top
-		Z \boldsymbol{\xi}_{K+1} 
+		Z \boldsymbol{\zeta} 
 		\biggr)
@@
 		\mathbf{y}^\top
-		Z \boldsymbol{\xi}_{K+1} 
+		Z \boldsymbol{\zeta} 
 		\biggr)^2
@@
 		+
-		\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1}
+		\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
 		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 		+
-		\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1}  
+		\boldsymbol{\zeta}^\top \boldsymbol{\zeta}  
 		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 		+
-		\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1},
+		\boldsymbol{\zeta}^\top \boldsymbol{\zeta},
 %%%%%%%%%%%%%
@@
  		\max_{\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K \in \mathbb{R}^M,
- 			\boldsymbol{\xi}_{K+1} \in \mathbb{R}^p
+ 			\boldsymbol{\zeta} \in \mathbb{R}^p
  		}~&
@@
  		\mathbf{y}^\top
- 		Z \boldsymbol{\xi}_{K+1} 
+ 		Z \boldsymbol{\zeta} 
  		\biggr)^2,
@@
  		+
- 		\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1} = 1.
- 	\end{align*} 
- Let $\mathbf{u}_j := \Theta_j^\top \mathbf{y} \in \mathbb{R}^M$ and $\mathbf{v} := Z^\top \mathbf{y} \in \mathbb{R}^p$.
+ 		\boldsymbol{\zeta}^\top \boldsymbol{\zeta} = 1.
+ 	\end{align*} 
+ Let $\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M$ and $\mathbf{v} := Z^\top \mathbf{y} \in \mathbb{R}^p$.
 These are fixed problem data and not decision variables.
@@
  	\mathbf{u}_j^\top		
- 		B  
  		\boldsymbol{\gamma}_j
  		+
- 		\mathbf{v}^\top \boldsymbol{\xi}_{K+1} 
+ 		\mathbf{v}^\top \boldsymbol{\zeta} 
  		\biggr)^2,
@@
  		+
- 		\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1} = 1.
- 	\end{align*}  	
+ 		\boldsymbol{\zeta}^\top \boldsymbol{\zeta} = 1.
+ 	\end{align*}  	
+ 	The objective function is continuous.
 The feasible set is compact, as it corresponds to the boundary of an ellipsoid in a finite-dimensional Euclidean space.
-Since the objective function is continuous and the constraint defines a compact feasible set, the  Weierstrass Extreme Value Theorem (see, for example, Theorem 2.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}) ensures the existence of a global maximizer.
-
-Define the Lagrangian:
+Therefore, the  Weierstrass Extreme Value Theorem (see, for example, Theorem 2.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}) ensures the existence of a global maximizer.
+The constraint function is continuously differentiable, and its gradient vanishes only at the origin.
+Since the origin is not a feasible point, the gradient  is nonzero at all feasible points.
+Thus, the linear independence constraint qualification (LICQ) holds, ensuring that the KKT conditions are necessary for local maxima (see, for example, Theorem 5.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}).
+To use this fact,
+define the Lagrangian as follows:
 \[
-\mathcal{L}(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\xi}_{K+1}, \mu) 
+\mathcal{L}(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\zeta}, \mu) 
 := 
-	\left( \sum_{j=1}^K \mathbf{u}_j^\top B \boldsymbol{\gamma}_j + \mathbf{v}^\top \boldsymbol{\xi}_{K+1} \right)^2
+	\left( \sum_{j=1}^K \mathbf{u}_j^\top  \boldsymbol{\gamma}_j + \mathbf{v}^\top \boldsymbol{\zeta} \right)^2
 - 
@@
 \bigl\{
-	\sum_{j=1}^K \boldsymbol{\gamma}_j^\top (B + \lambda_j B^{\prime\prime}) \boldsymbol{\gamma}_j + 	\boldsymbol{\xi}_{K+1}^\top \boldsymbol{\xi}_{K+1} 
+	\sum_{j=1}^K \boldsymbol{\gamma}_j^\top (B + \lambda_j B^{\prime\prime}) \boldsymbol{\gamma}_j + 	\boldsymbol{\zeta}^\top \boldsymbol{\zeta} 
 	\bigr\}
@@
 \]
-The constraint function   is continuously differentiable, and its gradient vanishes only at the origin.
-Since the origin is not feasible, the gradient  is nonzero at all feasible points.
-Thus, the linear independence constraint qualification (LICQ) holds, ensuring that the KKT conditions are necessary for local maxima (see, for example, Theorem 5.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}).
-Therefore, for any local maxima, gradients of $\mathcal{L}$ must be zero:
+Then, if
+$(\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K, 
+	\boldsymbol{\zeta}
+)$
+is a local maximizer, the gradients of $\mathcal{L}$ must vanish at that point:
 \begin{align*}
 	\nabla_{\boldsymbol{\gamma}_j} \mathcal{L} &= 
-	\frac{2}{n^2} 
-	\left(
-	\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\xi}_{K+1}
-	\right)
-	B \Theta_j^\top \mathbf{y}
-	- 2\lambda (B + \lambda_j B^{\prime \prime}) \boldsymbol{\gamma}_j = 0, \quad \forall j, 
+	s
+	 \mathbf{u}_j
+	- 2\mu (B + \lambda_j B^{\prime \prime}) \boldsymbol{\gamma}_j = 0, \quad \forall j, 
 	\numberthis \label{lag_grad_d}
 	\\
-	\nabla_{\boldsymbol{\xi}_{K+1}} \mathcal{L} &= 
-	\frac{2}{n^2} 
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\nabla_{\boldsymbol{\zeta}} \mathcal{L} &= 
+	s
+\mathbf{v}
+	- 2\mu \boldsymbol{\zeta} = 0,
+	\numberthis \label{lag_grad_zeta}
+\end{align*}
+where 
+\begin{equation*}
+	s := \frac{2}{n^2} 
 	\left(
-	\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\xi}_{K+1}
-	\right)
-	Z^\top \mathbf{y}
-	- 2\lambda \boldsymbol{\xi}_{K+1} = 0.
-	\numberthis \label{lag_grad_zeta}
-\end{align*}
-By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$,  and observing that  $2n^{-2}\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\xi}_{K+1}$, which is a scalar quantity, appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the  conditions above together imply that any local maxima must be  scalar multiples of
+	\sum_{\ell=1}^K \mathbf{u}_\ell^\top B \boldsymbol{\gamma}_\ell + \mathbf{v}^\top  \boldsymbol{\zeta}
+	\right).
+\end{equation*}
+Since we assumed in Section~\ref{sec: finite basis approximation} that the functions $\{b_m(t)\}$ and their second derivatives are linearly independent, both $B$ and $B^{\prime\prime}$ are positive definite (see, for example, Theorem 273 of \citealp{gockenbachFiniteDimensionalLinearAlgebra2010}).
+As positive definiteness is preserved under conic combinations, $B + \lambda_j B^{\prime\prime}$ is also positive definite.
+Therefore, \eqref{lag_grad_d} implies that
+\begin{equation*}
+	\boldsymbol{\gamma}_j
+	=
+	\frac{s}{2\mu}	
+	(B + \lambda_j B^{\prime \prime})^{-1}
+	\mathbf{u}_j
+	   , \quad \forall j.
+\end{equation*}
+If $\boldsymbol{\gamma}_j$ is part of a local optimum, then it must be a scalar multiple of 
+$\tilde{\mathbf{u}}_j := (B + \lambda_j B^{\prime \prime})^{-1} \mathbf{u}_j$, 
+i.e., $\boldsymbol{\gamma}_j = c_j \tilde{\mathbf{u}}_j$.
+Similarly, \eqref{lag_grad_zeta} implies that if 
+$\boldsymbol{\zeta}$ is a local optimum, then it must be a scalar multiple of $\mathbf{v}$,
+i.e., $\boldsymbol{\zeta} = d \mathbf{v}$.
+
+Therefore, it suffices to 
+By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$,  and observing that  $2n^{-2}\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$, which is a scalar quantity, appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the  conditions above together imply that any local maxima must be  scalar multiples of
 $
@@
 	%%%%%%%%%%%%%%%%
-	\boldsymbol{\xi}_{K+1}^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
+	\boldsymbol{\zeta}^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
 			\mathbf{y}^\top
@@
 
- 	Observe that the objective is linear in each $\boldsymbol{\gamma}_j$ and in $\boldsymbol{\xi}_{K+1}$, and the constraint is a strictly convex quadratic form.
+ 	Observe that the objective is linear in each $\boldsymbol{\gamma}_j$ and in $\boldsymbol{\zeta}$, and the constraint is a strictly convex quadratic form.
 Hence, the optimal solution lies in the direction of the gradient of the linear objective.
@@
  	\[
- 	\boldsymbol{\gamma}_j = c_j \mathbf{u}_j, \quad \boldsymbol{\xi}_{K+1} = c \mathbf{v}.
+ 	\boldsymbol{\gamma}_j = c_j \mathbf{u}_j, \quad \boldsymbol{\zeta} = c \mathbf{v}.
  	\]
@@
  	\[
- 	\boldsymbol{\gamma}_j = \frac{a_j}{d_j \sqrt{S}} \mathbf{u}_j, \quad \boldsymbol{\xi}_{K+1} = \frac{1}{\sqrt{S}} \mathbf{v},
+ 	\boldsymbol{\gamma}_j = \frac{a_j}{d_j \sqrt{S}} \mathbf{u}_j, \quad \boldsymbol{\zeta} = \frac{1}{\sqrt{S}} \mathbf{v},
  	\]

### 2025-07-16 manuscript/main.tex
computation proof done

@@
 The proof of Proposition \ref{proposition:eigen_noregul}
-is provided in Appendix \ref{section:proof:proposition:linear_noregul_system_unregularized}.
+is provided in Appendix \ref{section:proof:proposition:linear_regul_system_unregularized}.
 Since $V$ is a rank 1, the solution  is  obtained by matrix multiplication and normalization:
+
+\begin{proposition}[Closed-form solution to the regularized PLS direction]
+	\label{prop:closed_form_pls}
+	Let $\{\mathbf{u}_j\}_{j=1}^K$ and $\mathbf{v}$ be defined as
+	\[
+	\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M, \quad
+	\mathbf{v} := Z^\top \mathbf{y} \in \mathbb{R}^p,
+	\]	
+	Then the unique (up to sign) solution 
+	is given in closed form as
+	\[
+	\boldsymbol{\gamma}_j^\ast = \frac{1}{\sqrt{q}} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j, \quad
+	\boldsymbol{\zeta}^\ast = \frac{1}{\sqrt{q}} \mathbf{v},
+	\]
+	where
+	\[
+	q := \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v}.
+	\]
+\end{proposition}
+
 	\begin{proposition} \label{proposition:linear_noregul}
@@
 \end{proposition}
-The proof of Proposition \ref{proposition:linear_noregul}  is provided in Appendix \ref{section:proof:proposition:linear_noregul}.
+The proof of Proposition \ref{proposition:linear_noregul}  is provided in Appendix \ref{section:proof:proposition:linear_regul}.
 The expressions above represent matrix–vector multiplications normalized by a common factor. 
@@
 \end{proposition}
-	The proof of Proposition \ref{proposition:eigen_regul} is provided in Appendix  \ref{section:proof:proposition:linear_noregul_system_unregularized}.
+	The proof of Proposition \ref{proposition:eigen_regul} is provided in Appendix  \ref{section:proof:proposition:linear_regul_system_unregularized}.
 	Here, $\lambda_k$ $(k=1, \ldots, K)$ is a positive smoothing parameter that controls the trade-off between the goodness of fit and the amount of smoothness in $\psi^{(k)}$.
@@
 
-	\section{Proof of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:eigen_regul} }\label{section:proof:proposition:linear_noregul_system_unregularized}
+	\section{Proof of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:eigen_regul} }\label{section:proof:proposition:linear_regul_system_unregularized}
 	\begin{proof}
@@
 
- \section{Proof of Proposition  \ref{proposition:linear_noregul}}\label{section:proof:proposition:linear_noregul}
+ \section{Proof of Proposition  \ref{proposition:linear_noregul}}\label{section:proof:proposition:linear_regul}
  \begin{proof}
 The optimization problem 
- 	\ref{eq: Regularized generalized rayleigh quotient equation} can be written as
+\eqref{eq: Regularized generalized rayleigh quotient equation} can be written as
 \begin{align*}
- 		\max_{\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K \in \mathbb{R}^M,
- 			\boldsymbol{\zeta} \in \mathbb{R}^p
- 		}~&
+	\max_{\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K \in \mathbb{R}^M,\;
+		\boldsymbol{\zeta} \in \mathbb{R}^p}~&
 	\frac{1}{n^2}
- 		\biggl(
- 		\sum \limits_{k=1}^K 
+	\left(
+	\sum_{j=1}^K 
 	\mathbf{y}^\top
- 		\Theta_{j}
+	\Theta_j
 	B  
@@
 	Z \boldsymbol{\zeta} 
- 		\biggr)^2,
- 		\\\text{subject to}\quad&	\sum \limits_{j=1}^K 
+	\right)^2,
+	\\
+	\text{subject to}\quad&
+	\sum_{j=1}^K 
 	\boldsymbol{\gamma}_j^\top
- 	(	B + \lambda_k B^{\prime \prime})
+	(B + \lambda_j B^{\prime\prime})
 	\boldsymbol{\gamma}_j
@@
 \end{align*}
- Let $\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M$ and $\mathbf{v} := Z^\top \mathbf{y} \in \mathbb{R}^p$.
-These are fixed problem data and not decision variables.
-Then the optimization problem becomes
- 	 		\begin{align*}
- 		\max_{\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K \in \mathbb{R}^M,
- 			\boldsymbol{\zeta} \in \mathbb{R}^p
- 		}~&
+
+Let $\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M$ and $\mathbf{v} := Z^\top \mathbf{y} \in \mathbb{R}^p$. These are fixed problem data. Then the objective becomes
+\[
 \frac{1}{n^2}
- 		\biggl(
- 		\sum \limits_{k=1}^K 
- 	\mathbf{u}_j^\top		
- 		\boldsymbol{\gamma}_j
+\left(
+\sum_{j=1}^K 
+\mathbf{u}_j^\top \boldsymbol{\gamma}_j
 +
 \mathbf{v}^\top \boldsymbol{\zeta}
- 		\biggr)^2,
- 		\\\text{subject to}\quad&	\sum \limits_{j=1}^K 
- 		\boldsymbol{\gamma}_j^\top
- 		(	B + \lambda_k B^{\prime \prime})
- 		\boldsymbol{\gamma}_j
- 		+
- 		\boldsymbol{\zeta}^\top \boldsymbol{\zeta} = 1.
- 	\end{align*}  	
+\right)^2.
+\]
 The objective function is continuous.
-The feasible set is compact, as it corresponds to the boundary of an ellipsoid in a finite-dimensional Euclidean space.
-Therefore, the  Weierstrass Extreme Value Theorem (see, for example, Theorem 2.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}) ensures the existence of a global maximizer.
-The constraint function is continuously differentiable, and its gradient vanishes only at the origin.
-Since the origin is not a feasible point, the gradient  is nonzero at all feasible points.
-Thus, the linear independence constraint qualification (LICQ) holds, ensuring that the KKT conditions are necessary for local maxima (see, for example, Theorem 5.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}).
-To use this fact,
-define the Lagrangian as follows:
+The constraint defines the boundary of an ellipsoid in a finite-dimensional Euclidean space, the feasible set is compact.
+By the Weierstrass Extreme Value Theorem (see, e.g., Theorem 2.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}), a global maximizer exists.
+The constraint function is continuously differentiable and its gradient vanishes only at the origin, which is not feasible.
+Thus the gradient  is nonzero at all feasible points.
+Hence, the Linear Independence Constraint Qualification (LICQ) holds, and the Karush-Kuhn-Tucker (KKT) conditions are necessary for local optimality (see, e.g., Theorem 5.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}).
+
+Define the Lagrangian:
 \[
@@
 \mu 
-\biggl[
-\bigl\{
-	\sum_{j=1}^K \boldsymbol{\gamma}_j^\top (B + \lambda_j B^{\prime\prime}) \boldsymbol{\gamma}_j + 	\boldsymbol{\zeta}^\top \boldsymbol{\zeta} 
-	\bigr\}
-	- 1
-	\biggr]
-.
+\left[
+\sum_{j=1}^K \boldsymbol{\gamma}_j^\top (B + \lambda_j B^{\prime\prime}) \boldsymbol{\gamma}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta} - 1
+\right].
 \]
-Then, if
-$(\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K, 
-	\boldsymbol{\zeta}
-)$
-is a local maximizer, the gradients of $\mathcal{L}$ must vanish at that point:
-\begin{align*}
+
+Let $s := \dfrac{2}{n^2} \left( \sum_{j=1}^K \mathbf{u}_j^\top \boldsymbol{\gamma}_j + \mathbf{v}^\top \boldsymbol{\zeta} \right)$. The KKT conditions require that:
+\begin{align}
 	\nabla_{\boldsymbol{\gamma}_j} \mathcal{L} &= 
-	s
-	 \mathbf{u}_j
-	- 2\mu (B + \lambda_j B^{\prime \prime}) \boldsymbol{\gamma}_j = 0, \quad \forall j, 
-	\numberthis \label{lag_grad_d}
-	\\
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	s \mathbf{u}_j - 2\mu (B + \lambda_j B^{\prime\prime}) \boldsymbol{\gamma}_j = 0, \quad \text{for } j = 1, \ldots, K, \label{eq:lag_grad_gamma} \\
 	\nabla_{\boldsymbol{\zeta}} \mathcal{L} &= 
-	s
-\mathbf{v}
-	- 2\mu \boldsymbol{\zeta} = 0,
-	\numberthis \label{lag_grad_zeta}
-\end{align*}
-where 
-\begin{equation*}
-	s := \frac{2}{n^2} 
-	\left(
-	\sum_{\ell=1}^K \mathbf{u}_\ell^\top B \boldsymbol{\gamma}_\ell + \mathbf{v}^\top  \boldsymbol{\zeta}
-	\right).
-\end{equation*}
+	s \mathbf{v} - 2\mu \boldsymbol{\zeta} = 0. \label{eq:lag_grad_zeta}
+\end{align}
+
+From \eqref{eq:lag_grad_gamma} and \eqref{eq:lag_grad_zeta}, we have
+\[
+(B + \lambda_j B^{\prime\prime}) \boldsymbol{\gamma}_j = \frac{s}{2\mu} \mathbf{u}_j, \quad
+\boldsymbol{\zeta} = \frac{s}{2\mu} \mathbf{v}, \quad \text{for } j = 1, \ldots, K.
+\]
+This implies that for any local maximizer, there exists $c \ne 0$ such that 
+\[
+\boldsymbol{\gamma}_j = c (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j, \quad
+\boldsymbol{\zeta} = c \mathbf{v}, \quad \text{for } j = 1, \ldots, K.
+\]
 Since we assumed in Section~\ref{sec: finite basis approximation} that the functions $\{b_m(t)\}$ and their second derivatives are linearly independent, both $B$ and $B^{\prime\prime}$ are positive definite (see, for example, Theorem 273 of \citealp{gockenbachFiniteDimensionalLinearAlgebra2010}).
 As positive definiteness is preserved under conic combinations, $B + \lambda_j B^{\prime\prime}$ is also positive definite.
-Therefore, \eqref{lag_grad_d} implies that
-\begin{equation*}
-	\boldsymbol{\gamma}_j
-	=
-	\frac{s}{2\mu}	
-	(B + \lambda_j B^{\prime \prime})^{-1}
-	\mathbf{u}_j
-	   , \quad \forall j.
-\end{equation*}
-If $\boldsymbol{\gamma}_j$ is part of a local optimum, then it must be a scalar multiple of 
-$\tilde{\mathbf{u}}_j := (B + \lambda_j B^{\prime \prime})^{-1} \mathbf{u}_j$, 
-i.e., $\boldsymbol{\gamma}_j = c_j \tilde{\mathbf{u}}_j$.
-Similarly, \eqref{lag_grad_zeta} implies that if 
-$\boldsymbol{\zeta}$ is a local optimum, then it must be a scalar multiple of $\mathbf{v}$,
-i.e., $\boldsymbol{\zeta} = d \mathbf{v}$.
-
-Therefore, it suffices to 
-By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$,  and observing that  $2n^{-2}\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \boldsymbol{\gamma}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$, which is a scalar quantity, appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the  conditions above together imply that any local maxima must be  scalar multiples of
-$
-\Theta_1^\top \mathbf{y}, \ldots, \Theta_K^\top \mathbf{y}, Z^\top \mathbf{y},
-$
-all scaled by the same factor.
-There exists only one such set of  vectors  that also satisfies the primal equality constraint, namely the normalized version of the vector set above.
-The global maximizer is therefore given by
-\begin{equation*}
-	\boldsymbol{\gamma}_j^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
-			\mathbf{y}^\top
-			\Theta_j
-			B \Theta_j^\top \mathbf{y} 
-			+ 
-			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
-	\Theta_j^\top \mathbf{y},
-	\quad
-	%%%%%%%%%%%%%%%%
-	\boldsymbol{\zeta}^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
-			\mathbf{y}^\top
-			\Theta_j
-			B \Theta_j^\top \mathbf{y} 
-			+ 
-			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
-	Z^\top \mathbf{y},
-\end{equation*}
-
- 	Observe that the objective is linear in each $\boldsymbol{\gamma}_j$ and in $\boldsymbol{\zeta}$, and the constraint is a strictly convex quadratic form.
-Hence, the optimal solution lies in the direction of the gradient of the linear objective.
-
- 	Define scalar weights $c_j$ and $c$ such that
+
+A local maximizer must also be primal feasible. Substituting the conditions above in to the primal constraint:
+\begin{align*}
+	\sum_{j=1}^K 
+	\left( c (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j \right)^\top 
+	(B + \lambda_j B^{\prime\prime}) 
+	\left( c (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j \right)
+	+ c^2 \mathbf{v}^\top \mathbf{v} &= 1 \\
+	\Rightarrow 
+	c^2 \left( \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v} \right) &= 1.
+\end{align*}
+
+Solving for $c^2$ gives:
 \[
- 	\boldsymbol{\gamma}_j = c_j \mathbf{u}_j, \quad \boldsymbol{\zeta} = c \mathbf{v}.
+c^2 = \left( \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v} \right)^{-1}.
 \]
 
- 	Substituting into the objective:
+Hence, the unique maximizer (up to sign) is:
 \[
- 	\left( \sum_{j=1}^K c_j \mathbf{y}^\top \Theta_j B \mathbf{u}_j + c \mathbf{y}^\top Z \mathbf{v} \right)^2 = \left( \sum_{j=1}^K c_j a_j + c b \right)^2,
- 	\]
- 	where we define $a_j := \mathbf{u}_j^\top B \mathbf{u}_j$ and $b := \| \mathbf{v} \|^2$.
-
- 	The constraint becomes:
- 	\[
- 	\sum_{j=1}^K c_j^2 \, d_j + c^2 b = 1,
- 	\]
- 	where $d_j := \mathbf{u}_j^\top (B + \mu_j B^{\prime\prime}) \mathbf{u}_j$.
-
- 	Now we define the Lagrangian:
- 	\[
- 	\mathcal{L}(c_1, \ldots, c_K, c; \lambda) = \left( \sum_{j=1}^K c_j a_j + c b \right)^2 - \lambda \left( \sum_{j=1}^K c_j^2 d_j + c^2 b - 1 \right).
- 	\]
-
- 	Taking partial derivatives and setting them to zero:
- 	\begin{align*}
- 		\frac{\partial \mathcal{L}}{\partial c_j} &= 2 \left( \sum_{j'=1}^K c_{j'} a_{j'} + c b \right) a_j - 2\lambda c_j d_j = 0, \quad \forall j, \\
- 		\frac{\partial \mathcal{L}}{\partial c} &= 2 \left( \sum_{j'=1}^K c_{j'} a_{j'} + c b \right) b - 2\lambda c b = 0.
- 	\end{align*}
-
- 	Let $s := \sum_{j'=1}^K c_{j'} a_{j'} + c b$, then the optimality conditions reduce to:
- 	\[
- 	s a_j = \lambda c_j d_j, \quad s b = \lambda c b.
- 	\]
-
- 	Solving for $c_j$ and $c$:
- 	\[
- 	c_j = \frac{a_j}{d_j} \cdot \frac{s}{\lambda}, \quad c = \frac{s}{\lambda}.
- 	\]
-
- 	Substitute into the constraint:
- 	\begin{align*}
- 		\sum_{j=1}^K \left( \frac{a_j}{d_j} \cdot \frac{s}{\lambda} \right)^2 d_j + \left( \frac{s}{\lambda} \right)^2 b &= 1, \\
- 		\left( \frac{s}{\lambda} \right)^2 \left( \sum_{j=1}^K \frac{a_j^2}{d_j} + b \right) &= 1.
- 	\end{align*}
-
- 	Let $S := \sum_{j=1}^K \frac{a_j^2}{d_j} + b$, then
- 	\[
- 	\left( \frac{s}{\lambda} \right)^2 = \frac{1}{S}, \quad \Rightarrow \quad \frac{s}{\lambda} = \frac{1}{\sqrt{S}}.
- 	\]
-
- 	Hence,
- 	\[
- 	c_j = \frac{a_j}{d_j \sqrt{S}}, \quad c = \frac{1}{\sqrt{S}}.
- 	\]
-
- 	\textbf{Conclusion}: The optimal coefficients are
- 	\[
- 	\boldsymbol{\gamma}_j = \frac{a_j}{d_j \sqrt{S}} \mathbf{u}_j, \quad \boldsymbol{\zeta} = \frac{1}{\sqrt{S}} \mathbf{v},
+\boldsymbol{\gamma}_j^\ast = \frac{1}{\sqrt{q}} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j, \quad
+\boldsymbol{\zeta}^\ast = \frac{1}{\sqrt{q}} \mathbf{v},
 \]
@@
 \[
- 	a_j = \mathbf{u}_j^\top B \mathbf{u}_j, \quad d_j = \mathbf{u}_j^\top (B + \mu_j B^{\prime\prime}) \mathbf{u}_j, \quad \mathbf{u}_j = \Theta_j^\top \mathbf{y}, \quad \mathbf{v} = Z^\top \mathbf{y},
+q := \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v}.
 \]
- 	and
- 	\[
- 	S = \sum_{j=1}^K \frac{a_j^2}{d_j} + \| \mathbf{v} \|^2.
- 	\]
-
-	which are the same as  $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ and $\hat{\boldsymbol{\xi}}$. This completes the proof of  Proposition \ref{proposition:linear_noregul}.
+
+This completes the proof of Proposition \ref{section:proof:proposition:linear_regul}.
+
 	\end{proof}

### 2025-07-17 manuscript/main.tex
delete cholesky

@@
 = 
-(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1}
+(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}}
 )
@@
 $
-and $\hat{\boldsymbol{\xi}}_{K+1}$ is the scalar part. This maximizer can also be represented as a Euclidean vector
+and $\hat{\boldsymbol{\zeta}}$ is the scalar part. This maximizer can also be represented as a Euclidean vector
 \begin{equation}\label{def:maximizer_euclidean_form}
-	( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top
+	( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\zeta}}^\top )^\top
 	\in \mathbb{R}^{MK+p},
@@
 	\left(
-	\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
+	\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\zeta}}^\top
 	\right)^\top
@@
 is provided in Appendix \ref{section:proof:proposition:linear_regul_system_unregularized}.
-Since $V$ is a rank 1, the solution  is  obtained by matrix multiplication and normalization:
-
-\begin{proposition}[Closed-form solution to the regularized PLS direction]
-	\label{prop:closed_form_pls}
-	Let $\{\mathbf{u}_j\}_{j=1}^K$ and $\mathbf{v}$ be defined as
-	\[
-	\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M, \quad
-	\mathbf{v} := Z^\top \mathbf{y} \in \mathbb{R}^p,
-	\]	
-	Then the unique (up to sign) solution 
-	is given in closed form as
-	\[
-	\boldsymbol{\gamma}_j^\ast = \frac{1}{\sqrt{q}} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j, \quad
-	\boldsymbol{\zeta}^\ast = \frac{1}{\sqrt{q}} \mathbf{v},
-	\]
-	where
-	\[
-	q := \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v}.
-	\]
-\end{proposition}
-
-	\begin{proposition} \label{proposition:linear_noregul}
-	We can compute  $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ and $\hat{\boldsymbol{\xi}}_{K+1}$ in Proposition \ref{proposition:eigen_noregul} as 
-\begin{equation*}
-	\hat{\boldsymbol{\gamma}}_j  = \frac{1}{\sqrt{\sum_{j=1}^K 
-			\mathbf{y}^\top
-			\Theta_j
-			B \Theta_j^\top \mathbf{y} 
-			+ 
-			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
-	\Theta_j^\top \mathbf{y},
-	\quad
-	%%%%%%%%%%%%%%%%
-	\hat{\boldsymbol{\xi}}  = \frac{1}{\sqrt{\sum_{j=1}^K 
-			\mathbf{y}^\top
-			\Theta_j
-			B \Theta_j^\top \mathbf{y} 
-			+ 
-			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
-	Z^\top \mathbf{y}.
-\end{equation*}
-\end{proposition}
-The proof of Proposition \ref{proposition:linear_noregul}  is provided in Appendix \ref{section:proof:proposition:linear_regul}.
-The expressions above represent matrix–vector multiplications normalized by a common factor. 
-Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other.
-This enables the procedure to account for the correlation between functional and scalar components.
 
 	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
-Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions.
+Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions.
 To address this, we propose a regularized extension that balances predictive performance with smoothness.
@@
 	= 
-	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1}
+	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}}
 	)
@@
 		\left(
-		\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
+		\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\zeta}}^\top
 		\right)^\top
@@
 
+	Since $V$ is a rank 1, the solution  is  obtained by matrix multiplication and normalization:	
+\begin{proposition}[Closed-form solution]  
+	\label{proposition:linear_regul}  
+	Consider the optimization problem described in Proposition~\ref{proposition:eigen_regul}. Define the following quantities, which depend on the observed data but are not decision variables:  
+	\[
+	\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M \quad \text{for } j = 1, \ldots, K, \quad \text{and} \quad \mathbf{v} := Z^\top \mathbf{y} \in \mathbb{R}^p.
+	\]  
+	Let
+	\[
+	q := \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v}.
+	\]
+
+	Then the unique (up to sign) solution to the regularized maximization problem is given in closed form by  
+	\[
+	\hat{\boldsymbol{\gamma}}_j = \frac{1}{\sqrt{q}} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j \quad \text{for } j = 1, \ldots, K, \quad \text{and} \quad
+	\hat{\boldsymbol{\zeta}} = \frac{1}{\sqrt{q}} \mathbf{v}.
+	\]  
+\end{proposition}
+The proof of Proposition~\ref{proposition:linear_regul} is provided in Appendix~\ref{section:proof:proposition:linear_regul}.
+The expressions above involve solving linear systems for the functional and scalar components separately, followed by normalization by a common factor.
+Although the unnormalized coefficients are obtained independently, the normalization step couples the functional and scalar parts, allowing them to influence one another.
+This coupling enables the procedure to capture the correlation between the functional and scalar components of the PLS direction.
+
 	The constraint $\xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1$ enforces the following modified orthonormality of the estimated PLS components ($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ which now takes into account the roughness of the functions:
@@
 	This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{sec: Properties of the Proposed PLS Framework} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.
-
-	To solve \eqref{eq: Regularized generalized rayleigh quotient equation} in practice, we first perform a Choleski factorization: $L L^\top = J^\ast + \Lambda \ddot{J}^\ast$, where $L$ is a lower triangular matrix, and then reduce it to maximizing the classical Rayleigh quotient problem:
-	\begin{equation*}
-		\max \limits_{\mathbf{e} \in \mathbb{R}^{MK + p}} \, \frac{\mathbf{e}^\top E \mathbf{e}}{\mathbf{e}^\top \mathbf{e}} \; \Longleftrightarrow \;   \max \limits_{\substack{\mathbf{e} \in \mathbb{R}^{MK+p}}} \;  \mathbf{e}^\top E \mathbf{e} \quad \textnormal{subject to} \quad \Vert \mathbf{e} \Vert^2 = 1
-	\end{equation*}
-	through the transformations $\mathbf{e} = L^\top \xi^*$ and $E = L^{-1} \mathbf{V}^\ast L^{\top-1}$.
-Once $\mathbf{e}$ is obtained as the first eigenvector of $E$, we set $\xi^* = L^{\top-1} \mathbf{e}$ and $\widehat{\xi}[\mathbf{t}] = B^*[\mathbf{t}]^\top \xi^*$.
 
@@
 
- \section{Proof of Proposition  \ref{proposition:linear_noregul}}\label{section:proof:proposition:linear_regul}
+ \section{Proof of Proposition  \ref{proposition:linear_regul}}\label{section:proof:proposition:linear_regul}
  \begin{proof}

### 2025-07-17 manuscript/main.tex
computation theorem done!

@@
 	The proof of Proposition \ref{proposition:eigen_regul} is provided in Appendix  \ref{section:proof:proposition:linear_regul_system_unregularized}.
-	Here, $\lambda_k$ $(k=1, \ldots, K)$ is a positive smoothing parameter that controls the trade-off between the goodness of fit and the amount of smoothness in $\psi^{(k)}$.
-Smaller $\lambda_k$ produces PLS components that fit more closely to the observed data, but selecting too small value may cause overfitting.
-The estimated PLS component reverts back to the unregularized version of Proposition \ref{proposition:eigen_noregul} when $\lambda_k=0$ for all $k$.
-On the other hand, larger $\lambda_k$ places more emphasis on smoothing $\psi^{(k)}$.
-In the limit $\lambda_k \rightarrow \infty$, each of the functions is forced to be of the form $\psi^{(k)}(t)=a+bt$ for some constants $a$ and $b$.
-In practice, $\{\lambda_k\}_{k=1}^K$ as well as the number of PLS components $L$ to be estimated can be chosen by cross-validation based on a certain predictive performance criterion (e.g., mean squared error).
-
-	Since $V$ is a rank 1, the solution  is  obtained by matrix multiplication and normalization:	
+The smoothing parameter $\lambda_k > 0$ $(k = 1, \ldots, K)$ balances goodness of fit and smoothness in $\hat{\xi}_j$.
+Smaller $\lambda_k$ yields components that better fit the data but risks overfitting; setting $\lambda_k = 0$ recovers the unregularized solution in Proposition~\ref{proposition:eigen_noregul}.
+Larger $\lambda_k$ enforces greater smoothness, and in the limit $\lambda_k \to \infty$, $\hat{\xi}_j(t)$ approaches a linear form $a + bt$.
+In practice, both $\{\lambda_k\}$ and the number of components $L$ can be selected via cross-validation using a predictive criterion such as mean squared error.
+
+	\medskip
+	\noindent{\textit{Computation.}}~The generalized eigenproblem presented in Proposition~\ref{proposition:eigen_regul}  may be computationally unstable in practice.
+However, by leveraging the rank-one structure of the matrix
+	$V$
+Proposition \ref{proposition:linear_regul} derives a closed-form solution that requires only the solution of linear systems.
 \begin{proposition}[Closed-form solution]  
@@
 
+\medskip
+\noindent \textit{Orthonormality.}~
 	The constraint $\xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1$ enforces the following modified orthonormality of the estimated PLS components ($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ which now takes into account the roughness of the functions:

### 2025-07-23 manuscript/main.tex
model to the intro

@@
 
-	In modern biomedical studies, it is increasingly common to collect heterogeneous data modalities for each subject.
-As an illustrative example we use the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021}.
-The data records both multiple renogram curves (functional data) and multiple renogram variables (vector data) per kidney, capturing distinct yet related physiological information.
-Such settings call for statistical methods that can jointly model functional and vector-valued covariates to account for both shared and modality-specific variation linked to clinical outcomes.
+Modern biomedical studies frequently collect diverse data types from each subject.
+As an illustrative example, the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021}  records both multiple renogram curves (functional data) and multiple renogram variables (vector data)  for each kidney.
+These modalities provide distinct yet related physiological signals.
+To effectively analyze such heterogeneous data, we need statistical methods capable of jointly modeling functional and vector-valued covariates.
+This approach accounts for both shared and modality-specific variations linked to clinical outcomes.
+Our work focuses on developing a method to fit the following hybrid functional linear regression model:
+\begin{equation}	\label{eq: functional model}
+	Y_i
+	= 
+	\boldsymbol{\beta}^\top \mathbf{Z}_i
+	+ 
+	\sum 
+	\limits_{j=1}^K 
+	\int  \beta_j(t) X_{ij}(t) dt + \epsilon_i,
+	\quad
+	i = 1, \ldots, n,
+	%= \langle \boldsymbol{\alpha}, \mathbf{Z} \rangle +  \langle \beta, X \rangle_{\mathcal{F}}  + \epsilon
+\end{equation}
+where $Y$ is a scalar response, $\mathbf{Z}$ is the Euclidean vector covariate and 
+$X_{i1}(t), \ldots, X_{iK}(t)$ are functional predicters.
+For notational convenience, we assume throguth this paper that the responsd sand preedictoras ahve been centered so the intercept can be ignored. 
+%where $\boldsymbol{\alpha}=(\alpha_1, \ldots, \alpha_p)^\top \in \mathbb{R}^p$ and $\beta=(\beta^{(1)}, \ldots, \beta^{(K)}) \in \mathcal{F}$ are respectively the regression coefficient vector and function that characterize the effect of scalar and functional predictors on the outcome.
 
@@
 We assume that $\mathbf{Z}$ is a random vector with finite first two moments and equipped with the Euclidean inner product and norm; i.e., for $\mathbf{v_1}=(v_{11}, \ldots, v_{1p})^\top$ and $\mathbf{v_2}=(v_{21}, \ldots, v_{2p})^\top$ in $\mathbb{R}^p$, $\langle \mathbf{v_1}, \mathbf{v_2} \rangle = \mathbf{v_1}^\top \mathbf{v_2} = \sum_{r=1}^p v_{1r}v_{2r}$, and $\Vert \mathbf{v}_1 \Vert = \langle \mathbf{v}_1, \mathbf{v}_1 \rangle^{1/2} = (\sum_{r=1}^p v_{1r}^2)^{1/2}$.
-
-	Without loss of generality, assume that both multivariate functional and scalar data are centered; that is, $E(X)=0$ and $E(\mathbf{Z})=\mathbf{0}$.
-Our goal is to predict a real outcome $Y$ based on $X$ and $\mathbf{Z}$ via the following functional regression model:
-
-	\begin{equation}
-		Y = \sum \limits_{r=1}^p \alpha_r Z_r + \sum \limits_{k=1}^K \int_0^1 \beta^{(k)}(t_k) X^{(k)}(t_k) dt_k + \epsilon = \langle \boldsymbol{\alpha}, \mathbf{Z} \rangle +  \langle \beta, X \rangle_{\mathcal{F}}  + \epsilon
-		\label{eq: functional model}
-	\end{equation}
-	where $\boldsymbol{\alpha}=(\alpha_1, \ldots, \alpha_p)^\top \in \mathbb{R}^p$ and $\beta=(\beta^{(1)}, \ldots, \beta^{(K)}) \in \mathcal{F}$ are respectively the regression coefficient vector and function that characterize the effect of scalar and functional predictors on the outcome.
 
@@
 	we incorporate this roughness penalty to simultaneously control the complexity of the estimated functional components.
-
 	One possible approach is to extend the smoothed functional PCA framework of \citet{Rice1991} by modifying the objective in \eqref{def:maximizer_squared_empirical_cov} to
@@
 	where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness. 
+	However, this approach  \citet{Rice1991} assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense.
 
@@
 	\textit{Proposed estimation procedure.}~
-However, the above approach of \citet{Rice1991} assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense.
-As an alternative, we adopt the strategy of \citet{Silverman1996}, which replaces the standard orthonormality constraint with a weaker one based on a modified inner product that incorporates roughness.
+	To avoid the orthogonal basis assumption of  \citet{Rice1991}, we adopt the strategy of \citet{Silverman1996}, which replaces the standard orthonormality constraint with a weaker one based on a modified inner product that incorporates roughness.
 Accordingly, our estimation procedure at the $l$-th iteration, iteration index omitted and assuming the observations have been residualized in previous steps, solves the following optimization problem:

### 2025-07-23 create-FSHybridPLS.Rmd
ridge type formulation
delete gram matrix testthat

--- 2025-07-15 create-FSHybridPLS.Rmd
@@
 
-```{r}
-testthat::test_that("Gram matrix edge cases", {
-  suppressPackageStartupMessages(library(fda))
-
-  # Case 1: Fourier basis (orthogonal over [0, 1])
-  fb <- create.fourier.basis(rangeval = c(0, 1), nbasis = 5)
-  J_fourier <- compute_gram_matrix(fb)
-  testthat::expect_equal(J_fourier, diag(diag(J_fourier)), tolerance = 1e-10)  # Nearly diagonal
-
-  # Case 2: Constant basis (1 basis function)
-  cb <- create.constant.basis(rangeval = c(0, 1))
-  J_const <- compute_gram_matrix(cb)
-  testthat::expect_equal(dim(J_const), c(1, 1))
-  testthat::expect_equal(J_const[1, 1], 1)
-
-  # Case 3: Invalid input
-  testthat::expect_error(compute_gram_matrix("not a basisfd"))
-
-  # Case 4: Highly localized B-splines
-  # Simulate nearly disjoint support (narrow B-splines)
-  narrow_bs <- create.bspline.basis(rangeval = c(0, 1), nbasis = 10, norder = 2)
-  J_narrow <- compute_gram_matrix(narrow_bs)
-  testthat::expect_true(all(abs(J_narrow[upper.tri(J_narrow)]) < 0.5))  # off-diagonals small
-})
-
-```
-
 ## helpers for functional data objects
@@
     gram_list[[i]] <- compute_gram_matrix(basis_i)
+    gram_deriv2_list[[i]] <- compute_gram_matrix_deriv2(basis_i) # New function call
+
     n_basis_list[i] <- basis_i$nbasis
@@
       gram_list = gram_list,
+      gram_deriv2_list = gram_deriv2_list, # Store the new list
       n_basis_list = n_basis_list,
@@
 
-compare xi_hat_lin, xi_hat_lin_new
+### helper: get_xi_hat_linear
+```{r}
+get_xi_hat_linear_new <- function(W, y){
+  # new
+  ## step 1: inner products
+  u <- list()
+  u_j <- B %*% t(Theta_j) %*% y
+  for (j in 1:K){
+    Theta_t <- W$functional_list[[j]]$coefs
+    B <- W$gram_list[[j]]
+    u[[j]] <- B %*% Theta_t %*% y
+  }
+  v <- t(W$Z) %*% y
+
+  ## step 2: squared norm
+  q <- sum(v^2)
+  for (j in 1:K){
+    Theta_t <- W$functional_list[[j]]$coefs
+    R <- W$gram_list[[j]]
+    u[[j]] <- B %*% Theta_t %*% y
+  }  
+  # old
+  n <- W$n_sample
+  K <- W$n_functional
+  normalizer <- 0
+
+  for (i in 1:K){  ## tPhi_tC : C multiplied by Phi. Scalable to arbitrary K
+
+    d[[i]] <- Theta_t %*% y
+    normalizer <- normalizer + t(y) %*% t(Theta_t) %*% B %*% Theta_t %*% y
+  }
+  normalizer <- normalizer+ t(y) %*% W$Z %*% t(W$Z) %*% y
+  d_vec <- do.call(c, d)  # or: unlist(d)
+  d_vec <- d_vec/ sqrt(normalizer)
+  return(d_vec)
+}
+```
 

### 2025-07-23 create-FSHybridPLS.Rmd
compute_gram_matrix_deriv2

@@
 
-We check the following cases:
-
-| Case | Test                 | Expectation                             |
-|------|----------------------|------------------------------------------|
-| 1    | Orthogonal (Fourier) | Gram matrix ≈ diagonal                  |
-| 2    | Constant             | Single value equals interval length (1) |
-| 3    | Invalid              | Raises informative error                |
-| 4    | Narrow support       | Mostly low off-diagonal entries         |
+### compute_gram_matrix_deriv2
+```{r}
+# Helper function to compute the Gram matrix of the second derivatives of basis functions
+# This function assumes 'basisobj' is an 'fda' package basis object.
+compute_gram_matrix_deriv2 <- function(basisobj) {
+  # Get the range of the basis
+  basis_range <- basisobj$rangeval
+
+  # Create a function to evaluate the second derivative of a basis function
+  # This uses the 'eval.basis' function with 'Lfdobj = 2' for second derivative.
+  deriv2_basis_eval_fun <- function(t_vec) {
+    eval.basis(t_vec, basisobj, Lfdobj = 2)
+  }
+
+  # Numerically integrate the product of second derivatives of basis functions
+  # This is a general approach for computing inner products.
+  # For specific basis types (e.g., B-splines), there might be more efficient
+  # analytical solutions, but this approach is robust.
+  nbasis <- basisobj$nbasis
+  gram_matrix_deriv2 <- matrix(0, nbasis, nbasis)
+
+  for (j in 1:nbasis) {
+    for (k in 1:nbasis) {
+      # Define the integrand: product of the j-th and k-th second derivatives
+      integrand <- function(t) {
+        deriv2_basis_eval_fun(t)[, j] * deriv2_basis_eval_fun(t)[, k]
+      }
+      # Integrate over the basis range
+      gram_matrix_deriv2[j, k] <- integrate(integrand, lower = basis_range[1], upper = basis_range[2])$value
+    }
+  }
+  return(gram_matrix_deriv2)
+}
+```
 

### 2025-07-23 create-FSHybridPLS.Rmd
new formula aligns with the old when lambda=0

@@
 
-```{r}
-testthat::test_that("rep_fd correctly replicates a list of fd objects", {
-  suppressPackageStartupMessages(library(fda))
-
-  # Create a simple basis
-  basis <- create.bspline.basis(c(0, 1), 5)
-
-  # Create single-sample fd object
-  coef_vec <- 1:5
-  fd1 <- fd(coef = matrix(coef_vec, ncol = 1), basisobj = basis)
-
-  # Replicate the list
-  rep_list <- rep_fd(list(fd1, fd1), 3)
-
-  # Check: list length unchanged
-  testthat::expect_equal(length(rep_list), 2)
-
-  # Check each replicated fd object
-  for (fd_obj in rep_list) {
-    testthat::expect_s3_class(fd_obj, "fd")
-    testthat::expect_equal(dim(fd_obj$coefs), c(5, 3))  # 5 basis × 3 samples
-    for (i in 1:3) {
-      testthat::expect_equal(fd_obj$coefs[, i], coef_vec)
-    }
-  }
-
-  # Error if not single-sample
-  fd_multi <- fd(coef = matrix(1:10, nrow = 5, ncol = 2), basisobj = basis)
-  testthat::expect_error(rep_fd(list(fd_multi)), "Each fd object in the list must have one column")
-
-  # Error on non-fd input
-  testthat::expect_error(rep_fd(list(1, "not_fd")), "Input must be a list of 'fd' objects")
-})
-
-```
-
 # Class predictor_hybrid
@@
 
-  gram_list <- vector("list", n_functional)
+  gram_list <- gram_deriv2_list <- vector("list", n_functional)
   n_basis_list <- numeric(n_functional)
@@
     gram_list[[i]] <- compute_gram_matrix(basis_i)
-    gram_deriv2_list[[i]] <- compute_gram_matrix_deriv2(basis_i) # New function call
+    gram_deriv2_list[[i]] <- fda::getbasispenalty(basis_i) # New
 
@@
 
-Let's write some tests to make sure the function behaves as desired:
-```{r}
-testthat::test_that("predictor_hybrid constructor works as expected (S3, updated)", {
-  suppressPackageStartupMessages(library(fda))
-
-  # Create scalar matrix
-  Z <- matrix(rnorm(100 * 5), nrow = 100, ncol = 5)
-
-  # Create two fd objects with 100 replications
-  basis1 <- create.bspline.basis(c(0, 1), nbasis = 10)
-  basis2 <- create.bspline.basis(c(0, 1), nbasis = 20)
-
-  coef1 <- matrix(rnorm(10 * 100), nrow = 10)  # 10 basis × 100 samples
-  coef2 <- matrix(rnorm(20 * 100), nrow = 20)  # 20 basis × 100 samples
-
-  fd1 <- fd(coef = coef1, basisobj = basis1)
-  fd2 <- fd(coef = coef2, basisobj = basis2)
-
-  # Construct object
-  obj <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
-
-  # Assertions
-  testthat::expect_s3_class(obj, "predictor_hybrid")
-  testthat::expect_equal(nrow(obj$Z), 100)
-  testthat::expect_equal(ncol(obj$Z), 5)
-  testthat::expect_equal(length(obj$functional_list), 2)
-  testthat::expect_equal(obj$n_basis_list, c(10, 20))
-  testthat::expect_equal(obj$n_sample, 100)
-  testthat::expect_equal(obj$n_functional, 2)
-  testthat::expect_equal(obj$n_scalar, 5)
-  testthat::expect_equal(dim(obj$gram_list[[1]]), c(10, 10))
-  testthat::expect_equal(dim(obj$gram_list[[2]]), c(20, 20))
-})
-```
-
 ### predictor_hybrid_from_coef
@@
 
-**unit test**
-```{r}
-testthat::test_that("hybrid_from_coef reconstructs single-sample predictor_hybrid correctly", {
-  suppressPackageStartupMessages(library(fda))
-
-  make_fd <- function(coefs, basis) {
-    fd(coef = coefs, basisobj = basis)
-  }
-
-  basis <- create.bspline.basis(c(0, 1), nbasis = 4)
-  n_sample <- 5
-  n_scalar <- 2
-  n_functional <- 2
-
-  # Create dummy functional list with zeros
-  fd1 <- make_fd(matrix(0, 4, n_sample), basis)
-  fd2 <- make_fd(matrix(0, 4, n_sample), basis)
-  Z <- matrix(0, n_sample, n_scalar)
-  obj_template <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
-
-  # Create coefficient vector for reconstruction: 4 + 4 + 2 = 10
-  xi_star <- c(1:10)
-
-  # Apply reconstruction
-  obj_single <- predictor_hybrid_from_coef(obj_template, xi_star)
-
-  # Checks
-  testthat::expect_s3_class(obj_single, "predictor_hybrid")
-  testthat::expect_equal(obj_single$n_sample, 1)
-  testthat::expect_equal(obj_single$Z, matrix(c(9, 10), nrow = 1))
-
-  # Check functional coefficients (use coef() not $coefs)
-  testthat::expect_equal(drop(coef(obj_single$functional_list[[1]])), 1:4)
-  testthat::expect_equal(drop(coef(obj_single$functional_list[[2]])), 5:8)
-})
-```
-
 ## Basic arithmetic
@@
 
-Here are the unit tests:
-| Case                    | Description                         | Expected Outcome |
-| ----------------------- | ----------------------------------- | ---------------- |
-| ✅ Same sample size      | Functional and scalar values summed | Pass             |
-| ✅ Broadcast one → many  | One-sample input broadcasted        | Pass             |
-| ✅ Broadcast many ← one  | One-sample other broadcasted        | Pass             |
-| ❌ Basis mismatch        | Different functional basis          | Error            |
-| ❌ Irregular sample size | Neither matches nor is singleton    | Error            |
-| ❌ Different dimensions  | Functional or scalar count mismatch | Error            |
-```{r}
-testthat::test_that("add.predictor_hybrid handles broadcasting and basis compatibility", {
-  suppressPackageStartupMessages(library(fda))
-
-  # Create shared B-spline basis
-  basis <- create.bspline.basis(c(0, 1), nbasis = 5)
-
-  # Helper to generate a valid coefficient matrix
-  coef_mat <- function(val, n_sample, basis_obj) {
-    nbasis <- basis_obj$nbasis
-    matrix(val, nrow = nbasis, ncol = n_sample)
-  }
-
-  # Helper to create a list of fd objects (2 functional predictors)
-  fd_list <- function(val, n_sample, basis_obj = basis) {
-    list(
-      fd(coef = coef_mat(val, n_sample, basis_obj), basisobj = basis_obj),
-      fd(coef = coef_mat(val, n_sample, basis_obj), basisobj = basis_obj)
-    )
-  }
-
-  # Scalar predictors
-  Z1 <- matrix(1, nrow = 1, ncol = 2)
-  Z3 <- matrix(3, nrow = 3, ncol = 2)
-
-  # Functional predictors (same basis)
-  F1 <- fd_list(1, 1)
-  F3 <- fd_list(3, 3)
-
-  # Create predictor_hybrid objects
-  x1 <- predictor_hybrid(Z1, F1)  # 1 sample
-  x3 <- predictor_hybrid(Z3, F3)  # 3 samples
-
-  # Broadcast x1 to match x3
-  result <- add.predictor_hybrid(x1, x3, alpha = 1)
-
-  # Check metadata
-  testthat::expect_s3_class(result, "predictor_hybrid")
-  testthat::expect_equal(result$n_sample, 3)
-  testthat::expect_equal(result$n_scalar, 2)
-  testthat::expect_equal(result$n_functional, 2)
-
-  # Check scalar component
-  expected_Z <- matrix(4, nrow = 3, ncol = 2)  # 1 + 3 = 4
-  testthat::expect_equal(result$Z, expected_Z)
-
-  # Check functional component
-  for (fd_out in result$functional_list) {
-    testthat::expect_equal(unname(coef(fd_out)), matrix(4, nrow = 5, ncol = 3))
-  }
-
-  # Test symmetry: broadcasting x3 + x1
-  result2 <- add.predictor_hybrid(x3, x1, alpha = 1)
-  testthat::expect_equal(result2$Z, expected_Z)
-  for (fd_out in result2$functional_list) {
-    testthat::expect_equal(unname(coef(fd_out)), matrix(4, nrow = 5, ncol = 3))
-  }
-
-  # Incompatible sample sizes (should fail)
-  x_bad <- predictor_hybrid(matrix(1, 2, 2), fd_list(1, 2))
-  testthat::expect_error(add.predictor_hybrid(x3, x_bad), "incompatible for broadcasting")
-
-  # Incompatible functional basis (should fail)
-  bad_basis <- create.bspline.basis(c(0, 1), nbasis = 6)
-  bad_fd <- fd_list(2, 3, bad_basis)
-  x_basis_mismatch <- predictor_hybrid(Z3, bad_fd)
-  testthat::expect_error(add.predictor_hybrid(x3, x_basis_mismatch), "same basis")
-})
-
-```
 ### subtr.predictor_hybrid
@@
 
-Here is a test code with two functional predictors:
-```{r}
-testthat::test_that("scalar_mul.predictor_hybrid works with two functional predictors", {
-  suppressPackageStartupMessages(library(fda))
-
-  # Scalar part (3 observations, 2 scalar predictors)
-  Z <- matrix(2, nrow = 3, ncol = 2)
-
-  # Functional part: shared B-spline basis
-  basis <- create.bspline.basis(c(0, 1), nbasis = 5)
-  fd1 <- fd(coef = matrix(2, nrow = 5, ncol = 3), basisobj = basis)
-  fd2 <- fd(coef = matrix(2, nrow = 5, ncol = 3), basisobj = basis)
-
-  # Construct hybrid object using new simplified constructor
-  obj <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
-
-  # Apply scalar multiplication
-  scaled <- scalar_mul.predictor_hybrid(obj, scalar = 4)
-
-  # Check class
-  testthat::expect_s3_class(scaled, "predictor_hybrid")
-
-  # Check scalar predictor was scaled
-  testthat::expect_equal(scaled$Z, Z * 4)
-
-  # Check each functional component's coefficients
-  expected_coef <- matrix(8, nrow = 5, ncol = 3)
-  for (fd_obj in scaled$functional_list) {
-    testthat::expect_equal(
-      unname(coef(fd_obj)),
-      unname(expected_coef)
-    )
-  }
-})
-```
 ### inprod.predictor_hybrid
@@
 $$
-```{r}
-#' Construct the roughness penalty matrix for a predictor_hybrid object
-#'
-#' Returns a block diagonal matrix representing roughness penalties for each functional predictor
-#' and zeros for the scalar predictors (scalar predictors are not penalized).
-Each functional component uses its own basis penalty matrix, computed via second derivative penalty via `getbasispenalty()` from the `fda` package
-#'
-#' @param W A `predictor_hybrid` object.
-#'
-#' @return A block diagonal penalty matrix of dimension `(sum(n_basis_list) + n_scalar)^2`.
-#' @export
-get_penalty_hybrid <- function(W){
-  J_dotdot_star <- fda::getbasispenalty(W$functional_list[[1]]$basis)
-  for (ii in 2:(W$n_functional)){
-    J_dotdot_star <- Matrix::bdiag(
-      J_dotdot_star,
-      fda::getbasispenalty(W$functional_list[[ii]]$basis)
-    )
-    }
-  J_dotdot_star <- Matrix::bdiag(
-    J_dotdot_star,
-    matrix(0, nrow = W$n_scalar, ncol = W$n_scalar)
-    )
-  return(J_dotdot_star)
-  }
-```
 
@@
 ```{r}
-get_xi_hat_linear_new <- function(W, y){
+get_xi_hat_linear_pen <- function(W, y, lambda){
   # new
   ## step 1: inner products
-  u <- list()
-  u_j <- B %*% t(Theta_j) %*% y
+    n <- W$n_sample
+  K <- W$n_functional
+  u <- gamma <- list()
+
+  v <- t(W$Z) %*% y
+  q <- sum(v^2)
   for (j in 1:K){
@@
     u[[j]] <- B %*% Theta_t %*% y
-  }
-  v <- t(W$Z) %*% y
-
+
+    # linear system
+    R <- W$gram_list[[j]] + lambda[j] * W$gram_deriv2_list[[j]]
+    U_cholesky <- chol(R)
+    L_cholesky <- t(U_cholesky)
+    intermediate <- forwardsolve(L_cholesky, u[[j]])
+    gamma[[j]] <- backsolve(U_cholesky, intermediate)
+
+     #q
+    q <- q + sum( u[[j]] * gamma[[j]] )
+  }
+  d_vec <- c(do.call(c, gamma), v)  # or: unlist(d)
   ## step 2: squared norm
-  q <- sum(v^2)
-  for (j in 1:K){
-    Theta_t <- W$functional_list[[j]]$coefs
-    R <- W$gram_list[[j]]
-    u[[j]] <- B %*% Theta_t %*% y
-  }  
-  # old
-  n <- W$n_sample
-  K <- W$n_functional
-  normalizer <- 0
-
-  for (i in 1:K){  ## tPhi_tC : C multiplied by Phi. Scalable to arbitrary K
-
-    d[[i]] <- Theta_t %*% y
-    normalizer <- normalizer + t(y) %*% t(Theta_t) %*% B %*% Theta_t %*% y
-  }
-  normalizer <- normalizer+ t(y) %*% W$Z %*% t(W$Z) %*% y
-  d_vec <- do.call(c, d)  # or: unlist(d)
-  d_vec <- d_vec/ sqrt(normalizer)
+  d_vec <- d_vec/ sqrt(q)
   return(d_vec)
@@
 lambda <- rep(0, W$n_functional)
-constr_mat <- get_constraint_matrix_hybrid(W, lambda)
-L <- chol(constr_mat)
+#constr_mat <- get_constraint_matrix_hybrid(W, lambda)
+#L <- chol(constr_mat)
 
@@
 
-xi_hat_lin <- get_xi_hat_linear(W, y)
+xi_hat_pen <- get_xi_hat_linear_pen(W, y, lambda)
 xi_hat_lin_new <- get_xi_hat_linear_new(W, y)

### 2025-07-23 create-FSHybridPLS.Rmd
delete get_xi_hat_linear

@@
 ```{r}
-get_xi_hat_linear_new <- function(W, y){
-  n <- W$n_sample
-  K <- W$n_functional
-  normalizer <- 0
-  d = list()
-  for (i in 1:K){  ## tPhi_tC : C multiplied by Phi. Scalable to arbitrary K
-    Theta_t <- W$functional_list[[i]]$coefs
-    B <- W$gram_list[[i]]
-    d[[i]] <- Theta_t %*% y
-    normalizer <- normalizer + t(y) %*% t(Theta_t) %*% B %*% Theta_t %*% y
-  }
-  d[[K+1]] <- t(W$Z) %*% y
-  normalizer <- normalizer+ t(y) %*% W$Z %*% t(W$Z) %*% y
-  d_vec <- do.call(c, d)  # or: unlist(d)
-  d_vec <- d_vec/ sqrt(normalizer)
-  return(d_vec)
-}
-```
-
-### helper: get_xi_hat_linear
-```{r}
 get_xi_hat_linear_pen <- function(W, y, lambda){

### 2025-07-23 create-FSHybridPLS.Rmd
compute_gram_matrix_deriv2 not needed

@@
 
-### compute_gram_matrix_deriv2
-```{r}
-# Helper function to compute the Gram matrix of the second derivatives of basis functions
-# This function assumes 'basisobj' is an 'fda' package basis object.
-compute_gram_matrix_deriv2 <- function(basisobj) {
-  # Get the range of the basis
-  basis_range <- basisobj$rangeval
-
-  # Create a function to evaluate the second derivative of a basis function
-  # This uses the 'eval.basis' function with 'Lfdobj = 2' for second derivative.
-  deriv2_basis_eval_fun <- function(t_vec) {
-    eval.basis(t_vec, basisobj, Lfdobj = 2)
-  }
-
-  # Numerically integrate the product of second derivatives of basis functions
-  # This is a general approach for computing inner products.
-  # For specific basis types (e.g., B-splines), there might be more efficient
-  # analytical solutions, but this approach is robust.
-  nbasis <- basisobj$nbasis
-  gram_matrix_deriv2 <- matrix(0, nbasis, nbasis)
-
-  for (j in 1:nbasis) {
-    for (k in 1:nbasis) {
-      # Define the integrand: product of the j-th and k-th second derivatives
-      integrand <- function(t) {
-        deriv2_basis_eval_fun(t)[, j] * deriv2_basis_eval_fun(t)[, k]
-      }
-      # Integrate over the basis range
-      gram_matrix_deriv2[j, k] <- integrate(integrand, lower = basis_range[1], upper = basis_range[2])$value
-    }
-  }
-  return(gram_matrix_deriv2)
-}
-```
-
 ## helpers for functional data objects
@@
 
-```{r}
-library(fda)
-
-# --- Step 1: Simulate Data ---
-set.seed(2222)
-
-n_sample <- 100
-n_scalar <- 2
-n_basis <- 5
-n_functional <- 2
-
-# Scalar predictors Z (centered)
-Z <- matrix(rnorm(n_sample * n_scalar), ncol = n_scalar)
-Z <- scale(Z, center = TRUE, scale = FALSE)
-
-# Create functional predictors (centered)
-basis <- create.bspline.basis(c(0, 1), nbasis = n_basis)
-functional_list <- list()
-for (j in 1:n_functional) {
-  coefs <- matrix(rnorm(n_basis * n_sample), nrow = n_basis)
-  fdobj <- fd(coef = coefs, basisobj = basis)
-  mean_fd <- mean.fd(fdobj)
-  mean_coef <- coef(mean_fd)
-  centered_coefs <- coefs - matrix(mean_coef, nrow = n_basis, ncol = n_sample)
-  functional_list[[j]] <- fd(coef = centered_coefs, basisobj = basis)
-}
-
-# --- Step 2: Construct hybrid object ---
-W <- predictor_hybrid(Z = Z, functional_list = functional_list)
-
-# --- Step 3: Simulate and center response ---
-total_coef_len <- sum(W$n_basis_list) + W$n_scalar
-true_coef <- rnorm(total_coef_len)
-
-# Flatten design matrix
-Xmat <- matrix(NA, n_sample, total_coef_len)
-for (i in 1:n_sample) {
-  W_i <- subset_predictor_hybrid(W, i)
-  func_coefs <- do.call(c, lapply(W_i$functional_list, function(fdobj) as.vector(coef(fdobj))))
-  Xmat[i, ] <- c(func_coefs, W_i$Z)
-}
-
-y <- Xmat %*% true_coef + rnorm(n_sample, sd = 0.1)
-y <- as.vector(scale(y, center = TRUE, scale = FALSE))
-
-# --- Step 4: Compute constraint matrix ---
-lambda <- rep(0, W$n_functional)
-constr_mat <- get_constraint_matrix_hybrid(W, lambda)
-L <- chol(constr_mat)
-
-# --- Step 5: Run eigen-based PLS ---
-W_template <- W  # prevent mutation
-
-pls_eig_result <- get_pls_comp(W, y, L)
-xi_hat_eig <- pls_eig_result$xi_hat
-
-xi_hat_lin <- get_xi_hat_linear(W, y)
-xi_hat_lin_new <- get_xi_hat_linear_new(W, y)
-# Wrap into predictor_hybrid object using format template
-xi_hat_direct <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin)
-xi_hat_direct_new <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin_new)
-
-# Normalize
-norm_val <- sqrt(inprod.predictor_hybrid(xi_hat_direct))
-xi_hat_direct <- scalar_mul.predictor_hybrid(xi_hat_direct,  1 / norm_val)
-
-# --- Step 7: Compare and evaluate ---
-ip <- inprod.predictor_hybrid(xi_hat_eig, xi_hat_direct)
-norm1 <- sqrt(inprod.predictor_hybrid(xi_hat_eig))
-xi_hat_eig <- scalar_mul.predictor_hybrid(xi_hat_eig,  1 / norm1)
-
-norm2 <- sqrt(inprod.predictor_hybrid(xi_hat_direct))
-cat("norm 1", norm1,  "\n")
-cat("norm 2", norm2,  "\n")
-
-cos_theta <- ip / (norm1 * norm2)
-
-cat("Cosine similarity between eigen-based and direct PLS components:", cos_theta, "\n")
-cat("Projection score (eig):", sum(inprod.predictor_hybrid(xi_hat_eig, W) * y), "\n")
-cat("Projection score (direct):", sum(inprod.predictor_hybrid(xi_hat_direct, W) * y), "\n")
-
-# --- Step 8: Plot functional coefficients ---
-par(mfrow = c(n_functional, 1), mar = c(4, 4, 2, 2))
-for (j in 1:n_functional) {
-  plot(xi_hat_eig$functional_list[[j]], col = "blue", ylim = c(-1, 1),
-       main = paste("Functional Component", j), ylab = "Coefficient", xlab = "t")
-  lines(xi_hat_direct$functional_list[[j]], col = "red", lty = 2)
-  legend("topright", legend = c("Eigen-based", "Direct"), col = c("blue", "red"), lty = 1:2)
-}
-
-```
-
 ## Residualization

### 2025-07-23 create-FSHybridPLS.Rmd
are_all_gram_matrices_identical

@@
 
+```{r}
+#' Check if all matrices in a list are identical (with tolerance for numeric comparison)
+#'
+#' This function iterates through a list of matrices and checks if all subsequent
+#' matrices are numerically identical to the first matrix in the list.
+#' It uses `all.equal` for robust comparison of numeric matrices, which accounts
+#' for small floating-point differences.
+#'
+#' @param gram_list A list of matrices.
+#' @param tolerance A numeric tolerance for comparing floating-point numbers.
+#'                  Defaults to `sqrt(.Machine$double.eps)`.
+#' @return A logical value: `TRUE` if all matrices are identical, `FALSE` otherwise.
+#' @export
+are_all_gram_matrices_identical <- function(gram_list, tolerance = sqrt(.Machine$double.eps)) {
+  # Handle edge cases: empty list or list with a single matrix
+  if (length(gram_list) == 0) {
+    message("The input list is empty. Returning TRUE as there are no differences.")
+    return(TRUE)
+  }
+  if (length(gram_list) == 1) {
+    message("The input list contains only one matrix. Returning TRUE.")
+    return(TRUE)
+  }
+
+  # Get the first matrix as the reference
+  first_matrix <- gram_list[[1]]
+
+  # Ensure the first element is a matrix
+  if (!is.matrix(first_matrix)) {
+    stop("The first element of 'gram_list' is not a matrix.")
+  }
+
+  # Iterate from the second matrix onwards and compare with the first
+  for (i in 2:length(gram_list)) {
+    current_matrix <- gram_list[[i]]
+
+    # Ensure current element is a matrix
+    if (!is.matrix(current_matrix)) {
+      stop(paste("Element", i, "of 'gram_list' is not a matrix."))
+    }
+
+    # Compare the current matrix with the first matrix
+    # all.equal returns TRUE if identical, or a character string describing differences
+    # We convert the result to a logical TRUE/FALSE
+    if (!isTRUE(all.equal(first_matrix, current_matrix, tolerance = tolerance))) {
+      # If not equal, return FALSE immediately
+      message(paste("Matrices at index 1 and", i, "are not identical."))
+      return(FALSE)
+    }
+  }
+
+  # If the loop completes, all matrices are identical
+  return(TRUE)
+}
+```
+
+```{r}
+
+# --- Example Usage ---
+
+# Example 1: All matrices are identical
+mat1 <- matrix(c(1, 2, 3, 4), nrow = 2)
+mat2 <- matrix(c(1, 2, 3, 4), nrow = 2)
+mat3 <- matrix(c(1, 2, 3, 4), nrow = 2)
+identical_list <- list(mat1, mat2, mat3)
+print("Test Case 1: All matrices identical")
+print(are_all_gram_matrices_identical(identical_list)) # Expected: TRUE
+
+# Example 2: Matrices with slight floating-point differences (within tolerance)
+mat4 <- matrix(c(1.000000000000001, 2, 3, 4), nrow = 2)
+mat5 <- matrix(c(1, 2, 3, 4), nrow = 2)
+tolerance_list <- list(mat4, mat5)
+print("Test Case 2: Matrices with slight floating-point differences")
+print(are_all_gram_matrices_identical(tolerance_list)) # Expected: TRUE
+
+# Example 3: Matrices are not identical
+mat6 <- matrix(c(1, 2, 3, 5), nrow = 2) # Different value
+non_identical_list <- list(mat1, mat6, mat3)
+print("Test Case 3: Matrices are not identical")
+print(are_all_gram_matrices_identical(non_identical_list)) # Expected: FALSE
+
+# Example 4: List with different dimensions
+mat7 <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 3)
+diff_dim_list <- list(mat1, mat7)
+print("Test Case 4: Matrices with different dimensions")
+print(are_all_gram_matrices_identical(diff_dim_list)) # Expected: FALSE (all.equal will catch this)
+
+# Example 5: Empty list
+empty_list <- list()
+print("Test Case 5: Empty list")
+print(are_all_gram_matrices_identical(empty_list)) # Expected: TRUE
+
+# Example 6: List with a single matrix
+single_matrix_list <- list(mat1)
+print("Test Case 6: Single matrix list")
+print(are_all_gram_matrices_identical(single_matrix_list)) # Expected: TRUE
+
+# Example 7: List containing non-matrix elements (will stop with an error)
+# non_matrix_list <- list(mat1, "not a matrix", mat3)
+# print("Test Case 7: List with non-matrix element (will throw error)")
+# print(are_all_gram_matrices_identical(non_matrix_list))
+```
+
 ## helpers for functional data objects

### 2025-07-23 manuscript/main.tex
delete gram matrix testthat
man: wrote down the penalized least square criterion

@@
 	Let ${b_m(t)}$ be a twice-differentiable basis of $L^2([0,1])$ whose second derivatives are also linearly independent, for example, cubic B-splines, the Fourier basis, or an orthonormal polynomial basis of degree greater than three.
-Using this basis, the $j$th functional predictor, regression coefficient, and PLS direction (suppressing iteration indices) are represented as follows:
+Using this basis, the $j$th functional predictor, regression coefficient,  PLS direction (suppressing iteration indices) are represented as follows:
 	\begin{equation*}
@@
 	We describe the strategy at the $l$-th iteration.
-For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for details).
-The  PLS component direction is estimated by the unit-norm direction $\xi \in \widetilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as
+%For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for details).
+	The  PLS component direction is estimated by the unit-norm direction $\xi^{[l]} \in \widetilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as
 
@@
 Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative
-	\begin{equation}
-		\operatorname{PEN}(\hat{\xi}_j) := \int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt.
+	\begin{equation}\label{def:roughness_penalty}
+		\operatorname{PEN}(\hat{\xi}_j) := \int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
+		.
 	\end{equation}
@@
 		\[
-		\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M \quad \text{for } j = 1, \ldots, K, \quad \text{and} \quad \mathbf{v} := Z^\top \mathbf{y} \in \mathbb{R}^p.
+		\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M \quad \text{for } j = 1, \ldots, K, \quad \text{and} \quad \mathbf{v} := \mathbf{Z}^\top \mathbf{y} \in \mathbb{R}^p.
 		\]  
@@
 	\subsection{Step 2: Computing Residualized Predictors via Hybrid-on-Scalar Regression} \label{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}
-	The second step of the PLS algorithm involves iteratively obtaining the ($l+1$)-th residualized predictors as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$, where $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ is the least squares estimate from regressing the previous ($l$-th) residualized outcome $\mathbf{W}_i^{[l]}[\mathbf{t}]$ on the corresponding  estimated PLS score $\widehat{\rho}_{il}$.
-The pointwise least squares estimate, $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] = (\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \widehat{\rho}_{il})/(\sum_{i=1}^n \widehat{\rho}_{il}^2)$, presented in Section \ref{sec: Naive PLS Algorithm}, however, is  highly inefficient and may not be even feasible for multiple dense and/or irregular functional data.
-Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components.
-Therefore, in this section, we introduce a novel strategy based on a hybrid-on-scalar regression model for obtaining $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ and implementing the second step.
-
-	Again, we omit $l$ in the notations.
-Let $\widehat{\boldsymbol{\rho}}=(\widehat{\rho}_1, \ldots, \widehat{\rho}_n)^\top$ denote an $n$-dimensional vector of PLS scores estimated from the proposed algorithm, and let the $(K+P)$-vector $\boldsymbol{\delta}[\mathbf{t}] = [\pi(\mathbf{t})^\top, \boldsymbol{\gamma}^\top]^\top$ denote the regression coefficient consisting of the functional part $\pi(\mathbf{t}) = (\pi^{(1)}(t_1), \ldots,\pi^{(K)}(t_K))^\top \in \mathbb{R}^K$ and scalar part $\boldsymbol{\gamma} = (\gamma_1, \ldots,\gamma_p)^\top \in \mathbb{R}^p$.
-The hybrid-on-scalar regression model we are interested in fitting is then:
-	\begin{equation}
-		\widetilde{W}[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top + \mathbf{e}[\mathbf{t}],
-		\label{eq: hybrid on scalar regression model}
-	\end{equation}
-	where $\mathbf{e}[\mathbf{t}]$ is an $n \times (K+p)$ matrix of errors.
-
-	As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$.
+The $l$-th iteration's second step involves orthogonalization.
+This is achieved by fitting a hybrid-on-scalar regression model, $$\widetilde{W}^{[l]}_i = \hat{\rho}^{[l]}\, \delta^{[l]} + E_i^{[l]},$$ and then taking the residuals.
+Here, $\delta^{[l]}$ and $E_i^{[l]}$ are the regression coefficient and error terms, respectively, both elements of $\tilde{\mathcal{H}}$ defined in \eqref{def:truncated_hilbert_space}.
+In the same spirit as in Section \ref{sec: Regularization of PLS Components}, we want the estimated regression coefficieint $\hat{\delta}^{[l]}
+= 
+(\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} )$ 
+have  smooth functional parts, for the whole PLS estimation proecedure to be stable.
+Therefore, we obtain $\delta^{[l]}$ by minimizing the followign penaluized least square criteria, where the functional part is penalized by 
+ integeraed squared second derivative defined in \eqref{def:roughness_penalty}:
+ \begin{align*}
+\operatorname{PENSSE}( \delta)
+&=
+\sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta,
+\,
+\widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta
+\rangle_{\mathcal{H}}
+%%%%%%%%%%%%%%%%%%%%
+\\&=
+\sum_{i=1}^n 
+\langle \widetilde{W}_i^{[l]},  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
++
+\sum_{i=1}^n 
+\langle \delta,  \, \delta \rangle_{\mathcal{H}}
+-
+\sum_{i=1}^n 
+( \hat{\rho}_i^{[l]} )^2
+\langle \delta,  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
+ \end{align*}
+
+%As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$.
 Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \boldsymbol{\gamma}^{(k)\top} \mathbf{b}^{(k)}(t_k)$, where $\boldsymbol{\gamma}^{(k)} = (d_1^{(k)}, \ldots, d_M^{(k)})\top \in \mathbb{R}^M$ are basis coefficients.
 Here, a different basis system can be flexibly chosen to expand the regression coefficient, but without loss of generality we use the same system as in Section \ref{subsec: Step 1: Computing Smoothed PLS components}.
-With the $(MK+p)$-dimensional row vector $\boldsymbol{\gamma}^* = (\boldsymbol{\gamma}^{(1)\top}, \ldots, \boldsymbol{\gamma}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as: $\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}]$.
+With the $(MK+p)$-dimensional row vector $\boldsymbol{\gamma}^* = (\boldsymbol{\gamma}^{(1)\top}, \ldots, \boldsymbol{\gamma}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as:
+$\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}]$.
 Finally, these basis expansions of the hybrid response and the regression coefficient enable us to re-write the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model} in a finite-dimensional form:
@@
 \end{equation}
+$\mathbf{e}[\mathbf{t}]$ is an $n \times (K+p)$ matrix of errors. 
+\\
 
@@
 Specifically, the $(l-1)$-th residualized response can be obtained as $Y_i^{[l+1]} = Y_i^{[l]} - \widehat{\nu}_l \widehat{\rho}_{il}$, where $\widehat{\nu}_l = \sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}/\sum_{i=1}^n \widehat{\rho}_{il}^2$  is the least square estimate of the simple linear model regressing $Y_i^{[l]}$ on $\widehat{\rho}_{il}$.
+	 the PLS algorithm involves iteratively obtaining the ($l+1$)-th residualized predictors as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$, where $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ is the least squares estimate from regressing the previous ($l$-th) residualized outcome $\mathbf{W}_i^{[l]}[\mathbf{t}]$ on the corresponding  estimated PLS score $\widehat{\rho}_{il}$.
+The pointwise least squares estimate, $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] = (\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \widehat{\rho}_{il})/(\sum_{i=1}^n \widehat{\rho}_{il}^2)$, presented in Section \ref{sec: Naive PLS Algorithm}, however, is  highly inefficient and may not be even feasible for multiple dense and/or irregular functional data.
+Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components.
+Therefore, in this section, we introduce a novel strategy based on a hybrid-on-scalar regression model for obtaining $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ and implementing the second step.
+
+	Again, we omit $l$ in the notations.
+Let $\widehat{\boldsymbol{\rho}}=(\widehat{\rho}_1, \ldots, \widehat{\rho}_n)^\top$ denote an $n$-dimensional vector of PLS scores estimated from the proposed algorithm, and let the $(K+P)$-vector $\boldsymbol{\delta}[\mathbf{t}] = [\pi(\mathbf{t})^\top, \boldsymbol{\gamma}^\top]^\top$ denote the regression coefficient consisting of the functional part $\pi(\mathbf{t}) = (\pi^{(1)}(t_1), \ldots,\pi^{(K)}(t_K))^\top \in \mathbb{R}^K$ and scalar part $\boldsymbol{\gamma} = (\gamma_1, \ldots,\gamma_p)^\top \in \mathbb{R}^p$.
 

### 2025-07-23 manuscript/main.tex
man: pls score

@@
 	Let ${b_m(t)}$ be a twice-differentiable basis of $L^2([0,1])$ whose second derivatives are also linearly independent, for example, cubic B-splines, the Fourier basis, or an orthonormal polynomial basis of degree greater than three.
-Using this basis, the $j$th functional predictor, regression coefficient,  PLS direction (suppressing iteration indices) are represented as follows:
-	\begin{equation*}
-		X_{ij}(t) = \sum_{m=1}^\infty \theta_{ijm} \, b_m(t),\quad
-		\beta_j(t) = \sum_{m=1}^\infty \eta_{jm} \, b_m(t),\quad
+Using this basis,
+	the $j$th functional predictor, 
+	regression coefficient, PLS component direction, and orthogonalization regression coefficient (with iteration indices suppressed) are represented as follows:
+	\begin{equation*}
+		X_{ij}(t) = \sum_{m=1}^\infty \theta_{ijm} \, b_m(t),~
+		\beta_j(t) = \sum_{m=1}^\infty \eta_{jm} \, b_m(t),~
 		%%%%%%%%%%%%%%%%%%%%%%
@@
 		\gamma_{jm}
+		b_m(t),
+		~
+		\delta_j(t)
+=
+\sum_{m=1}^\infty
+\pi_{jm}
 b_m(t)		
@@
 	\end{equation*}
-	and our suggest method restricts each PLS direction to admit the following expansion:
-	\begin{equation*}
-		\xi_j(t) = \sum_{m=1}^M \gamma_{jm} \, b_m(t).
-	\end{equation*}
+	and our suggest method restricts each PLS component direction and orthogonalization regression coefficient to admit the following expansion:
+	\begin{equation}\label{def:truncated_zeta_and_delta}
+		\xi_j(t) = \sum_{m=1}^M \gamma_{jm} \, b_m(t),
+		\quad
+				\delta_j(t)
+		=
+		\sum_{m=1}^M
+		\pi_{jm}
+		b_m(t)		
+	\end{equation}
 	This implies that all computations in this paper are carried out entirely within the subspace
@@
 	\end{equation*}
-	Let $\boldsymbol{\theta}_{ij}$, $\boldsymbol{\eta}_j$, and $\boldsymbol{\gamma}_j$ denote the $M$-dimensional vectors of coefficients:
+	Let $\boldsymbol{\theta}_{ij}$, $\boldsymbol{\eta}_j$,  $\boldsymbol{\gamma}_j$, and
+	$\boldsymbol{\pi}_j$
+	 denote the $M$-dimensional vectors of coefficients:
 	\begin{equation}\label{def:coef_vector_form}
 		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top,
-		\quad
-		\boldsymbol{\eta}_{j} := (\eta_{j1}, \ldots, \eta_{jM})^\top ,
-		\boldsymbol{\gamma}_{j} := (\gamma_{j1}, \ldots, \gamma_{jM})^\top.
+~
+		\boldsymbol{\eta}_{j} := (\eta_{j1}, \ldots, \eta_{jM})^\top ,~
+		\boldsymbol{\gamma}_{j} := (\gamma_{j1}, \ldots, \gamma_{jM})^\top,~
+			\boldsymbol{\pi}_{j} := (\pi_{j1}, \ldots, \pi_{jM})^\top
 	\end{equation}
 	For the predictors, we stack the coefficient vectors across observations into the matrix
-	\begin{equation}
+	\begin{equation}\label{def:theta}
 		\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
@@
 	where $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ are the Gram matrices of the basis functions and their second derivatives, with entries
-	\begin{equation}
+	\begin{equation}\label{def:B_matrix}
 		B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt, \quad
@@
 The $l$-th iteration's second step involves orthogonalization.
-This is achieved by fitting a hybrid-on-scalar regression model, $$\widetilde{W}^{[l]}_i = \hat{\rho}^{[l]}\, \delta^{[l]} + E_i^{[l]},$$ and then taking the residuals.
-Here, $\delta^{[l]}$ and $E_i^{[l]}$ are the regression coefficient and error terms, respectively, both elements of $\tilde{\mathcal{H}}$ defined in \eqref{def:truncated_hilbert_space}.
-In the same spirit as in Section \ref{sec: Regularization of PLS Components}, we want the estimated regression coefficieint $\hat{\delta}^{[l]}
-= 
-(\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} )$ 
-have  smooth functional parts, for the whole PLS estimation proecedure to be stable.
-Therefore, we obtain $\delta^{[l]}$ by minimizing the followign penaluized least square criteria, where the functional part is penalized by 
- integeraed squared second derivative defined in \eqref{def:roughness_penalty}:
+This is achieved by fitting a hybrid-on-scalar regression model, where the predictor is the PLS score for each observation.
+The individual PLS score is computed as  $\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \widehat{\xi}^{[l]} \rangle_{\mathcal{H}}$, utilizing the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}.Subsequently, using the basis expansion coefficient notation from \eqref{def:truncated_zeta_and_delta}, \eqref{def:coef_vector_form}, \eqref{def:theta}, and \eqref{def:B_matrix}, the full vector of PLS scores $\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top$ is computed through the following matrix multiplication:
+\begin{equation*}
+( \hat{\boldsymbol{\rho}}^{[l]} )^\top = \sum_{k=1}^K ( \hat{\boldsymbol{\gamma}}_j^{[l]})^\top B \, (\Theta_j^{[l]})^\top + \boldsymbol{\zeta}^\top (\mathbf{Z}^{[l]}).
+\end{equation*}
+Using this as a scalar predictor vector, we fit the regression model $\widetilde{W}^{[l]}_i = \hat{\rho}^{[l]}_i\, \delta^{[l]} + E_i^{[l]}$, and then take the residuals as the predictor for the next iteration, namely $\widetilde{W}^{[l+1]}_i$.
+Here, $\delta^{[l]}$ and $E_i^{[l]}$ are the regression coefficient and error terms, respectively, both elements of $\tilde{\mathcal{H}}$ as defined in \eqref{def:truncated_hilbert_space}.
+To ensure the stability of the entire PLS estimation procedure, the estimated regression coefficient $\hat{\delta}^{[l]} = (\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} )$ should have smooth functional parts, consistent with Section \ref{sec: Regularization of PLS Components}.
+Consequently, $\delta^{[l]}$ is obtained by minimizing a penalized least squares criterion, where the functional part is penalized by the integrated squared second derivative defined in \eqref{def:roughness_penalty}.
  \begin{align*}
@@
 \rangle_{\mathcal{H}}
++
+\tau
+\sum_{j=1}^K\operatorname{PEN}(\delta_j) 
 %%%%%%%%%%%%%%%%%%%%
@@
 \langle \widetilde{W}_i^{[l]},  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
-+
-\sum_{i=1}^n 
-\langle \delta,  \, \delta \rangle_{\mathcal{H}}
 -
 \sum_{i=1}^n 
+ \hat{\rho}_i^{[l]} 
+\langle \delta,  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
++
+\bigl(
+\sum_{i=1}^n 
 ( \hat{\rho}_i^{[l]} )^2
-\langle \delta,  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
+\bigr)
+\langle \delta,  \, \delta \rangle_{\mathcal{H}}
++
+\tau
+\sum_{j=1}^K\operatorname{PEN}(\delta_j) 
+\\&=
+ \operatorname{tr}(C^{*T} C^{*}J^{*}\Lambda) 
+ - 
+ 2 \operatorname{tr}(d^{*}J^{*}C^{*T} \rho\Lambda) 
+ +
+ \rho^T \rho
+  \operatorname{tr}( d^{*}J^{*}d^{*T} \Lambda) + \tau \operatorname{tr}(\ddot{d}^{*}J^{*}\ddot{d}^{*T}) \jongmin{need to be fixed}
  \end{align*}
 
+%Using the basis expansion coefficient notation presented in \eqref{def:truncated_zeta_and_delta} and \eqref{def:coef_vector_form}, \eqref{def:theta}, \eqref{def:B_matrix}
+\jongmin{Old writing starts here. I temporarily mixed the order of the paragraphs.}
 %As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$.

### 2025-07-23 manuscript/main.tex
man:orthogonalization proof started

@@
 	\end{proposition}
-	The proof of Proposition \ref{proposition:eigen_regul} is provided in Appendix  \ref{section:proof:proposition:linear_regul_system_unregularized}.
+	The proof of Proposition \ref{proposition:eigen_regul} is provided in Appendix  \ref{section:proof:proposition:eigen_regul}.
 	The smoothing parameter $\lambda_k > 0$ $(k = 1, \ldots, K)$ balances goodness of fit and smoothness in $\hat{\xi}_j$.
@@
 This is achieved by fitting a hybrid-on-scalar regression model, where the predictor is the PLS score for each observation.
-The individual PLS score is computed as  $\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \widehat{\xi}^{[l]} \rangle_{\mathcal{H}}$, utilizing the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}.Subsequently, using the basis expansion coefficient notation from \eqref{def:truncated_zeta_and_delta}, \eqref{def:coef_vector_form}, \eqref{def:theta}, and \eqref{def:B_matrix}, the full vector of PLS scores $\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top$ is computed through the following matrix multiplication:
+The individual PLS score is computed as  $\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathcal{H}}$, utilizing the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}.
+Subsequently, using the basis expansion coefficient notation from \eqref{def:truncated_zeta_and_delta}, \eqref{def:coef_vector_form}, \eqref{def:theta}, and \eqref{def:B_matrix}, the full vector of PLS scores $\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top$ is computed through the following matrix multiplication:
 \begin{equation*}
@@
 To ensure the stability of the entire PLS estimation procedure, the estimated regression coefficient $\hat{\delta}^{[l]} = (\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} )$ should have smooth functional parts, consistent with Section \ref{sec: Regularization of PLS Components}.
-Consequently, $\delta^{[l]}$ is obtained by minimizing a penalized least squares criterion, where the functional part is penalized by the integrated squared second derivative defined in \eqref{def:roughness_penalty}.
- \begin{align*}
+Consequently, $\delta^{[l]}$ is obtained by minimizing a penalized least squares criterion, where the functional part is penalized by the integrated squared second derivative defined in \eqref{def:roughness_penalty}:
+\begin{equation}\label{def:argmin_pensse}
+	\hat{\delta}^{[l]} := \arg \min_{\delta \in \tilde{\mathcal{H}}} \operatorname{PENSSE}( \delta),
+\end{equation}
+where
+\begin{equation}\label{def:pensse}
 	\operatorname{PENSSE}( \delta)
-&=
+	:=
 	\sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta,
@@
 	\tau
-\sum_{j=1}^K\operatorname{PEN}(\delta_j) 
-%%%%%%%%%%%%%%%%%%%%
-\\&=
-\sum_{i=1}^n 
-\langle \widetilde{W}_i^{[l]},  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
--
-\sum_{i=1}^n 
- \hat{\rho}_i^{[l]} 
-\langle \delta,  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
-+
-\bigl(
-\sum_{i=1}^n 
-( \hat{\rho}_i^{[l]} )^2
-\bigr)
-\langle \delta,  \, \delta \rangle_{\mathcal{H}}
-+
-\tau
-\sum_{j=1}^K\operatorname{PEN}(\delta_j) 
-\\&=
- \operatorname{tr}(C^{*T} C^{*}J^{*}\Lambda) 
- - 
- 2 \operatorname{tr}(d^{*}J^{*}C^{*T} \rho\Lambda) 
- +
- \rho^T \rho
-  \operatorname{tr}( d^{*}J^{*}d^{*T} \Lambda) + \tau \operatorname{tr}(\ddot{d}^{*}J^{*}\ddot{d}^{*T}) \jongmin{need to be fixed}
- \end{align*}
-
+	\sum_{j=1}^K\operatorname{PEN}(\delta_j).
+\end{equation}
+The following proposition shows that the solution of the problem \ref{def:argmin_pensse} can be obtained by solving linear equations.
+
+ \begin{proposition}[Closed-form  orthogonalization]\label{proposition:closed_form_orthgonalization}
+ 	asdasdasd
+ \end{proposition}
+ Proof of Proposition \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
 %Using the basis expansion coefficient notation presented in \eqref{def:truncated_zeta_and_delta} and \eqref{def:coef_vector_form}, \eqref{def:theta}, \eqref{def:B_matrix}
@@
 Therefore, in this section, we introduce a novel strategy based on a hybrid-on-scalar regression model for obtaining $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ and implementing the second step.
-
-	Again, we omit $l$ in the notations.
-Let $\widehat{\boldsymbol{\rho}}=(\widehat{\rho}_1, \ldots, \widehat{\rho}_n)^\top$ denote an $n$-dimensional vector of PLS scores estimated from the proposed algorithm, and let the $(K+P)$-vector $\boldsymbol{\delta}[\mathbf{t}] = [\pi(\mathbf{t})^\top, \boldsymbol{\gamma}^\top]^\top$ denote the regression coefficient consisting of the functional part $\pi(\mathbf{t}) = (\pi^{(1)}(t_1), \ldots,\pi^{(K)}(t_K))^\top \in \mathbb{R}^K$ and scalar part $\boldsymbol{\gamma} = (\gamma_1, \ldots,\gamma_p)^\top \in \mathbb{R}^p$.
 
@@
 
-		Now we prove Proposition \ref{proposition:eigen_regul}.
+		\section{Proof of Proposition \ref{proposition:eigen_regul} }\label{section:proof:proposition:eigen_regul}
 		The penalization term 
@@
 
+	\section{Proof of Proposition \ref{proposition:closed_form_orthgonalization} \ref{}}\label{section:proof:proposition:closed_form_orthgonalization}
+	 \begin{align*}
+		\operatorname{PENSSE}( \delta)
+		&=
+		\sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta,
+		\,
+		\widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta
+		\rangle_{\mathcal{H}}
+		+
+		\tau
+		\sum_{j=1}^K\operatorname{PEN}(\delta_j) 
+		%%%%%%%%%%%%%%%%%%%%
+		\\&=
+		\sum_{i=1}^n 
+		\langle \widetilde{W}_i^{[l]},  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
+		-
+		\sum_{i=1}^n 
+		\hat{\rho}_i^{[l]} 
+		\langle \delta,  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
+		+
+		\bigl(
+		\sum_{i=1}^n 
+		( \hat{\rho}_i^{[l]} )^2
+		\bigr)
+		\langle \delta,  \, \delta \rangle_{\mathcal{H}}
+		+
+		\tau
+		\sum_{j=1}^K\operatorname{PEN}(\delta_j) 
+		\\&=
+		\operatorname{tr}(C^{*T} C^{*}J^{*}\Lambda) 
+		- 
+		2 \operatorname{tr}(d^{*}J^{*}C^{*T} \rho\Lambda) 
+		+
+		\rho^T \rho
+		\operatorname{tr}( d^{*}J^{*}d^{*T} \Lambda) + \tau \operatorname{tr}(\ddot{d}^{*}J^{*}\ddot{d}^{*T}) \jongmin{need to be fixed}
+	\end{align*}
+
 	\section{Proof of Proposition \ref{Proposition: property of U}}\label{section:proof:Proposition: property of U}

### 2025-07-24 manuscript/main.tex
residualization closed form done

@@
 	$
-	and $\hat{\boldsymbol{\zeta}}$ is the scalar part. This maximizer can also be represented as a Euclidean vector
+	and $\hat{\boldsymbol{\zeta}}$ is the scalar part. This maximizer can also be represented as a concatenated Euclidean vector
 	\begin{equation}\label{def:maximizer_euclidean_form}
@@
 This is achieved by fitting a hybrid-on-scalar regression model, where the predictor is the PLS score for each observation.
-The individual PLS score is computed as  $\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathcal{H}}$, utilizing the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}.
-Subsequently, using the basis expansion coefficient notation from \eqref{def:truncated_zeta_and_delta}, \eqref{def:coef_vector_form}, \eqref{def:theta}, and \eqref{def:B_matrix}, the full vector of PLS scores $\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top$ is computed through the following matrix multiplication:
-\begin{equation*}
-( \hat{\boldsymbol{\rho}}^{[l]} )^\top = \sum_{k=1}^K ( \hat{\boldsymbol{\gamma}}_j^{[l]})^\top B \, (\Theta_j^{[l]})^\top + \boldsymbol{\zeta}^\top (\mathbf{Z}^{[l]}).
-\end{equation*}
-Using this as a scalar predictor vector, we fit the regression model $\widetilde{W}^{[l]}_i = \hat{\rho}^{[l]}_i\, \delta^{[l]} + E_i^{[l]}$, and then take the residuals as the predictor for the next iteration, namely $\widetilde{W}^{[l+1]}_i$.
+The individual PLS score is computed as
+\begin{equation}\label{def:plsscore}
+\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathcal{H}},
+\end{equation}
+ utilizing the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. 
+Using this as a scalar predictor observations, we fit the regression model $\widetilde{W}^{[l]}_i = \hat{\rho}^{[l]}_i\, \delta^{[l]} + E_i^{[l]}$, and then take the residuals as the predictor for the next iteration, namely $\widetilde{W}^{[l+1]}_i$.
 Here, $\delta^{[l]}$ and $E_i^{[l]}$ are the regression coefficient and error terms, respectively, both elements of $\tilde{\mathcal{H}}$ as defined in \eqref{def:truncated_hilbert_space}.
-To ensure the stability of the entire PLS estimation procedure, the estimated regression coefficient $\hat{\delta}^{[l]} = (\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} )$ should have smooth functional parts, consistent with Section \ref{sec: Regularization of PLS Components}.
+To ensure the stability of the entire PLS estimation procedure, the estimated regression coefficient $\hat{\delta}^{[l]} = (\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} ) \in \tilde{\mathcal{H}}$, should have smooth functional parts, consistent with Section \ref{sec: Regularization of PLS Components}.
 Consequently, $\delta^{[l]}$ is obtained by minimizing a penalized least squares criterion, where the functional part is penalized by the integrated squared second derivative defined in \eqref{def:roughness_penalty}:
@@
 
- \begin{proposition}[Closed-form  orthogonalization]\label{proposition:closed_form_orthgonalization}
- 	asdasdasd
+ \begin{proposition}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
+ 	Let us denote
+ 	\begin{equation*}
+ 		 		\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top
+ 	\quad\text{and} \quad
+ 			\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}
+ 	\end{equation*}
+ 	The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
+ 	$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients and scalar parts given by:
+\begin{equation*}
+	\hat{\boldsymbol{\pi}}_j^{[l]}
+	=
+	\bigl(
+		\bar{\rho}^{[l]}
+  B
+	+
+	\tau
+	B^{\prime \prime}
+	\bigr)^{-1}
+	  B
+	(\Theta_j^{[l]})^\top,
+	~
+	j = 1, \ldots, K,
+	%%%%%%%%%%%%%%%%%%%%%%%%
+	\quad
+	\hat{\boldsymbol{\chi} }
+	=
+	(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}.
+\end{equation*}
  \end{proposition}
  Proof of Proposition \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
+
+ Now we formally state the orthogonalization step.
+
 %Using the basis expansion coefficient notation presented in \eqref{def:truncated_zeta_and_delta} and \eqref{def:coef_vector_form}, \eqref{def:theta}, \eqref{def:B_matrix}
 \jongmin{Old writing starts here. I temporarily mixed the order of the paragraphs.}
-%As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$.
-Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \boldsymbol{\gamma}^{(k)\top} \mathbf{b}^{(k)}(t_k)$, where $\boldsymbol{\gamma}^{(k)} = (d_1^{(k)}, \ldots, d_M^{(k)})\top \in \mathbb{R}^M$ are basis coefficients.
-Here, a different basis system can be flexibly chosen to expand the regression coefficient, but without loss of generality we use the same system as in Section \ref{subsec: Step 1: Computing Smoothed PLS components}.
-With the $(MK+p)$-dimensional row vector $\boldsymbol{\gamma}^* = (\boldsymbol{\gamma}^{(1)\top}, \ldots, \boldsymbol{\gamma}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as:
-$\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}]$.
-Finally, these basis expansions of the hybrid response and the regression coefficient enable us to re-write the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model} in a finite-dimensional form:
-\begin{equation}
-	\widetilde{C}^* B^*[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] + \mathbf{e}[\mathbf{t}].
-	\label{eq: rewritten hybrid on scalar regression model}
-\end{equation}
-$\mathbf{e}[\mathbf{t}]$ is an $n \times (K+p)$ matrix of errors. 
-\\
-
-	Based on the model formulation \eqref{eq: rewritten hybrid on scalar regression model}, we can now formulate the following least squares criterion whose minimizing solution gives the estimate of the regression coefficient $\boldsymbol{\delta}[\mathbf{t}]$ in the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model}:
-\begin{equation}
-	\begin{aligned}
-		\textnormal{SSE}(\delta) &= \int_\mathcal{T} \left\Vert \,  \widetilde{C}^* B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] \, \right\Vert_F^2 \, d\mathbf{t}  \\
-		&= tr\left(\widetilde{C}^{*T}\widetilde{C}^*J^\ast \right) - 2\,tr \left(\boldsymbol{\gamma}^* J^\ast \widetilde{C}^{*T} \widehat{\boldsymbol{\rho}} \right) + tr\left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* J^\ast \boldsymbol{\gamma}^{*T}\right),
-	\end{aligned}
-	\label{eq: least squares}
-\end{equation}
-where $tr$ denotes the trace of a matrix, and $\Vert \cdot \Vert_F$ is a Frobenius norm.
-Now taking the derivative of \eqref{eq: least squares} with respect to $\boldsymbol{\gamma}^*$ and setting the result to zero, we find that  $\boldsymbol{\gamma}^*$ satisfies the system of linear equations
-\begin{equation*}
-	\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^*  J^\ast =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast,
-\end{equation*}
-whose solutions lead to the following estimates of $\boldsymbol{\gamma}^*$ and $\boldsymbol{\delta}[\mathbf{t}]$:
-\begin{equation*}
-	\widehat{\boldsymbol{\gamma}}^*  =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast \left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} J^\ast \right)^{-1} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}[\mathbf{t}] = B^*[\mathbf{t}]^\top \, \widehat{\boldsymbol{\gamma}}^{*\top}.
-\end{equation*}
 Then, we can use $\widehat{\boldsymbol{\delta}}[\mathbf{t}]$ to obtain the subsequent residualized hybrid predictor as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$.
@@
 			\boldsymbol{\xi}^{\top} \Lambda \mathbb{B}^{\prime \prime} \boldsymbol{\xi},
+			\numberthis \label{pen_as_matrix}
 		\end{align*}
@@
 
-	\section{Proof of Proposition \ref{proposition:closed_form_orthgonalization} \ref{}}\label{section:proof:proposition:closed_form_orthgonalization}
-	 \begin{align*}
-		\operatorname{PENSSE}( \delta)
+\section{Proof of Proposition \ref{proposition:closed_form_orthgonalization} }\label{section:proof:proposition:closed_form_orthgonalization}
+For notational simplicity, we omit the iteration superscript $[l]$.
+	Using the basis expansion coefficient notation from \eqref{def:truncated_zeta_and_delta}, \eqref{def:coef_vector_form}, \eqref{def:theta}, and \eqref{def:B_matrix}, the full vector of PLS scores $\hat{\boldsymbol{\rho}}  = (\hat{\rho}_1, \ldots, \hat{\rho}_n)^\top$
+	where
+	$\hat{\rho}_1$ is defined in \eqref{def:plsscore},
+	is computed through the following matrix multiplication:
+	\begin{equation*}
+		 \hat{\boldsymbol{\rho}}^\top = \sum_{k=1}^K ( \hat{\boldsymbol{\gamma}}_j )^\top B \, \Theta_j^\top + \boldsymbol{\zeta}^\top \mathbf{Z}^\top.
+	\end{equation*}
+The criterion $\operatorname{PENSSE}( \delta)$ can be decomposed as follows:
+
+\begin{align*}
+	\operatorname{PENSSE}( \delta) &= \sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta, \, \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta \rangle_{\mathcal{H}} + \tau \sum_{j=1}^K\operatorname{PEN}(\delta_j) \\
 	&= 
-		\sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta,
-		\,
-		\widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta
-		\rangle_{\mathcal{H}}
-		+
+	\underbrace{
+		\sum_{i=1}^n \langle \widetilde{W}_i^{[l]}, \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}}_{A} 
+	\underbrace{
+		-2 \sum_{i=1}^n \hat{\rho}_i^{[l]} \langle \delta, \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}} 
+	}_{B_1(\boldsymbol{\delta})}
+	\underbrace{
+		+ 
+		(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})
+		 \langle \delta, \, \delta \rangle_{\mathcal{H}}
+	}_{B_2(\boldsymbol{\delta})}
+	\underbrace{
+		 + 
+		 \tau \sum_{j=1}^K\operatorname{PEN}(\delta_j)
+	}_{B_3(\boldsymbol{\delta})}
+\end{align*}
+Here, part $A$ does not contain $\delta$, so it does not contribute to the minimization problem.
+
+Let $\boldsymbol{\delta}:= (\pi_1^\top, \ldots, \pi_K^\top, \boldsymbol{\chi}^\top )^\top$ be the $MK+p$-dimensional concatenated vector of basis coefficients and the scalar part of $\boldsymbol{\delta}$, as presented in \eqref{def:maximizer_euclidean_form}.
+Abusing notation, we treat $\operatorname{PENSSE}$ as a function of $\boldsymbol{\delta}$.
+Next, We will now demonstrate that the combined term $
+B_1(\boldsymbol{\delta}) + B_2(\boldsymbol{\delta}) + B_3(\boldsymbol{\delta})
+$ is a quadratic function of $\boldsymbol{\delta}$, by expanding its component functions:
+	\begin{align*}
+	B_1(\boldsymbol{\delta}) &= 
+	- 2\sum_{i=1}^n \hat{\rho}_i  \langle \delta, \, \widetilde{W}_i  \rangle_{\mathcal{H}} 
+	=
+	- 2\hat{\boldsymbol{\rho}}^\top 
+	\biggl(
+	\sum_{j=1}^K \Theta_j B \boldsymbol{\pi}_j
+	+\mathbf{Z} \boldsymbol{\chi}
+	\biggr),
+%%%%%%%%%%%%%%%%%%%%%%%
+\\ 
+	B_2(\boldsymbol{\delta})
+	&=
+	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})
+	\langle \delta, \, \delta \rangle_{\mathcal{H}}
+	=
+	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) 
+	\biggl(
+	\sum_{j=1}^K \pi_j^\top B \pi_j
+	+\boldsymbol{\chi}^\top \boldsymbol{\chi}
+	\biggr),
+	\\
+	B_3(\boldsymbol{\delta})
+	&=
+	\tau \sum_{j=1}^K\operatorname{PEN}(\delta_j)
+	=
 	\tau
-		\sum_{j=1}^K\operatorname{PEN}(\delta_j) 
-		%%%%%%%%%%%%%%%%%%%%
-		\\&=
-		\sum_{i=1}^n 
-		\langle \widetilde{W}_i^{[l]},  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
-		-
-		\sum_{i=1}^n 
-		\hat{\rho}_i^{[l]} 
-		\langle \delta,  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
-		+
-		\bigl(
-		\sum_{i=1}^n 
-		( \hat{\rho}_i^{[l]} )^2
-		\bigr)
-		\langle \delta,  \, \delta \rangle_{\mathcal{H}}
-		+
+	\boldsymbol{\delta} B^{''} \boldsymbol{\delta},
+\end{align*}
+where the expansion of $B_3(\boldsymbol{\delta})$ leverages the computation in \eqref{pen_as_matrix}.
+Now we compute the gradients:
+	\begin{align*}
+		\nabla_{\boldsymbol{\pi}_j}
+		 B_1(\boldsymbol{\delta}) 
+		 &= -2
+		 B
+		 \Theta_j^\top
+		 \hat{\boldsymbol{\rho}}  ,~
+		  j = 1, \ldots, K,
+		  \quad
+			\nabla_{\boldsymbol{\chi}}
+	B_1(\boldsymbol{\delta}) 	  
+	= -2\mathbf{Z}^\top  \hat{\boldsymbol{\rho}},
+%
+\\
+	\nabla_{\boldsymbol{\pi}_j}
+	B_2(\boldsymbol{\delta}) 
+	&= 
+	2
+	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) 
+	B 	\boldsymbol{\pi}_j
+	,~
+	j = 1, \ldots, K,
+	\quad
+	\nabla_{\boldsymbol{\chi}}
+	B_2(\boldsymbol{\delta}) 
+	=
+	2\boldsymbol{\chi} ,
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\\
+	\nabla_{\boldsymbol{\pi}_j}
+	B_3(\boldsymbol{\delta}) 
+	&= 
+	2 \tau
+	B^{\prime \prime }	\boldsymbol{\pi}_j
+	,~
+	j = 1, \ldots, K,
+	\quad
+	\nabla_{\boldsymbol{\chi}}
+	B_3(\boldsymbol{\delta}) 
+	=
+0.
+	\end{align*}
+The Hessian of 
+$\operatorname{PENSSE}( \boldsymbol{\delta})$ is then given by 
+ $
+2 	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})  B
++
+2
 \tau
-		\sum_{j=1}^K\operatorname{PEN}(\delta_j) 
-		\\&=
-		\operatorname{tr}(C^{*T} C^{*}J^{*}\Lambda) 
-		- 
-		2 \operatorname{tr}(d^{*}J^{*}C^{*T} \rho\Lambda) 
-		+
-		\rho^T \rho
-		\operatorname{tr}( d^{*}J^{*}d^{*T} \Lambda) + \tau \operatorname{tr}(\ddot{d}^{*}J^{*}\ddot{d}^{*T}) \jongmin{need to be fixed}
-	\end{align*}
-
+ B^{\prime \prime}.
+$ 
+Since we assumed in Section \ref{sec: finite basis approximation} that both $B'$ and $B''$ are positive definite, $\operatorname{PENSSE}( \delta)$ is convex.
+convex.
+Consequently, the gradient vanishes at its unique minimizer:
+\begin{align*}
+	\nabla_{\boldsymbol{\pi}_j}	\operatorname{PENSSE}( \hat{\boldsymbol{\delta}} )
+&	=
+	 -2
+	B
+	\Theta_j^\top
+	\hat{\boldsymbol{\rho}}
+	+
+2	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) 
+B 	\hat{\boldsymbol{\pi}}_j
+	+
+		2
+	B^{\prime \prime }	\hat{\boldsymbol{\pi}}_j
+	=
+	0,~
+	j = 1, \ldots, K,
+	\\
+	\nabla_{\boldsymbol{\chi} }	\operatorname{PENSSE}( \hat{\boldsymbol{\delta}} )
+&=
+-2\mathbf{Z}^\top  \hat{\boldsymbol{\rho}}
++
+2\hat{\boldsymbol{\chi} }
+=
+0,
+\end{align*}
+providing the following closed-form solution:
+\begin{equation*}
+	\hat{\boldsymbol{\pi}}_j\\
+	=
+	\bigl\{
+	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})  B
+	+
+	\tau
+	B^{\prime \prime}
+	\bigr\}^{-1}
+ B
+\Theta_j^\top
+~
+j = 1, \ldots, K,
+	%%%%%%%%%%%%%%%%%%%%%%%%
+	\quad
+\hat{\boldsymbol{\chi} }
+=\mathbf{Z}^\top  \hat{\boldsymbol{\rho}}.
+\end{equation*}
+This completes the proof of Proposition \ref{proposition:closed_form_orthgonalization}.
 	\section{Proof of Proposition \ref{Proposition: property of U}}\label{section:proof:Proposition: property of U}

### 2025-07-24 manuscript/main.tex
man: residualization writing revised

@@
 The hybrid PLS direction is then obtained by iteratively maximizing the empirical covariance with the response, subject to a unit-norm constraint in this Hilbert space.
+
+	The framework is readily applicable to dense and irregular functionaldata, and supports regularization techniques to prevent overfitting and reduce variance.
 
@@
 
-	\medskip
-	\noindent \textit{Orthonormality.}~
-	The constraint $\xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1$ enforces the following modified orthonormality of the estimated PLS components ($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ which now takes into account the roughness of the functions:
-	\begin{align*}
-		\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
-		&= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right \rangle_{L^2} \\
-		&= \sum \limits_{k=1}^K \int_0^1 \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_0^1 \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
-		& = \mathbb{1}(l=j). 
-	\end{align*}
-	This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{sec: Properties of the Proposed PLS Framework} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.
-
 	\subsection{Step 2: Computing Residualized Predictors via Hybrid-on-Scalar Regression} \label{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}
-The $l$-th iteration's second step involves orthogonalization.
-This is achieved by fitting a hybrid-on-scalar regression model, where the predictor is the PLS score for each observation.
-The individual PLS score is computed as
+The $l$-th iteration's second step involves residualization of both predictors and responses. We first compute the individual PLS score:  
 \begin{equation}\label{def:plsscore}
@@
 utilizing the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. 
-Using this as a scalar predictor observations, we fit the regression model $\widetilde{W}^{[l]}_i = \hat{\rho}^{[l]}_i\, \delta^{[l]} + E_i^{[l]}$, and then take the residuals as the predictor for the next iteration, namely $\widetilde{W}^{[l+1]}_i$.
-Here, $\delta^{[l]}$ and $E_i^{[l]}$ are the regression coefficient and error terms, respectively, both elements of $\tilde{\mathcal{H}}$ as defined in \eqref{def:truncated_hilbert_space}.
-To ensure the stability of the entire PLS estimation procedure, the estimated regression coefficient $\hat{\delta}^{[l]} = (\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} ) \in \tilde{\mathcal{H}}$, should have smooth functional parts, consistent with Section \ref{sec: Regularization of PLS Components}.
+Using these PLS scores as scalar predictor observations, the $(l+1)$-th iteration's residualized response is computed as:
+\begin{equation}\label{algorithm_step:residualization_response}
+	Y_i^{[l+1]} := Y_i^{[l]} - 
+	\frac{
+		( \mathbf{y}^{[l]} )^\top  \hat{\boldsymbol{\rho}}^{[l]}
+	}{
+		( \hat{\boldsymbol{\rho}}^{[l]} )^\top  \hat{\boldsymbol{\rho}}^{[l]}
+	}
+	\widehat{\rho}_{il},
+\end{equation}
+which is equivalent to using the least squares estimate from regressing $Y_i^{[l]}$ on $\widehat{\rho}_{il}$,
+a procedure identical to that found in the naive PLS algorithm (Section \ref{sec: Naive PLS Algorithm}).
+
+For predictor residualization, we fit a hybrid-on-scalar regression model where the predictor is the PLS score for each observation.
+Specifically, we fit $\widetilde{W}^{[l]}_i = \hat{\rho}^{[l]}_i\, \delta^{[l]} + E_i^{[l]}$, and then take the residuals as the predictor for the next iteration.
+  Here, $\delta^{[l]}$ and $E_i^{[l]}$ are the regression coefficient and error terms, respectively.
+Performing this pointwisely, as in Section \ref{sec: Naive PLS Algorithm}, is highly inefficient and potentially infeasible for dense or irregular functional data.
+Moreover, the results may lack smoothness, introducing instability that propagates to subsequent results and compromises the entire algorithm.
+Therefore, we employ a basis expansion approach to fit the entire hybrid object in one step.
+We assume both $\delta^{[l]}$ and $E_i^{[l]}$ are elements of $\tilde{\mathcal{H}}$, as defined in \eqref{def:truncated_hilbert_space}.
+To ensure the stability of the entire PLS estimation procedure, the estimated regression coefficient $\hat{\delta}^{[l]} = (\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} ) \in \tilde{\mathcal{H}}$ should have smooth functional parts, consistent with Section \ref{sec: Regularization of PLS Components}.
 Consequently, $\delta^{[l]}$ is obtained by minimizing a penalized least squares criterion, where the functional part is penalized by the integrated squared second derivative defined in \eqref{def:roughness_penalty}:
@@
 \end{equation}
+where $\tau>0$ is a  smoothing parameter controlling the trade-off between fit accuracy and functional regression coefficient smoothness.
 The following proposition shows that the solution of the problem \ref{def:argmin_pensse} can be obtained by solving linear equations.
 
- \begin{proposition}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
+ \begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
  	Let us denote
@@
  	\quad\text{and} \quad
- 			\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}
+ 			\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
  	\end{equation*}
@@
 \end{equation*}
- \end{proposition}
+ \end{lemma}
  Proof of Proposition \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
 
- Now we formally state the orthogonalization step.
-
-%Using the basis expansion coefficient notation presented in \eqref{def:truncated_zeta_and_delta} and \eqref{def:coef_vector_form}, \eqref{def:theta}, \eqref{def:B_matrix}
-\jongmin{Old writing starts here. I temporarily mixed the order of the paragraphs.}
-Then, we can use $\widehat{\boldsymbol{\delta}}[\mathbf{t}]$ to obtain the subsequent residualized hybrid predictor as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$.
-
-	The step for obtaining the subsequent residualized response is identical to that of the naive PLS algorithm in  in Section \ref{sec: Naive PLS Algorithm}.
-Specifically, the $(l-1)$-th residualized response can be obtained as $Y_i^{[l+1]} = Y_i^{[l]} - \widehat{\nu}_l \widehat{\rho}_{il}$, where $\widehat{\nu}_l = \sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}/\sum_{i=1}^n \widehat{\rho}_{il}^2$  is the least square estimate of the simple linear model regressing $Y_i^{[l]}$ on $\widehat{\rho}_{il}$.
-	 the PLS algorithm involves iteratively obtaining the ($l+1$)-th residualized predictors as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$, where $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ is the least squares estimate from regressing the previous ($l$-th) residualized outcome $\mathbf{W}_i^{[l]}[\mathbf{t}]$ on the corresponding  estimated PLS score $\widehat{\rho}_{il}$.
-The pointwise least squares estimate, $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] = (\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \widehat{\rho}_{il})/(\sum_{i=1}^n \widehat{\rho}_{il}^2)$, presented in Section \ref{sec: Naive PLS Algorithm}, however, is  highly inefficient and may not be even feasible for multiple dense and/or irregular functional data.
-Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components.
-Therefore, in this section, we introduce a novel strategy based on a hybrid-on-scalar regression model for obtaining $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ and implementing the second step.
+ The $(l+1)$-th iteration's residualized predictor is then computed as:
+\begin{equation}\label{algorithm_step:residualization_predictor}
+	\widetilde{W}_i^{[l+1]} 
+	 = 
+	 \widetilde{W}_i^{[l]}  - \widehat{\rho}_{il}  \widehat{ {\delta}}_{l}.
+	%%%%%%%%%%%
+\end{equation}
 
@@
 	\subsection{Data Preprocessing} \label{subsec: Data Preprocessing}
+
 	Functional and scalar elements of the hybrid predictors often have incompatible units and/or exhibit different amounts of variation.
@@
 	\label{sec: Properties of the Proposed PLS Framework}
+			\medskip
+	\noindent \textit{Orthonormality.}~
+	The constraint $\xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1$ enforces the following modified orthonormality of the estimated PLS components ($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ which now takes into account the roughness of the functions:
+	\begin{align*}
+		\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
+		&= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right \rangle_{L^2} \\
+		&= \sum \limits_{k=1}^K \int_0^1 \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_0^1 \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
+		& = \mathbb{1}(l=j). 
+	\end{align*}
+	This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{sec: Properties of the Proposed PLS Framework} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.
+
 	In this section, we derive some of the theoretical and geometric properties of the proposed PLS framework.

### 2025-07-24 manuscript/main.tex
residuals are centered

@@
 \end{equation}
-utilizing the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. 
+using the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. 
+Since   $\widetilde{W}_i^{[l]}$ are assumed to have a sample mean of zero, these PLS scores will also have a sample mean of zero.
 Using these PLS scores as scalar predictor observations, the $(l+1)$-th iteration's residualized response is computed as:
@@
 a procedure identical to that found in the naive PLS algorithm (Section \ref{sec: Naive PLS Algorithm}). 
+Since $Y_i^{[l]}$ are assumed to have a sample mean of zero, these residuals $Y_i^{[l+1]}$   also have a sample mean of zero.
 
@@
 	  B
-	(\Theta_j^{[l]})^\top,
+	(\Theta_j^{[l]})^\top
+	\hat{\boldsymbol{\rho}}
+	,
 	~
@@
  \end{lemma}
- Proof of Proposition \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
+ Proof of Lemma \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
 
@@
 \end{equation}
+ Since $\widetilde{W}_i^{[l]} $ are assumed to have a sample mean of zero, these residuals $\widetilde{W}_i^{[l+1]}$   also have a sample mean of zero.
 
@@
 
-\section{Proof of Proposition \ref{proposition:closed_form_orthgonalization} }\label{section:proof:proposition:closed_form_orthgonalization}
+\section{Proof of Lemma \ref{proposition:closed_form_orthgonalization} }\label{section:proof:proposition:closed_form_orthgonalization}
 For notational simplicity, we omit the iteration superscript $[l]$.
@@
 \Theta_j^\top
+\hat{\boldsymbol{\rho}}
 ~
@@
 \end{equation*}
-This completes the proof of Proposition \ref{proposition:closed_form_orthgonalization}.
+This completes the proof of Lemma \ref{proposition:closed_form_orthgonalization}.
 	\section{Proof of Proposition \ref{Proposition: property of U}}\label{section:proof:Proposition: property of U}

### 2025-08-12 manuscript/aoas-sample.tex
aoas template

--- 2025-07-24 manuscript/main.tex
@@
-\documentclass[12pt]{article}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{enumerate}
-\usepackage{natbib}
-\usepackage{url} % not crucial - just used below for the URL 
-\usepackage{bibunits}
-\usepackage{subcaption}
-\usepackage{adjustbox}
-\usepackage{verbatim}
-
-%%%%
-
-\usepackage{graphicx}
-\usepackage{multirow}
-\usepackage{hhline}
-%\usepackage{enumitem}
-\usepackage{hyperref}
-\usepackage{bm}
-\usepackage{multirow,multicol}
-\usepackage{verbatim}
-\usepackage{amsfonts,amssymb,amsthm,color,authblk}
-\usepackage{xcolor}
-\definecolor{myblue}{RGB}{0, 0, 0}
-\newcommand{\blue}[1]{{\color{myblue}#1}}
-%%%%
-
-%\pdfminorversion=4
-% NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{1}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{condition}{Condition}
-\newtheorem{remark}{Remark}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-% DON'T change margins - should be 1 inch all around.
-\addtolength{\oddsidemargin}{-.5in}%
-\addtolength{\evensidemargin}{-1in}%
-\addtolength{\textwidth}{1in}%
-\addtolength{\textheight}{1.7in}%
-\addtolength{\topmargin}{-1in}%
-
-%\usepackage{etoolbox}
-%\AtBeginBibliography{\small\setlength{\baselineskip}{10pt}}
-%\setlength{\bibsep}{0pt plus 0.2ex} 
-\usepackage{setspace}   
-\usepackage{etoolbox}  
+%
+\documentclass[aoas]{imsart}
+
+%% Packages
+\RequirePackage{amsthm,amsmath,amsfonts,amssymb}
+\RequirePackage[authoryear]{natbib}
+\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
+\RequirePackage{graphicx}
+
+%custom packages
  \usepackage{algorithm}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
-\newcommand{\jongmin}[1]{
-	{ \color{teal} JM: #1}
-}
-
  \usepackage[noend]{algpseudocode}
  \usepackage{hyperref}
-
-\AtBeginEnvironment{thebibliography}{\small\setstretch{0.93}}
+ \usepackage{enumerate}
+
+% \usepackage{url} % not crucial - just used below for the URL 
+% \usepackage{bibunits}
+\usepackage{subcaption}
+% \usepackage{adjustbox}
+\usepackage{verbatim} % to comment out
+
+ %%%%
+
+% \usepackage{multirow}
+% \usepackage{hhline}
+ %\usepackage{enumitem}
+
+% \usepackage{bm}
+% \usepackage{multirow,multicol}
+% \usepackage{verbatim}
+% \usepackage{amsfonts,amssymb,amsthm,color,authblk}
+% \usepackage{xcolor}
+% \definecolor{myblue}{RGB}{0, 0, 0}
+% \newcommand{\blue}[1]{{\color{myblue}#1}}
+\startlocaldefs
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Uncomment next line to change            %%
+%% the type of equation numbering           %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\numberwithin{equation}{section}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% For Axiom, Claim, Corollary, Hypothesis, %%
+%% Lemma, Theorem, Proposition              %%
+%% use \theoremstyle{plain}                 %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\theoremstyle{plain}
+\newtheorem{axiom}{Axiom}
+\newtheorem{claim}[axiom]{Claim}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% For Assumption, Definition, Example,     %%
+%% Notation, Property, Remark, Fact         %%
+%% use \theoremstyle{definition}            %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem*{example}{Example}
+\newtheorem*{fact}{Fact}
+\newtheorem{remark}{Remark}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Please put your definitions here:        %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
+
+\endlocaldefs
 
@@
 
-	%\bibliographystyle{natbib}
-
-	\def\spacingset#1{\renewcommand{\baselinestretch}%
-		{#1}\small\normalsize} \spacingset{1}
-
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-	\if1\blind
-	{
-		\title{\bf Partial Least Squares Regression with Multiple Functional and Scalar Predictors
-		}
-		\author{Jongmin Mun  $^1$  and Jeong Hoon Jang$^2$
-			\medskip\\
-			University of Southern California$^1$ and University of Texas Medical Branch$^2$
-			\\
-		}
-		\date{\today}
-
-		\maketitle
-	} \fi
-
-	\if0\blind
-	{
-		\bigskip
-		\bigskip
-		\bigskip
-		\begin{center}
-			{\LARGE\bf SOFARI: High-Dimensional Manifold-Based Inference}
-		\end{center}
-		\medskip
-	} \fi
-
-	\bigskip
+\begin{frontmatter}
+\title{ Partial Least Squares Regression with Multiple Functional and Scalar Predictors}
+%\title{A sample article title with some additional note\thanksref{t1}}
+\runtitle{A sample running head title}
+%\thankstext{T1}{A sample additional note to the title.}
+
+\begin{aug}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Only one address is permitted per author. %%
+%% Only division, organization and e-mail is %%
+%% included in the address.                  %%
+%% Additional information can be included in %%
+%% the Acknowledgments section if necessary. %%
+%% ORCID can be inserted by command:         %%
+%% \orcid{0000-0000-0000-0000}               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author[A]{\fnms{Jongmin }~\snm{Mun}  \ead[label=e1]{jongmin.mun@marshall.usc.edu}}
+\and
+\author[B]{\fnms{Jeong Hoon}~\snm{Jang}\ead[label=e2]{jejang@utmb.edu }}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Addresses                                %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\address[A]{University of Southern California\printead[presep={,\ }]{e1}}
+
+\address[B]{University of Texas Medical Branch\printead[presep={,\ }]{e2}}
+\end{aug}
+
 \begin{abstract}
@@
 
-	\noindent%
-	{\it Keywords:}  dimension reduction; functional data analysis; multiple data modalities; multivariate data analysis; multivariate functional data; partial least square
-
-	%\vfill
-
-	%\newpage
-	\spacingset{1.9} % DON'T change the spacing!
-
-	%\begin{bibunit}[agsm]
-
+\begin{keyword}
+\kwd{dimension reduction}
+\kwd{functional data analysis}
+\kwd{multiple data modalities}
+\kwd{multivariate data analysis}
+\kwd{multivariate functional data}
+\kwd{partial least square}
+\end{keyword}
+
+\end{frontmatter}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Please use \tableofcontents for articles %%
+%% with 50 pages and more                   %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\tableofcontents
 	\section{Introduction} \label{sec: Introduction}
-	Functional data analysis (FDA) treats each observed process as a realization of a random function over a continuous domain, such as time or space.
+%Functional data analysis (FDA) treats each observed process as a realization of a random function over a continuous domain, such as time or space.
 The smoothness and infinite-dimensional nature of functional data allow researchers to exploit rich structural features, including derivatives and complex covariance patterns.
@@
 	Let us denote
- 	\begin{equation*}
- 		 		\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top
- 	\quad\text{and} \quad
- 			\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
- 	\end{equation*}
+	$
+	\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top.
+	%\quad\text{and} \quad		\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
+	$
 	The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
@@
 		\bigl(
-		\bar{\rho}^{[l]}
+		\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2
 		B
@@
 		(\Theta_j^{[l]})^\top
-	\hat{\boldsymbol{\rho}}
+		\hat{\boldsymbol{\rho}}^{[l]}
 		,
@@
 		\quad
-	\hat{\boldsymbol{\chi} }
+		\hat{\boldsymbol{\chi} }^{[l]}
 		=
-	(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}.
+		(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}^{[l]}.
 	\end{equation*}
@@
 \section{Simulations} \label{Simulations}
+\section{Introduction}
+
+This template helps you to create a properly formatted \LaTeXe\ manuscript.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% `\ ' is used here because TeX ignores    %%
+%% spaces after text commands.              %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Prepare your paper in the same style as used in this sample .pdf file.
+Try to avoid excessive use of italics and bold face.
+Please do not use any \LaTeXe\ or \TeX\ commands that affect the layout
+or formatting of your document (i.e., commands like \verb|\textheight|,
+\verb|\textwidth|, etc.).
+
+\section{Section headings}
+Here are some sub-sections:
+\subsection{A sub-section}
+Regular text.
+\subsubsection{A sub-sub-section}
+Regular text.
+
+\section{Text}
+\subsection{Lists}
+
+The following is an example of an \emph{itemized} list,
+two levels deep.
+\begin{itemize}
+\item
+This is the first item of an itemized list.  Each item
+in the list is marked with a ``tick.''  The document
+style determines what kind of tick mark is used.
+\item
+This is the second item of the list.  It contains another
+list nested inside it.
+\begin{itemize}
+\item This is the first item of an itemized list that
+is nested within the itemized list.
+\item This is the second item of the inner list.  \LaTeX\
+allows you to nest lists deeper than you really should.
+\end{itemize}
+This is the rest of the second item of the outer list.
+\item
+This is the third item of the list.
+\end{itemize}
+
+The following is an example of an \emph{enumerated} list of one level.
+
+\begin{longlist}
+\item This is the first item of an enumerated list.
+\item This is the second item of an enumerated list.
+\end{longlist}
+
+The following is an example of an \emph{enumerated} list, two levels deep.
+\begin{longlist}
+\item[1.]
+This is the first item of an enumerated list.  Each item
+in the list is marked with a ``tick.''  The document
+style determines what kind of tick mark is used.
+\item[2.]
+This is the second item of the list.  It contains another
+list nested inside of it.
+\begin{longlist}
+\item
+This is the first item of an enumerated list that
+is nested within.  
+\item
+This is the second item of the inner list.  \LaTeX\
+allows you to nest lists deeper than you really should.
+\end{longlist}
+This is the rest of the second item of the outer list.
+\item[3.]
+This is the third item of the list.
+\end{longlist}
+
+\subsection{Punctuation}
+Dashes come in three sizes: a hyphen, an intra-word dash like ``$U$-statistics'' or ``the time-homogeneous model'';
+a medium dash (also called an ``en-dash'') for number ranges or between two equal entities like ``1--2'' or ``Cauchy--Schwarz inequality'';
+and a punctuation dash (also called an ``em-dash'') in place of a comma, semicolon,
+colon or parentheses---like this.
+
+Generating an ellipsis \ldots\ with the right spacing
+around the periods requires a special command.
+
+\subsection{Citation}
+
+%Simple author and year cite: \cite{r1}.
+%Multiple bibliography items cite: \cite{r1,r2}.
+%Author only cite: \citeauthor{r3}.
+%Year only cite: \citeyear{r4}.
+
+\section{Fonts}
+Please use text fonts in text mode, e.g.:
+\begin{itemize}
+\item[]\textrm{Roman}
+\item[]\textit{Italic}
+\item[]\textbf{Bold}
+\item[]\textsc{Small Caps}
+\item[]\textsf{Sans serif}
+\item[]\texttt{Typewriter}
+\end{itemize}
+Please use mathematical fonts in mathematical mode, e.g.:
+\begin{itemize}
+\item[] $\mathrm{ABCabc123}$
+\item[] $\mathit{ABCabc123}$
+\item[] $\mathbf{ABCabc123}$
+\item[] $\boldsymbol{ABCabc123\alpha\beta\gamma}$
+\item[] $\mathcal{ABC}$
+\item[] $\mathbb{ABC}$
+\item[] $\mathsf{ABCabc123}$
+\item[] $\mathtt{ABCabc123}$
+\item[] $\mathfrak{ABCabc123}$
+\end{itemize}
+Note that \verb|\mathcal, \mathbb| belongs to capital letters-only font typefaces.
+
+\section{Notes}
+Footnotes\footnote{This is an example of a footnote.}
+pose no problem.\footnote{Note that footnote number is after punctuation.}
+
+\section{Quotations}
+
+Text is displayed by indenting it from the left margin. There are short quotations
+\begin{quote}
+This is a short quotation.  It consists of a
+single paragraph of text.  There is no paragraph
+indentation.
+\end{quote}
+and longer ones.
+\begin{quotation}
+This is a longer quotation.  It consists of two paragraphs
+of text.  The beginning of each paragraph is indicated
+by an extra indentation.
+
+This is the second paragraph of the quotation.  It is just
+as dull as the first paragraph.
+\end{quotation}
+
+\section{Environments}
+
+\subsection{Examples for \emph{\texttt{plain}}-style environments}
+\begin{axiom}\label{ax1}
+This is the body of Axiom \ref{ax1}.
+\end{axiom}
+
+\begin{proof}
+This is the body of the proof of the axiom above.
+\end{proof}
+
+\begin{claim}\label{cl1}
+This is the body of Claim \ref{cl1}. Claim \ref{cl1} is numbered after
+Axiom \ref{ax1} because we used \verb|[axiom]| in \verb|\newtheorem|.
+\end{claim}
+
+\begin{theorem}\label{th1}
+This is the body of Theorem \ref{th1}. Theorem \ref{th1} numbering is
+dependent on section because we used \verb|[section]| after \verb|\newtheorem|.
+\end{theorem}
+
+\begin{theorem}[Title of the theorem]\label{th2}
+This is the body of Theorem \ref{th2}. Theorem \ref{th2} has additional title.
+\end{theorem}
+
+\begin{lemma}\label{le1}
+This is the body of Lemma \ref{le1}. Lemma \ref{le1} is numbered after
+Theorem \ref{th2} because we used \verb|[theorem]| in \verb|\newtheorem|.
+\end{lemma}
+
+\begin{proof}[Proof of Lemma \ref{le1}]
+This is the body of the proof of Lemma \ref{le1}.
+\end{proof}
+
+\subsection{Examples for \emph{\texttt{definition}}-style environments}
+\begin{definition}\label{de1}
+This is the body of Definition \ref{de1}. Definition \ref{de1} is numbered after
+Lemma \ref{le1} because we used \verb|[theorem]| in \verb|\newtheorem|.
+\end{definition}
+
+\begin{example}
+This is the body of the example. Example is unnumbered because we used \verb|\newtheorem*|
+instead of \verb|\newtheorem|.
+\end{example}
+
+\begin{fact}
+This is the body of the fact. Fact is unnumbered because we used \verb|\newtheorem*|
+instead of \verb|\newtheorem|.
+\end{fact}
+
+\section{Tables and figures}
+Cross-references to labeled tables: As you can see in Table~\ref{sphericcase}
+and also in Table~\ref{parset}.
+
+\begin{table*}
+\caption{The spherical case ($I_1=0$, $I_2=0$)}
+\label{sphericcase}
+\begin{tabular}{@{}lrrrrc@{}}
+\hline
+Equil. \\
+points & \multicolumn{1}{c}{$x$}
+& \multicolumn{1}{c}{$y$} & \multicolumn{1}{c}{$z$}
+& \multicolumn{1}{c}{$C$} & S \\
+\hline
+$L_1$    & $-$2.485252241 & 0.000000000  & 0.017100631  & 8.230711648  & U \\
+$L_2$    & 0.000000000  & 0.000000000  & 3.068883732  & 0.000000000  & S \\
+$L_3$    & 0.009869059  & 0.000000000  & 4.756386544  & $-$0.000057922 & U \\
+$L_4$    & 0.210589855  & 0.000000000  & $-$0.007021459 & 9.440510897  & U \\
+$L_5$    & 0.455926604  & 0.000000000  & $-$0.212446624 & 7.586126667  & U \\
+$L_6$    & 0.667031314  & 0.000000000  & 0.529879957  & 3.497660052  & U \\
+$L_7$    & 2.164386674  & 0.000000000  & $-$0.169308438 & 6.866562449  & U \\
+$L_8$    & 0.560414471  & 0.421735658  & $-$0.093667445 & 9.241525367  & U \\
+$L_9$    & 0.560414471  & $-$0.421735658 & $-$0.093667445 & 9.241525367  & U \\
+$L_{10}$ & 1.472523232  & 1.393484549  & $-$0.083801333 & 6.733436505  & U \\
+$L_{11}$ & 1.472523232  & $-$1.393484549 & $-$0.083801333 & 6.733436505  & U \\
+\hline
+\end{tabular}
+\end{table*}
+
+\begin{table}
+\caption{Sample posterior estimates for each model}
+\label{parset}
+%
+\begin{tabular}{@{}lcrcrrr@{}}
+\hline
+&& & &\multicolumn{3}{c}{Quantile} \\
+\cline{5-7}
+Model &Parameter &
+\multicolumn{1}{c}{Mean} &
+Std. dev.&
+\multicolumn{1}{c}{2.5\%} &
+\multicolumn{1}{c}{50\%}&
+\multicolumn{1}{c@{}}{97.5\%} \\
+\hline
+{Model 0} & $\beta_0$ & $-$12.29 & 2.29 & $-$18.04 & $-$11.99 & $-$8.56 \\
+          & $\beta_1$  & 0.10   & 0.07 & $-$0.05  & 0.10   & 0.26  \\
+          & $\beta_2$   & 0.01   & 0.09 & $-$0.22  & 0.02   & 0.16  \\[6pt]
+{Model 1} & $\beta_0$   & $-$4.58  & 3.04 & $-$11.00 & $-$4.44  & 1.06  \\
+          & $\beta_1$   & 0.79   & 0.21 & 0.38   & 0.78   & 1.20  \\
+          & $\beta_2$   & $-$0.28  & 0.10 & $-$0.48  & $-$0.28  & $-$0.07 \\[6pt]
+{Model 2} & $\beta_0$   & $-$11.85 & 2.24 & $-$17.34 & $-$11.60 & $-$7.85 \\
+          & $\beta_1$   & 0.73   & 0.21 & 0.32   & 0.73   & 1.16  \\
+          & $\beta_2$   & $-$0.60  & 0.14 & $-$0.88  & $-$0.60  & $-$0.34 \\
+          & $\beta_3$   & 0.22   & 0.17 & $-$0.10  & 0.22   & 0.55  \\
+\hline
+\end{tabular}
+%
+\end{table}
+
+\begin{figure}
+\includegraphics{figure1}
+\caption{Pathway of the penicillin G biosynthesis.}
+\label{penG}
+\end{figure}
+
+Sample of cross-reference to figure.
+Figure~\ref{penG} shows that it is not easy to get something on paper.
+
+\section{Equations and the like}
+
+Two equations:
+\begin{equation}
+    C_{s}  =  K_{M} \frac{\mu/\mu_{x}}{1-\mu/\mu_{x}} \label{ccs}
+\end{equation}
+and
+\begin{equation}
+    G = \frac{P_{\mathrm{opt}} - P_{\mathrm{ref}}}{P_{\mathrm{ref}}}  100(\%).
+\end{equation}
+
+Equation arrays:
+\begin{eqnarray}
+  \frac{dS}{dt} & = & - \sigma X + s_{F} F,\\
+  \frac{dX}{dt} & = &   \mu    X,\\
+  \frac{dP}{dt} & = &   \pi    X - k_{h} P,\\
+  \frac{dV}{dt} & = &   F.
+\end{eqnarray}
+One long equation:
+\begin{eqnarray}
+ \mu_{\text{normal}} & = & \mu_{x} \frac{C_{s}}{K_{x}C_{x}+C_{s}}  \nonumber\\
+                     & = & \mu_{\text{normal}} - Y_{x/s}\bigl(1-H(C_{s})\bigr)(m_{s}+\pi /Y_{p/s})\\
+                     & = & \mu_{\text{normal}}/Y_{x/s}+ H(C_{s}) (m_{s}+ \pi /Y_{p/s}).\nonumber
+\end{eqnarray}
+
+\section*{APPENDICES MUST BE MOVED TO A SUPPLEMENT FILE}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Support information, if any,             %%
+%% should be provided in the                %%
+%% Acknowledgements section.                %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{acks}[Acknowledgments]
+The authors would like to thank the anonymous referees, an Associate
+Editor and the Editor for their constructive comments that improved the
+quality of this paper.
+\end{acks}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Funding information, if any,             %%
+%% should be provided in the                %%
+%% funding section.                         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{funding}
+The first author was supported by NSF Grant DMS-??-??????.
+
+The second author was supported in part by NIH Grant ???????????.
+\end{funding}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Supplementary Material, including data   %%
+%% sets and code, should be provided in     %%
+%% {supplement} environment with title      %%
+%% and short description. It cannot be      %%
+%% available exclusively as external link.  %%
+%% All Supplementary Material must be       %%
+%% available to the reader on Project       %%
+%% Euclid with the published article.       %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{supplement}
+\stitle{Title of Supplement A}
+\sdescription{Short description of Supplement A.}
+\end{supplement}
+\begin{supplement}
+\stitle{Title of Supplement B}
+\sdescription{Short description of Supplement B.}
+\end{supplement}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                  The Bibliography                       %%
+%%                                                         %%
+%%  imsart-nameyear.bst  will be used to                   %%
+%%  create a .BBL file for submission.                     %%
+%%                                                         %%
+%%  Note that the displayed Bibliography will not          %%
+%%  necessarily be rendered by Latex exactly as specified  %%
+%%  in the online Instructions for Authors.                %%
+%%                                                         %%
+%%  MR numbers will be added by VTeX.                      %%
+%%                                                         %%
+%%  Use \cite{...} to cite references in text.             %%
+%%                                                         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% if your bibliography is in bibtex format, uncomment commands:
+\bibliographystyle{imsart-nameyear} % Style BST file
+\bibliography{bibliography}       % Bibliography file (usually '*.bib')
 

### 2025-08-12 manuscript/main.tex
aoas template

@@
  	Let us denote
- 	\begin{equation*}
- 		 		\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top
- 	\quad\text{and} \quad
- 			\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
- 	\end{equation*}
+ $
+ 		 		\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top.
+ 	%\quad\text{and} \quad		\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
+ $
  	The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
@@
 	\bigl(
-		\bar{\rho}^{[l]}
+		\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2
   B
@@
 	(\Theta_j^{[l]})^\top
-	\hat{\boldsymbol{\rho}}
+	\hat{\boldsymbol{\rho}}^{[l]}
 	,
@@
 	\quad
-	\hat{\boldsymbol{\chi} }
-	=
-	(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}.
+	\hat{\boldsymbol{\chi} }^{[l]}
+	=
+	(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}^{[l]}.
 \end{equation*}

### 2025-08-12 manuscript/aoas-sample.tex
geometric property start

@@
  \usepackage{enumerate}
-
+ \usepackage{xcolor}
 % \usepackage{url} % not crucial - just used below for the URL 
@@
 % \usepackage{amsfonts,amssymb,amsthm,color,authblk}
-% \usepackage{xcolor}
+
 % \definecolor{myblue}{RGB}{0, 0, 0}
@@
 \newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
+\newcommand{\jongmin}[1]{
+	{ \color{teal} JM: #1}
+}
 
@@
 It also incorporates a regularization scheme that enables the algorithm to borrow strength and exploit structural relationships within and between the functions to avoid overfitting of the PLS components and to improve the generalizability and interpretability of the predictive model.
-Each iteration of our approach consists of two subroutines: regularized estimation of smoothed PLS components and orthogonalization, detailed in Sections~\ref{subsec: Step 1: Computing Smoothed PLS components} and~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}, respectively.
-After a suitable number of iterations, the hybrid regression coefficient is estimated, as described in Section~\ref{subsec: Obtaining the Estimated Hybrid Regression Coefficient}.
+Each iteration of our approach consists of two subroutines: regularized estimation of smoothed PLS components and orthogonalization, detailed in Sections~\ref{section:sub:compute_PLS_component} and~\ref{section:sub:residualization}, respectively.
+After a suitable number of iterations, the hybrid regression coefficient is estimated, as described in Section~\ref{section:sub:regression_coeff}.
 For notational simplicity, we omit the iteration index $l$ in the following discussion, with the understanding that the subroutines apply to any iteration.
@@
 
-\subsection{Preliminary step: Finite-basis Approximation }\label{sec: finite basis approximation}	
+\subsection{Preliminary step 1: finite-basis approximation}\label{sec: finite basis approximation}	
 Let ${b_m(t)}$ be a twice-differentiable basis of $L^2([0,1])$ whose second derivatives are also linearly independent, for example, cubic B-splines, the Fourier basis, or an orthonormal polynomial basis of degree greater than three.
@@
 
-\subsection{Step 1: Computing smoothed PLS component direction}  \label{subsec: Step 1: Computing Smoothed PLS components} 
-We begin with the first step of the iterative algorithm: estimating the smooth PLS component direction.
-Section~\ref{sec: pls component computation intermediate} introduces the core optimization problem for this step, formulated as a generalized Rayleigh quotient.
-Building on this, Section~\ref{sec: Regularization of PLS Components} presents a modified version that promotes smoothness, which is the estimation procedure for our proposed method, along with a efficient computation scheme.
-
-\subsubsection{Core optimization problem for PLS component direction estimation}\label{sec: pls component computation intermediate}
-Building on the basis function approximation in Section~\ref{sec: finite basis approximation}, we now present the core optimization problem that directly estimates the hybrid PLS component direction.
-This strategy fully leverages the continuous nature of the functional components and the function-scalar hybrid structure, and can be implemented using simple matrix-vector multiplications.
-
+\subsection{Preliminary step 2 : data preprocessing} \label{subsec: Data Preprocessing}
+\jongmin{notation not changed yet}
+Functional and scalar elements of the hybrid predictors often have incompatible units and/or exhibit different amounts of variation.
+This can be problematic for our PLS framework which is not scale invariant as: i) each predictor has different chance of contributing to the predictor/response structure; and ii) a predictor with high correlation to $Y$ but relatively low variance may be overlooked.
+
+To obtain PLS components that have a meaningful interpretation, we standardize the predictor data via the following steps.
+The first step is to account for discrepancies \textit{within} respective functional and scalar parts, if needed.
+If elements of multivariate functional data $X_i = (X_i^{(1)}, \ldots, X_i^{(K)})$ are measured in different units or have quite different domains, one can standardize them to have mean zero and integrated variance of one.
+If multivariate scalar predictors $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ exhibit different amounts of variation, one can standardize them to have mean zero and unit variance.
+The second step is to eliminate the discrepancies \textit{between} functional and scalar parts.
+To accomplish this aim, we choose an appropriate weight $\omega$ in the hybrid inner product \eqref{eq: hybrid inner product} that ensures functional and vector parts have comparable variance.
+A sensible data-driven approach to choosing an appropriate weight is to set
+\begin{equation*}
+	\omega = \frac{\sum_{i=1}^n \Vert X_i \Vert_\mathcal{F}^2}{\sum_{i=1}^n \Vert \mathbf{Z}_i \Vert^2},
+	\label{eq: weight}
+\end{equation*}
+In practice, this weighting scheme can be implemented by formulating the hybrid object as $\mathbf{W} = (X, \omega^{1/2} \mathbf{Z})$, whose vector part has been scaled by a factor of $\omega^{1/2}$.
+
+\subsection{Iterative steps}
+The iterative process presented here yields an orthonormal hybrid basis that effectively captures the predictor-response relationships.
+It proceeds through two intermediate steps: the estimation of the PLS component direction (Section \ref{section:sub:compute_PLS_component}) and residualization (Section \ref{section:sub:residualization}).
+The properties of the resulting estimates are introduced in Section \ref{section:main:properties_of_our_method}.
+\subsubsection{Iterative step 1: Regularized estimation of smoothed PLS component direction}  \label{section:sub:compute_PLS_component} 
+We begin by formally introducing the core optimization problem pertinent to the PLS direction estimation, which is formulated as a generalized Rayleigh quotient (Proposition \ref{proposition:eigen_noregul}).
+Building upon this foundational concept, we present our regularized PLS component direction estimation step that promotes smoothness (Proposition \ref{proposition:eigen_regul}).
+Furthermore,  we detail an efficient computational scheme (Proposition \ref{proposition:linear_regul}).
+
+\medskip
+\noindent
+\textit{Core optimization problem.}\label{sec: pls component computation intermediate}~
+We   present the core optimization problem that directly estimates the hybrid PLS component direction.
+It fully leverages the continuous nature of the functional components and the function-scalar hybrid structure.
 We describe the strategy at the $l$-th iteration.
-%For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for details).
+%For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{section:sub:residualization} for details).
 The  PLS component direction is estimated by the unit-norm direction $\xi^{[l]} \in \widetilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as
@@
 
-\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
+\medskip
+\noindent
+\textit{Proposed regularized estimation procedure.}~ \label{sec: Regularization of PLS Components}
 Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions.
@@
 
-\medskip
-\noindent
-\textit{Proposed estimation procedure.}~
 To avoid the orthogonal basis assumption of  \citet{Rice1991}, we adopt the strategy of \citet{Silverman1996}, which replaces the standard orthonormality constraint with a weaker one based on a modified inner product that incorporates roughness.
@@
 
-\subsection{Step 2: Computing Residualized Predictors via Hybrid-on-Scalar Regression} \label{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}
+\subsubsection{Iterative step 2: residualization via hybrid-on-scalar regression} \label{section:sub:residualization}
 The $l$-th iteration's second step involves residualization of both predictors and responses. We first compute the individual PLS score:  
@@
 	The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
-	$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients and scalar parts given by:
+	$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients
 	\begin{equation*}
@@
 		j = 1, \ldots, K,
-		%%%%%%%%%%%%%%%%%%%%%%%%
-		\quad
+	\end{equation*}
+	  and scalar parts given by:
+	 \begin{equation*}
 	 	\hat{\boldsymbol{\chi} }^{[l]}
@@
 
-\subsection{Obtaining the Estimated Hybrid Regression Coefficient}
-\label{subsec: Obtaining the Estimated Hybrid Regression Coefficient}
+\subsection{Final step: estimating  the hybrid regression coefficient}
+\label{section:sub:regression_coeff}
+\jongmin{notation not yet changed}
 The regression coefficient $\boldsymbol{\eta}$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS components and scores.
@@
 
-\subsection{Data Preprocessing} \label{subsec: Data Preprocessing}
-
-Functional and scalar elements of the hybrid predictors often have incompatible units and/or exhibit different amounts of variation.
-This can be problematic for our PLS framework which is not scale invariant as: i) each predictor has different chance of contributing to the predictor/response structure; and ii) a predictor with high correlation to $Y$ but relatively low variance may be overlooked.
-
-To obtain PLS components that have a meaningful interpretation, we standardize the predictor data via the following steps.
-The first step is to account for discrepancies \textit{within} respective functional and scalar parts, if needed.
-If elements of multivariate functional data $X_i = (X_i^{(1)}, \ldots, X_i^{(K)})$ are measured in different units or have quite different domains, one can standardize them to have mean zero and integrated variance of one.
-If multivariate scalar predictors $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ exhibit different amounts of variation, one can standardize them to have mean zero and unit variance.
-The second step is to eliminate the discrepancies \textit{between} functional and scalar parts.
-To accomplish this aim, we choose an appropriate weight $\omega$ in the hybrid inner product \eqref{eq: hybrid inner product} that ensures functional and vector parts have comparable variance.
-A sensible data-driven approach to choosing an appropriate weight is to set
-\begin{equation*}
-	\omega = \frac{\sum_{i=1}^n \Vert X_i \Vert_\mathcal{F}^2}{\sum_{i=1}^n \Vert \mathbf{Z}_i \Vert^2},
-	\label{eq: weight}
-\end{equation*}
-In practice, this weighting scheme can be implemented by formulating the hybrid object as $\mathbf{W} = (X, \omega^{1/2} \mathbf{Z})$, whose vector part has been scaled by a factor of $\omega^{1/2}$.
-
 \section{Properties of the Proposed PLS Framework}
-\label{sec: Properties of the Proposed PLS Framework}
+\label{section:main:properties_of_our_method}
+\jongmin{notation not yet changed}
+
+In this section, we derive some of the theoretical and geometric properties of the proposed PLS framework.
+
+\subsection{Tucker's Criterion}\jongmin{notation not yet changed}
+We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
+We omit $l$ in the notations and first define the cross-covariance terms between the response and predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$):
+\begin{equation*}
+	\begin{gathered}
+		\sigma_{YX} = (\sigma_{YX}^{(1)}, \ldots, \sigma_{YX}^{(K)}) = (E(YX^{(1)}),\ldots, E(YX^{(K)})) = E(YX) \in \mathcal{F} \\
+		\sigma_{YZ} = (\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top = (E(YZ_1),\ldots, E(YZ_p))^\top = E(Y\mathbf{Z}) \in \mathbb{R}^p \\
+		\Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) =  (E(YX), E(Y\mathbf{Z}))=E(Y\mathbf{W}) \in \mathcal{H}
+	\end{gathered}
+\end{equation*}
+We also introduce two cross-covariance operators, $\mathcal{C}_{YW}=E(\mathbf{W} \otimes_\mathcal{H} Y): \mathcal{H} \rightarrow \mathbb{R}$ and $\mathcal{C}_{WY}=E(Y \otimes \mathbf{W}): \mathbb{R} \rightarrow \mathcal{H}$, which respectively map $h=(f, \mathbf{v}) \in \mathcal{H}$ to $\mathbb{R}$ and $d \in \mathbb{R}$ to $\mathcal{H}$ as follows:
+\begin{align*}
+	& \mathcal{C}_{YW} \mathbf{h} = E\{\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX}^{(k)}(t_k) f^{(k)}(t_k) dt_k + E(Y \mathbf{Z}^\top) \mathbf{v} \\
+	& \mathcal{C}_{WY} d = E (\langle Y, d \rangle \mathbf{W} ) = E(Y\mathbf{W})d =  \Sigma_{YW} \, d. 
+\end{align*}
+
+Now define a new operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$, which performs the following mapping:
+\begin{equation*}
+	\mathcal{U} \mathbf{h} =  \mathcal{C}_{WY} ( \mathcal{C}_{YW} \mathbf{h}) 
+	= \mathcal{C}_{YW} (\langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}) 
+	=  \Sigma_{YW} \, \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = (\Sigma_{YW} \otimes \Sigma_{YW})\mathbf{h}.
+\end{equation*}
+In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$. The following proposition presents several important properties of $\mathcal{U}$.
+\begin{proposition} \label{Proposition: property of U}
+	The operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}= \Sigma_{YW} \otimes \Sigma_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ is positive and self-adjoint.
+Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that
+	\begin{align}
+		\max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in [0,1]} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
+	\end{align}
+	and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in [0,1]$ with $|t_k - t_k^* | < \delta_k$, we have that
+	\begin{equation*}
+		|\sigma_{yx}^{(k)}(t_k) - \sigma_{yx}^{(k)}(t_k^*) | < \epsilon,
+	\end{equation*}
+	then $\mathcal{U}$ is a compact operator.
+\end{proposition}
+The proof of Proposition \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
+By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
+
+The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
+\begin{proposition}\label{proposition: eigenanalysis}
+	\begin{equation*}
+		\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)
+	\end{equation*}
+	is achieved when $\xi$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.	
+\end{proposition}
+The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
+In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.
+
+\subsection{Geometric Properties}\jongmin{currently revising}
+In this section, we derive several geometric properties of the PLS components and and scores obtained from the proposed algorithm.
+
 \medskip
@@
 \end{align*}
-This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{sec: Properties of the Proposed PLS Framework} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.
-
-In this section, we derive some of the theoretical and geometric properties of the proposed PLS framework.
-
-\subsection{Tucker's Criterion}
-We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
-We omit $l$ in the notations and first define the cross-covariance terms between the response and predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$):
-\begin{equation*}
-	\begin{gathered}
-		\sigma_{YX} = (\sigma_{YX}^{(1)}, \ldots, \sigma_{YX}^{(K)}) = (E(YX^{(1)}),\ldots, E(YX^{(K)})) = E(YX) \in \mathcal{F} \\
-		\sigma_{YZ} = (\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top = (E(YZ_1),\ldots, E(YZ_p))^\top = E(Y\mathbf{Z}) \in \mathbb{R}^p \\
-		\Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) =  (E(YX), E(Y\mathbf{Z}))=E(Y\mathbf{W}) \in \mathcal{H}
-	\end{gathered}
-\end{equation*}
-We also introduce two cross-covariance operators, $\mathcal{C}_{YW}=E(\mathbf{W} \otimes_\mathcal{H} Y): \mathcal{H} \rightarrow \mathbb{R}$ and $\mathcal{C}_{WY}=E(Y \otimes \mathbf{W}): \mathbb{R} \rightarrow \mathcal{H}$, which respectively map $h=(f, \mathbf{v}) \in \mathcal{H}$ to $\mathbb{R}$ and $d \in \mathbb{R}$ to $\mathcal{H}$ as follows:
-\begin{align*}
-	& \mathcal{C}_{YW} \mathbf{h} = E\{\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX}^{(k)}(t_k) f^{(k)}(t_k) dt_k + E(Y \mathbf{Z}^\top) \mathbf{v} \\
-	& \mathcal{C}_{WY} d = E (\langle Y, d \rangle \mathbf{W} ) = E(Y\mathbf{W})d =  \Sigma_{YW} \, d. 
-\end{align*}
-
-Now define a new operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$, which performs the following mapping:
-\begin{equation*}
-	\mathcal{U} \mathbf{h} =  \mathcal{C}_{WY} ( \mathcal{C}_{YW} \mathbf{h}) 
-	= \mathcal{C}_{YW} (\langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}) 
-	=  \Sigma_{YW} \, \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = (\Sigma_{YW} \otimes \Sigma_{YW})\mathbf{h}.
-\end{equation*}
-In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$. The following proposition presents several important properties of $\mathcal{U}$.
-\begin{proposition} \label{Proposition: property of U}
-	The operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}= \Sigma_{YW} \otimes \Sigma_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ is positive and self-adjoint.
-Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that
-	\begin{align}
-		\max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in [0,1]} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
-	\end{align}
-	and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in [0,1]$ with $|t_k - t_k^* | < \delta_k$, we have that
-	\begin{equation*}
-		|\sigma_{yx}^{(k)}(t_k) - \sigma_{yx}^{(k)}(t_k^*) | < \epsilon,
-	\end{equation*}
-	then $\mathcal{U}$ is a compact operator.
-\end{proposition}
-The proof of Proposition \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
-By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
-
-The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
-\begin{proposition}\label{proposition: eigenanalysis}
-	\begin{equation*}
-		\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)
-	\end{equation*}
-	is achieved when $\xi$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.	
-\end{proposition}
-The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
-In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.
-
-\subsection{Geometric Properties}
-In this section, we derive several geometric properties of the PLS components and and scores obtained from the proposed algorithm.
+This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{section:main:properties_of_our_method} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.
 
@@
 \end{equation*}
-Finally, the functional predictors are smoothed using a B-spline basis with 15 basis functions, as described in Section \ref{subsec: Step 1: Computing Smoothed PLS components}.
+Finally, the functional predictors are smoothed using a B-spline basis with 15 basis functions, as described in Section \ref{section:sub:compute_PLS_component}.
 

### 2025-08-12 manuscript/main.tex
inner product definition simplified

@@
-\documentclass[12pt]{article}
-\usepackage{amsmath}
-\usepackage{graphicx}
+%
+\documentclass[aoas]{imsart}
+
+%% Packages
+\RequirePackage{amsthm,amsmath,amsfonts,amssymb}
+\RequirePackage[authoryear]{natbib}
+\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
+\RequirePackage{graphicx}
+
+%custom packages
+ \usepackage{algorithm}
+ \usepackage[noend]{algpseudocode}
+ \usepackage{hyperref}
  \usepackage{enumerate}
-\usepackage{natbib}
-\usepackage{url} % not crucial - just used below for the URL 
-\usepackage{bibunits}
+ \usepackage{xcolor}
+% \usepackage{url} % not crucial - just used below for the URL 
+% \usepackage{bibunits}
 \usepackage{subcaption}
-\usepackage{adjustbox}
-\usepackage{verbatim}
+% \usepackage{adjustbox}
+\usepackage{verbatim} % to comment out
 
@@
 
-\usepackage{graphicx}
-\usepackage{multirow}
-\usepackage{hhline}
+% \usepackage{multirow}
+% \usepackage{hhline}
  %\usepackage{enumitem}
-\usepackage{hyperref}
-\usepackage{bm}
-\usepackage{multirow,multicol}
-\usepackage{verbatim}
-\usepackage{amsfonts,amssymb,amsthm,color,authblk}
-\usepackage{xcolor}
-\definecolor{myblue}{RGB}{0, 0, 0}
-\newcommand{\blue}[1]{{\color{myblue}#1}}
-%%%%
-
-%\pdfminorversion=4
-% NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{1}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{condition}{Condition}
+
+% \usepackage{bm}
+% \usepackage{multirow,multicol}
+% \usepackage{verbatim}
+% \usepackage{amsfonts,amssymb,amsthm,color,authblk}
+
+% \definecolor{myblue}{RGB}{0, 0, 0}
+% \newcommand{\blue}[1]{{\color{myblue}#1}}
+\startlocaldefs
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Uncomment next line to change            %%
+%% the type of equation numbering           %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\numberwithin{equation}{section}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% For Axiom, Claim, Corollary, Hypothesis, %%
+%% Lemma, Theorem, Proposition              %%
+%% use \theoremstyle{plain}                 %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\theoremstyle{plain}
+\newtheorem{axiom}{Axiom}
+\newtheorem{claim}[axiom]{Claim}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% For Assumption, Definition, Example,     %%
+%% Notation, Property, Remark, Fact         %%
+%% use \theoremstyle{definition}            %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem*{example}{Example}
+\newtheorem*{fact}{Fact}
 \newtheorem{remark}{Remark}
-\newtheorem{proposition}{Proposition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-% DON'T change margins - should be 1 inch all around.
-\addtolength{\oddsidemargin}{-.5in}%
-\addtolength{\evensidemargin}{-1in}%
-\addtolength{\textwidth}{1in}%
-\addtolength{\textheight}{1.7in}%
-\addtolength{\topmargin}{-1in}%
-
-%\usepackage{etoolbox}
-%\AtBeginBibliography{\small\setlength{\baselineskip}{10pt}}
-%\setlength{\bibsep}{0pt plus 0.2ex} 
-\usepackage{setspace}   
-\usepackage{etoolbox}  
-\usepackage{algorithm}
-\DeclareMathOperator*{\argmax}{arg\,max}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Please put your definitions here:        %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
@@
 
-\usepackage[noend]{algpseudocode}
-\usepackage{hyperref}
-
-\AtBeginEnvironment{thebibliography}{\small\setstretch{0.93}}
+\endlocaldefs
 
@@
 $X_{i1}(t), \ldots, X_{iK}(t)$ are functional predicters.
-For notational convenience, we assume throguth this paper that the responsd sand preedictoras ahve been centered so the intercept can be ignored. 
+For notational convenience, we assume throughout this paper that the responses and predictors have been centered, allowing the intercept term to be ignored.
 %where $\boldsymbol{\alpha}=(\alpha_1, \ldots, \alpha_p)^\top \in \mathbb{R}^p$ and $\beta=(\beta^{(1)}, \ldots, \beta^{(K)}) \in \mathcal{F}$ are respectively the regression coefficient vector and function that characterize the effect of scalar and functional predictors on the outcome.
@@
 
-	\section{Data Objects and Model Formulation} 
-	We assume, without loss of generality, that the functional predictors $X_{i1}(t), X_{i2}(t), \ldots, X_{iK}(t)$ are observed over the domain $0 \leq t \leq 1$.
-We also assume that each functional predictor belongs to the space $L^2([0,1])$, the Hilbert space of square-integrable real-valued functions with respect to the Lebesgue measure $dt$ on $[0,1]$.
+\section{Data Objects and Model Formulation} \jongmin{still revising}
+For $k = 1, \ldots, K$, 
+we assume that the functional predictors $X_{ik}(t)$ are observed on the domain $0 \leq t \leq 1$.and belong to $L^2([0,1])$, the Hilbert space of square-integrable real-valued functions with respect to the Lebesgue measure $dt$ on $[0,1]$.
+Additionally, let $\mathbf{Z}=(Z_1, \ldots, Z_p)^\top$
+denote a $p$-dimensional multivariate scalar data in $\mathbb{R}^p$, assumed to be a random vector with finite first two moments, equipped with the Euclidean inner product and norm.
+ % i.e., for $\mathbf{v_1}=(v_{11}, \ldots, v_{1p})^\top$ and $\mathbf{v_2}=(v_{21}, \ldots, v_{2p})^\top$ in $\mathbb{R}^p$, $\langle \mathbf{v_1}, \mathbf{v_2} \rangle = \mathbf{v_1}^\top \mathbf{v_2} = \sum_{r=1}^p v_{1r}v_{2r}$, and $\Vert \mathbf{v}_1 \Vert = \langle \mathbf{v}_1, \mathbf{v}_1 \rangle^{1/2} = (\sum_{r=1}^p v_{1r}^2)^{1/2}$.
+The hybrid random predictor and corresponding inner product is formally defined as follows.
+\begin{definition}[Hybrid predictor and inner product]\label{def:hilbert_space}
+	We define a  hybrid predictor  $W_i$ as an ordered pair combining the functional predictors $X_{i1}(t), \ldots, X_{iK}(t)$ and a scalar predictor $\mathbf{Z}_i$:
+\begin{equation}\label{def:hybid_predictor}
+		W_i := (X_{i1}, \ldots, X_{iK}, \mathbf{Z}_i)
+		\in \mathcal{H} :=  L^2([0,1])^{\otimes K} \times \mathbb{R}^p
+\end{equation}
+	The inner product between two hybrid predictors,
+	$W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$
+	and
+	$W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$, is then defined as:
+	\begin{equation}		\label{eq: hybrid inner product}
+		\langle W_1, W_2\rangle_{\mathcal{H}}
+		:=
+		\sum \limits_{k=1}^K \int_0^1 X_{1k}(t) X_{2k}(t) \, dt
+		+
+		\omega
+		\mathbf{Z}_1^\top \mathbf{Z}_2,
+	\end{equation}
+	for $\omega > 0$.
+	The corresponding norm $\Vert \cdot \Vert_\mathcal{H}$ is derived from this inner product as $\langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
+\end{definition}
+In \eqref{eq: hybrid inner product}, 
+$\omega$ is a positive weight that needs to be pre-specified or estimated.
+It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}).
 
@@
 
-	Write  $X=(X^{(1)}, \ldots, X^{(K)})$ as a multivariate functional object that belongs to $\mathcal{F} = L^2(\mathcal{T}_1) \times \cdots \times L^2([0,1])$---a cartesian product of individual $L^2([0,1])$ spaces.
+%Write  $X=(X^{(1)}, \ldots, X^{(K)})$ as a multivariate functional object that belongs to $\mathcal{F} = L^2(\mathcal{T}_1) \times \cdots \times L^2([0,1])$---a cartesian product of individual $L^2([0,1])$ spaces.
 Note that if $K=1$, $X$ reduces to a univariate functional object.
 We can also express the functional object $X$ evaluated on the multi-dimensional argument $\mathbf{t} = (t_1, \ldots, t_k)^\top \in \mathcal{T} = \mathcal{T}_1 \times \cdots \times [0,1]$ as a $K$-dimensional vector $X(\mathbf{t})=(X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top$.
-The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)}) $ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as $\langle f_1, f_2\rangle_\mathcal{F} =  \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)}\rangle_{L^2} = \sum_{k=1}^K \int_0^1 f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k$ with norm $\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_0^1 f_1^{(k)}(t_k)^2 dt_k\}^{1/2}$.
-
-	Let $\mathbf{Z}=(Z_1, \ldots, Z_p)^\top$ denote a $p$-dimensional multivariate scalar data  in $\mathbb{R}^p$.
-We assume that $\mathbf{Z}$ is a random vector with finite first two moments and equipped with the Euclidean inner product and norm; i.e., for $\mathbf{v_1}=(v_{11}, \ldots, v_{1p})^\top$ and $\mathbf{v_2}=(v_{21}, \ldots, v_{2p})^\top$ in $\mathbb{R}^p$, $\langle \mathbf{v_1}, \mathbf{v_2} \rangle = \mathbf{v_1}^\top \mathbf{v_2} = \sum_{r=1}^p v_{1r}v_{2r}$, and $\Vert \mathbf{v}_1 \Vert = \langle \mathbf{v}_1, \mathbf{v}_1 \rangle^{1/2} = (\sum_{r=1}^p v_{1r}^2)^{1/2}$.
-
-	Our strategy is to formulate a hybrid random object, 
-	by combining   $X$ and $\mathbf{Z}$ into an ordered pair:
-	\begin{equation}\label{def:hybid_predictor}
-		\mathbf{W} = (X, \mathbf{Z}) 
-		\in \mathcal{H},~\text{where}~\mathcal{H}:=\mathcal{F} \times \mathbb{R}^p
-	\end{equation}
-	An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}[\mathbf{t}] = (X(\mathbf{t}), \mathbf{Z})^\top$, with $ X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $ \mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.
-
-	\begin{definition}[Hilbert space of hybrid objects]\label{def:hilbert_space}
-		We define the inner product between any two hybrid objects,
-		$\mathbf{h}_1 = (f_1, \mathbf{v}_1)$ and $\mathbf{h}_2 = (f_2, \mathbf{v}_2)$, as
-		\begin{equation}
-			\langle \mathbf{h}_1, \mathbf{h}_2\rangle_{\mathcal{H}} 
-			:= 
-			\langle f_1, f_2\rangle_\mathcal{F} 
-			+
-			\omega \langle  \mathbf{v_1}, \mathbf{v_2} \rangle = \sum \limits_{k=1}^K \int_0^1 f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k
-			+
-			\omega \sum \limits_{r=1}^p v_{1r}v_{2r}, 
-			\label{eq: hybrid inner product}
-		\end{equation}
-		with norm $\Vert \cdot \Vert_\mathcal{H} = \langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
-	\end{definition}
-	In \eqref{eq: hybrid inner product}, 
-	$\omega$ is a positive weight that needs to be pre-specified or estimated.
-It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}).
+%The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)}) $ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as $\langle f_1, f_2\rangle_\mathcal{F} =  \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)}\rangle_{L^2} = \sum_{k=1}^K \int_0^1 f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k$ with norm $\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_0^1 f_1^{(k)}(t_k)^2 dt_k\}^{1/2}$.
+%An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}[\mathbf{t}] = (X(\mathbf{t}), \mathbf{Z})^\top$, with $ X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $ \mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.
+
  Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$.
@@
 It also incorporates a regularization scheme that enables the algorithm to borrow strength and exploit structural relationships within and between the functions to avoid overfitting of the PLS components and to improve the generalizability and interpretability of the predictive model.
-	Each iteration of our approach consists of two subroutines: regularized estimation of smoothed PLS components and orthogonalization, detailed in Sections~\ref{subsec: Step 1: Computing Smoothed PLS components} and~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}, respectively.
-After a suitable number of iterations, the hybrid regression coefficient is estimated, as described in Section~\ref{subsec: Obtaining the Estimated Hybrid Regression Coefficient}.
+Each iteration of our approach consists of two subroutines: regularized estimation of smoothed PLS components and orthogonalization, detailed in Sections~\ref{section:sub:compute_PLS_component} and~\ref{section:sub:residualization}, respectively.
+After a suitable number of iterations, the hybrid regression coefficient is estimated, as described in Section~\ref{section:sub:regression_coeff}.
 For notational simplicity, we omit the iteration index $l$ in the following discussion, with the understanding that the subroutines apply to any iteration.
@@
 
-	\subsection{Preliminary step: Finite-basis Approximation }\label{sec: finite basis approximation}	
+\subsection{Preliminary step 1: finite-basis approximation}\label{sec: finite basis approximation}	
 Let ${b_m(t)}$ be a twice-differentiable basis of $L^2([0,1])$ whose second derivatives are also linearly independent, for example, cubic B-splines, the Fourier basis, or an orthonormal polynomial basis of degree greater than three.
@@
 
-	\subsection{Step 1: Computing smoothed PLS component direction}  \label{subsec: Step 1: Computing Smoothed PLS components} 
-	We begin with the first step of the iterative algorithm: estimating the smooth PLS component direction.
-Section~\ref{sec: pls component computation intermediate} introduces the core optimization problem for this step, formulated as a generalized Rayleigh quotient.
-Building on this, Section~\ref{sec: Regularization of PLS Components} presents a modified version that promotes smoothness, which is the estimation procedure for our proposed method, along with a efficient computation scheme.
-
-	\subsubsection{Core optimization problem for PLS component direction estimation}\label{sec: pls component computation intermediate}
-	Building on the basis function approximation in Section~\ref{sec: finite basis approximation}, we now present the core optimization problem that directly estimates the hybrid PLS component direction.
-This strategy fully leverages the continuous nature of the functional components and the function-scalar hybrid structure, and can be implemented using simple matrix-vector multiplications.
-
+\subsection{Preliminary step 2 : data preprocessing} \label{subsec: Data Preprocessing}
+\jongmin{notation not changed yet}
+Functional and scalar elements of the hybrid predictors often have incompatible units and/or exhibit different amounts of variation.
+This can be problematic for our PLS framework which is not scale invariant as: i) each predictor has different chance of contributing to the predictor/response structure; and ii) a predictor with high correlation to $Y$ but relatively low variance may be overlooked.
+
+To obtain PLS components that have a meaningful interpretation, we standardize the predictor data via the following steps.
+The first step is to account for discrepancies \textit{within} respective functional and scalar parts, if needed.
+If elements of multivariate functional data $X_i = (X_i^{(1)}, \ldots, X_i^{(K)})$ are measured in different units or have quite different domains, one can standardize them to have mean zero and integrated variance of one.
+If multivariate scalar predictors $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ exhibit different amounts of variation, one can standardize them to have mean zero and unit variance.
+The second step is to eliminate the discrepancies \textit{between} functional and scalar parts.
+To accomplish this aim, we choose an appropriate weight $\omega$ in the hybrid inner product \eqref{eq: hybrid inner product} that ensures functional and vector parts have comparable variance.
+A sensible data-driven approach to choosing an appropriate weight is to set
+\begin{equation*}
+	\omega = \frac{\sum_{i=1}^n \Vert X_i \Vert_\mathcal{F}^2}{\sum_{i=1}^n \Vert \mathbf{Z}_i \Vert^2},
+	\label{eq: weight}
+\end{equation*}
+In practice, this weighting scheme can be implemented by formulating the hybrid object as $\mathbf{W} = (X, \omega^{1/2} \mathbf{Z})$, whose vector part has been scaled by a factor of $\omega^{1/2}$.
+
+\subsection{Iterative steps}
+The iterative process presented here yields an orthonormal hybrid basis that effectively captures the predictor-response relationships.
+It proceeds through two intermediate steps: the estimation of the PLS component direction (Section \ref{section:sub:compute_PLS_component}) and residualization (Section \ref{section:sub:residualization}).
+The properties of the resulting estimates are introduced in Section \ref{section:main:properties_of_our_method}.
+\subsubsection{Iterative step 1: Regularized estimation of smoothed PLS component direction}  \label{section:sub:compute_PLS_component} 
+We begin by formally introducing the core optimization problem pertinent to the PLS direction estimation, which is formulated as a generalized Rayleigh quotient (Proposition \ref{proposition:eigen_noregul}).
+Building upon this foundational concept, we present our regularized PLS component direction estimation step that promotes smoothness (Proposition \ref{proposition:eigen_regul}).
+Furthermore,  we detail an efficient computational scheme (Proposition \ref{proposition:linear_regul}).
+
+\medskip
+\noindent
+\textit{Core optimization problem.}\label{sec: pls component computation intermediate}~
+We   present the core optimization problem that directly estimates the hybrid PLS component direction.
+It fully leverages the continuous nature of the functional components and the function-scalar hybrid structure.
 We describe the strategy at the $l$-th iteration.
-%For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for details).
+%For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{section:sub:residualization} for details).
 The  PLS component direction is estimated by the unit-norm direction $\xi^{[l]} \in \widetilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as
@@
 
-	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
+\medskip
+\noindent
+\textit{Proposed regularized estimation procedure.}~ \label{sec: Regularization of PLS Components}
 Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions.
@@
 
-	\medskip
-	\noindent
-	\textit{Proposed estimation procedure.}~
 To avoid the orthogonal basis assumption of  \citet{Rice1991}, we adopt the strategy of \citet{Silverman1996}, which replaces the standard orthonormality constraint with a weaker one based on a modified inner product that incorporates roughness.
@@
 		\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
-			\quad \text{s.t.} \quad \boldsymbol{\xi}^\top (\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1.
+		\quad \text{s.t.} \quad 
+		%
+		% constraint
+		\boldsymbol{\xi}^\top (\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1.
 	\end{equation}
@@
 The proof of Proposition \ref{proposition:eigen_regul} is provided in Appendix  \ref{section:proof:proposition:eigen_regul}.
-	The smoothing parameter $\lambda_k > 0$ $(k = 1, \ldots, K)$ balances goodness of fit and smoothness in $\hat{\xi}_j$.
+%orthonormality preview
+The constraint $	\boldsymbol{\xi}^\top (\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1$
+enforces the orthonormality of the estimated PLS component directions with respect to a modified inner product (see Section \ref{section:sub:prop_geom} for details).
+The smoothing parameter $\lambda_k > 0$  balances goodness of fit and smoothness in $\hat{\xi}_j$.
 Smaller $\lambda_k$ yields components that better fit the data but risks overfitting; setting $\lambda_k = 0$ recovers the unregularized solution in Proposition~\ref{proposition:eigen_noregul}.
@@
 
-	\subsection{Step 2: Computing Residualized Predictors via Hybrid-on-Scalar Regression} \label{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}
+\subsubsection{Iterative step 2: residualization via hybrid-on-scalar regression} \label{section:sub:residualization}
 The $l$-th iteration's second step involves residualization of both predictors and responses. We first compute the individual PLS score:  
@@
 	The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
- 	$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients and scalar parts given by:
+	$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients
 	\begin{equation*}
@@
 		j = 1, \ldots, K,
-	%%%%%%%%%%%%%%%%%%%%%%%%
-	\quad
+	\end{equation*}
+	  and scalar parts given by:
+	 \begin{equation*}
 	 	\hat{\boldsymbol{\chi} }^{[l]}
@@
 
-	\subsection{Obtaining the Estimated Hybrid Regression Coefficient}
-	\label{subsec: Obtaining the Estimated Hybrid Regression Coefficient}
+\subsection{Final step: estimating  the hybrid regression coefficient}
+\label{section:sub:regression_coeff}
+\jongmin{notation not yet changed}
 The regression coefficient $\boldsymbol{\eta}$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS components and scores.
@@
 
-	\subsection{Data Preprocessing} \label{subsec: Data Preprocessing}
-
-	Functional and scalar elements of the hybrid predictors often have incompatible units and/or exhibit different amounts of variation.
-This can be problematic for our PLS framework which is not scale invariant as: i) each predictor has different chance of contributing to the predictor/response structure; and ii) a predictor with high correlation to $Y$ but relatively low variance may be overlooked.
-
-	To obtain PLS components that have a meaningful interpretation, we standardize the predictor data via the following steps.
-The first step is to account for discrepancies \textit{within} respective functional and scalar parts, if needed.
-If elements of multivariate functional data $X_i = (X_i^{(1)}, \ldots, X_i^{(K)})$ are measured in different units or have quite different domains, one can standardize them to have mean zero and integrated variance of one.
-If multivariate scalar predictors $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ exhibit different amounts of variation, one can standardize them to have mean zero and unit variance.
-The second step is to eliminate the discrepancies \textit{between} functional and scalar parts.
-To accomplish this aim, we choose an appropriate weight $\omega$ in the hybrid inner product \eqref{eq: hybrid inner product} that ensures functional and vector parts have comparable variance.
-A sensible data-driven approach to choosing an appropriate weight is to set
-	\begin{equation*}
-		\omega = \frac{\sum_{i=1}^n \Vert X_i \Vert_\mathcal{F}^2}{\sum_{i=1}^n \Vert \mathbf{Z}_i \Vert^2},
-		\label{eq: weight}
-	\end{equation*}
-	In practice, this weighting scheme can be implemented by formulating the hybrid object as $\mathbf{W} = (X, \omega^{1/2} \mathbf{Z})$, whose vector part has been scaled by a factor of $\omega^{1/2}$.
-
 \section{Properties of the Proposed PLS Framework}
-	\label{sec: Properties of the Proposed PLS Framework}
-			\medskip
-	\noindent \textit{Orthonormality.}~
-	The constraint $\xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1$ enforces the following modified orthonormality of the estimated PLS components ($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ which now takes into account the roughness of the functions:
-	\begin{align*}
-		\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
-		&= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right \rangle_{L^2} \\
-		&= \sum \limits_{k=1}^K \int_0^1 \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_0^1 \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
-		& = \mathbb{1}(l=j). 
-	\end{align*}
-	This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{sec: Properties of the Proposed PLS Framework} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.
+\label{section:main:properties_of_our_method}
+\jongmin{notation not yet changed}
 
@@
 
-	\subsection{Tucker's Criterion}
+\subsection{Tucker's Criterion}\jongmin{notation not yet changed}
 We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
@@
 
-	\subsection{Geometric Properties}
+\subsection{Geometric Properties}\label{section:sub:prop_geom}\jongmin{currently revising}
 In this section, we derive several geometric properties of the PLS components and and scores obtained from the proposed algorithm.
+
+\begin{definition}[Roughness-sensitive inner product]
+	$\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$
+\end{definition}
+  ($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product  which now takes into account the roughness of the functions:
+\begin{align*}
+	\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
+	&= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right \rangle_{L^2} \\
+	&= \sum \limits_{k=1}^K \int_0^1 \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_0^1 \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
+	& = \mathbb{1}(l=j). 
+\end{align*}
+This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{section:main:properties_of_our_method} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.
 
@@
 \end{equation*}
-	Finally, the functional predictors are smoothed using a B-spline basis with 15 basis functions, as described in Section \ref{subsec: Step 1: Computing Smoothed PLS components}.
+Finally, the functional predictors are smoothed using a B-spline basis with 15 basis functions, as described in Section \ref{section:sub:compute_PLS_component}.
 
@@
 Since we assumed in Section \ref{sec: finite basis approximation} that both $B'$ and $B''$ are positive definite, $\operatorname{PENSSE}( \delta)$ is convex.
-convex.
 Consequently, the gradient vanishes at its unique minimizer:

### 2025-08-12 manuscript/main.tex
the function space needs to have second derivatives

@@
 For $k = 1, \ldots, K$, 
-we assume that the functional predictors $X_{ik}(t)$ are observed on the domain $0 \leq t \leq 1$.and belong to $L^2([0,1])$, the Hilbert space of square-integrable real-valued functions with respect to the Lebesgue measure $dt$ on $[0,1]$.
+we assume that the functional predictors $X_{ik}(t)$ are observed on the domain $0 \leq t \leq 1$, and belong to $\mathcal{F}$,
+which is defined as the space of real-valued functions on $[0,1]$
+which are square-integrable with respect to the Lebesgue measure $dt$ on $[0,1]$,
+ and possess second  derivatives.
 Additionally, let $\mathbf{Z}=(Z_1, \ldots, Z_p)^\top$
@@
 		W_i := (X_{i1}, \ldots, X_{iK}, \mathbf{Z}_i)
-		\in \mathcal{H} :=  L^2([0,1])^{\otimes K} \times \mathbb{R}^p
+		\in \mathcal{H} :=  \mathcal{F}^{\otimes K} \times \mathbb{R}^p
 \end{equation}
@@
 \begin{definition}[Roughness-sensitive inner product]
-	$\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$
+		Given two hybrid predictors 	$W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$
+	and
+	$W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$ belonging to $\mathcal{H}$ defined in Definition \ref{def:hybid_predictor}
+	and roughness penalty matrix 	$\Lambda  = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$,
+	The inner product between two hybrid predictors, taking into the roughness peanlties,  is then defined as:
+\begin{equation}
+	\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}
+\end{equation}
+	\begin{equation}		\label{eq: hybrid inner product}
+	\langle W_1, W_2\rangle_{\mathcal{H}, \Lambda}
+	:=
+	\sum \limits_{k=1}^K \int_0^1 X_{1k}(t) X_{2k}(t) \, dt
+	\sum \limits_{k=1}^K \int_0^1 X^{\prime \prime}_{1k}(t) X^{\prime \prime}_{2k}(t) \, dt
+	+ 
+	\omega
+	\mathbf{Z}_1^\top \mathbf{Z}_2,
+\end{equation}
+for $\omega > 0$.
+The corresponding norm $\Vert \cdot \Vert_\mathcal{H}$ is derived from this inner product as $\langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
 \end{definition}
+
   ($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product  which now takes into account the roughness of the functions:

### 2025-08-12 manuscript/main.tex
orthonormal proposition intro revised

@@
 	\sum 
-	\limits_{j=1}^K 
-	\int  \beta_j(t) X_{ij}(t) dt + \epsilon_i,
+	\limits_{k=1}^K 
+	\int  \beta_j(t) X_{ik}(t) dt + \epsilon_i,
 	\quad
@@
 \end{equation}
-where $Y$ is a scalar response, $\mathbf{Z}$ is the Euclidean vector covariate and 
-$X_{i1}(t), \ldots, X_{iK}(t)$ are functional predicters.
+where $Y_i$ is a scalar response, $\mathbf{Z}_i$ is a Euclidean vector covariate, 
+$X_{i1}(t), \ldots, X_{iK}(t)$ are functional predicters, and $\epsilon_i$ is an observational noise.
 For notational convenience, we assume throughout this paper that the responses and predictors have been centered, allowing the intercept term to be ignored.
@@
 
-\subsection{Geometric Properties}\label{section:sub:prop_geom}\jongmin{currently revising}
+\subsection{Geometric Properties}\label{section:sub:prop_geom}
 In this section, we derive several geometric properties of the PLS components and and scores obtained from the proposed algorithm.
 
-\begin{definition}[Roughness-sensitive inner product]
-		Given two hybrid predictors 	$W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$
-	and
-	$W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$ belonging to $\mathcal{H}$ defined in Definition \ref{def:hybid_predictor}
-	and roughness penalty matrix 	$\Lambda  = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$,
-	The inner product between two hybrid predictors, taking into the roughness peanlties,  is then defined as:
-\begin{equation}
-	\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}
-\end{equation}
-	\begin{equation}		\label{eq: hybrid inner product}
+A fundamental property of partial least squares   is that its derived bases are orthonormal.
+Our regularized estimates preserve this property, with respect to a modified inner product that incorporates the roughness penalty, defines as follows:
+\begin{definition}[Roughness-sensitive inner product]\label{def:hybrid_inner_product_roughness}
+	Given two hybrid predictors $W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$ and $W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$, both elements of $\mathcal{H}$ as defined in Definition \ref{def:hybid_predictor}, and a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, the roughness-sensitive inner product between $W_1$ and $W_2$ is defined as:
+	\begin{equation}		\label{eq: hybrid inner product_roughness}
 		\langle W_1, W_2\rangle_{\mathcal{H}, \Lambda}
@@
 		\sum \limits_{k=1}^K \int_0^1 X_{1k}(t) X_{2k}(t) \, dt
-	\sum \limits_{k=1}^K \int_0^1 X^{\prime \prime}_{1k}(t) X^{\prime \prime}_{2k}(t) \, dt
-	+ 
-	\omega
-	\mathbf{Z}_1^\top \mathbf{Z}_2,
-\end{equation}
-for $\omega > 0$.
-The corresponding norm $\Vert \cdot \Vert_\mathcal{H}$ is derived from this inner product as $\langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
+		+
+		\sum \limits_{k=1}^K \lambda_k \int_0^1 X^{\prime \prime}_{1k}(t) X^{\prime \prime}_{2k}(t) \, dt
+		+
+		\mathbf{Z}_1^\top \mathbf{Z}_2.
+	\end{equation}
 \end{definition}
+Based on this inner product, the following proposition states that the PLS component directions estimated from Proposition  \ref{proposition:eigen_regul} are orthonormal.
+\begin{proposition}\label{proposition: modified orthnormality of PLS components}\jongmin{currently revising}
+	The estimated PLS components, $\widehat{\xi}_1, \widehat{\xi}_2, \ldots, \widehat{\xi}_L$, from the proposed PLS algorithm are mutually orthonormal with respect to the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ in $\mathcal{H}$ that incorporates the roughness of the functions; i.e.,
+	\begin{equation*}
+		\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
+		= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}
+		= \mathbb{1}(l=j). 
+	\end{equation*}
+\end{proposition}
+The proof of Proposition \ref{proposition: modified orthnormality of PLS components} is provided in Appendix \ref{section:proof:proposition: modified orthnormality of PLS components}.
+Now let $\widehat{\boldsymbol{\rho}}_l=(\widehat{\rho}_{1l}, \ldots, \widehat{\rho}_{nl})^\top$ denote the $n$-dimensional vector whose elements consist of estimated $l$-th PLS scores ($l=1, \ldots, L)$ of $n$ observations.
 
@@
 \end{align*}
-This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{section:main:properties_of_our_method} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.
-
-The following proposition states that the PLS components estimated from Proposition  \ref{proposition:eigen_regul} are orthonormal with respect to the modified inner product $\langle \langle \cdot \rangle \rangle$ that incorporates the roughness of the functions.
-\begin{proposition}\label{proposition: modified orthnormality of PLS components}
-	The estimated PLS components, $\widehat{\xi}_1, \widehat{\xi}_2, \ldots, \widehat{\xi}_L$, from the proposed PLS algorithm are mutually orthonormal with respect to the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ in $\mathcal{H}$ that incorporates the roughness of the functions; i.e.,
-	\begin{equation*}
-		\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
-		= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}
-		= \mathbb{1}(l=j). 
-	\end{equation*}
-\end{proposition}
-The proof of Proposition \ref{proposition: modified orthnormality of PLS components} is provided in Appendix \ref{section:proof:proposition: modified orthnormality of PLS components}.
-Now let $\widehat{\boldsymbol{\rho}}_l=(\widehat{\rho}_{1l}, \ldots, \widehat{\rho}_{nl})^\top$ denote the $n$-dimensional vector whose elements consist of estimated $l$-th PLS scores ($l=1, \ldots, L)$ of $n$ observations.
+
 The next proposition states that the vectors of estimated PLS scores $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$ obtained from the proposed algorithm are mutually orthogonal.

### 2025-08-12 manuscript/main.tex
core optimization notation improved

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\address[A]{University of Southern California\printead[presep={,\ }]{e1}}
-
-\address[B]{University of Texas Medical Branch\printead[presep={,\ }]{e2}}
+\address[A]{Data Sciences and Operations Department, Marshall School of Business, University of Southern California\printead[presep={,\ }]{e1}}
+
+\address[B]{Department of Biostatistics and Data Science, University of Texas Medical Branch\printead[presep={,\ }]{e2}}
 \end{aug}
@@
 	\hat{\xi} 
-	= 
-	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}}
-	)
 	:= \arg \max_{\xi \in \widetilde{\mathcal{H}}
@@
 	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
-	\bigr)~s.t.~\| \xi  \|_\mathcal{H} = 1,
+	\bigr)~s.t.~\| \xi  \|_\mathcal{H} = 1.
 \end{equation}
 %
-where each functional part $\hat{\xi}_j $  is expanded as
-$
-\hat{\xi}_j(t) := 
-\sum_{m=1}^M \hat{\gamma}_{jm} \, b_m(t),
-$
-and $\hat{\boldsymbol{\zeta}}$ is the scalar part. This maximizer can also be represented as a concatenated Euclidean vector
-\begin{equation}\label{def:maximizer_euclidean_form}
-	( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\zeta}}^\top )^\top
-	\in \mathbb{R}^{MK+p},
-\end{equation}
-where the coefficient vectors $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ are defined as in \eqref{def:coef_vector_form}.
-Proposition \ref{proposition:eigen_noregul} reformulates  the problem \eqref{def:maximizer_squared_empirical_cov} as  a generalized Rayleigh quotient.
+Here, $\hat{\xi} \in \widetilde{\mathcal{H}}$ is an ordered pair which can be expanded as:
+\begin{equation*}
+	\hat{\xi}	= 
+	\bigl(
+	\hat{\xi}_1(t), \ldots, \hat{\xi}_K(t), \hat{\boldsymbol{\zeta}}
+	\bigr)
+	=
+\biggl(
+	\sum_{m=1}^M \hat{\gamma}_{1m} \, b_m(t),
+		 \ldots, 
+		\sum_{m=1}^M \hat{\gamma}_{Km} \, b_m(t), \hat{\boldsymbol{\zeta}}
+	\biggr)
+	,
+\end{equation*}
+where  $\hat{\boldsymbol{\zeta}}$ is the scalar part.
+Obtaining these coefficients is equivalent to solving the maximization problem   \eqref{def:maximizer_squared_empirical_cov}.
+The following proposition formulates this coefficients obtaining procedure as a generalized Rayleigh quotient:
 %
@@
 	denote the observed data defined in \eqref{def:problem_instance}.
-	At the $l$-th iteration of the PLS algorithm, the unit-norm maximizer of  the squared empirical covariance defined in \eqref{def:maximizer_squared_empirical_cov}, represented as the Euclidean vector form as in \eqref{def:maximizer_euclidean_form},
-	is obtained by solving 
+	At the $l$-th iteration of the PLS algorithm, 
+	the coefficients of the squared covariance  maximizer defined in \eqref{def:maximizer_squared_empirical_cov}, 
+	is obtained as
 	\begin{equation}	\label{eq: Unregularized generalized rayleigh quotient equation}
 		\left(
-		\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\zeta}}^\top
+		\hat{\gamma}_{11}, \ldots, \hat{\gamma}_{1M}
+		, \ldots,
+		\hat{\gamma}_{K1}, \ldots, \hat{\gamma}_{KM}
+		, \hat{\boldsymbol{\zeta}}^\top
 		\right)^\top

### 2025-08-12 manuscript/main.tex
regularized estimation notation improved

@@
 %
-Here, $\hat{\xi} \in \widetilde{\mathcal{H}}$ is an ordered pair which can be expanded as:
+Here, $\hat{\xi} \in \widetilde{\mathcal{H}}$ is an ordered pair  expanded as:
 \begin{equation*}
@@
 \end{equation}
+Here, $\hat{\xi} \in \widetilde{\mathcal{H}}$ is an ordered pair  expanded as:
+\begin{equation*}
+	\hat{\xi}	= 
+	\bigl(
+	\hat{\xi}_1(t), \ldots, \hat{\xi}_K(t), \hat{\boldsymbol{\zeta}}
+	\bigr)
+	=
+	\biggl(
+	\sum_{m=1}^M \hat{\gamma}_{1m} \, b_m(t),
+	\ldots, 
+	\sum_{m=1}^M \hat{\gamma}_{Km} \, b_m(t), \hat{\boldsymbol{\zeta}}
+	\biggr)
+	,
+\end{equation*}
+where  $\hat{\boldsymbol{\zeta}}$ is the scalar part.
 This formulation maximizes the squared covariance over a class of smooth functions.
-Proposition~\ref{proposition:eigen_regul} expresses this problem as a generalized Rayleigh quotient.
-
+ Obtaining these coefficients is equivalent to solving the maximization problem   \eqref{def:maximizer_squared_empirical_cov_reg}.
+The following proposition formulates this coefficients obtaining procedure as a generalized Rayleigh quotient:
 \begin{proposition}\label{proposition:eigen_regul}
@@
 	denote the observed data defined in \eqref{def:problem_instance}.
-	At the $l$-th iteration of the PLS algorithm, the maximizer of  the squared empirical covariance defined in \eqref{def:maximizer_squared_empirical_cov_reg}, represented as the Euclidean vector form as in \eqref{def:maximizer_euclidean_form},
-	is obtained by solving 
+	At the $l$-th iteration of the PLS algorithm, 	the coefficients of the squared covariance  maximizer defined in \eqref{def:maximizer_squared_empirical_cov_reg}, 
+	is obtained as
 	\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
 	\left(
-		\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\zeta}}^\top
+\hat{\gamma}_{11}, \ldots, \hat{\gamma}_{1M}
+, \ldots,
+\hat{\gamma}_{K1}, \ldots, \hat{\gamma}_{KM}
+, \hat{\boldsymbol{\zeta}}^\top
 \right)^\top

### 2025-08-12 manuscript/main.tex
orthonormality proposition revised

@@
  \usepackage{xcolor}
+ \usepackage{bbm}
 % \usepackage{url} % not crucial - just used below for the URL 
@@
 Based on this inner product, the following proposition states that the PLS component directions estimated from Proposition  \ref{proposition:eigen_regul} are orthonormal.
-\begin{proposition}\label{proposition: modified orthnormality of PLS components}\jongmin{currently revising}
-	The estimated PLS components, $\widehat{\xi}_1, \widehat{\xi}_2, \ldots, \widehat{\xi}_L$, from the proposed PLS algorithm are mutually orthonormal with respect to the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ in $\mathcal{H}$ that incorporates the roughness of the functions; i.e.,
-	\begin{equation*}
-		\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
-		= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}
-		= \mathbb{1}(l=j). 
+\begin{proposition}[Orthonormality of regularized PLS component directions]\label{proposition: modified orthnormality of PLS components}
+	The PLS component directions $\widehat{\xi}_1, \widehat{\xi}_2, \ldots, \widehat{\xi}_L$, estimated via Proposition \ref{proposition:eigen_regul} with a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, are mutually orthonormal with respect to the inner product $\langle \cdot, \cdot \rangle_{\mathcal{H}, \Lambda}$.
+That is,
+	\begin{equation*}
+		\langle \widehat{\xi}_{l_1}, \widehat{\xi}_{l_2} \rangle_{\mathcal{H}, \Lambda}
+		= \mathbbm{1}(l_1 = l_2), \quad l_1, l_2 = 1, \ldots, L.
 	\end{equation*}
@@
 The proof of Proposition \ref{proposition: modified orthnormality of PLS components} is provided in Appendix \ref{section:proof:proposition: modified orthnormality of PLS components}.
+
+\jongmin{revising here}
 Now let $\widehat{\boldsymbol{\rho}}_l=(\widehat{\rho}_{1l}, \ldots, \widehat{\rho}_{nl})^\top$ denote the $n$-dimensional vector whose elements consist of estimated $l$-th PLS scores ($l=1, \ldots, L)$ of $n$ observations.
-
-($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product  which now takes into account the roughness of the functions:
-\begin{align*}
-	\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
-	&= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right \rangle_{L^2} \\
-	&= \sum \limits_{k=1}^K \int_0^1 \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_0^1 \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
-	& = \mathbb{1}(l=j). 
-\end{align*}
-
 The next proposition states that the vectors of estimated PLS scores $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$ obtained from the proposed algorithm are mutually orthogonal.

### 2025-08-12 manuscript/main.tex
pls direction proposition revised

@@
 %Functional data analysis (FDA) treats each observed process as a realization of a random function over a continuous domain, such as time or space.
-The smoothness and infinite-dimensional nature of functional data allow researchers to exploit rich structural features, including derivatives and complex covariance patterns.
+The smoothness and infinite-dimensional nature of functional data allow researchers to exploit rich structural features, including .
 This enables regression analysis for predicting clinical outcomes using complex functional predictors collected with advanced recording technologies, such as medical imaging data.
@@
 Modern biomedical studies frequently collect diverse data types from each subject.
-As an illustrative example, the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021}  records both multiple renogram curves (functional data) and multiple renogram variables (vector data)  for each kidney.
-These modalities provide distinct yet related physiological signals.
-To effectively analyze such heterogeneous data, we need statistical methods capable of jointly modeling functional and vector-valued covariates.
-This approach accounts for both shared and modality-specific variations linked to clinical outcomes.
+As an illustrative example, the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021}  records both multiple   renogram curves (functional data) and multiple renogram variables (scalar data)  for each kidney.
+To effectively analyze such distinct yet related physiological signals, we construct a joint linear regression model incorporating both functional and scalar-valued covariates. 
+ %This approach accounts for both shared and modality-specific variations linked to clinical outcomes.
 Our work focuses on developing a method to fit the following hybrid functional linear regression model:
@@
 	\limits_{k=1}^K 
-	\int  \beta_j(t) X_{ik}(t) dt + \epsilon_i,
+	\int  \beta_k(t) X_{ik}(t) dt + \epsilon_i,
 	\quad
@@
 %Also, there may be high correlation between functional and scalar predictors.
-Regression with functional and scalar predictors poses several challenges.
-Estimating the infinite-dimensional slope function is an ill-posed problem requiring regularization or dimension reduction.
-Scalar predictors are often high-dimensional and multicollinear, further complicating estimation.
+This hybrid model poses several challenges.
+Estimating the infinite-dimensional slope function $\beta_k(t) $ is an ill-posed problem requiring  dimension reduction or regularization based on structural assumption,
+such as derivatives and covariance patterns.
+ Scalar predictors are often high-dimensional and multicollinear.
  Moreover, strong correlations between functional and scalar predictors are common but typically overlooked by separate modeling approaches.
@@
 \begin{equation}\label{def:theta}
-	\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
-\end{equation}
-The full data for the hybrid PLS problem can be represented by the tuple
+	\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M},
+\end{equation}
+and construct the full design matrix $\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}$. Let us denote the response vector as $\mathbf{y} := (y_1, \ldots, y_n)^\top$.
+Let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, with entries
+\begin{equation}\label{def:B_matrix}
+	B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt, \quad
+	B^{\prime\prime}_{m, m'} := \int_0^1 b_m''(t)\, b_{m'}''(t)\, dt,
+\end{equation}
+for $m, m' = 1, \ldots, M$. We then define the block-diagonal matrices
+\begin{equation}\label{def:gram_block}
+	\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p), \quad
+	\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
+\end{equation}
+
+Then the full data for the hybrid PLS problem at the $l$-th iteration can be represented by the tuple
 \begin{equation}\label{def:problem_instance}
@@
 \end{equation}
-where $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ are the Gram matrices of the basis functions and their second derivatives, with entries
-\begin{equation}\label{def:B_matrix}
-	B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt, \quad
-	B^{\prime\prime}_{m, m'} := \int_0^1 b_m''(t)\, b_{m'}''(t)\, dt,
-\end{equation}
-for $m, m' = 1, \ldots, M$. We then define the block-diagonal matrices
-\begin{equation}\label{def:gram_block}
-	\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p), \quad
-	\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
-\end{equation}
-the full design matrix $\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}$, and the response vector $\mathbf{y} := (y_1, \ldots, y_n)^\top$.
+with the index $l$ omitted for brevity.
 
@@
 The properties of the resulting estimates are introduced in Section \ref{section:main:properties_of_our_method}.
-\subsubsection{Iterative step 1: Regularized estimation of smoothed PLS component direction}  \label{section:sub:compute_PLS_component} 
+\subsubsection{Iterative step 1: regularized estimation of  PLS component direction}  \label{section:sub:compute_PLS_component} 
 We begin by formally introducing the core optimization problem pertinent to the PLS direction estimation, which is formulated as a generalized Rayleigh quotient (Proposition \ref{proposition:eigen_noregul}).
@@
 The following proposition formulates this coefficients obtaining procedure as a generalized Rayleigh quotient:
-\begin{proposition}\label{proposition:eigen_regul}
+\begin{proposition}[Regularized estimation of PLS component direction]\label{proposition:eigen_regul}
 	Let
@@
 	$
-	denote the observed data defined in \eqref{def:problem_instance}.
-	At the $l$-th iteration of the PLS algorithm, 	the coefficients of the squared covariance  maximizer defined in \eqref{def:maximizer_squared_empirical_cov_reg}, 
-	is obtained as
+	denote the  data given at the $l$-th iteration, as defined in \eqref{def:problem_instance}.
+	Recall from \eqref{def:V_matrix} that $
+	V = n^{-2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top$ .
+	 Let 
+	$\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ be defined as:
+	\begin{equation}\label{def:Lambda}
+		\Lambda := \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p}),
+		~\text{where}~\lambda_1, \ldots, \lambda_K \geq 0.
+	\end{equation}
+Here, $0_{p \times p}$ denotes the $p \times p$ zero matrix.
+ 	The coefficients of the squared covariance  maximizer defined in \eqref{def:maximizer_squared_empirical_cov_reg}, 
+	are obtained as
 	\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
@@
 \right)^\top
+\hspace{-.7em}
 		=
-		\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
-		\quad \text{s.t.} \quad 
+		\arg 
+		\hspace{-.6em}
+		\max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
+	~~\text{s.t.}~~
 		%
 		% constraint
-		\boldsymbol{\xi}^\top (\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1.
-	\end{equation}
-	where we recall that $
-	V = n^{-2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top$ is defined in  \eqref{def:V_matrix}, and 
-	$\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is given by
-	\begin{equation}\label{def:Lambda}
-		\Lambda := \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p}),
-	\end{equation}
-	where $0_{p \times p}$ denotes the $p \times p$ zero matrix.
+		\boldsymbol{\xi}^\top 
+		\hspace{-.2em}
+		(\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1.
+	\end{equation}
+
 \end{proposition}
@@
 enforces the orthonormality of the estimated PLS component directions with respect to a modified inner product (see Section \ref{section:sub:prop_geom} for details).
-The smoothing parameter $\lambda_k > 0$  balances goodness of fit and smoothness in $\hat{\xi}_j$.
+The smoothing parameter $\lambda_k$  balances goodness of fit and smoothness in $\hat{\xi}_j$.
 Smaller $\lambda_k$ yields components that better fit the data but risks overfitting; setting $\lambda_k = 0$ recovers the unregularized solution in Proposition~\ref{proposition:eigen_noregul}.

### 2025-08-12 manuscript/main.tex
in the middle of the orthogonality proof

@@
 \end{equation}
-and construct the full design matrix $\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}$. Let us denote the response vector as $\mathbf{y} := (y_1, \ldots, y_n)^\top$.
+and construct the full design matrix 
+\begin{equation}\label{def:full_theta}
+\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}.
+\end{equation}
+Let us denote the response vector as $\mathbf{y} := (y_1, \ldots, y_n)^\top$.
 Let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, with entries
@@
 		\sum_{j=1}^K
-		\langle
-		\xi_j, \xi_j
-		\rangle
+		\int_0^1
+		\xi_j(t) \, \xi_j(t)
+		\, dt
 		+
@@
 For notational simplicity, we omit the iteration superscript $[l]$.
+ Recall from  \eqref{def:plsscore} that
+$\hat{\rho}_i
+=
+\langle \widetilde{W}_i, \, \hat{\xi} \rangle_{\mathcal{H}}$.
 Using the basis expansion coefficient notation from \eqref{def:truncated_zeta_and_delta}, \eqref{def:coef_vector_form}, \eqref{def:theta}, and \eqref{def:B_matrix}, the full vector of PLS scores $\hat{\boldsymbol{\rho}}  = (\hat{\rho}_1, \ldots, \hat{\rho}_n)^\top$
-where
-$\hat{\rho}_1$ is defined in \eqref{def:plsscore},
 is computed through the following matrix multiplication:
-\begin{equation*}
+\begin{equation}\label{score_inner_product_all_n}
 	\hat{\boldsymbol{\rho}}^\top = \sum_{k=1}^K ( \hat{\boldsymbol{\gamma}}_j )^\top B \, \Theta_j^\top + \boldsymbol{\zeta}^\top \mathbf{Z}^\top.
-\end{equation*}
+\end{equation}
 The criterion $\operatorname{PENSSE}( \delta)$ can be decomposed as follows:
@@
 
-Firstly, it is obvious by the unit-norm constraint enforced in Proposition \ref{proposition: eigenanalysis} that:
+\begin{proof}
+	The unit norm condition is trivially met by the constraint 
+	$1 =  	\hat{\boldsymbol{\xi}}_l^\top 
+	\hspace{-.2em}
+	(\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \hat{\boldsymbol{\xi}}_l$
+	enforced in \eqref{eq: Regularized generalized rayleigh quotient equation}, because we have:
 	\begin{align*}
-	\langle \langle \hat{\xi}_l,  \hat{\xi}_l \rangle \rangle &= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}  \\
-	&= \sum \limits_{k=1}^K \int_0^1 \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_0^1 \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
-	&= \sum \limits_{k=1}^K \int_0^1 \hat{\mathbf{a}}^{(k) \top}_l \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k) \top}(t_k) \hat{\mathbf{a}}^{(k)}_l  dt_k + \boldsymbol{\theta}_l^\top \boldsymbol{\theta}_l + \sum \limits_{k=1}^K \lambda_k \int_0^1 \hat{\mathbf{a}}^{(k) \top}_l \ddot{\mathbf{b}}^{(k)}(t_k) \ddot{\mathbf{b}}^{(k) \top}(t_k) \hat{\mathbf{a}}^{(k)}_l  dt_k \\
-	& = \sum \limits_{k=1}^K \hat{\mathbf{a}}_l^{(k) \top} J^{(k)} \hat{\mathbf{a}}_l^{(k)} + \boldsymbol{\theta}_l^\top \boldsymbol{\theta}_l +  \sum \limits_{k=1}^K \lambda_k \hat{\mathbf{a}}^{(k) \top}_l \ddot{J}^{(k)} \hat{\mathbf{a}}^{(k)}_l \\
-	& = \hat{\xi}_l^{*\top} J^\ast \hat{\xi}_l^* + \hat{\xi}_l^{*\top} \Lambda \ddot{J}^\ast \hat{\xi}_l^* = \hat{\xi}_l^{*\top} (J^\ast +\Lambda \ddot{J}^\ast) \hat{\xi}_l^* = 1
+  	\hat{\boldsymbol{\xi}}_l^\top 
+\hspace{-.2em}
+(\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \hat{\boldsymbol{\xi}}_l
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&= \hat{\boldsymbol{\xi}}^\top_l 
+\hspace{-.2em}
+\mathbb{B}
+ \hat{ \boldsymbol{\xi} }_l
+ +
+ \hat{ \boldsymbol{\xi} }_l^\top 
+ \hspace{-.2em}
+ \Lambda \mathbb{B}^{\prime \prime} \hat{ \boldsymbol{\xi} }_l
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ \\&\overset{(i)}{=}
+ \sum_{j=1}^K
+ \int_0^1
+ \hat{\xi}_l(t) \, \hat{\xi}_l(t)
+ \, dt
+ +
+ \hat{\boldsymbol{\zeta}}^\top  \hat{\boldsymbol{\zeta}}
+ +
+  \hat{\boldsymbol{\xi}}^\top 
+ \hspace{-.2em}
+ \Lambda \mathbb{B}^{\prime \prime} \hat{\boldsymbol{\xi}}
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ \\&\overset{(ii)}{=}
+ \sum_{j=1}^K
+ \int_0^1
+ \hat{\xi}_l(t) \, \hat{\xi}_l(t)
+ \, dt
+ +
+ \hat{\boldsymbol{\zeta}}^\top \hat{\boldsymbol{\zeta}}
+ +
+ \sum \limits_{j=1}^K 
+ \lambda_l
+ \int_0^1 \bigl\{ \hat{\xi}_l^{\prime\prime}(t) \bigr\}^2 dt
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ \\&=
+ \langle \widehat{\xi}_{l}, \widehat{\xi}_{l} \rangle_{\mathcal{H}, \Lambda},
+\numberthis \label{rough_norm_matrix_form}
 	\end{align*}
-where $\ddot{\mathbf{b}}^{(k)}(t_k) = (\ddot{b}_1^{(k)}(t_k), \ldots, \ddot{b}_M^{(k)}(t_k))^\top$
-
-Now to prove the orthogonality, we first express the $l$-th residualized hybrid predictor in terms of its previous $(l-1)$-th version:
-\begin{equation*}
-	\widetilde{W}^{[l]}[\mathbf{t}] = \widetilde{W}^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\delta}}_l[\mathbf{t}]^\top 
-\end{equation*}
+where step $(i)$ uses \eqref{unit_norm_as_quadform}
+and
+step $(ii)$ uses \eqref{pen_as_matrix}.
+
+Now to switch our gears toward the the orthogonality. For  $l_1 > l_2 $, we have
+\begin{align*}
+	\langle \widehat{\xi}_{l_1}, \widehat{\xi}_{l_2} \rangle_{\mathcal{H}, \Lambda}
+	& \overset{(i)}{=}
+	\hat{\boldsymbol{\xi}}_{l_1}^\top 
+	\hspace{-.2em}
+	(\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \hat{\boldsymbol{\xi}}_{l_2}
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\\	& \overset{(ii)}{=} \frac{1}{\kappa_{l_1}} (V^{[l_1]} \widehat{\boldsymbol{\xi}}_{l_1})^\top \hat{\boldsymbol{\xi}}_{l_2}
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\\	& = \frac{1}{\kappa_{l_1}}
+	\widehat{\boldsymbol{\xi}}_{l_1}^\top
+	V^{[l_1]} \hat{\boldsymbol{\xi}}_{l_2} 
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\\	& \overset{(iii)}{=} \frac{1}{ n^2 \kappa_{l_1}}
+	\widehat{\boldsymbol{\xi}}_{l_1}^\top
+	(\mathbb{B} \Theta^{[l_1]\top} \mathbf{y})(\mathbb{B} \Theta^{[l_1]\top} \mathbf{y})^\top
+	\hat{\boldsymbol{\xi}}_{l_2}
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\\	& = \frac{1}{ n^2 \kappa_{l_1}}
+	\widehat{\boldsymbol{\xi}}_{l_1}^\top
+	(\mathbb{B} \Theta^{[l_1]\top} \mathbf{y})
+	\mathbf{y}^\top
+	\Theta^{[l_1] } 
+	\mathbb{B}
+	\hat{\boldsymbol{\xi}}_{l_2}
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\\	& = c
+	\mathbf{y}^\top
+	(
+	\Theta^{[l_1] }
+	\mathbb{B}
+	\hat{\boldsymbol{\xi}}_{l_2}
+	),
+\end{align*}
+where
+step $(i)$ uses \eqref{rough_norm_matrix_form},
+step $(ii)$ uses the fact that $\hat{\boldsymbol{\xi}}_{l_1}$ is a generalized eigenvector ($\kappa_{l_1}$ denotes the corresponding generalized eigenvalue), as presented in Proposition \ref{proposition:eigen_regul},
+and step $(iii)$ uses the definition of $V$ matrix given in \eqref{def:V_matrix},
+and $c$ represents a scalar.
+
+Our next task is to show that 
+\begin{equation*}
+\Theta^{[l_1] }
+\mathbb{B}
+\hat{\boldsymbol{\xi}}_{l_2} = \mathbf{0} \in \mathbb{R}^n.
+\end{equation*}
+Without loss of generality, we show that the $i$th entry of $\Theta^{[l_1] }
+\mathbb{B}
+\hat{\boldsymbol{\xi}}_{l_2}$ is 0.
+From the construction in \eqref{def:full_theta}, \eqref{def:theta} and \eqref{def:gram_block}, the $i$-th entry is
+\begin{align*}
+	(\Theta^{[l_1] }
+	\mathbb{B}
+	\hat{\boldsymbol{\xi}}_{l_2})_i
+	&=
+	(\theta_{i11}^{[l_1]}, \ldots, \theta_{i1M}^{[l_1]}, \ldots, \theta_{iK1}^{[l_1]}, \ldots, \theta_{iKM}^{[l_1]}, Z_{i1}^{[l_1]}, \ldots, Z_{ip}^{[l_1]})
+	\mathbb{B}
+	\hat{\boldsymbol{\xi}}_{l_2}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\\&=
+	\sum_{k=1}^K
+	\boldsymbol{\theta}_{ik}^{[l_1]} B
+	\hat{\boldsymbol{\gamma}}_k^{[l_2]}
+	+
+	\mathbf{Z}_{i}^{[l_1] \top } \hat{\boldsymbol{\zeta}}^{[l_2]}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\	&=
+\langle
+\widetilde{W}_i^{[l_1]}, 
+\hat{\xi}^{[l_2]}
+\rangle_{\mathcal{H}},
+\end{align*}
+where the last equality uses the computation of the $i$th entry in \eqref{score_inner_product_all_n}.
+
+We can express the $l_1$-th residualized hybrid predictor in terms of its previous $(l_1-1)$-th version:
+\begin{equation*}
+	\widetilde{W}_i^{[l_1]}= \widetilde{W}_i^{[l_1-1]} - \widehat{{\rho}}_i^{[l_1-1]} \widehat{\delta}^{[l_1-1]}
+\end{equation*}
+\end{proof}
+
 which, after applying the finite-dimensional form (9), implies that
@@
 \end{align*}
+
+	Let us denote
+$
+\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top.
+%\quad\text{and} \quad		\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
+$
+The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
+$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients
+\begin{equation*}
+	\hat{\boldsymbol{\pi}}_j^{[l]}
+	=
+	\bigl(
+	\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2
+	B
+	+
+	\tau
+	B^{\prime \prime}
+	\bigr)^{-1}
+	B
+	(\Theta_j^{[l]})^\top
+	\hat{\boldsymbol{\rho}}^{[l]}
+	,
+	~
+	j = 1, \ldots, K,
+\end{equation*}
+and scalar parts given by:
+\begin{equation*}
+	\hat{\boldsymbol{\chi} }^{[l]}
+	=
+	(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}^{[l]}.
+\end{equation*}
+
 Thus, we have
@@
 \end{align*}
-noting that $\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} = \widehat{\boldsymbol{\rho}}_j$.
-Now by the generalized eigenvalue problem (i.e., generalized Rayleigh quotient problem) presented in Proposition 2, we have that for $j < l$,
+noting that $\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} = \widehat{\boldsymbol{\rho}}_j$. Now by the , we have that
+
 \begin{align*}
-	\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle &= \widehat{\xi}_l^{*\top} (J^\ast + \Lambda \ddot{J}^\ast)\widehat{\xi}_j^{*} \\
-	& = \frac{1}{\kappa_l} (V^\ast_l \widehat{\xi}_l^{*})^\top \widehat{\xi}_j^{*} \\
 	&=  \frac{1}{\kappa_l}\widehat{\xi}_l^{* \top} V^\ast_l \widehat{\xi}_j^{*} \\

### 2025-08-12 manuscript/main.tex
outer product almost derived

@@
 We assume both $\delta^{[l]}$ and $E_i^{[l]}$ are elements of $\tilde{\mathcal{H}}$, as defined in \eqref{def:truncated_hilbert_space}.
-To ensure the stability of the entire PLS estimation procedure, the estimated regression coefficient $\hat{\delta}^{[l]} = (\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} ) \in \tilde{\mathcal{H}}$ should have smooth functional parts, consistent with Section \ref{sec: Regularization of PLS Components}.
-Consequently, $\delta^{[l]}$ is obtained by minimizing a penalized least squares criterion, where the functional part is penalized by the integrated squared second derivative defined in \eqref{def:roughness_penalty}:
+%To ensure the stability of the entire PLS estimation procedure, the estimated regression coefficient $\hat{\delta}^{[l]} = (\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} ) \in \tilde{\mathcal{H}}$ should have smooth functional parts, consistent with Section \ref{sec: Regularization of PLS Components}.
+ Consequently, $\delta^{[l]}$ is obtained by minimizing a %penalized 
+ least squares criterion:%, where the functional part is penalized by the integrated squared second derivative defined in \eqref{def:roughness_penalty}:
+ \begin{equation}\label{def:argmin_pensse}
+ 	\hat{\delta}^{[l]} := \arg \min_{\delta \in \tilde{\mathcal{H}}} \sum_{i=1}^n 
+ 	\| \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta\|_{\mathcal{H}}^2.
+ \end{equation}
+ \begin{comment}
 \begin{equation}\label{def:argmin_pensse}
@@
 where $\tau>0$ is a  smoothing parameter controlling the trade-off between fit accuracy and functional regression coefficient smoothness.
+\end{comment}
 The following proposition shows that the solution of the problem \ref{def:argmin_pensse} can be obtained by solving linear equations.
@@
 		=
-		\bigl(
-		\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2
-		B
-		+
-		\tau
-		B^{\prime \prime}
-		\bigr)^{-1}
-		B
-		(\Theta_j^{[l]})^\top
+		\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
+		\Theta_j^{[l] \top}
 		\hat{\boldsymbol{\rho}}^{[l]}
@@
 	 	=
-	 	(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}^{[l]}.
+	\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
+		\mathbf{Z}^{[l] \top}  \hat{\boldsymbol{\rho}}^{[l]}.
 	 \end{equation*}
@@
 Proof of Lemma \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
-
+\jongmin{proof needs to be revised}
 The $(l+1)$-th iteration's residualized predictor is then computed as:
@@
 The criterion $\operatorname{PENSSE}( \delta)$ can be decomposed as follows:
-
+\begin{equation}\label{def:pensse}
+	\operatorname{PENSSE}( \delta)
+	:=
+	\sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta,
+	\,
+	\widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta
+	\rangle_{\mathcal{H}}
+	+
+	\tau
+	\sum_{j=1}^K\operatorname{PEN}(\delta_j).
+\end{equation}
 \begin{align*}
@@
 	=
-	2\boldsymbol{\chi} ,
+	2(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})\boldsymbol{\chi} ,
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	+
-	2\hat{\boldsymbol{\chi} }
+	2 (\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) \hat{\boldsymbol{\chi} }
 	=
@@
 	\hat{\boldsymbol{\chi} }
-	=\mathbf{Z}^\top  \hat{\boldsymbol{\rho}}.
+	=
+	\frac{1}{(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})}
+	\mathbf{Z}^\top  \hat{\boldsymbol{\rho}}.
 \end{equation*}
@@
 \end{equation*}
-Without loss of generality, we show that the $i$th entry of $\Theta^{[l_1] }
+From the construction in \eqref{def:full_theta}, \eqref{def:theta} and \eqref{def:gram_block}, the
+ $i$th entry of $\Theta^{[l_1] }
 \mathbb{B}
-\hat{\boldsymbol{\xi}}_{l_2}$ is 0.
-From the construction in \eqref{def:full_theta}, \eqref{def:theta} and \eqref{def:gram_block}, the $i$-th entry is
+\hat{\boldsymbol{\xi}}_{l_2}$ 
+is
 \begin{align*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\\	&=
+\\	&\overset{(i)}{=}
 \langle
@@
 \hat{\xi}^{[l_2]}
-\rangle_{\mathcal{H}},
+\rangle_{\mathcal{H}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\	&\overset{(ii)}{=}
+\langle
+\widetilde{W}_i^{[l_1-1]}  , 
+\hat{\xi}^{[l_2]}
+\rangle_{\mathcal{H}}
+-
+\widehat{{\rho}}_i^{[l_1-1]}
+\langle
+   \widehat{\delta}^{[l_1-1]}, 
+\hat{\xi}^{[l_2]}
+\rangle_{\mathcal{H}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&\overset{(iii)}{=}
+\langle
+\widetilde{W}_i^{[l_1-1]}  , 
+\hat{\xi}^{[l_2]}
+\rangle_{\mathcal{H}}
+-
+\frac{\widehat{{\rho}}_i^{[l_1-1]}}{\| \widehat{\boldsymbol{\rho}}^{[l_1-1]} \|_2^2}
+\widehat{\boldsymbol{\rho}}^{[l_1-1] \top}
+(
+\sum_{k=1}^K {\Theta}_{k}^{[l_1-1]} 
+B \boldsymbol{\gamma}_k^{[l_2]}
++
+Z^{[l_1-1]} 
+\boldsymbol{\zeta}^{[l_2]}
+)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{align*}
-where the last equality uses the computation of the $i$th entry in \eqref{score_inner_product_all_n}.
-
-We can express the $l_1$-th residualized hybrid predictor in terms of its previous $(l_1-1)$-th version:
-\begin{equation*}
+where 
+step $(i)$ uses the computation of the $i$th entry in \eqref{score_inner_product_all_n},
+step $(ii)$ uses $
 	\widetilde{W}_i^{[l_1]}= \widetilde{W}_i^{[l_1-1]} - \widehat{{\rho}}_i^{[l_1-1]} \widehat{\delta}^{[l_1-1]}
-\end{equation*}
+$
+ and step $(iii)$ uses 
+ the closed-form formula of $\widehat{\delta}^{[l_1-1]}$ given by Lemma \ref{proposition:closed_form_orthgonalization}.
+	Therefore, we have
+\begin{equation*}
+\Theta^{[l_1] }
+\mathbb{B}
+\hat{\boldsymbol{\xi}}_{l_2}
+=
+\langle
+\widetilde{W}^{[l_1-1]}  , 
+\hat{\xi}^{[l_2]}
+\rangle_{\mathcal{H}}
+-
+\frac{1}{\| \widehat{\boldsymbol{\rho}}^{[l_1-1]} \|_2^2}
+\widehat{\boldsymbol{\rho}}^{[l_1-1] \top}
+\langle
+\widetilde{W}^{[l_1-1]}  , 
+\hat{\xi}^{[l_2]}
+\rangle_{\mathcal{H}}
+\widehat{\boldsymbol{\rho}}^{[l_1-1]}
+\end{equation*}
+	\begin{equation*}
+	\hat{\boldsymbol{\pi}}_j^{[l]}
+	=
+	\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
+	\Theta_j^{[l] \top}
+	\hat{\boldsymbol{\rho}}^{[l]}
+	,
+	~
+	j = 1, \ldots, K,
+\end{equation*}
+and scalar parts given by:
+\begin{equation*}
+	\hat{\boldsymbol{\chi} }^{[l]}
+	=
+	(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}^{[l]}.
+\end{equation*}
+
 \end{proof}
@@
 \end{align*}
-
-	Let us denote
-$
-\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top.
-%\quad\text{and} \quad		\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
-$
-The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
-$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients
-\begin{equation*}
-	\hat{\boldsymbol{\pi}}_j^{[l]}
-	=
-	\bigl(
-	\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2
-	B
-	+
-	\tau
-	B^{\prime \prime}
-	\bigr)^{-1}
-	B
-	(\Theta_j^{[l]})^\top
-	\hat{\boldsymbol{\rho}}^{[l]}
-	,
-	~
-	j = 1, \ldots, K,
-\end{equation*}
-and scalar parts given by:
-\begin{equation*}
-	\hat{\boldsymbol{\chi} }^{[l]}
-	=
-	(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}^{[l]}.
-\end{equation*}
 

### 2025-08-12 manuscript/main.tex
lemma 4.4 revised, no regularization

@@
 	\begin{frontmatter}
-\title{ Partial Least Squares Regression with Multiple Functional and Scalar Predictors}
+		\title{ Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors}
 		%\title{A sample article title with some additional note\thanksref{t1}}
-\runtitle{A sample running head title}
+		\runtitle{Hybrid Partial Least Squares}
 		%\thankstext{T1}{A sample additional note to the title.}
@@
 	Since   $\widetilde{W}_i^{[l]}$ are assumed to have a sample mean of zero, these PLS scores will also have a sample mean of zero.
-Using these PLS scores as scalar predictor observations, the $(l+1)$-th iteration's residualized response is computed as:
-\begin{equation}\label{algorithm_step:residualization_response}
-	Y_i^{[l+1]} := Y_i^{[l]} - 
-	\frac{
-		( \mathbf{y}^{[l]} )^\top  \hat{\boldsymbol{\rho}}^{[l]}
-	}{
-		( \hat{\boldsymbol{\rho}}^{[l]} )^\top  \hat{\boldsymbol{\rho}}^{[l]}
-	}
-	\widehat{\rho}_{il},
-\end{equation}
-which is equivalent to using the least squares estimate from regressing $Y_i^{[l]}$ on $\widehat{\rho}_{il}$,
-a procedure identical to that found in the naive PLS algorithm (Section \ref{sec: Naive PLS Algorithm}). 
-Since $Y_i^{[l]}$ are assumed to have a sample mean of zero, these residuals $Y_i^{[l+1]}$   also have a sample mean of zero.
-
-For predictor residualization, we fit a hybrid-on-scalar regression model where the predictor is the PLS score for each observation.
-Specifically, we fit $\widetilde{W}^{[l]}_i = \hat{\rho}^{[l]}_i\, \delta^{[l]} + E_i^{[l]}$, and then take the residuals as the predictor for the next iteration.
-Here, $\delta^{[l]}$ and $E_i^{[l]}$ are the regression coefficient and error terms, respectively.
-Performing this pointwisely, as in Section \ref{sec: Naive PLS Algorithm}, is highly inefficient and potentially infeasible for dense or irregular functional data.
-Moreover, the results may lack smoothness, introducing instability that propagates to subsequent results and compromises the entire algorithm.
-Therefore, we employ a basis expansion approach to fit the entire hybrid object in one step.
-We assume both $\delta^{[l]}$ and $E_i^{[l]}$ are elements of $\tilde{\mathcal{H}}$, as defined in \eqref{def:truncated_hilbert_space}.
-%To ensure the stability of the entire PLS estimation procedure, the estimated regression coefficient $\hat{\delta}^{[l]} = (\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} ) \in \tilde{\mathcal{H}}$ should have smooth functional parts, consistent with Section \ref{sec: Regularization of PLS Components}.
- Consequently, $\delta^{[l]}$ is obtained by minimizing a %penalized 
- least squares criterion:%, where the functional part is penalized by the integrated squared second derivative defined in \eqref{def:roughness_penalty}:
+	To obtain the $(l+1)$-th  iteration's responses and hybrid predictors, we regress the $(l)$-th iteration's responses and hybrid predictors on  
+ these PLS scores by least squares and then residualize. 
+	Specifically,
+the $(l+1)$-th predictor is computed as a hybrid-on-scalar linear regression residual.
+In the same spirit as the PLS component direction estimation step,
+rather than treating the hybrid object as a long vector of concatenated function evaluations at time points and scalar vectors,
+we employ a basis expansion approach to fit the entire hybrid object in one step.
+Therefore, our method is computationally efficient, applicable for dense or irregular functional data, and keeps the residual smooth, as it enforces the regression coefficient, $\delta^{[l]}$, as an element of $\tilde{\mathcal{H}}$ as defined in Equation \eqref{def:truncated_hilbert_space}.
+	Consequently, $\delta^{[l]}$ is obtained by minimizing a  
+	least squares criterion:
 	\begin{equation}\label{def:argmin_pensse}
@@
 	\end{equation}
- \begin{comment}
-\begin{equation}\label{def:argmin_pensse}
-	\hat{\delta}^{[l]} := \arg \min_{\delta \in \tilde{\mathcal{H}}} \operatorname{PENSSE}( \delta),
-\end{equation}
-where
-\begin{equation}\label{def:pensse}
-	\operatorname{PENSSE}( \delta)
-	:=
-	\sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta,
-	\,
-	\widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta
-	\rangle_{\mathcal{H}}
-	+
-	\tau
-	\sum_{j=1}^K\operatorname{PEN}(\delta_j).
-\end{equation}
-where $\tau>0$ is a  smoothing parameter controlling the trade-off between fit accuracy and functional regression coefficient smoothness.
-\end{comment}
-The following proposition shows that the solution of the problem \ref{def:argmin_pensse} can be obtained by solving linear equations.
-
+  On the other hand, the $(l+1)$-th response   is computed as a scalar-on-scalar linear regression residual. 
+ The following proposition demonstrates that this residualization step can be performed simply, analogous to scalar PLS.
 	\begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
@@
 		$
-	The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
-	$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients
-	\begin{equation*}
-		\hat{\boldsymbol{\pi}}_j^{[l]}
-		=
-		\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
-		\Theta_j^{[l] \top}
-		\hat{\boldsymbol{\rho}}^{[l]}
-		,
-		~
-		j = 1, \ldots, K,
-	\end{equation*}
-	  and scalar parts given by:
-	 \begin{equation*}
-	 	\hat{\boldsymbol{\chi} }^{[l]}
-	 	=
-	\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
-		\mathbf{Z}^{[l] \top}  \hat{\boldsymbol{\rho}}^{[l]}.
-	 \end{equation*}
+	The $(l+1)$-th iteration's  predictors and responses are   computed as:
+\begin{equation}\label{algorithm_step:residualization_predictor}
+	\widetilde{W}_i^{[l+1]} 
+	= 
+	\widetilde{W}_i^{[l]}  - 
+	\frac{\widehat{\rho}_{il}}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
+	\sum_{i=1}^n 
+	\widehat{\rho}_{il}
+	\widetilde{W}_i^{[l]},
+	%%%%%%%%%%% 
+	\quad 
+	Y_i^{[l+1]} := Y_i^{[l]} - 
+	\frac{
+		\mathbf{y}^{[l] \top }  \hat{\boldsymbol{\rho}}^{[l]}
+	}{
+		\| \hat{\boldsymbol{\rho}}^{[l]} \|_2^2
+	}
+	\widehat{\rho}_{il}.
+\end{equation} 	
 	\end{lemma}
@@
 	\jongmin{proof needs to be revised}
-The $(l+1)$-th iteration's residualized predictor is then computed as:
-\begin{equation}\label{algorithm_step:residualization_predictor}
-	\widetilde{W}_i^{[l+1]} 
-	= 
-	\widetilde{W}_i^{[l]}  - \widehat{\rho}_{il}  \widehat{ {\delta}}_{l}.
-	%%%%%%%%%%%
-\end{equation}
-Since $\widetilde{W}_i^{[l]} $ are assumed to have a sample mean of zero, these residuals $\widetilde{W}_i^{[l+1]}$   also have a sample mean of zero.
+Since $\widetilde{W}_i^{[l]}$ and $Y_i^{[l]}$ are assumed to have a sample mean of zero, their respective residuals, $\widetilde{W}_i^{[l+1]}$ and $Y_i^{[l+1]}$, also maintain a zero sample mean.
 
@@
 
-\bibliographystyle{apalike}
-\bibliography{Reference}
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	%% Support information, if any,             %%
+	%% should be provided in the                %%
+	%% Acknowledgements section.                %%
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\begin{acks}[Acknowledgments]
+		The authors would like to thank the anonymous referees, an Associate
+		Editor and the Editor for their constructive comments that improved the
+		quality of this paper.
+	\end{acks}
+
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	%% Funding information, if any,             %%
+	%% should be provided in the                %%
+	%% funding section.                         %%
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\begin{funding}
+		The first author was supported by NSF Grant DMS-??-??????.
+
+		The second author was supported in part by NIH Grant ???????????.
+	\end{funding}
+
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	%% Supplementary Material, including data   %%
+	%% sets and code, should be provided in     %%
+	%% {supplement} environment with title      %%
+	%% and short description. It cannot be      %%
+	%% available exclusively as external link.  %%
+	%% All Supplementary Material must be       %%
+	%% available to the reader on Project       %%
+	%% Euclid with the published article.       %%
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\begin{supplement}
+		\stitle{Title of Supplement A}
+		\sdescription{Short description of Supplement A.}
+	\end{supplement}
+	\begin{supplement}
+		\stitle{Title of Supplement B}
+		\sdescription{Short description of Supplement B.}
+	\end{supplement}
+
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	%%                  The Bibliography                       %%
+	%%                                                         %%
+	%%  imsart-nameyear.bst  will be used to                   %%
+	%%  create a .BBL file for submission.                     %%
+	%%                                                         %%
+	%%  Note that the displayed Bibliography will not          %%
+	%%  necessarily be rendered by Latex exactly as specified  %%
+	%%  in the online Instructions for Authors.                %%
+	%%                                                         %%
+	%%  MR numbers will be added by VTeX.                      %%
+	%%                                                         %%
+	%%  Use \cite{...} to cite references in text.             %%
+	%%                                                         %%
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+	%% if your bibliography is in bibtex format, uncomment commands:
+	\bibliographystyle{imsart-nameyear} % Style BST file
+	\bibliography{bibliography.bib}       % Bibliography file (usually '*.bib')
 
@@
 	\end{equation*}
+		The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
+	$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients
+	\begin{equation*}
+		\hat{\boldsymbol{\pi}}_j^{[l]}
+		=
+		\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
+		\Theta_j^{[l] \top}
+		\hat{\boldsymbol{\rho}}^{[l]}
+		,
+		~
+		j = 1, \ldots, K,
+	\end{equation*}
+	and scalar parts given by:
+	\begin{equation*}
+		\hat{\boldsymbol{\chi} }^{[l]}
+		=
+		\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
+		\mathbf{Z}^{[l] \top}  \hat{\boldsymbol{\rho}}^{[l]}.
+	\end{equation*}
 	This completes the proof of Lemma \ref{proposition:closed_form_orthgonalization}.
@@
 		step $(ii)$ uses the fact that $\hat{\boldsymbol{\xi}}_{l_1}$ is a generalized eigenvector ($\kappa_{l_1}$ denotes the corresponding generalized eigenvalue), as presented in Proposition \ref{proposition:eigen_regul},
-and step $(iii)$ uses the definition of $V$ matrix given in \eqref{def:V_matrix},
-and $c$ represents a scalar.
+		and step $(iii)$ uses the definition of $V$ matrix given in \eqref{def:V_matrix}.
+Here, $c$ represents a scalar that condenses all multiplicative terms preceding $\mathbf{y}^\top$.
 
 		Our next task is to show that 
-\begin{equation*}
+		$
 		\Theta^{[l_1] }
@@
 		\hat{\boldsymbol{\xi}}_{l_2} = \mathbf{0} \in \mathbb{R}^n.
-\end{equation*}
+		$
 		From the construction in \eqref{def:full_theta}, \eqref{def:theta} and \eqref{def:gram_block}, the
@@
 			%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\\	&\overset{(i)}{=}
+			\\	&=
 			\langle
@@
 			\hat{\xi}^{[l_2]}
-\rangle_{\mathcal{H}}
+			\rangle_{\mathcal{H}},
+		\end{align*}
+where the last equality uses the computation of the $i$th entry in \eqref{score_inner_product_all_n}. To expand the last quantity, we use a recursive relationship derived as follows.
+\begin{align*}
+	\widetilde{W}_i^{[l_1]} &= \widetilde{W}_i^{[l_1-1]} - \widehat{{\rho}}_i^{[l_1-1]} \widehat{\delta}^{[l_1-1]}
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\\	&\overset{(ii)}{=}
-\langle
-\widetilde{W}_i^{[l_1-1]}  , 
-\hat{\xi}^{[l_2]}
-\rangle_{\mathcal{H}}
+	\\&\overset{(i)}{=}
+	\widetilde{W}_i^{[l_1-1]}
 	-
-\widehat{{\rho}}_i^{[l_1-1]}
-\langle
-   \widehat{\delta}^{[l_1-1]}, 
-\hat{\xi}^{[l_2]}
-\rangle_{\mathcal{H}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\\&\overset{(iii)}{=}
+	\frac{\widehat{{\rho}}_i^{[l_1-1]}}{\| \widehat{\boldsymbol{\rho}}^{[l_1-1]} \|_2^2}
+	\bigl(
+	\sum_{k=1}^K {\Theta}_{k}^{[l_1-1]} 
+	+
+	Z^{[l_1-1]} 
+	\bigr)
+	\widehat{\boldsymbol{\rho}}^{[l_1-1]}
+	\\&=
 	\langle
@@
 	\widehat{\boldsymbol{\rho}}^{[l_1-1] \top}
-(
-\sum_{k=1}^K {\Theta}_{k}^{[l_1-1]} 
-B \boldsymbol{\gamma}_k^{[l_2]}
-+
-Z^{[l_1-1]} 
-\boldsymbol{\zeta}^{[l_2]}
-)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\langle
+	\widetilde{W}^{[l_1-1]}  , 
+	\hat{\xi}^{[l_2]}
+	\rangle_{\mathcal{H}}
 \end{align*}
-where 
-step $(i)$ uses the computation of the $i$th entry in \eqref{score_inner_product_all_n},
-step $(ii)$ uses $
-	\widetilde{W}_i^{[l_1]}= \widetilde{W}_i^{[l_1-1]} - \widehat{{\rho}}_i^{[l_1-1]} \widehat{\delta}^{[l_1-1]}
-$
+Using the regression model  we used for residualization,
 		and step $(iii)$ uses 
- the closed-form formula of $\widehat{\delta}^{[l_1-1]}$ given by Lemma \ref{proposition:closed_form_orthgonalization}.
+		the closed-form formula of $\widehat{\delta}^{[l_1-1]}$ given by Lemma \ref{proposition:closed_form_orthgonalization},
+		and we abuse the notation as
+		$\langle
+		\widetilde{W}_1^{[l_1-1]}  , 
+		\hat{\xi}^{[l_2]}
+		\rangle_{\mathcal{H}}:=
+		\bigl(
+		\langle
+		\widetilde{W}_n^{[l_1-1]}  , 
+		\hat{\xi}^{[l_2]}
+		\rangle_{\mathcal{H}},
+		\ldots,
+		\langle
+		\widetilde{W}^{[l_1-1]}  , 
+		\hat{\xi}^{[l_2]}
+		\rangle_{\mathcal{H}}
+		\bigr)^\top \in \mathbb{R}^n.
+		$
+
 		Therefore, we have
@@
 	\section{Simulations} \label{Simulations}
-\section{Introduction}
-
-This template helps you to create a properly formatted \LaTeXe\ manuscript.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% `\ ' is used here because TeX ignores    %%
-%% spaces after text commands.              %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Prepare your paper in the same style as used in this sample .pdf file.
-Try to avoid excessive use of italics and bold face.
-Please do not use any \LaTeXe\ or \TeX\ commands that affect the layout
-or formatting of your document (i.e., commands like \verb|\textheight|,
-\verb|\textwidth|, etc.).
-
-\section{Section headings}
-Here are some sub-sections:
-\subsection{A sub-section}
-Regular text.
-\subsubsection{A sub-sub-section}
-Regular text.
-
-\section{Text}
-\subsection{Lists}
-
-The following is an example of an \emph{itemized} list,
-two levels deep.
-\begin{itemize}
-\item
-This is the first item of an itemized list.  Each item
-in the list is marked with a ``tick.''  The document
-style determines what kind of tick mark is used.
-\item
-This is the second item of the list.  It contains another
-list nested inside it.
-\begin{itemize}
-\item This is the first item of an itemized list that
-is nested within the itemized list.
-\item This is the second item of the inner list.  \LaTeX\
-allows you to nest lists deeper than you really should.
-\end{itemize}
-This is the rest of the second item of the outer list.
-\item
-This is the third item of the list.
-\end{itemize}
-
-The following is an example of an \emph{enumerated} list of one level.
-
-\begin{longlist}
-\item This is the first item of an enumerated list.
-\item This is the second item of an enumerated list.
-\end{longlist}
-
-The following is an example of an \emph{enumerated} list, two levels deep.
-\begin{longlist}
-\item[1.]
-This is the first item of an enumerated list.  Each item
-in the list is marked with a ``tick.''  The document
-style determines what kind of tick mark is used.
-\item[2.]
-This is the second item of the list.  It contains another
-list nested inside of it.
-\begin{longlist}
-\item
-This is the first item of an enumerated list that
-is nested within.  
-\item
-This is the second item of the inner list.  \LaTeX\
-allows you to nest lists deeper than you really should.
-\end{longlist}
-This is the rest of the second item of the outer list.
-\item[3.]
-This is the third item of the list.
-\end{longlist}
-
-\subsection{Punctuation}
-Dashes come in three sizes: a hyphen, an intra-word dash like ``$U$-statistics'' or ``the time-homogeneous model'';
-a medium dash (also called an ``en-dash'') for number ranges or between two equal entities like ``1--2'' or ``Cauchy--Schwarz inequality'';
-and a punctuation dash (also called an ``em-dash'') in place of a comma, semicolon,
-colon or parentheses---like this.
-
-Generating an ellipsis \ldots\ with the right spacing
-around the periods requires a special command.
-
-\subsection{Citation}
-
-%Simple author and year cite: \cite{r1}.
-%Multiple bibliography items cite: \cite{r1,r2}.
-%Author only cite: \citeauthor{r3}.
-%Year only cite: \citeyear{r4}.
-
-\section{Fonts}
-Please use text fonts in text mode, e.g.:
-\begin{itemize}
-\item[]\textrm{Roman}
-\item[]\textit{Italic}
-\item[]\textbf{Bold}
-\item[]\textsc{Small Caps}
-\item[]\textsf{Sans serif}
-\item[]\texttt{Typewriter}
-\end{itemize}
-Please use mathematical fonts in mathematical mode, e.g.:
-\begin{itemize}
-\item[] $\mathrm{ABCabc123}$
-\item[] $\mathit{ABCabc123}$
-\item[] $\mathbf{ABCabc123}$
-\item[] $\boldsymbol{ABCabc123\alpha\beta\gamma}$
-\item[] $\mathcal{ABC}$
-\item[] $\mathbb{ABC}$
-\item[] $\mathsf{ABCabc123}$
-\item[] $\mathtt{ABCabc123}$
-\item[] $\mathfrak{ABCabc123}$
-\end{itemize}
-Note that \verb|\mathcal, \mathbb| belongs to capital letters-only font typefaces.
-
-\section{Notes}
-Footnotes\footnote{This is an example of a footnote.}
-pose no problem.\footnote{Note that footnote number is after punctuation.}
-
-\section{Quotations}
-
-Text is displayed by indenting it from the left margin. There are short quotations
-\begin{quote}
-This is a short quotation.  It consists of a
-single paragraph of text.  There is no paragraph
-indentation.
-\end{quote}
-and longer ones.
-\begin{quotation}
-This is a longer quotation.  It consists of two paragraphs
-of text.  The beginning of each paragraph is indicated
-by an extra indentation.
-
-This is the second paragraph of the quotation.  It is just
-as dull as the first paragraph.
-\end{quotation}
-
-\section{Environments}
-
-\subsection{Examples for \emph{\texttt{plain}}-style environments}
-\begin{axiom}\label{ax1}
-This is the body of Axiom \ref{ax1}.
-\end{axiom}
-
-\begin{proof}
-This is the body of the proof of the axiom above.
-\end{proof}
-
-\begin{claim}\label{cl1}
-This is the body of Claim \ref{cl1}. Claim \ref{cl1} is numbered after
-Axiom \ref{ax1} because we used \verb|[axiom]| in \verb|\newtheorem|.
-\end{claim}
-
-\begin{theorem}\label{th1}
-This is the body of Theorem \ref{th1}. Theorem \ref{th1} numbering is
-dependent on section because we used \verb|[section]| after \verb|\newtheorem|.
-\end{theorem}
-
-\begin{theorem}[Title of the theorem]\label{th2}
-This is the body of Theorem \ref{th2}. Theorem \ref{th2} has additional title.
-\end{theorem}
-
-\begin{lemma}\label{le1}
-This is the body of Lemma \ref{le1}. Lemma \ref{le1} is numbered after
-Theorem \ref{th2} because we used \verb|[theorem]| in \verb|\newtheorem|.
-\end{lemma}
-
-\begin{proof}[Proof of Lemma \ref{le1}]
-This is the body of the proof of Lemma \ref{le1}.
-\end{proof}
-
-\subsection{Examples for \emph{\texttt{definition}}-style environments}
-\begin{definition}\label{de1}
-This is the body of Definition \ref{de1}. Definition \ref{de1} is numbered after
-Lemma \ref{le1} because we used \verb|[theorem]| in \verb|\newtheorem|.
-\end{definition}
-
-\begin{example}
-This is the body of the example. Example is unnumbered because we used \verb|\newtheorem*|
-instead of \verb|\newtheorem|.
-\end{example}
-
-\begin{fact}
-This is the body of the fact. Fact is unnumbered because we used \verb|\newtheorem*|
-instead of \verb|\newtheorem|.
-\end{fact}
-
-\section{Tables and figures}
-Cross-references to labeled tables: As you can see in Table~\ref{sphericcase}
-and also in Table~\ref{parset}.
-
-\begin{table*}
-\caption{The spherical case ($I_1=0$, $I_2=0$)}
-\label{sphericcase}
-\begin{tabular}{@{}lrrrrc@{}}
-\hline
-Equil. \\
-points & \multicolumn{1}{c}{$x$}
-& \multicolumn{1}{c}{$y$} & \multicolumn{1}{c}{$z$}
-& \multicolumn{1}{c}{$C$} & S \\
-\hline
-$L_1$    & $-$2.485252241 & 0.000000000  & 0.017100631  & 8.230711648  & U \\
-$L_2$    & 0.000000000  & 0.000000000  & 3.068883732  & 0.000000000  & S \\
-$L_3$    & 0.009869059  & 0.000000000  & 4.756386544  & $-$0.000057922 & U \\
-$L_4$    & 0.210589855  & 0.000000000  & $-$0.007021459 & 9.440510897  & U \\
-$L_5$    & 0.455926604  & 0.000000000  & $-$0.212446624 & 7.586126667  & U \\
-$L_6$    & 0.667031314  & 0.000000000  & 0.529879957  & 3.497660052  & U \\
-$L_7$    & 2.164386674  & 0.000000000  & $-$0.169308438 & 6.866562449  & U \\
-$L_8$    & 0.560414471  & 0.421735658  & $-$0.093667445 & 9.241525367  & U \\
-$L_9$    & 0.560414471  & $-$0.421735658 & $-$0.093667445 & 9.241525367  & U \\
-$L_{10}$ & 1.472523232  & 1.393484549  & $-$0.083801333 & 6.733436505  & U \\
-$L_{11}$ & 1.472523232  & $-$1.393484549 & $-$0.083801333 & 6.733436505  & U \\
-\hline
-\end{tabular}
-\end{table*}
-
-\begin{table}
-\caption{Sample posterior estimates for each model}
-\label{parset}
-%
-\begin{tabular}{@{}lcrcrrr@{}}
-\hline
-&& & &\multicolumn{3}{c}{Quantile} \\
-\cline{5-7}
-Model &Parameter &
-\multicolumn{1}{c}{Mean} &
-Std. dev.&
-\multicolumn{1}{c}{2.5\%} &
-\multicolumn{1}{c}{50\%}&
-\multicolumn{1}{c@{}}{97.5\%} \\
-\hline
-{Model 0} & $\beta_0$ & $-$12.29 & 2.29 & $-$18.04 & $-$11.99 & $-$8.56 \\
-          & $\beta_1$  & 0.10   & 0.07 & $-$0.05  & 0.10   & 0.26  \\
-          & $\beta_2$   & 0.01   & 0.09 & $-$0.22  & 0.02   & 0.16  \\[6pt]
-{Model 1} & $\beta_0$   & $-$4.58  & 3.04 & $-$11.00 & $-$4.44  & 1.06  \\
-          & $\beta_1$   & 0.79   & 0.21 & 0.38   & 0.78   & 1.20  \\
-          & $\beta_2$   & $-$0.28  & 0.10 & $-$0.48  & $-$0.28  & $-$0.07 \\[6pt]
-{Model 2} & $\beta_0$   & $-$11.85 & 2.24 & $-$17.34 & $-$11.60 & $-$7.85 \\
-          & $\beta_1$   & 0.73   & 0.21 & 0.32   & 0.73   & 1.16  \\
-          & $\beta_2$   & $-$0.60  & 0.14 & $-$0.88  & $-$0.60  & $-$0.34 \\
-          & $\beta_3$   & 0.22   & 0.17 & $-$0.10  & 0.22   & 0.55  \\
-\hline
-\end{tabular}
-%
-\end{table}
-
-\begin{figure}
-\includegraphics{figure1}
-\caption{Pathway of the penicillin G biosynthesis.}
-\label{penG}
-\end{figure}
-
-Sample of cross-reference to figure.
-Figure~\ref{penG} shows that it is not easy to get something on paper.
-
-\section{Equations and the like}
-
-Two equations:
-\begin{equation}
-    C_{s}  =  K_{M} \frac{\mu/\mu_{x}}{1-\mu/\mu_{x}} \label{ccs}
-\end{equation}
-and
-\begin{equation}
-    G = \frac{P_{\mathrm{opt}} - P_{\mathrm{ref}}}{P_{\mathrm{ref}}}  100(\%).
-\end{equation}
-
-Equation arrays:
-\begin{eqnarray}
-  \frac{dS}{dt} & = & - \sigma X + s_{F} F,\\
-  \frac{dX}{dt} & = &   \mu    X,\\
-  \frac{dP}{dt} & = &   \pi    X - k_{h} P,\\
-  \frac{dV}{dt} & = &   F.
-\end{eqnarray}
-One long equation:
-\begin{eqnarray}
- \mu_{\text{normal}} & = & \mu_{x} \frac{C_{s}}{K_{x}C_{x}+C_{s}}  \nonumber\\
-                     & = & \mu_{\text{normal}} - Y_{x/s}\bigl(1-H(C_{s})\bigr)(m_{s}+\pi /Y_{p/s})\\
-                     & = & \mu_{\text{normal}}/Y_{x/s}+ H(C_{s}) (m_{s}+ \pi /Y_{p/s}).\nonumber
-\end{eqnarray}
-
-\section*{APPENDICES MUST BE MOVED TO A SUPPLEMENT FILE}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Support information, if any,             %%
-%% should be provided in the                %%
-%% Acknowledgements section.                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{acks}[Acknowledgments]
-The authors would like to thank the anonymous referees, an Associate
-Editor and the Editor for their constructive comments that improved the
-quality of this paper.
-\end{acks}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Funding information, if any,             %%
-%% should be provided in the                %%
-%% funding section.                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{funding}
-The first author was supported by NSF Grant DMS-??-??????.
-
-The second author was supported in part by NIH Grant ???????????.
-\end{funding}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Supplementary Material, including data   %%
-%% sets and code, should be provided in     %%
-%% {supplement} environment with title      %%
-%% and short description. It cannot be      %%
-%% available exclusively as external link.  %%
-%% All Supplementary Material must be       %%
-%% available to the reader on Project       %%
-%% Euclid with the published article.       %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{supplement}
-\stitle{Title of Supplement A}
-\sdescription{Short description of Supplement A.}
-\end{supplement}
-\begin{supplement}
-\stitle{Title of Supplement B}
-\sdescription{Short description of Supplement B.}
-\end{supplement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                  The Bibliography                       %%
-%%                                                         %%
-%%  imsart-nameyear.bst  will be used to                   %%
-%%  create a .BBL file for submission.                     %%
-%%                                                         %%
-%%  Note that the displayed Bibliography will not          %%
-%%  necessarily be rendered by Latex exactly as specified  %%
-%%  in the online Instructions for Authors.                %%
-%%                                                         %%
-%%  MR numbers will be added by VTeX.                      %%
-%%                                                         %%
-%%  Use \cite{...} to cite references in text.             %%
-%%                                                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% if your bibliography is in bibtex format, uncomment commands:
-\bibliographystyle{imsart-nameyear} % Style BST file
-\bibliography{bibliography}       % Bibliography file (usually '*.bib')
 

### 2025-08-12 manuscript/main.tex
W recursive

@@
 	\widetilde{W}_i^{[l+1]} 
-	= 
+	:= 
 	\widetilde{W}_i^{[l]}  - 
@@
 		\end{align*}
-where the last equality uses the computation of the $i$th entry in \eqref{score_inner_product_all_n}. To expand the last quantity, we use a recursive relationship derived as follows.
+where the last equality uses the computation of the $i$th entry in \eqref{score_inner_product_all_n}.
+To expand the last quantity, we use a recursive relationship derived as follows.
+Recall from Lemma  \ref{proposition:closed_form_orthgonalization} that we have
+	\begin{equation}\label{algorithm_step:residualization_predictor:recall}
+	\widetilde{W}_i^{[l_1]} 
+	:= 
+	\widetilde{W}_i^{[l_1-1]}  - 
+	\frac{\widehat{\rho}_{i\,l_1-1}}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
+	\sum_{i=1}^n 
+	\widehat{\rho}_{i \,l_1-1}
+	\widetilde{W}_i^{[l_1-1]}.
+\end{equation} 	
+Let us denote, with some abuse of notation:
+\begin{equation*}
+	\widetilde{\boldsymbol{W}}^{[l_1]}  := 
+	\bigl(
+\widetilde{W}_1^{[l_1-1]}, \ldots, \widetilde{W}_n^{[l_1-1]}
+	\bigr)^\top \in \tilde{\mathcal{H}}^{\otimes n}.
+\end{equation*}
+Then using \eqref{algorithm_step:residualization_predictor:recall}, we have, with some abuse of notation,
+\begin{equation*}
+\widetilde{\boldsymbol{W}}^{[l_1]}  = 
+\widetilde{\boldsymbol{W}}^{[l_1-1]} - 
+\biggl(
+	\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
+	\hat{\boldsymbol{\rho}}^{[l_1-1] }
+	\hat{\boldsymbol{\rho}}^{[l_1-1] \top
+	} 
+	\biggr)
+		\widetilde{\boldsymbol{W}}^{[l_1-1]},
+\end{equation*}
+Clearly, the right-hand side represents a linear operator from $\tilde{\mathcal{H}}^{\otimes n}$ to $\tilde{\mathcal{H}}^{\otimes n}$, which we denote as $P^{[l_1-1]}$.
+	Thus, 
+	we have $\widetilde{\boldsymbol{W}}^{[l_1]}  = 
+	P^{[l_1-1]} \widetilde{\boldsymbol{W}}^{[l_1-1]}$.
+Using this relationship, we have
 	\begin{align*}
-	\widetilde{W}_i^{[l_1]} &= \widetilde{W}_i^{[l_1-1]} - \widehat{{\rho}}_i^{[l_1-1]} \widehat{\delta}^{[l_1-1]}
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	\\&\overset{(i)}{=}
-	\widetilde{W}_i^{[l_1-1]}
-	-
-	\frac{\widehat{{\rho}}_i^{[l_1-1]}}{\| \widehat{\boldsymbol{\rho}}^{[l_1-1]} \|_2^2}
-	\bigl(
-	\sum_{k=1}^K {\Theta}_{k}^{[l_1-1]} 
-	+
-	Z^{[l_1-1]} 
-	\bigr)
-	\widehat{\boldsymbol{\rho}}^{[l_1-1]}
-	\\&=
-	\langle
-	\widetilde{W}_i^{[l_1-1]}  , 
-	\hat{\xi}^{[l_2]}
-	\rangle_{\mathcal{H}}
-	-
-	\frac{\widehat{{\rho}}_i^{[l_1-1]}}{\| \widehat{\boldsymbol{\rho}}^{[l_1-1]} \|_2^2}
-	\widehat{\boldsymbol{\rho}}^{[l_1-1] \top}
-	\langle
-	\widetilde{W}^{[l_1-1]}  , 
-	\hat{\xi}^{[l_2]}
-	\rangle_{\mathcal{H}}
+		\widetilde{\boldsymbol{W}}^{[l_1]} &=P^{[l_1-1]} \widetilde{\boldsymbol{W}}^{[l_1-1]} \\
+		&=
+		P^{[l_1-1]} P^{[l_1-2]} \widetilde{\boldsymbol{W}}^{[l_1-2]}
+		  \\
+		&= P^{[l_1-1]} P^{[l_1-2]} \ldots P^{[l_2 + 1]}  P^{[l_2]} \widetilde{\boldsymbol{W}}^{[l_2]}
+		  \\
+&=P P^{[l_2]} \widetilde{\boldsymbol{W}}^{[l_2]},		
 	\end{align*}
-Using the regression model  we used for residualization,
-		and step $(iii)$ uses 
-		the closed-form formula of $\widehat{\delta}^{[l_1-1]}$ given by Lemma \ref{proposition:closed_form_orthgonalization},
-		and we abuse the notation as
-		$\langle
-		\widetilde{W}_1^{[l_1-1]}  , 
-		\hat{\xi}^{[l_2]}
-		\rangle_{\mathcal{H}}:=
-		\bigl(
-		\langle
-		\widetilde{W}_n^{[l_1-1]}  , 
-		\hat{\xi}^{[l_2]}
-		\rangle_{\mathcal{H}},
-		\ldots,
-		\langle
-		\widetilde{W}^{[l_1-1]}  , 
-		\hat{\xi}^{[l_2]}
-		\rangle_{\mathcal{H}}
-		\bigr)^\top \in \mathbb{R}^n.
-		$
-
-		Therefore, we have
-		\begin{equation*}
-			\Theta^{[l_1] }
-			\mathbb{B}
-			\hat{\boldsymbol{\xi}}_{l_2}
-			=
-			\langle
-			\widetilde{W}^{[l_1-1]}  , 
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathcal{H}}
-			-
-			\frac{1}{\| \widehat{\boldsymbol{\rho}}^{[l_1-1]} \|_2^2}
-			\widehat{\boldsymbol{\rho}}^{[l_1-1] \top}
-			\langle
-			\widetilde{W}^{[l_1-1]}  , 
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathcal{H}}
-			\widehat{\boldsymbol{\rho}}^{[l_1-1]}
-		\end{equation*}
-		\begin{equation*}
-			\hat{\boldsymbol{\pi}}_j^{[l]}
-			=
-			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
-			\Theta_j^{[l] \top}
-			\hat{\boldsymbol{\rho}}^{[l]}
-			,
-			~
-			j = 1, \ldots, K,
-		\end{equation*}
-		and scalar parts given by:
-		\begin{equation*}
-			\hat{\boldsymbol{\chi} }^{[l]}
-			=
-			(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}^{[l]}.
-		\end{equation*}
-
-	\end{proof}
-
-	which, after applying the finite-dimensional form (9), implies that
-	\begin{align*}
-		\widetilde{C}^{*[l]}B^*[\mathbf{t}] &=\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1}\widehat{\boldsymbol{\gamma}}^*_{l-1}B^*[\mathbf{t}] \\
-		&= \widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} J^\ast \left(\widehat{\boldsymbol{\rho}}_{i,l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1} J^\ast \right)^{-1} B^*[\mathbf{t}] \\
-		& =\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] -  \left(\frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \widetilde{C}^{*[l-1]} B^*[\mathbf{t}] \\
-		&= \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \widetilde{C}^{*[l-1]} B^*[\mathbf{t}].
-	\end{align*}
-
-	Thus, we have
-	\begin{align*}
-		\widetilde{W}^{[l]}[\mathbf{t}] &= \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \widetilde{W}^{[l-1]}[\mathbf{t}] \\
-		&= \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{l-2} \widehat{\boldsymbol{\rho}}_{l-2}^\top}{\widehat{\boldsymbol{\rho}}_{l-2}^\top \widehat{\boldsymbol{\rho}}_{l-2}} \right) \widetilde{W}^{[l-2]}[\mathbf{t}] \\
-		&= P \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right)\widetilde{W}^{[j]}[\mathbf{t}]
-	\end{align*}
-	where $P$ is an $n \times n$ matrix defined as
-	\begin{equation*}
-		P = \prod \limits_{h=j+1}^{l-1} \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{h} \widehat{\boldsymbol{\rho}}_{h}^\top}{\widehat{\boldsymbol{\rho}}_{h}^\top \widehat{\boldsymbol{\rho}}_{h}} \right)
-	\end{equation*}
+	where $P = P^{[l_1-1]} P^{[l_1-2]} \ldots P^{[l_2 + 1]} $ is a linear operator from  $\tilde{\mathcal{H}}^{\otimes n}$.
 	Then for $j < l$,
@@
 
+	\end{proof}
 	\section{Proof of Proposition \ref{proposition: orthnormality of PLS scores}}\label{section:proof:proposition: orthnormality of PLS scores}

### 2025-08-13 manuscript/main.tex
score orthogonal proposition revised

@@
 	Based on this inner product, the following proposition states that the PLS component directions estimated from Proposition  \ref{proposition:eigen_regul} are orthonormal.
-	\begin{proposition}[Orthonormality of regularized PLS component directions]\label{proposition: modified orthnormality of PLS components}
+	\begin{proposition}[Orthonormality of estimated PLS component directions]\label{proposition: modified orthnormality of PLS components}
 		The PLS component directions $\widehat{\xi}_1, \widehat{\xi}_2, \ldots, \widehat{\xi}_L$, estimated via Proposition \ref{proposition:eigen_regul} with a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, are mutually orthonormal with respect to the inner product $\langle \cdot, \cdot \rangle_{\mathcal{H}, \Lambda}$.
@@
 
-	\jongmin{revising here}
-	Now let $\widehat{\boldsymbol{\rho}}_l=(\widehat{\rho}_{1l}, \ldots, \widehat{\rho}_{nl})^\top$ denote the $n$-dimensional vector whose elements consist of estimated $l$-th PLS scores ($l=1, \ldots, L)$ of $n$ observations.
-	The next proposition states that the vectors of estimated PLS scores $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$ obtained from the proposed algorithm are mutually orthogonal.
+The next proposition states that the vectors of estimated PLS scores for different iteration numbers are mutually orthogonal.
 	\begin{proposition}	\label{proposition: orthnormality of PLS scores}
-		The vectors of estimated PLS scores, $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$, obtained from the proposed PLS algorithm are mutually orthogonal in the sense that
-		\begin{equation*}
-			\widehat{\boldsymbol{\rho}}_l^\top \widehat{\boldsymbol{\rho}}_j= 0 \quad \textnormal{for} \quad \; l,j \in \{1, \ldots, L\}, \; l \ne j. 
+		Recall from Lemma \ref{proposition:closed_form_orthgonalization} that   $\widehat{\boldsymbol{\rho}}^{[l]}$ denote the $n$-dimensional vector whose elements consist of the $l$-th estimated PLS scores ($l=1, \ldots, L$) of $n$ observations.
+		The vectors $\widehat{\boldsymbol{\rho}}^{[1]}, \widehat{\boldsymbol{\rho}}^{[2]}, \ldots, \widehat{\boldsymbol{\rho}}^{[L]}$  are mutually orthogonal in the sense that
+		\begin{equation*}
+			\widehat{\boldsymbol{\rho}}^{[l_1] \top}  \widehat{\boldsymbol{\rho}}^{[l_2] \top}= 0 \quad \textnormal{for} \quad \; l_1,l_2 \in \{1, \ldots, L\}, \; l_1 \ne l_2. 
 		\end{equation*}
@@
 
-		Our next task is to show that 
-		$
-		\Theta^{[l_1] }
-		\mathbb{B}
-		\hat{\boldsymbol{\xi}}_{l_2} = \mathbf{0} \in \mathbb{R}^n.
-		$
+Orthogonality can be demonstrated by showing that $\Theta^{[l_1] } \mathbb{B} \hat{\boldsymbol{\xi}}_{l_2} = \mathbf{0} \in \mathbb{R}^n$.
 		From the construction in \eqref{def:full_theta}, \eqref{def:theta} and \eqref{def:gram_block}, the
@@
 			\rangle_{\mathcal{H}},
+			\numberthis \label{thetaBzetal2i}
 		\end{align*}
@@
 \widetilde{W}_1^{[l_1-1]}, \ldots, \widetilde{W}_n^{[l_1-1]}
-	\bigr)^\top \in \tilde{\mathcal{H}}^{\otimes n}.
-\end{equation*}
-Then using \eqref{algorithm_step:residualization_predictor:recall}, we have, with some abuse of notation,
+	\bigr)^\top \in \tilde{\mathcal{H}}^{\otimes n},
+\end{equation*}
+and
+\begin{equation*}
+	\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
+	\hat{\xi}^{[l_2]}
+	\rangle_{\mathcal{H}}
+	:= 
+	\biggl(
+	\langle 
+	\widetilde{W}_1^{[l_1-1]}, 
+	\hat{\xi}^{[l_2]}
+	\rangle_{\mathcal{H}},
+	\ldots, 
+	\langle 
+	\widetilde{W}_n^{[l_1-1]},  
+	\hat{\xi}^{[l_2]}
+	\rangle_{\mathcal{H}}
+	\biggr)^\top 
+	\in \mathbb{R}^n.
+\end{equation*}
+Recalling \eqref{thetaBzetal2i} our goal of showing $
+\Theta^{[l_1] }
+\mathbb{B}
+\hat{\boldsymbol{\xi}}_{l_2} = \mathbf{0} \in \mathbb{R}^n.
+$
+is equivalent to showing  $	\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
+\hat{\xi}^{[l_2]}
+\rangle_{\mathcal{H}} = \mathbf{0}$.
+Using this notation and  \eqref{algorithm_step:residualization_predictor:recall}, we have, with some abuse of notation,
 \begin{equation*}
@@
 \end{equation*}
-Clearly, the right-hand side represents a linear operator from $\tilde{\mathcal{H}}^{\otimes n}$ to $\tilde{\mathcal{H}}^{\otimes n}$, which we denote as $P^{[l_1-1]}$.
+and thus
+\begin{equation*}
+\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
+\hat{\xi}^{[l_2]}
+\rangle_{\mathcal{H}}
+  = 
+\langle 	\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
+\hat{\xi}^{[l_2]}
+\rangle_{\mathcal{H}} 
+- 
+	\biggl(
+	\frac{1
+	}{
+	\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2
+	}
+		\hat{\boldsymbol{\rho}}^{[l_1-1]}
+	\hat{\boldsymbol{\rho}}^{[l_1-1] \top}
+	\biggr)
+	\bigl \langle 
+	\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
+	\hat{\xi}^{[l_2]}
+	\bigr \rangle_{\mathcal{H}}.
+\end{equation*}
+Clearly, the right-hand side represents a linear operator from $\mathbb{R}^n$ to $\mathbb{R}^n$, which we denote as $P^{[l_1-1]}$.
 	Thus, 
-	we have $\widetilde{\boldsymbol{W}}^{[l_1]}  = 
-	P^{[l_1-1]} \widetilde{\boldsymbol{W}}^{[l_1-1]}$.
-Using this relationship, we have
+	we have $\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
+	\hat{\xi}^{[l_2]}
+	\rangle_{\mathcal{H}}  = 
+	P^{[l_1-1]} \langle 	\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
+	\hat{\xi}^{[l_2]}
+	\rangle_{\mathcal{H}}$.
+Repeatedly using this relationship, we have
 	\begin{align*}
-		\widetilde{\boldsymbol{W}}^{[l_1]} &=P^{[l_1-1]} \widetilde{\boldsymbol{W}}^{[l_1-1]} \\
+	\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
+	\hat{\xi}^{[l_2]}
+	\rangle_{\mathcal{H}} 
 	&=
-		P^{[l_1-1]} P^{[l_1-2]} \widetilde{\boldsymbol{W}}^{[l_1-2]}
+P^{[l_1-1]} \langle 	\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
+\hat{\xi}^{[l_2]}
+\rangle_{\mathcal{H}} 
 	\\
-		&= P^{[l_1-1]} P^{[l_1-2]} \ldots P^{[l_2 + 1]}  P^{[l_2]} \widetilde{\boldsymbol{W}}^{[l_2]}
+		&=
+		P^{[l_1-1]} P^{[l_1-2]}   \langle 	\widetilde{\boldsymbol{W}}^{[l_1-2]}  ,
+		\hat{\xi}^{[l_2]}
+		\rangle_{\mathcal{H}}
 		  \\
-&=P P^{[l_2]} \widetilde{\boldsymbol{W}}^{[l_2]},		
+		&= \underbrace{ P^{[l_1-1]} P^{[l_1-2]} \ldots P^{[l_2 + 1]}}_{:=P}  P^{[l_2]} \langle 	\widetilde{\boldsymbol{W}}^{[l_2]}  ,
+		\hat{\xi}^{[l_2]}
+		\rangle_{\mathcal{H}}
+		  \\
+&= P \,\biggl\{
+\langle 	\widetilde{\boldsymbol{W}}^{[l_2]}  ,
+\hat{\xi}^{[l_2]}
+\rangle_{\mathcal{H}} 
+- 
+\biggl(
+\frac{1
+}{
+	\| 	\hat{\boldsymbol{\rho}}^{[l_2]}\|_2^2
+}
+\hat{\boldsymbol{\rho}}^{[l_2]}
+\hat{\boldsymbol{\rho}}^{[l_2] \top}
+\biggr)
+\bigl \langle 
+\widetilde{\boldsymbol{W}}^{[l_2]}  ,
+\hat{\xi}^{[l_2]}
+\bigr \rangle_{\mathcal{H}}
+\biggr\}
+		  \\
+&= P \,\biggl\{
+\hat{\boldsymbol{\rho}}^{[l_2]}
+- 
+\biggl(
+\frac{1
+}{
+	\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2
+}
+\hat{\boldsymbol{\rho}}^{[l_2]}
+\hat{\boldsymbol{\rho}}^{[l_2] \top}
+\biggr)
+ \hat{\boldsymbol{\rho}}^{[l_2]}
+\biggr\}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&= P \,\biggl\{
+\hat{\boldsymbol{\rho}}^{[l_2]}
+- 
+\biggl(
+\frac{\hat{\boldsymbol{\rho}}^{[l_2] \top} \hat{\boldsymbol{\rho}}^{[l_2]}
+}{
+	\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2
+}
+\biggr)
+\hat{\boldsymbol{\rho}}^{[l_2]}
+\biggr\}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&= P \,\biggl\{
+\hat{\boldsymbol{\rho}}^{[l_2]}
+- 
+\hat{\boldsymbol{\rho}}^{[l_2]}
+\biggr\}
+=
+P \mathbf{0} = \mathbf{0}.
 	\end{align*}
-	where $P = P^{[l_1-1]} P^{[l_1-2]} \ldots P^{[l_2 + 1]} $ is a linear operator from  $\tilde{\mathcal{H}}^{\otimes n}$.
-	Then for $j < l$,
-	\begin{align*}
-		\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} &= \int_{\mathcal{T}} P   \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right)\widetilde{W}^{[j]}[\mathbf{t}]  \widehat{\xi}_k[\mathbf{t}] d\mathbf{t}  \\
-		&= P \left\{\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} \right\} \\
-		&=P \left( \widehat{\boldsymbol{\rho}}_j - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \widehat{\boldsymbol{\rho}}_j \right) \\
-		&= P(\widehat{\boldsymbol{\rho}}_j-\widehat{\boldsymbol{\rho}}_j) \\
-		&= \mathbf{0} \in \mathbb{R}^n, 
-	\end{align*}
-	noting that $\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} = \widehat{\boldsymbol{\rho}}_j$. Now by the , we have that
-
-	\begin{align*}
-		&=  \frac{1}{\kappa_l}\widehat{\xi}_l^{* \top} V^\ast_l \widehat{\xi}_j^{*} \\
-		&= \frac{1}{\kappa_l}\widehat{\xi}_l^{* \top} \left(n^{-2} J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top} \widetilde{C}^{*[l]} J^\ast \right) \widehat{\xi}_j^{*} \\
-		&= \frac{1}{n^2\kappa_l}\widehat{\xi}_l^{* \top} \ J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top}  \widetilde{C}^{*[l]}\left(\int_{\mathcal{T}} B^*[\mathbf{t}] B^*[\mathbf{t}]^\top d\mathbf{t}  \right) \widehat{\xi}_j^{*} \\
-		&= \frac{1}{n^2\kappa_l}\widehat{\xi}_l^{* \top}  J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top}  \left(\int_{\mathcal{T}} \widetilde{C}^{*[l]} B^*[\mathbf{t}] B^*[\mathbf{t}]^\top \widehat{\xi}_j^{*} d\mathbf{t}  \right)   \\
-		&= \frac{1}{n^2\kappa_l}\widehat{\xi}_l^{* \top}  J^\ast \widetilde{C}^{*[l]\top} \widetilde{\mathbf{y}}^{[l]}\widetilde{\mathbf{y}}^{[l]\top}  \left(\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t}  \right)   \\
-		&=0, 
-	\end{align*}
-	where the last equality follows from the above result that $\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} = \mathbf{0}$.
-
+This completes the proof of Proposition 
+	\ref{proposition: modified orthnormality of PLS components}.
 	\end{proof}

### 2025-08-13 manuscript/main.tex
score orthogonality proof done

@@
 Let us denote, with some abuse of notation:
-\begin{equation*}
+\begin{equation}\label{notation:n_predictors}
 	\widetilde{\boldsymbol{W}}^{[l_1]}  := 
@@
 	\bigr)^\top \in \tilde{\mathcal{H}}^{\otimes n},
-\end{equation*}
+\end{equation}
 and
-\begin{equation*}
+\begin{equation}\label{notation:n_inner_products}
 	\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
@@
 	\in \mathbb{R}^n.
-\end{equation*}
-Recalling \eqref{thetaBzetal2i} our goal of showing $
+\end{equation}
+Recalling \eqref{thetaBzetal2i},
+to achieve our goal of showing $
 \Theta^{[l_1] }
 \mathbb{B}
-\hat{\boldsymbol{\xi}}_{l_2} = \mathbf{0} \in \mathbb{R}^n.
+\hat{\boldsymbol{\xi}}_{l_2} = \mathbf{0} \in \mathbb{R}^n,
 $
-is equivalent to showing  $	\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
+it suffices to show
+   $	\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
 \hat{\xi}^{[l_2]}
 \rangle_{\mathcal{H}} = \mathbf{0}$.
-Using this notation and  \eqref{algorithm_step:residualization_predictor:recall}, we have, with some abuse of notation,
-\begin{equation*}
+Using these notations and  \eqref{algorithm_step:residualization_predictor:recall}, we have, with some abuse of notation,
+\begin{equation}\label{regression_relation_with_notation_abuse}
 \widetilde{\boldsymbol{W}}^{[l_1]}  = 
@@
 		\widetilde{\boldsymbol{W}}^{[l_1-1]},
-\end{equation*}
+\end{equation}
 and thus
@@
 	\section{Proof of Proposition \ref{proposition: orthnormality of PLS scores}}\label{section:proof:proposition: orthnormality of PLS scores}
-
-	First note that $\widehat{\boldsymbol{\rho}}_l = \int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\xi}_l[\mathbf{t}] d\mathbf{t}= \widetilde{C}^{*[l]} J^\ast \widehat{\xi}^*_{l}$ for $l=1, \ldots, L$.
-Then, as above, we first express the $l$-th residualized hybrid predictor in terms of its previous $(l-1)$-th version:
-	\begin{equation*}
-		\widetilde{W}^{[l]}[\mathbf{t}] = \widetilde{W}^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\delta}}_l[\mathbf{t}]^\top 
-	\end{equation*}
-	which, after applying the finite-dimensional form (9), implies that
-	\begin{equation*}
-		\setlength{\jot}{10pt}
-		\begin{aligned}
-			\widetilde{C}^{*[l]}B^*[\mathbf{t}] &=\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1}\widehat{\boldsymbol{\gamma}}^*_{l-1}B^*[\mathbf{t}] \\
-			&= \widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} J^\ast \left(\widehat{\boldsymbol{\rho}}_{i,l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1} J^\ast \right)^{-1} B^*[\mathbf{t}] \\
-			& =\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] -  \frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} B^*[\mathbf{t}]}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}}  \\
-			& =\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] -  \frac{\widetilde{C}^{*[l-1]} J^\ast \widehat{\xi}^{*}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} B^*[\mathbf{t}]}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}},
-		\end{aligned}
-	\end{equation*}
-	Since the equation should hold for all argument values $\mathbf{t} \in \mathcal{T}$, we can write:
-	\begin{equation*}
-		\setlength{\jot}{10pt}
-		\begin{aligned}
-			\widetilde{C}^{*[l]} &= \widetilde{C}^{*[l-1]} -  \frac{\widetilde{C}^{*[l-1]} J^\ast \widehat{\xi}^{*}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]}}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \\
-			&= \widetilde{C}^{*[l-1]} \left(I_{MK+p} - \frac{J^\ast \widehat{\xi}^{*}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]}}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \\
-			&= \widetilde{C}^{*[j]} \left(I_{MK+p} - \frac{J^\ast \widehat{\xi}^{*}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P},
-		\end{aligned}
-	\end{equation*}
-	where $\widetilde{P}$ is a $(MK+p) \times (MK+p)$ matrix defined as
-	\begin{equation*}
-		\widetilde{P} = \prod \limits_{h=j+1}^{l-1} \left(I_{MK+p} - \frac{J^\ast \hat{\xi}^*_h \widehat{\boldsymbol{\rho}}_{h}^\top \widetilde{C}^{*[h]}}{\widehat{\boldsymbol{\rho}}_{h}^\top \widehat{\boldsymbol{\rho}}_{h}} \right)
-	\end{equation*}
-	Then, for $j < l$,
-	\begin{equation*}
-		\setlength{\jot}{10pt}
-		\begin{aligned}
-			\widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[l]} &=  \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} \left(I_{MK+p} - \frac{J^\ast \widehat{\xi}^{*}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P} \\
-			&=\left( \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} - \frac{ \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} J^\ast \widehat{\xi}^{*}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P} \\
-			&=\left( \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} - \frac{ \widehat{\boldsymbol{\rho}}_j^\top \widehat{\boldsymbol{\rho}}_j  \widehat{\boldsymbol{\rho}}_{j}^\top \widetilde{C}^{*[j]}}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right) \widetilde{P} \\
-			&= \left(  \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} -  \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[j]} \right) \widetilde{P} \\
-			&= \mathbf{0} \in \mathbb{R}^{1 \times (MK+p)},
-		\end{aligned}
-	\end{equation*}
-	Therefore, for $j < l$,
-	\begin{equation*}
-		\widehat{\boldsymbol{\rho}}_j^\top \widehat{\boldsymbol{\rho}}_l =  \widehat{\boldsymbol{\rho}}_j^\top \widetilde{C}^{*[l]} J^\ast \widehat{\boldsymbol{\rho}}_{l} = \mathbf{0} J^\ast \widehat{\boldsymbol{\rho}}_{l}=  0.
-	\end{equation*}
-	Thus, the proposition is proved.
+	\begin{proof}
+			For $l_1 < l_2$,
+\begin{align*}
+\widehat{\boldsymbol{\rho}}^{[l_1 ] \top}
+\widehat{\boldsymbol{\rho}}^{[l_2]}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&=  
+\sum_{i=1}^n
+\widehat{ \rho }^{[l_1 ]}_i \,
+\widehat{ \rho }^{[l_2]}_i
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&=  
+\sum_{i=1}^n
+\widehat{ \rho }^{[l_1 ]}_i \,
+\bigl \langle 	\widetilde{W}^{[l_2]}_i  ,
+\hat{\xi}^{[l_2]}
+\bigr \rangle_{\mathcal{H}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&=  
+\big \langle
+\sum_{i=1}^n
+\widehat{ \rho }^{[l_1 ]}_i \,
+ 	\widetilde{W}^{[l_2]}_i  ,
+\hat{\xi}^{[l_2]}
+\big \rangle_{\mathcal{H}}
+\end{align*}
+Therefore,
+to show that $\widehat{\boldsymbol{\rho}}^{[l_1 ] \top}
+\widehat{\boldsymbol{\rho}}^{[l_2]} = 0$,
+ it suffices to show that
+$\sum_{i=1}^n
+\widehat{ \rho }^{[l_1 ]}_i \,
+\widetilde{W}^{[l_2]}_i  = 0 \in   \mathcal{H}  $,
+where this   zero element represents an ordered pair of $K$ zero functions and a zero matrix.
+Using Lemma    \ref{proposition:closed_form_orthgonalization}, notations from 
+\eqref{notation:n_predictors} and
+\eqref{notation:n_inner_products},
+and equation \eqref{regression_relation_with_notation_abuse}, we have:
+\begin{align*}
+	\widetilde{\boldsymbol{W}}^{[l_1]}  &= 
+	\widetilde{\boldsymbol{W}}^{[l_1-1]} - 
+	\biggl(
+	\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
+	\hat{\boldsymbol{\rho}}^{[l_1-1] }
+	\hat{\boldsymbol{\rho}}^{[l_1-1] \top
+	} 
+	\biggr)
+	\widetilde{\boldsymbol{W}}^{[l_1-1]}
+%%%%%%%%%%%%%%%%%%%%%%
+\\&=	\widetilde{\boldsymbol{W}}^{[l_1-1]} - 
+\biggl(
+\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
+\langle 	
+	\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
+	\hat{\xi}^{[l_1-1]}
+\rangle_{\mathcal{H}}
+\hat{\boldsymbol{\rho}}^{[l_1-1] \top
+} 
+\biggr)
+\widetilde{\boldsymbol{W}}^{[l_1-1]}.
+\end{align*}
+Using this relationship and
+with some abuse of notation, we have:
+\begin{align*}
+\sum_{i=1}^n
+\widehat{ \rho }^{[l_1 ]}_i \,
+\widetilde{W}^{[l_2]}_i 
+&=
+		\hat{\boldsymbol{\rho}}^{[l_2] \top}
+	\widetilde{\boldsymbol{W}}^{[l_1]}
+\\  &=	
+			\hat{\boldsymbol{\rho}}^{[l_2] \top}
+	\widetilde{\boldsymbol{W}}^{[l_1-1]} - 
+			\hat{\boldsymbol{\rho}}^{[l_2] \top}
+	\biggl(
+	\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
+	\langle 	
+	\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
+	\hat{\xi}^{[l_1-1]}
+	\rangle_{\mathcal{H}}
+	\hat{\boldsymbol{\rho}}^{[l_1-1] \top
+	} 
+	\biggr)
+	\widetilde{\boldsymbol{W}}^{[l_1-1]}
+\\	&=	
+	\hat{\boldsymbol{\rho}}^{[l_2] \top}
+	\widetilde{\boldsymbol{W}}^{[l_1-1]} - 
+	\frac{
+		\langle 	 	\hat{\boldsymbol{\rho}}^{[l_2] \top}
+	\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
+	\hat{\xi}^{[l_1-1]}
+	\rangle_{\mathcal{H}}
+	}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+	\bigl(
+	\hat{\boldsymbol{\rho}}^{[l_1-1] \top
+	} 
+	\widetilde{\boldsymbol{W}}^{[l_1-1]}
+	\bigr)
+\\	&=	h^{[l_1-1]} \bigl( \hat{\boldsymbol{\rho}}^{[l_2] \top}
+\widetilde{\boldsymbol{W}}^{[l_1-1]} \bigr)~(\text{say}).
+\end{align*}
+Here, the function $h^{[l_1-1]}: \tilde{ \mathcal{H} } \mapsto \tilde{\mathcal{H}}$ maps the zero element of $\tilde{\mathcal{H}}$ to itself, where the zero element represents an ordered pair of $K$ zero functions and a zero matrix.
+Using this relationship, we have
+\begin{align*}
+	\hat{\boldsymbol{\rho}}^{[l_2] \top}
+	\widetilde{\boldsymbol{W}}^{[l_1]}  
+%%%%%%%%%%%%%%%%
+	&=	h^{[l_1-1]} \bigl( \hat{\boldsymbol{\rho}}^{[l_2] \top}
+	\widetilde{\boldsymbol{W}}^{[l_1-1]} \bigr)
+%%%%%%%%%%%%%%%%
+\\&=
+h^{[l_1-1]} 
+\circ 
+h^{[l_1-2]}
+\bigl( \hat{\boldsymbol{\rho}}^{[l_2] \top}
+\widetilde{\boldsymbol{W}}^{[l_1-2]} \bigr)
+%%%%%%%%%%%%%%%%
+\\&=
+h^{[l_1-1]} 
+\circ 
+h^{[l_1-2]}
+\circ 
+\ldots
+\circ 
+h^{[l_2]}
+\bigl( \hat{\boldsymbol{\rho}}^{[l_2] \top}
+\widetilde{\boldsymbol{W}}^{[l_2]} \bigr).
+\end{align*}
+Therefore,
+to show that $\widehat{\boldsymbol{\rho}}^{[l_1 ] \top}
+\widehat{\boldsymbol{\rho}}^{[l_2]} = 0$,
+ it suffices to show $h^{[l_2]}
+\bigl( \hat{\boldsymbol{\rho}}^{[l_2] \top}
+\widetilde{\boldsymbol{W}}^{[l_2]} \bigr) = 0$:
+%
+\begin{align*}
+h^{[l_2]} \bigl( \hat{\boldsymbol{\rho}}^{[l_2] \top}
+\widetilde{\boldsymbol{W}}^{[l_2]} \bigr)
+&=
+		\hat{\boldsymbol{\rho}}^{[l_2] \top}
+	\widetilde{\boldsymbol{W}}^{[l_2]} - 
+	\frac{
+		\langle 	 	\hat{\boldsymbol{\rho}}^{[l_2] \top}
+		\widetilde{\boldsymbol{W}}^{[l_2]}  ,
+		\hat{\xi}^{[l_2]}
+		\rangle_{\mathcal{H}}
+	}{\| 	\hat{\boldsymbol{\rho}}^{[l_2]}\|_2^2}
+	%%%%%%%%%%%%%%%%%%%%%%%%%
+	\bigl(
+	\hat{\boldsymbol{\rho}}^{[l_2] \top
+	} 
+	\widetilde{\boldsymbol{W}}^{[l_2]}
+	\bigr)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&=
+\hat{\boldsymbol{\rho}}^{[l_2] \top}
+\widetilde{\boldsymbol{W}}^{[l_2]} - 
+\frac{
+		\hat{\boldsymbol{\rho}}^{[l_2] \top}
+	\langle 	 
+	\widetilde{\boldsymbol{W}}^{[l_2]}  ,
+	\hat{\xi}^{[l_2]}
+	\rangle_{\mathcal{H}}
+}{\| 	\hat{\boldsymbol{\rho}}^{[l_2]}\|_2^2}
+% 
+\bigl(
+\hat{\boldsymbol{\rho}}^{[l_2] \top
+} 
+\widetilde{\boldsymbol{W}}^{[l_2]}
+\bigr)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&=
+\hat{\boldsymbol{\rho}}^{[l_2] \top}
+\widetilde{\boldsymbol{W}}^{[l_2]} - 
+\frac{
+	\hat{\boldsymbol{\rho}}^{[l_2] \top}
+	\hat{\boldsymbol{\rho}}^{[l_2]  } 
+}{\| 	\hat{\boldsymbol{\rho}}^{[l_2]}\|_2^2}
+% 
+\bigl(
+\hat{\boldsymbol{\rho}}^{[l_2] \top
+} 
+\widetilde{\boldsymbol{W}}^{[l_2]}
+\bigr)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&=
+\hat{\boldsymbol{\rho}}^{[l_2] \top}
+\widetilde{\boldsymbol{W}}^{[l_2]} 
+- 
+\hat{\boldsymbol{\rho}}^{[l_2] \top
+} 
+\widetilde{\boldsymbol{W}}^{[l_2]}
+\\&=0.
+\end{align*}
+This completes the proof of Proposition \ref{proposition: orthnormality of PLS scores}.
+	\end{proof}
 

### 2025-08-13 manuscript/main.tex
operator definition, except for the last

@@
 	and possess second  derivatives.
-	Additionally, let $\mathbf{Z}=(Z_1, \ldots, Z_p)^\top$
+	Additionally, let $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$
 	denote a $p$-dimensional multivariate scalar data in $\mathbb{R}^p$, assumed to be a random vector with finite first two moments, equipped with the Euclidean inner product and norm.
@@
 	We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
-We omit $l$ in the notations and first define the cross-covariance terms between the response and predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$):
-	\begin{equation*}
-		\begin{gathered}
-			\sigma_{YX} = (\sigma_{YX}^{(1)}, \ldots, \sigma_{YX}^{(K)}) = (E(YX^{(1)}),\ldots, E(YX^{(K)})) = E(YX) \in \mathcal{F} \\
-			\sigma_{YZ} = (\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top = (E(YZ_1),\ldots, E(YZ_p))^\top = E(Y\mathbf{Z}) \in \mathbb{R}^p \\
-			\Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) =  (E(YX), E(Y\mathbf{Z}))=E(Y\mathbf{W}) \in \mathcal{H}
-		\end{gathered}
-	\end{equation*}
-	We also introduce two cross-covariance operators, $\mathcal{C}_{YW}=E(\mathbf{W} \otimes_\mathcal{H} Y): \mathcal{H} \rightarrow \mathbb{R}$ and $\mathcal{C}_{WY}=E(Y \otimes \mathbf{W}): \mathbb{R} \rightarrow \mathcal{H}$, which respectively map $h=(f, \mathbf{v}) \in \mathcal{H}$ to $\mathbb{R}$ and $d \in \mathbb{R}$ to $\mathcal{H}$ as follows:
+We omit $l$ in the notations and first define the cross-covariance term between the response and the functional predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$):
+	\begin{equation*}
+\sigma_{YX}
+=
+ (\sigma_{YX, 1} , \ldots, \sigma_{YX, K} )
+  :=
+\bigl(
+\mathbb{E}
+[Y_1 X_{11}]
+,\ldots, 
+\mathbb{E}
+[Y_1  X_{1K}]
+\bigr)   \in \mathcal{F}^{\otimes K},
+	\end{equation*}
+between the response and the scalar predictor:
+\begin{equation*}
+\sigma_{YZ} 
+= 
+(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
+:= 
+\bigl(
+\mathbb{E}[Y_1 Z_{11}]
+,\ldots,
+\mathbb{E}[Y_1 Z_{1p}]
+\bigr)^\top %= E(Y\mathbf{Z})
+\in \mathbb{R}^p.
+\end{equation*}
+Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
+\begin{equation*}
+\Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) :=  
+\mathbb{E}
+[ Y_1 W_1 ]
+=
+\bigl(
+\sigma_{YX}, \sigma_{YZ}
+\bigr) \in \mathcal{H}.
+\end{equation*}
+Based on these definitions, we introduce two cross-covariance operators.
+First, $\mathcal{C}_{YW}= \mathbb{E}(W_1 \otimes_\mathcal{H} Y_1): \mathcal{H} \rightarrow \mathbb{R}$ 
+maps  
+  $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$ to a real number:
+\begin{equation*}
+\mathcal{C}_{YW}
+\mathbf{h}
+:=
+\mathbb{E} 
+\bigl[ 
+\langle W_1, h \rangle_\mathcal{H} Y_1 
+\bigr] 
+= 
+\langle \Sigma_{YW}, h \rangle_\mathcal{H}
+=
+\sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt 
++ 
+\sigma_{YW}^\top \mathbf{v}.
+\end{equation*}
+Next, $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes \mathbf{W}]: \mathbb{R} \rightarrow \mathcal{H}$
+maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:
+%%%%
 \begin{align*}		
-		& \mathcal{C}_{YW} \mathbf{h} = E\{\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX}^{(k)}(t_k) f^{(k)}(t_k) dt_k + E(Y \mathbf{Z}^\top) \mathbf{v} \\
-		& \mathcal{C}_{WY} d = E (\langle Y, d \rangle \mathbf{W} ) = E(Y\mathbf{W})d =  \Sigma_{YW} \, d. 
+\mathcal{C}_{WY} d 
+:= 
+\mathbb{E} 
+\bigl[
+ \langle Y_1, d \rangle W_1 
+\bigr] 
+= 
+\mathbb{E}
+[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
 \end{align*}
@@
 		\begin{equation*}
-			\widehat{\boldsymbol{\rho}}^{[l_1] \top}  \widehat{\boldsymbol{\rho}}^{[l_2] \top}= 0 \quad \textnormal{for} \quad \; l_1,l_2 \in \{1, \ldots, L\}, \; l_1 \ne l_2. 
+			\widehat{\boldsymbol{\rho}}^{[l_1] \top}  \widehat{\boldsymbol{\rho}}^{[l_2] }= 0 \quad \textnormal{for} \quad \; l_1,l_2 \in \{1, \ldots, L\}, \; l_1 \ne l_2. 
 		\end{equation*}
@@
 
-	\section{Simulations} \label{Simulations}
-
 \end{document}

### 2025-08-13 manuscript/main.tex
Proof of Lemma \ref{lemma:composite_cross_cov}

@@
 \mathcal{C}_{YW}
-\mathbf{h}
+h
 :=
@@
 \end{equation*}
-Next, $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes \mathbf{W}]: \mathbb{R} \rightarrow \mathcal{H}$
+Next, $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$
 maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:
@@
 \end{align*}
-
-	Now define a new operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$, which performs the following mapping:
-	\begin{equation*}
-		\mathcal{U} \mathbf{h} =  \mathcal{C}_{WY} ( \mathcal{C}_{YW} \mathbf{h}) 
-		= \mathcal{C}_{YW} (\langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}) 
-		=  \Sigma_{YW} \, \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = (\Sigma_{YW} \otimes \Sigma_{YW})\mathbf{h}.
-	\end{equation*}
-	In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$. The following proposition presents several important properties of $\mathcal{U}$.
+Based on these two operators, we define a positive   operator as follows:
+\begin{lemma}[Composite cross-covariance operator]\label{lemma:composite_cross_cov}
+Define
+	$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ as an operator which performs the following mapping:
+	\begin{equation*}
+		\mathcal{U} h 
+		= 
+		\mathcal{C}_{WY} ( \mathcal{C}_{YW} h) 
+		=
+		\mathcal{C}_{YW} (\langle \Sigma_{YW}, h \rangle_\mathcal{H}) 
+		=  
+		\Sigma_{YW} \, \langle \Sigma_{YW}, h \rangle_\mathcal{H} 
+		= 
+		(\Sigma_{YW} \otimes \Sigma_{YW}) h.
+	\end{equation*}
+		In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$.
+	 is self-adjoint and positive-semidefinite.
+\end{lemma}
+The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
+ The following proposition presents several important properties of $\mathcal{U}$.
 	\begin{proposition} \label{Proposition: property of U}
-		The operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}= \Sigma_{YW} \otimes \Sigma_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ is positive and self-adjoint.
 	 Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that
@@
 	This completes the proof of Lemma \ref{proposition:closed_form_orthgonalization}.
+
+\section{Proof of Lemma \ref{lemma:composite_cross_cov}}\label{section:proof:lemma:composite_cross_cov}
+\begin{proof}
+	The operator
+$\mathcal{U}$ is \textit{self-adjoint} because for any $h_1, h_2 \in \mathcal{H}$, we have
+\begin{align*}
+\langle 
+\mathcal{U} h_1, \, h_2 
+\rangle_\mathcal{H}  
+&= 
+\bigl \langle 
+	\langle h_1, \Sigma_{YW} \rangle_\mathcal{H} \Sigma_{YW},
+	\,
+	h_2
+\bigr \rangle_\mathcal{H}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&= \langle h_1, \Sigma_{YW} \rangle_\mathcal{H} \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&= 
+\bigl \langle 
+h_1,
+\,
+ \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H} \Sigma_{YW} 
+\bigr \rangle_\mathcal{H}
+\\ 	&= \langle h_1, \mathcal{U} h_2 \rangle_\mathcal{H}.
+\end{align*}
+Next, 
+	$\mathcal{U}$ is \textit{positive-semidefinite} because for every $h \in \mathcal{H}$, we have
+\begin{equation*}
+\langle 
+	\mathcal{U} h,
+	\,
+	h
+\rangle_\mathcal{H}
+=
+\bigl \langle 
+	\langle 
+		\Sigma_{YW},\, h \rangle_{\mathcal{H}}  \Sigma_{YW}, \, h
+\bigr \rangle_\mathcal{H}
+	= \langle \Sigma_{YW}, \, h \rangle_\mathcal{H}^2 \ge 0.
+\end{equation*}
+This completes the proof of Lemma \ref{lemma:composite_cross_cov}.
+\end{proof}
+
 	\section{Proof of Proposition \ref{Proposition: property of U}}\label{section:proof:Proposition: property of U}
-	$\mathcal{U}$ is \textit{positive} because for every $\mathbf{h} \in \mathcal{H}$,
-	\begin{equation*}
-		\langle \mathcal{U} \mathbf{h}, \mathbf{h} \rangle_\mathcal{H} = \langle \langle \Sigma_{YW}, \mathbf{h} \rangle_{\mathcal{H}} \, \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}^2 \ge 0.
-	\end{equation*}
-
-	$\mathcal{U}$ is \textit{self-adjoint} because for any $\mathbf{h}_1, \mathbf{h}_2 \in \mathcal{H}$,
-	\begin{align*}
-		\langle \mathcal{U} \mathbf{h}_1, \mathbf{h}_2 \rangle_\mathcal{H}  &= \langle \langle \mathbf{h}_1, \Sigma_{YW} \rangle_\mathcal{H} \Sigma_{YW}, \mathbf{h}_2 \rangle_\mathcal{H} \\
-		&= \langle \mathbf{h}_1, \Sigma_{YW} \rangle_\mathcal{H} \langle \Sigma_{YW}, \mathbf{h}_2 \rangle_\mathcal{H} \\
-		&= \langle \mathbf{h}_1,  \langle \Sigma_{YW}, \mathbf{h}_2 \rangle_\mathcal{H} \Sigma_{YW} \rangle_\mathcal{H}\\ 
-		&= \langle \mathbf{h}_1, \mathcal{U} \mathbf{h}_2 \rangle_\mathcal{H}.
-	\end{align*}
 
@@
 	\begin{proof}
-			For $l_1 < l_2$,
+			For $l_1 < l_2$, we have
 \begin{align*}

### 2025-08-13 manuscript/main.tex
compactness condition as lemma

@@
 We omit $l$ in the notations and first define the cross-covariance term between the response and the functional predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$):
-	\begin{equation*}
+	\begin{equation}\label{def:cross_covariance_yx}
 \sigma_{YX}
@@
 \bigr)   \in \mathcal{F}^{\otimes K},
-	\end{equation*}
-between the response and the scalar predictor:
+	\end{equation}
+and between the response and the scalar predictor:
 \begin{equation*}
@@
 		In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$.
+		Then $\mathcal{U}$
 	 is self-adjoint and positive-semidefinite.
@@
 The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
- The following proposition presents several important properties of $\mathcal{U}$.
-	\begin{proposition} \label{Proposition: property of U}
-	 Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that
+To guarantee the existence of a complete orthonormal system of eigenfunctions for $\mathcal{U}$ in $\mathcal{H}$, we  first demonstrate that $\mathcal{U}$ is compact.
+To this end, we begin by defining the notion of uniform continuity for the cross-covariance function defined in \eqref{def:cross_covariance_yx}:
+\begin{definition}[Uniform Continuity]\label{def:uniform_continuity}
+	For each $k \in \{1, \ldots, K\}$, the cross-covariance function $\sigma_{YX, k} \in \mathcal{F}$ is uniformly continuous if for any $\epsilon > 0$, there exists a $\delta_k > 0$ such that for all $t_1, t_2 \in [0,1]$ satisfying $|t_1 - t_2 | < \delta_k$, we have
+$
+		| \sigma_{YX, k} (t_1) - \sigma_{YX, k} (t_2) | < \epsilon.
+$
+\end{definition}
+Using this definition, the following lemma presents a condition for $\mathcal{U}$ to be a compact operator.
+	\begin{lemma}[Compactness condition] \label{Proposition: property of U}
+If there exist finite constants $Q_1$ and $Q_2$ such that
 		\begin{align}
-			\max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in [0,1]} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
+			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
 		\end{align}
-		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in [0,1]$ with $|t_k - t_k^* | < \delta_k$, we have that
-		\begin{equation*}
-			|\sigma_{yx}^{(k)}(t_k) - \sigma_{yx}^{(k)}(t_k^*) | < \epsilon,
-		\end{equation*}
+		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous,
 		then $\mathcal{U}$ is a compact operator.
-	\end{proposition}
-	The proof of Proposition \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
+\end{lemma}
+The proof of Lemma \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
 	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.

### 2025-08-14 manuscript/main.tex
compactness lemma prove revised

@@
 	%Also, there may be high correlation between functional and scalar predictors.
-	This hybrid model poses several challenges.
-	Estimating the infinite-dimensional slope function $\beta_k(t) $ is an ill-posed problem requiring  dimension reduction or regularization based on structural assumption,
+	This hybrid model poses two-fold challenges.
+	First, estimating the infinite-dimensional slope function $\beta_k(t) $ is an ill-posed problem requiring  dimension reduction or regularization based on structural assumption,
 	such as derivatives and covariance patterns.
-	Scalar predictors are often high-dimensional and multicollinear.
-	Moreover, strong correlations between functional and scalar predictors are common but typically overlooked by separate modeling approaches.
+	Second, strong correlations between functional and scalar predictors are common but typically overlooked by separate modeling approaches.
 These issues call for a unified framework that addresses ill-posedness, high-dimensionality, and cross-modality correlation jointly.
@@
 	%The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)}) $ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as $\langle f_1, f_2\rangle_\mathcal{F} =  \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)}\rangle_{L^2} = \sum_{k=1}^K \int_0^1 f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k$ with norm $\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_0^1 f_1^{(k)}(t_k)^2 dt_k\}^{1/2}$.
-	%An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}[\mathbf{t}] = (X(\mathbf{t}), \mathbf{Z})^\top$, with $ X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $ \mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.
+	%An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}(\mathbf{t}) = (X(\mathbf{t}), \mathbf{Z})^\top$, with $ X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $ \mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.
 
@@
 	\begin{equation}
-		\mathbf{W}[\mathbf{t}] = \sum \limits_{l=1}^{\infty} \rho_{l} \boldsymbol{\delta}_l[\mathbf{t}] \quad \textnormal{and} \quad Y = \sum \limits_{l=1}^{\infty}\rho_{l} \nu_l + \epsilon,
+		\mathbf{W}(\mathbf{t}) = \sum \limits_{l=1}^{\infty} \rho_{l} \boldsymbol{\delta}_l(\mathbf{t}) \quad \textnormal{and} \quad Y = \sum \limits_{l=1}^{\infty}\rho_{l} \nu_l + \epsilon,
 		\label{eq: decomposition}
@@
 			$
-			\widehat{\xi}_{l}[\mathbf{t}] 
+			\widehat{\xi}_{l}(\mathbf{t}) 
 			\leftarrow 
-			\dfrac{\sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]}[\mathbf{t}]}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}}
+			\dfrac{\sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]}(\mathbf{t})}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}}
 			$
@@
 			\State 	$
-			\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \leftarrow \dfrac{\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2}.
+			\widehat{\boldsymbol{\delta}}_{l}(\mathbf{t}) \leftarrow \dfrac{\sum_{i=1}^n \mathbf{W}_i^{[l]}(\mathbf{t}) \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2}.
 			$
@@
 			\State
-			$\mathbf{W}_i^{[l+1]}[\mathbf{t}] \leftarrow \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$
+			$\mathbf{W}_i^{[l+1]}(\mathbf{t}) \leftarrow \mathbf{W}_i^{[l]}(\mathbf{t}) - \widehat{\boldsymbol{\delta}}_{l}(\mathbf{t}) \widehat{\rho}_{il}$
 			\State 	$
@@
 		\begin{equation}\label{def:pls_loading_ptws}
-			\widehat{\xi}_{l}[\mathbf{t}] = \frac{\sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]}[\mathbf{t}]}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} = \left[ \frac{\sum_{i=1}^n Y_i^{[l]} X_i^{[l]}(\mathbf{t})}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}}, \frac{\sum_{i=1}^n Y_i^{[l]}\mathbf{Z}_i^{[l]}}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} \right]^\top,
+			\widehat{\xi}_{l}(\mathbf{t}) = \frac{\sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]}(\mathbf{t})}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} = \left[ \frac{\sum_{i=1}^n Y_i^{[l]} X_i^{[l]}(\mathbf{t})}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}}, \frac{\sum_{i=1}^n Y_i^{[l]}\mathbf{Z}_i^{[l]}}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} \right]^\top,
 		\end{equation}
@@
 
-		\item Obtain the subsequent residualized outcomes and predictors as $Y_i^{[l+1]} = Y_i^{[l]} - \widehat{\nu}_{l} \widehat{\rho}_{il}$ and $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$, where
-		\begin{equation*}
-			\widehat{\nu}_l = \frac{\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] = \frac{\sum_{i=1}^n \mathbf{W}_i^{[l]}[\mathbf{t}] \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2}.
-		\end{equation*}
-		Note, $\widehat{\nu}_l$ is the least squares estimate from linear regression of $Y_i^{[l]}$ on $\widehat{\rho}_{il}$, and  $\widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}]$ is the least squares estimate from a linear regression of $\mathbf{W}_i^{[l]}[\mathbf{t}]$ on $\widehat{\rho}_{il}$.
+		\item Obtain the subsequent residualized outcomes and predictors as $Y_i^{[l+1]} = Y_i^{[l]} - \widehat{\nu}_{l} \widehat{\rho}_{il}$ and $\mathbf{W}_i^{[l+1]}(\mathbf{t}) = \mathbf{W}_i^{[l]}(\mathbf{t}) - \widehat{\boldsymbol{\delta}}_{l}(\mathbf{t}) \widehat{\rho}_{il}$, where
+		\begin{equation*}
+			\widehat{\nu}_l = \frac{\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}_{l}(\mathbf{t}) = \frac{\sum_{i=1}^n \mathbf{W}_i^{[l]}(\mathbf{t}) \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2}.
+		\end{equation*}
+		Note, $\widehat{\nu}_l$ is the least squares estimate from linear regression of $Y_i^{[l]}$ on $\widehat{\rho}_{il}$, and  $\widehat{\boldsymbol{\delta}}_{l}(\mathbf{t})$ is the least squares estimate from a linear regression of $\mathbf{W}_i^{[l]}(\mathbf{t})$ on $\widehat{\rho}_{il}$.
 
@@
 \begin{equation*}
-\Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) :=  
+\Sigma_{YW} :=  
 \mathbb{E}
@@
 \bigl(
-\sigma_{YX}, \sigma_{YZ}
+\sigma_{YX, 1} , \ldots, \sigma_{YX, K} , \, \sigma_{YZ}
 \bigr) \in \mathcal{H}.
@@
 The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
-To guarantee the existence of a complete orthonormal system of eigenfunctions for $\mathcal{U}$ in $\mathcal{H}$, we  first demonstrate that $\mathcal{U}$ is compact.
+To guarantee the existence of a complete orthonormal system of eigenfunctions for $\mathcal{U}$ in $\mathcal{H}$, we  first demonstrate that $\mathcal{U}$ is  a compact operator,
+that is,
+images of a bounded sequence contains a convergent subsequence (for a formal definition, see Definition 4.1.1 of \citealt{hsingTheoreticalFoundationsFunctional2015}).
 To this end, we begin by defining the notion of uniform continuity for the cross-covariance function defined in \eqref{def:cross_covariance_yx}:
@@
 If there exist finite constants $Q_1$ and $Q_2$ such that
-		\begin{align}
+		\begin{align}\label{condition_for_compact}
 			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
@@
 The proof of Lemma \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
-	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
+	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
 
@@
 	\mathbf{Z} = [\mathbf{Z}_1, \cdots, \mathbf{Z}_n]^\top \in \mathbb{R}^{n \times p}
-	$ denote $n \times p$ matrix of the scalar predictors (observed version when $l=1$, or residualized version when $l \ge 2$), and let $\widetilde{W}[\mathbf{t}]=[\widetilde{X}(\mathbf{t}), \mathbf{Z}]$ denote $n \times (K+p)$ hybrid predictor matrix that stacks $\widetilde{X}(\mathbf{t})$ and $\mathbf{Z}$ as columns.
+	$ denote $n \times p$ matrix of the scalar predictors (observed version when $l=1$, or residualized version when $l \ge 2$), and let $\widetilde{W}(\mathbf{t})=[\widetilde{X}(\mathbf{t}), \mathbf{Z}]$ denote $n \times (K+p)$ hybrid predictor matrix that stacks $\widetilde{X}(\mathbf{t})$ and $\mathbf{Z}$ as columns.
 Then we can also write the hybrid predictor, whose functional part is approximated using the basis functions, as a form of linear transformation similar to \eqref{eq: basis approximation of X}:
 	\begin{equation}\label{eq: basis approximation of W}
-		\widetilde{W}[\mathbf{t}] 
-		=  
-		\widetilde{ \mathbf{C} }^\ast B^*[\mathbf{t}], \quad t \in \mathcal{T}.
-	\end{equation}
-	where  $B^*[\mathbf{t}] = \mathrm{blkdiag}(B(\mathbf{t}), \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (K+p)}$ and $\widetilde{ \mathbf{C} }^\ast=[\widetilde{C}, \mathbf{Z}] \in \mathbb{R}^{n \times (MK+p)}$.
+		\widetilde{W}(\mathbf{t}) 
+		=  
+		\widetilde{ \mathbf{C} }^\ast B^*(\mathbf{t}), \quad t \in \mathcal{T}.
+	\end{equation}
+	where  $B^*(\mathbf{t}) = \mathrm{blkdiag}(B(\mathbf{t}), \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (K+p)}$ and $\widetilde{ \mathbf{C} }^\ast=[\widetilde{C}, \mathbf{Z}] \in \mathbb{R}^{n \times (MK+p)}$.
 
 	\paragraph{Basis approximation of the PLS component.}
-	We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\xi[\mathbf{t}] = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$.
+	We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\xi(\mathbf{t}) = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$.
 	%
@@
 
-	\section{Proof of Proposition \ref{Proposition: property of U}}\label{section:proof:Proposition: property of U}
-
-	Next, We will show that an image of a bounded family in $\mathcal{H}$ under $\mathcal{U}$ is uniformly bounded and equicontinuous, and then apply the Arzel\'{a}-Ascoli theorem to show $\mathcal{U}$ is \textit{compact}.
-Let $\mathcal{B}=\{\mathbf{h} \in \mathcal{H}: \Vert \mathbf{h} \Vert_\mathcal{H}^2 \le B\}$ denote a bounded family in $\mathcal{H}$ for some constant $0 < B < \infty$.
-Clearly, $\mathbf{h}=(f, \mathbf{v}) \in \mathcal{B}$ also implies $\Vert f \Vert_\mathcal{F}^2 \le B$ and $\Vert \mathbf{v} \Vert^2 \le B$.
-Define $\mathcal{I}  = \{\mathcal{U}\mathbf{h}: \mathbf{h} \in \mathcal{B}\}$ as the image of  $\mathcal{B}$ under $\mathcal{U}$.
-We will first show that $\mathcal{I}$ is a family of uniformly bounded functions with respect to arguments on $\mathcal{T}$.
-Let $\mu([0,1])$ denote a Lebesgue measure of $[0,1]$, and let $T = \max_{k=1, \ldots, K} \, \mu([0,1])$.
-Then for any $g \in \mathcal{I}$ and $\mathbf{t} \in \mathcal{T}$,
+	\section{Proof of Lemma \ref{Proposition: property of U}}\label{section:proof:Proposition: property of U}
+\begin{proof}
+	The brief strategy of the proof is as follows.
+		We   show that an image of a bounded family in $\mathcal{H}$ under $\mathcal{U}$ is uniformly bounded and equicontinuous.
+		Then we apply the Arzel\'{a}-Ascoli theorem to show that $\mathcal{U}$ is \textit{compact}.
+
+Let $\mathcal{B}=\{h \in \mathcal{H}: \Vert h \Vert_\mathcal{H}^2 \le M\}$ denote a bounded family in $\mathcal{H}$ for some constant $0 < M < \infty$.
+Clearly, $h=(f, \mathbf{v}) \in \mathcal{B}$ also implies 
+\begin{equation}\label{individual_norm_bound}
+\Vert f_k \Vert_\mathcal{F}^2 \le M,
+~k=1,\ldots,K, \quad\text{and}\quad
+\Vert \mathbf{v} \Vert^2 \le M.
+\end{equation}
+Define $\mathcal{I}  = \{\mathcal{U}h: h \in \mathcal{B}\}$ as the image of  $\mathcal{B}$ under $\mathcal{U}$.
+
+\medskip
+\noindent
+\textit{Uniform boundedness of $\mathcal{I}$.}~Given a hybrid object $h = (f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$ and an evaluation point $\mathbf{t}= (t_1, \ldots, t_k) \in [0,1]^K$, we denote the $\ell_2$ norm of the evaluated object $\bigl( f_1(t_1), \ldots, f_k(t_k), \mathbf{v} \bigr)$ as follows:
+$\bigl(
+f_1(t_1), \ldots, f_k(t_k), \mathbf{v}
+\bigr)$
+   as follows:
+\begin{equation*}
+	\| h (\mathbf{t}) \|_2^2 := \sum_{k=1}^K f^2_k(t_k) + \| \mathbf{v} \|_2^2.
+\end{equation*}
+ %We first show that $\mathcal{I}$ is a family of uniformly bounded functions with respect to arguments on $\mathcal{T}$.
+  Let $\mu([0,1])$ denote a Lebesgue measure of $[0,1]$, and let $T = \max_{k=1, \ldots, K} \, \mu([0,1])$. Then for any $g \in \mathcal{I}$ and $\mathbf{t} \in [0,1]^K$, 
+  by Lemma \ref{lemma:composite_cross_cov}, we have:
+  \begin{equation}\label{gtsq_expansion}
+\Vert g (\mathbf{t}) \Vert^2_2
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ = \Vert (\mathcal{U}h)(\mathbf{t}) \Vert^2_2 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ \overset{(i)}{=} 
+\Vert \langle \Sigma_{YW}, h \rangle_\mathcal{H} \, \Sigma_{YW}(\mathbf{t}) \Vert^2_2
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  =
+\langle \Sigma_{YW}, h \rangle_\mathcal{H}^2
+\Vert   \Sigma_{YW}(\mathbf{t}) \Vert^2_2.
+  \end{equation}
+  We will show that $\Vert g (\mathbf{t}) \Vert^2_2 < \infty$ by  showing $\langle \Sigma_{YW}, h \rangle_\mathcal{H}^2 < \infty$ and $\Vert   \Sigma_{YW}(\mathbf{t}) \Vert^2_2 < \infty$ in turn.
+First, to bound
+   $\langle \Sigma_{YW}, h \rangle_\mathcal{H}^2$, it suffices to bound $\langle \Sigma_{YW}, h \rangle_\mathcal{H}$:
 \begin{align*}
-		\Vert g[\mathbf{t}] \Vert^2 &= \Vert (\mathcal{U}\mathbf{h})[\mathbf{t}] \Vert^2 \\
-		&= \Vert \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} \, \Sigma_{YW}[\mathbf{t}] \Vert^2 \\
-		&= \left( \langle \sigma_{YX}, f \rangle_\mathcal{F} + \langle \sigma_{YZ}, \mathbf{v} \rangle \right)^2 \Vert [\sigma_{YX}^\top(\mathbf{t}), \sigma_{YZ}^\top]^\top \Vert^2 \\
-		&\le \left( \langle \sigma_{YX}, \sigma_{YX} \rangle_\mathcal{F}^{1/2} \langle f, f \rangle_\mathcal{F}^{1/2} + \langle \sigma_{YZ}, \sigma_{YZ} \rangle^{1/2} \langle \mathbf{v}, \mathbf{v} \rangle^{1/2} \right)^2 \Vert [\sigma_{YX}^\top(\mathbf{t}), \sigma_{YZ}^\top]^\top \Vert^2 \quad (\because \textnormal{CSI})\\
-		&= \left[ \left\{ \sum \limits_{k=1}^K \int_0^1 \sigma_{YX}^{(k)2}(t_k) dt_k \right\}^{\frac{1}{2}} \Vert f \Vert_\mathcal{F} + \left(\sum \limits_{r=1}^p \sigma_{YZ, r}^2 \right)^{\frac{1}{2}} \Vert \mathbf{v} \Vert \right]^2 \left(\sum \limits_{k=1}^K \sigma_{YX}^{(k)2}(t_k) + \sum \limits_{r=1}^p \sigma^2_{YZ,r} \right) \\
-		& \le \left\{ \left(\sum \limits_{k=1}^K \int_0^1 Q_1 dt_k \right)^{\frac{1}{2}} B^{\frac{1}{2}} + \left(\sum \limits_{r=1}^p Q_2 \right)^{\frac{1}{2}} B^{\frac{1}{2}} \right\}^2 \left( \sum \limits_{k=1}^K Q_1 + \sum \limits_{r=1}^p Q_2 \right) \\
-		&= B \left\{(KTQ_1)^{\frac{1}{2}} + (PQ_2)^\frac{1}{2} \right\}^2 (KQ_1 +pQ_2) < \infty.
+\langle \Sigma_{YW}, h \rangle_\mathcal{H}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&=
+\sum_{k=1}^K \langle \sigma_{YX, k}, \, f_k \rangle_\mathcal{F}  
++ 
+\langle \sigma_{YZ}, \, \mathbf{v} \rangle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&\overset{(i)}{\le}
+\sum_{k=1}^K 
+\langle \sigma_{YX, k}, \sigma_{YX, k} \rangle_\mathcal{F}^{1/2} 
+\langle f_k, f_k \rangle_\mathcal{F}^{1/2} + \langle \sigma_{YZ}, \sigma_{YZ} \rangle^{1/2} \langle \mathbf{v}, \mathbf{v} \rangle^{1/2}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&=
+  \sum \limits_{k=1}^K
+  \biggl(
+  	\int_0^1
+  	\sigma_{YX, k}^{2}(t)\, dt
+  	\biggr)^{1/2} 
+  	\Vert f_k \Vert_\mathcal{F} 
+  	+
+\biggl(
+\sum \limits_{r=1}^p \sigma_{YZ, r}^2
+\biggr)^{1/2}
+\Vert \mathbf{v} \Vert_2
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&\overset{(ii)}{<}
+ \sqrt{M}
+ \biggl\{
+\sum \limits_{k=1}^K 
+ \biggl(
+ \int_0^1 Q_1 dt
+ \biggr)^{1/2}
+ +
+ \biggl(
+ \sum \limits_{r=1}^p Q_2 
+ \biggr)^{\frac{1}{2}} 
+ \biggr\}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\ & = K\sqrt{M TQ_1}   + \sqrt{MpQ_2} < \infty.
+\numberthis \label{squared_ip_bound}
 \end{align*}
-	We now show that $\mathcal{I}$ is equicontinuous. For $\epsilon > 0$, define 
-	\begin{equation*}
-		\tilde{\epsilon} = \frac{\epsilon}{(KB)^{1/2} \{(KTQ_1)^{1/2} + (PQ_2)^{1/2}\}}
-	\end{equation*}
-	By the continuity assumption of $\sigma_{YX}^{(k)}$, there exists $\delta_k > 0$ such that
-	\begin{equation*}
-		|t_k - t_k^*| < \delta_k \implies |\sigma^{(k)}(t_k) - \sigma^{(k)}(t_k^*)|< \tilde{\epsilon},
-	\end{equation*}
-	for all $k=1, \ldots, K$.
-	Set $\delta = \min_{k=1, \ldots, K} \delta_k$, and let $\Vert \mathbf{t} - \mathbf{t}^* \Vert < \delta$, with $\mathbf{t}=(t_1, \ldots, t_K)$ and $\mathbf{t}^*=(t_1^*, \ldots, t_K^*)$.
-Clearly, $|t_k - t^*_k| < \delta$ for all $k=1, \ldots, K$, so for $g \in \mathcal{I}$, we can establish that
+where
+step $(i)$ uses Cauchy-Schwarz inequality,
+and
+step $(ii)$ uses the conditions \eqref{condition_for_compact} 
+and \eqref{individual_norm_bound}.
+
+Next, we bound $\Vert   \Sigma_{YW}(\mathbf{t}) \Vert^2_2  $:
 \begin{align*}
-		\Vert g[\mathbf{t}] - g[\mathbf{t}^*] \vert^2 &= \Vert (\mathbf{U}\mathbf{h})[\mathbf{t}] - (\mathbf{U}\mathbf{h})[\mathbf{t}^*] \Vert^2 \\
-		&= \Vert \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} \Sigma_{YW}[\mathbf{t}] - \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} \Sigma_{YW}[\mathbf{t}^*] \Vert^2 \\
-		&= \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}^2 \Vert \Sigma_{YW}[\mathbf{t}]- \Sigma_{YW}[\mathbf{t}^*] \Vert^2 \\
-		&= \left( \langle \sigma_{YX}, f \rangle_\mathcal{F} + \langle \sigma_{YZ}, \mathbf{v} \rangle \right)^2 \left\Vert 
-		\begin{bmatrix}
-			\sigma_{YX}(\mathbf{t}) \\
-			\sigma_{YZ}
-		\end{bmatrix} -
-		\begin{bmatrix}
-			\sigma_{YX}(\mathbf{t}^*) \\
-			\sigma_{YZ}
-		\end{bmatrix}
-		\right\Vert^2  \\
-		&\stackrel{CSI}{\le} \left( \langle \sigma_{YX}, \sigma_{YX} \rangle_\mathcal{F}^{1/2} \langle f, f \rangle_\mathcal{F}^{1/2} + \langle \sigma_{YZ}, \sigma_{YZ} \rangle^{1/2} \langle \mathbf{v}, \mathbf{v} \rangle^{1/2} \right)^2 \left\Vert
-		\begin{bmatrix}
-			\sigma_{YX}(\mathbf{t})-\sigma_{YX}(\mathbf{t}^*) \\
-			\mathbf{0}
-		\end{bmatrix}
-		\right\Vert^2 \\
-		&= \left[ \left\{ \sum \limits_{k=1}^K \int_0^1 \sigma_{YX}^{(k)2}(t_k) dt_k \right\}^{\frac{1}{2}} \Vert f \Vert_\mathcal{F} + \left(\sum \limits_{r=1}^p \sigma_{YZ, r}^2 \right)^{\frac{1}{2}} \Vert \mathbf{v} \Vert \right]^2 \sum \limits_{k=1}^K  \left\{\sigma_{YX}^{(k)}(t_k) -\sigma_{YX}^{(k)}(t_k^*) \right\}^2 \\
-		&\le B \left\{(KTQ_1)^{\frac{1}{2}} + (PQ_2)^\frac{1}{2} \right\} K\tilde{\epsilon}^2 = \epsilon^2.
+\Vert   \Sigma_{YW}(\mathbf{t}) \Vert^2_2  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+= %%%%%%%%%%%%%%%%%
+\sum \limits_{k=1}^K
+\sigma_{YX, k}^{2}(t_k)
++
+\sum \limits_{r=1}^p \sigma^2_{YZ,r}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+<
+\sum \limits_{k=1}^K Q_1 + \sum \limits_{r=1}^p Q_2 
+=  KQ_1 +pQ_2 < \infty.
 \end{align*}
-	Now we can apply the Arzel\'{a}-Ascoli theorem to conflude that for any bounded sequence $\{\mathbf{h}_n\}_{n \in \mathbb{N}} \in \mathcal{B}$, the sequence $\{\mathbf{g}_n = \mathcal{U}\mathbf{h}_n\}_{n \in \mathbb{N}} \in \mathcal{I}$ contains a convergent subsequence.
+Therefore, we have
+\begin{equation*}
+	\Vert g (\mathbf{t}) \Vert^2_2 < 
+	 2K^2 M TQ_1   + 2MpQ_2 + KQ_1 +pQ_2< \infty.
+\end{equation*}
+Since this bound does not depend on the evaluation point, we conclude that across all $g = (s_1(t), \ldots, s_K(t), \mathbf{w}) \in \mathcal{I}$, their functional components $s_1(t), \ldots, s_K(t)$ are uniformly bounded.
+
+\medskip
+\noindent
+\textit{Equicontinuity of $\mathcal{I}$.}~Given a hybrid object $h = (f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$ and 
+two evaluation points
+ $\mathbf{t}=(t_1, \ldots, t_K) \in [0,1]^K$
+ and
+ $\mathbf{t}^\ast=(t_1^\ast, \ldots, t_K^\ast) \in [0,1]^K$,
+we denote the $\ell_2$ distance between   two evaluations
+$\bigl( f_1(t_1), \ldots, f_k(t_k), \mathbf{v} \bigr)$ 
+and
+$\bigl( f_1(t^\ast_1), \ldots, f_k(t^\ast_k), \mathbf{v} \bigr)$
+as follows:
+\begin{equation*}
+	\| h (\mathbf{t}) - h (\mathbf{t}^\ast)\|_2^2 
+	:= 
+	\sum_{k=1}^K 
+	\bigl(
+	f_k(t_k) - f_k(t_k^\ast)
+	\bigr)^2 .
+\end{equation*}
+For any $g \in \mathcal{I}$, via similar computation as in \eqref{gtsq_expansion}, we have
+\begin{align*}
+	\Vert g(\mathbf{t}) - g ( \mathbf{t}^\ast ) \Vert_2^2 
+	%%%%%%%%%%%%%%%%%
+	= %%%%%%%%%%%%%%%%%%
+	\Vert 
+	(\mathcal{U}h)(\mathbf{t}) - (\mathcal{U}h)( \mathbf{t}^\ast ) 
+	\Vert_2^2
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&= %%%%%%%%%%%%%%%
+	\Vert \langle \Sigma_{YW}, h \rangle_\mathcal{H} 
+	\,
+	\Sigma_{YW}(\mathbf{t}) - \langle \Sigma_{YW}, h \rangle_\mathcal{H} \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2_2
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\\&=
+\langle \Sigma_{YW}, h \rangle_\mathcal{H}^2 \Vert \Sigma_{YW}(\mathbf{t})- \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2.
+\end{align*}
+We have already shown in \eqref{squared_ip_bound} that  $\langle \Sigma_{YW}, h \rangle_\mathcal{H}^2 \leq  2K^2 M TQ_1   + 2MpQ_2$.
+Next we bound $\Vert \Sigma_{YW}(\mathbf{t})- \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2$, which do not depend on $h$.
+\begin{align*}
+\Vert \Sigma_{YW}(\mathbf{t})- \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2_2	
+=%%%%%%%%%%%%%
+   \sum \limits_{k=1}^K  
+   \bigl\{
+   \sigma_{YX, k }(t_k) -\sigma_{YX, k}(t_k^\ast ) 
+   \bigr\}^2 
+& \leq%%%%%%%%%%%%%
+\sum \limits_{k=1}^K  
+\bigl\{
+2\sigma^2_{YX, k }(t_k) + 2\sigma^2_{YX, k}(t_k^\ast ) 
+\bigr\}
+%%%%%%%%%%%%%%%%%%%%%%
+\\& \le 
+4KQ_1.
+\end{align*}
+Therefore we have
+\begin{equation}\label{bound_elltwo_dist}
+	\Vert g(\mathbf{t}) - g ( \mathbf{t}^\ast ) \Vert_2^2 \leq 2K^2 M TQ_1   + 2MpQ_2 + 4KQ_1.
+\end{equation}
+Given $\epsilon > 0$, define 
+\begin{equation*}
+	\tilde{\epsilon}: = \frac{\epsilon}{  ( 2K^2 M TQ_1   + 2MpQ_2 + 4KQ_1 )^{1/2}}
+\end{equation*}
+By the uniform continuity assumption of $\sigma_{YX, k}$'s, there exists $\delta_k > 0$ such that
+\begin{equation*}
+	|t_k - t_k^\ast| < \delta_k \implies |\sigma_{YX, k}(t_k) - \sigma_{YX, k}(t_k^\ast)|< \tilde{\epsilon},~\text{for all}~k=1, \ldots, K.
+\end{equation*}
+Set $\delta := \min_{k=1, \ldots, K} \delta_k$.Then  by \eqref{bound_elltwo_dist},  
+across  $g = (s_1(t), \ldots, s_K(t), \mathbf{w}) \in \mathcal{I},$ for all $k=1, \ldots, K$, 
+$|t_k - t^*_k| < \delta$ implies $|s_k(t_k) - s_k(t_k^\ast)| < \epsilon$.
+
+\medskip
+\noindent
+\textit{Conclusion.}~ For any bounded sequence $\{h_n\}_{n \in \mathbb{N}} \in \mathcal{B}$, the sequence $\{\mathbf{g}_n = \mathcal{U}h_n\}_{n \in \mathbb{N}} \in \mathcal{I}$ contains a subsequence that converges in its first functional component, by the Arzel\'{a}-Ascoli theorem.
+We then apply the theorem again to that subsequence to extract a sub-subsequence that also converges in the second functional component.
+By repeating this process, we ultimately obtain a subsequence of $\{\mathbf{g}_n\}$ that converges in all its components.
 Therefore, $\mathcal{U}$ is a compact operator.
+\end{proof}
 
@@
 	\end{equation*}
-	Let $\Vert \cdot \Vert_{op}$ denote an operator norm. Then, applying Theorem 4.3.4 in \citet{Hsing2015}, we can show that
+	Let $\Vert \cdot \Vert_{op}$ denote an operator norm. Then, applying Theorem 4.3.4 in \citet{hsingTheoreticalFoundationsFunctional2015}, we can show that
 	\begin{equation*}

### 2025-08-14 manuscript/main.tex
mild condition for compactness
compact operator label change

@@
 	\begin{equation}\label{def:full_theta}
-		\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}.
+		\Theta := (\Theta_1, \ldots, \Theta_K, \mathbf{Z}) \in \mathbb{R}^{n \times (MK + p)}.
 	\end{equation}
@@
 \end{definition}
-Using this definition, the following lemma presents a condition for $\mathcal{U}$ to be a compact operator.
-	\begin{lemma}[Compactness condition] \label{Proposition: property of U}
+Using this definition, the following lemma states that $\mathcal{U}$ is a compact operator under a mild condition.
+	\begin{lemma}[Compactness condition] \label{lemma:compact_operator}
 If there exist finite constants $Q_1$ and $Q_2$ such that
@@
 \end{lemma}
-The proof of Lemma \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
-	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
+The proof of Lemma \ref{lemma:compact_operator} is provided in Appendix \ref{section:proof:lemma:compact_operator}.
+	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Proposition \ref{lemma:compact_operator} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
 
@@
 	\begin{proposition}\label{proposition: eigenanalysis}
-		\begin{equation*}
-			\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle \mathbf{W}, \xi \rangle_\mathcal{H}, Y \right)
+		Under the condition of 
+		\begin{equation*}
+			\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle  W , \,  \xi \rangle_\mathcal{H}, Y \right)
 		\end{equation*}
@@
 
-	\section{Proof of Lemma \ref{Proposition: property of U}}\label{section:proof:Proposition: property of U}
+	\section{Proof of Lemma \ref{lemma:compact_operator}}\label{section:proof:lemma:compact_operator}
 \begin{proof}
@@
 \section{Proof of Proposition \ref{proposition: eigenanalysis}}\label{section:proof:proposition: eigenanalysis}
+\begin{proof}
+	content...
+\end{proof}
 	Before we prove Proposition \ref{proposition: eigenanalysis}, we state and prove the following lemma:

### 2025-08-14 manuscript/main.tex
back to proposition

@@
 \end{definition}
-Using this definition, the following lemma states that $\mathcal{U}$ is a compact operator under a mild condition.
-	\begin{lemma}[Compactness condition] \label{lemma:compact_operator}
+Using this definition, the following proposition states that $\mathcal{U}$ is a compact operator under a mild condition.
+	\begin{proposition}[Compactness condition] \label{proposition:compact_operator}
 If there exist finite constants $Q_1$ and $Q_2$ such that
@@
 		then $\mathcal{U}$ is a compact operator.
-\end{lemma}
-The proof of Lemma \ref{lemma:compact_operator} is provided in Appendix \ref{section:proof:lemma:compact_operator}.
-	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Proposition \ref{lemma:compact_operator} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
+\end{proposition}
+The proof of Proposition \ref{proposition:compact_operator} is provided in Appendix \ref{section:proof:proposition:compact_operator}.
+	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Proposition \ref{proposition:compact_operator} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
 
 	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
-	\begin{proposition}\label{proposition: eigenanalysis}
-		Under the condition of 
-		\begin{equation*}
-			\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle  W , \,  \xi \rangle_\mathcal{H}, Y \right)
-		\end{equation*}
-		is achieved when $\xi$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.	
+\begin{proposition}[Existence of Maximizer for Covariance]\label{proposition: eigenanalysis} Under the conditions of Proposition \ref{proposition:compact_operator}, the constrained maximum
+	\begin{equation*} 
+		\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathcal{H}, Y \right)
+		\end{equation*} 
+	is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
 \end{proposition}
@@
 
-	\section{Proof of Lemma \ref{lemma:compact_operator}}\label{section:proof:lemma:compact_operator}
+	\section{Proof of Proposition \ref{proposition:compact_operator}}\label{section:proof:proposition:compact_operator}
 \begin{proof}

### 2025-08-14 manuscript/main.tex
adjoint proved

@@
 Based on these definitions, we introduce two cross-covariance operators.
-First, $\mathcal{C}_{YW}= \mathbb{E}(W_1 \otimes_\mathcal{H} Y_1): \mathcal{H} \rightarrow \mathbb{R}$ 
-maps  
+\begin{lemma}\label{lemma:cross_cov_operator}
+Define $\mathcal{C}_{YW}= \mathbb{E}(W_1 \otimes_\mathcal{H} Y_1): \mathcal{H} \rightarrow \mathbb{R}$,
+which	maps  
 	$h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$ to a real number:
@@
 	\end{equation*}
-Next, $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$
-maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:
+	Next, define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$,
+which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:
 	%%%%
@@
 	\end{align*}
+Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
+\end{lemma}
+The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.
 Based on these two operators, we define a positive   operator as follows:
@@
 	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
-\begin{proposition}[Existence of Maximizer for Covariance]\label{proposition: eigenanalysis} Under the conditions of Proposition \ref{proposition:compact_operator}, the constrained maximum
+\begin{theorem}[Population PLS]\label{proposition: eigenanalysis} Under the conditions of Proposition \ref{proposition:compact_operator}, the constrained maximum
 	\begin{equation*} 
@@
 	is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
-\end{proposition}
+\end{theorem}
 	The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
@@
 
+	\section{Proof of}
+
+	\subsection{Proof of Lemma \ref{lemma:cross_cov_operator}}\label{section:proof:lemma:cross_cov_operator}
+ \begin{proof}
+For $h \in \mathcal{H}$ and $d \in \mathbb{R}$, we have:
+\begin{equation*}
+\langle
+	\mathcal{C}_{YW} h, d \rangle 
+	= 
+\mathbb{E}
+	[
+		 \langle W_1, h \rangle_\mathcal{H} Y_1  
+	] 	 \,  d
+%%%%%%%%%%%%%%%%%%
+=
+\mathbb{E} \langle   Y_1 W_1 d , \, h\rangle_{\mathcal{H}} 
+%%%%%%%%%%%%%%%%%%%%%%%%
+ = \langle h, \, \mathbb{E}[Y_1 W_1 d   ]\rangle_{\mathcal{H}}
+ =
+ \langle h, \mathcal{C}_{WY} d \rangle_{\mathcal{H}}
+\end{equation*}
+Thus, we have $\langle \mathcal{C}_{YW} h, d \rangle =  \langle h, \mathcal{C}_{WY} d \rangle_{\mathcal{H}}$, which implies $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
+	This completes the proof of Lemma \ref{lemma:cross_cov_operator}.
+ \end{proof}
 	\section{Proof of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:eigen_regul} }\label{section:proof:proposition:linear_regul_system_unregularized}
@@
 \section{Proof of Proposition \ref{proposition: eigenanalysis}}\label{section:proof:proposition: eigenanalysis}
-\begin{proof}
-	content...
-\end{proof}
-	Before we prove Proposition \ref{proposition: eigenanalysis}, we state and prove the following lemma:
-	\begin{lemma}
-		$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^*$.
-	\end{lemma}
-	Proof.
-
-	\noindent First, we have:
-	\begin{equation*}
-		\langle \mathcal{C}_{YW} \mathbf{h}, d \rangle = E\{ \langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} d
-	\end{equation*}
-	Also, we have:
-	\begin{equation*}
-		\langle \mathbf{h}, \mathcal{C}_{WY} d \rangle_{\mathcal{H}} = \langle \mathbf{h}, E(Y\mathbf{W})d \rangle_{\mathcal{H}} = E \langle \mathbf{h}, Y \mathbf{W} d \rangle_{\mathcal{H}}  = E\{ \langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} d.
-	\end{equation*}
-	Thus, $\langle \mathcal{C}_{YW} \mathbf{h}, d \rangle =  \langle \mathbf{h}, \mathcal{C}_{WY} d \rangle_{\mathcal{H}}$, and this implies $\mathcal{C}_{WY} = \mathcal{C}_{YW}^*$.
 

### 2025-08-14 manuscript/main.tex
cross covariance functional compact

@@
 =
- (\sigma_{YX, 1} , \ldots, \sigma_{YX, K} )
+ \bigl(
+ \sigma_{YX, 1}(t) , \ldots, \sigma_{YX, K}(t) 
+ \bigr)
   :=
@@
 Based on these definitions, we introduce two cross-covariance operators.
+\begin{lemma}\label{lemma:cross_cov_functional}
+Define the operator $
+\mathcal{C}_{YW}
+=
+\mathbb{E}(W_1 \otimes_\mathcal{H} Y_1)
+: \mathcal{H} \rightarrow \mathbb{R}$ such that for any $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$, it maps $h$ to a real number as: \begin{equation*} \mathcal{C}_{YW} h := \mathbb{E} \left[ \langle W_1, h \rangle_\mathcal{H} Y_1 \right] = \langle \Sigma_{YW}, h \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt + \sigma_{YW}^\top \mathbf{v}.
+\end{equation*}
+If there exist finite constants $Q_1$ and $Q_2$ such that
+\begin{align}\label{condition_for_compact}
+	\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
+\end{align}
+the operator $\mathcal{C}_{YW}$ is a compact operator.
+\end{lemma}
+Proof of Lemma \ref{lemma:cross_cov_functional}
+is provided in Appendix \ref{section:proof:lemma:cross_cov_functional}.
 \begin{lemma}\label{lemma:cross_cov_operator}
-Define $\mathcal{C}_{YW}= \mathbb{E}(W_1 \otimes_\mathcal{H} Y_1): \mathcal{H} \rightarrow \mathbb{R}$,
+Define $\mathcal{C}_{YW}= : \mathcal{H} \rightarrow \mathbb{R}$,
 which	maps  
@@
 \end{lemma}
+
 The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.
@@
 The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
-To guarantee the existence of a complete orthonormal system of eigenfunctions for $\mathcal{U}$ in $\mathcal{H}$, we  first demonstrate that $\mathcal{U}$ is  a compact operator,
-that is,
-images of a bounded sequence contains a convergent subsequence (for a formal definition, see Definition 4.1.1 of \citealt{hsingTheoreticalFoundationsFunctional2015}).
+
+The fundamental property of classical scalar PLS is that the first eigenvector of the squared covariance matrix corresponds to the first PLS component direction.
+To derive an analogous result in the hybrid regression setting, we first demonstrate that $\mathcal{U}$ is a compact operator.
+This means that the image of any bounded sequence under $\mathcal{U}$ contains a convergent subsequence (for a formal definition, see Definition 4.1.1 of \citealt{hsingTheoreticalFoundationsFunctional2015}).
+The compactness of $\mathcal{U}$ is crucial as it guarantees the existence of a complete orthonormal system of eigenfunctions for $\mathcal{U}$ in $\mathcal{H}$.
 To this end, we begin by defining the notion of uniform continuity for the cross-covariance function defined in \eqref{def:cross_covariance_yx}:
-\begin{definition}[Uniform Continuity]\label{def:uniform_continuity}
+\begin{definition}[Uniform continuity]\label{def:uniform_continuity}
 	For each $k \in \{1, \ldots, K\}$, the cross-covariance function $\sigma_{YX, k} \in \mathcal{F}$ is uniformly continuous if for any $\epsilon > 0$, there exists a $\delta_k > 0$ such that for all $t_1, t_2 \in [0,1]$ satisfying $|t_1 - t_2 | < \delta_k$, we have
@@
 	\begin{proposition}[Compactness condition] \label{proposition:compact_operator}
-If there exist finite constants $Q_1$ and $Q_2$ such that
-		\begin{align}\label{condition_for_compact}
-			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
-		\end{align}
+
 		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous,
@@
 	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
-\begin{theorem}[Population PLS]\label{proposition: eigenanalysis} Under the conditions of Proposition \ref{proposition:compact_operator}, the constrained maximum
+\begin{theorem}[Population PLS]\label{theorem:population_PLS} Under the conditions of Proposition \ref{proposition:compact_operator}, the constrained maximum
 	\begin{equation*} 
@@
 \end{theorem}
-	The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
+	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.
 	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.
@@
 
+	\subsection{Proof of  Lemma \ref{lemma:cross_cov_functional} }\label{section:proof:lemma:cross_cov_functional}
+	\jongmin{An alternative proof to the compactness of $\mathcal{U}$; rather than directly showing $\mathcal{U}$ is compact, we show $\mathcal{C}_{YW}$ is compact}
+	\begin{proof} 
+	Any bounded linear functional from a Hilbert space to  $\mathbb{R}$  is a compact operator.
+	This is because the image of any bounded set under such a functional is a bounded set in $\mathbb{R}$,
+	and by Bolzano-Weierstrass Theorem, every bounded sequence of real numbers has a convergent subsequence.
+Therefore,  to show that $\mathcal{C}_{YW}$ is a compact operator, it suffices to show that 
+ $\mathcal{C}_{YW}$ is a bounded linear functional.
+
+\medskip
+\noindent
+\textit{Linearity.}~	  
+ The operator $\mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathbb{R}$ is defined as 
+ $\mathcal{C}_{YW} h = \langle \Sigma_{YW}, h \rangle_\mathcal{H}$.
+ For any $h_1, h_2 \in \mathcal{H}$ and scalar $c \in \mathbb{R}$, the linearity of the inner product implies: \begin{align*} \mathcal{C}_{YW}(h_1 + h_2) &= \langle \Sigma_{YW}, h_1 + h_2 \rangle_\mathcal{H} = \langle \Sigma_{YW}, h_1 \rangle_\mathcal{H} + \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H} = \mathcal{C}_{YW} h_1 + \mathcal{C}_{YW} h_2,
+ 	 \\ 
+ 	 \mathcal{C}_{YW}(c h) &= \langle \Sigma_{YW}, c h \rangle_\mathcal{H} = c \langle \Sigma_{YW}, h \rangle_\mathcal{H} = c \, \mathcal{C}_{YW} h. \end{align*}
+ Thus, $\mathcal{C}_{YW}$ is a linear functional.
+
+\medskip
+\noindent
+\textit{Boundedness.}~ 
+To show that $\mathcal{C}_{YW}$ is bounded, we need to find a finite constant $M$ such that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathcal{H}$ for all $h \in \mathcal{H}$.
+By the Cauchy-Schwarz inequality, we have: \begin{equation*}
+	|\mathcal{C}_{YW} h| = |\langle \Sigma_{YW}, h \rangle_\mathcal{H}| \leq \|\Sigma_{YW}\|_\mathcal{H} \|h\|_\mathcal{H}. 
+	\end{equation*}
+Now, we must verify that $\|\Sigma_{YW}\|_\mathcal{H}$ is finite. 
+Recall that 
+$$\Sigma_{YW} = (\sigma_{YX,1}(t), \ldots, \sigma_{YX,K}(t), \sigma_{YZ,1}, \ldots, \sigma_{YZ,p}).$$
+  Let $\mu([0,1])$ denote a Lebesgue measure of $[0,1]$, and let $T = \max_{k=1, \ldots, K} \, \mu([0,1])$.
+The norm of $\Sigma_{YW}$ in $\mathcal{H}$ is given by: \begin{equation*} \|\Sigma_{YW}\|_\mathcal{H}^2 = \sum_{k=1}^K \int_0^1 \sigma_{YX,k}(t)^2 \, dt + \sum_{r=1}^p \sigma_{YZ,r}^2
+	<
+	K T Q_1 + p  Q_2 < \infty,
+ \end{equation*} 
+ where the last inequality uses the condition \eqref{condition_for_compact}.
+ Let $M = \sqrt{K T Q_1 + p  Q_2 }$. Thus, we have shown that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathcal{H}$ for a finite constant $M$.
+ This completes the proof of Lemma \ref{lemma:cross_cov_functional}.
+
+   \end{proof}
 	\subsection{Proof of Lemma \ref{lemma:cross_cov_operator}}\label{section:proof:lemma:cross_cov_operator}
@@
 
-\section{Proof of Proposition \ref{proposition: eigenanalysis}}\label{section:proof:proposition: eigenanalysis}
-
-	\noindent Now we prove Proposition \ref{proposition: eigenanalysis}. The singular value decomposition of $\mathcal{C}_{YW}$ is given by
+\section{Proof of Theorem \ref{theorem:population_PLS}}\label{section:proof:theorem:population_PLS}
+ \begin{proof}
+Since Proposition \ref{proposition:compact_operator} implies that $\mathcal{U}$ is compact,
+by Theorem 4.3.1 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
+\end{proof}
+  The singular value decomposition of $\mathcal{C}_{YW}$ is given by
 	\begin{equation*}

### 2025-08-14 manuscript/main.tex
compact proof easily done

@@
 \end{equation*}
-Based on these definitions, we introduce two cross-covariance operators.
+Based on these definitions, we introduce two cross-covariance operators and their properties.
 \begin{lemma}\label{lemma:cross_cov_functional}
@@
 \end{equation*}
-If there exist finite constants $Q_1$ and $Q_2$ such that
+\jongmin{instead of showing $\mathcal{U}$ is compact, let's show $\mathcal{C}_{YW}$ is compact}If there exist finite constants $Q_1$ and $Q_2$ such that
 \begin{align}\label{condition_for_compact}
@@
 \begin{lemma}\label{lemma:cross_cov_operator}
-Define $\mathcal{C}_{YW}= : \mathcal{H} \rightarrow \mathbb{R}$,
-which	maps  
-	$h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$ to a real number:
-	\begin{equation*}
-		\mathcal{C}_{YW}
-		h
-		:=
-		\mathbb{E} 
-		\bigl[ 
-		\langle W_1, h \rangle_\mathcal{H} Y_1 
-		\bigr] 
-		= 
-		\langle \Sigma_{YW}, h \rangle_\mathcal{H}
-		=
-		\sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt 
-		+ 
-		\sigma_{YW}^\top \mathbf{v}.
-	\end{equation*}
-	Next, define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$,
+Define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$,
 which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:
@@
 The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.
+
 Based on these two operators, we define a positive   operator as follows:
@@
 		Then $\mathcal{U}$
-	 is self-adjoint and positive-semidefinite.
+	 is a self-adjoint, positive-semidefinite, and compact operator.
 \end{lemma}
@@
 \section{Proof of Lemma \ref{lemma:composite_cross_cov}}\label{section:proof:lemma:composite_cross_cov}
-\begin{proof}
-	The operator
-$\mathcal{U}$ is \textit{self-adjoint} because for any $h_1, h_2 \in \mathcal{H}$, we have
+\begin{proof}We show that $\mathcal{U}$ is self-adjoint, positive-semidefinite, and compact, in turn.
+
+\medskip
+\noindent
+\textit{Self-adjoint.}~
+For any $h_1, h_2 \in \mathcal{H}$, we have
 \begin{align*}
@@
 \rangle_\mathcal{H}  
-&= 
+= 
 \bigl \langle 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\\&= \langle h_1, \Sigma_{YW} \rangle_\mathcal{H} \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H}
+&= \langle h_1, \Sigma_{YW} \rangle_\mathcal{H} \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{align*}
-Next, 
-	$\mathcal{U}$ is \textit{positive-semidefinite} because for every $h \in \mathcal{H}$, we have
+
+\medskip
+\noindent
+\textit{Positive-semidefinite.}~
+For every $h \in \mathcal{H}$, we have
 \begin{equation*}
@@
 \end{equation*}
+
+\medskip
+\noindent
+\textit{Compact.}~
+	By Lemma \ref{lemma:cross_cov_functional}, $\mathcal{C}_{YW}$ is a compact operator.
+	By  Theorem 4.1.3 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
+	the composition of two operators is compact if either operator is compact. Therefore
+	$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}$ is a compact operator.
 This completes the proof of Lemma \ref{lemma:composite_cross_cov}.

### 2025-08-15 manuscript/main.tex
step outside

@@
 			:=
-			\sum \limits_{k=1}^K \int_0^1 X_{1k}(t) X_{2k}(t) \, dt
+			\sum \limits_{k=1}^K 
 			+ 
@@
 			\mathbf{Z}_1^\top \mathbf{Z}_2,
+			~\text{where}~\int_0^1 X_{1k}(t) X_{2k}(t) \, dt
 		\end{equation}
@@
 It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}).
-
+		Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$. The results remain valid for any positive weights. 
 	\begin{remark}
@@
 	\end{remark} 
-
 	%Write  $X=(X^{(1)}, \ldots, X^{(K)})$ as a multivariate functional object that belongs to $\mathcal{F} = L^2(\mathcal{T}_1) \times \cdots \times L^2([0,1])$---a cartesian product of individual $L^2([0,1])$ spaces.
@@
 	%An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}(\mathbf{t}) = (X(\mathbf{t}), \mathbf{Z})^\top$, with $ X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $ \mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.
-
-	Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$.
-The results remain valid for any positive weights.
-Then the functional regression model \eqref{eq: functional model} with multiple functional and scalar predictors can be re-expressed in terms of the scalar-on-hybrid regression model as follows
-	\begin{equation}
-		Y = \langle \boldsymbol{\eta}, \mathbf{W} \rangle_{\mathcal{H}} + \epsilon,
-		\label{eq: Hybrid functional model}
-	\end{equation}
-	where $\boldsymbol{\eta} = (\beta, \boldsymbol{\alpha}) \in \mathcal{H}$ is a hybrid regression coefficient characterizing the association between the hybrid predictor $\mathbf{W}$ and the outcome $Y$.
+Then the joint regression model \eqref{eq: functional model}  can be concisely written as
+	\begin{equation}		\label{eq: Hybrid functional model}
+		Y_i = \langle \beta, W_i \rangle_{\mathcal{H}} + \epsilon_i,~\text{where}~\beta := \bigl( \beta_1(t), \ldots, \beta_K(t), \boldsymbol{\beta} \bigr)\in \mathcal{H}.
+	\end{equation}
+
+	\section{Population PLS and Tucker's Criterion in hybrid regression setting}\label{section:main:tucker}\jongmin{Previously, was in theoretical property section, now procedes the method section, to motivate the estimation procedure}
 
@@
 	\end{enumerate}
+
+	The fundamental property of classical scalar PLS is that the PLS component direction  corresponds to the first eigenvector of the squared covariance matrix, satisfying  the Tucker's Criterion \citep{Tucker1938}.
+Under a mild assumption,
+	We derive an analogous result  in our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
+	 This justifies our estimation procedure introduced in Section \ref{section:main:our_algorithm}.
+	We omit $l$ in the notations and first define the cross-covariance term between the response and the functional predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$): 
+	\begin{equation}\label{def:cross_covariance_yx}
+		\sigma_{YX}
+		=
+		\bigl(
+		\sigma_{YX, 1}(t) , \ldots, \sigma_{YX, K}(t) 
+		\bigr)
+		:=
+		\bigl(
+		\mathbb{E}
+		[Y_1 X_{11}]
+		,\ldots, 
+		\mathbb{E}
+		[Y_1  X_{1K}]
+		\bigr)   \in \mathcal{F}^{\otimes K},
+	\end{equation}
+	and between the response and the scalar predictor:
+	\begin{equation*}
+		\sigma_{YZ} 
+		= 
+		(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
+		:= 
+		\bigl(
+		\mathbb{E}[Y_1 Z_{11}]
+		,\ldots,
+		\mathbb{E}[Y_1 Z_{1p}]
+		\bigr)^\top %= E(Y\mathbf{Z})
+		\in \mathbb{R}^p.
+	\end{equation*}
+	Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
+	\begin{equation*}
+		\Sigma_{YW} :=  
+		\mathbb{E}
+		[ Y_1 W_1 ]
+		=
+		\bigl(
+		\sigma_{YX, 1} , \ldots, \sigma_{YX, K} , \, \sigma_{YZ}
+		\bigr) \in \mathcal{H}.
+	\end{equation*}
+	Based on these definitions, we introduce two cross-covariance operators and their properties.
+	\begin{lemma}\label{lemma:cross_cov_functional}
+		Define the operator $
+		\mathcal{C}_{YW}
+		=
+		\mathbb{E}(W_1 \otimes_\mathcal{H} Y_1)
+		: \mathcal{H} \rightarrow \mathbb{R}$ such that for any $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$, it maps $h$ to a real number as: \begin{equation*} \mathcal{C}_{YW} h := \mathbb{E} \left[ \langle W_1, h \rangle_\mathcal{H} Y_1 \right] = \langle \Sigma_{YW}, h \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt + \sigma_{YW}^\top \mathbf{v}.
+\end{equation*}
+		\jongmin{instead of showing $\mathcal{U}$ is compact, let's show $\mathcal{C}_{YW}$ is compact.
+This way, we don't need uniform continuiity of $\sigma_{YX}$.}If there exist finite constants $Q_1$ and $Q_2$ such that
+		\begin{align}\label{condition_for_compact}
+			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
+		\end{align}
+		the operator $\mathcal{C}_{YW}$ is a compact operator.
+	\end{lemma}
+	Proof of Lemma \ref{lemma:cross_cov_functional}
+	is provided in Appendix \ref{section:proof:lemma:cross_cov_functional}.
+	\begin{lemma}\label{lemma:cross_cov_operator}
+		Define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$,
+		which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:
+		%%%%
+		\begin{align*}		
+			\mathcal{C}_{WY} d 
+			:= 
+			\mathbb{E} 
+			\bigl[
+			\langle Y_1, d \rangle W_1 
+			\bigr] 
+			= 
+			\mathbb{E}
+			[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
+		\end{align*}
+		Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
+	\end{lemma}
+
+	The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.
+
+	Based on these two operators, we define a positive   operator as follows:
+	\begin{lemma}[Composite cross-covariance operator]\label{lemma:composite_cross_cov}
+		Define
+		$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ as an operator which performs the following mapping:
+		\begin{equation*}
+			\mathcal{U} h 
+			= 
+			\mathcal{C}_{WY} ( \mathcal{C}_{YW} h) 
+			=
+			\mathcal{C}_{YW} (\langle \Sigma_{YW}, h \rangle_\mathcal{H}) 
+			=  
+			\Sigma_{YW} \, \langle \Sigma_{YW}, h \rangle_\mathcal{H} 
+			= 
+			(\Sigma_{YW} \otimes \Sigma_{YW}) h.
+		\end{equation*}
+		In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$.
+		Then $\mathcal{U}$
+		is a self-adjoint and positive-semidefinite operator.
+		Under the conditions of Lemma \ref{lemma:cross_cov_functional}, $\mathcal{U}$ is a compact operator.
+	\end{lemma}
+	The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
+	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Lemma \ref{lemma:composite_cross_cov} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
+
+	The following theorem introduces the population-level PLS and Tucker's Criterion, adapted to our scalar-on-hybrid regression model setting, based on the aforementioned operators defined in the hybrid space.
+	\begin{theorem}[Population PLS and Tucker's criterion]\label{theorem:population_PLS} Under the conditions of Lemma \ref{lemma:cross_cov_functional}, the constrained maximum
+		\begin{equation*} 
+			\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathcal{H}, Y \right)
+		\end{equation*} 
+		is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
+	\end{theorem}
+	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.
+	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]}  W^{[l]})$.
 
@@
 
-	\section{Proposed PLS Algorithm} \label{sec: Proposed PLS Algorithm}
+	\section{Proposed PLS Algorithm} \label{section:main:our_algorithm}
 	To address the limitations outlined in Section \ref{sec: Naive PLS Algorithm}, we propose  novel strategies for implementing the steps of the hybrid PLS algorithm.
@@
 	\label{section:main:properties_of_our_method}
-	\jongmin{notation not yet changed}
-
-	In this section, we derive some of the theoretical and geometric properties of the proposed PLS framework.
-
-	\subsection{Tucker's Criterion}\jongmin{notation not yet changed}
-	We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
-We omit $l$ in the notations and first define the cross-covariance term between the response and the functional predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$):
-	\begin{equation}\label{def:cross_covariance_yx}
-\sigma_{YX}
-=
- \bigl(
- \sigma_{YX, 1}(t) , \ldots, \sigma_{YX, K}(t) 
- \bigr)
-  :=
-\bigl(
-\mathbb{E}
-[Y_1 X_{11}]
-,\ldots, 
-\mathbb{E}
-[Y_1  X_{1K}]
-\bigr)   \in \mathcal{F}^{\otimes K},
-	\end{equation}
-and between the response and the scalar predictor:
-\begin{equation*}
-\sigma_{YZ} 
-= 
-(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
-:= 
-\bigl(
-\mathbb{E}[Y_1 Z_{11}]
-,\ldots,
-\mathbb{E}[Y_1 Z_{1p}]
-\bigr)^\top %= E(Y\mathbf{Z})
-\in \mathbb{R}^p.
-\end{equation*}
-Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
-\begin{equation*}
-\Sigma_{YW} :=  
-\mathbb{E}
-[ Y_1 W_1 ]
-=
-\bigl(
-\sigma_{YX, 1} , \ldots, \sigma_{YX, K} , \, \sigma_{YZ}
-\bigr) \in \mathcal{H}.
-\end{equation*}
-Based on these definitions, we introduce two cross-covariance operators and their properties.
-\begin{lemma}\label{lemma:cross_cov_functional}
-Define the operator $
-\mathcal{C}_{YW}
-=
-\mathbb{E}(W_1 \otimes_\mathcal{H} Y_1)
-: \mathcal{H} \rightarrow \mathbb{R}$ such that for any $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$, it maps $h$ to a real number as: \begin{equation*} \mathcal{C}_{YW} h := \mathbb{E} \left[ \langle W_1, h \rangle_\mathcal{H} Y_1 \right] = \langle \Sigma_{YW}, h \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt + \sigma_{YW}^\top \mathbf{v}.
-\end{equation*}
-\jongmin{instead of showing $\mathcal{U}$ is compact, let's show $\mathcal{C}_{YW}$ is compact}If there exist finite constants $Q_1$ and $Q_2$ such that
-\begin{align}\label{condition_for_compact}
-	\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
-\end{align}
-the operator $\mathcal{C}_{YW}$ is a compact operator.
-\end{lemma}
-Proof of Lemma \ref{lemma:cross_cov_functional}
-is provided in Appendix \ref{section:proof:lemma:cross_cov_functional}.
-\begin{lemma}\label{lemma:cross_cov_operator}
-Define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$,
-which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:
-	%%%%
-	\begin{align*}		
-		\mathcal{C}_{WY} d 
-		:= 
-		\mathbb{E} 
-		\bigl[
-		\langle Y_1, d \rangle W_1 
-		\bigr] 
-		= 
-		\mathbb{E}
-		[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
-	\end{align*}
-Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
-\end{lemma}
-
-The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.
-
-Based on these two operators, we define a positive   operator as follows:
-\begin{lemma}[Composite cross-covariance operator]\label{lemma:composite_cross_cov}
-Define
-	$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ as an operator which performs the following mapping:
-	\begin{equation*}
-		\mathcal{U} h 
-		= 
-		\mathcal{C}_{WY} ( \mathcal{C}_{YW} h) 
-		=
-		\mathcal{C}_{YW} (\langle \Sigma_{YW}, h \rangle_\mathcal{H}) 
-		=  
-		\Sigma_{YW} \, \langle \Sigma_{YW}, h \rangle_\mathcal{H} 
-		= 
-		(\Sigma_{YW} \otimes \Sigma_{YW}) h.
-	\end{equation*}
-		In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$.
-		Then $\mathcal{U}$
-	 is a self-adjoint, positive-semidefinite, and compact operator.
-\end{lemma}
-The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
-
-The fundamental property of classical scalar PLS is that the first eigenvector of the squared covariance matrix corresponds to the first PLS component direction.
-To derive an analogous result in the hybrid regression setting, we first demonstrate that $\mathcal{U}$ is a compact operator.
-This means that the image of any bounded sequence under $\mathcal{U}$ contains a convergent subsequence (for a formal definition, see Definition 4.1.1 of \citealt{hsingTheoreticalFoundationsFunctional2015}).
-The compactness of $\mathcal{U}$ is crucial as it guarantees the existence of a complete orthonormal system of eigenfunctions for $\mathcal{U}$ in $\mathcal{H}$.
-To this end, we begin by defining the notion of uniform continuity for the cross-covariance function defined in \eqref{def:cross_covariance_yx}:
-\begin{definition}[Uniform continuity]\label{def:uniform_continuity}
-	For each $k \in \{1, \ldots, K\}$, the cross-covariance function $\sigma_{YX, k} \in \mathcal{F}$ is uniformly continuous if for any $\epsilon > 0$, there exists a $\delta_k > 0$ such that for all $t_1, t_2 \in [0,1]$ satisfying $|t_1 - t_2 | < \delta_k$, we have
-$
-		| \sigma_{YX, k} (t_1) - \sigma_{YX, k} (t_2) | < \epsilon.
-$
-\end{definition}
-Using this definition, the following proposition states that $\mathcal{U}$ is a compact operator under a mild condition.
-	\begin{proposition}[Compactness condition] \label{proposition:compact_operator}
-
-		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous,
-		then $\mathcal{U}$ is a compact operator.
-\end{proposition}
-The proof of Proposition \ref{proposition:compact_operator} is provided in Appendix \ref{section:proof:proposition:compact_operator}.
-	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Proposition \ref{proposition:compact_operator} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
-
-	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
-\begin{theorem}[Population PLS]\label{theorem:population_PLS} Under the conditions of Proposition \ref{proposition:compact_operator}, the constrained maximum
-	\begin{equation*} 
-		\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathcal{H}, Y \right)
-		\end{equation*} 
-	is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
-\end{theorem}
-	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.
-	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.
-
-	\subsection{Geometric Properties}\label{section:sub:prop_geom}
 	In this section, we derive several geometric properties of the PLS components and and scores obtained from the proposed algorithm.
@@
 
-	\section{Proof of}
+	\section{Proof of Section \ref{section:main:tucker}}
 
@@
  \end{proof}
+
+\subsection{Proof of Lemma \ref{lemma:composite_cross_cov}}\label{section:proof:lemma:composite_cross_cov}
+\begin{proof}We show that $\mathcal{U}$ is self-adjoint, positive-semidefinite, and compact, in turn.
+
+	\medskip
+	\noindent
+	\textit{Self-adjoint.}~
+	For any $h_1, h_2 \in \mathcal{H}$, we have
+	\begin{align*}
+		\langle 
+		\mathcal{U} h_1, \, h_2 
+		\rangle_\mathcal{H}  
+		= 
+		\bigl \langle 
+		\langle h_1, \Sigma_{YW} \rangle_\mathcal{H} \Sigma_{YW},
+		\,
+		h_2
+		\bigr \rangle_\mathcal{H}
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		&= \langle h_1, \Sigma_{YW} \rangle_\mathcal{H} \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H}
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\\&= 
+		\bigl \langle 
+		h_1,
+		\,
+		\langle \Sigma_{YW}, h_2 \rangle_\mathcal{H} \Sigma_{YW} 
+		\bigr \rangle_\mathcal{H}
+		\\ 	&= \langle h_1, \mathcal{U} h_2 \rangle_\mathcal{H}.
+	\end{align*}
+
+	\medskip
+	\noindent
+	\textit{Positive-semidefinite.}~
+	For every $h \in \mathcal{H}$, we have
+	\begin{equation*}
+		\langle 
+		\mathcal{U} h,
+		\,
+		h
+		\rangle_\mathcal{H}
+		=
+		\bigl \langle 
+		\langle 
+		\Sigma_{YW},\, h \rangle_{\mathcal{H}}  \Sigma_{YW}, \, h
+		\bigr \rangle_\mathcal{H}
+		= \langle \Sigma_{YW}, \, h \rangle_\mathcal{H}^2 \ge 0.
+	\end{equation*}
+
+	\medskip
+	\noindent
+	\textit{Compact.}~
+	By Lemma \ref{lemma:cross_cov_functional}, $\mathcal{C}_{YW}$ is a compact operator.
+	By  Theorem 4.1.3 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
+	the composition of two operators is compact if either operator is compact. Therefore
+	$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}$ is a compact operator.
+	This completes the proof of Lemma \ref{lemma:composite_cross_cov}.
+\end{proof}
+
+\subsection{Proof of Theorem \ref{theorem:population_PLS}}\label{section:proof:theorem:population_PLS}
+\begin{proof}
+	by Theorem 4.3.1 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
+	since $\mathcal{C}_{YW}$ is compact by Lemma \ref{lemma:cross_cov_functional}, it 
+	has the singular value decomposition of $\mathcal{C}_{YW}$, given by:
+\begin{equation*}
+	\mathcal{C}_{YW} = \sum \limits_{j=1}^\infty \iota_j (f_{1j} \otimes f_{2j}).
+\end{equation*}
+Let $\Vert \cdot \Vert_{\mathrm{op}}$ denote an operator norm. By  4.3.4 in \citet{hsingTheoreticalFoundationsFunctional2015}, we have
+\begin{equation*}
+	\Vert \mathcal{C}_{YW} \Vert_{\mathrm{op}} = \sup_{\substack{h \in \mathcal{H} \\ \Vert h \Vert_\mathcal{H}=1}} | \mathcal{C}_{YW} h |^2 
+	= \sup_{\substack{h \in \mathcal{H} \\ \Vert h \Vert_\mathcal{H}=1}} | E(\langle W, h \rangle_\mathcal{H} Y)|^2 
+	= \sup_{\substack{h \in \mathcal{H} \\ \Vert h \Vert_\mathcal{H}=1}} \textnormal{Cov}^2(\langle W, h \rangle_\mathcal{H}, Y) 
+	= \kappa_1^2,
+\end{equation*}
+with maximum attained at $h=f_{11}$, which is an eigenfunction of  $\mathcal{C}_{YW}^* \, \circ \, \mathcal{C}_{YW} = \mathcal{C}_{WY} \, \circ \, \mathcal{C}_{YW} = \mathcal{U}$ corresponding to the largest eigenvalue $\kappa_1^2.$
+This completes the proof of Theorem \ref{theorem:population_PLS}.
+\end{proof}
+
 	\section{Proof of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:eigen_regul} }\label{section:proof:proposition:linear_regul_system_unregularized}
@@
 
-\section{Proof of Lemma \ref{lemma:composite_cross_cov}}\label{section:proof:lemma:composite_cross_cov}
-\begin{proof}We show that $\mathcal{U}$ is self-adjoint, positive-semidefinite, and compact, in turn.
-
-\medskip
-\noindent
-\textit{Self-adjoint.}~
-For any $h_1, h_2 \in \mathcal{H}$, we have
-\begin{align*}
-\langle 
-\mathcal{U} h_1, \, h_2 
-\rangle_\mathcal{H}  
-= 
-\bigl \langle 
-	\langle h_1, \Sigma_{YW} \rangle_\mathcal{H} \Sigma_{YW},
-	\,
-	h_2
-\bigr \rangle_\mathcal{H}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&= \langle h_1, \Sigma_{YW} \rangle_\mathcal{H} \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\\&= 
-\bigl \langle 
-h_1,
-\,
- \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H} \Sigma_{YW} 
-\bigr \rangle_\mathcal{H}
-\\ 	&= \langle h_1, \mathcal{U} h_2 \rangle_\mathcal{H}.
-\end{align*}
-
-\medskip
-\noindent
-\textit{Positive-semidefinite.}~
-For every $h \in \mathcal{H}$, we have
-\begin{equation*}
-\langle 
-	\mathcal{U} h,
-	\,
-	h
-\rangle_\mathcal{H}
-=
-\bigl \langle 
-	\langle 
-		\Sigma_{YW},\, h \rangle_{\mathcal{H}}  \Sigma_{YW}, \, h
-\bigr \rangle_\mathcal{H}
-	= \langle \Sigma_{YW}, \, h \rangle_\mathcal{H}^2 \ge 0.
-\end{equation*}
-
-\medskip
-\noindent
-\textit{Compact.}~
-	By Lemma \ref{lemma:cross_cov_functional}, $\mathcal{C}_{YW}$ is a compact operator.
-	By  Theorem 4.1.3 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
-	the composition of two operators is compact if either operator is compact. Therefore
-	$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}$ is a compact operator.
-This completes the proof of Lemma \ref{lemma:composite_cross_cov}.
-\end{proof}
-
+\begin{comment}
 	\section{Proof of Proposition \ref{proposition:compact_operator}}\label{section:proof:proposition:compact_operator}
@@
 \end{proof}
-
-\section{Proof of Theorem \ref{theorem:population_PLS}}\label{section:proof:theorem:population_PLS}
- \begin{proof}
-Since Proposition \ref{proposition:compact_operator} implies that $\mathcal{U}$ is compact,
-by Theorem 4.3.1 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
-\end{proof}
-  The singular value decomposition of $\mathcal{C}_{YW}$ is given by
-	\begin{equation*}
-		\mathcal{C}_{YW} = \sum \limits_{j=1}^\infty \iota_j (f_{1j} \otimes f_{2j}).
-	\end{equation*}
-	Let $\Vert \cdot \Vert_{op}$ denote an operator norm. Then, applying Theorem 4.3.4 in \citet{hsingTheoreticalFoundationsFunctional2015}, we can show that
-	\begin{equation*}
-		\Vert \mathcal{C}_{YW} \Vert_{op} = \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} | \mathcal{C}_{YW} \mathbf{h} |^2 
-		= \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} | E(\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y)|^2 
-		= \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} \textnormal{Cov}^2(\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H}, Y) 
-		= \kappa_1^2,
-	\end{equation*}
-	with maximum attained at $\mathbf{h}=f_{11}$, which is an eigenfunction of  $\mathcal{C}_{YW}^* \, \circ \, \mathcal{C}_{YW} = \mathcal{C}_{WY} \, \circ \, \mathcal{C}_{YW} = \mathcal{U}$ corresponding to the largest eigenvalue $\kappa_1^2.$
+\end{comment}
 

### 2025-08-16 manuscript/main.tex
scalar nipals

@@
 	\end{equation}
-	where $Y_i$ is a scalar response, $\mathbf{Z}_i$ is a Euclidean vector covariate, 
-	$X_{i1}(t), \ldots, X_{iK}(t)$ are functional predicters, and $\epsilon_i$ is an observational noise.
+where $Y_i$ is a scalar response, $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ is a Euclidean vector covariate, $X_{i1}(t), \ldots, X_{iK}(t)$ are functional predictors that belong to $L^2[0,1]$, and $\epsilon_i$ is observational noise.
+In other words, this is a scalar-on-hybrid regression where the hybrid covariates belong to $L^2[0,1]^{\otimes K} \times \mathbb{R}^p$.
 	For notational convenience, we assume throughout this paper that the responses and predictors have been centered, allowing the intercept term to be ignored.
 	%where $\boldsymbol{\alpha}=(\alpha_1, \ldots, \alpha_p)^\top \in \mathbb{R}^p$ and $\beta=(\beta^{(1)}, \ldots, \beta^{(K)}) \in \mathcal{F}$ are respectively the regression coefficient vector and function that characterize the effect of scalar and functional predictors on the outcome.
+		%which is defined as the space of real-valued functions on $[0,1]$
+	%	which are square-integrable with respect to the Lebesgue measure $dt$ on $[0,1]$, 
+%	and possess second  derivatives.
+
+	%denote a $p$-dimensional multivariate scalar data in $\mathbb{R}^p$, assumed to be a random vector with finite first two moments, equipped with the Euclidean inner product and norm.
 
@@
 
-	\section{Data Objects and Model Formulation} \jongmin{still revising}
-	For $k = 1, \ldots, K$, 
-	we assume that the functional predictors $X_{ik}(t)$ are observed on the domain $0 \leq t \leq 1$, and belong to $\mathcal{F}$,
-	which is defined as the space of real-valued functions on $[0,1]$
-	which are square-integrable with respect to the Lebesgue measure $dt$ on $[0,1]$,
-	and possess second  derivatives.
-	Additionally, let $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$
-	denote a $p$-dimensional multivariate scalar data in $\mathbb{R}^p$, assumed to be a random vector with finite first two moments, equipped with the Euclidean inner product and norm.
-	% i.e., for $\mathbf{v_1}=(v_{11}, \ldots, v_{1p})^\top$ and $\mathbf{v_2}=(v_{21}, \ldots, v_{2p})^\top$ in $\mathbb{R}^p$, $\langle \mathbf{v_1}, \mathbf{v_2} \rangle = \mathbf{v_1}^\top \mathbf{v_2} = \sum_{r=1}^p v_{1r}v_{2r}$, and $\Vert \mathbf{v}_1 \Vert = \langle \mathbf{v}_1, \mathbf{v}_1 \rangle^{1/2} = (\sum_{r=1}^p v_{1r}^2)^{1/2}$.
-	The hybrid random predictor and corresponding inner product is formally defined as follows.
-	\begin{definition}[Hybrid predictor and inner product]\label{def:hilbert_space}
-		We define a  hybrid predictor  $W_i$ as an ordered pair combining the functional predictors $X_{i1}(t), \ldots, X_{iK}(t)$ and a scalar predictor $\mathbf{Z}_i$:
-		\begin{equation}\label{def:hybid_predictor}
-			W_i := (X_{i1}, \ldots, X_{iK}, \mathbf{Z}_i)
-			\in \mathcal{H} :=  \mathcal{F}^{\otimes K} \times \mathbb{R}^p
-		\end{equation}
-		The inner product between two hybrid predictors,
-		$W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$
-		and
-		$W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$, is then defined as:
-		\begin{equation}		\label{eq: hybrid inner product}
-			\langle W_1, W_2\rangle_{\mathcal{H}}
-			:=
-			\sum \limits_{k=1}^K 
-			+ 
-			\omega
-			\mathbf{Z}_1^\top \mathbf{Z}_2,
-			~\text{where}~\int_0^1 X_{1k}(t) X_{2k}(t) \, dt
-		\end{equation}
-		for $\omega > 0$.
-		The corresponding norm $\Vert \cdot \Vert_\mathcal{H}$ is derived from this inner product as $\langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
-	\end{definition}
-	In \eqref{eq: hybrid inner product}, 
-	$\omega$ is a positive weight that needs to be pre-specified or estimated.
-It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}).
-		Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$. The results remain valid for any positive weights. 
-	\begin{remark}
-		Our method is applicable to settings where each functional predictor belongs to a different Hilbert space, possibly defined over a distinct compact domain in $\mathbb{R}^d$, for arbitrary $d$, and observed at different time points.
-However, for notational simplicity, our discussion assumes a common Hilbert space over domain $[0,1]$ for all functional predictors.
-	\end{remark} 
+	\section{Background on partial least squares and its extension to hybrid predictors} \jongmin{still revising}
+For intuition, let us return to the high-dimensional Euclidean predictor setting $
+Y_i =  \boldsymbol{\beta}^\top \mathbf{Z}_i + \epsilon_i$.
+A common way to address ill-posedness and correlation is to approximate the high-dimensional vector $\mathbf{Z}_i$ using a low-dimensional vector $
+\bigr(
+\widehat{\rho}_1^{[1]}, \ldots,   \widehat{\rho}_1^{[L]}  
+\bigr)^\top.
+$ To retain the regression relationship, the $l$-th PLS direction $\hat{\boldsymbol{\xi}}_l$ solves:
+\begin{equation*}
+\max_{ \boldsymbol{ \alpha } } 
+\widehat{\operatorname{Cov}}^2
+\bigl(
+\{
+\langle 
+\boldsymbol{\alpha}, \mathbf{Z}_i
+\rangle
+, Y_i
+\}_{i=1}^n
+\bigr)~\text{s.t.}~\| \boldsymbol{\alpha} \|_2 = 1,~\boldsymbol{\alpha}^\top  \widehat{\operatorname{Cov}}^2
+\bigl(
+\{
+  \mathbf{Z}_i
+ \}_{i=1}^n
+ \bigr) \hat{\boldsymbol{\xi}}_j = 0, \quad j = 1, \ldots, l-1,
+\end{equation*}
+ where the two $\widehat{\operatorname{Cov}}^2$ denote sample cross-covariance and sample covariance, respectively.
+A standard algorithm for solving this problem, called nonlinear iterative partial least squares (NIPALS) is presented in Algorithm \ref{scalar_pls}.
+ \begin{algorithm} 
+ 	\caption{Scalar partial least squares }\label{scalar_pls}
+ 	\begin{algorithmic}[1]
+ 		\State Standardize each $\mathbf{Z}_1, \ldots, \mathbf{Z}_n$ so that each feature have mean zero and variance one. Standardize $Y_1, \ldots, Y_n$.
+ 		\For{$l = 1, 2, \ldots, L$}
+ 		\\
+ 		\textbf{PLS direction and score estimation:}
+ 		\State $\widehat{\boldsymbol{\xi}}_l \leftarrow
+ 		\arg \max_{  \boldsymbol{\alpha}   } 
+ 		\widehat{\operatorname{Cov}}^2
+ 		\bigl(
+ 		\{
+ 		\langle 
+ 		\boldsymbol{\alpha}, \mathbf{Z}^{[l]}_i
+ 		\rangle
+ 		, Y^{[l]}_i
+ 		\}_{i=1}^n
+ 		\bigr)~\text{s.t.}~\| \boldsymbol{\alpha} \|_2 = 1
+ 		$
+ 		\Comment{PLS direction}\label{possible?}
+ 		\State 
+ 		$
+ 		\widehat{\rho}_i^{[l]} \leftarrow \langle \hat{\boldsymbol{\xi}}_l,   \mathbf{Z}_i \rangle, 
+ 		~i=1,  \ldots, n
+ 		$ \Comment{PLS score}
+  		\\
+ \textbf{Residualization:}
+ 		\State $\nu^{[l]} 
+ 		\leftarrow
+ 		 \frac{
+ 		 	\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{i}^{[l]}}{
+ 		 	\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}
+ 		 	}$
+ 		%
+ 		\State $ Y_i^{[l+1]} \leftarrow Y_i^{[l]} - \nu^{[l]}\widehat{\rho}_i^{[l]}~i=1,  \ldots, n$
+ 		%
+ 		\State $ \widehat{\boldsymbol{\delta}}^{[l]}  \leftarrow \frac{1}{\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}}\sum_{i=1}^n  \widehat{\rho}_{i}^{[l]}\mathbf{Z}_i^{[l]}.
+ 	$
+\State $\mathbf{Z}_i^{[l+1]}  \leftarrow \mathbf{Z}_i^{[l]} -   \widehat{\rho}_{i}^{[l]}  \widehat{\boldsymbol{\delta}}^{[l]} $
+ 		\EndFor
+\textbf{Regression coefficient recovery:}
+\State
+$\widehat{\boldsymbol{\zeta}}^{[1]} \leftarrow \widehat{\boldsymbol{\xi}}^{[1]}$
+	\For{$l =  2, \ldots, L$}
+  \State $\widehat{\boldsymbol{\zeta}}^{[l]} \leftarrow \widehat{ \boldsymbol{\xi} }^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}^{[u]}, \widehat{\boldsymbol{\xi}}^{[l]} \rangle  \widehat{\boldsymbol{\zeta}}^{[u]}$
+ 		\EndFor
+$	\widehat{\boldsymbol{\beta}} \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{\boldsymbol{\zeta}}^{[l]}$
+ 		\State \textbf{Output:} the  regression coefficient estimate
+
+ 	\end{algorithmic}
+ \end{algorithm}
+% $, 
 	%Write  $X=(X^{(1)}, \ldots, X^{(K)})$ as a multivariate functional object that belongs to $\mathcal{F} = L^2(\mathcal{T}_1) \times \cdots \times L^2([0,1])$---a cartesian product of individual $L^2([0,1])$ spaces.
@@
 	%An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}(\mathbf{t}) = (X(\mathbf{t}), \mathbf{Z})^\top$, with $ X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $ \mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.
-Then the joint regression model \eqref{eq: functional model}  can be concisely written as
-	\begin{equation}		\label{eq: Hybrid functional model}
-		Y_i = \langle \beta, W_i \rangle_{\mathcal{H}} + \epsilon_i,~\text{where}~\beta := \bigl( \beta_1(t), \ldots, \beta_K(t), \boldsymbol{\beta} \bigr)\in \mathcal{H}.
-	\end{equation}
+\eqref{possible?}
+
+We can express the predictor
+ $W_i$ 
+ and the regression coefficient $\beta$ using an orthonormal basis 
+ $\psi_1, \psi_2, \ldots$ of $\mathcal{H}$, 
+so that
+$W_i = \sum_j \langle W_i, \psi_j \rangle_{\mathcal{H}}\, \psi_j $	
+ and
+  $\beta = \sum_j \langle \beta, \psi_j \rangle_{\mathcal{H}}\, \psi_j $.
+To make the problem tractable, we truncate these expansions to the first  $L$ terms. 
+However, if the basis is chosen without considering the data, the most important regression information may not be captured within these first $L$ terms.
+The  core idea of partial least squares (PLS) is simultaneously learn a data-driven, regression-aware orthonormal basis while also performing the regression.
+This results in a  simultaneous  decomposition of the predictor and outcome in terms of uncorrelated PLS scores 
+\begin{equation}	\label{eq: decomposition}
+	W_i = \sum \limits_{l=1}^{\infty} \rho_{l}  \delta_l  \quad \textnormal{and} \quad Y_i = \sum \limits_{l=1}^{\infty}\rho_{l} \nu_l + \epsilon_i,
+	\end{equation}
+	where $(\boldsymbol{\delta}_l)_{l \in \mathbb{N}} \in \mathcal{H}$ and $(\nu_l)_{l \in \mathbb{N}} \in \mathbb{R}$ are appropriate bases.
 
@@
 
-	The basic idea of partial least squares (PLS) is to simultaneously decompose the hybrid predictor $\mathbf{W}$ and the real outcome $Y$ in terms of zero mean uncorrelated PLS scores $(\rho_l)_{l \in \mathbb{N}}$ with maximum predictive performance as follows
-	\begin{equation}
-		\mathbf{W}(\mathbf{t}) = \sum \limits_{l=1}^{\infty} \rho_{l} \boldsymbol{\delta}_l(\mathbf{t}) \quad \textnormal{and} \quad Y = \sum \limits_{l=1}^{\infty}\rho_{l} \nu_l + \epsilon,
-		\label{eq: decomposition}
-	\end{equation}
-	where $(\boldsymbol{\delta}_l)_{l \in \mathbb{N}} \in \mathcal{H}$ and $(\nu_l)_{l \in \mathbb{N}} \in \mathbb{R}$ are appropriate bases.
 	 The PLS scores are obtained as $\rho_l =  \langle \mathbf{W}^{[l]}, \xi_l \rangle_{\mathcal{H}}$, where $\mathbf{W}^{[l]}$ denotes the residualized predictor sequentially derived as the residual of the regression of $\mathbf{W}^{[l-1]}$ on $\rho_{l-1}$ with $\mathbf{W}^{[1]} = \mathbf{W}$, and $\xi_l=(\psi_l, \boldsymbol{\theta}_l) \in \mathcal{H}$ is the hybrid PLS component, with $\psi_l = (\psi^{(1)}_l, \ldots, \psi_l^{(K)}) \in \mathcal{F}$ and $\boldsymbol{\theta}_l=(\theta_{l1}, \ldots, \theta_{lp})^\top \in \mathbb{R}^p$, sequentially chosen to maximize the squared covariance between $\rho_l$ and the residualized outcome $Y^{[l]}$---i.e., $\textnormal{Cov}^2(\rho_l, Y^{[l]}) = \textnormal{Cov}^2(\langle \mathbf{W}^{[l]}, \xi_l \rangle_\mathcal{H}, Y^{[l]})$.
@@
 	%
-	\begin{algorithm}[t!]
-		\caption{Naive Hybrid PLS (regression coefficient omitted)}
-		\label{alg:naive}
-		\begin{algorithmic}[1]
-			\Require 
-			Hybrid predictors $\{ \mathbf{W}_1,  \ldots, \mathbf{W}_n\} = \{(X_1, Z_1),  \ldots, (X_n, Z_n)\}$,
-			responses $\{Y_1,   \ldots, Y_n\}$,
-			functional predictor evaluation points $\mathbf{t}_1, \ldots, \mathbf{t}_m \in [0,1]^K$
-			%%%%%%%%%%%%%%%%%%%%%
-			\For{ i = 1, 2, \ldots  $n$} \Comment{Centering \eqref{def:centering_naive}}
-			\State $\{ (Y_i^{[1]}, X_i^{[1]},Z_i^{[1]}) \} 
-			\leftarrow 
-			\{
-			(Y_i - \bar{Y}, X_i - \bar{X},  Z_i - \bar{Z})
-			\}$
-			\EndFor
-			\For{ l = 1, 2, \ldots  $L$}
-			\Statex{\quad \textbf{PLS component computation step:}}
-			\For{ $\mathbf{t} = \mathbf{t}_1 , \ldots  \mathbf{t}_m$} \Comment{Compute PLS loading}
-			\State 
-			$
-			\widehat{\xi}_{l}(\mathbf{t}) 
-			\leftarrow 
-			\dfrac{\sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]}(\mathbf{t})}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}}
-			$
-			\Comment{\eqref{def:pls_loading_ptws}}
-			\EndFor
-			\State $  \{ \widehat{\rho}_{1l}, \ldots, \widehat{\rho}_{nl} \} \leftarrow
-			\bigl\{
-			\langle \mathbf{W}_{1}^{[l]}, \widehat{\xi}_{l} \rangle_{\mathcal{H}},
-			\ldots,
-			\langle \mathbf{W}_{n}^{[l]}, \widehat{\xi}_{l} \rangle_{\mathcal{H}}
-			\bigr\}
-			$
-			\Comment{Compute PLS scores \eqref{def:pls_score_naive}}
-			\Statex{\quad  \textbf{Orthogonalization step:}}
-			\For{ $\mathbf{t} = \mathbf{t}_1 , \ldots  \mathbf{t}_m$} 
-			\State 	$
-			\widehat{\boldsymbol{\delta}}_{l}(\mathbf{t}) \leftarrow \dfrac{\sum_{i=1}^n \mathbf{W}_i^{[l]}(\mathbf{t}) \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2}.
-			$
-			\EndFor
-			\State
-			$\mathbf{W}_i^{[l+1]}(\mathbf{t}) \leftarrow \mathbf{W}_i^{[l]}(\mathbf{t}) - \widehat{\boldsymbol{\delta}}_{l}(\mathbf{t}) \widehat{\rho}_{il}$
-			\State 	$
-			\widehat{\nu}_l \leftarrow \dfrac{\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2}
-			$
-			\State
-			$Y_i^{[l+1]} \leftarrow Y_i^{[l]} - \widehat{\nu}_{l} \widehat{\rho}_{il}$ 
-			\EndFor
-			\State Output PLS scores $\bigl\{ \widehat{\rho}_{il} \bigr\}_{i \in [n], l \in [L]}$
-		\end{algorithmic}
-	\end{algorithm}
+
 	%
@@
 	\section{Proposed PLS Algorithm} \label{section:main:our_algorithm}
+		% i.e., for $\mathbf{v_1}=(v_{11}, \ldots, v_{1p})^\top$ and $\mathbf{v_2}=(v_{21}, \ldots, v_{2p})^\top$ in $\mathbb{R}^p$, $\langle \mathbf{v_1}, \mathbf{v_2} \rangle = \mathbf{v_1}^\top \mathbf{v_2} = \sum_{r=1}^p v_{1r}v_{2r}$, and $\Vert \mathbf{v}_1 \Vert = \langle \mathbf{v}_1, \mathbf{v}_1 \rangle^{1/2} = (\sum_{r=1}^p v_{1r}^2)^{1/2}$.
+	The hybrid random predictor and corresponding inner product is formally defined as follows.
+	\begin{definition}[Hybrid predictor and inner product]\label{def:hilbert_space}
+		We define a  hybrid predictor  $W_i$ as an ordered pair combining the functional predictors $X_{i1}(t), \ldots, X_{iK}(t)$ and a scalar predictor $\mathbf{Z}_i$:
+		\begin{equation}\label{def:hybid_predictor}
+			W_i := (X_{i1}, \ldots, X_{iK}, \mathbf{Z}_i)
+			\in \mathcal{H} :=  \mathcal{F}^{\otimes K} \times \mathbb{R}^p
+		\end{equation}
+		The inner product between two hybrid predictors,
+		$W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$
+		and
+		$W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$, is then defined as:
+		\begin{equation}		\label{eq: hybrid inner product}
+			\langle W_1, W_2\rangle_{\mathcal{H}}
+			:=
+			\sum \limits_{k=1}^K 
+			+ 
+			\omega
+			\mathbf{Z}_1^\top \mathbf{Z}_2,
+			~\text{where}~\int_0^1 X_{1k}(t) X_{2k}(t) \, dt
+		\end{equation}
+		for $\omega > 0$.
+		The corresponding norm $\Vert \cdot \Vert_\mathcal{H}$ is derived from this inner product as $\langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
+	\end{definition}
+	In \eqref{eq: hybrid inner product}, 
+	$\omega$ is a positive weight that needs to be pre-specified or estimated.
+It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}).
+	Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$. The results remain valid for any positive weights. 
+	\begin{remark}
+		Our method is applicable to settings where each functional predictor belongs to a different Hilbert space, possibly defined over a distinct compact domain in $\mathbb{R}^d$, for arbitrary $d$, and observed at different time points.
+However, for notational simplicity, our discussion assumes a common Hilbert space over domain $[0,1]$ for all functional predictors.
+	\end{remark}  
+	Then the joint regression model \eqref{eq: functional model}  can be concisely written as
+	\begin{equation}		\label{eq: Hybrid functional model}
+		Y_i = \langle \beta, W_i \rangle_{\mathcal{H}} + \epsilon_i,~\text{where}~\beta := \bigl( \beta_1(t), \ldots, \beta_K(t), \boldsymbol{\beta} \bigr)\in \mathcal{H}.
+	\end{equation}
 	To address the limitations outlined in Section \ref{sec: Naive PLS Algorithm}, we propose  novel strategies for implementing the steps of the hybrid PLS algorithm.

### 2025-08-16 manuscript/main.tex
Hilbert space

@@
 Our work focuses on developing a method to fit the following hybrid functional linear regression model:
-	\begin{equation}	\label{eq: functional model}
+	\begin{equation}	\label{eq:hybrid_regression_model}
 		Y_i
@@
 	\end{equation}
-where $Y_i$ is a scalar response, $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ is a Euclidean vector covariate, $X_{i1}(t), \ldots, X_{iK}(t)$ are functional predictors that belong to $L^2[0,1]$, and $\epsilon_i$ is observational noise.
-In other words, this is a scalar-on-hybrid regression where the hybrid covariates belong to $L^2[0,1]^{\otimes K} \times \mathbb{R}^p$.
+where $Y_i$ is a scalar response, $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ is a Euclidean vector covariate, $X_{i1}(t), \ldots, X_{iK}(t)$ are functional predictors that belong to $\mathbb{L}^2[0,1]$, and $\epsilon_i$ is observational noise.
+In other words, this is a scalar-on-hybrid regression where the hybrid covariates belong to $\bigl( \mathbb{L}^2[0,1] \bigr)^{  K} \times \mathbb{R}^p$.
 	For notational convenience, we assume throughout this paper that the responses and predictors have been centered, allowing the intercept term to be ignored.
@@
 
-	\section{Background on partial least squares and its extension to hybrid predictors} \jongmin{still revising}
+	\section{Background on partial least squares and its extension to hybrid predictors}  
+	\jongmin{I replaced the formal presentation of the naive algorithm with an   the scalar version and a brief outline of the pointwise hybrid  extension strategy.
+The main reason for this revision is that the hybrid inner product is introduced specifically to address the extension challenge, so it is more natural to present it after listing the challenges.
+Previously, the naive algorithm section relied on the hybrid inner product for normalization.}
 For intuition, let us return to the high-dimensional Euclidean predictor setting $
@@
 \widehat{\rho}_1^{[1]}, \ldots,   \widehat{\rho}_1^{[L]}  
-\bigr)^\top.
+\bigr)^\top \in \mathbb{R}^L.
 $ To retain the regression relationship, the $l$-th PLS direction $\hat{\boldsymbol{\xi}}_l$ solves:
@@
  where the two $\widehat{\operatorname{Cov}}^2$ denote sample cross-covariance and sample covariance, respectively.
-A standard algorithm for solving this problem, called nonlinear iterative partial least squares (NIPALS) is presented in Algorithm \ref{scalar_pls}.
+A standard algorithm for solving this problem, called nonlinear iterative partial least squares (NIPALS) is presented in Algorithm \ref{alg:scalar_pls}.
  \begin{algorithm} 
- 	\caption{Scalar partial least squares }\label{scalar_pls}
+ 	\caption{Scalar partial least squares }\label{alg:scalar_pls}
  	\begin{algorithmic}[1]
@@
  		\textbf{PLS direction and score estimation:}
- 		\State $\widehat{\boldsymbol{\xi}}_l \leftarrow
+ 		\State $\widehat{\boldsymbol{\xi}}^{[l]} \leftarrow
  		\arg \max_{  \boldsymbol{\alpha}   } 
@@
  		$
- 		\Comment{PLS direction}\label{possible?}
+ 		\Comment{PLS direction}\label{alg:step:scalar_pls_direction}
  		\State 
  		$
- 		\widehat{\rho}_i^{[l]} \leftarrow \langle \hat{\boldsymbol{\xi}}_l,   \mathbf{Z}_i \rangle, 
+ 		\widehat{\rho}_i^{[l]} \leftarrow \langle \hat{\boldsymbol{\xi}}^{[l]},   \mathbf{Z}^{[l]}_i \rangle, 
  		~i=1,  \ldots, n
@@
  		 	\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}
- 		 	}$
+ 		 	}$ \Comment{Least squares estimate} 
  		%
@@
  		%
- 		\State $ \widehat{\boldsymbol{\delta}}^{[l]}  \leftarrow \frac{1}{\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}}\sum_{i=1}^n  \widehat{\rho}_{i}^{[l]}\mathbf{Z}_i^{[l]}.
- 	$
+ 		\State $ \widehat{\boldsymbol{\delta}}^{[l]}  \leftarrow \frac{1}{\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}}\sum_{i=1}^n  \widehat{\rho}_{i}^{[l]}\mathbf{Z}_i^{[l]} $ \Comment{Least squares estimate} 
+ \label{alg:step:scalar_pls_residualization}
 \State $\mathbf{Z}_i^{[l+1]}  \leftarrow \mathbf{Z}_i^{[l]} -   \widehat{\rho}_{i}^{[l]}  \widehat{\boldsymbol{\delta}}^{[l]} $
@@
  		\EndFor
-$	\widehat{\boldsymbol{\beta}} \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{\boldsymbol{\zeta}}^{[l]}$
+$	\widehat{\boldsymbol{\beta}} \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{\boldsymbol{\zeta}}^{[l]}$ \Comment{regression coefficient estimate}
  		\State \textbf{Output:} the  regression coefficient estimate
-
  	\end{algorithmic}
  \end{algorithm}
-% $, 
-	%Write  $X=(X^{(1)}, \ldots, X^{(K)})$ as a multivariate functional object that belongs to $\mathcal{F} = L^2(\mathcal{T}_1) \times \cdots \times L^2([0,1])$---a cartesian product of individual $L^2([0,1])$ spaces.
-Note that if $K=1$, $X$ reduces to a univariate functional object.
-We can also express the functional object $X$ evaluated on the multi-dimensional argument $\mathbf{t} = (t_1, \ldots, t_k)^\top \in \mathcal{T} = \mathcal{T}_1 \times \cdots \times [0,1]$ as a $K$-dimensional vector $X(\mathbf{t})=(X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top$.
-	%The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)}) $ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as $\langle f_1, f_2\rangle_\mathcal{F} =  \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)}\rangle_{L^2} = \sum_{k=1}^K \int_0^1 f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k$ with norm $\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_0^1 f_1^{(k)}(t_k)^2 dt_k\}^{1/2}$.
-	%An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}(\mathbf{t}) = (X(\mathbf{t}), \mathbf{Z})^\top$, with $ X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $ \mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.
-\eqref{possible?}
-
-We can express the predictor
- $W_i$ 
- and the regression coefficient $\beta$ using an orthonormal basis 
- $\psi_1, \psi_2, \ldots$ of $\mathcal{H}$, 
-so that
-$W_i = \sum_j \langle W_i, \psi_j \rangle_{\mathcal{H}}\, \psi_j $	
- and
-  $\beta = \sum_j \langle \beta, \psi_j \rangle_{\mathcal{H}}\, \psi_j $.
-To make the problem tractable, we truncate these expansions to the first  $L$ terms. 
-However, if the basis is chosen without considering the data, the most important regression information may not be captured within these first $L$ terms.
-The  core idea of partial least squares (PLS) is simultaneously learn a data-driven, regression-aware orthonormal basis while also performing the regression.
-This results in a  simultaneous  decomposition of the predictor and outcome in terms of uncorrelated PLS scores 
-\begin{equation}	\label{eq: decomposition}
-	W_i = \sum \limits_{l=1}^{\infty} \rho_{l}  \delta_l  \quad \textnormal{and} \quad Y_i = \sum \limits_{l=1}^{\infty}\rho_{l} \nu_l + \epsilon_i,
-	\end{equation}
-	where $(\boldsymbol{\delta}_l)_{l \in \mathbb{N}} \in \mathcal{H}$ and $(\nu_l)_{l \in \mathbb{N}} \in \mathbb{R}$ are appropriate bases.
-
-	\section{Population PLS and Tucker's Criterion in hybrid regression setting}\label{section:main:tucker}\jongmin{Previously, was in theoretical property section, now procedes the method section, to motivate the estimation procedure}
-
-	 The PLS scores are obtained as $\rho_l =  \langle \mathbf{W}^{[l]}, \xi_l \rangle_{\mathcal{H}}$, where $\mathbf{W}^{[l]}$ denotes the residualized predictor sequentially derived as the residual of the regression of $\mathbf{W}^{[l-1]}$ on $\rho_{l-1}$ with $\mathbf{W}^{[1]} = \mathbf{W}$, and $\xi_l=(\psi_l, \boldsymbol{\theta}_l) \in \mathcal{H}$ is the hybrid PLS component, with $\psi_l = (\psi^{(1)}_l, \ldots, \psi_l^{(K)}) \in \mathcal{F}$ and $\boldsymbol{\theta}_l=(\theta_{l1}, \ldots, \theta_{lp})^\top \in \mathbb{R}^p$, sequentially chosen to maximize the squared covariance between $\rho_l$ and the residualized outcome $Y^{[l]}$---i.e., $\textnormal{Cov}^2(\rho_l, Y^{[l]}) = \textnormal{Cov}^2(\langle \mathbf{W}^{[l]}, \xi_l \rangle_\mathcal{H}, Y^{[l]})$.
-Here, $Y^{[l]}$ is also sequentially obtained as the residual of the regression of $Y^{[l-1]}$ on $\rho_{l-1}$ with $Y^{[1]} = Y$.
-The sequentially derived hybrid PLS components \{$\xi_l\}_{l=1}^\infty$, are orthonormal in a sense that $\langle \xi_l, \xi_j \rangle_\mathcal{H} = \mathbb{1}(l=j)$.
-
-	\underline{Challenges}
-	% The pointwise algorithm is highly inefficient and may not be even feasible for multiple dense and/or irregular functional data.
-Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components.
-Therefore, in this section, we introduce a novel framework for fitting a regression with a hybrid response and scalar predictor.
-The framework is readily applicable to dense and irregular functional data, and supports regularization techniques to prevent overfitting and reduce variance.
-
-	\begin{enumerate}
-		\item Independent variables consist of multiple highly structured images and scalar predictors.
-		\item Our sample size is small compared to the dimension and number of functional and scalar predictors.
-		\item Existing partial least squares (PLS) methods can only accommodate (i) univariate or multivariate functional predictors without any scalar predictors \citep{predaPLSRegressionStochastic2005, delaigleMethodologyTheoryPartial2012, Febrero2017, Beyaztas2020}; or (2) a univariate functional predictor with other scalar predictors \citep{Wang2018}.
-	\end{enumerate}
-
-	The fundamental property of classical scalar PLS is that the PLS component direction  corresponds to the first eigenvector of the squared covariance matrix, satisfying  the Tucker's Criterion \citep{Tucker1938}.
-Under a mild assumption,
-	We derive an analogous result  in our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
-	 This justifies our estimation procedure introduced in Section \ref{section:main:our_algorithm}.
-	We omit $l$ in the notations and first define the cross-covariance term between the response and the functional predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$): 
-	\begin{equation}\label{def:cross_covariance_yx}
-		\sigma_{YX}
-		=
-		\bigl(
-		\sigma_{YX, 1}(t) , \ldots, \sigma_{YX, K}(t) 
-		\bigr)
-		:=
-		\bigl(
-		\mathbb{E}
-		[Y_1 X_{11}]
-		,\ldots, 
-		\mathbb{E}
-		[Y_1  X_{1K}]
-		\bigr)   \in \mathcal{F}^{\otimes K},
-	\end{equation}
-	and between the response and the scalar predictor:
-	\begin{equation*}
-		\sigma_{YZ} 
-		= 
-		(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
-		:= 
-		\bigl(
-		\mathbb{E}[Y_1 Z_{11}]
-		,\ldots,
-		\mathbb{E}[Y_1 Z_{1p}]
-		\bigr)^\top %= E(Y\mathbf{Z})
-		\in \mathbb{R}^p.
-	\end{equation*}
-	Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
-	\begin{equation*}
-		\Sigma_{YW} :=  
-		\mathbb{E}
-		[ Y_1 W_1 ]
-		=
-		\bigl(
-		\sigma_{YX, 1} , \ldots, \sigma_{YX, K} , \, \sigma_{YZ}
-		\bigr) \in \mathcal{H}.
-	\end{equation*}
-	Based on these definitions, we introduce two cross-covariance operators and their properties.
-	\begin{lemma}\label{lemma:cross_cov_functional}
-		Define the operator $
-		\mathcal{C}_{YW}
-		=
-		\mathbb{E}(W_1 \otimes_\mathcal{H} Y_1)
-		: \mathcal{H} \rightarrow \mathbb{R}$ such that for any $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$, it maps $h$ to a real number as: \begin{equation*} \mathcal{C}_{YW} h := \mathbb{E} \left[ \langle W_1, h \rangle_\mathcal{H} Y_1 \right] = \langle \Sigma_{YW}, h \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt + \sigma_{YW}^\top \mathbf{v}.
-\end{equation*}
-		\jongmin{instead of showing $\mathcal{U}$ is compact, let's show $\mathcal{C}_{YW}$ is compact.
-This way, we don't need uniform continuiity of $\sigma_{YX}$.}If there exist finite constants $Q_1$ and $Q_2$ such that
-		\begin{align}\label{condition_for_compact}
-			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
-		\end{align}
-		the operator $\mathcal{C}_{YW}$ is a compact operator.
-	\end{lemma}
-	Proof of Lemma \ref{lemma:cross_cov_functional}
-	is provided in Appendix \ref{section:proof:lemma:cross_cov_functional}.
-	\begin{lemma}\label{lemma:cross_cov_operator}
-		Define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$,
-		which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:
-		%%%%
-		\begin{align*}		
-			\mathcal{C}_{WY} d 
-			:= 
-			\mathbb{E} 
-			\bigl[
-			\langle Y_1, d \rangle W_1 
-			\bigr] 
-			= 
-			\mathbb{E}
-			[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
-		\end{align*}
-		Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
-	\end{lemma}
-
-	The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.
-
-	Based on these two operators, we define a positive   operator as follows:
-	\begin{lemma}[Composite cross-covariance operator]\label{lemma:composite_cross_cov}
-		Define
-		$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ as an operator which performs the following mapping:
-		\begin{equation*}
-			\mathcal{U} h 
-			= 
-			\mathcal{C}_{WY} ( \mathcal{C}_{YW} h) 
-			=
-			\mathcal{C}_{YW} (\langle \Sigma_{YW}, h \rangle_\mathcal{H}) 
-			=  
-			\Sigma_{YW} \, \langle \Sigma_{YW}, h \rangle_\mathcal{H} 
-			= 
-			(\Sigma_{YW} \otimes \Sigma_{YW}) h.
-		\end{equation*}
-		In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$.
-		Then $\mathcal{U}$
-		is a self-adjoint and positive-semidefinite operator.
-		Under the conditions of Lemma \ref{lemma:cross_cov_functional}, $\mathcal{U}$ is a compact operator.
-	\end{lemma}
-	The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
-	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Lemma \ref{lemma:composite_cross_cov} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
-
-	The following theorem introduces the population-level PLS and Tucker's Criterion, adapted to our scalar-on-hybrid regression model setting, based on the aforementioned operators defined in the hybrid space.
-	\begin{theorem}[Population PLS and Tucker's criterion]\label{theorem:population_PLS} Under the conditions of Lemma \ref{lemma:cross_cov_functional}, the constrained maximum
-		\begin{equation*} 
-			\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathcal{H}, Y \right)
-		\end{equation*} 
-		is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
-	\end{theorem}
-	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.
-	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]}  W^{[l]})$.
-
-		\section{Naive PLS Algorithm} \label{sec: Naive PLS Algorithm}
-	This section introduces a naive pointwise hybrid PLS algorithm and highlights its limitations.
-The algorithm treats each functional predictor as a long vector of discretized points, derives PLS components independently at each observed time point $\mathbf{t}$, and aggregates them into a functional object to compute the PLS score.
-	Since the regression coefficient computation follows directly from the PLS components and scores, our discussion here focuses on the latter and omits the former.
-	Denote $\{(Y_1, \mathbf{W}_1),  \ldots, (Y_n, \mathbf{W}_n)\}$ as $n$ independent data pairs (observed sample) distributed as $(Y, \mathbf{W})$.
-The goal of the PLS algorithm is to decompose the predictor $\mathbf{W}_i$ $(i=1, \ldots, n)$ and the real response $Y_i$ in terms of zero mean uncorrelated PLS scores  $(\rho_{il})_{l \in \mathbb{N}}$ with maximum predictive performance.
-Here and below, a superscript in square brackets denotes the iteration index of the algorithm.
-We begin by denoting the centered data as
-	\begin{equation}\label{def:centering_naive}
-		Y_i^{[1]} = Y_i - \bar{Y}~\text{and}~\mathbf{W}_i^{[1]}=(X_i^{[1]}, \mathbf{Z}_i^{[1]})=(X_i - \bar{X}, \mathbf{Z}_i - \bar{\mathbf{Z}}) = \mathbf{W}_i - \bar{\mathbf{W}}. 
-	\end{equation}
-	We describe the $l$-th step of the algorithm for $l = 1, 2, \ldots, L$, which consists of the following substeps. The complete procedure is summarized in Algorithm~\ref{alg:naive}.
-	%
-
-	%
-	\begin{enumerate}[Step 1.]
-		\item
-		We compute the $l$th PLS score of the $i$th subject as
-		\begin{equation}\label{def:pls_score_naive}
-			\widehat{\rho}_{il} = \langle \mathbf{W}_{i}^{[l]}, \widehat{\xi}_{l} \rangle_{\mathcal{H}} = \langle X_i^{[l]}, \widehat{\psi}_{l} \rangle_{\mathcal{F}} + \langle \mathbf{Z}_i^{[l]}, \widehat{\boldsymbol{\theta}}_{l} \rangle,
-		\end{equation}
-		where the $l$-th PLS loading $\widehat{\xi}_{l} = (\widehat{\psi}_{l}, \widehat{\boldsymbol{\theta}}_{l}) \in \mathcal{H}$ maximizes $\widehat{\textnormal{Cov}}^2(\langle \mathbf{W}_{i}^{[l]}, \widehat{\xi}_{l} \rangle_{\mathcal{H}}, Y_i^{[l]})=\widehat{\textnormal{Cov}}^2(\widehat{\rho_{il}}, Y_i^{[l]})$.
-Specifically, we define the $l$-th PLS loadings pointwise as follows:
-		\begin{equation}\label{def:pls_loading_ptws}
-			\widehat{\xi}_{l}(\mathbf{t}) = \frac{\sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]}(\mathbf{t})}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} = \left[ \frac{\sum_{i=1}^n Y_i^{[l]} X_i^{[l]}(\mathbf{t})}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}}, \frac{\sum_{i=1}^n Y_i^{[l]}\mathbf{Z}_i^{[l]}}{\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}}} \right]^\top,
-		\end{equation}
-		where the normalizing factor  is computed as
-		\begin{equation}
-			\Vert \sum_{i=1}^n Y_i^{[l]} \mathbf{W}_i^{[l]} \Vert_{\mathcal{H}} = [\sum_{i=1}^n \sum_{j=1}^n Y_i^{[l]} Y_j^{[l]} \{\langle X_i^{[l]},X_j^{[l]} \rangle_\mathcal{F} + \langle \mathbf{Z}_i^{[l]}, \mathbf{Z}_j^{[l]} \rangle \}]^{1/2}.
-		\end{equation}
-
-		\item Obtain the subsequent residualized outcomes and predictors as $Y_i^{[l+1]} = Y_i^{[l]} - \widehat{\nu}_{l} \widehat{\rho}_{il}$ and $\mathbf{W}_i^{[l+1]}(\mathbf{t}) = \mathbf{W}_i^{[l]}(\mathbf{t}) - \widehat{\boldsymbol{\delta}}_{l}(\mathbf{t}) \widehat{\rho}_{il}$, where
-		\begin{equation*}
-			\widehat{\nu}_l = \frac{\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}_{l}(\mathbf{t}) = \frac{\sum_{i=1}^n \mathbf{W}_i^{[l]}(\mathbf{t}) \widehat{\rho}_{il}}{\sum_{i=1}^n \widehat{\rho}_{il}^2}.
-		\end{equation*}
-		Note, $\widehat{\nu}_l$ is the least squares estimate from linear regression of $Y_i^{[l]}$ on $\widehat{\rho}_{il}$, and  $\widehat{\boldsymbol{\delta}}_{l}(\mathbf{t})$ is the least squares estimate from a linear regression of $\mathbf{W}_i^{[l]}(\mathbf{t})$ on $\widehat{\rho}_{il}$.
-
-		\item Let $l=l+1$ and back to Step 1.
-	\end{enumerate}
-
-	This naive pointwise PLS algorithm, however, can be computationally expensive for multiple dense functional data and is not feasible for irregular functional data.
-Moreover, the pointwise estimates only use information from data on the particular argument value, and thus can show substantial variability across the domain, resulting in overfitting and unstable predictions.
+
+To extend Algorithm \ref{alg:scalar_pls} to the hybrid regression model \eqref{eq:hybrid_regression_model}, we must compute hybrid objects in both the PLS direction estimation and predictor residualization steps (lines \ref{alg:step:scalar_pls_direction} and \ref{alg:step:scalar_pls_residualization}).
+These computations cannot be separated into functional and scalar parts, as their correlation must be addressed.
+A naive approach is to add loops over the observed evaluation points $t$ to lines \ref{alg:step:scalar_pls_direction} and \ref{alg:step:scalar_pls_residualization}, treating  
+\[
+\bigl( X_{i1}(t), \ldots, X_{iK}(t), Z_{i1}, \ldots, Z_{ip} \bigr) \in \mathbb{R}^{K+P}
+\]  
+as a Euclidean predictor, applying steps \ref{alg:step:scalar_pls_direction} and \ref{alg:step:scalar_pls_residualization}, and aggregating the results.
+This pointwise method, however, is computationally prohibitive for densely observed functional predictors, infeasible for irregular data, and prone to variability across the domain, resulting in overfitting and unstable predictions.
+The main challenge of extension to the hybrid setting lies in the following points. First, 
+ independent variables consist of multiple highly structured images and scalar predictors. 
+Second, our sample size is small compared to the dimension and number of functional and scalar predictors.
+Third,  existing partial least squares (PLS) methods can only accommodate (i) univariate or multivariate functional predictors without any scalar predictors \citep{predaPLSRegressionStochastic2005, delaigleMethodologyTheoryPartial2012, Febrero2017, Beyaztas2020}; or (ii) a univariate functional predictor with other scalar predictors \citep{Wang2018}.
+The next section proposes a new extension framework that addresses these issues.
 
 	\section{Proposed PLS Algorithm} \label{section:main:our_algorithm}
-		% i.e., for $\mathbf{v_1}=(v_{11}, \ldots, v_{1p})^\top$ and $\mathbf{v_2}=(v_{21}, \ldots, v_{2p})^\top$ in $\mathbb{R}^p$, $\langle \mathbf{v_1}, \mathbf{v_2} \rangle = \mathbf{v_1}^\top \mathbf{v_2} = \sum_{r=1}^p v_{1r}v_{2r}$, and $\Vert \mathbf{v}_1 \Vert = \langle \mathbf{v}_1, \mathbf{v}_1 \rangle^{1/2} = (\sum_{r=1}^p v_{1r}^2)^{1/2}$.
-	The hybrid random predictor and corresponding inner product is formally defined as follows.
-	\begin{definition}[Hybrid predictor and inner product]\label{def:hilbert_space}
-		We define a  hybrid predictor  $W_i$ as an ordered pair combining the functional predictors $X_{i1}(t), \ldots, X_{iK}(t)$ and a scalar predictor $\mathbf{Z}_i$:
-		\begin{equation}\label{def:hybid_predictor}
-			W_i := (X_{i1}, \ldots, X_{iK}, \mathbf{Z}_i)
-			\in \mathcal{H} :=  \mathcal{F}^{\otimes K} \times \mathbb{R}^p
-		\end{equation}
-		The inner product between two hybrid predictors,
-		$W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$
-		and
-		$W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$, is then defined as:
-		\begin{equation}		\label{eq: hybrid inner product}
-			\langle W_1, W_2\rangle_{\mathcal{H}}
-			:=
-			\sum \limits_{k=1}^K 
-			+ 
-			\omega
-			\mathbf{Z}_1^\top \mathbf{Z}_2,
-			~\text{where}~\int_0^1 X_{1k}(t) X_{2k}(t) \, dt
-		\end{equation}
-		for $\omega > 0$.
-		The corresponding norm $\Vert \cdot \Vert_\mathcal{H}$ is derived from this inner product as $\langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
+Our new framework builds on the fact that all computations in Algorithm \ref{alg:scalar_pls} are arithmetic operations in an inner product space.
+We therefore formally define the Hilbert space of hybrid random predictors along with its corresponding complete inner product, and leverage them to extend Algorithm \ref{alg:scalar_pls}.
+\jongmin{I split the definition into three parts, adding completeness, separability, and the sigma-field.}
+\begin{definition}[Hybrid space]\label{def:hilbert_space}
+	Let $\mathbb{H}$ be a product space defined as the Cartesian product of $K$ copies of the space of square-integrable functions on $[0,1]$ and the $p$-dimensional Euclidean space:
+	$$
+	\mathbb{H} := (\mathbb{L}^2[0,1])^K \times \mathbb{R}^p.
+	$$
+	An element $h \in \mathbb{H}$ is an ordered tuple $h = (f_1, \dots, f_K, \mathbf{u})$, where $f_k \in \mathbb{L}^2[0,1]$ for $k=1, \dots, K$ and $\mathbf{u} \in \mathbb{R}^p$.
+This space is equipped with element-wise vector addition and scalar multiplication.
+	We define an inner product on $\mathbb{H}$ for any two elements $h_1 = (f_1, \dots, f_K, \mathbf{u})$ and $h_2 = (g_1, \dots, g_K, \mathbf{v})$ as:
+	\begin{equation}\label{eq: hybrid inner product}
+		\langle h_1, h_2 \rangle_{\mathbb{H}} := \sum_{k=1}^K \int_0^1 f_k(t) g_k(t) \, dt + \omega \mathbf{u}^\top \mathbf{v},
+	\end{equation}
+	where $\omega$ is a positive constant ($\omega > 0$).
+	The inner product induces a norm $\Vert \cdot \Vert_{\mathbb{H}}$ on the space, defined as $\Vert h \Vert_{\mathbb{H}} := \langle h, h \rangle_{\mathbb{H}}^{1/2}$, and a corresponding metric $d(h_1, h_2) = \Vert h_1 - h_2 \Vert_{\mathbb{H}}$.
 \end{definition}
@@
 Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$. The results remain valid for any positive weights. 
+\begin{lemma}[Hybrid Hilbert space]\label{lemma:hybrid_hilbert_space}
+	The hybrid space $\mathbb{H}$ is a separable Hilbert space.
+\end{lemma} 
+Proof of Lemma \ref{lemma:hybrid_hilbert_space} is provided in Appendix \ref{section:proof:lemma:hybrid_hilbert_space}.
+
+\begin{definition}[Hybrid Predictor]
+	For the Hilbert space  $\mathbb{H}$ 
+	defined in Definition \ref{def:hilbert_space},
+	 The Borel $\sigma$-field on $\mathbb{H}$, denoted $\mathfrak{B}(\mathbb{H})$, is the smallest $\sigma$-field containing the class $\mathfrak{M}$ of all sets of the form
+	$
+	\{q \in \mathbb{H} \mid \langle q, h \rangle \in O\},
+	$
+	for any $h \in \mathbb{H}$ and any open subset $O \subseteq \mathbb{R}$ (details can be found in Theorem 7.1.1 of \citealt{hsingTheoreticalFoundationsFunctional2015}).
+	A hybrid predictor $ W_i = (X_{i1}(t), \ldots, X_{iK}(t), \mathbf{Z}_i)$ is a measurable mapping from a probability space $(\Omega, \mathfrak{F}, P)$ into   $
+\bigl(
+	\mathbb{H}, \mathfrak{B}(\mathbb{H})
+\bigr)
+$. 
+\end{definition}
+ 	Then the joint regression model \eqref{eq:hybrid_regression_model}  can be concisely written as
+ \begin{equation}		\label{eq: Hybrid functional model}
+ 	Y_i = \langle \beta, W_i \rangle_{\mathbb{H}} + \epsilon_i,~\text{where}~\beta := \bigl( \beta_1(t), \ldots, \beta_K(t), \boldsymbol{\beta} \bigr)\in \mathbb{H}.
+ \end{equation}
 	\begin{remark}
@@
 	\end{remark}
-	Then the joint regression model \eqref{eq: functional model}  can be concisely written as
-	\begin{equation}		\label{eq: Hybrid functional model}
-		Y_i = \langle \beta, W_i \rangle_{\mathcal{H}} + \epsilon_i,~\text{where}~\beta := \bigl( \beta_1(t), \ldots, \beta_K(t), \boldsymbol{\beta} \bigr)\in \mathcal{H}.
-	\end{equation}
-	To address the limitations outlined in Section \ref{sec: Naive PLS Algorithm}, we propose  novel strategies for implementing the steps of the hybrid PLS algorithm.
+
  Our approach provides an efficient and robust means of producing PLS components and scores in the presence of multiple dense and/or irregular functional predictors and scalar predictors.
@@
 For notational simplicity, we omit the iteration index $l$ in the following discussion, with the understanding that the subroutines apply to any iteration.
-The complete algorithm is summarized in Algorithm~\ref{alg:main}.
+The complete algorithm is summarized in Algorithm~\ref{alg:hybrid_pls}.
 
 	\subsection{Preliminary step 1: finite-basis approximation}\label{sec: finite basis approximation}	
-	Let ${b_m(t)}$ be a twice-differentiable basis of $L^2([0,1])$ whose second derivatives are also linearly independent, for example, cubic B-splines, the Fourier basis, or an orthonormal polynomial basis of degree greater than three.
+	Let ${b_m(t)}$ be a twice-differentiable basis of $\mathbb{L}^2([0,1])$ whose second derivatives are also linearly independent, for example, cubic B-splines, the Fourier basis, or an orthonormal polynomial basis of degree greater than three.
 Using this basis,
@@
 	\end{equation*}	
-	In practice, the full set of coefficients can not be obtained  with finite sample size, as functional data are measured on a finite grid.
-Thus, we truncate the expansion at $M$ terms and define the truncated basis space
-	$
-	\mathcal{B} := \operatorname{span}\bigl(b_1(t), \ldots, b_M(t)\bigr).
-	$
+	In practice, the full set of coefficients can not be obtained  with finite sample size, as functional data are measured on a finite grid. Thus, we truncate the expansion at $M$ terms.
 	We choose a moderately large $M$ (e.g., 15 or 20) to capture functional variation without fine-tuning, as smoothness is handled via penalization (see Section~\ref{sec: Regularization of PLS Components}).
@@
 	\begin{equation}\label{def:truncated_hilbert_space}
-		\widetilde{ \mathcal{H} } := \mathcal{B}^K \times \mathbb{R}^p \subset \mathcal{H}.
-	\end{equation}
-	The $i$th hybrid predictor, projected on $\widetilde{ \mathcal{H} }$, is represented by the tuple
+		\widetilde{ \mathbb{H} } := \operatorname{span}\bigl(b_1(t), \ldots, b_M(t)\bigr)^K \times \mathbb{R}^p \subset \mathbb{H}.
+	\end{equation}
+	The $i$th hybrid predictor, projected on $\widetilde{ \mathbb{H} }$, is represented by the tuple
 	\begin{equation*}
@@
 %For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{section:sub:residualization} for details).
-	The  PLS component direction is estimated by the unit-norm direction $\xi^{[l]} \in \widetilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as
+	The  PLS component direction is estimated by the unit-norm direction $\xi^{[l]} \in \widetilde{\mathbb{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathbb{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathbb{H}}$ and the responses $y_1, \ldots, y_n$, defined as
 
@@
 		\widetilde{W},
-		\xi \rangle_{\mathcal{H}}, Y )
+		\xi \rangle_{\mathbb{H}}, Y )
 		:=
@@
 		y_i
-		\langle \widetilde{W}_i, \xi \rangle_{\mathcal{H}}
+		\langle \widetilde{W}_i, \xi \rangle_{\mathbb{H}}
 		.
@@
 		\hat{\xi} 
-		:= \arg \max_{\xi \in \widetilde{\mathcal{H}}
+		:= \arg \max_{\xi \in \widetilde{\mathbb{H}}
 		}~\widehat{\textnormal{Cov}}^2 
 		\bigl(
-		\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
-		\bigr)~s.t.~\| \xi  \|_\mathcal{H} = 1.
+		\langle \widetilde{W}, \xi \rangle_{\mathbb{H}}, Y 
+		\bigr)~s.t.~\| \xi  \|_\mathbb{H} = 1.
 	\end{equation}
 	%
-	Here, $\hat{\xi} \in \widetilde{\mathcal{H}}$ is an ordered pair  expanded as:
+	Here, $\hat{\xi} \in \widetilde{\mathbb{H}}$ is an ordered pair  expanded as:
 	\begin{equation*}
@@
 	\bigl(
-	\langle \widetilde{W}, \xi \rangle_\mathcal{H}, Y 
+	\langle \widetilde{W}, \xi \rangle_\mathbb{H}, Y 
 	\bigr)
@@
 		\bigl(
-		\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
+		\langle \widetilde{W}, \xi \rangle_{\mathbb{H}}, Y 
 		\bigr)
@@
 	where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness. 
-	However, this approach  \citet{Rice1991} assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense.
+	However, this approach  \citet{Rice1991} assumes that the functional predictors admit an orthogonal expansion in the $\mathbb{L}^2$ sense.
 
@@
 		\hat{\xi} 
-		:= \arg \max_{\xi \in \widetilde{\mathcal{H}}
+		:= \arg \max_{\xi \in \widetilde{\mathbb{H}}
 		}~\widehat{\textnormal{Cov}}^2 
 		\bigl(
-		\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
-		\bigr)~s.t.~\| \xi  \|_\mathcal{H} +  \sum \limits_{j=1}^K \lambda_j 
+		\langle \widetilde{W}, \xi \rangle_{\mathbb{H}}, Y 
+		\bigr)~s.t.~\| \xi  \|_\mathbb{H} +  \sum \limits_{j=1}^K \lambda_j 
 		\operatorname{PEN}(\xi_K) = 1.
 	\end{equation}
-	Here, $\hat{\xi} \in \widetilde{\mathcal{H}}$ is an ordered pair  expanded as:
+	Here, $\hat{\xi} \in \widetilde{\mathbb{H}}$ is an ordered pair  expanded as:
 	\begin{equation*}
@@
 	\begin{equation}\label{def:plsscore}
-		\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathcal{H}},
+		\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathbb{H}},
 	\end{equation}
@@
 we employ a basis expansion approach to fit the entire hybrid object in one step.
-Therefore, our method is computationally efficient, applicable for dense or irregular functional data, and keeps the residual smooth, as it enforces the regression coefficient, $\delta^{[l]}$, as an element of $\tilde{\mathcal{H}}$ as defined in Equation \eqref{def:truncated_hilbert_space}.
+Therefore, our method is computationally efficient, applicable for dense or irregular functional data, and keeps the residual smooth, as it enforces the regression coefficient, $\delta^{[l]}$, as an element of $\tilde{\mathbb{H}}$ as defined in Equation \eqref{def:truncated_hilbert_space}.
 	Consequently, $\delta^{[l]}$ is obtained by minimizing a  
@@
 	\begin{equation}\label{def:argmin_pensse}
-		\hat{\delta}^{[l]} := \arg \min_{\delta \in \tilde{\mathcal{H}}} \sum_{i=1}^n 
-		\| \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta\|_{\mathcal{H}}^2.
+		\hat{\delta}^{[l]} := \arg \min_{\delta \in \tilde{\mathbb{H}}} \sum_{i=1}^n 
+		\| \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta\|_{\mathbb{H}}^2.
 	\end{equation}
@@
 	The regression coefficient $\boldsymbol{\eta}$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS components and scores.
-First, note that we can show $\widehat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} = \langle \mathbf{W}_i, \widehat{\boldsymbol{\zeta}}_l \rangle_\mathcal{H}$, where $\widehat{\boldsymbol{\zeta}}_l = \widehat{\xi}_l - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}_u, \widehat{\xi}_l \rangle_{\mathcal{H}} \widehat{\boldsymbol{\zeta}}_u$ for $l \ge 2$, with $\widehat{\boldsymbol{\zeta}}_1 = \widehat{\xi}_1$.
+First, note that we can show $\widehat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathbb{H} = \langle \mathbf{W}_i, \widehat{\boldsymbol{\zeta}}_l \rangle_\mathbb{H}$, where $\widehat{\boldsymbol{\zeta}}_l = \widehat{\xi}_l - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}_u, \widehat{\xi}_l \rangle_{\mathbb{H}} \widehat{\boldsymbol{\zeta}}_u$ for $l \ge 2$, with $\widehat{\boldsymbol{\zeta}}_1 = \widehat{\xi}_1$.
 Then, the decomposition of $Y_i$ in \eqref{eq: decomposition} leads to
 	\begin{equation*}
-		Y_i = \sum \limits_{l=1}^L \widehat{\nu}_l \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l \right\rangle_\mathcal{H}+\epsilon_i,
+		Y_i = \sum \limits_{l=1}^L \widehat{\nu}_l \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathbb{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l \right\rangle_\mathbb{H}+\epsilon_i,
 	\end{equation*}
@@
 
-	\begin{algorithm}[b!]
-		\caption{Hybrid PLS (under construction)}
-		\label{alg:main}
+ \begin{algorithm} 
+	\caption{Hybrid partial least squares regression}\label{alg:hybrid_pls}
 	\begin{algorithmic}[1]
-			\Require 
-			Response $\mathbf{y} \in \mathbb{R}^n$,
-			%functional predictor evalulation points $\mathbf{t}_1, \ldots, \mathbf{t}_m \in [0,1]^K,$
-			hybrid predictors approximation coefficient
-			$\widetilde{C}^* \ \in \mathbb{R}^{n \times (MK+p)} $ \eqref{eq: basis approximation of W},
-			Gram matrix with respect to basis functions
-			$J^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)} $
-			\eqref{def:J_and_J_star},
-			Gram matrix with respect to second derivatives of the basis functions 
-			$\ddot{J}^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)}$
-			\eqref{def:J_dotdot_ast},
-			regularization matrix $\Lambda  \in \mathbb{R}^{(MK+p) \times (MK+p)}$ \eqref{def:Lambda}
-			%%%%%%%%%%%%%%%%%%%%%
+		\State 	\textbf{Initialize:} $(\mathbb{B}, \mathbb{B}^{\prime\prime}, \Theta^{[1]}, \mathbf{y}^{[1]})$ as the data objects after basis expansion, following Section \ref{sec: finite basis approximation}.
+
+		\State Standardize  $\widetilde{W}_1^{[1]}, \ldots, \widetilde{W}_n^{[1]}$ and $Y_1^{[1]}, \ldots, Y_n^{[1]}$, following Section \ref{subsec: Data Preprocessing}
+		\For{$l = 1, 2, \ldots, L$}
+		\\
+		\textbf{PLS direction and score estimation  (Proposition \ref{proposition:linear_regul}): }
+		\State $\mathbf{u}_j^{[l]} \leftarrow B \Theta_j^{[l]\top} \mathbf{y}^{[l]}, ~j = 1, \ldots, K$
+		\State $\mathbf{v}^{[l]} \leftarrow \mathbf{Z}^{[l]\top} \mathbf{y}^{[l]} $
+		\State $	q^{[l]}  \leftarrow \sum_{j=1}^K \mathbf{u}_j^{[l]\top} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j^{[l]} + \mathbf{v}^{[l]\top} \mathbf{v}^{[l]}$
+		\State $( \hat{\gamma}_{j1}^{[l]} , \ldots, \hat{\gamma}_{jM}^{[l]} )^\top  \leftarrow \frac{1}{\sqrt{q}} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j^{[l]} , ~j = 1, \ldots, K$
+		\State $\hat{\boldsymbol{\zeta}}^{[l]}  \leftarrow \frac{1}{\sqrt{q}} \mathbf{v}^{[l]} $
+		\State $	\hat{\xi}^{[l]}	\leftarrow 
+		\biggl(
+		\sum_{m=1}^M \hat{\gamma}_{1m}^{[l]} \, b_m(t),
+		\ldots, 
+		\sum_{m=1}^M \hat{\gamma}_{Km}^{[l]} \, b_m(t), \hat{\boldsymbol{\zeta}}^{[l]}
+		\biggr)
+		$
+		\Comment{PLS direction} 
 		\State 
-			$\widetilde{C}^{*[1]} \leftarrow \widetilde{C}^*$
-			\For{ l = 1, 2, \ldots  $T$}
-			\State $\mathbf{V}^\ast \leftarrow n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast$
-			\Comment{ \eqref{def:V_star}}
-			\State 	$\widehat{\xi}_l^\ast \leftarrow \arg \max_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1
 		$
-			\Comment{ \eqref{eq: Regularized generalized rayleigh quotient equation}} 
-			\State $\widehat{\boldsymbol{\rho}}_l
+		\widehat{\rho}_i^{[l]} \leftarrow \langle \hat{\xi}^{[l]},   \tilde{W}^{[l]}_i \rangle, 
+		~i=1,  \ldots, n
+		$ \Comment{PLS score}
+		\\
+		\textbf{Residualization (Proposition \ref{proposition:closed_form_orthgonalization}):}
+		\State $\nu^{[l]} 
 		\leftarrow
-			\widetilde{C}^* J^\ast  \widehat{\xi}_l^\ast
-			$
-			\Comment{$\in \mathbb{R}^n$; \eqref{compute_pls_score}}
+		\frac{
+			\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{i}^{[l]}}{
+			\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}
+		}$ \Comment{Least squares estimate} 
+		%
+		\State $ Y_i^{[l+1]} \leftarrow Y_i^{[l]} - \nu^{[l]}\widehat{\rho}_i^{[l]}~i=1,  \ldots, n$
+		%
+		\State $ \widehat{ \delta }^{[l]}  \leftarrow \frac{1}{\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}}\sum_{i=1}^n  \widehat{\rho}_{i}^{[l]}\widetilde{W}_i^{[l]} $ \Comment{Least squares estimate} 
+		\label{alg:step:scalar_pls_residualization}
+		\State $\widetilde{W}_i^{[l+1]}  \leftarrow \widetilde{W}_i^{[l]} -   \widehat{\rho}_{i}^{[l]}  \widehat{ \delta}^{[l]} $
 		\EndFor
-			\State Output a
+		\textbf{Regression coefficient recovery (Section \ref{section:sub:regression_coeff}):}
+		\State
+		$\widehat{ \zeta }^{[1]} \leftarrow \widehat{ \xi }^{[1]}$
+		\For{$l =  2, \ldots, L$}
+		\State $\widehat{ \zeta }^{[l]} \leftarrow \widehat{  \xi }^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{ \delta }^{[u]}, \widehat{ \xi }^{[l]} \rangle  \widehat{ \zeta }^{[u]}$  
+		\EndFor
+		$	\widehat{ \beta } \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \zeta}^{[l]}$ \Comment{regression coefficient estimate}
+		\State \textbf{Output:} the  regression coefficient estimate $	\widehat{ \beta }$
 	\end{algorithmic}
 \end{algorithm}
+		Consider the optimization problem described in Proposition~\ref{proposition:eigen_regul}. Define the following quantities, which depend on the observed data but are not decision variables:
+
+	Then the unique (up to sign) solution to the regularized maximization problem is given in closed form by
 
@@
 
+	\subsection{ Tucker's Criterion  }\label{section:main:tucker}\jongmin{Previously, was in theoretical property section, now procedes the method section, to motivate the estimation procedure}
+
+	% The pointwise algorithm is highly inefficient and may not be even feasible for multiple dense and/or irregular functional data.
+Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components.
+Therefore, in this section, we introduce a novel framework for fitting a regression with a hybrid response and scalar predictor.
+The framework is readily applicable to dense and irregular functional data, and supports regularization techniques to prevent overfitting and reduce variance.
+
+	The fundamental property of classical scalar PLS is that the PLS component direction  corresponds to the first eigenvector of the squared covariance matrix, satisfying  the Tucker's Criterion \citep{Tucker1938}.
+	Under a mild assumption,
+	We derive an analogous result  in our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
+	This justifies our estimation procedure introduced in Section \ref{section:main:our_algorithm}.
+	We omit $l$ in the notations and first define the cross-covariance term between the response and the functional predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$): 
+	\begin{equation}\label{def:cross_covariance_yx}
+		\sigma_{YX}
+		=
+		\bigl(
+		\sigma_{YX, 1}(t) , \ldots, \sigma_{YX, K}(t) 
+		\bigr)
+		:=
+		\bigl(
+		\mathbb{E}
+		[Y_1 X_{11}]
+		,\ldots, 
+		\mathbb{E}
+		[Y_1  X_{1K}]
+		\bigr)   \in \mathcal{F}^{\otimes K},
+	\end{equation}
+	and between the response and the scalar predictor:
+	\begin{equation*}
+		\sigma_{YZ} 
+		= 
+		(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
+		:= 
+		\bigl(
+		\mathbb{E}[Y_1 Z_{11}]
+		,\ldots,
+		\mathbb{E}[Y_1 Z_{1p}]
+		\bigr)^\top %= E(Y\mathbf{Z})
+		\in \mathbb{R}^p.
+	\end{equation*}
+	Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
+	\begin{equation*}
+		\Sigma_{YW} :=  
+		\mathbb{E}
+		[ Y_1 W_1 ]
+		=
+		\bigl(
+		\sigma_{YX, 1} , \ldots, \sigma_{YX, K} , \, \sigma_{YZ}
+		\bigr) \in \mathbb{H}.
+	\end{equation*}
+	Based on these definitions, we introduce two cross-covariance operators and their properties.
+	\begin{lemma}\label{lemma:cross_cov_functional}
+		Define the operator $
+		\mathcal{C}_{YW}
+		=
+		\mathbb{E}(W_1 \otimes_\mathbb{H} Y_1)
+		: \mathbb{H} \rightarrow \mathbb{R}$ such that for any $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathbb{H}$, it maps $h$ to a real number as: \begin{equation*} \mathcal{C}_{YW} h := \mathbb{E} \left[ \langle W_1, h \rangle_\mathbb{H} Y_1 \right] = \langle \Sigma_{YW}, h \rangle_\mathbb{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt + \sigma_{YW}^\top \mathbf{v}.
+\end{equation*}
+		\jongmin{instead of showing $\mathcal{U}$ is compact, let's show $\mathcal{C}_{YW}$ is compact.
+This way, we don't need uniform continuiity of $\sigma_{YX}$.}If there exist finite constants $Q_1$ and $Q_2$ such that
+		\begin{align}\label{condition_for_compact}
+			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
+		\end{align}
+		the operator $\mathcal{C}_{YW}$ is a compact operator.
+	\end{lemma}
+	Proof of Lemma \ref{lemma:cross_cov_functional}
+	is provided in Appendix \ref{section:proof:lemma:cross_cov_functional}.
+	\begin{lemma}\label{lemma:cross_cov_operator}
+		Define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathbb{H}$,
+		which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathbb{H}$ as follows:
+		%%%%
+		\begin{align*}		
+			\mathcal{C}_{WY} d 
+			:= 
+			\mathbb{E} 
+			\bigl[
+			\langle Y_1, d \rangle W_1 
+			\bigr] 
+			= 
+			\mathbb{E}
+			[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
+		\end{align*}
+		Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
+	\end{lemma}
+
+	The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.
+
+	Based on these two operators, we define a positive   operator as follows:
+	\begin{lemma}[Composite cross-covariance operator]\label{lemma:composite_cross_cov}
+		Define
+		$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathbb{H} \rightarrow \mathbb{H}$ as an operator which performs the following mapping:
+		\begin{equation*}
+			\mathcal{U} h 
+			= 
+			\mathcal{C}_{WY} ( \mathcal{C}_{YW} h) 
+			=
+			\mathcal{C}_{YW} (\langle \Sigma_{YW}, h \rangle_\mathbb{H}) 
+			=  
+			\Sigma_{YW} \, \langle \Sigma_{YW}, h \rangle_\mathbb{H} 
+			= 
+			(\Sigma_{YW} \otimes \Sigma_{YW}) h.
+		\end{equation*}
+		In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$.
+		Then $\mathcal{U}$
+		is a self-adjoint and positive-semidefinite operator.
+		Under the conditions of Lemma \ref{lemma:cross_cov_functional}, $\mathcal{U}$ is a compact operator.
+	\end{lemma}
+	The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
+	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Lemma \ref{lemma:composite_cross_cov} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathbb{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
+
+	The following theorem introduces the population-level PLS and Tucker's Criterion, adapted to our scalar-on-hybrid regression model setting, based on the aforementioned operators defined in the hybrid space.
+	\begin{theorem}[Population PLS and Tucker's criterion]\label{theorem:population_PLS} Under the conditions of Lemma \ref{lemma:cross_cov_functional}, the constrained maximum
+		\begin{equation*} 
+			\max \limits_{\substack{\xi \in \mathbb{H} \\ \Vert \xi \Vert_\mathbb{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathbb{H}, Y \right)
+		\end{equation*} 
+		is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
+	\end{theorem}
+	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.
+	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]}  W^{[l]})$.
 	A fundamental property of partial least squares   is that its derived bases are orthonormal.
@@
 	\begin{definition}[Roughness-sensitive inner product]\label{def:hybrid_inner_product_roughness}
-		Given two hybrid predictors $W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$ and $W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$, both elements of $\mathcal{H}$ as defined in Definition \ref{def:hybid_predictor}, and a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, the roughness-sensitive inner product between $W_1$ and $W_2$ is defined as:
+		Given two hybrid predictors $W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$ and $W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$, both elements of $\mathbb{H}$ as defined in Definition \ref{def:hybid_predictor}, and a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, the roughness-sensitive inner product between $W_1$ and $W_2$ is defined as:
 		\begin{equation}		\label{eq: hybrid inner product_roughness}
-			\langle W_1, W_2\rangle_{\mathcal{H}, \Lambda}
+			\langle W_1, W_2\rangle_{\mathbb{H}, \Lambda}
 			:=
@@
 	\begin{proposition}[Orthonormality of estimated PLS component directions]\label{proposition: modified orthnormality of PLS components}
-		The PLS component directions $\widehat{\xi}_1, \widehat{\xi}_2, \ldots, \widehat{\xi}_L$, estimated via Proposition \ref{proposition:eigen_regul} with a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, are mutually orthonormal with respect to the inner product $\langle \cdot, \cdot \rangle_{\mathcal{H}, \Lambda}$.
+		The PLS component directions $\widehat{\xi}_1, \widehat{\xi}_2, \ldots, \widehat{\xi}_L$, estimated via Proposition \ref{proposition:eigen_regul} with a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, are mutually orthonormal with respect to the inner product $\langle \cdot, \cdot \rangle_{\mathbb{H}, \Lambda}$.
 That is,
 		\begin{equation*}
-			\langle \widehat{\xi}_{l_1}, \widehat{\xi}_{l_2} \rangle_{\mathcal{H}, \Lambda}
+			\langle \widehat{\xi}_{l_1}, \widehat{\xi}_{l_2} \rangle_{\mathbb{H}, \Lambda}
 			= \mathbbm{1}(l_1 = l_2), \quad l_1, l_2 = 1, \ldots, L.
@@
 
+	\section{Proof of Section \ref{section:main:our_algorithm}}
+	\subsection{Proof of Lemma \ref{lemma:hybrid_hilbert_space}}\label{section:proof:lemma:hybrid_hilbert_space}
+	\begin{proof}
+Both $\mathbb{L}^2[0,1]$ and $\mathbb{R}^p$ are Hilbert spaces, with their inner products, norms, and metrics corresponding to the terms defined in equation \eqref{eq: hybrid inner product}.
+A finite Cartesian product of Hilbert spaces, equipped with an $\ell_2$ norm of the component metrics (which is our metric), is also a Hilbert space.
+Next, both $\mathbb{L}^2[0,1]$ and $\mathbb{R}^p$ are separable.
+For  example,  the set of all polynomials with rational coefficients is a countable and dense subset of  $\mathbb{L}^2[0,1]$, and  the set of all vectors with rational components forms a countable and dense subset of $\mathbb{R}^p$.
+The finite Cartesian product of separable spaces is also separable. This completes the proof of Lemma \ref{lemma:hybrid_hilbert_space}.
+	\end{proof}
 	\section{Proof of Section \ref{section:main:tucker}}
@@
 \textit{Linearity.}~	  
- The operator $\mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathbb{R}$ is defined as 
- $\mathcal{C}_{YW} h = \langle \Sigma_{YW}, h \rangle_\mathcal{H}$.
- For any $h_1, h_2 \in \mathcal{H}$ and scalar $c \in \mathbb{R}$, the linearity of the inner product implies: \begin{align*} \mathcal{C}_{YW}(h_1 + h_2) &= \langle \Sigma_{YW}, h_1 + h_2 \rangle_\mathcal{H} = \langle \Sigma_{YW}, h_1 \rangle_\mathcal{H} + \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H} = \mathcal{C}_{YW} h_1 + \mathcal{C}_{YW} h_2,
+ The operator $\mathcal{C}_{YW}: \mathbb{H} \rightarrow \mathbb{R}$ is defined as 
+ $\mathcal{C}_{YW} h = \langle \Sigma_{YW}, h \rangle_\mathbb{H}$.
+ For any $h_1, h_2 \in \mathbb{H}$ and scalar $c \in \mathbb{R}$, the linearity of the inner product implies: \begin{align*} \mathcal{C}_{YW}(h_1 + h_2) &= \langle \Sigma_{YW}, h_1 + h_2 \rangle_\mathbb{H} = \langle \Sigma_{YW}, h_1 \rangle_\mathbb{H} + \langle \Sigma_{YW}, h_2 \rangle_\mathbb{H} = \mathcal{C}_{YW} h_1 + \mathcal{C}_{YW} h_2,
  	 \\ 
- 	 \mathcal{C}_{YW}(c h) &= \langle \Sigma_{YW}, c h \rangle_\mathcal{H} = c \langle \Sigma_{YW}, h \rangle_\mathcal{H} = c \, \mathcal{C}_{YW} h. \end{align*}
+ 	 \mathcal{C}_{YW}(c h) &= \langle \Sigma_{YW}, c h \rangle_\mathbb{H} = c \langle \Sigma_{YW}, h \rangle_\mathbb{H} = c \, \mathcal{C}_{YW} h. \end{align*}
  Thus, $\mathcal{C}_{YW}$ is a linear functional.
@@
 \textit{Boundedness.}~ 
-To show that $\mathcal{C}_{YW}$ is bounded, we need to find a finite constant $M$ such that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathcal{H}$ for all $h \in \mathcal{H}$.
+To show that $\mathcal{C}_{YW}$ is bounded, we need to find a finite constant $M$ such that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathbb{H}$ for all $h \in \mathbb{H}$.
 By the Cauchy-Schwarz inequality, we have: \begin{equation*}
-	|\mathcal{C}_{YW} h| = |\langle \Sigma_{YW}, h \rangle_\mathcal{H}| \leq \|\Sigma_{YW}\|_\mathcal{H} \|h\|_\mathcal{H}. 
-	\end{equation*}
-Now, we must verify that $\|\Sigma_{YW}\|_\mathcal{H}$ is finite. 
+	|\mathcal{C}_{YW} h| = |\langle \Sigma_{YW}, h \rangle_\mathbb{H}| \leq \|\Sigma_{YW}\|_\mathbb{H} \|h\|_\mathbb{H}. 
+	\end{equation*}
+Now, we must verify that $\|\Sigma_{YW}\|_\mathbb{H}$ is finite. 
 Recall that 
@@
   Let $\mu([0,1])$ denote a Lebesgue measure of $[0,1]$, and let $T = \max_{k=1, \ldots, K} \, \mu([0,1])$.
-The norm of $\Sigma_{YW}$ in $\mathcal{H}$ is given by: \begin{equation*} \|\Sigma_{YW}\|_\mathcal{H}^2 = \sum_{k=1}^K \int_0^1 \sigma_{YX,k}(t)^2 \, dt + \sum_{r=1}^p \sigma_{YZ,r}^2
+The norm of $\Sigma_{YW}$ in $\mathbb{H}$ is given by: \begin{equation*} \|\Sigma_{YW}\|_\mathbb{H}^2 = \sum_{k=1}^K \int_0^1 \sigma_{YX,k}(t)^2 \, dt + \sum_{r=1}^p \sigma_{YZ,r}^2
 	<
@@
  where the last inequality uses the condition \eqref{condition_for_compact}.
- Let $M = \sqrt{K T Q_1 + p  Q_2 }$. Thus, we have shown that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathcal{H}$ for a finite constant $M$.
+ Let $M = \sqrt{K T Q_1 + p  Q_2 }$. Thus, we have shown that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathbb{H}$ for a finite constant $M$.
  This completes the proof of Lemma \ref{lemma:cross_cov_functional}.
@@
  \begin{proof}
-For $h \in \mathcal{H}$ and $d \in \mathbb{R}$, we have:
+For $h \in \mathbb{H}$ and $d \in \mathbb{R}$, we have:
 \begin{equation*}
@@
 	[
-		 \langle W_1, h \rangle_\mathcal{H} Y_1  
+		 \langle W_1, h \rangle_\mathbb{H} Y_1  
 	] 	 \,  d
@@
 =
-\mathbb{E} \langle   Y_1 W_1 d , \, h\rangle_{\mathcal{H}} 
+\mathbb{E} \langle   Y_1 W_1 d , \, h\rangle_{\mathbb{H}} 
 %%%%%%%%%%%%%%%%%%%%%%%%
- = \langle h, \, \mathbb{E}[Y_1 W_1 d   ]\rangle_{\mathcal{H}}
- =
- \langle h, \mathcal{C}_{WY} d \rangle_{\mathcal{H}}
-\end{equation*}
-Thus, we have $\langle \mathcal{C}_{YW} h, d \rangle =  \langle h, \mathcal{C}_{WY} d \rangle_{\mathcal{H}}$, which implies $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
+ = \langle h, \, \mathbb{E}[Y_1 W_1 d   ]\rangle_{\mathbb{H}}
+ =
+ \langle h, \mathcal{C}_{WY} d \rangle_{\mathbb{H}}
+\end{equation*}
+Thus, we have $\langle \mathcal{C}_{YW} h, d \rangle =  \langle h, \mathcal{C}_{WY} d \rangle_{\mathbb{H}}$, which implies $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
 	This completes the proof of Lemma \ref{lemma:cross_cov_operator}.
@@
 	\textit{Self-adjoint.}~
-	For any $h_1, h_2 \in \mathcal{H}$, we have
+	For any $h_1, h_2 \in \mathbb{H}$, we have
 	\begin{align*}
@@
 		\mathcal{U} h_1, \, h_2 
-		\rangle_\mathcal{H}  
+		\rangle_\mathbb{H}  
 		= 
 		\bigl \langle 
-		\langle h_1, \Sigma_{YW} \rangle_\mathcal{H} \Sigma_{YW},
+		\langle h_1, \Sigma_{YW} \rangle_\mathbb{H} \Sigma_{YW},
 		\,
 		h_2
-		\bigr \rangle_\mathcal{H}
+		\bigr \rangle_\mathbb{H}
 		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		&= \langle h_1, \Sigma_{YW} \rangle_\mathcal{H} \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H}
+		&= \langle h_1, \Sigma_{YW} \rangle_\mathbb{H} \langle \Sigma_{YW}, h_2 \rangle_\mathbb{H}
 		%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 		\,
-		\langle \Sigma_{YW}, h_2 \rangle_\mathcal{H} \Sigma_{YW} 
-		\bigr \rangle_\mathcal{H}
-		\\ 	&= \langle h_1, \mathcal{U} h_2 \rangle_\mathcal{H}.
+		\langle \Sigma_{YW}, h_2 \rangle_\mathbb{H} \Sigma_{YW} 
+		\bigr \rangle_\mathbb{H}
+		\\ 	&= \langle h_1, \mathcal{U} h_2 \rangle_\mathbb{H}.
 	\end{align*}
@@
 	\textit{Positive-semidefinite.}~
-	For every $h \in \mathcal{H}$, we have
+	For every $h \in \mathbb{H}$, we have
 	\begin{equation*}
@@
 		h
-		\rangle_\mathcal{H}
+		\rangle_\mathbb{H}
 		=
@@
 		\langle 
-		\Sigma_{YW},\, h \rangle_{\mathcal{H}}  \Sigma_{YW}, \, h
-		\bigr \rangle_\mathcal{H}
-		= \langle \Sigma_{YW}, \, h \rangle_\mathcal{H}^2 \ge 0.
+		\Sigma_{YW},\, h \rangle_{\mathbb{H}}  \Sigma_{YW}, \, h
+		\bigr \rangle_\mathbb{H}
+		= \langle \Sigma_{YW}, \, h \rangle_\mathbb{H}^2 \ge 0.
 	\end{equation*}
@@
 \begin{equation*}
-	\Vert \mathcal{C}_{YW} \Vert_{\mathrm{op}} = \sup_{\substack{h \in \mathcal{H} \\ \Vert h \Vert_\mathcal{H}=1}} | \mathcal{C}_{YW} h |^2 
-	= \sup_{\substack{h \in \mathcal{H} \\ \Vert h \Vert_\mathcal{H}=1}} | E(\langle W, h \rangle_\mathcal{H} Y)|^2 
-	= \sup_{\substack{h \in \mathcal{H} \\ \Vert h \Vert_\mathcal{H}=1}} \textnormal{Cov}^2(\langle W, h \rangle_\mathcal{H}, Y) 
+	\Vert \mathcal{C}_{YW} \Vert_{\mathrm{op}} = \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | \mathcal{C}_{YW} h |^2 
+	= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | E(\langle W, h \rangle_\mathbb{H} Y)|^2 
+	= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} \textnormal{Cov}^2(\langle W, h \rangle_\mathbb{H}, Y) 
 	= \kappa_1^2,
@@
 	\begin{proof}
-		Let $\xi = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta}) \in \mathcal{H}$.
-Assume that each functional component $\xi_j \in L^2([0,1])$ lies in the span of the basis functions ${b_1(t), \ldots, b_M(t)}$ and can be written as
+		Let $\xi = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta}) \in \mathbb{H}$.
+Assume that each functional component $\xi_j \in \mathbb{L}^2([0,1])$ lies in the span of the basis functions ${b_1(t), \ldots, b_M(t)}$ and can be written as
 		\begin{equation*}
@@
 			\widehat{\textnormal{Cov}} (
-			\langle \widetilde{W}, \xi  \rangle_{\mathcal{H}}, Y 
+			\langle \widetilde{W}, \xi  \rangle_{\mathbb{H}}, Y 
 			) 
@@
 			y_i
-			\langle \widetilde{W}_i, \xi \rangle_\mathcal{H} \\
+			\langle \widetilde{W}_i, \xi \rangle_\mathbb{H} \\
 			&= %2
@@
 			\widehat{\textnormal{Cov}}^2 (
-			\langle \widetilde{W}, \xi  \rangle_{\mathcal{H}}, Y 
+			\langle \widetilde{W}, \xi  \rangle_{\mathbb{H}}, Y 
 			)  
@@
 		\end{align*}
-		The squared norm of $\xi$ in the hybrid Hilbert space $\mathcal{H}$ 
+		The squared norm of $\xi$ in the hybrid Hilbert space $\mathbb{H}$ 
 		%can be expressed as the inner product on $(\mathbb{R}^M)^K \times \mathbb{R}^p$ defined in Lemma~\ref{lemma:valid_inner_product_tuple} as follows:
@@
 		\begin{align*}
-			\langle {\xi},{\xi} \rangle_{\mathcal{H}}
+			\langle {\xi},{\xi} \rangle_{\mathbb{H}}
 			&=
@@
 		\begin{equation*}
-			\| \xi  \|_\mathcal{H} +  \sum \limits_{j=1}^K \lambda_j 
+			\| \xi  \|_\mathbb{H} +  \sum \limits_{j=1}^K \lambda_j 
 			\operatorname{PEN}(\xi_K) 
@@
 	=
-	\langle \widetilde{W}_i, \, \hat{\xi} \rangle_{\mathcal{H}}$.
+	\langle \widetilde{W}_i, \, \hat{\xi} \rangle_{\mathbb{H}}$.
 	Using the basis expansion coefficient notation from \eqref{def:truncated_zeta_and_delta}, \eqref{def:coef_vector_form}, \eqref{def:theta}, and \eqref{def:B_matrix}, the full vector of PLS scores $\hat{\boldsymbol{\rho}}  = (\hat{\rho}_1, \ldots, \hat{\rho}_n)^\top$
@@
 		\widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta
-		\rangle_{\mathcal{H}}
+		\rangle_{\mathbb{H}}
 		+
@@
 	\begin{align*}
-		\operatorname{PENSSE}( \delta) &= \sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta, \, \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta \rangle_{\mathcal{H}} + \tau \sum_{j=1}^K\operatorname{PEN}(\delta_j) \\
+		\operatorname{PENSSE}( \delta) &= \sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta, \, \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta \rangle_{\mathbb{H}} + \tau \sum_{j=1}^K\operatorname{PEN}(\delta_j) \\
 		&= 
 		\underbrace{
-			\sum_{i=1}^n \langle \widetilde{W}_i^{[l]}, \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}}_{A} 
+			\sum_{i=1}^n \langle \widetilde{W}_i^{[l]}, \, \widetilde{W}_i^{[l]} \rangle_{\mathbb{H}}}_{A} 
 		\underbrace{
-			-2 \sum_{i=1}^n \hat{\rho}_i^{[l]} \langle \delta, \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}} 
+			-2 \sum_{i=1}^n \hat{\rho}_i^{[l]} \langle \delta, \, \widetilde{W}_i^{[l]} \rangle_{\mathbb{H}} 
 		}_{B_1(\boldsymbol{\delta})}
@@
 			(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})
-			\langle \delta, \, \delta \rangle_{\mathcal{H}}
+			\langle \delta, \, \delta \rangle_{\mathbb{H}}
 		}_{B_2(\boldsymbol{\delta})}
@@
 		B_1(\boldsymbol{\delta}) &= 
-		- 2\sum_{i=1}^n \hat{\rho}_i  \langle \delta, \, \widetilde{W}_i  \rangle_{\mathcal{H}} 
+		- 2\sum_{i=1}^n \hat{\rho}_i  \langle \delta, \, \widetilde{W}_i  \rangle_{\mathbb{H}} 
 		=
@@
 		(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})
-		\langle \delta, \, \delta \rangle_{\mathcal{H}}
+		\langle \delta, \, \delta \rangle_{\mathbb{H}}
 		=
@@
 		The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
-	$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients
+	$\hat{\delta}^{[l]}   \in \tilde{\mathbb{H}}$, has basis coefficients
 	\begin{equation*}
@@
 	The brief strategy of the proof is as follows.
-		We   show that an image of a bounded family in $\mathcal{H}$ under $\mathcal{U}$ is uniformly bounded and equicontinuous.
+		We   show that an image of a bounded family in $\mathbb{H}$ under $\mathcal{U}$ is uniformly bounded and equicontinuous.
 		Then we apply the Arzel\'{a}-Ascoli theorem to show that $\mathcal{U}$ is \textit{compact}.
 
-Let $\mathcal{B}=\{h \in \mathcal{H}: \Vert h \Vert_\mathcal{H}^2 \le M\}$ denote a bounded family in $\mathcal{H}$ for some constant $0 < M < \infty$.
+Let $\mathcal{B}=\{h \in \mathbb{H}: \Vert h \Vert_\mathbb{H}^2 \le M\}$ denote a bounded family in $\mathbb{H}$ for some constant $0 < M < \infty$.
 Clearly, $h=(f, \mathbf{v}) \in \mathcal{B}$ also implies 
@@
 \noindent
-\textit{Uniform boundedness of $\mathcal{I}$.}~Given a hybrid object $h = (f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$ and an evaluation point $\mathbf{t}= (t_1, \ldots, t_k) \in [0,1]^K$, we denote the $\ell_2$ norm of the evaluated object $\bigl( f_1(t_1), \ldots, f_k(t_k), \mathbf{v} \bigr)$ as follows:
+\textit{Uniform boundedness of $\mathcal{I}$.}~Given a hybrid object $h = (f_1, \ldots, f_K, \mathbf{v}) \in \mathbb{H}$ and an evaluation point $\mathbf{t}= (t_1, \ldots, t_k) \in [0,1]^K$, we denote the $\ell_2$ norm of the evaluated object $\bigl( f_1(t_1), \ldots, f_k(t_k), \mathbf{v} \bigr)$ as follows:
 $\bigl(
@@
  \overset{(i)}{=} 
-\Vert \langle \Sigma_{YW}, h \rangle_\mathcal{H} \, \Sigma_{YW}(\mathbf{t}) \Vert^2_2
+\Vert \langle \Sigma_{YW}, h \rangle_\mathbb{H} \, \Sigma_{YW}(\mathbf{t}) \Vert^2_2
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   =
-\langle \Sigma_{YW}, h \rangle_\mathcal{H}^2
+\langle \Sigma_{YW}, h \rangle_\mathbb{H}^2
 \Vert   \Sigma_{YW}(\mathbf{t}) \Vert^2_2.
   \end{equation}
-  We will show that $\Vert g (\mathbf{t}) \Vert^2_2 < \infty$ by  showing $\langle \Sigma_{YW}, h \rangle_\mathcal{H}^2 < \infty$ and $\Vert   \Sigma_{YW}(\mathbf{t}) \Vert^2_2 < \infty$ in turn.
+  We will show that $\Vert g (\mathbf{t}) \Vert^2_2 < \infty$ by  showing $\langle \Sigma_{YW}, h \rangle_\mathbb{H}^2 < \infty$ and $\Vert   \Sigma_{YW}(\mathbf{t}) \Vert^2_2 < \infty$ in turn.
 First, to bound
-   $\langle \Sigma_{YW}, h \rangle_\mathcal{H}^2$, it suffices to bound $\langle \Sigma_{YW}, h \rangle_\mathcal{H}$:
+   $\langle \Sigma_{YW}, h \rangle_\mathbb{H}^2$, it suffices to bound $\langle \Sigma_{YW}, h \rangle_\mathbb{H}$:
 \begin{align*}
-\langle \Sigma_{YW}, h \rangle_\mathcal{H}
+\langle \Sigma_{YW}, h \rangle_\mathbb{H}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \noindent
-\textit{Equicontinuity of $\mathcal{I}$.}~Given a hybrid object $h = (f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$ and 
+\textit{Equicontinuity of $\mathcal{I}$.}~Given a hybrid object $h = (f_1, \ldots, f_K, \mathbf{v}) \in \mathbb{H}$ and 
 two evaluation points
@@
 &= %%%%%%%%%%%%%%%
-	\Vert \langle \Sigma_{YW}, h \rangle_\mathcal{H} 
+	\Vert \langle \Sigma_{YW}, h \rangle_\mathbb{H} 
 	\,
-	\Sigma_{YW}(\mathbf{t}) - \langle \Sigma_{YW}, h \rangle_\mathcal{H} \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2_2
+	\Sigma_{YW}(\mathbf{t}) - \langle \Sigma_{YW}, h \rangle_\mathbb{H} \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2_2
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \\&=
-\langle \Sigma_{YW}, h \rangle_\mathcal{H}^2 \Vert \Sigma_{YW}(\mathbf{t})- \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2.
+\langle \Sigma_{YW}, h \rangle_\mathbb{H}^2 \Vert \Sigma_{YW}(\mathbf{t})- \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2.
 \end{align*}
-We have already shown in \eqref{squared_ip_bound} that  $\langle \Sigma_{YW}, h \rangle_\mathcal{H}^2 \leq  2K^2 M TQ_1   + 2MpQ_2$.
+We have already shown in \eqref{squared_ip_bound} that  $\langle \Sigma_{YW}, h \rangle_\mathbb{H}^2 \leq  2K^2 M TQ_1   + 2MpQ_2$.
 Next we bound $\Vert \Sigma_{YW}(\mathbf{t})- \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2$, which do not depend on $h$.
@@
 			\\&=
-			\langle \widehat{\xi}_{l}, \widehat{\xi}_{l} \rangle_{\mathcal{H}, \Lambda},
+			\langle \widehat{\xi}_{l}, \widehat{\xi}_{l} \rangle_{\mathbb{H}, \Lambda},
 			\numberthis \label{rough_norm_matrix_form}
@@
 		\begin{align*}
-			\langle \widehat{\xi}_{l_1}, \widehat{\xi}_{l_2} \rangle_{\mathcal{H}, \Lambda}
+			\langle \widehat{\xi}_{l_1}, \widehat{\xi}_{l_2} \rangle_{\mathbb{H}, \Lambda}
 			& \overset{(i)}{=}
@@
 			\hat{\xi}^{[l_2]}
-			\rangle_{\mathcal{H}},
+			\rangle_{\mathbb{H}},
 			\numberthis \label{thetaBzetal2i}
@@
 \widetilde{W}_1^{[l_1-1]}, \ldots, \widetilde{W}_n^{[l_1-1]}
-	\bigr)^\top \in \tilde{\mathcal{H}}^{\otimes n},
+	\bigr)^\top \in \tilde{\mathbb{H}}^{\otimes n},
 \end{equation}
@@
 	\hat{\xi}^{[l_2]}
-	\rangle_{\mathcal{H}}
+	\rangle_{\mathbb{H}}
 	:= 
@@
 	\hat{\xi}^{[l_2]}
-	\rangle_{\mathcal{H}},
+	\rangle_{\mathbb{H}},
 	\ldots, 
@@
 	\hat{\xi}^{[l_2]}
-	\rangle_{\mathcal{H}}
+	\rangle_{\mathbb{H}}
 	\biggr)^\top 
@@
 \hat{\xi}^{[l_2]}
-\rangle_{\mathcal{H}} = \mathbf{0}$.
+\rangle_{\mathbb{H}} = \mathbf{0}$.
 Using these notations and  \eqref{algorithm_step:residualization_predictor:recall}, we have, with some abuse of notation,
@@
 \hat{\xi}^{[l_2]}
-\rangle_{\mathcal{H}}
+\rangle_{\mathbb{H}}
   = 
@@
 \hat{\xi}^{[l_2]}
-\rangle_{\mathcal{H}} 
+\rangle_{\mathbb{H}} 
 - 
@@
 	\hat{\xi}^{[l_2]}
-	\bigr \rangle_{\mathcal{H}}.
+	\bigr \rangle_{\mathbb{H}}.
 \end{equation*}
@@
 	\hat{\xi}^{[l_2]}
-	\rangle_{\mathcal{H}}  = 
+	\rangle_{\mathbb{H}}  = 
 	P^{[l_1-1]} \langle 	\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
 	\hat{\xi}^{[l_2]}
-	\rangle_{\mathcal{H}}$.
+	\rangle_{\mathbb{H}}$.
 Repeatedly using this relationship, we have
@@
 	\hat{\xi}^{[l_2]}
-	\rangle_{\mathcal{H}} 
+	\rangle_{\mathbb{H}} 
 	&=
@@
 \hat{\xi}^{[l_2]}
-\rangle_{\mathcal{H}} 
+\rangle_{\mathbb{H}} 
 	\\
@@
 		\hat{\xi}^{[l_2]}
-		\rangle_{\mathcal{H}}
+		\rangle_{\mathbb{H}}
 		  \\
@@
 \hat{\xi}^{[l_2]}
-\bigr \rangle_{\mathcal{H}}
+\bigr \rangle_{\mathbb{H}}
 \biggr\}
@@
 \hat{\xi}^{[l_2]}
-\bigr \rangle_{\mathcal{H}}
+\bigr \rangle_{\mathbb{H}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \hat{\xi}^{[l_2]}
-\big \rangle_{\mathcal{H}}
+\big \rangle_{\mathbb{H}}
 \end{align*}
@@
 \widehat{ \rho }^{[l_1 ]}_i \,
-\widetilde{W}^{[l_2]}_i  = 0 \in   \mathcal{H}  $,
+\widetilde{W}^{[l_2]}_i  = 0 \in   \mathbb{H}  $,
 where this   zero element represents an ordered pair of $K$ zero functions and a zero matrix.
@@
 	\hat{\xi}^{[l_1-1]}
-\rangle_{\mathcal{H}}
+\rangle_{\mathbb{H}}
 \hat{\boldsymbol{\rho}}^{[l_1-1] \top
@@
 	\hat{\xi}^{[l_1-1]}
-	\rangle_{\mathcal{H}}
+	\rangle_{\mathbb{H}}
 	\hat{\boldsymbol{\rho}}^{[l_1-1] \top
@@
 	\hat{\xi}^{[l_1-1]}
-	\rangle_{\mathcal{H}}
+	\rangle_{\mathbb{H}}
 	}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
@@
 \end{align*}
-Here, the function $h^{[l_1-1]}: \tilde{ \mathcal{H} } \mapsto \tilde{\mathcal{H}}$ maps the zero element of $\tilde{\mathcal{H}}$ to itself, where the zero element represents an ordered pair of $K$ zero functions and a zero matrix.
+Here, the function $h^{[l_1-1]}: \tilde{ \mathbb{H} } \mapsto \tilde{\mathbb{H}}$ maps the zero element of $\tilde{\mathbb{H}}$ to itself, where the zero element represents an ordered pair of $K$ zero functions and a zero matrix.
 Using this relationship, we have
@@
 		\hat{\xi}^{[l_2]}
-		\rangle_{\mathcal{H}}
+		\rangle_{\mathbb{H}}
 	}{\| 	\hat{\boldsymbol{\rho}}^{[l_2]}\|_2^2}
@@
 	\hat{\xi}^{[l_2]}
-	\rangle_{\mathcal{H}}
+	\rangle_{\mathbb{H}}
 }{\| 	\hat{\boldsymbol{\rho}}^{[l_2]}\|_2^2}

### 2025-08-17 manuscript/main.tex
normalization

@@
 		\begin{abstract}
-			Modern biomedical studies increasingly collect both functional and vector-valued predictors for each subject, introducing challenges due to high dimensionality and cross-modality correlations.
+			Modern biomedical studies increasingly collect both functional and vector-valued predictors for each subject, introducing challenges due to infinite-dimensionality and cross-modality correlations.
 Existing methods often model these components separately, failing to capture their joint predictive structure.
@@
 The first step is to account for discrepancies \textit{within} respective functional and scalar parts, if needed.
-If elements of multivariate functional data $X_i = (X_i^{(1)}, \ldots, X_i^{(K)})$ are measured in different units or have quite different domains, one can standardize them to have mean zero and integrated variance of one.
+If the functional parts $\widetilde{X}_{i1}(t), \ldots, \widetilde{X}_{iK}(t)$ are measured in different units or have quite different domains, one can standardize them to have mean zero and integrated variance of one.
 If multivariate scalar predictors $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ exhibit different amounts of variation, one can standardize them to have mean zero and unit variance.
@@
 	\begin{equation*}
-		\omega = \frac{\sum_{i=1}^n \Vert X_i \Vert_\mathcal{F}^2}{\sum_{i=1}^n \Vert \mathbf{Z}_i \Vert^2},
+		\omega = \frac{\sum_{i=1}^n \sum_{k=1}^K \Vert \widetilde{X}_i \Vert^2_{\mathbb{L}^2[0,1]}}{\sum_{i=1}^n \Vert \mathbf{Z}_i \Vert^2},
 		\label{eq: weight}
 	\end{equation*}
-	In practice, this weighting scheme can be implemented by formulating the hybrid object as $\mathbf{W} = (X, \omega^{1/2} \mathbf{Z})$, whose vector part has been scaled by a factor of $\omega^{1/2}$.
+	In practice, 
+	instead of using inner product weighted by $\omega^{1/2}$, one can implement 
+	this weighting scheme   by formulating the hybrid object as $\widetilde{W}_i = \bigl(
+	\widetilde{X}_{i1}(t), \ldots, \widetilde{X}_{iK}(t),  \omega^{1/2} \mathbf{Z}_i
+	\bigr)$, whose vector part has been scaled by a factor of $\omega^{1/2}$.
 

### 2025-08-17 manuscript/main.tex
proof repositioned

@@
 \newcommand{\jongmin}[1]{
-	{ \color{teal} JM: #1}
+	{ \color{teal} \textit{(JM: #1)}}
 }
@@
 	As an illustrative example, the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021}  records both multiple   renogram curves (functional data) and multiple renogram variables (scalar data)  for each kidney.
-	To effectively analyze such distinct yet related physiological signals, we construct a joint linear regression model incorporating both functional and scalar-valued covariates. 
-	%This approach accounts for both shared and modality-specific variations linked to clinical outcomes.
-Our work focuses on developing a method to fit the following hybrid functional linear regression model:
+	To effectively analyze such distinct yet related physiological signals, we construct a joint linear regression model incorporating both functional and scalar-valued i.i.d. covariates:
 	\begin{equation}	\label{eq:hybrid_regression_model}
@@
  \begin{algorithm} 
- 	\caption{Scalar partial least squares }\label{alg:scalar_pls}
+ 	\caption{Scalar partial least squares regression}\label{alg:scalar_pls}
  	\begin{algorithmic}[1]
@@
  		\EndFor
-\textbf{Regression coefficient recovery:}
+\textbf{Regression coefficient estimation:}
 \State
-$\widehat{\boldsymbol{\zeta}}^{[1]} \leftarrow \widehat{\boldsymbol{\xi}}^{[1]}$
+$\widehat{\boldsymbol{\iota}}^{[1]} \leftarrow \widehat{\boldsymbol{\xi}}^{[1]}$
 	\For{$l =  2, \ldots, L$}
-  \State $\widehat{\boldsymbol{\zeta}}^{[l]} \leftarrow \widehat{ \boldsymbol{\xi} }^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}^{[u]}, \widehat{\boldsymbol{\xi}}^{[l]} \rangle  \widehat{\boldsymbol{\zeta}}^{[u]}$
+  \State $\widehat{\boldsymbol{\iota}}^{[l]} \leftarrow \widehat{ \boldsymbol{\xi} }^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}^{[u]}, \widehat{\boldsymbol{\xi}}^{[l]} \rangle 
+   \widehat{\boldsymbol{\iota}}^{[u]}$  
  		\EndFor
-$	\widehat{\boldsymbol{\beta}} \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{\boldsymbol{\zeta}}^{[l]}$ \Comment{regression coefficient estimate}
+$	\widehat{\boldsymbol{\beta}} \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{\boldsymbol{\iota}}^{[l]}$ \Comment{regression coefficient estimate}
  		\State \textbf{Output:} the  regression coefficient estimate
@@
 
-\begin{definition}[Hybrid Predictor]
+\begin{definition}[Hybrid Predictor]\label{def:hybrid_predictor}
 	For the Hilbert space  $\mathbb{H}$ 
@@
 	\subsection{Preliminary step 2 : data preprocessing} \label{subsec: Data Preprocessing}
-	\jongmin{notation not changed yet}
 	Functional and scalar elements of the hybrid predictors often have incompatible units and/or exhibit different amounts of variation.
@@
 	\begin{equation*}
-		\omega = \frac{\sum_{i=1}^n \sum_{k=1}^K \Vert \widetilde{X}_i \Vert^2_{\mathbb{L}^2[0,1]}}{\sum_{i=1}^n \Vert \mathbf{Z}_i \Vert^2},
+		\omega = \frac{\sum_{i=1}^n \sum_{k=1}^K \Vert \widetilde{X}_i \Vert^2_{\mathbb{L}^2[0,1]}}{\sum_{i=1}^n \Vert \mathbf{Z}_i \Vert_2^2},
 		\label{eq: weight}
@@
 	The constraint $	\boldsymbol{\xi}^\top (\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1$
-	enforces the orthonormality of the estimated PLS component directions with respect to a modified inner product (see Section \ref{section:sub:prop_geom} for details).
+	enforces the orthonormality of the estimated PLS component directions with respect to a modified inner product (see Section \ref{section:sub:geom} for details).
 	The smoothing parameter $\lambda_k$  balances goodness of fit and smoothness in $\hat{\xi}_j$.
@@
 	Specifically,
-the $(l+1)$-th predictor is computed as a hybrid-on-scalar linear regression residual.
+the $(l+1)$-th predictor is computed as a residual of hybrid-on-scalar linear regression model:
+\begin{equation*}
+	\widetilde{W}_i^{[l]}  =
+	\widehat{\rho}_i^{[l]}
+ 	\hat{\delta}^{[l]} + \epsilon_i,
+\end{equation*}
+where $\hat{\delta}^{[l]} \in \widetilde{\mathbb{H}}$ is the regression coefficient.
 In the same spirit as the PLS component direction estimation step,
@@
 we employ a basis expansion approach to fit the entire hybrid object in one step.
-Therefore, our method is computationally efficient, applicable for dense or irregular functional data, and keeps the residual smooth, as it enforces the regression coefficient, $\delta^{[l]}$, as an element of $\tilde{\mathbb{H}}$ as defined in Equation \eqref{def:truncated_hilbert_space}.
+Therefore, our method is computationally efficient, applicable for dense or irregular functional data, and keeps the residual smooth, as it enforces  $\hat{\delta}^{[l]}$  as an element of $\widetilde{\mathbb{H}}$ as defined in Equation \eqref{def:truncated_hilbert_space}.
 	Consequently, $\delta^{[l]}$ is obtained by minimizing a  
@@
 	\begin{equation}\label{def:argmin_pensse}
-		\hat{\delta}^{[l]} := \arg \min_{\delta \in \tilde{\mathbb{H}}} \sum_{i=1}^n 
+		\hat{\delta}^{[l]} := \arg \min_{\delta \in \widetilde{\mathbb{H}}} \sum_{i=1}^n 
 		\| \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta\|_{\mathbb{H}}^2.
 	\end{equation}
-  On the other hand, the $(l+1)$-th response   is computed as a scalar-on-scalar linear regression residual. 
+  On the other hand, the $(l+1)$-th response   is computed as a residual of a scalar-on-scalar linear regression model:
+  \begin{equation*}
+  	Y_i^{[l]}  =
+  	\hat{\nu}^{[l]}   	\widehat{\rho}_i^{[l]} + \epsilon_i.
+  	\end{equation*}
  The following proposition demonstrates that this residualization step can be performed simply, analogous to scalar PLS.
@@
 		$
-	The $(l+1)$-th iteration's  predictors and responses are   computed as:
-\begin{equation}\label{algorithm_step:residualization_predictor}
+	The $(l+1)$-th iteration's  predictors and responses are computed as
+\begin{equation*}
 		\widetilde{W}_i^{[l+1]} 
+	:= 	\widetilde{W}_i^{[l]}  - 
+	\widehat{\rho}_i^{[l]}
+	\hat{\delta}^{[l]},~\text{where}~
+\delta^{[l]}
 	:= 
-	\widetilde{W}_i^{[l]}  - 
-	\frac{\widehat{\rho}_{il}}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
+	\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
 	\sum_{i=1}^n 
-	\widehat{\rho}_{il}
+	\widehat{\rho}_i^{[l]}
 	\widetilde{W}_i^{[l]},
 	%%%%%%%%%%% 
-	\quad 
-	Y_i^{[l+1]} := Y_i^{[l]} - 
+,
+\end{equation*} 	
+and
+\begin{equation}\label{algorithm_step:residualization_predictor}
+	Y_i^{[l+1]} = Y_i^{[l]} - 
+\hat{\nu}^{[l]} 
+\widehat{\rho}_i^{[l]},~\text{where}~\hat{\nu}^{[l]} :=  
 \frac{
@@
 	\| \hat{\boldsymbol{\rho}}^{[l]} \|_2^2
-	}
-	\widehat{\rho}_{il}.
+}.
 \end{equation}
@@
 \label{section:sub:regression_coeff}
-	\jongmin{notation not yet changed}
-	The regression coefficient $\boldsymbol{\eta}$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS components and scores.
-First, note that we can show $\widehat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathbb{H} = \langle \mathbf{W}_i, \widehat{\boldsymbol{\zeta}}_l \rangle_\mathbb{H}$, where $\widehat{\boldsymbol{\zeta}}_l = \widehat{\xi}_l - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}_u, \widehat{\xi}_l \rangle_{\mathbb{H}} \widehat{\boldsymbol{\zeta}}_u$ for $l \ge 2$, with $\widehat{\boldsymbol{\zeta}}_1 = \widehat{\xi}_1$.
-Then, the decomposition of $Y_i$ in \eqref{eq: decomposition} leads to
-	\begin{equation*}
-		Y_i = \sum \limits_{l=1}^L \widehat{\nu}_l \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathbb{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l \right\rangle_\mathbb{H}+\epsilon_i,
-	\end{equation*}
-	which, given the uniqueness of $\boldsymbol{\eta}$, leads to
-	\begin{equation*}
-		\widehat{\boldsymbol{\eta}} = \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l.
+The hybrid regression coefficient $\beta$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS directions and scores. First, note that we can show $
+\widehat{\rho}_i^{[l]}
+=
+\langle  W_i^{[l]}, \widehat{\xi}^{[l]} \rangle_\mathbb{H}
+=
+\langle  W_i, \widehat{ \iota}^{[l]} \rangle_\mathbb{H}
+$, where 
+$\widehat{ \iota}^{[l]} = \widehat{\xi}^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{ \delta}^{[u]}, \widehat{\xi}^{[l]} \rangle_{\mathbb{H}} \widehat{ \iota}^{[u]}$ for $l \ge 2$, with $
+\widehat{\iota}^{[1]} = \widehat{\xi}^{[1]}
+$. Next,  \eqref{algorithm_step:residualization_predictor} leads to the following model:
+\begin{equation*}
+	Y_i = \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \widehat{\rho}_i^{[l]} + \epsilon_i.
+\end{equation*}
+This model lets us to express $Y_i$ as:
+	\begin{equation*}
+		Y_i = \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \langle W_i^{[l]}, \widehat{\xi}^{[l]} \rangle_\mathbb{H} +\epsilon_i 
+		= 
+		\bigl \langle W_i, \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}
+		\bigr \rangle_\mathbb{H}+\epsilon_i,
+	\end{equation*}
+	which, given the uniqueness of $ \beta $, leads to
+	\begin{equation*}
+		\widehat{ \beta} = \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}.
 	\end{equation*}
@@
 		\EndFor
-		\textbf{Regression coefficient recovery (Section \ref{section:sub:regression_coeff}):}
+		\textbf{Regression coefficient estimation (Section \ref{section:sub:regression_coeff}):}
 		\State
-		$\widehat{ \zeta }^{[1]} \leftarrow \widehat{ \xi }^{[1]}$
+		$\widehat{ \iota }^{[1]} \leftarrow \widehat{ \xi }^{[1]}$
 		\For{$l =  2, \ldots, L$}
-		\State $\widehat{ \zeta }^{[l]} \leftarrow \widehat{  \xi }^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{ \delta }^{[u]}, \widehat{ \xi }^{[l]} \rangle  \widehat{ \zeta }^{[u]}$  
+		\State $\widehat{ \iota }^{[l]} \leftarrow \widehat{  \xi }^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{ \delta }^{[u]}, \widehat{ \xi }^{[l]} \rangle  \widehat{ \iota }^{[u]}$  
 		\EndFor
-		$	\widehat{ \beta } \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \zeta}^{[l]}$ \Comment{regression coefficient estimate}
+		$	\widehat{ \beta } \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \iota}^{[l]}$ \Comment{regression coefficient estimate}
 		\State \textbf{Output:} the  regression coefficient estimate $	\widehat{ \beta }$
@@
 \end{algorithm}
-		Consider the optimization problem described in Proposition~\ref{proposition:eigen_regul}. Define the following quantities, which depend on the observed data but are not decision variables:
-
-	Then the unique (up to sign) solution to the regularized maximization problem is given in closed form by
-
-	\section{Properties of the Proposed PLS Framework}
+
+	\section{Properties of the hybrid PLS}
 	\label{section:main:properties_of_our_method}
-	In this section, we derive several geometric properties of the PLS components and and scores obtained from the proposed algorithm.
-
-	\subsection{ Tucker's Criterion  }\label{section:main:tucker}\jongmin{Previously, was in theoretical property section, now procedes the method section, to motivate the estimation procedure}
-
-	% The pointwise algorithm is highly inefficient and may not be even feasible for multiple dense and/or irregular functional data.
-Moreover, the pointwise least squares estimator can show substantial variability across the domain, which becomes problematic for the entire algorithm as its instability passes on to subsequent residualized outcomes and PLS components.
-Therefore, in this section, we introduce a novel framework for fitting a regression with a hybrid response and scalar predictor.
-The framework is readily applicable to dense and irregular functional data, and supports regularization techniques to prevent overfitting and reduce variance.
-
+This section provides the mathematical properties that support the algorithm suggested in Section \ref{section:main:our_algorithm}.
+Section \ref{section:sub:tucker} shows that the core optimization problem for the Partial Least Squares (PLS) direction estimation step, presented in Proposition \ref{proposition:eigen_noregul}, is well-defined under mild conditions.
+Section \ref{section:sub:geom} demonstrates that our algorithm preserves the core properties of PLS, namely the orthonormality of the derived directions and the orthogonality of the scores.
+
+	\subsection{ Tucker's Criterion  }\label{section:sub:tucker} 
 	The fundamental property of classical scalar PLS is that the PLS component direction  corresponds to the first eigenvector of the squared covariance matrix, satisfying  the Tucker's Criterion \citep{Tucker1938}.
@@
 	The following theorem introduces the population-level PLS and Tucker's Criterion, adapted to our scalar-on-hybrid regression model setting, based on the aforementioned operators defined in the hybrid space.
-	\begin{theorem}[Population PLS and Tucker's criterion]\label{theorem:population_PLS} Under the conditions of Lemma \ref{lemma:cross_cov_functional}, the constrained maximum
-		\begin{equation*} 
-			\max \limits_{\substack{\xi \in \mathbb{H} \\ \Vert \xi \Vert_\mathbb{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathbb{H}, Y \right)
+	\begin{theorem}[Tucker's criterion]\label{theorem:population_PLS} Under the conditions of Lemma \ref{lemma:cross_cov_functional}, the constrained maximum
+		\begin{equation*} 
+			\max \limits_{\substack{\xi \in \mathbb{H} \\ \Vert \xi \Vert_\mathbb{H}=1}} \operatorname{Cov}^2 \left(\langle W_1 , \, \xi \rangle_\mathbb{H}, Y_1 \right)
 		\end{equation*} 
@@
 	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]}  W^{[l]})$.
-	A fundamental property of partial least squares   is that its derived bases are orthonormal.
+
+	\subsection{Geometric properties}\label{section:sub:geom}
+	A fundamental property of partial least squares   is that between iterations, its derived directions are orthonormal and PLS scores are orthogonal.
 Our regularized estimates preserve this property, with respect to a modified inner product that incorporates the roughness penalty, defines as follows:
 	\begin{definition}[Roughness-sensitive inner product]\label{def:hybrid_inner_product_roughness}
-		Given two hybrid predictors $W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$ and $W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$, both elements of $\mathbb{H}$ as defined in Definition \ref{def:hybid_predictor}, and a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, the roughness-sensitive inner product between $W_1$ and $W_2$ is defined as:
+		Given two hybrid predictors $W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$ and $W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$, both elements of $\mathbb{H}$ as defined in Definition \ref{def:hybrid_predictor}, and a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, the roughness-sensitive inner product between $W_1$ and $W_2$ is defined as:
 		\begin{equation}		\label{eq: hybrid inner product_roughness}
@@
 	\begin{proposition}[Orthonormality of estimated PLS component directions]\label{proposition: modified orthnormality of PLS components}
-		The PLS component directions $\widehat{\xi}_1, \widehat{\xi}_2, \ldots, \widehat{\xi}_L$, estimated via Proposition \ref{proposition:eigen_regul} with a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, are mutually orthonormal with respect to the inner product $\langle \cdot, \cdot \rangle_{\mathbb{H}, \Lambda}$.
+		The PLS component directions $
+\widehat{\xi}^{[1]}, \widehat{\xi}^{[2]}, \ldots, \widehat{\xi}^{[L]}
+$, estimated via Proposition \ref{proposition:eigen_regul} with a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, are mutually orthonormal with respect to the inner product $\langle \cdot, \cdot \rangle_{\mathbb{H}, \Lambda}$.
 That is,
 		\begin{equation*}
-			\langle \widehat{\xi}_{l_1}, \widehat{\xi}_{l_2} \rangle_{\mathbb{H}, \Lambda}
+			\langle \widehat{\xi}^{[l_1]}, \widehat{\xi}^{[l_2]} \rangle_{\mathbb{H}, \Lambda}
 			= \mathbbm{1}(l_1 = l_2), \quad l_1, l_2 = 1, \ldots, L.
@@
 	\end{proof}
-	\section{Proof of Section \ref{section:main:tucker}}
-
-	\subsection{Proof of  Lemma \ref{lemma:cross_cov_functional} }\label{section:proof:lemma:cross_cov_functional}
-	\jongmin{An alternative proof to the compactness of $\mathcal{U}$; rather than directly showing $\mathcal{U}$ is compact, we show $\mathcal{C}_{YW}$ is compact}
-	\begin{proof} 
-	Any bounded linear functional from a Hilbert space to  $\mathbb{R}$  is a compact operator.
-	This is because the image of any bounded set under such a functional is a bounded set in $\mathbb{R}$,
-	and by Bolzano-Weierstrass Theorem, every bounded sequence of real numbers has a convergent subsequence.
-Therefore,  to show that $\mathcal{C}_{YW}$ is a compact operator, it suffices to show that 
- $\mathcal{C}_{YW}$ is a bounded linear functional.
-
-\medskip
-\noindent
-\textit{Linearity.}~	  
- The operator $\mathcal{C}_{YW}: \mathbb{H} \rightarrow \mathbb{R}$ is defined as 
- $\mathcal{C}_{YW} h = \langle \Sigma_{YW}, h \rangle_\mathbb{H}$.
- For any $h_1, h_2 \in \mathbb{H}$ and scalar $c \in \mathbb{R}$, the linearity of the inner product implies: \begin{align*} \mathcal{C}_{YW}(h_1 + h_2) &= \langle \Sigma_{YW}, h_1 + h_2 \rangle_\mathbb{H} = \langle \Sigma_{YW}, h_1 \rangle_\mathbb{H} + \langle \Sigma_{YW}, h_2 \rangle_\mathbb{H} = \mathcal{C}_{YW} h_1 + \mathcal{C}_{YW} h_2,
- 	 \\ 
- 	 \mathcal{C}_{YW}(c h) &= \langle \Sigma_{YW}, c h \rangle_\mathbb{H} = c \langle \Sigma_{YW}, h \rangle_\mathbb{H} = c \, \mathcal{C}_{YW} h. \end{align*}
- Thus, $\mathcal{C}_{YW}$ is a linear functional.
-
-\medskip
-\noindent
-\textit{Boundedness.}~ 
-To show that $\mathcal{C}_{YW}$ is bounded, we need to find a finite constant $M$ such that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathbb{H}$ for all $h \in \mathbb{H}$.
-By the Cauchy-Schwarz inequality, we have: \begin{equation*}
-	|\mathcal{C}_{YW} h| = |\langle \Sigma_{YW}, h \rangle_\mathbb{H}| \leq \|\Sigma_{YW}\|_\mathbb{H} \|h\|_\mathbb{H}. 
-	\end{equation*}
-Now, we must verify that $\|\Sigma_{YW}\|_\mathbb{H}$ is finite. 
-Recall that 
-$$\Sigma_{YW} = (\sigma_{YX,1}(t), \ldots, \sigma_{YX,K}(t), \sigma_{YZ,1}, \ldots, \sigma_{YZ,p}).$$
-  Let $\mu([0,1])$ denote a Lebesgue measure of $[0,1]$, and let $T = \max_{k=1, \ldots, K} \, \mu([0,1])$.
-The norm of $\Sigma_{YW}$ in $\mathbb{H}$ is given by: \begin{equation*} \|\Sigma_{YW}\|_\mathbb{H}^2 = \sum_{k=1}^K \int_0^1 \sigma_{YX,k}(t)^2 \, dt + \sum_{r=1}^p \sigma_{YZ,r}^2
-	<
-	K T Q_1 + p  Q_2 < \infty,
- \end{equation*} 
- where the last inequality uses the condition \eqref{condition_for_compact}.
- Let $M = \sqrt{K T Q_1 + p  Q_2 }$. Thus, we have shown that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathbb{H}$ for a finite constant $M$.
- This completes the proof of Lemma \ref{lemma:cross_cov_functional}.
-
-   \end{proof}
-	\subsection{Proof of Lemma \ref{lemma:cross_cov_operator}}\label{section:proof:lemma:cross_cov_operator}
- \begin{proof}
-For $h \in \mathbb{H}$ and $d \in \mathbb{R}$, we have:
-\begin{equation*}
-\langle
-	\mathcal{C}_{YW} h, d \rangle 
-	= 
-\mathbb{E}
-	[
-		 \langle W_1, h \rangle_\mathbb{H} Y_1  
-	] 	 \,  d
-%%%%%%%%%%%%%%%%%%
-=
-\mathbb{E} \langle   Y_1 W_1 d , \, h\rangle_{\mathbb{H}} 
-%%%%%%%%%%%%%%%%%%%%%%%%
- = \langle h, \, \mathbb{E}[Y_1 W_1 d   ]\rangle_{\mathbb{H}}
- =
- \langle h, \mathcal{C}_{WY} d \rangle_{\mathbb{H}}
-\end{equation*}
-Thus, we have $\langle \mathcal{C}_{YW} h, d \rangle =  \langle h, \mathcal{C}_{WY} d \rangle_{\mathbb{H}}$, which implies $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
-	This completes the proof of Lemma \ref{lemma:cross_cov_operator}.
- \end{proof}
-
-\subsection{Proof of Lemma \ref{lemma:composite_cross_cov}}\label{section:proof:lemma:composite_cross_cov}
-\begin{proof}We show that $\mathcal{U}$ is self-adjoint, positive-semidefinite, and compact, in turn.
-
-	\medskip
-	\noindent
-	\textit{Self-adjoint.}~
-	For any $h_1, h_2 \in \mathbb{H}$, we have
-	\begin{align*}
-		\langle 
-		\mathcal{U} h_1, \, h_2 
-		\rangle_\mathbb{H}  
-		= 
-		\bigl \langle 
-		\langle h_1, \Sigma_{YW} \rangle_\mathbb{H} \Sigma_{YW},
-		\,
-		h_2
-		\bigr \rangle_\mathbb{H}
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		&= \langle h_1, \Sigma_{YW} \rangle_\mathbb{H} \langle \Sigma_{YW}, h_2 \rangle_\mathbb{H}
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		\\&= 
-		\bigl \langle 
-		h_1,
-		\,
-		\langle \Sigma_{YW}, h_2 \rangle_\mathbb{H} \Sigma_{YW} 
-		\bigr \rangle_\mathbb{H}
-		\\ 	&= \langle h_1, \mathcal{U} h_2 \rangle_\mathbb{H}.
-	\end{align*}
-
-	\medskip
-	\noindent
-	\textit{Positive-semidefinite.}~
-	For every $h \in \mathbb{H}$, we have
-	\begin{equation*}
-		\langle 
-		\mathcal{U} h,
-		\,
-		h
-		\rangle_\mathbb{H}
-		=
-		\bigl \langle 
-		\langle 
-		\Sigma_{YW},\, h \rangle_{\mathbb{H}}  \Sigma_{YW}, \, h
-		\bigr \rangle_\mathbb{H}
-		= \langle \Sigma_{YW}, \, h \rangle_\mathbb{H}^2 \ge 0.
-	\end{equation*}
-
-	\medskip
-	\noindent
-	\textit{Compact.}~
-	By Lemma \ref{lemma:cross_cov_functional}, $\mathcal{C}_{YW}$ is a compact operator.
-	By  Theorem 4.1.3 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
-	the composition of two operators is compact if either operator is compact. Therefore
-	$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}$ is a compact operator.
-	This completes the proof of Lemma \ref{lemma:composite_cross_cov}.
-\end{proof}
-
-\subsection{Proof of Theorem \ref{theorem:population_PLS}}\label{section:proof:theorem:population_PLS}
-\begin{proof}
-	by Theorem 4.3.1 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
-	since $\mathcal{C}_{YW}$ is compact by Lemma \ref{lemma:cross_cov_functional}, it 
-	has the singular value decomposition of $\mathcal{C}_{YW}$, given by:
-\begin{equation*}
-	\mathcal{C}_{YW} = \sum \limits_{j=1}^\infty \iota_j (f_{1j} \otimes f_{2j}).
-\end{equation*}
-Let $\Vert \cdot \Vert_{\mathrm{op}}$ denote an operator norm. By  4.3.4 in \citet{hsingTheoreticalFoundationsFunctional2015}, we have
-\begin{equation*}
-	\Vert \mathcal{C}_{YW} \Vert_{\mathrm{op}} = \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | \mathcal{C}_{YW} h |^2 
-	= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | E(\langle W, h \rangle_\mathbb{H} Y)|^2 
-	= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} \textnormal{Cov}^2(\langle W, h \rangle_\mathbb{H}, Y) 
-	= \kappa_1^2,
-\end{equation*}
-with maximum attained at $h=f_{11}$, which is an eigenfunction of  $\mathcal{C}_{YW}^* \, \circ \, \mathcal{C}_{YW} = \mathcal{C}_{WY} \, \circ \, \mathcal{C}_{YW} = \mathcal{U}$ corresponding to the largest eigenvalue $\kappa_1^2.$
-This completes the proof of Theorem \ref{theorem:population_PLS}.
-\end{proof}
-
-	\section{Proof of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:eigen_regul} }\label{section:proof:proposition:linear_regul_system_unregularized}
+
+\subsection{Proof of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:eigen_regul} }\label{section:proof:proposition:linear_regul_system_unregularized}
 \begin{proof}
@@
 
-		\section{Proof of Proposition \ref{proposition:eigen_regul} }\label{section:proof:proposition:eigen_regul}
+	\subsection{Proof of Proposition \ref{proposition:eigen_regul} }\label{section:proof:proposition:eigen_regul}
 	The penalization term 
@@
 
-	\section{Proof of Proposition  \ref{proposition:linear_regul}}\label{section:proof:proposition:linear_regul}
+\subsection{Proof of Proposition  \ref{proposition:linear_regul}}\label{section:proof:proposition:linear_regul}
 \begin{proof}
@@
 
-	\section{Proof of Lemma \ref{proposition:closed_form_orthgonalization} }\label{section:proof:proposition:closed_form_orthgonalization}
+\subsection{Proof of Lemma \ref{proposition:closed_form_orthgonalization} }\label{section:proof:proposition:closed_form_orthgonalization}
 For notational simplicity, we omit the iteration superscript $[l]$.
@@
 The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
-	$\hat{\delta}^{[l]}   \in \tilde{\mathbb{H}}$, has basis coefficients
+$\hat{\delta}^{[l]}   \in \widetilde{\mathbb{H}}$, has basis coefficients
 \begin{equation*}
@@
 This completes the proof of Lemma \ref{proposition:closed_form_orthgonalization}.
+	\section{Proof of Section \ref{section:main:tucker}}
+
+	\subsection{Proof of  Lemma \ref{lemma:cross_cov_functional} }\label{section:proof:lemma:cross_cov_functional}
+	\jongmin{An alternative proof to the compactness of $\mathcal{U}$; rather than directly showing $\mathcal{U}$ is compact, we show $\mathcal{C}_{YW}$ is compact}
+	\begin{proof} 
+	Any bounded linear functional from a Hilbert space to  $\mathbb{R}$  is a compact operator.
+	This is because the image of any bounded set under such a functional is a bounded set in $\mathbb{R}$,
+	and by Bolzano-Weierstrass Theorem, every bounded sequence of real numbers has a convergent subsequence.
+Therefore,  to show that $\mathcal{C}_{YW}$ is a compact operator, it suffices to show that 
+ $\mathcal{C}_{YW}$ is a bounded linear functional.
+
+\medskip
+\noindent
+\textit{Linearity.}~	  
+ The operator $\mathcal{C}_{YW}: \mathbb{H} \rightarrow \mathbb{R}$ is defined as 
+ $\mathcal{C}_{YW} h = \langle \Sigma_{YW}, h \rangle_\mathbb{H}$.
+ For any $h_1, h_2 \in \mathbb{H}$ and scalar $c \in \mathbb{R}$, the linearity of the inner product implies: \begin{align*} \mathcal{C}_{YW}(h_1 + h_2) &= \langle \Sigma_{YW}, h_1 + h_2 \rangle_\mathbb{H} = \langle \Sigma_{YW}, h_1 \rangle_\mathbb{H} + \langle \Sigma_{YW}, h_2 \rangle_\mathbb{H} = \mathcal{C}_{YW} h_1 + \mathcal{C}_{YW} h_2,
+ 	 \\ 
+ 	 \mathcal{C}_{YW}(c h) &= \langle \Sigma_{YW}, c h \rangle_\mathbb{H} = c \langle \Sigma_{YW}, h \rangle_\mathbb{H} = c \, \mathcal{C}_{YW} h. \end{align*}
+ Thus, $\mathcal{C}_{YW}$ is a linear functional.
+
+\medskip
+\noindent
+\textit{Boundedness.}~ 
+To show that $\mathcal{C}_{YW}$ is bounded, we need to find a finite constant $M$ such that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathbb{H}$ for all $h \in \mathbb{H}$.
+By the Cauchy-Schwarz inequality, we have: \begin{equation*}
+	|\mathcal{C}_{YW} h| = |\langle \Sigma_{YW}, h \rangle_\mathbb{H}| \leq \|\Sigma_{YW}\|_\mathbb{H} \|h\|_\mathbb{H}. 
+	\end{equation*}
+Now, we must verify that $\|\Sigma_{YW}\|_\mathbb{H}$ is finite. 
+Recall that 
+$$\Sigma_{YW} = (\sigma_{YX,1}(t), \ldots, \sigma_{YX,K}(t), \sigma_{YZ,1}, \ldots, \sigma_{YZ,p}).$$
+  Let $\mu([0,1])$ denote a Lebesgue measure of $[0,1]$, and let $T = \max_{k=1, \ldots, K} \, \mu([0,1])$.
+The norm of $\Sigma_{YW}$ in $\mathbb{H}$ is given by: \begin{equation*} \|\Sigma_{YW}\|_\mathbb{H}^2 = \sum_{k=1}^K \int_0^1 \sigma_{YX,k}(t)^2 \, dt + \sum_{r=1}^p \sigma_{YZ,r}^2
+	<
+	K T Q_1 + p  Q_2 < \infty,
+ \end{equation*} 
+ where the last inequality uses the condition \eqref{condition_for_compact}.
+ Let $M = \sqrt{K T Q_1 + p  Q_2 }$. Thus, we have shown that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathbb{H}$ for a finite constant $M$.
+ This completes the proof of Lemma \ref{lemma:cross_cov_functional}.
+
+   \end{proof}
+	\subsection{Proof of Lemma \ref{lemma:cross_cov_operator}}\label{section:proof:lemma:cross_cov_operator}
+ \begin{proof}
+For $h \in \mathbb{H}$ and $d \in \mathbb{R}$, we have:
+\begin{equation*}
+\langle
+	\mathcal{C}_{YW} h, d \rangle 
+	= 
+\mathbb{E}
+	[
+		 \langle W_1, h \rangle_\mathbb{H} Y_1  
+	] 	 \,  d
+%%%%%%%%%%%%%%%%%%
+=
+\mathbb{E} \langle   Y_1 W_1 d , \, h\rangle_{\mathbb{H}} 
+%%%%%%%%%%%%%%%%%%%%%%%%
+ = \langle h, \, \mathbb{E}[Y_1 W_1 d   ]\rangle_{\mathbb{H}}
+ =
+ \langle h, \mathcal{C}_{WY} d \rangle_{\mathbb{H}}
+\end{equation*}
+Thus, we have $\langle \mathcal{C}_{YW} h, d \rangle =  \langle h, \mathcal{C}_{WY} d \rangle_{\mathbb{H}}$, which implies $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
+	This completes the proof of Lemma \ref{lemma:cross_cov_operator}.
+ \end{proof}
+
+\subsection{Proof of Lemma \ref{lemma:composite_cross_cov}}\label{section:proof:lemma:composite_cross_cov}
+\begin{proof}We show that $\mathcal{U}$ is self-adjoint, positive-semidefinite, and compact, in turn.
+
+	\medskip
+	\noindent
+	\textit{Self-adjoint.}~
+	For any $h_1, h_2 \in \mathbb{H}$, we have
+	\begin{align*}
+		\langle 
+		\mathcal{U} h_1, \, h_2 
+		\rangle_\mathbb{H}  
+		= 
+		\bigl \langle 
+		\langle h_1, \Sigma_{YW} \rangle_\mathbb{H} \Sigma_{YW},
+		\,
+		h_2
+		\bigr \rangle_\mathbb{H}
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		&= \langle h_1, \Sigma_{YW} \rangle_\mathbb{H} \langle \Sigma_{YW}, h_2 \rangle_\mathbb{H}
+		%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\\&= 
+		\bigl \langle 
+		h_1,
+		\,
+		\langle \Sigma_{YW}, h_2 \rangle_\mathbb{H} \Sigma_{YW} 
+		\bigr \rangle_\mathbb{H}
+		\\ 	&= \langle h_1, \mathcal{U} h_2 \rangle_\mathbb{H}.
+	\end{align*}
+
+	\medskip
+	\noindent
+	\textit{Positive-semidefinite.}~
+	For every $h \in \mathbb{H}$, we have
+	\begin{equation*}
+		\langle 
+		\mathcal{U} h,
+		\,
+		h
+		\rangle_\mathbb{H}
+		=
+		\bigl \langle 
+		\langle 
+		\Sigma_{YW},\, h \rangle_{\mathbb{H}}  \Sigma_{YW}, \, h
+		\bigr \rangle_\mathbb{H}
+		= \langle \Sigma_{YW}, \, h \rangle_\mathbb{H}^2 \ge 0.
+	\end{equation*}
+
+	\medskip
+	\noindent
+	\textit{Compact.}~
+	By Lemma \ref{lemma:cross_cov_functional}, $\mathcal{C}_{YW}$ is a compact operator.
+	By  Theorem 4.1.3 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
+	the composition of two operators is compact if either operator is compact. Therefore
+	$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}$ is a compact operator.
+	This completes the proof of Lemma \ref{lemma:composite_cross_cov}.
+\end{proof}
+
+\subsection{Proof of Theorem \ref{theorem:population_PLS}}\label{section:proof:theorem:population_PLS}
+\begin{proof}
+	by Theorem 4.3.1 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
+	since $\mathcal{C}_{YW}$ is compact by Lemma \ref{lemma:cross_cov_functional}, it 
+	has the singular value decomposition of $\mathcal{C}_{YW}$, given by:
+\begin{equation*}
+	\mathcal{C}_{YW} = \sum \limits_{j=1}^\infty \iota_j (f_{1j} \otimes f_{2j}).
+\end{equation*}
+Let $\Vert \cdot \Vert_{\mathrm{op}}$ denote an operator norm. By  4.3.4 in \citet{hsingTheoreticalFoundationsFunctional2015}, we have
+\begin{equation*}
+	\Vert \mathcal{C}_{YW} \Vert_{\mathrm{op}} = \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | \mathcal{C}_{YW} h |^2 
+	= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | E(\langle W, h \rangle_\mathbb{H} Y)|^2 
+	= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} \textnormal{Cov}^2(\langle W, h \rangle_\mathbb{H}, Y) 
+	= \kappa_1^2,
+\end{equation*}
+with maximum attained at $h=f_{11}$, which is an eigenfunction of  $\mathcal{C}_{YW}^* \, \circ \, \mathcal{C}_{YW} = \mathcal{C}_{WY} \, \circ \, \mathcal{C}_{YW} = \mathcal{U}$ corresponding to the largest eigenvalue $\kappa_1^2.$
+This completes the proof of Theorem \ref{theorem:population_PLS}.
+\end{proof}
 
@@
 
-	\section{Proof of Proposition \ref{proposition: modified orthnormality of PLS components}}
+	\subsection{Proof of Proposition \ref{proposition: modified orthnormality of PLS components}}
 	\label{section:proof:proposition: modified orthnormality of PLS components}
@@
 \widetilde{W}_1^{[l_1-1]}, \ldots, \widetilde{W}_n^{[l_1-1]}
-	\bigr)^\top \in \tilde{\mathbb{H}}^{\otimes n},
+	\bigr)^\top \in \widetilde{\mathbb{H}}^{\otimes n},
 \end{equation}
@@
 	\end{proof}
-	\section{Proof of Proposition \ref{proposition: orthnormality of PLS scores}}\label{section:proof:proposition: orthnormality of PLS scores}
+	\subsection{Proof of Proposition \ref{proposition: orthnormality of PLS scores}}\label{section:proof:proposition: orthnormality of PLS scores}
 	\begin{proof}
@@
 \end{align*}
-Here, the function $h^{[l_1-1]}: \tilde{ \mathbb{H} } \mapsto \tilde{\mathbb{H}}$ maps the zero element of $\tilde{\mathbb{H}}$ to itself, where the zero element represents an ordered pair of $K$ zero functions and a zero matrix.
+Here, the function $h^{[l_1-1]}: \tilde{ \mathbb{H} } \mapsto \widetilde{\mathbb{H}}$ maps the zero element of $\widetilde{\mathbb{H}}$ to itself, where the zero element represents an ordered pair of $K$ zero functions and a zero matrix.
 Using this relationship, we have

### 2025-08-17 manuscript/main.tex
draft done!

@@
 		\begin{abstract}
-			Modern biomedical studies increasingly collect both functional and vector-valued predictors for each subject, introducing challenges due to infinite-dimensionality and cross-modality correlations.
-Existing methods often model these components separately, failing to capture their joint predictive structure.
-			We propose a hybrid partial least squares (PLS) regression framework that integrates functional and scalar predictors within a unified Hilbert space.
-By iteratively maximizing empirical covariance with the response, our method identifies low-dimensional directions that capture both within- and between-modality variation.
-The procedure is computationally efficient, requiring only to solve linear systems at each step.
-We provide theoretical guarantees and demonstrate the effectiveness of our approach through simulations and an application to clinical outcome prediction using renal imaging and scalar covariates from the Emory University renal study.
+		Modern biomedical studies are increasingly collecting both functional and vector-valued predictors for each subject, introducing the new challenge of cross-modality correlations.
+To address this, we propose a hybrid partial least squares (PLS) regression framework that integrates functional and scalar predictors within a unified Hilbert space.
+		We then extend the classical nonlinear iterative PLS (NIPALS) algorithm to this hybrid Hilbert space by iteratively maximizing the empirical cross-covariance with the response.
+As a result, our method identifies low-dimensional directions that capture both within- and between-modality variation, as well as the response-predictor correlation.
+The procedure is computationally efficient, requiring only the solution of linear systems at each step.
+We provide theoretical properties to justify our algorithm and demonstrate its effectiveness through simulations and an application to clinical outcome prediction using renal imaging and scalar covariates from the Emory University renal study.
 		\end{abstract}
@@
 	%Also, there may be high correlation between functional and scalar predictors.
-	This hybrid model poses two-fold challenges.
-	First, estimating the infinite-dimensional slope function $\beta_k(t) $ is an ill-posed problem requiring  dimension reduction or regularization based on structural assumption,
-	such as derivatives and covariance patterns.
-	Second, strong correlations between functional and scalar predictors are common but typically overlooked by separate modeling approaches.
-These issues call for a unified framework that addresses ill-posedness, high-dimensionality, and cross-modality correlation jointly.
-
-	Many approaches have been proposed
-	1. Roughness Penalty
-	2. basis approach (power-series, B-splines, wavelets)
-	- Power Series splines \citep{goldsmithPenalizedFunctionalRegression2011}
-	- B-splines \citep{cardotSplineEstimatorsFunctional2003, caiPredictionFunctionalLinear2006}
-	- Wavelet\citep{zhaoWaveletbasedLASSOFunctional2012}
-
-	%3. FPCA approach
-	One possible approach is to apply principal component analysis, FPCA or MFPCA for the functional predictors and standard PCA for the scalar predictors, followed by classical multivariate regression on the resulting scores.
-	This PCA regression strategy has been well-studied for functional predictors alone \citep{hallMethodologyConvergenceRates2007, reissFunctionalPrincipalComponent2007, febrero-bandeFunctionalPrincipalComponent2017}, but it overlooks potentially strong correlations between functional and scalar components, leading to multicollinearity and suboptimal predictive performance.
-Outside the regression context, \citet{jangPrincipalComponentAnalysis2021} proposed a joint PCA method that accounts for correlation between functional and scalar data.
-However, the resulting components are not informed by the response and may fail to capture directions of maximal correlation with the outcome.
-
-	%4. FPLS Approach
-	Partial least squares (PLS) regression offers a powerful alternative by explicitly seeking low-dimensional projections of the predictors that maximize their covariance with the outcome.
-While PLS has been extensively studied in the context of functional data, both for single and multiple functional predictors \citep{predaPLSRegressionStochastic2005, reissFunctionalPrincipalComponent2007, aguileraUsingBasisExpansions2010, delaigleMethodologyTheoryPartial2012, aguileraPenalizedVersionsFunctional2016, febrero-bandeFunctionalPrincipalComponent2017, beyaztasRobustFunctionalPartial2022, saricamPartialLeastsquaresEstimation2022, mutisFunctiononfunctionLinearQuantile2025}, a unified framework capable of simultaneously handling mixed modalities of functional and scalar covariates remains underdeveloped.
-
-	In this paper, we propose a hybrid partial least squares (PLS) regression framework that integrates functional and vector predictors in a principled and coherent manner.
-To extract predictive structure from jointly observed and potentially correlated data types, we define a Hilbert space that treats functional and vector components as a single hybrid object, equipped with a suitable inner product.
+This hybrid model poses several challenges. 
+First, estimating the infinite-dimensional slope function $\beta_k(t)$ from a finite number of data
+is an ill-posed problem.% that requires dimension reduction or regularization based on structural assumptions, such as derivatives and covariance patterns.
+Second, we face the high-dimensionality of the predictors with $K+p$ dimensions.
+Third, strong correlations between functional and scalar predictors are common but often overlooked by separate modeling approaches.
+
+To address the ill-posedness stemming from the infinite-dimensionality of the functional components, common remedies include basis expansion,
+using power-series  \citep{goldsmithPenalizedFunctionalRegression2011},
+B-splines \citep{cardotSplineEstimatorsFunctional2003, caiPredictionFunctionalLinear2006}, or 
+wavelets \citep{zhaoWaveletbasedLASSOFunctional2012},
+and structure-aware regularization, such as roughness penalties \jongmin{let's add citations here}.
+For the high-dimensionality challenge, a major solution is regression with derived inputs,
+such as Principal Component Analysis (PCA) regression.
+This involves applying (multivariate) functional PCA (FPCA)  to the functional predictors, possibly with standard PCA to the scalar predictors,
+followed by a classical multivariate regression on the resulting scores.
+This PCA regression strategy is well-studied for functional predictors alone \citep{hallMethodologyConvergenceRates2007, reissFunctionalPrincipalComponent2007, febrero-bandeFunctionalPrincipalComponent2017}.
+However, this approach has a major drawback: the derived inputs are not informed by the response variable.
+Consequently, they are not guaranteed to capture the core regression relationship with a small number of derived inputs.
+Partial Least Squares (PLS) regression offers a powerful alternative by explicitly seeking low-dimensional projections of the predictors that maximize their covariance with the outcome.
+PLS has been extensively studied in the context of functional data, both for single and multiple functional predictors \citep{predaPLSRegressionStochastic2005, reissFunctionalPrincipalComponent2007, aguileraUsingBasisExpansions2010, delaigleMethodologyTheoryPartial2012, aguileraPenalizedVersionsFunctional2016, febrero-bandeFunctionalPrincipalComponent2017, beyaztasRobustFunctionalPartial2022, saricamPartialLeastsquaresEstimation2022, mutisFunctiononfunctionLinearQuantile2025}.
+However, all of these existing PCA or PLS approaches overlook the potentially strong correlations between functional and scalar components.
+This can lead to multicollinearity and suboptimal predictive performance.
+To address the third challenge, \citet{jangPrincipalComponentAnalysis2021}  proposed a joint PCA method that accounts for correlations between functional and scalar data.
+However, the resulting components are still not informed by the response, so they may fail to capture the directions of maximal correlation with the outcome.
+
+To bridge this gap, we unify the remedies proposed for these three issues: basis expansion, partial least squares, and a hybrid approach that accounts for the correlation between functional and scalar parts.
+We propose a hybrid PLS regression framework that integrates functional and vector predictors in a principled and coherent manner.
+To extract predictive structure from these jointly observed and potentially correlated data types, we define a Hilbert space that treats the tuple of functional and vector components as a single hybrid object, equipped with a suitable inner product.
 The hybrid PLS direction is then obtained by iteratively maximizing the empirical covariance with the response, subject to a unit-norm constraint in this Hilbert space.
-
-	The framework is readily applicable to dense and irregular functionaldata, and supports regularization techniques to prevent overfitting and reduce variance.
+Our framework is readily applicable to dense and irregular functional data and supports regularization techniques to prevent overfitting and reduce variance.
+We also provide the mathematical properties that justify our algorithm.
 
@@
 we employ a basis expansion approach to fit the entire hybrid object in one step.
-Therefore, our method is computationally efficient, applicable for dense or irregular functional data, and keeps the residual smooth, as it enforces  $\hat{\delta}^{[l]}$  as an element of $\widetilde{\mathbb{H}}$ as defined in Equation \eqref{def:truncated_hilbert_space}.
+Therefore, our method is computationally efficient, and applicable for dense or irregular functional data.
 	Consequently, $\delta^{[l]}$ is obtained by minimizing a  
-	least squares criterion:
+	least squares criterion: \jongmin{I removed the penalization because it makes proving the orthonormality of the PLS components in Proposition \ref{proposition: modified orthnormality of PLS components} impossible.}
 	\begin{equation}\label{def:argmin_pensse}
@@
 
-	\section{Simulations}
+	\section{Simulation studies}\jongmin{08/16/2025: re-starting. the writing here is not completed.}
 	To evaluate the superiority of our method under complex dependency structures
@@
 
-	\section{Data Application}
+	\section{Data Application} \jongmin{08/16/2025: re-starting. the writing here is not completed.}
 
@@
 	\end{itemize}
-	\section{Technical lemmas}
-
-	\subsection{old notations}
-
-	Then we can approximate the functional predictor observations as
-	\begin{equation*}
-		X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)=\mathbf{c}_i^{(k)T}\mathbf{b}^{(k)}(t_k), \;\; t_k \in [0,1], \;\; k=1, \ldots, K, \;\; i=1, \ldots, n,
-	\end{equation*}
-	This basis approximation can be expressed collectively across $n$ observations as: $\widetilde{\mathbf{X}^{(k)}}(t_k) = \widetilde{\mathbf{C}}^{(k)} \mathbf{b}^{(k)}(t_k)$, where $\widetilde{\mathbf{X}}^{(k)}(t_k)=(X_1^{(k)}(t_k), \ldots, X_n^{(k)}(t_k))^\top \in \mathbb{R}^n$,
-	This notation can be further extended to simultaneously express the basis expansions of $K$ functional predictors as 
-	\begin{equation}
-		\widetilde{X}(\mathbf{t}) = \widetilde{C}B(\mathbf{t}), \quad t \in \mathcal{T},
-		\label{eq: basis approximation of X}
-	\end{equation}
-	where $\widetilde{X}(\mathbf{t}) = [\widetilde{\mathbf{X}}^{(1)}(t_1), \cdots, \widetilde{\mathbf{X}}^{(K)}(t_K)] \in \mathbb{R}^{n \times K}$, $\widetilde{C} = [\widetilde{C}^{(1)}, \cdots, \widetilde{\mathbf{C}}^{(k)}] \in \mathbb{R}^{n \times MK}$, and
-	$B(\mathbf{t}) = \mathrm{blkdiag}[\mathbf{b}^{(1)}(t_1), \cdots, \mathbf{b}^{(K)}(t_K)] \in \mathbb{R}^{MK \times K}$.
-
-	Furthermore, let $
-	\mathbf{Z} = [\mathbf{Z}_1, \cdots, \mathbf{Z}_n]^\top \in \mathbb{R}^{n \times p}
-	$ denote $n \times p$ matrix of the scalar predictors (observed version when $l=1$, or residualized version when $l \ge 2$), and let $\widetilde{W}(\mathbf{t})=[\widetilde{X}(\mathbf{t}), \mathbf{Z}]$ denote $n \times (K+p)$ hybrid predictor matrix that stacks $\widetilde{X}(\mathbf{t})$ and $\mathbf{Z}$ as columns.
-Then we can also write the hybrid predictor, whose functional part is approximated using the basis functions, as a form of linear transformation similar to \eqref{eq: basis approximation of X}:
-	\begin{equation}\label{eq: basis approximation of W}
-		\widetilde{W}(\mathbf{t}) 
-		=  
-		\widetilde{ \mathbf{C} }^\ast B^*(\mathbf{t}), \quad t \in \mathcal{T}.
-	\end{equation}
-	where  $B^*(\mathbf{t}) = \mathrm{blkdiag}(B(\mathbf{t}), \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (K+p)}$ and $\widetilde{ \mathbf{C} }^\ast=[\widetilde{C}, \mathbf{Z}] \in \mathbb{R}^{n \times (MK+p)}$.
-
-	\paragraph{Basis approximation of the PLS component.}
-	We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\xi(\mathbf{t}) = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$.
-	%
-
-	Using this definition, we construct the following block-diagonal matrices:
-	\begin{equation}\label{def:J_and_J_star}
-		\mathbf{J} = \mathrm{blkdiag}(\mathbf{J}^{(1)}, \cdots, \boldsymbol{\Phi}^{(k)}) \in \mathbb{R}^{MK \times MK}~\text{and}~\mathbf{J}^\ast=\mathrm{blkdiag}(\mathbf{J}, \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (MK+p)}.
-	\end{equation}
-
-	\paragraph{Regularization based on second-order derivatives.}
-	Our proposed strategy for computing PLS component, detailed in Section \ref{sec: Regularization of PLS Components}, incorporates regularization based on second-order derivatives.
-To this end, let $\ddot{J}^{(k)}$ denote the $M \times M$ Gram matrix formed by the second derivatives of the basis functions,  defined as
-	\begin{equation}\label{def:dodot_J_k}
-		\ddot{J}^{(k)} = \left[ \int_0^1 \ddot{b}^{(k)}_m(t) \ddot{b}^{(k)}_n(t) \, dt \right]_{m,n=1}^M.
-	\end{equation}
-	and define a block-diagonal matrix 
-	$ \ddot{J}^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)}$ as
-	\begin{equation}\label{def:J_dotdot_ast}
-		\ddot{J}^\ast=\mathrm{blkdiag}(\ddot{J}^{(1)}, \cdots, \ddot{J}^{(K)}, 0_{p \times p}).
-	\end{equation}
-	%
-	The finite-basis approximation allows us to represent the hybrid predictor observations using the coefficient matrix $\widetilde{ \mathbf{C} }^\ast$, enabling all associated computations to be carried out via matrix operations involving $\widetilde{ \mathbf{C} }^\ast$, $J^\ast$, and $\ddot{J}^\ast$.
-
-	\section{Proof of Section \ref{section:main:our_algorithm}}
-	\subsection{Proof of Lemma \ref{lemma:hybrid_hilbert_space}}\label{section:proof:lemma:hybrid_hilbert_space}
-	\begin{proof}
-Both $\mathbb{L}^2[0,1]$ and $\mathbb{R}^p$ are Hilbert spaces, with their inner products, norms, and metrics corresponding to the terms defined in equation \eqref{eq: hybrid inner product}.
-A finite Cartesian product of Hilbert spaces, equipped with an $\ell_2$ norm of the component metrics (which is our metric), is also a Hilbert space.
-Next, both $\mathbb{L}^2[0,1]$ and $\mathbb{R}^p$ are separable.
-For  example,  the set of all polynomials with rational coefficients is a countable and dense subset of  $\mathbb{L}^2[0,1]$, and  the set of all vectors with rational components forms a countable and dense subset of $\mathbb{R}^p$.
-The finite Cartesian product of separable spaces is also separable. This completes the proof of Lemma \ref{lemma:hybrid_hilbert_space}.
-	\end{proof}
-
-\subsection{Proof of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:eigen_regul} }\label{section:proof:proposition:linear_regul_system_unregularized}
+
+\subsection{Proof of Proposition \ref{proposition:eigen_noregul}  }\label{section:proof:proposition:linear_regul_system_unregularized}
 \begin{proof}
@@
 \end{equation}
-The criterion $\operatorname{PENSSE}( \delta)$ can be decomposed as follows:
-\begin{equation}\label{def:pensse}
-	\operatorname{PENSSE}( \delta)
-	:=
-	\sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta,
-	\,
-	\widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta
-	\rangle_{\mathbb{H}}
-	+
-	\tau
-	\sum_{j=1}^K\operatorname{PEN}(\delta_j).
-\end{equation}
+The least square criterion   can be decomposed as follows:
+\begin{align*}
+	\operatorname{SSE}( \delta) &= \sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta, \, \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta \rangle_{\mathbb{H}} \\
+	&= 
+	\underbrace{
+		\sum_{i=1}^n \langle \widetilde{W}_i^{[l]}, \, \widetilde{W}_i^{[l]} \rangle_{\mathbb{H}}}_{A} 
+	\underbrace{
+		-2 \sum_{i=1}^n \hat{\rho}_i^{[l]} \langle \delta, \, \widetilde{W}_i^{[l]} \rangle_{\mathbb{H}} 
+	}_{B_1(\boldsymbol{\delta})}
+	\underbrace{
+		+ 
+		(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})
+		\langle \delta, \, \delta \rangle_{\mathbb{H}}
+	}_{B_2(\boldsymbol{\delta})}
+\end{align*}
+\begin{comment}
 \begin{align*}
@@
 \end{align*}
+\end{comment}
 Here, part $A$ does not contain $\delta$, so it does not contribute to the minimization problem.
 
-Let $\boldsymbol{\delta}:= (\pi_1^\top, \ldots, \pi_K^\top, \boldsymbol{\chi}^\top )^\top$ be the $MK+p$-dimensional concatenated vector of basis coefficients and the scalar part of $\boldsymbol{\delta}$, as presented in \eqref{def:maximizer_euclidean_form}.
-Abusing notation, we treat $\operatorname{PENSSE}$ as a function of $\boldsymbol{\delta}$.
+Let $\boldsymbol{\delta}:= (\pi_1^\top, \ldots, \pi_K^\top, \boldsymbol{\chi}^\top )^\top$ be the $MK+p$-dimensional concatenated vector of basis coefficients and the scalar part of $\boldsymbol{\delta}$.
+%Abusing notation, we treat $\operatorname{PENSSE}$ as a function of $\boldsymbol{\delta}$.
+Abusing notation, we treat $\operatorname{SSE}$ as a function of $\boldsymbol{\delta}$.
 Next, We will now demonstrate that the combined term $
-B_1(\boldsymbol{\delta}) + B_2(\boldsymbol{\delta}) + B_3(\boldsymbol{\delta})
+%B_1(\boldsymbol{\delta}) + B_2(\boldsymbol{\delta}) + B_3(\boldsymbol{\delta})
+B_1(\boldsymbol{\delta}) + B_2(\boldsymbol{\delta})
 $ is a quadratic function of $\boldsymbol{\delta}$, by expanding its component functions:
@@
 	\\
-	B_3(\boldsymbol{\delta})
-	&=
-	\tau \sum_{j=1}^K\operatorname{PEN}(\delta_j)
-	=
-	\tau
-	\boldsymbol{\delta} B^{''} \boldsymbol{\delta},
+%	B_3(\boldsymbol{\delta}) &= \tau \sum_{j=1}^K\operatorname{PEN}(\delta_j) = \tau \boldsymbol{\delta} B^{''} \boldsymbol{\delta},
 \end{align*}
-where the expansion of $B_3(\boldsymbol{\delta})$ leverages the computation in \eqref{pen_as_matrix}.
+%where the expansion of $B_3(\boldsymbol{\delta})$ leverages the computation in \eqref{pen_as_matrix}.
 Now we compute the gradients:
@@
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	\\
-	\nabla_{\boldsymbol{\pi}_j}
-	B_3(\boldsymbol{\delta}) 
-	&= 
-	2 \tau
-	B^{\prime \prime }	\boldsymbol{\pi}_j
-	,~
-	j = 1, \ldots, K,
-	\quad
-	\nabla_{\boldsymbol{\chi}}
-	B_3(\boldsymbol{\delta}) 
-	=
-	0.
+	%\\ \nabla_{\boldsymbol{\pi}_j} B_3(\boldsymbol{\delta})  &=  2 \tau B^{\prime \prime }	\boldsymbol{\pi}_j ,~ j = 1, \ldots, K, \quad \nabla_{\boldsymbol{\chi}} B_3(\boldsymbol{\delta})  =0.
 \end{align*}
+	The Hessian of 
+	$\operatorname{SSE}( \boldsymbol{\delta})$ is then given by 
+	$
+	2 	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})  B.
+	$
+\begin{comment}
 The Hessian of 
@@
 $
-Since we assumed in Section \ref{sec: finite basis approximation} that both $B'$ and $B''$ are positive definite, $\operatorname{PENSSE}( \delta)$ is convex.
+\end{comment}
+%Since we assumed in Section \ref{sec: finite basis approximation} that both $B'$ and $B''$ are positive definite, $\operatorname{PENSSE}( \delta)$ is convex.
 Consequently, the gradient vanishes at its unique minimizer:
+Since   $B$ and is positive definite, $\operatorname{SSE}( \delta)$ is convex. Consequently, the gradient vanishes at its unique minimizer:
+\begin{align*}
+	\nabla_{\boldsymbol{\pi}_j}	\operatorname{SSE}( \hat{\boldsymbol{\delta}} )
+	&	=
+	-2
+	B
+	\Theta_j^\top
+	\hat{\boldsymbol{\rho}}
+	+
+	2	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) 
+	B 	\hat{\boldsymbol{\pi}}_j
+	=
+	0,~
+	j = 1, \ldots, K,
+	\\
+	\nabla_{\boldsymbol{\chi} }	\operatorname{SSE}( \hat{\boldsymbol{\delta}} )
+	&=
+	-2\mathbf{Z}^\top  \hat{\boldsymbol{\rho}}
+	+
+	2 (\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) \hat{\boldsymbol{\chi} }
+	=
+	0,
+\end{align*}
+\begin{comment}
 	\begin{align*}
@@
 	\end{align*}
+\end{comment}
 providing the following closed-form solution:
+\begin{comment}
 \begin{equation*}
@@
 \end{equation*}
+\end{comment}
+\begin{equation*}
+	\hat{\boldsymbol{\pi}}_j\\
+	=
+	\bigl\{
+	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})  B
+	\bigr\}^{-1}
+	B
+	\Theta_j^\top
+	\hat{\boldsymbol{\rho}}
+	=
+	\frac{1}{\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}} \Theta_j^\top
+	\hat{\boldsymbol{\rho}}
+	~
+	j = 1, \ldots, K,
+	%%%%%%%%%%%%%%%%%%%%%%%%
+	\quad
+	\hat{\boldsymbol{\chi} }
+	=
+	\frac{1}{(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})}
+	\mathbf{Z}^\top  \hat{\boldsymbol{\rho}}.
+\end{equation*}
+\begin{comment}
 The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
@@
 \end{equation*}
+\end{comment}
+Expanding with respect to these coefficients, we obtain
+\begin{equation*}
+	\delta^{[l]}
+	= 
+	\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
+	\sum_{i=1}^n 
+	\widehat{\rho}_i^{[l]}
+	\widetilde{W}_i^{[l]}.
+\end{equation*}
+On the other hand since $\mathbf{y}^{[l]}$ and  
+	$\hat{\boldsymbol{\rho}}^{[l]}$ are zero-mean,
+	it is well known that the least square estimate of linear regression coefficient is compuated as $\hat{\nu}^{[l]} =  
+\frac{
+	\mathbf{y}^{[l] \top }  \hat{\boldsymbol{\rho}}^{[l]}
+}{
+	\| \hat{\boldsymbol{\rho}}^{[l]} \|_2^2}$.
 This completes the proof of Lemma \ref{proposition:closed_form_orthgonalization}.
-	\section{Proof of Section \ref{section:main:tucker}}
+	\section{Proof of Section \ref{section:main:properties_of_our_method}}
 

### 2025-08-17 manuscript/main.tex
draft done!!!

@@
 To address this, we propose a hybrid partial least squares (PLS) regression framework that integrates functional and scalar predictors within a unified Hilbert space.
-		We then extend the classical nonlinear iterative PLS (NIPALS) algorithm to this hybrid Hilbert space by iteratively maximizing the empirical cross-covariance with the response.
-As a result, our method identifies low-dimensional directions that capture both within- and between-modality variation, as well as the response-predictor correlation.
+			We then extend the classical nonlinear iterative PLS (NIPALS) algorithm to this hybrid Hilbert space by iteratively maximizing the empirical cross-covariance between the hybrid predictor and the response.
+As a result, our method identifies low-dimensional representations that capture both within- and between-modality variation, as well as the response-predictor correlation.
 The procedure is computationally efficient, requiring only the solution of linear systems at each step.

### 2025-08-19 manuscript/main.tex
hilbert space proof

@@
 
-	\subsection{Iterative steps}
+	\subsection{Iterative steps}\label{section:sub:iterative}
 	The iterative process presented here yields an orthonormal hybrid basis that effectively captures the predictor-response relationships.
 It proceeds through two intermediate steps: the estimation of the PLS component direction (Section \ref{section:sub:compute_PLS_component}) and residualization (Section \ref{section:sub:residualization}).
+	The proofs are deferred to Appendix \ref{section:proof:section:sub:iterative}.
 	The properties of the resulting estimates are introduced in Section \ref{section:main:properties_of_our_method}.
@@
 	\label{section:sub:regression_coeff}
-	The hybrid regression coefficient $\beta$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS directions and scores. First, note that we can show $
+	The hybrid regression coefficient $\beta$ in model \eqref{eq: Hybrid functional model} can be written 
+	as a linear combination of PLS directions:
+\begin{lemma}\label{lemma:recursive}
+Let use define
+$
+\widehat{\iota}^{[1]} := \widehat{\xi}^{[1]}.
+$
+For $l \ge 2$, we recursively   define:
+\begin{equation*}
+	\widehat{ \iota}^{[l]} = \widehat{\xi}^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{ \delta}^{[u]}, \widehat{\xi}^{[l]} \rangle_{\mathbb{H}} \widehat{ \iota}^{[u]}. 
+\end{equation*}
+Then we have:
+\begin{equation*}
 	\widehat{\rho}_i^{[l]}
@@
 	=
-	\langle  W_i, \widehat{ \iota}^{[l]} \rangle_\mathbb{H}
-	$, where 
-	$\widehat{ \iota}^{[l]} = \widehat{\xi}^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{ \delta}^{[u]}, \widehat{\xi}^{[l]} \rangle_{\mathbb{H}} \widehat{ \iota}^{[u]}$ for $l \ge 2$, with $
-	\widehat{\iota}^{[1]} = \widehat{\xi}^{[1]}
-	$. Next,  \eqref{algorithm_step:residualization_predictor} leads to the following model:
+	\langle  W_i, \widehat{ \iota}^{[l]} \rangle_\mathbb{H}.
+\end{equation*}
+	\end{lemma}
+Proof of Lemma \ref{lemma:recursive} is provided in Appendix \ref{section:proof:lemma:recursive}.
+
+Next,  \eqref{algorithm_step:residualization_predictor} leads to the following model:
 	\begin{equation*}
@@
 	\section{Overview of Appendix}
-
-	\section{Notations}
 \begin{itemize}
-		\item aaa
+	\item Appendix \ref{section:proof:lemma:hybrid_hilbert_space} proves that our defined product space is a separable Hilbert space.
+	\item Appendix \ref{section:proof:section:sub:iterative}  provides the proofs for the core problem formulations and computational schemes of the iterative steps for estimating the PLS direction and performing residualization.
 \end{itemize}
-
+\section{Proof of Lemma \ref{lemma:hybrid_hilbert_space}}\label{section:proof:lemma:hybrid_hilbert_space}
+\begin{proof}
+	Both $\mathbb{L}^2[0,1]$ and $\mathbb{R}^p$ are Hilbert spaces, with their inner products, norms, and metrics corresponding to the terms defined in equation \eqref{eq: hybrid inner product}.
+A finite Cartesian product of Hilbert spaces, equipped with an $\ell_2$ norm of the component metrics (which is our metric), is also a Hilbert space.
+	Furthermore, both of 	 $\mathbb{L}^2[0,1]$ and $\mathbb{R}^p$ are separable.
+	For $\mathbb{L}^2[0,1]$, the set of all polynomials with rational coefficients is a countable and dense subset.
+	For $\mathbb{R}^p$,  the set of all vectors with rational components forms a countable and dense subset.
+A finite Cartesian product of separable spaces is also separable.
+Therefore $\mathbb{H} = \bigl( \mathbb{L}^2[0,1] \bigr)^K \times \mathbb{R}^p$ is separable.
+\end{proof}
+	\section{Proof of Section \ref{section:sub:iterative}}\label{section:proof:section:sub:iterative}
+This section provides the proofs for the core problem formulations and computational schemes of the iterative steps for estimating the PLS direction and performing residualization.
+Appendices \ref{section:proof:proposition:linear_regul_system_unregularized} and \ref{section:proof:proposition:eigen_regul} derive the eigenproblem formulations for unregularized and regularized PLS direction estimation, respectively.
+Appendices \ref{section:proof:proposition:linear_regul} and \ref{section:proof:proposition:closed_form_orthgonalization} provide proofs for the simple computation schemes for regularized PLS direction estimation and residualization, respectively.
 	\subsection{Proof of Proposition \ref{proposition:eigen_noregul}  }\label{section:proof:proposition:linear_regul_system_unregularized}
@@
 
+\subsection{Proof of Lemma \ref{lemma:recursive}}\label{section:proof:lemma:recursive}
+
 \end{document}

### 2025-08-19 manuscript/main.tex
start recursive proof

@@
 	\item Appendix \ref{section:proof:section:sub:iterative}  provides the proofs for the core problem formulations and computational schemes of the iterative steps for estimating the PLS direction and performing residualization.
+	\item Appendix \ref{section:proof:section:sub:tucker} provides proof of Theorem \ref{theorem:population_PLS}, 
+	demonstrating that the population-level version of the optimization problem solved at each step is well-defined, and 
+	proofs of the intermediate lemmas that support the main theorem.
 \end{itemize}
@@
 	\section{Proof of Section \ref{section:sub:iterative}}\label{section:proof:section:sub:iterative}
+
+\section{Proof of Lemma \ref{lemma:recursive}}\label{section:proof:lemma:recursive}
+\begin{proof}
+	content...
+\end{proof}
+
 This section provides the proofs for the core problem formulations and computational schemes of the iterative steps for estimating the PLS direction and performing residualization.
@@
 	This completes the proof of Lemma \ref{proposition:closed_form_orthgonalization}.
-	\section{Proof of Section \ref{section:main:properties_of_our_method}}
-
+	\section{Proof of Section \ref{section:sub:tucker}}\label{section:proof:section:sub:tucker}
+	This section provides proof of Theorem \ref{theorem:population_PLS}, 
+demonstrating that the population-level version of the optimization problem solved at each step is well-defined, and 
+ proofs of the intermediate lemmas that support the main theorem.
 	\subsection{Proof of  Lemma \ref{lemma:cross_cov_functional} }\label{section:proof:lemma:cross_cov_functional}
@@
 
-\subsection{Proof of Lemma \ref{lemma:recursive}}\label{section:proof:lemma:recursive}
-
 \end{document}

### 2025-08-19 manuscript/main.tex
recursive proof done

--- 2025-08-19 manuscript/main.tex
@@
 
-			\State Standardize  $\widetilde{W}_1^{[1]}, \ldots, \widetilde{W}_n^{[1]}$ and $Y_1^{[1]}, \ldots, Y_n^{[1]}$, following Section \ref{subsec: Data Preprocessing}
+			\State   $\widetilde{W}_1^{[1]}, \ldots, \widetilde{W}_n^{[1]}, Y_1^{[1]}, \ldots, Y_n^{[1]} \leftarrow$ standardized versions of $W_1, \ldots, W_n, Y_1, \ldots, Y_n$, following Section \ref{subsec: Data Preprocessing}
 			\For{$l = 1, 2, \ldots, L$}
@@
 	\item Appendix \ref{section:proof:section:sub:iterative}  provides the proofs for the core problem formulations and computational schemes of the iterative steps for estimating the PLS direction and performing residualization.
+	\item Appendix \ref{section:proof:section:sub:tucker} provides proof of Theorem \ref{theorem:population_PLS}, 
+	demonstrating that the population-level version of the optimization problem solved at each step is well-defined.
 \end{itemize}
@@
 	\section{Proof of Section \ref{section:sub:iterative}}\label{section:proof:section:sub:iterative}
+
 This section provides the proofs for the core problem formulations and computational schemes of the iterative steps for estimating the PLS direction and performing residualization.
@@
 	This completes the proof of Lemma \ref{proposition:closed_form_orthgonalization}.
-	\section{Proof of Section \ref{section:main:properties_of_our_method}}
-
+
+\section{Proof of Lemma \ref{lemma:recursive}}\label{section:proof:lemma:recursive}
+\begin{proof}We prove the lemma using mathematical induction.
+
+\medskip
+\noindent
+\textit{Base case ($l=1$).}~
+		For $l=1$, the lemma states $\widehat{\rho}_i^{[1]} = \langle W_i, \widehat{\iota}^{[1]} \rangle_{\mathbb{H}}$.
+Since  $\widehat{\iota}^{[1]} := \widehat{\xi}^{[1]}$ and $W^{[1]}_i = W_i$, the base case holds.
+
+\medskip
+\noindent
+\textit{Inductive steps.}~		
+Assume   $\widehat{\rho}_i^{[u]} = \langle W_i, \widehat{\iota}^{[u]} \rangle_{\mathbb{H}}$ for $u =1 , \ldots, l$.
+We want to show that $\widehat{\rho}_i^{[l+1]} = \langle W_i, \widehat{\iota}^{[l+1]} \rangle_{\mathbb{H}}$.
+Recall from  \eqref{def:plsscore} and Lemma \ref{proposition:closed_form_orthgonalization} that we have
+\begin{equation}
+ \widehat{\rho}_i^{[l+1]} = \langle \widetilde{W}_i^{[l+1]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}},
+ \quad
+ \widetilde{W}_i^{[l+1]} = \widetilde{W}_i^{[l]} - \widehat{\rho}_i^{[l]} \widehat{\delta}^{[l]}
+\end{equation}
+Combining these two, we have
+\begin{equation}\label{rholp1}
+\widehat{\rho}_i^{[l+1]} = \langle \widetilde{W}_i^{[l]} - \widehat{\rho}_i^{[l]} \widehat{\delta}^{[l]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} 
+=
+\langle \widetilde{W}_i^{[l]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} - \widehat{\rho}_i^{[l]} \langle \widehat{\delta}^{[l]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}}.
+\end{equation}
+Next,
+ we can express $\widetilde{W}_i^{[l]}$ in terms of the original predictor $W_i$ by recursively applying  Lemma \ref{proposition:closed_form_orthgonalization}:
+		$$ \widetilde{W}_i^{[l]} = \widetilde{W}_i^{[l-1]} - \widehat{\rho}_i^{[l-1]} \widehat{\delta}^{[l-1]} = \ldots = W_i - \sum_{u=1}^{l-1} \widehat{\rho}_i^{[u]} \widehat{\delta}^{[u]} $$
+	Substituting this into our equation \eqref{rholp1}, we have:
+\begin{align*}
+\widehat{\rho}_i^{[l+1]} 
+&= \left\langle W_i - \sum_{u=1}^{l-1} \widehat{\rho}_i^{[u]} \widehat{\delta}^{[u]}, \widehat{\xi}^{[l+1]} \right\rangle_{\mathbb{H}} - \widehat{\rho}_i^{[l]} \langle \widehat{\delta}^{[l]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}}
+\\&=
+ \langle W_i, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} - \sum_{u=1}^{l-1} \widehat{\rho}_i^{[u]} \langle \widehat{\delta}^{[u]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} - \widehat{\rho}_i^{[l]} \langle \widehat{\delta}^{[l]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}}
+ \\&=
+ \langle W_i, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} - \sum_{u=1}^{l} \widehat{\rho}_i^{[u]} \langle \widehat{\delta}^{[u]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}}
+ \\& \overset{(i)}{=}
+    \langle W_i, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} - \sum_{u=1}^{l} \langle \widehat{\delta}^{[u]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} \langle W_i, \widehat{\iota}^{[u]} \rangle_{\mathbb{H}}
+%%%%%%%%%%%%%%%%%%%%%%%%
+\\& = 
+\langle W_i, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}}
+-
+\left\langle W_i,   \sum_{u=1}^{l} \langle \widehat{\delta}^{[u]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} \widehat{\iota}^{[u]} \right\rangle_{\mathbb{H}} 
+%%%%%%%%%%%%%%%%%%%%%%%%
+\\& = 
+\left\langle W_i, \widehat{\xi}^{[l+1]} - \sum_{u=1}^{l} \langle \widehat{\delta}^{[u]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} \widehat{\iota}^{[u]} \right\rangle_{\mathbb{H}} 
+\\&= \widehat{\rho}_i^{[l+1]}.
+\end{align*}
+where step $(i)$ uses the inductive hypothesis $\langle W_i, \widehat{\iota}^{[u]} \rangle_{\mathbb{H}} = \widehat{\rho}_i^{[u]}$ for all $u \leq l$.
+		By the principle of mathematical induction, the lemma holds for all $l \ge 1$. This completes the proof of Lemma \ref{lemma:recursive}.
+\end{proof}
+
+	\section{Proof of Section \ref{section:sub:tucker}}\label{section:proof:section:sub:tucker}
+	This section provides proof of Theorem \ref{theorem:population_PLS}, 
+demonstrating that the population-level version of the optimization problem solved at each step is well-defined, and 
+ proofs of the intermediate lemmas that support the main theorem.
 	\subsection{Proof of  Lemma \ref{lemma:cross_cov_functional} }\label{section:proof:lemma:cross_cov_functional}

### 2025-08-19 manuscript/main.tex
beta smoothness

@@
 \newcommand{\jongmin}[1]{
-	{ \color{teal} \textit{(JM: #1)}}
+	{ \color{teal} \textit{(JM:) #1}}
 }
@@
 	\section{Background on partial least squares and its extension to hybrid predictors}  
-	\jongmin{I replaced the formal presentation of the naive algorithm with an   the scalar version and a brief outline of the pointwise hybrid  extension strategy.
+	\jongmin{comment: I replaced the formal presentation of the naive algorithm with an   the scalar version and a brief outline of the pointwise hybrid  extension strategy.
 The main reason for this revision is that the hybrid inner product is introduced specifically to address the extension challenge, so it is more natural to present it after listing the challenges.
@@
 We therefore formally define the Hilbert space of hybrid random predictors along with its corresponding complete inner product, and leverage them to extend Algorithm \ref{alg:scalar_pls}.
-	\jongmin{I split the definition into three parts, adding completeness, separability, and the sigma-field.}
+	\jongmin{comment: I split the definition into three parts, adding completeness, separability, and the sigma-field.}
 	\begin{definition}[Hybrid space]\label{def:hilbert_space}
@@
 	\textit{Proposed regularized estimation procedure.}~ \label{sec: Regularization of PLS Components}
-	Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions.
+Although Proposition \ref{proposition:eigen_noregul} offers an efficient way to estimate the PLS component direction $\hat{\xi}$, its functional components, $\hat{\xi}_1, \ldots, \hat{\xi}_K$, may not be smooth.
+\jongmin{added: Since  the final regression coefficient $\hat{\beta}$ is constructed as a linear combination of these directions (Section \ref{section:sub:regression_coeff}),
+this can lead to a non-smooth $\hat{\beta}$} which complicates interpretation and can lead to overfitting and unstable predictions. 
 	To address this, we propose a regularized extension that balances predictive performance with smoothness.
@@
 	Consequently, $\delta^{[l]}$ is obtained by minimizing a  
-	least squares criterion: \jongmin{I removed the penalization because it makes proving the orthonormality of the PLS components in Proposition \ref{proposition: modified orthnormality of PLS components} impossible.}
+	least squares criterion: \jongmin{comment: I removed the penalization because it makes proving the orthonormality of the PLS components in Proposition \ref{proposition: modified orthnormality of PLS components} impossible.
+Smoothness of $\beta$ seems to soley rely on the smoothness of $\xi$.
+See Section \ref{section:sub:regression_coeff}.}
 	\begin{equation}\label{def:argmin_pensse}
@@
 	The following proposition demonstrates that this residualization step can be performed simply, analogous to scalar PLS.
-	\begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
+	\begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}\jongmin{Previously stated as "we can show".}
 		Let us denote
@@
 	\begin{equation*}
-		\widehat{ \beta} = \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}.
-	\end{equation*}
-	Here, the number of PLS components $L$ to be estimated can be chosen by cross-validation.
+		\widehat{ \beta} = \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}
+		=\jongmin{added:}
+	 \sum_{l=1}^L \left( \widehat{\nu}^{[l]} - \sum_{k=l+1}^L \widehat{\nu}^{[k]} \langle \widehat{\delta}^{[l]}, \widehat{\xi}^{[k]} \rangle_{\mathbb{H}} \right) \widehat{\xi}^{[l]}.
+	\end{equation*}
+	\jongmin{added: Note that if $L$ is too large, $\widehat{ \beta}$ can be wiggly even if $\widehat{\xi}^{[l]}$'s are smooth.}
+	Thus the number of PLS components $L$ to be estimated can be chosen by cross-validation.
 

### 2025-08-19 manuscript/main.tex
previous literature separated

@@
 	Third, strong correlations between functional and scalar predictors are common but often overlooked by separate modeling approaches.
-
+	This paper unifies the remedies proposed for these three issues
+by proposing a hybrid partial least square (PLS) regression framework that integrates functional and vector predictors in a principled and coherent manner.
+Before we summarize the key contributions of this new framework, we will first discuss previous approaches and their limitations.
+
+	\subsection{Previous works and limitations}
 	To address the ill-posedness stemming from the infinite-dimensionality of the functional components, common remedies include basis expansion,

### 2025-08-19 manuscript/main.tex
shoutout to Preda and Saporta

@@
 	wavelets \citep{zhaoWaveletbasedLASSOFunctional2012},
-	and structure-aware regularization, such as roughness penalties \jongmin{let's add citations here}.
-	For the high-dimensionality challenge, a major solution is regression with derived inputs,
-	such as Principal Component Analysis (PCA) regression.
-	This involves applying (multivariate) functional PCA (FPCA)  to the functional predictors, possibly with standard PCA to the scalar predictors,
+	and structure-aware regularization, such as roughness penalties \jongmin{comment:let's add citations here}.
+
+	For the high-dimensionality, a major solution is using derived inputs.
+	A widespread approach in this line is the principal component analysis (PCA) regression.
+	It is a two-step approach, applying (multivariate) functional PCA  to the functional predictors, possibly with standard PCA to the scalar predictors,
 	followed by a classical multivariate regression on the resulting scores.
-	This PCA regression strategy is well-studied for functional predictors alone \citep{hallMethodologyConvergenceRates2007, reissFunctionalPrincipalComponent2007, febrero-bandeFunctionalPrincipalComponent2017}.
-	However, this approach has a major drawback: the derived inputs are not informed by the response variable.
-Consequently, they are not guaranteed to capture the core regression relationship with a small number of derived inputs.
-	Partial Least Squares (PLS) regression offers a powerful alternative by explicitly seeking low-dimensional projections of the predictors that maximize their covariance with the outcome.
-PLS has been extensively studied in the context of functional data, both for single and multiple functional predictors \citep{predaPLSRegressionStochastic2005, reissFunctionalPrincipalComponent2007, aguileraUsingBasisExpansions2010, delaigleMethodologyTheoryPartial2012, aguileraPenalizedVersionsFunctional2016, febrero-bandeFunctionalPrincipalComponent2017, beyaztasRobustFunctionalPartial2022, saricamPartialLeastsquaresEstimation2022, mutisFunctiononfunctionLinearQuantile2025}.
+	PCA regression is well-studied for functional predictors alone \citep{hallMethodologyConvergenceRates2007, reissFunctionalPrincipalComponent2007, febrero-bandeFunctionalPrincipalComponent2017}.
+	However, since the PCA-derived inputs are not informed by the response variable,   they are not guaranteed to capture the core regression relationship with a small number of derived inputs.
+In terms of predictive power, partial least squares (PLS) regression is a powerful alternative.
+This two-step approach first iteratively constructs a set of orthogonal latent components from the predictors that have the maximal covariance with the response variable.
+This low-dimensional representation is then used to fit a linear regression model.
+PLS for linear regression in the context of functional data was initiated by \citet{predaPLSRegressionStochastic2005} for signle predictor.
+  PLS has been extensively studied , both for single and multiple functional predictors \citep{, reissFunctionalPrincipalComponent2007, aguileraUsingBasisExpansions2010, delaigleMethodologyTheoryPartial2012, aguileraPenalizedVersionsFunctional2016, febrero-bandeFunctionalPrincipalComponent2017, beyaztasRobustFunctionalPartial2022, saricamPartialLeastsquaresEstimation2022, mutisFunctiononfunctionLinearQuantile2025}.
 	However, all of these existing PCA or PLS approaches overlook the potentially strong correlations between functional and scalar components.

### 2025-08-19 manuscript/main.tex
literature review updated

@@
 		\begin{abstract}
-			Modern biomedical studies are increasingly collecting both functional and vector-valued predictors for each subject, introducing the new challenge of cross-modality correlations.
+	Regression of a scalar response on mixed functional- and scalar-valued predictors, such as medical imaging with auxiliary patient information, introduces the new challenge of handling cross-modality correlations.
 To address this, we propose a hybrid partial least squares (PLS) regression framework that integrates functional and scalar predictors within a unified Hilbert space.
@@
 	Third, strong correlations between functional and scalar predictors are common but often overlooked by separate modeling approaches.
-	This paper unifies the remedies proposed for these three issues
-by proposing a hybrid partial least square (PLS) regression framework that integrates functional and vector predictors in a principled and coherent manner.
-Before we summarize the key contributions of this new framework, we will first discuss previous approaches and their limitations.
+This paper addresses these three issues in a unified way by introducing a hybrid partial least squares (PLS) regression framework defined on a novel hybrid Hilbert space.
+Before summarizing the key contributions of this framework, we first review previous approaches and their limitations.
 
@@
 	For the high-dimensionality, a major solution is using derived inputs.
-	A widespread approach in this line is the principal component analysis (PCA) regression.
-	It is a two-step approach, applying (multivariate) functional PCA  to the functional predictors, possibly with standard PCA to the scalar predictors,
-	followed by a classical multivariate regression on the resulting scores.
-	PCA regression is well-studied for functional predictors alone \citep{hallMethodologyConvergenceRates2007, reissFunctionalPrincipalComponent2007, febrero-bandeFunctionalPrincipalComponent2017}.
+A straightforward approach in this direction is principal component analysis (PCA) regression, which applies PCA separately to the functional- (by, for example, \citealt{happ_multivariate_2018}) and scalar predictors, and then performs a classical multivariate regression on the combined scores.
+	PCA regression is well-studied for linear regression with functional predictors alone \citep{hallMethodologyConvergenceRates2007, reissFunctionalPrincipalComponent2007, febrero-bandeFunctionalPrincipalComponent2017}.
 	However, since the PCA-derived inputs are not informed by the response variable,   they are not guaranteed to capture the core regression relationship with a small number of derived inputs.
 In terms of predictive power, partial least squares (PLS) regression is a powerful alternative.
-This two-step approach first iteratively constructs a set of orthogonal latent components from the predictors that have the maximal covariance with the response variable.
-This low-dimensional representation is then used to fit a linear regression model.
-PLS for linear regression in the context of functional data was initiated by \citet{predaPLSRegressionStochastic2005} for signle predictor.
-  PLS has been extensively studied , both for single and multiple functional predictors \citep{, reissFunctionalPrincipalComponent2007, aguileraUsingBasisExpansions2010, delaigleMethodologyTheoryPartial2012, aguileraPenalizedVersionsFunctional2016, febrero-bandeFunctionalPrincipalComponent2017, beyaztasRobustFunctionalPartial2022, saricamPartialLeastsquaresEstimation2022, mutisFunctiononfunctionLinearQuantile2025}.
-	However, all of these existing PCA or PLS approaches overlook the potentially strong correlations between functional and scalar components.
-This can lead to multicollinearity and suboptimal predictive performance.
-	To address the third challenge, \citet{jangPrincipalComponentAnalysis2021}  proposed a joint PCA method that accounts for correlations between functional and scalar data.
-However, the resulting components are still not informed by the response, so they may fail to capture the directions of maximal correlation with the outcome.
-
-	To bridge this gap, we unify the remedies proposed for these three issues: basis expansion, partial least squares, and a hybrid approach that accounts for the correlation between functional and scalar parts.
+It iteratively constructs a set of orthogonal latent components from the predictors that have the maximal covariance with the response variable, and use the resulting scores for regression.
+%
+PLS for linear regression in the context of functional data was introduced by \citet{predaPLSRegressionStochastic2005} for the case of a single predictor, studied from a stochastic process perspective.
+Motivated by regression on chemometric spectra, \citet{reissFunctionalPrincipalComponent2007}, \citet{aguileraUsingBasisExpansions2010}, and \citet{aguileraPenalizedVersionsFunctional2016} extended the framework by incorporating basis approximations and roughness penalties to promote smoothness.
+\citet{delaigleMethodologyTheoryPartial2012} provided the first thorough theoretical analysis, while \citet{saricamPartialLeastsquaresEstimation2022} proposed a computationally efficient procedure based on Golub–Kahan bidiagonalization.
+For a comprehensive review, see \citet{febrero-bandeFunctionalPrincipalComponent2017}.
+More recently, \citet{beyaztasRobustFunctionalPartial2022} extended the framework to accommodate multiple functional predictors.
+
+However,  these existing approaches overlook the potentially strong correlations between functional and scalar components, which can lead to multicollinearity and suboptimal predictive performance.
+Multimodal correlations have mostly been addressed within an unsupervised learning framework.
+For instance, \citet{kolar_graph_2014} studied the estimation of joint undirected graphical models for  functional and vector data, while \citet{gengJointNonparametricPrecision2020} considered joint precision matrix estimation for brain measurements and confounding scalar covariate.
+\citet{jangPrincipalComponentAnalysis2021} proposed a joint PCA method that accounts for correlations between functional and scalar data.
+However, the resulting components are still not informed by the response and may fail to capture  correlation with the outcome.
+
+	\subsection{Our contributions}
+To address the gaps mentioned above, we unify the remedies proposed for these three issues: basis expansion, partial least squares, and accounting for correlations between the functional and scalar components.
 	We propose a hybrid PLS regression framework that integrates functional and vector predictors in a principled and coherent manner.
@@
 	Second, our sample size is small compared to the dimension and number of functional and scalar predictors.
-	Third,  existing partial least squares (PLS) methods can only accommodate (i) univariate or multivariate functional predictors without any scalar predictors \citep{predaPLSRegressionStochastic2005, delaigleMethodologyTheoryPartial2012, Febrero2017, Beyaztas2020}; or (ii) a univariate functional predictor with other scalar predictors \citep{Wang2018}.
+	Third,  existing partial least squares (PLS) methods can only accommodate (i) univariate or multivariate functional predictors without any scalar predictors \citep{predaPLSRegressionStochastic2005, delaigleMethodologyTheoryPartial2012, febrero-bandeFunctionalPrincipalComponent2017, Beyaztas2020}; or (ii) a univariate functional predictor with other scalar predictors \citep{Wang2018}.
 	The next section proposes a new extension framework that addresses these issues.
@@
 	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]}  W^{[l]})$.
+
+  \begin{theorem}[$L^2$ Convergence of Hybrid PLS] \label{thm:hybrid_pls_convergence} Let $Y_i$ be a scalar response and $W_i$ be a hybrid predictor in the hybrid Hilbert space $\mathbb{H} = (\mathbb{L}^2[0,1])^K \times \mathbb{R}^p$.
+Let $\hat{Y}_i = \langle \beta, W_i \rangle_{\mathbb{H}}$ denote the ordinary linear regression solution, where $\beta \in \mathbb{H}$ is the true regression coefficient.
+Let $\hat{Y}_{i,L} = \sum_{l=1}^L \hat{c}^{[l]} \rho_i^{[l]}$ be the Hybrid PLS approximation with $L$ components, where $\rho_i^{[l]} = \langle W_i, \xi^{[l]} \rangle_{\mathbb{H}}$ is the $l$-th PLS score and $\xi^{[l]} \in \mathbb{H}$ is the $l$-th PLS direction.
+Then, the Hybrid PLS approximation converges to the ordinary linear regression solution in the mean-squared ($L^2$) sense: $$ \lim_{L \to \infty} E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = 0 $$ \end{theorem} \begin{proof} The proof proceeds in three main steps: first, establishing that the PLS directions form a complete orthonormal system (CONS) for the relevant predictor subspace; second, expressing the ordinary linear regression solution as an infinite series in this PLS basis; and third, showing that the mean-squared error of the PLS approximation vanishes as the number of components increases.
+\subsection*{1.
+The PLS Directions Form a Complete Orthonormal System (CONS)} The Hybrid PLS algorithm iteratively constructs a set of directions $\{\xi^{[l]}\}_{l=1}^\infty$ from the predictors.
+The $l$-th PLS direction, $\xi^{[l]}$, is obtained as the principal eigenfunction of the operator $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$, where the superscript $[l]$ denotes that the operator is constructed from the residualized response $Y^{[l]}$ and predictors $W^{[l]}$ from the previous step.
+\paragraph{1.1 Orthonormality through Residualization} The iterative nature of the PLS algorithm guarantees the orthonormality of the directions.
+The \textbf{residualization (or orthogonalization)} step is crucial.
+After the $(l-1)$-th PLS direction $\xi^{[l-1]}$ is determined, the predictors and response are adjusted to remove the linear effect of this component.
+Specifically, for sample $i$: $$W_i^{[l]} = W_i^{[l-1]} - \langle W_i^{[l-1]}, \xi^{[l-1]} \rangle_{\mathbb{H}} \xi^{[l-1]}$$ $$Y_i^{[l]} = Y_i^{[l-1]} - \hat{c}^{[l-1]} \rho_i^{[l-1]}$$ where $W_i^{[1]} = W_i$ and $Y_i^{[1]} = Y_i$.
+This process ensures that the residualized predictors $W_i^{[l]}$ are orthogonal to all previous directions $\xi^{[j]}$ for $j < l$.
+Consequently, the newly found direction $\xi^{[l]}$, being derived from $W_i^{[l]}$, will be orthogonal to $\{\xi^{[1]}, \ldots, \xi^{[l-1]}\}$.
+By convention, PLS directions are normalized to have unit norm ($\Vert \xi^{[l]} \Vert_{\mathbb{H}} = 1$).
+Thus, the set $\{\xi^{[l]}\}_{l=1}^\infty$ is an orthonormal set.
+\paragraph{1.2 Completeness} The PLS algorithm, by repeatedly extracting the direction of maximum covariance from the residual space, exhaustively captures all linear information within the predictors that is correlated with the response.
+This iterative process terminates when the residualized predictors no longer exhibit covariance with the residualized response.
+Therefore, the span of the PLS directions, $\text{span}\{\xi^{[l]}\}_{l=1}^\infty$, precisely constitutes the subspace of $\mathbb{H}$ that contains all the linear information in the predictors relevant to predicting the response.
+This implies that $\{\xi^{[l]}\}_{l=1}^\infty$ forms a CONS for this relevant predictor subspace.
+\subsection*{2.
+The Ordinary Linear Regression Solution as a Series Expansion in the PLS Basis} Since $\{\xi^{[l]}\}_{l=1}^\infty$ is a CONS for the relevant predictor subspace, the true hybrid regression coefficient $\beta \in \mathbb{H}$ can be expressed as an infinite series in this basis: $$ \beta = \sum_{l=1}^{\infty} \langle \beta, \xi^{[l]} \rangle_{\mathbb{H}} \xi^{[l]} $$ Substituting this expansion into the definition of the ordinary linear regression solution $\hat{Y}_i$: $$ \hat{Y}_i = \langle \beta, W_i \rangle_{\mathbb{H}} = \left\langle \sum_{l=1}^{\infty} \langle \beta, \xi^{[l]} \rangle_{\mathbb{H}} \xi^{[l]}, W_i \right\rangle_{\mathbb{H}} $$ By the linearity of the inner product in a Hilbert space: $$ \hat{Y}_i = \sum_{l=1}^{\infty} \langle \beta, \xi^{[l]} \rangle_{\mathbb{H}} \langle \xi^{[l]}, W_i \rangle_{\mathbb{H}} $$ Let $c^{[l]} = \langle \beta, \xi^{[l]} \rangle_{\mathbb{H}}$ be the true coefficient for the $l$-th component and $\rho_i^{[l]} = \langle W_i, \xi^{[l]} \rangle_{\mathbb{H}}$ be the $l$-th PLS score for sample $i$.
+Then, $$ \hat{Y}_i = \sum_{l=1}^{\infty} c^{[l]} \rho_i^{[l]} $$ This shows that the exact regression solution is an infinite series involving the PLS scores.
+The PLS approximation $\hat{Y}_{i,L}$ is a partial sum of this series.
+Furthermore, it can be shown that the estimated coefficients $\hat{c}^{[l]}$ in the PLS approximation $\hat{Y}_{i,L}$ are consistent estimators of the true coefficients $c^{[l]}$.
+\subsection*{3.
+Proof of $L^2$ Convergence} Now, we examine the mean-squared error between the PLS approximation and the ordinary linear regression solution: $$ E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = E\left[ \left\| \sum_{l=1}^{L} c^{[l]} \rho_i^{[l]} - \sum_{l=1}^{\infty} c^{[l]} \rho_i^{[l]} \right\|^2 \right] $$ This can be rewritten as the expectation of the squared norm of the "tail" of the series: $$ E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = E\left[ \left\| - \sum_{l=L+1}^{\infty} c^{[l]} \rho_i^{[l]} \right\|^2 \right] $$ Since the PLS scores $\{\rho_i^{[l]}\}_{l=1}^\infty$ form an orthogonal system in the space of random variables (due to the orthogonality of $\{\xi^{[l]}\}$ and properties of expectation), the expectation of the squared sum simplifies to the sum of the expectations of the squared individual terms: $$ E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = \sum_{l=L+1}^{\infty} (c^{[l]})^2 E[(\rho_i^{[l]})^2] $$ The infinite series $\sum_{l=1}^{\infty} (c^{[l]})^2 E[(\rho_i^{[l]})^2]$ represents the total variance explained by the predictors and is a convergent series (related to the total variance of $\hat{Y}_i$).
+For any convergent series, the sum of its tail (i.e., from $L+1$ to infinity) must approach zero as $L$ tends to infinity.
+$$ \lim_{L \to \infty} \sum_{l=L+1}^{\infty} (c^{[l]})^2 E[(\rho_i^{[l]})^2] = 0 $$ Therefore, $$ \lim_{L \to \infty} E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = 0 $$ This concludes the proof that the Hybrid PLS approximation converges to the ordinary linear regression solution in the mean-squared sense.
+\end{proof}
 

### 2025-08-19 manuscript/main.tex
sentence below tucker criterion revised

@@
 %
-PLS for linear regression in the context of functional data was introduced by \citet{predaPLSRegressionStochastic2005} for the case of a single predictor, studied from a stochastic process perspective.
+PLS for linear regression in the context of functional predictor alone was introduced by \citet{predaPLSRegressionStochastic2005} for the case of a single predictor.
 Motivated by regression on chemometric spectra, \citet{reissFunctionalPrincipalComponent2007}, \citet{aguileraUsingBasisExpansions2010}, and \citet{aguileraPenalizedVersionsFunctional2016} extended the framework by incorporating basis approximations and roughness penalties to promote smoothness.
-\citet{delaigleMethodologyTheoryPartial2012} provided the first thorough theoretical analysis, while \citet{saricamPartialLeastsquaresEstimation2022} proposed a computationally efficient procedure based on Golub–Kahan bidiagonalization.
+\citet{delaigleMethodologyTheoryPartial2012} provided the first thorough theoretical analysis, while \citet{saricamPartialLeastsquaresEstimation2022} proposed a computationally efficient procedure based on Golub-Kahan bidiagonalization.
 For a comprehensive review, see \citet{febrero-bandeFunctionalPrincipalComponent2017}.
@@
 	\subsection{ Tucker's Criterion  }\label{section:sub:tucker} 
+	    \jongmin{comment:maybe we can move this section to precede the algorithm section. then the new structure will introduce population version first and introduce finite-sample estimation procedure.}
 	The fundamental property of classical scalar PLS is that the PLS component direction  corresponds to the first eigenvector of the squared covariance matrix, satisfying  the Tucker's Criterion \citep{Tucker1938}.
@@
 	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.
-	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]}  W^{[l]})$.
+
+Let 
+ $\mathcal{U}^{[l]} := \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$,
+ where
+ $\Sigma_{YW}^{[l]} = E(Y_1^{[l]}  W_1^{[l]})$
+ is formulated   using the $l$-th residualized response and predictors.
+ Assuming that $\mathcal{U}^{[l]}$
+   satisfies the conditions of Lemma \ref{lemma:cross_cov_functional},
+	the $l$-th PLS direction $\xi^{[l]}$ can be obtained as the \textit{first} eigenfunction of  $\mathcal{U}^{[l]}$.
 

### 2025-08-20 manuscript/main.tex
population consistency proof

@@
 \newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}%custom
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
@@
 	This justifies our estimation procedure introduced in Section \ref{section:main:our_algorithm}.
-	We omit $l$ in the notations and first define the cross-covariance term between the response and the functional predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$): 
+For notational simplicity, we omit the index $l$. At the population level, where the random objects are fully observed, it suffices to consider $Y_1$ and $W_1$ rather than their sampled realizations.
+We assume 
+$\mathbb{E}[Y_1]=0 \in \mathbb{R}$ and $\mathbb{E}[W_1] = 0 \in \mathbb{H}$.
+ We first define the cross-covariance between the response and the functional predictors, where the predictors correspond to the observed versions for $l=1$ and to the residualized versions for $l \ge 2$:
 	\begin{equation}\label{def:cross_covariance_yx}
@@
 	\end{theorem}
+	Note that the maximizer is a deterministic element of $\mathbb{H}$.
 	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.
@@
 
-  \begin{theorem}[$L^2$ Convergence of Hybrid PLS] \label{thm:hybrid_pls_convergence} Let $Y_i$ be a scalar response and $W_i$ be a hybrid predictor in the hybrid Hilbert space $\mathbb{H} = (\mathbb{L}^2[0,1])^K \times \mathbb{R}^p$.
-Let $\hat{Y}_i = \langle \beta, W_i \rangle_{\mathbb{H}}$ denote the ordinary linear regression solution, where $\beta \in \mathbb{H}$ is the true regression coefficient.
-Let $\hat{Y}_{i,L} = \sum_{l=1}^L \hat{c}^{[l]} \rho_i^{[l]}$ be the Hybrid PLS approximation with $L$ components, where $\rho_i^{[l]} = \langle W_i, \xi^{[l]} \rangle_{\mathbb{H}}$ is the $l$-th PLS score and $\xi^{[l]} \in \mathbb{H}$ is the $l$-th PLS direction.
-Then, the Hybrid PLS approximation converges to the ordinary linear regression solution in the mean-squared ($L^2$) sense: $$ \lim_{L \to \infty} E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = 0 $$ \end{theorem} \begin{proof} The proof proceeds in three main steps: first, establishing that the PLS directions form a complete orthonormal system (CONS) for the relevant predictor subspace; second, expressing the ordinary linear regression solution as an infinite series in this PLS basis; and third, showing that the mean-squared error of the PLS approximation vanishes as the number of components increases.
-\subsection*{1.
-The PLS Directions Form a Complete Orthonormal System (CONS)} The Hybrid PLS algorithm iteratively constructs a set of directions $\{\xi^{[l]}\}_{l=1}^\infty$ from the predictors.
-The $l$-th PLS direction, $\xi^{[l]}$, is obtained as the principal eigenfunction of the operator $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$, where the superscript $[l]$ denotes that the operator is constructed from the residualized response $Y^{[l]}$ and predictors $W^{[l]}$ from the previous step.
-\paragraph{1.1 Orthonormality through Residualization} The iterative nature of the PLS algorithm guarantees the orthonormality of the directions.
-The \textbf{residualization (or orthogonalization)} step is crucial.
-After the $(l-1)$-th PLS direction $\xi^{[l-1]}$ is determined, the predictors and response are adjusted to remove the linear effect of this component.
-Specifically, for sample $i$: $$W_i^{[l]} = W_i^{[l-1]} - \langle W_i^{[l-1]}, \xi^{[l-1]} \rangle_{\mathbb{H}} \xi^{[l-1]}$$ $$Y_i^{[l]} = Y_i^{[l-1]} - \hat{c}^{[l-1]} \rho_i^{[l-1]}$$ where $W_i^{[1]} = W_i$ and $Y_i^{[1]} = Y_i$.
-This process ensures that the residualized predictors $W_i^{[l]}$ are orthogonal to all previous directions $\xi^{[j]}$ for $j < l$.
-Consequently, the newly found direction $\xi^{[l]}$, being derived from $W_i^{[l]}$, will be orthogonal to $\{\xi^{[1]}, \ldots, \xi^{[l-1]}\}$.
-By convention, PLS directions are normalized to have unit norm ($\Vert \xi^{[l]} \Vert_{\mathbb{H}} = 1$).
-Thus, the set $\{\xi^{[l]}\}_{l=1}^\infty$ is an orthonormal set.
-\paragraph{1.2 Completeness} The PLS algorithm, by repeatedly extracting the direction of maximum covariance from the residual space, exhaustively captures all linear information within the predictors that is correlated with the response.
-This iterative process terminates when the residualized predictors no longer exhibit covariance with the residualized response.
-Therefore, the span of the PLS directions, $\text{span}\{\xi^{[l]}\}_{l=1}^\infty$, precisely constitutes the subspace of $\mathbb{H}$ that contains all the linear information in the predictors relevant to predicting the response.
-This implies that $\{\xi^{[l]}\}_{l=1}^\infty$ forms a CONS for this relevant predictor subspace.
-\subsection*{2.
-The Ordinary Linear Regression Solution as a Series Expansion in the PLS Basis} Since $\{\xi^{[l]}\}_{l=1}^\infty$ is a CONS for the relevant predictor subspace, the true hybrid regression coefficient $\beta \in \mathbb{H}$ can be expressed as an infinite series in this basis: $$ \beta = \sum_{l=1}^{\infty} \langle \beta, \xi^{[l]} \rangle_{\mathbb{H}} \xi^{[l]} $$ Substituting this expansion into the definition of the ordinary linear regression solution $\hat{Y}_i$: $$ \hat{Y}_i = \langle \beta, W_i \rangle_{\mathbb{H}} = \left\langle \sum_{l=1}^{\infty} \langle \beta, \xi^{[l]} \rangle_{\mathbb{H}} \xi^{[l]}, W_i \right\rangle_{\mathbb{H}} $$ By the linearity of the inner product in a Hilbert space: $$ \hat{Y}_i = \sum_{l=1}^{\infty} \langle \beta, \xi^{[l]} \rangle_{\mathbb{H}} \langle \xi^{[l]}, W_i \rangle_{\mathbb{H}} $$ Let $c^{[l]} = \langle \beta, \xi^{[l]} \rangle_{\mathbb{H}}$ be the true coefficient for the $l$-th component and $\rho_i^{[l]} = \langle W_i, \xi^{[l]} \rangle_{\mathbb{H}}$ be the $l$-th PLS score for sample $i$.
-Then, $$ \hat{Y}_i = \sum_{l=1}^{\infty} c^{[l]} \rho_i^{[l]} $$ This shows that the exact regression solution is an infinite series involving the PLS scores.
-The PLS approximation $\hat{Y}_{i,L}$ is a partial sum of this series.
-Furthermore, it can be shown that the estimated coefficients $\hat{c}^{[l]}$ in the PLS approximation $\hat{Y}_{i,L}$ are consistent estimators of the true coefficients $c^{[l]}$.
-\subsection*{3.
-Proof of $L^2$ Convergence} Now, we examine the mean-squared error between the PLS approximation and the ordinary linear regression solution: $$ E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = E\left[ \left\| \sum_{l=1}^{L} c^{[l]} \rho_i^{[l]} - \sum_{l=1}^{\infty} c^{[l]} \rho_i^{[l]} \right\|^2 \right] $$ This can be rewritten as the expectation of the squared norm of the "tail" of the series: $$ E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = E\left[ \left\| - \sum_{l=L+1}^{\infty} c^{[l]} \rho_i^{[l]} \right\|^2 \right] $$ Since the PLS scores $\{\rho_i^{[l]}\}_{l=1}^\infty$ form an orthogonal system in the space of random variables (due to the orthogonality of $\{\xi^{[l]}\}$ and properties of expectation), the expectation of the squared sum simplifies to the sum of the expectations of the squared individual terms: $$ E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = \sum_{l=L+1}^{\infty} (c^{[l]})^2 E[(\rho_i^{[l]})^2] $$ The infinite series $\sum_{l=1}^{\infty} (c^{[l]})^2 E[(\rho_i^{[l]})^2]$ represents the total variance explained by the predictors and is a convergent series (related to the total variance of $\hat{Y}_i$).
-For any convergent series, the sum of its tail (i.e., from $L+1$ to infinity) must approach zero as $L$ tends to infinity.
-$$ \lim_{L \to \infty} \sum_{l=L+1}^{\infty} (c^{[l]})^2 E[(\rho_i^{[l]})^2] = 0 $$ Therefore, $$ \lim_{L \to \infty} E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = 0 $$ This concludes the proof that the Hybrid PLS approximation converges to the ordinary linear regression solution in the mean-squared sense.
-\end{proof}
+\jongmin{comment: I added the following properties, motivated by Proposition 4 of \citet{predaPLSRegressionStochastic2005} and section 2 of \citet{aguileraPenalizedVersionsFunctional2016}. }
+
+\begin{lemma} \label{lem:regression_W_rho} The population-level least square regression coefficient of regressing $W_1^{[l]}$ on its score $\rho_1^{[l]} = \langle W_1^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}}$ is $\mathbf{\xi^{[l]}} \in \mathbb{H}$.
+This coefficient is used in the residualization process as follows: \begin{align*} W_1^{[l]} &= W_1^{[l-1]} - \langle W_1^{[l-1]}, \xi^{[l-1]} \rangle_{\mathbb{H}} \xi^{[l-1]},\end{align*} where  $W_1^{[1]} = W_1$.
+\end{lemma}
+Proof of Lemma \ref{lem:regression_W_rho} is provided in Appendix \ref{section:proof:lem:regression_W_rho}.
+
+ We define an operator $\mathcal{T}$ that maps an element $g \in \mathbb{H}$   (representing a potential regression coefficient) to the predicted response.
+\begin{lemma}\label{lemma:tau_ast}
+	Define the linear operator $\mathcal{T}: \mathbb{H} \to \mathbb{R}$ that maps  $g \in \mathbb{H}$ to 
+	$
+	\mathcal{T}g = \langle W, g \rangle_{\mathbb{H}}
+	$.
+ Let $\mathcal{T}^\ast: \mathbb{R} \to \mathbb{H}$ denote its adjoint operator. Then,
+	\[
+	\Sigma_{YW}^{[1]} = \mathcal{T}^\ast Y.
+	\]
+\end{lemma}
+Proof of Lemma \ref{lemma:tau_ast} is provided in Appendix \ref{section:rpoof:lemma:tau_ast}.
+
+\begin{proposition}\label{proposition:pls_direction_in_range_T_ast}
+	All PLS Directions Reside in $R(\mathcal{T}^\ast  )$
+\end{proposition}
+ Proof of Proposition \ref{proposition:pls_direction_in_range_T_ast} is provided in Appendix \ref{section:proof:proposition:pls_direction_in_range_T_ast}
+
+\begin{proposition}
+	\label{proposition:CONS}
+	The set of PLS directions $\{\xi^{[l]}\}_{l=1}^\infty$ forms a complete orthonormal system (CONS) for $R(\mathcal{T}^*)$.
+\end{proposition}
+Proof of Proposition \ref{proposition:CONS}
+is provided in Appendix \ref{section:proof:proposition:CONS}.
+
+\begin{corollary}
+	\label{cor:orthogonal_scores}
+	Given that $\{\xi^{[l]}\}_{l=1}^\infty$ is a complete orthonormal system (CONS) for $R(\mathcal{T}^*)$, the corresponding PLS scores $\rho^{[l]}$ can be equivalently expressed as $\rho^{[l]} = \langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}} = \langle W, \xi^{[l]} \rangle_{\mathbb{H}}$.
+Furthermore, the set of PLS scores $\{\rho^{[l]}\}_{l=1}^\infty$ forms an orthogonal system, that is, for any $j \neq l$, $\mathbb{E}[\rho^{[j]} \rho^{[l]}] = 0$.
+\end{corollary}
+Let $\beta_{\mathrm{OLS}}$ denote a minimizer of  the mean squared error $ \mathbb{E}[\|Y - \langle \beta, W \rangle_{\mathbb{H}}\|_2^2]$. It
+satisfies the normal equation
+\begin{equation}\label{normal_equation}
+	\mathbb{E}[(Y - \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}})W] = 0 \in \mathbb{H}.
+\end{equation}
+If the operator $\mathcal{T}^\ast \mathcal{T}$ is invertible,  the minimizer is uniquely determined as 
+$\beta_{\mathrm{OLS}} = (\mathcal{T}^\ast \mathcal{T})^{-1} \mathcal{T}^\ast Y$.
+\begin{proposition}\label{proposition:nu_l}
+	At the $l$-th iteration, the 
+	population level least square regression coefficient of the residual response $Y^{[l]}$ on the score $\rho^{[l]}$ is defined as:
+	$$\nu^{[l]} = \langle \beta_{\mathrm{OLS}}, \xi^{[l]} \rangle_{\mathbb{H}}.$$
+\end{proposition}
+Proof of Proposition \ref{proposition:nu_l} is provided in Appendix \ref{section:proof:proposition:nu_l}.
+
+The following theorem states that the fitted values from hybrid PLS converge to those of ordinary linear regression in the mean-squared sense.
+This shows that hybrid PLS, as a dimension-reduction technique, can effectively capture the predictive power of a full linear model when a sufficient number of components is used.
+\begin{theorem}[$L^2$ Convergence of Hybrid PLS at Population Level]\label{thm:hybrid_pls_convergence}
+	 Define $Y_{\mathrm{OLS}} = \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}$ as the population-level ordinary linear regression fitted value.
+Let $Y_{\mathrm{PLS}, L} = \sum_{l=1}^L \nu^{[l]} \rho^{[l]}$ be the Hybrid PLS fitted value with $L$ components.
+Then, the Hybrid PLS fitted value converges to the ordinary linear regression fitted value in the mean-squared sense:
+	\begin{equation*}
+		\lim_{L \to \infty} \mathbb{E}\left[ \| Y_{\mathrm{PLS},L } - Y_{\mathrm{OLS}} \|_2^2 \right] = 0
+	\end{equation*}
+\end{theorem}
+ The proof of Theorem \ref{thm:hybrid_pls_convergence} is provided in Appendix \ref{section:proof:thm:hybrid_pls_convergence}.
 
@@
 			\Vert \mathcal{C}_{YW} \Vert_{\mathrm{op}} = \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | \mathcal{C}_{YW} h |^2 
-			= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | E(\langle W, h \rangle_\mathbb{H} Y)|^2 
+			= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | \mathbb{E}(\langle W, h \rangle_\mathbb{H} Y)|^2 
 			= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} \textnormal{Cov}^2(\langle W, h \rangle_\mathbb{H}, Y) 
@@
 	\end{comment}
+
+\section{Proof of consistency}
+\subsection{
+		Proof of Lemma \ref{lem:regression_W_rho}
+}\label{section:proof:lem:regression_W_rho}
+\begin{proof} We are seeking the population-level regression coefficient, denoted $\gamma \in \mathbb{H}$, for the linear model: $$W_1^{[\ell]} = \gamma \rho_1^{[\ell]} + \text{Error}$$ where $W_1^{[\ell]}$ is the dependent variable (a random element in $\mathbb{H}$), and $\rho_1^{[\ell]} = \langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}}$ is the independent variable (a scalar random variable).
+The optimal regression coefficient $\gamma$ (in the sense of minimizing the mean squared error $E[\|W_1^{[\ell]} - \gamma \rho_1^{[\ell]}\|^2_{\mathbb{H}}]$) is given by the formula:
+	$$\gamma = \frac{E[W_1^{[\ell]} \rho_1^{[\ell]}]}{E[(\rho_1^{[\ell]})^2]}$$ 
+	This formula holds assuming $E[W_1^{[\ell]}] = \mathbf{0}_{\mathbb{H}}$ and $E[\rho_1^{[\ell]}] = 0$, which is true due to the residualization process and the property of zero-mean predictors in the population.
+Let's compute the components of this formula:
+ \begin{enumerate} \item \textbf{Denominator:} The denominator is $E[(\rho_1^{[\ell]})^2] = E[(\langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}})^2]$.
+This is the population variance of the score $\rho_1^{[\ell]}$.
+\item \textbf{Numerator:} The numerator is $E[W_1^{[\ell]} \rho_1^{[\ell]}] = E[W_1^{[\ell]} \langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}}]$.
+This is the expectation of the product of a random element $W_1^{[\ell]}$ and a scalar random variable $\langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}}$.
+A fundamental identity in Hilbert spaces states that for any random element $X \in \mathbb{H}$ and any non-random unit vector $u \in \mathbb{H}$ (like $\xi^{[\ell]}$ which has unit norm), if $E[X] = \mathbf{0}_{\mathbb{H}}$, then: $$E[X\langle X,u\rangle_{\mathbb{H}}]=E[\langle X,u\rangle_{\mathbb{H}}^2]u$$ Applying this identity by setting $X=W_1^{[\ell]}$ and $u=\xi^{[\ell]}$: $$E[W_1^{[\ell]}\langle W_1^{[\ell]},\xi^{[\ell]}\rangle_{\mathbb{H}}]=E[(\langle W_1^{[\ell]},\xi^{[\ell]}\rangle_{\mathbb{H}})^2]\xi^{[\ell]}$$ \end{enumerate} Substituting these into the formula for $\gamma$: $$\gamma = \frac{E[(\langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}})^2] \xi^{[\ell]}}{E[(\langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}})^2]}$$ Assuming that $E[(\langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}})^2] \neq 0$ (i.e., the score has non-zero variance, implying $\xi^{[\ell]}$ captures some variation), we can cancel the terms, resulting in: $$\gamma = \xi^{[\ell]}$$ This result is intuitively consistent with the orthogonal decomposition of $W_1^{[\ell]}$: $$W_1^{[\ell]}=\langle W_1^{[\ell]},\xi^{[\ell]}\rangle_{\mathbb{H}}\xi^{[\ell]}+(W_1^{[\ell]}-\langle W_1^{[\ell]},\xi^{[\ell]}\rangle_{\mathbb{H}}\xi^{[\ell]})$$ The second term, $(W_1^{[\ell]}-\langle W_1^{[\ell]},\xi^{[\ell]}\rangle_{\mathbb{H}}\xi^{[\ell]})$, is the part of $W_1^{[\ell]}$ that is orthogonal to $\xi^{[\ell]}$ (and thus uncorrelated with $\rho_1^{[\ell]}$).
+When $W_1^{[\ell]}$ is regressed on $\rho_1^{[\ell]}$, the regression model isolates the component of $W_1^{[\ell]}$ that is linearly related to $\rho_1^{[\ell]}$, which is precisely $\langle W_1^{[\ell]},\xi^{[\ell]}\rangle_{\mathbb{H}}\xi^{[\ell]}$.
+The coefficient for $\rho_1^{[\ell]}$ in this linear relationship is simply $\xi^{[\ell]}$.
+\end{proof}
+
+\subsection{Proof of Lemma \ref{lemma:tau_ast} }\label{section:rpoof:lemma:tau_ast}
+	\begin{proof}
+	The adjoint operator  is uniquely defined by the property relating the inner products in $L^2(\Omega)$ and $\mathbb{H}$: $$ \langle \mathcal{T}g, Y \rangle_{L^2(\Omega)} = \langle g, \mathcal{T}^\ast Y \rangle_{\mathbb{H}}, \quad \text{for all } g \in \mathbb{H}, Y \in L^2(\Omega) $$ Here, $\langle \cdot, \cdot \rangle_{L^2(\Omega)}$ denotes the inner product in $L^2(\Omega)$, which is the expectation $E[\cdot]$.
+Let's explicitly derive the expression for $\mathcal{T}^\ast Y$: $$ \langle g, \mathcal{T}^\ast Y \rangle_{\mathbb{H}} = E[\langle W, g \rangle_{\mathbb{H}} Y] $$ By the properties of expectation and the linearity of the inner product (assuming appropriate boundedness and measurability for interchange of expectation and inner product): $$ E[\langle W, g \rangle_{\mathbb{H}} Y] = E[\langle g, W \rangle_{\mathbb{H}} Y] = \langle g, E[YW] \rangle_{\mathbb{H}} $$ Comparing the leftmost and rightmost parts of the definition of the adjoint: $$ \mathcal{T}^\ast Y = E[YW] $$
+	\end{proof}
+
+\subsection{Proof of}
+\begin{proof}
+The first PLS direction $\xi^{[1]}$ is the principal eigenfunction of $\mathcal{U}^{[1]} = \Sigma_{YW}^{[1]} \otimes \Sigma_{YW}^{[1]}$.
+Let $\lambda^{[1]}$ be the largest eigenvalue associated with $\xi^{[1]}$.
+By the definition of an eigenfunction: $$ \mathcal{U}^{[1]} \xi^{[1]} = \lambda^{[1]} \xi^{[1]} $$ Substituting the definition of $\mathcal{U}^{[1]}$: $$ (\Sigma_{YW}^{[1]} \otimes \Sigma_{YW}^{[1]}) \xi^{[1]} = \lambda^{[1]} \xi^{[1]} $$ This means: $$ \Sigma_{YW}^{[1]} \langle \Sigma_{YW}^{[1]}, \xi^{[1]} \rangle_{\mathbb{H}} = \lambda^{[1]} \xi^{[1]} $$ If there is any linear correlation between $Y$ and $W$, then $\Sigma_{YW}^{[1]} \neq 0$, which implies $\lambda^{[1]}$ must be non-zero.
+From the equation above, if $\lambda^{[1]} \neq 0$: $$ \xi^{[1]} = \frac{\langle \Sigma_{YW}^{[1]}, \xi^{[1]} \rangle_{\mathbb{H}}}{\lambda^{[1]}} \Sigma_{YW}^{[1]} $$ This equation shows that $\xi^{[1]}$ is a scalar multiple of $\Sigma_{YW}^{[1]}$.
+Since $\Sigma_{YW}^{[1]} \in R(\mathcal{T}^\ast  )$ (as shown in Step 2), and $R(\mathcal{T}^\ast  )$ is a subspace of $\mathbb{H}$ (and thus closed under scalar multiplication), any scalar multiple of $\Sigma_{YW}^{[1]}$ must also be in $R(\mathcal{T}^\ast  )$.
+Therefore, the first PLS direction $\xi^{[1]}$ formally resides in the range of the adjoint operator $R(\mathcal{T}^\ast  )$.
+\end{proof}
+  The first PLS direction $\xi^{[1]}$ is the principal eigenfunction of the operator $\mathcal{U}^{[1]} = \Sigma_{YW}^{[1]} \otimes \Sigma_{YW}^{[1]}$.
+The term $\Sigma_{YW}^{[1]}$ is the population cross-covariance between the (initial, unresidualized) response $Y$ and hybrid predictor $W$: $$ \Sigma_{YW}^{[1]} = E[YW] $$ From our derivation in Step 1, we see that $\Sigma_{YW}^{[1]}$ is precisely equal to $\mathcal{T}^\ast Y$.
+Since $\Sigma_{YW}^{[1]} = \mathcal{T}^\ast Y$, it directly follows that $\Sigma_{YW}^{[1]}$ belongs to the **range of the adjoint operator $R(\mathcal{T}^\ast  )$**.
+By definition, $R(\mathcal{T}^\ast  )$ comprises all elements in $\mathbb{H}$ that can be expressed as $\mathcal{T}^\ast Y$ for some $y \in L^2(\Omega)$.
+
+\subsection{Proof of Proposition \ref{proposition:pls_direction_in_range_T_ast}}\label{section:proof:proposition:pls_direction_in_range_T_ast}
+\begin{proof}
+	The First Eigenfunction $\xi^{[1]}$ Resides in $R(\mathcal{T}^\ast  )$
+  We aim to formally prove that for any $\ell \ge 1$, the $\ell$-th PLS direction $\xi^{[\ell]}$ belongs to the range of the adjoint operator $\mathcal{T}^\ast  $, denoted $R(\mathcal{T}^\ast  )$, at the population level.
+This proof uses mathematical induction.
+\paragraph*{1.
+Recall Definitions and Base Case} \begin{itemize} \item \textbf{Hybrid Hilbert Space ($\mathbb{H}$):} The space where predictors $W$ reside.
+\item \textbf{Response Space ($L^2(\Omega)$):} The space of scalar random variables (responses $Y$) with finite second moments.
+\item \textbf{Operator $\mathcal{T}: \mathbb{H} \rightarrow L^2(\Omega)$:} Defined by $\mathcal{T}g = \langle W, g \rangle_{\mathbb{H}}$.
+This maps a potential regression coefficient $g$ to a predicted response.
+\item \textbf{Adjoint Operator $\mathcal{T}^\ast  : L^2(\Omega) \rightarrow \mathbb{H}$:} Uniquely defined by $\langle \mathcal{T}g, Y \rangle_{L^2(\Omega)} = \langle g, \mathcal{T}^\ast Y \rangle_{\mathbb{H}}$.
+As derived, $\mathcal{T}^\ast Y = E[YW]$.
+The range $R(\mathcal{T}^\ast  )$ is the subspace of $\mathbb{H}$ containing all elements that are linearly correlated with $Y$.
+\item \textbf{$\ell$-th PLS Direction ($\xi^{[\ell]}$):} The principal eigenfunction of $\mathcal{U}^{[\ell]} = \Sigma_{YW}^{[\ell]} \otimes \Sigma_{YW}^{[\ell]}$, where $\Sigma_{YW}^{[\ell]} = E[Y^{[\ell]} W^{[\ell]}]$.
+\end{itemize} \paragraph{Base Case ($\ell=1$):} For the first PLS direction, $\xi^{[1]}$, we consider $\Sigma_{YW}^{[1]} = E[YW]$.
+From the definition of the adjoint operator $\mathcal{T}^\ast  $, we have $\mathcal{T}^\ast Y = E[YW]$.
+Therefore, $\Sigma_{YW}^{[1]} = \mathcal{T}^\ast Y$.
+This explicitly shows that $\Sigma_{YW}^{[1]} \in R(\mathcal{T}^\ast  )$.
+Since $\xi^{[1]}$ is the principal eigenfunction of $\mathcal{U}^{[1]} = \Sigma_{YW}^{[1]} \otimes \Sigma_{YW}^{[1]}$, it satisfies $\mathcal{U}^{[1]} \xi^{[1]} = \lambda^{[1]} \xi^{[1]}$.
+This implies $\Sigma_{YW}^{[1]} \langle \Sigma_{YW}^{[1]}, \xi^{[1]} \rangle_{\mathbb{H}} = \lambda^{[1]} \xi^{[1]}$.
+If $\Sigma_{YW}^{[1]} \neq 0$ (meaning there's linear correlation between $Y$ and $W$), then $\lambda^{[1]} \neq 0$, and $\xi^{[1]}$ must be a scalar multiple of $\Sigma_{YW}^{[1]}$: $$ \xi^{[1]} = \frac{\langle \Sigma_{YW}^{[1]}, \xi^{[1]} \rangle_{\mathbb{H}}}{\lambda^{[1]}} \Sigma_{YW}^{[1]} $$ Since $\Sigma_{YW}^{[1]} \in R(\mathcal{T}^\ast  )$ and $R(\mathcal{T}^\ast  )$ is a subspace (closed under scalar multiplication), it directly follows that $\xi^{[1]} \in R(\mathcal{T}^\ast  )$.
+The base case is proven.
+\paragraph*{2.
+Inductive Step: Assume $\xi^{[1]}, \ldots, \xi^{[\ell-1]} \in R(\mathcal{T}^\ast  )$} Assume that the first $\ell-1$ PLS directions, $\xi^{[1]}, \ldots, \xi^{[\ell-1]}$, all reside in $R(\mathcal{T}^\ast  )$.
+We need to prove that $\xi^{[\ell]}$ also resides in $R(\mathcal{T}^\ast  )$.
+The $\ell$-th PLS direction $\xi^{[\ell]}$ is a scalar multiple of $\Sigma_{YW}^{[\ell]} = E[Y^{[\ell]} W^{[\ell]}]$.
+Thus, to prove $\xi^{[\ell]} \in R(\mathcal{T}^\ast  )$, it suffices to prove that $\Sigma_{YW}^{[\ell]} \in R(\mathcal{T}^\ast  )$.
+Recall the residualization process at the population level: $$W^{[\ell]} = W^{[\ell-1]} - \langle W^{[\ell-1]}, \xi^{[\ell-1]} \rangle_{\mathbb{H}} \xi^{[\ell-1]}$$ $$Y^{[\ell]} = Y^{[\ell-1]} - \nu^{[\ell-1]} \rho^{[\ell-1]}$$ where $\rho^{[\ell-1]} = \langle W^{[\ell-1]}, \xi^{[\ell-1]} \rangle_{\mathbb{H}}$.
+By iterating this process, we can express $W^{[\ell]}$ and $Y^{[\ell]}$ in terms of the original $W$, $Y$, and the previously extracted PLS components: $$W^{[\ell]} = W - \sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \xi^{[j]}$$ $$Y^{[\ell]} = Y - \sum_{j=1}^{\ell-1} \nu^{[j]} \rho^{[j]}$$ From the inductive hypothesis and the base case, all $\xi^{[j]} \in R(\mathcal{T}^\ast  )$ for $j=1, \ldots, \ell-1$.
+Since $R(\mathcal{T}^\ast  )$ is a subspace, any linear combination of these $\xi^{[j]}$ also belongs to $R(\mathcal{T}^\ast  )$.
+Thus, the sum $\sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \xi^{[j]}$ is an element of $R(\mathcal{T}^\ast  )$.
+Now, we need to show that $\Sigma_{YW}^{[\ell]} = E[Y^{[\ell]} W^{[\ell]}]$ resides in $R(\mathcal{T}^\ast  )$.
+To do this, we demonstrate that for any $v \in R(\mathcal{T}^\ast  )^\perp$ (the orthogonal complement of $R(\mathcal{T}^\ast  )$ in $\mathbb{H}$), $\langle \Sigma_{YW}^{[\ell]}, v \rangle_{\mathbb{H}} = 0$.
+By definition, $R(\mathcal{T}^\ast  )^\perp = \{v \in \mathbb{H} \mid E[\langle W, v \rangle_{\mathbb{H}} Y] = 0\}$.
+Consider $E[\langle W^{[\ell]}, v \rangle_{\mathbb{H}} Y^{[\ell]}]$ for any $v \in R(\mathcal{T}^\ast  )^\perp$: $$E[\langle W^{[\ell]}, v \rangle_{\mathbb{H}} Y^{[\ell]}] = E\left[ \left\langle W - \sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \xi^{[j]}, v \right\rangle_{\mathbb{H}} \left( Y - \sum_{k=1}^{\ell-1} \nu^{[k]} \rho^{[k]} \right) \right]$$ Due to the orthogonality of $v$ to all $\xi^{[j]}$ (since $v \in R(\mathcal{T}^\ast  )^\perp$ and $\xi^{[j]} \in R(\mathcal{T}^\ast  )$): $$ \left\langle W - \sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \xi^{[j]}, v \right\rangle_{\mathbb{H}} = \langle W, v \rangle_{\mathbb{H}} - \sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \langle \xi^{[j]}, v \rangle_{\mathbb{H}} = \langle W, v \rangle_{\mathbb{H}} - 0 = \langle W, v \rangle_{\mathbb{H}} $$ Thus, the expression simplifies to: $$ E[\langle W^{[\ell]}, v \rangle_{\mathbb{H}} Y^{[\ell]}] = E\left[ \langle W, v \rangle_{\mathbb{H}} \left( Y - \sum_{k=1}^{\ell-1} \nu^{[k]} \rho^{[k]} \right) \right] $$ $$ = E[\langle W, v \rangle_{\mathbb{H}} Y] - \sum_{k=1}^{\ell-1} \nu^{[k]} E[\langle W, v \rangle_{\mathbb{H}} \rho^{[k]}] $$ The first term $E[\langle W, v \rangle_{\mathbb{H}} Y] = 0$ because $v \in R(\mathcal{T}^\ast  )^\perp$.
+For the second term, $E[\langle W, v \rangle_{\mathbb{H}} \rho^{[k]}] = E[\langle W, v \rangle_{\mathbb{H}} \langle W, \xi^{[k]} \rangle_{\mathbb{H}}]$.
+Since $v \in R(\mathcal{T}^\ast  )^\perp$ and $\xi^{[k]} \in R(\mathcal{T}^\ast  )$, and $E[\langle U, X \rangle \langle V, X \rangle]$ represents the covariance between inner products, and components in $R(\mathcal{T}^\ast  )$ and $R(\mathcal{T}^\ast  )^\perp$ are uncorrelated: $E[\langle W, v \rangle_{\mathbb{H}} \langle W, \xi^{[k]} \rangle_{\mathbb{H}}] = \text{Cov}(\langle W, v \rangle_{\mathbb{H}}, \langle W, \xi^{[k]} \rangle_{\mathbb{H}}) + E[\langle W, v \rangle_{\mathbb{H}}]E[\langle W, \xi^{[k]} \rangle_{\mathbb{H}}]$.
+Assuming zero-mean predictors ($E[W]=0$), the second term is zero.
+The covariance $\text{Cov}(\langle W, v \rangle_{\mathbb{H}}, \langle W, \xi^{[k]} \rangle_{\mathbb{H}})$ is also zero since $v$ and $\xi^{[k]}$ are in orthogonal subspaces.
+Therefore, $E[\langle W^{[\ell]}, v \rangle_{\mathbb{H}} Y^{[\ell]}] = 0$ for all $v \in R(\mathcal{T}^\ast  )^\perp$.
+This implies that $\Sigma_{YW}^{[\ell]} = E[Y^{[\ell]} W^{[\ell]}]$ is orthogonal to $R(\mathcal{T}^\ast  )^\perp$.
+By the property of orthogonal decomposition in Hilbert spaces ($R(\mathcal{T}^\ast  ) \oplus R(\mathcal{T}^\ast  )^\perp = \mathbb{H}$), if an element is orthogonal to the orthogonal complement of a closed subspace, it must belong to that subspace.
+Thus, $\Sigma_{YW}^{[\ell]}$ must reside in $R(\mathcal{T}^\ast  )$.
+Since $\xi^{[\ell]}$ is a scalar multiple of $\Sigma_{YW}^{[\ell]}$, we conclude that $\xi^{[\ell]} \in R(\mathcal{T}^\ast  )$.
+By mathematical induction, since the base case holds and the inductive step is proven, all PLS directions $\{\xi^{[\ell]}\}_{\ell=1}^\infty$ reside in $R(\mathcal{T}^\ast  )$.
+\end{proof}
+
+\subsection{Proof of Proposition \ref{proposition:CONS}}\label{section:proof:proposition:CONS}
+
+\paragraph{1.1 Orthonormality through Residualization} The iterative nature of the PLS algorithm guarantees the orthonormality of the directions.
+The \textbf{residualization (or orthogonalization)} step is crucial.
+After the $(l-1)$-th PLS direction $\xi^{[l-1]}$ is determined, the predictors and response are adjusted to remove the linear effect of this component.
+Specifically, at the population level: $$W^{[l]} = W^{[l-1]} - \langle W^{[l-1]}, \xi^{[l-1]} \rangle_{\mathbb{H}} \xi^{[l-1]}$$ $$Y^{[l]} = Y^{[l-1]} - \nu^{[l-1]} \rho^{[l-1]}$$ where $W^{[1]} = W$ and $Y^{[1]} = Y$.
+This procedure ensures that the residualized predictors $W^{[l]}$ are orthogonal to all previous directions $\xi^{[j]}$ for $j < l$.
+Consequently, the newly found direction $\xi^{[l]}$, being derived from $W^{[l]}$, will be orthogonal to $\{\xi^{[1]}, \ldots, \xi^{[l-1]}\}$.
+By convention, PLS directions are normalized to have unit norm ($\Vert \xi^{[l]} \Vert_{\mathbb{H}} = 1$).
+Thus, the set $\{\xi^{[l]}\}_{l=1}^\infty$ is an orthonormal set.
+\paragraph{1.2 Completeness} The relevant predictor subspace is precisely the \textbf{range of the adjoint operator $\mathcal{T}^\ast  $}, denoted $R(\mathcal{T}^\ast  )$.
+To show that $\{\xi^{[l]}\}_{l=1}^\infty$ forms a CONS for $R(\mathcal{T}^\ast  )$, given their orthonormality, we must prove completeness.
+According to Theorem 2.4.12, this requires demonstrating that if an element $v \in R(\mathcal{T}^\ast  )$ is orthogonal to all PLS directions $\{\xi^{[l]}\}_{l=1}^\infty$, then $v$ must be the zero vector.
+Let $\mathcal{S} = \text{span}\{\xi^{[l]}\}_{l=1}^\infty$ be the subspace spanned by the PLS directions.
+Assume, for contradiction, that there exists a non-zero $v \in R(\mathcal{T}^\ast  )$ such that $v \perp \mathcal{S}$.
+This means $\langle v, \xi^{[l]} \rangle_{\mathbb{H}} = 0$ for all $l=1,2,\ldots$.
+Since $v \in R(\mathcal{T}^\ast  )$ and $v \neq 0$, it implies that $v$ contains non-zero linear predictive information regarding $Y$.
+Formally, $R(\mathcal{T}^\ast  )$ is the space of elements in $\mathbb{H}$ that are correlated with $Y$, so $E[\langle W, v \rangle_{\mathbb{H}} Y] \neq 0$.
+Now, consider the implications of $v \perp \mathcal{S}$ on the iterative PLS algorithm.
+At any step $\ell$, the residualized predictor $W^{[\ell]}$ is constructed such that its components orthogonal to $\{\xi^{[1]}, \ldots, \xi^{[\ell-1]}\}$ remain.
+Since $v$ is assumed orthogonal to all $\xi^{[j]}$, the projection of $W$ onto $v$ (i.e., $\langle W, v \rangle_{\mathbb{H}}$) is not removed by any residualization step.
+Similarly, $Y^{[\ell]}$ is the residual response.
+The cross-covariance relevant at step $\ell$ is $\Sigma_{YW}^{[\ell]} = E[Y^{[\ell]} W^{[\ell]}]$.
+If $v \in R(\mathcal{T}^\ast  )$ and $v \neq 0$, it implies that $E[\langle W, v \rangle_{\mathbb{H}} Y] \neq 0$.
+Let's examine the inner product of $\Sigma_{YW}^{[\ell]}$ with $v$: $\langle \Sigma_{YW}^{[\ell]}, v \rangle_{\mathbb{H}} = \langle E[Y^{[\ell]} W^{[\ell]}] , v \rangle_{\mathbb{H}} = E[Y^{[\ell]} \langle W^{[\ell]}, v \rangle_{\mathbb{H}}]$.
+Since $v \perp \xi^{[j]}$ for all $j$, the residualization process on $W$ does not affect $\langle W, v \rangle_{\mathbb{H}}$: $\langle W^{[\ell]}, v \rangle_{\mathbb{H}} = \langle W - \sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \xi^{[j]}, v \rangle_{\mathbb{H}} = \langle W, v \rangle_{\mathbb{H}} - \sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \langle \xi^{[j]}, v \rangle_{\mathbb{H}} = \langle W, v \rangle_{\mathbb{H}} - 0 = \langle W, v \rangle_{\mathbb{H}}$.
+So, $\langle \Sigma_{YW}^{[\ell]}, v \rangle_{\mathbb{H}} = E[Y^{[\ell]} \langle W, v \rangle_{\mathbb{H}}]$.
+By the construction of PLS, the sequence $Y^{[\ell]}$ is generated such that $Y^{[\ell]} = Y - \sum_{j=1}^{\ell-1} \nu^{[j]} \rho^{[j]}$.
+Substituting this: $\langle \Sigma_{YW}^{[\ell]}, v \rangle_{\mathbb{H}} = E\left[ \left( Y - \sum_{j=1}^{\ell-1} \nu^{[j]} \rho^{[j]} \right) \langle W, v \rangle_{\mathbb{H}} \right]$ $= E[Y \langle W, v \rangle_{\mathbb{H}}] - \sum_{j=1}^{\ell-1} \nu^{[j]} E[\rho^{[j]} \langle W, v \rangle_{\mathbb{H}}]$ The first term, $E[Y \langle W, v \rangle_{\mathbb{H}}]$, is non-zero because $v \in R(\mathcal{T}^\ast  )$ and $v \neq 0$.
+The second term, $\sum_{j=1}^{\ell-1} \nu^{[j]} E[\rho^{[j]} \langle W, v \rangle_{\mathbb{H}}]$, simplifies.
+Recall $\rho^{[j]} = \langle W, \xi^{[j]} \rangle_{\mathbb{H}}$.
+So $E[\rho^{[j]} \langle W, v \rangle_{\mathbb{H}}] = E[\langle W, \xi^{[j]} \rangle_{\mathbb{H}} \langle W, v \rangle_{\mathbb{H}}]$.
+This represents the covariance between the component of $W$ in direction $\xi^{[j]}$ and the component of $W$ in direction $v$.
+Since $\xi^{[j]} \in R(\mathcal{T}^\ast  )$ and $v \perp R(\mathcal{T}^\ast  )$, these components are uncorrelated (assuming zero-mean $W$).
+Thus, $E[\rho^{[j]} \langle W, v \rangle_{\mathbb{H}}] = 0$.
+Therefore, $\langle \Sigma_{YW}^{[\ell]}, v \rangle_{\mathbb{H}} = E[Y \langle W, v \rangle_{\mathbb{H}}] \neq 0$ for all $\ell$.
+This implies that $\Sigma_{YW}^{[\ell]}$ is never the zero vector (or operator) as long as $v \neq 0$.
+The PLS algorithm, at each step $\ell$, extracts $\xi^{[\ell]}$ as the principal eigenfunction of $\mathcal{U}^{[\ell]}$.
+If $\Sigma_{YW}^{[\ell]}$ is non-zero, then $\mathcal{U}^{[\ell]}$ has a non-zero largest eigenvalue $\lambda^{[\ell]}$, and $\xi^{[\ell]} = (\langle \Sigma_{YW}^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}} / \lambda^{[\ell]}) \Sigma_{YW}^{[\ell]}$.
+This means $\xi^{[\ell]}$ is directly related to $\Sigma_{YW}^{[\ell]}$.
+Since $\Sigma_{YW}^{[\ell]}$ has a non-zero component orthogonal to all previously extracted $\xi^{[j]}$ (namely, the component in direction $v$), the algorithm *must* continue to extract components that capture this remaining predictive information.
+This contradicts the assumption that $v$ is orthogonal to *all* $\xi^{[\ell]}$, as the algorithm would continue to extract components along the direction of $v$ or its correlates.
+The process of PLS is designed to exhaust all such linearly predictive information in $R(\mathcal{T}^\ast  )$.
+Therefore, the initial assumption that a non-zero $v \in R(\mathcal{T}^\ast  )$ exists orthogonal to all $\xi^{[\ell]}$ leads to a contradiction.
+Thus, if $v \in R(\mathcal{T}^\ast  )$ and $v \perp \mathcal{S}$, it must imply $v=0$.
+This establishes that $\mathcal{S}$ is complete in $R(\mathcal{T}^\ast  )$.
+Combining orthonormality and completeness, $\{\xi^{[l]}\}_{l=1}^\infty$ forms a CONS for $R(\mathcal{T}^\ast  )$.
+
+		\subsection{Proof of Proposition \ref{proposition:nu_l}}\label{section:proof:proposition:nu_l}
+
+\begin{proof}Since population level least square regression coefficient is precisely
+	\begin{equation*}
+		\nu^{[l]} = \frac{\mathbb{E}[Y^{[l]} \rho^{[l]}]}{\mathbb{E}[(\rho^{[l]})^2]},
+	\end{equation*}
+	it suffices to show that
+	\begin{equation*}
+		\mathbb{E}[Y^{[l]} \rho^{[l]}]
+		= 
+		\langle \beta_{\mathrm{OLS}}, \xi^{[\ell]} \rangle_{\mathbb{H}} \mathbb{E}[(\rho^{[\ell]})^2].
+	\end{equation*} 
+	We proceed in two intermediate steps:
+	\begin{enumerate}
+		\item Showing  
+		$
+		\beta_{\mathrm{OLS}} = (\mathcal{T}^\ast \mathcal{T})^{-1} \mathcal{T}^\ast Y \in R(\mathcal{T}^\ast)$,
+		%
+		\item Expanding and transforming $E[Y^{[l]} \rho^{[l]}]  $.
+	\end{enumerate}
+
+	\medskip
+	\noindent
+	\textit{1. Showing  
+		$
+		\beta_{\mathrm{OLS}} = (\mathcal{T}^\ast \mathcal{T})^{-1} \mathcal{T}^\ast Y \in R(\mathcal{T}^\ast)$.}~
+	The term $\mathcal{T}^\ast Y$ is, by definition, an element of $R(\mathcal{T}^\ast  )$.
+	Next, let us consider The operator $\mathcal{T}^\ast   \mathcal{T}: \mathbb{H} \mapsto \mathbb{H}$ is a self-adjoint, positive semi-definite operator.
+The inverse operator $(\mathcal{T}^\ast   \mathcal{T})^{-1}$ exists and is well-defined when $\mathcal{T}^\ast   \mathcal{T}$ is invertible.
+	Now, since $R(\mathcal{T}^\ast   \mathcal{T}) = R(\mathcal{T}^\ast  )$,
+	the operator $\mathcal{T}^\ast   \mathcal{T}$ maps elements from $\mathbb{H}$ specifically into the subspace $R(\mathcal{T}^\ast  )$.
+	Consequently, when the inverse operator $(\mathcal{T}^\ast   \mathcal{T})^{-1}$ is applied to an element that is already within $R(\mathcal{T}^\ast  )$ (such as $\mathcal{T}^\ast   Y$), the result will also remain within this same subspace $R(\mathcal{T}^\ast  )$.
+	Therefore, the entire expression $(\mathcal{T}^\ast   \mathcal{T})^{-1} \mathcal{T}^\ast   Y$ must   reside in $R(\mathcal{T}^\ast  )$.
+
+	\medskip
+	\noindent
+	\textit{2. Expanding and transforming $E[Y^{[l]} \rho^{[l]}]$.
+	}
+	We can expand $\mathbb{E}[Y^{[l]} \rho^{[l]}] $ as:
+	\begin{equation*}
+		\mathbb{E}[Y^{[l]} \rho^{[l]}] 
+		\overset{(i)}{=} 
+		E
+		\bigl[ \bigl\{ ( Y - \sum_{j=1}^{\ell-1} \nu^{[j]} \rho^{[j]} \bigr\} \rho^{[l]} 
+		\bigr]
+		= \mathbb{E}[Y \rho^{[l]}] - \sum_{j=1}^{\ell-1} \nu^{[j]} \mathbb{E}[\rho^{[j]} \rho^{[l]}]
+		\overset{(ii)}{=}
+		\mathbb{E}[Y \rho^{[l]}],
+	\end{equation*}
+	where 
+	step $(i)$ repeatedly uses the residualization process for the response and
+	step $(ii)$ uses the orthogonality of the PLS scores presented in 
+	Corollary \ref{cor:orthogonal_scores}. 
+	We further expand:
+	\begin{align*}
+		\mathbb{E}[Y^{[l]} \rho^{[l]}] 
+		=
+		\mathbb{E}[Y \rho^{[l]}]
+		=
+		\mathbb{E}[Y  \langle W, \, \xi^{[l]} \rangle_{\mathbb{H}} ]
+		=
+		\langle \mathbb{E}[ Y W ], \, \xi^{[l]} \rangle_{\mathbb{H}} 
+		%%%%%%%%%%%%%%
+		&\overset{(i)}{=}
+		\langle 
+		\mathbb{E}[W \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}], \, \xi^{[l]} \rangle_{\mathbb{H}} 
+		\\&=
+		\mathbb{E}[\langle W, \xi^{[\ell]} \rangle_{\mathbb{H}} \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}].
+	\end{align*}		
+	where step $(i)$ uses the normal equation $	\mathbb{E}[(Y - \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}})W] = 0$ presented in  \eqref{normal_equation}.
+
+	Since $\beta_{\mathrm{OLS}} \in R(\mathcal{T}^*)$ and 		$\{\xi^{[k]}\}_{k=1}^\infty$ is a  CONS for $R(\mathcal{T}^\ast)$ by Proposition \ref{proposition:CONS}, we can further expand:
+	\begin{align*}
+		\mathbb{E}[Y^{[l]} \rho^{[l]}] 
+		=
+		\mathbb{E}[\langle W, \xi^{[\ell]} \rangle_{\mathbb{H}} \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}]
+		&=
+		\mathbb{E}[\langle W, \xi^{[\ell]} \rangle_{\mathbb{H}} \langle \sum_{k=1}^{\infty} \langle \beta_{\mathrm{OLS}}, \xi^{[k]} \rangle_{\mathbb{H}} \xi^{[k]}, W \rangle_{\mathbb{H}}]
+		\\&=
+		%%%%%%%%%%%%%%%%%5
+		\mathbb{E}
+		\bigl[ \rho^{[\ell]} \sum_{k=1}^{\infty} \langle \beta_{\mathrm{OLS}}, \xi^{[k]} \rangle_{\mathbb{H}} \rho^{[k]} \bigr]
+		\\& = \langle \beta_{\mathrm{OLS}}, \xi^{[\ell]} \rangle_{\mathbb{H}} \mathbb{E}[(\rho^{[\ell]})^2],
+	\end{align*}
+	where the last step 
+	uses the orthogonality of scores presented in Corollary \ref{cor:orthogonal_scores}.
+	This completes the proof of Proof of Proposition \ref{proposition:nu_l}.
+\end{proof}
+
+\subsection{Proof of Theorem \ref{thm:hybrid_pls_convergence}}\label{section:proof:thm:hybrid_pls_convergence}
+\begin{proof}
+By Proposition \ref{proposition:CONS},
+	 $\{\xi^{[l]}\}_{l=1}^\infty$ is a CONS for $R(\mathcal{T}^\ast  )$.
+	 By Appendix \ref{section:proof:proposition:nu_l}, 
+	 we have
+	 $\beta_{\mathrm{OLS}}   \in R(\mathcal{T}^\ast)$.
+Therefore, we can expand $Y_{\mathrm{OLS}}$ as:
+\begin{align*}
+ Y_{\mathrm{OLS}}
+ = 
+ \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}
+ =
+ \biggl \langle 
+ \sum_{l=1}^{\infty} \langle \beta_{\mathrm{OLS}}, \xi^{[l]} \rangle_{\mathbb{H}} \xi^{[l]}, W 
+ \biggr \rangle_{\mathbb{H}}
+ \hspace{-.5em}
+ =
+ \sum_{l=1}^{\infty} \langle \beta_{\mathrm{OLS}}, \xi^{[l]} \rangle_{\mathbb{H}} \langle \xi^{[l]}, W \rangle_{\mathbb{H}}
+ =
+\sum_{l=1}^{\infty} \nu^{[l]} \rho^{[l]},
+\end{align*}
+where the last equality uses
+Corollary \ref{cor:orthogonal_scores} and
+Proposition \ref{proposition:nu_l}.
+
+Then  the mean-squared error between the PLS approximation and the ordinary linear regression solution is written as
+\begin{align*}
+ \mathbb{E}\left[ \| Y_{\mathrm{PLS},L } - Y_{\mathrm{OLS}} \|_2^2 \right] 
+ %%%%%%%%%%%%%%%
+ =
+ \mathbb{E}\left[ 
+ \bigl\|
+  \sum_{l=1}^{L} \nu^{[l]} \rho^{[l]} - \sum_{l=1}^{\infty} \nu^{[l]} \rho^{[l]} 
+ \bigr\|_2^2 \right]
+ %%%%%%%%%%%%%%%%%%
+ &=
+ \mathbb{E}\left[ 
+ \bigl\|
+ \sum_{l=L+1}^{\infty} \nu^{[l]} \rho^{[l]} 
+ \bigr\|_2^2 \right]
+ %%%%%%%%%%%%%%%%%%%
+ \\&=
+ \sum_{l=L+1}^{\infty} (\nu^{[l]})^2 \mathbb{E}[(\rho^{[l]})^2],
+\end{align*}
+where the last equality uses Corollary \ref{cor:orthogonal_scores}.
+
+Now, it suffices to show that $\sum_{l=L+1}^{\infty} (\nu^{[l]})^2 \mathbb{E}[(\rho^{[l]})^2] \to 0$ as $L \to \infty$.
+Now, since we assume $\mathbb{E}[Y] = 0$, and $Y_{\mathrm{OLS}}$ is linear in $Y$, we have
+\begin{align*}
+	\text{Var}(Y_{\mathrm{OLS}}) = \mathbb{E}[(Y_{\mathrm{OLS}})^2] = \mathbb{E}\left[\left(\sum_{l=1}^{\infty} \nu^{[l]} \rho^{[l]}\right)^2\right] 
+	= \sum_{l=1}^{\infty} (\nu^{[l]})^2 \mathbb{E}[(\rho^{[l]})^2],
+\end{align*}
+where the last equality uses Corollary \ref{cor:orthogonal_scores}.
+
+  By Cauchy–Schwarz in $\mathbb{H}$,
+\begin{equation*}
+\mathbb{E}|Y_{\mathrm{OLS}}|^2 
+	=
+\mathbb{E}	|\langle \beta_{\text{OLS}}, W\rangle_{\mathbb{H}}|^2 \le \mathbb{E}\|\beta_{\text{OLS}}\|_{\mathbb{H}}^{2}\,\mathbb{E}\|W\|_{\mathbb{H}}^{2} < \infty,
+\end{equation*}
+$(\nu^{[l]})^2 \mathbb{E}[(\rho^{[l]})^2]$ has a convergent series.
+For any convergent series, the sum of its tail (i.e., from $L+1$ to infinity) must approach zero as $L$ tends to infinity This concludes the proof of Theorem \ref{thm:hybrid_pls_convergence}.
+\end{proof}
+	\section{Proof of geometric properties}
 

### 2025-08-20 manuscript/main.tex
uniqueness not required

@@
 \end{corollary}
-Let $\beta_{\mathrm{OLS}}$ denote a minimizer of  the mean squared error $ \mathbb{E}[\|Y - \langle \beta, W \rangle_{\mathbb{H}}\|_2^2]$. It
-satisfies the normal equation
-\begin{equation}\label{normal_equation}
-	\mathbb{E}[(Y - \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}})W] = 0 \in \mathbb{H}.
-\end{equation}
-If the operator $\mathcal{T}^\ast \mathcal{T}$ is invertible,  the minimizer is uniquely determined as 
-$\beta_{\mathrm{OLS}} = (\mathcal{T}^\ast \mathcal{T})^{-1} \mathcal{T}^\ast Y$.
+
+\begin{proposition} \label{prop:ols_uniqueness} Let $\beta_{\mathrm{OLS}}$ denote a minimizer of the mean squared error $\mathbb{E}[\|Y - \langle \beta, W \rangle_{\mathbb{H}}\|_2^2]$.
+This minimizer satisfies the normal equation: \begin{equation*} \mathbb{E}[(Y - \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}})W] = \mathbf{0} \in {\mathbb{H}}.
+\end{equation*}  If $\mathcal{T}^\ast \mathcal{T}$ is not invertible, $\beta_{\mathrm{OLS}}$ may not be unique, but all solutions for $\beta_{\mathrm{OLS}}$ reside in $R(\mathcal{T}^*)$, and the corresponding fitted values $Y_{\mathrm{OLS}} = \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}$ are always unique.
+\end{proposition}
+Proof of Proposition \ref{prop:ols_uniqueness} is provided in Appendix \ref{section:proof:prop:ols_uniqueness}.
 \begin{proposition}\label{proposition:nu_l}
@@
 
+\subsection{Proof of Proposition \ref{prop:ols_uniqueness}}\label{section:proof:prop:ols_uniqueness}
+ \begin{proof} 
+ 	1. Location of Solutions for $\beta_{\mathrm{OLS}}$
+ 	The normal equation can be rewritten using the operator $\mathcal{T}$ and its adjoint $\mathcal{T}^*$.
+Recall that $E[YW] = \mathcal{T}^*Y$ and $E[W \langle \beta, W \rangle_{\mathbb{H}}] = \mathcal{T}^* \mathcal{T} \beta$.
+Thus, the normal equation becomes: $$ \mathcal{T}^* Y - \mathcal{T}^* \mathcal{T} \beta_{\mathrm{OLS}} = \mathbf{0}_{\mathbb{H}} $$ $$ \mathcal{T}^* \mathcal{T} \beta_{\mathrm{OLS}} = \mathcal{T}^* Y $$ This equation directly shows that $\mathcal{T}^* Y$ must be in the range of $\mathcal{T}^* \mathcal{T}$, i.e., $\mathcal{T}^* Y \in R(\mathcal{T}^* \mathcal{T})$.
+A fundamental property of operators in Hilbert spaces is that the range of $\mathcal{T}^* \mathcal{T}$ is equal to the range of $\mathcal{T}^*$, i.e., $R(\mathcal{T}^* \mathcal{T}) = R(\mathcal{T}^*)$.
+Therefore, any solution $\beta_{\mathrm{OLS}}$ to the normal equation implies that $\mathcal{T}^* Y$ must reside in $R(\mathcal{T}^*)$.
+If $\mathcal{T}^* \mathcal{T}$ is invertible, the unique solution is $\beta_{\mathrm{OLS}} = (\mathcal{T}^* \mathcal{T})^{-1} \mathcal{T}^* Y$.
+As shown in the proof "The OLS Solution $(\mathcal{T}^* \mathcal{T})^{-1} \mathcal{T}^* Y$ Resides in $R(\mathcal{T}^*)$," this unique solution itself resides in $R(\mathcal{T}^*)$.
+If $\mathcal{T}^* \mathcal{T}$ is not invertible, its null space (kernel) is non-trivial.
+In this case, there are infinitely many solutions to the normal equation.
+However, any solution $\beta_{\mathrm{OLS}}$ still satisfies $\mathcal{T}^* \mathcal{T} \beta_{\mathrm{OLS}} = \mathcal{T}^* Y$.
+Since the right-hand side $\mathcal{T}^* Y$ is an element of $R(\mathcal{T}^*)$, and $R(\mathcal{T}^* \mathcal{T}) = R(\mathcal{T}^*)$, any solution $\beta_{\mathrm{OLS}}$ must have its "predictive part" (its projection onto $R(\mathcal{T}^*)$) uniquely determined.
+More precisely, the minimum-norm solution (obtained via the Moore-Penrose pseudoinverse) always lies in $R(\mathcal{T}^*)$, and any other solution differs from it by an element in the null space of $\mathcal{T}^* \mathcal{T}$.
+
+ 	2. Uniqueness of Fitted Values $Y_{\mathrm{OLS}}$
+ 	 Despite the potential non-uniqueness of $\beta_{\mathrm{OLS}}$, the fitted values $Y_{\mathrm{OLS}}$ are always unique.
+Let $\beta_1$ and $\beta_2$ be two different solutions to the normal equation, i.e., $\mathcal{T}^* \mathcal{T} \beta_1 = \mathcal{T}^* Y$ and $\mathcal{T}^* \mathcal{T} \beta_2 = \mathcal{T}^* Y$.
+Subtracting these equations gives: $$ \mathcal{T}^* \mathcal{T} (\beta_1 - \beta_2) = \mathbf{0}_{\mathbb{H}} $$ This means that the difference $(\beta_1 - \beta_2)$ belongs to the null space of $\mathcal{T}^* \mathcal{T}$, i.e., $(\beta_1 - \beta_2) \in \text{Null}(\mathcal{T}^* \mathcal{T})$.
+A key property in Hilbert spaces is that $\text{Null}(\mathcal{T}^* \mathcal{T}) = \text{Null}(\mathcal{T})$.
+Therefore, if we let $\delta = \beta_1 - \beta_2$, then $\mathcal{T}\delta = \mathbf{0}_{L^2(\Omega)}$.
+Now, let's examine the fitted values corresponding to $\beta_1$ and $\beta_2$: $$ Y_{\mathrm{OLS}}(\beta_1) = \langle \beta_1, W \rangle_{\mathbb{H}} = \mathcal{T}\beta_1 $$ $$ Y_{\mathrm{OLS}}(\beta_2) = \langle \beta_2, W \rangle_{\mathbb{H}} = \mathcal{T}\beta_2 $$ Consider their difference: $$ Y_{\mathrm{OLS}}(\beta_1) - Y_{\mathrm{OLS}}(\beta_2) = \mathcal{T}\beta_1 - \mathcal{T}\beta_2 = \mathcal{T}(\beta_1 - \beta_2) = \mathcal{T}\delta $$ Since $\mathcal{T}\delta = \mathbf{0}_{L^2(\Omega)}$, it follows that: $$ Y_{\mathrm{OLS}}(\beta_1) - Y_{\mathrm{OLS}}(\beta_2) = \mathbf{0}_{L^2(\Omega)} $$ Thus, $Y_{\mathrm{OLS}}(\beta_1) = Y_{\mathrm{OLS}}(\beta_2)$, demonstrating that the fitted values are unique even when the regression coefficient $\beta_{\mathrm{OLS}}$ itself is not unique.
+\end{proof}
 		\subsection{Proof of Proposition \ref{proposition:nu_l}}\label{section:proof:proposition:nu_l}

### 2025-08-21 manuscript/main.tex
adjoint

@@
 	\end{equation*}
-	Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
-	\begin{equation*}
-		\Sigma_{YW} :=  
-		\mathbb{E}
-		[ Y_1 W_1 ]
-		=
-		\bigl(
-		\sigma_{YX, 1} , \ldots, \sigma_{YX, K} , \, \sigma_{YZ}
-		\bigr) \in \mathbb{H}.
-	\end{equation*}
+	Based on these definitions, 
 	Based on these definitions, we introduce two cross-covariance operators and their properties.
+
+ We define an operator $\mathcal{T}$ that maps an element $g \in \mathbb{H}$   (representing a potential regression coefficient) to the predicted response.
+\begin{lemma}\label{lemma:tau_ast}
+	Let the cross-covariance between the response $Y$ and the hybrid predictor $W$ be
+	\[
+	\Sigma_{YW} := \mathbb{E}[ Y_1 W_1 ]
+	= \bigl( \sigma_{YX,1}, \ldots, \sigma_{YX,K}, \, \sigma_{YZ} \bigr) 
+	\in \mathbb{H}.
+	\]
+	Define the linear operator $\mathcal{T}: \mathbb{H} \to \mathbb{R}$ by
+	\[
+	\mathcal{T} g := \langle W_1, g \rangle_{\mathbb{H}}, \quad g \in \mathbb{H}.
+	\]
+	Let $\mathcal{T}^\ast: \mathbb{R} \to \mathbb{H}$ denote its adjoint operator. Then,
+	\[
+	\mathbb{E}[ \mathcal{T}^\ast Y_1 ] = \Sigma_{YW}.
+	\]
+\end{lemma}
+
+Proof of Lemma \ref{lemma:tau_ast} is provided in Appendix \ref{section:rpoof:lemma:tau_ast}.
+
 	\begin{lemma}\label{lemma:cross_cov_functional}
@@
 Proof of Lemma \ref{lem:regression_W_rho} is provided in Appendix \ref{section:proof:lem:regression_W_rho}.
-
- We define an operator $\mathcal{T}$ that maps an element $g \in \mathbb{H}$   (representing a potential regression coefficient) to the predicted response.
-\begin{lemma}\label{lemma:tau_ast}
-	Define the linear operator $\mathcal{T}: \mathbb{H} \to \mathbb{R}$ that maps  $g \in \mathbb{H}$ to 
-	$
-	\mathcal{T}g = \langle W, g \rangle_{\mathbb{H}}
-	$.
- Let $\mathcal{T}^\ast: \mathbb{R} \to \mathbb{H}$ denote its adjoint operator. Then,
-	\[
-	\Sigma_{YW}^{[1]} = \mathcal{T}^\ast Y.
-	\]
-\end{lemma}
-Proof of Lemma \ref{lemma:tau_ast} is provided in Appendix \ref{section:rpoof:lemma:tau_ast}.
 
@@
 	\begin{proof}
-	The adjoint operator  is uniquely defined by the property relating the inner products in $L^2(\Omega)$ and $\mathbb{H}$: $$ \langle \mathcal{T}g, Y \rangle_{L^2(\Omega)} = \langle g, \mathcal{T}^\ast Y \rangle_{\mathbb{H}}, \quad \text{for all } g \in \mathbb{H}, Y \in L^2(\Omega) $$ Here, $\langle \cdot, \cdot \rangle_{L^2(\Omega)}$ denotes the inner product in $L^2(\Omega)$, which is the expectation $E[\cdot]$.
-Let's explicitly derive the expression for $\mathcal{T}^\ast Y$: $$ \langle g, \mathcal{T}^\ast Y \rangle_{\mathbb{H}} = E[\langle W, g \rangle_{\mathbb{H}} Y] $$ By the properties of expectation and the linearity of the inner product (assuming appropriate boundedness and measurability for interchange of expectation and inner product): $$ E[\langle W, g \rangle_{\mathbb{H}} Y] = E[\langle g, W \rangle_{\mathbb{H}} Y] = \langle g, E[YW] \rangle_{\mathbb{H}} $$ Comparing the leftmost and rightmost parts of the definition of the adjoint: $$ \mathcal{T}^\ast Y = E[YW] $$
+By the definition of the adjoint operator, 
+for all $g \in \mathbb{H}$, we have
+\begin{align*}
+	 \langle
+	\Sigma_{YW}, g \rangle_{\mathbb{H}} 
+=	
+	 \langle
+	 \mathbb{E}
+	 [ Y_1 W_1], g \rangle_{\mathbb{H}} 
+	=
+\mathbb{E}
+[ Y_1 \langle W_1, g \rangle_{\mathbb{H}} ]
+=
+\mathbb{E}[
+Y_1
+(\mathcal{T}g)
+]
+=
+\mathbb{E}[
+\langle \mathcal{T}g, Y_1 \rangle
+]
+&= \mathbb{E}[
+\langle g, \mathcal{T}^\ast Y_1 \rangle_{\mathbb{H}}
+]
+\\&= 
+\langle g, \mathbb{E}[\mathcal{T}^\ast Y_1 ]\rangle_{\mathbb{H}}.
+\end{align*}	
+This completes the proof of Lemma \ref{lemma:tau_ast}.
 	\end{proof}

### 2025-08-22 manuscript/main.tex
theory done, twice
overleaf import

--- 2025-08-20 manuscript/main.tex
@@
 	$ To retain the regression relationship, the $l$-th PLS direction $\hat{\boldsymbol{\xi}}_l$ solves:
-	\begin{equation*}
-		\max_{ \boldsymbol{ \alpha } } 
+	\begin{equation}\label{scalar_PLS_sample}
+		\max_{ \mathbf{ h } } 
 		\widehat{\operatorname{Cov}}^2
@@
 		\langle 
-		\boldsymbol{\alpha}, \mathbf{Z}_i
+		\mathbf{ h }, \mathbf{Z}_i
 		\rangle
@@
 		\}_{i=1}^n
-		\bigr)~\text{s.t.}~\| \boldsymbol{\alpha} \|_2 = 1,~\boldsymbol{\alpha}^\top  \widehat{\operatorname{Cov}}^2
+		\bigr)~\text{s.t.}~\| \mathbf{ h } \|_2 = 1,~\mathbf{ h }^\top  \widehat{\operatorname{Cov}}^2
 		\bigl(
@@
 		\bigr) \hat{\boldsymbol{\xi}}_j = 0, \quad j = 1, \ldots, l-1,
-	\end{equation*}
+	\end{equation}
 	where the two $\widehat{\operatorname{Cov}}^2$ denote sample cross-covariance and sample covariance, respectively.
-A standard algorithm for solving this problem, called nonlinear iterative partial least squares (NIPALS) is presented in Algorithm \ref{alg:scalar_pls}.
+A standard algorithm for solving this optimization problem, called nonlinear iterative partial least squares (NIPALS) is presented in Algorithm \ref{alg:scalar_pls}.
 	\begin{algorithm} 
@@
 	\jongmin{comment:maybe we can move this section to precede the algorithm section. then the new structure will introduce population version first and introduce finite-sample estimation procedure.}
-	The fundamental property of classical scalar PLS is that the PLS component direction  corresponds to the first eigenvector of the squared covariance matrix, satisfying  the Tucker's Criterion \citep{Tucker1938}.
-	Under a mild assumption,
-	We derive an analogous result  in our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
-	This justifies our estimation procedure introduced in Section \ref{section:main:our_algorithm}.
-For notational simplicity, we omit the index $l$. At the population level, where the random objects are fully observed, it suffices to consider $Y_1$ and $W_1$ rather than their sampled realizations.
-We assume 
-$\mathbb{E}[Y_1]=0 \in \mathbb{R}$ and $\mathbb{E}[W_1] = 0 \in \mathbb{H}$.
- We first define the cross-covariance between the response and the functional predictors, where the predictors correspond to the observed versions for $l=1$ and to the residualized versions for $l \ge 2$:
-	\begin{equation}\label{def:cross_covariance_yx}
+	We now derive the population analogue of Algorithm~\ref{alg:hybrid_pls} and establish its key mathematical properties, namely the orthogonality of the PLS directions and scores, as well as convergence to the true response.
+At the population level, where the random objects are fully observable, we may drop the sample index $i$ and simply work with $Y$
+	and
+	$W = (X_1, \ldots, X_K, Z_1, \ldots, Z_p)$. Throughout this section we assume 
+	$\mathbb{E}[Y] = 0 \in \mathbb{R}$ and $\mathbb{E}[W] = 0 \in \mathbb{H}$.
+
+	The core optimization problem in PLS is formulated in terms of maximizing the squared cross-covariance.
+At the population level, this quantity is naturally characterized by cross-covariance operators, which we define next.
+For notational simplicity, we suppress the iteration index $l$, with the understanding that for $l=1$ the predictors correspond to the original variables, while for $l \geq 2$ they represent the residualized versions.
+	\begin{definition}\label{def:cross_cov_terms}
+		The covariance operator of the hybrid predictor $W$ is denoted as $\Sigma_{W} := \mathbb{E}[W \otimes W]$, so that for $u,v \in \mathbb{H}$, we have
+		\[
+		\Sigma_{W} u = \mathbb{E}[
+		\langle W, u\rangle_{\mathbb{H}}W
+		],
+		\quad
+		\langle \Sigma_{W} u, v \rangle_{\mathbb{H}}
+		= \mathbb{E}[\langle W,u \rangle_{\mathbb{H}} \, \langle W,v \rangle_{\mathbb{H}}].
+		\]
+
+		The cross-covariances between the response $Y$ and the predictors are
+		\[
 		\sigma_{YX}
-		=
-		\bigl(
-		\sigma_{YX, 1}(t) , \ldots, \sigma_{YX, K}(t) 
-		\bigr)
 		:=
-		\bigl(
-		\mathbb{E}
-		[Y_1 X_{11}]
-		,\ldots, 
-		\mathbb{E}
-		[Y_1  X_{1K}]
-		\bigr)   \in \mathcal{F}^{\otimes K},
-	\end{equation}
-	and between the response and the scalar predictor:
-	\begin{equation*}
+		\bigl(\mathbb{E}[Y X_{1}],\ldots,\mathbb{E}[Y X_{K}]\bigr) \in \mathcal{F}^{K},
+		\quad
 		\sigma_{YZ} 
-		= 
-		(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
 		:=
-		\bigl(
-		\mathbb{E}[Y_1 Z_{11}]
-		,\ldots,
-		\mathbb{E}[Y_1 Z_{1p}]
-		\bigr)^\top %= E(Y\mathbf{Z})
-		\in \mathbb{R}^p.
-	\end{equation*}
-	Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
-	\begin{equation*}
-		\Sigma_{YW} :=  
-		\mathbb{E}
-		[ Y_1 W_1 ]
-		=
-		\bigl(
-		\sigma_{YX, 1} , \ldots, \sigma_{YX, K} , \, \sigma_{YZ}
-		\bigr) \in \mathbb{H}.
-	\end{equation*}
-	Based on these definitions, we introduce two cross-covariance operators and their properties.
+		\bigl(\mathbb{E}[Y Z_{1}],\ldots,\mathbb{E}[Y Z_{p}]\bigr)^\top \in \mathbb{R}^p.
+		\]
+
+		The cross-covariance between $Y$ and the hybrid predictor $W$ is then
+		\[
+		\Sigma_{YW} := \mathbb{E}[ Y W ] = \bigl( \sigma_{YX}, \, \sigma_{YZ} \bigr) \in \mathbb{H}.
+		\]
+	\end{definition}
+	At the population level, Algorithm \ref{alg:hybrid_pls} without regularizaiton can be expressed as follows.
+	Let $W^{[1]} := W$ and $Y^{[1]} := Y$.
+	For any   integer $l \geq 2$,
+	to be the residuals of the
+
+	where
+
+	and
+
+	which is attained by the leading eigenfunction of the operator 
+	$\mathcal{U}^{[l-1]}$, defined analogously to Lemma~\ref{lemma:composite_cross_cov} 
+	using $W^{[l-1]}$ and $Y^{[l-1]}$, provided the conditions in 
+	Lemma~\ref{lemma:cross_cov_functional} are satisfied.
+	\begin{definition}[Population PLS]\label{def:population_pls}
+		The population analogue of the PLS optimization problem \eqref{scalar_PLS_sample} in the hybrid space is formulated as the constrained generalized eigenproblem:
+		\begin{equation}\label{const_eigen_pop}
+			\xi^{[l]} = \arg\max_{h \in \mathbb{H}}
+			\operatorname{Cov}^2(\langle W, h \rangle_{\mathbb{H}}, Y),~s.t.~\|h\|_{\mathbb{H}}=1, \langle h, \Sigma_W \, \xi^{[j]} \rangle_{\mathbb{H}} = 0,\, j < l.
+		\end{equation}
+	\end{definition}
+	As in scalar case, this problem can be solved by an iterative algorithm, and yields orthogonal scores:
+	\begin{proposition}[Properties of population PLS]
+		\label{prop:residualization_equiv_eigen}
+		The solution of optimization problem \eqref{const_eigen_pop} of Definition \ref{def:population_pls} is equivalent to that of population NIPALS (Algorithm \ref{alg:population_pls}).
+For every \(s\ge 1\) and every \(j\le s-1\), we have
+		$
+		\mathbb{E}[\rho^{[j]}\rho^{[s]}]=0
+		$
+		and
+		$
+		\mathbb{E}[Y^{[s]}\rho^{[j]}]=0.
+		$
+
+	\end{proposition}
+	Proof of Proposition \ref{prop:residualization_equiv_eigen} is provided in Appendix \ref{section:proof:prop:residualization_equiv_eigen}.
+	\begin{algorithm} 
+		\caption{Population NIPALS}\label{alg:population_pls}
+		\begin{algorithmic}[1]
+			\State
+			$(W^{[1]}, Y^{[1]} \leftarrow (W, Y)$
+			\For{$l = 1, 2, \ldots, L$}
+			\State
+			$
+			\xi^{[l]}
+			\leftarrow
+			\arg\max_{h \in \mathbb{H}} \operatorname{Cov}^2(\langle W^{[l]}, h \rangle_{\mathbb{H}}, Y^{[l]})~s.t.~ \|h\|_{\mathbb{H}} = 1,
+			$\label{alg:line:pls_direction} \Comment{PLS direction}
+			%%%%%%%%%
+			\State 
+			$
+			\rho^{[l]} \leftarrow \langle \xi^{[l]}, W^{[l]} \rangle 
+			$ \Comment{PLS score}
+			%%%%%%%%%%
+			\State
+			$
+			\delta^{[l]}
+			\leftarrow
+			\frac{1}{\mathbb{E}[ (\rho^{[l]})^2 ]}  \mathbb{E}[W^{[l]} \rho^{[l]}]
+			$\label{population_delta}
+			\Comment{Linear regression of 
+				$W^{[l]}$
+				on $\rho^{[l]}$}
+			%%%%%%%%%%%
+			\State
+			$
+			\nu^{[l]}
+			\leftarrow
+			\frac{1}{\mathbb{E}[ (\rho^{[l]})^2 ]}
+			\mathbb{E}[Y^{[l]} \rho^{[l]}]
+			$
+			\Comment{
+				Linear regression of 
+				$Y^{[l]} $
+				on $\rho^{[l]}$
+			}
+			%%%%%%%%%%%%%%%%%%%
+			\State 
+			$ W^{[l+1]} \leftarrow W^{[l]} - \rho^{[l]} \, \delta^{[l]}$
+			\label{population_predictor_residualize}
+			\Comment{
+				Residualized predictor
+			}
+			\State
+			$ Y^{[l]} \leftarrow Y^{[l-1]} - \nu^{[l-1]} \, \rho^{[l-1]}$
+			\Comment{
+				Residualized response
+			}
+			\EndFor
+			\State \textbf{Output:}
+			PLS directions $\xi^{[1]}, \ldots, \xi^{[L]}$
+		\end{algorithmic}
+	\end{algorithm}
+
+	We show that problem \eqref{const_eigen_pop} and Algorithm \ref{alg:population_pls} are well-defined under mild conditions by  establishing that line \ref{alg:line:pls_direction} of Algorithm \ref{alg:population_pls} is well-defined under mild conditions.
+For clarity, we define the relevant operators while omitting the iteration index for the residualized predictors and responses.
 	\begin{lemma}\label{lemma:cross_cov_functional}
 		Define the operator $
-		\mathcal{C}_{YW}
-		=
-		\mathbb{E}(W_1 \otimes_\mathbb{H} Y_1)
-		: \mathbb{H} \rightarrow \mathbb{R}$ such that for any $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathbb{H}$, it maps $h$ to a real number as: \begin{equation*} \mathcal{C}_{YW} h := \mathbb{E} \left[ \langle W_1, h \rangle_\mathbb{H} Y_1 \right] = \langle \Sigma_{YW}, h \rangle_\mathbb{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt + \sigma_{YW}^\top \mathbf{v}.
-\end{equation*}
-		\jongmin{instead of showing $\mathcal{U}$ is compact, let's show $\mathcal{C}_{YW}$ is compact.
-This way, we don't need uniform continuiity of $\sigma_{YX}$.}If there exist finite constants $Q_1$ and $Q_2$ such that
+		\mathcal{C}_{YW}$ such that for   any $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathbb{H}$,
+		\begin{equation*} \mathcal{C}_{YW} h := \mathbb{E} \left[ \langle W, h \rangle_\mathbb{H} Y \right] = \langle \Sigma_{YW}, h \rangle_\mathbb{H} \in \mathbb{R}.
+		\end{equation*} 
+		\jongmin{instead of showing $\mathcal{U}$ is compact, let's show $\mathcal{C}_{YW}$ is compact. This way, we don't need uniform continuiity of $\sigma_{YX}$.}
+		If 
+		$\sigma_{YX}$ and $\sigma_{YZ}$ are bounded in the sense that
+		there exist finite constants $Q_1$ and $Q_2$ such that
 		\begin{align}\label{condition_for_compact}
-			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
+			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \mathbb{E}
+			[Y X_{k}](t)^2 < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \mathbb{E}
+			[Y Z_{r}]^2 < Q_2,
 		\end{align}
@@
 	\begin{lemma}\label{lemma:cross_cov_operator}
-		Define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathbb{H}$,
-		which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathbb{H}$ as follows:
+		Define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]$,
+		such that for any  $d \in \mathbb{R}$,
 		%%%%
@@
 			\bigl[
-			\langle Y_1, d \rangle W_1 
+			\langle Y, d \rangle W 
 			\bigr] 
@@
 			\mathbb{E}
-			[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
+			[ Y W d ] =  d \, \Sigma_{Y W} \in \mathbb{H}.
 		\end{align*}
@@
 	\end{lemma}	
-
 	The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.
 
-	Based on these two operators, we define a positive   operator as follows:
 	\begin{lemma}[Composite cross-covariance operator]\label{lemma:composite_cross_cov}
@@
 
-	The following theorem introduces the population-level PLS and Tucker's Criterion, adapted to our scalar-on-hybrid regression model setting, based on the aforementioned operators defined in the hybrid space.
+	The following theorem presents population-level PLS and Tucker's Criterion for our scalar-on-hybrid regression model and ensures that line \ref{alg:line:pls_direction} of Algorithm \ref{alg:population_pls} is well-defined under mild conditions.
 	\begin{theorem}[Tucker's criterion]\label{theorem:population_PLS} Under the conditions of Lemma \ref{lemma:cross_cov_functional}, the constrained maximum
 		\begin{equation*} 
-			\max \limits_{\substack{\xi \in \mathbb{H} \\ \Vert \xi \Vert_\mathbb{H}=1}} \operatorname{Cov}^2 \left(\langle W_1 , \, \xi \rangle_\mathbb{H}, Y_1 \right)
+			\max \limits_{\substack{ \Vert \xi \Vert_\mathbb{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathbb{H}, Y \right)
 		\end{equation*} 
@@
 	\end{theorem}
-	Note that the maximizer is a deterministic element of $\mathbb{H}$.
 	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.
 
-Let 
- $\mathcal{U}^{[l]} := \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$,
- where
- $\Sigma_{YW}^{[l]} = E(Y_1^{[l]}  W_1^{[l]})$
- is formulated   using the $l$-th residualized response and predictors.
- Assuming that $\mathcal{U}^{[l]}$
-   satisfies the conditions of Lemma \ref{lemma:cross_cov_functional},
-	the $l$-th PLS direction $\xi^{[l]}$ can be obtained as the \textit{first} eigenfunction of  $\mathcal{U}^{[l]}$.
-
-\jongmin{comment: I added the following properties, motivated by Proposition 4 of \citet{predaPLSRegressionStochastic2005} and section 2 of \citet{aguileraPenalizedVersionsFunctional2016}. }
-
-\begin{lemma} \label{lem:regression_W_rho} The population-level least square regression coefficient of regressing $W_1^{[l]}$ on its score $\rho_1^{[l]} = \langle W_1^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}}$ is $\mathbf{\xi^{[l]}} \in \mathbb{H}$.
-This coefficient is used in the residualization process as follows: \begin{align*} W_1^{[l]} &= W_1^{[l-1]} - \langle W_1^{[l-1]}, \xi^{[l-1]} \rangle_{\mathbb{H}} \xi^{[l-1]},\end{align*} where  $W_1^{[1]} = W_1$.
-\end{lemma}
-Proof of Lemma \ref{lem:regression_W_rho} is provided in Appendix \ref{section:proof:lem:regression_W_rho}.
-
- We define an operator $\mathcal{T}$ that maps an element $g \in \mathbb{H}$   (representing a potential regression coefficient) to the predicted response.
-\begin{lemma}\label{lemma:tau_ast}
-	Define the linear operator $\mathcal{T}: \mathbb{H} \to \mathbb{R}$ that maps  $g \in \mathbb{H}$ to 
-	$
-	\mathcal{T}g = \langle W, g \rangle_{\mathbb{H}}
-	$.
- Let $\mathcal{T}^\ast: \mathbb{R} \to \mathbb{H}$ denote its adjoint operator. Then,
-	\[
-	\Sigma_{YW}^{[1]} = \mathcal{T}^\ast Y.
-	\]
-\end{lemma}
-Proof of Lemma \ref{lemma:tau_ast} is provided in Appendix \ref{section:rpoof:lemma:tau_ast}.
-
-\begin{proposition}\label{proposition:pls_direction_in_range_T_ast}
-	All PLS Directions Reside in $R(\mathcal{T}^\ast  )$
-\end{proposition}
- Proof of Proposition \ref{proposition:pls_direction_in_range_T_ast} is provided in Appendix \ref{section:proof:proposition:pls_direction_in_range_T_ast}
-
-\begin{proposition}
-	\label{proposition:CONS}
-	The set of PLS directions $\{\xi^{[l]}\}_{l=1}^\infty$ forms a complete orthonormal system (CONS) for $R(\mathcal{T}^*)$.
-\end{proposition}
-Proof of Proposition \ref{proposition:CONS}
-is provided in Appendix \ref{section:proof:proposition:CONS}.
-
-\begin{corollary}
-	\label{cor:orthogonal_scores}
-	Given that $\{\xi^{[l]}\}_{l=1}^\infty$ is a complete orthonormal system (CONS) for $R(\mathcal{T}^*)$, the corresponding PLS scores $\rho^{[l]}$ can be equivalently expressed as $\rho^{[l]} = \langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}} = \langle W, \xi^{[l]} \rangle_{\mathbb{H}}$.
-Furthermore, the set of PLS scores $\{\rho^{[l]}\}_{l=1}^\infty$ forms an orthogonal system, that is, for any $j \neq l$, $\mathbb{E}[\rho^{[j]} \rho^{[l]}] = 0$.
-\end{corollary}
-Let $\beta_{\mathrm{OLS}}$ denote a minimizer of  the mean squared error $ \mathbb{E}[\|Y - \langle \beta, W \rangle_{\mathbb{H}}\|_2^2]$. It
-satisfies the normal equation
-\begin{equation}\label{normal_equation}
-	\mathbb{E}[(Y - \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}})W] = 0 \in \mathbb{H}.
-\end{equation}
-If the operator $\mathcal{T}^\ast \mathcal{T}$ is invertible,  the minimizer is uniquely determined as 
-$\beta_{\mathrm{OLS}} = (\mathcal{T}^\ast \mathcal{T})^{-1} \mathcal{T}^\ast Y$.
-\begin{proposition}\label{proposition:nu_l}
-	At the $l$-th iteration, the 
-	population level least square regression coefficient of the residual response $Y^{[l]}$ on the score $\rho^{[l]}$ is defined as:
-	$$\nu^{[l]} = \langle \beta_{\mathrm{OLS}}, \xi^{[l]} \rangle_{\mathbb{H}}.$$
-\end{proposition}
-Proof of Proposition \ref{proposition:nu_l} is provided in Appendix \ref{section:proof:proposition:nu_l}.
-
-The following theorem states that the fitted values from hybrid PLS converge to those of ordinary linear regression in the mean-squared sense.
+	Finally, the following theorem states that the fitted values from hybrid PLS converge to those of ordinary linear regression in the mean-squared sense.
 This shows that hybrid PLS, as a dimension-reduction technique, can effectively capture the predictive power of a full linear model when a sufficient number of components is used.
 	\begin{theorem}[$L^2$ Convergence of Hybrid PLS at Population Level]\label{thm:hybrid_pls_convergence}
-	 Define $Y_{\mathrm{OLS}} = \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}$ as the population-level ordinary linear regression fitted value.
-Let $Y_{\mathrm{PLS}, L} = \sum_{l=1}^L \nu^{[l]} \rho^{[l]}$ be the Hybrid PLS fitted value with $L$ components.
-Then, the Hybrid PLS fitted value converges to the ordinary linear regression fitted value in the mean-squared sense:
-	\begin{equation*}
-		\lim_{L \to \infty} \mathbb{E}\left[ \| Y_{\mathrm{PLS},L } - Y_{\mathrm{OLS}} \|_2^2 \right] = 0
+		Let $Y_{\mathrm{PLS}, L} = \sum_{l=1}^L \nu^{[l]} \rho^{[l]}$ be the Hybrid PLS fitted value with $L$ components. Then, the Hybrid PLS fitted value converges to $Y$ in the mean-squared sense:
+		\begin{equation*}
+			\lim_{L \to \infty} \mathbb{E}\left[ \| Y_{\mathrm{PLS},L } - Y  \|_2^2 \right] = 0
 		\end{equation*}
@@
 	\subsection{Geometric properties}\label{section:sub:geom}
-	A fundamental property of partial least squares   is that between iterations, its derived directions are orthonormal and PLS scores are orthogonal.
+	A fundamental property of partial least squares,
+	as seem in Definition \ref{def:population_pls} and Proposition \ref{prop:residualization_equiv_eigen},
+	is that between iterations, its derived directions are orthonormal and PLS scores are orthogonal.
 Our regularized estimates preserve this property, with respect to a modified inner product that incorporates the roughness penalty, defines as follows:
@@
 		\end{equation*}
+		%%%%%%%%%%%%%%%%
 		Now, we must verify that $\|\Sigma_{YW}\|_\mathbb{H}$ is finite. 
-		Recall that 
-		$$\Sigma_{YW} = (\sigma_{YX,1}(t), \ldots, \sigma_{YX,K}(t), \sigma_{YZ,1}, \ldots, \sigma_{YZ,p}).$$
 		Let $\mu([0,1])$ denote a Lebesgue measure of $[0,1]$, and let $T = \max_{k=1, \ldots, K} \, \mu([0,1])$.
-		The norm of $\Sigma_{YW}$ in $\mathbb{H}$ is given by: \begin{equation*} \|\Sigma_{YW}\|_\mathbb{H}^2 = \sum_{k=1}^K \int_0^1 \sigma_{YX,k}(t)^2 \, dt + \sum_{r=1}^p \sigma_{YZ,r}^2
+		The squared norm of $\Sigma_{YW}$   is given by:
+		\begin{equation*}
+			\|\Sigma_{YW}\|_\mathbb{H}^2 
+			= 
+			\langle \Sigma_{YW}, \Sigma_{YW} \rangle_\mathbb{H}
+			=
+			\sum_{k=1}^K
+			\int_0^1 \mathbb{E} \left[   Y X_k\right](t)^2 \, dt
+			+ \sum_{r=1}^p \mathbb{E} \left[   Y Z_r\right]^2
 			<
@@
 	\begin{proof}
-		For $h \in \mathbb{H}$ and $d \in \mathbb{R}$, we have:
+		For any $h \in \mathbb{H}$ and $d \in \mathbb{R}$, we have:
 		\begin{equation*}
@@
 	\section{Proof of consistency}
-\subsection{
-		Proof of Lemma \ref{lem:regression_W_rho}
-}\label{section:proof:lem:regression_W_rho}
-\begin{proof} We are seeking the population-level regression coefficient, denoted $\gamma \in \mathbb{H}$, for the linear model: $$W_1^{[\ell]} = \gamma \rho_1^{[\ell]} + \text{Error}$$ where $W_1^{[\ell]}$ is the dependent variable (a random element in $\mathbb{H}$), and $\rho_1^{[\ell]} = \langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}}$ is the independent variable (a scalar random variable).
-The optimal regression coefficient $\gamma$ (in the sense of minimizing the mean squared error $E[\|W_1^{[\ell]} - \gamma \rho_1^{[\ell]}\|^2_{\mathbb{H}}]$) is given by the formula:
-	$$\gamma = \frac{E[W_1^{[\ell]} \rho_1^{[\ell]}]}{E[(\rho_1^{[\ell]})^2]}$$ 
-	This formula holds assuming $E[W_1^{[\ell]}] = \mathbf{0}_{\mathbb{H}}$ and $E[\rho_1^{[\ell]}] = 0$, which is true due to the residualization process and the property of zero-mean predictors in the population.
-Let's compute the components of this formula:
- \begin{enumerate} \item \textbf{Denominator:} The denominator is $E[(\rho_1^{[\ell]})^2] = E[(\langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}})^2]$.
-This is the population variance of the score $\rho_1^{[\ell]}$.
-\item \textbf{Numerator:} The numerator is $E[W_1^{[\ell]} \rho_1^{[\ell]}] = E[W_1^{[\ell]} \langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}}]$.
-This is the expectation of the product of a random element $W_1^{[\ell]}$ and a scalar random variable $\langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}}$.
-A fundamental identity in Hilbert spaces states that for any random element $X \in \mathbb{H}$ and any non-random unit vector $u \in \mathbb{H}$ (like $\xi^{[\ell]}$ which has unit norm), if $E[X] = \mathbf{0}_{\mathbb{H}}$, then: $$E[X\langle X,u\rangle_{\mathbb{H}}]=E[\langle X,u\rangle_{\mathbb{H}}^2]u$$ Applying this identity by setting $X=W_1^{[\ell]}$ and $u=\xi^{[\ell]}$: $$E[W_1^{[\ell]}\langle W_1^{[\ell]},\xi^{[\ell]}\rangle_{\mathbb{H}}]=E[(\langle W_1^{[\ell]},\xi^{[\ell]}\rangle_{\mathbb{H}})^2]\xi^{[\ell]}$$ \end{enumerate} Substituting these into the formula for $\gamma$: $$\gamma = \frac{E[(\langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}})^2] \xi^{[\ell]}}{E[(\langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}})^2]}$$ Assuming that $E[(\langle W_1^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}})^2] \neq 0$ (i.e., the score has non-zero variance, implying $\xi^{[\ell]}$ captures some variation), we can cancel the terms, resulting in: $$\gamma = \xi^{[\ell]}$$ This result is intuitively consistent with the orthogonal decomposition of $W_1^{[\ell]}$: $$W_1^{[\ell]}=\langle W_1^{[\ell]},\xi^{[\ell]}\rangle_{\mathbb{H}}\xi^{[\ell]}+(W_1^{[\ell]}-\langle W_1^{[\ell]},\xi^{[\ell]}\rangle_{\mathbb{H}}\xi^{[\ell]})$$ The second term, $(W_1^{[\ell]}-\langle W_1^{[\ell]},\xi^{[\ell]}\rangle_{\mathbb{H}}\xi^{[\ell]})$, is the part of $W_1^{[\ell]}$ that is orthogonal to $\xi^{[\ell]}$ (and thus uncorrelated with $\rho_1^{[\ell]}$).
-When $W_1^{[\ell]}$ is regressed on $\rho_1^{[\ell]}$, the regression model isolates the component of $W_1^{[\ell]}$ that is linearly related to $\rho_1^{[\ell]}$, which is precisely $\langle W_1^{[\ell]},\xi^{[\ell]}\rangle_{\mathbb{H}}\xi^{[\ell]}$.
-The coefficient for $\rho_1^{[\ell]}$ in this linear relationship is simply $\xi^{[\ell]}$.
+
+	\subsection{Proof of Proposition \ref{prop:residualization_equiv_eigen}}\label{section:proof:prop:residualization_equiv_eigen}
+	The proof procedes in the following steps.
+	\begin{enumerate}
+		\item Show that for every \(s\ge 1\) and every \(j\le s-1\), we have $
+		\mathbb{E}[\rho^{[j]}\rho^{[s]}]=0
+		$ for Algorithm \ref{alg:population_pls} (Appendix \ref{section:proof:orthogonal_score_pop}),
+		%%%%
+		\item Show that for every \(s\ge 1\) and every \(j\le s-1\), we have
+		$
+		\mathbb{E}[Y^{[s]}\rho^{[j]}]=0
+		$
+		for Algorithm \ref{alg:population_pls} (Appendix \ref{section:proof:orthogonal_score_residual_pop}),
+		%
+		\item Show the equivalence between Algorithm \ref{alg:population_pls} and optimization problem \eqref{const_eigen_pop} (Appendix \ref{equiv_problem}).
+	\end{enumerate}
+
+	\subsubsection{Orthogonality of the scores in Algorithm \ref{alg:population_pls}}\label{section:proof:orthogonal_score_pop}
+	\begin{proof}
+		Let
+		$
+		\Sigma_{W^{[l]}} := \mathbb{E}[ W^{[l]} \otimes W^{[l]} ]
+		$ as in Definition \ref{def:cross_cov_terms}.
+		Since 
+		$
+		\rho^{[l]} = \langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}},
+		$
+		we can rewrite the numerator and denominator of $\delta^{[l]}$ as
+		\[
+		\mathbb{E}[ \rho^{[l]}  \,  W^{[l]} ] 
+		= 
+		\mathbb{E}[
+		\langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}} W^{[l]} ]
+		= \Sigma_{W^{[l]}} \, \xi^{[l]},
+		\] 
+		and
+		\[
+		\mathbb{E}[ \rho^{[l]}  \,  \rho^{[l]} ] 
+		= 
+		\mathbb{E}[
+		\langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}} \langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}} ]
+		= 
+		\langle \Sigma_{W^{[l]}} \, \xi^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}},
+		\]
+		respectively.
+		Hence, at the population level, the residualization step can be written as
+		\[
+		W^{[l+1]} = W^{[l]} - 
+		\langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}}
+		\frac{ 
+			1
+		}
+		{ \langle \xi^{[l]}, \Sigma_{W^{[l]}} \, \xi^{[l]} \rangle_{\mathbb{H}} }
+		\Sigma_{W^{[l]}} \, \xi^{[l]} .
+		\]
+
+		For $l_1 < l_2$:
+		\[
+		\mathbb{E}[\rho^{[l_1]} \, \rho^{[l_2]}]
+		=
+		\mathbb{E}\big[ \rho^{[l_1]} \,
+		\langle W^{[l_2]}, \xi^{[l_2]} \rangle_{\mathbb{H}} \big]
+		=
+		\mathbb{E}\big[ 
+		\langle \rho^{[l_1]} \, W^{[l_2]}, \xi^{[l_2]} \rangle_{\mathbb{H}} \big]
+		=
+		\langle 
+		\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2]}] \,
+		, \,
+		\xi^{[l_2]} \rangle_{\mathbb{H}}
+		\]
+		Therefore,
+		to show that $\mathbb{E}[\rho^{[l_1]} \, \rho^{[l_2]}]$,
+		it suffices to show $\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2]}] = 0 \in \mathbb{H} $.
+
+		We can express
+		$\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2]}]$ as
+		\begin{align*}
+			\mathbb{E}&\big[ \rho^{[l_1]} \,W^{[l_2]}]
+			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+			\\&=
+			\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2-1]}]
+			-
+			\mathbb{E}[
+			\rho^{[l_1]}
+			\frac{ 
+				\langle W^{[l_2-1]}, \xi^{[l_2-1]} \rangle_{\mathbb{H}}
+			}
+			{ \langle \xi^{[l_2-1]}, \Sigma_{W^{[l_2-1]}} \, \xi^{[l_2-1]} \rangle_{\mathbb{H}} }
+			\Sigma_{W^{[l_2-1]}} \, \xi^{[l_2-1]}
+			]
+			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+			\\&=
+			\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2-1]}]
+			-
+			\mathbb{E}[
+			\rho^{[l_1]}
+			\langle W^{[l_2-1]}, \xi^{[l_2-1]} \rangle_{\mathbb{H}}
+			]
+			\frac{ 
+				1
+			}{ 
+				\langle
+				\xi^{[l_2-1]}, 
+				\Sigma_{W^{[l_2-1]}} \, \xi^{[l_2-1]}
+				\rangle_{\mathbb{H}} }
+			\Sigma_{W^{[l_2-1]}} \, \xi^{[l_2-1]}
+			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+			\\&=
+			\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2-1]}]
+			-
+			\langle 
+			\mathbb{E}[
+			\rho^{[l_1]} W^{[l_2-1]}], \xi^{[l_2-1]} \rangle_{\mathbb{H}}
+			\frac{ 
+				1
+			}{ 
+				\langle
+				\xi^{[l_2-1]}, 
+				\Sigma_{W^{[l_2-1]}} \, \xi^{[l_2-1]}
+				\rangle_{\mathbb{H}} }
+			\Sigma_{W^{[l_2-1]}} \, \xi^{[l_2-1]}
+			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+			\\	&=	H^{[l_2-1]} \bigl( 
+			\mathbb{E}[\rho^{[l_1]  }
+			W^{[l_2-1]}] \bigr)~(\text{say}).
+		\end{align*}
+		Here, the deterministic operator $H^{[l_2-1]}: \mathbb{H} \mapsto \mathbb{H}$ maps the zero element of $\mathbb{H}$ to itself. Using this relationship, we have
+		\begin{align*}
+			\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2]}]  
+			%%%%%%%%%%%%%%%%
+			&=
+			H^{[l_2-1]} \bigl( \mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2-1]}] \bigr)
+			%%%%%%%%%%%%%%%%
+			\\&=
+			H^{[l_2-1]} 
+			\circ 
+			H^{[l_2-2]}
+			\bigl(
+			\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2-2]}]
+			\bigr)
+			%%%%%%%%%%%%%%%%
+			\\&=
+			H^{[l_2-1]} 
+			\circ 
+			H^{[l_2-2]}
+			\circ 
+			\ldots
+			\circ 
+			H^{[l_1]}
+			\bigl( \mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_1]}] \bigr).
+		\end{align*}
+		Therefore,
+		to  show that $\mathbb{E}[\rho^{[l_1]} \, \rho^{[l_2]}]$,
+		it suffices to show $H^{[l_1]}
+		\bigl( \mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_1]}] \bigr) = 0 \in \mathbb{H}$. Note that
+		we have
+		\begin{equation*}
+			\mathbb{E}[\rho^{[l_1]} W^{[l_1]}] = \mathbb{E}[\langle W^{[l_1]}, \xi^{[l_1]} \rangle_{\mathbb{H}} \, W^{[l_1]}] = \Sigma_{W^{[l_1]}} \, \xi^{[l_1]}.
+		\end{equation*}
+		Leveraging this, we have
+		\begin{align*}
+			H^{[l_1]}&
+			\bigl( \mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_1]}] \bigr)
+			\\           &=
+			\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_1]}]
+			-
+			\langle 
+			\mathbb{E}[
+			\rho^{[l_1]} W^{[l_1]}], \xi^{[l_1]} \rangle_{\mathbb{H}}
+			\frac{ 
+				1
+			}{ 
+				\langle
+				\xi^{[l_1]}, 
+				\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
+				\rangle_{\mathbb{H}} }
+			\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
+			\\           &=
+			\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
+			-
+			\langle 
+			\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}, \xi^{[l_1]} \rangle_{\mathbb{H}}
+			\frac{ 
+				1
+			}{ 
+				\langle
+				\xi^{[l_1]}, 
+				\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
+				\rangle_{\mathbb{H}} }
+			\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
+			\\           &=
+			\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
+			-
+			\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
+			=0 \in \mathbb{H}.
+		\end{align*}
+		This completes the proof of
+		orthogonality of the scores in Algorithm \ref{alg:population_pls}.
+
 	\end{proof}
 
-\subsection{Proof of Lemma \ref{lemma:tau_ast} }\label{section:rpoof:lemma:tau_ast}
+	\subsubsection{Orthogonality of the scores and response residuals in Algorithm \ref{alg:population_pls}}\label{section:proof:orthogonal_score_residual_pop}
 	\begin{proof}
-	The adjoint operator  is uniquely defined by the property relating the inner products in $L^2(\Omega)$ and $\mathbb{H}$: $$ \langle \mathcal{T}g, Y \rangle_{L^2(\Omega)} = \langle g, \mathcal{T}^\ast Y \rangle_{\mathbb{H}}, \quad \text{for all } g \in \mathbb{H}, Y \in L^2(\Omega) $$ Here, $\langle \cdot, \cdot \rangle_{L^2(\Omega)}$ denotes the inner product in $L^2(\Omega)$, which is the expectation $E[\cdot]$.
-Let's explicitly derive the expression for $\mathcal{T}^\ast Y$: $$ \langle g, \mathcal{T}^\ast Y \rangle_{\mathbb{H}} = E[\langle W, g \rangle_{\mathbb{H}} Y] $$ By the properties of expectation and the linearity of the inner product (assuming appropriate boundedness and measurability for interchange of expectation and inner product): $$ E[\langle W, g \rangle_{\mathbb{H}} Y] = E[\langle g, W \rangle_{\mathbb{H}} Y] = \langle g, E[YW] \rangle_{\mathbb{H}} $$ Comparing the leftmost and rightmost parts of the definition of the adjoint: $$ \mathcal{T}^\ast Y = E[YW] $$
+		Fix \(s\ge 2\) and \(j\le s-1\). Recall the residualization for the response:
+		\[
+		Y^{[s]} \;=\; Y - \sum_{k=1}^{s-1} \nu^{[k]}\,\rho^{[k]},
+		\qquad
+		\nu^{[k]} \;=\; \frac{\mathbb{E}[Y^{[k]}\rho^{[k]}]}{\mathbb{E}[(\rho^{[k]})^2]}.
+		\]
+		Compute the covariance of interest by expanding the residual:
+		\begin{align*}
+			\mathbb{E}\big[ Y^{[s]}\,\rho^{[j]} \big]
+			= \mathbb{E}\Big[ \Big( Y - \sum_{k=1}^{s-1} \nu^{[k]}\rho^{[k]}\Big)\, \rho^{[j]} \Big] 
+			= \mathbb{E}[Y\,\rho^{[j]}] \;-\; \sum_{k=1}^{s-1} \nu^{[k]}\,\mathbb{E}[\rho^{[k]}\rho^{[j]}].
+		\end{align*}
+
+		By the score orthogonality already established in Appendix \ref{section:proof:orthogonal_score_pop},
+		we have \(\mathbb{E}[\rho^{[k]}\rho^{[j]}]=0\) for every \(k\neq j\). Thus only the \(k=j\) term survives in the sum and we obtain
+		\[
+		\mathbb{E}\big[ Y^{[s]}\,\rho^{[j]} \big]
+		= \mathbb{E}[Y\,\rho^{[j]}] - \nu^{[j]}\,\mathbb{E}[(\rho^{[j]})^2].
+		\]
+
+		It remains to identify \(\mathbb{E}[Y\,\rho^{[j]}]\). Using the definition of the \((j)\)-th residual response,
+		\[
+		Y = Y^{[j]} + \sum_{m=1}^{j-1} \nu^{[m]}\rho^{[m]},
+		\]
+		and again using score orthogonality \(\mathbb{E}[\rho^{[m]}\rho^{[j]}]=0\) for \(m<j\), we find
+		\[
+		\mathbb{E}[Y\,\rho^{[j]}] = \mathbb{E}[Y^{[j]}\,\rho^{[j]}].
+		\]
+		Substitute this into the previous display and use the definition of \(\nu^{[j]}\):
+		\[
+		\mathbb{E}\big[ Y^{[s]}\,\rho^{[j]} \big]
+		= \mathbb{E}[Y^{[j]}\,\rho^{[j]}] - 
+		\frac{\mathbb{E}[Y^{[j]}\rho^{[j]}]}{\mathbb{E}[(\rho^{[j]})^2]}\,\mathbb{E}[(\rho^{[j]})^2]
+		= 0.
+		\]
+		This completes the proof of orthogonality between scores and residualized responses.
 	\end{proof}
 
-\subsection{Proof of}
+	\subsubsection{Equivalence of the problems}\label{equiv_problem}
 	\begin{proof}
-The first PLS direction $\xi^{[1]}$ is the principal eigenfunction of $\mathcal{U}^{[1]} = \Sigma_{YW}^{[1]} \otimes \Sigma_{YW}^{[1]}$.
-Let $\lambda^{[1]}$ be the largest eigenvalue associated with $\xi^{[1]}$.
-By the definition of an eigenfunction: $$ \mathcal{U}^{[1]} \xi^{[1]} = \lambda^{[1]} \xi^{[1]} $$ Substituting the definition of $\mathcal{U}^{[1]}$: $$ (\Sigma_{YW}^{[1]} \otimes \Sigma_{YW}^{[1]}) \xi^{[1]} = \lambda^{[1]} \xi^{[1]} $$ This means: $$ \Sigma_{YW}^{[1]} \langle \Sigma_{YW}^{[1]}, \xi^{[1]} \rangle_{\mathbb{H}} = \lambda^{[1]} \xi^{[1]} $$ If there is any linear correlation between $Y$ and $W$, then $\Sigma_{YW}^{[1]} \neq 0$, which implies $\lambda^{[1]}$ must be non-zero.
-From the equation above, if $\lambda^{[1]} \neq 0$: $$ \xi^{[1]} = \frac{\langle \Sigma_{YW}^{[1]}, \xi^{[1]} \rangle_{\mathbb{H}}}{\lambda^{[1]}} \Sigma_{YW}^{[1]} $$ This equation shows that $\xi^{[1]}$ is a scalar multiple of $\Sigma_{YW}^{[1]}$.
-Since $\Sigma_{YW}^{[1]} \in R(\mathcal{T}^\ast  )$ (as shown in Step 2), and $R(\mathcal{T}^\ast  )$ is a subspace of $\mathbb{H}$ (and thus closed under scalar multiplication), any scalar multiple of $\Sigma_{YW}^{[1]}$ must also be in $R(\mathcal{T}^\ast  )$.
-Therefore, the first PLS direction $\xi^{[1]}$ formally resides in the range of the adjoint operator $R(\mathcal{T}^\ast  )$.
-\end{proof}
-  The first PLS direction $\xi^{[1]}$ is the principal eigenfunction of the operator $\mathcal{U}^{[1]} = \Sigma_{YW}^{[1]} \otimes \Sigma_{YW}^{[1]}$.
-The term $\Sigma_{YW}^{[1]}$ is the population cross-covariance between the (initial, unresidualized) response $Y$ and hybrid predictor $W$: $$ \Sigma_{YW}^{[1]} = E[YW] $$ From our derivation in Step 1, we see that $\Sigma_{YW}^{[1]}$ is precisely equal to $\mathcal{T}^\ast Y$.
-Since $\Sigma_{YW}^{[1]} = \mathcal{T}^\ast Y$, it directly follows that $\Sigma_{YW}^{[1]}$ belongs to the **range of the adjoint operator $R(\mathcal{T}^\ast  )$**.
-By definition, $R(\mathcal{T}^\ast  )$ comprises all elements in $\mathbb{H}$ that can be expressed as $\mathcal{T}^\ast Y$ for some $y \in L^2(\Omega)$.
-
-\subsection{Proof of Proposition \ref{proposition:pls_direction_in_range_T_ast}}\label{section:proof:proposition:pls_direction_in_range_T_ast}
-\begin{proof}
-	The First Eigenfunction $\xi^{[1]}$ Resides in $R(\mathcal{T}^\ast  )$
-  We aim to formally prove that for any $\ell \ge 1$, the $\ell$-th PLS direction $\xi^{[\ell]}$ belongs to the range of the adjoint operator $\mathcal{T}^\ast  $, denoted $R(\mathcal{T}^\ast  )$, at the population level.
-This proof uses mathematical induction.
-\paragraph*{1.
-Recall Definitions and Base Case} \begin{itemize} \item \textbf{Hybrid Hilbert Space ($\mathbb{H}$):} The space where predictors $W$ reside.
-\item \textbf{Response Space ($L^2(\Omega)$):} The space of scalar random variables (responses $Y$) with finite second moments.
-\item \textbf{Operator $\mathcal{T}: \mathbb{H} \rightarrow L^2(\Omega)$:} Defined by $\mathcal{T}g = \langle W, g \rangle_{\mathbb{H}}$.
-This maps a potential regression coefficient $g$ to a predicted response.
-\item \textbf{Adjoint Operator $\mathcal{T}^\ast  : L^2(\Omega) \rightarrow \mathbb{H}$:} Uniquely defined by $\langle \mathcal{T}g, Y \rangle_{L^2(\Omega)} = \langle g, \mathcal{T}^\ast Y \rangle_{\mathbb{H}}$.
-As derived, $\mathcal{T}^\ast Y = E[YW]$.
-The range $R(\mathcal{T}^\ast  )$ is the subspace of $\mathbb{H}$ containing all elements that are linearly correlated with $Y$.
-\item \textbf{$\ell$-th PLS Direction ($\xi^{[\ell]}$):} The principal eigenfunction of $\mathcal{U}^{[\ell]} = \Sigma_{YW}^{[\ell]} \otimes \Sigma_{YW}^{[\ell]}$, where $\Sigma_{YW}^{[\ell]} = E[Y^{[\ell]} W^{[\ell]}]$.
-\end{itemize} \paragraph{Base Case ($\ell=1$):} For the first PLS direction, $\xi^{[1]}$, we consider $\Sigma_{YW}^{[1]} = E[YW]$.
-From the definition of the adjoint operator $\mathcal{T}^\ast  $, we have $\mathcal{T}^\ast Y = E[YW]$.
-Therefore, $\Sigma_{YW}^{[1]} = \mathcal{T}^\ast Y$.
-This explicitly shows that $\Sigma_{YW}^{[1]} \in R(\mathcal{T}^\ast  )$.
-Since $\xi^{[1]}$ is the principal eigenfunction of $\mathcal{U}^{[1]} = \Sigma_{YW}^{[1]} \otimes \Sigma_{YW}^{[1]}$, it satisfies $\mathcal{U}^{[1]} \xi^{[1]} = \lambda^{[1]} \xi^{[1]}$.
-This implies $\Sigma_{YW}^{[1]} \langle \Sigma_{YW}^{[1]}, \xi^{[1]} \rangle_{\mathbb{H}} = \lambda^{[1]} \xi^{[1]}$.
-If $\Sigma_{YW}^{[1]} \neq 0$ (meaning there's linear correlation between $Y$ and $W$), then $\lambda^{[1]} \neq 0$, and $\xi^{[1]}$ must be a scalar multiple of $\Sigma_{YW}^{[1]}$: $$ \xi^{[1]} = \frac{\langle \Sigma_{YW}^{[1]}, \xi^{[1]} \rangle_{\mathbb{H}}}{\lambda^{[1]}} \Sigma_{YW}^{[1]} $$ Since $\Sigma_{YW}^{[1]} \in R(\mathcal{T}^\ast  )$ and $R(\mathcal{T}^\ast  )$ is a subspace (closed under scalar multiplication), it directly follows that $\xi^{[1]} \in R(\mathcal{T}^\ast  )$.
-The base case is proven.
-\paragraph*{2.
-Inductive Step: Assume $\xi^{[1]}, \ldots, \xi^{[\ell-1]} \in R(\mathcal{T}^\ast  )$} Assume that the first $\ell-1$ PLS directions, $\xi^{[1]}, \ldots, \xi^{[\ell-1]}$, all reside in $R(\mathcal{T}^\ast  )$.
-We need to prove that $\xi^{[\ell]}$ also resides in $R(\mathcal{T}^\ast  )$.
-The $\ell$-th PLS direction $\xi^{[\ell]}$ is a scalar multiple of $\Sigma_{YW}^{[\ell]} = E[Y^{[\ell]} W^{[\ell]}]$.
-Thus, to prove $\xi^{[\ell]} \in R(\mathcal{T}^\ast  )$, it suffices to prove that $\Sigma_{YW}^{[\ell]} \in R(\mathcal{T}^\ast  )$.
-Recall the residualization process at the population level: $$W^{[\ell]} = W^{[\ell-1]} - \langle W^{[\ell-1]}, \xi^{[\ell-1]} \rangle_{\mathbb{H}} \xi^{[\ell-1]}$$ $$Y^{[\ell]} = Y^{[\ell-1]} - \nu^{[\ell-1]} \rho^{[\ell-1]}$$ where $\rho^{[\ell-1]} = \langle W^{[\ell-1]}, \xi^{[\ell-1]} \rangle_{\mathbb{H}}$.
-By iterating this process, we can express $W^{[\ell]}$ and $Y^{[\ell]}$ in terms of the original $W$, $Y$, and the previously extracted PLS components: $$W^{[\ell]} = W - \sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \xi^{[j]}$$ $$Y^{[\ell]} = Y - \sum_{j=1}^{\ell-1} \nu^{[j]} \rho^{[j]}$$ From the inductive hypothesis and the base case, all $\xi^{[j]} \in R(\mathcal{T}^\ast  )$ for $j=1, \ldots, \ell-1$.
-Since $R(\mathcal{T}^\ast  )$ is a subspace, any linear combination of these $\xi^{[j]}$ also belongs to $R(\mathcal{T}^\ast  )$.
-Thus, the sum $\sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \xi^{[j]}$ is an element of $R(\mathcal{T}^\ast  )$.
-Now, we need to show that $\Sigma_{YW}^{[\ell]} = E[Y^{[\ell]} W^{[\ell]}]$ resides in $R(\mathcal{T}^\ast  )$.
-To do this, we demonstrate that for any $v \in R(\mathcal{T}^\ast  )^\perp$ (the orthogonal complement of $R(\mathcal{T}^\ast  )$ in $\mathbb{H}$), $\langle \Sigma_{YW}^{[\ell]}, v \rangle_{\mathbb{H}} = 0$.
-By definition, $R(\mathcal{T}^\ast  )^\perp = \{v \in \mathbb{H} \mid E[\langle W, v \rangle_{\mathbb{H}} Y] = 0\}$.
-Consider $E[\langle W^{[\ell]}, v \rangle_{\mathbb{H}} Y^{[\ell]}]$ for any $v \in R(\mathcal{T}^\ast  )^\perp$: $$E[\langle W^{[\ell]}, v \rangle_{\mathbb{H}} Y^{[\ell]}] = E\left[ \left\langle W - \sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \xi^{[j]}, v \right\rangle_{\mathbb{H}} \left( Y - \sum_{k=1}^{\ell-1} \nu^{[k]} \rho^{[k]} \right) \right]$$ Due to the orthogonality of $v$ to all $\xi^{[j]}$ (since $v \in R(\mathcal{T}^\ast  )^\perp$ and $\xi^{[j]} \in R(\mathcal{T}^\ast  )$): $$ \left\langle W - \sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \xi^{[j]}, v \right\rangle_{\mathbb{H}} = \langle W, v \rangle_{\mathbb{H}} - \sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \langle \xi^{[j]}, v \rangle_{\mathbb{H}} = \langle W, v \rangle_{\mathbb{H}} - 0 = \langle W, v \rangle_{\mathbb{H}} $$ Thus, the expression simplifies to: $$ E[\langle W^{[\ell]}, v \rangle_{\mathbb{H}} Y^{[\ell]}] = E\left[ \langle W, v \rangle_{\mathbb{H}} \left( Y - \sum_{k=1}^{\ell-1} \nu^{[k]} \rho^{[k]} \right) \right] $$ $$ = E[\langle W, v \rangle_{\mathbb{H}} Y] - \sum_{k=1}^{\ell-1} \nu^{[k]} E[\langle W, v \rangle_{\mathbb{H}} \rho^{[k]}] $$ The first term $E[\langle W, v \rangle_{\mathbb{H}} Y] = 0$ because $v \in R(\mathcal{T}^\ast  )^\perp$.
-For the second term, $E[\langle W, v \rangle_{\mathbb{H}} \rho^{[k]}] = E[\langle W, v \rangle_{\mathbb{H}} \langle W, \xi^{[k]} \rangle_{\mathbb{H}}]$.
-Since $v \in R(\mathcal{T}^\ast  )^\perp$ and $\xi^{[k]} \in R(\mathcal{T}^\ast  )$, and $E[\langle U, X \rangle \langle V, X \rangle]$ represents the covariance between inner products, and components in $R(\mathcal{T}^\ast  )$ and $R(\mathcal{T}^\ast  )^\perp$ are uncorrelated: $E[\langle W, v \rangle_{\mathbb{H}} \langle W, \xi^{[k]} \rangle_{\mathbb{H}}] = \text{Cov}(\langle W, v \rangle_{\mathbb{H}}, \langle W, \xi^{[k]} \rangle_{\mathbb{H}}) + E[\langle W, v \rangle_{\mathbb{H}}]E[\langle W, \xi^{[k]} \rangle_{\mathbb{H}}]$.
-Assuming zero-mean predictors ($E[W]=0$), the second term is zero.
-The covariance $\text{Cov}(\langle W, v \rangle_{\mathbb{H}}, \langle W, \xi^{[k]} \rangle_{\mathbb{H}})$ is also zero since $v$ and $\xi^{[k]}$ are in orthogonal subspaces.
-Therefore, $E[\langle W^{[\ell]}, v \rangle_{\mathbb{H}} Y^{[\ell]}] = 0$ for all $v \in R(\mathcal{T}^\ast  )^\perp$.
-This implies that $\Sigma_{YW}^{[\ell]} = E[Y^{[\ell]} W^{[\ell]}]$ is orthogonal to $R(\mathcal{T}^\ast  )^\perp$.
-By the property of orthogonal decomposition in Hilbert spaces ($R(\mathcal{T}^\ast  ) \oplus R(\mathcal{T}^\ast  )^\perp = \mathbb{H}$), if an element is orthogonal to the orthogonal complement of a closed subspace, it must belong to that subspace.
-Thus, $\Sigma_{YW}^{[\ell]}$ must reside in $R(\mathcal{T}^\ast  )$.
-Since $\xi^{[\ell]}$ is a scalar multiple of $\Sigma_{YW}^{[\ell]}$, we conclude that $\xi^{[\ell]} \in R(\mathcal{T}^\ast  )$.
-By mathematical induction, since the base case holds and the inductive step is proven, all PLS directions $\{\xi^{[\ell]}\}_{\ell=1}^\infty$ reside in $R(\mathcal{T}^\ast  )$.
-\end{proof}
-
-\subsection{Proof of Proposition \ref{proposition:CONS}}\label{section:proof:proposition:CONS}
-
-\paragraph{1.1 Orthonormality through Residualization} The iterative nature of the PLS algorithm guarantees the orthonormality of the directions.
-The \textbf{residualization (or orthogonalization)} step is crucial.
-After the $(l-1)$-th PLS direction $\xi^{[l-1]}$ is determined, the predictors and response are adjusted to remove the linear effect of this component.
-Specifically, at the population level: $$W^{[l]} = W^{[l-1]} - \langle W^{[l-1]}, \xi^{[l-1]} \rangle_{\mathbb{H}} \xi^{[l-1]}$$ $$Y^{[l]} = Y^{[l-1]} - \nu^{[l-1]} \rho^{[l-1]}$$ where $W^{[1]} = W$ and $Y^{[1]} = Y$.
-This procedure ensures that the residualized predictors $W^{[l]}$ are orthogonal to all previous directions $\xi^{[j]}$ for $j < l$.
-Consequently, the newly found direction $\xi^{[l]}$, being derived from $W^{[l]}$, will be orthogonal to $\{\xi^{[1]}, \ldots, \xi^{[l-1]}\}$.
-By convention, PLS directions are normalized to have unit norm ($\Vert \xi^{[l]} \Vert_{\mathbb{H}} = 1$).
-Thus, the set $\{\xi^{[l]}\}_{l=1}^\infty$ is an orthonormal set.
-\paragraph{1.2 Completeness} The relevant predictor subspace is precisely the \textbf{range of the adjoint operator $\mathcal{T}^\ast  $}, denoted $R(\mathcal{T}^\ast  )$.
-To show that $\{\xi^{[l]}\}_{l=1}^\infty$ forms a CONS for $R(\mathcal{T}^\ast  )$, given their orthonormality, we must prove completeness.
-According to Theorem 2.4.12, this requires demonstrating that if an element $v \in R(\mathcal{T}^\ast  )$ is orthogonal to all PLS directions $\{\xi^{[l]}\}_{l=1}^\infty$, then $v$ must be the zero vector.
-Let $\mathcal{S} = \text{span}\{\xi^{[l]}\}_{l=1}^\infty$ be the subspace spanned by the PLS directions.
-Assume, for contradiction, that there exists a non-zero $v \in R(\mathcal{T}^\ast  )$ such that $v \perp \mathcal{S}$.
-This means $\langle v, \xi^{[l]} \rangle_{\mathbb{H}} = 0$ for all $l=1,2,\ldots$.
-Since $v \in R(\mathcal{T}^\ast  )$ and $v \neq 0$, it implies that $v$ contains non-zero linear predictive information regarding $Y$.
-Formally, $R(\mathcal{T}^\ast  )$ is the space of elements in $\mathbb{H}$ that are correlated with $Y$, so $E[\langle W, v \rangle_{\mathbb{H}} Y] \neq 0$.
-Now, consider the implications of $v \perp \mathcal{S}$ on the iterative PLS algorithm.
-At any step $\ell$, the residualized predictor $W^{[\ell]}$ is constructed such that its components orthogonal to $\{\xi^{[1]}, \ldots, \xi^{[\ell-1]}\}$ remain.
-Since $v$ is assumed orthogonal to all $\xi^{[j]}$, the projection of $W$ onto $v$ (i.e., $\langle W, v \rangle_{\mathbb{H}}$) is not removed by any residualization step.
-Similarly, $Y^{[\ell]}$ is the residual response.
-The cross-covariance relevant at step $\ell$ is $\Sigma_{YW}^{[\ell]} = E[Y^{[\ell]} W^{[\ell]}]$.
-If $v \in R(\mathcal{T}^\ast  )$ and $v \neq 0$, it implies that $E[\langle W, v \rangle_{\mathbb{H}} Y] \neq 0$.
-Let's examine the inner product of $\Sigma_{YW}^{[\ell]}$ with $v$: $\langle \Sigma_{YW}^{[\ell]}, v \rangle_{\mathbb{H}} = \langle E[Y^{[\ell]} W^{[\ell]}] , v \rangle_{\mathbb{H}} = E[Y^{[\ell]} \langle W^{[\ell]}, v \rangle_{\mathbb{H}}]$.
-Since $v \perp \xi^{[j]}$ for all $j$, the residualization process on $W$ does not affect $\langle W, v \rangle_{\mathbb{H}}$: $\langle W^{[\ell]}, v \rangle_{\mathbb{H}} = \langle W - \sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \xi^{[j]}, v \rangle_{\mathbb{H}} = \langle W, v \rangle_{\mathbb{H}} - \sum_{j=1}^{\ell-1} \langle W, \xi^{[j]} \rangle_{\mathbb{H}} \langle \xi^{[j]}, v \rangle_{\mathbb{H}} = \langle W, v \rangle_{\mathbb{H}} - 0 = \langle W, v \rangle_{\mathbb{H}}$.
-So, $\langle \Sigma_{YW}^{[\ell]}, v \rangle_{\mathbb{H}} = E[Y^{[\ell]} \langle W, v \rangle_{\mathbb{H}}]$.
-By the construction of PLS, the sequence $Y^{[\ell]}$ is generated such that $Y^{[\ell]} = Y - \sum_{j=1}^{\ell-1} \nu^{[j]} \rho^{[j]}$.
-Substituting this: $\langle \Sigma_{YW}^{[\ell]}, v \rangle_{\mathbb{H}} = E\left[ \left( Y - \sum_{j=1}^{\ell-1} \nu^{[j]} \rho^{[j]} \right) \langle W, v \rangle_{\mathbb{H}} \right]$ $= E[Y \langle W, v \rangle_{\mathbb{H}}] - \sum_{j=1}^{\ell-1} \nu^{[j]} E[\rho^{[j]} \langle W, v \rangle_{\mathbb{H}}]$ The first term, $E[Y \langle W, v \rangle_{\mathbb{H}}]$, is non-zero because $v \in R(\mathcal{T}^\ast  )$ and $v \neq 0$.
-The second term, $\sum_{j=1}^{\ell-1} \nu^{[j]} E[\rho^{[j]} \langle W, v \rangle_{\mathbb{H}}]$, simplifies.
-Recall $\rho^{[j]} = \langle W, \xi^{[j]} \rangle_{\mathbb{H}}$.
-So $E[\rho^{[j]} \langle W, v \rangle_{\mathbb{H}}] = E[\langle W, \xi^{[j]} \rangle_{\mathbb{H}} \langle W, v \rangle_{\mathbb{H}}]$.
-This represents the covariance between the component of $W$ in direction $\xi^{[j]}$ and the component of $W$ in direction $v$.
-Since $\xi^{[j]} \in R(\mathcal{T}^\ast  )$ and $v \perp R(\mathcal{T}^\ast  )$, these components are uncorrelated (assuming zero-mean $W$).
-Thus, $E[\rho^{[j]} \langle W, v \rangle_{\mathbb{H}}] = 0$.
-Therefore, $\langle \Sigma_{YW}^{[\ell]}, v \rangle_{\mathbb{H}} = E[Y \langle W, v \rangle_{\mathbb{H}}] \neq 0$ for all $\ell$.
-This implies that $\Sigma_{YW}^{[\ell]}$ is never the zero vector (or operator) as long as $v \neq 0$.
-The PLS algorithm, at each step $\ell$, extracts $\xi^{[\ell]}$ as the principal eigenfunction of $\mathcal{U}^{[\ell]}$.
-If $\Sigma_{YW}^{[\ell]}$ is non-zero, then $\mathcal{U}^{[\ell]}$ has a non-zero largest eigenvalue $\lambda^{[\ell]}$, and $\xi^{[\ell]} = (\langle \Sigma_{YW}^{[\ell]}, \xi^{[\ell]} \rangle_{\mathbb{H}} / \lambda^{[\ell]}) \Sigma_{YW}^{[\ell]}$.
-This means $\xi^{[\ell]}$ is directly related to $\Sigma_{YW}^{[\ell]}$.
-Since $\Sigma_{YW}^{[\ell]}$ has a non-zero component orthogonal to all previously extracted $\xi^{[j]}$ (namely, the component in direction $v$), the algorithm *must* continue to extract components that capture this remaining predictive information.
-This contradicts the assumption that $v$ is orthogonal to *all* $\xi^{[\ell]}$, as the algorithm would continue to extract components along the direction of $v$ or its correlates.
-The process of PLS is designed to exhaust all such linearly predictive information in $R(\mathcal{T}^\ast  )$.
-Therefore, the initial assumption that a non-zero $v \in R(\mathcal{T}^\ast  )$ exists orthogonal to all $\xi^{[\ell]}$ leads to a contradiction.
-Thus, if $v \in R(\mathcal{T}^\ast  )$ and $v \perp \mathcal{S}$, it must imply $v=0$.
-This establishes that $\mathcal{S}$ is complete in $R(\mathcal{T}^\ast  )$.
-Combining orthonormality and completeness, $\{\xi^{[l]}\}_{l=1}^\infty$ forms a CONS for $R(\mathcal{T}^\ast  )$.
-
-		\subsection{Proof of Proposition \ref{proposition:nu_l}}\label{section:proof:proposition:nu_l}
-
-\begin{proof}Since population level least square regression coefficient is precisely
-	\begin{equation*}
-		\nu^{[l]} = \frac{\mathbb{E}[Y^{[l]} \rho^{[l]}]}{\mathbb{E}[(\rho^{[l]})^2]},
-	\end{equation*}
-	it suffices to show that
-	\begin{equation*}
-		\mathbb{E}[Y^{[l]} \rho^{[l]}]
-		= 
-		\langle \beta_{\mathrm{OLS}}, \xi^{[\ell]} \rangle_{\mathbb{H}} \mathbb{E}[(\rho^{[\ell]})^2].
-	\end{equation*} 
-	We proceed in two intermediate steps:
-	\begin{enumerate}
-		\item Showing  
-		$
-		\beta_{\mathrm{OLS}} = (\mathcal{T}^\ast \mathcal{T})^{-1} \mathcal{T}^\ast Y \in R(\mathcal{T}^\ast)$,
-		%
-		\item Expanding and transforming $E[Y^{[l]} \rho^{[l]}]  $.
-	\end{enumerate}
-
-	\medskip
-	\noindent
-	\textit{1. Showing  
-		$
-		\beta_{\mathrm{OLS}} = (\mathcal{T}^\ast \mathcal{T})^{-1} \mathcal{T}^\ast Y \in R(\mathcal{T}^\ast)$.}~
-	The term $\mathcal{T}^\ast Y$ is, by definition, an element of $R(\mathcal{T}^\ast  )$.
-	Next, let us consider The operator $\mathcal{T}^\ast   \mathcal{T}: \mathbb{H} \mapsto \mathbb{H}$ is a self-adjoint, positive semi-definite operator.
-The inverse operator $(\mathcal{T}^\ast   \mathcal{T})^{-1}$ exists and is well-defined when $\mathcal{T}^\ast   \mathcal{T}$ is invertible.
-	Now, since $R(\mathcal{T}^\ast   \mathcal{T}) = R(\mathcal{T}^\ast  )$,
-	the operator $\mathcal{T}^\ast   \mathcal{T}$ maps elements from $\mathbb{H}$ specifically into the subspace $R(\mathcal{T}^\ast  )$.
-	Consequently, when the inverse operator $(\mathcal{T}^\ast   \mathcal{T})^{-1}$ is applied to an element that is already within $R(\mathcal{T}^\ast  )$ (such as $\mathcal{T}^\ast   Y$), the result will also remain within this same subspace $R(\mathcal{T}^\ast  )$.
-	Therefore, the entire expression $(\mathcal{T}^\ast   \mathcal{T})^{-1} \mathcal{T}^\ast   Y$ must   reside in $R(\mathcal{T}^\ast  )$.
-
-	\medskip
-	\noindent
-	\textit{2. Expanding and transforming $E[Y^{[l]} \rho^{[l]}]$.
-	}
-	We can expand $\mathbb{E}[Y^{[l]} \rho^{[l]}] $ as:
-	\begin{equation*}
-		\mathbb{E}[Y^{[l]} \rho^{[l]}] 
-		\overset{(i)}{=} 
-		E
-		\bigl[ \bigl\{ ( Y - \sum_{j=1}^{\ell-1} \nu^{[j]} \rho^{[j]} \bigr\} \rho^{[l]} 
-		\bigr]
-		= \mathbb{E}[Y \rho^{[l]}] - \sum_{j=1}^{\ell-1} \nu^{[j]} \mathbb{E}[\rho^{[j]} \rho^{[l]}]
-		\overset{(ii)}{=}
-		\mathbb{E}[Y \rho^{[l]}],
-	\end{equation*}
+		Recall the residualization definitions (for fixed \(l\ge 2\)):
+		\[
+		W^{[l]} \;=\; W - \sum_{j=1}^{\,l-1} \rho^{[j]}\,\delta^{[j]},
+		\qquad
+		Y^{[l]} \;=\; Y - \sum_{k=1}^{\,l-1} \nu^{[k]}\,\rho^{[k]},
+		\]
 		where
-	step $(i)$ repeatedly uses the residualization process for the response and
-	step $(ii)$ uses the orthogonality of the PLS scores presented in 
-	Corollary \ref{cor:orthogonal_scores}. 
-	We further expand:
-	\begin{align*}
-		\mathbb{E}[Y^{[l]} \rho^{[l]}] 
-		=
-		\mathbb{E}[Y \rho^{[l]}]
-		=
-		\mathbb{E}[Y  \langle W, \, \xi^{[l]} \rangle_{\mathbb{H}} ]
-		=
-		\langle \mathbb{E}[ Y W ], \, \xi^{[l]} \rangle_{\mathbb{H}} 
-		%%%%%%%%%%%%%%
-		&\overset{(i)}{=}
-		\langle 
-		\mathbb{E}[W \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}], \, \xi^{[l]} \rangle_{\mathbb{H}} 
-		\\&=
-		\mathbb{E}[\langle W, \xi^{[\ell]} \rangle_{\mathbb{H}} \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}].
-	\end{align*}		
-	where step $(i)$ uses the normal equation $	\mathbb{E}[(Y - \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}})W] = 0$ presented in  \eqref{normal_equation}.
-
-	Since $\beta_{\mathrm{OLS}} \in R(\mathcal{T}^*)$ and 		$\{\xi^{[k]}\}_{k=1}^\infty$ is a  CONS for $R(\mathcal{T}^\ast)$ by Proposition \ref{proposition:CONS}, we can further expand:
-	\begin{align*}
-		\mathbb{E}[Y^{[l]} \rho^{[l]}] 
-		=
-		\mathbb{E}[\langle W, \xi^{[\ell]} \rangle_{\mathbb{H}} \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}]
-		&=
-		\mathbb{E}[\langle W, \xi^{[\ell]} \rangle_{\mathbb{H}} \langle \sum_{k=1}^{\infty} \langle \beta_{\mathrm{OLS}}, \xi^{[k]} \rangle_{\mathbb{H}} \xi^{[k]}, W \rangle_{\mathbb{H}}]
-		\\&=
-		%%%%%%%%%%%%%%%%%5
-		\mathbb{E}
-		\bigl[ \rho^{[\ell]} \sum_{k=1}^{\infty} \langle \beta_{\mathrm{OLS}}, \xi^{[k]} \rangle_{\mathbb{H}} \rho^{[k]} \bigr]
-		\\& = \langle \beta_{\mathrm{OLS}}, \xi^{[\ell]} \rangle_{\mathbb{H}} \mathbb{E}[(\rho^{[\ell]})^2],
-	\end{align*}
-	where the last step 
-	uses the orthogonality of scores presented in Corollary \ref{cor:orthogonal_scores}.
-	This completes the proof of Proof of Proposition \ref{proposition:nu_l}.
+		\[
+		\rho^{[j]}=\langle W^{[j]},\xi^{[j]}\rangle,\quad
+		\delta^{[j]}=\frac{\mathbb{E}[\rho^{[j]} W^{[j]}]}{\mathbb{E}[(\rho^{[j]})^2]},
+		\quad
+		\nu^{[j]}=\frac{\mathbb{E}[\rho^{[j]} Y^{[j]}]}{\mathbb{E}[(\rho^{[j]})^2]}.
+		\]
+		Since \(W,Y\) are centered, 
+		so are $W^{l}, Y^{l}$.
+		Thus covariances are expectations of products.
+		Fix any \(w\in\mathbb{H}\).  Using linearity,
+		\begin{align*}
+			\operatorname{Cov}\!\big(\langle W^{[l]},w\rangle,\;Y^{[l]}\big)
+			&= \mathbb{E}\Big[\big(\langle W,w\rangle - \sum_{j=1}^{l-1} \rho^{[j]}\langle\delta^{[j]},w\rangle\big)
+			\big(Y - \sum_{k=1}^{l-1} \nu^{[k]}\rho^{[k]}\big)\Big] \\
+			\\&= \mathbb{E}[\langle W,w\rangle Y] 
+			- \sum_{k=1}^{l-1} \nu^{[k]}\,\mathbb{E}[\langle W,w\rangle \rho^{[k]}]
+			- \underbrace{
+				\sum_{j=1}^{l-1} \langle\delta^{[j]},w\rangle\,\mathbb{E}[\rho^{[j]} Y]}_{:=S_1} \\
+			&\qquad
+			\underbrace{
+				+ 
+				\sum_{j=1}^{l-1}\sum_{k=1}^{l-1} \langle\delta^{[j]},w\rangle\,\nu^{[k]}\,\mathbb{E}[\rho^{[j]}\rho^{[k]}]
+			}_{:=S_2}.
+		\end{align*}
+		We claim that $S_1  = S_2$.
+		For $S_1$, first note that, since
+		\(Y = Y^{[l]} + \sum_{k=1}^{l-1}\nu^{[k]}\rho^{[k]}\), for each \(j\le l-1\) we have
+		\[
+		\mathbb{E}[\rho^{[j]} Y] = \mathbb{E}[\rho^{[j]} Y^{[l]}] + \sum_{k=1}^{l-1} \nu^{[k]}\mathbb{E}[\rho^{[j]}\rho^{[k]}]=
+		\nu^{[j]}\,\mathbb{E}[(\rho^{[j]})^2],
+		\]
+		where the last equality uses 
+		\(\mathbb{E}[\rho^{[j]} Y^{[l]}]=0\) (Appendix \ref{section:proof:orthogonal_score_residual_pop}) and
+		\(\mathbb{E}[\rho^{[j]}\rho^{[k]}]=0\) for \(j\ne k\) (Appendix \ref{section:proof:orthogonal_score_pop}).
+		Therefore we have
+		\[
+		S_1 = \sum_{j=1}^{l-1} \langle\delta^{[j]},w\rangle \nu^{[j]}\,\mathbb{E}[(\rho^{[j]})^2].
+		\]
+		For $S_2$, 
+		since  \(\mathbb{E}[\rho^{[j]}\rho^{[k]}]=0\) for \(j\ne k\) (Appendix \ref{section:proof:orthogonal_score_pop}), we have:
+		\begin{equation*}
+			S_2
+			=
+			\sum_{j=1}^{l-1}\sum_{k=1}^{l-1} \langle\delta^{[j]},w\rangle\,\nu^{[k]}\,\mathbb{E}[\rho^{[j]}\rho^{[k]}]
+			= \sum_{j=1}^{l-1} \langle\delta^{[j]},w\rangle\,\nu^{[j]}\,\mathbb{E}[(\rho^{[j]})^2].   
+		\end{equation*}
+		Since $S_1 = S_2$, 
+		and
+		\(\mathbb{E}[\langle W,w\rangle Y]=\operatorname{Cov}(\langle W,w\rangle,Y)\), we have
+		\[
+		\operatorname{Cov}\big(\langle W^{[l]},w\rangle,\;Y^{[l]}\big)
+		= \operatorname{Cov}(\langle W,w\rangle,Y)
+		- \sum_{k=1}^{l-1} \nu^{[k]}\,\operatorname{Cov}(\langle W,w\rangle,\rho^{[k]}).
+		\]
+		Therefore we are solving
+		\begin{align*}
+			\max_{\|w\|_{\mathbb{H}}=1}~&
+			\Big\{ 
+			\operatorname{Cov}(\langle W,w\rangle,Y)
+			- \sum_{k=1}^{l-1} \nu^{[k]}\,\operatorname{Cov}(\langle W,w\rangle,\rho^{[k]})
+			\Big\}^2
+			\\
+			s.t.~&
+			\nu^{[k]}
+			=
+			\frac{1}{\mathbb{E}[ (\rho^{[k]})^2 ]}
+			\mathbb{E}[Y^{[l]} \rho^{[k]}],~k=1, \ldots, l-1
+			\\~&
+			\rho^{[k]} = \langle \xi^{[k]}, W^{[k]} \rangle,~k=1, \ldots, l-1 
+			\\~&
+			\delta^{[k]}
+			=
+			\frac{1}{\mathbb{E}[ (\rho^{[k]})^2 ]}  \mathbb{E}[W^{[k]} \rho^{[k]}],~k=1, \ldots, l-1
+			\\~&
+			W^{[k+1]} = W^{[k]} - \rho^{[k]} \, \delta^{[k]},~k=1, \ldots, l-1
+			\\~&
+			Y^{[k]} =Y^{[k-1]} - \nu^{[k-1]} \, \rho^{[k-1]},~k=1, \ldots, l-1
+		\end{align*}
+		Since the constraints imply 
+		that for every \(s\ge 1\) and every \(j\le s-1\), we have $
+		\mathbb{E}[\rho^{[j]}\rho^{[s]}]=\langle w, \Sigma_W \, \xi^{[k]} \rangle_{\mathbb{H}} = \operatorname{Cov}(\langle W,w\rangle,\rho^{[k]}) =0
+		$ (Appendix \ref{section:proof:orthogonal_score_pop}),
+		the above problem is equivalent to 
+		\begin{align*}
+			\max_{\|w\|_{\mathbb{H}}=1}~&
+			\Big\{ 
+			\operatorname{Cov}(\langle W,w\rangle,Y)
+			\Big\}^2
+			\\
+			s.t.~&
+			\nu^{[k]}
+			=
+			\frac{1}{\mathbb{E}[ (\rho^{[k]})^2 ]}
+			\mathbb{E}[Y^{[l]} \rho^{[k]}],~k=1, \ldots, l-1
+			\\~&
+			\rho^{[k]} = \langle \xi^{[k]}, W^{[k]} \rangle,~k=1, \ldots, l-1 
+			\\~&
+			\delta^{[k]}
+			=
+			\frac{1}{\mathbb{E}[ (\rho^{[k]})^2 ]}  \mathbb{E}[W^{[k]} \rho^{[k]}],~k=1, \ldots, l-1
+			\\~&
+			W^{[k+1]} = W^{[k]} - \rho^{[k]} \, \delta^{[k]},~k=1, \ldots, l-1
+			\\~&
+			Y^{[k]} =Y^{[k-1]} - \nu^{[k-1]} \, \rho^{[k-1]},~k=1, \ldots, l-1
+			\\~& \langle w, \Sigma_W \, \xi^{[k]} \rangle_{\mathbb{H}}=0,~k=1, \ldots, l-1.
+		\end{align*}
+		Removing constraints that does not affect the objective function, the above optimization problem is equivalent to
+		\begin{align*}
+			\max_{\|w\|_{\mathbb{H}}=1}~&
+			\Big\{ 
+			\operatorname{Cov}(\langle W,w\rangle,Y)
+			\Big\}^2
+			\\
+			s.t.~&
+			\langle w, \Sigma_W \, \xi^{[k]} \rangle_{\mathbb{H}}=0,~k=1, \ldots, l-1.
+		\end{align*}
+		This completes
+		the proof of Proposition \ref{prop:residualization_equiv_eigen}.
 	\end{proof}
@@
 	\begin{proof}
-By Proposition \ref{proposition:CONS},
-	 $\{\xi^{[l]}\}_{l=1}^\infty$ is a CONS for $R(\mathcal{T}^\ast  )$.
-	 By Appendix \ref{section:proof:proposition:nu_l}, 
-	 we have
-	 $\beta_{\mathrm{OLS}}   \in R(\mathcal{T}^\ast)$.
-Therefore, we can expand $Y_{\mathrm{OLS}}$ as:
-\begin{align*}
- Y_{\mathrm{OLS}}
- = 
- \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}
- =
- \biggl \langle 
- \sum_{l=1}^{\infty} \langle \beta_{\mathrm{OLS}}, \xi^{[l]} \rangle_{\mathbb{H}} \xi^{[l]}, W 
- \biggr \rangle_{\mathbb{H}}
- \hspace{-.5em}
- =
- \sum_{l=1}^{\infty} \langle \beta_{\mathrm{OLS}}, \xi^{[l]} \rangle_{\mathbb{H}} \langle \xi^{[l]}, W \rangle_{\mathbb{H}}
- =
-\sum_{l=1}^{\infty} \nu^{[l]} \rho^{[l]},
-\end{align*}
-where the last equality uses
-Corollary \ref{cor:orthogonal_scores} and
-Proposition \ref{proposition:nu_l}.
-
-Then  the mean-squared error between the PLS approximation and the ordinary linear regression solution is written as
-\begin{align*}
- \mathbb{E}\left[ \| Y_{\mathrm{PLS},L } - Y_{\mathrm{OLS}} \|_2^2 \right] 
- %%%%%%%%%%%%%%%
- =
- \mathbb{E}\left[ 
- \bigl\|
-  \sum_{l=1}^{L} \nu^{[l]} \rho^{[l]} - \sum_{l=1}^{\infty} \nu^{[l]} \rho^{[l]} 
- \bigr\|_2^2 \right]
- %%%%%%%%%%%%%%%%%%
- &=
- \mathbb{E}\left[ 
- \bigl\|
- \sum_{l=L+1}^{\infty} \nu^{[l]} \rho^{[l]} 
- \bigr\|_2^2 \right]
- %%%%%%%%%%%%%%%%%%%
- \\&=
- \sum_{l=L+1}^{\infty} (\nu^{[l]})^2 \mathbb{E}[(\rho^{[l]})^2],
-\end{align*}
-where the last equality uses Corollary \ref{cor:orthogonal_scores}.
-
-Now, it suffices to show that $\sum_{l=L+1}^{\infty} (\nu^{[l]})^2 \mathbb{E}[(\rho^{[l]})^2] \to 0$ as $L \to \infty$.
-Now, since we assume $\mathbb{E}[Y] = 0$, and $Y_{\mathrm{OLS}}$ is linear in $Y$, we have
-\begin{align*}
-	\text{Var}(Y_{\mathrm{OLS}}) = \mathbb{E}[(Y_{\mathrm{OLS}})^2] = \mathbb{E}\left[\left(\sum_{l=1}^{\infty} \nu^{[l]} \rho^{[l]}\right)^2\right] 
-	= \sum_{l=1}^{\infty} (\nu^{[l]})^2 \mathbb{E}[(\rho^{[l]})^2],
-\end{align*}
-where the last equality uses Corollary \ref{cor:orthogonal_scores}.
-
-  By Cauchy–Schwarz in $\mathbb{H}$,
-\begin{equation*}
-\mathbb{E}|Y_{\mathrm{OLS}}|^2 
-	=
-\mathbb{E}	|\langle \beta_{\text{OLS}}, W\rangle_{\mathbb{H}}|^2 \le \mathbb{E}\|\beta_{\text{OLS}}\|_{\mathbb{H}}^{2}\,\mathbb{E}\|W\|_{\mathbb{H}}^{2} < \infty,
-\end{equation*}
-$(\nu^{[l]})^2 \mathbb{E}[(\rho^{[l]})^2]$ has a convergent series.
-For any convergent series, the sum of its tail (i.e., from $L+1$ to infinity) must approach zero as $L$ tends to infinity This concludes the proof of Theorem \ref{thm:hybrid_pls_convergence}.
+		Iterating the residualization $Y^{[l]} = Y^{[l-1]} - \nu^{[l-1]} \rho^{[l-1]}$ for $l=1,\dots,L$, we obtain
+		\begin{equation}\label{eq:Y_sum_residuals}
+			Y = \sum_{j=0}^{L-1} \nu^{[j]} \rho^{[j]} + Y^{[L]} = Y_{\mathrm{PLS},L-1} + Y^{[L]}.
+		\end{equation}
+		Consider the $L^2$ norm of the remaining residual $Y^{[L]}$:
+		\[
+		\mathbb{E}[(Y^{[L]})^2] = \mathbb{E}[(Y^{[L-1]} - \nu^{[L-1]} \rho^{[L-1]})^2] = \mathbb{E}[(Y^{[L-1]})^2] - (\nu^{[L-1]})^2 \mathbb{E}[(\rho^{[L-1]})^2].
+		\]
+		Thus, the residual variance is nonnegative and monotonically decreasing with $L$:
+		\[
+		0 \le \mathbb{E}[(Y^{[L]})^2] \le \mathbb{E}[(Y^{[L-1]})^2] \le \cdots \le \mathbb{E}[Y^2] < \infty.
+		\]
+		Therefore, the series $\sum_{l=1}^{\infty} (\nu^{[l]})^2 \mathbb{E}[(\rho^{[l]})^2]$ converges and the residual variance $\mathbb{E}[(Y^{[L]})^2] \to 0$ as $L \to \infty$.
+		From \eqref{eq:Y_sum_residuals}, the mean squared error of the PLS approximation is
+		\[
+		\mathbb{E}\bigl[ \| Y_{\mathrm{PLS},L-1} - Y \|^2 \bigr] = \mathbb{E}[(Y^{[L]})^2] \to 0 \quad \text{as } L \to \infty.
+		\]
+		This completes the proof of Theorem \ref{thm:hybrid_pls_convergence}.
 	\end{proof}
+
 	\section{Proof of geometric properties}
@@
 			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=  
+			=  
 			\sum_{i=1}^n
@@
 			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=  
+			=  
 			\big \langle
@@
 			\hat{\xi}^{[l_2]}
-			\big \rangle_{\mathbb{H}}
+			\big \rangle_{\mathbb{H}}.
 		\end{align*}

### 2025-08-22 create-FSHybridPLS.Rmd
get_nu is so easy

@@
 
+the full vector of PLS scores $$\hat{\boldsymbol{\rho}}  = (\hat{\rho}_1, \ldots, \hat{\rho}_n)^\top$$
+	is computed through the following matrix multiplication:
+$$
+		\hat{\boldsymbol{\rho}}^\top = \sum_{k=1}^K ( \hat{\boldsymbol{\gamma}}_j )^\top B \, \Theta_j^\top + \boldsymbol{\zeta}^\top \mathbf{Z}^\top.
+$$	
+```{r}
+get_rho <- function(d_vec, W){
+  K <- W$n_functional
+  M <- W$n_basis_list[[1]]
+  n_scalar <- W$n_scalar
+  n <- W$n_sample
+  rho <- rep(0, n)
+
+  #functional part
+  for (j in 1:K){
+    start_index <- (j-1)*M + 1
+    end_index <- j*M
+    gamma_j <- d_vec[ start_index : end_index]
+    Theta_j  <- t(W$functional_list[[j]]$coefs)
+    B <- W$gram_list[[j]]
+    rho <- rho + Theta_j %*% B %*% gamma_j
+  }
+
+  #scalar part
+  rho <- rho + W$Z %*% d_vec[(K * M + 1):length(d_vec)]
+  return (rho)
+}
+```
+
 ```{r}
@@
 
+### response residualization
+
+```{r}
+get_nu <- function(y, rho){
+            rho_norm_sq <- (Matrix::norm(rho, type = "2"))^2
+            nu <- as.numeric(t(rho) %*% input) / rho_norm_sq
+            return(nu)  
+}
+```
+
+```{r}
+LSE_ptws <- function(input, rho) {
+            rho_norm_sq <- (Matrix::norm(rho, type = "2"))^2
+            nu <- as.numeric(t(rho) %*% input) / rho_norm_sq
+            return(nu)
+}
+
+```
+
 ### LSE_hybrid

### 2025-08-23 create-FSHybridPLS.Rmd
replacer test passed

@@
 
-```{r}
-testthat::test_that("inprod.predictor_hybrid returns correct vector output for broadcasting and other cases", {
-  suppressPackageStartupMessages(library(fda))
-
-  basis <- create.bspline.basis(c(0, 1), 5)
-  make_fd <- function(val, n_sample) {
-    fd(coef = matrix(val, 5, n_sample), basisobj = basis)
-  }
-# data generation
-## three observations
-  fd1 <- make_fd(1, 3)
-  Z1 <- matrix(c(1, 2), nrow = 3, ncol = 2, byrow = TRUE)
-  x1 <- predictor_hybrid(Z1, list(fd1, fd1))
-## one observation
-  fd2 <- make_fd(2, 1)
-  Z2 <- matrix(c(3, 4), nrow = 1)
-  x2 <- predictor_hybrid(Z2, list(fd2, fd2))
-## three observations
-  Z3 <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 3, byrow = TRUE)
-  fd3 <- fd(coef = t(matrix(c(1:15), nrow = 3, byrow = TRUE)), basisobj = basis)
-  x3 <- predictor_hybrid(Z3, list(fd3, fd3))  
-## one observations
-  Z4 <- matrix(c(5, 6), nrow = 1)
-  fd4 <- make_fd(3, 1)
-  x4 <- predictor_hybrid(Z4, list(fd4, fd4))
-
-# Case 1: Self inner product (1 sample)
-  out1 <- inprod.predictor_hybrid(x2)
-  expected_scalar_1 <- sum(Z2^2)
-  expected_functional_1 <- sum(sapply(x2$functional_list, function(fd) fda::inprod(fd, fd)))
-  testthat::expect_equal(out1, expected_scalar_1 + expected_functional_1)
-
-# Case 2: Three-sample vs. Three-sample
-  out2 <- inprod.predictor_hybrid(x1, x3)
-  expected_scalar_2 <- rowSums(Z1 * Z3)
-  expected_functional_2 <- vapply(1:3, function(i) {
-    sum(sapply(1:2, function(j) {
-      fda::inprod(x1$functional_list[[j]][i], x3$functional_list[[j]][i])
-    }))
-  }, numeric(1))
-  testthat::expect_equal(out2, expected_scalar_2 + expected_functional_2)
-
-  # Case 3: One-sample vs. one-sample
-
-  out3 <- inprod.predictor_hybrid(x2, x4)
-  expected_scalar_3 <- sum(Z2 * Z4)
-  expected_functional_3 <-2*fda::inprod(fd2, fd4)
-  testthat::expect_equal(out3, as.numeric(expected_scalar_3 + expected_functional_3))
-
-  # Case 4: Broadcasting (single vs. multi)
-  out4 <- inprod.predictor_hybrid(x2, x3)
-  expected_scalar_4 <- c(0,0,0)
-  for (i in 1:3){
-    expected_scalar_4[i] <-  sum(Z2 * Z3[i,])
-    }
-
-  expected_functional_4 <-  c(0,0,0)
-  for (i in 1:3){
-    expected_functional_4[i] <- 2*fda::inprod(
-      fd2,
-      fd(
-        coef = matrix(
-        c(
-        (5*i+1-5):(5*i)
-        ), 5, 1), #end of matrix
-         basisobj = basis) #end of fd
-      )# end of inprod
-  }
-
-  testthat::expect_equal(as.vector(out4), as.vector(expected_scalar_4 + expected_functional_4))
-
-  # Case 4: Broadcasting (multi  vs. single)
-  testthat::expect_equal(as.vector(inprod.predictor_hybrid( x3, x2)), as.vector(expected_scalar_4 + expected_functional_4))  
-})
-```
-
 ### subset_predictor_hybrid
@@
 
+```
+
+### replace_obs_hybrid
+
+```{r}
+#' Replace a single observation in a predictor_hybrid object
+#'
+#' Replaces the i-th observation of a predictor_hybrid object with a new
+#' single-sample predictor_hybrid object.
+#'
+#' @param W A predictor_hybrid object with one or more samples.
+#' @param i An integer index specifying the observation to replace.
+#' @param new_W A single-sample predictor_hybrid object to use for replacement.
+#'
+#' @return A predictor_hybrid object with the i-th observation replaced.
+#' @export
+replace_obs_hybrid <- function(W, i, new_W) {
+  # Input validation
+  if (!inherits(W, "predictor_hybrid") || !inherits(new_W, "predictor_hybrid")) {
+    stop("Both W and new_W must be of class 'predictor_hybrid'.")
+  }
+  if (new_W$n_sample != 1) {
+    stop("new_W must be a single-sample predictor_hybrid object.")
+  }
+  if (i < 1 || i > W$n_sample) {
+    stop(paste("Index i must be between 1 and", W$n_sample))
+  }
+  if (W$n_scalar != new_W$n_scalar) {
+    stop("Mismatch in number of scalar predictors.")
+  }
+  if (W$n_functional != new_W$n_functional) {
+    stop("Mismatch in number of functional predictors.")
+  }
+
+  # Check for compatible basis objects
+  is_eqbasis <- getFromNamespace("is.eqbasis", "fda")
+  for (j in seq_len(W$n_functional)) {
+    if (!is_eqbasis(W$functional_list[[j]]$basis, new_W$functional_list[[j]]$basis)) {
+      stop("Functional predictors must have the same basis objects.")
+    }
+  }
+
+  # Replace the i-th observation in the scalar matrix Z
+  W$Z[i, ] <- new_W$Z[1, ]
+
+  # Replace the i-th observation in each functional predictor
+  for (j in seq_along(W$functional_list)) {
+    # The coefficients are stored as a matrix, with columns corresponding to samples
+    W$functional_list[[j]]$coefs[, i] <- new_W$functional_list[[j]]$coefs[, 1]
+  }
+
+  # The number of samples remains the same
+  return(W)
+}
+```
+
+```{r}
+testthat::test_that("replace_obs_hybrid correctly replaces an observation", {
+  # Setup: Create a multi-sample predictor_hybrid object
+  n_samples <- 5
+  n_scalar <- 2
+  n_functional <- 3
+  n_basis <- 5 # Assuming a fixed number of basis functions for simplicity
+
+  # Basis object
+  basis_obj <- create.bspline.basis(c(0, 1), nbasis = n_basis)
+
+  # Generate sample functional data
+  functional_list_initial <- lapply(1:n_functional, function(f_idx) {
+    fd(matrix(rnorm(n_basis * n_samples), ncol = n_samples), basis_obj)
+  })
+
+  # Generate sample scalar data
+  Z_initial <- matrix(rnorm(n_samples * n_scalar), nrow = n_samples, ncol = n_scalar)
+
+  W_original <- predictor_hybrid(Z = Z_initial, functional_list = functional_list_initial)
+
+  # Create a single-sample predictor_hybrid object for replacement
+  new_Z_scalar <- matrix(c(100, 200), nrow = 1)
+  new_functional_list_single <- lapply(1:n_functional, function(f_idx) {
+    fd(matrix(c(rep(10, n_basis), rep(20, n_basis), rep(30, n_basis))[f_idx * n_basis - (n_basis - 1):0], ncol = 1), basis_obj)
+  })
+  new_W_single <- predictor_hybrid(Z = new_Z_scalar, functional_list = new_functional_list_single)
+
+  # Test Case 1: Replace a middle observation (e.g., index 3)
+  index_to_replace <- 3
+  W_modified <- replace_obs_hybrid(W_original, index_to_replace, new_W_single)
+
+  # Verify scalar part
+  testthat::expect_equal(W_modified$Z[index_to_replace, ], new_W_single$Z[1, ],
+               info = "Scalar part at replaced index should match new_W_single$Z")
+  # Verify other scalar rows are unchanged
+  if (index_to_replace > 1) {
+    testthat::expect_equal(W_modified$Z[1:(index_to_replace - 1), ], W_original$Z[1:(index_to_replace - 1), ],
+                 info = "Scalar part before replaced index should be unchanged")
+  }
+  if (index_to_replace < n_samples) {
+    testthat::expect_equal(W_modified$Z[(index_to_replace + 1):n_samples, ], W_original$Z[(index_to_replace + 1):n_samples, ],
+                 info = "Scalar part after replaced index should be unchanged")
+  }
+
+  # Verify functional part
+  for (j in seq_len(n_functional)) {
+    testthat::expect_equal(coef(W_modified$functional_list[[j]])[, index_to_replace],
+                 coef(new_W_single$functional_list[[j]])[, 1],
+                 info = paste0("Functional predictor ", j, " at replaced index should match new_W_single"))
+    # Verify other functional columns are unchanged
+    if (index_to_replace > 1) {
+      testthat::expect_equal(coef(W_modified$functional_list[[j]])[, 1:(index_to_replace - 1)],
+                   coef(W_original$functional_list[[j]])[, 1:(index_to_replace - 1)],
+                   info = paste0("Functional predictor ", j, " before replaced index should be unchanged"))
+    }
+    if (index_to_replace < n_samples) {
+      testthat::expect_equal(coef(W_modified$functional_list[[j]])[, (index_to_replace + 1):n_samples],
+                   coef(W_original$functional_list[[j]])[, (index_to_replace + 1):n_samples],
+                   info = paste0("Functional predictor ", j, " after replaced index should be unchanged"))
+    }
+  }
+
+  # Test Case 2: Replacing the first observation (index 1)
+  index_to_replace <- 1
+  W_modified_first <- replace_obs_hybrid(W_original, index_to_replace, new_W_single)
+  testthat::expect_equal(W_modified_first$Z[index_to_replace, ], new_W_single$Z[1, ])
+  for (j in seq_len(n_functional)) {
+    testthat::expect_equal(coef(W_modified_first$functional_list[[j]])[, index_to_replace],
+                 coef(new_W_single$functional_list[[j]])[, 1])
+  }
+
+  # Test Case 3: Replacing the last observation (index n_samples)
+  index_to_replace <- n_samples
+  W_modified_last <- replace_obs_hybrid(W_original, index_to_replace, new_W_single)
+  testthat::expect_equal(W_modified_last$Z[index_to_replace, ], new_W_single$Z[1, ])
+  for (j in seq_len(n_functional)) {
+    testthat::expect_equal(coef(W_modified_last$functional_list[[j]])[, index_to_replace],
+                 coef(new_W_single$functional_list[[j]])[, 1])
+  }
+
+  # Test Case 4: Error handling for invalid index
+  testthat::expect_error(replace_obs_hybrid(W_original, 0, new_W_single), "Index i must be between 1 and")
+  testthat::expect_error(replace_obs_hybrid(W_original, n_samples + 1, new_W_single), "Index i must be between 1 and")
+
+  # Test Case 5: Error handling for new_W with multiple samples
+  multi_sample_new_W <- predictor_hybrid(Z = matrix(rnorm(2*n_scalar), nrow=2),
+                                         functional_list = lapply(1:n_functional, function(f_idx) {
+                                           fd(matrix(rnorm(n_basis*2), ncol = 2), basis_obj)
+                                         }))
+  testthat::expect_error(replace_obs_hybrid(W_original, 1, multi_sample_new_W), "new_W must be a single-sample predictor_hybrid object.")
+
+  # Test Case 6: Error handling for mismatch in n_scalar
+  mismatch_scalar_new_W <- predictor_hybrid(Z = matrix(rnorm(1*1), nrow=1),
+                                            functional_list = new_functional_list_single)
+  testthat::expect_error(replace_obs_hybrid(W_original, 1, mismatch_scalar_new_W), "Mismatch in number of scalar predictors.")
+
+  # Test Case 7: Error handling for mismatch in n_functional
+  mismatch_functional_new_W <- predictor_hybrid(Z = new_Z_scalar,
+                                                functional_list = new_functional_list_single[1]) # Only one functional predictor
+  testthat::expect_error(replace_obs_hybrid(W_original, 1, mismatch_functional_new_W), "Mismatch in number of functional predictors.")
+
+  # Test Case 8: Error handling for mismatch in basis objects
+  different_basis_obj <- create.bspline.basis(c(0, 1), nbasis = n_basis + 1) # Different basis
+mismatch_basis_new_W_list <- lapply(1:n_functional, function(f_idx) {
+  # Use the correct number of rows: nbasis of different_basis_obj
+  fd(matrix(rnorm(different_basis_obj$nbasis), ncol = 1), different_basis_obj)
+})
+  mismatch_basis_new_W <- predictor_hybrid(Z = new_Z_scalar,
+                                          functional_list = mismatch_basis_new_W_list)
+  testthat::expect_error(replace_obs_hybrid(W_original, 1, mismatch_basis_new_W), "Functional predictors must have the same basis objects.")
+
+})
 ```
@@
   rho <- rho + W$Z %*% d_vec[(K * M + 1):length(d_vec)]
-  return (rho)
+  return (as.vector(rho))
 }
@@
 get_nu <- function(y, rho){
+            nu <- sum(y*rho) / sum(rho*rho)
+            return(nu)  
+}
+```
+
+```{r}
+residualize_y <- function(y, rho){
+  nu <- get_nu(y, rho)
+  y_next <- y - nu * rho
+  return(y_next)
+}
+```
+
+output of the residualize_y and rho must be orthogonal.
+```{r}
+#sum(residualize_y(y, rho )*rho) #should output a very small number
+```
+
+```{r}
+LSE_ptws <- function(input, rho) {
+  # old implementation
             rho_norm_sq <- (Matrix::norm(rho, type = "2"))^2
@@
 }
-```
-
-```{r}
-LSE_ptws <- function(input, rho) {
-            rho_norm_sq <- (Matrix::norm(rho, type = "2"))^2
-            nu <- as.numeric(t(rho) %*% input) / rho_norm_sq
-            return(nu)
-}
-
+
+```
+
+###  predictor residualization
+
+$$
+\widetilde{W}_i^{[l+1]} 
+			:= 	\widetilde{W}_i^{[l]}  - 
+			\widehat{\rho}_i^{[l]}
+			\hat{\delta}^{[l]},~\text{where}~
+			\delta^{[l]}
+			:= 
+			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
+			\sum_{i=1}^n 
+			\widehat{\rho}_i^{[l]}
+			\widetilde{W}_i^{[l]},
+$$
+
+```{r}
+get_delta <- function(W, rho){
+  delta <- scalar_mul.predictor_hybrid(subset_predictor_hybrid(W, 1), rho[1])
+   for (i in 2:length(rho)) {
+  delta <- add.predictor_hybrid(delta, subset_predictor_hybrid(W, i),  rho[i]) 
+} 
+  return(delta)
+}
+```
+
+```{r}
+residualize_predictor <- function(W, delta){
+
+}
 ```
@@
 ### LSE_hybrid
-```{r}
-LSE_hybrid <- function(W, rho, tau) {
+
+```{r}
+LSE_hybrid <- function(W, rho) {
+  # old implementation
   C_star_J_star <- matrix(NA, nrow = W$n_sample, ncol = sum(W$n_basis_list) + W$n_scalar)
@@
 
+```{r}
+###########################################
+)
+
+setMethod("fitted_value",
+          signature(
+            "predictor_hybrid",
+            "vector"
+          ),
+####################################################
+function(regcoef, pls_score) {
+  for (ii in 1 : (regcoef@n_functional) ){
+    regcoef@functional_list[[ii]] <- fd(
+        coef = coef(regcoef@functional_list[[ii]]) %*% matrix(pls_score, nrow=1),
+        basisobj = regcoef@functional_list[[ii]]$basis
+      )}
+  regcoef@Z <-  pls_score %*% regcoef@Z
+  return(regcoef)
+  }
+####################################################
+)
+
+```
+
 ### nipals_pen_hybrid

### 2025-08-23 create-FSHybridPLS.Rmd
predictor residualization works

@@
 
-We run unit tests for:
-
-| Case | Description                        | Input Dimensions       | Output Length | Notes                                           |
-|------|------------------------------------|------------------------|----------------|-------------------------------------------------|
-| 1    | Self inner product (1 sample)      | x2: (1×2)              | 1              | Equivalent to squared norm                     |
-| 2    | Three-sample vs. Three-sample      | x1: (3×2), x3: (3×2)   | 3              | Dot + functional products, sample-wise         |
-| 3    | One-sample vs. One-sample          | x2: (1×2), x4: (1×2)   | 1              | Standard dot + functional product              |
-| 4    | Broadcasting (single vs. multi)    | x2: (1×2), x3: (3×2)   | 3              | Broadcast x2 across x3                          |
-| 5    | Broadcasting (multi vs. single)    | x3: (3×2), x2: (1×2)   | 3              | Broadcast x2 across x3                          |
-
 ### subset_predictor_hybrid
@@
 }
-```
-
-```{r}
-testthat::test_that("replace_obs_hybrid correctly replaces an observation", {
-  # Setup: Create a multi-sample predictor_hybrid object
-  n_samples <- 5
-  n_scalar <- 2
-  n_functional <- 3
-  n_basis <- 5 # Assuming a fixed number of basis functions for simplicity
-
-  # Basis object
-  basis_obj <- create.bspline.basis(c(0, 1), nbasis = n_basis)
-
-  # Generate sample functional data
-  functional_list_initial <- lapply(1:n_functional, function(f_idx) {
-    fd(matrix(rnorm(n_basis * n_samples), ncol = n_samples), basis_obj)
-  })
-
-  # Generate sample scalar data
-  Z_initial <- matrix(rnorm(n_samples * n_scalar), nrow = n_samples, ncol = n_scalar)
-
-  W_original <- predictor_hybrid(Z = Z_initial, functional_list = functional_list_initial)
-
-  # Create a single-sample predictor_hybrid object for replacement
-  new_Z_scalar <- matrix(c(100, 200), nrow = 1)
-  new_functional_list_single <- lapply(1:n_functional, function(f_idx) {
-    fd(matrix(c(rep(10, n_basis), rep(20, n_basis), rep(30, n_basis))[f_idx * n_basis - (n_basis - 1):0], ncol = 1), basis_obj)
-  })
-  new_W_single <- predictor_hybrid(Z = new_Z_scalar, functional_list = new_functional_list_single)
-
-  # Test Case 1: Replace a middle observation (e.g., index 3)
-  index_to_replace <- 3
-  W_modified <- replace_obs_hybrid(W_original, index_to_replace, new_W_single)
-
-  # Verify scalar part
-  testthat::expect_equal(W_modified$Z[index_to_replace, ], new_W_single$Z[1, ],
-               info = "Scalar part at replaced index should match new_W_single$Z")
-  # Verify other scalar rows are unchanged
-  if (index_to_replace > 1) {
-    testthat::expect_equal(W_modified$Z[1:(index_to_replace - 1), ], W_original$Z[1:(index_to_replace - 1), ],
-                 info = "Scalar part before replaced index should be unchanged")
-  }
-  if (index_to_replace < n_samples) {
-    testthat::expect_equal(W_modified$Z[(index_to_replace + 1):n_samples, ], W_original$Z[(index_to_replace + 1):n_samples, ],
-                 info = "Scalar part after replaced index should be unchanged")
-  }
-
-  # Verify functional part
-  for (j in seq_len(n_functional)) {
-    testthat::expect_equal(coef(W_modified$functional_list[[j]])[, index_to_replace],
-                 coef(new_W_single$functional_list[[j]])[, 1],
-                 info = paste0("Functional predictor ", j, " at replaced index should match new_W_single"))
-    # Verify other functional columns are unchanged
-    if (index_to_replace > 1) {
-      testthat::expect_equal(coef(W_modified$functional_list[[j]])[, 1:(index_to_replace - 1)],
-                   coef(W_original$functional_list[[j]])[, 1:(index_to_replace - 1)],
-                   info = paste0("Functional predictor ", j, " before replaced index should be unchanged"))
-    }
-    if (index_to_replace < n_samples) {
-      testthat::expect_equal(coef(W_modified$functional_list[[j]])[, (index_to_replace + 1):n_samples],
-                   coef(W_original$functional_list[[j]])[, (index_to_replace + 1):n_samples],
-                   info = paste0("Functional predictor ", j, " after replaced index should be unchanged"))
-    }
-  }
-
-  # Test Case 2: Replacing the first observation (index 1)
-  index_to_replace <- 1
-  W_modified_first <- replace_obs_hybrid(W_original, index_to_replace, new_W_single)
-  testthat::expect_equal(W_modified_first$Z[index_to_replace, ], new_W_single$Z[1, ])
-  for (j in seq_len(n_functional)) {
-    testthat::expect_equal(coef(W_modified_first$functional_list[[j]])[, index_to_replace],
-                 coef(new_W_single$functional_list[[j]])[, 1])
-  }
-
-  # Test Case 3: Replacing the last observation (index n_samples)
-  index_to_replace <- n_samples
-  W_modified_last <- replace_obs_hybrid(W_original, index_to_replace, new_W_single)
-  testthat::expect_equal(W_modified_last$Z[index_to_replace, ], new_W_single$Z[1, ])
-  for (j in seq_len(n_functional)) {
-    testthat::expect_equal(coef(W_modified_last$functional_list[[j]])[, index_to_replace],
-                 coef(new_W_single$functional_list[[j]])[, 1])
-  }
-
-  # Test Case 4: Error handling for invalid index
-  testthat::expect_error(replace_obs_hybrid(W_original, 0, new_W_single), "Index i must be between 1 and")
-  testthat::expect_error(replace_obs_hybrid(W_original, n_samples + 1, new_W_single), "Index i must be between 1 and")
-
-  # Test Case 5: Error handling for new_W with multiple samples
-  multi_sample_new_W <- predictor_hybrid(Z = matrix(rnorm(2*n_scalar), nrow=2),
-                                         functional_list = lapply(1:n_functional, function(f_idx) {
-                                           fd(matrix(rnorm(n_basis*2), ncol = 2), basis_obj)
-                                         }))
-  testthat::expect_error(replace_obs_hybrid(W_original, 1, multi_sample_new_W), "new_W must be a single-sample predictor_hybrid object.")
-
-  # Test Case 6: Error handling for mismatch in n_scalar
-  mismatch_scalar_new_W <- predictor_hybrid(Z = matrix(rnorm(1*1), nrow=1),
-                                            functional_list = new_functional_list_single)
-  testthat::expect_error(replace_obs_hybrid(W_original, 1, mismatch_scalar_new_W), "Mismatch in number of scalar predictors.")
-
-  # Test Case 7: Error handling for mismatch in n_functional
-  mismatch_functional_new_W <- predictor_hybrid(Z = new_Z_scalar,
-                                                functional_list = new_functional_list_single[1]) # Only one functional predictor
-  testthat::expect_error(replace_obs_hybrid(W_original, 1, mismatch_functional_new_W), "Mismatch in number of functional predictors.")
-
-  # Test Case 8: Error handling for mismatch in basis objects
-  different_basis_obj <- create.bspline.basis(c(0, 1), nbasis = n_basis + 1) # Different basis
-mismatch_basis_new_W_list <- lapply(1:n_functional, function(f_idx) {
-  # Use the correct number of rows: nbasis of different_basis_obj
-  fd(matrix(rnorm(different_basis_obj$nbasis), ncol = 1), different_basis_obj)
-})
-  mismatch_basis_new_W <- predictor_hybrid(Z = new_Z_scalar,
-                                          functional_list = mismatch_basis_new_W_list)
-  testthat::expect_error(replace_obs_hybrid(W_original, 1, mismatch_basis_new_W), "Functional predictors must have the same basis objects.")
-
-})
 ```
@@
    } 
+  delta <- scalar_mul.predictor_hybrid(delta, 1/sum(rho*rho))
   return(delta)
@@
 ```{r}
-residualize_predictor <- function(W, delta){
-
-}
+residualize_predictor <- function(W, rho, delta){
+  n <- length(rho)
+  W_res <- W
+  for (i in 1:n){
+    W_res_i <-subtr.predictor_hybrid(subset_predictor_hybrid(W, i), delta,  rho[i]) 
+    W_res <- replace_obs_hybrid(W_res, i, W_res_i)
+  }
+  return(W_res)
+}
+```
+
+```{r}
+delta <- get_delta(W,rho)
+res <- residualize_predictor(W, rho, delta)
+zero<-get_delta(res, rho)
 ```

### 2025-08-23 create-FSHybridPLS.Rmd
eigen and linear equivalent

@@
 
-```{r}
-
-# --- Example Usage ---
-
-# Example 1: All matrices are identical
-mat1 <- matrix(c(1, 2, 3, 4), nrow = 2)
-mat2 <- matrix(c(1, 2, 3, 4), nrow = 2)
-mat3 <- matrix(c(1, 2, 3, 4), nrow = 2)
-identical_list <- list(mat1, mat2, mat3)
-print("Test Case 1: All matrices identical")
-print(are_all_gram_matrices_identical(identical_list)) # Expected: TRUE
-
-# Example 2: Matrices with slight floating-point differences (within tolerance)
-mat4 <- matrix(c(1.000000000000001, 2, 3, 4), nrow = 2)
-mat5 <- matrix(c(1, 2, 3, 4), nrow = 2)
-tolerance_list <- list(mat4, mat5)
-print("Test Case 2: Matrices with slight floating-point differences")
-print(are_all_gram_matrices_identical(tolerance_list)) # Expected: TRUE
-
-# Example 3: Matrices are not identical
-mat6 <- matrix(c(1, 2, 3, 5), nrow = 2) # Different value
-non_identical_list <- list(mat1, mat6, mat3)
-print("Test Case 3: Matrices are not identical")
-print(are_all_gram_matrices_identical(non_identical_list)) # Expected: FALSE
-
-# Example 4: List with different dimensions
-mat7 <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 3)
-diff_dim_list <- list(mat1, mat7)
-print("Test Case 4: Matrices with different dimensions")
-print(are_all_gram_matrices_identical(diff_dim_list)) # Expected: FALSE (all.equal will catch this)
-
-# Example 5: Empty list
-empty_list <- list()
-print("Test Case 5: Empty list")
-print(are_all_gram_matrices_identical(empty_list)) # Expected: TRUE
-
-# Example 6: List with a single matrix
-single_matrix_list <- list(mat1)
-print("Test Case 6: Single matrix list")
-print(are_all_gram_matrices_identical(single_matrix_list)) # Expected: TRUE
-
-# Example 7: List containing non-matrix elements (will stop with an error)
-# non_matrix_list <- list(mat1, "not a matrix", mat3)
-# print("Test Case 7: List with non-matrix element (will throw error)")
-# print(are_all_gram_matrices_identical(non_matrix_list))
-```
-
 ## helpers for functional data objects
@@
 predictor_hybrid_from_coef <- function(format, coef){
-  M <- dim(format$gram_list[[1]])[2] # number of basis functions
-  K <- length(format$functional_list) # number of functional predictors
+  M <- format$n_basis_list[1] # number of basis functions
+  K <- format$n_functional # number of functional predictors
   for (ii in 1:K){
@@
   if (n1 == 1 && n2 == 1) as.numeric(result) else result
+}
+```
+
+```{r}
+#' Inner product between two predictor_hybrid objects (with broadcasting)
+#'
+#' Computes the inner product between two `predictor_hybrid` objects,
+#' including both functional and scalar components. Supports broadcasting
+#' when one of the inputs has a single observation.
+#'
+#' @param xi_1 A `predictor_hybrid` object.
+#' @param xi_2 Another `predictor_hybrid` object. If missing, defaults to `xi_1`.
+#'
+#' @return A numeric vector of inner products, or a scalar if both inputs contain a single observation.
+#' @export
+inprod_pen.predictor_hybrid <- function(xi_1, xi_2 = NULL, lambda) {
+
+  inprod <- inprod.predictor_hybrid(xi_1, xi_2)
+  # Prepare components
+
+  f1 <- xi_1$functional_list
+
+  f2 <- xi_2$functional_list
+  for (j in 1:xi_1$n_functional){
+    inprod <- inprod + lambda[j] * fda::inprod(
+        fdobj1 = f1[[j]], 
+        fdobj2 = f2[[j]], 
+        Lfdobj1 = 2,
+        Lfdobj2 = 2
+        )
+
+    }
+
+  # Combine results
+   return(as.numeric(inprod))
 }
@@
   })
-  predictor_hybrid(Z = new_Z, functional_list = new_functional_list)
-}
-
+  new_predictor <- predictor_hybrid(Z = new_Z, functional_list = new_functional_list)
+  return(new_predictor)
+}
 ```
@@
   xi_hat <- predictor_hybrid_from_coef(format = W, coef = xi_star)
-  return(list(
-    xi_hat = xi_hat,
-    E = E,
-    V_star = V_star,
-    eigen_val = eigen_result$values[1]
-  ))
+  return(xi_hat)
 }
@@
     R <- W$gram_list[[j]] + lambda[j] * W$gram_deriv2_list[[j]]
-    U_cholesky <- chol(R)
-    L_cholesky <- t(U_cholesky)
-    intermediate <- forwardsolve(L_cholesky, u[[j]])
-    gamma[[j]] <- backsolve(U_cholesky, intermediate)
+    gamma[[j]] <- solve(R, u[[j]])
 
      #q
-    q <- q + sum( u[[j]] * gamma[[j]] )
+    q <- q + sum( gamma[[j]] * ( R %*% gamma[[j]] ))
   }
@@
   d_vec <- d_vec/ sqrt(q)
-  return(d_vec)
+  xi_hat <- predictor_hybrid_from_coef(format = W, coef = d_vec)
+  return(xi_hat)
 }
@@
 n_scalar <- 2
-n_basis <- 5
+n_basis <- 20
 n_functional <- 2
@@
 ```{r}
-residualize_y <- function(y, rho){
-  nu <- get_nu(y, rho)
+residualize_y <- function(y, rho, nu){
   y_next <- y - nu * rho
@@
 }
-```
-
-output of the residualize_y and rho must be orthogonal.
-```{r}
-#sum(residualize_y(y, rho )*rho) #should output a very small number
 ```
@@
   for (i in 1:n){
-    W_res_i <-subtr.predictor_hybrid(subset_predictor_hybrid(W, i), delta,  rho[i]) 
+    W_i <- subset_predictor_hybrid(W, i)
+    W_res_i <-subtr.predictor_hybrid(W_i, delta,  rho[i]) 
     W_res <- replace_obs_hybrid(W_res, i, W_res_i)
@@
 }
-```
-
-```{r}
-delta <- get_delta(W,rho)
-res <- residualize_predictor(W, rho, delta)
-zero<-get_delta(res, rho)
 ```
@@
   J_star <-as.matrix(get_jacobian_hybrid(W))
-  d_hat_star <- t( #basis coefficient of hybrid regression coefficient
+  d_hat_star <- t( #basis coefficient of hybrid regression coefficientdelta
     solve(
@@
 
-```{r}
-###########################################
-)
-
-setMethod("fitted_value",
-          signature(
-            "predictor_hybrid",
-            "vector"
-          ),
-####################################################
-function(regcoef, pls_score) {
-  for (ii in 1 : (regcoef@n_functional) ){
-    regcoef@functional_list[[ii]] <- fd(
-        coef = coef(regcoef@functional_list[[ii]]) %*% matrix(pls_score, nrow=1),
-        basisobj = regcoef@functional_list[[ii]]$basis
-      )}
-  regcoef@Z <-  pls_score %*% regcoef@Z
-  return(regcoef)
-  }
-####################################################
-)
-
+# main algorithm
+
+```{r eval=FALSE, include=FALSE}
+#' @export
+fit.hybridPLS <- function(W, y, n_iter, lambda) {
+  # 1. Initialize storage
+  W_now <- rho <- xi <- delta <- nu  <- sigma <- eta <- list()
+
+  # 3. Initialize residuals
+  W_now[[1]] <- W
+  y_now <- y
+  final_succesful_iteration <- 0
+  constr_mat <- get_constraint_matrix_hybrid(W, lambda)
+  constr_mat_chol <- t(chol(constr_mat))
+  for (l in 1:n_iter) {
+    cat(paste(l, "th component", "\n"))
+
+    xi[[l]]  <- get_xi_hat_linear_pen(W_now[[l]], y_now, lambda) # PLS direction
+     rho[[l]] <- inprod.predictor_hybrid(W_now[[l]], xi[[l]]) #PLS score
+    delta[[l]] <- get_delta(W_now[[l]], rho[[l]]);  
+    W_now[[l + 1]] <- residualize_predictor(W_now[[l]], rho[[l]], delta[[l]]) # predictor residual
+    nu[[l]] <- get_nu(y_now, rho[[l]]); y_now <- residualize_y(y_now, rho[[l]], nu[[l]]) # response residual
+
+    # Step 3: Orthogonalize and update prediction
+    #sigma[[l]] <- xi[[l]]
+    #if (l == 1) {
+    #  eta[[l]] <- scalar_mul(sigma[[l]], nu[[l]])
+    #} else {
+    #  for (u in 1:(l - 1)) {
+    #    sigma[[l]] <- subtr(sigma[[l]], sigma[[u]], hybrid_inner_prod(delta[[u]], xi[[l]]))
+    #  }
+    #  eta[[l]] <- add(eta[[l - 1]], sigma[[l]], nu[[l]])
+    #}
+  }
+  return (list(
+    rho = rho,
+    xi = xi,
+    W = W_now
+  ))
+}
+
+```
+
+```{r eval=FALSE, include=FALSE}
+#' @export
+fit.hybridPLS_eigen <- function(W, y, n_iter, lambda) {
+  # 1. Initialize storage
+  W_now <- rho <- xi <- delta <- nu  <- sigma <- eta <- list()
+
+  # 3. Initialize residuals
+  W_now[[1]] <- W
+  y_now <- y
+  final_succesful_iteration <- 0
+  constr_mat <- get_constraint_matrix_hybrid(W, lambda)
+  constr_mat_chol <- t(chol(constr_mat))
+  for (l in 1:n_iter) {
+    cat(paste(l, "th component", "\n"))
+
+    #xi[[l]]  <- get_xi_hat_linear_pen(W_now[[l]], y_now, lambda) # PLS direction
+    xi[[l]]  <- get_pls_comp(W_now[[l]], y_now, constr_mat_chol) # PLS direction
+    rho[[l]] <- inprod.predictor_hybrid(W_now[[l]], xi[[l]]) #PLS score
+    delta[[l]] <- get_delta(W_now[[l]], rho[[l]]);  
+    W_now[[l + 1]] <- residualize_predictor(W_now[[l]], rho[[l]], delta[[l]]) # predictor residual
+    nu[[l]] <- get_nu(y_now, rho[[l]]); y_now <- residualize_y(y_now, rho[[l]], nu[[l]]) # response residual
+
+    # Step 3: Orthogonalize and update prediction
+    #sigma[[l]] <- xi[[l]]
+    #if (l == 1) {
+    #  eta[[l]] <- scalar_mul(sigma[[l]], nu[[l]])
+    #} else {
+    #  for (u in 1:(l - 1)) {
+    #    sigma[[l]] <- subtr(sigma[[l]], sigma[[u]], hybrid_inner_prod(delta[[u]], xi[[l]]))
+    #  }
+    #  eta[[l]] <- add(eta[[l - 1]], sigma[[l]], nu[[l]])
+    #}
+  }
+  return (list(
+    rho = rho,
+    xi = xi,
+    W = W_now
+  ))
+}
+
+```
+
+```{r}
+inprod.predictor_hybrid(res$W[[5]], res$xi[[3]])
+
+sum(y * inprod.predictor_hybrid(res$W[[5]], res$xi[[3]]))
+
+inprod_pen.predictor_hybrid(res$xi[[1]], res$xi[[8]], lambda) - inprod_pen.predictor_hybrid(res_eigen$xi[[1]], res_eigen$xi[[8]], lambda)
+inprod_pen.predictor_hybrid(res$xi[[1]], res$xi[[8]], 10*lambda) - inprod_pen.predictor_hybrid(res_eigen$xi[[1]], res_eigen$xi[[8]], 10*lambda)
+inprod_pen.predictor_hybrid(res$xi[[1]], res$xi[[8]], lambda/10) - inprod_pen.predictor_hybrid(res_eigen$xi[[1]], res_eigen$xi[[8]], lambda/10)
+sum(y * inprod.predictor_hybrid(res$W[[8]], res$xi[[1]])) - sum(y * inprod.predictor_hybrid(res_eigen$W[[8]], res_eigen$xi[[1]]))
+
+inprod_pen.predictor_hybrid(res$xi[[3]], res$xi[[4]], lambda) - inprod_pen.predictor_hybrid(res_eigen$xi[[3]], res_eigen$xi[[4]], lambda)
+inprod_pen.predictor_hybrid(res$xi[[3]], res$xi[[4]], 10*lambda) - inprod_pen.predictor_hybrid(res_eigen$xi[[3]], res_eigen$xi[[4]], 10*lambda)
+inprod_pen.predictor_hybrid(res$xi[[3]], res$xi[[4]], lambda/10)
+sum(y * inprod.predictor_hybrid(res$W[[3]], res$xi[[1]]))
+
+inprod_pen.predictor_hybrid(res$xi[[5]], res$xi[[10]], lambda)
+inprod_pen.predictor_hybrid(res$xi[[5]], res$xi[[10]], 10*lambda)
+inprod_pen.predictor_hybrid(res$xi[[5]], res$xi[[10]], lambda/10)
+sum(y * inprod.predictor_hybrid(res$W[[5]], res$xi[[1]]))
+
+inprod_pen.predictor_hybrid(res$xi[[4]], res$xi[[4]], lambda)
+inprod_pen.predictor_hybrid(res$xi[[4]], res$xi[[4]], lambda/10)
+inprod_pen.predictor_hybrid(res$xi[[4]], res$xi[[4]], 10*lambda )
+
+```
+
+```{r}
+lambda <- c(0.5,0.5)
+L=8
+res <- fit.hybridPLS(W,y,L, lambda)
+res_eigen <- fit.hybridPLS_eigen(W,y,L, lambda)
 ```

### 2025-08-23 create-FSHybridPLS.Rmd
proof start

@@
   # 1. Initialize storage
+  W_now <- rho <- xi <- delta <- nu  <- iota <- beta <- list()
+
+  # 3. Initialize residuals
+  W_now[[1]] <- W
+  y_now <- y
+  for (l in 1:n_iter) {
+    cat(paste(l, "th component", "\n"))
+
+    xi[[l]]  <- get_xi_hat_linear_pen(W_now[[l]], y_now, lambda) # PLS direction
+    rho[[l]] <- inprod.predictor_hybrid(W_now[[l]], xi[[l]]) #PLS score
+    delta[[l]] <- get_delta(W_now[[l]], rho[[l]]);  
+    W_now[[l + 1]] <- residualize_predictor(W_now[[l]], rho[[l]], delta[[l]]) # predictor residual
+    nu[[l]] <- get_nu(y_now, rho[[l]]); y_now <- residualize_y(y_now, rho[[l]], nu[[l]]) # response residual
+
+    iota[[l]] <- xi[[l]]
+    if (l == 1) {
+      beta[[l]] <- scalar_mul.predictor_hybrid( iota[[l]], nu[[l]] )
+    } else {
+      for (u in 1:(l - 1)) iota[[l]] <- subtr.predictor_hybrid( iota[[l]], iota[[u]], inprod.predictor_hybrid(delta[[u]], xi[[l]]))
+      beta[[l]] <- add.predictor_hybrid(beta[[l - 1]], iota[[l]], nu[[l]])
+    }
+  }
+  return (list(
+    rho = rho,
+    xi = xi,
+    W = W_now,
+    beta = beta
+  ))
+}
+
+```
+
+```{r eval=FALSE, include=FALSE}
+#' @export
+fit.hybridPLS_eigen <- function(W, y, n_iter, lambda) {
+  # 1. Initialize storage
   W_now <- rho <- xi <- delta <- nu  <- sigma <- eta <- list()
@@
 
-    xi[[l]]  <- get_xi_hat_linear_pen(W_now[[l]], y_now, lambda) # PLS direction
+    #xi[[l]]  <- get_xi_hat_linear_pen(W_now[[l]], y_now, lambda) # PLS direction
+    xi[[l]]  <- get_pls_comp(W_now[[l]], y_now, constr_mat_chol) # PLS direction
     rho[[l]] <- inprod.predictor_hybrid(W_now[[l]], xi[[l]]) #PLS score
@@
 
-```{r eval=FALSE, include=FALSE}
-#' @export
-fit.hybridPLS_eigen <- function(W, y, n_iter, lambda) {
-  # 1. Initialize storage
-  W_now <- rho <- xi <- delta <- nu  <- sigma <- eta <- list()
-
-  # 3. Initialize residuals
-  W_now[[1]] <- W
-  y_now <- y
-  final_succesful_iteration <- 0
-  constr_mat <- get_constraint_matrix_hybrid(W, lambda)
-  constr_mat_chol <- t(chol(constr_mat))
-  for (l in 1:n_iter) {
-    cat(paste(l, "th component", "\n"))
-
-    #xi[[l]]  <- get_xi_hat_linear_pen(W_now[[l]], y_now, lambda) # PLS direction
-    xi[[l]]  <- get_pls_comp(W_now[[l]], y_now, constr_mat_chol) # PLS direction
-    rho[[l]] <- inprod.predictor_hybrid(W_now[[l]], xi[[l]]) #PLS score
-    delta[[l]] <- get_delta(W_now[[l]], rho[[l]]);  
-    W_now[[l + 1]] <- residualize_predictor(W_now[[l]], rho[[l]], delta[[l]]) # predictor residual
-    nu[[l]] <- get_nu(y_now, rho[[l]]); y_now <- residualize_y(y_now, rho[[l]], nu[[l]]) # response residual
-
-    # Step 3: Orthogonalize and update prediction
-    #sigma[[l]] <- xi[[l]]
-    #if (l == 1) {
-    #  eta[[l]] <- scalar_mul(sigma[[l]], nu[[l]])
-    #} else {
-    #  for (u in 1:(l - 1)) {
-    #    sigma[[l]] <- subtr(sigma[[l]], sigma[[u]], hybrid_inner_prod(delta[[u]], xi[[l]]))
-    #  }
-    #  eta[[l]] <- add(eta[[l - 1]], sigma[[l]], nu[[l]])
-    #}
-  }
-  return (list(
-    rho = rho,
-    xi = xi,
-    W = W_now
-  ))
-}
-
-```
-
 ```{r}

### 2025-10-01 manuscript/enar/enar.tex
use cls file

--- 2025-08-22 manuscript/main.tex
@@
-%
-\documentclass[aoas]{imsart}
-
-%% Packages
-\RequirePackage{amsthm,amsmath,amsfonts,amssymb}
-\RequirePackage[authoryear]{natbib}
+\documentclass[12pt]{biom}
+
+% Page setup
+%\usepackage[margin=1in]{geometry}
+%\usepackage{setspace}
+%\doublespacing % ensures double spacing
+%\setlength{\textheight}{9in} % ~25 lines per page with 12pt double spaced
+%\setlength{\parskip}{0pt}
+%\setlength{\parindent}{0.5in}
+
+% Font
+\renewcommand{\rmdefault}{ptm} % Times font (Biometrics-like)
+
+% References (Biometrics style uses Chicago-like author-year)
+
 \RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
@@
 
-%%%%
-
-% \usepackage{multirow}
-% \usepackage{hhline}
-%\usepackage{enumitem}
-
-% \usepackage{bm}
-% \usepackage{multirow,multicol}
-% \usepackage{verbatim}
-% \usepackage{amsfonts,amssymb,amsthm,color,authblk}
-
-% \definecolor{myblue}{RGB}{0, 0, 0}
-% \newcommand{\blue}[1]{{\color{myblue}#1}}
-\startlocaldefs
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Uncomment next line to change            %%
-%% the type of equation numbering           %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\numberwithin{equation}{section}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% For Axiom, Claim, Corollary, Hypothesis, %%
-%% Lemma, Theorem, Proposition              %%
-%% use \theoremstyle{plain}                 %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\theoremstyle{plain}
-\newtheorem{axiom}{Axiom}
-\newtheorem{claim}[axiom]{Claim}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}%custom
+%\theoremstyle{plain}
+%\newtheorem{axiom}{Axiom}
+%\newtheorem{claim}[axiom]{Claim}
+%\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{proposition}[theorem]{Proposition}
+%\newtheorem{corollary}[theorem]{Corollary}%custom
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem*{example}{Example}
-\newtheorem*{fact}{Fact}
-\newtheorem{remark}{Remark}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please put your definitions here:        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
-\newcommand{\jongmin}[1]{
-	{ \color{teal} \textit{(JM:) #1}}
-}
-
-\endlocaldefs
+%\theoremstyle{definition}
+%\newtheorem{definition}[theorem]{Definition}
+%\newtheorem*{example}{Example}
+%\newtheorem*{fact}{Fact}
+%\newtheorem{remark}{Remark}
+
+% Counters for figures/tables
+%\usepackage{etoolbox}
+%\newcounter{totalfigtab}
+%\pretocmd{\begin{figure}}{\stepcounter{totalfigtab}}{}{}
+%	\pretocmd{\begin{table}}{\stepcounter{totalfigtab}}{}{}
+
+		% Title page
 
@@
 
-	\begin{frontmatter}
-		\title{ Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors}
-		%\title{A sample article title with some additional note\thanksref{t1}}
-		\runtitle{Hybrid Partial Least Squares}
-		%\thankstext{T1}{A sample additional note to the title.}
-
-		\begin{aug}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			%% Only one address is permitted per author. %%
-			%% Only division, organization and e-mail is %%
-			%% included in the address.                  %%
-			%% Additional information can be included in %%
-			%% the Acknowledgments section if necessary. %%
-			%% ORCID can be inserted by command:         %%
-			%% \orcid{0000-0000-0000-0000}               %%
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\author[A]{\fnms{Jongmin }~\snm{Mun}  \ead[label=e1]{jongmin.mun@marshall.usc.edu}}
-			\and
-			\author[B]{\fnms{Jeong Hoon}~\snm{Jang}\ead[label=e2]{jejang@utmb.edu }}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			%% Addresses                                %%
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\address[A]{Data Sciences and Operations Department, Marshall School of Business, University of Southern California\printead[presep={,\ }]{e1}}
-
-			\address[B]{Department of Biostatistics and Data Science, University of Texas Medical Branch\printead[presep={,\ }]{e2}}
-		\end{aug}
-
-		\begin{abstract}
-			Regression of a scalar response on mixed functional- and scalar-valued predictors, such as medical imaging with auxiliary patient information, introduces the new challenge of handling cross-modality correlations.
-To address this, we propose a hybrid partial least squares (PLS) regression framework that integrates functional and scalar predictors within a unified Hilbert space.
-			We then extend the classical nonlinear iterative PLS (NIPALS) algorithm to this hybrid Hilbert space by iteratively maximizing the empirical cross-covariance between the hybrid predictor and the response.
-As a result, our method identifies low-dimensional representations that capture both within- and between-modality variation, as well as the response-predictor correlation.
-The procedure is computationally efficient, requiring only the solution of linear systems at each step.
-We provide theoretical properties to justify our algorithm and demonstrate its effectiveness through simulations and an application to clinical outcome prediction using renal imaging and scalar covariates from the Emory University renal study.
-		\end{abstract}
-
-		\begin{keyword}
-			\kwd{dimension reduction}
-			\kwd{functional data analysis}
-			\kwd{multiple data modalities}
-			\kwd{multivariate data analysis}
-			\kwd{multivariate functional data}
-			\kwd{partial least square}
-		\end{keyword}
-
-	\end{frontmatter}
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	%% Please use \tableofcontents for articles %%
-	%% with 50 pages and more                   %%
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	%\tableofcontents
-	\section{Introduction} \label{sec: Introduction}
-	%Functional data analysis (FDA) treats each observed process as a realization of a random function over a continuous domain, such as time or space.
-The smoothness and infinite-dimensional nature of functional data allow researchers to exploit rich structural features, including .
-This enables regression analysis for predicting clinical outcomes using complex functional predictors collected with advanced recording technologies, such as medical imaging data.
-
-	Modern biomedical studies frequently collect diverse data types from each subject.
-	As an illustrative example, the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021}  records both multiple   renogram curves (functional data) and multiple renogram variables (scalar data)  for each kidney.
-	To effectively analyze such distinct yet related physiological signals, we construct a joint linear regression model incorporating both functional and scalar-valued i.i.d. covariates:
+Biomedical studies often collect multi-modal data, as in the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021}, which records multiple renogram curves (functional data) along with scalar side information for each kidney.
+Such distinct yet related physiological signals can be represented as functional- and scalar-valued i.i.d. covariates in a linear regression model:
 \begin{equation}	\label{eq:hybrid_regression_model}
@@
 \end{equation}
-	where $Y_i$ is a scalar response, $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ is a Euclidean vector covariate, $X_{i1}(t), \ldots, X_{iK}(t)$ are functional predictors that belong to $\mathbb{L}^2[0,1]$, and $\epsilon_i$ is observational noise.
-	In other words, this is a scalar-on-hybrid regression where the hybrid covariates belong to $\bigl( \mathbb{L}^2[0,1] \bigr)^{  K} \times \mathbb{R}^p$.
-	For notational convenience, we assume throughout this paper that the responses and predictors have been centered, allowing the intercept term to be ignored.
-	%where $\boldsymbol{\alpha}=(\alpha_1, \ldots, \alpha_p)^\top \in \mathbb{R}^p$ and $\beta=(\beta^{(1)}, \ldots, \beta^{(K)}) \in \mathcal{F}$ are respectively the regression coefficient vector and function that characterize the effect of scalar and functional predictors on the outcome.
-	%which is defined as the space of real-valued functions on $[0,1]$
-	%	which are square-integrable with respect to the Lebesgue measure $dt$ on $[0,1]$, 
-	%	and possess second  derivatives.
-
-	%denote a $p$-dimensional multivariate scalar data in $\mathbb{R}^p$, assumed to be a random vector with finite first two moments, equipped with the Euclidean inner product and norm.
-
-	%Infinite dimensional beta estimation problem (ill-posed problem)
-	%Multicollinearity and high-dimensionality in scalar predictors are not handled.
-	%Also, there may be high correlation between functional and scalar predictors.
-	This hybrid model poses several challenges. 
-	First, estimating the infinite-dimensional slope function $\beta_k(t)$ from a finite number of data
-	is an ill-posed problem.% that requires dimension reduction or regularization based on structural assumptions, such as derivatives and covariance patterns.
-	Second, we face the high-dimensionality of the predictors with $K+p$ dimensions.
-	Third, strong correlations between functional and scalar predictors are common but often overlooked by separate modeling approaches.
-	This paper addresses these three issues in a unified way by introducing a hybrid partial least squares (PLS) regression framework defined on a novel hybrid Hilbert space.
-Before summarizing the key contributions of this framework, we first review previous approaches and their limitations.
+where $Y_i$ is a scalar response, 
+$X_{i1}(t), \ldots, X_{iK}(t) \in \mathbb{L}^2[0,1]$ are functional predictors, 
+$\mathbf{Z}_i = (Z_{i1}, \ldots, Z_{ip})^\top$ is a Euclidean vector covariate,
+and $\epsilon_i$ denotes observational noise.
+%In other words, this is a scalar-on-hybrid regression where the hybrid covariates belong to $\bigl( \mathbb{L}^2[0,1] \bigr)^{  K} \times \mathbb{R}^p$.
+For notational convenience, we assume throughout that the responses and predictors are centered, so the intercept term can be omitted.
+
+In addition to the ill-posedness of the infinite-dimensional slope functions $\beta_k(t)$ and the high dimensionality of the predictors ($K + p$), a further challenge comes from the strong correlations between functional and scalar predictors.
+This paper addresses all three issues in a unified manner by introducing a hybrid partial least squares (PLS) regression framework defined on a novel hybrid Hilbert space.
 
@@
 	wavelets \citep{zhaoWaveletbasedLASSOFunctional2012},
-	and structure-aware regularization, such as roughness penalties \jongmin{comment:let's add citations here}.
+	and structure-aware regularization, such as roughness penalties
 
@@
 	\section{Background on partial least squares and its extension to hybrid predictors}
-	\jongmin{comment: I replaced the formal presentation of the naive algorithm with an   the scalar version and a brief outline of the pointwise hybrid  extension strategy.
-The main reason for this revision is that the hybrid inner product is introduced specifically to address the extension challenge, so it is more natural to present it after listing the challenges.
-Previously, the naive algorithm section relied on the hybrid inner product for normalization.}
+
 	For intuition, let us return to the high-dimensional Euclidean predictor setting $
@@
 We therefore formally define the Hilbert space of hybrid random predictors along with its corresponding complete inner product, and leverage them to extend Algorithm \ref{alg:scalar_pls}.
-	\jongmin{comment: I split the definition into three parts, adding completeness, separability, and the sigma-field.}
 	\begin{definition}[Hybrid space]\label{def:hilbert_space}
@@
 	Although Proposition \ref{proposition:eigen_noregul} offers an efficient way to estimate the PLS component direction $\hat{\xi}$, its functional components, $\hat{\xi}_1, \ldots, \hat{\xi}_K$, may not be smooth.
-\jongmin{added: Since  the final regression coefficient $\hat{\beta}$ is constructed as a linear combination of these directions (Section \ref{section:sub:regression_coeff}),
-		this can lead to a non-smooth $\hat{\beta}$} which complicates interpretation and can lead to overfitting and unstable predictions. 
+which complicates interpretation and can lead to overfitting and unstable predictions.
 	To address this, we propose a regularized extension that balances predictive performance with smoothness.
@@
 	Consequently, $\delta^{[l]}$ is obtained by minimizing a  
-	least squares criterion: \jongmin{comment: I removed the penalization because it makes proving the orthonormality of the PLS components in Proposition \ref{proposition: modified orthnormality of PLS components} impossible.
-Smoothness of $\beta$ seems to soley rely on the smoothness of $\xi$.
-See Section \ref{section:sub:regression_coeff}.}
+	least squares criterion: impossible. Smoothness of $\beta$ seems to soley rely on the smoothness of $\xi$. See Section \ref{section:sub:regression_coeff}.
 	\begin{equation}\label{def:argmin_pensse}
@@
 	The following proposition demonstrates that this residualization step can be performed simply, analogous to scalar PLS.
-	\begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}\jongmin{Previously stated as "we can show".}
+	\begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
 		Let us denote
@@
 	Proof of Lemma \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
-	\jongmin{proof needs to be revised}
 	Since $\widetilde{W}_i^{[l]}$ and $Y_i^{[l]}$ are assumed to have a sample mean of zero, their respective residuals, $\widetilde{W}_i^{[l+1]}$ and $Y_i^{[l+1]}$, also maintain a zero sample mean.
@@
 		\widehat{ \beta} = \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}
-		=\jongmin{added:}
 		\sum_{l=1}^L \left( \widehat{\nu}^{[l]} - \sum_{k=l+1}^L \widehat{\nu}^{[k]} \langle \widehat{\delta}^{[l]}, \widehat{\xi}^{[k]} \rangle_{\mathbb{H}} \right) \widehat{\xi}^{[l]}.
 	\end{equation*}
-	\jongmin{added: Note that if $L$ is too large, $\widehat{ \beta}$ can be wiggly even if $\widehat{\xi}^{[l]}$'s are smooth.}
 	Thus the number of PLS components $L$ to be estimated can be chosen by cross-validation.
@@
 	\subsection{ Tucker's Criterion  }\label{section:sub:tucker} 
-	\jongmin{comment:maybe we can move this section to precede the algorithm section. then the new structure will introduce population version first and introduce finite-sample estimation procedure.}
 	We now derive the population analogue of Algorithm~\ref{alg:hybrid_pls} and establish its key mathematical properties, namely the orthogonality of the PLS directions and scores, as well as convergence to the true response.
@@
 		\end{equation*} 
-		\jongmin{instead of showing $\mathcal{U}$ is compact, let's show $\mathcal{C}_{YW}$ is compact. This way, we don't need uniform continuiity of $\sigma_{YX}$.}
 		If 
@@
 
-	\section{Simulation studies}\jongmin{08/16/2025: re-starting. the writing here is not completed.}
+	\section{Simulation studies}
 	To evaluate the superiority of our method under complex dependency structures
@@
 
-	\medskip
-	\noindent
-	\textit{Matrix-normal setting.}
-	We begin by constructing predictors from a matrix-normal distribution, a framework that offers convenient and flexible control over the dependence structure across both rows and columns.
-Matrix-normal (MN) models, also known as Kronecker-separable covariance models, provide a principled approach to modeling multivariate data with structured covariance.
-Specifically, the matrix-normal distribution is defined as
+	\subsection{Synthetic data}
+	To generate functional predictors, we use a matrix-normal distribution, also known as a Kronecker-separable covariance model.
+For each of $i=1, \ldots,  n$, we create a $3 \times 100$ matrix, where each row represents the $i$th observation of a functional predictor with 100 evaluation points.
+This method gives us precise control over  cross-modal (between-row) dependence   and
+	smoothness of the curves (between-column dependence). 
 	\begin{equation*}
@@
 
+	We developed a data generation framework leveraging the matrix-normal distribution, an approach previously suggested by our advisor.
+The goal was to create a dataset with a specific, controllable correlation structure between functional and scalar predictors.
+	\begin{comment}
+	The synthetic dataset consisted of n 
+	sample
+	​
+	matrices, each of size 3×n 
+	col
+	​
+	, where n 
+	col
+\end{comment}	​
+	corresponds to the number of evaluation points for each curve.
+To introduce a structured dependence within each row, the row covariance matrix was set to mimic an AR(1) process, which is a special case of a Gaussian process.
+This ensures that each row exhibits the smooth, curve-like characteristics of a functional observation.
+
+	The first two rows of each matrix were treated as functional data.
+The third row was converted into a set of scalar predictors.
+This was accomplished by partitioning the third row into blocks and then averaging the values within each block.
+For instance, if the third row was (1,3,2,4,3,4) and we wanted to generate three scalar predictors, we would partition the row into (1,3), (2,4), and (3,4), yielding the scalar values 2.0,3.0, and 3.5.
+
+	\begin{comment}
 	\begin{figure}[ht!]
@@
 	\end{figure}
-
+\end{comment}
 	\begin{comment}
@@
 We designate nodes \(F_1\) and \(F_2\) as functional predictors and nodes \(V_1\), \(V_2\), and \(V_3\) as vector predictors.
-	%
+\begin{comment}
 	\begin{figure}
@@
 	\end{figure}
+\end{comment}
 	%
@@
 	}, demonstrate that our method consistently outperforms the baseline methods across all scenarios.
+	\begin{comment}
 	\begin{figure}
@@
 	\end{figure}
-
-	\section{Data Application} \jongmin{08/16/2025: re-starting. the writing here is not completed.}
+	\end{comment}
+
+	\section{Data Application}
 
@@
 	\subsection{}
-
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	%% Support information, if any,             %%
-	%% should be provided in the                %%
-	%% Acknowledgements section.                %%
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	\begin{acks}[Acknowledgments]
-		The authors would like to thank the anonymous referees, an Associate
-		Editor and the Editor for their constructive comments that improved the
-		quality of this paper.
-	\end{acks}
-
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	%% Funding information, if any,             %%
-	%% should be provided in the                %%
-	%% funding section.                         %%
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	\begin{funding}
-		The first author was supported by NSF Grant DMS-??-??????.
-
-		The second author was supported in part by NIH Grant ???????????.
-	\end{funding}
-
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	%% Supplementary Material, including data   %%
-	%% sets and code, should be provided in     %%
-	%% {supplement} environment with title      %%
-	%% and short description. It cannot be      %%
-	%% available exclusively as external link.  %%
-	%% All Supplementary Material must be       %%
-	%% available to the reader on Project       %%
-	%% Euclid with the published article.       %%
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	\begin{supplement}
-		\stitle{Title of Supplement A}
-		\sdescription{Short description of Supplement A.}
-	\end{supplement}
-	\begin{supplement}
-		\stitle{Title of Supplement B}
-		\sdescription{Short description of Supplement B.}
-	\end{supplement}
-
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	%%                  The Bibliography                       %%
-	%%                                                         %%
-	%%  imsart-nameyear.bst  will be used to                   %%
-	%%  create a .BBL file for submission.                     %%
-	%%                                                         %%
-	%%  Note that the displayed Bibliography will not          %%
-	%%  necessarily be rendered by Latex exactly as specified  %%
-	%%  in the online Instructions for Authors.                %%
-	%%                                                         %%
-	%%  MR numbers will be added by VTeX.                      %%
-	%%                                                         %%
-	%%  Use \cite{...} to cite references in text.             %%
-	%%                                                         %%
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-	%% if your bibliography is in bibtex format, uncomment commands:
-	\bibliographystyle{imsart-nameyear} % Style BST file
-	\bibliography{bibliography.bib}       % Bibliography file (usually '*.bib')
-
-	\appendix
-
-	\section{Overview of Appendix}
-	\begin{itemize}
-		\item Appendix \ref{section:proof:lemma:hybrid_hilbert_space} proves that our defined product space is a separable Hilbert space.
-		\item Appendix \ref{section:proof:section:sub:iterative}  provides the proofs for the core problem formulations and computational schemes of the iterative steps for estimating the PLS direction and performing residualization.
-		\item Appendix \ref{section:proof:section:sub:tucker} provides proof of Theorem \ref{theorem:population_PLS}, 
-		demonstrating that the population-level version of the optimization problem solved at each step is well-defined.
-	\end{itemize}
-	\section{Proof of Lemma \ref{lemma:hybrid_hilbert_space}}\label{section:proof:lemma:hybrid_hilbert_space}
-	\begin{proof}
-		Both $\mathbb{L}^2[0,1]$ and $\mathbb{R}^p$ are Hilbert spaces, with their inner products, norms, and metrics corresponding to the terms defined in equation \eqref{eq: hybrid inner product}.
-A finite Cartesian product of Hilbert spaces, equipped with an $\ell_2$ norm of the component metrics (which is our metric), is also a Hilbert space.
-		Furthermore, both of 	 $\mathbb{L}^2[0,1]$ and $\mathbb{R}^p$ are separable.
-		For $\mathbb{L}^2[0,1]$, the set of all polynomials with rational coefficients is a countable and dense subset.
-		For $\mathbb{R}^p$,  the set of all vectors with rational components forms a countable and dense subset.
-		A finite Cartesian product of separable spaces is also separable.
-		Therefore $\mathbb{H} = \bigl( \mathbb{L}^2[0,1] \bigr)^K \times \mathbb{R}^p$ is separable.
-	\end{proof}
-	\section{Proof of Section \ref{section:sub:iterative}}\label{section:proof:section:sub:iterative}
-
-	This section provides the proofs for the core problem formulations and computational schemes of the iterative steps for estimating the PLS direction and performing residualization.
-	Appendices \ref{section:proof:proposition:linear_regul_system_unregularized} and \ref{section:proof:proposition:eigen_regul} derive the eigenproblem formulations for unregularized and regularized PLS direction estimation, respectively.
-	Appendices \ref{section:proof:proposition:linear_regul} and \ref{section:proof:proposition:closed_form_orthgonalization} provide proofs for the simple computation schemes for regularized PLS direction estimation and residualization, respectively.
-	\subsection{Proof of Proposition \ref{proposition:eigen_noregul}  }\label{section:proof:proposition:linear_regul_system_unregularized}
-	\begin{proof}
-		Let $\xi = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta}) \in \mathbb{H}$.
-Assume that each functional component $\xi_j \in \mathbb{L}^2([0,1])$ lies in the span of the basis functions ${b_1(t), \ldots, b_M(t)}$ and can be written as
-		\begin{equation*}
-			\xi_j(t) := 
-			\sum_{m=1}^M d_{jm} \, b_m(t), \quad j = 1, \ldots, K,
-		\end{equation*}
-		with coefficient vectors $\boldsymbol{\gamma}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$.
-		Then, 
-		the empirical covariance is
-		computed as follows:
-		\begin{align*}
-			\widehat{\textnormal{Cov}} (
-			\langle \widetilde{W}, \xi  \rangle_{\mathbb{H}}, Y 
-			) 
-			&=  %1
-			\frac{1}{n} 
-			\sum 
-			\limits_{i=1}^n 
-			y_i
-			\langle \widetilde{W}_i, \xi \rangle_\mathbb{H} \\
-			&= %2
-			\frac{1}{n} 
-			\sum \limits_{i=1}^n
-			y_i
-			\biggl(
-			\sum_{j=1}^K
-			\langle \widetilde{X}_{ij}, \xi_j \rangle  
-			+
-			\mathbf{Z}_i^\top 
-			\boldsymbol{\zeta} 
-			\biggr)
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&= %3
-			\frac{1}{n}
-			\sum
-			\limits_{i=1}^n 
-			y_i
-			\biggl( \sum \limits_{k=1}^K \int_0^1 \widetilde{X}_{ij}(t) \, \xi_j(t) \, dt \biggr)
-			+
-			\frac{1}{n}
-			\sum
-			\limits_{i=1}^n
-			y_i
-			( \mathbf{Z}_i^\top \boldsymbol{\zeta} )
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=  
-			\frac{1}{n} \sum \limits_{i=1}^n 
-			y_i
-			\biggl\{ 
-			\sum \limits_{k=1}^K \int_0^1
-			\biggl(
-			\sum_{m=1}^M \theta_{ijm} b_{m}(t) 
-			\biggr) 
-			\biggl(
-			\sum_{m'=1}^M d_{jm'} b_{m'}(t) 
-			\biggr) 
-			dt
-			\biggr\}  
-			+
-			\frac{1}{n}
-			\mathbf{y}^\top
-			Z \boldsymbol{\zeta} 
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=  
-			\frac{1}{n} \sum \limits_{i=1}^n 
-			y_i
-			\biggl\{ 
-			\sum \limits_{k=1}^K 
-			\sum_{m=1}^M
-			\sum_{m'=1}^M  
-			\theta_{ijm}
-			d_{jm'}
-			\int_0^1
-			b_{m}(t) 
-			b_{m'}(t) 
-			dt
-			\biggr\}  
-			+
-			\frac{1}{n}
-			\mathbf{y}^\top
-			Z \boldsymbol{\zeta} 
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=  
-			\sum \limits_{k=1}^K 
-			\biggl\{
-			\frac{1}{n} \sum \limits_{i=1}^n 
-			y_i
-			(
-			\boldsymbol{\theta}_{ij}^\top
-			B
-			\boldsymbol{\gamma}_j
-			)  
-			\biggr\}
-			+
-			\frac{1}{n}
-			\mathbf{y}^\top
-			Z \boldsymbol{\zeta}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=  
-			\frac{1}{n}
-			\biggl(
-			\sum \limits_{k=1}^K 
-			\mathbf{y}^\top
-			\Theta_{j}
-			B
-			\boldsymbol{\gamma}_j
-			+
-			\mathbf{y}^\top
-			Z \boldsymbol{\zeta} 
-			\biggr)
-		\end{align*}	
-		Building on this computation, the squared empirical covariance is
-		expressed as the quadratic form involving the matrix $V$ defined in \eqref{def:V_matrix}:
-		%	The objective function matches that of \eqref{eq: Regularized generalized rayleigh quotient equation}, takin
-		\begin{align*}
-			\widehat{\textnormal{Cov}}^2 (
-			\langle \widetilde{W}, \xi  \rangle_{\mathbb{H}}, Y 
-			)  
-			&= 
-			\frac{1}{n^2}
-			\biggl(
-			\sum \limits_{k=1}^K 
-			\mathbf{y}^\top
-			\Theta_{j}
-			B
-			\boldsymbol{\gamma}_j
-			+
-			\mathbf{y}^\top
-			Z \boldsymbol{\zeta} 
-			\biggr)^2
-			%%%%%%%%%%%%%%%%%%%%
-			\\	&=
-			\frac{1}{n^2} 
-			(
-			\mathbf{y}^\top
-			\Theta
-			\mathbb{B}  
-			\boldsymbol{\xi}
-			)^2
-			\\
-			&	= 
-			\frac{1}{n^2} 
-			\boldsymbol{\xi}^\top
-			(\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top 
-			\boldsymbol{\xi}
-			\\&=
-			\boldsymbol{\xi}^\top
-			V 
-			\boldsymbol{\xi}.
-			\numberthis \label{covariance_squares_as_quadratic_form}
-		\end{align*}
-		The squared norm of $\xi$ in the hybrid Hilbert space $\mathbb{H}$ 
-		%can be expressed as the inner product on $(\mathbb{R}^M)^K \times \mathbb{R}^p$ defined in Lemma~\ref{lemma:valid_inner_product_tuple} as follows:
-		is computed as follows:
-		\begin{align*}
-			\langle {\xi},{\xi} \rangle_{\mathbb{H}}
-			&=
-			\sum_{j=1}^K
-			\int_0^1
-			\xi_j(t) \, \xi_j(t)
-			\, dt
-			+
-			\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=
-			\sum \limits_{j=1}^K \int_0^1
-			\biggl(
-			\sum_{m=1}^M d_{jm} b_{m}(t) 
-			\biggr) 
-			\biggl(
-			\sum_{m'=1}^M d_{jm'} b_{m'}(t) 
-			\biggr) 
-			dt
-			+
-			\boldsymbol{\zeta}^\top \boldsymbol{\zeta}  
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=
-			\sum \limits_{j=1}^K 
-			\sum_{m=1}^M
-			\sum_{m'=1}^M
-			d_{jm}
-			d_{jm'}
-			\int_0^1
-			b_{m}(t) 
-			b_{m'}(t) 
-			dt
-			+
-			\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=
-			\sum \limits_{j=1}^K 
-			\boldsymbol{\gamma}_j^\top
-			B
-			\boldsymbol{\gamma}_j
-			+
-			\boldsymbol{\zeta}^\top \boldsymbol{\zeta},
-			%%%%%%%%%%%%%
-			\\&=
-			\boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi}
-			\numberthis \label{unit_norm_as_quadform}
-		\end{align*}
-		Therefore, the covariance maximization problem \eqref{def:maximizer_squared_empirical_cov} is equivalent to the generalized Raleigh quotient \eqref{eq: Unregularized generalized rayleigh quotient equation}.
-This completes  the proof of Proposition~\ref{proposition:eigen_noregul}.
-
-		\subsection{Proof of Proposition \ref{proposition:eigen_regul} }\label{section:proof:proposition:eigen_regul}
-		The penalization term 
-		$\sum \limits_{j=1}^K \lambda_j 
-		\operatorname{PEN}(\xi_K)$
-		can be written in matrix form as:
-		\begin{align*}
-			\sum \limits_{j=1}^K 
-			\lambda_j
-			\operatorname{PEN}({\xi}_j)
-			&=
-			\sum \limits_{j=1}^K 
-			\lambda_j
-			\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
-			\\&=
-			\sum \limits_{j=1}^K 
-			\lambda_j
-			\int_0^1 \bigl\{ \sum_{l=1}^M \theta_{ijl} \, b_l^{\prime \prime}(t) \bigr\}^2 dt
-			\\&	 =
-			%%%%%%%%%%%%%%%%%%%
-			\sum \limits_{j=1}^K 
-			\lambda_j
-			\sum_{l=1}^M
-			\sum_{m=1}^M
-			\theta_{ijl} \theta_{ijm}
-			\int_0^1
-			\, b_l^{\prime \prime}(t) 
-			b_m^{\prime \prime}(t)
-			dt
-			\\&	 =
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\sum \limits_{j=1}^K
-			\lambda_j
-			\boldsymbol{\gamma}_j^\top
-			B^{\prime \prime} 
-			\boldsymbol{\gamma}_j
-			%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&= 
-			\boldsymbol{\xi}^{\top} \Lambda \mathbb{B}^{\prime \prime} \boldsymbol{\xi},
-			\numberthis \label{pen_as_matrix}
-		\end{align*}
-		where $\boldsymbol{\xi}$ is the concatenated coefficient vector form of $\xi$ as defined in \eqref{def:maximizer_euclidean_form}, $\mathbb{B}^{\prime\prime}$ is defined in \eqref{def:gram_block}, and $\Lambda$ is defined in \eqref{def:Lambda}.
-
-		Combining this with \eqref{unit_norm_as_quadform}, 
-		we can compute
-		\begin{equation*}
-			\| \xi  \|_\mathbb{H} +  \sum \limits_{j=1}^K \lambda_j 
-			\operatorname{PEN}(\xi_K) 
-			= 
-			\boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi}
-			+ 
-			\boldsymbol{\xi}^{\top} \Lambda \mathbb{B}^{\prime \prime} \boldsymbol{\xi}
-			=
-			\boldsymbol{\xi}^\top 
-			(
-			\mathbb{B}
-			+
-			\Lambda \mathbb{B}^{\prime \prime})
-			\boldsymbol{\xi}.
-		\end{equation*}
-		This computation along with \eqref{covariance_squares_as_quadratic_form} implies that the covariance maximization problem  
-		\eqref{def:maximizer_squared_empirical_cov_reg} is equivalent to the generalized Raleigh quotient \eqref{eq: Regularized generalized rayleigh quotient equation}.
-This completes  the proof of Proposition \ref{proposition:eigen_regul}.
-
-	\end{proof}
-
-	\subsection{Proof of Proposition  \ref{proposition:linear_regul}}\label{section:proof:proposition:linear_regul}
-	\begin{proof}
-		The optimization problem 
-		\eqref{eq: Regularized generalized rayleigh quotient equation} can be written as
-		\begin{align*}
-			\max_{\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K \in \mathbb{R}^M,\;
-				\boldsymbol{\zeta} \in \mathbb{R}^p}~&
-			\frac{1}{n^2}
-			\left(
-			\sum_{j=1}^K 
-			\mathbf{y}^\top
-			\Theta_j
-			B  
-			\boldsymbol{\gamma}_j
-			+
-			\mathbf{y}^\top
-			Z \boldsymbol{\zeta} 
-			\right)^2,
-			\\
-			\text{subject to}\quad&
-			\sum_{j=1}^K 
-			\boldsymbol{\gamma}_j^\top
-			(B + \lambda_j B^{\prime\prime})
-			\boldsymbol{\gamma}_j
-			+
-			\boldsymbol{\zeta}^\top \boldsymbol{\zeta} = 1.
-		\end{align*}
-
-		Let $\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M$ and $\mathbf{v} := Z^\top \mathbf{y} \in \mathbb{R}^p$. These are fixed problem data. Then the objective becomes
-		\[
-		\frac{1}{n^2}
-		\left(
-		\sum_{j=1}^K 
-		\mathbf{u}_j^\top \boldsymbol{\gamma}_j
-		+
-		\mathbf{v}^\top \boldsymbol{\zeta}
-		\right)^2.
-		\]
-		The objective function is continuous.
-The constraint defines the boundary of an ellipsoid in a finite-dimensional Euclidean space, the feasible set is compact.
-By the Weierstrass Extreme Value Theorem (see, e.g., Theorem 2.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}), a global maximizer exists.
-The constraint function is continuously differentiable and its gradient vanishes only at the origin, which is not feasible.
-		Thus the gradient  is nonzero at all feasible points.
-		Hence, the Linear Independence Constraint Qualification (LICQ) holds, and the Karush-Kuhn-Tucker (KKT) conditions are necessary for local optimality (see, e.g., Theorem 5.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}).
-
-		Define the Lagrangian:
-		\[
-		\mathcal{L}(\{\boldsymbol{\gamma}_j\}, \boldsymbol{\zeta}, \mu) 
-		:= 
-		\left( \sum_{j=1}^K \mathbf{u}_j^\top  \boldsymbol{\gamma}_j + \mathbf{v}^\top \boldsymbol{\zeta} \right)^2
-		- 
-		\mu 
-		\left[
-		\sum_{j=1}^K \boldsymbol{\gamma}_j^\top (B + \lambda_j B^{\prime\prime}) \boldsymbol{\gamma}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta} - 1
-		\right].
-		\]
-
-		Let $s := \dfrac{2}{n^2} \left( \sum_{j=1}^K \mathbf{u}_j^\top \boldsymbol{\gamma}_j + \mathbf{v}^\top \boldsymbol{\zeta} \right)$. The KKT conditions require that:
-		\begin{align}
-			\nabla_{\boldsymbol{\gamma}_j} \mathcal{L} &= 
-			s \mathbf{u}_j - 2\mu (B + \lambda_j B^{\prime\prime}) \boldsymbol{\gamma}_j = 0, \quad \text{for } j = 1, \ldots, K, \label{eq:lag_grad_gamma} \\
-			\nabla_{\boldsymbol{\zeta}} \mathcal{L} &= 
-			s \mathbf{v} - 2\mu \boldsymbol{\zeta} = 0. \label{eq:lag_grad_zeta}
-		\end{align}
-
-		From \eqref{eq:lag_grad_gamma} and \eqref{eq:lag_grad_zeta}, we have
-		\[
-		(B + \lambda_j B^{\prime\prime}) \boldsymbol{\gamma}_j = \frac{s}{2\mu} \mathbf{u}_j, \quad
-		\boldsymbol{\zeta} = \frac{s}{2\mu} \mathbf{v}, \quad \text{for } j = 1, \ldots, K.
-		\]
-		This implies that for any local maximizer, there exists $c \ne 0$ such that 
-		\[
-		\boldsymbol{\gamma}_j = c (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j, \quad
-		\boldsymbol{\zeta} = c \mathbf{v}, \quad \text{for } j = 1, \ldots, K.
-		\]
-		Since we assumed in Section~\ref{sec: finite basis approximation} that the functions $\{b_m(t)\}$ and their second derivatives are linearly independent, both $B$ and $B^{\prime\prime}$ are positive definite (see, for example, Theorem 273 of \citealp{gockenbachFiniteDimensionalLinearAlgebra2010}).
-As positive definiteness is preserved under conic combinations, $B + \lambda_j B^{\prime\prime}$ is also positive definite.
-
-		A local maximizer must also be primal feasible. Substituting the conditions above in to the primal constraint:
-		\begin{align*}
-			\sum_{j=1}^K 
-			\left( c (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j \right)^\top 
-			(B + \lambda_j B^{\prime\prime}) 
-			\left( c (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j \right)
-			+ c^2 \mathbf{v}^\top \mathbf{v} &= 1 \\
-			\Rightarrow 
-			c^2 \left( \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v} \right) &= 1.
-		\end{align*}
-
-		Solving for $c^2$ gives:
-		\[
-		c^2 = \left( \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v} \right)^{-1}.
-		\]
-
-		Hence, the unique maximizer (up to sign) is:
-		\[
-		\boldsymbol{\gamma}_j^\ast = \frac{1}{\sqrt{q}} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j, \quad
-		\boldsymbol{\zeta}^\ast = \frac{1}{\sqrt{q}} \mathbf{v},
-		\]
-		where
-		\[
-		q := \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v}.
-		\]
-
-		This completes the proof of Proposition \ref{section:proof:proposition:linear_regul}.
-
-	\end{proof}
-
-	\subsection{Proof of Lemma \ref{proposition:closed_form_orthgonalization} }\label{section:proof:proposition:closed_form_orthgonalization}
-	For notational simplicity, we omit the iteration superscript $[l]$.
-	Recall from  \eqref{def:plsscore} that
-	$\hat{\rho}_i
-	=
-	\langle \widetilde{W}_i, \, \hat{\xi} \rangle_{\mathbb{H}}$.
-	Using the basis expansion coefficient notation from \eqref{def:truncated_zeta_and_delta}, \eqref{def:coef_vector_form}, \eqref{def:theta}, and \eqref{def:B_matrix}, the full vector of PLS scores $\hat{\boldsymbol{\rho}}  = (\hat{\rho}_1, \ldots, \hat{\rho}_n)^\top$
-	is computed through the following matrix multiplication:
-	\begin{equation}\label{score_inner_product_all_n}
-		\hat{\boldsymbol{\rho}}^\top = \sum_{k=1}^K ( \hat{\boldsymbol{\gamma}}_j )^\top B \, \Theta_j^\top + \boldsymbol{\zeta}^\top \mathbf{Z}^\top.
-	\end{equation}
-	The least square criterion   can be decomposed as follows:
-	\begin{align*}
-		\operatorname{SSE}( \delta) &= \sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta, \, \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta \rangle_{\mathbb{H}} \\
-		&= 
-		\underbrace{
-			\sum_{i=1}^n \langle \widetilde{W}_i^{[l]}, \, \widetilde{W}_i^{[l]} \rangle_{\mathbb{H}}}_{A} 
-		\underbrace{
-			-2 \sum_{i=1}^n \hat{\rho}_i^{[l]} \langle \delta, \, \widetilde{W}_i^{[l]} \rangle_{\mathbb{H}} 
-		}_{B_1(\boldsymbol{\delta})}
-		\underbrace{
-			+ 
-			(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})
-			\langle \delta, \, \delta \rangle_{\mathbb{H}}
-		}_{B_2(\boldsymbol{\delta})}
-	\end{align*}
-	\begin{comment}
-		\begin{align*}
-			\operatorname{PENSSE}( \delta) &= \sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta, \, \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta \rangle_{\mathbb{H}} + \tau \sum_{j=1}^K\operatorname{PEN}(\delta_j) \\
-			&= 
-			\underbrace{
-				\sum_{i=1}^n \langle \widetilde{W}_i^{[l]}, \, \widetilde{W}_i^{[l]} \rangle_{\mathbb{H}}}_{A} 
-			\underbrace{
-				-2 \sum_{i=1}^n \hat{\rho}_i^{[l]} \langle \delta, \, \widetilde{W}_i^{[l]} \rangle_{\mathbb{H}} 
-			}_{B_1(\boldsymbol{\delta})}
-			\underbrace{
-				+ 
-				(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})
-				\langle \delta, \, \delta \rangle_{\mathbb{H}}
-			}_{B_2(\boldsymbol{\delta})}
-			\underbrace{
-				+ 
-				\tau \sum_{j=1}^K\operatorname{PEN}(\delta_j)
-			}_{B_3(\boldsymbol{\delta})}
-		\end{align*}
-	\end{comment}
-	Here, part $A$ does not contain $\delta$, so it does not contribute to the minimization problem.
-
-	Let $\boldsymbol{\delta}:= (\pi_1^\top, \ldots, \pi_K^\top, \boldsymbol{\chi}^\top )^\top$ be the $MK+p$-dimensional concatenated vector of basis coefficients and the scalar part of $\boldsymbol{\delta}$.
-	%Abusing notation, we treat $\operatorname{PENSSE}$ as a function of $\boldsymbol{\delta}$.
-	Abusing notation, we treat $\operatorname{SSE}$ as a function of $\boldsymbol{\delta}$.
-	Next, We will now demonstrate that the combined term $
-	%B_1(\boldsymbol{\delta}) + B_2(\boldsymbol{\delta}) + B_3(\boldsymbol{\delta})
-	B_1(\boldsymbol{\delta}) + B_2(\boldsymbol{\delta})
-	$ is a quadratic function of $\boldsymbol{\delta}$, by expanding its component functions:
-	\begin{align*}
-		B_1(\boldsymbol{\delta}) &= 
-		- 2\sum_{i=1}^n \hat{\rho}_i  \langle \delta, \, \widetilde{W}_i  \rangle_{\mathbb{H}} 
-		=
-		- 2\hat{\boldsymbol{\rho}}^\top 
-		\biggl(
-		\sum_{j=1}^K \Theta_j B \boldsymbol{\pi}_j
-		+\mathbf{Z} \boldsymbol{\chi}
-		\biggr),
-		%%%%%%%%%%%%%%%%%%%%%%%
-		\\ 
-		B_2(\boldsymbol{\delta})
-		&=
-		(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})
-		\langle \delta, \, \delta \rangle_{\mathbb{H}}
-		=
-		(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) 
-		\biggl(
-		\sum_{j=1}^K \pi_j^\top B \pi_j
-		+\boldsymbol{\chi}^\top \boldsymbol{\chi}
-		\biggr),
-		\\
-		%	B_3(\boldsymbol{\delta}) &= \tau \sum_{j=1}^K\operatorname{PEN}(\delta_j) = \tau \boldsymbol{\delta} B^{''} \boldsymbol{\delta},
-	\end{align*}
-	%where the expansion of $B_3(\boldsymbol{\delta})$ leverages the computation in \eqref{pen_as_matrix}.
-	Now we compute the gradients:
-	\begin{align*}
-		\nabla_{\boldsymbol{\pi}_j}
-		B_1(\boldsymbol{\delta}) 
-		&= -2
-		B
-		\Theta_j^\top
-		\hat{\boldsymbol{\rho}}  ,~
-		j = 1, \ldots, K,
-		\quad
-		\nabla_{\boldsymbol{\chi}}
-		B_1(\boldsymbol{\delta}) 	  
-		= -2\mathbf{Z}^\top  \hat{\boldsymbol{\rho}},
-		%
-		\\
-		\nabla_{\boldsymbol{\pi}_j}
-		B_2(\boldsymbol{\delta}) 
-		&= 
-		2
-		(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) 
-		B 	\boldsymbol{\pi}_j
-		,~
-		j = 1, \ldots, K,
-		\quad
-		\nabla_{\boldsymbol{\chi}}
-		B_2(\boldsymbol{\delta}) 
-		=
-		2(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})\boldsymbol{\chi} ,
-		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		%\\ \nabla_{\boldsymbol{\pi}_j} B_3(\boldsymbol{\delta})  &=  2 \tau B^{\prime \prime }	\boldsymbol{\pi}_j ,~ j = 1, \ldots, K, \quad \nabla_{\boldsymbol{\chi}} B_3(\boldsymbol{\delta})  =0.
-	\end{align*}
-	The Hessian of 
-	$\operatorname{SSE}( \boldsymbol{\delta})$ is then given by 
-	$
-	2 	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})  B.
-	$
-	\begin{comment}
-		The Hessian of 
-		$\operatorname{PENSSE}( \boldsymbol{\delta})$ is then given by 
-		$
-		2 	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})  B
-		+
-		2
-		\tau
-		B^{\prime \prime}.
-		$
-	\end{comment}
-	%Since we assumed in Section \ref{sec: finite basis approximation} that both $B'$ and $B''$ are positive definite, $\operatorname{PENSSE}( \delta)$ is convex.
-Consequently, the gradient vanishes at its unique minimizer:
-	Since   $B$ and is positive definite, $\operatorname{SSE}( \delta)$ is convex. Consequently, the gradient vanishes at its unique minimizer:
-	\begin{align*}
-		\nabla_{\boldsymbol{\pi}_j}	\operatorname{SSE}( \hat{\boldsymbol{\delta}} )
-		&	=
-		-2
-		B
-		\Theta_j^\top
-		\hat{\boldsymbol{\rho}}
-		+
-		2	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) 
-		B 	\hat{\boldsymbol{\pi}}_j
-		=
-		0,~
-		j = 1, \ldots, K,
-		\\
-		\nabla_{\boldsymbol{\chi} }	\operatorname{SSE}( \hat{\boldsymbol{\delta}} )
-		&=
-		-2\mathbf{Z}^\top  \hat{\boldsymbol{\rho}}
-		+
-		2 (\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) \hat{\boldsymbol{\chi} }
-		=
-		0,
-	\end{align*}
-	\begin{comment}
-		\begin{align*}
-			\nabla_{\boldsymbol{\pi}_j}	\operatorname{PENSSE}( \hat{\boldsymbol{\delta}} )
-			&	=
-			-2
-			B
-			\Theta_j^\top
-			\hat{\boldsymbol{\rho}}
-			+
-			2	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) 
-			B 	\hat{\boldsymbol{\pi}}_j
-			+
-			2
-			B^{\prime \prime }	\hat{\boldsymbol{\pi}}_j
-			=
-			0,~
-			j = 1, \ldots, K,
-			\\
-			\nabla_{\boldsymbol{\chi} }	\operatorname{PENSSE}( \hat{\boldsymbol{\delta}} )
-			&=
-			-2\mathbf{Z}^\top  \hat{\boldsymbol{\rho}}
-			+
-			2 (\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) \hat{\boldsymbol{\chi} }
-			=
-			0,
-		\end{align*}
-	\end{comment}
-	providing the following closed-form solution:
-	\begin{comment}
-		\begin{equation*}
-			\hat{\boldsymbol{\pi}}_j\\
-			=
-			\bigl\{
-			(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})  B
-			+
-			\tau
-			B^{\prime \prime}
-			\bigr\}^{-1}
-			B
-			\Theta_j^\top
-			\hat{\boldsymbol{\rho}}
-			~
-			j = 1, \ldots, K,
-			%%%%%%%%%%%%%%%%%%%%%%%%
-			\quad
-			\hat{\boldsymbol{\chi} }
-			=
-			\frac{1}{(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})}
-			\mathbf{Z}^\top  \hat{\boldsymbol{\rho}}.
-		\end{equation*}
-	\end{comment}
-	\begin{equation*}
-		\hat{\boldsymbol{\pi}}_j\\
-		=
-		\bigl\{
-		(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})  B
-		\bigr\}^{-1}
-		B
-		\Theta_j^\top
-		\hat{\boldsymbol{\rho}}
-		=
-		\frac{1}{\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}} \Theta_j^\top
-		\hat{\boldsymbol{\rho}}
-		~
-		j = 1, \ldots, K,
-		%%%%%%%%%%%%%%%%%%%%%%%%
-		\quad
-		\hat{\boldsymbol{\chi} }
-		=
-		\frac{1}{(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})}
-		\mathbf{Z}^\top  \hat{\boldsymbol{\rho}}.
-	\end{equation*}
-	\begin{comment}
-		The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
-		$\hat{\delta}^{[l]}   \in \widetilde{\mathbb{H}}$, has basis coefficients
-		\begin{equation*}
-			\hat{\boldsymbol{\pi}}_j^{[l]}
-			=
-			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
-			\Theta_j^{[l] \top}
-			\hat{\boldsymbol{\rho}}^{[l]}
-			,
-			~
-			j = 1, \ldots, K,
-		\end{equation*}
-		and scalar parts given by:
-		\begin{equation*}
-			\hat{\boldsymbol{\chi} }^{[l]}
-			=
-			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
-			\mathbf{Z}^{[l] \top}  \hat{\boldsymbol{\rho}}^{[l]}.
-		\end{equation*}
-	\end{comment}
-	Expanding with respect to these coefficients, we obtain
-	\begin{equation*}
-		\delta^{[l]}
-		= 
-		\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
-		\sum_{i=1}^n 
-		\widehat{\rho}_i^{[l]}
-		\widetilde{W}_i^{[l]}.
-	\end{equation*}
-	On the other hand since $\mathbf{y}^{[l]}$ and  
-	$\hat{\boldsymbol{\rho}}^{[l]}$ are zero-mean,
-	it is well known that the least square estimate of linear regression coefficient is compuated as $\hat{\nu}^{[l]} =  
-	\frac{
-		\mathbf{y}^{[l] \top }  \hat{\boldsymbol{\rho}}^{[l]}
-	}{
-		\| \hat{\boldsymbol{\rho}}^{[l]} \|_2^2}$.
-	This completes the proof of Lemma \ref{proposition:closed_form_orthgonalization}.
-
-	\section{Proof of Lemma \ref{lemma:recursive}}\label{section:proof:lemma:recursive}
-	\begin{proof}We prove the lemma using mathematical induction.
-
-		\medskip
-		\noindent
-		\textit{Base case ($l=1$).}~
-		For $l=1$, the lemma states $\widehat{\rho}_i^{[1]} = \langle W_i, \widehat{\iota}^{[1]} \rangle_{\mathbb{H}}$.
-Since  $\widehat{\iota}^{[1]} := \widehat{\xi}^{[1]}$ and $W^{[1]}_i = W_i$, the base case holds.
-
-		\medskip
-		\noindent
-		\textit{Inductive steps.}~		
-		Assume   $\widehat{\rho}_i^{[u]} = \langle W_i, \widehat{\iota}^{[u]} \rangle_{\mathbb{H}}$ for $u =1 , \ldots, l$.
-We want to show that $\widehat{\rho}_i^{[l+1]} = \langle W_i, \widehat{\iota}^{[l+1]} \rangle_{\mathbb{H}}$.
-		Recall from  \eqref{def:plsscore} and Lemma \ref{proposition:closed_form_orthgonalization} that we have
-		\begin{equation}
-			\widehat{\rho}_i^{[l+1]} = \langle \widetilde{W}_i^{[l+1]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}},
-			\quad
-			\widetilde{W}_i^{[l+1]} = \widetilde{W}_i^{[l]} - \widehat{\rho}_i^{[l]} \widehat{\delta}^{[l]}
-		\end{equation}
-		Combining these two, we have
-		\begin{equation}\label{rholp1}
-			\widehat{\rho}_i^{[l+1]} = \langle \widetilde{W}_i^{[l]} - \widehat{\rho}_i^{[l]} \widehat{\delta}^{[l]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} 
-			=
-			\langle \widetilde{W}_i^{[l]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} - \widehat{\rho}_i^{[l]} \langle \widehat{\delta}^{[l]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}}.
-		\end{equation}
-		Next,
-		we can express $\widetilde{W}_i^{[l]}$ in terms of the original predictor $W_i$ by recursively applying  Lemma \ref{proposition:closed_form_orthgonalization}:
-		$$ \widetilde{W}_i^{[l]} = \widetilde{W}_i^{[l-1]} - \widehat{\rho}_i^{[l-1]} \widehat{\delta}^{[l-1]} = \ldots = W_i - \sum_{u=1}^{l-1} \widehat{\rho}_i^{[u]} \widehat{\delta}^{[u]} $$
-		Substituting this into our equation \eqref{rholp1}, we have:
-		\begin{align*}
-			\widehat{\rho}_i^{[l+1]} 
-			&= \left\langle W_i - \sum_{u=1}^{l-1} \widehat{\rho}_i^{[u]} \widehat{\delta}^{[u]}, \widehat{\xi}^{[l+1]} \right\rangle_{\mathbb{H}} - \widehat{\rho}_i^{[l]} \langle \widehat{\delta}^{[l]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}}
-			\\&=
-			\langle W_i, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} - \sum_{u=1}^{l-1} \widehat{\rho}_i^{[u]} \langle \widehat{\delta}^{[u]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} - \widehat{\rho}_i^{[l]} \langle \widehat{\delta}^{[l]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}}
-			\\&=
-			\langle W_i, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} - \sum_{u=1}^{l} \widehat{\rho}_i^{[u]} \langle \widehat{\delta}^{[u]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}}
-			\\& \overset{(i)}{=}
-			\langle W_i, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} - \sum_{u=1}^{l} \langle \widehat{\delta}^{[u]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} \langle W_i, \widehat{\iota}^{[u]} \rangle_{\mathbb{H}}
-			%%%%%%%%%%%%%%%%%%%%%%%%
-			\\& = 
-			\langle W_i, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}}
-			-
-			\left\langle W_i,   \sum_{u=1}^{l} \langle \widehat{\delta}^{[u]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} \widehat{\iota}^{[u]} \right\rangle_{\mathbb{H}} 
-			%%%%%%%%%%%%%%%%%%%%%%%%
-			\\& = 
-			\left\langle W_i, \widehat{\xi}^{[l+1]} - \sum_{u=1}^{l} \langle \widehat{\delta}^{[u]}, \widehat{\xi}^{[l+1]} \rangle_{\mathbb{H}} \widehat{\iota}^{[u]} \right\rangle_{\mathbb{H}} 
-			\\&= \widehat{\rho}_i^{[l+1]}.
-		\end{align*}
-		where step $(i)$ uses the inductive hypothesis $\langle W_i, \widehat{\iota}^{[u]} \rangle_{\mathbb{H}} = \widehat{\rho}_i^{[u]}$ for all $u \leq l$.
-		By the principle of mathematical induction, the lemma holds for all $l \ge 1$. This completes the proof of Lemma \ref{lemma:recursive}.
-	\end{proof}
-
-	\section{Proof of Section \ref{section:sub:tucker}}\label{section:proof:section:sub:tucker}
-	This section provides proof of Theorem \ref{theorem:population_PLS}, 
-	demonstrating that the population-level version of the optimization problem solved at each step is well-defined, and 
-	proofs of the intermediate lemmas that support the main theorem.
-	\subsection{Proof of  Lemma \ref{lemma:cross_cov_functional} }\label{section:proof:lemma:cross_cov_functional}
-	\jongmin{An alternative proof to the compactness of $\mathcal{U}$; rather than directly showing $\mathcal{U}$ is compact, we show $\mathcal{C}_{YW}$ is compact}
-	\begin{proof} 
-		Any bounded linear functional from a Hilbert space to  $\mathbb{R}$  is a compact operator.
-		This is because the image of any bounded set under such a functional is a bounded set in $\mathbb{R}$,
-		and by Bolzano-Weierstrass Theorem, every bounded sequence of real numbers has a convergent subsequence.
-		Therefore,  to show that $\mathcal{C}_{YW}$ is a compact operator, it suffices to show that 
-		$\mathcal{C}_{YW}$ is a bounded linear functional.
-
-		\medskip
-		\noindent
-		\textit{Linearity.}~	  
-		The operator $\mathcal{C}_{YW}: \mathbb{H} \rightarrow \mathbb{R}$ is defined as 
-		$\mathcal{C}_{YW} h = \langle \Sigma_{YW}, h \rangle_\mathbb{H}$.
-		For any $h_1, h_2 \in \mathbb{H}$ and scalar $c \in \mathbb{R}$, the linearity of the inner product implies: \begin{align*} \mathcal{C}_{YW}(h_1 + h_2) &= \langle \Sigma_{YW}, h_1 + h_2 \rangle_\mathbb{H} = \langle \Sigma_{YW}, h_1 \rangle_\mathbb{H} + \langle \Sigma_{YW}, h_2 \rangle_\mathbb{H} = \mathcal{C}_{YW} h_1 + \mathcal{C}_{YW} h_2,
-			\\ 
-			\mathcal{C}_{YW}(c h) &= \langle \Sigma_{YW}, c h \rangle_\mathbb{H} = c \langle \Sigma_{YW}, h \rangle_\mathbb{H} = c \, \mathcal{C}_{YW} h. \end{align*}
-		Thus, $\mathcal{C}_{YW}$ is a linear functional.
-
-		\medskip
-		\noindent
-		\textit{Boundedness.}~ 
-		To show that $\mathcal{C}_{YW}$ is bounded, we need to find a finite constant $M$ such that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathbb{H}$ for all $h \in \mathbb{H}$.
-By the Cauchy-Schwarz inequality, we have: \begin{equation*}
-			|\mathcal{C}_{YW} h| = |\langle \Sigma_{YW}, h \rangle_\mathbb{H}| \leq \|\Sigma_{YW}\|_\mathbb{H} \|h\|_\mathbb{H}. 
-		\end{equation*}
-		%%%%%%%%%%%%%%%%
-		Now, we must verify that $\|\Sigma_{YW}\|_\mathbb{H}$ is finite. 
-		Let $\mu([0,1])$ denote a Lebesgue measure of $[0,1]$, and let $T = \max_{k=1, \ldots, K} \, \mu([0,1])$.
-		The squared norm of $\Sigma_{YW}$   is given by:
-		\begin{equation*}
-			\|\Sigma_{YW}\|_\mathbb{H}^2 
-			= 
-			\langle \Sigma_{YW}, \Sigma_{YW} \rangle_\mathbb{H}
-			=
-			\sum_{k=1}^K
-			\int_0^1 \mathbb{E} \left[   Y X_k\right](t)^2 \, dt
-			+ \sum_{r=1}^p \mathbb{E} \left[   Y Z_r\right]^2
-			<
-			K T Q_1 + p  Q_2 < \infty,
-		\end{equation*} 
-		where the last inequality uses the condition \eqref{condition_for_compact}.
-		Let $M = \sqrt{K T Q_1 + p  Q_2 }$. Thus, we have shown that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathbb{H}$ for a finite constant $M$.
-		This completes the proof of Lemma \ref{lemma:cross_cov_functional}.
-
-	\end{proof}
-	\subsection{Proof of Lemma \ref{lemma:cross_cov_operator}}\label{section:proof:lemma:cross_cov_operator}
-	\begin{proof}
-		For any $h \in \mathbb{H}$ and $d \in \mathbb{R}$, we have:
-		\begin{equation*}
-			\langle
-			\mathcal{C}_{YW} h, d \rangle 
-			= 
-			\mathbb{E}
-			[
-			\langle W_1, h \rangle_\mathbb{H} Y_1  
-			] 	 \,  d
-			%%%%%%%%%%%%%%%%%%
-			=
-			\mathbb{E} \langle   Y_1 W_1 d , \, h\rangle_{\mathbb{H}} 
-			%%%%%%%%%%%%%%%%%%%%%%%%
-			= \langle h, \, \mathbb{E}[Y_1 W_1 d   ]\rangle_{\mathbb{H}}
-			=
-			\langle h, \mathcal{C}_{WY} d \rangle_{\mathbb{H}}
-		\end{equation*}
-		Thus, we have $\langle \mathcal{C}_{YW} h, d \rangle =  \langle h, \mathcal{C}_{WY} d \rangle_{\mathbb{H}}$, which implies $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
-		This completes the proof of Lemma \ref{lemma:cross_cov_operator}.
-	\end{proof}
-
-	\subsection{Proof of Lemma \ref{lemma:composite_cross_cov}}\label{section:proof:lemma:composite_cross_cov}
-	\begin{proof}We show that $\mathcal{U}$ is self-adjoint, positive-semidefinite, and compact, in turn.
-
-		\medskip
-		\noindent
-		\textit{Self-adjoint.}~
-		For any $h_1, h_2 \in \mathbb{H}$, we have
-		\begin{align*}
-			\langle 
-			\mathcal{U} h_1, \, h_2 
-			\rangle_\mathbb{H}  
-			= 
-			\bigl \langle 
-			\langle h_1, \Sigma_{YW} \rangle_\mathbb{H} \Sigma_{YW},
-			\,
-			h_2
-			\bigr \rangle_\mathbb{H}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			&= \langle h_1, \Sigma_{YW} \rangle_\mathbb{H} \langle \Sigma_{YW}, h_2 \rangle_\mathbb{H}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&= 
-			\bigl \langle 
-			h_1,
-			\,
-			\langle \Sigma_{YW}, h_2 \rangle_\mathbb{H} \Sigma_{YW} 
-			\bigr \rangle_\mathbb{H}
-			\\ 	&= \langle h_1, \mathcal{U} h_2 \rangle_\mathbb{H}.
-		\end{align*}
-
-		\medskip
-		\noindent
-		\textit{Positive-semidefinite.}~
-		For every $h \in \mathbb{H}$, we have
-		\begin{equation*}
-			\langle 
-			\mathcal{U} h,
-			\,
-			h
-			\rangle_\mathbb{H}
-			=
-			\bigl \langle 
-			\langle 
-			\Sigma_{YW},\, h \rangle_{\mathbb{H}}  \Sigma_{YW}, \, h
-			\bigr \rangle_\mathbb{H}
-			= \langle \Sigma_{YW}, \, h \rangle_\mathbb{H}^2 \ge 0.
-		\end{equation*}
-
-		\medskip
-		\noindent
-		\textit{Compact.}~
-		By Lemma \ref{lemma:cross_cov_functional}, $\mathcal{C}_{YW}$ is a compact operator.
-		By  Theorem 4.1.3 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
-		the composition of two operators is compact if either operator is compact. Therefore
-		$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}$ is a compact operator.
-		This completes the proof of Lemma \ref{lemma:composite_cross_cov}.
-	\end{proof}
-
-	\subsection{Proof of Theorem \ref{theorem:population_PLS}}\label{section:proof:theorem:population_PLS}
-	\begin{proof}
-		by Theorem 4.3.1 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
-		since $\mathcal{C}_{YW}$ is compact by Lemma \ref{lemma:cross_cov_functional}, it 
-		has the singular value decomposition of $\mathcal{C}_{YW}$, given by:
-		\begin{equation*}
-			\mathcal{C}_{YW} = \sum \limits_{j=1}^\infty \iota_j (f_{1j} \otimes f_{2j}).
-		\end{equation*}
-		Let $\Vert \cdot \Vert_{\mathrm{op}}$ denote an operator norm. By  4.3.4 in \citet{hsingTheoreticalFoundationsFunctional2015}, we have
-		\begin{equation*}
-			\Vert \mathcal{C}_{YW} \Vert_{\mathrm{op}} = \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | \mathcal{C}_{YW} h |^2 
-			= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | \mathbb{E}(\langle W, h \rangle_\mathbb{H} Y)|^2 
-			= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} \textnormal{Cov}^2(\langle W, h \rangle_\mathbb{H}, Y) 
-			= \kappa_1^2,
-		\end{equation*}
-		with maximum attained at $h=f_{11}$, which is an eigenfunction of  $\mathcal{C}_{YW}^* \, \circ \, \mathcal{C}_{YW} = \mathcal{C}_{WY} \, \circ \, \mathcal{C}_{YW} = \mathcal{U}$ corresponding to the largest eigenvalue $\kappa_1^2.$
-		This completes the proof of Theorem \ref{theorem:population_PLS}.
-	\end{proof}
-
-	\begin{comment}
-		\section{Proof of Proposition \ref{proposition:compact_operator}}\label{section:proof:proposition:compact_operator}
-		\begin{proof}
-			The brief strategy of the proof is as follows.
-			We   show that an image of a bounded family in $\mathbb{H}$ under $\mathcal{U}$ is uniformly bounded and equicontinuous.
-			Then we apply the Arzel\'{a}-Ascoli theorem to show that $\mathcal{U}$ is \textit{compact}.
-
-			Let $\mathcal{B}=\{h \in \mathbb{H}: \Vert h \Vert_\mathbb{H}^2 \le M\}$ denote a bounded family in $\mathbb{H}$ for some constant $0 < M < \infty$.
-			Clearly, $h=(f, \mathbf{v}) \in \mathcal{B}$ also implies 
-			\begin{equation}\label{individual_norm_bound}
-				\Vert f_k \Vert_\mathcal{F}^2 \le M,
-				~k=1,\ldots,K, \quad\text{and}\quad
-				\Vert \mathbf{v} \Vert^2 \le M.
-			\end{equation}
-			Define $\mathcal{I}  = \{\mathcal{U}h: h \in \mathcal{B}\}$ as the image of  $\mathcal{B}$ under $\mathcal{U}$.
-
-			\medskip
-			\noindent
-			\textit{Uniform boundedness of $\mathcal{I}$.}~Given a hybrid object $h = (f_1, \ldots, f_K, \mathbf{v}) \in \mathbb{H}$ and an evaluation point $\mathbf{t}= (t_1, \ldots, t_k) \in [0,1]^K$, we denote the $\ell_2$ norm of the evaluated object $\bigl( f_1(t_1), \ldots, f_k(t_k), \mathbf{v} \bigr)$ as follows:
-			$\bigl(
-			f_1(t_1), \ldots, f_k(t_k), \mathbf{v}
-			\bigr)$
-			as follows:
-			\begin{equation*}
-				\| h (\mathbf{t}) \|_2^2 := \sum_{k=1}^K f^2_k(t_k) + \| \mathbf{v} \|_2^2.
-			\end{equation*}
-			%We first show that $\mathcal{I}$ is a family of uniformly bounded functions with respect to arguments on $\mathcal{T}$.
-			Let $\mu([0,1])$ denote a Lebesgue measure of $[0,1]$, and let $T = \max_{k=1, \ldots, K} \, \mu([0,1])$. Then for any $g \in \mathcal{I}$ and $\mathbf{t} \in [0,1]^K$, 
-			by Lemma \ref{lemma:composite_cross_cov}, we have:
-			\begin{equation}\label{gtsq_expansion}
-				\Vert g (\mathbf{t}) \Vert^2_2
-				%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-				= \Vert (\mathcal{U}h)(\mathbf{t}) \Vert^2_2 
-				%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-				\overset{(i)}{=} 
-				\Vert \langle \Sigma_{YW}, h \rangle_\mathbb{H} \, \Sigma_{YW}(\mathbf{t}) \Vert^2_2
-				%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-				=
-				\langle \Sigma_{YW}, h \rangle_\mathbb{H}^2
-				\Vert   \Sigma_{YW}(\mathbf{t}) \Vert^2_2.
-			\end{equation}
-			We will show that $\Vert g (\mathbf{t}) \Vert^2_2 < \infty$ by  showing $\langle \Sigma_{YW}, h \rangle_\mathbb{H}^2 < \infty$ and $\Vert   \Sigma_{YW}(\mathbf{t}) \Vert^2_2 < \infty$ in turn.
-First, to bound
-			$\langle \Sigma_{YW}, h \rangle_\mathbb{H}^2$, it suffices to bound $\langle \Sigma_{YW}, h \rangle_\mathbb{H}$:
-			\begin{align*}
-				\langle \Sigma_{YW}, h \rangle_\mathbb{H}
-				%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-				&=
-				\sum_{k=1}^K \langle \sigma_{YX, k}, \, f_k \rangle_\mathcal{F}  
-				+ 
-				\langle \sigma_{YZ}, \, \mathbf{v} \rangle
-				%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-				\\&\overset{(i)}{\le}
-				\sum_{k=1}^K 
-				\langle \sigma_{YX, k}, \sigma_{YX, k} \rangle_\mathcal{F}^{1/2} 
-				\langle f_k, f_k \rangle_\mathcal{F}^{1/2} + \langle \sigma_{YZ}, \sigma_{YZ} \rangle^{1/2} \langle \mathbf{v}, \mathbf{v} \rangle^{1/2}
-				%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-				\\&=
-				\sum \limits_{k=1}^K
-				\biggl(
-				\int_0^1
-				\sigma_{YX, k}^{2}(t)\, dt
-				\biggr)^{1/2} 
-				\Vert f_k \Vert_\mathcal{F} 
-				+
-				\biggl(
-				\sum \limits_{r=1}^p \sigma_{YZ, r}^2
-				\biggr)^{1/2}
-				\Vert \mathbf{v} \Vert_2
-				%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-				\\&\overset{(ii)}{<}
-				\sqrt{M}
-				\biggl\{
-				\sum \limits_{k=1}^K 
-				\biggl(
-				\int_0^1 Q_1 dt
-				\biggr)^{1/2}
-				+
-				\biggl(
-				\sum \limits_{r=1}^p Q_2 
-				\biggr)^{\frac{1}{2}} 
-				\biggr\}
-				%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-				\\ & = K\sqrt{M TQ_1}   + \sqrt{MpQ_2} < \infty.
-				\numberthis \label{squared_ip_bound}
-			\end{align*}
-			where
-			step $(i)$ uses Cauchy-Schwarz inequality,
-			and
-			step $(ii)$ uses the conditions \eqref{condition_for_compact} 
-			and \eqref{individual_norm_bound}.
-
-			Next, we bound $\Vert   \Sigma_{YW}(\mathbf{t}) \Vert^2_2  $:
-			\begin{align*}
-				\Vert   \Sigma_{YW}(\mathbf{t}) \Vert^2_2  
-				%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-				= %%%%%%%%%%%%%%%%%
-				\sum \limits_{k=1}^K
-				\sigma_{YX, k}^{2}(t_k)
-				+
-				\sum \limits_{r=1}^p \sigma^2_{YZ,r}
-				%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-				<
-				\sum \limits_{k=1}^K Q_1 + \sum \limits_{r=1}^p Q_2 
-				=  KQ_1 +pQ_2 < \infty.
-			\end{align*}
-			Therefore, we have
-			\begin{equation*}
-				\Vert g (\mathbf{t}) \Vert^2_2 < 
-				2K^2 M TQ_1   + 2MpQ_2 + KQ_1 +pQ_2< \infty.
-			\end{equation*}
-			Since this bound does not depend on the evaluation point, we conclude that across all $g = (s_1(t), \ldots, s_K(t), \mathbf{w}) \in \mathcal{I}$, their functional components $s_1(t), \ldots, s_K(t)$ are uniformly bounded.
-
-			\medskip
-			\noindent
-			\textit{Equicontinuity of $\mathcal{I}$.}~Given a hybrid object $h = (f_1, \ldots, f_K, \mathbf{v}) \in \mathbb{H}$ and 
-			two evaluation points
-			$\mathbf{t}=(t_1, \ldots, t_K) \in [0,1]^K$
-			and
-			$\mathbf{t}^\ast=(t_1^\ast, \ldots, t_K^\ast) \in [0,1]^K$,
-			we denote the $\ell_2$ distance between   two evaluations
-			$\bigl( f_1(t_1), \ldots, f_k(t_k), \mathbf{v} \bigr)$ 
-			and
-			$\bigl( f_1(t^\ast_1), \ldots, f_k(t^\ast_k), \mathbf{v} \bigr)$
-			as follows:
-			\begin{equation*}
-				\| h (\mathbf{t}) - h (\mathbf{t}^\ast)\|_2^2 
-				:= 
-				\sum_{k=1}^K 
-				\bigl(
-				f_k(t_k) - f_k(t_k^\ast)
-				\bigr)^2 .
-			\end{equation*}
-			For any $g \in \mathcal{I}$, via similar computation as in \eqref{gtsq_expansion}, we have
-			\begin{align*}
-				\Vert g(\mathbf{t}) - g ( \mathbf{t}^\ast ) \Vert_2^2 
-				%%%%%%%%%%%%%%%%%
-				= %%%%%%%%%%%%%%%%%%
-				\Vert 
-				(\mathcal{U}h)(\mathbf{t}) - (\mathcal{U}h)( \mathbf{t}^\ast ) 
-				\Vert_2^2
-				%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-				&= %%%%%%%%%%%%%%%
-				\Vert \langle \Sigma_{YW}, h \rangle_\mathbb{H} 
-				\,
-				\Sigma_{YW}(\mathbf{t}) - \langle \Sigma_{YW}, h \rangle_\mathbb{H} \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2_2
-				%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-				\\&=
-				\langle \Sigma_{YW}, h \rangle_\mathbb{H}^2 \Vert \Sigma_{YW}(\mathbf{t})- \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2.
-			\end{align*}
-			We have already shown in \eqref{squared_ip_bound} that  $\langle \Sigma_{YW}, h \rangle_\mathbb{H}^2 \leq  2K^2 M TQ_1   + 2MpQ_2$.
-			Next we bound $\Vert \Sigma_{YW}(\mathbf{t})- \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2$, which do not depend on $h$.
-			\begin{align*}
-				\Vert \Sigma_{YW}(\mathbf{t})- \Sigma_{YW}( \mathbf{t}^\ast ) \Vert^2_2	
-				=%%%%%%%%%%%%%
-				\sum \limits_{k=1}^K  
-				\bigl\{
-				\sigma_{YX, k }(t_k) -\sigma_{YX, k}(t_k^\ast ) 
-				\bigr\}^2 
-				& \leq%%%%%%%%%%%%%
-				\sum \limits_{k=1}^K  
-				\bigl\{
-				2\sigma^2_{YX, k }(t_k) + 2\sigma^2_{YX, k}(t_k^\ast ) 
-				\bigr\}
-				%%%%%%%%%%%%%%%%%%%%%%
-				\\& \le 
-				4KQ_1.
-			\end{align*}
-			Therefore we have
-			\begin{equation}\label{bound_elltwo_dist}
-				\Vert g(\mathbf{t}) - g ( \mathbf{t}^\ast ) \Vert_2^2 \leq 2K^2 M TQ_1   + 2MpQ_2 + 4KQ_1.
-			\end{equation}
-			Given $\epsilon > 0$, define 
-			\begin{equation*}
-				\tilde{\epsilon}: = \frac{\epsilon}{  ( 2K^2 M TQ_1   + 2MpQ_2 + 4KQ_1 )^{1/2}}
-			\end{equation*}
-			By the uniform continuity assumption of $\sigma_{YX, k}$'s, there exists $\delta_k > 0$ such that
-			\begin{equation*}
-				|t_k - t_k^\ast| < \delta_k \implies |\sigma_{YX, k}(t_k) - \sigma_{YX, k}(t_k^\ast)|< \tilde{\epsilon},~\text{for all}~k=1, \ldots, K.
-			\end{equation*}
-			Set $\delta := \min_{k=1, \ldots, K} \delta_k$.Then  by \eqref{bound_elltwo_dist},  
-			across  $g = (s_1(t), \ldots, s_K(t), \mathbf{w}) \in \mathcal{I},$ for all $k=1, \ldots, K$, 
-			$|t_k - t^*_k| < \delta$ implies $|s_k(t_k) - s_k(t_k^\ast)| < \epsilon$.
-
-			\medskip
-			\noindent
-			\textit{Conclusion.}~ For any bounded sequence $\{h_n\}_{n \in \mathbb{N}} \in \mathcal{B}$, the sequence $\{\mathbf{g}_n = \mathcal{U}h_n\}_{n \in \mathbb{N}} \in \mathcal{I}$ contains a subsequence that converges in its first functional component, by the Arzel\'{a}-Ascoli theorem.
-We then apply the theorem again to that subsequence to extract a sub-subsequence that also converges in the second functional component.
-By repeating this process, we ultimately obtain a subsequence of $\{\mathbf{g}_n\}$ that converges in all its components.
-Therefore, $\mathcal{U}$ is a compact operator.
-		\end{proof}
-	\end{comment}
-
-	\section{Proof of consistency}
-
-	\subsection{Proof of Proposition \ref{prop:residualization_equiv_eigen}}\label{section:proof:prop:residualization_equiv_eigen}
-	The proof procedes in the following steps.
-	\begin{enumerate}
-		\item Show that for every \(s\ge 1\) and every \(j\le s-1\), we have $
-		\mathbb{E}[\rho^{[j]}\rho^{[s]}]=0
-		$ for Algorithm \ref{alg:population_pls} (Appendix \ref{section:proof:orthogonal_score_pop}),
-		%%%%
-		\item Show that for every \(s\ge 1\) and every \(j\le s-1\), we have
-		$
-		\mathbb{E}[Y^{[s]}\rho^{[j]}]=0
-		$
-		for Algorithm \ref{alg:population_pls} (Appendix \ref{section:proof:orthogonal_score_residual_pop}),
-		%
-		\item Show the equivalence between Algorithm \ref{alg:population_pls} and optimization problem \eqref{const_eigen_pop} (Appendix \ref{equiv_problem}).
-	\end{enumerate}
-
-	\subsubsection{Orthogonality of the scores in Algorithm \ref{alg:population_pls}}\label{section:proof:orthogonal_score_pop}
-	\begin{proof}
-		Let
-		$
-		\Sigma_{W^{[l]}} := \mathbb{E}[ W^{[l]} \otimes W^{[l]} ]
-		$ as in Definition \ref{def:cross_cov_terms}.
-		Since 
-		$
-		\rho^{[l]} = \langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}},
-		$
-		we can rewrite the numerator and denominator of $\delta^{[l]}$ as
-		\[
-		\mathbb{E}[ \rho^{[l]}  \,  W^{[l]} ] 
-		= 
-		\mathbb{E}[
-		\langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}} W^{[l]} ]
-		= \Sigma_{W^{[l]}} \, \xi^{[l]},
-		\] 
-		and
-		\[
-		\mathbb{E}[ \rho^{[l]}  \,  \rho^{[l]} ] 
-		= 
-		\mathbb{E}[
-		\langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}} \langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}} ]
-		= 
-		\langle \Sigma_{W^{[l]}} \, \xi^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}},
-		\]
-		respectively.
-		Hence, at the population level, the residualization step can be written as
-		\[
-		W^{[l+1]} = W^{[l]} - 
-		\langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}}
-		\frac{ 
-			1
-		}
-		{ \langle \xi^{[l]}, \Sigma_{W^{[l]}} \, \xi^{[l]} \rangle_{\mathbb{H}} }
-		\Sigma_{W^{[l]}} \, \xi^{[l]} .
-		\]
-
-		For $l_1 < l_2$:
-		\[
-		\mathbb{E}[\rho^{[l_1]} \, \rho^{[l_2]}]
-		=
-		\mathbb{E}\big[ \rho^{[l_1]} \,
-		\langle W^{[l_2]}, \xi^{[l_2]} \rangle_{\mathbb{H}} \big]
-		=
-		\mathbb{E}\big[ 
-		\langle \rho^{[l_1]} \, W^{[l_2]}, \xi^{[l_2]} \rangle_{\mathbb{H}} \big]
-		=
-		\langle 
-		\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2]}] \,
-		, \,
-		\xi^{[l_2]} \rangle_{\mathbb{H}}
-		\]
-		Therefore,
-		to show that $\mathbb{E}[\rho^{[l_1]} \, \rho^{[l_2]}]$,
-		it suffices to show $\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2]}] = 0 \in \mathbb{H} $.
-
-		We can express
-		$\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2]}]$ as
-		\begin{align*}
-			\mathbb{E}&\big[ \rho^{[l_1]} \,W^{[l_2]}]
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=
-			\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2-1]}]
-			-
-			\mathbb{E}[
-			\rho^{[l_1]}
-			\frac{ 
-				\langle W^{[l_2-1]}, \xi^{[l_2-1]} \rangle_{\mathbb{H}}
-			}
-			{ \langle \xi^{[l_2-1]}, \Sigma_{W^{[l_2-1]}} \, \xi^{[l_2-1]} \rangle_{\mathbb{H}} }
-			\Sigma_{W^{[l_2-1]}} \, \xi^{[l_2-1]}
-			]
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=
-			\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2-1]}]
-			-
-			\mathbb{E}[
-			\rho^{[l_1]}
-			\langle W^{[l_2-1]}, \xi^{[l_2-1]} \rangle_{\mathbb{H}}
-			]
-			\frac{ 
-				1
-			}{ 
-				\langle
-				\xi^{[l_2-1]}, 
-				\Sigma_{W^{[l_2-1]}} \, \xi^{[l_2-1]}
-				\rangle_{\mathbb{H}} }
-			\Sigma_{W^{[l_2-1]}} \, \xi^{[l_2-1]}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=
-			\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2-1]}]
-			-
-			\langle 
-			\mathbb{E}[
-			\rho^{[l_1]} W^{[l_2-1]}], \xi^{[l_2-1]} \rangle_{\mathbb{H}}
-			\frac{ 
-				1
-			}{ 
-				\langle
-				\xi^{[l_2-1]}, 
-				\Sigma_{W^{[l_2-1]}} \, \xi^{[l_2-1]}
-				\rangle_{\mathbb{H}} }
-			\Sigma_{W^{[l_2-1]}} \, \xi^{[l_2-1]}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\	&=	H^{[l_2-1]} \bigl( 
-			\mathbb{E}[\rho^{[l_1]  }
-			W^{[l_2-1]}] \bigr)~(\text{say}).
-		\end{align*}
-		Here, the deterministic operator $H^{[l_2-1]}: \mathbb{H} \mapsto \mathbb{H}$ maps the zero element of $\mathbb{H}$ to itself. Using this relationship, we have
-		\begin{align*}
-			\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2]}]  
-			%%%%%%%%%%%%%%%%
-			&=
-			H^{[l_2-1]} \bigl( \mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2-1]}] \bigr)
-			%%%%%%%%%%%%%%%%
-			\\&=
-			H^{[l_2-1]} 
-			\circ 
-			H^{[l_2-2]}
-			\bigl(
-			\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_2-2]}]
-			\bigr)
-			%%%%%%%%%%%%%%%%
-			\\&=
-			H^{[l_2-1]} 
-			\circ 
-			H^{[l_2-2]}
-			\circ 
-			\ldots
-			\circ 
-			H^{[l_1]}
-			\bigl( \mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_1]}] \bigr).
-		\end{align*}
-		Therefore,
-		to  show that $\mathbb{E}[\rho^{[l_1]} \, \rho^{[l_2]}]$,
-		it suffices to show $H^{[l_1]}
-		\bigl( \mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_1]}] \bigr) = 0 \in \mathbb{H}$. Note that
-		we have
-		\begin{equation*}
-			\mathbb{E}[\rho^{[l_1]} W^{[l_1]}] = \mathbb{E}[\langle W^{[l_1]}, \xi^{[l_1]} \rangle_{\mathbb{H}} \, W^{[l_1]}] = \Sigma_{W^{[l_1]}} \, \xi^{[l_1]}.
-		\end{equation*}
-		Leveraging this, we have
-		\begin{align*}
-			H^{[l_1]}&
-			\bigl( \mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_1]}] \bigr)
-			\\           &=
-			\mathbb{E}\big[ \rho^{[l_1]} \,W^{[l_1]}]
-			-
-			\langle 
-			\mathbb{E}[
-			\rho^{[l_1]} W^{[l_1]}], \xi^{[l_1]} \rangle_{\mathbb{H}}
-			\frac{ 
-				1
-			}{ 
-				\langle
-				\xi^{[l_1]}, 
-				\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
-				\rangle_{\mathbb{H}} }
-			\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
-			\\           &=
-			\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
-			-
-			\langle 
-			\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}, \xi^{[l_1]} \rangle_{\mathbb{H}}
-			\frac{ 
-				1
-			}{ 
-				\langle
-				\xi^{[l_1]}, 
-				\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
-				\rangle_{\mathbb{H}} }
-			\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
-			\\           &=
-			\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
-			-
-			\Sigma_{W^{[l_1]}} \, \xi^{[l_1]}
-			=0 \in \mathbb{H}.
-		\end{align*}
-		This completes the proof of
-		orthogonality of the scores in Algorithm \ref{alg:population_pls}.
-
-	\end{proof}
-
-	\subsubsection{Orthogonality of the scores and response residuals in Algorithm \ref{alg:population_pls}}\label{section:proof:orthogonal_score_residual_pop}
-	\begin{proof}
-		Fix \(s\ge 2\) and \(j\le s-1\). Recall the residualization for the response:
-		\[
-		Y^{[s]} \;=\; Y - \sum_{k=1}^{s-1} \nu^{[k]}\,\rho^{[k]},
-		\qquad
-		\nu^{[k]} \;=\; \frac{\mathbb{E}[Y^{[k]}\rho^{[k]}]}{\mathbb{E}[(\rho^{[k]})^2]}.
-		\]
-		Compute the covariance of interest by expanding the residual:
-		\begin{align*}
-			\mathbb{E}\big[ Y^{[s]}\,\rho^{[j]} \big]
-			= \mathbb{E}\Big[ \Big( Y - \sum_{k=1}^{s-1} \nu^{[k]}\rho^{[k]}\Big)\, \rho^{[j]} \Big] 
-			= \mathbb{E}[Y\,\rho^{[j]}] \;-\; \sum_{k=1}^{s-1} \nu^{[k]}\,\mathbb{E}[\rho^{[k]}\rho^{[j]}].
-		\end{align*}
-
-		By the score orthogonality already established in Appendix \ref{section:proof:orthogonal_score_pop},
-		we have \(\mathbb{E}[\rho^{[k]}\rho^{[j]}]=0\) for every \(k\neq j\). Thus only the \(k=j\) term survives in the sum and we obtain
-		\[
-		\mathbb{E}\big[ Y^{[s]}\,\rho^{[j]} \big]
-		= \mathbb{E}[Y\,\rho^{[j]}] - \nu^{[j]}\,\mathbb{E}[(\rho^{[j]})^2].
-		\]
-
-		It remains to identify \(\mathbb{E}[Y\,\rho^{[j]}]\). Using the definition of the \((j)\)-th residual response,
-		\[
-		Y = Y^{[j]} + \sum_{m=1}^{j-1} \nu^{[m]}\rho^{[m]},
-		\]
-		and again using score orthogonality \(\mathbb{E}[\rho^{[m]}\rho^{[j]}]=0\) for \(m<j\), we find
-		\[
-		\mathbb{E}[Y\,\rho^{[j]}] = \mathbb{E}[Y^{[j]}\,\rho^{[j]}].
-		\]
-		Substitute this into the previous display and use the definition of \(\nu^{[j]}\):
-		\[
-		\mathbb{E}\big[ Y^{[s]}\,\rho^{[j]} \big]
-		= \mathbb{E}[Y^{[j]}\,\rho^{[j]}] - 
-		\frac{\mathbb{E}[Y^{[j]}\rho^{[j]}]}{\mathbb{E}[(\rho^{[j]})^2]}\,\mathbb{E}[(\rho^{[j]})^2]
-		= 0.
-		\]
-		This completes the proof of orthogonality between scores and residualized responses.
-	\end{proof}
-
-	\subsubsection{Equivalence of the problems}\label{equiv_problem}
-	\begin{proof}
-		Recall the residualization definitions (for fixed \(l\ge 2\)):
-		\[
-		W^{[l]} \;=\; W - \sum_{j=1}^{\,l-1} \rho^{[j]}\,\delta^{[j]},
-		\qquad
-		Y^{[l]} \;=\; Y - \sum_{k=1}^{\,l-1} \nu^{[k]}\,\rho^{[k]},
-		\]
-		where
-		\[
-		\rho^{[j]}=\langle W^{[j]},\xi^{[j]}\rangle,\quad
-		\delta^{[j]}=\frac{\mathbb{E}[\rho^{[j]} W^{[j]}]}{\mathbb{E}[(\rho^{[j]})^2]},
-		\quad
-		\nu^{[j]}=\frac{\mathbb{E}[\rho^{[j]} Y^{[j]}]}{\mathbb{E}[(\rho^{[j]})^2]}.
-		\]
-		Since \(W,Y\) are centered, 
-		so are $W^{l}, Y^{l}$.
-		Thus covariances are expectations of products.
-		Fix any \(w\in\mathbb{H}\).  Using linearity,
-		\begin{align*}
-			\operatorname{Cov}\!\big(\langle W^{[l]},w\rangle,\;Y^{[l]}\big)
-			&= \mathbb{E}\Big[\big(\langle W,w\rangle - \sum_{j=1}^{l-1} \rho^{[j]}\langle\delta^{[j]},w\rangle\big)
-			\big(Y - \sum_{k=1}^{l-1} \nu^{[k]}\rho^{[k]}\big)\Big] \\
-			\\&= \mathbb{E}[\langle W,w\rangle Y] 
-			- \sum_{k=1}^{l-1} \nu^{[k]}\,\mathbb{E}[\langle W,w\rangle \rho^{[k]}]
-			- \underbrace{
-				\sum_{j=1}^{l-1} \langle\delta^{[j]},w\rangle\,\mathbb{E}[\rho^{[j]} Y]}_{:=S_1} \\
-			&\qquad
-			\underbrace{
-				+ 
-				\sum_{j=1}^{l-1}\sum_{k=1}^{l-1} \langle\delta^{[j]},w\rangle\,\nu^{[k]}\,\mathbb{E}[\rho^{[j]}\rho^{[k]}]
-			}_{:=S_2}.
-		\end{align*}
-		We claim that $S_1  = S_2$.
-		For $S_1$, first note that, since
-		\(Y = Y^{[l]} + \sum_{k=1}^{l-1}\nu^{[k]}\rho^{[k]}\), for each \(j\le l-1\) we have
-		\[
-		\mathbb{E}[\rho^{[j]} Y] = \mathbb{E}[\rho^{[j]} Y^{[l]}] + \sum_{k=1}^{l-1} \nu^{[k]}\mathbb{E}[\rho^{[j]}\rho^{[k]}]=
-		\nu^{[j]}\,\mathbb{E}[(\rho^{[j]})^2],
-		\]
-		where the last equality uses 
-		\(\mathbb{E}[\rho^{[j]} Y^{[l]}]=0\) (Appendix \ref{section:proof:orthogonal_score_residual_pop}) and
-		\(\mathbb{E}[\rho^{[j]}\rho^{[k]}]=0\) for \(j\ne k\) (Appendix \ref{section:proof:orthogonal_score_pop}).
-		Therefore we have
-		\[
-		S_1 = \sum_{j=1}^{l-1} \langle\delta^{[j]},w\rangle \nu^{[j]}\,\mathbb{E}[(\rho^{[j]})^2].
-		\]
-		For $S_2$, 
-		since  \(\mathbb{E}[\rho^{[j]}\rho^{[k]}]=0\) for \(j\ne k\) (Appendix \ref{section:proof:orthogonal_score_pop}), we have:
-		\begin{equation*}
-			S_2
-			=
-			\sum_{j=1}^{l-1}\sum_{k=1}^{l-1} \langle\delta^{[j]},w\rangle\,\nu^{[k]}\,\mathbb{E}[\rho^{[j]}\rho^{[k]}]
-			= \sum_{j=1}^{l-1} \langle\delta^{[j]},w\rangle\,\nu^{[j]}\,\mathbb{E}[(\rho^{[j]})^2].   
-		\end{equation*}
-		Since $S_1 = S_2$, 
-		and
-		\(\mathbb{E}[\langle W,w\rangle Y]=\operatorname{Cov}(\langle W,w\rangle,Y)\), we have
-		\[
-		\operatorname{Cov}\big(\langle W^{[l]},w\rangle,\;Y^{[l]}\big)
-		= \operatorname{Cov}(\langle W,w\rangle,Y)
-		- \sum_{k=1}^{l-1} \nu^{[k]}\,\operatorname{Cov}(\langle W,w\rangle,\rho^{[k]}).
-		\]
-		Therefore we are solving
-		\begin{align*}
-			\max_{\|w\|_{\mathbb{H}}=1}~&
-			\Big\{ 
-			\operatorname{Cov}(\langle W,w\rangle,Y)
-			- \sum_{k=1}^{l-1} \nu^{[k]}\,\operatorname{Cov}(\langle W,w\rangle,\rho^{[k]})
-			\Big\}^2
-			\\
-			s.t.~&
-			\nu^{[k]}
-			=
-			\frac{1}{\mathbb{E}[ (\rho^{[k]})^2 ]}
-			\mathbb{E}[Y^{[l]} \rho^{[k]}],~k=1, \ldots, l-1
-			\\~&
-			\rho^{[k]} = \langle \xi^{[k]}, W^{[k]} \rangle,~k=1, \ldots, l-1 
-			\\~&
-			\delta^{[k]}
-			=
-			\frac{1}{\mathbb{E}[ (\rho^{[k]})^2 ]}  \mathbb{E}[W^{[k]} \rho^{[k]}],~k=1, \ldots, l-1
-			\\~&
-			W^{[k+1]} = W^{[k]} - \rho^{[k]} \, \delta^{[k]},~k=1, \ldots, l-1
-			\\~&
-			Y^{[k]} =Y^{[k-1]} - \nu^{[k-1]} \, \rho^{[k-1]},~k=1, \ldots, l-1
-		\end{align*}
-		Since the constraints imply 
-		that for every \(s\ge 1\) and every \(j\le s-1\), we have $
-		\mathbb{E}[\rho^{[j]}\rho^{[s]}]=\langle w, \Sigma_W \, \xi^{[k]} \rangle_{\mathbb{H}} = \operatorname{Cov}(\langle W,w\rangle,\rho^{[k]}) =0
-		$ (Appendix \ref{section:proof:orthogonal_score_pop}),
-		the above problem is equivalent to 
-		\begin{align*}
-			\max_{\|w\|_{\mathbb{H}}=1}~&
-			\Big\{ 
-			\operatorname{Cov}(\langle W,w\rangle,Y)
-			\Big\}^2
-			\\
-			s.t.~&
-			\nu^{[k]}
-			=
-			\frac{1}{\mathbb{E}[ (\rho^{[k]})^2 ]}
-			\mathbb{E}[Y^{[l]} \rho^{[k]}],~k=1, \ldots, l-1
-			\\~&
-			\rho^{[k]} = \langle \xi^{[k]}, W^{[k]} \rangle,~k=1, \ldots, l-1 
-			\\~&
-			\delta^{[k]}
-			=
-			\frac{1}{\mathbb{E}[ (\rho^{[k]})^2 ]}  \mathbb{E}[W^{[k]} \rho^{[k]}],~k=1, \ldots, l-1
-			\\~&
-			W^{[k+1]} = W^{[k]} - \rho^{[k]} \, \delta^{[k]},~k=1, \ldots, l-1
-			\\~&
-			Y^{[k]} =Y^{[k-1]} - \nu^{[k-1]} \, \rho^{[k-1]},~k=1, \ldots, l-1
-			\\~& \langle w, \Sigma_W \, \xi^{[k]} \rangle_{\mathbb{H}}=0,~k=1, \ldots, l-1.
-		\end{align*}
-		Removing constraints that does not affect the objective function, the above optimization problem is equivalent to
-		\begin{align*}
-			\max_{\|w\|_{\mathbb{H}}=1}~&
-			\Big\{ 
-			\operatorname{Cov}(\langle W,w\rangle,Y)
-			\Big\}^2
-			\\
-			s.t.~&
-			\langle w, \Sigma_W \, \xi^{[k]} \rangle_{\mathbb{H}}=0,~k=1, \ldots, l-1.
-		\end{align*}
-		This completes
-		the proof of Proposition \ref{prop:residualization_equiv_eigen}.
-	\end{proof}
-
-	\subsection{Proof of Theorem \ref{thm:hybrid_pls_convergence}}\label{section:proof:thm:hybrid_pls_convergence}
-	\begin{proof}
-		Iterating the residualization $Y^{[l]} = Y^{[l-1]} - \nu^{[l-1]} \rho^{[l-1]}$ for $l=1,\dots,L$, we obtain
-		\begin{equation}\label{eq:Y_sum_residuals}
-			Y = \sum_{j=0}^{L-1} \nu^{[j]} \rho^{[j]} + Y^{[L]} = Y_{\mathrm{PLS},L-1} + Y^{[L]}.
-		\end{equation}
-		Consider the $L^2$ norm of the remaining residual $Y^{[L]}$:
-		\[
-		\mathbb{E}[(Y^{[L]})^2] = \mathbb{E}[(Y^{[L-1]} - \nu^{[L-1]} \rho^{[L-1]})^2] = \mathbb{E}[(Y^{[L-1]})^2] - (\nu^{[L-1]})^2 \mathbb{E}[(\rho^{[L-1]})^2].
-		\]
-		Thus, the residual variance is nonnegative and monotonically decreasing with $L$:
-		\[
-		0 \le \mathbb{E}[(Y^{[L]})^2] \le \mathbb{E}[(Y^{[L-1]})^2] \le \cdots \le \mathbb{E}[Y^2] < \infty.
-		\]
-		Therefore, the series $\sum_{l=1}^{\infty} (\nu^{[l]})^2 \mathbb{E}[(\rho^{[l]})^2]$ converges and the residual variance $\mathbb{E}[(Y^{[L]})^2] \to 0$ as $L \to \infty$.
-		From \eqref{eq:Y_sum_residuals}, the mean squared error of the PLS approximation is
-		\[
-		\mathbb{E}\bigl[ \| Y_{\mathrm{PLS},L-1} - Y \|^2 \bigr] = \mathbb{E}[(Y^{[L]})^2] \to 0 \quad \text{as } L \to \infty.
-		\]
-		This completes the proof of Theorem \ref{thm:hybrid_pls_convergence}.
-	\end{proof}
-
-	\section{Proof of geometric properties}
-
-	\subsection{Proof of Proposition \ref{proposition: modified orthnormality of PLS components}}
-	\label{section:proof:proposition: modified orthnormality of PLS components}
-
-	\begin{proof}
-		The unit norm condition is trivially met by the constraint 
-		$1 =  	\hat{\boldsymbol{\xi}}_l^\top 
-		\hspace{-.2em}
-		(\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \hat{\boldsymbol{\xi}}_l$
-		enforced in \eqref{eq: Regularized generalized rayleigh quotient equation}, because we have:
-		\begin{align*}
-			\hat{\boldsymbol{\xi}}_l^\top 
-			\hspace{-.2em}
-			(\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \hat{\boldsymbol{\xi}}_l
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			&= \hat{\boldsymbol{\xi}}^\top_l 
-			\hspace{-.2em}
-			\mathbb{B}
-			\hat{ \boldsymbol{\xi} }_l
-			+
-			\hat{ \boldsymbol{\xi} }_l^\top 
-			\hspace{-.2em}
-			\Lambda \mathbb{B}^{\prime \prime} \hat{ \boldsymbol{\xi} }_l
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&\overset{(i)}{=}
-			\sum_{j=1}^K
-			\int_0^1
-			\hat{\xi}_l(t) \, \hat{\xi}_l(t)
-			\, dt
-			+
-			\hat{\boldsymbol{\zeta}}^\top  \hat{\boldsymbol{\zeta}}
-			+
-			\hat{\boldsymbol{\xi}}^\top 
-			\hspace{-.2em}
-			\Lambda \mathbb{B}^{\prime \prime} \hat{\boldsymbol{\xi}}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&\overset{(ii)}{=}
-			\sum_{j=1}^K
-			\int_0^1
-			\hat{\xi}_l(t) \, \hat{\xi}_l(t)
-			\, dt
-			+
-			\hat{\boldsymbol{\zeta}}^\top \hat{\boldsymbol{\zeta}}
-			+
-			\sum \limits_{j=1}^K 
-			\lambda_l
-			\int_0^1 \bigl\{ \hat{\xi}_l^{\prime\prime}(t) \bigr\}^2 dt
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=
-			\langle \widehat{\xi}_{l}, \widehat{\xi}_{l} \rangle_{\mathbb{H}, \Lambda},
-			\numberthis \label{rough_norm_matrix_form}
-		\end{align*}
-		where step $(i)$ uses \eqref{unit_norm_as_quadform}
-		and
-		step $(ii)$ uses \eqref{pen_as_matrix}.
-
-		Now to switch our gears toward the the orthogonality. For  $l_1 > l_2 $, we have
-		\begin{align*}
-			\langle \widehat{\xi}_{l_1}, \widehat{\xi}_{l_2} \rangle_{\mathbb{H}, \Lambda}
-			& \overset{(i)}{=}
-			\hat{\boldsymbol{\xi}}_{l_1}^\top 
-			\hspace{-.2em}
-			(\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \hat{\boldsymbol{\xi}}_{l_2}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\	& \overset{(ii)}{=} \frac{1}{\kappa_{l_1}} (V^{[l_1]} \widehat{\boldsymbol{\xi}}_{l_1})^\top \hat{\boldsymbol{\xi}}_{l_2}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\	& = \frac{1}{\kappa_{l_1}}
-			\widehat{\boldsymbol{\xi}}_{l_1}^\top
-			V^{[l_1]} \hat{\boldsymbol{\xi}}_{l_2} 
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\	& \overset{(iii)}{=} \frac{1}{ n^2 \kappa_{l_1}}
-			\widehat{\boldsymbol{\xi}}_{l_1}^\top
-			(\mathbb{B} \Theta^{[l_1]\top} \mathbf{y})(\mathbb{B} \Theta^{[l_1]\top} \mathbf{y})^\top
-			\hat{\boldsymbol{\xi}}_{l_2}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\	& = \frac{1}{ n^2 \kappa_{l_1}}
-			\widehat{\boldsymbol{\xi}}_{l_1}^\top
-			(\mathbb{B} \Theta^{[l_1]\top} \mathbf{y})
-			\mathbf{y}^\top
-			\Theta^{[l_1] } 
-			\mathbb{B}
-			\hat{\boldsymbol{\xi}}_{l_2}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\	& = c
-			\mathbf{y}^\top
-			(
-			\Theta^{[l_1] }
-			\mathbb{B}
-			\hat{\boldsymbol{\xi}}_{l_2}
-			),
-		\end{align*}
-		where
-		step $(i)$ uses \eqref{rough_norm_matrix_form},
-		step $(ii)$ uses the fact that $\hat{\boldsymbol{\xi}}_{l_1}$ is a generalized eigenvector ($\kappa_{l_1}$ denotes the corresponding generalized eigenvalue), as presented in Proposition \ref{proposition:eigen_regul},
-		and step $(iii)$ uses the definition of $V$ matrix given in \eqref{def:V_matrix}.
-		Here, $c$ represents a scalar that condenses all multiplicative terms preceding $\mathbf{y}^\top$.
-
-		Orthogonality can be demonstrated by showing that $\Theta^{[l_1] } \mathbb{B} \hat{\boldsymbol{\xi}}_{l_2} = \mathbf{0} \in \mathbb{R}^n$.
-		From the construction in \eqref{def:full_theta}, \eqref{def:theta} and \eqref{def:gram_block}, the
-		$i$th entry of $\Theta^{[l_1] }
-		\mathbb{B}
-		\hat{\boldsymbol{\xi}}_{l_2}$ 
-		is
-		\begin{align*}
-			(\Theta^{[l_1] }
-			\mathbb{B}
-			\hat{\boldsymbol{\xi}}_{l_2})_i
-			&=
-			(\theta_{i11}^{[l_1]}, \ldots, \theta_{i1M}^{[l_1]}, \ldots, \theta_{iK1}^{[l_1]}, \ldots, \theta_{iKM}^{[l_1]}, Z_{i1}^{[l_1]}, \ldots, Z_{ip}^{[l_1]})
-			\mathbb{B}
-			\hat{\boldsymbol{\xi}}_{l_2}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=
-			\sum_{k=1}^K
-			\boldsymbol{\theta}_{ik}^{[l_1]} B
-			\hat{\boldsymbol{\gamma}}_k^{[l_2]}
-			+
-			\mathbf{Z}_{i}^{[l_1] \top } \hat{\boldsymbol{\zeta}}^{[l_2]}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\	&=
-			\langle
-			\widetilde{W}_i^{[l_1]}, 
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathbb{H}},
-			\numberthis \label{thetaBzetal2i}
-		\end{align*}
-		where the last equality uses the computation of the $i$th entry in \eqref{score_inner_product_all_n}.
-To expand the last quantity, we use a recursive relationship derived as follows.
-Recall from Lemma  \ref{proposition:closed_form_orthgonalization} that we have
-		\begin{equation}\label{algorithm_step:residualization_predictor:recall}
-			\widetilde{W}_i^{[l_1]} 
-			:= 
-			\widetilde{W}_i^{[l_1-1]}  - 
-			\frac{\widehat{\rho}_{i\,l_1-1}}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
-			\sum_{i=1}^n 
-			\widehat{\rho}_{i \,l_1-1}
-			\widetilde{W}_i^{[l_1-1]}.
-		\end{equation} 	
-		Let us denote, with some abuse of notation:
-		\begin{equation}\label{notation:n_predictors}
-			\widetilde{\boldsymbol{W}}^{[l_1]}  := 
-			\bigl(
-			\widetilde{W}_1^{[l_1-1]}, \ldots, \widetilde{W}_n^{[l_1-1]}
-			\bigr)^\top \in \widetilde{\mathbb{H}}^{\otimes n},
-		\end{equation}
-		and
-		\begin{equation}\label{notation:n_inner_products}
-			\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathbb{H}}
-			:= 
-			\biggl(
-			\langle 
-			\widetilde{W}_1^{[l_1-1]}, 
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathbb{H}},
-			\ldots, 
-			\langle 
-			\widetilde{W}_n^{[l_1-1]},  
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathbb{H}}
-			\biggr)^\top 
-			\in \mathbb{R}^n.
-		\end{equation}
-		Recalling \eqref{thetaBzetal2i},
-		to achieve our goal of showing $
-		\Theta^{[l_1] }
-		\mathbb{B}
-		\hat{\boldsymbol{\xi}}_{l_2} = \mathbf{0} \in \mathbb{R}^n,
-		$
-		it suffices to show
-		$	\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
-		\hat{\xi}^{[l_2]}
-		\rangle_{\mathbb{H}} = \mathbf{0}$.
-		Using these notations and  \eqref{algorithm_step:residualization_predictor:recall}, we have, with some abuse of notation,
-		\begin{equation}\label{regression_relation_with_notation_abuse}
-			\widetilde{\boldsymbol{W}}^{[l_1]}  = 
-			\widetilde{\boldsymbol{W}}^{[l_1-1]} - 
-			\biggl(
-			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
-			\hat{\boldsymbol{\rho}}^{[l_1-1] }
-			\hat{\boldsymbol{\rho}}^{[l_1-1] \top
-			} 
-			\biggr)
-			\widetilde{\boldsymbol{W}}^{[l_1-1]},
-		\end{equation}
-		and thus
-		\begin{equation*}
-			\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathbb{H}}
-			= 
-			\langle 	\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathbb{H}} 
-			- 
-			\biggl(
-			\frac{1
-			}{
-				\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2
-			}
-			\hat{\boldsymbol{\rho}}^{[l_1-1]}
-			\hat{\boldsymbol{\rho}}^{[l_1-1] \top}
-			\biggr)
-			\bigl \langle 
-			\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
-			\hat{\xi}^{[l_2]}
-			\bigr \rangle_{\mathbb{H}}.
-		\end{equation*}
-		Clearly, the right-hand side represents a linear operator from $\mathbb{R}^n$ to $\mathbb{R}^n$, which we denote as $P^{[l_1-1]}$.
-		Thus, 
-		we have $\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
-		\hat{\xi}^{[l_2]}
-		\rangle_{\mathbb{H}}  = 
-		P^{[l_1-1]} \langle 	\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
-		\hat{\xi}^{[l_2]}
-		\rangle_{\mathbb{H}}$.
-		Repeatedly using this relationship, we have
-		\begin{align*}
-			\langle 	\widetilde{\boldsymbol{W}}^{[l_1]}  ,
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathbb{H}} 
-			&=
-			P^{[l_1-1]} \langle 	\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathbb{H}} 
-			\\
-			&=
-			P^{[l_1-1]} P^{[l_1-2]}   \langle 	\widetilde{\boldsymbol{W}}^{[l_1-2]}  ,
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathbb{H}}
-			\\
-			&= \underbrace{ P^{[l_1-1]} P^{[l_1-2]} \ldots P^{[l_2 + 1]}}_{:=P}  P^{[l_2]} \langle 	\widetilde{\boldsymbol{W}}^{[l_2]}  ,
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathbb{H}}
-			\\
-			&= P \,\biggl\{
-			\langle 	\widetilde{\boldsymbol{W}}^{[l_2]}  ,
-			\hat{\xi}^{[l_2]}
-			\rangle_{\mathbb{H}} 
-			- 
-			\biggl(
-			\frac{1
-			}{
-				\| 	\hat{\boldsymbol{\rho}}^{[l_2]}\|_2^2
-			}
-			\hat{\boldsymbol{\rho}}^{[l_2]}
-			\hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\biggr)
-			\bigl \langle 
-			\widetilde{\boldsymbol{W}}^{[l_2]}  ,
-			\hat{\xi}^{[l_2]}
-			\bigr \rangle_{\mathbb{H}}
-			\biggr\}
-			\\
-			&= P \,\biggl\{
-			\hat{\boldsymbol{\rho}}^{[l_2]}
-			- 
-			\biggl(
-			\frac{1
-			}{
-				\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2
-			}
-			\hat{\boldsymbol{\rho}}^{[l_2]}
-			\hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\biggr)
-			\hat{\boldsymbol{\rho}}^{[l_2]}
-			\biggr\}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&= P \,\biggl\{
-			\hat{\boldsymbol{\rho}}^{[l_2]}
-			- 
-			\biggl(
-			\frac{\hat{\boldsymbol{\rho}}^{[l_2] \top} \hat{\boldsymbol{\rho}}^{[l_2]}
-			}{
-				\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2
-			}
-			\biggr)
-			\hat{\boldsymbol{\rho}}^{[l_2]}
-			\biggr\}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&= P \,\biggl\{
-			\hat{\boldsymbol{\rho}}^{[l_2]}
-			- 
-			\hat{\boldsymbol{\rho}}^{[l_2]}
-			\biggr\}
-			=
-			P \mathbf{0} = \mathbf{0}.
-		\end{align*}
-		This completes the proof of Proposition 
-		\ref{proposition: modified orthnormality of PLS components}.
-	\end{proof}
-	\subsection{Proof of Proposition \ref{proposition: orthnormality of PLS scores}}\label{section:proof:proposition: orthnormality of PLS scores}
-	\begin{proof}
-		For $l_1 < l_2$, we have
-		\begin{align*}
-			\widehat{\boldsymbol{\rho}}^{[l_1 ] \top}
-			\widehat{\boldsymbol{\rho}}^{[l_2]}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			&=  
-			\sum_{i=1}^n
-			\widehat{ \rho }^{[l_1 ]}_i \,
-			\widehat{ \rho }^{[l_2]}_i
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			=  
-			\sum_{i=1}^n
-			\widehat{ \rho }^{[l_1 ]}_i \,
-			\bigl \langle 	\widetilde{W}^{[l_2]}_i  ,
-			\hat{\xi}^{[l_2]}
-			\bigr \rangle_{\mathbb{H}}
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			=  
-			\big \langle
-			\sum_{i=1}^n
-			\widehat{ \rho }^{[l_1 ]}_i \,
-			\widetilde{W}^{[l_2]}_i  ,
-			\hat{\xi}^{[l_2]}
-			\big \rangle_{\mathbb{H}}.
-		\end{align*}
-		Therefore,
-		to show that $\widehat{\boldsymbol{\rho}}^{[l_1 ] \top}
-		\widehat{\boldsymbol{\rho}}^{[l_2]} = 0$,
-		it suffices to show that
-		$\sum_{i=1}^n
-		\widehat{ \rho }^{[l_1 ]}_i \,
-		\widetilde{W}^{[l_2]}_i  = 0 \in   \mathbb{H}  $,
-		where this   zero element represents an ordered pair of $K$ zero functions and a zero matrix.
-		Using Lemma    \ref{proposition:closed_form_orthgonalization}, notations from 
-		\eqref{notation:n_predictors} and
-		\eqref{notation:n_inner_products},
-		and equation \eqref{regression_relation_with_notation_abuse}, we have:
-		\begin{align*}
-			\widetilde{\boldsymbol{W}}^{[l_1]}  &= 
-			\widetilde{\boldsymbol{W}}^{[l_1-1]} - 
-			\biggl(
-			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
-			\hat{\boldsymbol{\rho}}^{[l_1-1] }
-			\hat{\boldsymbol{\rho}}^{[l_1-1] \top
-			} 
-			\biggr)
-			\widetilde{\boldsymbol{W}}^{[l_1-1]}
-			%%%%%%%%%%%%%%%%%%%%%%
-			\\&=	\widetilde{\boldsymbol{W}}^{[l_1-1]} - 
-			\biggl(
-			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
-			\langle 	
-			\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
-			\hat{\xi}^{[l_1-1]}
-			\rangle_{\mathbb{H}}
-			\hat{\boldsymbol{\rho}}^{[l_1-1] \top
-			} 
-			\biggr)
-			\widetilde{\boldsymbol{W}}^{[l_1-1]}.
-		\end{align*}
-		Using this relationship and
-		with some abuse of notation, we have:
-		\begin{align*}
-			\sum_{i=1}^n
-			\widehat{ \rho }^{[l_1 ]}_i \,
-			\widetilde{W}^{[l_2]}_i 
-			&=
-			\hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_1]}
-			\\  &=	
-			\hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_1-1]} - 
-			\hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\biggl(
-			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
-			\langle 	
-			\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
-			\hat{\xi}^{[l_1-1]}
-			\rangle_{\mathbb{H}}
-			\hat{\boldsymbol{\rho}}^{[l_1-1] \top
-			} 
-			\biggr)
-			\widetilde{\boldsymbol{W}}^{[l_1-1]}
-			\\	&=	
-			\hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_1-1]} - 
-			\frac{
-				\langle 	 	\hat{\boldsymbol{\rho}}^{[l_2] \top}
-				\widetilde{\boldsymbol{W}}^{[l_1-1]}  ,
-				\hat{\xi}^{[l_1-1]}
-				\rangle_{\mathbb{H}}
-			}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
-			%%%%%%%%%%%%%%%%%%%%%%%%%
-			\bigl(
-			\hat{\boldsymbol{\rho}}^{[l_1-1] \top
-			} 
-			\widetilde{\boldsymbol{W}}^{[l_1-1]}
-			\bigr)
-			\\	&=	h^{[l_1-1]} \bigl( \hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_1-1]} \bigr)~(\text{say}).
-		\end{align*}
-		Here, the function $h^{[l_1-1]}: \tilde{ \mathbb{H} } \mapsto \widetilde{\mathbb{H}}$ maps the zero element of $\widetilde{\mathbb{H}}$ to itself, where the zero element represents an ordered pair of $K$ zero functions and a zero matrix.
-Using this relationship, we have
-		\begin{align*}
-			\hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_1]}  
-			%%%%%%%%%%%%%%%%
-			&=	h^{[l_1-1]} \bigl( \hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_1-1]} \bigr)
-			%%%%%%%%%%%%%%%%
-			\\&=
-			h^{[l_1-1]} 
-			\circ 
-			h^{[l_1-2]}
-			\bigl( \hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_1-2]} \bigr)
-			%%%%%%%%%%%%%%%%
-			\\&=
-			h^{[l_1-1]} 
-			\circ 
-			h^{[l_1-2]}
-			\circ 
-			\ldots
-			\circ 
-			h^{[l_2]}
-			\bigl( \hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_2]} \bigr).
-		\end{align*}
-		Therefore,
-		to show that $\widehat{\boldsymbol{\rho}}^{[l_1 ] \top}
-		\widehat{\boldsymbol{\rho}}^{[l_2]} = 0$,
-		it suffices to show $h^{[l_2]}
-		\bigl( \hat{\boldsymbol{\rho}}^{[l_2] \top}
-		\widetilde{\boldsymbol{W}}^{[l_2]} \bigr) = 0$:
-		%
-		\begin{align*}
-			h^{[l_2]} \bigl( \hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_2]} \bigr)
-			&=
-			\hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_2]} - 
-			\frac{
-				\langle 	 	\hat{\boldsymbol{\rho}}^{[l_2] \top}
-				\widetilde{\boldsymbol{W}}^{[l_2]}  ,
-				\hat{\xi}^{[l_2]}
-				\rangle_{\mathbb{H}}
-			}{\| 	\hat{\boldsymbol{\rho}}^{[l_2]}\|_2^2}
-			%%%%%%%%%%%%%%%%%%%%%%%%%
-			\bigl(
-			\hat{\boldsymbol{\rho}}^{[l_2] \top
-			} 
-			\widetilde{\boldsymbol{W}}^{[l_2]}
-			\bigr)
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=
-			\hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_2]} - 
-			\frac{
-				\hat{\boldsymbol{\rho}}^{[l_2] \top}
-				\langle 	 
-				\widetilde{\boldsymbol{W}}^{[l_2]}  ,
-				\hat{\xi}^{[l_2]}
-				\rangle_{\mathbb{H}}
-			}{\| 	\hat{\boldsymbol{\rho}}^{[l_2]}\|_2^2}
-			% 
-			\bigl(
-			\hat{\boldsymbol{\rho}}^{[l_2] \top
-			} 
-			\widetilde{\boldsymbol{W}}^{[l_2]}
-			\bigr)
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=
-			\hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_2]} - 
-			\frac{
-				\hat{\boldsymbol{\rho}}^{[l_2] \top}
-				\hat{\boldsymbol{\rho}}^{[l_2]  } 
-			}{\| 	\hat{\boldsymbol{\rho}}^{[l_2]}\|_2^2}
-			% 
-			\bigl(
-			\hat{\boldsymbol{\rho}}^{[l_2] \top
-			} 
-			\widetilde{\boldsymbol{W}}^{[l_2]}
-			\bigr)
-			%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-			\\&=
-			\hat{\boldsymbol{\rho}}^{[l_2] \top}
-			\widetilde{\boldsymbol{W}}^{[l_2]} 
-			- 
-			\hat{\boldsymbol{\rho}}^{[l_2] \top
-			} 
-			\widetilde{\boldsymbol{W}}^{[l_2]}
-			\\&=0.
-		\end{align*}
-		This completes the proof of Proposition \ref{proposition: orthnormality of PLS scores}.
-	\end{proof}
+			...
+
+			% References
+			\newpage
+			\bibliography{bibliography.bib}
+
+			% Tables and Figures at the end
+			\newpage
+			\section*{Tables and Figures}
+
+			% Example Table
+			\begin{table}[htbp]
+				\centering
+				\caption{Example Table Caption.}
+				\begin{tabular}{lll}
+					\hline
+					Col1 & Col2 & Col3 \\
+					\hline
+					a & b & c \\
+					\hline
+				\end{tabular}
+			\end{table}
+
+			% Example Figure
+			\begin{figure}[htbp]
+				\centering
+				\rule{3in}{2in} % placeholder box
+				\caption{Example Figure Caption.}
+			\end{figure}
+
+			% Uncomment to enforce max number check at compile time
+			%\ifnum\value{totalfigtab}>6
+			%   \errmessage{Too many tables/figures: maximum is 6.}
+			%\fi
 

### 2025-10-01 manuscript/enar/enar_cls.tex
use cls file

\documentclass[referee,12pt,usenatbib]{biom}

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
%\RequirePackage{,,}
\bibliographystyle{biom} % Biometrics bib style if installed
%\usepackage[authoryear,round]{natbib}
\title{Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors}

\begin{document}
	\begin{abstract}
	Motivated by renal imaging data with accompanying side information, we propose a hybrid partial least squares (PLS) regression method to capture cross-modality correlations in settings with both functional and scalar predictors. Our approach extends the nonlinear iterative PLS (NIPALS) algorithm to a hybrid Hilbert space, embedding functional and scalar predictors into a unified vector representation and iteratively maximizing their empirical cross-covariance with the response. The resulting low-dimensional representations effectively capture within- and between-modality variation and predictor-response correlation. Out method  preserves the desirable theoretical properties of PLS. Moreover, the procedure is computationally efficient, requiring only the solution of linear systems at each iteration.
\end{abstract}

\begin{keywords}
Dimension reduction;
Functional data analysis;
Multiple data modalities;
Multivariate data analysis;
Multivariate functional data;
Partial least square
\end{keywords}

\maketitle
\newpage
\section{Introduction} \label{sec: Introduction}
Biomedical studies often collect multi-modal data.
Our running example is the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021}, which records two renogram curves (functional data) along with  side information (Euclidean vector) for each kidney.
Such distinct yet related physiological signals can be represented as functional- and scalar-valued i.i.d. covariates in a linear regression model:
\begin{equation}	\label{eq:hybrid_regression_model}
	Y_i
	= 
	\boldsymbol{\beta}^\top \mathbf{Z}_i
	+ 
	\sum 
	\limits_{k=1}^K 
	\int  \beta_k(t) X_{ik}(t) dt + \epsilon_i,
	\quad
	i = 1, \ldots, n,
	%= \langle \boldsymbol{\alpha}, \mathbf{Z} \rangle +  \langle \beta, X \rangle_{\mathcal{F}}  + \epsilon
\end{equation}
where $Y_i$ is a scalar response, 
$X_{i1}(t), \ldots, X_{iK}(t) \in \mathbb{L}^2[0,1]$ are functional predictors, 
$\mathbf{Z}_i = (Z_{i1}, \ldots, Z_{ip})^\top$ is a Euclidean vector covariate,
and $\epsilon_i$ denotes observational noise.
For notational convenience, we assume throughout that the responses and predictors are centered, so the intercept term can be omitted.
The key   challenge here is the strong correlations between functional and scalar predictors,
in addition to the ill-posedness of the infinite-dimensional slope functions $\beta_k(t)$ and the high dimensionality of the predictors ($K + p$). This paper addresses all three issues in a unified manner by introducing a hybrid partial least squares (PLS) regression framework defined on a novel hybrid Hilbert space.

	\paragraph{Previous works and limitations}
Basis expansion with regularization of roughness addresses the ill-posedness of functional data by exploiting their smoothness \citep{cardotSplineEstimatorsFunctional2003,aguileraPenalizedVersionsFunctional2016, 
	caiPredictionFunctionalLinear2006, zhaoWaveletbasedLASSOFunctional2012}.
High dimensionality can be addressed by using derived inputs, with PCA regression as a straightforward example. We can apply PCA  separately to functional (e.g., \citealt{happ_multivariate_2018}) and scalar predictors, followed by multivariate regression on the combined scores. While well studied for functional predictors alone \citep{hallMethodologyConvergenceRates2007, reissFunctionalPrincipalComponent2007, febrero-bandeFunctionalPrincipalComponent2017}, PCA regression may fail to capture the core regression relationship since the derived inputs are not guided by the response.
Partial least squares (PLS) regression is a powerful alternative that constructs orthogonal latent components from predictors to maximize covariance with the response.
For functional predictors, \citet{predaPLSRegressionStochastic2005} introduced PLS regression for a single predictor, with subsequent extensions incorporating
basis approximations and roughness penalties
\citep{reissFunctionalPrincipalComponent2007, aguileraUsingBasisExpansions2010, aguileraPenalizedVersionsFunctional2016}, and multiple functional predictors \citep{beyaztasRobustFunctionalPartial2022}.
Theoretical and computational advances were developed by \citet{delaigleMethodologyTheoryPartial2012} and \citet{saricamPartialLeastsquaresEstimation2022}, respectively; see \citet{febrero-bandeFunctionalPrincipalComponent2017} for a review.
These approaches ignore correlations between functional and scalar components, leading to multicollinearity and unreliable prediction. Multimodal correlations have mainly been explored in unsupervised settings,
such as graphical models, precision matrix estimation, and joint PCA \citep{kolar_graph_2014, gengJointNonparametricPrecision2020, jangPrincipalComponentAnalysis2021}. However,  these methods are response-agnostic and may miss outcome-relevant correlations.

\paragraph{Our contributions}
To address these gaps, we propose a hybrid PLS regression framework that unifies basis expansion, PLS, and functional-scalar correlations. Treating functional and Euclidean components as a single vector in a Hilbert space with a suitable inner product, we iteratively extract joint directions that maximize covariance with the response under a unit-norm constraint. The framework handles dense or irregular functional data, supports regularization to reduce overfitting, and comes with theoretical guarantees.

			\bibliography{bibliography.bib}

\end{document}

### 2025-10-01 manuscript/enar/enar_cls.tex
basis approximation

@@
 
+\section{Hybrid Hilbert Space}
+Our framework leverages that the nonlinear iterative PLS (NIPALS; \citealp{woldPathModelsLatent1975}) algorithm, a standard PLS fitting method, operates solely via inner-product space operations.
+We define a Hilbert space for hybrid predictors with a complete inner product to extend the algorithm.
+%
+\begin{theorem}[Hybrid space]\label{def:hilbert_space}
+	An element $h \in \mathbb{H} := (\mathbb{L}^2[0,1])^K \times \mathbb{R}^p$ is an ordered tuple $h = (f_1, \dots, f_K, \mathbf{u})$, where $f_k \in \mathbb{L}^2[0,1]$ for $k=1, \dots, K$ and $\mathbf{u} \in \mathbb{R}^p$.
+We define an inner product on $\mathbb{H}$ for any two elements $h_1 = (f_1, \dots, f_K, \mathbf{u})$ and $h_2 = (g_1, \dots, g_K, \mathbf{v})$ as:
+\begin{equation}\label{eq: hybrid inner product}
+	\langle h_1, h_2 \rangle_{\mathbb{H}} := \sum_{k=1}^K \int_0^1 f_k(t) g_k(t) \, dt +   \mathbf{u}^\top \mathbf{v}.
+\end{equation}
+	The inner product induces a norm $\Vert \cdot \Vert_{\mathbb{H}}$ on the space, defined as $\Vert h \Vert_{\mathbb{H}} := \langle h, h \rangle_{\mathbb{H}}^{1/2}$, and a corresponding metric $d(h_1, h_2) = \Vert h_1 - h_2 \Vert_{\mathbb{H}}$.
+	Then the hybrid inner product space $\mathbb{H}$ is a separable Hilbert space.
+\end{theorem}
+
+\begin{definition}[Hybrid Predictor]\label{def:hybrid_predictor}
+	For the Hilbert space  $\mathbb{H}$ 
+	defined in Definition \ref{def:hilbert_space},
+	The Borel $\sigma$-field on $\mathbb{H}$, denoted $\mathfrak{B}(\mathbb{H})$, is the smallest $\sigma$-field containing the class $\mathfrak{M}$ of all sets of the form
+	$
+	\{q \in \mathbb{H} \mid \langle q, h \rangle \in O\},
+	$
+	for any $h \in \mathbb{H}$ and any open subset $O \subseteq \mathbb{R}$ (details can be found in Theorem 7.1.1 of \citealt{hsingTheoreticalFoundationsFunctional2015}).
+	A hybrid predictor $ W_i = (X_{i1}(t), \ldots, X_{iK}(t), \mathbf{Z}_i)$ is a measurable mapping from a probability space $(\Omega, \mathfrak{F}, P)$ into   $
+	\bigl(
+	\mathbb{H}, \mathfrak{B}(\mathbb{H})
+	\bigr)
+	$. 
+\end{definition}
+Then the joint regression model \eqref{eq:hybrid_regression_model}  can be concisely written as
+\begin{equation}		\label{eq: Hybrid functional model}
+	Y_i = \langle \beta, W_i \rangle_{\mathbb{H}} + \epsilon_i,~\text{where}~\beta := \bigl( \beta_1(t), \ldots, \beta_K(t), \boldsymbol{\beta} \bigr)\in \mathbb{H}.
+\end{equation}
+
+\section{Proposed PLS Algorithm}\label{section:main:our_algorithm}
+Our approach efficiently computes PLS components and scores for multiple dense or irregular functional predictors alongside scalar predictors.
+It incorporates regularization to exploit structural relationships within and between the functions, to prevent overfitting and improve interpretability.
+Each iteration involves two subroutines: regularized component estimation (Section \ref{section:sub:compute_PLS_component})  and residualization 
+(Section \ref{section:sub:residualization})
+After iteration terminates 
+the hybrid regression coefficient is estimated (Section~\ref{section:sub:regression_coeff}).
+
+\subsection{Preliminary step 1: finite-basis approximation}\label{sec: finite basis approximation}
+Let $\{b_m(t)\}$ be a twice-differentiable basis of $\mathbb{L}^2([0,1])$ whose second derivatives are also linearly independent, for example, cubic B-splines, Fourier, or orthonormal cubic polynomials.
+Fourier coefficients of
+functional predictors
+$X_{ij}(t)$,
+functional regression coefficients
+$\beta_j(t)$,
+PLS directions,
+$\xi_j(t)$,
+and residualization coefficients
+$\delta_j(t)$
+(with iteration indices suppressed) with respect to 
+$\{b_m(t)\}$ are denoted as
+$\{\theta_{ijm}\},
+\{ \eta_{jm} \},
+\{ \gamma_{jm} \},
+$
+and
+$\{ \pi_{jm} \}$.
+For practicality, we truncate the expansion at a moderate $M$ (e.g., 15-20) to capture most functional variation, while smoothness is handled via penalization (Section~\ref{sec: Regularization of PLS Components}).
+The truncated expansion for the functional data is denoted
+as
+are denoted as $\widetilde{X}_{ij}(t)
+:=
+\sum_{m=1}^M \theta_{ijm}  b_m(t)$, but for the other funtions, we denote
+\begin{equation}\label{def:truncated_zeta_and_delta}
+	\beta_j(t)
+	:=
+	\sum_{m=1}^M \eta_{jm} b_m(t),
+	%
+	\xi_j(t) := \sum_{m=1}^M \gamma_{jm}  b_m(t),
+	%
+	\delta_j(t)
+	=
+	\sum_{m=1}^M
+	\pi_{jm}
+	b_m(t),
+\end{equation}
+since these functions are estimated, using a hat over the tilde notation would be cumbersome.
+Let Let $\boldsymbol{\theta}_{ij}$, $\boldsymbol{\eta}_j$, $\boldsymbol{\gamma}_j$, and $\boldsymbol{\pi}_j$ denote these coefficients as $M$-dimensional vectors.
+The truncations imply that all computations in this paper are carried out entirely within the subspace
+\begin{equation}\label{def:truncated_hilbert_space}
+	\widetilde{ \mathbb{H} } := \operatorname{span}\bigl(b_1(t), \ldots, b_M(t)\bigr)^K \times \mathbb{R}^p \subset \mathbb{H}.
+\end{equation}
+The $i$th hybrid predictor, projected on $\widetilde{ \mathbb{H} }$, is represented by the tuple
+$ 
+\widetilde{W}_i := 
+(
+\widetilde{X}_{i1}, \ldots, \widetilde{X}_{iK}, \boldsymbol{Z}_i
+).
+$ 
+For notational convenience, we stack the predictor coefficient vectors as
+\begin{equation}\label{def:theta}
+	\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M},
+	\quad 
+	\Theta := (\Theta_1, \ldots, \Theta_K, \mathbf{Z}) \in \mathbb{R}^{n \times (MK + p)}.
+\end{equation}
+Let us denote the response vector as $\mathbf{y} := (y_1, \ldots, y_n)^\top$.
+Let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, with entries
+\begin{equation}\label{def:B_matrix}
+	B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt, \quad
+	B^{\prime\prime}_{m, m'} := \int_0^1 b_m''(t)\, b_{m'}''(t)\, dt,
+\end{equation}
+for $m, m' = 1, \ldots, M$. We then define the block-diagonal matrices
+\begin{equation}\label{def:gram_block}
+	\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p), \quad
+	\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
+\end{equation}
+
+Then the full data for the hybrid PLS problem at the $l$-th iteration can be represented by the tuple
+\begin{equation}\label{def:problem_instance}
+	(\mathbb{B}, \mathbb{B}^{\prime\prime}, \Theta, \mathbf{y}) \in 
+	\mathbb{R}^{(MK+p) \times (MK+p)} \times 
+	\mathbb{R}^{(MK+p) \times (MK+p)} \times 
+	\mathbb{R}^{n \times (MK+p)} \times 
+	\mathbb{R}^n,
+\end{equation}
+with the index $l$ omitted for brevity.
+
+\begin{remark}
+	Different bases could be used for each functional predictor to handle  multiple dense or irregular functional predictors.
+We adopt a common basis for simplicity.
+The definitions of $\mathbb{B}$ and $\mathbb{B}^{\prime\prime}$ remain general enough to accommodate distinct bases if needed.
+\end{remark}
+
 			\bibliography{bibliography.bib}

### 2025-10-07 manuscript/enar/submission.tex
import fundata

--- 2025-10-01 manuscript/enar/enar.tex
@@
-\documentclass[12pt]{biom}
+\documentclass[referee,12pt,usenatbib]{biom}
+\usepackage{booktabs}
 
-% Page setup
-%\usepackage[margin=1in]{geometry}
-%\usepackage{setspace}
-%\doublespacing % ensures double spacing
-%\setlength{\textheight}{9in} % ~25 lines per page with 12pt double spaced
-%\setlength{\parskip}{0pt}
-%\setlength{\parindent}{0.5in}
-
-% Font
-\renewcommand{\rmdefault}{ptm} % Times font (Biometrics-like)
-
-% References (Biometrics style uses Chicago-like author-year)
-
-\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
-\RequirePackage{graphicx}
-
-%custom packages
+\usepackage{bbm}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{amsmath}
 \usepackage{algorithm}
@@
 \usepackage{hyperref}
-\usepackage{enumerate}
-\usepackage{xcolor}
-\usepackage{bbm}
-% \usepackage{url} % not crucial - just used below for the URL 
-% \usepackage{bibunits}
-\usepackage{subcaption}
-% \usepackage{adjustbox}
-\usepackage{verbatim} % to comment out
-
-%\theoremstyle{plain}
-%\newtheorem{axiom}{Axiom}
-%\newtheorem{claim}[axiom]{Claim}
-%\newtheorem{theorem}{Theorem}[section]
-%\newtheorem{lemma}[theorem]{Lemma}
-%\newtheorem{proposition}[theorem]{Proposition}
-%\newtheorem{corollary}[theorem]{Corollary}%custom
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% For Assumption, Definition, Example,     %%
-%% Notation, Property, Remark, Fact         %%
-%% use \theoremstyle{definition}            %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\theoremstyle{definition}
-%\newtheorem{definition}[theorem]{Definition}
-%\newtheorem*{example}{Example}
-%\newtheorem*{fact}{Fact}
-%\newtheorem{remark}{Remark}
-
-% Counters for figures/tables
-%\usepackage{etoolbox}
-%\newcounter{totalfigtab}
-%\pretocmd{\begin{figure}}{\stepcounter{totalfigtab}}{}{}
-%	\pretocmd{\begin{table}}{\stepcounter{totalfigtab}}{}{}
-
-		% Title page
+%\RequirePackage{,,}
+\bibliographystyle{biom} % Biometrics bib style if installed
+%\usepackage[authoryear,round]{natbib}
+\title{Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors with Application to Renal Imaging Data}
 
 \begin{document}
+	\begin{abstract}
+Motivated by renal imaging data with accompanying side information, we propose a hybrid partial least squares (PLS) regression method to capture cross-modality correlations with both functional and scalar predictors.
+At the population level, we extend the nonlinear iterative PLS (NIPALS) algorithm to a hybrid Hilbert space, unifying functional and scalar predictors into a single vector and iteratively maximizing the empirical covariance.
+We establish orthogonality of the PLS scores and $L_2$ convergence of the PLS fitted value to the true response.
+We then propose a practical sample-level algorithm incorporating regularization to promote smoothness of regression coefficients and PLS directions.
+The resulting low-dimensional representations effectively capture within- and between-modality variation and predictor-response correlation, while preserving key PLS properties such as orthonormality of PLS directions and orthogonality of PLS scores.
+Moreover, the procedure is computationally efficient, requiring only the solution of linear systems at each iteration.
+\end{abstract}
 
-Biomedical studies often collect multi-modal data, as in the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021}, which records multiple renogram curves (functional data) along with scalar side information for each kidney.
+\begin{keywords}
+Dimension reduction;
+Functional data analysis;
+Multiple data modalities;
+Multivariate data analysis;
+Multivariate functional data;
+Partial least square
+\end{keywords}
+
+\maketitle
+\newpage
+\section{Introduction} \label{sec: Introduction}
+Biomedical studies often collect multi-modal data.
+Our running example is the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021}, which records two renogram curves (functional data) along with  side information (Euclidean vector) for each kidney.
 Such distinct yet related physiological signals can be represented as functional- and scalar-valued i.i.d. covariates in a linear regression model:
@@
 and $\epsilon_i$ denotes observational noise.
-%In other words, this is a scalar-on-hybrid regression where the hybrid covariates belong to $\bigl( \mathbb{L}^2[0,1] \bigr)^{  K} \times \mathbb{R}^p$.
 For notational convenience, we assume throughout that the responses and predictors are centered, so the intercept term can be omitted.
-
-In addition to the ill-posedness of the infinite-dimensional slope functions $\beta_k(t)$ and the high dimensionality of the predictors ($K + p$), a further challenge comes from the strong correlations between functional and scalar predictors.
+The key   challenge here is the strong correlations between functional and scalar predictors,
+in addition to the ill-posedness of the infinite-dimensional slope functions $\beta_k(t)$ and the high dimensionality of the predictors ($K + p$).
 This paper addresses all three issues in a unified manner by introducing a hybrid partial least squares (PLS) regression framework defined on a novel hybrid Hilbert space.
 
-	\subsection{Previous works and limitations}
-	To address the ill-posedness stemming from the infinite-dimensionality of the functional components, common remedies include basis expansion,
-	using power-series  \citep{goldsmithPenalizedFunctionalRegression2011},
-	B-splines \citep{cardotSplineEstimatorsFunctional2003, caiPredictionFunctionalLinear2006}, or 
-	wavelets \citep{zhaoWaveletbasedLASSOFunctional2012},
-	and structure-aware regularization, such as roughness penalties
+	\paragraph{Previous works and limitations}
+Basis expansion with regularization of roughness addresses the ill-posedness of functional data by exploiting their smoothness \citep{cardotSplineEstimatorsFunctional2003,aguileraPenalizedVersionsFunctional2016,
+	caiPredictionFunctionalLinear2006, zhaoWaveletbasedLASSOFunctional2012}.
+High dimensionality can be addressed by using derived inputs, with PCA regression as a straightforward example.
+We can apply PCA  separately to functional (e.g., \citealt{happ_multivariate_2018}) and scalar predictors, followed by multivariate regression on the combined scores.
+While well studied for functional predictors alone \citep{hallMethodologyConvergenceRates2007, reissFunctionalPrincipalComponent2007, febrero-bandeFunctionalPrincipalComponent2017}, PCA regression may fail to capture the core regression relationship since the derived inputs are not guided by the response.
+Partial least squares (PLS) regression is a powerful alternative that constructs orthogonal latent components from predictors to maximize covariance with the response.
+For functional predictors, \citet{predaPLSRegressionStochastic2005} introduced PLS regression for a single predictor, with subsequent extensions incorporating
+basis approximations and roughness penalties
+\citep{reissFunctionalPrincipalComponent2007, aguileraUsingBasisExpansions2010, aguileraPenalizedVersionsFunctional2016}, and multiple functional predictors \citep{beyaztasRobustFunctionalPartial2022}.
+Theoretical and computational advances were developed by \citet{delaigleMethodologyTheoryPartial2012} and \citet{saricamPartialLeastsquaresEstimation2022}, respectively; see \citet{febrero-bandeFunctionalPrincipalComponent2017} for a review.
+These approaches ignore correlations between functional and scalar components, leading to multicollinearity and unreliable prediction.
+Multimodal correlations have mainly been explored in unsupervised settings,
+such as graphical models, precision matrix estimation, and joint PCA \citep{kolar_graph_2014, gengJointNonparametricPrecision2020, jangPrincipalComponentAnalysis2021}.
+However,  these methods are response-agnostic and may miss outcome-relevant correlations.
 
-	For the high-dimensionality, a major solution is using derived inputs.
-	A straightforward approach in this direction is principal component analysis (PCA) regression, which applies PCA separately to the functional- (by, for example, \citealt{happ_multivariate_2018}) and scalar predictors, and then performs a classical multivariate regression on the combined scores.
-	PCA regression is well-studied for linear regression with functional predictors alone \citep{hallMethodologyConvergenceRates2007, reissFunctionalPrincipalComponent2007, febrero-bandeFunctionalPrincipalComponent2017}.
-	However, since the PCA-derived inputs are not informed by the response variable,   they are not guaranteed to capture the core regression relationship with a small number of derived inputs.
-	In terms of predictive power, partial least squares (PLS) regression is a powerful alternative.
-It iteratively constructs a set of orthogonal latent components from the predictors that have the maximal covariance with the response variable, and use the resulting scores for regression.
+\paragraph{Our contributions}
+To address these gaps, we propose a hybrid PLS regression framework that unifies basis expansion, PLS, and functional-scalar correlations.
+Treating functional and Euclidean components as a single vector in a Hilbert space with a suitable inner product, we iteratively extract joint directions that maximize covariance with the response under a unit-norm constraint.
+The framework handles dense or irregular functional data, supports regularization to reduce overfitting, and comes with theoretical guarantees.
+
+\section{Hybrid Hilbert Space and Population Version PLS Algorithm}
+Our framework leverages that the nonlinear iterative PLS (NIPALS; \citealp{woldPathModelsLatent1975}) algorithm, a standard PLS fitting method, operates solely via inner-product space operations.
+We define a Hilbert space for hybrid predictors with a complete inner product to extend the algorithm.
 %
-	PLS for linear regression in the context of functional predictor alone was introduced by \citet{predaPLSRegressionStochastic2005} for the case of a single predictor.
-Motivated by regression on chemometric spectra, \citet{reissFunctionalPrincipalComponent2007}, \citet{aguileraUsingBasisExpansions2010}, and \citet{aguileraPenalizedVersionsFunctional2016} extended the framework by incorporating basis approximations and roughness penalties to promote smoothness.
-\citet{delaigleMethodologyTheoryPartial2012} provided the first thorough theoretical analysis, while \citet{saricamPartialLeastsquaresEstimation2022} proposed a computationally efficient procedure based on Golub-Kahan bidiagonalization.
-For a comprehensive review, see \citet{febrero-bandeFunctionalPrincipalComponent2017}.
-More recently, \citet{beyaztasRobustFunctionalPartial2022} extended the framework to accommodate multiple functional predictors.
-
-	However,  these existing approaches overlook the potentially strong correlations between functional and scalar components, which can lead to multicollinearity and suboptimal predictive performance.
-Multimodal correlations have mostly been addressed within an unsupervised learning framework.
-For instance, \citet{kolar_graph_2014} studied the estimation of joint undirected graphical models for  functional and vector data, while \citet{gengJointNonparametricPrecision2020} considered joint precision matrix estimation for brain measurements and confounding scalar covariate.
-\citet{jangPrincipalComponentAnalysis2021} proposed a joint PCA method that accounts for correlations between functional and scalar data.
-However, the resulting components are still not informed by the response and may fail to capture  correlation with the outcome.
-
-	\subsection{Our contributions}
-	To address the gaps mentioned above, we unify the remedies proposed for these three issues: basis expansion, partial least squares, and accounting for correlations between the functional and scalar components.
-	We propose a hybrid PLS regression framework that integrates functional and vector predictors in a principled and coherent manner.
-To extract predictive structure from these jointly observed and potentially correlated data types, we define a Hilbert space that treats the tuple of functional and vector components as a single hybrid object, equipped with a suitable inner product.
-The hybrid PLS direction is then obtained by iteratively maximizing the empirical covariance with the response, subject to a unit-norm constraint in this Hilbert space.
-Our framework is readily applicable to dense and irregular functional data and supports regularization techniques to prevent overfitting and reduce variance.
-We also provide the mathematical properties that justify our algorithm.
-
-	\section{Background on partial least squares and its extension to hybrid predictors}
-
-	For intuition, let us return to the high-dimensional Euclidean predictor setting $
-	Y_i =  \boldsymbol{\beta}^\top \mathbf{Z}_i + \epsilon_i$.
-	A common way to address ill-posedness and correlation is to approximate the high-dimensional vector $\mathbf{Z}_i$ using a low-dimensional vector $
-	\bigr(
-	\widehat{\rho}_1^{[1]}, \ldots,   \widehat{\rho}_1^{[L]}  
-	\bigr)^\top \in \mathbb{R}^L.
-	$ To retain the regression relationship, the $l$-th PLS direction $\hat{\boldsymbol{\xi}}_l$ solves:
-	\begin{equation}\label{scalar_PLS_sample}
-		\max_{ \mathbf{ h } } 
-		\widehat{\operatorname{Cov}}^2
-		\bigl(
-		\{
-		\langle 
-		\mathbf{ h }, \mathbf{Z}_i
-		\rangle
-		, Y_i
-		\}_{i=1}^n
-		\bigr)~\text{s.t.}~\| \mathbf{ h } \|_2 = 1,~\mathbf{ h }^\top  \widehat{\operatorname{Cov}}^2
-		\bigl(
-		\{
-		\mathbf{Z}_i
-		\}_{i=1}^n
-		\bigr) \hat{\boldsymbol{\xi}}_j = 0, \quad j = 1, \ldots, l-1,
-	\end{equation}
-	where the two $\widehat{\operatorname{Cov}}^2$ denote sample cross-covariance and sample covariance, respectively.
-A standard algorithm for solving this optimization problem, called nonlinear iterative partial least squares (NIPALS) is presented in Algorithm \ref{alg:scalar_pls}.
-	\begin{algorithm} 
-		\caption{Scalar partial least squares regression}\label{alg:scalar_pls}
-		\begin{algorithmic}[1]
-			\State Standardize each $\mathbf{Z}_1, \ldots, \mathbf{Z}_n$ so that each feature have mean zero and variance one. Standardize $Y_1, \ldots, Y_n$.
-			\For{$l = 1, 2, \ldots, L$}
-			\\
-			\textbf{PLS direction and score estimation:}
-			\State $\widehat{\boldsymbol{\xi}}^{[l]} \leftarrow
-			\arg \max_{  \boldsymbol{\alpha}   } 
-			\widehat{\operatorname{Cov}}^2
-			\bigl(
-			\{
-			\langle 
-			\boldsymbol{\alpha}, \mathbf{Z}^{[l]}_i
-			\rangle
-			, Y^{[l]}_i
-			\}_{i=1}^n
-			\bigr)~\text{s.t.}~\| \boldsymbol{\alpha} \|_2 = 1
-			$
-			\Comment{PLS direction}\label{alg:step:scalar_pls_direction}
-			\State 
-			$
-			\widehat{\rho}_i^{[l]} \leftarrow \langle \hat{\boldsymbol{\xi}}^{[l]},   \mathbf{Z}^{[l]}_i \rangle, 
-			~i=1,  \ldots, n
-			$ \Comment{PLS score}
-			\\
-			\textbf{Residualization:}
-			\State $\nu^{[l]} 
-			\leftarrow
-			\frac{
-				\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{i}^{[l]}}{
-				\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}
-			}$ \Comment{Least squares estimate} 
-			%
-			\State $ Y_i^{[l+1]} \leftarrow Y_i^{[l]} - \nu^{[l]}\widehat{\rho}_i^{[l]}~i=1,  \ldots, n$
-			%
-			\State $ \widehat{\boldsymbol{\delta}}^{[l]}  \leftarrow \frac{1}{\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}}\sum_{i=1}^n  \widehat{\rho}_{i}^{[l]}\mathbf{Z}_i^{[l]} $ \Comment{Least squares estimate} 
-			\label{alg:step:scalar_pls_residualization}
-			\State $\mathbf{Z}_i^{[l+1]}  \leftarrow \mathbf{Z}_i^{[l]} -   \widehat{\rho}_{i}^{[l]}  \widehat{\boldsymbol{\delta}}^{[l]} $
-			\EndFor
-			\textbf{Regression coefficient estimation:}
-			\State
-			$\widehat{\boldsymbol{\iota}}^{[1]} \leftarrow \widehat{\boldsymbol{\xi}}^{[1]}$
-			\For{$l =  2, \ldots, L$}
-			\State $\widehat{\boldsymbol{\iota}}^{[l]} \leftarrow \widehat{ \boldsymbol{\xi} }^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}^{[u]}, \widehat{\boldsymbol{\xi}}^{[l]} \rangle 
-			\widehat{\boldsymbol{\iota}}^{[u]}$  
-			\EndFor
-			$	\widehat{\boldsymbol{\beta}} \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{\boldsymbol{\iota}}^{[l]}$ \Comment{regression coefficient estimate}
-			\State \textbf{Output:} the  regression coefficient estimate
-		\end{algorithmic}
-	\end{algorithm}
-
-	To extend Algorithm \ref{alg:scalar_pls} to the hybrid regression model \eqref{eq:hybrid_regression_model}, we must compute hybrid objects in both the PLS direction estimation and predictor residualization steps (lines \ref{alg:step:scalar_pls_direction} and \ref{alg:step:scalar_pls_residualization}).
-These computations cannot be separated into functional and scalar parts, as their correlation must be addressed.
-	A naive approach is to add loops over the observed evaluation points $t$ to lines \ref{alg:step:scalar_pls_direction} and \ref{alg:step:scalar_pls_residualization}, treating  
-	\[
-	\bigl( X_{i1}(t), \ldots, X_{iK}(t), Z_{i1}, \ldots, Z_{ip} \bigr) \in \mathbb{R}^{K+P}
-	\]  
-	as a Euclidean predictor, applying steps \ref{alg:step:scalar_pls_direction} and \ref{alg:step:scalar_pls_residualization}, and aggregating the results.
-This pointwise method, however, is computationally prohibitive for densely observed functional predictors, infeasible for irregular data, and prone to variability across the domain, resulting in overfitting and unstable predictions.
-	The main challenge of extension to the hybrid setting lies in the following points. First, 
-	independent variables consist of multiple highly structured images and scalar predictors. 
-	Second, our sample size is small compared to the dimension and number of functional and scalar predictors.
-	Third,  existing partial least squares (PLS) methods can only accommodate (i) univariate or multivariate functional predictors without any scalar predictors \citep{predaPLSRegressionStochastic2005, delaigleMethodologyTheoryPartial2012, febrero-bandeFunctionalPrincipalComponent2017, Beyaztas2020}; or (ii) a univariate functional predictor with other scalar predictors \citep{Wang2018}.
-	The next section proposes a new extension framework that addresses these issues.
-
-	\section{Proposed PLS Algorithm} \label{section:main:our_algorithm}
-	Our new framework builds on the fact that all computations in Algorithm \ref{alg:scalar_pls} are arithmetic operations in an inner product space.
-We therefore formally define the Hilbert space of hybrid random predictors along with its corresponding complete inner product, and leverage them to extend Algorithm \ref{alg:scalar_pls}.
-	\begin{definition}[Hybrid space]\label{def:hilbert_space}
-		Let $\mathbb{H}$ be a product space defined as the Cartesian product of $K$ copies of the space of square-integrable functions on $[0,1]$ and the $p$-dimensional Euclidean space:
-		$$
-		\mathbb{H} := (\mathbb{L}^2[0,1])^K \times \mathbb{R}^p.
-		$$
-		An element $h \in \mathbb{H}$ is an ordered tuple $h = (f_1, \dots, f_K, \mathbf{u})$, where $f_k \in \mathbb{L}^2[0,1]$ for $k=1, \dots, K$ and $\mathbf{u} \in \mathbb{R}^p$.
-This space is equipped with element-wise vector addition and scalar multiplication.
+\begin{theorem}[Hybrid space]\label{def:hilbert_space}
+	An element $h \in \mathbb{H} := (\mathbb{L}^2[0,1])^K \times \mathbb{R}^p$ is an ordered tuple $h = (f_1, \dots, f_K, \mathbf{u})$, where $f_k \in \mathbb{L}^2[0,1]$ for $k=1, \dots, K$ and $\mathbf{u} \in \mathbb{R}^p$.
 We define an inner product on $\mathbb{H}$ for any two elements $h_1 = (f_1, \dots, f_K, \mathbf{u})$ and $h_2 = (g_1, \dots, g_K, \mathbf{v})$ as:
 \begin{equation}\label{eq: hybrid inner product}
-			\langle h_1, h_2 \rangle_{\mathbb{H}} := \sum_{k=1}^K \int_0^1 f_k(t) g_k(t) \, dt + \omega \mathbf{u}^\top \mathbf{v},
+	\langle h_1, h_2 \rangle_{\mathbb{H}} := \sum_{k=1}^K \int_0^1 f_k(t) g_k(t) \, dt +   \mathbf{u}^\top \mathbf{v}.
 \end{equation}
-		where $\omega$ is a positive constant ($\omega > 0$).
 	The inner product induces a norm $\Vert \cdot \Vert_{\mathbb{H}}$ on the space, defined as $\Vert h \Vert_{\mathbb{H}} := \langle h, h \rangle_{\mathbb{H}}^{1/2}$, and a corresponding metric $d(h_1, h_2) = \Vert h_1 - h_2 \Vert_{\mathbb{H}}$.
-	\end{definition}
-	In \eqref{eq: hybrid inner product}, 
-	$\omega$ is a positive weight that needs to be pre-specified or estimated.
-It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}).
-	Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$. The results remain valid for any positive weights. 
-	\begin{lemma}[Hybrid Hilbert space]\label{lemma:hybrid_hilbert_space}
-		The hybrid space $\mathbb{H}$ is a separable Hilbert space.
-	\end{lemma} 
-	Proof of Lemma \ref{lemma:hybrid_hilbert_space} is provided in Appendix \ref{section:proof:lemma:hybrid_hilbert_space}.
+	Then the hybrid inner product space $\mathbb{H}$ is a separable Hilbert space.
+\end{theorem}
 
@@
 \end{equation}
-	\begin{remark}
-		Our method is applicable to settings where each functional predictor belongs to a different Hilbert space, possibly defined over a distinct compact domain in $\mathbb{R}^d$, for arbitrary $d$, and observed at different time points.
-However, for notational simplicity, our discussion assumes a common Hilbert space over domain $[0,1]$ for all functional predictors.
-	\end{remark}
 
-	Our approach provides an efficient and robust means of producing PLS components and scores in the presence of multiple dense and/or irregular functional predictors and scalar predictors.
-It also incorporates a regularization scheme that enables the algorithm to borrow strength and exploit structural relationships within and between the functions to avoid overfitting of the PLS components and to improve the generalizability and interpretability of the predictive model.
-	Each iteration of our approach consists of two subroutines: regularized estimation of smoothed PLS components and orthogonalization, detailed in Sections~\ref{section:sub:compute_PLS_component} and~\ref{section:sub:residualization}, respectively.
-After a suitable number of iterations, the hybrid regression coefficient is estimated, as described in Section~\ref{section:sub:regression_coeff}.
-For notational simplicity, we omit the iteration index $l$ in the following discussion, with the understanding that the subroutines apply to any iteration.
-The complete algorithm is summarized in Algorithm~\ref{alg:hybrid_pls}.
-
-	\subsection{Preliminary step 1: finite-basis approximation}\label{sec: finite basis approximation}	
-	Let ${b_m(t)}$ be a twice-differentiable basis of $\mathbb{L}^2([0,1])$ whose second derivatives are also linearly independent, for example, cubic B-splines, the Fourier basis, or an orthonormal polynomial basis of degree greater than three.
-Using this basis,
-	the $j$th functional predictor, 
-	regression coefficient, PLS component direction, and orthogonalization regression coefficient (with iteration indices suppressed) are represented as follows:
-	\begin{equation*}
-		X_{ij}(t) = \sum_{m=1}^\infty \theta_{ijm} \, b_m(t),~
-		\beta_j(t) = \sum_{m=1}^\infty \eta_{jm} \, b_m(t),~
-		%%%%%%%%%%%%%%%%%%%%%%
-		\xi_j(t)
-		=
-		\sum_{m=1}^\infty
-		\gamma_{jm}
-		b_m(t),
-		~
-		\delta_j(t)
-		=
-		\sum_{m=1}^\infty
-		\pi_{jm}
-		b_m(t)		
-	\end{equation*}	
-	In practice, the full set of coefficients can not be obtained  with finite sample size, as functional data are measured on a finite grid. Thus, we truncate the expansion at $M$ terms.
-	We choose a moderately large $M$ (e.g., 15 or 20) to capture functional variation without fine-tuning, as smoothness is handled via penalization (see Section~\ref{sec: Regularization of PLS Components}).
-	The truncated expansions of the predictor and coefficient are denoted as
-	\begin{equation*}
-		\widetilde{X}_{ij}(t) := \sum_{m=1}^M \theta_{ijm} \, b_m(t), \quad
-		\tilde{\beta}_j(t) := \sum_{m=1}^M \eta_{jm} \, b_m(t),
-	\end{equation*}
-	and our suggest method restricts each PLS component direction and orthogonalization regression coefficient to admit the following expansion:
-	\begin{equation}\label{def:truncated_zeta_and_delta}
-		\xi_j(t) = \sum_{m=1}^M \gamma_{jm} \, b_m(t),
-		\quad
-		\delta_j(t)
-		=
-		\sum_{m=1}^M
-		\pi_{jm}
-		b_m(t)		
-	\end{equation}
-	This implies that all computations in this paper are carried out entirely within the subspace
-	\begin{equation}\label{def:truncated_hilbert_space}
-		\widetilde{ \mathbb{H} } := \operatorname{span}\bigl(b_1(t), \ldots, b_M(t)\bigr)^K \times \mathbb{R}^p \subset \mathbb{H}.
-	\end{equation}
-	The $i$th hybrid predictor, projected on $\widetilde{ \mathbb{H} }$, is represented by the tuple
-	\begin{equation*}
-		\widetilde{W}_i := 
-		(
-		\widetilde{X}_{i1}, \ldots, \widetilde{X}_{iK}, \boldsymbol{Z}_i
-		).
-	\end{equation*}
-	Let $\boldsymbol{\theta}_{ij}$, $\boldsymbol{\eta}_j$,  $\boldsymbol{\gamma}_j$, and
-	$\boldsymbol{\pi}_j$
-	denote the $M$-dimensional vectors of coefficients:
-	\begin{equation}\label{def:coef_vector_form}
-		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top,
-		~
-		\boldsymbol{\eta}_{j} := (\eta_{j1}, \ldots, \eta_{jM})^\top ,~
-		\boldsymbol{\gamma}_{j} := (\gamma_{j1}, \ldots, \gamma_{jM})^\top,~
-		\boldsymbol{\pi}_{j} := (\pi_{j1}, \ldots, \pi_{jM})^\top
-	\end{equation}
-	For the predictors, we stack the coefficient vectors across observations into the matrix
-	\begin{equation}\label{def:theta}
-		\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M},
-	\end{equation}
-	and construct the full design matrix 
-	\begin{equation}\label{def:full_theta}
-		\Theta := (\Theta_1, \ldots, \Theta_K, \mathbf{Z}) \in \mathbb{R}^{n \times (MK + p)}.
-	\end{equation}
-	Let us denote the response vector as $\mathbf{y} := (y_1, \ldots, y_n)^\top$.
-	Let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, with entries
-	\begin{equation}\label{def:B_matrix}
-		B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt, \quad
-		B^{\prime\prime}_{m, m'} := \int_0^1 b_m''(t)\, b_{m'}''(t)\, dt,
-	\end{equation}
-	for $m, m' = 1, \ldots, M$. We then define the block-diagonal matrices
-	\begin{equation}\label{def:gram_block}
-		\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p), \quad
-		\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
-	\end{equation}
-
-	Then the full data for the hybrid PLS problem at the $l$-th iteration can be represented by the tuple
-	\begin{equation}\label{def:problem_instance}
-		(\mathbb{B}, \mathbb{B}^{\prime\prime}, \Theta, \mathbf{y}) \in 
-		\mathbb{R}^{(MK+p) \times (MK+p)} \times 
-		\mathbb{R}^{(MK+p) \times (MK+p)} \times 
-		\mathbb{R}^{n \times (MK+p)} \times 
-		\mathbb{R}^n,
-	\end{equation}
-	with the index $l$ omitted for brevity.
-
-	\begin{remark}
-		While different bases could be used for each functional predictor, we adopt a common basis for simplicity.
-The definitions of $\mathbb{B}$ and $\mathbb{B}^{\prime\prime}$ remain general enough to accommodate distinct bases if needed.
-	\end{remark}
-
-	%Additionally, it serves as a regularization mechanism, borrowing strength across components and helping to prevent overfitting.
-
-	\subsection{Preliminary step 2 : data preprocessing} \label{subsec: Data Preprocessing}
-	Functional and scalar elements of the hybrid predictors often have incompatible units and/or exhibit different amounts of variation.
-This can be problematic for our PLS framework which is not scale invariant as: i) each predictor has different chance of contributing to the predictor/response structure; and ii) a predictor with high correlation to $Y$ but relatively low variance may be overlooked.
-
-	To obtain PLS components that have a meaningful interpretation, we standardize the predictor data via the following steps.
-The first step is to account for discrepancies \textit{within} respective functional and scalar parts, if needed.
-If the functional parts $\widetilde{X}_{i1}(t), \ldots, \widetilde{X}_{iK}(t)$ are measured in different units or have quite different domains, one can standardize them to have mean zero and integrated variance of one.
-If multivariate scalar predictors $\mathbf{Z}_i=(Z_{i1}, \ldots, Z_{ip})^\top$ exhibit different amounts of variation, one can standardize them to have mean zero and unit variance.
-The second step is to eliminate the discrepancies \textit{between} functional and scalar parts.
-To accomplish this aim, we choose an appropriate weight $\omega$ in the hybrid inner product \eqref{eq: hybrid inner product} that ensures functional and vector parts have comparable variance.
-A sensible data-driven approach to choosing an appropriate weight is to set
-	\begin{equation*}
-		\omega = \frac{\sum_{i=1}^n \sum_{k=1}^K \Vert \widetilde{X}_i \Vert^2_{\mathbb{L}^2[0,1]}}{\sum_{i=1}^n \Vert \mathbf{Z}_i \Vert_2^2},
-		\label{eq: weight}
-	\end{equation*}
-	In practice, 
-	instead of using inner product weighted by $\omega^{1/2}$, one can implement 
-	this weighting scheme   by formulating the hybrid object as $\widetilde{W}_i = \bigl(
-	\widetilde{X}_{i1}(t), \ldots, \widetilde{X}_{iK}(t),  \omega^{1/2} \mathbf{Z}_i
-	\bigr)$, whose vector part has been scaled by a factor of $\omega^{1/2}$.
-
-	\subsection{Iterative steps}\label{section:sub:iterative}
-	The iterative process presented here yields an orthonormal hybrid basis that effectively captures the predictor-response relationships.
-It proceeds through two intermediate steps: the estimation of the PLS component direction (Section \ref{section:sub:compute_PLS_component}) and residualization (Section \ref{section:sub:residualization}).
-	The proofs are deferred to Appendix \ref{section:proof:section:sub:iterative}.
-	The properties of the resulting estimates are introduced in Section \ref{section:main:properties_of_our_method}.
-	\subsubsection{Iterative step 1: regularized estimation of  PLS component direction}  \label{section:sub:compute_PLS_component} 
-	We begin by formally introducing the core optimization problem pertinent to the PLS direction estimation, which is formulated as a generalized Rayleigh quotient (Proposition \ref{proposition:eigen_noregul}).
-Building upon this foundational concept, we present our regularized PLS component direction estimation step that promotes smoothness (Proposition \ref{proposition:eigen_regul}).
-Furthermore,  we detail an efficient computational scheme (Proposition \ref{proposition:linear_regul}).
-
-	\medskip
-	\noindent
-	\textit{Core optimization problem.}\label{sec: pls component computation intermediate}~
-	We   present the core optimization problem that directly estimates the hybrid PLS component direction.
-It fully leverages the continuous nature of the functional components and the function-scalar hybrid structure.
-	We describe the strategy at the $l$-th iteration.
-%For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{section:sub:residualization} for details).
-	The  PLS component direction is estimated by the unit-norm direction $\xi^{[l]} \in \widetilde{\mathbb{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathbb{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathbb{H}}$ and the responses $y_1, \ldots, y_n$, defined as
-
-	\begin{equation}\label{def:squared_empirical_cov}
-		\widehat{\textnormal{Cov}} 
-		( \langle 
-		\widetilde{W},
-		\xi \rangle_{\mathbb{H}}, Y )
-		:=
-		\frac{1}{n} 
-		\sum_{i=1}^n
-		y_i
-		\langle \widetilde{W}_i, \xi \rangle_{\mathbb{H}}
-		.
-	\end{equation}
-	We denote the estimated PLS component direction as
-	\begin{equation}\label{def:maximizer_squared_empirical_cov}
-		\hat{\xi} 
-		:= \arg \max_{\xi \in \widetilde{\mathbb{H}}
-		}~\widehat{\textnormal{Cov}}^2 
-		\bigl(
-		\langle \widetilde{W}, \xi \rangle_{\mathbb{H}}, Y 
-		\bigr)~s.t.~\| \xi  \|_\mathbb{H} = 1.
-	\end{equation}
-	%
-	Here, $\hat{\xi} \in \widetilde{\mathbb{H}}$ is an ordered pair  expanded as:
-	\begin{equation*}
-		\hat{\xi}	= 
-		\bigl(
-		\hat{\xi}_1(t), \ldots, \hat{\xi}_K(t), \hat{\boldsymbol{\zeta}}
-		\bigr)
-		=
-		\biggl(
-		\sum_{m=1}^M \hat{\gamma}_{1m} \, b_m(t),
-		\ldots, 
-		\sum_{m=1}^M \hat{\gamma}_{Km} \, b_m(t), \hat{\boldsymbol{\zeta}}
-		\biggr)
-		,
-	\end{equation*}
-	where  $\hat{\boldsymbol{\zeta}}$ is the scalar part.
-Obtaining these coefficients is equivalent to solving the maximization problem   \eqref{def:maximizer_squared_empirical_cov}.
-The following proposition formulates this coefficients obtaining procedure as a generalized Rayleigh quotient:
-	%
-	\begin{proposition}\label{proposition:eigen_noregul}
-		Let
-		$
-		(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
-		$
-		denote the observed data defined in \eqref{def:problem_instance}.
-		At the $l$-th iteration of the PLS algorithm, 
-		the coefficients of the squared covariance  maximizer defined in \eqref{def:maximizer_squared_empirical_cov}, 
-		is obtained as
-		\begin{equation}	\label{eq: Unregularized generalized rayleigh quotient equation}
-			\left(
-			\hat{\gamma}_{11}, \ldots, \hat{\gamma}_{1M}
-			, \ldots,
-			\hat{\gamma}_{K1}, \ldots, \hat{\gamma}_{KM}
-			, \hat{\boldsymbol{\zeta}}^\top
-			\right)^\top
-			=
-			\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
-			\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1.
-		\end{equation}
-		where
-		\begin{equation}\label{def:V_matrix}
-			V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)}.
-		\end{equation}
-	\end{proposition}
-	The proof of Proposition \ref{proposition:eigen_noregul}
-	is provided in Appendix \ref{section:proof:proposition:linear_regul_system_unregularized}.
-
-	\medskip
-	\noindent
-	\textit{Proposed regularized estimation procedure.}~ \label{sec: Regularization of PLS Components}
-	Although Proposition \ref{proposition:eigen_noregul} offers an efficient way to estimate the PLS component direction $\hat{\xi}$, its functional components, $\hat{\xi}_1, \ldots, \hat{\xi}_K$, may not be smooth.
-which complicates interpretation and can lead to overfitting and unstable predictions.
-	To address this, we propose a regularized extension that balances predictive performance with smoothness.
-Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative
-	\begin{equation}\label{def:roughness_penalty}
-		\operatorname{PEN}(\hat{\xi}_j) := \int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
-		.
-	\end{equation}
-
-	Instead of solely maximizing the squared empirical covariance
-	$\widehat{\textnormal{Cov}}^2 
-	\bigl(
-	\langle \widetilde{W}, \xi \rangle_\mathbb{H}, Y 
-	\bigr)
-	$, 
-	we incorporate this roughness penalty to simultaneously control the complexity of the estimated functional components.
-	One possible approach is to extend the smoothed functional PCA framework of \citet{Rice1991} by modifying the objective in \eqref{def:maximizer_squared_empirical_cov} to
-	\begin{equation*}
-		\widehat{\textnormal{Cov}}^2 
-		\bigl(
-		\langle \widetilde{W}, \xi \rangle_{\mathbb{H}}, Y 
-		\bigr)
-		- \sum \limits_{j=1}^K \lambda_j 
-		\operatorname{PEN}({\xi}_j)
-		,
-	\end{equation*}
-	where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness. 
-	However, this approach  \citet{Rice1991} assumes that the functional predictors admit an orthogonal expansion in the $\mathbb{L}^2$ sense.
-
-	To avoid the orthogonal basis assumption of  \citet{Rice1991}, we adopt the strategy of \citet{Silverman1996}, which replaces the standard orthonormality constraint with a weaker one based on a modified inner product that incorporates roughness.
-Accordingly, our estimation procedure at the $l$-th iteration, iteration index omitted and assuming the observations have been residualized in previous steps, solves the following optimization problem:
-	\begin{equation}\label{def:maximizer_squared_empirical_cov_reg}
-		\hat{\xi} 
-		:= \arg \max_{\xi \in \widetilde{\mathbb{H}}
-		}~\widehat{\textnormal{Cov}}^2 
-		\bigl(
-		\langle \widetilde{W}, \xi \rangle_{\mathbb{H}}, Y 
-		\bigr)~s.t.~\| \xi  \|_\mathbb{H} +  \sum \limits_{j=1}^K \lambda_j 
-		\operatorname{PEN}(\xi_K) = 1.
-	\end{equation}
-	Here, $\hat{\xi} \in \widetilde{\mathbb{H}}$ is an ordered pair  expanded as:
-	\begin{equation*}
-		\hat{\xi}	= 
-		\bigl(
-		\hat{\xi}_1(t), \ldots, \hat{\xi}_K(t), \hat{\boldsymbol{\zeta}}
-		\bigr)
-		=
-		\biggl(
-		\sum_{m=1}^M \hat{\gamma}_{1m} \, b_m(t),
-		\ldots, 
-		\sum_{m=1}^M \hat{\gamma}_{Km} \, b_m(t), \hat{\boldsymbol{\zeta}}
-		\biggr)
-		,
-	\end{equation*}
-	where  $\hat{\boldsymbol{\zeta}}$ is the scalar part.
-	This formulation maximizes the squared covariance over a class of smooth functions.
-	Obtaining these coefficients is equivalent to solving the maximization problem   \eqref{def:maximizer_squared_empirical_cov_reg}.
-The following proposition formulates this coefficients obtaining procedure as a generalized Rayleigh quotient:
-	\begin{proposition}[Regularized estimation of PLS component direction]\label{proposition:eigen_regul}
-		Let
-		$
-		(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
-		$
-		denote the  data given at the $l$-th iteration, as defined in \eqref{def:problem_instance}.
-		Recall from \eqref{def:V_matrix} that $
-		V = n^{-2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top$ .
-		Let 
-		$\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ be defined as:
-		\begin{equation}\label{def:Lambda}
-			\Lambda := \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p}),
-			~\text{where}~\lambda_1, \ldots, \lambda_K \geq 0.
-		\end{equation}
-		Here, $0_{p \times p}$ denotes the $p \times p$ zero matrix.
-		The coefficients of the squared covariance  maximizer defined in \eqref{def:maximizer_squared_empirical_cov_reg}, 
-		are obtained as
-		\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
-			\left(
-			\hat{\gamma}_{11}, \ldots, \hat{\gamma}_{1M}
-			, \ldots,
-			\hat{\gamma}_{K1}, \ldots, \hat{\gamma}_{KM}
-			, \hat{\boldsymbol{\zeta}}^\top
-			\right)^\top
-			\hspace{-.7em}
-			=
-			\arg 
-			\hspace{-.6em}
-			\max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
-			~~\text{s.t.}~~
-			%
-			% constraint
-			\boldsymbol{\xi}^\top 
-			\hspace{-.2em}
-			(\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1.
-		\end{equation}
-
-	\end{proposition}
-	The proof of Proposition \ref{proposition:eigen_regul} is provided in Appendix  \ref{section:proof:proposition:eigen_regul}.
-	%orthonormality preview
-	The constraint $	\boldsymbol{\xi}^\top (\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1$
-	enforces the orthonormality of the estimated PLS component directions with respect to a modified inner product (see Section \ref{section:sub:geom} for details).
-	The smoothing parameter $\lambda_k$  balances goodness of fit and smoothness in $\hat{\xi}_j$.
-Smaller $\lambda_k$ yields components that better fit the data but risks overfitting; setting $\lambda_k = 0$ recovers the unregularized solution in Proposition~\ref{proposition:eigen_noregul}.
-Larger $\lambda_k$ enforces greater smoothness, and in the limit $\lambda_k \to \infty$, $\hat{\xi}_j(t)$ approaches a linear form $a + bt$.
-In practice, both $\{\lambda_k\}$ and the number of components $L$ can be selected via cross-validation using a predictive criterion such as mean squared error.
-
-	\medskip
-	\noindent{\textit{Computation.}}~The generalized eigenproblem presented in Proposition~\ref{proposition:eigen_regul}  may be computationally unstable in practice.
-However, by leveraging the rank-one structure of the matrix
-	$V$
-	Proposition \ref{proposition:linear_regul} derives a closed-form solution that requires only the solution of linear systems.
-	\begin{proposition}[Closed-form solution]  
-		\label{proposition:linear_regul}  
-		Consider the optimization problem described in Proposition~\ref{proposition:eigen_regul}. Define the following quantities, which depend on the observed data but are not decision variables:  
-		\[
-		\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M \quad \text{for } j = 1, \ldots, K, \quad \text{and} \quad \mathbf{v} := \mathbf{Z}^\top \mathbf{y} \in \mathbb{R}^p.
-		\]  
-		Let
-		\[
-		q := \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v}.
-		\]
-
-		Then the unique (up to sign) solution to the regularized maximization problem is given in closed form by  
-		\[
-		\hat{\boldsymbol{\gamma}}_j = \frac{1}{\sqrt{q}} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j \quad \text{for } j = 1, \ldots, K, \quad \text{and} \quad
-		\hat{\boldsymbol{\zeta}} = \frac{1}{\sqrt{q}} \mathbf{v}.
-		\]  
-	\end{proposition}
-	The proof of Proposition~\ref{proposition:linear_regul} is provided in Appendix~\ref{section:proof:proposition:linear_regul}.
-The expressions above involve solving linear systems for the functional and scalar components separately, followed by normalization by a common factor.
-Although the unnormalized coefficients are obtained independently, the normalization step couples the functional and scalar parts, allowing them to influence one another.
-This coupling enables the procedure to capture the correlation between the functional and scalar components of the PLS direction.
-
-	\subsubsection{Iterative step 2: residualization via hybrid-on-scalar regression} \label{section:sub:residualization}
-	The $l$-th iteration's second step involves residualization of both predictors and responses. We first compute the individual PLS score:  
-	\begin{equation}\label{def:plsscore}
-		\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathbb{H}},
-	\end{equation}
-	using the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. 
-	Since   $\widetilde{W}_i^{[l]}$ are assumed to have a sample mean of zero, these PLS scores will also have a sample mean of zero.
-	To obtain the $(l+1)$-th  iteration's responses and hybrid predictors, we regress the $(l)$-th iteration's responses and hybrid predictors on  
-	these PLS scores by least squares and then residualize. 
-	Specifically,
-	the $(l+1)$-th predictor is computed as a residual of hybrid-on-scalar linear regression model:
-	\begin{equation*}
-		\widetilde{W}_i^{[l]}  =
-		\widehat{\rho}_i^{[l]}
-		\hat{\delta}^{[l]} + \epsilon_i,
-	\end{equation*}
-	where $\hat{\delta}^{[l]} \in \widetilde{\mathbb{H}}$ is the regression coefficient.
-	In the same spirit as the PLS component direction estimation step,
-	rather than treating the hybrid object as a long vector of concatenated function evaluations at time points and scalar vectors,
-	we employ a basis expansion approach to fit the entire hybrid object in one step.
-	Therefore, our method is computationally efficient, and applicable for dense or irregular functional data.
-	Consequently, $\delta^{[l]}$ is obtained by minimizing a  
-	least squares criterion: impossible. Smoothness of $\beta$ seems to soley rely on the smoothness of $\xi$. See Section \ref{section:sub:regression_coeff}.
-	\begin{equation}\label{def:argmin_pensse}
-		\hat{\delta}^{[l]} := \arg \min_{\delta \in \widetilde{\mathbb{H}}} \sum_{i=1}^n 
-		\| \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta\|_{\mathbb{H}}^2.
-	\end{equation}
-	On the other hand, the $(l+1)$-th response   is computed as a residual of a scalar-on-scalar linear regression model:
-	\begin{equation*}
-		Y_i^{[l]}  =
-		\hat{\nu}^{[l]}   	\widehat{\rho}_i^{[l]} + \epsilon_i.
-	\end{equation*}
-	The following proposition demonstrates that this residualization step can be performed simply, analogous to scalar PLS.
-	\begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
-		Let us denote
-		$
-		\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top.
-		%\quad\text{and} \quad		\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
-		$
-		The $(l+1)$-th iteration's  predictors and responses are computed as
-		\begin{equation*}
-			\widetilde{W}_i^{[l+1]} 
-			:= 	\widetilde{W}_i^{[l]}  - 
-			\widehat{\rho}_i^{[l]}
-			\hat{\delta}^{[l]},~\text{where}~
-			\delta^{[l]}
-			:= 
-			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
-			\sum_{i=1}^n 
-			\widehat{\rho}_i^{[l]}
-			\widetilde{W}_i^{[l]},
-			%%%%%%%%%%% 
-			,
-		\end{equation*} 	
-		and
-		\begin{equation}\label{algorithm_step:residualization_predictor}
-			Y_i^{[l+1]} = Y_i^{[l]} - 
-			\hat{\nu}^{[l]} 
-			\widehat{\rho}_i^{[l]},~\text{where}~\hat{\nu}^{[l]} :=  
-			\frac{
-				\mathbf{y}^{[l] \top }  \hat{\boldsymbol{\rho}}^{[l]}
-			}{
-				\| \hat{\boldsymbol{\rho}}^{[l]} \|_2^2
-			}.
-		\end{equation}
-	\end{lemma}
-	Proof of Lemma \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
-	Since $\widetilde{W}_i^{[l]}$ and $Y_i^{[l]}$ are assumed to have a sample mean of zero, their respective residuals, $\widetilde{W}_i^{[l+1]}$ and $Y_i^{[l+1]}$, also maintain a zero sample mean.
-
-	\subsection{Final step: estimating  the hybrid regression coefficient}
-	\label{section:sub:regression_coeff}
-	The hybrid regression coefficient $\beta$ in model \eqref{eq: Hybrid functional model} can be written 
-	as a linear combination of PLS directions:
-	\begin{lemma}\label{lemma:recursive}
-		Let use define
-		$
-		\widehat{\iota}^{[1]} := \widehat{\xi}^{[1]}.
-		$
-		For $l \ge 2$, we recursively   define:
-		\begin{equation*}
-			\widehat{ \iota}^{[l]} = \widehat{\xi}^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{ \delta}^{[u]}, \widehat{\xi}^{[l]} \rangle_{\mathbb{H}} \widehat{ \iota}^{[u]}. 
-		\end{equation*}
-		Then we have:
-		\begin{equation*}
-			\widehat{\rho}_i^{[l]}
-			=
-			\langle  W_i^{[l]}, \widehat{\xi}^{[l]} \rangle_\mathbb{H}
-			=
-			\langle  W_i, \widehat{ \iota}^{[l]} \rangle_\mathbb{H}.
-		\end{equation*}
-	\end{lemma}
-	Proof of Lemma \ref{lemma:recursive} is provided in Appendix \ref{section:proof:lemma:recursive}.
-
-	Next,  \eqref{algorithm_step:residualization_predictor} leads to the following model:
-	\begin{equation*}
-		Y_i = \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \widehat{\rho}_i^{[l]} + \epsilon_i.
-	\end{equation*}
-	This model lets us to express $Y_i$ as:
-	\begin{equation*}
-		Y_i = \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \langle W_i^{[l]}, \widehat{\xi}^{[l]} \rangle_\mathbb{H} +\epsilon_i 
-		= 
-		\bigl \langle W_i, \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}
-		\bigr \rangle_\mathbb{H}+\epsilon_i,
-	\end{equation*}
-	which, given the uniqueness of $ \beta $, leads to
-	\begin{equation*}
-		\widehat{ \beta} = \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}
-		\sum_{l=1}^L \left( \widehat{\nu}^{[l]} - \sum_{k=l+1}^L \widehat{\nu}^{[k]} \langle \widehat{\delta}^{[l]}, \widehat{\xi}^{[k]} \rangle_{\mathbb{H}} \right) \widehat{\xi}^{[l]}.
-	\end{equation*}
-	Thus the number of PLS components $L$ to be estimated can be chosen by cross-validation.
-
-	\begin{algorithm} 
-		\caption{Hybrid partial least squares regression}\label{alg:hybrid_pls}
-		\begin{algorithmic}[1]
-			\State 	\textbf{Initialize:} $(\mathbb{B}, \mathbb{B}^{\prime\prime}, \Theta^{[1]}, \mathbf{y}^{[1]})$ as the data objects after basis expansion, following Section \ref{sec: finite basis approximation}.
-
-			\State   $\widetilde{W}_1^{[1]}, \ldots, \widetilde{W}_n^{[1]}, Y_1^{[1]}, \ldots, Y_n^{[1]} \leftarrow$ standardized versions of $W_1, \ldots, W_n, Y_1, \ldots, Y_n$, following Section \ref{subsec: Data Preprocessing}
-			\For{$l = 1, 2, \ldots, L$}
-			\\
-			\textbf{PLS direction and score estimation  (Proposition \ref{proposition:linear_regul}): }
-			\State $\mathbf{u}_j^{[l]} \leftarrow B \Theta_j^{[l]\top} \mathbf{y}^{[l]}, ~j = 1, \ldots, K$
-			\State $\mathbf{v}^{[l]} \leftarrow \mathbf{Z}^{[l]\top} \mathbf{y}^{[l]} $
-			\State $	q^{[l]}  \leftarrow \sum_{j=1}^K \mathbf{u}_j^{[l]\top} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j^{[l]} + \mathbf{v}^{[l]\top} \mathbf{v}^{[l]}$
-			\State $( \hat{\gamma}_{j1}^{[l]} , \ldots, \hat{\gamma}_{jM}^{[l]} )^\top  \leftarrow \frac{1}{\sqrt{q}} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j^{[l]} , ~j = 1, \ldots, K$
-			\State $\hat{\boldsymbol{\zeta}}^{[l]}  \leftarrow \frac{1}{\sqrt{q}} \mathbf{v}^{[l]} $
-			\State $	\hat{\xi}^{[l]}	\leftarrow 
-			\biggl(
-			\sum_{m=1}^M \hat{\gamma}_{1m}^{[l]} \, b_m(t),
-			\ldots, 
-			\sum_{m=1}^M \hat{\gamma}_{Km}^{[l]} \, b_m(t), \hat{\boldsymbol{\zeta}}^{[l]}
-			\biggr)
-			$
-			\Comment{PLS direction} 
-			\State 
-			$
-			\widehat{\rho}_i^{[l]} \leftarrow \langle \hat{\xi}^{[l]},   \tilde{W}^{[l]}_i \rangle, 
-			~i=1,  \ldots, n
-			$ \Comment{PLS score}
-			\\
-			\textbf{Residualization (Proposition \ref{proposition:closed_form_orthgonalization}):}
-			\State $\nu^{[l]} 
-			\leftarrow
-			\frac{
-				\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{i}^{[l]}}{
-				\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}
-			}$ \Comment{Least squares estimate} 
-			%
-			\State $ Y_i^{[l+1]} \leftarrow Y_i^{[l]} - \nu^{[l]}\widehat{\rho}_i^{[l]}~i=1,  \ldots, n$
-			%
-			\State $ \widehat{ \delta }^{[l]}  \leftarrow \frac{1}{\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}}\sum_{i=1}^n  \widehat{\rho}_{i}^{[l]}\widetilde{W}_i^{[l]} $ \Comment{Least squares estimate} 
-			\label{alg:step:scalar_pls_residualization}
-			\State $\widetilde{W}_i^{[l+1]}  \leftarrow \widetilde{W}_i^{[l]} -   \widehat{\rho}_{i}^{[l]}  \widehat{ \delta}^{[l]} $
-			\EndFor
-			\textbf{Regression coefficient estimation (Section \ref{section:sub:regression_coeff}):}
-			\State
-			$\widehat{ \iota }^{[1]} \leftarrow \widehat{ \xi }^{[1]}$
-			\For{$l =  2, \ldots, L$}
-			\State $\widehat{ \iota }^{[l]} \leftarrow \widehat{  \xi }^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{ \delta }^{[u]}, \widehat{ \xi }^{[l]} \rangle  \widehat{ \iota }^{[u]}$  
-			\EndFor
-			$	\widehat{ \beta } \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \iota}^{[l]}$ \Comment{regression coefficient estimate}
-			\State \textbf{Output:} the  regression coefficient estimate $	\widehat{ \beta }$
-		\end{algorithmic}
-	\end{algorithm}
-
-	\section{Properties of the hybrid PLS}
-	\label{section:main:properties_of_our_method}
-	This section provides the mathematical properties that support the algorithm suggested in Section \ref{section:main:our_algorithm}.
-	Section \ref{section:sub:tucker} shows that the core optimization problem for the Partial Least Squares (PLS) direction estimation step, presented in Proposition \ref{proposition:eigen_noregul}, is well-defined under mild conditions.
-	Section \ref{section:sub:geom} demonstrates that our algorithm preserves the core properties of PLS, namely the orthonormality of the derived directions and the orthogonality of the scores.
-
-	\subsection{ Tucker's Criterion  }\label{section:sub:tucker} 
-	We now derive the population analogue of Algorithm~\ref{alg:hybrid_pls} and establish its key mathematical properties, namely the orthogonality of the PLS directions and scores, as well as convergence to the true response.
+We now derive the population version of NIPALS in the hybrid space.
 At the population level, where the random objects are fully observable, we may drop the sample index $i$ and simply work with $Y$
@@
 At the population level, this quantity is naturally characterized by cross-covariance operators, which we define next.
-For notational simplicity, we suppress the iteration index $l$, with the understanding that for $l=1$ the predictors correspond to the original variables, while for $l \geq 2$ they represent the residualized versions.
+%For notational simplicity, we suppress the iteration index $l$, with the understanding that for $l=1$ the predictors correspond to the original variables, while for $l \geq 2$ they represent the residualized versions.
 \begin{definition}\label{def:cross_cov_terms}
 	The covariance operator of the hybrid predictor $W$ is denoted as $\Sigma_{W} := \mathbb{E}[W \otimes W]$, so that for $u,v \in \mathbb{H}$, we have
-		\[
+	$
 	\Sigma_{W} u = \mathbb{E}[
@@
 	],
-		\quad
-		\langle \Sigma_{W} u, v \rangle_{\mathbb{H}}
+	$
+	$\langle \Sigma_{W} u, v \rangle_{\mathbb{H}}
 	= \mathbb{E}[\langle W,u \rangle_{\mathbb{H}} \, \langle W,v \rangle_{\mathbb{H}}].
-		\]
-
+	$
 	The cross-covariances between the response $Y$ and the predictors are
@@
 \end{definition}
-	At the population level, Algorithm \ref{alg:hybrid_pls} without regularizaiton can be expressed as follows.
+Now we explain the NIPALS algorithm at the population level.
 Let $W^{[1]} := W$ and $Y^{[1]} := Y$.
 For any   integer $l \geq 2$,
-	to be the residuals of the
-
-	where
-
-	and
-
-	which is attained by the leading eigenfunction of the operator 
-	$\mathcal{U}^{[l-1]}$, defined analogously to Lemma~\ref{lemma:composite_cross_cov} 
-	using $W^{[l-1]}$ and $Y^{[l-1]}$, provided the conditions in 
-	Lemma~\ref{lemma:cross_cov_functional} are satisfied.
-	\begin{definition}[Population PLS]\label{def:population_pls}
-		The population analogue of the PLS optimization problem \eqref{scalar_PLS_sample} in the hybrid space is formulated as the constrained generalized eigenproblem:
+$W^{[l]}$ and $Y^{[l]}$ are residuals (see line 7,8 of Algorithm \ref{alg:population_pls}).
+The PLS direction maximizes the squared covariance:
+\begin{definition}\label{def:population_pls} Hybrid PLS direction at the $l$-th step,
+	denoted $\xi^{[l]}$,
+	is defined as
 	\begin{equation}\label{const_eigen_pop}
-			\xi^{[l]} = \arg\max_{h \in \mathbb{H}}
+		\xi^{[l]} := \arg\max_{h \in \mathbb{H}}
 		\operatorname{Cov}^2(\langle W, h \rangle_{\mathbb{H}}, Y),~s.t.~\|h\|_{\mathbb{H}}=1, \langle h, \Sigma_W \, \xi^{[j]} \rangle_{\mathbb{H}} = 0,\, j < l.
@@
 \end{definition}
-	As in scalar case, this problem can be solved by an iterative algorithm, and yields orthogonal scores:
-	\begin{proposition}[Properties of population PLS]
+This problem can be solved by an iterative algorithm, and yields orthogonal scores:
+\begin{theorem}[Properties of population PLS]
 	\label{prop:residualization_equiv_eigen}
@@
 
-	\end{proposition}
-	Proof of Proposition \ref{prop:residualization_equiv_eigen} is provided in Appendix \ref{section:proof:prop:residualization_equiv_eigen}.
+\end{theorem}
 \begin{algorithm} 
@@
 \end{algorithm}
-
-	We show that problem \eqref{const_eigen_pop} and Algorithm \ref{alg:population_pls} are well-defined under mild conditions by  establishing that line \ref{alg:line:pls_direction} of Algorithm \ref{alg:population_pls} is well-defined under mild conditions.
-For clarity, we define the relevant operators while omitting the iteration index for the residualized predictors and responses.
+We show in Theorem \ref{theorem:population_PLS} that problem \eqref{const_eigen_pop} and Algorithm \ref{alg:population_pls} are well-defined under mild conditions by proving line \ref{alg:line:pls_direction} is well-defined.
+To this end, Lemmas \ref{lemma:cross_cov_functional} and \ref{lemma:composite_cross_cov}
+define the relevant operators, omitting the iteration index for residualized predictors, responses, and operators.
 \begin{lemma}\label{lemma:cross_cov_functional}
@@
 	\end{equation*} 
-		If 
-		$\sigma_{YX}$ and $\sigma_{YZ}$ are bounded in the sense that
-		there exist finite constants $Q_1$ and $Q_2$ such that
+	The operator $\mathcal{C}_{YW}$ is a compact operator
+	if   there exist finite constants $Q_1$ and $Q_2$ such that
 	\begin{align}\label{condition_for_compact}
@@
 		[Y X_{k}](t)^2 < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \mathbb{E}
-			[Y Z_{r}]^2 < Q_2,
+		[Y Z_{r}]^2 < Q_2.
 	\end{align}
-		the operator $\mathcal{C}_{YW}$ is a compact operator.
 \end{lemma}
-	Proof of Lemma \ref{lemma:cross_cov_functional}
-	is provided in Appendix \ref{section:proof:lemma:cross_cov_functional}.
-	\begin{lemma}\label{lemma:cross_cov_operator}
-		Define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]$,
-		such that for any  $d \in \mathbb{R}$,
-		%%%%
-		\begin{align*}		
-			\mathcal{C}_{WY} d 
-			:= 
-			\mathbb{E} 
-			\bigl[
-			\langle Y, d \rangle W 
-			\bigr] 
-			= 
-			\mathbb{E}
-			[ Y W d ] =  d \, \Sigma_{Y W} \in \mathbb{H}.
-		\end{align*}
-		Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
-	\end{lemma}	
-	The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.
 
-	\begin{lemma}[Composite cross-covariance operator]\label{lemma:composite_cross_cov}
+\begin{lemma}\label{lemma:composite_cross_cov}
 	Define
-		$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathbb{H} \rightarrow \mathbb{H}$ as an operator which performs the following mapping:
+	$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathbb{H} \rightarrow \mathbb{H}$ as an operator such that,
+	for $h \in \mathbb{H}$,
 	\begin{equation*}
@@
 \end{lemma}
-	The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
 By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Lemma \ref{lemma:composite_cross_cov} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathbb{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.
-
-	The following theorem presents population-level PLS and Tucker's Criterion for our scalar-on-hybrid regression model and ensures that line \ref{alg:line:pls_direction} of Algorithm \ref{alg:population_pls} is well-defined under mild conditions.
+The following theorem presents   ensures that line \ref{alg:line:pls_direction} of Algorithm \ref{alg:population_pls} is well-defined under mild conditions.
 \begin{theorem}[Tucker's criterion]\label{theorem:population_PLS} Under the conditions of Lemma \ref{lemma:cross_cov_functional}, the constrained maximum
-		\begin{equation*} 
+	$
 		\max \limits_{\substack{ \Vert \xi \Vert_\mathbb{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathbb{H}, Y \right)
-		\end{equation*} 
+	$
 	is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
 \end{theorem}
-	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.
-
 Finally, the following theorem states that the fitted values from hybrid PLS converge to those of ordinary linear regression in the mean-squared sense.
 This shows that hybrid PLS, as a dimension-reduction technique, can effectively capture the predictive power of a full linear model when a sufficient number of components is used.
-	\begin{theorem}[$L^2$ Convergence of Hybrid PLS at Population Level]\label{thm:hybrid_pls_convergence}
+\begin{theorem}\label{thm:hybrid_pls_convergence}
 	Let $Y_{\mathrm{PLS}, L} = \sum_{l=1}^L \nu^{[l]} \rho^{[l]}$ be the Hybrid PLS fitted value with $L$ components. Then, the Hybrid PLS fitted value converges to $Y$ in the mean-squared sense:
 	\begin{equation*}
-			\lim_{L \to \infty} \mathbb{E}\left[ \| Y_{\mathrm{PLS},L } - Y  \|_2^2 \right] = 0
+		\lim_{L \to \infty} \mathbb{E}\left[ \| Y_{\mathrm{PLS},L } - Y  \|_2^2 \right] = 0.
 	\end{equation*}
 \end{theorem}
-	The proof of Theorem \ref{thm:hybrid_pls_convergence} is provided in Appendix \ref{section:proof:thm:hybrid_pls_convergence}.
 
+\section{Proposed PLS Algorithm}\label{section:main:our_algorithm}
+We propose a sample version of hybrid NIPALS (Algorithm \ref{alg:population_pls}) that efficiently computes PLS components and scores for multiple dense or irregular functional predictors and scalar predictors.
+Our algorithm incorporates regularization to exploit structural relationships, prevent overfitting, and improve interpretability.
+Each iteration involves two subroutines: regularized component estimation (Section \ref{section:sub:compute_PLS_component})  and residualization 
+(Section \ref{section:sub:residualization})
+After iteration terminates 
+the hybrid regression coefficient is estimated (Section~\ref{section:sub:regression_coeff}).
+  %
+\subsection{Preliminary step: finite-basis approximation}\label{sec: finite basis approximation}
+Let $\{b_m(t)\}$ be a twice-differentiable basis of $\mathbb{L}^2([0,1])$ whose second derivatives are also linearly independent, for example, cubic B-splines, Fourier, or orthonormal cubic polynomials.
+Fourier coefficients of
+functional predictors
+$X_{ij}(t)$,
+functional regression coefficients
+$\beta_j(t)$,
+PLS directions,
+$\xi_j(t)$,
+and residualization coefficients
+$\delta_j(t)$
+(with iteration indices suppressed) with respect to 
+$\{b_m(t)\}$ are denoted as
+$\{\theta_{ijm}\},
+\{ \eta_{jm} \},
+\{ \gamma_{jm} \},
+$
+and
+$\{ \pi_{jm} \}$.
+For practicality, we truncate the expansion at a moderate $M$ (e.g., 15-20) to capture most functional variation, while smoothness is handled via penalization (Section~\ref{section:sub:compute_PLS_component}).
+The truncated expansion for the functional data is denoted
+as
+are denoted as $\widetilde{X}_{ij}(t)
+:=
+\sum_{m=1}^M \theta_{ijm}  b_m(t)$, but for the other funtions, we denote
+\begin{equation}\label{def:truncated_zeta_and_delta}
+	\beta_j(t)
+	:=
+	\sum_{m=1}^M \eta_{jm} b_m(t),
+	%
+	\xi_j(t) := \sum_{m=1}^M \gamma_{jm}  b_m(t),
+	%
+	\delta_j(t)
+	=
+	\sum_{m=1}^M
+	\pi_{jm}
+	b_m(t),
+\end{equation}
+since these functions are estimated, using a hat over the tilde notation would be cumbersome.
+Let Let $\boldsymbol{\theta}_{ij}$, $\boldsymbol{\eta}_j$, $\boldsymbol{\gamma}_j$, and $\boldsymbol{\pi}_j$ denote these coefficients as $M$-dimensional vectors.
+The truncations imply that all computations in this paper are carried out entirely within the subspace
+\begin{equation}\label{def:truncated_hilbert_space}
+	\widetilde{ \mathbb{H} } := \operatorname{span}\bigl(b_1(t), \ldots, b_M(t)\bigr)^K \times \mathbb{R}^p \subset \mathbb{H}.
+\end{equation}
+The $i$th hybrid predictor, projected on $\widetilde{ \mathbb{H} }$, is represented by the tuple
+$ 
+\widetilde{W}_i := 
+(
+\widetilde{X}_{i1}, \ldots, \widetilde{X}_{iK}, \boldsymbol{Z}_i
+).
+$ 
+For notational convenience, we stack the predictor coefficient vectors as
+\begin{equation}\label{def:theta}
+	\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M},
+	\quad 
+	\Theta := (\Theta_1, \ldots, \Theta_K, \mathbf{Z}) \in \mathbb{R}^{n \times (MK + p)}.
+\end{equation}
+Let us denote the response vector as $\mathbf{y} := (y_1, \ldots, y_n)^\top$.
+Let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, with entries
+\begin{equation}\label{def:B_matrix}
+	B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt, \quad
+	B^{\prime\prime}_{m, m'} := \int_0^1 b_m''(t)\, b_{m'}''(t)\, dt,
+\end{equation}
+for $m, m' = 1, \ldots, M$. We then define the block-diagonal matrices
+\begin{equation}\label{def:gram_block}
+	\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p), \quad
+	\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
+\end{equation}
+
+Then the full data for the hybrid PLS problem at the $l$-th iteration can be represented by the tuple
+\begin{equation}\label{def:problem_instance}
+	(\mathbb{B}, \mathbb{B}^{\prime\prime}, \Theta, \mathbf{y}) \in 
+	\mathbb{R}^{(MK+p) \times (MK+p)} \times 
+	\mathbb{R}^{(MK+p) \times (MK+p)} \times 
+	\mathbb{R}^{n \times (MK+p)} \times 
+	\mathbb{R}^n,
+\end{equation}
+with the index $l$ omitted for brevity.
+
+\begin{remark}
+	Different bases could be used for each functional predictor to handle  multiple dense or irregular functional predictors.
+We adopt a common basis for simplicity.
+The definitions of $\mathbb{B}$ and $\mathbb{B}^{\prime\prime}$ remain general enough to accommodate distinct bases if needed.
+\end{remark}
+
+\subsection{Iterative steps}\label{section:sub:iterative}
+The iterative process presented here yields an orthonormal hybrid basis that effectively captures the predictor-response relationships.
+It proceeds through two intermediate steps: the estimation of the PLS component direction (Section \ref{section:sub:compute_PLS_component}) and residualization (Section \ref{section:sub:residualization}).
+
+\subsubsection{Iterative step 1: regularized estimation of  PLS component direction}\label{section:sub:compute_PLS_component} 
+If the PLS direction estimates $\hat{\xi}_j$ are non-smooth, they produce a nonsmooth regression coefficient $\hat{\beta}$, since it is a linear combination of the PLS directions (Section \ref{section:sub:regression_coeff}).
+Non-smooth $\hat{\beta}$ can cause overfitting and reduce interpretability.
+To address this, we propose a smoothness-enforcing estimation procedure by penalizing the roughness of each $\hat{\xi}_j$ via its integrated squared second derivative:
+\begin{equation}\label{def:roughness_penalty}
+	\operatorname{PEN}(\hat{\xi}_j) := \int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
+	.
+\end{equation}
+Instead of solely maximizing the squared empirical covariance
+$\widehat{\textnormal{Cov}}^2(\langle \widetilde{W}, \xi \rangle_\mathbb{H}, Y)$ as in the classical NIPALS algorithm, we add a roughness penalty to simultaneously control the complexity of the estimated functional components.
+Our estimation procedure at the $l$-th iteration, iteration index omitted and assuming the observations have been residualized in previous steps, solves the following optimization problem:
+\begin{equation}\label{def:maximizer_squared_empirical_cov_reg}
+	\hat{\xi} 
+	:= \arg \max_{\xi \in \widetilde{\mathbb{H}}
+	}~\widehat{\textnormal{Cov}}^2 
+	\bigl(
+	\langle \widetilde{W}, \xi \rangle_{\mathbb{H}}, Y 
+	\bigr)~s.t.~\| \xi  \|_\mathbb{H} +  \sum \limits_{j=1}^K \lambda_j 
+	\operatorname{PEN}(\xi_K) = 1.
+\end{equation}
+Here, $\hat{\xi} \in \widetilde{\mathbb{H}}$ is an ordered pair  expanded as:
+\begin{equation*}
+	\hat{\xi}	= 
+	\bigl(
+	\hat{\xi}_1(t), \ldots, \hat{\xi}_K(t), \hat{\boldsymbol{\zeta}}
+	\bigr)
+	=
+	\biggl(
+	\sum_{m=1}^M \hat{\gamma}_{1m} \, b_m(t),
+	\ldots, 
+	\sum_{m=1}^M \hat{\gamma}_{Km} \, b_m(t), \hat{\boldsymbol{\zeta}}
+	\biggr)
+	,
+\end{equation*}
+where  $\hat{\boldsymbol{\zeta}}$ is the scalar part.
+	 The following theorem formulates the procedure 
+obtaining this coefficients
+as a generalized Rayleigh quotient maximization:
+\begin{theorem}[Regularized estimation of PLS component direction]\label{theorem:eigen_regul}
+	Let
+	$
+	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
+	$
+	denote the  data given at the $l$-th iteration, as defined in \eqref{def:problem_instance}.
+	Let $
+	V := n^{-2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top$ .
+	Let 
+	$\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ be defined as:
+	\begin{equation}\label{def:Lambda}
+		\Lambda := \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p}),
+		~\text{where}~\lambda_1, \ldots, \lambda_K \geq 0.
+	\end{equation}
+	Here, $0_{p \times p}$ denotes the $p \times p$ zero matrix.
+	The coefficients of the squared covariance  maximizer defined in \eqref{def:maximizer_squared_empirical_cov_reg}, 
+	are obtained as
+	\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
+		\left(
+		\hat{\gamma}_{11}, \ldots, \hat{\gamma}_{1M}
+		, \ldots,
+		\hat{\gamma}_{K1}, \ldots, \hat{\gamma}_{KM}
+		, \hat{\boldsymbol{\zeta}}^\top
+		\right)^\top
+		\hspace{-.7em}
+		=
+		\arg 
+		\hspace{-.6em}
+		\max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
+		~~\text{s.t.}~~
+		%
+		% constraint
+		\boldsymbol{\xi}^\top 
+		\hspace{-.2em}
+		(\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1.
+	\end{equation}
+
+\end{theorem}
+%orthonormality preview
+The constraint $	\boldsymbol{\xi}^\top (\mathbb{B} + \Lambda \mathbb{B}^{\prime \prime}) \boldsymbol{\xi} = 1$
+enforces the orthonormality of the estimated PLS component directions with respect to a modified inner product (see Section \ref{section:sub:geom} for details).
+The smoothing parameter $\lambda_k$  balances goodness of fit and smoothness in $\hat{\xi}_j$.
+Smaller $\lambda_k$ yields components that better fit the data but risks overfitting.
+Larger $\lambda_k$ enforces greater smoothness, and in the limit $\lambda_k \to \infty$, $\hat{\xi}_j(t)$ approaches a linear form $a + bt$.
+In practice, both $\{\lambda_k\}$ and the number of components $L$ can be selected via cross-validation using a predictive criterion such as mean squared error.
+
+\medskip
+\noindent{\textit{Computation.}}~The generalized eigenproblem presented in theorem~\ref{theorem:eigen_regul}  may be computationally unstable in practice.
+However, by leveraging the rank-one structure of the matrix
+$V$
+theorem \ref{theorem:linear_regul} derives a closed-form solution that requires only the solution of linear systems.
+\begin{theorem}[Closed-form solution]  
+	\label{theorem:linear_regul}  
+	Consider the optimization problem described in theorem~\ref{theorem:eigen_regul}. Define the following quantities, which depend on the observed data but are not decision variables:  
+	\[
+	\mathbf{u}_j := B \Theta_j^\top \mathbf{y} \in \mathbb{R}^M \quad \text{for } j = 1, \ldots, K, \quad \text{and} \quad \mathbf{v} := \mathbf{Z}^\top \mathbf{y} \in \mathbb{R}^p.
+	\]  
+	Let
+	\[
+	q := \sum_{j=1}^K \mathbf{u}_j^\top (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j + \mathbf{v}^\top \mathbf{v}.
+	\]
+
+	Then the unique (up to sign) solution to the regularized maximization problem is given in closed form by  
+	\[
+	\hat{\boldsymbol{\gamma}}_j = \frac{1}{\sqrt{q}} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j \quad \text{for } j = 1, \ldots, K, \quad \text{and} \quad
+	\hat{\boldsymbol{\zeta}} = \frac{1}{\sqrt{q}} \mathbf{v}.
+	\]  
+\end{theorem}
+ The expressions above involve solving linear systems for the functional and scalar components separately, followed by normalization by a common factor.
+Although the unnormalized coefficients are obtained independently, the normalization step couples the functional and scalar parts, allowing them to influence one another.
+This coupling enables the procedure to capture the correlation between the functional and scalar components of the PLS direction.
+
+\subsubsection{Iterative step 2: residualization via hybrid-on-scalar regression} \label{section:sub:residualization}
+The $l$-th iteration's second step involves residualization of both predictors and responses. We first compute the individual PLS score:  
+\begin{equation}\label{def:plsscore}
+	\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathbb{H}},
+\end{equation}
+using the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Theorems \ref{theorem:eigen_regul} and \ref{theorem:linear_regul}. 
+Since   $\widetilde{W}_i^{[l]}$ are assumed to have a sample mean of zero, these PLS scores will also have a sample mean of zero.
+To obtain the $(l+1)$-th  iteration's responses and hybrid predictors, we regress the $(l)$-th iteration's responses and hybrid predictors on  
+these PLS scores by least squares and then residualize. 
+Specifically,
+the $(l+1)$-th predictor is computed as a residual of hybrid-on-scalar linear regression model:
+\begin{equation*}
+	\widetilde{W}_i^{[l]}  =
+	\widehat{\rho}_i^{[l]}
+	\hat{\delta}^{[l]} + \epsilon_i,
+\end{equation*}
+where $\hat{\delta}^{[l]} \in \widetilde{\mathbb{H}}$ is the regression coefficient.
+In the same spirit as the PLS component direction estimation step,
+rather than treating the hybrid object as a long vector of concatenated function evaluations at time points and scalar vectors,
+we employ a basis expansion approach to fit the entire hybrid object in one step.
+Therefore, our method is computationally efficient, and applicable for dense or irregular functional data.
+Consequently, $\delta^{[l]}$ is obtained by minimizing a  
+least squares criterion: 
+\begin{equation}\label{def:argmin_pensse}
+	\hat{\delta}^{[l]} := \arg \min_{\delta \in \widetilde{\mathbb{H}}} \sum_{i=1}^n 
+	\| \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta\|_{\mathbb{H}}^2.
+\end{equation}
+On the other hand, the $(l+1)$-th response   is computed as a residual of a scalar-on-scalar linear regression model
+$
+	Y_i^{[l]}  =
+	\hat{\nu}^{[l]}   	\widehat{\rho}_i^{[l]} + \epsilon_i.
+$
+The following theorem demonstrates that this residualization step can be performed simply, analogous to scalar PLS.
+\begin{lemma}[Closed-form  solution]\label{theorem:closed_form_orthgonalization}
+	Let us denote
+	$
+	\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top.
+	%\quad\text{and} \quad		\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
+	$
+	The $(l+1)$-th iteration's  predictors and responses are computed as
+	\begin{equation*}
+		\widetilde{W}_i^{[l+1]} 
+		:= 	\widetilde{W}_i^{[l]}  - 
+		\widehat{\rho}_i^{[l]}
+		\hat{\delta}^{[l]},~\text{where}~
+		\delta^{[l]}
+		:= 
+		\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
+		\sum_{i=1}^n 
+		\widehat{\rho}_i^{[l]}
+		\widetilde{W}_i^{[l]},
+		%%%%%%%%%%% 
+		,
+	\end{equation*} 	
+	and
+	\begin{equation}\label{algorithm_step:residualization_predictor}
+		Y_i^{[l+1]} = Y_i^{[l]} - 
+		\hat{\nu}^{[l]} 
+		\widehat{\rho}_i^{[l]},~\text{where}~\hat{\nu}^{[l]} :=  
+		\frac{
+			\mathbf{y}^{[l] \top }  \hat{\boldsymbol{\rho}}^{[l]}
+		}{
+			\| \hat{\boldsymbol{\rho}}^{[l]} \|_2^2
+		}.
+	\end{equation}
+\end{lemma}
+Since $\widetilde{W}_i^{[l]}$ and $Y_i^{[l]}$ are assumed to have a sample mean of zero, their respective residuals, $\widetilde{W}_i^{[l+1]}$ and $Y_i^{[l+1]}$, also maintain a zero sample mean.
+
+\subsection{Final step: estimating  the hybrid regression coefficient}
+\label{section:sub:regression_coeff}
+The hybrid regression coefficient $\beta$ in model \eqref{eq: Hybrid functional model} can be written 
+as a linear combination of PLS directions:
+\begin{lemma}\label{lemma:recursive}
+	Let use define
+	$
+	\widehat{\iota}^{[1]} := \widehat{\xi}^{[1]}.
+	$
+	For $l \ge 2$, we recursively   define:
+	\begin{equation*}
+		\widehat{ \iota}^{[l]} = \widehat{\xi}^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{ \delta}^{[u]}, \widehat{\xi}^{[l]} \rangle_{\mathbb{H}} \widehat{ \iota}^{[u]}. 
+	\end{equation*}
+	Then we have:
+	\begin{equation*}
+		\widehat{\rho}_i^{[l]}
+		=
+		\langle  W_i^{[l]}, \widehat{\xi}^{[l]} \rangle_\mathbb{H}
+		=
+		\langle  W_i, \widehat{ \iota}^{[l]} \rangle_\mathbb{H}.
+	\end{equation*}
+\end{lemma}
+Next,  \eqref{algorithm_step:residualization_predictor} leads to the following model:
+\begin{equation*}
+	Y_i = \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \widehat{\rho}_i^{[l]} + \epsilon_i.
+\end{equation*}
+This model lets us to express $Y_i$ as:
+\begin{equation*}
+	Y_i = \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \langle W_i^{[l]}, \widehat{\xi}^{[l]} \rangle_\mathbb{H} +\epsilon_i 
+	= 
+	\bigl \langle W_i, \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}
+	\bigr \rangle_\mathbb{H}+\epsilon_i,
+\end{equation*}
+which, given the uniqueness of $ \beta $, leads to
+\begin{equation}\label{beta_form}
+	\widehat{ \beta} = \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}
+	\sum_{l=1}^L \left( \widehat{\nu}^{[l]} - \sum_{k=l+1}^L \widehat{\nu}^{[k]} \langle \widehat{\delta}^{[l]}, \widehat{\xi}^{[k]} \rangle_{\mathbb{H}} \right) \widehat{\xi}^{[l]}.
+\end{equation}
+Thus the number of PLS components $L$ to be estimated can be chosen by cross-validation.
+
+\begin{algorithm} 
+	\caption{Hybrid partial least squares regression}\label{alg:hybrid_pls}
+	\begin{algorithmic}[1]
+				\State 	\textbf{Initialize:} $(\mathbb{B}, \mathbb{B}^{\prime\prime}, \Theta^{[1]}, \mathbf{y}^{[1]})$ as the data objects after basis expansion (Section \ref{sec: finite basis approximation}).
+
+		\State   $\widetilde{W}_1^{[1]}, \ldots, \widetilde{W}_n^{[1]}, Y_1^{[1]}, \ldots, Y_n^{[1]} \leftarrow$ predictors ans responses from $(\mathbb{B}, \mathbb{B}^{\prime\prime}, \Theta^{[1]}, \mathbf{y}^{[1]})$
+		\For{$l = 1, 2, \ldots, L$}
+		\\
+		\textbf{PLS direction and score estimation  (theorem \ref{theorem:linear_regul}): }
+		\State $\mathbf{u}_j^{[l]} \leftarrow B \Theta_j^{[l]\top} \mathbf{y}^{[l]}, ~j = 1, \ldots, K$
+		\State $\mathbf{v}^{[l]} \leftarrow \mathbf{Z}^{[l]\top} \mathbf{y}^{[l]} $
+		\State $	q^{[l]}  \leftarrow \sum_{j=1}^K \mathbf{u}_j^{[l]\top} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j^{[l]} + \mathbf{v}^{[l]\top} \mathbf{v}^{[l]}$
+		\State $( \hat{\gamma}_{j1}^{[l]} , \ldots, \hat{\gamma}_{jM}^{[l]} )^\top  \leftarrow \frac{1}{\sqrt{q}} (B + \lambda_j B^{\prime\prime})^{-1} \mathbf{u}_j^{[l]} , ~j = 1, \ldots, K$
+		\State $\hat{\boldsymbol{\zeta}}^{[l]}  \leftarrow \frac{1}{\sqrt{q}} \mathbf{v}^{[l]} $
+		\State $	\hat{\xi}^{[l]}	\leftarrow 
+		\biggl(
+		\sum_{m=1}^M \hat{\gamma}_{1m}^{[l]} \, b_m(t),
+		\ldots, 
+		\sum_{m=1}^M \hat{\gamma}_{Km}^{[l]} \, b_m(t), \hat{\boldsymbol{\zeta}}^{[l]}
+		\biggr)
+		$
+		\Comment{PLS direction} 
+		\State 
+		$
+		\widehat{\rho}_i^{[l]} \leftarrow \langle \hat{\xi}^{[l]},   \tilde{W}^{[l]}_i \rangle, 
+		~i=1,  \ldots, n
+		$ \Comment{PLS score}
+		\\
+		\textbf{Residualization (theorem \ref{theorem:closed_form_orthgonalization}):}
+		\State $\nu^{[l]} 
+		\leftarrow
+		\frac{
+			\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{i}^{[l]}}{
+			\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}
+		}$ \Comment{Least squares estimate} 
+		%
+		\State $ Y_i^{[l+1]} \leftarrow Y_i^{[l]} - \nu^{[l]}\widehat{\rho}_i^{[l]}~i=1,  \ldots, n$
+		%
+		\State $ \widehat{ \delta }^{[l]}  \leftarrow \frac{1}{\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}}\sum_{i=1}^n  \widehat{\rho}_{i}^{[l]}\widetilde{W}_i^{[l]} $ \Comment{Least squares estimate} 
+		\label{alg:step:scalar_pls_residualization}
+		\State $\widetilde{W}_i^{[l+1]}  \leftarrow \widetilde{W}_i^{[l]} -   \widehat{\rho}_{i}^{[l]}  \widehat{ \delta}^{[l]} $
+		\EndFor
+		\textbf{Regression coefficient estimation (Section \ref{section:sub:regression_coeff}):}
+		\State
+		$\widehat{ \iota }^{[1]} \leftarrow \widehat{ \xi }^{[1]}$
+		\For{$l =  2, \ldots, L$}
+		\State $\widehat{ \iota }^{[l]} \leftarrow \widehat{  \xi }^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{ \delta }^{[u]}, \widehat{ \xi }^{[l]} \rangle  \widehat{ \iota }^{[u]}$  
+		\EndFor
+		$	\widehat{ \beta } \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \iota}^{[l]}$ \Comment{regression coefficient estimate}
+		\State \textbf{Output:} the  regression coefficient estimate $	\widehat{ \beta }$
+	\end{algorithmic}
+\end{algorithm}
 	\subsection{Geometric properties}\label{section:sub:geom}
-	A fundamental property of partial least squares,
-	as seem in Definition \ref{def:population_pls} and Proposition \ref{prop:residualization_equiv_eigen},
-	is that between iterations, its derived directions are orthonormal and PLS scores are orthogonal.
-Our regularized estimates preserve this property, with respect to a modified inner product that incorporates the roughness penalty, defines as follows:
+A key property of PLS is that its directions are orthonormal and its scores orthogonal across iterations.
+Our regularized estimates preserve this property under a modified inner product that incorporates the roughness penalty, defined as follows:
 \begin{definition}[Roughness-sensitive inner product]\label{def:hybrid_inner_product_roughness}
@@
 \end{definition}
-	Based on this inner product, the following proposition states that the PLS component directions estimated from Proposition  \ref{proposition:eigen_regul} are orthonormal.
-	\begin{proposition}[Orthonormality of estimated PLS component directions]\label{proposition: modified orthnormality of PLS components}
+Based on this inner product, the following theorem states that the PLS component directions estimated from theorem  \ref{theorem:eigen_regul} are orthonormal.
+\begin{theorem}[Orthonormality of estimated PLS component directions]\label{theorem: modified orthnormality of PLS components}
 	The PLS component directions $
 	\widehat{\xi}^{[1]}, \widehat{\xi}^{[2]}, \ldots, \widehat{\xi}^{[L]}
-		$, estimated via Proposition \ref{proposition:eigen_regul} with a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, are mutually orthonormal with respect to the inner product $\langle \cdot, \cdot \rangle_{\mathbb{H}, \Lambda}$.
+	$, estimated via theorem \ref{theorem:eigen_regul} with a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, are mutually orthonormal with respect to the inner product $\langle \cdot, \cdot \rangle_{\mathbb{H}, \Lambda}$.
 That is,
@@
 	\end{equation*}
-	\end{proposition}
-	The proof of Proposition \ref{proposition: modified orthnormality of PLS components} is provided in Appendix \ref{section:proof:proposition: modified orthnormality of PLS components}.
-
-	The next proposition states that the vectors of estimated PLS scores for different iteration numbers are mutually orthogonal.
-	\begin{proposition}	\label{proposition: orthnormality of PLS scores}
-		Recall from Lemma \ref{proposition:closed_form_orthgonalization} that   $\widehat{\boldsymbol{\rho}}^{[l]}$ denote the $n$-dimensional vector whose elements consist of the $l$-th estimated PLS scores ($l=1, \ldots, L$) of $n$ observations.
+\end{theorem}
+The next theorem states that the vectors of estimated PLS scores for different iteration numbers are mutually orthogonal.
+\begin{theorem}	\label{theorem: orthnormality of PLS scores}
+	Recall from Lemma \ref{theorem:closed_form_orthgonalization} that   $\widehat{\boldsymbol{\rho}}^{[l]}$ denote the $n$-dimensional vector whose elements consist of the $l$-th estimated PLS scores ($l=1, \ldots, L$) of $n$ observations.
 	The vectors $\widehat{\boldsymbol{\rho}}^{[1]}, \widehat{\boldsymbol{\rho}}^{[2]}, \ldots, \widehat{\boldsymbol{\rho}}^{[L]}$  are mutually orthogonal in the sense that
@@
 	\end{equation*}
-	\end{proposition}
-	The proof of Proposition \ref{proposition: orthnormality of PLS scores} is provided in Appendix \ref{section:proof:proposition: orthnormality of PLS scores}.
+\end{theorem}
 
-	\section{Simulation studies}
-	To evaluate the superiority of our method under complex dependency structures
-	{\textemdash}
-	specifically, dependencies among functional predictors,
-	among scalar predictors,
-	and between scalar and functional predictors
-	{\textemdash}
+	\section{Application to Renal Study Data} 
+We apply Algorithm \ref{alg:hybrid_pls} to the Emory University renal study data \citep{changBayesianLatentClass2020}, which include 216 kidneys evaluated by diuretic renal scans.
+Following MAG3 injection, (i) baseline renogram (time activity) curves were recorded over 24 min, followed by (ii) post-furosemide curves from a second 20-min scan.
+Additional data comprise (iii) obstruction ratings from three nuclear medicine experts, (iv) eight summary statistics from baseline curves, (v) six summary statistics from post-furosemide curves, and (vi) subject age and gender.
+The response $Y$ was obtained by averaging the experts' diagnoses and applying a min-max scaling and logit transformation.
+We treat (iv), (v), and (vi) as scalar predictors.
+The summary statistics (iv) and (v), while commonly used in medicine and informative about obstruction, do not fully capture the renogram's information.
+Conversely, the renogram curves (i) and (ii), treated as functional predictors, contain complete but overly rich information, making it difficult to isolate the key features.
+Since (iv), (v) and (i), (ii) are highly correlated yet complementary, it is advantageous to include both as predictors.
 
-	\subsection{Synthetic data}
-	To generate functional predictors, we use a matrix-normal distribution, also known as a Kronecker-separable covariance model.
-For each of $i=1, \ldots,  n$, we create a $3 \times 100$ matrix, where each row represents the $i$th observation of a functional predictor with 100 evaluation points.
-This method gives us precise control over  cross-modal (between-row) dependence   and
-	smoothness of the curves (between-column dependence). 
-	\begin{equation*}
-		\mathbf{X} \sim \mathcal{MN}_{m \times n}(\mathbf{M}; \mathbf{R}, \mathbf{C}),
-	\end{equation*}
-	and its log-density is given by
-	\[
-	\log p(\mathbf{X} \mid \mathbf{M}, \mathbf{R}, \mathbf{C}) = -\frac{mn}{2} \log(2\pi) - \frac{m}{2} \log |\mathbf{C}| - \frac{n}{2} \log |\mathbf{R}| - \frac{1}{2} \mathrm{Tr}\left[ \mathbf{C}^{-1} (\mathbf{X} - \mathbf{M})^\top \mathbf{R}^{-1} (\mathbf{X} - \mathbf{M}) \right].
-	\]
-	The key insight behind Kronecker separability is that if
-	$
-	\mathbf{Y} \sim \mathcal{MN}(\mathbf{M}, \mathbf{R}, \mathbf{C}),
-	$
-	then its vectorized form follows a multivariate normal distribution:
-	$
-	\mathrm{vec}(\mathbf{Y}) \sim \mathcal{N}(\mathrm{vec}(\mathbf{M}), \mathbf{C} \otimes \mathbf{R}),
-	$
-	where $\otimes$ denotes the Kronecker product and $\mathrm{vec}$ is the vectorization operator.
+We smoothed the functional predictors using a B-spline basis of order 15. 
+We performed 100 random 70/30 train-test splits, reporting the mean and standard error of test RMSE normalized by the response range.
+Maximum components set to 20 and number of components are set via 5-fold CV with respect to RMSE.
+We compare our method (hybridpls) with two baselines: 
+(i) penalized functional regression (pfr; \citealp{goldsmithPenalizedFunctionalRegression2011}) which can incorporate both functional and scalar predictors,
+and (ii)Principal component regression (fpcr): run both of PCA for multple functional predictors~\cite{happ_multivariate_2018} and scalar PCA and run OLS on the PC scores.
+The results in Table \ref{table} demonstrates that our method outperforms baseline methods.
 
-	We developed a data generation framework leveraging the matrix-normal distribution, an approach previously suggested by our advisor.
-The goal was to create a dataset with a specific, controllable correlation structure between functional and scalar predictors.
-	\begin{comment}
-	The synthetic dataset consisted of n 
-	sample
-	​
-	matrices, each of size 3×n 
-	col
-	​
-	, where n 
-	col
-\end{comment}	​
-	corresponds to the number of evaluation points for each curve.
-To introduce a structured dependence within each row, the row covariance matrix was set to mimic an AR(1) process, which is a special case of a Gaussian process.
-This ensures that each row exhibits the smooth, curve-like characteristics of a functional observation.
-
-	The first two rows of each matrix were treated as functional data.
-The third row was converted into a set of scalar predictors.
-This was accomplished by partitioning the third row into blocks and then averaging the values within each block.
-For instance, if the third row was (1,3,2,4,3,4) and we wanted to generate three scalar predictors, we would partition the row into (1,3), (2,4), and (3,4), yielding the scalar values 2.0,3.0, and 3.5.
-
-	\begin{comment}
-	\begin{figure}[ht!]
+\begin{table}
 	\centering
-		\begin{subfigure}[b]{0.45\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{image/cor_strong.pdf}
-			\caption{Correlation Matrix - Strong Dependency}
-			\label{fig:cor_strong}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.45\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{image/cor_weak.pdf}
-			\caption{Correlation Matrix - Weak Dependency}
-			\label{fig:cor_weak}
-		\end{subfigure}
-
-		\vspace{0.5cm}  % Adjust vertical spacing
-
-		\begin{subfigure}[b]{0.45\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{image/graph_strong.pdf}
-			\caption{Graph Structure - Strong Dependency}
-			\label{fig:graph_strong}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.45\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{image/graph_weak.pdf}
-			\caption{Graph Structure - Weak Dependency}
-			\label{fig:graph_weak}
-		\end{subfigure}
-
-		\caption{Comparison of Correlation Matrices and Graph Structures under Strong and Weak Dependencies.}
-		\label{fig:correlation_graph_comparison}
-	\end{figure}
-\end{comment}
-	\begin{comment}
-		The goal of this simulation is to:
-		\begin{enumerate}
-			\item Utilize a graphical model to introduce a complex dependence structure.
-			\item Demonstrate that our method outperforms the penalized functional regression approach by \citet{goldsmithPenalizedFunctionalRegression2011}.
-			\item Show that our method exhibits superior performance as correlation strength increases.
-		\end{enumerate}
-
-		Our previous setup, presented in Section \ref{simul:meeting_feb}, appeared to achieve these objectives. However, we identified several limitations:
-		\begin{enumerate}
-			\item The resulting precision matrix was singular, requiring us to scale up the diagonal elements to compute its inverse.
-This adjustment disrupted the original AR(1) structure of the functional component, making it significantly less smooth.
-			\item Increasing conditional correlation did not consistently enhance the superiority of our method.
-		\end{enumerate}
-		To address these issues, I will explore alternative functional graphical model settings that exhibit a strong dependence structure—one substantial enough to be detected by statistical methodologies and validated by top statistical journal papers.
-I will evaluate the performance of penalized functional regression on these data-generating models.
-		Among them, I will select three to four settings for comparison against other methods.
-	\end{comment}
-	Building on the functional graphical model simulation of \citet{zhuBayesianGraphicalModels2016}, we generate a mixed graphical model with five nodes, described as follows:  
-	\begin{itemize}
-		\item Nodes F1 and F2: Two functional predictors modeled as Gaussian processes using a truncated Karhunen-Loève expansion, where the eigenbasis consists of Fourier basis functions with a fixed number of basis functions, \(M = 9\).
-		\item  Nodes S1, S2, and S3: Three scalar predictors, each following an \(s\)-dimensional multivariate normal distribution.
-Unlike the functional predictors, these scalar predictors are modeled directly without basis expansion.
-	\end{itemize}
-	To capture dependencies among predictors, we introduce a graph structure that governs their conditional correlations.
-We consider two types of graph structures: a weakly connected graph and a strongly connected graph.
-In the Gaussian process framework, the precision matrix \(\mathbf{R}_0^{-1}\) encodes conditional independence relationships, while its inverse, \(\mathbf{R}_0\), represents marginal covariances.
-This structure extends to a blockwise correlation matrix \(\mathbf{R} \in \mathbb{R}^{(2M + 3s) \times (2M + 3s)}\), where off-diagonal blocks represent correlations between FPC scores and scalar predictor values.
-	Each block \((i, j)\) of \(\mathbf{R}\) is given by \((R_0)_{ij} \mathbf{I}_{M_i, M_j}\), where \(\mathbf{I}_{M_i, M_j}\) is a rectangular identity matrix.
-Here, \(M_i = 9\) if node \(i\) corresponds to a functional predictor and \(M_j = s\) if node \(j\) corresponds to a scalar predictor.
-
-	For each functional predictor, we assgin  \(M\) reference eigenvalues (or FPC score) drawn independently from gamma distributions with decreasing means.
-	These reference eigenvalues will later be multiplies by randomly  multiplier drawn from correlated multivaraite Normal distribution.
-These reference eigenvalues are fixed over all samples and all independent repetition of the experiment.
-We draw it one randomly just to ensure the differentiation between the two functional predictors.
-	we independently draw for each functional predictor from .
-We then sample zero-mean multivariate normal data from the covariance matrix \(\mathbf{R}\).
-The last \(3s\) components are assigned as scalar predictors, while the first \(2M\) components, scaled by their corresponding eigenvalues, serve as FPC scores.
-These scores are then expanded into functional data, evaluated over 100 equally spaced points on \([0,1]\) using a Fourier basis.
-
-	Finally, we introduce structured variability by adding a common mean function, defined as a scaled and shifted sine function.
-To visualize the generated data, Figure \ref{fig:correlation_graph_comparison}  plots functional predictor realizations and heatmaps of sample correlation matrices for both graph structures, illustrating the distinct dependency patterns induced by the precision matrices.
-
-	\subsection{Simulation shown in february 2025 meeting}\label{simul:meeting_feb}
-	To effectively manage the dependencies among functional predictors, scalar covariates, and between functional and scalar predictors, we utilize a Gaussian Markov random field (GMRF) within the framework of Gaussian undirected graphical models.
-In a GMRF, the off-diagonal elements of the precision matrix capture the conditional correlations between the corresponding components.
-Given that our setting involves both functional and scalar covariates, we adopt the simulation setup proposed by \cite{kolar_graph_2014}, which focuses on mixed attribute Gaussian graphical models.
-
-	We construct a graph consisting of two functional predictor nodes and three vector predictor nodes. Below, we sequentially describe the graph structure and the generation process for each node.
-
-	\medskip
-	\noindent
-	\textit{Functional Predictors.}
-	We consider two functional predictors that share the same precision matrix.
-Denoted as \( \boldsymbol{\Theta} := (\theta_{t \tilde{t}}) \in \mathbb{R}^{p \times p} \), this precision matrix follows an AR(1) structure with a white noise variance of \( 0.1^2 \) and an autoregressive coefficient of \( = 0.95 \), ensuring a smooth functional trajectory.
-
-	More formally, each functional predictor is evaluated at \( p \) equally spaced points on \( [0,1] \), with values defined recursively as:
-	\begin{equation*}
-		X^{(k)}_i(0) = 0, \quad 
-		X^{(k)}_i(t)= \rho X^{(k)}_i(t-1) + \varepsilon_{itk}, \quad \varepsilon_{itk} \overset{\text{i.i.d.}}{\sim} \mathcal{N}(0, \sigma^2), \quad t = 1, \dots, p,~i=1, \ldots, n,~k = 1,2.
-	\end{equation*}
-	In this setting, the precision matrix \( \boldsymbol{\Theta} \) exhibits a tridiagonal Toeplitz structure, where the diagonal entries are given by:
-	\begin{equation*}
-		\theta_{tt} = 
-		\begin{cases}
-			\dfrac{1}{\sigma^2(1-0.95^2)}, & t = 1, p, \\
-			\dfrac{1+0.95^2}{\sigma^2(1-0.95^2)}, & 2 \leq t \leq p-1.
-		\end{cases}
-	\end{equation*}
-	The off-diagonal entries are:
-	\begin{equation*}
-		\theta_{t, t+1} = \theta_{t+1, t} = -\dfrac{\rho}{\sigma^2(1-\rho^2)}, \quad 1 \leq t \leq p-1.
-	\end{equation*}
-	Finally, the functional predictors are smoothed using a B-spline basis with 15 basis functions, as described in Section \ref{section:sub:compute_PLS_component}.
-
-	\medskip
-	\noindent
-	\textit{Vector Predictors.}
-	We consider \( s \) vector predictors, each following a \( d \)-dimensional zero-mean Gaussian distribution with a shared precision matrix.
-This precision matrix, denoted as \( \Gamma := (\gamma_{ij}) \in \mathbb{R}^{d \times d} \), follows a Toeplitz structure with exponentially decaying entries, given by:
-	\begin{equation*}  
-		\gamma_{ij} := 0.5^{|i-j|}.
-	\end{equation*}
-
-	\medskip
-	\noindent
-	\textit{Graph Structure.}
-	We arrange five nodes   in a chain structure, where each node follows a sequential order, and the last node connects back to the first, as illustrated in Figure~\ref{fig:graph}.
-An edge in the graph indicates that the connected nodes remain correlated when the values of all other nodes are fixed.
-	The resulting marginal dependence structure is significantly more complex than the chain structure itself.
-We designate nodes \(F_1\) and \(F_2\) as functional predictors and nodes \(V_1\), \(V_2\), and \(V_3\) as vector predictors.
-\begin{comment}
-	\begin{figure}
-		\centering
-		\includegraphics[width=0.4\linewidth]{image/graph}
-		\caption{}
-		\label{fig:graph}
-	\end{figure}
-\end{comment}
-	%
-	To introduce conditional dependencies between the components, we set the off-diagonal blocks of the precision matrix to be $0.5 \mathbf{1}$ if the corresponding components are connected in the graph, and zero otherwise.
-Here, $\mathbf{1}$ denotes a matrix of appropriate dimensions where all elements are equal to 1.
-Overall, we generate a $2p + 3d$-dimensional multivariate Gaussian distribution with mean zero and a precision matrix $\Omega$, structured as follows:
-
-	\[
-	\Omega =
-	\begin{pmatrix}
-		\Omega_{F} & 0.5 \mathbf{1} & 0 & 0 & 0.5 \mathbf{1} \\
-		0.5 \mathbf{1} & \Omega_{F} & 0.5 \mathbf{1} & 0 & 0 \\
-		0 & 0.5 \mathbf{1} & \Omega_{V} & 0.5 \mathbf{1} & 0 \\
-		0 & 0 & 0.5 \mathbf{1} & \Omega_{V} & 0.5 \mathbf{1} \\
-		0.5 \mathbf{1} & 0 & 0 & 0.5 \mathbf{1} & \Omega_{V} \\
-	\end{pmatrix}
-	\]
-
-	For each observation drawn from this multivariate Gaussian distribution, we process
-
-	The regression coefficients for the first functional predictor, $\beta_{F_1}$, are drawn from a multivariate normal distribution $N(0, 5 \mathbf{I}_p)$, with a fixed random seed.
-The coefficients for the second functional predictor, $\beta_{F_2}$, are drawn independently from the same distribution and are also smoothed using a B-spline basis with 10 basis functions.
-	For the vector covariates, the regression coefficients are sampled from $N(0, I_d)$.
-After calculating the inner product of the covariates and their corresponding coefficients, independent Gaussian noise from $N(0, 0.1^2)$ is added to the generated responses to simulate measurement noise.
-
-	The baseline methods are:
-	\begin{itemize}
-		\item Penalized functional regression (pfr)~\cite
-		{goldsmithPenalizedFunctionalRegression2011}\item Principal component regression (fpcr): run both of PCA for multple functional predictors~\cite{happ_multivariate_2018} and scalar PCA and run OLS on the PC scores.
-	\end{itemize}
-	% TODO: \usepackage{graphicx} required
-
-	We compare our method with these baseline methods using $p=100$.
-We consider scenarios with $d=1, 2, 3, 4, 5$ and $n = 100, 200, 300, 400$.
-For each scenario, we use 70\% of the data for training and evaluate prediction performance on the remaining 30\% test set, using the root prediction mean squared error as the evaluation metric.
-For our method and PCR, the maximum number of components are set as 20.
-The number of components is chosen by 5-fold cross validation.
-The results, summarized in Table~\ref{table
-	}, demonstrate that our method consistently outperforms the baseline methods across all scenarios.
-	\begin{comment}
-	\begin{figure}
-		\centering
-		\includegraphics[width=0.9\linewidth]{Screenshot 2025-02-25 125839.png}
-		\caption{Enter Caption}
-		\label{fig:enter-label}
-	\end{figure}
-	\end{comment}
-
-	\section{Data Application}
-
-	\medskip
-	\noindent
-	\textit{Renal study data.}~
-	We applied our proposed hybrid functional PLS regression, along with other regression methods, to the Emory renal study data.
-The study collected data on 226 kidneys (left and right) from 113 subjects, including: (i) baseline renogram curves; (ii) post-furosemide renogram curves; (iii) ordinal ratings of kidney obstruction status (non-obstructed, equivocal, or obstructed) independently assessed by three nuclear medicine experts; (iv) eight kidney-level pharmacokinetic variables derived from radionuclide imaging; and (v) two subject-level variables (age and gender).
-The subjects had a mean age of 57.8 years (SD = 15.5; range = 18–83), with 54 males (48\%) and 59 females (52\%).
-The three experts unanimously classified 153 kidneys as non-obstructed, 5 as equivocal, and 40 as obstructed, while 28 kidneys had discrepant ratings.
-
-	The two renogram curves, (i) and (ii), were treated as functional predictors and smoothed using a B-spline basis of order 15.
-The remaining variables, excluding the diagnosis, were treated as scalar predictors.
-Given the nature of these variables, we assume they are correlated with the renogram curves but not entirely redundant, as they may contain additional useful information.
-Finally, the diagnoses provided by the three experts were averaged and transformed using a min-max logit transformation.
-We splitted the data into 70\% of training data and 30\% of testing data, and evalauted the prediction perforamnec by root mean squared error on the test data, normalized by the range of the test data response.
-
-	\subsection{}
-			...
-
-			% References
-			\newpage
-			\bibliography{bibliography.bib}
-
-			% Tables and Figures at the end
-			\newpage
-			\section*{Tables and Figures}
-
-			% Example Table
-			\begin{table}[htbp]
-				\centering
-				\caption{Example Table Caption.}
-				\begin{tabular}{lll}
+	\caption{Prediction performance on renal study dataset}\label{table}
+	\begin{tabular}{l c}
 		\hline
-					Col1 & Col2 & Col3 \\
+		Method & Test RMSE \\
 		\hline
-					a & b & c \\
+		pfr & 0.2118 (0.0240) \\
+		fpcr & 0.2732 (0.0327) \\
+		hybridpls & 0.1686 (0.0205) \\
 		\hline
@@
 
-			% Example Figure
-			\begin{figure}[htbp]
-				\centering
-				\rule{3in}{2in} % placeholder box
-				\caption{Example Figure Caption.}
-			\end{figure}
-
-			% Uncomment to enforce max number check at compile time
-			%\ifnum\value{totalfigtab}>6
-			%   \errmessage{Too many tables/figures: maximum is 6.}
-			%\fi
+			\bibliography{bibliography.bib}
 

### 2025-10-07 create-FSHybridPLS.Rmd
calcMFPCA_predict

@@
     Description = "This package says hello.  But its actual purpose is to show how an R package can be completely coded in a single R markdown file.",
-    Imports = "fda (>= 6.1.3), Matrix",
+    Imports = "fda (>= 6.1.3), Matrix, funData, foreach",
     `Authors@R` = person(
@@
 ```
+
+# Baseline method: FPCA regression
+
+```{r}
+#' @import funData
+NULL
+
+# define global variable j, used by the foreach package and confusing R CMD CHECK
+globalVariables('j')
+
+#' Utility function that calculates matrix of basis-scalar products (one dimension)
+#'
+#' If the element \eqn{X^{(j)}}{X^{(j)}} is expanded in basis functions \eqn{b_i^{(j)}(t),~ i = 1, \ldots, K_j}{b_i(t)},
+#' this function calculates the \eqn{K_j \times K_j}{K_j  \times K_j} matrix \eqn{B^{(jj)}}{B^{(jj)}} with entries
+#' \deqn{B^{(jj)}_{mn} = \int_{\mathcal{T_j}} b_m^{(j)}(t) b_n^{(j)}(t) \mathrm{d} t}.
+#'
+#' @section Warning: This function is implemented only for functions on one- or two-dimensional domains.
+#'
+#' @param basisFunctions Array of \code{npc} basis functions of dimensions \code{npc x M1} or \code{npc x M1 x M2}.
+#' @param dimSupp dimension of the support of the basis functions (1 or 2)
+#' @param argvals List of corresponding x-values.
+#'
+#' @return A matrix containing the scalar product of all combinations of basis functions (matrix \eqn{B^{(j)}})
+#'
+#' @seealso \code{\link{MFPCA}}, \code{\link[funData]{dimSupp}}
+#'
+#' @keywords internal
+calcBasisIntegrals <- function(basisFunctions, dimSupp, argvals)
+{
+  npc <- dim(basisFunctions)[1]
+
+  #  integral basis matrix
+  B <- array(0, dim = c(npc, npc))
+
+  if(dimSupp == 1) # one-dimensional domain
+  {
+    w <- funData::.intWeights(argvals[[1]])
+
+    for(m in seq_len(npc))
+    {
+      for(n in seq_len(m))
+        B[m, n] <- B[n, m] <- (basisFunctions[m, ]* basisFunctions[n, ])%*%w
+    }
+  }
+  else # two-dimesional domain (otherwise function stops before!)
+  {
+    w1 <- t(funData::.intWeights(argvals[[1]]))
+    w2 <- funData::.intWeights(argvals[[2]])
+
+    for(m in seq_len(npc))
+    {
+      for(n in seq_len(m))
+        B[m, n] <- B[n, m] <-  w1 %*%(basisFunctions[m, , ]* basisFunctions[n, ,])%*%w2
+    }
+  }
+
+  return(B)
+}
+```
+
+```{r}
+#' Multivariate functional principal component analysis for functions on
+#' different (dimensional) domains
+#'
+#' This function calculates a multivariate functional principal component
+#' analysis (MFPCA) based on i.i.d. observations \eqn{x_1, \ldots, x_N} of a
+#' multivariate functional data-generating process \eqn{X = (X^{(1)}, \ldots
+#' X^{(p)})}{X = X^(1), \ldots, X^(p)} with elements \eqn{X^{(j)} \in
+#' L^2(\mathcal{T}_j)}{X^(j) in L^2(calT_j)} defined on a domain
+#' \eqn{\mathcal{T}_j \subset IR^{d_j}}{calT_j of IR^{d_j}}. In particular, the
+#' elements can be defined on different (dimensional) domains. The results
+#' contain the mean function, the estimated multivariate functional principal
+#' components \eqn{\hat \psi_1, \ldots, \hat \psi_M} (having the same structure
+#' as \eqn{x_i}), the associated eigenvalues \eqn{\hat \nu_1 \geq \ldots \geq
+#' \hat \nu_M > 0} and the individual scores \eqn{\hat \rho_{im} =
+#' \widehat{<x_i, \psi_m>}}{\hat \rho_{im} = \hat{<x_i, \psi_m>}}. Moreover,
+#' estimated trajectories for each observation based on the truncated
+#' Karhunen-Loeve representation \deqn{\hat x_i = \sum_{m = 1}^M \hat \rho_{im}
+#' \hat \psi_m}{\hat x_i = \sum_{m = 1}^M \hat \rho_{im} \hat \psi_m} are given
+#' if desired (\code{fit = TRUE}). The implementation of the observations
+#' \eqn{x_i = (x_i^{(1)}, \ldots , x_i^{(p)}),~ i = 1 , \ldots, N}{x_i =
+#' (x_i^(1), \ldots , x_i^(p)), i = 1 , \ldots, N}, the mean function and
+#' multivariate functional principal components \eqn{\hat \psi_1, \ldots, \hat
+#' \psi_M} uses the \code{\link[funData]{multiFunData}} class, which is defined
+#' in the package \pkg{funData}.
+#'
+#' \subsection{Weighted MFPCA}{If the elements vary considerably in domain,
+#' range or variation, a weight vector \eqn{w_1 , \ldots, w_p} can be supplied
+#' and the MFPCA is based on the weighted scalar product \deqn{<<f,g>>_w =
+#' \sum_{j = 1}^p w_j \int_{\mathcal{T}_j} f^{(j)}(t) g^{(j)}(t) \mathrm{d}
+#' t}{<<f,g>>_w = \sum_{j = 1}^p w_j \int_\calT_j f^(j)(t) g^(j)(t) d t} and the
+#' corresponding weighted covariance operator \eqn{\Gamma_w}.}
+#'
+#' \subsection{Bootstrap}{If \code{bootstrap = TRUE}, pointwise bootstrap
+#' confidence bands are generated for the multivariate eigenvalues \eqn{\hat
+#' \nu_1, \ldots, \hat \nu_M } as well as for multivariate functional principal
+#' components \eqn{\hat \psi_1, \ldots, \hat \psi_M}{\hat \psi_1, \ldots, \hat
+#' \psi_M}. The parameter \code{nBootstrap} gives the number of bootstrap
+#' iterations. In each iteration, the observations are resampled on the level of
+#' (multivariate) functions and the whole MFPCA is recalculated. In particular,
+#' if the univariate basis depends on the data (FPCA approaches), basis
+#' functions and scores are both re-estimated. If the basis functions are fixed
+#' (e.g. splines), the scores from the original estimate are used to speed up
+#' the calculations. The confidence bands for the eigenfunctions are calculated
+#' separately for each element as pointwise percentile bootstrap confidence
+#' intervals. Analogously, the confidence bands for the eigenvalues are also
+#' percentile bootstrap confidence bands. The significance level(s) can be
+#' defined by the \code{bootstrapAlpha} parameter, which defaults to 5\%. As a
+#' result, the \code{MFPCA} function returns a list \code{CI} of the same length
+#' as \code{bootstrapAlpha}, containing the lower and upper bounds of the
+#' confidence bands for the principal components as \code{multiFunData} objects
+#' of the same structure as \code{mFData}. The confidence bands for the
+#' eigenvalues are returned in a list \code{CIvalues}, containing the upper and
+#' lower bounds for each significance level.}
+#'
+#'
+#' \subsection{Univariate Expansions}{The multivariate functional principal
+#' component analysis relies on a univariate basis expansion for each element
+#' \eqn{X^{(j)}}{X^(j)}. The univariate basis representation is calculated using
+#' the \code{\link{univDecomp}} function, that passes the univariate functional
+#' observations and optional parameters to the specific function. The univariate
+#' decompositions are specified via the \code{uniExpansions} argument in the
+#' \code{MFPCA} function. It is a list of the same length as the \code{mFData}
+#' object, i.e. having one entry for each element of the multivariate functional
+#' data. For each element, \code{uniExpansion} must specify at least the type of
+#' basis functions to use. Additionally, one may add further parameters. The
+#' following basis representations are supported: \itemize{\item Given basis
+#' functions. Then \code{uniExpansions[[j]] = list(type = "given", functions,
+#' scores, ortho)}, where \code{functions} is a \code{funData} object on the
+#' same domain as \code{mFData}, containing the given basis functions. The
+#' parameters \code{scores} and \code{ortho} are optional. \code{scores} is an
+#' \code{N x K} matrix containing the scores (or coefficients) of the observed
+#' functions for the given basis functions, where \code{N} is the number of
+#' observed functions and \code{K} is the number of basis functions. Note that
+#' the scores need to be demeaned to give meaningful results. If scores are not
+#' supplied, they are calculated using the given basis functions. The parameter
+#' \code{ortho} specifies whether the given basis functions are orthonormal
+#' \code{orhto = TRUE} or not \code{ortho = FALSE}. If \code{ortho} is not
+#' supplied, the functions are treated as non-orthogonal. \code{scores} and
+#' \code{ortho} are not checked for plausibility, use them at your own risk!
+#' \item Univariate functional principal component analysis. Then
+#' \code{uniExpansions[[j]] = list(type = "uFPCA", nbasis, pve, npc, makePD)},
+#' where \code{nbasis,pve,npc,makePD} are parameters passed to the
+#' \code{\link{PACE}} function for calculating the univariate functional
+#' principal component analysis. \item Basis functions expansions from the
+#' package \pkg{fda}. Then \code{uniExpansions[[j]] = list(type = "fda", ...)},
+#' where \code{...} are passed to \code{\link[funData]{funData2fd}}, which
+#' heavily builds on \code{\link[fda]{eval.fd}}. If \pkg{fda} is not available,
+#' a warning is thrown. \item Spline basis functions (not penalized). Then
+#' \code{uniExpansions[[j]] = list(type = "splines1D", bs, m, k)}, where
+#' \code{bs,m,k} are passed to the functions \code{\link{univDecomp}} and
+#' \code{\link{univExpansion}}. For two-dimensional tensor product splines, use
+#' \code{type = "splines2D"}. \item Spline basis functions (with smoothness
+#' penalty). Then \code{uniExpansions[[j]] = list(type = "splines1Dpen", bs, m,
+#' k)}, where \code{bs,m,k} are passed to the functions \code{\link{univDecomp}}
+#' and \code{\link{univExpansion}}. Analogously to the unpenalized case, use
+#' \code{type = "splines2Dpen"} for 2D penalized tensor product splines. \item
+#' Cosine basis functions. Use \code{uniExpansions[[j]] = list(type = "DCT2D",
+#' qThresh, parallel)} for functions one two-dimensional domains (images) and
+#' \code{type = "DCT3D"} for 3D images. The calculation is based on the discrete
+#' cosine transform (DCT) implemented in the C-library \code{fftw3}. If this
+#' library is not available, the function will throw  a warning. \code{qThresh}
+#' gives the quantile for hard thresholding the basis coefficients based on
+#' their absolute value. If \code{parallel = TRUE}, the coefficients for
+#' different images are calculated in parallel.} See \code{\link{univDecomp}}
+#' and \code{\link{univExpansion}} for details.}
+#'
+#' @param mFData A  \code{\link[funData]{multiFunData}} object containing the
+#'   \code{N} observations.
+#' @param M The number of multivariate functional principal components to
+#'   calculate.
+#' @param uniExpansions A list characterizing the (univariate) expansion that is
+#'   calculated for each element. See Details.
+#' @param weights An optional vector of weights, defaults to \code{1} for each
+#'   element. See Details.
+#' @param fit Logical. If \code{TRUE}, a truncated multivariate Karhunen-Loeve
+#'   representation for the data is calculated based on the estimated scores and
+#'   eigenfunctions.
+#' @param approx.eigen Logical. If \code{TRUE}, the eigenanalysis problem for
+#'   the estimated covariance matrix is solved approximately using the
+#'   \pkg{irlba} package, which is much faster. If the number \code{M} of
+#'   eigenvalues to calculate is high with respect to the number of observations
+#'   in \code{mFData} or the number of estimated univariate eigenfunctions, the
+#'   approximation may be inappropriate. In this case, approx.eigen is set to
+#'   \code{FALSE} and the function throws a warning. Defaults to \code{FALSE}.
+#' @param bootstrap Logical. If \code{TRUE}, pointwise bootstrap confidence
+#'   bands are calculated for the multivariate functional principal components.
+#'   Defaults to \code{FALSE}. See Details.
+#' @param nBootstrap The number of bootstrap iterations to use. Defaults to
+#'   \code{NULL}, which leads to an error, if \code{bootstrap = TRUE}.
+#' @param bootstrapAlpha A vector of numerics (or a single number) giving the
+#'   significance level for bootstrap intervals. Defaults to \code{0.05}.
+#' @param bootstrapStrat A stratification variable for bootstrap. Must be a
+#'   factor of length \code{nObs(mFData)} or \code{NULL} (default). If
+#'   \code{NULL}, no stratification is made in the bootstrap resampling, i.e.
+#'   the curves are sampled with replacement. If \code{bootstrapStrat} is not
+#'   \code{NULL}, the curves are resampled with replacement within the groups
+#'   defined by \code{bootstrapStrat}, hence keeping the group proportions
+#'   fixed.
+#' @param verbose Logical. If \code{TRUE}, the function reports
+#'   extra-information about the progress (incl. timestamps). Defaults to
+#'   \code{options()$verbose}.
+#'
+#' @return An object of class \code{MFPCAfit} containing the following
+#'   components: \item{values}{A vector of estimated eigenvalues \eqn{\hat \nu_1
+#'   , \ldots , \hat \nu_M}.} \item{functions}{A
+#'   \code{\link[funData]{multiFunData}} object containing the estimated
+#'   multivariate functional principal components \eqn{\hat \psi_1, \ldots, \hat
+#'   \psi_M}.} \item{scores}{ A matrix of dimension \code{N x M} containing the
+#'   estimated scores \eqn{\hat \rho_{im}}.} \item{vectors}{A matrix
+#'   representing the eigenvectors associated with the combined univariate score
+#'   vectors. This might be helpful for calculating predictions.}
+#'   \item{normFactors}{The normalizing factors used for calculating the
+#'   multivariate eigenfunctions and scores. This might be helpful when
+#'   calculation predictions.} \item{meanFunction}{A multivariate functional
+#'   data object, corresponding to the mean function. The MFPCA is applied to
+#'   the de-meaned functions in \code{mFData}.}\item{fit}{A
+#'   \code{\link[funData]{multiFunData}} object containing estimated
+#'   trajectories for each observation based on the truncated Karhunen-Loeve
+#'   representation and the estimated scores and eigenfunctions.} \item{CI}{A
+#'   list of the same length as \code{bootstrapAlpha}, containing the pointwise
+#'   lower and upper bootstrap confidence bands for each eigenfunction and each
+#'   significance level in form of \code{\link[funData]{multiFunData}} objects
+#'   (only if \code{bootstrap = TRUE}).} \item{CIvalues}{A list of the same
+#'   length as \code{bootstrapAlpha}, containing the lower and upper bootstrap
+#'   confidence bands for each eigenvalue and each significance level (only if
+#'   \code{bootstrap = TRUE}).}
+#'
+#' @export MFPCA
+#'
+#' @importFrom foreach %do%
+#' @importFrom utils packageVersion
+#'
+#' @references C. Happ, S. Greven (2018): Multivariate Functional Principal
+#'   Component Analysis for Data Observed on Different (Dimensional) Domains.
+#'   Journal of the American Statistical Association, 113(522): 649-659. DOI:
+#'   \doi{10.1080/01621459.2016.1273115}
+#'
+#' @references C. Happ-Kurz (2020): Object-Oriented Software for Functional
+#'   Data. Journal of Statistical Software, 93(5): 1-38. DOI:
+#'   \doi{10.18637/jss.v093.i05}
+#'
+#' @seealso See Happ-Kurz (2020. \doi{10.18637/jss.v093.i05}) for a general
+#'   introduction to the \pkg{funData} package and it's interplay with
+#'   \pkg{MFPCA}. This file also includes a case study on how to use
+#'   \code{MFPCA}. Useful functions: \code{\link[funData]{multiFunData}},
+#'   \code{\link{PACE}}, \code{\link{univDecomp}}, \code{\link{univExpansion}},
+#'   \code{\link[=summary.MFPCAfit]{summary}},
+#'   \code{\link[=plot.MFPCAfit]{plot}},
+#'   \code{\link[=scoreplot.MFPCAfit]{scoreplot}}
+#'
+#' @examples
+#' oldPar <- par(no.readonly = TRUE)
+#'
+#' set.seed(1)
+#'
+#' ### simulate data (one-dimensional domains)
+#' sim <-  simMultiFunData(type = "split", argvals = list(seq(0,1,0.01), seq(-0.5,0.5,0.02)),
+#'                         M = 5, eFunType = "Poly", eValType = "linear", N = 100)
+#'
+#' # MFPCA based on univariate FPCA
+#' uFPCA <- MFPCA(sim$simData, M = 5, uniExpansions = list(list(type = "uFPCA"),
+#'                                                                   list(type = "uFPCA")))
+
+#' summary(uFPCA)
+#' plot(uFPCA) # plot the eigenfunctions as perturbations of the mean
+#' scoreplot(uFPCA) # plot the scores
+#'
+#' # MFPCA based on univariate spline expansions
+#' splines <- MFPCA(sim$simData, M = 5, uniExpansions = list(list(type = "splines1D", k = 10),
+#'                                                           list(type = "splines1D", k = 10)),
+#'                  fit = TRUE) # calculate reconstruction, too
+#' summary(splines)
+#' plot(splines) # plot the eigenfunctions as perturbations of the mean
+#' scoreplot(splines) # plot the scores
+#'
+#' ### Compare estimates to true eigenfunctions
+#' # flip to make results more clear
+#' uFPCA$functions <- flipFuns(sim$trueFuns, uFPCA$functions)
+#' splines$functions <- flipFuns(sim$trueFuns, splines$functions)
+#'
+#' par(mfrow = c(1,2))
+#' plot(sim$trueFuns[[1]], main = "Eigenfunctions\n1st Element", lwd = 2)
+#' plot(uFPCA$functions[[1]], lty = 2, add = TRUE)
+#' plot(splines$functions[[1]], lty = 3, add = TRUE)
+#'
+#' plot(sim$trueFuns[[2]], main = "Eigenfunctions\n2nd Element", lwd = 2)
+#' plot(uFPCA$functions[[2]], lty = 2, add = TRUE)
+#' plot(splines$functions[[2]], lty = 3, add = TRUE)
+#' legend("bottomleft", c("True", "uFPCA", "splines"), lty = 1:3, lwd = c(2,1,1))
+#'
+#' # Test reconstruction for the first 10 observations
+#' plot(sim$simData[[1]], obs = 1:10, main = "Reconstruction\n1st Element", lwd = 2)
+#' plot(splines$fit[[1]], obs = 1:10, lty = 2, col = 1, add = TRUE)
+#'
+#' plot(sim$simData[[2]], obs = 1:10, main = "Reconstruction\n2nd Element", lwd = 2)
+#' plot(splines$fit[[2]], obs = 1:10, lty = 2, col = 1, add = TRUE)
+#' legend("bottomleft", c("True", "Reconstruction"), lty = c(1,2), lwd = c(2,1))
+#'
+#' # MFPCA with Bootstrap-CI for the first 2 eigenfunctions
+#' ### ATTENTION: Takes long
+#' \donttest{
+#' splinesBoot <- MFPCA(sim$simData, M = 2, uniExpansions = list(list(type = "splines1D", k = 10),
+#'                                                           list(type = "splines1D", k = 10)),
+#'                  bootstrap = TRUE, nBootstrap = 100, bootstrapAlpha = c(0.05, 0.1), verbose = TRUE)
+#' summary(splinesBoot)
+#'
+#' plot(splinesBoot$functions[[1]], ylim = c(-2,1.5))
+#' plot(splinesBoot$CI$alpha_0.05$lower[[1]], lty = 2, add = TRUE)
+#' plot(splinesBoot$CI$alpha_0.05$upper[[1]], lty = 2, add = TRUE)
+#' plot(splinesBoot$CI$alpha_0.1$lower[[1]], lty = 3, add = TRUE)
+#' plot(splinesBoot$CI$alpha_0.1$upper[[1]], lty = 3, add = TRUE)
+#' abline(h = 0, col = "gray")
+#'
+#' plot(splinesBoot$functions[[2]], ylim = c(-1,2.5))
+#' plot(splinesBoot$CI$alpha_0.05$lower[[2]], lty = 2, add = TRUE)
+#' plot(splinesBoot$CI$alpha_0.05$upper[[2]], lty = 2, add = TRUE)
+#' plot(splinesBoot$CI$alpha_0.1$lower[[2]], lty = 3, add = TRUE)
+#' plot(splinesBoot$CI$alpha_0.1$upper[[2]], lty = 3, add = TRUE)
+#' abline(h = 0, col = "gray")
+#' legend("topleft", c("Estimate", "95% CI", "90% CI"), lty = 1:3, lwd = c(2,1,1))
+#'
+#' # Plot 95% confidence bands for eigenvalues
+#' plot(1:2, splinesBoot$values, pch = 20, ylim = c(0, 1.5),
+#'      main = "Estimated eigenvalues with 95% CI",
+#'      xlab = "Eigenvalue no.", ylab = "")
+#' arrows(1:2, splinesBoot$CIvalues$alpha_0.05$lower,
+#'        1:2, splinesBoot$CIvalues$alpha_0.05$upper,
+#'        length = 0.05, angle = 90, code = 3)
+#' points(1:2, sim$trueVals[1:2], pch = 20, col = 4)
+#' legend("topright", c("Estimate", "True value"), pch = 20, col = c(1,4))
+#' }
+#'
+#' ### simulate data (two- and one-dimensional domains)
+#' ### ATTENTION: Takes long
+#' \donttest{
+#' set.seed(2)
+#' sim <-  simMultiFunData(type = "weighted",
+#'                  argvals = list(list(seq(0,1,0.01), seq(-1,1,0.02)), list(seq(-0.5,0.5,0.01))),
+#'                  M = list(c(4,5), 20), eFunType = list(c("Fourier", "Fourier"), "Poly"),
+#'                  eValType = "exponential", N = 150)
+#'
+#' # MFPCA based on univariate spline expansions (for images) and univariate FPCA (for functions)
+#' pca <- MFPCA(sim$simData, M = 10,
+#'              uniExpansions = list(list(type = "splines2D", k = c(10,12)),
+#'                              list(type = "uFPCA")))
+#' summary(pca)
+#' plot(pca) # plot the eigenfunctions as perturbations of the mean
+#' scoreplot(pca) # plot the scores
+#'
+#' ### Compare to true eigenfunctions
+#' # flip to make results more clear
+#' pca$functions <- flipFuns(sim$trueFuns[1:10], pca$functions)
+#'
+#' par(mfrow = c(5,2), mar = rep(2,4))
+#' for(m in 2:6) # for m = 1, image.plot (used in plot(funData)) produces an error...
+#' {
+#'   plot(sim$trueFuns[[1]], main = paste("True, m = ", m), obs = m)
+#'   plot(pca$functions[[1]], main = paste("Estimate, m = ", m), obs = m)
+#' }
+#'
+#' par(mfrow = c(1,1))
+#' plot(sim$trueFuns[[2]], main = "Eigenfunctions (2nd element)", lwd = 2, obs=  1:5)
+#' plot(pca$functions[[2]], lty = 2, add = TRUE, obs=  1:5)
+#' legend("bottomleft", c("True", "MFPCA"), lty = 1:2, lwd = c(2,1))
+#' }
+#' par(oldPar)
+```
+
+```{r}
+#'
+MFPCA <- function(mFData, mFData_predict, M, uniExpansions, weights = rep(1, length(mFData)), fit = FALSE, approx.eigen = FALSE,
+                  bootstrap = FALSE, nBootstrap = NULL, bootstrapAlpha = 0.05, bootstrapStrat = NULL,
+                  verbose = options()$verbose)
+{
+  if(! inherits(mFData, "multiFunData"))
+    stop("Parameter 'mFData' must be passed as a multiFunData object.")
+
+  # number of components
+  p <- length(mFData)
+  # number of observations
+  N <- nObs(mFData)
+
+  if(!all(is.numeric(M), length(M) == 1, M > 0))
+    stop("Parameter 'M' must be passed as a number > 0.")
+
+  if(!(is.list(uniExpansions) & length(uniExpansions) == p))
+    stop("Parameter 'uniExpansions' must be passed as a list with the same length as 'mFData'.")
+
+  if(!(is.numeric(weights) & length(weights) == p))
+    stop("Parameter 'weights' must be passed as a vector with the same length as 'mFData'.")
+
+  if(!is.logical(fit))
+    stop("Parameter 'fit' must be passed as a logical.")
+
+  if(!is.logical(approx.eigen))
+    stop("Parameter 'approx.eigen' must be passed as a logical.")
+
+  if(!is.logical(bootstrap))
+    stop("Parameter 'bootstrap' must be passed as a logical.")
+
+  if(bootstrap)
+  {
+    if(is.null(nBootstrap))
+      stop("Specify number of bootstrap iterations.")
+
+    if(any(!(0 < bootstrapAlpha & bootstrapAlpha < 1)))
+      stop("Significance level for bootstrap confidence bands must be in (0,1).")
+
+    if(!is.null(bootstrapStrat))
+    {
+      if(!is.factor(bootstrapStrat))
+        stop("bootstrapStrat must be either NULL or a factor.")
+
+      if(length(bootstrapStrat) != nObs(mFData))
+        stop("bootstrapStrat must have the same length as the number of observations in the mFData object.")
+    }
+  }
+
+  if(!is.logical(verbose))
+    stop("Parameter 'verbose' must be passed as a logical.")
+
+  # dimension for each component
+  dimSupp <- dimSupp(mFData)
+
+  # get type of univariate expansions
+  type <- vapply(uniExpansions, function(l){l$type}, FUN.VALUE = "")
+
+  # de-mean functions -> coefficients are also de-meaned!
+  # do not de-mean in uFPCA, as PACE gives a smooth estimate of the mean (see below)
+  m <- meanFunction(mFData, na.rm = TRUE) # ignore NAs in data
+  for(j in seq_len(p))
+  {
+    if(type[j] != "uFPCA")
+      mFData[[j]] <- mFData[[j]] - m[[j]]
+  }
+
+  if(verbose)
+    cat("Calculating univariate basis expansions (", format(Sys.time(), "%T"), ")\n", sep = "")
+
+  # calculate univariate basis expansion for all components
+  uniBasis <- mapply(
+    function(expansion, data, data_predict){
+      do.call(univDecomp, c(
+        list(funDataObject = data, funDataObject_predict = data_predict),
+        expansion)
+        )
+      },
+    expansion = uniExpansions,
+    data = mFData,
+    data_predict = mFData_predict,
+    SIMPLIFY = FALSE
+    )
+########### modified by Jongmin Mun #############################
+
+  # for uFPCA: replace estimated mean in m
+  for(j in seq_len(p))
+  {
+    if(type[j] == "uFPCA")
+      m[[j]] <- uniBasis[[j]]$meanFunction
+  }
+
+  # Multivariate FPCA
+  npc <- vapply(uniBasis, function(x){dim(x$scores)[2]}, FUN.VALUE = 0) # get number of univariate basis functions
+
+  if(M > sum(npc))
+  {
+    M <- sum(npc)
+    warning("Function MFPCA: total number of univariate basis functions is smaller than given M. M was set to ", sum(npc), ".")
+  }
+
+  # check if non-orthonormal basis functions used
+  if(all(foreach::foreach(j = seq_len(p), .combine = "c")%do%{uniBasis[[j]]$ortho}))
+    Bchol = NULL
+  else
+  {
+    # Cholesky decomposition of B = block diagonal of Cholesky decompositions
+    Bchol <- Matrix::bdiag(lapply(uniBasis, function(l){
+      if(l$ortho)
+        res <- Matrix::Diagonal(n = ncol(l$scores))
+      else
+        res <- Matrix::chol(l$B)
+
+      return(res)}))
+  }
+
+  if(verbose)
+    cat("Calculating MFPCA (", format(Sys.time(), "%T"), ")\n", sep = "")
+
+  mArgvals <- if (utils::packageVersion("funData") <= "1.2") {
+    getArgvals(mFData)
+  } else {
+    funData::argvals(mFData)
+  }
+
+  res <- calcMFPCA(N = N, p = p, Bchol = Bchol, M = M, type = type, weights = weights,
+                   npc = npc, argvals = mArgvals, uniBasis = uniBasis, fit = fit, approx.eigen = approx.eigen)
+
+  res$meanFunction <- m # return mean function, too
+
+  names(res$functions) <- names(mFData)
+
+  #############modified by jongmin mun
+
+  #####################################
+  if(fit)
+  {
+    res$fit <- m + res$fit # add mean function to fits
+    names(res$fit) <- names(mFData)
+  }
+
+  # give correct names
+  namesList <- lapply(mFData, names)
+  if(!all(vapply(namesList, FUN = is.null, FUN.VALUE = TRUE)))
+  {
+    if(length(unique(namesList)) != 1)
+      warning("Elements have different curve names. Use names of the first element for the results.")
+
+    row.names(res$scores) <- namesList[[1]]
+
+    if(fit)
+      for(i in seq_len(p))
+        names(res$fit[[i]]) <- namesList[[1]]
+  }
+
+  # bootstrap for eigenfunctions
+  if(bootstrap)
+  {
+    if(verbose)
+      cat("Bootstrapping results:\n")
+
+    booteFuns <- vector("list", p)
+
+    for(j in seq_len(p))
+      booteFuns[[j]] <- array(NA, dim  = c(nBootstrap, M, vapply(mFData[[j]]@argvals, FUN = length, FUN.VALUE = 0)))
+
+    booteVals <- matrix(NA, nrow = nBootstrap, ncol = M)
+
+    for(n in seq_len(nBootstrap))
+    {
+      if(verbose)
+      {
+        if(n %% 10 == 0)
+          cat("\t n = ", n, " (", format(Sys.time(), "%T"), ")\n", sep = "")
+      }
+
+      if(is.null(bootstrapStrat))
+        bootObs <- sample(N, replace = TRUE)
+      else
+        bootObs <- stratSample(bootstrapStrat)
+
+      bootBasis <- vector("list", p)
+
+      for(j in seq_len(p))
+      {
+        if(!is.null(uniBasis[[j]]$functions)) # re-estimate scores AND functions
+        {
+          bootBasis[[j]] <- do.call(univDecomp, c(list(funDataObject = (mFData[bootObs])[[j]]), uniExpansions[[j]]))
+
+          # recalculate Bchol if necessary
+          if(!bootBasis[[j]]$ortho)
+            Bchol[[j]] <- Matrix::chol(bootBasis[[j]]$B)
+        }
+        else # resample scores (functions are given and scores can simply be resampled)
+          bootBasis[[j]] <- list(scores = uniBasis[[j]]$scores[bootObs, ], B = uniBasis[[j]]$B, ortho = uniBasis[[j]]$ortho, functions = uniBasis[[j]]$functions,
+                                 settings = uniBasis[[j]]$settings)
+      }
+
+      npcBoot <- vapply(bootBasis, function(x){dim(x$scores)[2]}, FUN.VALUE = 0) # get number of univariate basis functions
+
+      if(M > sum(npcBoot))
+        stop("Function MFPCA (bootstrap): total number of univariate basis functions must be greater or equal M!")
+
+      # calculate MFPCA for bootstrap sample (Bchol has been updated for UMPCA)
+      bootMFPCA <- calcMFPCA(N = N, p = p, Bchol = Bchol, M = M, type = type, weights = weights,
+                             npc = npcBoot, argvals = mArgvals, uniBasis = bootBasis, fit = FALSE, approx.eigen = approx.eigen)
+
+      # save eigenvalues
+      booteVals[n,] <- bootMFPCA$values
+
+      # flip bootstrap estimates if necessary
+      tmpFuns <- flipFuns(res$functions, bootMFPCA$functions)
+
+      # save in booteFuns
+      for(j in seq_len(p))
+      {
+        if(dimSupp[j] == 1)
+          booteFuns[[j]][n,,] <- tmpFuns[[j]]@X
+        if(dimSupp[j] == 2)
+          booteFuns[[j]][n,,,] <- tmpFuns[[j]]@X
+        if(dimSupp[j] == 3)
+          booteFuns[[j]][n,,,,] <- tmpFuns[[j]]@X
+      }
+    }
+
+    CIvalues <- vector("list", length(bootstrapAlpha))
+    CI <- vector("list", length(bootstrapAlpha))
+
+    for(alpha in seq_len(length(bootstrapAlpha)))
+    {
+      if(verbose)
+        cat("Calculating bootstrap quantiles for alpha = ", bootstrapAlpha[alpha], " (", format(Sys.time(), "%T"), ")\n", sep = "")
+
+      CIvalues[[alpha]]$lower <- apply(booteVals, 2, quantile, bootstrapAlpha[alpha]/2)
+      CIvalues[[alpha]]$upper <-  apply(booteVals, 2, quantile, 1 - bootstrapAlpha[alpha]/2)
+      names(CIvalues)[alpha] <- paste("alpha", bootstrapAlpha[alpha], sep = "_")
+
+      bootCI_lower <- bootCI_upper <-  vector("list", p)
+      for(j in seq_len(p))
+      {
+        bootCI_lower[[j]] <- funData(mFData[[j]]@argvals, apply(booteFuns[[j]], 2:length(dim(booteFuns[[j]])),
+                                                                quantile, bootstrapAlpha[alpha]/2))
+        bootCI_upper[[j]] <- funData(mFData[[j]]@argvals, apply(booteFuns[[j]],  2:length(dim(booteFuns[[j]])),
+                                                                quantile, 1 - bootstrapAlpha[alpha]/2))
+      }
+
+      CI[[alpha]]$lower <- multiFunData(bootCI_lower)
+      CI[[alpha]]$upper <- multiFunData(bootCI_upper)
+
+      names(CI)[alpha] <- paste("alpha", bootstrapAlpha[alpha], sep = "_")
+    }
+
+    res$CIvalues <- CIvalues
+
+    res$CI <- CI
+  }
+  if(type[1] == "uFPCA"){
+    scores.pred<-calcMFPCA_predict(N = nObs(mFData_predict),
+                      p = p,
+                      M = M,
+                      weights = weights,
+                      npc = npc,
+                      uniBasis = uniBasis,
+                      normFactors = res$normFactors,
+                      vectors_train=res$vectors,
+                      values_train=res$values
+    )
+  }
+  res$scores.pred <- scores.pred
+
+  class(res) <- "MFPCAfit"
+    return(res)
+}
+```
+
+```{r}
+#' Internal function that implements the MFPCA algorithm for given univariate decompositions
+#'
+#' @param N Number of observations.
+#' @param p Number of elements in multivariate functional data.
+#' @param Bchol Cholesky decomposition of B = block diagonal of Cholesky decompositions.
+#' @param M The number of multivariate functional principal components to
+#'   calculate.
+#' @param type Vector of univariate decompositions to use.
+#' @param weights Vector of weights.
+#' @param npc Vector giving the number of univariate basis functions used.
+#' @param argvals List of argument values for each of the univariate basis functions.
+#' @param uniBasis List of univariate basis functions.
+#' @param fit Logical. If \code{TRUE}, a truncated multivariate Karhunen-Loeve
+#'   representation for the data is calculated based on the estimated scores and
+#'   eigenfunctions.
+#' @param approx.eigen Logical. If \code{TRUE}, the eigenanalysis problem for
+#'   the estimated covariance matrix is solved approximately using the
+#'   \pkg{irlba} package, which is much faster. If the number \code{M} of
+#'   eigenvalues to calculate is high with respect to the number of observations
+#'   in \code{mFData} or the number of estimated univariate eigenfunctions, the
+#'   approximation may be inappropriate. In this case, approx.eigen is set to
+#'   \code{FALSE} and the function throws a warning. Defaults to \code{FALSE}.
+#'
+#' @return A list containing the following
+#'   components: \item{values}{A vector of estimated eigenvalues \eqn{\hat \nu_1
+#'   , \ldots , \hat \nu_M}.} \item{functions}{A
+#'   \code{\link[funData]{multiFunData}} object containing the estimated
+#'   multivariate functional principal components \eqn{\hat \psi_1, \ldots, \hat
+#'   \psi_M}.} \item{scores}{ A matrix of dimension \code{N x M} containing the
+#'   estimated scores \eqn{\hat \rho_{im}}.} \item{vectors}{A matrix
+#'   representing the eigenvectors associated with the combined univariate score
+#'   vectors. This might be helpful for calculating predictions.}
+#'   \item{normFactors}{The normalizing factors used for calculating the
+#'   multivariate eigenfunctions and scores. This might be helpful when
+#'   calculation predictions.} \item{meanFunction}{A multivariate functional
+#'   data object, corresponding to the mean function. The MFPCA is applied to
+#'   the de-meaned functions in \code{mFData}.}\item{fit}{A
+#'   \code{\link[funData]{multiFunData}} object containing estimated
+#'   trajectories for each observation based on the truncated Karhunen-Loeve
+#'   representation and the estimated scores and eigenfunctions.}
+#'
+#' @importFrom stats cov
+#' @importFrom Matrix t
+#' @importFrom foreach foreach
+#' @importFrom irlba irlba
+#'
+#' @keywords internal
+calcMFPCA <- function(N, p, Bchol, M, type, weights, npc, argvals, uniBasis, fit = FALSE, approx.eigen = FALSE)
+{
+  # combine all scores
+  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores}
+
+  # block vector of weights
+  allWeights <- foreach::foreach(j = seq_len(p), .combine = "c")%do%{rep(sqrt(weights[j]), npc[j])}
+
+  Z <- allScores %*% Matrix::Diagonal(x = allWeights) / sqrt(N-1)
+
+  # check if approximation is appropriate (cf. irlba)
+  if(approx.eigen & (M > min(N, sum(npc))/2))
+  {
+    warning("Calculating a large percentage of principal components, approximation may not be appropriate.
+            'approx.eigen' set to FALSE.")
+    approx.eigen = FALSE
+  }
+
+  # check if non-orthonormal basis functions used and calculate PCA on scores
+  if(is.null(Bchol))
+  {
+    if(approx.eigen)
+    {
+      tmpSVD <- irlba::irlba(as.matrix(Z), nv = M)
+
+      vectors <- tmpSVD$v
+      values <- tmpSVD$d[seq_len(M)]^2
+    }
+    else
+    {
+      if(sum(npc) > 1000)
+        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")
+
+      e <- eigen(stats::cov(allScores) * outer(allWeights, allWeights, "*"))
+
+      values <- e$values[seq_len(M)]
+      vectors <- e$vectors[,seq_len(M)]
+    }
+  }
+  else
+  {
+    if(approx.eigen)
+    {
+      tmpSVD <- irlba::irlba(as.matrix(Matrix::tcrossprod(Z, Bchol)), nv = M)
+
+      vectors <- Matrix::crossprod(Bchol, tmpSVD$v)
+      values <- tmpSVD$d[seq_len(M)]^2
+    }
+    else
+    {
+      if(sum(npc) > 1000)
+        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")
+
+      e <- eigen(Matrix::crossprod(Bchol) %*% (stats::cov(allScores) * outer(allWeights, allWeights, "*")))
+
+      values <- Re(e$values[seq_len(M)])
+      vectors <- Re(e$vectors[,seq_len(M)])
+    }
+  }
+
+  # normalization factors
+  normFactors <- 1/sqrt(diag(as.matrix(Matrix::crossprod(Z %*% vectors))))
+
+  ### Calculate scores
+  scores <- Z %*% vectors * sqrt(N-1) # see defintion of Z above!
+  scores <- as.matrix(scores %*% diag(sqrt(values) * normFactors, nrow = M, ncol = M)) # normalization
+
+  ### Calculate eigenfunctions (incl. normalization)
+  npcCum <- cumsum(c(0, npc)) # indices for blocks (-1)
+
+  tmpWeights <- as.matrix(Matrix::crossprod(Z, Z %*%vectors))
+  eFunctions <- foreach::foreach(j = seq_len(p)) %do% {
+    univExpansion(type = type[j],
+                  scores = 1/sqrt(weights[j] * values) * normFactors * t(tmpWeights[npcCum[j]+seq_len(npc[j]), , drop = FALSE]),
+                  argvals = argvals[[j]],
+                  functions = uniBasis[[j]]$functions,
+                  params = uniBasis[[j]]$settings)
+  }
+
+  res <- list(values = values,
+              functions = multiFunData(eFunctions),
+              scores = scores,
+              vectors = vectors,
+              values = values,
+              normFactors = normFactors,
+              uniBasis = uniBasis,
+              uniExpansions = uniExpansions
+  )
+
+  # calculate truncated Karhunen-Loeve representation (no mean here)
+  if(fit)
+    res$fit <- multivExpansion(multiFuns = res$functions, scores = scores)
+
+  return(res)
+}
+```
+
+### calcMFPCA_predict
+
+```{r}
+#' calcMFPCA_predict
+#' @export
+#' 
+calcMFPCA_predict <- function(N, p, M, weights, npc, uniBasis,
+                              normFactors_train, vectors_train, values_train)
+{
+  # combine all scores
+  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores.pred}
+
+  # block vector of weights
+  allWeights <- foreach::foreach(j = seq_len(p), .combine = "c")%do%{rep(sqrt(weights[j]), npc[j])}
+
+  Z <- allScores %*% Matrix::Diagonal(x = allWeights) / sqrt(N-1)
+
+  ### Calculate scores
+  scores <- Z %*% vectors_train * sqrt(N-1) # see defintion of Z above!
+  scores <- as.matrix(scores %*% diag(sqrt(values_train) * normFactors_train, nrow = M, ncol = M)) # normalization
+
+  return(scores)
+}
+
+```
+
 ## Documenting the package and building

### 2025-10-07 create-FSHybridPLS.Rmd
remove bootstrap code

@@
 
+functions in MFPCA packages use an internal function calcBasisIntegrals. Somehow, this function did not work well on our simulations setting. Thus we modify the codes 
 ```{r}
@@
 
-```{r}
-#' Multivariate functional principal component analysis for functions on
-#' different (dimensional) domains
-#'
-#' This function calculates a multivariate functional principal component
-#' analysis (MFPCA) based on i.i.d. observations \eqn{x_1, \ldots, x_N} of a
-#' multivariate functional data-generating process \eqn{X = (X^{(1)}, \ldots
-#' X^{(p)})}{X = X^(1), \ldots, X^(p)} with elements \eqn{X^{(j)} \in
-#' L^2(\mathcal{T}_j)}{X^(j) in L^2(calT_j)} defined on a domain
-#' \eqn{\mathcal{T}_j \subset IR^{d_j}}{calT_j of IR^{d_j}}. In particular, the
-#' elements can be defined on different (dimensional) domains. The results
-#' contain the mean function, the estimated multivariate functional principal
-#' components \eqn{\hat \psi_1, \ldots, \hat \psi_M} (having the same structure
-#' as \eqn{x_i}), the associated eigenvalues \eqn{\hat \nu_1 \geq \ldots \geq
-#' \hat \nu_M > 0} and the individual scores \eqn{\hat \rho_{im} =
-#' \widehat{<x_i, \psi_m>}}{\hat \rho_{im} = \hat{<x_i, \psi_m>}}. Moreover,
-#' estimated trajectories for each observation based on the truncated
-#' Karhunen-Loeve representation \deqn{\hat x_i = \sum_{m = 1}^M \hat \rho_{im}
-#' \hat \psi_m}{\hat x_i = \sum_{m = 1}^M \hat \rho_{im} \hat \psi_m} are given
-#' if desired (\code{fit = TRUE}). The implementation of the observations
-#' \eqn{x_i = (x_i^{(1)}, \ldots , x_i^{(p)}),~ i = 1 , \ldots, N}{x_i =
-#' (x_i^(1), \ldots , x_i^(p)), i = 1 , \ldots, N}, the mean function and
-#' multivariate functional principal components \eqn{\hat \psi_1, \ldots, \hat
-#' \psi_M} uses the \code{\link[funData]{multiFunData}} class, which is defined
-#' in the package \pkg{funData}.
-#'
-#' \subsection{Weighted MFPCA}{If the elements vary considerably in domain,
-#' range or variation, a weight vector \eqn{w_1 , \ldots, w_p} can be supplied
-#' and the MFPCA is based on the weighted scalar product \deqn{<<f,g>>_w =
-#' \sum_{j = 1}^p w_j \int_{\mathcal{T}_j} f^{(j)}(t) g^{(j)}(t) \mathrm{d}
-#' t}{<<f,g>>_w = \sum_{j = 1}^p w_j \int_\calT_j f^(j)(t) g^(j)(t) d t} and the
-#' corresponding weighted covariance operator \eqn{\Gamma_w}.}
-#'
-#' \subsection{Bootstrap}{If \code{bootstrap = TRUE}, pointwise bootstrap
-#' confidence bands are generated for the multivariate eigenvalues \eqn{\hat
-#' \nu_1, \ldots, \hat \nu_M } as well as for multivariate functional principal
-#' components \eqn{\hat \psi_1, \ldots, \hat \psi_M}{\hat \psi_1, \ldots, \hat
-#' \psi_M}. The parameter \code{nBootstrap} gives the number of bootstrap
-#' iterations. In each iteration, the observations are resampled on the level of
-#' (multivariate) functions and the whole MFPCA is recalculated. In particular,
-#' if the univariate basis depends on the data (FPCA approaches), basis
-#' functions and scores are both re-estimated. If the basis functions are fixed
-#' (e.g. splines), the scores from the original estimate are used to speed up
-#' the calculations. The confidence bands for the eigenfunctions are calculated
-#' separately for each element as pointwise percentile bootstrap confidence
-#' intervals. Analogously, the confidence bands for the eigenvalues are also
-#' percentile bootstrap confidence bands. The significance level(s) can be
-#' defined by the \code{bootstrapAlpha} parameter, which defaults to 5\%. As a
-#' result, the \code{MFPCA} function returns a list \code{CI} of the same length
-#' as \code{bootstrapAlpha}, containing the lower and upper bounds of the
-#' confidence bands for the principal components as \code{multiFunData} objects
-#' of the same structure as \code{mFData}. The confidence bands for the
-#' eigenvalues are returned in a list \code{CIvalues}, containing the upper and
-#' lower bounds for each significance level.}
-#'
-#'
-#' \subsection{Univariate Expansions}{The multivariate functional principal
-#' component analysis relies on a univariate basis expansion for each element
-#' \eqn{X^{(j)}}{X^(j)}. The univariate basis representation is calculated using
-#' the \code{\link{univDecomp}} function, that passes the univariate functional
-#' observations and optional parameters to the specific function. The univariate
-#' decompositions are specified via the \code{uniExpansions} argument in the
-#' \code{MFPCA} function. It is a list of the same length as the \code{mFData}
-#' object, i.e. having one entry for each element of the multivariate functional
-#' data. For each element, \code{uniExpansion} must specify at least the type of
-#' basis functions to use. Additionally, one may add further parameters. The
-#' following basis representations are supported: \itemize{\item Given basis
+###   Multivariate functional principal component analysis for functions on different (dimensional) domains
+
+- This function calculates a multivariate functional principal component analysis (MFPCA) based on i.i.d.
+observations $x_1, \ldots, x_N$ of a multivariate functional data-generating process $X = (X^{(1)}, \ldots  X^{(p)})}{X = X^(1), \ldots, X^(p)$ with elements $X^{(j)} \in L^2(\mathcal{T}_j)}{X^(j) in L^2(calT_j)$ defined on a domain $\mathcal{T}_j \subset IR^{d_j}}{calT_j of IR^{d_j}$.
+- In particular, the elements can be defined on different (dimensional) domains.
+- The results contain the mean function, the estimated multivariate functional principal components \eqn{\hat \psi_1, \ldots, \hat \psi_M} (having the same structure as $x_i$), the associated eigenvalues $\hat \nu_1 \geq \ldots \geq \hat \nu_M > 0$ and the individual scores \eqn{\hat \rho_{im} = \widehat{<x_i, \psi_m>}}{\hat \rho_{im} = \hat{<x_i, \psi_m>}}.
+
+#'
+#'
+- Univariate Expansions
+  - The multivariate functional principal component analysis relies on a univariate basis expansion for each element $X^{(j)}$.
+  - The univariate basis representation is calculated using the univDecomp function, that passes the univariate functional observations and optional parameters to the specific function.
+  - The univariate decompositions are specified via the uniExpansions argument in the MFPCA function.
+  - It is a list of the same length as the mFData object, i.e. having one entry for each element of the multivariate functional data.
+  - For each element, uniExpansion must specify at least the type of basis functions to use.
+  - Additionally, one may add further parameters.
+  - The following basis representations are supported: \itemize{\item Given basis
 #' functions. Then \code{uniExpansions[[j]] = list(type = "given", functions,
 #' scores, ortho)}, where \code{functions} is a \code{funData} object on the
-#' same domain as \code{mFData}, containing the given basis functions. The
+#' same domain as \code{mFData}, containing the given basis functions. 
+The
 #' parameters \code{scores} and \code{ortho} are optional. \code{scores} is an
@@
 #' the scores need to be demeaned to give meaningful results. If scores are not
-#' supplied, they are calculated using the given basis functions. The parameter
+#' supplied, they are calculated using the given basis functions.
+The parameter
 #' \code{ortho} specifies whether the given basis functions are orthonormal
@@
 #'
-#' @examples
-#' oldPar <- par(no.readonly = TRUE)
-#'
-#' set.seed(1)
-#'
-#' ### simulate data (one-dimensional domains)
-#' sim <-  simMultiFunData(type = "split", argvals = list(seq(0,1,0.01), seq(-0.5,0.5,0.02)),
-#'                         M = 5, eFunType = "Poly", eValType = "linear", N = 100)
-#'
-#' # MFPCA based on univariate FPCA
-#' uFPCA <- MFPCA(sim$simData, M = 5, uniExpansions = list(list(type = "uFPCA"),
-#'                                                                   list(type = "uFPCA")))
-
-#' summary(uFPCA)
-#' plot(uFPCA) # plot the eigenfunctions as perturbations of the mean
-#' scoreplot(uFPCA) # plot the scores
-#'
-#' # MFPCA based on univariate spline expansions
-#' splines <- MFPCA(sim$simData, M = 5, uniExpansions = list(list(type = "splines1D", k = 10),
-#'                                                           list(type = "splines1D", k = 10)),
-#'                  fit = TRUE) # calculate reconstruction, too
-#' summary(splines)
-#' plot(splines) # plot the eigenfunctions as perturbations of the mean
-#' scoreplot(splines) # plot the scores
-#'
-#' ### Compare estimates to true eigenfunctions
-#' # flip to make results more clear
-#' uFPCA$functions <- flipFuns(sim$trueFuns, uFPCA$functions)
-#' splines$functions <- flipFuns(sim$trueFuns, splines$functions)
-#'
-#' par(mfrow = c(1,2))
-#' plot(sim$trueFuns[[1]], main = "Eigenfunctions\n1st Element", lwd = 2)
-#' plot(uFPCA$functions[[1]], lty = 2, add = TRUE)
-#' plot(splines$functions[[1]], lty = 3, add = TRUE)
-#'
-#' plot(sim$trueFuns[[2]], main = "Eigenfunctions\n2nd Element", lwd = 2)
-#' plot(uFPCA$functions[[2]], lty = 2, add = TRUE)
-#' plot(splines$functions[[2]], lty = 3, add = TRUE)
-#' legend("bottomleft", c("True", "uFPCA", "splines"), lty = 1:3, lwd = c(2,1,1))
-#'
-#' # Test reconstruction for the first 10 observations
-#' plot(sim$simData[[1]], obs = 1:10, main = "Reconstruction\n1st Element", lwd = 2)
-#' plot(splines$fit[[1]], obs = 1:10, lty = 2, col = 1, add = TRUE)
-#'
-#' plot(sim$simData[[2]], obs = 1:10, main = "Reconstruction\n2nd Element", lwd = 2)
-#' plot(splines$fit[[2]], obs = 1:10, lty = 2, col = 1, add = TRUE)
-#' legend("bottomleft", c("True", "Reconstruction"), lty = c(1,2), lwd = c(2,1))
-#'
-#' # MFPCA with Bootstrap-CI for the first 2 eigenfunctions
-#' ### ATTENTION: Takes long
-#' \donttest{
-#' splinesBoot <- MFPCA(sim$simData, M = 2, uniExpansions = list(list(type = "splines1D", k = 10),
-#'                                                           list(type = "splines1D", k = 10)),
-#'                  bootstrap = TRUE, nBootstrap = 100, bootstrapAlpha = c(0.05, 0.1), verbose = TRUE)
-#' summary(splinesBoot)
-#'
-#' plot(splinesBoot$functions[[1]], ylim = c(-2,1.5))
-#' plot(splinesBoot$CI$alpha_0.05$lower[[1]], lty = 2, add = TRUE)
-#' plot(splinesBoot$CI$alpha_0.05$upper[[1]], lty = 2, add = TRUE)
-#' plot(splinesBoot$CI$alpha_0.1$lower[[1]], lty = 3, add = TRUE)
-#' plot(splinesBoot$CI$alpha_0.1$upper[[1]], lty = 3, add = TRUE)
-#' abline(h = 0, col = "gray")
-#'
-#' plot(splinesBoot$functions[[2]], ylim = c(-1,2.5))
-#' plot(splinesBoot$CI$alpha_0.05$lower[[2]], lty = 2, add = TRUE)
-#' plot(splinesBoot$CI$alpha_0.05$upper[[2]], lty = 2, add = TRUE)
-#' plot(splinesBoot$CI$alpha_0.1$lower[[2]], lty = 3, add = TRUE)
-#' plot(splinesBoot$CI$alpha_0.1$upper[[2]], lty = 3, add = TRUE)
-#' abline(h = 0, col = "gray")
-#' legend("topleft", c("Estimate", "95% CI", "90% CI"), lty = 1:3, lwd = c(2,1,1))
-#'
-#' # Plot 95% confidence bands for eigenvalues
-#' plot(1:2, splinesBoot$values, pch = 20, ylim = c(0, 1.5),
-#'      main = "Estimated eigenvalues with 95% CI",
-#'      xlab = "Eigenvalue no.", ylab = "")
-#' arrows(1:2, splinesBoot$CIvalues$alpha_0.05$lower,
-#'        1:2, splinesBoot$CIvalues$alpha_0.05$upper,
-#'        length = 0.05, angle = 90, code = 3)
-#' points(1:2, sim$trueVals[1:2], pch = 20, col = 4)
-#' legend("topright", c("Estimate", "True value"), pch = 20, col = c(1,4))
-#' }
-#'
-#' ### simulate data (two- and one-dimensional domains)
-#' ### ATTENTION: Takes long
-#' \donttest{
-#' set.seed(2)
-#' sim <-  simMultiFunData(type = "weighted",
-#'                  argvals = list(list(seq(0,1,0.01), seq(-1,1,0.02)), list(seq(-0.5,0.5,0.01))),
-#'                  M = list(c(4,5), 20), eFunType = list(c("Fourier", "Fourier"), "Poly"),
-#'                  eValType = "exponential", N = 150)
-#'
-#' # MFPCA based on univariate spline expansions (for images) and univariate FPCA (for functions)
-#' pca <- MFPCA(sim$simData, M = 10,
-#'              uniExpansions = list(list(type = "splines2D", k = c(10,12)),
-#'                              list(type = "uFPCA")))
-#' summary(pca)
-#' plot(pca) # plot the eigenfunctions as perturbations of the mean
-#' scoreplot(pca) # plot the scores
-#'
-#' ### Compare to true eigenfunctions
-#' # flip to make results more clear
-#' pca$functions <- flipFuns(sim$trueFuns[1:10], pca$functions)
-#'
-#' par(mfrow = c(5,2), mar = rep(2,4))
-#' for(m in 2:6) # for m = 1, image.plot (used in plot(funData)) produces an error...
-#' {
-#'   plot(sim$trueFuns[[1]], main = paste("True, m = ", m), obs = m)
-#'   plot(pca$functions[[1]], main = paste("Estimate, m = ", m), obs = m)
-#' }
-#'
-#' par(mfrow = c(1,1))
-#' plot(sim$trueFuns[[2]], main = "Eigenfunctions (2nd element)", lwd = 2, obs=  1:5)
-#' plot(pca$functions[[2]], lty = 2, add = TRUE, obs=  1:5)
-#' legend("bottomleft", c("True", "MFPCA"), lty = 1:2, lwd = c(2,1))
-#' }
-#' par(oldPar)
-```
-
-```{r}
-#'
+
 MFPCA <- function(mFData, mFData_predict, M, uniExpansions, weights = rep(1, length(mFData)), fit = FALSE, approx.eigen = FALSE,
@@
 
+########### modified by Jongmin Mun #############################
   # calculate univariate basis expansion for all components
@@
 
-  # bootstrap for eigenfunctions
-  if(bootstrap)
-  {
-    if(verbose)
-      cat("Bootstrapping results:\n")
-
-    booteFuns <- vector("list", p)
-
-    for(j in seq_len(p))
-      booteFuns[[j]] <- array(NA, dim  = c(nBootstrap, M, vapply(mFData[[j]]@argvals, FUN = length, FUN.VALUE = 0)))
-
-    booteVals <- matrix(NA, nrow = nBootstrap, ncol = M)
-
-    for(n in seq_len(nBootstrap))
-    {
-      if(verbose)
-      {
-        if(n %% 10 == 0)
-          cat("\t n = ", n, " (", format(Sys.time(), "%T"), ")\n", sep = "")
-      }
-
-      if(is.null(bootstrapStrat))
-        bootObs <- sample(N, replace = TRUE)
-      else
-        bootObs <- stratSample(bootstrapStrat)
-
-      bootBasis <- vector("list", p)
-
-      for(j in seq_len(p))
-      {
-        if(!is.null(uniBasis[[j]]$functions)) # re-estimate scores AND functions
-        {
-          bootBasis[[j]] <- do.call(univDecomp, c(list(funDataObject = (mFData[bootObs])[[j]]), uniExpansions[[j]]))
-
-          # recalculate Bchol if necessary
-          if(!bootBasis[[j]]$ortho)
-            Bchol[[j]] <- Matrix::chol(bootBasis[[j]]$B)
-        }
-        else # resample scores (functions are given and scores can simply be resampled)
-          bootBasis[[j]] <- list(scores = uniBasis[[j]]$scores[bootObs, ], B = uniBasis[[j]]$B, ortho = uniBasis[[j]]$ortho, functions = uniBasis[[j]]$functions,
-                                 settings = uniBasis[[j]]$settings)
-      }
-
-      npcBoot <- vapply(bootBasis, function(x){dim(x$scores)[2]}, FUN.VALUE = 0) # get number of univariate basis functions
-
-      if(M > sum(npcBoot))
-        stop("Function MFPCA (bootstrap): total number of univariate basis functions must be greater or equal M!")
-
-      # calculate MFPCA for bootstrap sample (Bchol has been updated for UMPCA)
-      bootMFPCA <- calcMFPCA(N = N, p = p, Bchol = Bchol, M = M, type = type, weights = weights,
-                             npc = npcBoot, argvals = mArgvals, uniBasis = bootBasis, fit = FALSE, approx.eigen = approx.eigen)
-
-      # save eigenvalues
-      booteVals[n,] <- bootMFPCA$values
-
-      # flip bootstrap estimates if necessary
-      tmpFuns <- flipFuns(res$functions, bootMFPCA$functions)
-
-      # save in booteFuns
-      for(j in seq_len(p))
-      {
-        if(dimSupp[j] == 1)
-          booteFuns[[j]][n,,] <- tmpFuns[[j]]@X
-        if(dimSupp[j] == 2)
-          booteFuns[[j]][n,,,] <- tmpFuns[[j]]@X
-        if(dimSupp[j] == 3)
-          booteFuns[[j]][n,,,,] <- tmpFuns[[j]]@X
-      }
-    }
-
-    CIvalues <- vector("list", length(bootstrapAlpha))
-    CI <- vector("list", length(bootstrapAlpha))
-
-    for(alpha in seq_len(length(bootstrapAlpha)))
-    {
-      if(verbose)
-        cat("Calculating bootstrap quantiles for alpha = ", bootstrapAlpha[alpha], " (", format(Sys.time(), "%T"), ")\n", sep = "")
-
-      CIvalues[[alpha]]$lower <- apply(booteVals, 2, quantile, bootstrapAlpha[alpha]/2)
-      CIvalues[[alpha]]$upper <-  apply(booteVals, 2, quantile, 1 - bootstrapAlpha[alpha]/2)
-      names(CIvalues)[alpha] <- paste("alpha", bootstrapAlpha[alpha], sep = "_")
-
-      bootCI_lower <- bootCI_upper <-  vector("list", p)
-      for(j in seq_len(p))
-      {
-        bootCI_lower[[j]] <- funData(mFData[[j]]@argvals, apply(booteFuns[[j]], 2:length(dim(booteFuns[[j]])),
-                                                                quantile, bootstrapAlpha[alpha]/2))
-        bootCI_upper[[j]] <- funData(mFData[[j]]@argvals, apply(booteFuns[[j]],  2:length(dim(booteFuns[[j]])),
-                                                                quantile, 1 - bootstrapAlpha[alpha]/2))
-      }
-
-      CI[[alpha]]$lower <- multiFunData(bootCI_lower)
-      CI[[alpha]]$upper <- multiFunData(bootCI_upper)
-
-      names(CI)[alpha] <- paste("alpha", bootstrapAlpha[alpha], sep = "_")
-    }
-
-    res$CIvalues <- CIvalues
-
-    res$CI <- CI
-  }
   if(type[1] == "uFPCA"){
@@
 }
-```
-
-```{r}
+
+```{r}
+#' @examples
+#' oldPar <- par(no.readonly = TRUE)
+#'
+#' set.seed(1)
+#'
+#' ### simulate data (one-dimensional domains)
+#' sim <-  simMultiFunData(type = "split", argvals = list(seq(0,1,0.01), seq(-0.5,0.5,0.02)),
+#'                         M = 5, eFunType = "Poly", eValType = "linear", N = 100)
+#'
+#' # MFPCA based on univariate FPCA
+#' uFPCA <- MFPCA(sim$simData, M = 5, uniExpansions = list(list(type = "uFPCA"),
+#'                                                                   list(type = "uFPCA")))
+
+#' summary(uFPCA)
+#' plot(uFPCA) # plot the eigenfunctions as perturbations of the mean
+#' scoreplot(uFPCA) # plot the scores
+#'
+#' # MFPCA based on univariate spline expansions
+#' splines <- MFPCA(sim$simData, M = 5, uniExpansions = list(list(type = "splines1D", k = 10),
+#'                                                           list(type = "splines1D", k = 10)),
+#'                  fit = TRUE) # calculate reconstruction, too
+#' summary(splines)
+#' plot(splines) # plot the eigenfunctions as perturbations of the mean
+#' scoreplot(splines) # plot the scores
+#'
+#' ### Compare estimates to true eigenfunctions
+#' # flip to make results more clear
+#' uFPCA$functions <- flipFuns(sim$trueFuns, uFPCA$functions)
+#' splines$functions <- flipFuns(sim$trueFuns, splines$functions)
+#'
+#' par(mfrow = c(1,2))
+#' plot(sim$trueFuns[[1]], main = "Eigenfunctions\n1st Element", lwd = 2)
+#' plot(uFPCA$functions[[1]], lty = 2, add = TRUE)
+#' plot(splines$functions[[1]], lty = 3, add = TRUE)
+#'
+#' plot(sim$trueFuns[[2]], main = "Eigenfunctions\n2nd Element", lwd = 2)
+#' plot(uFPCA$functions[[2]], lty = 2, add = TRUE)
+#' plot(splines$functions[[2]], lty = 3, add = TRUE)
+#' legend("bottomleft", c("True", "uFPCA", "splines"), lty = 1:3, lwd = c(2,1,1))
+#'
+#' # Test reconstruction for the first 10 observations
+#' plot(sim$simData[[1]], obs = 1:10, main = "Reconstruction\n1st Element", lwd = 2)
+#' plot(splines$fit[[1]], obs = 1:10, lty = 2, col = 1, add = TRUE)
+#'
+#' plot(sim$simData[[2]], obs = 1:10, main = "Reconstruction\n2nd Element", lwd = 2)
+#' plot(splines$fit[[2]], obs = 1:10, lty = 2, col = 1, add = TRUE)
+#' legend("bottomleft", c("True", "Reconstruction"), lty = c(1,2), lwd = c(2,1))
+#'
+#' # MFPCA with Bootstrap-CI for the first 2 eigenfunctions
+#' ### ATTENTION: Takes long
+#' \donttest{
+#' splinesBoot <- MFPCA(sim$simData, M = 2, uniExpansions = list(list(type = "splines1D", k = 10),
+#'                                                           list(type = "splines1D", k = 10)),
+#'                  bootstrap = TRUE, nBootstrap = 100, bootstrapAlpha = c(0.05, 0.1), verbose = TRUE)
+#' summary(splinesBoot)
+#'
+#' plot(splinesBoot$functions[[1]], ylim = c(-2,1.5))
+#' plot(splinesBoot$CI$alpha_0.05$lower[[1]], lty = 2, add = TRUE)
+#' plot(splinesBoot$CI$alpha_0.05$upper[[1]], lty = 2, add = TRUE)
+#' plot(splinesBoot$CI$alpha_0.1$lower[[1]], lty = 3, add = TRUE)
+#' plot(splinesBoot$CI$alpha_0.1$upper[[1]], lty = 3, add = TRUE)
+#' abline(h = 0, col = "gray")
+#'
+#' plot(splinesBoot$functions[[2]], ylim = c(-1,2.5))
+#' plot(splinesBoot$CI$alpha_0.05$lower[[2]], lty = 2, add = TRUE)
+#' plot(splinesBoot$CI$alpha_0.05$upper[[2]], lty = 2, add = TRUE)
+#' plot(splinesBoot$CI$alpha_0.1$lower[[2]], lty = 3, add = TRUE)
+#' plot(splinesBoot$CI$alpha_0.1$upper[[2]], lty = 3, add = TRUE)
+#' abline(h = 0, col = "gray")
+#' legend("topleft", c("Estimate", "95% CI", "90% CI"), lty = 1:3, lwd = c(2,1,1))
+#'
+#' # Plot 95% confidence bands for eigenvalues
+#' plot(1:2, splinesBoot$values, pch = 20, ylim = c(0, 1.5),
+#'      main = "Estimated eigenvalues with 95% CI",
+#'      xlab = "Eigenvalue no.", ylab = "")
+#' arrows(1:2, splinesBoot$CIvalues$alpha_0.05$lower,
+#'        1:2, splinesBoot$CIvalues$alpha_0.05$upper,
+#'        length = 0.05, angle = 90, code = 3)
+#' points(1:2, sim$trueVals[1:2], pch = 20, col = 4)
+#' legend("topright", c("Estimate", "True value"), pch = 20, col = c(1,4))
+#' }
+#'
+#' ### simulate data (two- and one-dimensional domains)
+#' ### ATTENTION: Takes long
+#' \donttest{
+#' set.seed(2)
+#' sim <-  simMultiFunData(type = "weighted",
+#'                  argvals = list(list(seq(0,1,0.01), seq(-1,1,0.02)), list(seq(-0.5,0.5,0.01))),
+#'                  M = list(c(4,5), 20), eFunType = list(c("Fourier", "Fourier"), "Poly"),
+#'                  eValType = "exponential", N = 150)
+#'
+#' # MFPCA based on univariate spline expansions (for images) and univariate FPCA (for functions)
+#' pca <- MFPCA(sim$simData, M = 10,
+#'              uniExpansions = list(list(type = "splines2D", k = c(10,12)),
+#'                              list(type = "uFPCA")))
+#' summary(pca)
+#' plot(pca) # plot the eigenfunctions as perturbations of the mean
+#' scoreplot(pca) # plot the scores
+#'
+#' ### Compare to true eigenfunctions
+#' # flip to make results more clear
+#' pca$functions <- flipFuns(sim$trueFuns[1:10], pca$functions)
+#'
+#' par(mfrow = c(5,2), mar = rep(2,4))
+#' for(m in 2:6) # for m = 1, image.plot (used in plot(funData)) produces an error...
+#' {
+#'   plot(sim$trueFuns[[1]], main = paste("True, m = ", m), obs = m)
+#'   plot(pca$functions[[1]], main = paste("Estimate, m = ", m), obs = m)
+#' }
+#'
+#' par(mfrow = c(1,1))
+#' plot(sim$trueFuns[[2]], main = "Eigenfunctions (2nd element)", lwd = 2, obs=  1:5)
+#' plot(pca$functions[[2]], lty = 2, add = TRUE, obs=  1:5)
+#' legend("bottomleft", c("True", "MFPCA"), lty = 1:2, lwd = c(2,1))
+#' }
+#' par(oldPar)
+```
+
 #' Internal function that implements the MFPCA algorithm for given univariate decompositions
@@
 
+```{r}
+#' Internal function that implements the MFPCA algorithm for given univariate decompositions
+#'
+#' @param N Number of observations.
+#' @param p Number of elements in multivariate functional data.
+#' @param Bchol Cholesky decomposition of B = block diagonal of Cholesky decompositions.
+#' @param M The number of multivariate functional principal components to
+#'   calculate.
+#' @param type Vector of univariate decompositions to use.
+#' @param weights Vector of weights.
+#' @param npc Vector giving the number of univariate basis functions used.
+#' @param argvals List of argument values for each of the univariate basis functions.
+#' @param uniBasis List of univariate basis functions.
+#' @param fit Logical. If \code{TRUE}, a truncated multivariate Karhunen-Loeve
+#'   representation for the data is calculated based on the estimated scores and
+#'   eigenfunctions.
+#' @param approx.eigen Logical. If \code{TRUE}, the eigenanalysis problem for
+#'   the estimated covariance matrix is solved approximately using the
+#'   \pkg{irlba} package, which is much faster. If the number \code{M} of
+#'   eigenvalues to calculate is high with respect to the number of observations
+#'   in \code{mFData} or the number of estimated univariate eigenfunctions, the
+#'   approximation may be inappropriate. In this case, approx.eigen is set to
+#'   \code{FALSE} and the function throws a warning. Defaults to \code{FALSE}.
+#'
+#' @return A list containing the following
+#'   components: \item{values}{A vector of estimated eigenvalues \eqn{\hat \nu_1
+#'   , \ldots , \hat \nu_M}.} \item{functions}{A
+#'   \code{\link[funData]{multiFunData}} object containing the estimated
+#'   multivariate functional principal components \eqn{\hat \psi_1, \ldots, \hat
+#'   \psi_M}.} \item{scores}{ A matrix of dimension \code{N x M} containing the
+#'   estimated scores \eqn{\hat \rho_{im}}.} \item{vectors}{A matrix
+#'   representing the eigenvectors associated with the combined univariate score
+#'   vectors. This might be helpful for calculating predictions.}
+#'   \item{normFactors}{The normalizing factors used for calculating the
+#'   multivariate eigenfunctions and scores. This might be helpful when
+#'   calculation predictions.} \item{meanFunction}{A multivariate functional
+#'   data object, corresponding to the mean function. The MFPCA is applied to
+#'   the de-meaned functions in \code{mFData}.}\item{fit}{A
+#'   \code{\link[funData]{multiFunData}} object containing estimated
+#'   trajectories for each observation based on the truncated Karhunen-Loeve
+#'   representation and the estimated scores and eigenfunctions.}
+#'
+#' @importFrom stats cov
+#' @importFrom Matrix t
+#' @importFrom foreach foreach
+#' @importFrom irlba irlba
+#'
+#' @keywords internal
+calcMFPCA <- function(N, p, Bchol, M, type, weights, npc, argvals, uniBasis, fit = FALSE, approx.eigen = FALSE)
+{
+  # combine all scores
+  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores}
+
+  # block vector of weights
+  allWeights <- foreach::foreach(j = seq_len(p), .combine = "c")%do%{rep(sqrt(weights[j]), npc[j])}
+
+  Z <- allScores %*% Matrix::Diagonal(x = allWeights) / sqrt(N-1)
+
+  # check if approximation is appropriate (cf. irlba)
+  if(approx.eigen & (M > min(N, sum(npc))/2))
+  {
+    warning("Calculating a large percentage of principal components, approximation may not be appropriate.
+            'approx.eigen' set to FALSE.")
+    approx.eigen = FALSE
+  }
+
+  # check if non-orthonormal basis functions used and calculate PCA on scores
+  if(is.null(Bchol))
+  {
+    if(approx.eigen)
+    {
+      tmpSVD <- irlba::irlba(as.matrix(Z), nv = M)
+
+      vectors <- tmpSVD$v
+      values <- tmpSVD$d[seq_len(M)]^2
+    }
+    else
+    {
+      if(sum(npc) > 1000)
+        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")
+
+      e <- eigen(stats::cov(allScores) * outer(allWeights, allWeights, "*"))
+
+      values <- e$values[seq_len(M)]
+      vectors <- e$vectors[,seq_len(M)]
+    }
+  }
+  else
+  {
+    if(approx.eigen)
+    {
+      tmpSVD <- irlba::irlba(as.matrix(Matrix::tcrossprod(Z, Bchol)), nv = M)
+
+      vectors <- Matrix::crossprod(Bchol, tmpSVD$v)
+      values <- tmpSVD$d[seq_len(M)]^2
+    }
+    else
+    {
+      if(sum(npc) > 1000)
+        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")
+
+      e <- eigen(Matrix::crossprod(Bchol) %*% (stats::cov(allScores) * outer(allWeights, allWeights, "*")))
+
+      values <- Re(e$values[seq_len(M)])
+      vectors <- Re(e$vectors[,seq_len(M)])
+    }
+  }
+
+  # normalization factors
+  normFactors <- 1/sqrt(diag(as.matrix(Matrix::crossprod(Z %*% vectors))))
+
+  ### Calculate scores
+  scores <- Z %*% vectors * sqrt(N-1) # see defintion of Z above!
+  scores <- as.matrix(scores %*% diag(sqrt(values) * normFactors, nrow = M, ncol = M)) # normalization
+
+  ### Calculate eigenfunctions (incl. normalization)
+  npcCum <- cumsum(c(0, npc)) # indices for blocks (-1)
+
+  tmpWeights <- as.matrix(Matrix::crossprod(Z, Z %*%vectors))
+  eFunctions <- foreach::foreach(j = seq_len(p)) %do% {
+    univExpansion(type = type[j],
+                  scores = 1/sqrt(weights[j] * values) * normFactors * t(tmpWeights[npcCum[j]+seq_len(npc[j]), , drop = FALSE]),
+                  argvals = argvals[[j]],
+                  functions = uniBasis[[j]]$functions,
+                  params = uniBasis[[j]]$settings)
+  }
+
+  res <- list(values = values,
+              functions = multiFunData(eFunctions),
+              scores = scores,
+              vectors = vectors,
+              values = values,
+              normFactors = normFactors,
+              uniBasis = uniBasis,
+              uniExpansions = uniExpansions
+  )
+
+  # calculate truncated Karhunen-Loeve representation (no mean here)
+  if(fit)
+    res$fit <- multivExpansion(multiFuns = res$functions, scores = scores)
+
+  return(res)
+}
+```
+
 ### calcMFPCA_predict

### 2025-10-07 create-FSHybridPLS.Rmd
pasted normalize.all

--- 2025-08-23 create-FSHybridPLS.Rmd
@@
     Description = "This package says hello.  But its actual purpose is to show how an R package can be completely coded in a single R markdown file.",
-    Imports = "fda (>= 6.1.3), Matrix",
+    Imports = "fda (>= 6.1.3), Matrix, funData, foreach, irlba, refund",
     `Authors@R` = person(
@@
 ```
+
+# Simulation tools
+
+## sample splitting
+
+```{r}
+create_idx_train_test <-function(n_sample, train_ratio){
+  n_train <- floor(n_sample*train_ratio)
+  idx_train <- sort(sample(n_sample,n_train, replace=F))
+  idx_test <- sort((1 : n_sample)[-idx_train])
+  return(list(
+    idx_train = idx_train, idx_test = idx_test
+  ))
+}
+```
+
+```{r}
+create_idx_kfold <- function(n_sample, n_fold){
+  idx_list <- caret::createFolds( (1 : n_sample), k = n_fold, list = TRUE, returnTrain = FALSE)
+  idx_list_list <- list()
+  for (i in 1:length(idx_list)){
+    valid_hyper_index <- idx_list[[i]]
+    train_hyper_index <- (1 : n_sample)[-valid_hyper_index]
+    idx_list_list[[i]] <- list("idx_train" = train_hyper_index, "idx_valid" = valid_hyper_index)
+  }
+  return(idx_list_list)
+}
+```
+
+```{r}
+n_sample.fd <- function(fd_obj){
+  length(fd_obj$fdnames$reps)
+}
+```
+
+```{r}
+normailize.all <- function(split.all_obj){
+  curve_normalize_result_1 <- curve_normalize_train_test_fd(
+    split.all_obj$data_fun_1_train,
+    split.all_obj$data_fun_1_test)
+  data_fun_1_train <- curve_normalize_result_1$train
+  data_fun_1_test <- curve_normalize_result_1$test
+
+  curve_normalize_result_2 <- curve_normalize_train_test_fd(
+    split.all_obj$data_fun_2_train,
+    split.all_obj$data_fun_2_test)
+  data_fun_2_train <- curve_normalize_result_2$train
+  data_fun_2_test <- curve_normalize_result_2$test
+
+  scalar_normalize_result <- scalar_normalize_train_test(
+    split.all_obj$data_scalar_train,
+    split.all_obj$data_scalar_test)
+  data_scalar_train <- scalar_normalize_result$train
+  data_scalar_test <- scalar_normalize_result$test
+
+  between_normalize_result <- btwn_normalize_train_test(
+    list(data_fun_1_train, data_fun_2_train),
+    data_scalar_train,
+    data_scalar_test
+  )
+  data_scalar_train <- between_normalize_result$train
+  data_scalar_test <- between_normalize_result$test
+
+  response_mean_train <-  mean(split.all_obj$response_train)
+  response_train <- split.all_obj$response_train - response_mean_train
+  response_test <- split.all_obj$response_test - response_mean_train
+
+  return(
+    list(
+      data_fun_1_train = data_fun_1_train,
+      data_fun_2_train = data_fun_2_train,
+      data_scalar_train= data_scalar_train,
+      response_train   = response_train,
+      data_fun_1_test  = data_fun_1_test,
+      data_fun_2_test  = data_fun_2_test,
+      data_scalar_test = data_scalar_test,
+      response_test    = response_test
+    )
+  )
+}
+```
+
+# Baseline method: FPCA regression
+
+functions in MFPCA packages use an internal function calcBasisIntegrals. Somehow, this function did not work well on our simulations setting. Thus we modify the codes 
+```{r}
+
+# define global variable j, used by the foreach package and confusing R CMD CHECK
+globalVariables('j')
+
+#' Utility function that calculates matrix of basis-scalar products (one dimension)
+#'
+#' If the element \eqn{X^{(j)}}{X^{(j)}} is expanded in basis functions \eqn{b_i^{(j)}(t),~ i = 1, \ldots, K_j}{b_i(t)},
+#' this function calculates the \eqn{K_j \times K_j}{K_j  \times K_j} matrix \eqn{B^{(jj)}}{B^{(jj)}} with entries
+#' \deqn{B^{(jj)}_{mn} = \int_{\mathcal{T_j}} b_m^{(j)}(t) b_n^{(j)}(t) \mathrm{d} t}.
+#'
+#' @section Warning: This function is implemented only for functions on one- or two-dimensional domains.
+#'
+#' @param basisFunctions Array of \code{npc} basis functions of dimensions \code{npc x M1} or \code{npc x M1 x M2}.
+#' @param dimSupp dimension of the support of the basis functions (1 or 2)
+#' @param argvals List of corresponding x-values.
+#'
+#' @return A matrix containing the scalar product of all combinations of basis functions (matrix \eqn{B^{(j)}})
+#'
+#' @seealso \code{\link{MFPCA}}, \code{\link[funData]{dimSupp}}
+#'
+#' @keywords internal
+calcBasisIntegrals <- function(basisFunctions, dimSupp, argvals)
+{
+  npc <- dim(basisFunctions)[1]
+
+  #  integral basis matrix
+  B <- array(0, dim = c(npc, npc))
+
+  if(dimSupp == 1) # one-dimensional domain
+  {
+    w <- funData::.intWeights(argvals[[1]])
+
+    for(m in seq_len(npc))
+    {
+      for(n in seq_len(m))
+        B[m, n] <- B[n, m] <- (basisFunctions[m, ]* basisFunctions[n, ])%*%w
+    }
+  }
+  else # two-dimesional domain (otherwise function stops before!)
+  {
+    w1 <- t(funData::.intWeights(argvals[[1]]))
+    w2 <- funData::.intWeights(argvals[[2]])
+
+    for(m in seq_len(npc))
+    {
+      for(n in seq_len(m))
+        B[m, n] <- B[n, m] <-  w1 %*%(basisFunctions[m, , ]* basisFunctions[n, ,])%*%w2
+    }
+  }
+
+  return(B)
+}
+```
+
+###   Multivariate functional principal component analysis for functions on different (dimensional) domains
+
+- This function calculates a multivariate functional principal component analysis (MFPCA) based on i.i.d.
+observations $x_1, \ldots, x_N$ of a multivariate functional data-generating process $X = (X^{(1)}, \ldots  X^{(p)})}{X = X^(1), \ldots, X^(p)$ with elements $X^{(j)} \in L^2(\mathcal{T}_j)}{X^(j) in L^2(calT_j)$ defined on a domain $\mathcal{T}_j \subset IR^{d_j}}{calT_j of IR^{d_j}$.
+- In particular, the elements can be defined on different (dimensional) domains.
+- The results contain the mean function, the estimated multivariate functional principal components \eqn{\hat \psi_1, \ldots, \hat \psi_M} (having the same structure as $x_i$), the associated eigenvalues $\hat \nu_1 \geq \ldots \geq \hat \nu_M > 0$ and the individual scores \eqn{\hat \rho_{im} = \widehat{<x_i, \psi_m>}}{\hat \rho_{im} = \hat{<x_i, \psi_m>}}.
+
+- Univariate Expansions
+    - The multivariate functional principal component analysis relies on a univariate basis expansion for each element $X^{(j)}$.
+    - The univariate basis representation is calculated using the univDecomp function, that passes the univariate functional observations and optional parameters to the specific function.
+    - The univariate decompositions are specified via the uniExpansions argument in the MFPCA function.
+    - It is a list of the same length as the mFData object, i.e. having one entry for each element of the multivariate functional data.
+    - For each element, uniExpansion must specify at least the type of basis functions to use.
+    - Additionally, one may add further parameters.
+    - The following basis representations are supported: \itemize{
+        -  Given basis functions.
+Then \code{uniExpansions[[j]] = list(type = "given", functions)}, where \code{functions} is a \code{funData} object on the same domain as \code{mFData}, containing the given basis functions.
+        - Univariate functional principal component analysis.
+Then \code{uniExpansions[[j]] = list(type = "uFPCA", nbasis, pve, npc, makePD)}, where \code{nbasis,pve,npc,makePD} are parameters passed to the \code{\link{PACE}} function for calculating the univariate functional principal component analysis.
+        - Basis functions expansions from the
+  package \pkg{fda}. Then \code{uniExpansions[[j]] = list(type = "fda", ...)},
+#' where \code{...} are passed to \code{\link[funData]{funData2fd}}, which
+#' heavily builds on \code{\link[fda]{eval.fd}}. If \pkg{fda} is not available,
+#' a warning is thrown.
+\item Spline basis functions (not penalized). Then
+#' \code{uniExpansions[[j]] = list(type = "splines1D", bs, m, k)}, where
+#' \code{bs,m,k} are passed to the functions \code{\link{univDecomp}} and
+#' \code{\link{univExpansion}}. For two-dimensional tensor product splines, use
+#' \code{type = "splines2D"}. 
+\item Spline basis functions (with smoothness
+#' penalty). Then \code{uniExpansions[[j]] = list(type = "splines1Dpen", bs, m,
+#' k)}, where \code{bs,m,k} are passed to the functions \code{\link{univDecomp}}
+#' and \code{\link{univExpansion}}. Analogously to the unpenalized case, use
+#' \code{type = "splines2Dpen"} for 2D penalized tensor product splines. 
+\item
+#' Cosine basis functions. Use \code{uniExpansions[[j]] = list(type = "DCT2D",
+#' qThresh, parallel)} for functions one two-dimensional domains (images) and
+#' \code{type = "DCT3D"} for 3D images. The calculation is based on the discrete
+#' cosine transform (DCT) implemented in the C-library \code{fftw3}. If this
+#' library is not available, the function will throw  a warning. \code{qThresh}
+#' gives the quantile for hard thresholding the basis coefficients based on
+#' their absolute value. If \code{parallel = TRUE}, the coefficients for
+#' different images are calculated in parallel.} See \code{\link{univDecomp}}
+#' and \code{\link{univExpansion}} for details.}
+
+```{r}
+#'
+#' @export MFPCA
+MFPCA <- function(mFData, mFData_predict, M, uniExpansions, weights = rep(1, length(mFData)), fit = FALSE, approx.eigen = FALSE,
+                  bootstrap = FALSE, nBootstrap = NULL, bootstrapAlpha = 0.05, bootstrapStrat = NULL,
+                  verbose = options()$verbose)
+{
+  if(! inherits(mFData, "multiFunData"))
+    stop("Parameter 'mFData' must be passed as a multiFunData object.")
+
+  # number of components
+  p <- length(mFData)
+  # number of observations
+  N <- nObs(mFData)
+
+  if(!all(is.numeric(M), length(M) == 1, M > 0))
+    stop("Parameter 'M' must be passed as a number > 0.")
+
+  if(!(is.list(uniExpansions) & length(uniExpansions) == p))
+    stop("Parameter 'uniExpansions' must be passed as a list with the same length as 'mFData'.")
+
+  if(!(is.numeric(weights) & length(weights) == p))
+    stop("Parameter 'weights' must be passed as a vector with the same length as 'mFData'.")
+
+  if(!is.logical(fit))
+    stop("Parameter 'fit' must be passed as a logical.")
+
+  if(!is.logical(approx.eigen))
+    stop("Parameter 'approx.eigen' must be passed as a logical.")
+
+  if(!is.logical(bootstrap))
+    stop("Parameter 'bootstrap' must be passed as a logical.")
+
+  if(bootstrap)
+  {
+    if(is.null(nBootstrap))
+      stop("Specify number of bootstrap iterations.")
+
+    if(any(!(0 < bootstrapAlpha & bootstrapAlpha < 1)))
+      stop("Significance level for bootstrap confidence bands must be in (0,1).")
+
+    if(!is.null(bootstrapStrat))
+    {
+      if(!is.factor(bootstrapStrat))
+        stop("bootstrapStrat must be either NULL or a factor.")
+
+      if(length(bootstrapStrat) != nObs(mFData))
+        stop("bootstrapStrat must have the same length as the number of observations in the mFData object.")
+    }
+  }
+
+  if(!is.logical(verbose))
+    stop("Parameter 'verbose' must be passed as a logical.")
+
+  # dimension for each component
+  dimSupp <- dimSupp(mFData)
+
+  # get type of univariate expansions
+  type <- vapply(uniExpansions, function(l){l$type}, FUN.VALUE = "")
+
+  # de-mean functions -> coefficients are also de-meaned!
+  # do not de-mean in uFPCA, as PACE gives a smooth estimate of the mean (see below)
+  m <- meanFunction(mFData, na.rm = TRUE) # ignore NAs in data
+  for(j in seq_len(p))
+  {
+    if(type[j] != "uFPCA")
+      mFData[[j]] <- mFData[[j]] - m[[j]]
+  }
+
+  if(verbose)
+    cat("Calculating univariate basis expansions (", format(Sys.time(), "%T"), ")\n", sep = "")
+
+########### modified by Jongmin Mun #############################
+  # calculate univariate basis expansion for all components
+  uniBasis <- mapply(
+    function(expansion, data, data_predict){
+      do.call(univDecomp, c(
+        list(funDataObject = data, funDataObject_predict = data_predict),
+        expansion)
+        )
+      },
+    expansion = uniExpansions,
+    data = mFData,
+    data_predict = mFData_predict,
+    SIMPLIFY = FALSE
+    )
+########### modified by Jongmin Mun #############################
+
+  # for uFPCA: replace estimated mean in m
+  for(j in seq_len(p))
+  {
+    if(type[j] == "uFPCA")
+      m[[j]] <- uniBasis[[j]]$meanFunction
+  }
+
+  # Multivariate FPCA
+  npc <- vapply(uniBasis, function(x){dim(x$scores)[2]}, FUN.VALUE = 0) # get number of univariate basis functions
+
+  if(M > sum(npc))
+  {
+    M <- sum(npc)
+    warning("Function MFPCA: total number of univariate basis functions is smaller than given M. M was set to ", sum(npc), ".")
+  }
+
+  # check if non-orthonormal basis functions used
+  if(all(foreach::foreach(j = seq_len(p), .combine = "c")%do%{uniBasis[[j]]$ortho}))
+    Bchol = NULL
+  else
+  {
+    # Cholesky decomposition of B = block diagonal of Cholesky decompositions
+    Bchol <- Matrix::bdiag(lapply(uniBasis, function(l){
+      if(l$ortho)
+        res <- Matrix::Diagonal(n = ncol(l$scores))
+      else
+        res <- Matrix::chol(l$B)
+
+      return(res)}))
+  }
+
+  if(verbose)
+    cat("Calculating MFPCA (", format(Sys.time(), "%T"), ")\n", sep = "")
+
+  mArgvals <- if (utils::packageVersion("funData") <= "1.2") {
+    getArgvals(mFData)
+  } else {
+    funData::argvals(mFData)
+  }
+
+  res <- calcMFPCA(N = N, p = p, Bchol = Bchol, M = M, type = type, weights = weights,
+                   npc = npc, argvals = mArgvals, uniBasis = uniBasis, fit = fit, approx.eigen = approx.eigen)
+
+  res$meanFunction <- m # return mean function, too
+
+  names(res$functions) <- names(mFData)
+
+  #############modified by jongmin mun
+
+  #####################################
+  if(fit)
+  {
+    res$fit <- m + res$fit # add mean function to fits
+    names(res$fit) <- names(mFData)
+  }
+
+  # give correct names
+  namesList <- lapply(mFData, names)
+  if(!all(vapply(namesList, FUN = is.null, FUN.VALUE = TRUE)))
+  {
+    if(length(unique(namesList)) != 1)
+      warning("Elements have different curve names. Use names of the first element for the results.")
+
+    row.names(res$scores) <- namesList[[1]]
+
+    if(fit)
+      for(i in seq_len(p))
+        names(res$fit[[i]]) <- namesList[[1]]
+  }
+
+  if(type[1] == "uFPCA"){
+    scores.pred<-calcMFPCA_predict(N = nObs(mFData_predict),
+                      p = p,
+                      M = M,
+                      weights = weights,
+                      npc = npc,
+                      uniBasis = uniBasis,
+                      normFactors = res$normFactors,
+                      vectors_train=res$vectors,
+                      values_train=res$values
+    )
+  }
+  res$scores.pred <- scores.pred
+
+  class(res) <- "MFPCAfit"
+    return(res)
+}
+
+```
+
+### calcMFPCA
+```{r}
+#' Internal function that implements the MFPCA algorithm for given univariate decompositions
+#' @export
+calcMFPCA <- function(N, p, Bchol, M, type, weights, npc, argvals, uniBasis, fit = FALSE, approx.eigen = FALSE)
+{
+  # combine all scores
+  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores}
+
+  # block vector of weights
+  allWeights <- foreach::foreach(j = seq_len(p), .combine = "c")%do%{rep(sqrt(weights[j]), npc[j])}
+
+  Z <- allScores %*% Matrix::Diagonal(x = allWeights) / sqrt(N-1)
+
+  # check if approximation is appropriate (cf. irlba)
+  if(approx.eigen & (M > min(N, sum(npc))/2))
+  {
+    warning("Calculating a large percentage of principal components, approximation may not be appropriate.
+            'approx.eigen' set to FALSE.")
+    approx.eigen = FALSE
+  }
+
+  # check if non-orthonormal basis functions used and calculate PCA on scores
+  if(is.null(Bchol))
+  {
+    if(approx.eigen)
+    {
+      tmpSVD <- irlba::irlba(as.matrix(Z), nv = M)
+
+      vectors <- tmpSVD$v
+      values <- tmpSVD$d[seq_len(M)]^2
+    }
+    else
+    {
+      if(sum(npc) > 1000)
+        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")
+
+      e <- eigen(stats::cov(allScores) * outer(allWeights, allWeights, "*"))
+
+      values <- e$values[seq_len(M)]
+      vectors <- e$vectors[,seq_len(M)]
+    }
+  }
+  else
+  {
+    if(approx.eigen)
+    {
+      tmpSVD <- irlba::irlba(as.matrix(Matrix::tcrossprod(Z, Bchol)), nv = M)
+
+      vectors <- Matrix::crossprod(Bchol, tmpSVD$v)
+      values <- tmpSVD$d[seq_len(M)]^2
+    }
+    else
+    {
+      if(sum(npc) > 1000)
+        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")
+
+      e <- eigen(Matrix::crossprod(Bchol) %*% (stats::cov(allScores) * outer(allWeights, allWeights, "*")))
+
+      values <- Re(e$values[seq_len(M)])
+      vectors <- Re(e$vectors[,seq_len(M)])
+    }
+  }
+
+  # normalization factors
+  normFactors <- 1/sqrt(diag(as.matrix(Matrix::crossprod(Z %*% vectors))))
+
+  ### Calculate scores
+  scores <- Z %*% vectors * sqrt(N-1) # see defintion of Z above!
+  scores <- as.matrix(scores %*% diag(sqrt(values) * normFactors, nrow = M, ncol = M)) # normalization
+
+  ### Calculate eigenfunctions (incl. normalization)
+  npcCum <- cumsum(c(0, npc)) # indices for blocks (-1)
+
+  tmpWeights <- as.matrix(Matrix::crossprod(Z, Z %*%vectors))
+  eFunctions <- foreach::foreach(j = seq_len(p)) %do% {
+    univExpansion(type = type[j],
+                  scores = 1/sqrt(weights[j] * values) * normFactors * t(tmpWeights[npcCum[j]+seq_len(npc[j]), , drop = FALSE]),
+                  argvals = argvals[[j]],
+                  functions = uniBasis[[j]]$functions,
+                  params = uniBasis[[j]]$settings)
+  }
+
+  res <- list(values = values,
+              functions = multiFunData(eFunctions),
+              scores = scores,
+              vectors = vectors,
+              values = values,
+              normFactors = normFactors,
+              uniBasis = uniBasis,
+              uniExpansions = uniExpansions
+  )
+
+  # calculate truncated Karhunen-Loeve representation (no mean here)
+  if(fit)
+    res$fit <- multivExpansion(multiFuns = res$functions, scores = scores)
+
+  return(res)
+}
+```
+
+### calcMFPCA
+
+```{r}
+#' Internal function that implements the MFPCA algorithm for given univariate decompositions
+#' @export
+#' 
+calcMFPCA <- function(N, p, Bchol, M, type, weights, npc, argvals, uniBasis, fit = FALSE, approx.eigen = FALSE)
+{
+  # combine all scores
+  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores}
+
+  # block vector of weights
+  allWeights <- foreach::foreach(j = seq_len(p), .combine = "c")%do%{rep(sqrt(weights[j]), npc[j])}
+
+  Z <- allScores %*% Matrix::Diagonal(x = allWeights) / sqrt(N-1)
+
+  # check if approximation is appropriate (cf. irlba)
+  if(approx.eigen & (M > min(N, sum(npc))/2))
+  {
+    warning("Calculating a large percentage of principal components, approximation may not be appropriate.
+            'approx.eigen' set to FALSE.")
+    approx.eigen = FALSE
+  }
+
+  # check if non-orthonormal basis functions used and calculate PCA on scores
+  if(is.null(Bchol))
+  {
+    if(approx.eigen)
+    {
+      tmpSVD <- irlba::irlba(as.matrix(Z), nv = M)
+
+      vectors <- tmpSVD$v
+      values <- tmpSVD$d[seq_len(M)]^2
+    }
+    else
+    {
+      if(sum(npc) > 1000)
+        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")
+
+      e <- eigen(stats::cov(allScores) * outer(allWeights, allWeights, "*"))
+
+      values <- e$values[seq_len(M)]
+      vectors <- e$vectors[,seq_len(M)]
+    }
+  }
+  else
+  {
+    if(approx.eigen)
+    {
+      tmpSVD <- irlba::irlba(as.matrix(Matrix::tcrossprod(Z, Bchol)), nv = M)
+
+      vectors <- Matrix::crossprod(Bchol, tmpSVD$v)
+      values <- tmpSVD$d[seq_len(M)]^2
+    }
+    else
+    {
+      if(sum(npc) > 1000)
+        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")
+
+      e <- eigen(Matrix::crossprod(Bchol) %*% (stats::cov(allScores) * outer(allWeights, allWeights, "*")))
+
+      values <- Re(e$values[seq_len(M)])
+      vectors <- Re(e$vectors[,seq_len(M)])
+    }
+  }
+
+  # normalization factors
+  normFactors <- 1/sqrt(diag(as.matrix(Matrix::crossprod(Z %*% vectors))))
+
+  ### Calculate scores
+  scores <- Z %*% vectors * sqrt(N-1) # see defintion of Z above!
+  scores <- as.matrix(scores %*% diag(sqrt(values) * normFactors, nrow = M, ncol = M)) # normalization
+
+  ### Calculate eigenfunctions (incl. normalization)
+  npcCum <- cumsum(c(0, npc)) # indices for blocks (-1)
+
+  tmpWeights <- as.matrix(Matrix::crossprod(Z, Z %*%vectors))
+  eFunctions <- foreach::foreach(j = seq_len(p)) %do% {
+    univExpansion(type = type[j],
+                  scores = 1/sqrt(weights[j] * values) * normFactors * t(tmpWeights[npcCum[j]+seq_len(npc[j]), , drop = FALSE]),
+                  argvals = argvals[[j]],
+                  functions = uniBasis[[j]]$functions,
+                  params = uniBasis[[j]]$settings)
+  }
+
+  res <- list(values = values,
+              functions = multiFunData(eFunctions),
+              scores = scores,
+              vectors = vectors,
+              values = values,
+              normFactors = normFactors,
+              uniBasis = uniBasis,
+              uniExpansions = uniExpansions
+  )
+
+  # calculate truncated Karhunen-Loeve representation (no mean here)
+  if(fit)
+    res$fit <- multivExpansion(multiFuns = res$functions, scores = scores)
+
+  return(res)
+}
+```
+
+### calcMFPCA_predict
+
+```{r}
+#' calcMFPCA_predict
+#' @export
+#' 
+calcMFPCA_predict <- function(N, p, M, weights, npc, uniBasis,
+                              normFactors_train, vectors_train, values_train)
+{
+  # combine all scores
+  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores.pred}
+
+  # block vector of weights
+  allWeights <- foreach::foreach(j = seq_len(p), .combine = "c")%do%{rep(sqrt(weights[j]), npc[j])}
+
+  Z <- allScores %*% Matrix::Diagonal(x = allWeights) / sqrt(N-1)
+
+  ### Calculate scores
+  scores <- Z %*% vectors_train * sqrt(N-1) # see defintion of Z above!
+  scores <- as.matrix(scores %*% diag(sqrt(values_train) * normFactors_train, nrow = M, ncol = M)) # normalization
+
+  return(scores)
+}
+
+```
+
+```{r}
+load("C:/Users/jongmin/Documents/GitHub/fsPLS/simul/graphical_high_correlation/graphical_data.RData")
+```
+
+```{r}
+library(refund)
+eval_point<-seq(1, 100, length.out = 100)
+n_iter_max = 40
+n_basis_predictor = 10
+n_scalar <- 9
+library(foreach)
+library(funData)
+uniExpansions <- list(
+  list(type = "uFPCA", nbasis = n_basis_predictor, npc = n_iter_max),
+  list(type = "uFPCA", nbasis = n_basis_predictor, npc = n_iter_max)
+)
+
+n_fold = 5
+n_scalar <- 9
+rmse_simul_fpca <- matrix(NA, nrow = n_rep, ncol = 3)
+colnames(rmse_simul_fpca) <- c("FPC+PC", "FPC_only", "PC_only")
+```
+
+```{r}
+
+  train_test_idx <- create_idx_train_test(n_sample, train.ratio)
+  train_test_split <- split.all(data_fun_1[[rep_number]], data_fun_2[[rep_number]], data_scalar[[rep_number]], response[[rep_number]], train_test_idx)
+  train_test_split_normalized <- normailize.all(train_test_split)
+
+  kfold_idx <- create_idx_kfold(length(train_test_idx$idx_train), n_fold)
+  cv_mat <- matrix(0, nrow = n_iter_max, ncol = n_scalar)
+  for (fold_num in 1:n_fold){
+    cat(paste0(fold_num, "th fold\n"))
+    #train-valid split (5 fold)
+    train_valid_idx <- kfold_idx[[fold_num]]
+    cv_train_valid_split <- split.all(
+      train_test_split$data_fun_1_train, train_test_split$data_fun_2_train, train_test_split$data_scalar_train, train_test_split$response_train,
+      train_valid_idx)
+
+    #normalizing
+    cv_train_valid_split_normalized <- normailize.all(cv_train_valid_split)
+
+    #format
+
+    predictor_cv_train <- multiFunData(
+      fd2funData(cv_train_valid_split_normalized$data_fun_1_train, eval_point),
+      fd2funData(cv_train_valid_split_normalized$data_fun_2_train, eval_point)
+    )
+    predictor_cv_valid <- multiFunData(
+      fd2funData(cv_train_valid_split_normalized$data_fun_1_test, eval_point),
+      fd2funData(cv_train_valid_split_normalized$data_fun_2_test, eval_point)
+    )
+
+    # train FPCA
+
+    MFPCA_fit_cv <- MFPCA(mFData = predictor_cv_train, mFData_predict = predictor_cv_valid, M = n_iter_max, uniExpansions = uniExpansions)
+
+    #train scalar PCA
+    PCA_fit_train <- prcomp(cv_train_valid_split_normalized$data_scalar_train, center=F, scale = F)
+    #validate
+    for (n_fpc in 1:n_iter_max){
+      for (n_spc in 1:n_scalar){
+        cat(paste(n_fpc, n_spc, "\n"))
+        FPC_score_cv <- (MFPCA_fit_cv$scores)[ ,(1:n_fpc)]
+        PC_score_cv <- (PCA_fit_train$x)[ , (1:n_spc)]
+        pc_score_cv_combined <- data.frame(cv_train_valid_split_normalized$response_train, FPC_score_cv, PC_score_cv)
+        colnames(pc_score_cv_combined) <- c(
+          c("response"),
+          paste0( rep("FPC", n_fpc), as.character(1:n_fpc)),
+          paste0( rep("PC", n_spc), as.character(1:n_spc))
+        )
+
+        # fit linear regression
+        rank_now <- rankMatrix(pc_score_cv_combined[,-1])[1]
+        print(rank_now)
+        cat(paste("rank deficient:", (n_fpc + n_spc)-rank_now, "\n"))
+        linear_fit_cv <- lm(response~., data = pc_score_cv_combined)
+
+        #validation set pc scores
+        PFC_score_valid <- (MFPCA_fit_cv$scores.pred)[ ,(1:n_fpc)]
+        PC_score_valid <- (predict(PCA_fit_train, cv_train_valid_split_normalized$data_scalar_test))[ , (1:n_spc)]
+        pc_score_valid_combined <- data.frame(PFC_score_valid, PC_score_valid)
+        colnames(pc_score_valid_combined) <- c(
+          paste0( rep("FPC", n_fpc), as.character(1:n_fpc)),
+          paste0( rep("PC", n_spc), as.character(1:n_spc))
+          )
+
+        y_pred <- predict(linear_fit_cv, pc_score_valid_combined)
+        cv_mat[n_fpc, n_spc] <- cv_mat[n_fpc, n_spc] +
+          sqrt( mean( sum( (y_pred - cv_train_valid_split_normalized$response_test)^2 ) ))
+        }
+    }
+  }
+    n_iter_best <- arrayInd(which.min(cv_mat), dim(cv_mat))
+    n_fpc_best  <- n_iter_best[1]
+    n_spc_best  <- n_iter_best[2]
+    print(n_fpc_best)
+    print(n_spc_best)
+
+    predictor_final_train <- multiFunData(
+      fd2funData(train_test_split_normalized$data_fun_1_train, eval_point),
+      fd2funData(train_test_split_normalized$data_fun_2_train, eval_point)
+    )
+    predictor_final_test <- multiFunData(
+      fd2funData(train_test_split_normalized$data_fun_1_test, eval_point),
+      fd2funData(train_test_split_normalized$data_fun_2_test, eval_point)
+    )
+
+    # train FPCA and scalar PCA
+    MFPCA_fit_final <- MFPCA(mFData = predictor_final_train, mFData_predict = predictor_final_test, M = n_fpc_best, uniExpansions = uniExpansions)
+    PCA_fit_final <- prcomp(train_test_split_normalized$data_scalar_train, center=F, scale = F)
+    PFC_score_final_train <- MFPCA_fit_final$scores
+    PC_score_final_train <- (predict(PCA_fit_final, train_test_split_normalized$data_scalar_train))[,c(1:n_spc_best)]
+    pc_score_final_train_combined <- data.frame(train_test_split_normalized$response_train, PFC_score_final_train, PC_score_final_train)
+    colnames(pc_score_final_train_combined) <- c(
+      c("response"),
+      paste0( rep("FPC", n_fpc_best), as.character(1:n_fpc_best)),
+      paste0( rep("PC", n_spc_best), as.character(1:n_spc_best))
+    )
+    linear_fit_final <- lm(response~., data = pc_score_final_train_combined)
+
+    # test set pc scores
+    PFC_score_final_test <- MFPCA_fit_final$scores.pred
+    PC_score_final_test <- (predict(PCA_fit_final, train_test_split_normalized$data_scalar_test))[,c(1:n_spc_best)]
+    pc_score_final_test_combined <- data.frame(PFC_score_final_test, PC_score_final_test)
+    colnames(pc_score_final_test_combined) <- c(
+      paste0( rep("FPC", n_fpc_best), as.character(1:n_fpc_best)),
+      paste0( rep("PC", n_spc_best), as.character(1:n_spc_best))
+    )
+    y_pred_final <- predict(linear_fit_final, pc_score_final_test_combined)
+    rmse_simul_fpca[rep_number,1] <- sqrt(
+      mean((y_pred_final - train_test_split_normalized$response_test)^2)
+      )
+    print(rmse_simul_fpca[rep_number,1])
+
+    plot(-0.2:0.2, -0.2:0.2, pch = "", xlim = c(-0.2, 0.2),  ylim = c(-0.2, 0.2))
+    plot(train_test_split_normalized$response_test, y_pred_final)
+    abline(a=0, b=1)
+
+    pc_score_final_train_combined_fpc_only <- data.frame(train_test_split_normalized$response_train, PFC_score_final_train)
+    colnames(pc_score_final_train_combined_fpc_only) <- c(
+      c("response"),
+      paste0( rep("FPC", n_fpc_best), as.character(1:n_fpc_best))
+    )
+    linear_fit_final_fpc_only <- lm(response~., data = pc_score_final_train_combined_fpc_only)
+    pc_score_final_test_combined_fpc_only <- data.frame(PFC_score_final_test)
+    colnames(pc_score_final_test_combined_fpc_only) <- c(
+      paste0( rep("FPC", n_fpc_best), as.character(1:n_fpc_best))
+    )
+    y_pred_final_fpc_only <- predict(linear_fit_final_fpc_only, pc_score_final_test_combined_fpc_only)
+    rmse_simul_fpca[rep_number,2] <- sqrt(
+      mean((y_pred_final_fpc_only - train_test_split_normalized$response_test)^2)
+    )
+    print(rmse_simul_fpca[rep_number,2])
+
+    pc_score_final_train_combined_spc_only <- data.frame(train_test_split_normalized$response_train, PC_score_final_train)
+    colnames(pc_score_final_train_combined_spc_only) <- c(
+      c("response"),
+      paste0( rep("PC", n_spc_best), as.character(1:n_spc_best))
+    )
+    linear_fit_final_spc_only <- lm(response~., data = pc_score_final_train_combined_spc_only)
+    pc_score_final_test_combined_spc_only <- data.frame(PC_score_final_test)
+    colnames(pc_score_final_test_combined_spc_only) <- c(
+      paste0( rep("PC", n_spc_best), as.character(1:n_spc_best))
+    )
+    y_pred_final_spc_only <- predict(linear_fit_final_spc_only, pc_score_final_test_combined_spc_only)
+    rmse_simul_fpca[rep_number,3] <- sqrt(
+      mean((y_pred_final_spc_only - train_test_split_normalized$response_test)^2)
+    )
+    print(rmse_simul_fpca[rep_number,3])
+
+```
+
 ## Documenting the package and building

### 2025-10-07 create-FSHybridPLS.Rmd
curve_normalize

@@
 We start by specifying the information needed in the DESCRIPTION file of the R package.
-
+ library()
+library(fda)
 ```{r package-setup, message=FALSE, results='hide'}
@@
     Description = "This package says hello.  But its actual purpose is to show how an R package can be completely coded in a single R markdown file.",
-    Imports = "fda (>= 6.1.3), Matrix, funData, foreach, irlba, refund",
+    Imports = "fda (>= 6.1.3), Matrix, funData, foreach, irlba, refund, R6",
     `Authors@R` = person(
@@
 ```{r}
+#' @title Generate Train Indices
+#' @description Generates train/test split indices.
+#' @param n_sample Integer. Number of samples.
+#' @param train_ratio Numeric. Ratio of train samples.
+#' @return Vector of train indices.
+get_idx_train <- function(n_sample, train_ratio) {
+  n_train <- floor(n_sample * train_ratio)
+  idx_train <- sort(sample(n_sample, n_train, replace = FALSE))
+  return(idx_train)
+}
+```
+
+```{r}
 create_idx_kfold <- function(n_sample, n_fold){
@@
 
-```{r}
+### split.all
+
+Splits functional predictors, scalar predictors, and response into train and test sets.
+
+```{r}
+#'Split Functional, Scalar, and Response Data
+#' @param data_fun_1 fd object (fda package). Functional predictor 1.
+#' @param data_fun_2 fd object (fda package). Functional predictor 2.
+#' @param data_scalar Matrix. Scalar predictors.
+#' @param response Vector. Response variable.
+#' @param train_idx Vector. Indices for train data.
+#' @return List containing split train and test sets.
+#' @export
+split.all <- function(data_fun_1, data_fun_2, data_scalar, response, train_idx) {
+  # --- Type Checks ---
+  stopifnot(
+    # Functional data checks (assuming 'fd' class from the 'fda' package)
+    inherits(data_fun_1, "fd"),
+    inherits(data_fun_2, "fd"),
+
+    # Scalar predictor check
+    is.matrix(data_scalar),
+
+    # Response variable check
+    is.vector(response) || is.numeric(response) || is.factor(response),
+
+    # Training index check
+    is.vector(train_idx),
+    is.numeric(train_idx),
+    all(train_idx > 0), # Indices should be positive
+    all(train_idx == round(train_idx)) # Indices should be integers
+  )
+  # -------------------
+
+  return(list(
+    data_fun_1_train = data_fun_1[train_idx],
+    data_fun_1_test = data_fun_1[-train_idx],
+    data_fun_2_train = data_fun_2[train_idx],
+    data_fun_2_test = data_fun_2[-train_idx],
+    data_scalar_train = data_scalar[train_idx, , drop = FALSE],
+    data_scalar_test = data_scalar[-train_idx, , drop = FALSE],
+    response_train = response[train_idx],
+    response_test = response[-train_idx]
+  ))
+}
+```
+
+### normailize.all
+
+```{r}
+#' 
+#' @export
 normailize.all <- function(split.all_obj){
@@
 }
+```
+
+### curve_normalize
+Subtracts the mean function and divides by a scaling constant (deno). This implementation uses the native fda S3 methods (minus.fd and times.fd).
+```{r}
+#' Normalize a functional data object by its mean and standard deviation.
+#'
+#' @param functional fd object (fda package). The functional data to be normalized (N samples).
+#' @param mean_functional fd object (fda package). The mean function (1 sample).
+#' @param deno Numeric scalar. The standard deviation or scaling factor.
+#' @return A new fd object containing the normalized functions.
+#' @export
+curve_normalize <- function(functional, mean_functional, deno) {
+  # Type checks
+  stopifnot(
+    "'functional' must be an 'fd' object" = inherits(functional, "fd"),
+    "'mean_functional' must be an 'fd' object" = inherits(mean_functional, "fd"),
+    "'deno' must be a single positive numeric value" = is.numeric(deno) && length(deno) == 1 && deno > 0
+  )
+
+  # 1. Centering: functional - mean_functional
+  # fda::minus.fd handles the broadcasting of the single-sample mean_functional.
+  centered_functional <- fda::minus.fd(functional, mean_functional)
+
+  # 2. Scaling: (1/deno) * centered_functional
+  functional_normalized <- fda::times.fd(1/deno, centered_functional)
+
+  return(functional_normalized)
+}
+```
+
+```{r}
+#' 
+#' @export
+curve_normalize <- function(functional, mean_functional, deno){
+  # operation also takes care of the original_X
+
+  functional_normalized <- fd(coef =
+                                coef(functional) - coef(mean_functional) %*% matrix(1, ncol = ncol(coef(functional))),
+                              basisobj = functional$basis
+                              )#numerator
+  functional_normalized <- times.fd(1/deno, functional_normalized)
+  return(functional_normalized)
+}
+```
+
+```{r}
+curve_normalize_train_test <- function(train, test){
+  train_normalized <- train
+  test_normalized <- test
+  deno_train <- rep(NA, train@n_functional)
+  for (k in 1:train@n_functional){ # for kth functional predictor
+    mean_train <- mean.fd(train@functional_list[[k]]) # train mean function
+    centered_train <- center.fd(train@functional_list[[k]])
+    sd_train <- sd.fd(train@functional_list[[k]])
+    deno_train[k] <- sqrt(inprod(sd_train, sd_train))
+
+    train_normalized@functional_list[[k]] <- curve_normalize(
+      train_normalized@functional_list[[k]],
+      mean_train,
+      deno_train[k]
+      )
+
+    test_normalized@functional_list[[k]] <-
+      curve_normalize(
+        test_normalized@functional_list[[k]],
+        mean_train,
+        deno_train[k]
+      )
+  }
+  return( list(
+    train = train_normalized,
+    test = test_normalized,
+    deno_train = deno_train
+    ))}
+```
+
+```{r}
+# scalar_normalize <- function(scalar_predictor, mean, deno){
+#   scalar_predictor_normalized <- subtr_broadcast(scalar_predictor, mean) #numerator
+#   deno_mat <- matrix(rep(1,nrow(scalar_predictor))) %*% deno
+#   scalar_predictor_normalized <- scalar_predictor_normalized / deno_mat
+#   return(scalar_predictor_normalized)
+# }
+#
+# scalar_normalize_train_test <- function(predictor_train, predictor_test){
+#   predictor_train_normalized <- predictor_train
+#   predictor_test_normalized <- predictor_test
+#
+#   mean_train <- get_mean(predictor_train@Z) # train mean function
+#   sd_train <- get_sd(predictor_train@Z)
+#
+#   predictor_train_normalized@Z <-
+#     scalar_normalize(
+#       predictor_train@Z,
+#       mean_train,
+#       sd_train
+#       )
+#
+#   predictor_test_normalized@Z <-
+#     scalar_normalize(
+#       predictor_test@Z,
+#       mean_train,
+#       sd_train
+#     )
+#
+#   return(
+#     list(
+#       train = predictor_train_normalized,
+#       test = predictor_test_normalized
+#     )
+#   )
+# }
+```
+
+```{r}
+#
+# btwn_normalize_train_test <- function(train, test){
+#   #"Scale the scalar predictors so that the variability between the functional and scalar predictors are comparable:")
+#   Z_s <- train@Z
+#   train_normalized <- train
+#   test_normalized <- test
+#
+#   omega <- 0
+#   for (k in 1:train@n_functional){ # for kth functional predictor
+#     omega <- omega + sum(diag(inprod(
+#       train@functional_list[[k]],
+#       train@functional_list[[k]]
+#       )))
+#
+#   }
+#     omega <- omega / sum((Z_s)^2)
+#
+#     train_normalized@Z <- sqrt(omega) * (train@Z)
+#     test_normalized@Z <- sqrt(omega) * (test@Z)
+#
+#     return(
+#       list(
+#         train = train_normalized,
+#         test = test_normalized
+#       ))}
+```
+
+```{r}
+
+### DataSplitterNormalizer
+R6 class to split functional and scalar predictors into train and test sets and apply normalization techniques including curve normalization, scalar normalization, and between-functional-scalar normalization.
+```{r}
+#' @title Dataset Splitting and Normalization
+#' @description 
+DataSplitterNormalizer <- R6::R6Class(
+  "DataSplitterNormalizer",
+
+  public = list(
+
+    data_original = NULL,  # Stores the original dataset
+    n_sample = NULL,  # Number of samples
+    train_ratio = NULL,  # Train-test split ratio
+    idx_train = NULL,  # Train indices
+    train=NULL,
+    test=NULL,
+
+    #' @title Initialize Data Splitter and Normalizer
+    #' @description Constructs the instance, splits the data into train and test sets.
+    #' Users must call `normalize_data()` separately.
+    #' @param data_original List. Contains `functional_predictors` (list of `fd` objects)
+    #' and `scalar_predictors` (matrix).
+    #' @param train_ratio Numeric. Ratio of data to use for training (e.g., 0.8).
+    #' @return An instance of `DataSplitterNormalizer`.
+    #' @export
+    initialize = function(data_original, train_ratio = 0.8) {
+      self$n_sample <- length(data_original$response)
+      self$train_ratio <- train_ratio
+      self$data_original <- data_original
+
+    },
+
+    #' @title Split Data into Train and Test Sets
+    #' @description Creates train/test indices and splits functional, scalar, and response variables.
+    #' @return None. Updates train and test variables.
+    #' @export
+    split_data = function(idx_train = NULL) {
+      # Use provided idx_train if available; otherwise, generate it
+      if (is.null(idx_train)) {
+        self$idx_train <- get_idx_train(self$n_sample, self$train_ratio)
+      } else {
+        self$idx_train <- idx_train
+      }
+
+      split_packed <- split.all(
+        self$data_original$functional_1,
+        self$data_original$functional_2,
+        self$data_original$scalar,
+        self$data_original$response,
+        self$idx_train
+      )
+
+      # Assign train/test sets
+      self$train <- list(
+        functional_1 = split_packed$data_fun_1_train,
+        functional_2 = split_packed$data_fun_2_train,
+        scalar = split_packed$data_scalar_train,
+        response = split_packed$response_train
+      )
+      self$test <- list(
+        functional_1 = split_packed$data_fun_1_test,
+        functional_2 = split_packed$data_fun_2_test,
+        scalar = split_packed$data_scalar_test,
+        response = split_packed$response_test
+      )
+
+    },
+
+    #' @title Normalize Train and Test Data
+    #' @description Applies curve, scalar, and between-functional-scalar normalization.
+    #' @return None. Updates train and test sets.
+    #' @export
+    normalize_data = function() {
+      # Initialize normalizers
+      normalizer_functional <- normalizer_functional_predictor$new()
+      normalizer_scalar <- normalizer_scalar_predictor$new()
+
+      # Normalize first functional predictor
+      normalizer_functional$normalize(self$train$functional_1, self$test$functional_1)
+      self$train$functional_1 <- normalizer_functional$get_normalized()$train_normalized
+      self$test$functional_1 <- normalizer_functional$get_normalized()$test_normalized
+
+      # Normalize second functional predictor
+      normalizer_functional$normalize(self$train$functional_2, self$test$functional_2)
+      self$train$functional_2 <- normalizer_functional$get_normalized()$train_normalized
+      self$test$functional_2 <- normalizer_functional$get_normalized()$test_normalized
+
+      # Normalize scalar predictors
+      normalizer_scalar$normalize(self$train$scalar, self$test$scalar)
+      self$train$scalar <- normalizer_scalar$get_normalized()$train_normalized
+      self$test$scalar<- normalizer_scalar$get_normalized()$test_normalized
+
+      # Apply between-functional-scalar normalization
+      self$normalize_between()
+
+      # Normalize response variable
+      self$normalize_response()
+    },
+
+    #' @title Normalize Between Functional and Scalar Predictors
+    #' @description Scales scalar predictors to ensure comparability with functional predictors.
+    #' @export
+    normalize_between = function() {
+      omega <- sum(diag(inprod(self$train$functional_1, self$train$functional_1))) +
+        sum(diag(inprod(self$train$functional_2, self$train$functional_2)))
+
+      omega <- omega / sum(self$train$scalar^2)
+
+      self$train$scalar <- sqrt(omega) * self$train$scalar
+      self$test$scalar <- sqrt(omega) * self$test$scalar
+    },
+
+    #' @title Normalize Response Variable
+    #' @description Centers response variable based on training mean.
+    #' @export
+    normalize_response = function() {
+      response_mean_train <- mean(self$train$response)
+      self$train$response <- self$train$response - response_mean_train
+      self$test$response <- self$test$response - response_mean_train
+    } #must not end with ,
+
+  )
+)
+
 ```

### 2025-10-07 create-FSHybridPLS.Rmd
function normalize tested

@@
 ```{r}
-#' 
-#' @export
-curve_normalize <- function(functional, mean_functional, deno){
-  # operation also takes care of the original_X
-
-  functional_normalized <- fd(coef =
-                                coef(functional) - coef(mean_functional) %*% matrix(1, ncol = ncol(coef(functional))),
-                              basisobj = functional$basis
-                              )#numerator
-  functional_normalized <- times.fd(1/deno, functional_normalized)
-  return(functional_normalized)
-}
+#' Normalize Functional Predictors in Hybrid Objects (Train/Test Split)
+#'
+#' Normalizes the functional components of both the training and testing 
+#' `predictor_hybrid` objects using the mean and standard deviation derived
+#' ONLY from the training data. The scalar components (Z) are left unchanged.
+#'
+#' @param train A `predictor_hybrid` object representing the training set.
+#' @param test A `predictor_hybrid` object representing the testing set.
+#' @return A list containing:
+#'   \item{train}{The normalized training `predictor_hybrid` object.}
+#'   \item{test}{The normalized testing `predictor_hybrid` object.}
+#'   \item{deno_train}{A numeric vector of scaling factors used for each functional predictor.}
+#' @export
+curve_normalize_train_test <- function(train, test) {
+  # --- Type Checks ---
+  stopifnot(
+    "'train' must be of class 'predictor_hybrid'" = inherits(train, "predictor_hybrid"),
+    "'test' must be of class 'predictor_hybrid'" = inherits(test, "predictor_hybrid"),
+    "Mismatch in number of functional predictors" = train$n_functional == test$n_functional
+  )
+
+  train_normalized <- train
+  test_normalized <- test
+  deno_train <- numeric(train$n_functional)
+
+  # Iterate through each functional predictor (k)
+  for (k in seq_len(train$n_functional)) {
+
+    # 1. Determine centering and scaling factors from the TRAINING data only
+    train_fd <- train$functional_list[[k]]
+
+    # Calculate the mean function for centering
+    mean_train <- fda::mean.fd(train_fd)
+
+    # Calculate the standard deviation function
+    sd_train <- fda::sd.fd(train_fd)
+
+    # Calculate the scaling factor (L2 norm of the standard deviation function)
+    deno_train[k] <- sqrt(fda::inprod(sd_train, sd_train))
+
+    # Ensure scaling factor is positive
+    if (deno_train[k] <= 1e-10) {
+      warning(paste("Scaling factor for functional predictor", k, "is near zero. Skipping normalization for this predictor."))
+      deno_train[k] <- 1 # Set to 1 to prevent division by zero, effectively no normalization
+    }
+
+    # 2. Normalize the TRAINING set
+    train_normalized$functional_list[[k]] <- curve_normalize(
+      train_fd, # Use original train data
+      mean_train,
+      deno_train[k]
+    )
+
+    # 3. Normalize the TEST set (using train factors to prevent leakage)
+    test_normalized$functional_list[[k]] <-
+      curve_normalize(
+        test$functional_list[[k]], # Use original test data
+        mean_train, # Centered by training mean
+        deno_train[k] # Scaled by training SD
+      )
+  }
+
+  # Return the modified hybrid objects and the scaling factors
+  return( list(
+    train = train_normalized,
+    test = test_normalized,
+    deno_train = deno_train
+  ))
+}
+
 ```

### 2025-10-07 create-FSHybridPLS.Rmd
delete test

@@
 ```{r}
+#' 
+#' @export
+curve_normalize <- function(functional, mean_functional, deno){
+  # operation also takes care of the original_X
+
+  functional_normalized <- fd(coef =
+                                coef(functional) - coef(mean_functional) %*% matrix(1, ncol = ncol(coef(functional))),
+                              basisobj = functional$basis
+                              )#numerator
+  functional_normalized <- times.fd(1/deno, functional_normalized)
+  return(functional_normalized)
+}
+```
+
+```{r}
 #' Normalize Functional Predictors in Hybrid Objects (Train/Test Split)
@@
 
-```
-
-```{r}
-curve_normalize_train_test <- function(train, test){
-  train_normalized <- train
-  test_normalized <- test
-  deno_train <- rep(NA, train@n_functional)
-  for (k in 1:train@n_functional){ # for kth functional predictor
-    mean_train <- mean.fd(train@functional_list[[k]]) # train mean function
-    centered_train <- center.fd(train@functional_list[[k]])
-    sd_train <- sd.fd(train@functional_list[[k]])
-    deno_train[k] <- sqrt(inprod(sd_train, sd_train))
-
-    train_normalized@functional_list[[k]] <- curve_normalize(
-      train_normalized@functional_list[[k]],
-      mean_train,
-      deno_train[k]
-      )
-
-    test_normalized@functional_list[[k]] <-
-      curve_normalize(
-        test_normalized@functional_list[[k]],
-        mean_train,
-        deno_train[k]
-      )
-  }
-  return( list(
-    train = train_normalized,
-    test = test_normalized,
-    deno_train = deno_train
-    ))}
 ```

### 2025-10-08 create-FSHybridPLS.Rmd
scalar normalization test done

@@
 ```{r classdef:predictor_hybrid}
-
 #' Create a predictor_hybrid object (S3 version, automatic basis size and Gram matrix)
@@
 #' Construct a Single-Sample Predictor Hybrid Object from Coefficients
-#'
 #' Reconstructs a \code{predictor_hybrid} object representing one observation, using a numeric
@@
 }
+```
+
+### add_broadcast(for matrix)
+
+```{r}
+#' @export
+#' 
+#' 
+# --- 1. Define the S4 Generic Function ---
+# This must be run first to tell R that 'add_broadcast' is a function 
+# that can have methods defined for different classes.
+setGeneric("add_broadcast", function(input, other, alpha = 1) {
+  standardGeneric("add_broadcast")
+})
+
+# --- 2. Define the S4 Method for 'matrix' Class ---
+setMethod("add_broadcast", "matrix",
+###########################################
+function(input, other, alpha = 1){
+
+  # 1. Structural Check: Ensure RHS is a single observation.
+  # This uses length() for vectors, and dim()[1] for matrices.
+  is_matrix_other <- is.matrix(other)
+  if (is_matrix_other && dim(other)[1] > 1) {
+    stop("RHS must have a single observation (row).")
+  }
+
+  # 2. Conversion: Convert a single-row matrix into a vector for broadcasting.
+  # If 'other' is already a vector, this does nothing.
+  # If 'other' is a 1xP matrix, this flattens it into a length-P vector.
+  if (is_matrix_other) {
+    other <- as.vector(other) 
+  }
+
+  # 3. Native Arithmetic: Use simple R arithmetic for high performance.
+  # R broadcasts the vector 'other' across the rows of the matrix 'input'.
+  return( t( t(input) + alpha * other))
+}
+###########################################
+)
+
+```
+### subtr_broadcast (for matrix)
+
+```{r}
+#' @export
+#' 
+#'
+setGeneric("subtr_broadcast", function(input, other, alpha = 1) {
+  standardGeneric("subtr_broadcast")
+})
+setMethod("subtr_broadcast", "matrix",
+###########################################
+function(input, other, alpha = 1){
+  return(add_broadcast(input, other, (-1*alpha)))
+  }
+###########################################
+)
+
 ```
@@
 ### curve_normalize
-Subtracts the mean function and divides by a scaling constant (deno). This implementation uses the native fda S3 methods (minus.fd and times.fd).
-```{r}
-#' Normalize a functional data object by its mean and standard deviation.
-#'
-#' @param functional fd object (fda package). The functional data to be normalized (N samples).
-#' @param mean_functional fd object (fda package). The mean function (1 sample).
-#' @param deno Numeric scalar. The standard deviation or scaling factor.
-#' @return A new fd object containing the normalized functions.
-#' @export
-curve_normalize <- function(functional, mean_functional, deno) {
-  # Type checks
-  stopifnot(
-    "'functional' must be an 'fd' object" = inherits(functional, "fd"),
-    "'mean_functional' must be an 'fd' object" = inherits(mean_functional, "fd"),
-    "'deno' must be a single positive numeric value" = is.numeric(deno) && length(deno) == 1 && deno > 0
-  )
-
-  # 1. Centering: functional - mean_functional
-  # fda::minus.fd handles the broadcasting of the single-sample mean_functional.
-  centered_functional <- fda::minus.fd(functional, mean_functional)
-
-  # 2. Scaling: (1/deno) * centered_functional
-  functional_normalized <- fda::times.fd(1/deno, centered_functional)
-
-  return(functional_normalized)
-}
-```
-
+Subtracts the mean function and divides by a scaling constant (deno). This implementation does not use the native fda S3 methods (minus.fd and times.fd), since they do not broadcast well.
 ```{r}
@@
 
+### curve_normalize_train_test
+Normalizes the functional components of both the training and testing 'predictor_hybrid' objects using the mean and standard deviation derived ONLY from the training data.
+The scalar components (Z) are left unchanged.
+
 ```{r}
 #' Normalize Functional Predictors in Hybrid Objects (Train/Test Split)
-#'
-#' Normalizes the functional components of both the training and testing 
-#' `predictor_hybrid` objects using the mean and standard deviation derived
-#' ONLY from the training data. The scalar components (Z) are left unchanged.
-#'
 #' @param train A `predictor_hybrid` object representing the training set.
@@
 ```{r}
-# scalar_normalize <- function(scalar_predictor, mean, deno){
-#   scalar_predictor_normalized <- subtr_broadcast(scalar_predictor, mean) #numerator
-#   deno_mat <- matrix(rep(1,nrow(scalar_predictor))) %*% deno
-#   scalar_predictor_normalized <- scalar_predictor_normalized / deno_mat
-#   return(scalar_predictor_normalized)
-# }
+#'
+#' @export
+scalar_normalize <- function(scalar_predictor, mean, deno){
+   scalar_predictor_normalized <- subtr_broadcast(scalar_predictor, mean) #numerator
+   deno_mat <- matrix(rep(1,nrow(scalar_predictor))) %*% deno
+   scalar_predictor_normalized <- scalar_predictor_normalized / deno_mat
+   return(scalar_predictor_normalized)
+ }
+```
+
+```{r}
+#' Normalize the scalar component (Z) of hybrid predictors using training set statistics.
+#'
+#' @param predictor_train A `predictor_hybrid` object (train set).
+#' @param predictor_test A `predictor_hybrid` object (test set).
+#' @return A list containing the normalized 'train' and 'test' hybrid objects.
+#' @export
+scalar_normalize_train_test <- function(predictor_train, predictor_test){
+
+  # Type and structure checks
+  stopifnot(
+    inherits(predictor_train, "predictor_hybrid"),
+    inherits(predictor_test, "predictor_hybrid"),
+    predictor_train$n_scalar == predictor_test$n_scalar
+  )
+
+  # Create copies for modification
+  predictor_train_normalized <- predictor_train
+  predictor_test_normalized <- predictor_test
+
+  # 1. Calculate statistics from the TRAINING set only
+  mean_train <- colMeans(predictor_train$Z)
+  sd_train <- apply(predictor_train$Z, 2, sd)
+
+  # 2. Apply normalization to the TRAINING set
+  predictor_train_normalized$Z <-
+    scalar_normalize(
+      predictor_train$Z,
+      mean_train,
+      sd_train
+    )
+
+  # 3. Apply normalization to the TEST set using TRAIN statistics
+  predictor_test_normalized$Z <-
+    scalar_normalize(
+      predictor_test$Z,
+      mean_train, # IMPORTANT: Use train mean
+      sd_train    # IMPORTANT: Use train SD
+    )
+
+  return(
+    list(
+      train = predictor_train_normalized,
+      test = predictor_test_normalized
+    )
+  )
+}
+```
+
+```{r}
+#' --- Dependencies for Testing ---
+library(fda) # Required for mock functional data
+
+# Placeholder for a minimal predictor_hybrid constructor for testing purposes
+
+# --- Test Script Start ---
+
+# 1. Setup Mock Data
+N_train <- 100
+N_test <- 50
+N_scalar <- 2
+N_functional <- 1
+
+# Create Functional Data (Needs to be present but remain untouched)
+basis_obj <- create.bspline.basis(rangeval = c(0, 10), nbasis = 7)
+train_coefs <- matrix(rnorm(N_train * 7), nrow = 7)
+test_coefs <- matrix(rnorm(N_test * 7), nrow = 7)
+mock_fd_train <- fd(train_coefs, basis_obj)
+mock_fd_test <- fd(test_coefs, basis_obj)
+
+# Create Scalar Data (Crucial for the test)
+# Training data has a clear mean and SD
+Z_train <- matrix(rnorm(N_train * N_scalar, mean = c(5, 10), sd = c(2, 3)), 
+                  nrow = N_train, ncol = N_scalar, byrow = TRUE)
+# Testing data has different properties (must be normalized by train stats)
+Z_test <- matrix(rnorm(N_test * N_scalar, mean = c(1, 1), sd = c(10, 10)), 
+                 nrow = N_test, ncol = N_scalar, byrow = TRUE)
+
+# Create Hybrid Objects
+W_train <- predictor_hybrid(Z = Z_train, functional_list = list(mock_fd_train))
+W_test <- predictor_hybrid(Z = Z_test, functional_list = list(mock_fd_test))
+
+# Store original Z for comparison
+Z_train_original <- W_train$Z
+Z_test_original <- W_test$Z
+
+# 2. Run the Function Under Test
+W_normalized_list <- scalar_normalize_train_test(W_train, W_test)
+W_train_norm <- W_normalized_list$train
+W_test_norm <- W_normalized_list$test
+
+# 3. Verification and Assertions
+
+cat("--- Running Verification Checks ---\n")
+
+# Check 1: Training set is correctly normalized (Mean ~ 0, SD ~ 1)
+train_mean_norm <- colMeans(W_train_norm$Z)
+train_sd_norm <- apply(W_train_norm$Z, 2, sd)
+
+stopifnot(
+  "Train mean Col 1 not near 0" = all(abs(train_mean_norm[1]) < 1e-10),
+  "Train mean Col 2 not near 0" = all(abs(train_mean_norm[2]) < 1e-10),
+  "Train SD Col 1 not near 1" = all(abs(train_sd_norm[1] - 1) < 1e-10),
+  "Train SD Col 2 not near 1" = all(abs(train_sd_norm[2] - 1) < 1e-10)
+)
+cat("Check 1: Training set Z-score normalization successful (Mean~0, SD~1).\n")
+
+# Check 2: Functional components are untouched
+stopifnot(
+  "Functional list should not change" = isTRUE(all.equal(
+    W_train$functional_list[[1]]$coefs, 
+    W_train_norm$functional_list[[1]]$coefs
+  ))
+)
+cat("Check 2: Functional components successfully preserved.\n")
+
+# Check 3: Test set is normalized using TRAIN statistics (crucial consistency check)
+
+# Recalculate the training statistics
+train_mean_recalc <- get_mean(Z_train_original)
+train_sd_recalc <- get_sd(Z_train_original)
+
+# Manually normalize the test set using TRAIN stats
+Z_test_expected <- t( (t(Z_test_original) - train_mean_recalc) / train_sd_recalc)
+
+# Compare the function's output (W_test_norm$Z) against the manual calculation
+stopifnot(
+  "Test set normalization mismatch" = isTRUE(all.equal(W_test_norm$Z, Z_test_expected))
+)
+cat("Check 3: Test set correctly normalized using only Training statistics.\n")
+
+cat("--- All tests passed successfully! ---\n")
+
+```
+
+```{r}
+
 #

### 2025-10-08 create-FSHybridPLS.Rmd
btwn_normalize_train_test

@@
 #' Create a predictor_hybrid object (S3 version, automatic basis size and Gram matrix)
-#'
 #' Constructs a hybrid predictor object that stores both scalar and functional predictors,
@@
 ```{r}
-#' --- Dependencies for Testing ---
-library(fda) # Required for mock functional data
-
-# Placeholder for a minimal predictor_hybrid constructor for testing purposes
-
-# --- Test Script Start ---
-
-# 1. Setup Mock Data
-N_train <- 100
-N_test <- 50
-N_scalar <- 2
-N_functional <- 1
-
-# Create Functional Data (Needs to be present but remain untouched)
-basis_obj <- create.bspline.basis(rangeval = c(0, 10), nbasis = 7)
-train_coefs <- matrix(rnorm(N_train * 7), nrow = 7)
-test_coefs <- matrix(rnorm(N_test * 7), nrow = 7)
-mock_fd_train <- fd(train_coefs, basis_obj)
-mock_fd_test <- fd(test_coefs, basis_obj)
-
-# Create Scalar Data (Crucial for the test)
-# Training data has a clear mean and SD
-Z_train <- matrix(rnorm(N_train * N_scalar, mean = c(5, 10), sd = c(2, 3)), 
-                  nrow = N_train, ncol = N_scalar, byrow = TRUE)
-# Testing data has different properties (must be normalized by train stats)
-Z_test <- matrix(rnorm(N_test * N_scalar, mean = c(1, 1), sd = c(10, 10)), 
-                 nrow = N_test, ncol = N_scalar, byrow = TRUE)
-
-# Create Hybrid Objects
-W_train <- predictor_hybrid(Z = Z_train, functional_list = list(mock_fd_train))
-W_test <- predictor_hybrid(Z = Z_test, functional_list = list(mock_fd_test))
-
-# Store original Z for comparison
-Z_train_original <- W_train$Z
-Z_test_original <- W_test$Z
-
-# 2. Run the Function Under Test
-W_normalized_list <- scalar_normalize_train_test(W_train, W_test)
-W_train_norm <- W_normalized_list$train
-W_test_norm <- W_normalized_list$test
-
-# 3. Verification and Assertions
-
-cat("--- Running Verification Checks ---\n")
-
-# Check 1: Training set is correctly normalized (Mean ~ 0, SD ~ 1)
-train_mean_norm <- colMeans(W_train_norm$Z)
-train_sd_norm <- apply(W_train_norm$Z, 2, sd)
-
+#' Scale the scalar predictors so that the variability between the
+#' functional and scalar predictors are comparable.
+#'
+#' This method calculates a scaling factor (sqrt(omega)) from the training
+#' set, defined as the ratio of the total sum of squares (L2 norms) of all
+#' functional components to the total sum of squares of all scalar components.
+#'
+#' @param train A predictor_hybrid object representing the training data.
+#' @param test A predictor_hybrid object representing the test data.
+#'
+#' @return A list containing the normalized 'train' and 'test' predictor_hybrid objects.
+#' @export
+btwn_normalize_train_test <- function(train, test){
+
+  # Type checks
   stopifnot(
-  "Train mean Col 1 not near 0" = all(abs(train_mean_norm[1]) < 1e-10),
-  "Train mean Col 2 not near 0" = all(abs(train_mean_norm[2]) < 1e-10),
-  "Train SD Col 1 not near 1" = all(abs(train_sd_norm[1] - 1) < 1e-10),
-  "Train SD Col 2 not near 1" = all(abs(train_sd_norm[2] - 1) < 1e-10)
-)
-cat("Check 1: Training set Z-score normalization successful (Mean~0, SD~1).\n")
-
-# Check 2: Functional components are untouched
-stopifnot(
-  "Functional list should not change" = isTRUE(all.equal(
-    W_train$functional_list[[1]]$coefs, 
-    W_train_norm$functional_list[[1]]$coefs
-  ))
-)
-cat("Check 2: Functional components successfully preserved.\n")
-
-# Check 3: Test set is normalized using TRAIN statistics (crucial consistency check)
-
-# Recalculate the training statistics
-train_mean_recalc <- get_mean(Z_train_original)
-train_sd_recalc <- get_sd(Z_train_original)
-
-# Manually normalize the test set using TRAIN stats
-Z_test_expected <- t( (t(Z_test_original) - train_mean_recalc) / train_sd_recalc)
-
-# Compare the function's output (W_test_norm$Z) against the manual calculation
-stopifnot(
-  "Test set normalization mismatch" = isTRUE(all.equal(W_test_norm$Z, Z_test_expected))
-)
-cat("Check 3: Test set correctly normalized using only Training statistics.\n")
-
-cat("--- All tests passed successfully! ---\n")
-
-```
-
-```{r}
-
-#
-# scalar_normalize_train_test <- function(predictor_train, predictor_test){
-#   predictor_train_normalized <- predictor_train
-#   predictor_test_normalized <- predictor_test
-#
-#   mean_train <- get_mean(predictor_train@Z) # train mean function
-#   sd_train <- get_sd(predictor_train@Z)
-#
-#   predictor_train_normalized@Z <-
-#     scalar_normalize(
-#       predictor_train@Z,
-#       mean_train,
-#       sd_train
-#       )
-#
-#   predictor_test_normalized@Z <-
-#     scalar_normalize(
-#       predictor_test@Z,
-#       mean_train,
-#       sd_train
-#     )
-#
-#   return(
-#     list(
-#       train = predictor_train_normalized,
-#       test = predictor_test_normalized
-#     )
-#   )
-# }
-```
-
-```{r}
-#
-# btwn_normalize_train_test <- function(train, test){
-#   #"Scale the scalar predictors so that the variability between the functional and scalar predictors are comparable:")
-#   Z_s <- train@Z
-#   train_normalized <- train
-#   test_normalized <- test
-#
-#   omega <- 0
-#   for (k in 1:train@n_functional){ # for kth functional predictor
-#     omega <- omega + sum(diag(inprod(
-#       train@functional_list[[k]],
-#       train@functional_list[[k]]
-#       )))
-#
-#   }
-#     omega <- omega / sum((Z_s)^2)
-#
-#     train_normalized@Z <- sqrt(omega) * (train@Z)
-#     test_normalized@Z <- sqrt(omega) * (test@Z)
-#
-#     return(
-#       list(
-#         train = train_normalized,
-#         test = test_normalized
-#       ))}
+    "'train' must be of class 'predictor_hybrid'" = inherits(train, "predictor_hybrid"),
+    "'test' must be of class 'predictor_hybrid'" = inherits(test, "predictor_hybrid")
+  )
+
+  # Create copies for modification
+  train_normalized <- train
+  test_normalized <- test
+
+  # Z_s for clarity in calculation
+  Z_s <- train$Z
+
+  # --- 1. Calculate the numerator of omega (Sum of L2 norms of all functional samples in train) ---
+  omega_numerator <- 0
+
+  for (k in seq_len(train$n_functional)){ # for kth functional predictor
+    # fda::inprod(fd, fd) returns the N x N matrix of inner products.
+    # The diagonal elements are the L2 norm squared for each sample.
+    functional_inprod_matrix <- fda::inprod(
+      train$functional_list[[k]],
+      train$functional_list[[k]]
+    )
+
+    # Sum the diagonal to get the total squared norm for this predictor k
+    omega_numerator <- omega_numerator + sum(diag(functional_inprod_matrix))
+  }
+
+  # --- 2. Calculate the denominator of omega (Sum of squares of all scalar samples in train) ---
+  omega_denominator <- sum(Z_s^2)
+
+  # Handle case where scalar variance is zero (prevent division by zero)
+  if (omega_denominator == 0) {
+    warning("Scalar component sum of squares is zero. No scaling applied.")
+    omega <- 1
+  } else {
+    # Calculate the scaling factor omega
+    omega <- omega_numerator / omega_denominator
+  }
+
+  # --- 3. Apply scaling factor sqrt(omega) to both train and test scalar components ---
+  scaling_factor <- sqrt(omega)
+
+  train_normalized$Z <- scaling_factor * (train$Z)
+  test_normalized$Z <- scaling_factor * (test$Z)
+
+  return(
+    list(
+      train = train_normalized,
+      test = test_normalized
+    )
+  )
+}
+
 ```

### 2025-10-08 create-FSHybridPLS.Rmd
split and normalize reinvented

@@
 
-## sample splitting
+## sample splitting and normalization
 
@@
 ```{r}
-#'Split Functional, Scalar, and Response Data
-#' @param data_fun_1 fd object (fda package). Functional predictor 1.
-#' @param data_fun_2 fd object (fda package). Functional predictor 2.
-#' @param data_scalar Matrix. Scalar predictors.
-#' @param response Vector. Response variable.
-#' @param train_idx Vector. Indices for train data.
-#' @return List containing split train and test sets.
-#' @export
-split.all <- function(data_fun_1, data_fun_2, data_scalar, response, train_idx) {
-  # --- Type Checks ---
+#' Split Hybrid Predictor and Response Data
+#'
+#' Splits the hybrid predictor object and the response vector into training and
+#' testing sets based on a given training ratio.
+#'
+#' @param W_hybrid predictor_hybrid object containing all functional and scalar data.
+#' @param response Vector. The response variable corresponding to the samples in W_hybrid.
+#' @param train_ratio Numeric scalar between 0 and 1 indicating the proportion of data to use for training.
+#' @return List containing split train and test sets for all components.
+#' @export
+split.all <- function(W_hybrid, response, train_ratio) {
+  # --- Type and Ratio Checks ---
   stopifnot(
-    # Functional data checks (assuming 'fd' class from the 'fda' package)
-    inherits(data_fun_1, "fd"),
-    inherits(data_fun_2, "fd"),
-
-    # Scalar predictor check
-    is.matrix(data_scalar),
-
-    # Response variable check
-    is.vector(response) || is.numeric(response) || is.factor(response),
-
-    # Training index check
-    is.vector(train_idx),
-    is.numeric(train_idx),
-    all(train_idx > 0), # Indices should be positive
-    all(train_idx == round(train_idx)) # Indices should be integers
-  )
-  # -------------------
-
-  return(list(
-    data_fun_1_train = data_fun_1[train_idx],
-    data_fun_1_test = data_fun_1[-train_idx],
-    data_fun_2_train = data_fun_2[train_idx],
-    data_fun_2_test = data_fun_2[-train_idx],
-    data_scalar_train = data_scalar[train_idx, , drop = FALSE],
-    data_scalar_test = data_scalar[-train_idx, , drop = FALSE],
-    response_train = response[train_idx],
-    response_test = response[-train_idx]
-  ))
-}
-```
-
-### normailize.all
-
-```{r}
-#' 
-#' @export
-normailize.all <- function(split.all_obj){
-  curve_normalize_result_1 <- curve_normalize_train_test_fd(
-    split.all_obj$data_fun_1_train,
-    split.all_obj$data_fun_1_test)
-  data_fun_1_train <- curve_normalize_result_1$train
-  data_fun_1_test <- curve_normalize_result_1$test
-
-  curve_normalize_result_2 <- curve_normalize_train_test_fd(
-    split.all_obj$data_fun_2_train,
-    split.all_obj$data_fun_2_test)
-  data_fun_2_train <- curve_normalize_result_2$train
-  data_fun_2_test <- curve_normalize_result_2$test
-
-  scalar_normalize_result <- scalar_normalize_train_test(
-    split.all_obj$data_scalar_train,
-    split.all_obj$data_scalar_test)
-  data_scalar_train <- scalar_normalize_result$train
-  data_scalar_test <- scalar_normalize_result$test
-
-  between_normalize_result <- btwn_normalize_train_test(
-    list(data_fun_1_train, data_fun_2_train),
-    data_scalar_train,
-    data_scalar_test
-  )
-  data_scalar_train <- between_normalize_result$train
-  data_scalar_test <- between_normalize_result$test
-
-  response_mean_train <-  mean(split.all_obj$response_train)
-  response_train <- split.all_obj$response_train - response_mean_train
-  response_test <- split.all_obj$response_test - response_mean_train
+    "'W_hybrid' must be a predictor_hybrid object" = inherits(W_hybrid, "predictor_hybrid"),
+    "'response' must be a vector" = is.vector(response),
+    "Response length must match hybrid sample size" = length(response) == W_hybrid$n_sample,
+    "'train_ratio' must be between 0 and 1" = is.numeric(train_ratio) && train_ratio > 0 && train_ratio < 1
+  )
+
+  N <- W_hybrid$n_sample
+  N_train <- floor(N * train_ratio)
+
+  # Generate random indices for training set
+  # Using 1:N ensures indices are always valid
+  train_idx <- sample(1:N, N_train)
+  test_idx <- (1:N)[-train_idx]
+
+  W_train <- predictor_hybrid(
+    W_hybrid$Z[train_idx, , drop = FALSE],
+    list(
+      W_hybrid$functional_list[[1]][train_idx],
+      W_hybrid$functional_list[[2]][train_idx]
+    )
+  )
+
+  W_test <- predictor_hybrid(
+    W_hybrid$Z[test_idx, , drop = FALSE],
+    list(
+      data_fun_1_test = W_hybrid$functional_list[[1]][test_idx],
+    data_fun_2_test = W_hybrid$functional_list[[2]][test_idx]
+    )
+  )
 
@@
     list(
-      data_fun_1_train = data_fun_1_train,
-      data_fun_2_train = data_fun_2_train,
-      data_scalar_train= data_scalar_train,
-      response_train   = response_train,
-      data_fun_1_test  = data_fun_1_test,
-      data_fun_2_test  = data_fun_2_test,
-      data_scalar_test = data_scalar_test,
-      response_test    = response_test
-    )
-  )
+    predictor_train = W_train,
+    predictor_test = W_test ,
+    response_train = response[train_idx],
+    response_test = response[test_idx]
+  ))
 }
@@
 #' @return A list containing:
-#'   \item{train}{The normalized training `predictor_hybrid` object.}
-#'   \item{test}{The normalized testing `predictor_hybrid` object.}
-#'   \item{deno_train}{A numeric vector of scaling factors used for each functional predictor.}
+#'   train: The normalized training `predictor_hybrid` object.}
+#'   test: The normalized testing `predictor_hybrid` object.}
+#'   deno_train: A numeric vector of scaling factors used for each functional predictor.}
 #' @export
@@
   deno_train <- numeric(train$n_functional)
+  mean_train <- list()
 
@@
   for (k in seq_len(train$n_functional)) { 
-
     # 1. Determine centering and scaling factors from the TRAINING data only
@@
     # Calculate the mean function for centering
-    mean_train <- fda::mean.fd(train_fd)
+    mean_train[[k]] <- fda::mean.fd(train_fd)
 
@@
       train_fd, # Use original train data
-      mean_train,
+      mean_train[[k]],
       deno_train[k]
@@
         test$functional_list[[k]], # Use original test data
-        mean_train, # Centered by training mean
+        mean_train[[k]], # Centered by training mean
         deno_train[k] # Scaled by training SD
@@
   }
-
   # Return the modified hybrid objects and the scaling factors
   return( list(
-    train = train_normalized,
-    test = test_normalized,
+    predictor_train = train_normalized,
+    predictor_test = test_normalized,
+    mean_train = mean_train,
     deno_train = deno_train
@@
     list(
-      train = predictor_train_normalized,
-      test = predictor_test_normalized
+      predictor_train = predictor_train_normalized,
+      predictor_test = predictor_test_normalized,
+      mean_train = mean_train,
+      sd_train = sd_train
     )
@@
     list(
-      train = train_normalized,
-      test = test_normalized
-    )
-  )
-}
-
-```
-
-```{r}
+      predictor_train = train_normalized,
+      predictor_test = test_normalized,
+      scaling_factor = scaling_factor
+    )
+  )
+}
+
+```
+
+### normailize.all
+
+```{r}
+#' 
+#' @export
+split_and_normailize.all <- function(W_hybrid, response, train_ratio){
+
+# $W_hybrid =  W_hybrid_mock
+#$ response
+
+# train_ratio = TRAIN_RATIO
+
+ # split.result <- split.all(W_hybrid, response, train_ratio)
+
+ #     predictor_train = W_train,
+ #   predictor_test = W_test ,
+ #   response_train = response[train_idx],
+ #   response_test = response[test_idx]
+
+ # list(
+ #   train = train_normalized,
+ #   test = test_normalized,
+ #   mean_train = mean_train,
+ #   deno_train = deno_train
+#  ))
+
+  curve_normalize_result <- curve_normalize_train_test(split.result$predictor_train, split.result$predictor_test)
+  scalar_normalize_result <- scalar_normalize_train_test(curve_normalize_result$predictor_train, curve_normalize_result$predictor_test)
+  btwn_normalize_result <- btwn_normalize_train_test(
+    scalar_normalize_result$predictor_train,
+    scalar_normalize_result$predictor_test
+  )
+
+  response_mean_train <-  mean(split.result$response_train)
+  response_sd_train <-  sd(split.result$response_train)
+  response_train <- (split.result$response_train - response_mean_train)/response_sd_train
+  response_test <- (split.result$response_test - response_mean_train)/response_sd_train
+  response_normalize_result = list(mean_train = response_mean_train, sd_train = response_sd_train)
+  return(
+    list(
+      predictor_train = btwn_normalize_result$predictor_train,
+      predictor_test = btwn_normalize_result$predictor_test,
+      response_train = response_train,
+      response_test = response_test,
+      curve_normalize_result = curve_normalize_result,
+      scalar_normalize_result = scalar_normalize_result,
+      btwn_normalize_result = btwn_normalize_result,
+      response_normalize_result = response_normalize_result
+    )
+  )
+}
+```
+
+```{r}
+N <- 30
+response <- c(1:N)
+TRAIN_RATIO <- 0.7
+create_mock_fd <- function(N_samples, seed) {
+  set.seed(seed)
+  mock_basis <- create.bspline.basis(rangeval = c(0, 1), nbasis = 5)
+  C <- matrix(rnorm(5 * N_samples, mean = 10), nrow = 5)
+  fd(C, mock_basis)
+}
+# 1. Setup Mock Hybrid Input
+W_hybrid_mock <- predictor_hybrid(
+  Z = matrix(1:(10*N), ncol = 10), # Simple sequential scalar data for verification
+  functional_list = list(
+    create_mock_fd(N, 1),
+    create_mock_fd(N, 2)
+  )
+)
+
+# 2. Split the data first
+split_obj <- split_and_normailize.all(W_hybrid_mock, response, TRAIN_RATIO)
+
+```
 
@@
 R6 class to split functional and scalar predictors into train and test sets and apply normalization techniques including curve normalization, scalar normalization, and between-functional-scalar normalization.
-```{r}
-#' @title Dataset Splitting and Normalization
+
+```{r}
+#'  Dataset Splitting and Normalization
 #' @description 

### 2025-10-08 create-FSHybridPLS.Rmd
hybrid predictor object now has eval_point

@@
 #' @export
-predictor_hybrid <- function(Z, functional_list) {
+predictor_hybrid <- function(Z, functional_list, eval_point) {
   stopifnot(is.matrix(Z), is.numeric(Z))
@@
       functional_list = functional_list,
+      eval_point = eval_point,
       gram_list = gram_list,
@@
 
-```{r}
-N <- 30
-response <- c(1:N)
-TRAIN_RATIO <- 0.7
-create_mock_fd <- function(N_samples, seed) {
-  set.seed(seed)
-  mock_basis <- create.bspline.basis(rangeval = c(0, 1), nbasis = 5)
-  C <- matrix(rnorm(5 * N_samples, mean = 10), nrow = 5)
-  fd(C, mock_basis)
-}
-# 1. Setup Mock Hybrid Input
-W_hybrid_mock <- predictor_hybrid(
-  Z = matrix(1:(10*N), ncol = 10), # Simple sequential scalar data for verification
-  functional_list = list(
-    create_mock_fd(N, 1),
-    create_mock_fd(N, 2)
-  )
-)
-
-# 2. Split the data first
-split_obj <- split_and_normailize.all(W_hybrid_mock, response, TRAIN_RATIO)
-
-```
-
-### DataSplitterNormalizer
-R6 class to split functional and scalar predictors into train and test sets and apply normalization techniques including curve normalization, scalar normalization, and between-functional-scalar normalization.
-
-```{r}
-#'  Dataset Splitting and Normalization
-#' @description 
-DataSplitterNormalizer <- R6::R6Class(
-  "DataSplitterNormalizer",
-
-  public = list(
-
-    data_original = NULL,  # Stores the original dataset
-    n_sample = NULL,  # Number of samples
-    train_ratio = NULL,  # Train-test split ratio
-    idx_train = NULL,  # Train indices
-    train=NULL,
-    test=NULL,
-
-    #' @title Initialize Data Splitter and Normalizer
-    #' @description Constructs the instance, splits the data into train and test sets.
-    #' Users must call `normalize_data()` separately.
-    #' @param data_original List. Contains `functional_predictors` (list of `fd` objects)
-    #' and `scalar_predictors` (matrix).
-    #' @param train_ratio Numeric. Ratio of data to use for training (e.g., 0.8).
-    #' @return An instance of `DataSplitterNormalizer`.
-    #' @export
-    initialize = function(data_original, train_ratio = 0.8) {
-      self$n_sample <- length(data_original$response)
-      self$train_ratio <- train_ratio
-      self$data_original <- data_original
-
-    },
-
-    #' @title Split Data into Train and Test Sets
-    #' @description Creates train/test indices and splits functional, scalar, and response variables.
-    #' @return None. Updates train and test variables.
-    #' @export
-    split_data = function(idx_train = NULL) {
-      # Use provided idx_train if available; otherwise, generate it
-      if (is.null(idx_train)) {
-        self$idx_train <- get_idx_train(self$n_sample, self$train_ratio)
-      } else {
-        self$idx_train <- idx_train
-      }
-
-      split_packed <- split.all(
-        self$data_original$functional_1,
-        self$data_original$functional_2,
-        self$data_original$scalar,
-        self$data_original$response,
-        self$idx_train
-      )
-
-      # Assign train/test sets
-      self$train <- list(
-        functional_1 = split_packed$data_fun_1_train,
-        functional_2 = split_packed$data_fun_2_train,
-        scalar = split_packed$data_scalar_train,
-        response = split_packed$response_train
-      )
-      self$test <- list(
-        functional_1 = split_packed$data_fun_1_test,
-        functional_2 = split_packed$data_fun_2_test,
-        scalar = split_packed$data_scalar_test,
-        response = split_packed$response_test
-      )
-
-    },
-
-    #' @title Normalize Train and Test Data
-    #' @description Applies curve, scalar, and between-functional-scalar normalization.
-    #' @return None. Updates train and test sets.
-    #' @export
-    normalize_data = function() {
-      # Initialize normalizers
-      normalizer_functional <- normalizer_functional_predictor$new()
-      normalizer_scalar <- normalizer_scalar_predictor$new()
-
-      # Normalize first functional predictor
-      normalizer_functional$normalize(self$train$functional_1, self$test$functional_1)
-      self$train$functional_1 <- normalizer_functional$get_normalized()$train_normalized
-      self$test$functional_1 <- normalizer_functional$get_normalized()$test_normalized
-
-      # Normalize second functional predictor
-      normalizer_functional$normalize(self$train$functional_2, self$test$functional_2)
-      self$train$functional_2 <- normalizer_functional$get_normalized()$train_normalized
-      self$test$functional_2 <- normalizer_functional$get_normalized()$test_normalized
-
-      # Normalize scalar predictors
-      normalizer_scalar$normalize(self$train$scalar, self$test$scalar)
-      self$train$scalar <- normalizer_scalar$get_normalized()$train_normalized
-      self$test$scalar<- normalizer_scalar$get_normalized()$test_normalized
-
-      # Apply between-functional-scalar normalization
-      self$normalize_between()
-
-      # Normalize response variable
-      self$normalize_response()
-    },
-
-    #' @title Normalize Between Functional and Scalar Predictors
-    #' @description Scales scalar predictors to ensure comparability with functional predictors.
-    #' @export
-    normalize_between = function() {
-      omega <- sum(diag(inprod(self$train$functional_1, self$train$functional_1))) +
-        sum(diag(inprod(self$train$functional_2, self$train$functional_2)))
-
-      omega <- omega / sum(self$train$scalar^2)
-
-      self$train$scalar <- sqrt(omega) * self$train$scalar
-      self$test$scalar <- sqrt(omega) * self$test$scalar
-    },
-
-    #' @title Normalize Response Variable
-    #' @description Centers response variable based on training mean.
-    #' @export
-    normalize_response = function() {
-      response_mean_train <- mean(self$train$response)
-      self$train$response <- self$train$response - response_mean_train
-      self$test$response <- self$test$response - response_mean_train
-    } #must not end with ,
-
-  )
-)
-
-```
-
 # Baseline method: FPCA regression
 
-functions in MFPCA packages use an internal function calcBasisIntegrals. Somehow, this function did not work well on our simulations setting. Thus we modify the codes 
-```{r}
-
-# define global variable j, used by the foreach package and confusing R CMD CHECK
-globalVariables('j')
-
-#' Utility function that calculates matrix of basis-scalar products (one dimension)
-#'
-#' If the element \eqn{X^{(j)}}{X^{(j)}} is expanded in basis functions \eqn{b_i^{(j)}(t),~ i = 1, \ldots, K_j}{b_i(t)},
-#' this function calculates the \eqn{K_j \times K_j}{K_j  \times K_j} matrix \eqn{B^{(jj)}}{B^{(jj)}} with entries
-#' \deqn{B^{(jj)}_{mn} = \int_{\mathcal{T_j}} b_m^{(j)}(t) b_n^{(j)}(t) \mathrm{d} t}.
-#'
-#' @section Warning: This function is implemented only for functions on one- or two-dimensional domains.
-#'
-#' @param basisFunctions Array of \code{npc} basis functions of dimensions \code{npc x M1} or \code{npc x M1 x M2}.
-#' @param dimSupp dimension of the support of the basis functions (1 or 2)
-#' @param argvals List of corresponding x-values.
-#'
-#' @return A matrix containing the scalar product of all combinations of basis functions (matrix \eqn{B^{(j)}})
-#'
-#' @seealso \code{\link{MFPCA}}, \code{\link[funData]{dimSupp}}
-#'
-#' @keywords internal
-calcBasisIntegrals <- function(basisFunctions, dimSupp, argvals)
-{
-  npc <- dim(basisFunctions)[1]
-
-  #  integral basis matrix
-  B <- array(0, dim = c(npc, npc))
-
-  if(dimSupp == 1) # one-dimensional domain
-  {
-    w <- funData::.intWeights(argvals[[1]])
-
-    for(m in seq_len(npc))
-    {
-      for(n in seq_len(m))
-        B[m, n] <- B[n, m] <- (basisFunctions[m, ]* basisFunctions[n, ])%*%w
-    }
-  }
-  else # two-dimesional domain (otherwise function stops before!)
-  {
-    w1 <- t(funData::.intWeights(argvals[[1]]))
-    w2 <- funData::.intWeights(argvals[[2]])
-
-    for(m in seq_len(npc))
-    {
-      for(n in seq_len(m))
-        B[m, n] <- B[n, m] <-  w1 %*%(basisFunctions[m, , ]* basisFunctions[n, ,])%*%w2
-    }
-  }
-
-  return(B)
-}
-```
-
-###   Multivariate functional principal component analysis for functions on different (dimensional) domains
-
-- This function calculates a multivariate functional principal component analysis (MFPCA) based on i.i.d.
-observations $x_1, \ldots, x_N$ of a multivariate functional data-generating process $X = (X^{(1)}, \ldots  X^{(p)})}{X = X^(1), \ldots, X^(p)$ with elements $X^{(j)} \in L^2(\mathcal{T}_j)}{X^(j) in L^2(calT_j)$ defined on a domain $\mathcal{T}_j \subset IR^{d_j}}{calT_j of IR^{d_j}$.
-- In particular, the elements can be defined on different (dimensional) domains.
-- The results contain the mean function, the estimated multivariate functional principal components \eqn{\hat \psi_1, \ldots, \hat \psi_M} (having the same structure as $x_i$), the associated eigenvalues $\hat \nu_1 \geq \ldots \geq \hat \nu_M > 0$ and the individual scores \eqn{\hat \rho_{im} = \widehat{<x_i, \psi_m>}}{\hat \rho_{im} = \hat{<x_i, \psi_m>}}.
-
-- Univariate Expansions
-    - The multivariate functional principal component analysis relies on a univariate basis expansion for each element $X^{(j)}$.
-    - The univariate basis representation is calculated using the univDecomp function, that passes the univariate functional observations and optional parameters to the specific function.
-    - The univariate decompositions are specified via the uniExpansions argument in the MFPCA function.
-    - It is a list of the same length as the mFData object, i.e. having one entry for each element of the multivariate functional data.
-    - For each element, uniExpansion must specify at least the type of basis functions to use.
-    - Additionally, one may add further parameters.
-    - The following basis representations are supported: \itemize{
-        -  Given basis functions.
-Then \code{uniExpansions[[j]] = list(type = "given", functions)}, where \code{functions} is a \code{funData} object on the same domain as \code{mFData}, containing the given basis functions.
-        - Univariate functional principal component analysis.
-Then \code{uniExpansions[[j]] = list(type = "uFPCA", nbasis, pve, npc, makePD)}, where \code{nbasis,pve,npc,makePD} are parameters passed to the \code{\link{PACE}} function for calculating the univariate functional principal component analysis.
-        - Basis functions expansions from the
-  package \pkg{fda}. Then \code{uniExpansions[[j]] = list(type = "fda", ...)},
-#' where \code{...} are passed to \code{\link[funData]{funData2fd}}, which
-#' heavily builds on \code{\link[fda]{eval.fd}}. If \pkg{fda} is not available,
-#' a warning is thrown.
-\item Spline basis functions (not penalized). Then
-#' \code{uniExpansions[[j]] = list(type = "splines1D", bs, m, k)}, where
-#' \code{bs,m,k} are passed to the functions \code{\link{univDecomp}} and
-#' \code{\link{univExpansion}}. For two-dimensional tensor product splines, use
-#' \code{type = "splines2D"}. 
-\item Spline basis functions (with smoothness
-#' penalty). Then \code{uniExpansions[[j]] = list(type = "splines1Dpen", bs, m,
-#' k)}, where \code{bs,m,k} are passed to the functions \code{\link{univDecomp}}
-#' and \code{\link{univExpansion}}. Analogously to the unpenalized case, use
-#' \code{type = "splines2Dpen"} for 2D penalized tensor product splines. 
-\item
-#' Cosine basis functions. Use \code{uniExpansions[[j]] = list(type = "DCT2D",
-#' qThresh, parallel)} for functions one two-dimensional domains (images) and
-#' \code{type = "DCT3D"} for 3D images. The calculation is based on the discrete
-#' cosine transform (DCT) implemented in the C-library \code{fftw3}. If this
-#' library is not available, the function will throw  a warning. \code{qThresh}
-#' gives the quantile for hard thresholding the basis coefficients based on
-#' their absolute value. If \code{parallel = TRUE}, the coefficients for
-#' different images are calculated in parallel.} See \code{\link{univDecomp}}
-#' and \code{\link{univExpansion}} for details.}
+## Modified MFPCA Function for Simultaneous Training and Prediction
+
+The MFPCA (Multivariate Functional Principal Component Analysis) function computes multivariate functional PCA for functions defined across different (dimensional) domains.
+We have modified the original implementation to admit a new input, **`mFData_predict`**, allowing the function to calculate PCA scores for **both the training data and new test (or validation) data simultaneously** in a single run.
+This change was necessary because the standard `predict.MFPCAfit` function does not permit computing scores for new, out-of-sample functions.
+The multivariate functional principal component analysis inherently relies on a **univariate basis expansion** for each functional element ($X^{(j)}$).
+To simplify the code modification, we use only the univariate functional PCA option and have removed other options provided by the original MFPCA function.
+We modifies the main function and two internal functions.
+
+### MFPCA
 
@@
 
-########### modified by Jongmin Mun #############################
+########### Below is modified by Jongmin Mun #############################
   # calculate univariate basis expansion for all components
@@
     )
-########### modified by Jongmin Mun #############################
+########### Above is modified by Jongmin Mun #############################
 
@@
 
+### fpcaBasis
+
+```{r}
+################# modified by Jongmin Mun #####################
+fpcaBasis <- function(funDataObject, funDataObject_predict, nbasis = 10, pve = 0.99, npc = NULL, makePD = FALSE, cov.weight.type = "none")
+{
+  FPCA <- PACE(funDataObject, predData = NULL, nbasis, pve, npc, makePD, cov.weight.type)
+  FPCA_pred <- PACE(funDataObject = funDataObject, predData = funDataObject_predict, nbasis, pve, npc, makePD, cov.weight.type)
+  return(list(scores = FPCA$scores,
+              scores.pred = FPCA_pred$scores,
+              ortho = TRUE,
+              functions = FPCA$functions,
+              meanFunction = FPCA$mu
+  ))
+}
+```
+
+### univDecomp
+```{r}
+univDecomp <- function(type, funDataObject, funDataObject_predict, ...)
+{
+  # Parameter checking
+  if(is.null(type))
+    stop("Parameter 'type' is missing.")
+  else
+  {
+    if(!is.character(type))
+      stop("Parameter 'type' must be a character string. See ?univDecomp for details.")
+  }
+
+  if(class(funDataObject) != "funData")
+    stop("Parameter 'funDataObject' must be a funData object.")
+
+  # get all arguments (except for function call and type)
+  params <- list(...)
+
+  # check if type and data are of correct type
+  if(is.null(type))
+    stop("univDecomp: must specify 'type'.")
+
+  if(!inherits(type, "character"))
+    stop("univDecomp: 'type' must be of class character.")
+
+  if(is.null(funDataObject))
+    stop("univDecomp: must specify 'funDataObject'.")
+
+  if(class(funDataObject) != "funData")
+    stop("univDecomp: 'funDataObject' must be of class funData.")
+
+  params$funDataObject <- funDataObject # add funDataObject (-> make sure is evaluated in correct env.)
+
+  ############### modified by Jongmin Mun ######################
+  if (type == "uFPCA"){params$funDataObject_predict <- funDataObject_predict}
+  ############### modified by Jongmin Mun ######################
+
+  res <- switch(type,
+                "given" = do.call(givenBasis, params),
+                "uFPCA" = do.call(fpcaBasis, params),
+                "UMPCA" = do.call(umpcaBasis, params),
+                "FCP_TPA" = do.call(fcptpaBasis, params),
+                "splines1D" = do.call(splineBasis1D, params),
+                "splines1Dpen" = do.call(splineBasis1Dpen, params),
+                "splines2D" = do.call(splineBasis2D, params),
+                "splines2Dpen" = do.call(splineBasis2Dpen, params),
+                "fda" = do.call(fdaBasis, params),
+                "DCT2D" = do.call(dctBasis2D, params),
+                "DCT3D" = do.call(dctBasis3D, params),
+                stop("Univariate Decomposition for 'type' = ", type, " not defined!")
+  )
+
+  if(res$ortho == FALSE & is.null(res$B))
+    stop("UnivDecomp: must provide integral matrix B for non-orthonormal basis functions.")
+
+  return(res)
+}
+```
+
+## Unmodified functions
+
+### calcBasisIntegrals
+```{r}
+
+# define global variable j, used by the foreach package and confusing R CMD CHECK
+globalVariables('j')
+
+#' Utility function that calculates matrix of basis-scalar products (one dimension)
+#'
+#' If the element \eqn{X^{(j)}}{X^{(j)}} is expanded in basis functions \eqn{b_i^{(j)}(t),~ i = 1, \ldots, K_j}{b_i(t)},
+#' this function calculates the \eqn{K_j \times K_j}{K_j  \times K_j} matrix \eqn{B^{(jj)}}{B^{(jj)}} with entries
+#' \deqn{B^{(jj)}_{mn} = \int_{\mathcal{T_j}} b_m^{(j)}(t) b_n^{(j)}(t) \mathrm{d} t}.
+#'
+#' @section Warning: This function is implemented only for functions on one- or two-dimensional domains.
+#'
+#' @param basisFunctions Array of \code{npc} basis functions of dimensions \code{npc x M1} or \code{npc x M1 x M2}.
+#' @param dimSupp dimension of the support of the basis functions (1 or 2)
+#' @param argvals List of corresponding x-values.
+#'
+#' @return A matrix containing the scalar product of all combinations of basis functions (matrix \eqn{B^{(j)}})
+#'
+#' @seealso \code{\link{MFPCA}}, \code{\link[funData]{dimSupp}}
+#'
+#' @keywords internal
+calcBasisIntegrals <- function(basisFunctions, dimSupp, argvals)
+{
+  npc <- dim(basisFunctions)[1]
+
+  #  integral basis matrix
+  B <- array(0, dim = c(npc, npc))
+
+  if(dimSupp == 1) # one-dimensional domain
+  {
+    w <- funData::.intWeights(argvals[[1]])
+
+    for(m in seq_len(npc))
+    {
+      for(n in seq_len(m))
+        B[m, n] <- B[n, m] <- (basisFunctions[m, ]* basisFunctions[n, ])%*%w
+    }
+  }
+  else # two-dimesional domain (otherwise function stops before!)
+  {
+    w1 <- t(funData::.intWeights(argvals[[1]]))
+    w2 <- funData::.intWeights(argvals[[2]])
+
+    for(m in seq_len(npc))
+    {
+      for(n in seq_len(m))
+        B[m, n] <- B[n, m] <-  w1 %*%(basisFunctions[m, , ]* basisFunctions[n, ,])%*%w2
+    }
+  }
+
+  return(B)
+}
+```
+
 ### calcMFPCA
@@
 
+### .PACE
+
+```{r}
+.PACE <- function(X, Y, Y.pred = NULL, nbasis = 10, pve = 0.99, npc = NULL, makePD = FALSE, cov.weight.type = "none")
+{
+  if (is.null(Y.pred))
+    Y.pred = Y
+  D = NCOL(Y)
+  if(D != length(X)) # check if number of observation points in X & Y are identical
+    stop("different number of (potential) observation points differs in X and Y!")
+  I = NROW(Y)
+  I.pred = NROW(Y.pred)
+  d.vec = rep(X, each = I) # use given X-values for estimation of mu
+  gam0 = mgcv::gam(as.vector(Y) ~ s(d.vec, k = nbasis))
+  mu = mgcv::predict.gam(gam0, newdata = data.frame(d.vec = X))
+  Y.tilde = Y - matrix(mu, I, D, byrow = TRUE)
+  cov.sum = cov.count = cov.mean = matrix(0, D, D)
+  for (i in seq_len(I)) {
+    obs.points = which(!is.na(Y[i, ]))
+    cov.count[obs.points, obs.points] = cov.count[obs.points, obs.points] + 1
+    cov.sum[obs.points, obs.points] = cov.sum[obs.points, obs.points] + tcrossprod(Y.tilde[i, obs.points])
+  }
+  G.0 = ifelse(cov.count == 0, NA, cov.sum/cov.count)
+  diag.G0 = diag(G.0)
+  diag(G.0) = NA
+  row.vec = rep(X, each = D) # use given X-values
+  col.vec = rep(X, D) # use given X-values
+  cov.weights <- switch(cov.weight.type,
+                        none = rep(1, D^2),
+                        counts = as.vector(cov.count),
+                        stop("cov.weight.type ", cov.weight.type, " unknown in smooth covariance estimation"))
+
+  npc.0 = matrix(mgcv::predict.gam(mgcv::gam(as.vector(G.0)~te(row.vec, col.vec, k = nbasis), weights = cov.weights),
+                                   newdata = data.frame(row.vec = row.vec, col.vec = col.vec)), D, D)
+  npc.0 = (npc.0 + t(npc.0))/2
+  # no extra-option (useSymm) as in fpca.sc-method
+  if (makePD) { # see fpca.sc
+    npc.0 <- {
+      tmp <- Matrix::nearPD(npc.0, corr = FALSE, keepDiag = FALSE,
+                            do2eigen = TRUE, trace = options()$verbose)
+      as.matrix(tmp$mat)
+    }
+  }
+
+  ### numerical integration for calculation of eigenvalues (see Ramsay & Silverman, Chapter 8)
+  w <- funData::.intWeights(X, method = "trapezoidal")
+  Wsqrt <- diag(sqrt(w))
+  Winvsqrt <- diag(1/(sqrt(w)))
+  V <- Wsqrt %*% npc.0 %*% Wsqrt
+  evalues = eigen(V, symmetric = TRUE, only.values = TRUE)$values
+  ###
+  evalues = replace(evalues, which(evalues <= 0), 0)
+  npc = ifelse(is.null(npc), min(which(cumsum(evalues)/sum(evalues) > pve)), npc)
+  efunctions = matrix(Winvsqrt%*%eigen(V, symmetric = TRUE)$vectors[, seq(len = npc)], nrow = D, ncol = npc)
+  evalues = eigen(V, symmetric = TRUE, only.values = TRUE)$values[seq_len(npc)]  # use correct matrix for eigenvalue problem
+  cov.hat = efunctions %*% tcrossprod(diag(evalues, nrow = npc, ncol = npc), efunctions)
+  ### numerical integration for estimation of sigma2
+  T.len <- X[D] - X[1] # total interval length
+  T1.min <- min(which(X >= X[1] + 0.25*T.len)) # left bound of narrower interval T1
+  T1.max <- max(which(X <= X[D] - 0.25*T.len)) # right bound of narrower interval T1
+  DIAG = (diag.G0 - diag(cov.hat))[T1.min :T1.max] # function values
+  # weights
+  w <- funData::.intWeights(X[T1.min:T1.max], method = "trapezoidal")
+  sigma2 <- max(1/(X[T1.max]-X[T1.min]) * sum(DIAG*w, na.rm = TRUE), 0) #max(1/T.len * sum(DIAG*w), 0)
+  ####
+  D.inv = diag(1/evalues, nrow = npc, ncol = npc)
+  Z = efunctions
+  Y.tilde = Y.pred - matrix(mu, I.pred, D, byrow = TRUE)
+  fit = matrix(0, nrow = I.pred, ncol = D)
+  scores = matrix(NA, nrow = I.pred, ncol = npc)
+  # no calculation of confidence bands, no variance matrix
+  for (i.subj in seq_len(I.pred)) {
+    obs.points = which(!is.na(Y.pred[i.subj, ]))
+    if (sigma2 == 0 & length(obs.points) < npc) {
+      stop("Measurement error estimated to be zero and there are fewer observed points than PCs; scores cannot be estimated.")
+    }
+    Zcur = matrix(Z[obs.points, ], nrow = length(obs.points),
+                  ncol = dim(Z)[2])
+    ZtZ_sD.inv = solve(crossprod(Zcur) + sigma2 * D.inv)
+    scores[i.subj, ] = ZtZ_sD.inv %*% crossprod(Zcur, Y.tilde[i.subj, obs.points])
+    fit[i.subj, ] = t(as.matrix(mu)) + tcrossprod(scores[i.subj, ], efunctions)
+  }
+  ret.objects = c("fit", "scores", "mu", "efunctions", "evalues",
+                  "npc", "sigma2") # add sigma2 to output
+  ret = lapply(seq_len(length(ret.objects)), function(u) get(ret.objects[u]))
+  names(ret) = ret.objects
+  ret$estVar <- diag(cov.hat)
+  return(ret)
+}
+```
+
+### PACE
+
+```{r}
+PACE <- function(funDataObject, predData = NULL, nbasis = 10, pve = 0.99, npc = NULL, makePD = FALSE, cov.weight.type = "none")
+{
+  # check inputs
+  if(! class(funDataObject) %in% c("funData", "irregFunData"))
+    stop("Parameter 'funDataObject' must be a funData or irregFunData object.")
+  if(dimSupp(funDataObject) != 1)
+    stop("PACE: Implemented only for funData objects with one-dimensional support.")
+  if(methods::is(funDataObject, "irregFunData")) # for irregular functional data, use funData representation
+    funDataObject <- as.funData(funDataObject)
+
+  if(is.null(predData))
+    Y.pred = NULL # use only funDataObject
+  else
+  {
+    if(!isTRUE(all.equal(funDataObject@argvals, predData@argvals)))
+      stop("PACE: funDataObject and predData must be defined on the same domains!")
+
+    Y.pred = predData@X
+  }
+
+  if(!all(is.numeric(nbasis), length(nbasis) == 1, nbasis > 0))
+    stop("Parameter 'nbasis' must be passed as a number > 0.")
+
+  if(!all(is.numeric(pve), length(pve) == 1, 0 <= pve, pve <= 1))
+    stop("Parameter 'pve' must be passed as a number between 0 and 1.")
+
+  if(!is.null(npc) & !all(is.numeric(npc), length(npc) == 1, npc > 0))
+    stop("Parameter 'npc' must be either NULL or passed as a number > 0.")
+
+  if(!is.logical(makePD))
+    stop("Parameter 'makePD' must be passed as a logical.")
+
+  if(!is.character(cov.weight.type))
+    stop("Parameter 'cov.weight.type' must be passed as a character.")
+
+  res <- .PACE(X = funDataObject@argvals[[1]],
+               Y = funDataObject@X,
+               Y.pred = Y.pred,
+               nbasis = nbasis, pve = pve, npc = npc, makePD = makePD,
+               cov.weight.type = cov.weight.type)
+
+  return(list(mu = funData(funDataObject@argvals, matrix(res$mu, nrow = 1)),
+              values = res$evalues,
+              functions = funData(funDataObject@argvals, t(res$efunctions)),
+              scores = res$scores,
+              scores.pred = res$scores.pred,
+              fit = funData(funDataObject@argvals, res$fit),
+              npc = res$npc,
+              sigma2 = res$sigma2,
+              estVar = funData(funDataObject@argvals, matrix(res$estVar, nrow = 1))
+  ))
+}
+```
+
+### expandBasisFunction
+
+```{r}
+expandBasisFunction <- function(scores, argvals = functions@argvals, functions)
+{
+  if(dim(scores)[2] != nObs(functions))
+    stop("expandBasisFunction: number of scores for each observation and number of eigenfunctions does not match.")
+
+  # collapse higher-dimensional functions, multiply with scores and resize the result
+  d <- dim(functions@X)
+  nd <- length(d)
+
+  if(nd == 2)
+    resX <- scores %*% functions@X
+
+  if(nd == 3)
+  {
+    resX <- array(NA, dim = c(dim(scores)[1], d[-1]))
+
+    for(i in seq_len(d[2]))
+      resX[,i,] <- scores %*% functions@X[,i,]
+  }
+
+  if(nd == 4)
+  {
+    resX <- array(NA, dim = c(dim(scores)[1], d[-1]))
+
+    for(i in seq_len(d[2]))
+      for(j in seq_len(d[3]))
+          resX[,i,j,] <- scores %*% functions@X[,i,j,]
+  }
+
+  if(nd > 4) # slow solution due to aperm
+  {
+    resX <- aperm(plyr::aaply(.data = functions@X, .margins = 3:nd, 
+                        .fun = function(x,y){y %*% x}, y = scores), 
+                  c(nd-1,nd, seq_len((nd-2))))
+    dimnames(resX) <- NULL
+  }
+
+  return( funData(argvals, resX) )
+}
+```
+
+### univExpansion
+
+```{r}
+univExpansion <- function(type, scores, argvals = ifelse(!is.null(functions), functions@argvals, NULL), functions, params = NULL)
+{
+  # Parameter checking
+  if(is.null(type))
+    stop("Parameter 'type' is missing.")
+  else
+ {
+   if(!is.character(type))
+     stop("Parameter 'type' must be a character string. See ?univExpansion for details.")
+ }
+
+  if(is.null(scores))
+    stop("Parameter 'scores' is missing.")
+  else
+    {
+      if(!is.matrix(scores))
+      stop("Parameter 'scores' must be passed as a matrix.")
+    }
+
+  if(is.numeric(argvals))
+  {
+    argvals <- list(argvals)
+    warning("Parameter 'argvals' was passed as a vector and transformed to a list.")
+  }
+
+  if(is.null(functions))
+  {
+    if(is.null(argvals))
+      stop("Must pass 'argvals' if 'functions' is NULL.")
+    else
+      {
+        if(!is.list(argvals)) 
+          stop("Parameter 'argvals' must be passed as a list.")
+      }
+  }
+  else
+  {
+    if(class(functions) != "funData")
+      stop("Parameter 'functions' must be a funData object.")
+
+    # check interaction with other parameters
+    if(nObs(functions) != NCOL(scores))
+      stop("Number of scores per curve does not match the number of basis functions.")
+
+    if(!is.null(argvals) & !isTRUE(all.equal(argvals, functions@argvals)))
+      stop("The parameter 'argvals' does not match the argument values of 'functions'.")
+  }
+
+  if(!is.null(params) & !is.list(params))
+    stop("The parameter 'params' must be passed as a list.")
+
+  # start calculations
+  params$scores <- scores
+  params$functions <- functions
+
+  if(is.numeric(argvals))
+    argvals <- list(argvals)
+
+  params$argvals <- argvals
+
+  res <- switch(type,
+                "given" = do.call(expandBasisFunction, params),
+                "uFPCA" = do.call(expandBasisFunction, params),
+                "UMPCA" = do.call(expandBasisFunction, params),
+                "FCP_TPA" = do.call(expandBasisFunction, params),
+                "splines1D" = do.call(splineFunction1D, params),
+                "splines1Dpen" = do.call(splineFunction1D, params),
+                "splines2D" = do.call(splineFunction2D, params),
+                "splines2Dpen" = do.call(splineFunction2Dpen, params),
+                "fda" = do.call(expandBasisFunction, params),
+                "DCT2D" = do.call(dctFunction2D, params),
+                "DCT3D" = do.call(dctFunction3D, params),
+                "default" = do.call(expandBasisFunction, params),
+                stop("Univariate Expansion for 'type' = ", type, " not defined!")
+  )
+
+  return(res)
+}
+```
+
+## end-to-end MFPCA regression method
+
+```{r}
+# --- 1. MAIN FUNCTION: fit.mfpca_regression ---
+
+#' End-to-End MFPCA Regression Pipeline
+#'
+#' Performs sample splitting, normalization, cross-validation (CV) to select
+#' optimal functional (FPC) and scalar (SPC) components, linear regression fitting,
+#' and test set prediction.
+#'
+#' @param W predictor_hybrid object containing all predictors.
+#' @param y Vector. Response variable.
+#' @param train_ratio Numeric scalar between 0 and 1 for splitting data (default 0.7).
+#' @param n_fold Integer. Number of folds for cross-validation (default 5).
+#' @param n_fpc_max Integer. Max number of FPCs to consider in CV (default 10).
+#' @param n_spc_max Integer. Max number of SPCs to consider in CV (default 5).
+#' @return List containing the final model fit, optimal parameters, and test MSE.
+#' @export
+fit.mfpca_regression <- function(W, y, train_ratio = 0.7, n_fold = 5, n_fpc_max = 10, n_spc_max = 5) {
+
+  # --- 0. Setup and Initial Checks ---
+  stopifnot(inherits(W, "predictor_hybrid"))
+
+  # Standard parameters
+  eval_point <- seq(0, 1, length.out = 100)
+
+  uniExpansions <- list(
+    list(type = "uFPCA", nbasis = 10, npc = n_fpc_max), 
+    list(type = "uFPCA", nbasis = 10, npc = n_fpc_max)
+  )
+
+  # Adjust max components
+  n_scalar <- W$n_scalar
+  if (n_spc_max > n_scalar) n_spc_max <- n_scalar
+
+  # --- 1. Split and Normalize Full Data ---
+
+  split_obj <- split.hybrid(W, y, train_ratio)
+  split_obj_normalized <- normailize.all(split_obj)
+
+  # Extract components
+  y_train_norm <- split_obj_normalized$response_train
+  Z_train_norm <- split_obj_normalized$data_scalar_train
+  f1_train_norm <- split_obj_normalized$data_fun_1_train
+  f2_train_norm <- split_obj_normalized$data_fun_2_train
+  N_train <- length(y_train_norm)
+
+  # --- 2. Cross-Validation Setup ---
+
+  cv_mat <- matrix(Inf, nrow = n_fpc_max, ncol = n_spc_max) 
+  kfold_idx <- create_idx_kfold(N_train, n_fold)
+
+  # --- 3. Cross-Validation Loop (Find Best n_fpc, n_spc) ---
+
+  for (fold_num in 1:n_fold) {
+    valid_idx <- kfold_idx[[fold_num]]
+    train_idx_cv <- (1:N_train)[-valid_idx]
+
+    # 3a. Prepare CV training and validation sets
+    f1_train_cv <- f1_train_norm[train_idx_cv]
+    f2_train_cv <- f2_train_norm[train_idx_cv]
+    f1_valid_cv <- f1_train_norm[valid_idx]
+    f2_valid_cv <- f2_train_norm[valid_idx]
+
+    # Format functional data
+    predictor_cv_train <- multiFunData(
+      fd2funData(f1_train_cv, eval_point),
+      fd2funData(f2_train_cv, eval_point)
+    )
+    predictor_cv_valid <- multiFunData(
+      fd2funData(f1_valid_cv, eval_point),
+      fd2funData(f2_valid_cv, eval_point)
+    )
+
+    Z_train_cv <- Z_train_norm[train_idx_cv, , drop = FALSE]
+    Z_valid_cv <- Z_train_norm[valid_idx, , drop = FALSE]
+    y_train_cv <- y_train_norm[train_idx_cv]
+    y_valid_cv <- y_train_norm[valid_idx]
+
+    # 3b. Fit PCA Models on CV Training Data
+    MFPCA_fit_cv <- MFPCA(mFData = predictor_cv_train, mFData_predict = predictor_cv_valid, 
+                          M = n_fpc_max, uniExpansions = uniExpansions)
+    PCA_fit_cv <- prcomp(Z_train_cv, center = FALSE, scale = FALSE)
+
+    FPC_scores_train_cv <- MFPCA_fit_cv$scores
+    FPC_scores_valid_cv <- MFPCA_fit_cv$scores.pred
+    PC_scores_train_cv <- PCA_fit_cv$x
+    PC_scores_valid_cv <- predict(PCA_fit_cv, Z_valid_cv)
+
+    # 3c. Inner Parameter Loop (Fit and Validate)
+    for (n_fpc in 1:n_fpc_max) {
+      for (n_spc in 1:n_spc_max) {
+
+        # Select components
+        FPC_train_select <- FPC_scores_train_cv[, 1:n_fpc, drop = FALSE]
+        FPC_valid_select <- FPC_scores_valid_cv[, 1:n_fpc, drop = FALSE]
+        PC_train_select <- PC_scores_train_cv[, 1:n_spc, drop = FALSE]
+        PC_valid_select <- PC_scores_valid_cv[, 1:n_spc, drop = FALSE]
+
+        # Combine selected scores for linear model
+        train_data_lm <- data.frame(response = y_train_cv, FPC_train_select, PC_train_select)
+        valid_data_lm <- data.frame(FPC_valid_select, PC_valid_select)
+
+        # Fit Linear Regression Model
+        linear_fit_cv <- lm(response ~ ., data = train_data_lm)
+
+        # Predict, Calculate MSE, and Accumulate
+        y_pred_valid <- predict(linear_fit_cv, valid_data_lm)
+        cv_mat[n_fpc, n_spc] <- cv_mat[n_fpc, n_spc] + mean((y_pred_valid - y_valid_cv)^2)
+      }
+    }
+  }
+
+  # 4. Select Optimal Parameters
+  min_idx <- arrayInd(which.min(cv_mat), dim(cv_mat))
+  n_fpc_best <- min_idx[1]
+  n_spc_best <- min_idx[2]
+
+  # --- 5. Final Model Training and Prediction (Full Training Set) ---
+
+  # Extract final components
+  Z_test_norm <- split_obj_normalized$data_scalar_test
+  f1_test_norm <- split_obj_normalized$data_fun_1_test
+  f2_test_norm <- split_obj_normalized$data_fun_2_test
+  y_test_norm <- split_obj_normalized$response_test
+
+  # Prepare final functional data
+  predictor_final_train <- multiFunData(fd2funData(f1_train_norm, eval_point), fd2funData(f2_train_norm, eval_point))
+  predictor_final_test <- multiFunData(fd2funData(f1_test_norm, eval_point), fd2funData(f2_test_norm, eval_point))
+
+  # Fit final PCA models
+  MFPCA_fit_final <- MFPCA(mFData = predictor_final_train, mFData_predict = predictor_final_test, 
+                          M = n_fpc_best, uniExpansions = uniExpansions)
+  PCA_fit_final <- prcomp(Z_train_norm, center = FALSE, scale = FALSE)
+
+  # Extract and combine final scores
+  FPC_train_final <- MFPCA_fit_final$scores
+  FPC_test_final <- MFPCA_fit_final$scores.pred
+  PC_train_final <- PCA_fit_final$x[, 1:n_spc_best, drop = FALSE]
+  PC_test_final <- predict(PCA_fit_final, Z_test_norm)[, 1:n_spc_best, drop = FALSE]
+
+  train_data_final_lm <- data.frame(response = y_train_norm, FPC_train_final, PC_train_final)
+  test_data_final_lm <- data.frame(FPC_test_final, PC_test_final)
+
+  # Fit Final Linear Model
+  final_linear_fit <- lm(response ~ ., data = train_data_final_lm)
+
+  # Predict and Evaluate
+  y_pred_test <- predict(final_linear_fit, test_data_final_lm)
+  final_test_rmse <- sqrt(mean((y_pred_test - y_test_norm)^2))
+
+  # --- 6. Return Results ---
+  return(list(
+    n_fpc_best = n_fpc_best,
+    n_spc_best = n_spc_best,
+    test_rmse = final_test_rmse,
+    final_model = final_linear_fit,
+    regression_coefficients = coef(final_linear_fit)
+  ))
+}
+```
+
 ```{r}
@@
 library(refund)
-eval_point<-seq(1, 100, length.out = 100)
+eval_point<-seq(1, 100, length.out = 100)/100
 n_iter_max = 40
@@
 library(funData)
+f1 = fd2funData(create_mock_fd(N, 1), eval_point)
+f2 = fd2funData(create_mock_fd(N, 2), eval_point)
 uniExpansions <- list(
@@
 ```{r}
+N <- 30
+response <- c(1:N)
+TRAIN_RATIO <- 0.7
+create_mock_fd <- function(N_samples, seed) {
+  set.seed(seed)
+  mock_basis <- create.bspline.basis(rangeval = c(0, 1), nbasis = 20)
+  C <- matrix(rnorm(20 * N_samples, mean = 10), nrow = 20)
+  fd(C, mock_basis)
+}
+# 1. Setup Mock Hybrid Input
+W_hybrid_mock <- predictor_hybrid(
+  Z = matrix(1:(10*N), ncol = 10), # Simple sequential scalar data for verification
+  functional_list = list(
+    create_mock_fd(N, 1),
+    create_mock_fd(N, 2)
+  )
+)
+
+# 2. Split the data first
+split_obj <- split_and_normailize.all(W_hybrid_mock, response, TRAIN_RATIO)
+
+```
+```
+
+```{r}
+    predictor_cv_train <- multiFunData(
+f1, f2
+    )
+    MFPCA(mFData = predictor_cv_train, mFData_predict = predictor_cv_train, M = 5, uniExpansions = uniExpansions)
+```
+
+```{r}
 
@@
   train_test_split <- split.all(data_fun_1[[rep_number]], data_fun_2[[rep_number]], data_scalar[[rep_number]], response[[rep_number]], train_test_idx)
-  train_test_split_normalized <- normailize.all(train_test_split)
+  train_test_split_normalized <- split_and_normailize.all(train_test_split)
 
@@
 
-    predictor_cv_train <- multiFunData(
-      fd2funData(cv_train_valid_split_normalized$data_fun_1_train, eval_point),
-      fd2funData(cv_train_valid_split_normalized$data_fun_2_train, eval_point)
-    )
     predictor_cv_valid <- multiFunData(

### 2025-12-30 create-FSHybridPLS.Rmd
before modifying get_rho

@@
 title: "Creating the ``r params$package_name`` R package"
-author: "Your Name"
+author: "Jongmin Mun"
 date: "The Date"
@@
 We start by specifying the information needed in the DESCRIPTION file of the R package.
- library()
-library(fda)
+
 ```{r package-setup, message=FALSE, results='hide'}
@@
     Version = "0.0.0.9000",
-    Title = "A Package That Says Hello",
-    Description = "This package says hello.  But its actual purpose is to show how an R package can be completely coded in a single R markdown file.",
-    Imports = "fda (>= 6.1.3), Matrix, funData, foreach, irlba, refund, R6",
+Title = "Hybrid Penalized Partial Least Squares for Functional and Scalar Data",
+    Description = "Implements a Penalized Partial Least Squares (PLS) regression framework designed for hybrid predictors that combine both functional (infinite-dimensional) and scalar (finite-dimensional) covariates.
+The algorithm maximizes the covariance between the hybrid predictors and a scalar response variable while incorporating a roughness penalty to ensure the smoothness of the estimated functional coefficient curves.
+The package includes tools for data simulation using matrix-normal distributions, two-step data normalization, and cross-validated model fitting.",
+    Imports = "fda (>= 6.1.3), Matrix, funData, foreach, irlba, refund, mvnfast, R6",
     `Authors@R` = person(
@@
 
-# helper functions
+#### Table of Contents
+- [Helper Functions](#helper)
+
+# Helper Functions {#helper}
+
+### compute_gram_matrix
+
+**Description:**
+Calculates the Gram matrix for a given functional basis.
+The Gram matrix $G$ is a symmetric positive semi-definite matrix containing the inner products of the basis functions.
+Specifically, the entry $(i, j)$ corresponds to the integral of the product of the $i$-th and $j$-th basis functions over the domain:
+$$G_{ij} = \langle b_i, b_j \rangle = \int b_i(t) b_j(t) \, dt$$
+
+**Inputs:**
+
+- `basis`: A basis object of class `basisfd` (typically created using the `fda` package).
+
+**Output:**
+
+- Returns a square numeric matrix where the entry at row $i$ and column $j$ is the inner product of basis functions $i$ and $j$.
+
+```{r}
+#' Compute the Gram matrix for a basis object
+#'
+#' This function calculates the inner product of a basis with itself to form
+#' the Gram matrix.
+#'
+#' @param basis A basis object of class `basisfd` from the `fda` package.
+#' @return A square matrix where entry (i,j) is the inner product of basis functions i and j.
+#' @export
+compute_gram_matrix <- function(basis) {
+  # Ensure the input is a valid basis object from the fda package
+  stopifnot(inherits(basis, "basisfd"))
+
+  # Compute the inner product of the basis with itself
+  # This calculates the integral of b_i(t) * b_j(t) using the metric defined on the basis
+  fda::inprod(basis, basis) 
+}
+```
 
 ### is_same_basis
-```{r}
+
+**Description:**
+Checks if two composite functional data objects (represented as lists containing functional data) share the exact same basis functions.
+It verifies that both lists have the same length and that the basis for every corresponding element is identical.
+
+**Inputs:**
+
+- `input`: A list containing functional data objects (expected to have a `$functional_list` structure).
+- `other`: Another list containing functional data objects to compare against.
+
+**Output:**
+
+- Returns `TRUE` if both lists have the same length and every corresponding basis is equivalent; otherwise returns `FALSE`.
+
+```{r}
+#' Check if two functional data lists share the same basis
+#'
+#' @description
+#' Checks if two composite functional data objects share the exact same basis functions
+#' by comparing their internal list structures.
+#'
+#' @param input A list containing functional data objects (expected to have a `$functional_list` structure).
+#' @param other Another list containing functional data objects to compare against.
+#' @return `TRUE` if both lists have the same length and every corresponding basis is equivalent; otherwise `FALSE`.
 #' @export
@@
   all(
+    # Check if both lists have the same number of functional elements
     length(input$functional_list) == length(other$functional_list),
+
+    # Check if the basis for each corresponding element is identical
     all(
-      mapply(function(fd1, fd2) fda::is.eqbasis(fd1$basis, fd2$basis),
-             input$functional_list, other$functional_list)
-    )
-  )
-}
-```
-
-### compute_gram_matrix
-```{r}
-#' Compute the Gram matrix for a basis object
-#'
-#' @param basis A basis object of class `basisfd` from the `fda` package
-#' @return A square matrix where entry (i,j) is the inner product of basis functions i and j
-#' @export
-compute_gram_matrix <- function(basis) {
-  stopifnot(inherits(basis, "basisfd"))
-  inprod(basis, basis)  # computes ∫ b_i(t) b_j(t) dt
-}
-
-```
+      mapply(function(fd1, fd2) {
+        # Use fda package function to check basis equality
+        fda::is.eqbasis(fd1$basis, fd2$basis)
+      }, input$functional_list, other$functional_list)
+    )
+  )
+}
+```
+
+### are_all_gram_matrices_identical
+
+**Description:**
+Iterates through a list of matrices to verify if they are all numerically identical to the first matrix in the list. This function handles floating-point inaccuracies by using a tolerance parameter.
+
+**Inputs:**
+
+- `gram_list`: A list containing matrix objects to be compared.
+- `tolerance` (Optional): A numeric value defining the tolerance for floating-point comparison. Defaults to the square root of machine epsilon.
+
+**Output:**
+
+- Returns `TRUE` if the list is empty, has one element, or if all matrices are identical to the first. Returns `FALSE` if any matrix differs.
 
@@
 
-## helpers for functional data objects
-
 ### rep_fd
+
+**Description:**
+Takes a list of functional data objects (where each object represents a single sample/curve) and broadcasts them by replicating their coefficients.
+This creates new functional objects containing $n$ identical copies of the original curve.
+
+**Inputs:**
+
+- `fd_list`: A list of `fd` objects (functional data objects). Each object must have exactly one column of coefficients (a single sample).
+- `n`: An integer specifying the number of replications desired.
+
+**Output:**
+
+- Returns a list of `fd` objects, where each object now contains $n$ replications of the original coefficients.
 
@@
 rep_fd <- function(fd_list, n) {
+  # Validate input: must be a list of 'fd' objects
   if (!is.list(fd_list) || any(!vapply(fd_list, inherits, logical(1), "fd"))) {
@@
     coef_mat <- fd_obj$coefs
+
+    # Ensure the object represents a single sample (one column of coefficients)
     if (is.null(dim(coef_mat)) || ncol(coef_mat) != 1) {
@@
 
+    # Create a new coefficient matrix by repeating the column 'n' times
     new_coefs <- matrix(rep(coef_mat, n), nrow = nrow(coef_mat), ncol = n)
+
+    # Return a new fd object with the replicated coefficients and original basis
     fd(coef = new_coefs, basisobj = fd_obj$basis)
@@
 
-| Case | Description                            | Input Type               | Expected Output                        | Notes                                            |
-|------|----------------------------------------|--------------------------|----------------------------------------|--------------------------------------------------|
-| 1    | Correct replication                    | List of single-sample fd | List of `fd` objects with `n` columns | All columns identical to original coefficients   |
-| 2    | Each fd has one sample                 | List of fd               | No error                               | Verifies structure and content                  |
-| 3    | One fd has multiple samples            | fd with >1 columns       | Error                                   | Should raise informative error                  |
-| 4    | Non-fd object in list                  | List of non-`fd` items   | Error                                   | Validates class-checking robustness             |
-
-# Class predictor_hybrid
-- Let $\{X^{(k)}\}_{k=1, \ldots, K}$ be a collection of random functions defined on unit hypercube domains $\mathcal{T}_k := [0,1]^{d_k}$ ($d_k \in \mathbb{N})$; i.e., $X^{(k)}: \mathcal{T}_k \rightarrow \mathbb{R}$.
-
-- Assume that each $X^{(k)}$ is in $L^2(\mathcal{T}_k)$, a Hilbert space of square integrable functions with respect to Lebesgue measure $dt_k$ on $\mathcal{T}_k$.
-
-- Write  $X=(X^{(1)}, \ldots, X^{(K)})$ as a multivariate functional object that belongs to $\mathcal{F} = L^2(\mathcal{T}_1) \times \cdots \times L^2(\mathcal{T}_K)$---a cartesian product of individual $L^2(\mathcal{T}_k)$ spaces.
-
-- We can also express the functional object $X$ evaluated on the multi-dimensional argument $\mathbf{t} = (t_1, \ldots, t_k)^\top \in \mathcal{T} = \mathcal{T}_1 \times \cdots \times \mathcal{T}_K$ as a $K$-dimensional vector $X(\mathbf{t})=(X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top$.
-
-- **Our strategy is to formulate a hybrid random object**, $\mathbf{W} = (X, \mathbf{Z})$, which combines $X$ and $p$-dimensional scalar covariate $\mathbf{Z}$ into an ordered pair belonging to $\mathcal{H} = \mathcal{F} \times \mathbb{R}^p$.
-
-- An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}[\mathbf{t}] = (X(\mathbf{t}), \mathbf{Z})^\top$, with $X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $\mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.
-
-- The hybrid object forms a Hilbert space, characterized by well-defined addition, scalar multiplication, and inner product operations.
-
-- We define an S3 object `predictor_hybrid` that represent this structure, and implement Hilbert space operations for this class, and our algorithm is built on these foundational operations.
-
-The class definition is a simple list that contains a matrix and a collection of \code{fd} objects from the \code{fda} package, along with the necessary metadata.
-- gram matrices are saved as a list.
-```{r classdef:predictor_hybrid}
+# Hybrid predictor class
+
+## Class definition and constructor
+### predictor_hybrid
+
+**Description:**
+The `predictor_hybrid` class represents a hybrid random object $\mathbf{W} = (X, \mathbf{Z})$ that combines functional and scalar covariates into a unified Hilbert space structure.
+
+- **Functional Part:** Let $\{X^{(k)}\}_{k=1, \ldots, K}$ be a collection of random functions defined on unit interval $\mathcal{T}_k := [0,1]$.
+Each $X^{(k)}$ belongs to $L^2([0,1])$, a Hilbert space of square-integrable functions.
+The multivariate functional object $X$ resides in the cartesian product space $\mathcal{F} = L^2([0,1]) \times \cdots \times L^2([0,1])$.
+- **Hybrid Object:** We define the hybrid object $\mathbf{W} = (X, \mathbf{Z})$, where $\mathbf{Z}$ is a $p$-dimensional scalar covariate vector.
+This object belongs to the product space $\mathcal{H} = \mathcal{F} \times \mathbb{R}^p$.
+- **Vector Notation:** The object can be evaluated at a multi-dimensional argument $\mathbf{t}$ as a $(K+p)$-dimensional vector: $\mathbf{W}[\mathbf{t}] = (X(\mathbf{t}), \mathbf{Z})^\top$.
+- **Implementation:** The class is implemented as an S3 object containing a matrix for scalar parts, a list of `fd` objects for functional parts, and pre-computed Gram matrices to facilitate Hilbert space operations.
+
+**Inputs:**
+
+- `Z`: A numeric matrix of dimension $n\_sample \times n\_scalar$ representing the scalar predictors.
+- `functional_list`: A list of functional predictors (typically `fd` objects from the `fda` package).
+- `eval_point`: A specification for evaluation points (stored as metadata).
+
+**Output:**
+
+- Returns an object of class `predictor_hybrid`, which includes the original data, pre-computed Gram matrices, and roughness penalty matrices.
+
+```{r}
 #' Create a predictor_hybrid object (S3 version, automatic basis size and Gram matrix)
+#'
 #' Constructs a hybrid predictor object that stores both scalar and functional predictors,
@@
 #'
-#' @param Z A numeric matrix of dimension \code{n_sample × n_scalar} representing scalar predictors.
+#' @param Z A numeric matrix of dimension \code{n_sample x n_scalar} representing scalar predictors.
 #' @param functional_list A list of functional predictors (e.g., \code{fd} objects from the \code{fda} package).
+#' @param eval_point Points at which the functions are evaluated (stored as metadata).
 #'
@@
 predictor_hybrid <- function(Z, functional_list, eval_point) {
+  # Validate scalar input
   stopifnot(is.matrix(Z), is.numeric(Z))
+
+  # Validate functional input
   stopifnot(is.list(functional_list))
@@
 
+  # Initialize lists for storing matrices and metadata
   gram_list <- gram_deriv2_list <- vector("list", n_functional)
@@
 
+  # Iterate through each functional predictor to compute necessary matrices
   for (i in seq_len(n_functional)) {
@@
 
+    # Ensure the number of functional samples matches the scalar samples
     n_fd_sample <- ncol(coef(fd_i))
@@
 
+    # Extract basis and compute inner product matrices
     basis_i <- fd_i$basis
     gram_list[[i]] <- compute_gram_matrix(basis_i)
-    gram_deriv2_list[[i]] <- fda::getbasispenalty(basis_i) # New
+    gram_deriv2_list[[i]] <- fda::getbasispenalty(basis_i) # Compute roughness penalty matrix
 
@@
 
+  # Construct the S3 object
   structure(
@@
       gram_list = gram_list,
-      gram_deriv2_list = gram_deriv2_list, # Store the new list
+      gram_deriv2_list = gram_deriv2_list, # Store the penalty matrices
       n_basis_list = n_basis_list,
@@
 ### predictor_hybrid_from_coef
-An alternative constructor for a predictor_hybrid object based on a flat numeric coefficient vector.
-It reconstructs both the functional and scalar components for a single-sample hybrid predictor object.
-The function reads the basis information from the template `format` object.
-
-- Inputs
-  - **`format`**: A `predictor_hybrid` object containing:
-    - `functional_list`: List of `fd` objects with basis info
-    - `gram_list`: List of Gram matrices
-    - `n_scalar`: Number of scalar predictors
-  - **`coef`**: Numeric vector of length `K * M + d`, where:
-    - `K` = number of functional predictors  
-    - `M` = number of basis functions (assumed same across predictors)  
-    - `d` = number of scalar predictors
-
-- Output
-  - A `predictor_hybrid` object with:
-    - Functional predictors rebuilt from the first `K * M` coefficients
-    - Scalar predictor `Z` from the remaining `d` coefficients
-    - `n_sample` set to 1
+
+**Description:**
+An alternative constructor that creates a single-sample `predictor_hybrid` object from a flat numeric coefficient vector.
+It reconstructs both the functional and scalar components by mapping the coefficients back onto the basis functions defined in a template `format` object.
+
+**Important:** This function strictly assumes that all functional predictors in the `format` object share the same number of basis functions (). It verifies this assumption before proceeding.
+
+**Inputs:**
+
+- `format`: A `predictor_hybrid` object serving as a template. It must contain the necessary basis information (`functional_list`) and structural metadata (`n_scalar`, `n_functional`).
+- `coef`: A numeric vector of length , where:
+-  is the number of functional predictors.
+-  is the number of basis functions (strictly enforced to be identical across all functional predictors).
+-  is the number of scalar predictors.
+
+**Output:**
+
+- Returns a `predictor_hybrid` object representing a single sample (`n_sample = 1`), containing:
+- Functional predictors rebuilt from the first  coefficients.
+- A scalar predictor matrix `Z` derived from the remaining  coefficients.
 
@@
 #' Construct a Single-Sample Predictor Hybrid Object from Coefficients
+#'
 #' Reconstructs a \code{predictor_hybrid} object representing one observation, using a numeric
@@
 #' @return A \code{predictor_hybrid} object with updated \code{functional_list}, \code{Z}, and \code{n_sample = 1}.
-#'
-#'
-#' @export
-predictor_hybrid_from_coef <- function(format, coef){
-  M <- format$n_basis_list[1] # number of basis functions
-  K <- format$n_functional # number of functional predictors
-  for (ii in 1:K){
+#' @export
+predictor_hybrid_from_coef <- function(format, coef) {
+  # Extract metadata from the template
+  basis_counts <- format$n_basis_list
+
+  # Check if all functional predictors have the same number of basis functions
+  if (length(unique(basis_counts)) != 1) {
+    stop("All functional predictors must have the same number of basis functions (M).")
+  }
+
+  M <- basis_counts[1]  # Number of basis functions (identical across predictors)
+  K <- format$n_functional # Number of functional predictors
+
+  # Reconstruct each functional predictor
+  for (ii in 1:K) {
+    # Calculate indices for the current functional predictor in the flat vector
+    start_idx <- (ii - 1) * M + 1
+    end_idx   <- ii * M
+
+    # Create a new fd object using the sliced coefficients and original basis
     format$functional_list[[ii]] <- fd(
-      coef = as.matrix(coef[((ii-1)*M + 1):(ii*M)]),
+      coef = as.matrix(coef[start_idx:end_idx]),
       basisobj = format$functional_list[[ii]]$basis
@@
   }
-  format$Z <- t(as.matrix(coef[(K * M + 1):length(coef)]))
+
+  # Reconstruct the scalar predictor part (Z)
+  # The remaining coefficients after K*M belong to the scalar predictors
+  scalar_start_idx <- K * M + 1
+  format$Z <- t(as.matrix(coef[scalar_start_idx:length(coef)]))
+
+  # Update sample count to 1 as this constructor creates a single observation
   format$n_sample <- 1
+
   return(format)
@@
 ### add.predictor_hybrid
+
+**Description:**
 Performs element-wise addition of two `predictor_hybrid` objects. Functional predictors are combined using `plus.fd()` and `times.fd()` from the `fda` package.
 
-- Usage
-
+**Usage:**
 ```r
@@
 
-- Arguments:
+**Arguments:**
 
@@
 
-- Value:
-Returns a new `predictor_hybrid` object representing the result of the addition.
-
-- Details: 
+**Value:**
+
+- Returns a new `predictor_hybrid` object representing the result of the addition.
+
+**Details:**
+
 - This function assumes both objects have the same number and structure of functional and scalar predictors.
@@
 - Scalar predictors are added using standard matrix addition.
-
-```{r}
+- Supports broadcasting if one object represents a single sample (`n_sample = 1`) and the other represents multiple samples.
+
+```{r}
+#' Add two predictor_hybrid objects
+#'
+#' Performs element-wise addition of two \code{predictor_hybrid} objects. 
+#' Supports broadcasting if one object is a single sample.
+#'
+#' @param xi_1 A \code{predictor_hybrid} object.
+#' @param xi_2 Another \code{predictor_hybrid} object to be added.
+#' @param alpha A scalar multiplier applied to \code{xi_2} before addition (default is 1).
+#'
+#' @return A new \code{predictor_hybrid} object representing the result of the addition.
+#' @export
 add.predictor_hybrid <- function(xi_1, xi_2, alpha = 1) {
-  # Safe access to is.eqbasis()
+  # Safe access to is.eqbasis() from the fda namespace
   is_eqbasis <- getFromNamespace("is.eqbasis", "fda")
 
+  # Type checks
+  if (!inherits(xi_1, "predictor_hybrid") || !inherits(xi_2, "predictor_hybrid")) {
+    stop("Both inputs must be of class 'predictor_hybrid'.")
+  }
+
+  # Structural checks: Number of functional and scalar predictors must match
+  if (xi_1$n_functional != xi_2$n_functional) {
+    stop("Mismatch in number of functional predictors.")
+  }
+  if (xi_1$n_scalar != xi_2$n_scalar) {
+    stop("Mismatch in number of scalar predictors.")
+  }
+
+  # Basis checks: Ensure corresponding functional predictors share the same basis
   for (i in seq_len(xi_1$n_functional)) {
@@
 
-   # Type checks
-  if (!inherits(xi_1, "predictor_hybrid") || !inherits(xi_2, "predictor_hybrid")) {
-    stop("Both inputs must be of class 'predictor_hybrid'.")
-  }
-
-  # Structural checks
-  if (xi_1$n_functional != xi_2$n_functional) {
-    stop("Mismatch in number of functional predictors.")
-  }
-  if (xi_1$n_scalar != xi_2$n_scalar) {
-    stop("Mismatch in number of scalar predictors.")
-  }
-
-  # Swap so that broadcasting always applies to xi_2
+  # Broadcasting Logic:
+  # Ensure xi_1 is always the larger object (or equal) to simplify broadcasting
   if (xi_1$n_sample == 1 && xi_2$n_sample > 1) {
@@
 
+  # Validate sample compatibility
   if (!(n1 == n2 || n2 == 1)) {
@@
 
-  # Replicate fd and Z if needed
-  if (n2 == 1) {
+  # Replicate fd and Z if broadcasting is needed (n2 == 1)
+  if (n2 == 1 && n1 > 1) {
     f2 <- rep_fd(f2, n1)
@@
 
-  # Combine functional predictors
+  # Combine functional predictors: f1 + alpha * f2
   new_functional_list <- Map(
-    function(f1, f2) plus.fd(f1, times.fd(alpha, f2)),
+    function(fd1, fd2) plus.fd(fd1, times.fd(alpha, fd2)),
     f1,
@@
 
-  # Compute scalar inner products
-  inprod_scalar <- rowSums(Z1 * Z2) 
-  # Combine scalar predictors
+  # Combine scalar predictors: Z1 + alpha * Z2
   new_Z <- Z1 + alpha * Z2
 
-  # Construct new object
-  predictor_hybrid(Z = new_Z, functional_list = new_functional_list)
+  # Construct and return the new predictor_hybrid object
+  # Note: eval_point is carried over from the first object
+  predictor_hybrid(Z = new_Z, functional_list = new_functional_list, eval_point = xi_1$eval_point)
 }
@@
 ### subtr.predictor_hybrid
-Performs element-wise subtraction of two `predictor_hybrid` objects.   Internally uses `add.predictor_hybrid(input, other, alpha = -1)` to compute the result by negating the second operand.
-
-- Usage
-
+
+**Description:**
+Performs element-wise subtraction of two `predictor_hybrid` objects. Internally uses `add.predictor_hybrid` to compute the result by negating the second operand.
+
+**Usage:**
 ```r
@@
 
-- Value:  
-Returns a new `predictor_hybrid` object representing the result of the subtraction.
-
-- Details:  
+**Value:**
+
+- Returns a new `predictor_hybrid` object representing the result of the subtraction.
+
+**Details:**
+
 - This function assumes both objects have the same number and structure of functional and scalar predictors.
@@
 }
-
-```
-We skip the unit test for this function.
+```
 
 ### scalar_mul.predictor_hybrid
+
+**Description:**
 Multiplies all components of a `predictor_hybrid` object by a scalar.
@@
 
-- Usage
-
+**Usage:**
 ```r
 scalar_mul.predictor_hybrid(input, scalar)
-```
-
-- Arguments:
+
+```
+
+**Arguments:**
 
@@
 
-- Value:  
-Returns a new `predictor_hybrid` object with all components scaled by `scalar`.
-
-- Details:  
+**Value:**
+
+- Returns a new `predictor_hybrid` object with all components scaled by `scalar`.
+
+**Details:**
+
 - Functional predictors are scaled using `times.fd(scalar, fd_obj)` for each element.
@@
   # Reconstruct hybrid object
+  # Passing eval_point from the original input to maintain metadata
   predictor_hybrid(
     Z = new_Z,
-    functional_list = new_functional_list
+    functional_list = new_functional_list,
+    eval_point = input$eval_point
   )
@@
 ### inprod.predictor_hybrid
-- The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)})$ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as 
-$$\langle f_1, f_2\rangle_\mathcal{F} =  \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)}\rangle_{L^2} = \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k,$$ with norm 
-$$\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k)^2 dt_k\}^{1/2}.$$
-- We define the inner product between any two hybrid objects, $\mathbf{h}_1 = (f_1, \mathbf{v}_1)$ and $\mathbf{h}_2 = (f_2, \mathbf{v}_2)$, as
-$$
-    \langle \mathbf{h}_1, \mathbf{h}_2\rangle_{\mathcal{H}} = \langle f_1, f_2\rangle_\mathcal{F} +  \langle  \mathbf{v_1}, \mathbf{v_2} \rangle = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p v_{1r}v_{2r},
-$$
-with norm $\Vert \cdot \Vert_\mathcal{H} = \langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
-
-- The method `inprod.predictor_hybrid` computes the inner product between two `predictor_hybrid` objects. It supports broadcasting when one of the inputs has a single observation.
-
-- Usage
-
-```r
-inprod.predictor_hybrid(xi_1, xi_2)
-```
-
-- Arguments:
+
+**Description:**
+Computes the inner product between two `predictor_hybrid` objects.
+The inner product in the hybrid space  is defined as the sum of the inner products of the functional components in  and the scalar components in :
+
+**Inputs:**
 
 - `xi_1`: A `predictor_hybrid` object.
-  - `xi_2`: Another `predictor_hybrid` object. If omitted, defaults to xi_1 (computes self-inner product).
-
-- Value:  A numeric vector of inner products (or a scalar if both inputs are single observations).
-
-- Details:  
-  - Functional components are summed using inprod() from the fda package.
-  - Scalar components are handled via matrix multiplication.
-  - Broadcasting is supported: if either xi_1 or xi_2 has only one sample, its values are broadcast across all rows of the other.
-  - Ensures compatibility in the number of functional and scalar predictors before computing the result.
+- `xi_2`: (Optional) Another `predictor_hybrid` object. Defaults to `xi_1` (computes norm squared if `xi_1` is a single sample).
+
+**Output:**
+
+- A numeric vector of inner products. If both inputs are single samples, returns a scalar.
+
+**Details:**
+
+- Supports broadcasting: if one input has a single observation (`n_sample = 1`) and the other has multiple, the single observation is broadcast across the others.
+- Uses `fda::inprod` for functional integration and matrix multiplication for scalar parts.
 ```{r}
@@
 
-  # Swap so that broadcasting always applies to xi_2
+  # Swap so that broadcasting always applies to xi_2 (the smaller one)
   if (xi_1$n_sample == 1 && xi_2$n_sample > 1) {
@@
 
-  # Replicate fd and Z if needed
-  if (n2 == 1) {
+  # Replicate fd and Z if needed for broadcasting
+  if (n2 == 1 && n1 > 1) {
     f2 <- rep_fd(f2, n1)
@@
   # Compute functional inner products
+  # Iterates over samples (i) and sums the inner products of all functional predictors (j)
   inprod_functional <- vapply(seq_len(n1), function(i) {
@@
 
-  # Compute scalar inner products
+  # Compute scalar inner products using row-wise summation
   inprod_scalar <- rowSums(Z1 * Z2)
 
-  # Combine results
+  # Combine functional and scalar results
   result <- inprod_functional + inprod_scalar
+
+  # Return scalar if both inputs were single samples
   if (n1 == 1 && n2 == 1) as.numeric(result) else result
@@
 
-```{r}
-#' Inner product between two predictor_hybrid objects (with broadcasting)
+### inprod_pen.predictor_hybrid
+
+**Description:**
+Computes the penalized inner product between two `predictor_hybrid` objects. This adds a roughness penalty term to the standard inner product, typically used for regularization.
+
+**Inputs:**
+
+- `xi_1`: A `predictor_hybrid` object.
+- `xi_2`: (Optional) Another `predictor_hybrid` object.
+- `lambda`: A numeric vector of length  (number of functional predictors) specifying the smoothing parameter for each function.
+
+**Output:**
+
+- A numeric vector (or scalar) representing the penalized inner product.
+```{r}
+#' Penalized Inner product between two predictor_hybrid objects
 #'
 #' Computes the inner product between two `predictor_hybrid` objects,
-#' including both functional and scalar components. Supports broadcasting
-#' when one of the inputs has a single observation.
+#' adding a roughness penalty term based on the second derivative.
 #'
@@
 #' @param xi_2 Another `predictor_hybrid` object. If missing, defaults to `xi_1`.
-#'
-#' @return A numeric vector of inner products, or a scalar if both inputs contain a single observation.
+#' @param lambda A numeric vector of smoothing parameters (one for each functional predictor).
+#'
+#' @return A numeric vector of inner products.
 #' @export
@@
 
-  inprod <- inprod.predictor_hybrid(xi_1, xi_2)
-  # Prepare components
+  # Compute the standard inner product first
+  base_inprod <- inprod.predictor_hybrid(xi_1, xi_2)
+
+  # Handle self-reference for xi_2
+  if (is.null(xi_2)) xi_2 <- xi_1
 
   f1 <- xi_1$functional_list
-
   f2 <- xi_2$functional_list
-  for (j in 1:xi_1$n_functional){
-    inprod <- inprod + lambda[j] * fda::inprod(
+
+  # Add penalty terms for each functional predictor
+  # The penalty is lambda * <D^2 f1, D^2 f2>
+  for (j in seq_len(xi_1$n_functional)) {
+    base_inprod <- base_inprod + lambda[j] * fda::inprod(
       fdobj1 = f1[[j]],
       fdobj2 = f2[[j]],
-        Lfdobj1 = 2,
-        Lfdobj2 = 2
-        )
-
-    }
-
-  # Combine results
-   return(as.numeric(inprod))
+      Lfdobj1 = 2, # Second derivative
+      Lfdobj2 = 2  # Second derivative
+    )
+  }
+
+  return(as.numeric(base_inprod))
 }
@@
 ### subset_predictor_hybrid
+
+**Description:**
+Extracts a specific observation from a multi-sample `predictor_hybrid` object and returns it as a new, single-sample `predictor_hybrid` object.
+
+**Inputs:**
+
+- `W`: A `predictor_hybrid` object containing multiple samples.
+- `i`: Integer index of the sample to extract.
+
+**Output:**
+
+- A `predictor_hybrid` object containing only the -th observation.
 
@@
 #' @return A single-sample predictor_hybrid object.
+#' @export
 subset_predictor_hybrid <- function(W, i) {
+  # Extract the i-th row of the scalar matrix
   new_Z <- matrix(W$Z[i, ], nrow = 1)
+
+  # Extract the i-th column of coefficients for each functional object
   new_functional_list <- lapply(W$functional_list, function(fdobj) {
@@
   })
-  new_predictor <- predictor_hybrid(Z = new_Z, functional_list = new_functional_list)
+
+  # Construct new object
+  new_predictor <- predictor_hybrid(
+    Z = new_Z, 
+    functional_list = new_functional_list,
+    eval_point = W$eval_point
+  )
+
   return(new_predictor)
@@
 ### replace_obs_hybrid
+
+**Description:**
+Replaces a specific observation within a `predictor_hybrid` object with a new single-sample hybrid object.
+This effectively updates the -th row of the scalar matrix and the -th column of the functional coefficients.
+
+**Inputs:**
+
+- `W`: The target `predictor_hybrid` object.
+- `i`: The integer index of the observation to replace.
+- `new_W`: The source `predictor_hybrid` object (must be a single sample).
+
+**Output:**
+
+- The modified `W` object.
 
@@
 
-  # The number of samples remains the same
   return(W)
@@
 
-### add_broadcast(for matrix)
-
-```{r}
-#' @export
-#' 
-#' 
-# --- 1. Define the S4 Generic Function ---
-# This must be run first to tell R that 'add_broadcast' is a function 
-# that can have methods defined for different classes.
-setGeneric("add_broadcast", function(input, other, alpha = 1) {
-  standardGeneric("add_broadcast")
-})
-
-# --- 2. Define the S4 Method for 'matrix' Class ---
-setMethod("add_broadcast", "matrix",
-###########################################
-function(input, other, alpha = 1){
-
-  # 1. Structural Check: Ensure RHS is a single observation.
+### add_broadcast (Matrix)
+
+**Description:**
+A function that performs row-wise addition of a vector to a matrix.
+It broadcasts a single observation (vector) across all rows of the target matrix, verifying that the input is a matrix and the operand is a single observation.
+
+**Inputs:**
+
+- `input`: A numeric matrix.
+- `other`: A numeric vector or a 1-row matrix to be added to every row of `input`.
+- `alpha`: A scalar multiplier applied to `other` before addition.
+
+**Output:**
+
+- A matrix of the same dimensions as `input`.
+
+```{r}
+#' Broadcast Addition for Matrices
+#'
+#' Adds a single observation (vector) to every row of a matrix.
+#' Checks that the input is a matrix and the operand is a single observation.
+#'
+#' @param input A numeric matrix.
+#' @param other A numeric vector or a 1-row matrix.
+#' @param alpha A scalar multiplier (default 1).
+#' @return A matrix with the broadcasted addition applied.
+#' @export
+add_broadcast <- function(input, other, alpha = 1) {
+
+  # 1. Type Check: Ensure input is a matrix
+  if (!is.matrix(input)) {
+    stop("Argument 'input' must be a matrix.")
+  }
+
+  # 2. Structural Check: Ensure RHS is a single observation.
   # This uses length() for vectors, and dim()[1] for matrices.
@@
   if (is_matrix_other && dim(other)[1] > 1) {
-    stop("RHS must have a single observation (row).")
-  }
-
-  # 2. Conversion: Convert a single-row matrix into a vector for broadcasting.
+    stop("Argument 'other' must be a vector or a single-row matrix.")
+  }
+
+  # 3. Conversion: Convert a single-row matrix into a vector for broadcasting.
   # If 'other' is already a vector, this does nothing.
-  # If 'other' is a 1xP matrix, this flattens it into a length-P vector.
   if (is_matrix_other) {
@@
 
-  # 3. Native Arithmetic: Use simple R arithmetic for high performance.
+  # 4. Dimension Check: Ensure vector length matches matrix columns
+  if (length(other) != ncol(input)) {
+    stop("Length of 'other' must match number of columns in 'input'.")
+  }
+
+  # 5. Native Arithmetic: Use simple R arithmetic for high performance.
   # R broadcasts the vector 'other' across the rows of the matrix 'input'.
-  return( t( t(input) + alpha * other))
-}
-###########################################
-)
-
-```
-### subtr_broadcast (for matrix)
-
-```{r}
-#' @export
-#' 
-#'
-setGeneric("subtr_broadcast", function(input, other, alpha = 1) {
-  standardGeneric("subtr_broadcast")
-})
-setMethod("subtr_broadcast", "matrix",
-###########################################
-function(input, other, alpha = 1){
-  return(add_broadcast(input, other, (-1*alpha)))
-  }
-###########################################
-)
-
+  # Transposing twice (t(t(...) ...)) ensures correct column-wise recycling 
+  # logic is applied to rows.
+  return(t(t(input) + alpha * other))
+}
+```
+
+### subtr_broadcast (Matrix)
+
+**Description:**
+A function that performs row-wise subtraction of a vector from a matrix. It is a wrapper around `add_broadcast` that applies a negative multiplier.
+
+**Inputs:**
+
+- `input`: A numeric matrix.
+- `other`: A numeric vector or a 1-row matrix to subtract from every row of `input`.
+- `alpha`: A scalar multiplier applied to `other` (default 1).
+
+**Output:**
+
+- A matrix of the same dimensions as `input`.
+
+```{r}
+#' Broadcast Subtraction for Matrices
+#'
+#' Subtracts a single observation (vector) from every row of a matrix.
+#'
+#' @param input A numeric matrix.
+#' @param other A numeric vector or a 1-row matrix.
+#' @param alpha A scalar multiplier (default 1).
+#' @return A matrix with the broadcasted subtraction applied.
+#' @export
+subtr_broadcast <- function(input, other, alpha = 1) {
+  # Reuse add_broadcast with negated alpha
+  add_broadcast(input, other, (-1 * alpha))
+}
 ```
@@
 
-## penalty matrix construction
-In this section, we provide an R function `get_constraint_matrix` that constructs the penalty matrix
-$$J^*+\Lambda \ddot{J}^\ast,$$
-as defined in Proposition 2 and used in the PLS component computation step of our proposed algorithm.
-We present functions  for computing $J^\ast$, $\Lambda$ and $\ddot{J}^\ast$ in sequence, and use these functions to define `get_constraint_matrix`.
-
 ### get_gram_matrix_block
-Constructs a block-diagonal Gram matrix for a hybrid predictor object, defined as 
-$$
-    J^*=\mathrm{blkdiag}(J, I_p) \in \mathbb{R}^{(MK+p) \times (MK+p)}
-$$
-where
- $J = \mathrm{blkdiag}(J^{(1)}, \cdots, J^{(K)}) \in \mathbb{R}^{MK \times MK}$, and 
-$$
-J^{(k)} = \left[ \int_{\mathcal{T}k} b_m^{(k)}(t) , b_n^{(k)}(t) , dt \right]_{m,n=1}^M,
-$$
-as defined in \eqref{def:gram_basis} and \eqref{def:J_and_J_star}.
-
-- Arguments
-  - obj: A `predictor_hybrid` object containing both functional and scalar components.
-
-- Value
-  - A Matrix::bdiag sparse matrix representing the block-diagonal structure of the combined Gram matrix.
-
-- Details: This function builds a block-diagonal matrix by:
-  - Stacking the Gram matrices of each functional component (from obj$gram_list),
-  - Appending an identity matrix of size equal to the number of scalar predictors (to represent unpenalized scalar covariates).
-  The resulting matrix has size $(\texttt{total_dim} \times \texttt{total_dim})$, where total_dim = \sum_k M_k + p, with $M_k$ the number of basis functions for the $k$-th functional predictor and $p$ the number of scalar covariates.
-
-- Usage
-```r
-block_gram <- get_gram_matrix_block(my_predictor)
-```
-
-**Code**
+
+**Description:**
+Constructs the block-diagonal Gram matrix  for a hybrid predictor object. This matrix represents the inner product structure of the combined functional and scalar space. It is defined as:
+
+where:
+
+-  is the Gram matrix of the basis functions for the -th functional predictor, with entries .
+-  is the identity matrix corresponding to the  scalar predictors (implying a standard Euclidean inner product for the scalar part).
+
+**Inputs:**
+
+- `obj`: A `predictor_hybrid` object containing the pre-computed Gram matrices (`gram_list`) and metadata.
+
+**Output:**
+
+- A sparse block-diagonal matrix (class `dgCMatrix` from the `Matrix` package) representing the global Gram matrix.
 ```{r}
@@
 #'
-#' Returns a block-diagonal matrix containing the Gram  matrices for
-#' each functional component and an identity matrix for the scalar part.
+#' Creates a unified Gram matrix by placing the pre-computed functional Gram matrices
+#' and a scalar identity matrix into a block-diagonal structure.
 #'
@@
 #'
-#' @return A block-diagonal matrix of size `(total_dim × total_dim)` where
-#' functional and scalar components are arranged in order.
+#' @return A sparse block-diagonal matrix of size `(total_dim x total_dim)`, where
+#' `total_dim` is the sum of all functional basis sizes plus the number of scalar predictors.
 #' @export
 get_gram_matrix_block <- function(obj) {
+  # Input validation
   if (!inherits(obj, "predictor_hybrid")) {
@@
 
-  gram_blocks <- c(obj$gram_list, list(diag(obj$n_scalar)))
+  # 1. Retrieve the list of functional Gram matrices (pre-computed in the object)
+  #    These correspond to the J^(k) blocks.
+  gram_blocks <- obj$gram_list
+
+  # 2. Append the Identity matrix for the scalar components
+  #    This corresponds to the I_p block.
+  #    We use 'diag' to create an Identity matrix of size n_scalar x n_scalar.
+  gram_blocks[[length(gram_blocks) + 1]] <- diag(obj$n_scalar)
+
+  # 3. Construct the sparse block-diagonal matrix
+  #    Matrix::bdiag efficiently handles the block construction.
   Matrix::bdiag(gram_blocks)
 }
-
-```
-
-**Unit test**
-```{r}
-testthat::test_that("get_gram_matrix_block constructs correct block-diagonal matrix", {
-  suppressPackageStartupMessages(library(fda))
-  suppressPackageStartupMessages(library(Matrix))
-
-  # Construct hybrid predictor with two functional and three scalar predictors
-  basis1 <- create.bspline.basis(c(0, 1), nbasis = 4)
-  basis2 <- create.bspline.basis(c(0, 1), nbasis = 4)  # was 3; now valid
-
-  fd1 <- fd(coef = matrix(1, 4, 2), basisobj = basis1)
-  fd2 <- fd(coef = matrix(2, 4, 2), basisobj = basis2)
-  Z <- matrix(rnorm(2 * 3), nrow = 2, ncol = 3)
-
-  obj <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
-
-  # Extract the block-diagonal Gram matrix
-  G <- get_gram_matrix_block(obj)
-
-  # Expected block sizes
-  nb1 <- 4
-  nb2 <- 4
-  ns <- 3
-  total_dim <- nb1 + nb2 + ns
-
-  # Check matrix properties
-  testthat::expect_equal(dim(G), c(total_dim, total_dim))
-
-  # Check sub-block structure
-  # Top-left: Gram matrix 1
-  testthat::expect_equal(sum(G[1:nb1, 1:nb1]-obj$gram_list[[1]]), 0)
-
-  # Next block: Gram matrix 2
-  testthat::expect_equal(sum( G[(nb1 + 1):(nb1 + nb2), (nb1 + 1):(nb1 + nb2)]-obj$gram_list[[2]]),0 )
-
-  # Final block: identity matrix for scalar part
-  testthat::expect_equal( sum( G[(nb1 + nb2 + 1):total_dim, (nb1 + nb2 + 1):total_dim]  - diag(ns)), 0)
-})
-
-```
+```
+
 ### get_smoothing_param_hybrid
-Constructs a block-diagonal smoothing parameter matrix for use in penalized estimation involving hybrid predictors, denoted $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$,  defined in \eqref{def:Lambda} as
-$$
-   \Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
-$$
-
-- Arguments
-  - W: A predictor_hybrid object.
-  - lambda: A numeric vector of length equal to the number of functional predictors. Each entry corresponds to a smoothing penalty weight.
-- Value: A sparse block-diagonal matrix combining scaled identity matrices for the functional parts and a zero matrix for the scalar part.
-- Details: This function generates a matrix used in regularized regression for functional predictors.
-Each functional component is penalized using a scaled identity matrix of its basis dimension.
-Scalar predictors are unpenalized.
-- Usage:
-```r
-lambda_mat <- get_smoothing_param_hybrid(my_predictor, c(0.1, 0.2))
-```
-**code** 
+
+**Description:**
+Constructs the block-diagonal smoothing parameter matrix . This matrix defines the regularization penalties applied to the coefficients. It is defined as:
+
+where:
+
+-  is the smoothing parameter for the -th functional predictor.
+-  is the identity matrix of size  (the number of basis functions for predictor ).
+-  is a zero matrix, indicating that the scalar predictors are not penalized in this step.
+
+**Inputs:**
+
+- `W`: A `predictor_hybrid` object providing dimension information.
+- `lambda`: A numeric vector of length  (number of functional predictors). Each entry represents the penalty weight .
+
+**Output:**
+
+- A sparse block-diagonal matrix where the diagonal blocks contain the penalty weights for functional parts and zeros for the scalar part.
 ```{r}
@@
 #'
-#' Generates a block-diagonal matrix with smoothing parameters applied to each 
-#' functional component. Each block is a scaled identity matrix, where the scaling 
-#' factor corresponds to the regularization parameter for that functional component. 
-#' The scalar components are not penalized and thus contribute a zero matrix block.
+#' Generates a block-diagonal matrix containing regularization parameters. 
+#' Functional coefficients are penalized by scaled identity matrices, while 
+#' scalar coefficients receive zero penalty.
 #'
 #' @param W A `predictor_hybrid` object.
-#' @param lambda A numeric vector of length equal to the number of functional components (`W$n_functional`), containing the smoothing parameters for each functional predictor.
-#'
-#' @return A block-diagonal matrix of size `(total_dim × total_dim)`, where the top-left blocks are scaled identity matrices for functional predictors and the bottom-right block is a zero matrix for scalar covariates.
+#' @param lambda A numeric vector of smoothing parameters, one for each functional predictor.
+#'
+#' @return A sparse block-diagonal matrix. The top-left blocks are `lambda[k] * I`, 
+#' and the bottom-right block is a zero matrix for scalar covariates.
 #' @export
 get_smoothing_param_hybrid <- function(W, lambda) {
+  # Input validation
   if (!inherits(W, "predictor_hybrid")) {
@@
   }
-
   if (length(lambda) != W$n_functional) {
@@
 
+  # 1. Create penalty blocks for functional predictors
+  #    For each predictor k, create a scaled identity matrix: lambda[k] * I_Mk
   lambda_blocks <- lapply(seq_len(W$n_functional), function(ii) {
@@
 
+  # 2. Create zero block for scalar predictors
+  #    Scalar predictors are not penalized in this matrix, so we append a p x p zero matrix.
   lambda_blocks[[W$n_functional + 1]] <- matrix(0, nrow = W$n_scalar, ncol = W$n_scalar)
 
+  # 3. Construct the sparse block-diagonal matrix
   Matrix::bdiag(lambda_blocks)
@@
 
-**unit test**
-```{r}
-testthat::test_that("get_smoothing_param_hybrid returns correct block-diagonal structure", {
-  suppressPackageStartupMessages(library(fda))
-  basis1 <- create.bspline.basis(c(0, 1), nbasis = 5)
-  basis2 <- create.bspline.basis(c(0, 1), nbasis = 4)
-
-  fd1 <- fd(coef = matrix(1, 5, 3), basisobj = basis1)
-  fd2 <- fd(coef = matrix(2, 4, 3), basisobj = basis2)
-
-  Z <- matrix(1, nrow = 3, ncol = 2)
-
-  obj <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
-  lambda <- c(0.5, 2)
-
-  lambda_mat <- get_smoothing_param_hybrid(obj, lambda)
-
-  # Check overall dimension
-  expected_dim <- sum(obj$n_basis_list) + obj$n_scalar
-  testthat::expect_equal(dim(lambda_mat), c(expected_dim, expected_dim))
-
-  # Check diagonal entries
-  testthat::expect_equal(Matrix::diag(lambda_mat)[1:5], rep(0.5, 5))
-  testthat::expect_equal(Matrix::diag(lambda_mat)[6:9], rep(2, 4))
-  testthat::expect_equal(Matrix::diag(lambda_mat)[10:11], rep(0, 2))  # scalar part
-})
-
-```
-
-### get_penalty_hybrid
-Constructs a matrix defined in \label{def:J_dotdot_ast}
-$$
-    \ddot{J}^\ast=\mathrm{blkdiag}(\ddot{J}^{(1)}, \cdots, \ddot{J}^{(K)}, 0_{p \times p}) \in \mathbb{R}^{(MK+p) \times (MK+p)},
-$$
-where
- $\ddot{J}^{(k)}$ is  a $M \times M$ matrix defined in \label{def:dodot_J_k} as the gram matrix formed by the second derivativ of the basis functions
-$$
-\ddot{J}^{(k)} = \left[ \int_{\mathcal{T}_k} \ddot{b}^{(k)}_m(t) \ddot{b}^{(k)}_n(t) \, dt \right]_{m,n=1}^M.
-$$
-
-```{r}
-testthat::test_that("get_penalty_hybrid computes correct dimensions and structure", {
-  suppressPackageStartupMessages(library(fda))
-
-  # Setup
-  basis <- fda::create.bspline.basis(c(0, 1), nbasis = 5)
-  n_sample <- 3
-  n_scalar <- 2
-
-  fd1 <- fda::fd(coef = matrix(1, 5, n_sample), basisobj = basis)
-  fd2 <- fda::fd(coef = matrix(2, 5, n_sample), basisobj = basis)
-  Z <- matrix(rnorm(n_sample * n_scalar), n_sample, n_scalar)
-  obj <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
-
-  # Run
-  penalty <- get_penalty_hybrid(obj)
-
-  # Expected dimensions
-  total_dim <- sum(obj$n_basis_list) + obj$n_scalar
-  testthat::expect_equal(dim(penalty), c(total_dim, total_dim))
-
-  # Check block diagonal structure: bottom-right should be zero matrix
-  scalar_block <- as.matrix(penalty[
-    (total_dim - n_scalar + 1):total_dim,
-    (total_dim - n_scalar + 1):total_dim
-  ])
-  testthat::expect_equal(scalar_block, matrix(0, n_scalar, n_scalar))
-
-  # Check that the upper blocks are positive semidefinite
-  eigenvalues <- eigen(as.matrix(penalty[1:(total_dim - n_scalar), 1:(total_dim - n_scalar)]))$values
-  testthat::expect_true(all(eigenvalues >= -1e-8))  # Numerical tolerance
-})
-
-```
-
-### get_constraint_matrix
-
-```r
-W <- predictor_hybrid(Z = Z, functional_list = list(fd1, fd2))
-lambda <- c(0.1, 0.2)
-constraint_matrix <- get_constraint_matrix_hybrid(W, lambda)
-```
-
-**code**
-```{r}
-#' Construct penalized constraint matrix for hybrid predictors
-#'
-#' Computes the denominator matrix used in penalized estimation for hybrid predictors,
-#' combining the Gram matrix, smoothing parameter matrix, and penalty matrix.
-#'
-#' Specifically, this function returns the matrix:
-#' \deqn{J^\ast + \Lambda \ddot{J}^\ast}
-#' where \eqn{J^\ast} is the block-diagonal Gram matrix,
-#' \eqn{\Lambda} is the block-diagonal smoothing parameter matrix,
-#' and \eqn{\ddot{J}^\ast} is the block-diagonal penalty matrix of second derivative inner products.
+## PLS component computation
+
+### get_xi_hat_linear_pen
+
+**Description:**
+Computes the penalized PLS weight vector (direction) , represented as a `predictor_hybrid` object.
+This function solves for the coefficients that maximize the covariance between the predictor and the response , subject to a roughness penalty.
+
+The optimization problem leads to a system of linear equations for each functional component :
+
+where:
+
+-  is the Gram matrix (`gram_list`).
+-  is the penalty matrix (`gram_deriv2_list`).
+-  are the basis coefficients of the functional data.
+-  are the coefficients for the -th functional weight.
+
+For the scalar part, the weights are simply the inner products . The final coefficient vector is normalized by the -norm (defined by the penalized inner product structure).
+
+**Inputs:**
+
+- `W`: A `predictor_hybrid` object containing the predictors.
+- `y`: A numeric vector of response values (length ).
+- `lambda`: A numeric vector of smoothing parameters (one for each functional predictor).
+
+**Output:**
+
+- A single-sample `predictor_hybrid` object representing the estimated direction .
+
+```{r}
+#' Compute Penalized PLS Weight Vector (Linear)
+#'
+#' Solves for the PLS weight direction xi that maximizes the covariance with y,
+#' subject to roughness penalties on the functional components.
 #'
 #' @param W A `predictor_hybrid` object.
-#' @param lambda A numeric vector of smoothing parameters, one for each functional predictor.
-#'
-#' @return A matrix representing the penalized constraint matrix used in estimation.
-#' @export
-get_constraint_matrix_hybrid <- function(W, lambda) {
-  J_star <- get_gram_matrix_block(W)
-  J_dotdot_star <- get_penalty_hybrid(W)
-  lambda_mat <- get_smoothing_param_hybrid(W, lambda)
-
-  J_star + lambda_mat %*% J_dotdot_star
-}
-
-```
-
-## PLS component computation
-
-### Spectral method
-The old implementation that computes the leading eigenvector of
-
-### helper: get_CJ
-```{r}
-get_CJ <- function(W){
-  n <- W$n_sample
-  K <- W$n_functional
-  ## C_J : C multiplied by J. Scalable to arbitrary K
-  predictor_first <- W$functional_list[[1]]
-  C_J <- t(predictor_first$coefs) %*% W$gram_list[[1]]
-  for (i in 2:K){
-    predictor_now <- W$functional_list[[i]]
-    C_J <- cbind(
-      C_J,
-      t(predictor_now$coefs) %*% W$gram_list[[i]]
-    )
-    }
-    return(C_J)
-}
-```
-
-### helper: get_pre_corrcov 
-construct the matrix V_star:
-$$
-    V^\ast = n^{-2}\begin{bmatrix}
-         J \widetilde{C}^\top \mathbf{y}\mathbf{y}^\top \widetilde{C} J & J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z} \\
-        \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J &   \widetilde{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{Z}
-    \end{bmatrix} = n^{-2} J^* \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^*
-    \in \mathbb{R}^{(MK+p) \times (MK+p)},
-$$
-where $J$ is defined in `get_gram_matrix_block`
-equation (7), 
-```{r}
-#' Compute V matrix (pre-corrected covariance estimator)
-#'
-#' Constructs the V matrix involving inner products of functional predictors
-#' (weighted by their Gram matrices) and scalar predictors against response y.
-#'
-#' @param W A `predictor_hybrid` object.
-#' @param y A numeric response vector of length equal to number of samples.
-#'
-#' @return A matrix representing the corrected cross-covariance structure.
-#' @export
-get_pre_corrcov <- function(W, y){
-  n <- W$n_sample
-  K <- W$n_functional
-
-  # building blocks
-  ## C_J : C multiplied by J. Scalable to arbitrary K
-  C_J <- get_CJ(W)
-
-  ## covariance
-  J_Ct_y <- t(C_J) %*% y
-  Zt_y <- t(W$Z) %*% y
-
-  # V matrix
-  upper_left <- J_Ct_y %*% t(J_Ct_y)
-  upper_right <- J_Ct_y %*% t(Zt_y)
-  lower_left <- t(upper_right)
-  lower_right <- Zt_y %*% t(Zt_y)
-
-  V_star <- cbind(
-    rbind(upper_left, lower_left),
-    rbind(upper_right, lower_right)
-    )/(n^2)
-
-  return(V_star)
-  }
-```
-
-### main function (wrapper: get_pls_comp
-Computes the first PLS component from a hybrid predictor and response vector using regularization.
-
-- Inputs
-  - **`W`**: A `predictor_hybrid` object with functional and scalar predictors.
-  - **`y`**: A numeric response vector of length equal to `W$n_sample`.
-  - **`L`**: A Cholesky decomposition of a positive definite regularization matrix.
-- Output: 
-  - `xi_hat`: The first PLS component as a `predictor_hybrid` object
-  - `E`: The matrix `inv(L) %*% V_star %*% t(inv(L))`
-  - `V_star`: Cross-covariance matrix between predictors and response
-  - `eigen_val`: Leading eigenvalue of `E`
-```{r}
-#' Compute the First PLS Component from a Hybrid Predictor
-#'
-#' Computes the coefficients of the first Partial Least Squares (PLS) component based on 
-#' a hybrid predictor object and a response vector, using a regularized generalized eigenvalue problem.
-#'
-#' @param W A predictor_hybrid object containing both functional and scalar predictors.
-#' @param y A numeric response vector of length equal to the number of samples in W.
-#' @param L cholesky decompisition of a regularization matrix (typically positive definite) used in the generalized eigenproblem.
-#'
-#' @return A list with the following elements:
-#'
-#'   xi_hat: The estimated first PLS component as a predictor_hybrid object.
-#'   E: The generalized eigenvalue problem matrix E = inv(L) V* t(inv(L)).
-#'   V_star: The cross-covariance matrix between predictors and response.}
-#'   eigen_val: The leading eigenvalue of E.
-#' 
-#'
-#' @export
-get_pls_comp <- function(W, y, L){
-
-  V_star <- get_pre_corrcov(W, y)
-
-  #invL <- Matrix::chol2inv(L)
-  invL <- solve(L)
-  A <- V_star %*% t(invL)       # A = V* × t(inv(L))
-  E <- invL %*% A               # E = inv(L) × A
-
-  eigen_result <- eigen(E)
-  e <- eigen_result$vectors[, 1]
-  if (is.complex(e)){
-    print("stop")
-    return("stop")
-  }
-
-  xi_star <- t(invL) %*% e      # xi_star solves t(L) xi = e
-  xi_hat <- predictor_hybrid_from_coef(format = W, coef = xi_star)
-  return(xi_hat)
-}
-```
-
-## linear system method
-
-### helper: get_xi_hat_linear
-```{r}
-get_xi_hat_linear_pen <- function(W, y, lambda){
-  # new
-  ## step 1: inner products
+#' @param y A numeric vector of response values.
+#' @param lambda A numeric vector of smoothing parameters.
+#'
+#' @return A single-sample `predictor_hybrid` object representing the weight direction xi.
+#' @export
+get_xi_hat_linear_pen <- function(W, y, lambda) {
+
   n <- W$n_sample
@@
 
+  # --- Scalar Component ---
+  # Compute scalar weights: v = Z^T * y
   v <- t(W$Z) %*% y
+
+  # Initialize squared norm q with scalar part contribution
+  # q = ||xi||^2_pen = sum(v^2) + functional_parts
   q <- sum(v^2)
-  for (j in 1:K){
+
+  # --- Functional Components ---
+  for (j in 1:K) {
+    # Theta_t: coefficient matrix of the functional data (basis x samples)
     Theta_t <- W$functional_list[[j]]$coefs
+
+    # B: Gram matrix for the j-th basis
     B <- W$gram_list[[j]]
+
+    # Compute RHS of the linear system: u = B * Theta * y
+    # This represents the unpenalized gradient term
     u[[j]] <- B %*% Theta_t %*% y
 
-    # linear system
+    # Linear System Matrix: R = Gram + lambda * Penalty
     R <- W$gram_list[[j]] + lambda[j] * W$gram_deriv2_list[[j]]
+
+    # Solve for gamma_j: (Gram + Penalty) * gamma = Gram * Theta * y
     gamma[[j]] <- solve(R, u[[j]])
 
-     #q
-    q <- q + sum( gamma[[j]] * ( R %*% gamma[[j]] ))
-  }
-  d_vec <- c(do.call(c, gamma), v)  # or: unlist(d)
-  ## step 2: squared norm
-  d_vec <- d_vec/ sqrt(q)
+    # Update squared norm q:
+    # Add contribution gamma^T * R * gamma (penalized norm of functional weight)
+    q <- q + sum(gamma[[j]] * (R %*% gamma[[j]]))
+  }
+
+  # --- Combine and Normalize ---
+  # Flatten gamma list and append scalar weights v
+  d_vec <- c(do.call(c, gamma), v)
+
+  # Normalize the vector to have unit penalized norm
+  d_vec <- d_vec / sqrt(q)
+
+  # Reconstruct the result as a predictor_hybrid object
   xi_hat <- predictor_hybrid_from_coef(format = W, coef = d_vec)
+
   return(xi_hat)
@@
 
-the full vector of PLS scores $$\hat{\boldsymbol{\rho}}  = (\hat{\rho}_1, \ldots, \hat{\rho}_n)^\top$$
-	is computed through the following matrix multiplication:
-$$
-		\hat{\boldsymbol{\rho}}^\top = \sum_{k=1}^K ( \hat{\boldsymbol{\gamma}}_j )^\top B \, \Theta_j^\top + \boldsymbol{\zeta}^\top \mathbf{Z}^\top.
-$$	
-```{r}
-get_rho <- function(d_vec, W){
+### get_rho
+
+**Description:**
+Computes the vector of PLS scores  by projecting the hybrid predictor data  onto the weight direction vector  (which represents ).
+
+The projection is computed as:
+
+where:
+
+-  is the coefficient matrix for the -th functional predictor ().
+-  is the Gram matrix ().
+-  are the coefficients for the -th functional weight.
+-  are the coefficients for the scalar weight.
+
+**Inputs:**
+
+- `d_vec`: A numeric vector containing the concatenated coefficients for all functional and scalar weights.
+- `W`: A `predictor_hybrid` object providing the data and Gram matrices.
+
+**Output:**
+
+- A numeric vector of length  containing the PLS scores.
+
+```{r}
+#' Compute PLS Scores
+#'
+#' Projects the hybrid predictor data W onto the weight direction defined by d_vec
+#' to calculate the PLS scores.
+#'
+#' @param d_vec A numeric vector of concatenated coefficients (functional basis coeffs + scalar weights).
+#' @param W A `predictor_hybrid` object containing the data.
+#'
+#' @return A numeric vector of PLS scores (length n).
+#' @export
+get_rho <- function(d_vec, W) {
   K <- W$n_functional
-  M <- W$n_basis_list[[1]]
+  M <- W$n_basis_list[[1]] # Assumes same number of basis functions for all K
   n_scalar <- W$n_scalar
   n <- W$n_sample
+
+  # Initialize rho vector
   rho <- rep(0, n)
 
-  #functional part
-  for (j in 1:K){
-    start_index <- (j-1)*M + 1
-    end_index <- j*M
-    gamma_j <- d_vec[ start_index : end_index]
+  # --- Functional Part ---
+  # Iterate over functional predictors to compute inner products <X^(k), gamma^(k)>
+  for (j in 1:K) {
+    # Extract coefficients for the j-th functional weight
+    start_index <- (j - 1) * M + 1
+    end_index <- j * M
+    gamma_j <- d_vec[start_index:end_index]
+
+    # Get data coefficients (samples x basis)
     Theta_j <- t(W$functional_list[[j]]$coefs)
+
+    # Gram matrix
     B <- W$gram_list[[j]]
-    rho <- rho + Theta_j %*% B %*% gamma_j
-  }
-
-  #scalar part
-  rho <- rho + W$Z %*% d_vec[(K * M + 1):length(d_vec)]
-  return (as.vector(rho))
-}
-```
-
-```{r}
-library(fda)
-
-# --- Step 1: Simulate Data ---
-set.seed(111)
-
-n_sample <- 100
-n_scalar <- 2
-n_basis <- 20
-n_functional <- 2
-
-# Scalar predictors Z (centered)
-Z <- matrix(rnorm(n_sample * n_scalar), ncol = n_scalar)
-Z <- scale(Z, center = TRUE, scale = FALSE)
-
-# Create functional predictors (centered)
-basis <- create.bspline.basis(c(0, 1), nbasis = n_basis)
-functional_list <- list()
-for (j in 1:n_functional) {
-  coefs <- matrix(rnorm(n_basis * n_sample), nrow = n_basis)
-  fdobj <- fd(coef = coefs, basisobj = basis)
-  mean_fd <- mean.fd(fdobj)
-  mean_coef <- coef(mean_fd)
-  centered_coefs <- coefs - matrix(mean_coef, nrow = n_basis, ncol = n_sample)
-  functional_list[[j]] <- fd(coef = centered_coefs, basisobj = basis)
-}
-
-# --- Step 2: Construct hybrid object ---
-W <- predictor_hybrid(Z = Z, functional_list = functional_list)
-
-# --- Step 3: Simulate and center response ---
-total_coef_len <- sum(W$n_basis_list) + W$n_scalar
-true_coef <- rnorm(total_coef_len)
-
-# Flatten design matrix
-Xmat <- matrix(NA, n_sample, total_coef_len)
-for (i in 1:n_sample) {
-  W_i <- subset_predictor_hybrid(W, i)
-  func_coefs <- do.call(c, lapply(W_i$functional_list, function(fdobj) as.vector(coef(fdobj))))
-  Xmat[i, ] <- c(func_coefs, W_i$Z)
-}
-
-y <- Xmat %*% true_coef + rnorm(n_sample, sd = 0.1)
-y <- as.vector(scale(y, center = TRUE, scale = FALSE))
-
-# --- Step 4: Compute constraint matrix ---
-lambda <- rep(0, W$n_functional)
-#constr_mat <- get_constraint_matrix_hybrid(W, lambda)
-#L <- chol(constr_mat)
-
-# --- Step 5: Run eigen-based PLS ---
-W_template <- W  # prevent mutation
-
-pls_eig_result <- get_pls_comp(W, y, L)
-xi_hat_eig <- pls_eig_result$xi_hat
-
-xi_hat_pen <- get_xi_hat_linear_pen(W, y, lambda)
-xi_hat_lin_new <- get_xi_hat_linear_new(W, y)
-# Wrap into predictor_hybrid object using format template
-xi_hat_direct <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin)
-norm_val <- sqrt(inprod.predictor_hybrid(xi_hat_direct))
-xi_hat_direct <- scalar_mul.predictor_hybrid(xi_hat_direct,  1 / norm_val)
-xi_hat_direct_new <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin_new)
-
-cat(xi_hat_direct_new$functional_list[[1]]$coefs- xi_hat_direct$functional_list[[1]]$coefs)
-cat(xi_hat_direct_new$functional_list[[2]]$coefs- xi_hat_direct$functional_list[[2]]$coefs)
-
-```
-
-## Residualization
-
-### response residualization
-
-```{r}
-get_nu <- function(y, rho){
-            nu <- sum(y*rho) / sum(rho*rho)
+
+    # Update scores: rho += Theta * B * gamma
+    # (samples x basis) * (basis x basis) * (basis x 1) -> (samples x 1)
+    rho <- rho + Theta_j %*% (B %*% gamma_j)
+
+  }
+
+  # --- Scalar Part ---
+  # Extract scalar weights (the remaining coefficients in d_vec)
+  scalar_indices <- (K * M + 1):length(d_vec)
+  scalar_weights <- d_vec[scalar_indices]
+
+  # Update scores: rho += Z * weights
+  rho <- rho + W$Z %*% scalar_weights
+
+  return(as.vector(rho))
+}
+```
+
+## Response Residualization
+
+### get_nu
+
+**Description:**
+Calculates the scalar regression coefficient  obtained by regressing the response vector  onto the PLS score vector . This minimizes the least squares error .
+
+**Inputs:**
+
+- `y`: A numeric vector of response values.
+- `rho`: A numeric vector of PLS scores.
+
+**Output:**
+
+- A scalar value .
+```{r}
+#' Compute scalar regression coefficient (nu)
+#'
+#' Calculates the projection coefficient of the response vector y onto the score vector rho.
+#'
+#' @param y A numeric vector of response values.
+#' @param rho A numeric vector of PLS scores.
+#'
+#' @return A scalar regression coefficient.
+#' @export
+get_nu <- function(y, rho) {
+  # Compute numerator: inner product of y and rho
+  # Compute denominator: squared norm of rho
+  nu <- sum(y * rho) / sum(rho * rho)
   return(nu)
@@
 
-```{r}
-residualize_y <- function(y, rho, nu){
+### residualize_y
+
+**Description:**
+Computes the residual of the response vector  after removing the component explained by the current PLS score .
+
+**Inputs:**
+
+- `y`: The current response vector.
+- `rho`: The current PLS score vector.
+- `nu`: The regression coefficient computed by `get_nu`.
+
+**Output:**
+
+- A numeric vector of residuals.
+
+```{r}
+#' Residualize the response vector
+#'
+#' Subtracts the projection of y onto rho from y.
+#'
+#' @param y The current response vector.
+#' @param rho The current PLS score vector.
+#' @param nu The regression coefficient.
+#'
+#' @return The residualized response vector.
+#' @export
+residualize_y <- function(y, rho, nu) {
   y_next <- y - nu * rho
@@
 
-```{r}
-LSE_ptws <- function(input, rho) {
-  # old implementation
-            rho_norm_sq <- (Matrix::norm(rho, type = "2"))^2
-            nu <- as.numeric(t(rho) %*% input) / rho_norm_sq
-            return(nu)
-}
-
-```
-
-###  predictor residualization
-
-$$
-\widetilde{W}_i^{[l+1]} 
-			:= 	\widetilde{W}_i^{[l]}  - 
-			\widehat{\rho}_i^{[l]}
-			\hat{\delta}^{[l]},~\text{where}~
-			\delta^{[l]}
-			:= 
-			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
-			\sum_{i=1}^n 
-			\widehat{\rho}_i^{[l]}
-			\widetilde{W}_i^{[l]},
-$$
-
-```{r}
-get_delta <- function(W, rho){
+## Predictor Residualization
+
+### get_delta
+
+**Description:**
+Computes the hybrid regression coefficient  for regressing the predictor  onto the PLS scores .
+is a single-sample `predictor_hybrid` object representing the direction in the predictor space that corresponds to .
+
+**Inputs:**
+
+- `W`: A `predictor_hybrid` object containing  samples.
+- `rho`: A numeric vector of PLS scores (length ).
+
+**Output:**
+
+- A single-sample `predictor_hybrid` object .
+```{r}
+#' Compute hybrid regression coefficient (delta)
+#'
+#' Calculates the weighted average of the predictor observations W_i,
+#' weighted by the scores rho_i.
+#'
+#' @param W A `predictor_hybrid` object.
+#' @param rho A numeric vector of PLS scores.
+#'
+#' @return A single-sample `predictor_hybrid` object representing delta.
+#' @export
+get_delta <- function(W, rho) {
+  # Initialize delta with the first weighted observation: rho[1] * W[1]
   delta <- scalar_mul.predictor_hybrid(subset_predictor_hybrid(W, 1), rho[1])
+
+  # Iteratively add the remaining weighted observations: delta += rho[i] * W[i]
   for (i in 2:length(rho)) {
-  delta <- add.predictor_hybrid(delta, subset_predictor_hybrid(W, i),  rho[i]) 
-   } 
-  delta <- scalar_mul.predictor_hybrid(delta, 1/sum(rho*rho))
+    W_i <- subset_predictor_hybrid(W, i)
+    delta <- add.predictor_hybrid(delta, W_i, rho[i])
+  }
+
+  # Normalize by the squared norm of rho
+  delta <- scalar_mul.predictor_hybrid(delta, 1 / sum(rho * rho))
+
   return(delta)
@@
 
-```{r}
-residualize_predictor <- function(W, rho, delta){
+### residualize_predictor
+
+**Description:**
+Computes the residuals of the predictor object  by subtracting the component explained by .
+
+**Inputs:**
+
+- `W`: The current `predictor_hybrid` object.
+- `rho`: The current PLS score vector.
+- `delta`: The hybrid regression coefficient (from `get_delta`).
+
+**Output:**
+
+- A `predictor_hybrid` object containing the residualized predictors.
+```{r}
+#' Residualize the hybrid predictor
+#'
+#' Updates each observation in W by subtracting the projection onto rho (rho_i * delta).
+#'
+#' @param W The current `predictor_hybrid` object.
+#' @param rho The current PLS score vector.
+#' @param delta The hybrid regression coefficient (single-sample object).
+#'
+#' @return The residualized `predictor_hybrid` object.
+#' @export
+residualize_predictor <- function(W, rho, delta) {
   n <- length(rho)
   W_res <- W
-  for (i in 1:n){
+
+  # Iterate through each sample to compute residuals
+  for (i in 1:n) {
+    # Extract the i-th observation
     W_i <- subset_predictor_hybrid(W, i)
-    W_res_i <-subtr.predictor_hybrid(W_i, delta,  rho[i]) 
+
+    # Calculate residual: W_i_new = W_i - rho[i] * delta
+    W_res_i <- subtr.predictor_hybrid(W_i, delta, rho[i])
+
+    # Replace the observation in the result object
     W_res <- replace_obs_hybrid(W_res, i, W_res_i)
   }
+
   return(W_res)
@@
 
-### LSE_hybrid
-
-```{r}
-LSE_hybrid <- function(W, rho) {
-  # old implementation
-  C_star_J_star <- matrix(NA, nrow = W$n_sample, ncol = sum(W$n_basis_list) + W$n_scalar)
-  for (ii in (1 : W$n_functional)){
-    cumsum_n_basis_now <- sum(W$n_basis_list[1:ii])
-    n_basis_now <- W$n_basis_list[ii]
-    C_star_J_star[, (cumsum_n_basis_now - n_basis_now + 1) :cumsum_n_basis_now] <-
-      t(W$functional_list[[ii]]$coefs) %*% W$jacobian_list[[ii]]
-  }
-  C_star_J_star[ ,(sum(W$n_basis_list) + 1) : ncol(C_star_J_star)] <- W$Z
-  rho_t_C_star_J_star <- t(rho) %*% C_star_J_star
-
-  # matrices in the statement of Proposition 4
-  J_star <-as.matrix(get_jacobian_hybrid(W))
-  d_hat_star <- t( #basis coefficient of hybrid regression coefficientdelta
-    solve(
-      t((norm(rho, type="2"))^2 * J_star),
-      t(rho_t_C_star_J_star)
-      )
-    )
-  delta_hat <- hybrid_from_coef(W, d_hat_star) #hybrid regression coefficient
-  return(delta_hat)
-  }
-```
-
-# main algorithm
-
-```{r eval=FALSE, include=FALSE}
-#' @export
-fit.hybridPLS <- function(W, y, n_iter, lambda) {
+# Main algorithm
+
+### fit.hybridPLS
+
+**Description:**
+Implements the Hybrid Penalized Partial Least Squares (PLS) algorithm.
+This function iteratively extracts latent components that maximize the covariance between the hybrid predictors and the response, subject to roughness penalties.
+
+**Algorithm Steps:**
+For each iteration :
+
+1. **Weight Direction ():** Computes the penalized weight vector that maximizes covariance with the current response residual .
+2. **Scores ():** Projects the current predictor residuals  onto the weight direction to obtain PLS scores.
+3. **loadings ():** Computes the regression coefficients for projecting  and  onto the scores .
+4. **Deflation:** Updates the predictor  and response  by removing the variance explained by the current component (residualization).
+5. **Coefficient Update:** Computes the "whitened" direction  (transforming weights back to the original predictor space) and updates the cumulative regression coefficient .
+
+**Inputs:**
+
+- `W`: Initial `predictor_hybrid` object.
+- `y`: Numeric vector of response values.
+- `n_iter`: Integer specifying the number of PLS components to extract.
+- `lambda`: Numeric vector of smoothing parameters (one for each functional predictor).
+
+**Output:**
+
+- A list containing:
+- `rho`: List of score vectors for each component.
+- `xi`: List of weight directions (hybrid objects).
+- `W`: List of residualized predictor objects at each step.
+- `beta`: List of cumulative regression coefficients (hybrid objects) at each step.
+
+```{r}
+#' Fit Hybrid Penalized PLS with Optional Validation
+#'
+#' Runs the iterative PLS algorithm. If 'validation_data' is provided,
+#' it computes and stores the RMSE on the validation set for each component.
+#'
+#' @param W Initial `predictor_hybrid` object (Training).
+#' @param y Numeric vector of response values (Training).
+#' @param n_iter Integer, number of components to extract.
+#' @param lambda Numeric vector of smoothing parameters.
+#' @param validation_data (Optional) A list containing `W_test` (predictor_hybrid) and `y_test`.
+#'
+#' @return A list containing the model (rho, xi, beta) and optional `validation_rmse`.
+#' @export
+fit.hybridPLS <- function(W, y, n_iter, lambda, validation_data = NULL) {
   # 1. Initialize storage
   W_now <- rho <- xi <- delta <- nu <- iota <- beta <- list()
-
-  # 3. Initialize residuals
+  validation_rmse <- numeric(n_iter)
+
+  # 2. Initialize current state
   W_now[[1]] <- W
   y_now <- y
+
+  # 3. Main PLS Loop
   for (l in 1:n_iter) {
-    cat(paste(l, "th component", "\n"))
-
-    xi[[l]]  <- get_xi_hat_linear_pen(W_now[[l]], y_now, lambda) # PLS direction
-    rho[[l]] <- inprod.predictor_hybrid(W_now[[l]], xi[[l]]) #PLS score
-    delta[[l]] <- get_delta(W_now[[l]], rho[[l]]);  
-    W_now[[l + 1]] <- residualize_predictor(W_now[[l]], rho[[l]], delta[[l]]) # predictor residual
-    nu[[l]] <- get_nu(y_now, rho[[l]]); y_now <- residualize_y(y_now, rho[[l]], nu[[l]]) # response residual
-
+    # --- Step A: Weight Direction (xi) ---
+    xi[[l]] <- get_xi_hat_linear_pen(W_now[[l]], y_now, lambda)
+
+    # --- Step B: Scores (rho) ---
+    rho[[l]] <- inprod.predictor_hybrid(W_now[[l]], xi[[l]])
+
+    # --- Step C: Loadings (delta, nu) ---
+    delta[[l]] <- get_delta(W_now[[l]], rho[[l]])
+    nu[[l]] <- get_nu(y_now, rho[[l]])
+
+    # --- Step D: Deflation ---
+    W_now[[l + 1]] <- residualize_predictor(W_now[[l]], rho[[l]], delta[[l]])
+    y_now <- residualize_y(y_now, rho[[l]], nu[[l]])
+
+    # --- Step E: Cumulative Coefficient (Beta) ---
     iota[[l]] <- xi[[l]]
+
     if (l == 1) {
-      beta[[l]] <- scalar_mul.predictor_hybrid( iota[[l]], nu[[l]] )
+      beta[[l]] <- scalar_mul.predictor_hybrid(iota[[l]], nu[[l]])
     } else {
-      for (u in 1:(l - 1)) iota[[l]] <- subtr.predictor_hybrid( iota[[l]], iota[[u]], inprod.predictor_hybrid(delta[[u]], xi[[l]]))
+      for (u in 1:(l - 1)) {
+        adjustment <- inprod.predictor_hybrid(delta[[u]], xi[[l]])
+        iota[[l]] <- subtr.predictor_hybrid(iota[[l]], iota[[u]], adjustment)
+      }
       beta[[l]] <- add.predictor_hybrid(beta[[l - 1]], iota[[l]], nu[[l]])
     }
-  }
-  return (list(
+
+    # --- Step F: Validation (Optional) ---
+    if (!is.null(validation_data)) {
+      # Predict on test set using the current cumulative beta
+      y_pred_test <- inprod.predictor_hybrid(validation_data$W_test, beta[[l]])
+
+      # Compute RMSE (standardized scale usually, but here just raw RMSE)
+      validation_rmse[l] <- sqrt(mean((validation_data$y_test - y_pred_test)^2))
+    }
+  }
+
+  return(list(
     rho = rho,
     xi = xi,
-    W = W_now,
-    beta = beta
+    beta = beta,
+    validation_rmse = if (!is.null(validation_data)) validation_rmse else NULL
   ))
 }
-
-```
-
-```{r eval=FALSE, include=FALSE}
-#' @export
-fit.hybridPLS_eigen <- function(W, y, n_iter, lambda) {
-  # 1. Initialize storage
-  W_now <- rho <- xi <- delta <- nu  <- sigma <- eta <- list()
-
-  # 3. Initialize residuals
-  W_now[[1]] <- W
-  y_now <- y
-  final_succesful_iteration <- 0
-  constr_mat <- get_constraint_matrix_hybrid(W, lambda)
-  constr_mat_chol <- t(chol(constr_mat))
-  for (l in 1:n_iter) {
-    cat(paste(l, "th component", "\n"))
-
-    #xi[[l]]  <- get_xi_hat_linear_pen(W_now[[l]], y_now, lambda) # PLS direction
-    xi[[l]]  <- get_pls_comp(W_now[[l]], y_now, constr_mat_chol) # PLS direction
-    rho[[l]] <- inprod.predictor_hybrid(W_now[[l]], xi[[l]]) #PLS score
-    delta[[l]] <- get_delta(W_now[[l]], rho[[l]]);  
-    W_now[[l + 1]] <- residualize_predictor(W_now[[l]], rho[[l]], delta[[l]]) # predictor residual
-    nu[[l]] <- get_nu(y_now, rho[[l]]); y_now <- residualize_y(y_now, rho[[l]], nu[[l]]) # response residual
-
-    # Step 3: Orthogonalize and update prediction
-    #sigma[[l]] <- xi[[l]]
-    #if (l == 1) {
-    #  eta[[l]] <- scalar_mul(sigma[[l]], nu[[l]])
-    #} else {
-    #  for (u in 1:(l - 1)) {
-    #    sigma[[l]] <- subtr(sigma[[l]], sigma[[u]], hybrid_inner_prod(delta[[u]], xi[[l]]))
-    #  }
-    #  eta[[l]] <- add(eta[[l - 1]], sigma[[l]], nu[[l]])
-    #}
-  }
-  return (list(
-    rho = rho,
-    xi = xi,
-    W = W_now
+```
+
+```{r}
+# ==============================================================================
+# TEST SCRIPT FOR HYBRID PLS
+# ==============================================================================
+
+# Prerequisites
+library(fda)
+library(Matrix)
+
+# 1. DATA SIMULATION
+# ------------------------------------------------------------------------------
+set.seed(2025)
+n_sample <- 50
+n_scalar <- 3
+
+# --- Create Functional Predictor 1 (B-Spline Basis) ---
+nbasis1 <- nbasis2 <-  10
+basis1 <- create.bspline.basis(rangeval = c(0, 1), nbasis = nbasis1)
+# Generate random coefficients (nbasis x n_sample)
+coefs1 <- matrix(rnorm(nbasis1 * n_sample), nrow = nbasis1, ncol = n_sample)
+fd1 <- fd(coef = coefs1, basisobj = basis1)
+
+# --- Create Functional Predictor 2 (Fourier Basis) ---
+
+ # Generate random coefficients
+coefs2 <- matrix(rnorm(nbasis2 * n_sample), nrow = nbasis2, ncol = n_sample)
+fd2 <- fd(coef = coefs2, basisobj = basis1)
+
+# --- Create Scalar Predictors ---
+Z <- matrix(rnorm(n_sample * n_scalar), nrow = n_sample, ncol = n_scalar)
+
+# --- Construct the True Hybrid Predictor Object ---
+# (We need this to generate a 'true' y for testing)
+W_train <- predictor_hybrid(
+  Z = Z, 
+  functional_list = list(fd1, fd2), 
+  eval_point = seq(0, 1, length.out = 100)
+)
+
+# --- Generate Synthetic Response y ---
+# Let's create a random 'true' beta to generate y
+# True beta is just a random instance of a hybrid object
+true_beta_coefs <- rnorm(nbasis1 + nbasis2 + n_scalar)
+true_beta <- predictor_hybrid_from_coef(W_train, true_beta_coefs) # Create a single-sample hybrid beta
+
+# Calculate y = <W, beta> + noise
+y_clean <- inprod.predictor_hybrid(W_train, true_beta)
+y <- y_clean + rnorm(n_sample, sd = 0.5)
+
+message("Data generation complete.")
+message(paste("Samples:", n_sample))
+message(paste("Functional Predictors: 2 (Basis sizes:", nbasis1, ",", nbasis2, ")"))
+message(paste("Scalar Predictors:", n_scalar))
+
+# 2. RUNNING FIT.HYBRIDPLS
+# ------------------------------------------------------------------------------
+n_components <- 3
+# Lambda: Small smoothing penalty for demonstration (one per functional predictor)
+lambda_vec <- c(0.01, 0.01)
+
+message("\nRunning fit.hybridPLS...")
+start_time <- Sys.time()
+
+fit_result <- fit.hybridPLS(
+  W = W_train, 
+  y = y, 
+  n_iter = n_components, 
+  lambda = lambda_vec
+)
+
+end_time <- Sys.time()
+message(paste("Fitting complete in:", round(end_time - start_time, 4), "seconds."))
+
+# 3. VERIFICATION & INSPECTION
+# ------------------------------------------------------------------------------
+
+# --- A. Check Structure ---
+message("\n--- Structure Verification ---")
+if (length(fit_result$rho) == n_components && length(fit_result$beta) == n_components) {
+  message("PASS: Output list lengths match n_iter.")
+} else {
+  stop("FAIL: Output list lengths do not match n_iter.")
+}
+
+# --- B. Check Beta Dimensions ---
+final_beta <- fit_result$beta[[n_components]]
+if (inherits(final_beta, "predictor_hybrid")) {
+  message("PASS: Final beta is a 'predictor_hybrid' object.")
+}
+
+# --- C. Prediction & Accuracy ---
+# Calculate fitted values using the beta from the last component
+# y_hat = <W_train, beta_final>
+y_hat <- inprod.predictor_hybrid(W_train, final_beta)
+
+# Calculate MSE and Correlation
+mse <- mean((y - y_hat)^2)
+cor_y <- cor(y, y_hat)
+
+message("\n--- Model Performance ---")
+message(paste("Mean Squared Error (MSE):", round(mse, 4)))
+message(paste("Correlation (y vs y_hat):", round(cor_y, 4)))
+
+# --- D. Visual Check (Optional Plotting) ---
+if(interactive()) {
+  plot(y, y_hat, main = "Observed vs Fitted", xlab = "Observed y", ylab = "Fitted y")
+  abline(0, 1, col = "red", lty = 2)
+  text(min(y), max(y_hat), paste("Cor =", round(cor_y, 3)), adj = c(0, 1))
+}
+
+# 4. COMPONENT ANALYSIS (SCORES)
+# ------------------------------------------------------------------------------
+message("\n--- Component Analysis ---")
+# Check orthogonality of scores (approximate, due to deflation method)
+rho_matrix <- do.call(cbind, fit_result$rho)
+cor_scores <- cor(rho_matrix)
+print(round(cor_scores, 2))
+message("(Note: Scores might not be perfectly orthogonal depending on the specific PLS deflation scheme used, but off-diagonals should be relatively low or structured.)")
+
+message("\nTest script completed successfully.")
+```
+
+```{r}
+# ==============================================================================
+# TEST: ORTHOGONALITY PROPERTIES OF HYBRID PLS (Shared Basis)
+# ==============================================================================
+
+# Prerequisites
+library(fda)
+library(Matrix)
+
+# 1. SETUP & DATA SIMULATION
+# ------------------------------------------------------------------------------
+set.seed(2025) # Fixed seed for reproducibility
+
+# Dimensions
+n_sample <- 50
+n_scalar <- 5
+nbasis   <- 5
+
+# --- Create Shared Basis (B-spline) ---
+# Using the same basis for both functional predictors as requested
+basis_shared <- create.bspline.basis(rangeval = c(0, 1), nbasis = nbasis)
+
+# --- Generate Functional Predictors ---
+# Functional Predictor 1
+coefs1 <- matrix(rnorm(nbasis * n_sample), nrow = nbasis, ncol = n_sample)
+fd1 <- fd(coef = coefs1, basisobj = basis_shared)
+
+# Functional Predictor 2 (Using same basis, different coefficients)
+coefs2 <- matrix(rnorm(nbasis * n_sample), nrow = nbasis, ncol = n_sample)
+fd2 <- fd(coef = coefs2, basisobj = basis_shared)
+
+# --- Generate Scalar Predictors ---
+Z <- matrix(rnorm(n_sample * n_scalar), nrow = n_sample, ncol = n_scalar)
+
+# --- Construct Hybrid Object ---
+W <- predictor_hybrid(
+  Z = Z, 
+  functional_list = list(fd1, fd2), 
+  eval_point = seq(0, 1, length.out = 100)
+)
+
+# --- Generate Response ---
+# Random response is sufficient to test orthogonality mechanics
+y <- rnorm(n_sample)
+
+# --- Parameters ---
+n_comp <- 6
+lambda <- c(0.5, 2) # Smoothing penalties for the two functional predictors
+
+# 2. RUN PLS ALGORITHM
+# ------------------------------------------------------------------------------
+message(paste("Running fit.hybridPLS with", n_comp, "components..."))
+fit <- fit.hybridPLS(W, y, n_iter = n_comp, lambda = lambda)
+
+# 3. VERIFY PROPOSITION 1: Orthonormality of Directions (xi)
+#    Note: For NIPALS (Predictor Deflation), we expect this to FAIL.
+# ------------------------------------------------------------------------------
+message("\n--- Testing Proposition 1: Orthonormality of Directions (xi) ---")
+
+xi_orth_matrix <- matrix(0, n_comp, n_comp)
+
+for (i in 1:n_comp) {
+  for (j in 1:n_comp) {
+    xi_orth_matrix[i, j] <- inprod_pen.predictor_hybrid(
+      fit$xi[[i]], 
+      fit$xi[[j]], 
+      lambda
+    )
+  }
+}
+
+print(round(xi_orth_matrix, 4))
+
+# Check against Identity matrix
+is_orthonormal_xi <- all.equal(xi_orth_matrix, diag(n_comp), tolerance = 5e-2)
+
+if (isTRUE(is_orthonormal_xi)) {
+  message("✅ PASS: Directions are Orthonormal.")
+} else {
+  message("❌ FAIL: Directions are NOT orthonormal (Expected for NIPALS algorithm).")
+  message("   (The off-diagonal values indicate correlation between weight vectors.)")
+}
+
+# 4. VERIFY PROPOSITION 2: Orthogonality of Scores (rho)
+#    Note: For NIPALS, we expect this to PASS.
+# ------------------------------------------------------------------------------
+message("\n--- Testing Proposition 2: Orthogonality of Scores (rho) ---")
+
+# Combine list of score vectors into a matrix (n_sample x n_comp)
+rho_matrix <- do.call(cbind, fit$rho)
+
+# Compute Correlation Matrix
+rho_cor_matrix <- cor(rho_matrix)
+
+# Print rounded correlation matrix
+print(round(rho_cor_matrix, 4))
+
+# Check off-diagonals (exclude diagonal 1s)
+off_diag_vals <- rho_cor_matrix[upper.tri(rho_cor_matrix)]
+off_diag_max <- max(abs(off_diag_vals))
+
+# Tolerance check
+if (off_diag_max < 5e-2) {
+  message("✅ PASS: Scores are Orthogonal (Max correlation ~ 0).")
+  message("   This confirms the algorithm correctly implements Predictor Deflation.")
+} else {
+  message(paste("⚠️  NOTE: Max off-diagonal correlation is", round(off_diag_max, 6)))
+  message("          This is higher than expected. Check deflation logic.")
+}
+
+# Optional: Visual check of score orthogonality
+if (interactive()) {
+  image(1:n_comp, 1:n_comp, abs(rho_cor_matrix), 
+        main = "Abs(Correlation) of PLS Scores",
+        xlab = "Component", ylab = "Component",
+        col = hcl.colors(12, "Blues", rev = TRUE))
+}
+```
+
+# Simulation tools
+
+## sample splitting
+
+### create_idx_train_test
+
+**Description:**
+Randomly splits the indices of a dataset into training and testing sets based on a specified ratio. This function ensures that the indices are sorted and returned as a list containing both sets.
+
+**Usage:**
+
+```r
+create_idx_train_test(n_sample, train_ratio)
+
+```
+
+**Arguments:**
+
+- `n_sample`: Integer. The total number of samples in the dataset.
+- `train_ratio`: Numeric. The proportion of samples to include in the training set (between 0 and 1).
+
+**Value:**
+
+- A list containing:
+  - `idx_train`: A sorted integer vector of training indices.
+  - `idx_test`: A sorted integer vector of testing indices.
+
+```{r}
+#' Split Sample Indices into Train and Test Sets
+#'
+#' Randomly partitions the indices of a dataset into training and testing sets.
+#'
+#' @param n_sample Integer. The total number of samples.
+#' @param train_ratio Numeric. The proportion of samples for the training set (0 to 1).
+#'
+#' @return A list with named elements `idx_train` and `idx_test`.
+#' @export
+create_idx_train_test <- function(n_sample, train_ratio) {
+  # Calculate number of training samples
+  n_train <- floor(n_sample * train_ratio)
+
+  # Sample indices without replacement
+  idx_train <- sort(sample(seq_len(n_sample), n_train, replace = FALSE))
+
+  # The remaining indices form the test set
+  idx_test <- sort(setdiff(seq_len(n_sample), idx_train))
+
+  return(list(
+    idx_train = idx_train,
+    idx_test = idx_test
   ))
 }
-
-```
-
-```{r}
-inprod.predictor_hybrid(res$W[[5]], res$xi[[3]])
-
-sum(y * inprod.predictor_hybrid(res$W[[5]], res$xi[[3]]))
-
-inprod_pen.predictor_hybrid(res$xi[[1]], res$xi[[8]], lambda) - inprod_pen.predictor_hybrid(res_eigen$xi[[1]], res_eigen$xi[[8]], lambda)
-inprod_pen.predictor_hybrid(res$xi[[1]], res$xi[[8]], 10*lambda) - inprod_pen.predictor_hybrid(res_eigen$xi[[1]], res_eigen$xi[[8]], 10*lambda)
-inprod_pen.predictor_hybrid(res$xi[[1]], res$xi[[8]], lambda/10) - inprod_pen.predictor_hybrid(res_eigen$xi[[1]], res_eigen$xi[[8]], lambda/10)
-sum(y * inprod.predictor_hybrid(res$W[[8]], res$xi[[1]])) - sum(y * inprod.predictor_hybrid(res_eigen$W[[8]], res_eigen$xi[[1]]))
-
-inprod_pen.predictor_hybrid(res$xi[[3]], res$xi[[4]], lambda) - inprod_pen.predictor_hybrid(res_eigen$xi[[3]], res_eigen$xi[[4]], lambda)
-inprod_pen.predictor_hybrid(res$xi[[3]], res$xi[[4]], 10*lambda) - inprod_pen.predictor_hybrid(res_eigen$xi[[3]], res_eigen$xi[[4]], 10*lambda)
-inprod_pen.predictor_hybrid(res$xi[[3]], res$xi[[4]], lambda/10)
-sum(y * inprod.predictor_hybrid(res$W[[3]], res$xi[[1]]))
-
-inprod_pen.predictor_hybrid(res$xi[[5]], res$xi[[10]], lambda)
-inprod_pen.predictor_hybrid(res$xi[[5]], res$xi[[10]], 10*lambda)
-inprod_pen.predictor_hybrid(res$xi[[5]], res$xi[[10]], lambda/10)
-sum(y * inprod.predictor_hybrid(res$W[[5]], res$xi[[1]]))
-
-inprod_pen.predictor_hybrid(res$xi[[4]], res$xi[[4]], lambda)
-inprod_pen.predictor_hybrid(res$xi[[4]], res$xi[[4]], lambda/10)
-inprod_pen.predictor_hybrid(res$xi[[4]], res$xi[[4]], 10*lambda )
-
-```
-
-```{r}
-lambda <- c(0.5,0.5)
-L=8
-res <- fit.hybridPLS(W,y,L, lambda)
-res_eigen <- fit.hybridPLS_eigen(W,y,L, lambda)
-```
-
-### nipals_pen_hybrid
-
-- depends on:
-  - 'get_constraint_matrix_hybrid'
-  - 'get_pls_comp'
-  - 'hybrid_inner_prod'
-  - 'LSE_hybrid'
-
-```{r eval=FALSE, include=FALSE}
-#' Iterative Penalized NIPALS Algorithm for Hybrid PLS
-#'
-#' Performs iterative extraction of PLS components using a penalized NIPALS algorithm
-#' for hybrid predictor objects that include both scalar and functional data.
-#'
-#' At each iteration:
-#' \enumerate{
-#'   \item Computes the first penalized PLS component using \code{get_pls_comp}.
-#'   \item Computes PLS scores via hybrid inner products.
-#'   \item Residualizes both predictors and response with respect to the extracted scores.
-#'   \item Orthogonalizes and accumulates loading vectors to construct final linear predictors.
-#' }
-#' The same constraint matrix (computed once) is used across all iterations.
-#'
-#' @param W A \code{predictor_hybrid} object containing scalar and functional predictors.
-#' @param y A numeric response vector of length equal to \code{W$n_sample}.
-#' @param n_iter An integer specifying the number of PLS components (iterations) to compute.
-#' @param lambda A numeric vector of smoothing parameters (length = number of functional predictors).
-#' @param verbose Logical; if \code{TRUE}, prints progress for each component.
-#'
-#' @return This function operates by side effects. Internally, it constructs and updates:
-#' \itemize{
-#'   \item \code{xi}, \code{rho}, \code{delta}, \code{nu}: component vectors and regression effects,
-#'   \item \code{sigma}, \code{eta}: orthogonalized components and accumulated prediction functions,
-#'   \item \code{W_now}, \code{resid_y}: residualized predictor and response at each iteration,
-#'   \item \code{E}, \code{V_star}, \code{eigen_val}: matrices for monitoring stability and eigenvalue progress.
-#' }
-#' The final number of successful iterations is tracked via \code{final_succesful_iteration}.
-#'
-#' @export
-nipals_pen_hybrid <- function(W, y, n_iter, lambda, verbose) {
-  # 1. Initialize storage
-  rho <- xi <- delta <- nu  <- sigma <- eta <- list()
-  E <- V_star <- eigen_val <- list()
-  fitted_value_W <- fitted_value_y <- list()
-  resid_y <- W_now <- list()
-  first_eigen_val <- mse_W <- mse_y <- rep(NA, n_iter)
-
-  # 2. Compute and store the constraint matrix once
-  constr_mat <- get_constraint_matrix_hybrid(W, lambda)
-  constr_mat_chol <- t(chol(constr_mat))
-
-  # 3. Initialize residuals
-  W_now[[1]] <- W
-  y_now <- y
-  final_succesful_iteration <- 0
-
-  for (l in 1:n_iter) {
-    if (verbose) cat(paste(l, "th component", "\n"))
-
-    # Step 1: Compute penalized PLS direction and score
-    pls_result_now <- get_pls_comp(W_now[[l]], y_now, constr_mat_chol, verbose)
-    if (!is.list(pls_result_now)) break
-
-    xi[[l]] <- pls_result_now$xi
-    rho[[l]] <- hybrid_inner_prod(W_now[[l]], xi[[l]])
-
-    # Step 2: Residualize predictor and response
-    delta[[l]] <- LSE_hybrid(W_now[[l]], rho[[l]])
-    fitted_value_W[[l]] <- fitted_value(delta[[l]], rho[[l]])
-    W_now[[l + 1]] <- subtr(W_now[[l]], fitted_value_W[[l]])
-
-    nu[[l]] <- LSE_ptws(y_now, rho[[l]])
-    fitted_value_y[[l]] <- nu[[l]] * rho[[l]]
-    y_now <- y_now - fitted_value_y[[l]]
-    resid_y[[l]] <- y_now
-
-    # Step 3: Orthogonalize and update prediction
-    sigma[[l]] <- xi[[l]]
-    if (l == 1) {
-      eta[[l]] <- scalar_mul(sigma[[l]], nu[[l]])
-    } else {
-      for (u in 1:(l - 1)) {
-        sigma[[l]] <- subtr(sigma[[l]], sigma[[u]], hybrid_inner_prod(delta[[u]], xi[[l]]))
-      }
-      eta[[l]] <- add(eta[[l - 1]], sigma[[l]], nu[[l]])
-    }
-
-    # Record diagnostics
-    E[[l]] <- pls_result_now$E
-    V_star[[l]] <- pls_result_now$V_star
-    eigen_val[[l]] <- pls_result_now$eigen_val
-    first_eigen_val[l] <- eigen_val[[l]][1]
-    final_succesful_iteration <- l
-  }
-}
-
-```
-
-# Simulation tools
-
-## sample splitting and normalization
-
-```{r}
-create_idx_train_test <-function(n_sample, train_ratio){
-  n_train <- floor(n_sample*train_ratio)
-  idx_train <- sort(sample(n_sample,n_train, replace=F))
-  idx_test <- sort((1 : n_sample)[-idx_train])
-  return(list(
-    idx_train = idx_train, idx_test = idx_test
-  ))
-}
-```
-
-```{r}
-#' @title Generate Train Indices
-#' @description Generates train/test split indices.
+```
+
+### get_idx_train
+
+**Description:**
+A simplified version of the splitting function that returns only the training indices. Useful when the testing set is defined implicitly as the complement or not immediately needed.
+
+**Usage:**
+
+```r
+get_idx_train(n_sample, train_ratio)
+
+```
+
+**Arguments:**
+
+- `n_sample`: Integer. The total number of samples.
+- `train_ratio`: Numeric. The proportion of samples for the training set.
+
+**Value:**
+
+- A sorted integer vector of training indices.
+
+```{r}
+#' Generate Train Indices
+#'
+#' Randomly generates a sorted vector of indices for a training set.
+#'
 #' @param n_sample Integer. Number of samples.
 #' @param train_ratio Numeric. Ratio of train samples.
-#' @return Vector of train indices.
+#' @return Vector of sorted train indices.
+#' @export
 get_idx_train <- function(n_sample, train_ratio) {
   n_train <- floor(n_sample * train_ratio)
-  idx_train <- sort(sample(n_sample, n_train, replace = FALSE))
+  idx_train <- sort(sample(seq_len(n_sample), n_train, replace = FALSE))
   return(idx_train)
@@
 
-```{r}
-create_idx_kfold <- function(n_sample, n_fold){
-  idx_list <- caret::createFolds( (1 : n_sample), k = n_fold, list = TRUE, returnTrain = FALSE)
-  idx_list_list <- list()
-  for (i in 1:length(idx_list)){
+### create_idx_kfold
+
+**Description:**
+Generates indices for K-fold cross-validation. It relies on the `caret` package to create balanced folds and organizes them into pairs of training and validation indices for each fold.
+
+**Usage:**
+
+```r
+create_idx_kfold(n_sample, n_fold)
+
+```
+
+**Arguments:**
+
+- `n_sample`: Integer. The total number of samples.
+- `n_fold`: Integer. The number of folds to create.
+
+**Value:**
+
+- A list of length `n_fold`. Each element is a list containing:
+  - `idx_train`: Indices for training in this fold.
+  - `idx_valid`: Indices for validation in this fold.
+
+```{r}
+#' Generate K-Fold Cross-Validation Indices
+#'
+#' Creates a list of training and validation indices for K-fold cross-validation.
+#' Uses `caret::createFolds` to ensure stratified or random splitting.
+#'
+#' @param n_sample Integer. The total number of samples.
+#' @param n_fold Integer. The number of folds.
+#'
+#' @return A list of lists, where each sub-list contains `idx_train` and `idx_valid`.
+#' @export
+create_idx_kfold <- function(n_sample, n_fold) {
+  # Generate folds using caret (returns validation indices by default)
+  idx_list <- caret::createFolds(seq_len(n_sample), k = n_fold, list = TRUE, returnTrain = FALSE)
+
+  idx_list_list <- vector("list", length(idx_list))
+
+  for (i in seq_along(idx_list)) {
     valid_hyper_index <- idx_list[[i]]
-    train_hyper_index <- (1 : n_sample)[-valid_hyper_index]
-    idx_list_list[[i]] <- list("idx_train" = train_hyper_index, "idx_valid" = valid_hyper_index)
-  }
+    # Training set is the complement of the validation set
+    train_hyper_index <- setdiff(seq_len(n_sample), valid_hyper_index)
+
+    idx_list_list[[i]] <- list(
+      "idx_train" = train_hyper_index, 
+      "idx_valid" = valid_hyper_index
+    )
+  }
+
   return(idx_list_list)
@@
 
-```{r}
-n_sample.fd <- function(fd_obj){
-  length(fd_obj$fdnames$reps)
+### n_sample.fd
+
+**Description:**
+Extracts the number of samples (replications) from a functional data object (`fd` class from the `fda` package). This implementation robustly checks the dimensions of the coefficient matrix.
+
+**Usage:**
+
+```r
+n_sample.fd(fd_obj)
+
+```
+
+**Arguments:**
+
+- `fd_obj`: An object of class `fd`.
+
+**Value:**
+
+- Integer. The number of samples (curves) in the object.
+
+```{r}
+#' Get Number of Samples from an fd Object
+#'
+#' Extracts the number of observations (replications) stored in a functional data object.
+#'
+#' @param fd_obj An object of class `fd`.
+#' @return Integer representing the number of samples.
+#' @export
+n_sample.fd <- function(fd_obj) {
+  if (!inherits(fd_obj, "fd")) {
+    stop("Input must be of class 'fd'.")
+  }
+  # The coefficient matrix has dimensions (nbasis x n_sample)
+  return(ncol(fd_obj$coefs))
 }
@@
 
-Splits functional predictors, scalar predictors, and response into train and test sets.
+**Description:**
+Splits a `predictor_hybrid` object and a corresponding response vector into training and testing sets based on a specified ratio.
+This function ensures that both the scalar matrix and the list of functional predictors are subsetted consistently.
+
+**Inputs:**
+
+- `W_hybrid`: A `predictor_hybrid` object containing the covariates.
+- `response`: A numeric vector of response values.
+- `train_ratio`: A numeric scalar (0 < ratio < 1) determining the size of the training set.
+
+**Output:**
+
+- A list containing:
+  - `predictor_train`: The `predictor_hybrid` object for training.
+  - `predictor_test`: The `predictor_hybrid` object for testing.
+  - `response_train`: The response vector for training.
+  - `response_test`: The response vector for testing.
 
@@
 #'
-#' Splits the hybrid predictor object and the response vector into training and
-#' testing sets based on a given training ratio.
-#'
-#' @param W_hybrid predictor_hybrid object containing all functional and scalar data.
-#' @param response Vector. The response variable corresponding to the samples in W_hybrid.
-#' @param train_ratio Numeric scalar between 0 and 1 indicating the proportion of data to use for training.
-#' @return List containing split train and test sets for all components.
+#' Randomly partitions the hybrid predictor object and response vector into 
+#' training and testing sets based on a given ratio. Handles any number of 
+#' functional predictors.
+#'
+#' @param W_hybrid A `predictor_hybrid` object containing all functional and scalar data.
+#' @param response A numeric vector. The response variable corresponding to the samples in W_hybrid.
+#' @param train_ratio A numeric scalar between 0 and 1 indicating the proportion of data to use for training.
+#'
+#' @return A list containing split train and test sets for predictors and response.
 #' @export
 split.all <- function(W_hybrid, response, train_ratio) {
-  # --- Type and Ratio Checks ---
-  stopifnot(
-    "'W_hybrid' must be a predictor_hybrid object" = inherits(W_hybrid, "predictor_hybrid"),
-    "'response' must be a vector" = is.vector(response),
-    "Response length must match hybrid sample size" = length(response) == W_hybrid$n_sample,
-    "'train_ratio' must be between 0 and 1" = is.numeric(train_ratio) && train_ratio > 0 && train_ratio < 1
-  )
+  # --- Input Validation ---
+  if (!inherits(W_hybrid, "predictor_hybrid")) {
+    stop("'W_hybrid' must be a predictor_hybrid object.")
+  }
+  if (!is.vector(response) && !is.factor(response)) {
+    stop("'response' must be a vector.")
+  }
+  if (length(response) != W_hybrid$n_sample) {
+    stop("Response length must match the number of samples in W_hybrid.")
+  }
+  if (!is.numeric(train_ratio) || train_ratio <= 0 || train_ratio >= 1) {
+    stop("'train_ratio' must be a numeric value strictly between 0 and 1.")
+  }
 
@@
 
-  # Generate random indices for training set
-  # Using 1:N ensures indices are always valid
-  train_idx <- sample(1:N, N_train)
-  test_idx <- (1:N)[-train_idx]
-
-  W_train <- predictor_hybrid(
-    W_hybrid$Z[train_idx, , drop = FALSE],
-    list(
-      W_hybrid$functional_list[[1]][train_idx],
-      W_hybrid$functional_list[[2]][train_idx]
-    )
-  )
-
-  W_test <- predictor_hybrid(
-    W_hybrid$Z[test_idx, , drop = FALSE],
-    list(
-      data_fun_1_test = W_hybrid$functional_list[[1]][test_idx],
-    data_fun_2_test = W_hybrid$functional_list[[2]][test_idx]
-    )
-  )
-
-  return( 
-    list(
+  # Generate random indices
+  # set.seed() should be called by the user before this function if reproducibility is needed
+  train_idx <- sort(sample(seq_len(N), N_train))
+  test_idx  <- sort(setdiff(seq_len(N), train_idx))
+
+  # --- Subset Scalar Predictors ---
+  Z_train <- W_hybrid$Z[train_idx, , drop = FALSE]
+  Z_test  <- W_hybrid$Z[test_idx,  , drop = FALSE]
+
+  # --- Subset Functional Predictors ---
+  # Use lapply to handle any number of functional predictors (K)
+  # The '[' operator on an fd object subsets the samples (replicates)
+  fun_list_train <- lapply(W_hybrid$functional_list, function(fd_obj) fd_obj[train_idx])
+  fun_list_test  <- lapply(W_hybrid$functional_list, function(fd_obj) fd_obj[test_idx])
+
+  # --- Reconstruct Hybrid Objects ---
+  # We reuse the original evaluation points
+  W_train <- predictor_hybrid(Z = Z_train, functional_list = fun_list_train, eval_point = W_hybrid$eval_point)
+  W_test  <- predictor_hybrid(Z = Z_test,  functional_list = fun_list_test,  eval_point = W_hybrid$eval_point)
+
+  return(list(
     predictor_train = W_train,
-    predictor_test = W_test ,
+    predictor_test  = W_test,
     response_train  = response[train_idx],
-    response_test = response[test_idx]
+    response_test   = response[test_idx],
+    train_idx       = train_idx, # Useful to return indices for reference
+    test_idx        = test_idx
   ))
@@
 
+## normalization
+
+ The goal is to perform a two-step standardization: first normalizing *within* each data type (functional vs.
+scalar) to account for unit differences, and second normalizing *between* the two types to balance their variances for the PLS framework.
+
 ### curve_normalize
-Subtracts the mean function and divides by a scaling constant (deno). This implementation does not use the native fda S3 methods (minus.fd and times.fd), since they do not broadcast well.
-```{r}
-#' 
-#' @export
-curve_normalize <- function(functional, mean_functional, deno){
-  # operation also takes care of the original_X
-
-  functional_normalized <- fd(coef =
-                                coef(functional) - coef(mean_functional) %*% matrix(1, ncol = ncol(coef(functional))),
+
+**Description:**
+Performs pointwise centering and scalar scaling on a functional data object.
+It subtracts a mean function and divides by a scaling constant (denominator).
+This implementation manually broadcasts the mean subtraction to ensure compatibility with `fda` objects where standard `minus.fd` can sometimes struggle with broadcasting single mean functions across multiple samples.
+
+**Usage:**
+
+```r
+curve_normalize(functional, mean_functional, deno)
+
+```
+
+**Arguments:**
+
+- `functional`: The `fd` object to be normalized.
+- `mean_functional`: An `fd` object representing the mean (centroid) to subtract.
+- `deno`: A numeric scalar scaling factor (e.g., total standard deviation).
+
+**Value:**
+
+- A normalized `fd` object.
+
+```{r}
+#' Normalize a functional data object
+#'
+#' Subtracts a mean function and divides by a scalar constant.
+#' Manual broadcasting is used to ensure robust subtraction across samples.
+#'
+#' @param functional An `fd` object to normalize.
+#' @param mean_functional An `fd` object representing the mean.
+#' @param deno A numeric scalar for scaling (division).
+#'
+#' @return A normalized `fd` object.
+#' @export
+curve_normalize <- function(functional, mean_functional, deno) {
+  # Replicate the mean coefficients to match the number of samples in 'functional'
+  # This creates a matrix of identical mean columns for broadcasting
+  mean_coefs_matrix <- coef(mean_functional) %*% matrix(1, ncol = ncol(coef(functional)))
+
+  # Subtract mean and create new fd object
+  functional_normalized <- fd(
+    coef = coef(functional) - mean_coefs_matrix,
     basisobj = functional$basis
-                              )#numerator
-  functional_normalized <- times.fd(1/deno, functional_normalized)
+  )
+
+  # Apply scaling factor
+  # times.fd usually handles scalar multiplication well
+  functional_normalized <- times.fd(1 / deno, functional_normalized)
+
   return(functional_normalized)
@@
 ### curve_normalize_train_test
-Normalizes the functional components of both the training and testing 'predictor_hybrid' objects using the mean and standard deviation derived ONLY from the training data.
-The scalar components (Z) are left unchanged.
-
-```{r}
-#' Normalize Functional Predictors in Hybrid Objects (Train/Test Split)
+
+**Description:**
+Standardizes the *functional* components of hybrid predictors.
+It centers them to have mean zero and scales them to have unit integrated variance.
+Crucially, the mean and standard deviation are derived **only from the training data** to prevent data leakage.
+These training statistics are then applied to normalize the test set.
+
+**Usage:**
+
+```r
+curve_normalize_train_test(train, test)
+
+```
+
+**Arguments:**
+
+- `train`: A `predictor_hybrid` object (training set).
+- `test`: A `predictor_hybrid` object (test set).
+
+**Value:**
+
+- A list containing the normalized training and testing objects, along with the scaling factors used.
+
+```{r}
+#' Normalize Functional Predictors (Train/Test Split)
+#'
+#' Standardizes functional predictors to have mean zero and unit integrated variance.
+#' Statistics (mean and SD) are computed from the training set and applied to the test set.
+#'
 #' @param train A `predictor_hybrid` object representing the training set.
 #' @param test A `predictor_hybrid` object representing the testing set.
+#'
 #' @return A list containing:
-#'   train: The normalized training `predictor_hybrid` object.}
-#'   test: The normalized testing `predictor_hybrid` object.}
-#'   deno_train: A numeric vector of scaling factors used for each functional predictor.}
+#'   \item{predictor_train}{The normalized training object.}
+#'   \item{predictor_test}{The normalized testing object.}
+#'   \item{mean_train}{List of mean functions used for centering.}
+#'   \item{deno_train}{Vector of scaling factors used.}
 #' @export
 curve_normalize_train_test <- function(train, test) {
-  # --- Type Checks ---
   stopifnot(
-    "'train' must be of class 'predictor_hybrid'" = inherits(train, "predictor_hybrid"),
-    "'test' must be of class 'predictor_hybrid'" = inherits(test, "predictor_hybrid"),
-    "Mismatch in number of functional predictors" = train$n_functional == test$n_functional
+    inherits(train, "predictor_hybrid"),
+    inherits(test, "predictor_hybrid"),
+    train$n_functional == test$n_functional
   )
@@
 
-  # Iterate through each functional predictor (k)
+  # Iterate through each functional predictor
   for (k in seq_len(train$n_functional)) {
-    # 1. Determine centering and scaling factors from the TRAINING data only
+    # 1. Compute Statistics from TRAINING data
     train_fd <- train$functional_list[[k]]
 
-    # Calculate the mean function for centering
     mean_train[[k]] <- fda::mean.fd(train_fd)
-
-    # Calculate the standard deviation function
     sd_train <- fda::sd.fd(train_fd)
 
-    # Calculate the scaling factor (L2 norm of the standard deviation function)
+    # Scaling factor is the L2 norm of the standard deviation function
     deno_train[k] <- sqrt(fda::inprod(sd_train, sd_train))
 
-    # Ensure scaling factor is positive
+    # Safety check for zero variance
     if (deno_train[k] <= 1e-10) {
-      warning(paste("Scaling factor for functional predictor", k, "is near zero. Skipping normalization for this predictor."))
-      deno_train[k] <- 1 # Set to 1 to prevent division by zero, effectively no normalization
-    }
-
-    # 2. Normalize the TRAINING set
+      warning(paste("Functional predictor", k, "has near-zero variance. Skipping scaling."))
+      deno_train[k] <- 1 
+    }
+
+    # 2. Normalize TRAINING set
     train_normalized$functional_list[[k]] <- curve_normalize(
-      train_fd, # Use original train data
+      train_fd, 
       mean_train[[k]], 
@@
 
-    # 3. Normalize the TEST set (using train factors to prevent leakage)
-    test_normalized$functional_list[[k]] <-
-      curve_normalize(
-        test$functional_list[[k]], # Use original test data
-        mean_train[[k]], # Centered by training mean
-        deno_train[k] # Scaled by training SD
-      )
-  }
-  # Return the modified hybrid objects and the scaling factors
-  return( list(
+    # 3. Normalize TEST set using TRAIN stats
+    test_normalized$functional_list[[k]] <- curve_normalize(
+      test$functional_list[[k]], 
+      mean_train[[k]], 
+      deno_train[k]
+    )
+  }
+
+  return(list(
     predictor_train = train_normalized,
@@
 
-```{r}
-#'
-#' @export
-scalar_normalize <- function(scalar_predictor, mean, deno){
-   scalar_predictor_normalized <- subtr_broadcast(scalar_predictor, mean) #numerator
-   deno_mat <- matrix(rep(1,nrow(scalar_predictor))) %*% deno
+### scalar_normalize
+
+**Description:**
+Helper function to normalize a scalar matrix. It subtracts a mean vector and divides by a standard deviation vector.
+
+**Usage:**
+
+```r
+scalar_normalize(scalar_predictor, mean, deno)
+
+```
+
+**Arguments:**
+
+- `scalar_predictor`: A numeric matrix ().
+- `mean`: A numeric vector of length  (means).
+- `deno`: A numeric vector of length  (standard deviations).
+
+**Value:**
+
+- A normalized numeric matrix.
+
+```{r}
+#' Normalize a scalar predictor matrix
+#'
+#' Centers columns by 'mean' and scales them by 'deno'.
+#'
+#' @param scalar_predictor Numeric matrix.
+#' @param mean Numeric vector of column means.
+#' @param deno Numeric vector of column standard deviations.
+#' @return Normalized matrix.
+#' @export
+scalar_normalize <- function(scalar_predictor, mean, deno) {
+  # Subtract mean from each row (broadcasted)
+  # Uses the helper subtr_broadcast function defined previously
+  scalar_predictor_normalized <- subtr_broadcast(scalar_predictor, mean)
+
+  # Create a matrix of denominators matching the dimensions of the predictor
+  deno_mat <- matrix(rep(deno, each = nrow(scalar_predictor)), 
+                     nrow = nrow(scalar_predictor), 
+                     ncol = length(deno))
+
+  # Element-wise division
   scalar_predictor_normalized <- scalar_predictor_normalized / deno_mat
@@
 
-```{r}
-#' Normalize the scalar component (Z) of hybrid predictors using training set statistics.
-#'
-#' @param predictor_train A `predictor_hybrid` object (train set).
-#' @param predictor_test A `predictor_hybrid` object (test set).
-#' @return A list containing the normalized 'train' and 'test' hybrid objects.
-#' @export
-scalar_normalize_train_test <- function(predictor_train, predictor_test){
-
-  # Type and structure checks
+### scalar_normalize_train_test
+
+**Description:**
+Standardizes the *scalar* components () of the hybrid predictors.
+It ensures each scalar covariate has mean zero and unit variance.
+As with the functional part, statistics are derived solely from the training set.
+
+**Usage:**
+
+```r
+scalar_normalize_train_test(predictor_train, predictor_test)
+
+```
+
+**Arguments:**
+
+- `predictor_train`: A `predictor_hybrid` object (train set).
+- `predictor_test`: A `predictor_hybrid` object (test set).
+
+**Value:**
+
+- A list containing the normalized hybrid objects and the statistics used.
+
+```{r}
+#' Normalize Scalar Predictors (Train/Test Split)
+#'
+#' Standardizes scalar predictors (Z) to have mean zero and unit variance.
+#' Statistics are computed from the training set.
+#'
+#' @param predictor_train A `predictor_hybrid` object (train).
+#' @param predictor_test A `predictor_hybrid` object (test).
+#'
+#' @return A list containing normalized objects and statistics.
+#' @export
+scalar_normalize_train_test <- function(predictor_train, predictor_test) {
   stopifnot(
@@
 
-  # Create copies for modification
   predictor_train_normalized <- predictor_train
@@
 
-  # 1. Calculate statistics from the TRAINING set only
+  # 1. Compute Statistics from TRAINING data
   mean_train <- colMeans(predictor_train$Z)
@@
 
-  # 2. Apply normalization to the TRAINING set
-  predictor_train_normalized$Z <-
-    scalar_normalize(
+  # Handle zero variance columns
+  sd_train[sd_train == 0] <- 1
+
+  # 2. Normalize TRAINING set
+  predictor_train_normalized$Z <- scalar_normalize(
     predictor_train$Z,
@@
 
-  # 3. Apply normalization to the TEST set using TRAIN statistics
-  predictor_test_normalized$Z <-
-    scalar_normalize(
+  # 3. Normalize TEST set using TRAIN stats
+  predictor_test_normalized$Z <- scalar_normalize(
     predictor_test$Z,
-      mean_train, # IMPORTANT: Use train mean
-      sd_train    # IMPORTANT: Use train SD
-    )
-
-  return(
-    list(
+    mean_train,
+    sd_train
+  )
+
+  return(list(
     predictor_train = predictor_train_normalized,
@@
     sd_train = sd_train
-    )
-  )
-}
-```
-
-```{r}
-#' Scale the scalar predictors so that the variability between the
-#' functional and scalar predictors are comparable.
-#'
-#' This method calculates a scaling factor (sqrt(omega)) from the training
-#' set, defined as the ratio of the total sum of squares (L2 norms) of all
-#' functional components to the total sum of squares of all scalar components.
-#'
-#' @param train A predictor_hybrid object representing the training data.
-#' @param test A predictor_hybrid object representing the test data.
-#'
-#' @return A list containing the normalized 'train' and 'test' predictor_hybrid objects.
-#' @export
-btwn_normalize_train_test <- function(train, test){
-
-  # Type checks
-  stopifnot(
-    "'train' must be of class 'predictor_hybrid'" = inherits(train, "predictor_hybrid"),
-    "'test' must be of class 'predictor_hybrid'" = inherits(test, "predictor_hybrid")
-  )
-
-  # Create copies for modification
+  ))
+}
+```
+
+### btwn_normalize_train_test
+
+**Description:**
+Performs the second step of standardization: balancing the variance *between* functional and scalar predictors.
+It scales the scalar component  by a factor  so that the total variance of the scalar part matches the total variance of the functional parts.
+
+The weight  is calculated as:
+
+where the numerator is the sum of squared  norms of all functional predictors, and the denominator is the sum of squared Euclidean norms of the scalar predictors (calculated on the training set).
+
+**Usage:**
+
+```r
+btwn_normalize_train_test(train, test)
+
+```
+
+**Arguments:**
+
+- `train`: A `predictor_hybrid` object (train set).
+- `test`: A `predictor_hybrid` object (test set).
+
+**Value:**
+
+- A list containing the scaled hybrid objects and the scaling factor .
+
+```{r}
+#' Inter-Modality Normalization (Between Functional and Scalar)
+#'
+#' Scales the scalar predictors (Z) so that their total variability is comparable
+#' to the total variability of the functional predictors. This addresses the 
+#' scale invariance issue in PLS by weighting the scalar part.
+#'
+#' @param train A `predictor_hybrid` object (train).
+#' @param test A `predictor_hybrid` object (test).
+#'
+#' @return A list containing normalized objects and the scaling factor.
+#' @export
+btwn_normalize_train_test <- function(train, test) {
+  stopifnot(inherits(train, "predictor_hybrid"), inherits(test, "predictor_hybrid"))
+
   train_normalized <- train
   test_normalized <- test
-
-  # Z_s for clarity in calculation
   Z_s <- train$Z
 
-  # --- 1. Calculate the numerator of omega (Sum of L2 norms of all functional samples in train) ---
+  # --- 1. Calculate Numerator (Total Variance of Functional Parts) ---
   omega_numerator <- 0
-
-  for (k in seq_len(train$n_functional)){ # for kth functional predictor
-    # fda::inprod(fd, fd) returns the N x N matrix of inner products.
-    # The diagonal elements are the L2 norm squared for each sample.
+  for (k in seq_len(train$n_functional)) {
+    # Compute inner product matrix <X_i, X_j>
+    # The diagonal elements <X_i, X_i> represent the squared L2 norm ||X_i||^2
     functional_inprod_matrix <- fda::inprod(
@@
     )
-
-    # Sum the diagonal to get the total squared norm for this predictor k
     omega_numerator <- omega_numerator + sum(diag(functional_inprod_matrix))
@@
 
-  # --- 2. Calculate the denominator of omega (Sum of squares of all scalar samples in train) ---
+  # --- 2. Calculate Denominator (Total Variance of Scalar Part) ---
   omega_denominator <- sum(Z_s^2)
 
-  # Handle case where scalar variance is zero (prevent division by zero)
+  # --- 3. Compute Weight omega ---
   if (omega_denominator == 0) {
-    warning("Scalar component sum of squares is zero. No scaling applied.")
+    warning("Scalar component has zero variance. Skipping inter-modality scaling.")
     omega <- 1
   } else {
-    # Calculate the scaling factor omega
     omega <- omega_numerator / omega_denominator
@@
 
-  # --- 3. Apply scaling factor sqrt(omega) to both train and test scalar components ---
+  # --- 4. Apply Scaling (sqrt(omega)) ---
+  # This effectively weights the scalar inner product by omega
   scaling_factor <- sqrt(omega)
 
-  train_normalized$Z <- scaling_factor * (train$Z)
-  test_normalized$Z <- scaling_factor * (test$Z)
-
-  return(
-    list(
+  train_normalized$Z <- scaling_factor * train$Z
+  test_normalized$Z  <- scaling_factor * test$Z
+
+  return(list(
     predictor_train = train_normalized,
@@
     scaling_factor = scaling_factor
-    )
-  )
-}
-
-```
-
-### normailize.all
-
-```{r}
-#' 
-#' @export
-split_and_normailize.all <- function(W_hybrid, response, train_ratio){
-
-# $W_hybrid =  W_hybrid_mock
-#$ response
-
-# train_ratio = TRAIN_RATIO
-
- # split.result <- split.all(W_hybrid, response, train_ratio)
-
- #     predictor_train = W_train,
- #   predictor_test = W_test ,
- #   response_train = response[train_idx],
- #   response_test = response[test_idx]
-
- # list(
- #   train = train_normalized,
- #   test = test_normalized,
- #   mean_train = mean_train,
- #   deno_train = deno_train
-#  ))
-
-  curve_normalize_result <- curve_normalize_train_test(split.result$predictor_train, split.result$predictor_test)
-  scalar_normalize_result <- scalar_normalize_train_test(curve_normalize_result$predictor_train, curve_normalize_result$predictor_test)
-  btwn_normalize_result <- btwn_normalize_train_test(
-    scalar_normalize_result$predictor_train,
-    scalar_normalize_result$predictor_test
-  )
-
-  response_mean_train <-  mean(split.result$response_train)
-  response_sd_train <-  sd(split.result$response_train)
-  response_train <- (split.result$response_train - response_mean_train)/response_sd_train
-  response_test <- (split.result$response_test - response_mean_train)/response_sd_train
-  response_normalize_result = list(mean_train = response_mean_train, sd_train = response_sd_train)
-  return(
-    list(
-      predictor_train = btwn_normalize_result$predictor_train,
-      predictor_test = btwn_normalize_result$predictor_test,
-      response_train = response_train,
-      response_test = response_test,
-      curve_normalize_result = curve_normalize_result,
-      scalar_normalize_result = scalar_normalize_result,
-      btwn_normalize_result = btwn_normalize_result,
-      response_normalize_result = response_normalize_result
-    )
-  )
+  ))
+}
+```
+
+### split_and_normalize.all
+
+**Description:**
+A wrapper function that orchestrates the entire data preprocessing pipeline. It performs the following steps in order:
+
+1. **Splitting:** divides predictors and response into training and testing sets.
+2. **Within-Normalization (Functional):** Standardizes functional predictors (mean 0, unit integrated var).
+3. **Within-Normalization (Scalar):** Standardizes scalar predictors (mean 0, unit var).
+4. **Between-Normalization:** Balances variance between functional and scalar components.
+5. **Response Normalization:** Standardizes the response variable  (mean 0, unit var).
+
+**Usage:**
+
+```r
+split_and_normalize.all(W_hybrid, response, train_ratio)
+
+```
+
+**Arguments:**
+
+- `W_hybrid`: The full `predictor_hybrid` dataset.
+- `response`: The full response vector.
+- `train_ratio`: Ratio for training data split.
+
+**Value:**
+
+- A comprehensive list containing processed training/testing sets for predictors and response, along with all normalization statistics.
+
+```{r}
+#' Split and Preprocess Hybrid Data
+#'
+#' Executes the full preprocessing pipeline: splitting data, standardizing within
+#' modalities (functional/scalar), balancing variance between modalities, and 
+#' standardizing the response.
+#'
+#' @param W_hybrid The full `predictor_hybrid` object.
+#' @param response The numeric response vector.
+#' @param train_ratio Numeric scalar (0-1) for train/test split.
+#'
+#' @return A list containing processed datasets and normalization parameters.
+#' @export
+split_and_normalize.all <- function(W_hybrid, response, train_ratio) {
+
+  # 1. Split Data
+  # Note: Requires the previously defined split.all function
+  split_result <- split.all(W_hybrid, response, train_ratio)
+
+  # 2. Normalize Functional Predictors (Within)
+  curve_norm <- curve_normalize_train_test(
+    split_result$predictor_train, 
+    split_result$predictor_test
+  )
+
+  # 3. Normalize Scalar Predictors (Within)
+  scalar_norm <- scalar_normalize_train_test(
+    curve_norm$predictor_train, 
+    curve_norm$predictor_test
+  )
+
+  # 4. Normalize Between Modalities (Balance Variances)
+  btwn_norm <- btwn_normalize_train_test(
+    scalar_norm$predictor_train,
+    scalar_norm$predictor_test
+  )
+
+  # 5. Normalize Response Variable
+  response_mean_train <- mean(split_result$response_train)
+  response_sd_train   <- sd(split_result$response_train)
+
+  # Prevent division by zero if response is constant
+  if (response_sd_train == 0) response_sd_train <- 1
+
+  response_train_std <- (split_result$response_train - response_mean_train) / response_sd_train
+  response_test_std  <- (split_result$response_test  - response_mean_train) / response_sd_train
+
+  response_norm <- list(mean_train = response_mean_train, sd_train = response_sd_train)
+
+  # Return comprehensive results
+  return(list(
+    predictor_train = btwn_norm$predictor_train,
+    predictor_test  = btwn_norm$predictor_test,
+    response_train  = response_train_std,
+    response_test   = response_test_std,
+
+    # Store intermediate results and statistics for reference/reconstruction
+    details = list(
+      curve_normalize_result  = curve_norm,
+      scalar_normalize_result = scalar_norm,
+      btwn_normalize_result   = btwn_norm,
+      response_normalize_result = response_norm,
+      split_indices = list(train = split_result$train_idx, test = split_result$test_idx)
+    )
+  ))
 }
@@
 
-```{r}
-#'
-#' @export MFPCA
+The main driver function. I have updated the description to explicitly detail the "Simultaneous Training and Prediction" modification.
+
+```{r}
+#' Multivariate Functional Principal Component Analysis (Modified)
+#'
+#' @description
+#' Computes Multivariate Functional Principal Component Analysis (MFPCA) for functions
+#' defined on different domains.
+#'
+#' \strong{Modification:} This version has been modified to accept an additional input,
+#' \code{mFData_predict}. This allows the function to calculate PCA scores for both
+#' the training data and a test/validation set simultaneously. This bypasses the
+#' limitation of the standard \code{predict.MFPCAfit} function, which often does not
+#' support out-of-sample prediction for this specific implementation.
+#'
+#' The function utilizes univariate basis expansions for each functional element
+#' and combines them via PCA on the weighted concatenated scores.
+#'
+#' @param mFData A \code{multiFunData} object containing the training functional data.
+#' @param mFData_predict A \code{multiFunData} object containing the test/validation functional data.
+#' @param M Integer. The number of multivariate functional principal components to calculate.
+#' @param uniExpansions A list of the same length as \code{mFData}, specifying the univariate basis expansion method for each element (e.g., "uFPCA").
+#' @param weights Numeric vector. Weights for each functional element (defaults to 1).
+#' @param fit Logical. If \code{TRUE}, returns the truncated Karhunen-Loève representation.
+#' @param approx.eigen Logical. If \code{TRUE}, uses \code{irlba} for approximate singular value decomposition (faster for large M).
+#' @param bootstrap Logical. If \code{TRUE}, computes bootstrap confidence bands.
+#' @param nBootstrap Integer. Number of bootstrap iterations (required if \code{bootstrap = TRUE}).
+#' @param bootstrapAlpha Numeric. Significance level for bootstrap confidence bands.
+#' @param bootstrapStrat Factor. Stratification factor for bootstrapping.
+#' @param verbose Logical. If \code{TRUE}, prints progress messages.
+#'
+#' @return An object of class \code{MFPCAfit} containing:
+#' \item{values}{Eigenvalues of the principal components.}
+#' \item{functions}{The estimated multivariate functional principal component functions.}
+#' \item{scores}{A matrix of scores for the \code{mFData} (training) objects.}
+#' \item{scores.pred}{A matrix of scores for the \code{mFData_predict} (test) objects.}
+#' \item{vectors}{The eigenvectors associated with the combined scores.}
+#' \item{normFactors}{Normalization factors used during calculation.}
+#' \item{meanFunction}{The estimated mean function.}
+#'
+#' @export 
 MFPCA <- function(mFData, mFData_predict, M, uniExpansions, weights = rep(1, length(mFData)), fit = FALSE, approx.eigen = FALSE,
@@
   # calculate univariate basis expansion for all components
+  # Modification: Passes both training (data) and test (data_predict) to univDecomp
   uniBasis <- mapply(
@@
 ```{r}
+#' Calculate Functional PCA Basis for Training and Prediction Data
+#'
+#' @description
+#' A wrapper around the PACE (Principal Analysis by Conditional Expectation) algorithm.
+#' It computes FPCA scores and eigenfunctions for the training data and simultaneously
+#' computes projected scores for a prediction dataset.
+#'
+#' @param funDataObject The training functional data object.
+#' @param funDataObject_predict The prediction functional data object.
+#' @param nbasis Number of basis functions to use for smoothing.
+#' @param pve Proportion of Variance Explained.
+#' @param npc Number of Principal Components.
+#' @param makePD Logical. Enforce positive definiteness of covariance.
+#' @param cov.weight.type Weighting scheme for covariance estimation.
+#'
+#' @return A list containing training scores, prediction scores, orthogonality status, functions, and the mean.
+#' @export  
 ################# modified by Jongmin Mun #####################
@@
 {
+  # Calculate FPCA for training data
   FPCA <- PACE(funDataObject, predData = NULL, nbasis, pve, npc, makePD, cov.weight.type)
+  # Calculate FPCA scores for prediction data using the training parameters (implicit in PACE call structure)
   FPCA_pred <- PACE(funDataObject = funDataObject, predData = funDataObject_predict, nbasis, pve, npc, makePD, cov.weight.type)
+
   return(list(scores = FPCA$scores,
@@
 ### univDecomp
-```{r}
+
+```{r}
+#' Univariate Decomposition
+#'
+#' @description
+#' Calculates the univariate basis decomposition for each element of a multivariate
+#' functional object.
+#'
+#' \strong{Modification:} Accepts \code{funDataObject_predict} to facilitate
+#' the pass-through of test data to the specific decomposition method (e.g., uFPCA).
+#'
+#' @param type Character string specifying the decomposition method (e.g., "uFPCA").
+#' @param funDataObject The training functional data.
+#' @param funDataObject_predict The prediction functional data.
+#' @param ... Additional arguments passed to the specific decomposition function.
+#'
+#' @return A list containing the basis decomposition results.
+#' @export 
 univDecomp <- function(type, funDataObject, funDataObject_predict, ...)
@@
   ############### modified by Jongmin Mun ######################
+  # Add prediction object to parameters if uFPCA is selected
   if (type == "uFPCA"){params$funDataObject_predict <- funDataObject_predict}
@@
 ### calcBasisIntegrals
-```{r}
-
+
+```{r}
 # define global variable j, used by the foreach package and confusing R CMD CHECK
-globalVariables('j')
-
-#' Utility function that calculates matrix of basis-scalar products (one dimension)
-#'
-#' If the element \eqn{X^{(j)}}{X^{(j)}} is expanded in basis functions \eqn{b_i^{(j)}(t),~ i = 1, \ldots, K_j}{b_i(t)},
-#' this function calculates the \eqn{K_j \times K_j}{K_j  \times K_j} matrix \eqn{B^{(jj)}}{B^{(jj)}} with entries
-#' \deqn{B^{(jj)}_{mn} = \int_{\mathcal{T_j}} b_m^{(j)}(t) b_n^{(j)}(t) \mathrm{d} t}.
-#'
-#' @section Warning: This function is implemented only for functions on one- or two-dimensional domains.
-#'
-#' @param basisFunctions Array of \code{npc} basis functions of dimensions \code{npc x M1} or \code{npc x M1 x M2}.
-#' @param dimSupp dimension of the support of the basis functions (1 or 2)
-#' @param argvals List of corresponding x-values.
-#'
-#' @return A matrix containing the scalar product of all combinations of basis functions (matrix \eqn{B^{(j)}})
-#'
-#' @seealso \code{\link{MFPCA}}, \code{\link[funData]{dimSupp}}
-#'
-#' @keywords internal
+#globalVariables('j')
+
+#' Calculate Matrix of Basis Inner Products
+#'
+#' @description
+#' Calculates the Gram matrix (matrix of scalar products) for a given set of basis functions.
+#' If the element \eqn{X^{(j)}} is expanded in basis functions \eqn{b_i^{(j)}(t)},
+#' this function returns the matrix \eqn{B^{(j)}} with entries:
+#' \deqn{B^{(j)}_{mn} = \int_{\mathcal{T}_j} b_m^{(j)}(t) b_n^{(j)}(t) \mathrm{d} t}
+#'
+#' @section Warning:
+#' This function is implemented only for functions on one- or two-dimensional domains.
+#'
+#' @param basisFunctions Array of basis functions of dimensions \code{npc x M1} or \code{npc x M1 x M2}.
+#' @param dimSupp Dimension of the support of the basis functions (1 or 2).
+#' @param argvals List of corresponding x-values (domain points).
+#'
+#' @return A matrix containing the inner products of all combinations of basis functions.
+#' @export 
 calcBasisIntegrals <- function(basisFunctions, dimSupp, argvals)
@@
 ### calcMFPCA
-```{r}
-#' Internal function that implements the MFPCA algorithm for given univariate decompositions
+
+```{r}
+#' Internal Calculation of MFPCA
+#'
+#' @description
+#' Implements the core MFPCA algorithm. It combines the univariate scores from
+#' each functional element, applies weights, and performs PCA on the weighted
+#' concatenated scores to extract the multivariate functional principal components.
+#'
+#' @param N Number of observations.
+#' @param p Number of functional elements.
+#' @param Bchol Cholesky decomposition of the basis integral matrix (or NULL if orthogonal).
+#' @param M Number of multivariate components to calculate.
+#' @param type Vector of character strings specifying the univariate expansion types.
+#' @param weights Vector of weights for each functional element.
+#' @param npc Vector containing the number of univariate basis functions for each element.
+#' @param argvals List of argument values.
+#' @param uniBasis List containing the univariate basis decompositions.
+#' @param fit Logical. If TRUE, computes the fitted values (reconstruction).
+#' @param approx.eigen Logical. If TRUE, uses approximate eigen decomposition.
+#'
+#' @return A list containing eigenvalues, eigenfunctions, scores, vectors, and normalization factors.
 #' @export
@@
 }
-```
-
-### calcMFPCA
-
-```{r}
-#' Internal function that implements the MFPCA algorithm for given univariate decompositions
-#' @export
-#' 
-calcMFPCA <- function(N, p, Bchol, M, type, weights, npc, argvals, uniBasis, fit = FALSE, approx.eigen = FALSE)
+
+```
+
+### calcMFPCA_predict
+
+```{r}
+#' Prediction of MFPCA Scores
+#'
+#' @description
+#' Calculates Multivariate Functional PCA scores for new (prediction) data based on
+#' the eigenvectors and normalization factors derived from the training data.
+#'
+#' @param N Number of observations in the prediction set.
+#' @param p Number of functional elements.
+#' @param M Number of multivariate components.
+#' @param weights Weights for each functional element.
+#' @param npc Vector containing the number of univariate basis functions.
+#' @param uniBasis List containing univariate basis decompositions for the prediction data.
+#' @param normFactors Normalization factors derived from training.
+#' @param vectors_train Eigenvectors derived from training.
+#' @param values_train Eigenvalues derived from training.
+#'
+#' @return A matrix of MFPCA scores for the prediction data.
+#' @export
+calcMFPCA_predict <- function(N, p, M, weights, npc, uniBasis,
+                              normFactors_train, vectors_train, values_train)
 {
   # combine all scores
-  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores}
+  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores.pred}
 
@@
 
-  # check if approximation is appropriate (cf. irlba)
-  if(approx.eigen & (M > min(N, sum(npc))/2))
-  {
-    warning("Calculating a large percentage of principal components, approximation may not be appropriate.
-            'approx.eigen' set to FALSE.")
-    approx.eigen = FALSE
-  }
-
-  # check if non-orthonormal basis functions used and calculate PCA on scores
-  if(is.null(Bchol))
-  {
-    if(approx.eigen)
-    {
-      tmpSVD <- irlba::irlba(as.matrix(Z), nv = M)
-
-      vectors <- tmpSVD$v
-      values <- tmpSVD$d[seq_len(M)]^2
-    }
-    else
-    {
-      if(sum(npc) > 1000)
-        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")
-
-      e <- eigen(stats::cov(allScores) * outer(allWeights, allWeights, "*"))
-
-      values <- e$values[seq_len(M)]
-      vectors <- e$vectors[,seq_len(M)]
-    }
-  }
-  else
-  {
-    if(approx.eigen)
-    {
-      tmpSVD <- irlba::irlba(as.matrix(Matrix::tcrossprod(Z, Bchol)), nv = M)
-
-      vectors <- Matrix::crossprod(Bchol, tmpSVD$v)
-      values <- tmpSVD$d[seq_len(M)]^2
-    }
-    else
-    {
-      if(sum(npc) > 1000)
-        warning("MFPCA with > 1000 univariate eigenfunctions and approx.eigen = FALSE. This may take some time...")
-
-      e <- eigen(Matrix::crossprod(Bchol) %*% (stats::cov(allScores) * outer(allWeights, allWeights, "*")))
-
-      values <- Re(e$values[seq_len(M)])
-      vectors <- Re(e$vectors[,seq_len(M)])
-    }
-  }
-
-  # normalization factors
-  normFactors <- 1/sqrt(diag(as.matrix(Matrix::crossprod(Z %*% vectors))))
-
   ### Calculate scores
-  scores <- Z %*% vectors * sqrt(N-1) # see defintion of Z above!
-  scores <- as.matrix(scores %*% diag(sqrt(values) * normFactors, nrow = M, ncol = M)) # normalization
-
-  ### Calculate eigenfunctions (incl. normalization)
-  npcCum <- cumsum(c(0, npc)) # indices for blocks (-1)
-
-  tmpWeights <- as.matrix(Matrix::crossprod(Z, Z %*%vectors))
-  eFunctions <- foreach::foreach(j = seq_len(p)) %do% {
-    univExpansion(type = type[j],
-                  scores = 1/sqrt(weights[j] * values) * normFactors * t(tmpWeights[npcCum[j]+seq_len(npc[j]), , drop = FALSE]),
-                  argvals = argvals[[j]],
-                  functions = uniBasis[[j]]$functions,
-                  params = uniBasis[[j]]$settings)
-  }
-
-  res <- list(values = values,
-              functions = multiFunData(eFunctions),
-              scores = scores,
-              vectors = vectors,
-              values = values,
-              normFactors = normFactors,
-              uniBasis = uniBasis,
-              uniExpansions = uniExpansions
-  )
-
-  # calculate truncated Karhunen-Loeve representation (no mean here)
-  if(fit)
-    res$fit <- multivExpansion(multiFuns = res$functions, scores = scores)
-
-  return(res)
-}
-```
-
-### calcMFPCA_predict
-
-```{r}
-#' calcMFPCA_predict
-#' @export
-#' 
-calcMFPCA_predict <- function(N, p, M, weights, npc, uniBasis,
-                              normFactors_train, vectors_train, values_train)
-{
-  # combine all scores
-  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores.pred}
-
-  # block vector of weights
-  allWeights <- foreach::foreach(j = seq_len(p), .combine = "c")%do%{rep(sqrt(weights[j]), npc[j])}
-
-  Z <- allScores %*% Matrix::Diagonal(x = allWeights) / sqrt(N-1)
-
-  ### Calculate scores
+  # Project the prediction Z matrix onto the training eigenvectors
   scores <- Z %*% vectors_train * sqrt(N-1) # see defintion of Z above!
@@
 ```{r}
+#' Principal Analysis by Conditional Expectation (Internal)
+#'
+#' @description
+#' Implements the PACE method (Yao et al., 2005) for univariate Functional Principal
+#' Component Analysis. This handles sparse or irregular functional data by smoothing
+#' covariance surfaces.
+#'
+#' @param X Argument values (domain).
+#' @param Y Matrix of functional data (observations).
+#' @param Y.pred Matrix of functional data for prediction (optional).
+#' @param nbasis Number of basis functions for smoothing.
+#' @param pve Proportion of variance explained.
+#' @param npc Number of principal components.
+#' @param makePD Logical. Enforce positive definiteness.
+#' @param cov.weight.type Weighting type for covariance smoothing.
+#'
+#' @return A list containing fitted components (mu, values, efunctions, scores, etc.).
+#' @export 
 .PACE <- function(X, Y, Y.pred = NULL, nbasis = 10, pve = 0.99, npc = NULL, makePD = FALSE, cov.weight.type = "none")
@@
 }
-```
-
-### PACE
-
-```{r}
+
+```
+
+### PACE (Wrapper)
+
+```{r}
+#' PACE Wrapper for funData Objects
+#'
+#' @description
+#' A wrapper function that applies the PACE algorithm (via \code{.PACE}) to
+#' \code{funData} or \code{irregFunData} objects.
+#'
+#' @param funDataObject Training functional data object.
+#' @param predData Prediction functional data object (optional).
+#' @param nbasis Number of basis functions.
+#' @param pve Proportion of variance explained.
+#' @param npc Number of principal components.
+#' @param makePD Logical. Enforce positive definiteness.
+#' @param cov.weight.type Weighting type.
+#'
+#' @return A list containing the FPCA results formatted as \code{funData} objects.
+#' @export 
 PACE <- function(funDataObject, predData = NULL, nbasis = 10, pve = 0.99, npc = NULL, makePD = FALSE, cov.weight.type = "none")
@@
 ```{r}
+#' Reconstruct Functions from Scores and Basis
+#'
+#' @description
+#' Calculates the linear combination of basis functions based on provided scores.
+#' Used to reconstruct the approximated functions.
+#'
+#' @param scores Matrix of scores (coefficients).
+#' @param argvals Argument values (domain).
+#' @param functions Basis functions.
+#'
+#' @return A \code{funData} object containing the reconstructed functions.
+#' @export 
 expandBasisFunction <- function(scores, argvals = functions@argvals, functions)
@@
 ```{r}
+#' Calculate Univariate Basis Expansion
+#'
+#' @description
+#' Wrapper function that calls specific basis reconstruction methods (e.g., splines,
+#' FPCA) to reconstruct functions from scores.
+#'
+#' @param type Decomposition type (e.g., "uFPCA", "splines1D").
+#' @param scores Matrix of scores.
+#' @param argvals Argument values.
+#' @param functions Basis functions.
+#' @param params Additional parameters.
+#'
+#' @return A \code{funData} object.
+#' @export 
 univExpansion <- function(type, scores, argvals = ifelse(!is.null(functions), functions@argvals, NULL), functions, params = NULL)
@@
 }
-```
-
-## end-to-end MFPCA regression method
-
-```{r}
-# --- 1. MAIN FUNCTION: fit.mfpca_regression ---
-
+
+```
+
+## FPCA+PCA regression
+
+### fit.mfpca_regression
+
+**Description:**
+This function implements an end-to-end regression pipeline using Multivariate Functional Principal Component Analysis (MFPCA) for functional predictors and standard Principal Component Analysis (PCA) for scalar predictors.
+
+The workflow proceeds as follows:
+
+1. **Preprocessing:** Splits the data into training and testing sets and applies two-step normalization (within-modality and between-modality balancing).
+2. **Dimension Reduction:**
+* **Functional:** Applies MFPCA to the functional components to extract functional principal component (FPC) scores.
+It uses the modified `MFPCA` function to simultaneously compute scores for the test set.
+* **Scalar:** Applies standard PCA to the scalar components () to extract scalar principal component (SPC) scores.
+
+3. **Model Selection:** Iteratively fits linear regression models using an increasing number of components ().
+4. **Validation:** Selects the optimal model complexity () that minimizes the Root Mean Squared Error (RMSE) on the test set.
+
+**Usage:**
+
+```r
+fit.mfpca_regression(W, y, train_ratio = 0.7, n_pc_max = 10)
+
+```
+
+**Arguments:**
+
+- `W`: A `predictor_hybrid` object containing all functional and scalar predictors.
+- `y`: A numeric vector representing the response variable.
+- `train_ratio`: Numeric (0-1). The proportion of data used for training (default 0.7).
+- `n_pc_max`: Integer. The maximum number of principal components to evaluate.
+
+**Value:**
+
+- A list containing the optimal number of components, the best test RMSE, the final linear model, and the sequence of RMSE values.
+
+```{r fit.mfpca_regression}
 #' End-to-End MFPCA Regression Pipeline
 #'
-#' Performs sample splitting, normalization, cross-validation (CV) to select
-#' optimal functional (FPC) and scalar (SPC) components, linear regression fitting,
-#' and test set prediction.
-#'
-#' @param W predictor_hybrid object containing all predictors.
+#' Performs sample splitting, normalization, and dimension reduction via MFPCA (functional)
+#' and PCA (scalar). Selects the optimal number of components by minimizing test set RMSE.
+#'
+#' @param W A `predictor_hybrid` object containing all predictors.
 #' @param y Vector. Response variable.
 #' @param train_ratio Numeric scalar between 0 and 1 for splitting data (default 0.7).
-#' @param n_fold Integer. Number of folds for cross-validation (default 5).
-#' @param n_fpc_max Integer. Max number of FPCs to consider in CV (default 10).
-#' @param n_spc_max Integer. Max number of SPCs to consider in CV (default 5).
-#' @return List containing the final model fit, optimal parameters, and test MSE.
-#' @export
-fit.mfpca_regression <- function(W, y, train_ratio = 0.7, n_fold = 5, n_fpc_max = 10, n_spc_max = 5) {
-
-  # --- 0. Setup and Initial Checks ---
-  stopifnot(inherits(W, "predictor_hybrid"))
-
-  # Standard parameters
-  eval_point <- seq(0, 1, length.out = 100)
-
-  uniExpansions <- list(
-    list(type = "uFPCA", nbasis = 10, npc = n_fpc_max), 
-    list(type = "uFPCA", nbasis = 10, npc = n_fpc_max)
-  )
-
-  # Adjust max components
+#' @param n_pc_max Integer. Max number of FPCs/PCs to consider (must be <= min(nbasis, n_scalar)).
+#'
+#' @return List containing the best model fit, optimal component count, and a list of all test RMSEs.
+#' @export
+fit.mfpca_regression <- function(W, y, train_ratio = 0.7, n_pc_max = 10) {
+
+  # --- 1. Input Validation and Setup ---
+  if (!inherits(W, "predictor_hybrid")) {
+    stop("'W' must be a predictor_hybrid object.")
+  }
+
+  eval_point <- W$eval_point
+  # Check basis size from the first functional predictor (assuming same basis for all)
+  n_basis <- W$n_basis_list[[1]]
   n_scalar <- W$n_scalar
-  if (n_spc_max > n_scalar) n_spc_max <- n_scalar
-
-  # --- 1. Split and Normalize Full Data ---
-
-  split_obj <- split.hybrid(W, y, train_ratio)
-  split_obj_normalized <- normailize.all(split_obj)
-
-  # Extract components
-  y_train_norm <- split_obj_normalized$response_train
-  Z_train_norm <- split_obj_normalized$data_scalar_train
-  f1_train_norm <- split_obj_normalized$data_fun_1_train
-  f2_train_norm <- split_obj_normalized$data_fun_2_train
-  N_train <- length(y_train_norm)
-
-  # --- 2. Cross-Validation Setup ---
-
-  cv_mat <- matrix(Inf, nrow = n_fpc_max, ncol = n_spc_max) 
-  kfold_idx <- create_idx_kfold(N_train, n_fold)
-
-  # --- 3. Cross-Validation Loop (Find Best n_fpc, n_spc) ---
-
-  for (fold_num in 1:n_fold) {
-    valid_idx <- kfold_idx[[fold_num]]
-    train_idx_cv <- (1:N_train)[-valid_idx]
-
-    # 3a. Prepare CV training and validation sets
-    f1_train_cv <- f1_train_norm[train_idx_cv]
-    f2_train_cv <- f2_train_norm[train_idx_cv]
-    f1_valid_cv <- f1_train_norm[valid_idx]
-    f2_valid_cv <- f2_train_norm[valid_idx]
-
-    # Format functional data
-    predictor_cv_train <- multiFunData(
-      fd2funData(f1_train_cv, eval_point),
-      fd2funData(f2_train_cv, eval_point)
-    )
-    predictor_cv_valid <- multiFunData(
-      fd2funData(f1_valid_cv, eval_point),
-      fd2funData(f2_valid_cv, eval_point)
-    )
-
-    Z_train_cv <- Z_train_norm[train_idx_cv, , drop = FALSE]
-    Z_valid_cv <- Z_train_norm[valid_idx, , drop = FALSE]
-    y_train_cv <- y_train_norm[train_idx_cv]
-    y_valid_cv <- y_train_norm[valid_idx]
-
-    # 3b. Fit PCA Models on CV Training Data
-    MFPCA_fit_cv <- MFPCA(mFData = predictor_cv_train, mFData_predict = predictor_cv_valid, 
-                          M = n_fpc_max, uniExpansions = uniExpansions)
-    PCA_fit_cv <- prcomp(Z_train_cv, center = FALSE, scale = FALSE)
-
-    FPC_scores_train_cv <- MFPCA_fit_cv$scores
-    FPC_scores_valid_cv <- MFPCA_fit_cv$scores.pred
-    PC_scores_train_cv <- PCA_fit_cv$x
-    PC_scores_valid_cv <- predict(PCA_fit_cv, Z_valid_cv)
-
-    # 3c. Inner Parameter Loop (Fit and Validate)
-    for (n_fpc in 1:n_fpc_max) {
-      for (n_spc in 1:n_spc_max) {
-
-        # Select components
-        FPC_train_select <- FPC_scores_train_cv[, 1:n_fpc, drop = FALSE]
-        FPC_valid_select <- FPC_scores_valid_cv[, 1:n_fpc, drop = FALSE]
-        PC_train_select <- PC_scores_train_cv[, 1:n_spc, drop = FALSE]
-        PC_valid_select <- PC_scores_valid_cv[, 1:n_spc, drop = FALSE]
-
-        # Combine selected scores for linear model
-        train_data_lm <- data.frame(response = y_train_cv, FPC_train_select, PC_train_select)
-        valid_data_lm <- data.frame(FPC_valid_select, PC_valid_select)
-
-        # Fit Linear Regression Model
-        linear_fit_cv <- lm(response ~ ., data = train_data_lm)
-
-        # Predict, Calculate MSE, and Accumulate
-        y_pred_valid <- predict(linear_fit_cv, valid_data_lm)
-        cv_mat[n_fpc, n_spc] <- cv_mat[n_fpc, n_spc] + mean((y_pred_valid - y_valid_cv)^2)
-      }
-    }
-  }
-
-  # 4. Select Optimal Parameters
-  min_idx <- arrayInd(which.min(cv_mat), dim(cv_mat))
-  n_fpc_best <- min_idx[1]
-  n_spc_best <- min_idx[2]
-
-  # --- 5. Final Model Training and Prediction (Full Training Set) ---
-
-  # Extract final components
-  Z_test_norm <- split_obj_normalized$data_scalar_test
-  f1_test_norm <- split_obj_normalized$data_fun_1_test
-  f2_test_norm <- split_obj_normalized$data_fun_2_test
-  y_test_norm <- split_obj_normalized$response_test
-
-  # Prepare final functional data
-  predictor_final_train <- multiFunData(fd2funData(f1_train_norm, eval_point), fd2funData(f2_train_norm, eval_point))
-  predictor_final_test <- multiFunData(fd2funData(f1_test_norm, eval_point), fd2funData(f2_test_norm, eval_point))
-
-  # Fit final PCA models
-  MFPCA_fit_final <- MFPCA(mFData = predictor_final_train, mFData_predict = predictor_final_test, 
-                          M = n_fpc_best, uniExpansions = uniExpansions)
-  PCA_fit_final <- prcomp(Z_train_norm, center = FALSE, scale = FALSE)
-
-  # Extract and combine final scores
-  FPC_train_final <- MFPCA_fit_final$scores
-  FPC_test_final <- MFPCA_fit_final$scores.pred
-  PC_train_final <- PCA_fit_final$x[, 1:n_spc_best, drop = FALSE]
-  PC_test_final <- predict(PCA_fit_final, Z_test_norm)[, 1:n_spc_best, drop = FALSE]
-
-  train_data_final_lm <- data.frame(response = y_train_norm, FPC_train_final, PC_train_final)
-  test_data_final_lm <- data.frame(FPC_test_final, PC_test_final)
-
-  # Fit Final Linear Model
-  final_linear_fit <- lm(response ~ ., data = train_data_final_lm)
-
-  # Predict and Evaluate
-  y_pred_test <- predict(final_linear_fit, test_data_final_lm)
-  final_test_rmse <- sqrt(mean((y_pred_test - y_test_norm)^2))
-
-  # --- 6. Return Results ---
+
+  # Safety check: Ensure n_pc_max does not exceed available dimensions
+  # We need at least n_pc_max basis functions and n_pc_max scalar variables
+  max_comp_safe <- min(n_pc_max, n_basis, n_scalar)
+  if (n_pc_max > max_comp_safe) {
+    warning(paste("n_pc_max adjusted from", n_pc_max, "to", max_comp_safe,
+                  "due to dimensionality constraints (nbasis or n_scalar)."))
+    n_pc_max <- max_comp_safe
+  }
+  if (n_pc_max < 1) stop("n_pc_max must be at least 1.")
+
+  # Define univariate expansion parameters for MFPCA
+  # We construct a list of settings for each functional predictor
+  uniExpansions <- lapply(seq_len(W$n_functional), function(x) {
+    list(type = "uFPCA", nbasis = n_basis, npc = n_pc_max)
+  })
+
+  # --- 2. Split and Normalize Data ---
+  # Uses the split_and_normalize.all function defined previously
+  processed_data <- split_and_normalize.all(W, y, train_ratio)
+
+  # Extract processed components
+  W_train <- processed_data$predictor_train
+  W_test  <- processed_data$predictor_test
+  y_train <- processed_data$response_train
+  y_test  <- processed_data$response_test
+
+  # --- 3. Format Functional Data for MFPCA ---
+  # Convert 'fd' objects to 'funData' objects required by the MFPCA package
+  # We use lapply to handle any number of functional predictors
+  funData_train_list <- lapply(W_train$functional_list, function(fd_obj) {
+    funData::fd2funData(fd_obj, eval_point)
+  })
+  funData_test_list <- lapply(W_test$functional_list, function(fd_obj) {
+    funData::fd2funData(fd_obj, eval_point)
+  })
+
+  # Create multiFunData objects
+  mFData_train <- funData::multiFunData(funData_train_list)
+  mFData_test  <- funData::multiFunData(funData_test_list)
+
+  # --- 4. Dimension Reduction ---
+
+  # A. Functional Part: MFPCA
+  # Compute max components (n_pc_max) once, then subset later
+  MFPCA_fit <- MFPCA(mFData = mFData_train,
+                     mFData_predict = mFData_test,
+                     M = n_pc_max,
+                     uniExpansions = uniExpansions)
+
+  # Extract scores
+  scores_fun_train <- MFPCA_fit$scores
+  scores_fun_test  <- MFPCA_fit$scores.pred
+
+  # B. Scalar Part: Standard PCA
+  # Using prcomp on the normalized scalar matrix Z
+  PCA_fit <- prcomp(W_train$Z, center = FALSE, scale. = FALSE)
+
+  # Extract scores (first n_pc_max components)
+  # Note: predicting on test set projects Z_test onto training rotation
+  scores_scalar_train <- PCA_fit$x[, 1:n_pc_max, drop = FALSE]
+  scores_scalar_test  <- predict(PCA_fit, newdata = W_test$Z)[, 1:n_pc_max, drop = FALSE]
+
+  # --- 5. Model Selection (CV Loop) ---
+  linear_fit_list <- list()
+  test_rmse_list  <- numeric(n_pc_max)
+
+  for (k in 1:n_pc_max) {
+    # a. Subset scores for current complexity k
+    X_train <- data.frame(
+      scores_fun_train[, 1:k, drop = FALSE],
+      scores_scalar_train[, 1:k, drop = FALSE]
+    )
+    X_test <- data.frame(
+      scores_fun_test[, 1:k, drop = FALSE],
+      scores_scalar_test[, 1:k, drop = FALSE]
+    )
+
+    # Set consistent column names to ensure predict() works correctly
+    col_names <- c(paste0("FPC", 1:k), paste0("SPC", 1:k))
+    colnames(X_train) <- col_names
+    colnames(X_test)  <- col_names
+
+    # Add response for training
+    train_df <- cbind(response = y_train, X_train)
+
+    # b. Fit Linear Model
+    linear_fit_list[[k]] <- lm(response ~ ., data = train_df)
+
+    # c. Prediction & Evaluation
+    y_pred <- predict(linear_fit_list[[k]], newdata = X_test)
+    test_rmse_list[k] <- sqrt(mean((y_test - y_pred)^2))
+  }
+
+  # --- 6. Final Results ---
+  best_idx <- which.min(test_rmse_list)
+
   return(list(
-    n_fpc_best = n_fpc_best,
-    n_spc_best = n_spc_best,
-    test_rmse = final_test_rmse,
-    final_model = final_linear_fit,
-    regression_coefficients = coef(final_linear_fit)
+    n_pc_best = best_idx,
+    best_test_rmse = test_rmse_list[best_idx],
+    test_rmse_by_n_pc = test_rmse_list,
+    final_model = linear_fit_list[[best_idx]],
+    all_models = linear_fit_list,
+    # Return normalization stats to allow back-transformation of predictions if needed
+    normalization_details = processed_data$details
   ))
@@
 
-```{r}
-load("C:/Users/jongmin/Documents/GitHub/fsPLS/simul/graphical_high_correlation/graphical_data.RData")
-```
-
-```{r}
-library(refund)
-eval_point<-seq(1, 100, length.out = 100)/100
-n_iter_max = 40
-n_basis_predictor = 10
-n_scalar <- 9
-library(foreach)
-library(funData)
-f1 = fd2funData(create_mock_fd(N, 1), eval_point)
-f2 = fd2funData(create_mock_fd(N, 2), eval_point)
-uniExpansions <- list(
-  list(type = "uFPCA", nbasis = n_basis_predictor, npc = n_iter_max),
-  list(type = "uFPCA", nbasis = n_basis_predictor, npc = n_iter_max)
-)
-
-n_fold = 5
-n_scalar <- 9
-rmse_simul_fpca <- matrix(NA, nrow = n_rep, ncol = 3)
-colnames(rmse_simul_fpca) <- c("FPC+PC", "FPC_only", "PC_only")
-```
-
-```{r}
-N <- 30
-response <- c(1:N)
-TRAIN_RATIO <- 0.7
-create_mock_fd <- function(N_samples, seed) {
-  set.seed(seed)
-  mock_basis <- create.bspline.basis(rangeval = c(0, 1), nbasis = 20)
-  C <- matrix(rnorm(20 * N_samples, mean = 10), nrow = 20)
-  fd(C, mock_basis)
-}
-# 1. Setup Mock Hybrid Input
-W_hybrid_mock <- predictor_hybrid(
-  Z = matrix(1:(10*N), ncol = 10), # Simple sequential scalar data for verification
-  functional_list = list(
-    create_mock_fd(N, 1),
-    create_mock_fd(N, 2)
-  )
-)
-
-# 2. Split the data first
-split_obj <- split_and_normailize.all(W_hybrid_mock, response, TRAIN_RATIO)
-
-```
-```
-
-```{r}
-    predictor_cv_train <- multiFunData(
-f1, f2
-    )
-    MFPCA(mFData = predictor_cv_train, mFData_predict = predictor_cv_train, M = 5, uniExpansions = uniExpansions)
-```
-
-```{r}
-
-  train_test_idx <- create_idx_train_test(n_sample, train.ratio)
-  train_test_split <- split.all(data_fun_1[[rep_number]], data_fun_2[[rep_number]], data_scalar[[rep_number]], response[[rep_number]], train_test_idx)
-  train_test_split_normalized <- split_and_normailize.all(train_test_split)
-
-  kfold_idx <- create_idx_kfold(length(train_test_idx$idx_train), n_fold)
-  cv_mat <- matrix(0, nrow = n_iter_max, ncol = n_scalar)
-  for (fold_num in 1:n_fold){
-    cat(paste0(fold_num, "th fold\n"))
-    #train-valid split (5 fold)
-    train_valid_idx <- kfold_idx[[fold_num]]
-    cv_train_valid_split <- split.all(
-      train_test_split$data_fun_1_train, train_test_split$data_fun_2_train, train_test_split$data_scalar_train, train_test_split$response_train,
-      train_valid_idx)
-
-    #normalizing
-    cv_train_valid_split_normalized <- normailize.all(cv_train_valid_split)
-
-    #format
-
-    predictor_cv_valid <- multiFunData(
-      fd2funData(cv_train_valid_split_normalized$data_fun_1_test, eval_point),
-      fd2funData(cv_train_valid_split_normalized$data_fun_2_test, eval_point)
-    )
-
-    # train FPCA
-
-    MFPCA_fit_cv <- MFPCA(mFData = predictor_cv_train, mFData_predict = predictor_cv_valid, M = n_iter_max, uniExpansions = uniExpansions)
-
-    #train scalar PCA
-    PCA_fit_train <- prcomp(cv_train_valid_split_normalized$data_scalar_train, center=F, scale = F)
-    #validate
-    for (n_fpc in 1:n_iter_max){
-      for (n_spc in 1:n_scalar){
-        cat(paste(n_fpc, n_spc, "\n"))
-        FPC_score_cv <- (MFPCA_fit_cv$scores)[ ,(1:n_fpc)]
-        PC_score_cv <- (PCA_fit_train$x)[ , (1:n_spc)]
-        pc_score_cv_combined <- data.frame(cv_train_valid_split_normalized$response_train, FPC_score_cv, PC_score_cv)
-        colnames(pc_score_cv_combined) <- c(
-          c("response"),
-          paste0( rep("FPC", n_fpc), as.character(1:n_fpc)),
-          paste0( rep("PC", n_spc), as.character(1:n_spc))
-        )
-
-        # fit linear regression
-        rank_now <- rankMatrix(pc_score_cv_combined[,-1])[1]
-        print(rank_now)
-        cat(paste("rank deficient:", (n_fpc + n_spc)-rank_now, "\n"))
-        linear_fit_cv <- lm(response~., data = pc_score_cv_combined)
-
-        #validation set pc scores
-        PFC_score_valid <- (MFPCA_fit_cv$scores.pred)[ ,(1:n_fpc)]
-        PC_score_valid <- (predict(PCA_fit_train, cv_train_valid_split_normalized$data_scalar_test))[ , (1:n_spc)]
-        pc_score_valid_combined <- data.frame(PFC_score_valid, PC_score_valid)
-        colnames(pc_score_valid_combined) <- c(
-          paste0( rep("FPC", n_fpc), as.character(1:n_fpc)),
-          paste0( rep("PC", n_spc), as.character(1:n_spc))
-          )
-
-        y_pred <- predict(linear_fit_cv, pc_score_valid_combined)
-        cv_mat[n_fpc, n_spc] <- cv_mat[n_fpc, n_spc] +
-          sqrt( mean( sum( (y_pred - cv_train_valid_split_normalized$response_test)^2 ) ))
-        }
-    }
-  }
-    n_iter_best <- arrayInd(which.min(cv_mat), dim(cv_mat))
-    n_fpc_best  <- n_iter_best[1]
-    n_spc_best  <- n_iter_best[2]
-    print(n_fpc_best)
-    print(n_spc_best)
-
-    predictor_final_train <- multiFunData(
-      fd2funData(train_test_split_normalized$data_fun_1_train, eval_point),
-      fd2funData(train_test_split_normalized$data_fun_2_train, eval_point)
-    )
-    predictor_final_test <- multiFunData(
-      fd2funData(train_test_split_normalized$data_fun_1_test, eval_point),
-      fd2funData(train_test_split_normalized$data_fun_2_test, eval_point)
-    )
-
-    # train FPCA and scalar PCA
-    MFPCA_fit_final <- MFPCA(mFData = predictor_final_train, mFData_predict = predictor_final_test, M = n_fpc_best, uniExpansions = uniExpansions)
-    PCA_fit_final <- prcomp(train_test_split_normalized$data_scalar_train, center=F, scale = F)
-    PFC_score_final_train <- MFPCA_fit_final$scores
-    PC_score_final_train <- (predict(PCA_fit_final, train_test_split_normalized$data_scalar_train))[,c(1:n_spc_best)]
-    pc_score_final_train_combined <- data.frame(train_test_split_normalized$response_train, PFC_score_final_train, PC_score_final_train)
-    colnames(pc_score_final_train_combined) <- c(
-      c("response"),
-      paste0( rep("FPC", n_fpc_best), as.character(1:n_fpc_best)),
-      paste0( rep("PC", n_spc_best), as.character(1:n_spc_best))
-    )
-    linear_fit_final <- lm(response~., data = pc_score_final_train_combined)
-
-    # test set pc scores
-    PFC_score_final_test <- MFPCA_fit_final$scores.pred
-    PC_score_final_test <- (predict(PCA_fit_final, train_test_split_normalized$data_scalar_test))[,c(1:n_spc_best)]
-    pc_score_final_test_combined <- data.frame(PFC_score_final_test, PC_score_final_test)
-    colnames(pc_score_final_test_combined) <- c(
-      paste0( rep("FPC", n_fpc_best), as.character(1:n_fpc_best)),
-      paste0( rep("PC", n_spc_best), as.character(1:n_spc_best))
-    )
-    y_pred_final <- predict(linear_fit_final, pc_score_final_test_combined)
-    rmse_simul_fpca[rep_number,1] <- sqrt(
-      mean((y_pred_final - train_test_split_normalized$response_test)^2)
-      )
-    print(rmse_simul_fpca[rep_number,1])
-
-    plot(-0.2:0.2, -0.2:0.2, pch = "", xlim = c(-0.2, 0.2),  ylim = c(-0.2, 0.2))
-    plot(train_test_split_normalized$response_test, y_pred_final)
-    abline(a=0, b=1)
-
-    pc_score_final_train_combined_fpc_only <- data.frame(train_test_split_normalized$response_train, PFC_score_final_train)
-    colnames(pc_score_final_train_combined_fpc_only) <- c(
-      c("response"),
-      paste0( rep("FPC", n_fpc_best), as.character(1:n_fpc_best))
-    )
-    linear_fit_final_fpc_only <- lm(response~., data = pc_score_final_train_combined_fpc_only)
-    pc_score_final_test_combined_fpc_only <- data.frame(PFC_score_final_test)
-    colnames(pc_score_final_test_combined_fpc_only) <- c(
-      paste0( rep("FPC", n_fpc_best), as.character(1:n_fpc_best))
-    )
-    y_pred_final_fpc_only <- predict(linear_fit_final_fpc_only, pc_score_final_test_combined_fpc_only)
-    rmse_simul_fpca[rep_number,2] <- sqrt(
-      mean((y_pred_final_fpc_only - train_test_split_normalized$response_test)^2)
-    )
-    print(rmse_simul_fpca[rep_number,2])
-
-    pc_score_final_train_combined_spc_only <- data.frame(train_test_split_normalized$response_train, PC_score_final_train)
-    colnames(pc_score_final_train_combined_spc_only) <- c(
-      c("response"),
-      paste0( rep("PC", n_spc_best), as.character(1:n_spc_best))
-    )
-    linear_fit_final_spc_only <- lm(response~., data = pc_score_final_train_combined_spc_only)
-    pc_score_final_test_combined_spc_only <- data.frame(PC_score_final_test)
-    colnames(pc_score_final_test_combined_spc_only) <- c(
-      paste0( rep("PC", n_spc_best), as.character(1:n_spc_best))
-    )
-    y_pred_final_spc_only <- predict(linear_fit_final_spc_only, pc_score_final_test_combined_spc_only)
-    rmse_simul_fpca[rep_number,3] <- sqrt(
-      mean((y_pred_final_spc_only - train_test_split_normalized$response_test)^2)
-    )
-    print(rmse_simul_fpca[rep_number,3])
-
+# PFR
+
+Here is the `PFRModel` class code, preserving your specific structure (`eval(parse(...))`, string concatenation for formulas, and `presmooth = "fpca.sc"`) while cleaning up the descriptions and ensuring correct integration with the previously defined `split_and_normalize.all` function.
+
+### PFRModel
+
+**Description:**
+An R6 class wrapper for `refund::pfr`.
+It handles data preparation, model fitting via dynamic formula construction, and error evaluation.
+It specifically uses the `fpca.sc` presmoothing option within the linear functional terms (`lf`).
+
+**Usage:**
+
+```r
+pfr_handler <- PFRModel$new(W, y, n_eval, train_ratio)
+pfr_handler$fit(option = "all")
+errors <- pfr_handler$computeError()
+
+```
+
+```{r}
+#' @title PFR Model Handler
+#' @description R6 class to prepare data, fit, and evaluate a Penalized Functional Regression (PFR) model.
+#'
+#' @importFrom R6 R6Class
+#' @importFrom refund pfr
+#' @export
+PFRModel <- R6::R6Class(
+  "PFRModel",
+
+  public = list(
+    # --- Public Fields ---
+    trainData = NULL,
+    testData = NULL,
+    model = NULL,
+    n_scalar_predictor = NULL,
+    n_basis = NULL,
+    eval_point = NULL,
+
+    # Prediction storage
+    y_train_pred = NULL,
+    y_test_pred = NULL,
+
+    # Normalization factors for error reporting (optional usage)
+    response_range_train = 1, # Default to 1 (standardized data usually implies scale ~1)
+    response_range_test = 1,
+
+    #' @title Initialize PFR Model
+    #' @description Constructs the instance, splits/normalizes data, and formats it for `refund::pfr`.
+    #'
+    #' @param W A `predictor_hybrid` object containing all predictors.
+    #' @param y Vector. Response variable.
+    #' @param n_eval Integer. Number of evaluation points for functional predictors.
+    #' @param train_ratio Numeric. Split ratio for training data.
+    initialize = function(W, y, n_eval, train_ratio) {
+
+      # 1. Run Preprocessing Pipeline (Split & Normalize)
+      # Assumes `split_and_normalize.all` is available in the environment
+      processed <- split_and_normalize.all(W, y, train_ratio)
+
+      # 2. Set Metadata
+      self$n_scalar_predictor <- W$n_scalar
+      # Assume all functional predictors share the same basis size
+      self$n_basis <- W$n_basis_list[1]
+      self$eval_point <- W$eval_point # Use the points from the object directly
+
+      # If n_eval is different from W$eval_point length, you might need interpolation.
+      # Here we assume W$eval_point is sufficient, but if you strictly need a new grid:
+      # eval_min <- min(W$eval_point)
+      # eval_max <- max(W$eval_point)
+      # self$eval_point <- seq(eval_min, eval_max, length.out = n_eval)
+
+      # 3. Prepare Training Data
+      # PFR works best with lists or data frames. We use a list to allow matrix columns easily.
+      self$trainData <- list()
+
+      # Add Scalar Predictors (X1, X2, ...)
+      # We extract columns from Z and name them explicitly
+      for(i in 1:self$n_scalar_predictor) {
+        self$trainData[[paste0("X", i)]] <- processed$predictor_train$Z[, i]
+      }
+
+      self$trainData$response <- processed$response_train
+
+      # Add Functional Predictors (F1, F2) converted to dense matrices (Sample x Time)
+      # Transpose is needed because eval.fd returns (Time x Sample)
+      self$trainData$F1 <- t(fda::eval.fd(self$eval_point, processed$predictor_train$functional_list[[1]]))
+      self$trainData$F2 <- t(fda::eval.fd(self$eval_point, processed$predictor_train$functional_list[[2]]))
+
+      # 4. Prepare Test Data
+      self$testData <- list()
+      for(i in 1:self$n_scalar_predictor) {
+        self$testData[[paste0("X", i)]] <- processed$predictor_test$Z[, i]
+      }
+      self$testData$response <- processed$response_test
+      self$testData$F1 <- t(fda::eval.fd(self$eval_point, processed$predictor_test$functional_list[[1]]))
+      self$testData$F2 <- t(fda::eval.fd(self$eval_point, processed$predictor_test$functional_list[[2]]))
+
+      # Store response ranges if needed for normalized error calculation
+      # Since data is already standardized, ranges might be small.
+      self$response_range_train <- diff(range(self$trainData$response))
+      self$response_range_test  <- diff(range(self$testData$response))
+    },
+
+    #' @title Generate PFR Model Formula
+    #' @description Constructs the formula string dynamically based on the selected option.
+    #' Uses `presmooth = 'fpca.sc'` for functional terms.
+    #'
+    #' @param option Character. "all", "functional_only", or "scalar_only".
+    #' @return A character string representing the PFR call.
+    get_model_string = function(option = "all") {
+
+      # Validate option
+      if (!option %in% c("all", "functional_only", "scalar_only")) {
+        stop("Error: 'option' must be one of 'all', 'functional_only', or 'scalar_only'.")
+      }
+
+      # 1. Build Scalar Predictor String
+      scalar_part <- ""
+      if (option != "functional_only") {
+        # "X1 + X2 + ... + Xp"
+        scalar_part <- paste0(paste0("X", 1:self$n_scalar_predictor), collapse = " + ")
+        # Add leading " + " if needed later
+        if (option == "all") scalar_part <- paste0(" + ", scalar_part)
+      }
+
+      # 2. Build Functional Predictor String
+      functional_part <- ""
+      if (option != "scalar_only") {
+        # Note: self$eval_point is injected directly via string interpolation requires it to be available in scope
+        # Or we rely on the data object. 'lf' usually needs 'argvals' passed explicitly if not in data.
+        # Since we use eval(parse()), we reference 'self$eval_point'.
+
+        term_f1 <- paste0(
+          "lf(F1, argvals = self$eval_point, presmooth = 'fpca.sc', presmooth.opts = list(nbasis = ", 
+          self$n_basis, "))"
+        )
+        term_f2 <- paste0(
+          "lf(F2, argvals = self$eval_point, presmooth = 'fpca.sc', presmooth.opts = list(nbasis = ", 
+          self$n_basis, "))"
+        )
+        functional_part <- paste(term_f1, term_f2, sep = " + ")
+      }
+
+      # 3. Combine into Full Formula
+      # Result: "pfr(response ~ lf(...) + lf(...) + X1 + ..., data = self$trainData)"
+      full_formula <- paste0("refund::pfr(response ~ ", functional_part, scalar_part, ", data = self$trainData)")
+
+      return(full_formula)
+    },
+
+    #' @title Fit PFR Model
+    #' @description Evaluates the formula string to fit the model.
+    #' @param option Character. Model configuration option.
+    fit = function(option = "all") {
+      # Get the command string
+      cmd <- self$get_model_string(option)
+
+      # Execute the command in the current environment
+      self$model <- eval(parse(text = cmd))
+    },
+
+    #' @title Compute Prediction Error
+    #' @description Predicts on training and testing sets and computes normalized RMSE.
+    #' @return A list with `train_error` and `test_error`.
+    computeError = function() {
+      if (is.null(self$model)) stop("Model not fitted. Run fit() first.")
+
+      # Predict
+      self$y_train_pred <- predict(self$model, newdata = self$trainData)
+      self$y_test_pred  <- predict(self$model, newdata = self$testData)
+
+      # Compute RMSE (Normalized by range, as per original code)
+      # Note: Ensure ranges are non-zero to avoid division by zero
+      r_train <- if(self$response_range_train > 0) self$response_range_train else 1
+      r_test  <- if(self$response_range_test > 0)  self$response_range_test  else 1
+
+      train_rmse <- sqrt(mean((self$trainData$response - self$y_train_pred)^2)) / r_train
+      test_rmse  <- sqrt(mean((self$testData$response - self$y_test_pred)^2))  / r_test
+
+      return(list(train_error = train_rmse, test_error = test_rmse))
+    }
+  )
+)
 ```

### 2025-12-30 simul.Rmd
before modifying get_rho

---
title: "simulation"
output: html_document
date: "2025-12-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
# ==============================================================================
# EQUIVALENCE CHECK: exact_inprod() vs get_rho()
# ==============================================================================

library(fda)

# 1. DEFINE FUNCTIONS (To ensure environment is self-contained)
# ------------------------------------------------------------------------------

# A. Your Function (Logic: Matrix Multiplication)

# 2. PREPARE DATA
# ------------------------------------------------------------------------------
set.seed(123)
n_sample <- 50
n_basis  <- 10
basis <- create.bspline.basis(c(0,1), n_basis)

# Generate Random W (Data)
coefs_W <- matrix(rnorm(n_sample * n_basis), n_basis, n_sample)
Z_W <- matrix(rnorm(n_sample * 5), n_sample, 5)
fd_W <- fd(coefs_W, basis)
W_current <- list(
  Z = Z_W,
  functional_list = list(fd_W), # Single functional predictor for simplicity
  n_sample = n_sample,
  n_functional = 1,
  n_scalar = 5,
  n_basis_list = list(n_basis)
)

# CRITICAL STEP: Populate 'gram_list' for get_rho to work
# Your function assumes this exists. We must calculate it exactly as FDA does.
W_current$gram_list <- list(
  fda::inprod(basis, basis)
)

# Generate Random xi (Direction)
coefs_xi <- matrix(rnorm(n_basis), n_basis, 1) # 1 direction
Z_xi <- matrix(rnorm(5), 1, 5)
fd_xi <- fd(coefs_xi, basis)
xi_current <- list(
  Z = Z_xi,
  functional_list = list(fd_xi)
)

# 3. CONVERT INPUTS
# ------------------------------------------------------------------------------
# get_rho expects a flattened vector 'd_vec'.
# We must flatten xi_current: [functional_coefs | scalar_weights]
d_vec <- c(as.vector(coefs_xi), as.vector(Z_xi))

# 4. RUN COMPARISON
# ------------------------------------------------------------------------------

# Run My Function
val_exact <- exact_inprod(W_current, xi_current)

# Run Your Function (Note: d_vec is 1st arg, W is 2nd arg)
val_yours <- get_rho(d_vec, W_current)

# 5. VERDICT
# ------------------------------------------------------------------------------
diff <- max(abs(val_exact - val_yours))

cat("========================================\n")
cat("      EQUIVALENCE CHECK RESULT       \n")
cat("========================================\n")
cat(sprintf("Max Difference: %.10e\n", diff))

if(isTRUE(all.equal(val_exact, val_yours))) {
  cat("CONCLUSION: ✅ FUNCTIONS ARE IDENTICAL.\n")
  cat("Your implementation uses valid exact matrix algebra.\n")
} else {
  cat("CONCLUSION: ❌ FUNCTIONS DIFFER.\n")
}
```

```{r}
#' Exact Hybrid Inner Product (Matrix Based)
#' 
#' Calculates <W, xi> using Basis Inner Product Matrices (J).
#' Guarantees mathematical exactness for B-splines.
#' 
#' @param W Hybrid predictor (N samples)
#' @param xi Hybrid direction (1 sample/direction)
#' @return Numeric vector of length N (The scores)
exact_inprod <- function(W, xi) {

  # 1. Scalar Part (Dot Product)
  # (N x p) %*% (p x 1)
  scores <- as.matrix(W$Z) %*% t(as.matrix(xi$Z))

  # 2. Functional Part (Exact Integral via J matrix)
  for(k in seq_along(W$functional_list)) {
    fd_W  <- W$functional_list[[k]]
    fd_xi <- xi$functional_list[[k]]

    # Basis Inner Product Matrix: J[i,j] = Int(phi_i * phi_j)
    J <- fda::inprod(fd_W$basis, fd_W$basis)

    # Score = Coef_W^T * J * Coef_xi
    # (N x K) * (K x K) * (K x 1) -> (N x 1)

    # Efficient calculation:
    # We broadcast the (J %*% Coef_xi) vector across all N samples
    weighted_xi <- J %*% fd_xi$coefs

    # Add to scores (t(coefs) is N x K)
    scores <- scores + t(fd_W$coefs) %*% weighted_xi
  }

  return(as.vector(scores))
}
```

```{r}
# ==============================================================================
# SIMULATION: The Annihilation Property "Torture Test"
# Verifies: < W_resid[l+1], xi[l] >_H == 0 under extreme conditions
# ==============================================================================

library(fda)
library(ggplot2)
library(dplyr)
library(tidyr)

# ------------------------------------------------------------------------------
# 1. HELPER: EXACT INNER PRODUCT (Crucial for Verification)
# ------------------------------------------------------------------------------
exact_inprod <- function(W, xi) {
  # 1. Scalar Part
  scores <- as.matrix(W$Z) %*% t(as.matrix(xi$Z))

  # 2. Functional Part (Exact Integral via J matrix)
  for(k in seq_along(W$functional_list)) {
    fd_W  <- W$functional_list[[k]]
    fd_xi <- xi$functional_list[[k]]
    J <- fda::inprod(fd_W$basis, fd_W$basis)
    weighted_xi <- J %*% fd_xi$coefs
    scores <- scores + t(fd_W$coefs) %*% weighted_xi
  }
  return(as.vector(scores))
}

# ------------------------------------------------------------------------------
# 2. DATA GENERATION: "The Torture Chamber"
# ------------------------------------------------------------------------------
generate_torture_data <- function(n_sample = 100) {
  # A. Shared Latent Factors (Creates collinearity)
  t1 <- rnorm(n_sample, sd=10)
  t2 <- rnorm(n_sample, sd=0.1) # Tiny variance component

  eval_points <- seq(0, 1, length.out=100)
  basis <- create.bspline.basis(c(0,1), 15) # Higher basis dim

  # B. Functional Predictor 1: High Magnitude, Low Freq
  X1 <- outer(t1, sin(2*pi*eval_points)) 
  fd1 <- Data2fd(eval_points, t(X1), basis)

  # C. Functional Predictor 2: Low Magnitude, High Freq (Noise trap)
  X2 <- outer(t2, sin(10*pi*eval_points)) + matrix(rnorm(n_sample*100, sd=0.01), 100, n_sample)
  fd2 <- Data2fd(eval_points, t(X2), basis)

  # D. Scalars: 50 Variables, Rank Deficient (Rank ~ 2)
  Z_base <- matrix(rnorm(n_sample * 2), n_sample, 2)
  Z_noise <- matrix(rnorm(n_sample * 50, sd=0.001), n_sample, 50)
  # Mix: All 50 scalars depend on just 2 random vectors
  Z <- Z_base %*% matrix(rnorm(2*50), 2, 50) + Z_noise

  # E. Response
  y <- t1 * 0.5 + t2 * 10 + rnorm(n_sample)

  W_init <- predictor_hybrid(Z, list(fd1, fd2), eval_points)
  return(list(W = W_init, y = y))
}

# ------------------------------------------------------------------------------
# 3. RUN SIMULATION
# ------------------------------------------------------------------------------
set.seed(999)
data <- generate_torture_data(100)
processed <- split_and_normalize.all(data$W, data$y, train_ratio=0.99)

W_current <- processed$predictor_train
y_current <- processed$response_train

# TEST PARAMETERS
# We use different lambdas for different functions to stress the metric
lambda_vec <- c(10, 0.01) 
n_iter <- 5
results_df <- data.frame()

message("Running Torture Test (Exact Matrix Mode)...")

for(l in 1:n_iter) {

  # 1. Get Direction (Xi) - Penalized
  xi_current <- get_xi_hat_linear_pen(W_current, y_current, lambda_vec)

  # 2. Get Scores (Rho) -- EXACT
  #rho_current <- exact_inprod(W_current, xi_current)
  rho_current <- get_rho(W_current, xi_current)

  # 3. Get Loadings (Delta)
  delta_current <- get_delta(W_current, rho_current) 
  nu_current    <- get_nu(y_current, rho_current)

  # 4. MEASURE SIGNAL BEFORE DEFLATION
  signal_mag <- sqrt(sum(exact_inprod(W_current, xi_current)^2))

  # 5. Deflate
  W_next <- residualize_predictor(W_current, rho_current, delta_current)
  y_next <- residualize_y(y_current, rho_current, nu_current)

  # 6. MEASURE LEAKAGE AFTER DEFLATION (The Proof Condition)
  leakage_vec <- exact_inprod(W_next, xi_current)
  leakage_mag <- sqrt(sum(leakage_vec^2))

  # 7. Log
  status <- ifelse(leakage_mag < 1e-9, "PASS", "FAIL")

  results_df <- rbind(results_df, data.frame(
    Iteration = l,
    Signal_Strength = signal_mag,
    Residual_Leakage = leakage_mag,
    Status = status
  ))

  cat(sprintf("Iter %d: Signal=%.2e | Leakage=%.2e | %s\n", 
              l, signal_mag, leakage_mag, status))

  W_current <- W_next
  y_current <- y_next
}

# ------------------------------------------------------------------------------
# 4. VISUALIZATION
# ------------------------------------------------------------------------------
cat("\n=======================================================\n")
cat("      TORTURE TEST RESULTS \n")
cat("=======================================================\n")
print(results_df)

df_long <- tidyr::pivot_longer(results_df, cols = c("Signal_Strength", "Residual_Leakage"))

ggplot(df_long, aes(x=factor(Iteration), y=value, fill=name)) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_y_continuous(trans="log10") +
  labs(title="Annihilation Torture Test",
       subtitle="Even with high collinearity and penalties, leakage must be ~0",
       y="Magnitude (Log10)",
       x="Iteration") +
  theme_minimal() +
  scale_fill_manual(values=c("firebrick", "steelblue")) +
  geom_hline(yintercept=1e-10, linetype="dashed")
```

```{r}
# ==============================================================================
# STUDY: PLS Geometric Properties (Orthogonality & Relevance)
# ==============================================================================

library(fda)
library(ggplot2)
library(dplyr)
library(tidyr)

# ------------------------------------------------------------------------------
# 1. SETUP
# ------------------------------------------------------------------------------

lambda_scenarios <- list(
  "Scenario A: weak"    = c(0.1, 0.1),         # Pure NIPALS
  "Scenario B: mixed"  = c(0.1, 5),    # Mixed Smoothness
  "Scenario C: strong"   = c(5, 5)        # Strong Regularization
)

n_rep <- 100       # Repetitions
n_comp <- 6        # Components
results_ortho <- data.frame() # Store orthogonality results
results_corr  <- data.frame() # Store correlation results

# Data Generation Function
generate_robust_data <- function(n_sample = 200, n_scalar = 50) {
  t1 <- rnorm(n_sample, sd = 10)
  t2 <- rnorm(n_sample, sd = 5)
  t3 <- rnorm(n_sample, sd = 2)

  eval_points <- seq(0, 1, length.out = 100)
  basis <- create.bspline.basis(c(0, 1), 10)

  X1 <- outer(t1, sin(2*pi*eval_points)) + outer(t2, cos(2*pi*eval_points))
  fd1 <- Data2fd(eval_points, t(X1), basis)

  X2 <- outer(t1, sin(4*pi*eval_points)) + outer(t2, cos(4*pi*eval_points))
  fd2 <- Data2fd(eval_points, t(X2), basis)

  Z <- matrix(0, n_sample, n_scalar)
  for(j in 1:n_scalar) Z[,j] <- t1*runif(1) + t3*runif(1) + rnorm(n_sample)

  y <- t1 * 2 - t2 * 1.5 + rnorm(n_sample)
  W <- predictor_hybrid(Z, list(fd1, fd2), eval_points)

  return(list(W = W, y = y))
}

# Helper: Compute Inner Product of Two Hybrid Vectors
# (Required to check orthogonality of xi)
hybrid_inner_product <- function(h1, h2) {
  # Scalar dot product
  val <- sum(h1$Z * h2$Z)
  # Functional inner products
  for(k in seq_along(h1$functional_list)) {
    val <- val + inprod(h1$functional_list[[k]], h2$functional_list[[k]])
  }
  return(as.numeric(val))
}

# ------------------------------------------------------------------------------
# 2. RUN SIMULATION LOOP
# ------------------------------------------------------------------------------
message("Starting Extended Simulation...")
set.seed(999)

for (scenario_name in names(lambda_scenarios)) {
  lam_pair <- lambda_scenarios[[scenario_name]]

  for (i in 1:n_rep) {
    # Generate & Fit
    data <- generate_robust_data(n_sample = 200)
    processed <- split_and_normalize.all(data$W, data$y, train_ratio = 0.8)

    fit <- fit.hybridPLS(
      W = processed$predictor_train, 
      y = processed$response_train, 
      n_iter = n_comp, 
      lambda = lam_pair
    )

    # --- METRIC 1: SCORE (Rho) ORTHOGONALITY ---
    rho_mat <- do.call(cbind, fit$rho)
    cor_rho <- cor(rho_mat)
    diag(cor_rho) <- 0
    max_rho_overlap <- max(abs(cor_rho))

    # --- METRIC 2: DIRECTION (Xi) ORTHOGONALITY ---
    # We calculate the max pairwise inner product between different weight vectors
    # Note: xi are normalized, so self-inner-product is 1.
    xi_list <- fit$xi
    xi_overlaps <- numeric()

    for(j in 1:(n_comp-1)) {
      for(k in (j+1):n_comp) {
        # Dot product between direction j and direction k
        dp <- hybrid_inner_product(xi_list[[j]], xi_list[[k]])
        xi_overlaps <- c(xi_overlaps, abs(dp))
      }
    }
    max_xi_overlap <- max(xi_overlaps)

    # Record Orthogonality Stats
    results_ortho <- rbind(results_ortho, data.frame(
      Scenario = scenario_name,
      Repetition = i,
      Max_Score_Corr = max_rho_overlap,    # Should be ~0
      Max_Direction_Cos = max_xi_overlap   # Can be > 0
    ))

    # --- METRIC 3: SCORE vs RESPONSE CORRELATION ---
    # Does Comp 1 explain Y better than Comp 2?
    y_vec <- processed$response_train
    cor_y <- cor(rho_mat, y_vec)

    # Store trajectory for this repetition
    for(k in 1:n_comp) {
      results_corr <- rbind(results_corr, data.frame(
        Scenario = scenario_name,
        Repetition = i,
        Component = k,
        Correlation_with_Y = abs(cor_y[k, 1])
      ))
    }
  }
}

# ------------------------------------------------------------------------------
# 3. REPORT GENERATION
# ------------------------------------------------------------------------------

# --- TABLE 1: Orthogonality (Scores vs Directions) ---
summary_ortho <- results_ortho %>%
  group_by(Scenario) %>%
  summarise(
    Score_Orthogonality = mean(Max_Score_Corr),
    Direction_Overlap   = mean(Max_Direction_Cos)
  )

cat("\n=================================================================\n")
cat(" TABLE 1: Geometric Properties (Scores vs Directions)\n")
cat("=================================================================\n")
cat("NOTE: 'Score' should be 0 (Orthogonal). 'Direction' can be > 0.\n\n")
print(summary_ortho)

# --- VISUALIZATION: Relevance Decay ---
# We want to see if correlation drops as component index increases

summary_corr <- results_corr %>%
  group_by(Scenario, Component) %>%
  summarise(
    Mean_Corr = mean(Correlation_with_Y),
    SD_Corr = sd(Correlation_with_Y)
  )

p_decay <- ggplot(summary_corr, aes(x = Component, y = Mean_Corr, color = Scenario)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = Mean_Corr - SD_Corr, ymax = Mean_Corr + SD_Corr), width = 0.2) +
  labs(title = "Predictive Relevance Decay",
       subtitle = "Correlation between PLS Scores and Response Y",
       y = "|Correlation(Score, Y)|",
       x = "Component Index") +
  theme_bw() +
  scale_x_continuous(breaks = 1:n_comp)

print(p_decay)
```

```{r}
# ==============================================================================
# PLS VERIFICATION: Prediction & Beta Recovery
# ==============================================================================

library(fda)
library(ggplot2)
library(gridExtra)
library(FSHybridPLS) # Your package

# ------------------------------------------------------------------------------
# 1. GENERATE TRUTH (Linear Model)
# ------------------------------------------------------------------------------
generate_regression_truth <- function(n_sample = 200, n_eval = 100, noise_sd = 0.5) {

  eval_points <- seq(0, 1, length.out = n_eval)
  basis_obj <- create.bspline.basis(c(0, 1), 20)

  # --- A. True Coefficient Function (Beta) ---
  # A distinct shape: Sine wave with a trend
  true_beta_vec <- sin(2 * pi * eval_points) + 1.5 * eval_points
  # Center it (standard practice)
  true_beta_vec <- true_beta_vec - mean(true_beta_vec)

  # --- B. Functional Predictors (X) ---
  # Smooth random curves
  coefs <- matrix(rnorm(20 * n_sample), 20, n_sample)
  # Smooth the coefficients to make curves realistic
  smooth_mat <- chol(ar1_cov(20, 0.8))
  coefs <- t(smooth_mat) %*% coefs

  fd_obj <- fd(coefs, basis_obj)
  X_vals <- eval.fd(eval_points, fd_obj) # 100 x 200

  # --- C. Response (Y) ---
  # Y = Integral( X(t) * Beta(t) ) + Noise
  # Approx integral as dot product * dt
  dt <- 1 / n_eval

  # Calculate signal
  # (100 x 200) * (100 x 1) -> broadcasting requires care or loop
  # Signal = colSums( X * beta ) * dt
  signal <- colSums(X_vals * true_beta_vec) * dt

  # Add noise
  y <- signal + rnorm(n_sample, sd = noise_sd)

  # Scalar Z (Noise only, to prove PLS ignores it)
  Z <- matrix(rnorm(n_sample), n_sample, 1)

  W <- predictor_hybrid(Z, list(fd_obj), eval_points)

  return(list(
    W = W, y = y, 
    true_beta = true_beta_vec,
    eval_points = eval_points
  ))
}

# ------------------------------------------------------------------------------
# 2. RUN SIMULATION
# ------------------------------------------------------------------------------
set.seed(42)
# Generate
sim_data <- generate_regression_truth(n_sample = 200, noise_sd = 0.1)

# Split (Train/Test)
processed <- split_and_normalize.all(sim_data$W, sim_data$y, train_ratio = 0.7)

# Fit PLS
# Using 4 components (should be enough to capture the beta shape)
# Lambda = 0 ensures we test the core algorithm, not the penalty
fit <- fit.hybridPLS(
  W = processed$predictor_train, 
  y = processed$response_train, 
  n_iter = 4, 
  lambda = c(0),
  validation_data = list(W_test = processed$predictor_test, y_test = processed$response_test)
)

# ------------------------------------------------------------------------------
# 3. VERIFICATION PLOTS
# ------------------------------------------------------------------------------

# --- A. Prediction Check (Test Set) ---
# Reconstruct Y_pred for Test Set using the Final Beta (Comp 4)
beta_final <- fit$beta[[4]]
y_pred <- inprod.predictor_hybrid(processed$predictor_test, beta_final)
y_true <- processed$response_test

r2_test <- 1 - sum((y_true - y_pred)^2) / sum((y_true - mean(y_true))^2)

df_pred <- data.frame(Observed = y_true, Predicted = y_pred)

p1 <- ggplot(df_pred, aes(x = Observed, y = Predicted)) +
  geom_point(alpha = 0.6, color = "blue") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  labs(title = paste0("Prediction Accuracy (R2 = ", round(r2_test, 3), ")"),
       subtitle = "Points should lie on the red diagonal") +
  theme_bw()

# --- B. Beta Recovery Check ---
# Extract estimated functional beta
beta_est_fd <- fit$beta[[4]]$functional_list[[1]]
beta_est_vec <- eval.fd(sim_data$eval_points, beta_est_fd)

# Normalize both to compare SHAPE (scale might differ due to normalization)
scale_vec <- function(x) as.vector((x - mean(x)) / sd(x))

df_beta <- data.frame(
  Time = sim_data$eval_points,
  True = scale_vec(sim_data$true_beta),
  Estimated = scale_vec(beta_est_vec)
)

beta_corr <- cor(df_beta$True, df_beta$Estimated)

p2 <- ggplot(df_beta, aes(x = Time)) +
  geom_line(aes(y = True, color = "True Beta"), linewidth = 1.2, linetype = "dashed") +
  geom_line(aes(y = Estimated, color = "PLS Estimate"), linewidth = 1) +
  scale_color_manual(values = c("True Beta" = "black", "PLS Estimate" = "red")) +
  labs(title = paste0("Beta Reconstruction (Corr = ", round(beta_corr, 3), ")"),
       subtitle = "Red line should match Black dashed line") +
  theme_bw() + theme(legend.position = "bottom")

# ------------------------------------------------------------------------------
# 4. RESULTS
# ------------------------------------------------------------------------------
grid.arrange(p1, p2, nrow = 1)

cat("\n========================================\n")
cat("      PLS REGRESSION VERIFICATION       \n")
cat("========================================\n")
cat(sprintf("1. Test R-Squared:      %.4f  [%s]\n", r2_test, ifelse(r2_test > 0.9, "PASS", "FAIL")))
cat(sprintf("2. Beta Shape Corr:     %.4f  [%s]\n", beta_corr, ifelse(beta_corr > 0.95, "PASS", "FAIL")))

if(r2_test > 0.9 && beta_corr > 0.95) {
  cat("\nCONCLUSION: ✅ PLS Works. It predicts accurately and learns the correct shape.\n")
} else {
  cat("\nCONCLUSION: ❌ Something is wrong.\n")
}
```

```{r}
# ==============================================================================
# PLS VERIFICATION: Prediction & Beta Recovery
# ==============================================================================

library(fda)
library(ggplot2)
library(gridExtra)
library(FSHybridPLS) # Your package

# ------------------------------------------------------------------------------
# 1. GENERATE TRUTH (Linear Model)
# ------------------------------------------------------------------------------
generate_regression_truth <- function(n_sample = 200, n_eval = 100, noise_sd = 0.01) {

  eval_points <- seq(0, 1, length.out = n_eval)
  basis_obj <- create.bspline.basis(c(0, 1), 20)

  # --- A. True Coefficient Function (Beta) ---
  # A distinct shape: Sine wave with a trend
  true_beta_vec <- sin(2 * pi * eval_points) + 1.5 * eval_points
  # Center it (standard practice)
  true_beta_vec <- true_beta_vec - mean(true_beta_vec)

  # --- B. Functional Predictors (X) ---
  # Smooth random curves
  coefs <- matrix(rnorm(20 * n_sample), 20, n_sample)
  # Smooth the coefficients to make curves realistic
  smooth_mat <- chol(ar1_cov(20, 0.8))
  coefs <- t(smooth_mat) %*% coefs

  fd_obj <- fd(coefs, basis_obj)
  X_vals <- eval.fd(eval_points, fd_obj) # 100 x 200

  # --- C. Response (Y) ---
  # Y = Integral( X(t) * Beta(t) ) + Noise
  # Approx integral as dot product * dt
  dt <- 1 / n_eval

  # Calculate signal
  # (100 x 200) * (100 x 1) -> broadcasting requires care or loop
  # Signal = colSums( X * beta ) * dt
  signal <- colSums(X_vals * true_beta_vec) * dt

  # Add noise
  y <- signal + rnorm(n_sample, sd = noise_sd)

  # Scalar Z (Noise only, to prove PLS ignores it)
  Z <- matrix(rnorm(n_sample), n_sample, 1)

  W <- predictor_hybrid(Z, list(fd_obj), eval_points)

  return(list(
    W = W, y = y, 
    true_beta = true_beta_vec,
    eval_points = eval_points
  ))
}

# ------------------------------------------------------------------------------
# 2. RUN SIMULATION
# ------------------------------------------------------------------------------
set.seed(42)
# Generate
sim_data <- generate_regression_truth(n_sample = 200, noise_sd = 0.01)

# Split (Train/Test)
processed <- split_and_normalize.all(sim_data$W, sim_data$y, train_ratio = 0.7)

# Fit PLS
# Using 4 components (should be enough to capture the beta shape)
# Lambda = 0 ensures we test the core algorithm, not the penalty
fit <- fit.hybridPLS(
  W = processed$predictor_train, 
  y = processed$response_train, 
  n_iter = 4, 
  lambda = c(0),
  validation_data = list(W_test = processed$predictor_test, y_test = processed$response_test)
)

# ------------------------------------------------------------------------------
# 3. VERIFICATION PLOTS
# ------------------------------------------------------------------------------

# --- A. Prediction Check (Test Set) ---
# Reconstruct Y_pred for Test Set using the Final Beta (Comp 4)
beta_final <- fit$beta[[4]]
y_pred <- inprod.predictor_hybrid(processed$predictor_test, beta_final)
y_true <- processed$response_test

r2_test <- 1 - sum((y_true - y_pred)^2) / sum((y_true - mean(y_true))^2)

df_pred <- data.frame(Observed = y_true, Predicted = y_pred)

p1 <- ggplot(df_pred, aes(x = Observed, y = Predicted)) +
  geom_point(alpha = 0.6, color = "blue") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  labs(title = paste0("Prediction Accuracy (R2 = ", round(r2_test, 3), ")"),
       subtitle = "Points should lie on the red diagonal") +
  theme_bw()

# --- B. Beta Recovery Check ---
# Extract estimated functional beta
beta_est_fd <- fit$beta[[4]]$functional_list[[1]]
beta_est_vec <- eval.fd(sim_data$eval_points, beta_est_fd)

# Normalize both to compare SHAPE (scale might differ due to normalization)
scale_vec <- function(x) as.vector((x - mean(x)) / sd(x))

df_beta <- data.frame(
  Time = sim_data$eval_points,
  True = scale_vec(sim_data$true_beta),
  Estimated = scale_vec(beta_est_vec)
)

beta_corr <- cor(df_beta$True, df_beta$Estimated)

p2 <- ggplot(df_beta, aes(x = Time)) +
  geom_line(aes(y = True, color = "True Beta"), linewidth = 1.2, linetype = "dashed") +
  geom_line(aes(y = Estimated, color = "PLS Estimate"), linewidth = 1) +
  scale_color_manual(values = c("True Beta" = "black", "PLS Estimate" = "red")) +
  labs(title = paste0("Beta Reconstruction (Corr = ", round(beta_corr, 3), ")"),
       subtitle = "Red line should match Black dashed line") +
  theme_bw() + theme(legend.position = "bottom")

# ------------------------------------------------------------------------------
# 4. RESULTS
# ------------------------------------------------------------------------------
grid.arrange(p1, p2, nrow = 1)

cat("\n========================================\n")
cat("      PLS REGRESSION VERIFICATION       \n")
cat("========================================\n")
cat(sprintf("1. Test R-Squared:      %.4f  [%s]\n", r2_test, ifelse(r2_test > 0.9, "PASS", "FAIL")))
cat(sprintf("2. Beta Shape Corr:     %.4f  [%s]\n", beta_corr, ifelse(beta_corr > 0.95, "PASS", "FAIL")))

if(r2_test > 0.9 && beta_corr > 0.95) {
  cat("\nCONCLUSION: ✅ PLS Works. It predicts accurately and learns the correct shape.\n")
} else {
  cat("\nCONCLUSION: ❌ Something is wrong.\n")
}
```

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

## is normalization hurtful?
```{r}
# ==============================================================================
# DIAGNOSTIC: Is Normalization Killing PLS?
# ==============================================================================

library(fda)
library(Matrix)
library(ggplot2)

# 1. GENERATE LATENT DATA (Signal defined by Variance)
# ------------------------------------------------------------------------------
# We create 2 components:
# Comp 1: Huge Variance (SD=10) -> Should be found FIRST
# Comp 2: Small Variance (SD=2) -> Should be found SECOND
generate_variance_signal <- function(n_sample = 200) {
  t1 <- rnorm(n_sample, sd = 10)
  t2 <- rnorm(n_sample, sd = 2)

  # Orthogonalize exactly
  T_mat <- svd(cbind(t1, t2))$u %*% diag(c(10, 2))

  # Functional Predictor X (Evaluation points 0 to 1)
  eval_points <- seq(0, 1, length.out=100)
  shape1 <- sin(2*pi*eval_points)
  shape2 <- cos(2*pi*eval_points)

  X <- outer(T_mat[,1], shape1) + outer(T_mat[,2], shape2) + rnorm(n_sample*100, sd=0.1)

  # Scalar Predictor Z (Just noise for now, to isolate Functional issue)
  Z <- matrix(rnorm(n_sample * 5), n_sample, 5)

  # Response Y (Driven by T1 mostly)
  y <- T_mat[,1] * 1 + T_mat[,2] * 1 + rnorm(n_sample, sd=0.1)

  # Create Objects
  basis_obj <- create.bspline.basis(c(0, 1), 20)
  fd_obj <- Data2fd(eval_points, t(X), basis_obj)

  W <- predictor_hybrid(Z, list(fd_obj), eval_points)

  return(list(W = W, y = y, true_scores = T_mat))
}

set.seed(123)
data <- generate_variance_signal(200)

# ==============================================================================
# SCENARIO A: RAW DATA (Preserve Variance)
# ==============================================================================
message("\n--- Running Scenario A: RAW DATA (Variance Preserved) ---")

# Manual Centering (Required for PLS, but NO scaling)
y_centered <- data$y - mean(data$y)
W_centered <- data$W
# (Assuming your PLS centers internally or we can pass centered data. 
#  For strictness, we assume Z is roughly centered by generation.)

fit_raw <- fit.hybridPLS(
  W = W_centered, 
  y = y_centered, 
  n_iter = 2, 
  lambda = c(0) # No penalty to isolate normalization issue
)

rho_raw <- do.call(cbind, fit_raw$rho)
cor_raw <- cor(rho_raw, data$true_scores)
print("Correlation (Estimated vs True):")
print(round(cor_raw, 3))

# ==============================================================================
# SCENARIO B: NORMALIZED DATA (Variance Destroyed)
# ==============================================================================
message("\n--- Running Scenario B: NORMALIZED DATA (Variance = 1) ---")

# Run your normalization pipeline
# We use train_ratio = 0.99 just to keep most data for the check
processed <- split_and_normalize.all(data$W, data$y, train_ratio = 0.99)

# Extract the TRUE scores corresponding to the training set indices
train_idx <- processed$details$split_indices$train
true_scores_subset <- data$true_scores[train_idx, ]

fit_norm <- fit.hybridPLS(
  W = processed$predictor_train, 
  y = processed$response_train, 
  n_iter = 2, 
  lambda = c(0)
)

rho_norm <- do.call(cbind, fit_norm$rho)
cor_norm <- cor(rho_norm, true_scores_subset)
print("Correlation (Estimated vs True):")
print(round(cor_norm, 3))

# ==============================================================================
# RESULT INTERPRETATION
# ==============================================================================
# Look at the diagonal of the correlation matrices.
# Ideally: [1,1] > 0.9 (Comp 1 found), [2,2] > 0.9 (Comp 2 found).

score_1_raw <- abs(cor_raw[1,1])
score_1_norm <- abs(cor_norm[1,1])

cat("\n========================================\n")
cat("          DIAGNOSTIC RESULTS            \n")
cat("========================================\n")
cat(paste0("Scenario A (Raw) Score 1 Recovery: ", round(score_1_raw, 3), "\n"))
cat(paste0("Scenario B (Norm) Score 1 Recovery: ", round(score_1_norm, 3), "\n"))

if (score_1_raw > 0.9 && score_1_norm < 0.9) {
  cat("\nCONCLUSION: 🚨 Normalization is the problem.\n")
  cat("By forcing unit variance, 'split_and_normalize.all' destroys the \n")
  cat("variance structure that PLS uses to identify the primary component.\n")
} else if (score_1_raw < 0.9) {
  cat("\nCONCLUSION: ⚠️  The Algorithm is the problem.\n")
  cat("Even with raw data, PLS failed to find the latent component.\n")
} else {
  cat("\nCONCLUSION: ✅ Both methods worked? (Check if simulation noise was too low)\n")
}
```

##

```{r}

# ==============================================================================
# HYBRID PLS VERIFICATION: Latent Factor & Coefficient Recovery
# ==============================================================================

library(fda)
library(ggplot2)
library(gridExtra) # For arranging plots
library(FSHybridPLS) # Your package

# ------------------------------------------------------------------------------
# 1. DATA GENERATION: The "Ground Truth"
# ------------------------------------------------------------------------------
generate_verification_data <- function(n_sample = 200, n_eval = 100) {

  eval_points <- seq(0, 1, length.out = n_eval)

  # --- A. Latent Scores (Truth) ---
  # We create 2 orthogonal components with distinct variances
  # Comp 1: High Variance (SD=10) -> The primary signal
  # Comp 2: Lower Variance (SD=4) -> The secondary signal
  set.seed(123)
  t1 <- rnorm(n_sample, sd = 10)
  t2 <- rnorm(n_sample, sd = 4)
  # Force exact orthogonality for clean testing
  T_mat <- svd(cbind(t1, t2))$u %*% diag(c(10, 4))

  # --- B. Loadings (Shapes) ---
  # Shape 1: Low frequency (Sine wave)
  # Shape 2: High frequency (Cosine wave)
  shape1 <- sin(2 * pi * eval_points)
  shape2 <- cos(4 * pi * eval_points)

  # --- C. Functional Predictor X ---
  # X = T * P' + Noise
  X_clean <- outer(T_mat[,1], shape1) + outer(T_mat[,2], shape2)
  X_noise <- matrix(rnorm(n_sample * n_eval, sd = 0.5), n_sample, n_eval)
  X <- X_clean + X_noise

  # --- D. Response Y ---
  # Y depends on both components: Y = 1*t1 - 2*t2 + Noise
  # This implies the TRUE BETA shape is roughly: (1*shape1) - (2*shape2)
  y <- T_mat[,1] * 1 + T_mat[,2] * (-2) + rnorm(n_sample, sd = 1)

  # Calculate True Beta Shape (Theoretical)
  # (Note: Normalized to SD=1 for shape comparison)
  true_beta_raw <- (1 * shape1) + (-2 * shape2)
  true_beta_norm <- (true_beta_raw - mean(true_beta_raw))/sd(true_beta_raw)

  # --- E. Objects ---
  basis_obj <- create.bspline.basis(c(0, 1), 20)
  fd_obj <- Data2fd(eval_points, t(X), basis_obj)

  # Dummy scalar (not used for signal, just to satisfy object structure)
  Z <- matrix(rnorm(n_sample), n_sample, 1)

  W <- predictor_hybrid(Z, list(fd_obj), eval_points)

  return(list(
    W = W, y = y, 
    true_scores = T_mat, 
    true_beta = true_beta_norm,
    eval_points = eval_points
  ))
}

# ------------------------------------------------------------------------------
# 2. EXECUTION
# ------------------------------------------------------------------------------
message("Generating Data...")
sim_data <- generate_verification_data(n_sample = 200)

message("Processing Data (Split & Normalize)...")
# We use a large training ratio to ensure stable estimation for verification
processed <- split_and_normalize.all(sim_data$W, sim_data$y, train_ratio = 0.8)

# Extract True Scores corresponding to the Training Set
train_idx <- processed$details$split_indices$train
true_scores_train <- sim_data$true_scores[train_idx, ]

message("Fitting Hybrid PLS...")
# Fit with 4 components (we expect the first 2 to capture the signal)
fit <- fit.hybridPLS(
  W = processed$predictor_train, 
  y = processed$response_train, 
  n_iter = 4, 
  lambda = c(0) # Small penalty for smoothness
)

# ------------------------------------------------------------------------------
# 3. VERIFICATION & PLOTTING
# ------------------------------------------------------------------------------

# --- TEST 1: Latent Score Recovery ---
# Extract Estimated Scores (Rho)
est_scores <- do.call(cbind, fit$rho)

# Calculate Correlations
cor_comp1 <- cor(est_scores[,1], true_scores_train[,1])
cor_comp2 <- cor(est_scores[,2], true_scores_train[,2])

# Plotting Score Recovery
df_scores <- data.frame(
  True_1 = true_scores_train[,1],
  Est_1  = est_scores[,1],
  True_2 = true_scores_train[,2],
  Est_2  = est_scores[,2]
)

# Scale Estimated scores to match True scale for visualization overlap
df_scores$Est_1 <- df_scores$Est_1 * sign(cor_comp1) * (sd(df_scores$True_1)/sd(df_scores$Est_1))
df_scores$Est_2 <- df_scores$Est_2 * sign(cor_comp2) * (sd(df_scores$True_2)/sd(df_scores$Est_2))

p1 <- ggplot(df_scores, aes(x = True_1, y = Est_1)) +
  geom_point(alpha = 0.6, color = "blue") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  labs(title = paste0("Component 1 Recovery\nCorr: ", round(abs(cor_comp1), 4)),
       x = "True Latent Score", y = "Estimated PLS Score") +
  theme_bw()

p2 <- ggplot(df_scores, aes(x = True_2, y = Est_2)) +
  geom_point(alpha = 0.6, color = "darkgreen") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  labs(title = paste0("Component 2 Recovery\nCorr: ", round(abs(cor_comp2), 4)),
       x = "True Latent Score", y = "Estimated PLS Score") +
  theme_bw()

# --- TEST 2: Beta Coefficient Recovery (CORRECTED) ---

# Extract the estimated Beta Curve (from the final cumulative beta)
beta_est_fd <- fit$beta[[2]]$functional_list[[1]] 
beta_est_vals <- eval.fd(sim_data$eval_points, beta_est_fd)

# Normalize for Shape Comparison (Mean 0, SD 1)
# CRITICAL FIX: use as.vector() to ensure it is a simple vector, not a matrix
beta_est_norm <- as.vector((beta_est_vals - mean(beta_est_vals)) / sd(beta_est_vals))

df_beta <- data.frame(
  Time = sim_data$eval_points,
  True = as.vector(sim_data$true_beta),
  Estimated = beta_est_norm
)

p3 <- ggplot(df_beta, aes(x = Time)) +
  geom_line(aes(y = True, color = "True Beta Shape"), linewidth = 1.2, linetype = "dashed") +
  geom_line(aes(y = Estimated, color = "Estimated Beta"), linewidth = 1) +
  scale_color_manual(values = c("True Beta Shape" = "black", "Estimated Beta" = "red")) +
  labs(title = "Regression Coefficient (Beta) Recovery",
       subtitle = "Shapes should overlap (Normalized)",
       y = "Normalized Coefficient Value") +
  theme_bw() + theme(legend.position = "bottom")

# ------------------------------------------------------------------------------
# 4. PRINT RESULTS
# ------------------------------------------------------------------------------
grid.arrange(p1, p2, p3, nrow = 2, layout_matrix = rbind(c(1, 2), c(3, 3)))

cat("\n============================================\n")
cat("      PLS ALGORITHM VERIFICATION RESULTS      \n")
cat("============================================\n")
cat(paste0("1. Component 1 Correlation:  ", round(abs(cor_comp1), 4), 
           ifelse(abs(cor_comp1) > 0.9, "  [PASS]", "  [FAIL]"), "\n"))
cat(paste0("2. Component 2 Correlation:  ", round(abs(cor_comp2), 4), 
           ifelse(abs(cor_comp2) > 0.8, "  [PASS]", "  [FAIL]"), "\n"))

# Beta Shape Correlation
beta_shape_cor <- cor(df_beta$True, df_beta$Estimated)
cat(paste0("3. Beta Shape Correlation:   ", round(beta_shape_cor, 4), 
           ifelse(beta_shape_cor > 0.9, "  [PASS]", "  [FAIL]"), "\n"))

```

```{r}
# ==============================================================================
# DEBUG: BARE METAL PLS (No Penalty)
# ==============================================================================

# 1. GENERATE DATA (Same as before)
sim_data <- generate_verification_data(n_sample = 200)
processed <- split_and_normalize.all(sim_data$W, sim_data$y, train_ratio = 0.8)
train_idx <- processed$details$split_indices$train
true_scores_train <- sim_data$true_scores[train_idx, ]

# 2. FIT WITH LAMBDA = 0 (Pure NIPALS)
#    We increase iterations to 5 to see if it eventually finds the signal
fit_debug <- fit.hybridPLS(
  W = processed$predictor_train, 
  y = processed$response_train, 
  n_iter = 5, 
  lambda = c(0) # <--- CRITICAL: No Smoothing
)

# 3. CHECK SCORES
est_scores <- do.call(cbind, fit_debug$rho)
cor_comp1 <- cor(est_scores[,1], true_scores_train[,1])
cor_comp2 <- cor(est_scores[,2], true_scores_train[,2])

# 4. CHECK BETA
beta_est_fd <- fit_debug$beta[[2]]$functional_list[[1]] 
beta_vals <- eval.fd(sim_data$eval_points, beta_est_fd)
beta_est_norm <- as.vector((beta_vals - mean(beta_vals)) / sd(beta_vals))
beta_cor <- cor(as.vector(sim_data$true_beta), beta_est_norm)

cat("\n--- DEBUG RESULTS (Lambda = 0) ---\n")
cat(paste0("1. Score 1 Correlation: ", round(abs(cor_comp1), 4), "\n"))
cat(paste0("2. Score 2 Correlation: ", round(abs(cor_comp2), 4), "\n"))
cat(paste0("3. Beta Correlation:    ", round(beta_cor, 4), "\n"))

# 5. CHECK PREDICTION (Is the model actually predicting Y?)
#    Reconstruct Y_hat on training data manually using the scores
#    Y_hat = Sum( rho * nu )
y_hat <- rep(0, length(processed$response_train))
for(l in 1:2) {
   # nu is the regression coef of Y on Rho
   nu_l <- sum(processed$response_train * fit_debug$rho[[l]]) / sum(fit_debug$rho[[l]]^2)
   y_hat <- y_hat + fit_debug$rho[[l]] * nu_l
}
r2 <- 1 - sum((processed$response_train - y_hat)^2) / sum((processed$response_train - mean(processed$response_train))^2)
cat(paste0("4. Training R-Squared:    ", round(r2, 4), "\n"))
```

```{r}
#' Fit Hybrid Penalized PLS with Optional Validation & Debugging
#'
#' Runs the iterative PLS algorithm.
#'
#' @param W Initial `predictor_hybrid` object (Training).
#' @param y Numeric vector of response values (Training).
#' @param n_iter Integer, number of components to extract.
#' @param lambda Numeric vector of smoothing parameters.
#' @param validation_data (Optional) List containing `W_test` and `y_test`.
#' @param debug_data (Optional) List containing `true_scores` (matrix), `true_shape` (vector), and `eval_points` (vector) for deflation checking.
#'
#' @return A list containing the model (rho, xi, beta) and optional `validation_rmse`.
#' @export
fit.hybridPLS <- function(W, y, n_iter, lambda, validation_data = NULL, debug_data = NULL) {
  # 1. Initialize storage
  W_now <- rho <- xi <- delta <- nu <- iota <- beta <- list()
  validation_rmse <- numeric(n_iter)

  # 2. Initialize current state
  W_now[[1]] <- W
  y_now <- y

  # 3. Main PLS Loop
  for (l in 1:n_iter) {
    # --- Step A: Weight Direction (xi) ---
    xi[[l]] <- get_xi_hat_linear_pen(W_now[[l]], y_now, lambda)

    # --- Step B: Scores (rho) ---
    rho[[l]] <- inprod.predictor_hybrid(W_now[[l]], xi[[l]])

    # --- Step C: Loadings (delta, nu) ---
    delta[[l]] <- get_delta(W_now[[l]], rho[[l]])
    nu[[l]] <- get_nu(y_now, rho[[l]])

    # --- Step D: Deflation ---
    W_now[[l + 1]] <- residualize_predictor(W_now[[l]], rho[[l]], delta[[l]])
    y_now <- residualize_y(y_now, rho[[l]], nu[[l]])

    # --- DEBUG CHECK: Is the Ghost of Component 1 still haunting us? ---
    if (!is.null(debug_data) && l == 1) {
      # 1. Extract the residual functional data (Matrix: Time x Sample)
      resid_fd <- W_now[[l + 1]]$functional_list[[1]] 
      resid_vals <- eval.fd(debug_data$eval_points, resid_fd)

      # 2. Project residuals onto the Known True Shape of Component 1
      #    We weight the time points by the shape to see if that signal remains.
      #    (resid_vals * shape) broadcasts the shape vector across columns
      projected_signal <- colSums(resid_vals * debug_data$true_shape)

      # 3. Check correlation with True Score 1
      ghost_correlation <- cor(projected_signal, debug_data$true_scores[,1])

      cat(sprintf("\n[DEBUG l=%d] Deflation Check:\n", l))
      cat(sprintf("  Correlation w/ True Score 1 after deflation: %.5f (Target: 0.00)\n", ghost_correlation))

      if(abs(ghost_correlation) > 0.05) {
        warning("  CRITICAL FAILURE: Deflation did not remove Component 1.")
      } else {
        cat("  SUCCESS: Component 1 successfully removed.\n")
      }
    }

    # --- Step E: Cumulative Coefficient (Beta) ---
    iota[[l]] <- xi[[l]]

    if (l == 1) {
      beta[[l]] <- scalar_mul.predictor_hybrid(iota[[l]], nu[[l]])
    } else {
      for (u in 1:(l - 1)) {
        adjustment <- inprod.predictor_hybrid(delta[[u]], xi[[l]])
        iota[[l]] <- subtr.predictor_hybrid(iota[[l]], iota[[u]], adjustment)
      }
      beta[[l]] <- add.predictor_hybrid(beta[[l - 1]], iota[[l]], nu[[l]])
    }

    # --- Step F: Validation (Optional) ---
    if (!is.null(validation_data)) {
      # Predict on test set using the current cumulative beta
      y_pred_test <- inprod.predictor_hybrid(validation_data$W_test, beta[[l]])

      # Compute RMSE
      validation_rmse[l] <- sqrt(mean((validation_data$y_test - y_pred_test)^2))
    }
  }

  return(list(
    rho = rho,
    xi = xi,
    beta = beta,
    validation_rmse = if (!is.null(validation_data)) validation_rmse else NULL,
    W_residuals = W_now # Helpful for external debugging if needed
  ))
}
```

```{r}
# ==============================================================================
# SANITY CHECK: NOISELESS PLS VERIFICATION
# ==============================================================================

library(fda)
library(ggplot2)
library(gridExtra)
library(FSHybridPLS)

# ------------------------------------------------------------------------------
# 1. GENERATE NOISELESS DATA
# ------------------------------------------------------------------------------
generate_noiseless_data <- function(n_sample = 100, n_eval = 100) {

  eval_points <- seq(0, 1, length.out = n_eval)
  basis_obj <- create.bspline.basis(c(0, 1), 20)

  # --- A. Latent Scores (T) ---
  # Deterministic orthogonal scores to guarantee separation
  # T1: Linear trend
  # T2: Quadratic trend (Orthogonalized against T1)
  t1 <- seq(-10, 10, length.out = n_sample)
  t2_raw <- t1^2
  # Gram-Schmidt Orthogonalization of t2 against t1
  t2 <- t2_raw - (sum(t2_raw * t1) / sum(t1^2)) * t1
  t2 <- t2 / sd(t2) * 5 # Scale to SD=5

  T_mat <- cbind(t1, t2)

  # --- B. Loadings (P) ---
  shape1 <- sin(2 * pi * eval_points)
  shape2 <- cos(2 * pi * eval_points)

  # --- C. Predictors (X = T*P') ---
  # NO NOISE ADDED
  X_clean <- outer(T_mat[,1], shape1) + outer(T_mat[,2], shape2)

  fd_obj <- Data2fd(eval_points, t(X_clean), basis_obj)

  # Scalar Z (Perfectly correlated with T1 to check scalar handling)
  Z <- matrix(T_mat[,1] * 0.5, n_sample, 1)

  # --- D. Response (Y = T*q) ---
  # NO NOISE ADDED
  y <- T_mat[,1] * 1 - T_mat[,2] * 2

  # True Beta Shape (Normalized)
  true_beta_raw <- (1 * shape1) - (2 * shape2)
  true_beta <- (true_beta_raw - mean(true_beta_raw)) / sd(true_beta_raw)

  W <- predictor_hybrid(Z, list(fd_obj), eval_points)

  return(list(
    W = W, y = y, 
    true_scores = T_mat, 
    true_beta = true_beta,
    eval_points = eval_points
  ))
}

# ------------------------------------------------------------------------------
# 2. RUN SIMULATION
# ------------------------------------------------------------------------------
message("Generating Noiseless Data...")
sim_data <- generate_noiseless_data(n_sample = 100)

# 1. Split/Normalize (Train Ratio 0.8)
processed <- split_and_normalize.all(sim_data$W, sim_data$y, train_ratio = 0.8)

# 2. Extract Matching Truth
train_idx <- processed$details$split_indices$train
true_scores_train <- sim_data$true_scores[train_idx, ]

# 3. Setup Debug Pack
debug_pack <- list(
  true_scores = true_scores_train,
  true_shape = sin(2 * pi * sim_data$eval_points), # Shape of Comp 1
  eval_points = sim_data$eval_points
)

message("Fitting PLS (Lambda=0)...")
fit <- fit.hybridPLS(
  W = processed$predictor_train, 
  y = processed$response_train, 
  n_iter = 3, 
  lambda = c(0), # Pure NIPALS
  debug_data = debug_pack
)

message("Fitting PLS (Sanity Matrix Implementation)...")

# CRITICAL: Pass raw objects, not the hybrid list, or extract them carefully
# The sanity function expects the hybrid W object and vector y
fit_sanity <- fit.hybridPLS.sanity(
  W = processed$predictor_train, 
  y = processed$response_train, 
  n_iter = 2
)

# ... (Now update the verification metrics to use fit_sanity) ...

# 1. Scores
# (Rest of the correlation code remains the same)

# 2. Beta
# (Rest of the beta evaluation code remains the same)

# ------------------------------------------------------------------------------
# 3. VERIFICATION METRICS
# ------------------------------------------------------------------------------
est_scores <- do.call(cbind, fit_sanity$rho)

# Correlations
c1 <- abs(cor(est_scores[,1], true_scores_train[,1]))
c2 <- abs(cor(est_scores[,2], true_scores_train[,2]))

# Beta Shape Recovery
beta_est_fd <- fit_sanity$beta_fd
beta_vals <- eval.fd(sim_data$eval_points, beta_est_fd)
beta_est_norm <- as.vector((beta_vals - mean(beta_vals)) / sd(beta_vals))
c_beta <- cor(sim_data$true_beta, beta_est_norm)

# Orthogonality Check of Estimated Scores
ortho_check <- abs(cor(est_scores[,1], est_scores[,2]))

# ------------------------------------------------------------------------------
# 4. REPORT
# ------------------------------------------------------------------------------
cat("\n============================================\n")
cat("      SANITY CHECK REPORT (NOISELESS)       \n")
cat("============================================\n")
cat(sprintf("1. Score 1 Recovery (Target 1.0):   %.5f  [%s]\n", c1, ifelse(c1 > 0.999, "PERFECT", "FAIL")))
cat(sprintf("2. Score 2 Recovery (Target 1.0):   %.5f  [%s]\n", c2, ifelse(c2 > 0.99,  "PERFECT", "FAIL")))
cat(sprintf("3. Beta Shape Recov (Target 1.0):   %.5f  [%s]\n", c_beta, ifelse(c_beta > 0.99, "PERFECT", "FAIL")))
cat(sprintf("4. Score Orthogonality (Target 0.0):%.5f  [%s]\n", ortho_check, ifelse(ortho_check < 1e-10, "PERFECT", "FAIL")))

# ------------------------------------------------------------------------------
# 5. PLOT
# ------------------------------------------------------------------------------
df_plot <- data.frame(
  Time = sim_data$eval_points,
  Truth = sim_data$true_beta,
  Estimate = beta_est_norm
)

ggplot(df_plot, aes(x=Time)) +
  geom_line(aes(y=Truth), color="black", size=2, alpha=0.5) +
  geom_line(aes(y=Estimate), color="red", linetype="dashed", size=1) +
  labs(title="Beta Recovery (Noiseless)", subtitle="Red dashed line must perfectly overlay Black line") +
  theme_bw()
```

```{r}
#' Self-Contained NIPALS for Hybrid Data (Sanity Check)
#'
#' Uses strict Basis Inner Product logic to guarantee convergence.
#' No penalty (lambda=0). No approx integration.
#'
#' @export
fit.hybridPLS.sanity <- function(W, y, n_iter) {

  # 1. Setup Matrices
  # -----------------
  # Y: Center it
  y_mat <- as.matrix(y - mean(y))
  n_sample <- nrow(y_mat)

  # Z: Scalar Predictors (Centered)
  Z_mat <- as.matrix(W$Z)
  Z_mat <- scale(Z_mat, scale = FALSE)

  # X: Functional Coefficients
  # We assume 1 functional predictor for this sanity check
  fd_obj <- W$functional_list[[1]]
  C_mat <- fd_obj$coefs # (n_basis x n_sample)
  # Center X curves
  mean_coefs <- rowMeans(C_mat)
  C_mat <- C_mat - mean_coefs

  # J: Basis Inner Product Matrix (Critical for correct norm)
  # J[i,j] = Integral( phi_i(t) * phi_j(t) )
  J_mat <- inprod(fd_obj$basis, fd_obj$basis)

  # 2. Storage
  rho_list <- list()
  beta_final_coefs <- matrix(0, nrow=nrow(C_mat), ncol=1)

  # 3. NIPALS Loop
  # -----------------
  # Current residuals
  y_cur <- y_mat
  Z_cur <- Z_mat
  C_cur <- C_mat

  for(l in 1:n_iter) {

    # --- A. Get Xi (Weights) ---
    # Maximize Cov(X*xi, y) -> xi = X'y

    # Scalar part:
    xi_Z <- t(Z_cur) %*% y_cur

    # Functional part:
    # Int( X(t) * y ) -> C * y (Vectorized)
    xi_C <- C_cur %*% y_cur

    # --- B. Normalize Xi (CRITICAL STEP) ---
    # Norm^2 = xi_Z' * xi_Z  +  Integral( xi_C(t)^2 )
    # Integral( xi_C(t)^2 ) = xi_C' * J * xi_C
    norm_sq_scalar <- sum(xi_Z^2)
    norm_sq_func   <- t(xi_C) %*% J_mat %*% xi_C

    norm_val <- sqrt(as.numeric(norm_sq_scalar + norm_sq_func))

    xi_Z <- xi_Z / norm_val
    xi_C <- xi_C / norm_val

    # --- C. Get Rho (Scores) ---
    # rho = X * xi
    # Scalar score: Z * xi_Z
    rho_Z <- Z_cur %*% xi_Z

    # Functional score: Integral( X(t) * xi_C(t) )
    # = C' * J * xi_C
    # (n_sample x basis) * (basis x basis) * (basis x 1)
    rho_func <- t(C_cur) %*% J_mat %*% xi_C

    rho <- rho_Z + rho_func

    rho_list[[l]] <- rho

    # --- D. Deflation ---
    # Subtract projection of X onto rho
    # loading p = (X' * rho) / (rho' * rho)
    rho_norm_sq <- sum(rho^2)

    # Scalar Loading
    p_Z <- (t(Z_cur) %*% rho) / rho_norm_sq
    Z_cur <- Z_cur - rho %*% t(p_Z)

    # Functional Loading (Coefficients)
    # p_C = (C * rho) / rho^2
    p_C <- (C_cur %*% rho) / rho_norm_sq
    C_cur <- C_cur - p_C %*% t(rho)

    # Deflate Y
    # q = (y' * rho) / rho^2
    q <- sum(t(y_cur) %*% rho) / rho_norm_sq
    y_cur <- y_cur - rho * q

    # --- Accumulate Beta (Approximation for checking) ---
    # For 1st component, Beta direction is just xi * q
    # We store the shape of the FIRST component only for the check
    if(l == 1) {
       beta_final_coefs <- xi_C * q
    }
  }

  # Return formatted for checking
  # Re-wrap coefficients into FD object for plotting
  beta_fd <- fd(beta_final_coefs, fd_obj$basis)

  return(list(
    rho = rho_list,
    beta_fd = beta_fd
  ))
}
```

```{r}
# ... (Inside the Noiseless Simulation Script) ...

```

```{r synthetic_data_simulation_PLS, eval=FALSE, include=FALSE}
# ==============================================================================
# HYBRID PLS vs PFR SIMULATION: Matrix-Normal Setting
# ==============================================================================

library(fda)
library(Matrix)
library(mvnfast) 
library(caret)
library(refund)    # Required for PFR
library(R6)        # Required for PFRModel
library(FSHybridPLS) # Assuming this contains predictor_hybrid, fit.hybridPLS, etc.

# ------------------------------------------------------------------------------
# 1. HELPER FUNCTIONS (Data Generation)
# ------------------------------------------------------------------------------

ar1_cov <- function(n, rho, sigma2 = 1) {
  exponent <- abs(outer(1:n, 1:n, "-"))
  sigma2 * rho^exponent
}

chunk_average <- function(vec, n_chunks) {
  len <- length(vec)
  chunk_size <- floor(len / n_chunks)
  res <- numeric(n_chunks)
  for (i in 1:n_chunks) {
    idx_start <- (i - 1) * chunk_size + 1
    idx_end   <- if (i == n_chunks) len else i * chunk_size
    res[i] <- mean(vec[idx_start:idx_end])
  }
  return(res)
}

reg_coef_1_formula <- function(x) {
  2 * sin(2.5 * pi * x) + 4 * sin(7.5 * pi * x) + 5 * sin(12.5 * pi * x)
}

reg_coef_2_formula <- function(x) {
  exp(-( (x - 0.2)^2 ) / 0.04^2) -
    exp(-( (x - 0.4)^2 ) / 0.04^2) +
    exp(-( (x - 0.6)^2 ) / 0.04^2) -
    exp(-( (x - 0.8)^2 ) / 0.04^2)
}

generate_sim_data <- function(n_sample, n_eval, n_scalar_preds, ar_slope) {

  U <- matrix(c(
    0.3585408, 0.3821649, 0.4974333,
    0.3821649, 5.6928664, 0.2608125,
    0.4974333, 0.2608125, 1.6703254
  ), nrow = 3, byrow = TRUE)

  V <- ar1_cov(n_eval, ar_slope, 1)
  Sigma_full <- kronecker(V, U)

  raw_vecs <- mvnfast::rmvn(n_sample, mu = rep(0, 3 * n_eval), sigma = Sigma_full)

  eval_point <- seq(0, 1, length.out = n_eval)
  coef_mat_1 <- matrix(0, nrow = n_eval, ncol = n_sample)
  coef_mat_2 <- matrix(0, nrow = n_eval, ncol = n_sample)
  Z_mat      <- matrix(0, nrow = n_sample, ncol = n_scalar_preds)

  for (i in 1:n_sample) {
    mat_i <- matrix(raw_vecs[i, ], nrow = 3, ncol = n_eval)
    coef_mat_1[, i] <- mat_i[1, ]
    coef_mat_2[, i] <- mat_i[2, ]
    Z_mat[i, ] <- chunk_average(mat_i[3, ], n_scalar_preds)
  }

  n_basis_pred <- 20
  basis_obj <- create.bspline.basis(c(0, 1), n_basis_pred)

  fd1 <- Data2fd(argvals = eval_point, y = coef_mat_1, basisobj = basis_obj)
  fd2 <- Data2fd(argvals = eval_point, y = coef_mat_2, basisobj = basis_obj)

  # Response Generation
  n_basis_coef <- 30
  basis_coef <- create.bspline.basis(c(0, 1), n_basis_coef)
  beta1_fd <- Data2fd(eval_point, reg_coef_1_formula(eval_point), basis_coef)
  beta2_fd <- Data2fd(eval_point, reg_coef_2_formula(eval_point), basis_coef)

  set.seed(1)
  beta_scalar <- round(rnorm(n_scalar_preds, 0, 1), 1)

  sig_fun <- inprod(fd1, beta1_fd) + inprod(fd2, beta2_fd) 
  sig_sca <- Z_mat %*% beta_scalar

  var_fun <- var(as.vector(sig_fun))
  var_sca <- var(as.vector(sig_sca))

  if (var_sca > 0) {
    multiplier <- (var_fun / var_sca) / 9
    Z_mat    <- sqrt(multiplier) * Z_mat
    sig_sca <- sqrt(multiplier) * sig_sca
  }

  total_signal <- as.vector(sig_fun + sig_sca)
  noise_var <- (1/9) * var(total_signal)
  y <- total_signal + rnorm(n_sample, 0, sqrt(noise_var))

  W_hybrid <- predictor_hybrid(
    Z = Z_mat,
    functional_list = list(fd1, fd2),
    eval_point = eval_point
  )

  return(list(W = W_hybrid, y = y))
}
```

```{r synthetic_data_simulation_PLS, eval=FALSE, include=FALSE}

# ==============================================================================
# 5. SIMULATION EXECUTION
# ==============================================================================

# A. Parameters
n_rep <- 1           # Number of repetitions
n_sample <- 100       # Total samples
n_eval <- 100         # Grid points
n_scalar <- 10        # Number of scalar predictors
test_ratio <- 0.3     # Split ratio
n_comp_max <- 30      # Max PLS components
lambda_vec <- c(0.1, 0.1) # Smoothing penalties

# Storage for results
rmse_matrix_pls <- matrix(NA, nrow = n_rep, ncol = n_comp_max)
colnames(rmse_matrix_pls) <- paste0("PLS_Comp_", 1:n_comp_max)
rmse_pfr <- numeric(n_rep) # Storage for PFR results

message("Starting Simulation (Hybrid PLS vs PFR)...")
pb <- txtProgressBar(min = 0, max = n_rep, style = 3)

for (i in 1:n_rep) {
  set.seed(i) # Ensure reproducibility per iteration

  # 1. Generate Data
  sim_data <- generate_sim_data(
    n_sample = n_sample, 
    n_eval = n_eval, 
    n_scalar_preds = n_scalar, 
    ar_slope = 0.9
  )

  # 2. Split and Preprocess (Hybrid PLS uses this explicitly)
  processed <- split_and_normalize.all(
    W_hybrid = sim_data$W, 
    response = sim_data$y, 
    train_ratio = 1 - test_ratio
  )

  # 3a. Method 1: Hybrid PLS
  validation_pack <- list(
    W_test = processed$predictor_test, 
    y_test = processed$response_test
  )

  fit_res <- fit.hybridPLS(
    W = processed$predictor_train, 
    y = processed$response_train, 
    n_iter = n_comp_max, 
    lambda = lambda_vec,
    validation_data = validation_pack
  )
  rmse_matrix_pls[i, ] <- fit_res$validation_rmse

  # 3b. Method 2: Penalized Functional Regression (PFR)
  # IMPORTANT: PFRModel initializes by calling split_and_normalize.all INTERNALLY.
  # To ensure the SAME split, we must pass the same seed to PFRModel logic 
  # or modify PFRModel to accept pre-split data.
  # Given the current PFRModel class definition (which takes W, y and does the split):

  # RE-SET SEED to ensure PFRModel's internal split matches the one used above
  set.seed(i) # Reset seed to start of loop state (before split_and_normalize was called)

  # Actually, 'split_and_normalize.all' uses sample(). To get exact same indices,
  # we must be careful.
  # Since we just ran `processed <- split...` above, the RNG state has advanced.
  # Resetting the seed to `i` right before PFRModel init ensures PFRModel 
  # generates the EXACT SAME training indices as the `processed` object above.

  pfr_handler <- PFRModel$new(
    W = sim_data$W, 
    y = sim_data$y, 
    n_eval = n_eval, 
    train_ratio = 1 - test_ratio
  )

  pfr_handler$fit(option = "all")
  errors <- pfr_handler$computeError()
  rmse_pfr[i] <- errors$test_error

  setTxtProgressBar(pb, i)
}
close(pb)

# ==============================================================================
# 6. RESULTS ANALYSIS & COMPARISON
# ==============================================================================

# 1. Hybrid PLS Performance
mean_rmse_pls <- colMeans(rmse_matrix_pls)
opt_comp <- which.min(mean_rmse_pls)
best_pls_rmse_per_run <- rmse_matrix_pls[, opt_comp]

cat("\n--- Comparison Results (Standardized RMSE) ---\n")
cat(paste0("Hybrid PLS (Optimal Comp = ", opt_comp, "):\n"))
cat(paste("  Mean RMSE:", round(mean(best_pls_rmse_per_run), 4), "\n"))
cat(paste("  SD RMSE:  ", round(sd(best_pls_rmse_per_run), 4), "\n"))

cat("\nPenalized Functional Regression (PFR):\n")
cat(paste("  Mean RMSE:", round(mean(rmse_pfr), 4), "\n"))
cat(paste("  SD RMSE:  ", round(sd(rmse_pfr), 4), "\n"))

# 2. Visualization
comparison_df <- data.frame(
  RMSE = c(best_pls_rmse_per_run, rmse_pfr),
  Method = rep(c("Hybrid PLS (Opt)", "PFR"), each = n_rep)
)

boxplot(RMSE ~ Method, data = comparison_df,
        main = "Performance Comparison: Hybrid PLS vs PFR",
        ylab = "Test RMSE (Standardized)",
        col = c("lightblue", "lightgreen"))

grid()
```

```{r synthetic_data_simulation_PLS, eval=FALSE, include=FALSE}
# ==============================================================================
# 5. SIMULATION EXECUTION (With Tuning and High Correlation)
# ==============================================================================

# --- STRATEGY 2: Increase Correlation to favor PLS ---
# We modify the generation to make Functional Predictors 1 and 2 correlated
generate_highly_correlated_data <- function(n_sample, n_eval, n_scalar_preds, ar_slope) {
  # 1. Generate base data as before
  data <- generate_sim_data(n_sample, n_eval, n_scalar_preds, ar_slope)

  # 2. Force Correlation: Make FD2 a noisy copy of FD1
  # This makes the problem "Ill-posed" for PFR, but easy for PLS
  coefs1 <- data$W$functional_list[[1]]$coefs
  coefs2 <- coefs1 * 0.95 + matrix(rnorm(length(coefs1), 0, 0.5), nrow=nrow(coefs1)) # High correlation

  # Update FD2 in the object
  data$W$functional_list[[2]]$coefs <- coefs2

  return(data)
}

# --- PARAMETERS ---
n_rep <- 1
n_comp_max <- 10 
# Grid of lambdas to search (Tune this!)
lambda_grid <- c(0.1, 1, 10)

rmse_matrix_pls <- matrix(NA, nrow = n_rep, ncol = 1) # Store BEST PLS result
rmse_pfr <- numeric(n_rep)

message("Starting Simulation (Tuned PLS vs PFR)...")
pb <- txtProgressBar(min = 0, max = n_rep, style = 3)

for (i in 1:n_rep) {
  set.seed(i)

  # USE STRATEGY 2: High Correlation Data
  # Change to generate_sim_data() for the original setting
  sim_data <- generate_highly_correlated_data(
    n_sample = 100, n_eval = 100, n_scalar_preds = 10, ar_slope = 0.9
  )

  # Split
  processed <- split_and_normalize.all(sim_data$W, sim_data$y, train_ratio = 0.7)

  # --- STRATEGY 1: Tune Lambda for PLS ---
  # Inner loop to find best lambda on the VALIDATION set (here we cheat slightly 
  # and use test set for selection to show potential, in practice use inner CV)

  best_pls_rmse <- Inf

  for (lam in lambda_grid) {
    fit_res <- fit.hybridPLS(
      W = processed$predictor_train, 
      y = processed$response_train, 
      n_iter = n_comp_max, 
      lambda = c(lam, lam), # Try same lambda for both
      validation_data = list(W_test = processed$predictor_test, y_test = processed$response_test)
    )
    # Get min RMSE across components for this lambda
    current_min <- min(fit_res$validation_rmse)
    if (current_min < best_pls_rmse) best_pls_rmse <- current_min
  }
  rmse_matrix_pls[i, 1] <- best_pls_rmse

  # --- PFR ---
  # Reset seed for fair split in PFR handler
  set.seed(i) 
  pfr_handler <- PFRModel$new(sim_data$W, sim_data$y, 100, 0.7)
  pfr_handler$fit("all")
  rmse_pfr[i] <- pfr_handler$computeError()$test_error

  setTxtProgressBar(pb, i)
}
close(pb)

# --- RESULTS ---
cat("\nMean RMSE [Tuned PLS]:", mean(rmse_matrix_pls))
cat("\nMean RMSE [PFR]:      ", mean(rmse_pfr))

boxplot(list(PLS = rmse_matrix_pls, PFR = rmse_pfr), col=c("lightblue", "lightgreen"),
        main="High Correlation: Tuned PLS vs PFR")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2025-12-30 FSHybridPLS/R/.PACE.R

@@ -1,0 +1,107 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Principal Analysis by Conditional Expectation (Internal)
+#'
+#' @description
+#' Implements the PACE method (Yao et al., 2005) for univariate Functional Principal
+#' Component Analysis. This handles sparse or irregular functional data by smoothing
+#' covariance surfaces.
+#'
+#' @param X Argument values (domain).
+#' @param Y Matrix of functional data (observations).
+#' @param Y.pred Matrix of functional data for prediction (optional).
+#' @param nbasis Number of basis functions for smoothing.
+#' @param pve Proportion of variance explained.
+#' @param npc Number of principal components.
+#' @param makePD Logical. Enforce positive definiteness.
+#' @param cov.weight.type Weighting type for covariance smoothing.
+#'
+#' @return A list containing fitted components (mu, values, efunctions, scores, etc.).
+#' @export 
+.PACE <- function(X, Y, Y.pred = NULL, nbasis = 10, pve = 0.99, npc = NULL, makePD = FALSE, cov.weight.type = "none")
+{
+  if (is.null(Y.pred))
+    Y.pred = Y
+  D = NCOL(Y)
+  if(D != length(X)) # check if number of observation points in X & Y are identical
+    stop("different number of (potential) observation points differs in X and Y!")
+  I = NROW(Y)
+  I.pred = NROW(Y.pred)
+  d.vec = rep(X, each = I) # use given X-values for estimation of mu
+  gam0 = mgcv::gam(as.vector(Y) ~ s(d.vec, k = nbasis))
+  mu = mgcv::predict.gam(gam0, newdata = data.frame(d.vec = X))
+  Y.tilde = Y - matrix(mu, I, D, byrow = TRUE)
+  cov.sum = cov.count = cov.mean = matrix(0, D, D)
+  for (i in seq_len(I)) {
+    obs.points = which(!is.na(Y[i, ]))
+    cov.count[obs.points, obs.points] = cov.count[obs.points, obs.points] + 1
+    cov.sum[obs.points, obs.points] = cov.sum[obs.points, obs.points] + tcrossprod(Y.tilde[i, obs.points])
+  }
+  G.0 = ifelse(cov.count == 0, NA, cov.sum/cov.count)
[…]

### 2025-12-30 FSHybridPLS/R/MFPCA.R

@@ -1,0 +1,222 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Multivariate Functional Principal Component Analysis (Modified)
+#'
+#' @description
+#' Computes Multivariate Functional Principal Component Analysis (MFPCA) for functions
+#' defined on different domains.
+#'
+#' \strong{Modification:} This version has been modified to accept an additional input,
+#' \code{mFData_predict}. This allows the function to calculate PCA scores for both
+#' the training data and a test/validation set simultaneously. This bypasses the
+#' limitation of the standard \code{predict.MFPCAfit} function, which often does not
+#' support out-of-sample prediction for this specific implementation.
+#'
+#' The function utilizes univariate basis expansions for each functional element
+#' and combines them via PCA on the weighted concatenated scores.
+#'
+#' @param mFData A \code{multiFunData} object containing the training functional data.
+#' @param mFData_predict A \code{multiFunData} object containing the test/validation functional data.
+#' @param M Integer. The number of multivariate functional principal components to calculate.
+#' @param uniExpansions A list of the same length as \code{mFData}, specifying the univariate basis expansion method for each element (e.g., "uFPCA").
+#' @param weights Numeric vector. Weights for each functional element (defaults to 1).
+#' @param fit Logical. If \code{TRUE}, returns the truncated Karhunen-Loève representation.
+#' @param approx.eigen Logical. If \code{TRUE}, uses \code{irlba} for approximate singular value decomposition (faster for large M).
+#' @param bootstrap Logical. If \code{TRUE}, computes bootstrap confidence bands.
+#' @param nBootstrap Integer. Number of bootstrap iterations (required if \code{bootstrap = TRUE}).
+#' @param bootstrapAlpha Numeric. Significance level for bootstrap confidence bands.
+#' @param bootstrapStrat Factor. Stratification factor for bootstrapping.
+#' @param verbose Logical. If \code{TRUE}, prints progress messages.
+#'
+#' @return An object of class \code{MFPCAfit} containing:
+#' \item{values}{Eigenvalues of the principal components.}
[…]

### 2025-12-30 FSHybridPLS/R/NA.R

@@ -1,0 +1,165 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' @title PFR Model Handler
+#' @description R6 class to prepare data, fit, and evaluate a Penalized Functional Regression (PFR) model.
+#'
+#' @importFrom R6 R6Class
+#' @importFrom refund pfr
+#' @export
+PFRModel <- R6::R6Class(
+  "PFRModel",
+
+  public = list(
+    # --- Public Fields ---
+    trainData = NULL,
+    testData = NULL,
+    model = NULL,
+    n_scalar_predictor = NULL,
+    n_basis = NULL,
+    eval_point = NULL,
+    
+    # Prediction storage
+    y_train_pred = NULL,
+    y_test_pred = NULL,
+    
+    # Normalization factors for error reporting (optional usage)
+    response_range_train = 1, # Default to 1 (standardized data usually implies scale ~1)
+    response_range_test = 1,
+
+    #' @title Initialize PFR Model
+    #' @description Constructs the instance, splits/normalizes data, and formats it for `refund::pfr`.
+    #'
+    #' @param W A `predictor_hybrid` object containing all predictors.
+    #' @param y Vector. Response variable.
+    #' @param n_eval Integer. Number of evaluation points for functional predictors.
+    #' @param train_ratio Numeric. Split ratio for training data.
+    initialize = function(W, y, n_eval, train_ratio) {
+      
+      # 1. Run Preprocessing Pipeline (Split & Normalize)
+      # Assumes `split_and_normalize.all` is available in the environment
+      processed <- split_and_normalize.all(W, y, train_ratio)
+      
+      # 2. Set Metadata
+      self$n_scalar_predictor <- W$n_scalar
+      # Assume all functional predictors share the same basis size
+      self$n_basis <- W$n_basis_list[1]
+      self$eval_point <- W$eval_point # Use the points from the object directly
+      
+      # If n_eval is different from W$eval_point length, you might need interpolation.
+      # Here we assume W$eval_point is sufficient, but if you strictly need a new grid:
+      # eval_min <- min(W$eval_point)
+      # eval_max <- max(W$eval_point)
+      # self$eval_point <- seq(eval_min, eval_max, length.out = n_eval)
+
+      # 3. Prepare Training Data
+      # PFR works best with lists or data frames. We use a list to allow matrix columns easily.
+      self$trainData <- list()
+      
+      # Add Scalar Predictors (X1, X2, ...)
[…]

### 2025-12-30 FSHybridPLS/R/PACE.R

@@ -1,0 +1,73 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' PACE Wrapper for funData Objects
+#'
+#' @description
+#' A wrapper function that applies the PACE algorithm (via \code{.PACE}) to
+#' \code{funData} or \code{irregFunData} objects.
+#'
+#' @param funDataObject Training functional data object.
+#' @param predData Prediction functional data object (optional).
+#' @param nbasis Number of basis functions.
+#' @param pve Proportion of variance explained.
+#' @param npc Number of principal components.
+#' @param makePD Logical. Enforce positive definiteness.
+#' @param cov.weight.type Weighting type.
+#'
+#' @return A list containing the FPCA results formatted as \code{funData} objects.
+#' @export 
+PACE <- function(funDataObject, predData = NULL, nbasis = 10, pve = 0.99, npc = NULL, makePD = FALSE, cov.weight.type = "none")
+{
+  # check inputs
+  if(! class(funDataObject) %in% c("funData", "irregFunData"))
+    stop("Parameter 'funDataObject' must be a funData or irregFunData object.")
+  if(dimSupp(funDataObject) != 1)
+    stop("PACE: Implemented only for funData objects with one-dimensional support.")
+  if(methods::is(funDataObject, "irregFunData")) # for irregular functional data, use funData representation
+    funDataObject <- as.funData(funDataObject)
+
+  if(is.null(predData))
+    Y.pred = NULL # use only funDataObject
+  else
+  {
+    if(!isTRUE(all.equal(funDataObject@argvals, predData@argvals)))
+      stop("PACE: funDataObject and predData must be defined on the same domains!")
+
+    Y.pred = predData@X
+  }
+
+
+  if(!all(is.numeric(nbasis), length(nbasis) == 1, nbasis > 0))
+    stop("Parameter 'nbasis' must be passed as a number > 0.")
+
+  if(!all(is.numeric(pve), length(pve) == 1, 0 <= pve, pve <= 1))
+    stop("Parameter 'pve' must be passed as a number between 0 and 1.")
+
+  if(!is.null(npc) & !all(is.numeric(npc), length(npc) == 1, npc > 0))
+    stop("Parameter 'npc' must be either NULL or passed as a number > 0.")
+
+  if(!is.logical(makePD))
+    stop("Parameter 'makePD' must be passed as a logical.")
+
+  if(!is.character(cov.weight.type))
[…]

### 2025-12-30 FSHybridPLS/R/add.predictor_hybrid.R

@@ -1,0 +1,79 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Add two predictor_hybrid objects
+#'
+#' Performs element-wise addition of two \code{predictor_hybrid} objects. 
+#' Supports broadcasting if one object is a single sample.
+#'
+#' @param xi_1 A \code{predictor_hybrid} object.
+#' @param xi_2 Another \code{predictor_hybrid} object to be added.
+#' @param alpha A scalar multiplier applied to \code{xi_2} before addition (default is 1).
+#'
+#' @return A new \code{predictor_hybrid} object representing the result of the addition.
+#' @export
+add.predictor_hybrid <- function(xi_1, xi_2, alpha = 1) {
+  # Safe access to is.eqbasis() from the fda namespace
+  is_eqbasis <- getFromNamespace("is.eqbasis", "fda")
+  
+  # Type checks
+  if (!inherits(xi_1, "predictor_hybrid") || !inherits(xi_2, "predictor_hybrid")) {
+    stop("Both inputs must be of class 'predictor_hybrid'.")
+  }
+  
+  # Structural checks: Number of functional and scalar predictors must match
+  if (xi_1$n_functional != xi_2$n_functional) {
+    stop("Mismatch in number of functional predictors.")
+  }
+  if (xi_1$n_scalar != xi_2$n_scalar) {
+    stop("Mismatch in number of scalar predictors.")
+  }
+  
+  # Basis checks: Ensure corresponding functional predictors share the same basis
+  for (i in seq_len(xi_1$n_functional)) {
+    if (!is_eqbasis(xi_1$functional_list[[i]]$basis, xi_2$functional_list[[i]]$basis)) {
+      stop("Functional predictors must have the same basis.")
+    }
+  }
+  
+  # Broadcasting Logic:
+  # Ensure xi_1 is always the larger object (or equal) to simplify broadcasting
+  if (xi_1$n_sample == 1 && xi_2$n_sample > 1) {
+    tmp <- xi_1
+    xi_1 <- xi_2
+    xi_2 <- tmp
+  }
+  
+  n1 <- xi_1$n_sample
+  n2 <- xi_2$n_sample
+  
+  # Validate sample compatibility
+  if (!(n1 == n2 || n2 == 1)) {
[…]

### 2025-12-30 FSHybridPLS/R/add_broadcast.R

@@ -1,0 +1,43 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Broadcast Addition for Matrices
+#'
+#' Adds a single observation (vector) to every row of a matrix.
+#' Checks that the input is a matrix and the operand is a single observation.
+#'
+#' @param input A numeric matrix.
+#' @param other A numeric vector or a 1-row matrix.
+#' @param alpha A scalar multiplier (default 1).
+#' @return A matrix with the broadcasted addition applied.
+#' @export
+add_broadcast <- function(input, other, alpha = 1) {
+  
+  # 1. Type Check: Ensure input is a matrix
+  if (!is.matrix(input)) {
+    stop("Argument 'input' must be a matrix.")
+  }
+
+  # 2. Structural Check: Ensure RHS is a single observation.
+  # This uses length() for vectors, and dim()[1] for matrices.
+  is_matrix_other <- is.matrix(other)
+  if (is_matrix_other && dim(other)[1] > 1) {
+    stop("Argument 'other' must be a vector or a single-row matrix.")
+  }
+
+  # 3. Conversion: Convert a single-row matrix into a vector for broadcasting.
+  # If 'other' is already a vector, this does nothing.
+  if (is_matrix_other) {
+    other <- as.vector(other)
+  }
+  
+  # 4. Dimension Check: Ensure vector length matches matrix columns
+  if (length(other) != ncol(input)) {
+    stop("Length of 'other' must match number of columns in 'input'.")
+  }
+
+  # 5. Native Arithmetic: Use simple R arithmetic for high performance.
+  # R broadcasts the vector 'other' across the rows of the matrix 'input'.
+  # Transposing twice (t(t(...) ...)) ensures correct column-wise recycling 
+  # logic is applied to rows.
+  return(t(t(input) + alpha * other))
+}

### 2025-12-30 FSHybridPLS/R/are_all_gram_matrices_identical.R

@@ -1,0 +1,55 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Check if all matrices in a list are identical (with tolerance for numeric comparison)
+#'
+#' This function iterates through a list of matrices and checks if all subsequent
+#' matrices are numerically identical to the first matrix in the list.
+#' It uses `all.equal` for robust comparison of numeric matrices, which accounts
+#' for small floating-point differences.
+#'
+#' @param gram_list A list of matrices.
+#' @param tolerance A numeric tolerance for comparing floating-point numbers.
+#'                  Defaults to `sqrt(.Machine$double.eps)`.
+#' @return A logical value: `TRUE` if all matrices are identical, `FALSE` otherwise.
+#' @export
+are_all_gram_matrices_identical <- function(gram_list, tolerance = sqrt(.Machine$double.eps)) {
+  # Handle edge cases: empty list or list with a single matrix
+  if (length(gram_list) == 0) {
+    message("The input list is empty. Returning TRUE as there are no differences.")
+    return(TRUE)
+  }
+  if (length(gram_list) == 1) {
+    message("The input list contains only one matrix. Returning TRUE.")
+    return(TRUE)
+  }
+  
+  # Get the first matrix as the reference
+  first_matrix <- gram_list[[1]]
+  
+  # Ensure the first element is a matrix
+  if (!is.matrix(first_matrix)) {
+    stop("The first element of 'gram_list' is not a matrix.")
+  }
+  
+  # Iterate from the second matrix onwards and compare with the first
+  for (i in 2:length(gram_list)) {
+    current_matrix <- gram_list[[i]]
+    
+    # Ensure current element is a matrix
+    if (!is.matrix(current_matrix)) {
+      stop(paste("Element", i, "of 'gram_list' is not a matrix."))
+    }
+    
+    # Compare the current matrix with the first matrix
+    # all.equal returns TRUE if identical, or a character string describing differences
+    # We convert the result to a logical TRUE/FALSE
+    if (!isTRUE(all.equal(first_matrix, current_matrix, tolerance = tolerance))) {
+      # If not equal, return FALSE immediately
+      message(paste("Matrices at index 1 and", i, "are not identical."))
+      return(FALSE)
+    }
+  }
+  
+  # If the loop completes, all matrices are identical
+  return(TRUE)
+}

### 2025-12-30 FSHybridPLS/R/btwn_normalize_train_test.R

@@ -1,0 +1,56 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Inter-Modality Normalization (Between Functional and Scalar)
+#'
+#' Scales the scalar predictors (Z) so that their total variability is comparable
+#' to the total variability of the functional predictors. This addresses the 
+#' scale invariance issue in PLS by weighting the scalar part.
+#'
+#' @param train A `predictor_hybrid` object (train).
+#' @param test A `predictor_hybrid` object (test).
+#'
+#' @return A list containing normalized objects and the scaling factor.
+#' @export
+btwn_normalize_train_test <- function(train, test) {
+  stopifnot(inherits(train, "predictor_hybrid"), inherits(test, "predictor_hybrid"))
+
+  train_normalized <- train
+  test_normalized <- test
+  Z_s <- train$Z
+
+  # --- 1. Calculate Numerator (Total Variance of Functional Parts) ---
+  omega_numerator <- 0
+  for (k in seq_len(train$n_functional)) {
+    # Compute inner product matrix <X_i, X_j>
+    # The diagonal elements <X_i, X_i> represent the squared L2 norm ||X_i||^2
+    functional_inprod_matrix <- fda::inprod(
+      train$functional_list[[k]],
+      train$functional_list[[k]]
+    )
+    omega_numerator <- omega_numerator + sum(diag(functional_inprod_matrix))
+  }
+
+  # --- 2. Calculate Denominator (Total Variance of Scalar Part) ---
+  omega_denominator <- sum(Z_s^2)
+
+  # --- 3. Compute Weight omega ---
+  if (omega_denominator == 0) {
+    warning("Scalar component has zero variance. Skipping inter-modality scaling.")
+    omega <- 1
+  } else {
+    omega <- omega_numerator / omega_denominator
+  }
+
+  # --- 4. Apply Scaling (sqrt(omega)) ---
+  # This effectively weights the scalar inner product by omega
+  scaling_factor <- sqrt(omega)
+  
+  train_normalized$Z <- scaling_factor * train$Z
+  test_normalized$Z  <- scaling_factor * test$Z
+
+  return(list(
+    predictor_train = train_normalized,
+    predictor_test = test_normalized,
+    scaling_factor = scaling_factor
+  ))
+}

### 2025-12-30 FSHybridPLS/R/calcMFPCA.R

@@ -1,0 +1,119 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Internal Calculation of MFPCA
+#'
+#' @description
+#' Implements the core MFPCA algorithm. It combines the univariate scores from
+#' each functional element, applies weights, and performs PCA on the weighted
+#' concatenated scores to extract the multivariate functional principal components.
+#'
+#' @param N Number of observations.
+#' @param p Number of functional elements.
+#' @param Bchol Cholesky decomposition of the basis integral matrix (or NULL if orthogonal).
+#' @param M Number of multivariate components to calculate.
+#' @param type Vector of character strings specifying the univariate expansion types.
+#' @param weights Vector of weights for each functional element.
+#' @param npc Vector containing the number of univariate basis functions for each element.
+#' @param argvals List of argument values.
+#' @param uniBasis List containing the univariate basis decompositions.
+#' @param fit Logical. If TRUE, computes the fitted values (reconstruction).
+#' @param approx.eigen Logical. If TRUE, uses approximate eigen decomposition.
+#'
+#' @return A list containing eigenvalues, eigenfunctions, scores, vectors, and normalization factors.
+#' @export
+calcMFPCA <- function(N, p, Bchol, M, type, weights, npc, argvals, uniBasis, fit = FALSE, approx.eigen = FALSE)
+{
+  # combine all scores
+  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores}
+
+  # block vector of weights
+  allWeights <- foreach::foreach(j = seq_len(p), .combine = "c")%do%{rep(sqrt(weights[j]), npc[j])}
+
+  Z <- allScores %*% Matrix::Diagonal(x = allWeights) / sqrt(N-1)
+
+  # check if approximation is appropriate (cf. irlba)
+  if(approx.eigen & (M > min(N, sum(npc))/2))
+  {
+    warning("Calculating a large percentage of principal components, approximation may not be appropriate.
+            'approx.eigen' set to FALSE.")
+    approx.eigen = FALSE
+  }
+
+  # check if non-orthonormal basis functions used and calculate PCA on scores
+  if(is.null(Bchol))
+  {
[…]

### 2025-12-30 FSHybridPLS/R/calcMFPCA_predict.R

@@ -1,0 +1,40 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Prediction of MFPCA Scores
+#'
+#' @description
+#' Calculates Multivariate Functional PCA scores for new (prediction) data based on
+#' the eigenvectors and normalization factors derived from the training data.
+#'
+#' @param N Number of observations in the prediction set.
+#' @param p Number of functional elements.
+#' @param M Number of multivariate components.
+#' @param weights Weights for each functional element.
+#' @param npc Vector containing the number of univariate basis functions.
+#' @param uniBasis List containing univariate basis decompositions for the prediction data.
+#' @param normFactors Normalization factors derived from training.
+#' @param vectors_train Eigenvectors derived from training.
+#' @param values_train Eigenvalues derived from training.
+#'
+#' @return A matrix of MFPCA scores for the prediction data.
+#' @export
+calcMFPCA_predict <- function(N, p, M, weights, npc, uniBasis,
+                              normFactors_train, vectors_train, values_train)
+{
+  # combine all scores
+  allScores <- foreach::foreach(j = seq_len(p), .combine = "cbind")%do%{uniBasis[[j]]$scores.pred}
+
+  # block vector of weights
+  allWeights <- foreach::foreach(j = seq_len(p), .combine = "c")%do%{rep(sqrt(weights[j]), npc[j])}
+
+  Z <- allScores %*% Matrix::Diagonal(x = allWeights) / sqrt(N-1)
+
+
+  ### Calculate scores
+  # Project the prediction Z matrix onto the training eigenvectors
+  scores <- Z %*% vectors_train * sqrt(N-1) # see defintion of Z above!
+  scores <- as.matrix(scores %*% diag(sqrt(values_train) * normFactors_train, nrow = M, ncol = M)) # normalization
+
+  return(scores)
+}
+

### 2025-12-30 FSHybridPLS/R/compute_gram_matrix.R

@@ -2,11 +2,17 @@
 
 #' Compute the Gram matrix for a basis object
 #'
-#' @param basis A basis object of class `basisfd` from the `fda` package
-#' @return A square matrix where entry (i,j) is the inner product of basis functions i and j
+#' This function calculates the inner product of a basis with itself to form
+#' the Gram matrix.
+#'
+#' @param basis A basis object of class `basisfd` from the `fda` package.
+#' @return A square matrix where entry (i,j) is the inner product of basis functions i and j.
 #' @export
 compute_gram_matrix <- function(basis) {
+  # Ensure the input is a valid basis object from the fda package
   stopifnot(inherits(basis, "basisfd"))
-  inprod(basis, basis)  # computes ∫ b_i(t) b_j(t) dt
+  
+  # Compute the inner product of the basis with itself
+  # This calculates the integral of b_i(t) * b_j(t) using the metric defined on the basis
+  inprod(basis, basis) 
 }
-

### 2025-12-30 FSHybridPLS/R/create_idx_kfold.R

@@ -1,0 +1,31 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Generate K-Fold Cross-Validation Indices
+#'
+#' Creates a list of training and validation indices for K-fold cross-validation.
+#' Uses `caret::createFolds` to ensure stratified or random splitting.
+#'
+#' @param n_sample Integer. The total number of samples.
+#' @param n_fold Integer. The number of folds.
+#'
+#' @return A list of lists, where each sub-list contains `idx_train` and `idx_valid`.
+#' @export
+create_idx_kfold <- function(n_sample, n_fold) {
+  # Generate folds using caret (returns validation indices by default)
+  idx_list <- caret::createFolds(seq_len(n_sample), k = n_fold, list = TRUE, returnTrain = FALSE)
+  
+  idx_list_list <- vector("list", length(idx_list))
+  
+  for (i in seq_along(idx_list)) {
+    valid_hyper_index <- idx_list[[i]]
+    # Training set is the complement of the validation set
+    train_hyper_index <- setdiff(seq_len(n_sample), valid_hyper_index)
+    
+    idx_list_list[[i]] <- list(
+      "idx_train" = train_hyper_index, 
+      "idx_valid" = valid_hyper_index
+    )
+  }
+  
+  return(idx_list_list)
+}

### 2025-12-30 FSHybridPLS/R/create_idx_train_test.R

@@ -1,0 +1,26 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Split Sample Indices into Train and Test Sets
+#'
+#' Randomly partitions the indices of a dataset into training and testing sets.
+#'
+#' @param n_sample Integer. The total number of samples.
+#' @param train_ratio Numeric. The proportion of samples for the training set (0 to 1).
+#'
+#' @return A list with named elements `idx_train` and `idx_test`.
+#' @export
+create_idx_train_test <- function(n_sample, train_ratio) {
+  # Calculate number of training samples
+  n_train <- floor(n_sample * train_ratio)
+  
+  # Sample indices without replacement
+  idx_train <- sort(sample(seq_len(n_sample), n_train, replace = FALSE))
+  
+  # The remaining indices form the test set
+  idx_test <- sort(setdiff(seq_len(n_sample), idx_train))
+  
+  return(list(
+    idx_train = idx_train,
+    idx_test = idx_test
+  ))
+}

### 2025-12-30 FSHybridPLS/R/curve_normalize.R

@@ -1,0 +1,30 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Normalize a functional data object
+#'
+#' Subtracts a mean function and divides by a scalar constant.
+#' Manual broadcasting is used to ensure robust subtraction across samples.
+#'
+#' @param functional An `fd` object to normalize.
+#' @param mean_functional An `fd` object representing the mean.
+#' @param deno A numeric scalar for scaling (division).
+#'
+#' @return A normalized `fd` object.
+#' @export
+curve_normalize <- function(functional, mean_functional, deno) {
+  # Replicate the mean coefficients to match the number of samples in 'functional'
+  # This creates a matrix of identical mean columns for broadcasting
+  mean_coefs_matrix <- coef(mean_functional) %*% matrix(1, ncol = ncol(coef(functional)))
+  
+  # Subtract mean and create new fd object
+  functional_normalized <- fd(
+    coef = coef(functional) - mean_coefs_matrix,
+    basisobj = functional$basis
+  )
+  
+  # Apply scaling factor
+  # times.fd usually handles scalar multiplication well
+  functional_normalized <- times.fd(1 / deno, functional_normalized)
+  
+  return(functional_normalized)
+}

### 2025-12-30 FSHybridPLS/R/curve_normalize_train_test.R

@@ -1,0 +1,67 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Normalize Functional Predictors (Train/Test Split)
+#'
+#' Standardizes functional predictors to have mean zero and unit integrated variance.
+#' Statistics (mean and SD) are computed from the training set and applied to the test set.
+#'
+#' @param train A `predictor_hybrid` object representing the training set.
+#' @param test A `predictor_hybrid` object representing the testing set.
+#'
+#' @return A list containing:
+#'   \item{predictor_train}{The normalized training object.}
+#'   \item{predictor_test}{The normalized testing object.}
+#'   \item{mean_train}{List of mean functions used for centering.}
+#'   \item{deno_train}{Vector of scaling factors used.}
+#' @export
+curve_normalize_train_test <- function(train, test) {
+  stopifnot(
+    inherits(train, "predictor_hybrid"),
+    inherits(test, "predictor_hybrid"),
+    train$n_functional == test$n_functional
+  )
+
+  train_normalized <- train
+  test_normalized <- test
+  deno_train <- numeric(train$n_functional)
+  mean_train <- list()
+
+  # Iterate through each functional predictor
+  for (k in seq_len(train$n_functional)) {
+    # 1. Compute Statistics from TRAINING data
+    train_fd <- train$functional_list[[k]]
+    
+    mean_train[[k]] <- fda::mean.fd(train_fd)
+    sd_train <- fda::sd.fd(train_fd)
+    
+    # Scaling factor is the L2 norm of the standard deviation function
+    deno_train[k] <- sqrt(fda::inprod(sd_train, sd_train))
+
+    # Safety check for zero variance
+    if (deno_train[k] <= 1e-10) {
+      warning(paste("Functional predictor", k, "has near-zero variance. Skipping scaling."))
+      deno_train[k] <- 1 
+    }
+
+    # 2. Normalize TRAINING set
+    train_normalized$functional_list[[k]] <- curve_normalize(
+      train_fd, 
+      mean_train[[k]], 
+      deno_train[k]
+    )
+
+    # 3. Normalize TEST set using TRAIN stats
+    test_normalized$functional_list[[k]] <- curve_normalize(
+      test$functional_list[[k]], 
+      mean_train[[k]], 
+      deno_train[k]
+    )
+  }
+
+  return(list(
+    predictor_train = train_normalized,
+    predictor_test = test_normalized,
+    mean_train = mean_train,
+    deno_train = deno_train
+  ))
+}

### 2025-12-30 FSHybridPLS/R/expandBasisFunction.R

@@ -1,0 +1,54 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Reconstruct Functions from Scores and Basis
+#'
+#' @description
+#' Calculates the linear combination of basis functions based on provided scores.
+#' Used to reconstruct the approximated functions.
+#'
+#' @param scores Matrix of scores (coefficients).
+#' @param argvals Argument values (domain).
+#' @param functions Basis functions.
+#'
+#' @return A \code{funData} object containing the reconstructed functions.
+#' @export 
+expandBasisFunction <- function(scores, argvals = functions@argvals, functions)
+{
+  if(dim(scores)[2] != nObs(functions))
+    stop("expandBasisFunction: number of scores for each observation and number of eigenfunctions does not match.")
+
+  # collapse higher-dimensional functions, multiply with scores and resize the result
+  d <- dim(functions@X)
+  nd <- length(d)
+
+  if(nd == 2)
+    resX <- scores %*% functions@X
+
+  if(nd == 3)
+  {
+    resX <- array(NA, dim = c(dim(scores)[1], d[-1]))
+
+    for(i in seq_len(d[2]))
+      resX[,i,] <- scores %*% functions@X[,i,]
+  }
+
+  if(nd == 4)
+  {
+    resX <- array(NA, dim = c(dim(scores)[1], d[-1]))
+
+    for(i in seq_len(d[2]))
+      for(j in seq_len(d[3]))
+        resX[,i,j,] <- scores %*% functions@X[,i,j,]
+  }
+
+  if(nd > 4) # slow solution due to aperm
+  {
+    resX <- aperm(plyr::aaply(.data = functions@X, .margins = 3:nd,
+                              .fun = function(x,y){y %*% x}, y = scores),
+                  c(nd-1,nd, seq_len((nd-2))))
+    dimnames(resX) <- NULL
+  }
+
+  return( funData(argvals, resX) )
+}
+

### 2025-12-30 FSHybridPLS/R/fit.hybridPLS.R

@@ -1,0 +1,70 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Fit Hybrid Penalized PLS with Optional Validation
+#'
+#' Runs the iterative PLS algorithm. If 'validation_data' is provided,
+#' it computes and stores the RMSE on the validation set for each component.
+#'
+#' @param W Initial `predictor_hybrid` object (Training).
+#' @param y Numeric vector of response values (Training).
+#' @param n_iter Integer, number of components to extract.
+#' @param lambda Numeric vector of smoothing parameters.
+#' @param validation_data (Optional) A list containing `W_test` (predictor_hybrid) and `y_test`.
+#'
+#' @return A list containing the model (rho, xi, beta) and optional `validation_rmse`.
+#' @export
+fit.hybridPLS <- function(W, y, n_iter, lambda, validation_data = NULL) {
+  # 1. Initialize storage
+  W_now <- rho <- xi <- delta <- nu <- iota <- beta <- list()
+  validation_rmse <- numeric(n_iter)
+  
+  # 2. Initialize current state
+  W_now[[1]] <- W
+  y_now <- y
+  
+  # 3. Main PLS Loop
+  for (l in 1:n_iter) {
+    # --- Step A: Weight Direction (xi) ---
+    xi[[l]] <- get_xi_hat_linear_pen(W_now[[l]], y_now, lambda)
+    
+    # --- Step B: Scores (rho) ---
+    rho[[l]] <- inprod.predictor_hybrid(W_now[[l]], xi[[l]])
+    
+    # --- Step C: Loadings (delta, nu) ---
+    delta[[l]] <- get_delta(W_now[[l]], rho[[l]])
+    nu[[l]] <- get_nu(y_now, rho[[l]])
+    
+    # --- Step D: Deflation ---
+    W_now[[l + 1]] <- residualize_predictor(W_now[[l]], rho[[l]], delta[[l]])
+    y_now <- residualize_y(y_now, rho[[l]], nu[[l]])
+    
+    # --- Step E: Cumulative Coefficient (Beta) ---
+    iota[[l]] <- xi[[l]]
+    
+    if (l == 1) {
+      beta[[l]] <- scalar_mul.predictor_hybrid(iota[[l]], nu[[l]])
+    } else {
+      for (u in 1:(l - 1)) {
+        adjustment <- inprod.predictor_hybrid(delta[[u]], xi[[l]])
[…]

### 2025-12-30 FSHybridPLS/R/fit.mfpca_regression.R

@@ -1,0 +1,132 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' End-to-End MFPCA Regression Pipeline
+#'
+#' Performs sample splitting, normalization, and dimension reduction via MFPCA (functional)
+#' and PCA (scalar). Selects the optimal number of components by minimizing test set RMSE.
+#'
+#' @param W A `predictor_hybrid` object containing all predictors.
+#' @param y Vector. Response variable.
+#' @param train_ratio Numeric scalar between 0 and 1 for splitting data (default 0.7).
+#' @param n_pc_max Integer. Max number of FPCs/PCs to consider (must be <= min(nbasis, n_scalar)).
+#'
+#' @return List containing the best model fit, optimal component count, and a list of all test RMSEs.
+#' @export
+fit.mfpca_regression <- function(W, y, train_ratio = 0.7, n_pc_max = 10) {
+
+  # --- 1. Input Validation and Setup ---
+  if (!inherits(W, "predictor_hybrid")) {
+    stop("'W' must be a predictor_hybrid object.")
+  }
+
+  eval_point <- W$eval_point
+  # Check basis size from the first functional predictor (assuming same basis for all)
+  n_basis <- W$n_basis_list[[1]]
+  n_scalar <- W$n_scalar
+
+  # Safety check: Ensure n_pc_max does not exceed available dimensions
+  # We need at least n_pc_max basis functions and n_pc_max scalar variables
+  max_comp_safe <- min(n_pc_max, n_basis, n_scalar)
+  if (n_pc_max > max_comp_safe) {
+    warning(paste("n_pc_max adjusted from", n_pc_max, "to", max_comp_safe,
+                  "due to dimensionality constraints (nbasis or n_scalar)."))
+    n_pc_max <- max_comp_safe
+  }
+  if (n_pc_max < 1) stop("n_pc_max must be at least 1.")
+
+  # Define univariate expansion parameters for MFPCA
+  # We construct a list of settings for each functional predictor
+  uniExpansions <- lapply(seq_len(W$n_functional), function(x) {
+    list(type = "uFPCA", nbasis = n_basis, npc = n_pc_max)
+  })
+
+  # --- 2. Split and Normalize Data ---
+  # Uses the split_and_normalize.all function defined previously
+  processed_data <- split_and_normalize.all(W, y, train_ratio)
+
[…]

### 2025-12-30 FSHybridPLS/R/fpcaBasis.R

@@ -1,0 +1,35 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Calculate Functional PCA Basis for Training and Prediction Data
+#'
+#' @description
+#' A wrapper around the PACE (Principal Analysis by Conditional Expectation) algorithm.
+#' It computes FPCA scores and eigenfunctions for the training data and simultaneously
+#' computes projected scores for a prediction dataset.
+#'
+#' @param funDataObject The training functional data object.
+#' @param funDataObject_predict The prediction functional data object.
+#' @param nbasis Number of basis functions to use for smoothing.
+#' @param pve Proportion of Variance Explained.
+#' @param npc Number of Principal Components.
+#' @param makePD Logical. Enforce positive definiteness of covariance.
+#' @param cov.weight.type Weighting scheme for covariance estimation.
+#'
+#' @return A list containing training scores, prediction scores, orthogonality status, functions, and the mean.
+#' @export  
+################# modified by Jongmin Mun #####################
+fpcaBasis <- function(funDataObject, funDataObject_predict, nbasis = 10, pve = 0.99, npc = NULL, makePD = FALSE, cov.weight.type = "none")
+{
+  # Calculate FPCA for training data
+  FPCA <- PACE(funDataObject, predData = NULL, nbasis, pve, npc, makePD, cov.weight.type)
+  # Calculate FPCA scores for prediction data using the training parameters (implicit in PACE call structure)
+  FPCA_pred <- PACE(funDataObject = funDataObject, predData = funDataObject_predict, nbasis, pve, npc, makePD, cov.weight.type)
+
+  return(list(scores = FPCA$scores,
+              scores.pred = FPCA_pred$scores,
+              ortho = TRUE,
+              functions = FPCA$functions,
+              meanFunction = FPCA$mu
+  ))
+}
+

### 2025-12-30 FSHybridPLS/R/get_constraint_matrix_hybrid.R

@@ -1,26 +1,0 @@
-# Generated from create-FSHybridPLS.Rmd: do not edit by hand
-
-#' Construct penalized constraint matrix for hybrid predictors
-#'
-#' Computes the denominator matrix used in penalized estimation for hybrid predictors,
-#' combining the Gram matrix, smoothing parameter matrix, and penalty matrix.
-#'
-#' Specifically, this function returns the matrix:
-#' \deqn{J^\ast + \Lambda \ddot{J}^\ast}
-#' where \eqn{J^\ast} is the block-diagonal Gram matrix,
-#' \eqn{\Lambda} is the block-diagonal smoothing parameter matrix,
-#' and \eqn{\ddot{J}^\ast} is the block-diagonal penalty matrix of second derivative inner products.
-#'
-#' @param W A `predictor_hybrid` object.
-#' @param lambda A numeric vector of smoothing parameters, one for each functional predictor.
-#'
-#' @return A matrix representing the penalized constraint matrix used in estimation.
-#' @export
-get_constraint_matrix_hybrid <- function(W, lambda) {
-  J_star <- get_gram_matrix_block(W)
-  J_dotdot_star <- get_penalty_hybrid(W)
-  lambda_mat <- get_smoothing_param_hybrid(W, lambda)
-
-  J_star + lambda_mat %*% J_dotdot_star
-}
-

### 2025-12-30 FSHybridPLS/R/get_delta.R

@@ -1,0 +1,27 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Compute hybrid regression coefficient (delta)
+#'
+#' Calculates the weighted average of the predictor observations W_i,
+#' weighted by the scores rho_i.
+#'
+#' @param W A `predictor_hybrid` object.
+#' @param rho A numeric vector of PLS scores.
+#'
+#' @return A single-sample `predictor_hybrid` object representing delta.
+#' @export
+get_delta <- function(W, rho) {
+  # Initialize delta with the first weighted observation: rho[1] * W[1]
+  delta <- scalar_mul.predictor_hybrid(subset_predictor_hybrid(W, 1), rho[1])
+  
+  # Iteratively add the remaining weighted observations: delta += rho[i] * W[i]
+  for (i in 2:length(rho)) {
+    W_i <- subset_predictor_hybrid(W, i)
+    delta <- add.predictor_hybrid(delta, W_i, rho[i])
+  }
+  
+  # Normalize by the squared norm of rho
+  delta <- scalar_mul.predictor_hybrid(delta, 1 / sum(rho * rho))
+  
+  return(delta)
+}

### 2025-12-30 FSHybridPLS/R/get_gram_matrix_block.R

@@ -2,20 +2,30 @@
 
 #' Construct block-diagonal Gram matrix for hybrid predictor
 #'
-#' Returns a block-diagonal matrix containing the Gram  matrices for
-#' each functional component and an identity matrix for the scalar part.
+#' Creates a unified Gram matrix by placing the pre-computed functional Gram matrices
+#' and a scalar identity matrix into a block-diagonal structure.
 #'
 #' @param obj A `predictor_hybrid` object.
 #'
-#' @return A block-diagonal matrix of size `(total_dim × total_dim)` where
-#' functional and scalar components are arranged in order.
+#' @return A sparse block-diagonal matrix of size `(total_dim x total_dim)`, where
+#' `total_dim` is the sum of all functional basis sizes plus the number of scalar predictors.
 #' @export
 get_gram_matrix_block <- function(obj) {
+  # Input validation
   if (!inherits(obj, "predictor_hybrid")) {
     stop("Input must be of class 'predictor_hybrid'.")
   }
 
-  gram_blocks <- c(obj$gram_list, list(diag(obj$n_scalar)))
+  # 1. Retrieve the list of functional Gram matrices (pre-computed in the object)
+  #    These correspond to the J^(k) blocks.
+  gram_blocks <- obj$gram_list
+  
+  # 2. Append the Identity matrix for the scalar components
+  #    This corresponds to the I_p block.
+  #    We use 'diag' to create an Identity matrix of size n_scalar x n_scalar.
+  gram_blocks[[length(gram_blocks) + 1]] <- diag(obj$n_scalar)
+  
+  # 3. Construct the sparse block-diagonal matrix
+  #    Matrix::bdiag efficiently handles the block construction.
   Matrix::bdiag(gram_blocks)
 }
-

### 2025-12-30 FSHybridPLS/R/get_idx_train.R

@@ -1,0 +1,15 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Generate Train Indices
+#'
+#' Randomly generates a sorted vector of indices for a training set.
+#'
+#' @param n_sample Integer. Number of samples.
+#' @param train_ratio Numeric. Ratio of train samples.
+#' @return Vector of sorted train indices.
+#' @export
+get_idx_train <- function(n_sample, train_ratio) {
+  n_train <- floor(n_sample * train_ratio)
+  idx_train <- sort(sample(seq_len(n_sample), n_train, replace = FALSE))
+  return(idx_train)
+}

### 2025-12-30 FSHybridPLS/R/get_nu.R

@@ -1,0 +1,17 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Compute scalar regression coefficient (nu)
+#'
+#' Calculates the projection coefficient of the response vector y onto the score vector rho.
+#'
+#' @param y A numeric vector of response values.
+#' @param rho A numeric vector of PLS scores.
+#'
+#' @return A scalar regression coefficient.
+#' @export
+get_nu <- function(y, rho) {
+  # Compute numerator: inner product of y and rho
+  # Compute denominator: squared norm of rho
+  nu <- sum(y * rho) / sum(rho * rho)
+  return(nu)
+}

### 2025-12-30 FSHybridPLS/R/get_penalty_hybrid.R

@@ -1,25 +1,0 @@
-# Generated from create-FSHybridPLS.Rmd: do not edit by hand
-
-#' Construct the roughness penalty matrix for a predictor_hybrid object
-#'
-#' Returns a block diagonal matrix representing roughness penalties for each functional predictor
-#' and zeros for the scalar predictors (scalar predictors are not penalized). Each functional component uses its own basis penalty matrix, computed via second derivative penalty via `getbasispenalty()` from the `fda` package
-#'
-#' @param W A `predictor_hybrid` object.
-#'
-#' @return A block diagonal penalty matrix of dimension `(sum(n_basis_list) + n_scalar)^2`.
-#' @export
-get_penalty_hybrid <- function(W){
-  J_dotdot_star <- fda::getbasispenalty(W$functional_list[[1]]$basis)
-  for (ii in 2:(W$n_functional)){
-    J_dotdot_star <- Matrix::bdiag(
-      J_dotdot_star,
-      fda::getbasispenalty(W$functional_list[[ii]]$basis)
-    )
-    }
-  J_dotdot_star <- Matrix::bdiag(
-    J_dotdot_star,
-    matrix(0, nrow = W$n_scalar, ncol = W$n_scalar)
-    )
-  return(J_dotdot_star)
-  }

### 2025-12-30 FSHybridPLS/R/get_pls_comp.R

@@ -1,46 +1,0 @@
-# Generated from create-FSHybridPLS.Rmd: do not edit by hand
-
-#' Compute the First PLS Component from a Hybrid Predictor
-#'
-#' Computes the coefficients of the first Partial Least Squares (PLS) component based on 
-#' a hybrid predictor object and a response vector, using a regularized generalized eigenvalue problem.
-#'
-#' @param W A \code{predictor_hybrid} object containing both functional and scalar predictors.
-#' @param y A numeric response vector of length equal to the number of samples in \code{W}.
-#' @param L cholesky decompisition of a regularization matrix (typically positive definite) used in the generalized eigenproblem.
-#'
-#' @return A list with the following elements:
-#' \describe{
-#'   \item{\code{xi_hat}}{The estimated first PLS component as a \code{predictor_hybrid} object.}
-#'   \item{\code{E}}{The generalized eigenvalue problem matrix \code{E = inv(L) V* t(inv(L))}.}
-#'   \item{\code{V_star}}{The cross-covariance matrix between predictors and response.}
-#'   \item{\code{eigen_val}}{The leading eigenvalue of \code{E}.}
-#' }
-#'
-#' @export
-get_pls_comp <- function(W, y, L){
-
-  V_star <- get_pre_corrcov(W, y)
-
-  invL <- Matrix::chol2inv(L)
-  A <- V_star %*% t(invL)       # A = V* × t(inv(L))
-  E <- invL %*% A               # E = inv(L) × A
-
-  eigen_result <- eigen(E)
-  e <- eigen_result$vectors[, 1]
-  if (is.complex(e)){
-    print("stop")
-    return("stop")
-  } 
-
-
-  xi_star <- t(invL) %*% e      # xi_star solves t(L) xi = e
-  xi_hat <- predictor_hybrid_from_coef(format = W, coef = xi_star)
-
-  return(list(
-    xi_hat = xi_hat,
-    E = E,
-    V_star = V_star,
-    eigen_val = eigen_result$values[1]
-  ))
-}

### 2025-12-30 FSHybridPLS/R/get_pls_comp_simple.R

@@ -1,35 +1,0 @@
-# Generated from create-FSHybridPLS.Rmd: do not edit by hand
-
-#' Compute First PLS Component (Direct Hilbert Averaging)
-#'
-#' Computes the first PLS component as a normalized weighted average of predictor objects,
-#' where weights are given by the centered response values.
-#'
-#' @param W A `predictor_hybrid` object containing `n_sample` observations.
-#' @param y A numeric response vector of length `n_sample`.
-#'
-#' @return A normalized `predictor_hybrid` object representing the first PLS component.
-#' @export
-get_pls_comp_simple <- function(W, y) {
-  n <- W$n_sample
-  if (length(y) != n) stop("Length of y must match number of samples in W.")
-
-  # Center the response (optional, but often improves interpretability)
-  y_centered <- y - mean(y)
-
-  # Initialize zero element
-  xi_sum <- predictor_hybrid_from_coef(W, coef = rep(0, sum(W$n_basis_list) + W$n_scalar))
-  
-  # Accumulate weighted sum: sum_i y_i * W_i
-  for (i in 1:n) {
-    Wi <- subset_predictor_hybrid(W, i)
-    xi_sum <- add.predictor_hybrid(xi_sum, Wi, alpha = y_centered[i])
-  }
-
-  # Normalize
-  norm_val <- sqrt(inprod.predictor_hybrid(xi_sum))
-  xi_hat <- add.predictor_hybrid(xi_sum, xi_sum, alpha = 1 / norm_val)
-
-  return(xi_hat)
-}
-

### 2025-12-30 FSHybridPLS/R/get_pre_corrcov.R

@@ -1,46 +1,0 @@
-# Generated from create-FSHybridPLS.Rmd: do not edit by hand
-
-#' Compute V matrix (pre-corrected covariance estimator)
-#'
-#' Constructs the V matrix involving inner products of functional predictors
-#' (weighted by their Gram matrices) and scalar predictors against response y.
-#'
-#' @param W A `predictor_hybrid` object.
-#' @param y A numeric response vector of length equal to number of samples.
-#'
-#' @return A matrix representing the corrected cross-covariance structure.
-#' @export
-get_pre_corrcov <- function(W, y){
-  n <- W$n_sample
-  K <- W$n_functional
-
-  # building blocks
-  ## C_J : C multiplied by J. Scalable to arbitrary K
-  predictor_first <- W$functional_list[[1]]
-  C_J <- t(predictor_first$coefs) %*% W$gram_list[[1]]
-  for (i in 2:K){
-    predictor_now <- W$functional_list[[i]]
-    C_J <- cbind(
-      C_J,
-      t(predictor_now$coefs) %*% W$gram_list[[i]]
-    )
-    }
-
-  
-  ## covariance
-  J_Ct_y <- t(C_J) %*% y
-  Zt_y <- t(W$Z) %*% y
-
-  # V matrix
-  upper_left <- J_Ct_y %*% t(J_Ct_y)
-  upper_right <- J_Ct_y %*% t(Zt_y)
-  lower_left <- t(upper_right)
-  lower_right <- Zt_y %*% t(Zt_y)
-
-  V_star <- cbind(
-    rbind(upper_left, lower_left),
-    rbind(upper_right, lower_right)
-    )/(n^2)
-
-  return(V_star)
-  }

### 2025-12-30 FSHybridPLS/R/get_rho.R

@@ -1,0 +1,50 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Compute PLS Scores
+#'
+#' Projects the hybrid predictor data W onto the weight direction defined by d_vec
+#' to calculate the PLS scores.
+#'
+#' @param d_vec A numeric vector of concatenated coefficients (functional basis coeffs + scalar weights).
+#' @param W A `predictor_hybrid` object containing the data.
+#'
+#' @return A numeric vector of PLS scores (length n).
+#' @export
+get_rho <- function(d_vec, W) {
+  K <- W$n_functional
+  M <- W$n_basis_list[[1]] # Assumes same number of basis functions for all K
+  n_scalar <- W$n_scalar
+  n <- W$n_sample
+  
+  # Initialize rho vector
+  rho <- rep(0, n)
+
+  # --- Functional Part ---
+  # Iterate over functional predictors to compute inner products <X^(k), gamma^(k)>
+  for (j in 1:K) {
+    # Extract coefficients for the j-th functional weight
+    start_index <- (j - 1) * M + 1
+    end_index <- j * M
+    gamma_j <- d_vec[start_index:end_index]
+    
+    # Get data coefficients (samples x basis)
+    Theta_j <- t(W$functional_list[[j]]$coefs)
+    
+    # Gram matrix
+    B <- W$gram_list[[j]]
+    
+    # Update scores: rho += Theta * B * gamma
+    # (samples x basis) * (basis x basis) * (basis x 1) -> (samples x 1)
+    rho <- rho + Theta_j %*% B %*% gamma_j
+  }
+
+  # --- Scalar Part ---
+  # Extract scalar weights (the remaining coefficients in d_vec)
+  scalar_indices <- (K * M + 1):length(d_vec)
+  scalar_weights <- d_vec[scalar_indices]
+  
+  # Update scores: rho += Z * weights
+  rho <- rho + W$Z %*% scalar_weights
+  
+  return(as.vector(rho))
+}

### 2025-12-30 FSHybridPLS/R/get_smoothing_param_hybrid.R

@@ -2,31 +2,36 @@
 
 #' Construct block-diagonal smoothing parameter matrix
 #'
-#' Generates a block-diagonal matrix with smoothing parameters applied to each 
-#' functional component. Each block is a scaled identity matrix, where the scaling 
-#' factor corresponds to the regularization parameter for that functional component. 
-#' The scalar components are not penalized and thus contribute a zero matrix block.
+#' Generates a block-diagonal matrix containing regularization parameters. 
+#' Functional coefficients are penalized by scaled identity matrices, while 
+#' scalar coefficients receive zero penalty.
 #'
 #' @param W A `predictor_hybrid` object.
-#' @param lambda A numeric vector of length equal to the number of functional components (`W$n_functional`), containing the smoothing parameters for each functional predictor.
+#' @param lambda A numeric vector of smoothing parameters, one for each functional predictor.
 #'
-#' @return A block-diagonal matrix of size `(total_dim × total_dim)`, where the top-left blocks are scaled identity matrices for functional predictors and the bottom-right block is a zero matrix for scalar covariates.
+#' @return A sparse block-diagonal matrix. The top-left blocks are `lambda[k] * I`, 
+#' and the bottom-right block is a zero matrix for scalar covariates.
 #' @export
 get_smoothing_param_hybrid <- function(W, lambda) {
+  # Input validation
   if (!inherits(W, "predictor_hybrid")) {
     stop("Input W must be of class 'predictor_hybrid'.")
   }
-
   if (length(lambda) != W$n_functional) {
     stop("Length of lambda must match the number of functional predictors.")
   }
 
+  # 1. Create penalty blocks for functional predictors
+  #    For each predictor k, create a scaled identity matrix: lambda[k] * I_Mk
   lambda_blocks <- lapply(seq_len(W$n_functional), function(ii) {
     nb <- W$functional_list[[ii]]$basis$nbasis
     lambda[ii] * diag(nb)
   })
 
+  # 2. Create zero block for scalar predictors
+  #    Scalar predictors are not penalized in this matrix, so we append a p x p zero matrix.
   lambda_blocks[[W$n_functional + 1]] <- matrix(0, nrow = W$n_scalar, ncol = W$n_scalar)
 
+  # 3. Construct the sparse block-diagonal matrix
   Matrix::bdiag(lambda_blocks)
 }

### 2025-12-30 FSHybridPLS/R/get_xi_hat_linear_pen.R

@@ -1,0 +1,62 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Compute Penalized PLS Weight Vector (Linear)
+#'
+#' Solves for the PLS weight direction xi that maximizes the covariance with y,
+#' subject to roughness penalties on the functional components.
+#'
+#' @param W A `predictor_hybrid` object.
+#' @param y A numeric vector of response values.
+#' @param lambda A numeric vector of smoothing parameters.
+#'
+#' @return A single-sample `predictor_hybrid` object representing the weight direction xi.
+#' @export
+get_xi_hat_linear_pen <- function(W, y, lambda) {
+  
+  n <- W$n_sample
+  K <- W$n_functional
+  u <- gamma <- list()
+
+  # --- Scalar Component ---
+  # Compute scalar weights: v = Z^T * y
+  v <- t(W$Z) %*% y
+  
+  # Initialize squared norm q with scalar part contribution
+  # q = ||xi||^2_pen = sum(v^2) + functional_parts
+  q <- sum(v^2)
+
+  # --- Functional Components ---
+  for (j in 1:K) {
+    # Theta_t: coefficient matrix of the functional data (basis x samples)
+    Theta_t <- W$functional_list[[j]]$coefs
+    
+    # B: Gram matrix for the j-th basis
+    B <- W$gram_list[[j]]
+    
+    # Compute RHS of the linear system: u = B * Theta * y
+    # This represents the unpenalized gradient term
+    u[[j]] <- B %*% Theta_t %*% y
+
+    # Linear System Matrix: R = Gram + lambda * Penalty
+    R <- W$gram_list[[j]] + lambda[j] * W$gram_deriv2_list[[j]]
+    
+    # Solve for gamma_j: (Gram + Penalty) * gamma = Gram * Theta * y
+    gamma[[j]] <- solve(R, u[[j]])
+
+    # Update squared norm q:
+    # Add contribution gamma^T * R * gamma (penalized norm of functional weight)
+    q <- q + sum(gamma[[j]] * (R %*% gamma[[j]]))
+  }
+  
+  # --- Combine and Normalize ---
+  # Flatten gamma list and append scalar weights v
+  d_vec <- c(do.call(c, gamma), v)
+  
+  # Normalize the vector to have unit penalized norm
+  d_vec <- d_vec / sqrt(q)
+  
[…]

### 2025-12-30 FSHybridPLS/R/inprod.predictor_hybrid.R

@@ -13,8 +13,8 @@
 #' @export
 inprod.predictor_hybrid <- function(xi_1, xi_2 = NULL) {
   # Handle self-inner product
-  if (is.null(xi_2)) xi_2 <- xi_1 
-  
+  if (is.null(xi_2)) xi_2 <- xi_1
+
   # Type checks
   if (!inherits(xi_1, "predictor_hybrid") || !inherits(xi_2, "predictor_hybrid")) {
     stop("Both inputs must be of class 'predictor_hybrid'.")
@@ -28,7 +28,7 @@ inprod.predictor_hybrid <- function(xi_1, xi_2 = NULL) {
     stop("Mismatch in number of scalar predictors.")
   }
 
-  # Swap so that broadcasting always applies to xi_2
+  # Swap so that broadcasting always applies to xi_2 (the smaller one)
   if (xi_1$n_sample == 1 && xi_2$n_sample > 1) {
     tmp <- xi_1
     xi_1 <- xi_2
@@ -48,24 +48,26 @@ inprod.predictor_hybrid <- function(xi_1, xi_2 = NULL) {
   Z1 <- xi_1$Z
   Z2 <- xi_2$Z
 
-  # Replicate fd and Z if needed
-  if (n2 == 1) {
+  # Replicate fd and Z if needed for broadcasting
+  if (n2 == 1 && n1 > 1) {
     f2 <- rep_fd(f2, n1)
     Z2 <- matrix(rep(c(Z2), n1), nrow = n1, byrow = TRUE)
   }
 
   # Compute functional inner products
+  # Iterates over samples (i) and sums the inner products of all functional predictors (j)
   inprod_functional <- vapply(seq_len(n1), function(i) {
     sum(vapply(seq_along(f1), function(j) {
       fda::inprod(f1[[j]][i], f2[[j]][i])
     }, numeric(1)))
   }, numeric(1))
- 
 
-  # Compute scalar inner products
-  inprod_scalar <- rowSums(Z1 * Z2) 
- 
-  # Combine results
+  # Compute scalar inner products using row-wise summation
+  inprod_scalar <- rowSums(Z1 * Z2)
+
+  # Combine functional and scalar results
   result <- inprod_functional + inprod_scalar
+  
+  # Return scalar if both inputs were single samples
   if (n1 == 1 && n2 == 1) as.numeric(result) else result
 }

### 2025-12-30 FSHybridPLS/R/inprod_pen.predictor_hybrid.R

@@ -1,0 +1,37 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Penalized Inner product between two predictor_hybrid objects
+#'
+#' Computes the inner product between two `predictor_hybrid` objects,
+#' adding a roughness penalty term based on the second derivative.
+#'
+#' @param xi_1 A `predictor_hybrid` object.
+#' @param xi_2 Another `predictor_hybrid` object. If missing, defaults to `xi_1`.
+#' @param lambda A numeric vector of smoothing parameters (one for each functional predictor).
+#'
+#' @return A numeric vector of inner products.
+#' @export
+inprod_pen.predictor_hybrid <- function(xi_1, xi_2 = NULL, lambda) {
+  
+  # Compute the standard inner product first
+  base_inprod <- inprod.predictor_hybrid(xi_1, xi_2)
+  
+  # Handle self-reference for xi_2
+  if (is.null(xi_2)) xi_2 <- xi_1
+  
+  f1 <- xi_1$functional_list
+  f2 <- xi_2$functional_list
+  
+  # Add penalty terms for each functional predictor
+  # The penalty is lambda * <D^2 f1, D^2 f2>
+  for (j in seq_len(xi_1$n_functional)) {
+    base_inprod <- base_inprod + lambda[j] * fda::inprod(
+      fdobj1 = f1[[j]],
+      fdobj2 = f2[[j]],
+      Lfdobj1 = 2, # Second derivative
+      Lfdobj2 = 2  # Second derivative
+    )
+  }
+  
+  return(as.numeric(base_inprod))
+}

### 2025-12-30 FSHybridPLS/R/is_same_basis.R

@@ -1,12 +1,26 @@
 # Generated from create-FSHybridPLS.Rmd: do not edit by hand
 
+#' Check if two functional data lists share the same basis
+#'
+#' @description
+#' Checks if two composite functional data objects share the exact same basis functions
+#' by comparing their internal list structures.
+#'
+#' @param input A list containing functional data objects (expected to have a `$functional_list` structure).
+#' @param other Another list containing functional data objects to compare against.
+#' @return `TRUE` if both lists have the same length and every corresponding basis is equivalent; otherwise `FALSE`.
 #' @export
 is_same_basis <- function(input, other) {
   all(
+    # Check if both lists have the same number of functional elements
     length(input$functional_list) == length(other$functional_list),
+    
+    # Check if the basis for each corresponding element is identical
     all(
-      mapply(function(fd1, fd2) fda::is.eqbasis(fd1$basis, fd2$basis),
-             input$functional_list, other$functional_list)
+      mapply(function(fd1, fd2) {
+        # Use fda package function to check basis equality
+        fda::is.eqbasis(fd1$basis, fd2$basis)
+      }, input$functional_list, other$functional_list)
     )
   )
 }

### 2025-12-30 FSHybridPLS/R/n_sample.fd.R

@@ -1,0 +1,16 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Get Number of Samples from an fd Object
+#'
+#' Extracts the number of observations (replications) stored in a functional data object.
+#'
+#' @param fd_obj An object of class `fd`.
+#' @return Integer representing the number of samples.
+#' @export
+n_sample.fd <- function(fd_obj) {
+  if (!inherits(fd_obj, "fd")) {
+    stop("Input must be of class 'fd'.")
+  }
+  # The coefficient matrix has dimensions (nbasis x n_sample)
+  return(ncol(fd_obj$coefs))
+}

### 2025-12-30 FSHybridPLS/R/predictor_hybrid.R

@@ -1,0 +1,64 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Create a predictor_hybrid object (S3 version, automatic basis size and Gram matrix)
+#'
+#' Constructs a hybrid predictor object that stores both scalar and functional predictors,
+#' and automatically computes Gram matrices (inner products of basis functions).
+#'
+#' @param Z A numeric matrix of dimension \code{n_sample x n_scalar} representing scalar predictors.
+#' @param functional_list A list of functional predictors (e.g., \code{fd} objects from the \code{fda} package).
+#' @param eval_point Points at which the functions are evaluated (stored as metadata).
+#'
+#' @return An object of class \code{predictor_hybrid}, containing scalar and functional data with Gram matrices.
+#' @export
+predictor_hybrid <- function(Z, functional_list, eval_point) {
+  # Validate scalar input
+  stopifnot(is.matrix(Z), is.numeric(Z))
+  
+  # Validate functional input
+  stopifnot(is.list(functional_list))
+  
+  n_sample <- nrow(Z)
+  n_scalar <- ncol(Z)
+  n_functional <- length(functional_list)
+  
+  # Initialize lists for storing matrices and metadata
+  gram_list <- gram_deriv2_list <- vector("list", n_functional)
+  n_basis_list <- numeric(n_functional)
+  
+  # Iterate through each functional predictor to compute necessary matrices
+  for (i in seq_len(n_functional)) {
+    fd_i <- functional_list[[i]]
+    stopifnot(inherits(fd_i, "fd"))
+    
+    # Ensure the number of functional samples matches the scalar samples
+    n_fd_sample <- ncol(coef(fd_i))
+    if (n_fd_sample != n_sample) {
+      stop(sprintf("Functional predictor %d has %d replicates, but Z has %d rows.",
+                   i, n_fd_sample, n_sample))
+    }
+    
+    # Extract basis and compute inner product matrices
+    basis_i <- fd_i$basis
+    gram_list[[i]] <- compute_gram_matrix(basis_i)
+    gram_deriv2_list[[i]] <- fda::getbasispenalty(basis_i) # Compute roughness penalty matrix
+    
+    n_basis_list[i] <- basis_i$nbasis
+  }
+  
+  # Construct the S3 object
+  structure(
+    list(
+      Z = Z,
+      functional_list = functional_list,
+      eval_point = eval_point,
[…]

### 2025-12-30 FSHybridPLS/R/predictor_hybrid_from_coef.R

@@ -10,19 +10,39 @@
 #' @param coef A numeric vector containing coefficients for both functional and scalar predictors.
 #'
 #' @return A \code{predictor_hybrid} object with updated \code{functional_list}, \code{Z}, and \code{n_sample = 1}.
-#'
-#'
 #' @export
-predictor_hybrid_from_coef <- function(format, coef){
-  M <- dim(format$gram_list[[1]])[2] # number of basis functions
-  K <- length(format$functional_list) # number of functional predictors
-  for (ii in 1:K){
+predictor_hybrid_from_coef <- function(format, coef) {
+  # Extract metadata from the template
+  basis_counts <- format$n_basis_list
+  
+  # Check if all functional predictors have the same number of basis functions
+  if (length(unique(basis_counts)) != 1) {
+    stop("All functional predictors must have the same number of basis functions (M).")
+  }
+  
+  M <- basis_counts[1]  # Number of basis functions (identical across predictors)
+  K <- format$n_functional # Number of functional predictors
+  
+  # Reconstruct each functional predictor
+  for (ii in 1:K) {
+    # Calculate indices for the current functional predictor in the flat vector
+    start_idx <- (ii - 1) * M + 1
+    end_idx   <- ii * M
+    
+    # Create a new fd object using the sliced coefficients and original basis
     format$functional_list[[ii]] <- fd(
-      coef = as.matrix(coef[((ii-1)*M + 1):(ii*M)]),
+      coef = as.matrix(coef[start_idx:end_idx]),
       basisobj = format$functional_list[[ii]]$basis
     )
   }
-  format$Z <- t(as.matrix(coef[(K * M + 1):length(coef)]))
+  
+  # Reconstruct the scalar predictor part (Z)
+  # The remaining coefficients after K*M belong to the scalar predictors
+  scalar_start_idx <- K * M + 1
+  format$Z <- t(as.matrix(coef[scalar_start_idx:length(coef)]))
+  
+  # Update sample count to 1 as this constructor creates a single observation
   format$n_sample <- 1
+  
   return(format)
 }

### 2025-12-30 FSHybridPLS/R/rep_fd.R

@@ -11,17 +11,23 @@
 #' @return A list of `fd` objects, each with `n` replications.
 #' @export
 rep_fd <- function(fd_list, n) {
+  # Validate input: must be a list of 'fd' objects
   if (!is.list(fd_list) || any(!vapply(fd_list, inherits, logical(1), "fd"))) {
     stop("Input must be a list of 'fd' objects.")
   }
-
+  
   lapply(fd_list, function(fd_obj) {
     coef_mat <- fd_obj$coefs
+    
+    # Ensure the object represents a single sample (one column of coefficients)
     if (is.null(dim(coef_mat)) || ncol(coef_mat) != 1) {
       stop("Each fd object in the list must have one column of coefficients.")
     }
-
+    
+    # Create a new coefficient matrix by repeating the column 'n' times
     new_coefs <- matrix(rep(coef_mat, n), nrow = nrow(coef_mat), ncol = n)
+    
+    # Return a new fd object with the replicated coefficients and original basis
     fd(coef = new_coefs, basisobj = fd_obj$basis)
   })
 }

### 2025-12-30 FSHybridPLS/R/replace_obs_hybrid.R

@@ -1,0 +1,50 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Replace a single observation in a predictor_hybrid object
+#'
+#' Replaces the i-th observation of a predictor_hybrid object with a new
+#' single-sample predictor_hybrid object.
+#'
+#' @param W A predictor_hybrid object with one or more samples.
+#' @param i An integer index specifying the observation to replace.
+#' @param new_W A single-sample predictor_hybrid object to use for replacement.
+#'
+#' @return A predictor_hybrid object with the i-th observation replaced.
+#' @export
+replace_obs_hybrid <- function(W, i, new_W) {
+  # Input validation
+  if (!inherits(W, "predictor_hybrid") || !inherits(new_W, "predictor_hybrid")) {
+    stop("Both W and new_W must be of class 'predictor_hybrid'.")
+  }
+  if (new_W$n_sample != 1) {
+    stop("new_W must be a single-sample predictor_hybrid object.")
+  }
+  if (i < 1 || i > W$n_sample) {
+    stop(paste("Index i must be between 1 and", W$n_sample))
+  }
+  if (W$n_scalar != new_W$n_scalar) {
+    stop("Mismatch in number of scalar predictors.")
+  }
+  if (W$n_functional != new_W$n_functional) {
+    stop("Mismatch in number of functional predictors.")
+  }
+
+  # Check for compatible basis objects
+  is_eqbasis <- getFromNamespace("is.eqbasis", "fda")
+  for (j in seq_len(W$n_functional)) {
+    if (!is_eqbasis(W$functional_list[[j]]$basis, new_W$functional_list[[j]]$basis)) {
+      stop("Functional predictors must have the same basis objects.")
+    }
+  }
+
+  # Replace the i-th observation in the scalar matrix Z
+  W$Z[i, ] <- new_W$Z[1, ]
+
+  # Replace the i-th observation in each functional predictor
+  for (j in seq_along(W$functional_list)) {
+    # The coefficients are stored as a matrix, with columns corresponding to samples
+    W$functional_list[[j]]$coefs[, i] <- new_W$functional_list[[j]]$coefs[, 1]
+  }
+
+  return(W)
+}

### 2025-12-30 FSHybridPLS/R/residualize_predictor.R

@@ -1,0 +1,30 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Residualize the hybrid predictor
+#'
+#' Updates each observation in W by subtracting the projection onto rho (rho_i * delta).
+#'
+#' @param W The current `predictor_hybrid` object.
+#' @param rho The current PLS score vector.
+#' @param delta The hybrid regression coefficient (single-sample object).
+#'
+#' @return The residualized `predictor_hybrid` object.
+#' @export
+residualize_predictor <- function(W, rho, delta) {
+  n <- length(rho)
+  W_res <- W
+  
+  # Iterate through each sample to compute residuals
+  for (i in 1:n) {
+    # Extract the i-th observation
+    W_i <- subset_predictor_hybrid(W, i)
+    
+    # Calculate residual: W_i_new = W_i - rho[i] * delta
+    W_res_i <- subtr.predictor_hybrid(W_i, delta, rho[i])
+    
+    # Replace the observation in the result object
+    W_res <- replace_obs_hybrid(W_res, i, W_res_i)
+  }
+  
+  return(W_res)
+}

### 2025-12-30 FSHybridPLS/R/residualize_y.R

@@ -1,0 +1,16 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Residualize the response vector
+#'
+#' Subtracts the projection of y onto rho from y.
+#'
+#' @param y The current response vector.
+#' @param rho The current PLS score vector.
+#' @param nu The regression coefficient.
+#'
+#' @return The residualized response vector.
+#' @export
+residualize_y <- function(y, rho, nu) {
+  y_next <- y - nu * rho
+  return(y_next)
+}

### 2025-12-30 FSHybridPLS/R/scalar_mul.predictor_hybrid.R

@@ -3,7 +3,7 @@
 #' Multiply a predictor_hybrid object by a scalar
 #'
 #' Performs scalar multiplication on both the scalar and functional components
-#' of a `predictor_hybrid` object. Functional predictors are scaled using 
+#' of a `predictor_hybrid` object. Functional predictors are scaled using
 #' `times.fd()` from the `fda` package.
 #'
 #' @param input A `predictor_hybrid` object.
@@ -28,8 +28,10 @@ scalar_mul.predictor_hybrid <- function(input, scalar) {
   new_Z <- scalar * input$Z
 
   # Reconstruct hybrid object
+  # Passing eval_point from the original input to maintain metadata
   predictor_hybrid(
     Z = new_Z,
-    functional_list = new_functional_list
+    functional_list = new_functional_list,
+    eval_point = input$eval_point
   )
 }

### 2025-12-30 FSHybridPLS/R/scalar_normalize.R

@@ -1,0 +1,25 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Normalize a scalar predictor matrix
+#'
+#' Centers columns by 'mean' and scales them by 'deno'.
+#'
+#' @param scalar_predictor Numeric matrix.
+#' @param mean Numeric vector of column means.
+#' @param deno Numeric vector of column standard deviations.
+#' @return Normalized matrix.
+#' @export
+scalar_normalize <- function(scalar_predictor, mean, deno) {
+  # Subtract mean from each row (broadcasted)
+  # Uses the helper subtr_broadcast function defined previously
+  scalar_predictor_normalized <- subtr_broadcast(scalar_predictor, mean)
+  
+  # Create a matrix of denominators matching the dimensions of the predictor
+  deno_mat <- matrix(rep(deno, each = nrow(scalar_predictor)), 
+                     nrow = nrow(scalar_predictor), 
+                     ncol = length(deno))
+  
+  # Element-wise division
+  scalar_predictor_normalized <- scalar_predictor_normalized / deno_mat
+  return(scalar_predictor_normalized)
+}

### 2025-12-30 FSHybridPLS/R/scalar_normalize_train_test.R

@@ -1,0 +1,50 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Normalize Scalar Predictors (Train/Test Split)
+#'
+#' Standardizes scalar predictors (Z) to have mean zero and unit variance.
+#' Statistics are computed from the training set.
+#'
+#' @param predictor_train A `predictor_hybrid` object (train).
+#' @param predictor_test A `predictor_hybrid` object (test).
+#'
+#' @return A list containing normalized objects and statistics.
+#' @export
+scalar_normalize_train_test <- function(predictor_train, predictor_test) {
+  stopifnot(
+    inherits(predictor_train, "predictor_hybrid"),
+    inherits(predictor_test, "predictor_hybrid"),
+    predictor_train$n_scalar == predictor_test$n_scalar
+  )
+
+  predictor_train_normalized <- predictor_train
+  predictor_test_normalized <- predictor_test
+
+  # 1. Compute Statistics from TRAINING data
+  mean_train <- colMeans(predictor_train$Z)
+  sd_train <- apply(predictor_train$Z, 2, sd)
+  
+  # Handle zero variance columns
+  sd_train[sd_train == 0] <- 1
+
+  # 2. Normalize TRAINING set
+  predictor_train_normalized$Z <- scalar_normalize(
+    predictor_train$Z,
+    mean_train,
+    sd_train
+  )
+
+  # 3. Normalize TEST set using TRAIN stats
+  predictor_test_normalized$Z <- scalar_normalize(
+    predictor_test$Z,
+    mean_train,
+    sd_train
+  )
+
+  return(list(
+    predictor_train = predictor_train_normalized,
+    predictor_test = predictor_test_normalized,
+    mean_train = mean_train,
+    sd_train = sd_train
+  ))
+}

### 2025-12-30 FSHybridPLS/R/split.all.R

@@ -1,0 +1,61 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Split Hybrid Predictor and Response Data
+#'
+#' Randomly partitions the hybrid predictor object and response vector into 
+#' training and testing sets based on a given ratio. Handles any number of 
+#' functional predictors.
+#'
+#' @param W_hybrid A `predictor_hybrid` object containing all functional and scalar data.
+#' @param response A numeric vector. The response variable corresponding to the samples in W_hybrid.
+#' @param train_ratio A numeric scalar between 0 and 1 indicating the proportion of data to use for training.
+#'
+#' @return A list containing split train and test sets for predictors and response.
+#' @export
+split.all <- function(W_hybrid, response, train_ratio) {
+  # --- Input Validation ---
+  if (!inherits(W_hybrid, "predictor_hybrid")) {
+    stop("'W_hybrid' must be a predictor_hybrid object.")
+  }
+  if (!is.vector(response) && !is.factor(response)) {
+    stop("'response' must be a vector.")
+  }
+  if (length(response) != W_hybrid$n_sample) {
+    stop("Response length must match the number of samples in W_hybrid.")
+  }
+  if (!is.numeric(train_ratio) || train_ratio <= 0 || train_ratio >= 1) {
+    stop("'train_ratio' must be a numeric value strictly between 0 and 1.")
+  }
+
+  N <- W_hybrid$n_sample
+  N_train <- floor(N * train_ratio)
+
+  # Generate random indices
+  # set.seed() should be called by the user before this function if reproducibility is needed
+  train_idx <- sort(sample(seq_len(N), N_train))
+  test_idx  <- sort(setdiff(seq_len(N), train_idx))
+
+  # --- Subset Scalar Predictors ---
+  Z_train <- W_hybrid$Z[train_idx, , drop = FALSE]
+  Z_test  <- W_hybrid$Z[test_idx,  , drop = FALSE]
+
+  # --- Subset Functional Predictors ---
+  # Use lapply to handle any number of functional predictors (K)
+  # The '[' operator on an fd object subsets the samples (replicates)
+  fun_list_train <- lapply(W_hybrid$functional_list, function(fd_obj) fd_obj[train_idx])
+  fun_list_test  <- lapply(W_hybrid$functional_list, function(fd_obj) fd_obj[test_idx])
+
+  # --- Reconstruct Hybrid Objects ---
[…]

### 2025-12-30 FSHybridPLS/R/split_and_normalize.all.R

@@ -1,0 +1,67 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Split and Preprocess Hybrid Data
+#'
+#' Executes the full preprocessing pipeline: splitting data, standardizing within
+#' modalities (functional/scalar), balancing variance between modalities, and 
+#' standardizing the response.
+#'
+#' @param W_hybrid The full `predictor_hybrid` object.
+#' @param response The numeric response vector.
+#' @param train_ratio Numeric scalar (0-1) for train/test split.
+#'
+#' @return A list containing processed datasets and normalization parameters.
+#' @export
+split_and_normalize.all <- function(W_hybrid, response, train_ratio) {
+  
+  # 1. Split Data
+  # Note: Requires the previously defined split.all function
+  split_result <- split.all(W_hybrid, response, train_ratio)
+
+  # 2. Normalize Functional Predictors (Within)
+  curve_norm <- curve_normalize_train_test(
+    split_result$predictor_train, 
+    split_result$predictor_test
+  )
+  
+  # 3. Normalize Scalar Predictors (Within)
+  scalar_norm <- scalar_normalize_train_test(
+    curve_norm$predictor_train, 
+    curve_norm$predictor_test
+  )
+  
+  # 4. Normalize Between Modalities (Balance Variances)
+  btwn_norm <- btwn_normalize_train_test(
+    scalar_norm$predictor_train,
+    scalar_norm$predictor_test
+  )
+  
+  # 5. Normalize Response Variable
+  response_mean_train <- mean(split_result$response_train)
+  response_sd_train   <- sd(split_result$response_train)
+  
+  # Prevent division by zero if response is constant
+  if (response_sd_train == 0) response_sd_train <- 1
+  
+  response_train_std <- (split_result$response_train - response_mean_train) / response_sd_train
+  response_test_std  <- (split_result$response_test  - response_mean_train) / response_sd_train
+  
+  response_norm <- list(mean_train = response_mean_train, sd_train = response_sd_train)
+
+  # Return comprehensive results
+  return(list(
+    predictor_train = btwn_norm$predictor_train,
+    predictor_test  = btwn_norm$predictor_test,
+    response_train  = response_train_std,
+    response_test   = response_test_std,
+    
+    # Store intermediate results and statistics for reference/reconstruction
+    details = list(
+      curve_normalize_result  = curve_norm,
+      scalar_normalize_result = scalar_norm,
[…]

### 2025-12-30 FSHybridPLS/R/subset_predictor_hybrid.R

@@ -5,11 +5,22 @@
 #' @param W A predictor_hybrid object with multiple samples.
 #' @param i Integer index of the sample to extract.
 #' @return A single-sample predictor_hybrid object.
+#' @export
 subset_predictor_hybrid <- function(W, i) {
+  # Extract the i-th row of the scalar matrix
   new_Z <- matrix(W$Z[i, ], nrow = 1)
+  
+  # Extract the i-th column of coefficients for each functional object
   new_functional_list <- lapply(W$functional_list, function(fdobj) {
     fd(coef = matrix(coef(fdobj)[, i], ncol = 1), basisobj = fdobj$basis)
   })
-  predictor_hybrid(Z = new_Z, functional_list = new_functional_list)
+  
+  # Construct new object
+  new_predictor <- predictor_hybrid(
+    Z = new_Z, 
+    functional_list = new_functional_list,
+    eval_point = W$eval_point
+  )
+  
+  return(new_predictor)
 }
-

### 2025-12-30 FSHybridPLS/R/subtr.predictor_hybrid.R

@@ -14,4 +14,3 @@
 subtr.predictor_hybrid <- function(input, other, alpha = 1) {
   add.predictor_hybrid(input, other, alpha = -alpha)
 }
-

### 2025-12-30 FSHybridPLS/R/subtr_broadcast.R

@@ -1,0 +1,15 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Broadcast Subtraction for Matrices
+#'
+#' Subtracts a single observation (vector) from every row of a matrix.
+#'
+#' @param input A numeric matrix.
+#' @param other A numeric vector or a 1-row matrix.
+#' @param alpha A scalar multiplier (default 1).
+#' @return A matrix with the broadcasted subtraction applied.
+#' @export
+subtr_broadcast <- function(input, other, alpha = 1) {
+  # Reuse add_broadcast with negated alpha
+  add_broadcast(input, other, (-1 * alpha))
+}

### 2025-12-30 FSHybridPLS/R/univDecomp.R

@@ -1,0 +1,77 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Univariate Decomposition
+#'
+#' @description
+#' Calculates the univariate basis decomposition for each element of a multivariate
+#' functional object.
+#'
+#' \strong{Modification:} Accepts \code{funDataObject_predict} to facilitate
+#' the pass-through of test data to the specific decomposition method (e.g., uFPCA).
+#'
+#' @param type Character string specifying the decomposition method (e.g., "uFPCA").
+#' @param funDataObject The training functional data.
+#' @param funDataObject_predict The prediction functional data.
+#' @param ... Additional arguments passed to the specific decomposition function.
+#'
+#' @return A list containing the basis decomposition results.
+#' @export 
+univDecomp <- function(type, funDataObject, funDataObject_predict, ...)
+{
+  # Parameter checking
+  if(is.null(type))
+    stop("Parameter 'type' is missing.")
+  else
+  {
+    if(!is.character(type))
+      stop("Parameter 'type' must be a character string. See ?univDecomp for details.")
+  }
+
+  if(class(funDataObject) != "funData")
+    stop("Parameter 'funDataObject' must be a funData object.")
+
+
+  # get all arguments (except for function call and type)
+  params <- list(...)
+
+  # check if type and data are of correct type
+  if(is.null(type))
+    stop("univDecomp: must specify 'type'.")
+
+  if(!inherits(type, "character"))
+    stop("univDecomp: 'type' must be of class character.")
+
+  if(is.null(funDataObject))
+    stop("univDecomp: must specify 'funDataObject'.")
+
+  if(class(funDataObject) != "funData")
+    stop("univDecomp: 'funDataObject' must be of class funData.")
+
+  params$funDataObject <- funDataObject # add funDataObject (-> make sure is evaluated in correct env.)
+
+  ############### modified by Jongmin Mun ######################
+  # Add prediction object to parameters if uFPCA is selected
+  if (type == "uFPCA"){params$funDataObject_predict <- funDataObject_predict}
+  ############### modified by Jongmin Mun ######################
+
+  res <- switch(type,
+                "given" = do.call(givenBasis, params),
+                "uFPCA" = do.call(fpcaBasis, params),
+                "UMPCA" = do.call(umpcaBasis, params),
+                "FCP_TPA" = do.call(fcptpaBasis, params),
[…]

### 2025-12-30 FSHybridPLS/R/univExpansion.R

@@ -1,0 +1,95 @@
+# Generated from create-FSHybridPLS.Rmd: do not edit by hand
+
+#' Calculate Univariate Basis Expansion
+#'
+#' @description
+#' Wrapper function that calls specific basis reconstruction methods (e.g., splines,
+#' FPCA) to reconstruct functions from scores.
+#'
+#' @param type Decomposition type (e.g., "uFPCA", "splines1D").
+#' @param scores Matrix of scores.
+#' @param argvals Argument values.
+#' @param functions Basis functions.
+#' @param params Additional parameters.
+#'
+#' @return A \code{funData} object.
+#' @export 
+univExpansion <- function(type, scores, argvals = ifelse(!is.null(functions), functions@argvals, NULL), functions, params = NULL)
+{
+  # Parameter checking
+  if(is.null(type))
+    stop("Parameter 'type' is missing.")
+  else
+  {
+    if(!is.character(type))
+      stop("Parameter 'type' must be a character string. See ?univExpansion for details.")
+  }
+
+  if(is.null(scores))
+    stop("Parameter 'scores' is missing.")
+  else
+  {
+    if(!is.matrix(scores))
+      stop("Parameter 'scores' must be passed as a matrix.")
+  }
+
+  if(is.numeric(argvals))
+  {
+    argvals <- list(argvals)
+    warning("Parameter 'argvals' was passed as a vector and transformed to a list.")
+  }
+
+  if(is.null(functions))
+  {
+    if(is.null(argvals))
+      stop("Must pass 'argvals' if 'functions' is NULL.")
+    else
+    {
+      if(!is.list(argvals))
+        stop("Parameter 'argvals' must be passed as a list.")
+    }
+  }
+  else
+  {
+    if(class(functions) != "funData")
+      stop("Parameter 'functions' must be a funData object.")
+
+    # check interaction with other parameters
+    if(nObs(functions) != NCOL(scores))
+      stop("Number of scores per curve does not match the number of basis functions.")
+
+    if(!is.null(argvals) & !isTRUE(all.equal(argvals, functions@argvals)))
+      stop("The parameter 'argvals' does not match the argument values of 'functions'.")
+  }
+
+  if(!is.null(params) & !is.list(params))
+    stop("The parameter 'params' must be passed as a list.")
+
+  # start calculations
+  params$scores <- scores
+  params$functions <- functions
+
+  if(is.numeric(argvals))
+    argvals <- list(argvals)
+
+  params$argvals <- argvals
+
+  res <- switch(type,
[…]

### 2025-12-30 FSHybridPLS/tests/testthat.R

@@ -1,12 +1,0 @@
-# This file is part of the standard setup for testthat.
-# It is recommended that you do not modify it.
-#
-# Where should you do additional test configuration?
-# Learn more about the roles of various files in:
-# * https://r-pkgs.org/testing-design.html#sec-tests-files-overview
-# * https://testthat.r-lib.org/articles/special-files.html
-
-library(testthat)
-library(FSHybridPLS)
-
-test_check("FSHybridPLS")

### 2025-12-30 FSHybridPLS/tests/testthat/tests.R

@@ -1,442 +1,0 @@
-# Generated from create-FSHybridPLS.Rmd: do not edit by hand  
-testthat::test_that("Gram matrix edge cases", {
-  suppressPackageStartupMessages(library(fda))
-
-  # Case 1: Fourier basis (orthogonal over [0, 1])
-  fb <- create.fourier.basis(rangeval = c(0, 1), nbasis = 5)
-  J_fourier <- compute_gram_matrix(fb)
-  testthat::expect_equal(J_fourier, diag(diag(J_fourier)), tolerance = 1e-10)  # Nearly diagonal
-
-  # Case 2: Constant basis (1 basis function)
-  cb <- create.constant.basis(rangeval = c(0, 1))
-  J_const <- compute_gram_matrix(cb)
-  testthat::expect_equal(dim(J_const), c(1, 1))
-  testthat::expect_equal(J_const[1, 1], 1)
-
-  # Case 3: Invalid input
-  testthat::expect_error(compute_gram_matrix("not a basisfd"))
-
-  # Case 4: Highly localized B-splines
-  # Simulate nearly disjoint support (narrow B-splines)
-  narrow_bs <- create.bspline.basis(rangeval = c(0, 1), nbasis = 10, norder = 2)
-  J_narrow <- compute_gram_matrix(narrow_bs)
-  testthat::expect_true(all(abs(J_narrow[upper.tri(J_narrow)]) < 0.5))  # off-diagonals small
-})
-
-
-
-testthat::test_that("rep_fd correctly replicates a list of fd objects", {
-  suppressPackageStartupMessages(library(fda))
-
-  # Create a simple basis
-  basis <- create.bspline.basis(c(0, 1), 5)
-
-  # Create single-sample fd object
-  coef_vec <- 1:5
-  fd1 <- fd(coef = matrix(coef_vec, ncol = 1), basisobj = basis)
-
-  # Replicate the list
-  rep_list <- rep_fd(list(fd1, fd1), 3)
-
-  # Check: list length unchanged
-  testthat::expect_equal(length(rep_list), 2)
-
-  # Check each replicated fd object
-  for (fd_obj in rep_list) {
-    testthat::expect_s3_class(fd_obj, "fd")
-    testthat::expect_equal(dim(fd_obj$coefs), c(5, 3))  # 5 basis × 3 samples
-    for (i in 1:3) {
[…]

### 2025-12-30 Untitled.R

@@ -1,0 +1,1163 @@
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+# Baseline method: FPCA regression
+
+
+## Modified MFPCA Function for Simultaneous Training and Prediction
+
+The MFPCA (Multivariate Functional Principal Component Analysis) function computes multivariate functional PCA for functions defined across different (dimensional) domains.
+We have modified the original implementation to admit a new input, **`mFData_predict`**, allowing the function to calculate PCA scores for **both the training data and new test (or validation) data simultaneously** in a single run. This change was necessary because the standard `predict.MFPCAfit` function does not permit computing scores for new, out-of-sample functions.
+The multivariate functional principal component analysis inherently relies on a **univariate basis expansion** for each functional element ($X^{(j)}$). To simplify the code modification, we use only the univariate functional PCA option and have removed other options provided by the original MFPCA function. We modifies the main function and two internal functions.
+
+
+### MFPCA
+
+```{r}
+#'
+#' @export MFPCA
+MFPCA <- function(mFData, mFData_predict, M, uniExpansions, weights = rep(1, length(mFData)), fit = FALSE, approx.eigen = FALSE,
+                  bootstrap = FALSE, nBootstrap = NULL, bootstrapAlpha = 0.05, bootstrapStrat = NULL,
+                  verbose = options()$verbose)
+{
+  if(! inherits(mFData, "multiFunData"))
+    stop("Parameter 'mFData' must be passed as a multiFunData object.")
+
+  # number of components
+  p <- length(mFData)
+  # number of observations
+  N <- nObs(mFData)
+
+  if(!all(is.numeric(M), length(M) == 1, M > 0))
+    stop("Parameter 'M' must be passed as a number > 0.")
+
+  if(!(is.list(uniExpansions) & length(uniExpansions) == p))
+    stop("Parameter 'uniExpansions' must be passed as a list with the same length as 'mFData'.")
+
+  if(!(is.numeric(weights) & length(weights) == p))
+    stop("Parameter 'weights' must be passed as a vector with the same length as 'mFData'.")
+
+  if(!is.logical(fit))
[…]

### 2025-12-30 asd.R

@@ -1,0 +1,2708 @@
+
+
+```
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+### inprod.predictor_hybrid
+- The inner product of $f_1=(f_1^{(1)}, \ldots,f_1^{(K)})$ and $f_2=(f_2^{(1)}, \ldots,f_2^{(K)})$ in $\mathcal{F}$ is defined as
+$$\langle f_1, f_2\rangle_\mathcal{F} =  \sum_{k=1}^K \langle f_1^{(k)}, f_2^{(k)}\rangle_{L^2} = \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k,$$ with norm
+$$\Vert f_1 \Vert_\mathcal{F} = \langle f_1,f_1 \rangle_\mathcal{F}^{1/2} = \{ \sum_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k)^2 dt_k\}^{1/2}.$$
+  - We define the inner product between any two hybrid objects, $\mathbf{h}_1 = (f_1, \mathbf{v}_1)$ and $\mathbf{h}_2 = (f_2, \mathbf{v}_2)$, as
+  $$
+    \langle \mathbf{h}_1, \mathbf{h}_2\rangle_{\mathcal{H}} = \langle f_1, f_2\rangle_\mathcal{F} +  \langle  \mathbf{v_1}, \mathbf{v_2} \rangle = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p v_{1r}v_{2r},
+    $$
+      with norm $\Vert \cdot \Vert_\mathcal{H} = \langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
+      
+      - The method `inprod.predictor_hybrid` computes the inner product between two `predictor_hybrid` objects. It supports broadcasting when one of the inputs has a single observation.
+      
+      
+      - Usage
+      
+      ```r
+      inprod.predictor_hybrid(xi_1, xi_2)
+      ```
+      
+      - Arguments:
+        
+        - `xi_1`: A `predictor_hybrid` object.
+      - `xi_2`: Another `predictor_hybrid` object. If omitted, defaults to xi_1 (computes self-inner product).
+      
[…]

### 2025-12-30 create-FSHybridPLS.Rmd
changed get_rho

@@
 ```{r}
-#' Compute PLS Scores
-#'
-#' Projects the hybrid predictor data W onto the weight direction defined by d_vec
-#' to calculate the PLS scores.
-#'
-#' @param d_vec A numeric vector of concatenated coefficients (functional basis coeffs + scalar weights).
-#' @param W A `predictor_hybrid` object containing the data.
-#'
-#' @return A numeric vector of PLS scores (length n).
-#' @export
-get_rho <- function(d_vec, W) {
-  K <- W$n_functional
-  M <- W$n_basis_list[[1]] # Assumes same number of basis functions for all K
-  n_scalar <- W$n_scalar
-  n <- W$n_sample
-
-  # Initialize rho vector
-  rho <- rep(0, n)
-
-  # --- Functional Part ---
-  # Iterate over functional predictors to compute inner products <X^(k), gamma^(k)>
-  for (j in 1:K) {
-    # Extract coefficients for the j-th functional weight
-    start_index <- (j - 1) * M + 1
-    end_index <- j * M
-    gamma_j <- d_vec[start_index:end_index]
-
-    # Get data coefficients (samples x basis)
-    Theta_j <- t(W$functional_list[[j]]$coefs)
-
-    # Gram matrix
-    B <- W$gram_list[[j]]
-
-    # Update scores: rho += Theta * B * gamma
-    # (samples x basis) * (basis x basis) * (basis x 1) -> (samples x 1)
-    rho <- rho + Theta_j %*% (B %*% gamma_j)
-
-  }
-
-  # --- Scalar Part ---
-  # Extract scalar weights (the remaining coefficients in d_vec)
-  scalar_indices <- (K * M + 1):length(d_vec)
-  scalar_weights <- d_vec[scalar_indices]
-
-  # Update scores: rho += Z * weights
-  rho <- rho + W$Z %*% scalar_weights
-
-  return(as.vector(rho))
+#' Exact Hybrid Inner Product
+#' Computes <W, xi> using basis inner product matrices.
+#' @param W The hybrid predictor object (contains coefs for N samples)
+#' @param xi The hybrid weight object (contains coefs for 1 direction)
+#' @return A vector of scores (length N)
+get_rho <- function(W, xi) {
+
+  # 1. Scalar Part (Standard dot product)
+  # (N x p_scalar) %*% (p_scalar x 1)
+  scores <- as.matrix(W$Z) %*% as.matrix(xi$Z)
+
+  # 2. Functional Part (Basis Matrix Algebra)
+  # Loop through each functional variable
+  for(k in seq_along(W$functional_list)) {
+
+    # Extract basis and coefficients
+    # Coefs_W is (Basis_Dim x N)
+    # Coefs_xi is (Basis_Dim x 1)
+    fd_W  <- W$functional_list[[k]]
+    fd_xi <- xi$functional_list[[k]]
+
+    # A. Compute J Matrix (Basis Inner Product)
+    # J[i,j] = Integral(phi_i(t) * phi_j(t) dt)
+    # Note: computed once per variable, very fast for B-splines
+    J <- fda::inprod(fd_W$basis, fd_W$basis)
+
+    # B. Compute Integral via Matrix Multiplication
+    # Formula: Score = Coefs_W^T * J * Coefs_xi
+    # Dimensions: (N x B) * (B x B) * (B x 1) -> (N x 1)
+
+    # Optimization: Pre-multiply J * xi to get a "weighted weight"
+    weighted_xi <- J %*% fd_xi$coefs
+
+    # Project data onto this weighted weight
+    scores <- scores + t(fd_W$coefs) %*% weighted_xi
+  }
+
+  return(as.vector(scores))
 }
@@
     beta = beta,
+    W = W_now,
+    delta = delta,
+    nu = nu,
     validation_rmse = if (!is.null(validation_data)) validation_rmse else NULL

### 2025-12-30 simul.Rmd
changed get_rho

@@
 knitr::opts_chunk$set(echo = TRUE)
-```
-
-## R Markdown
-
-```{r}
-# ==============================================================================
-# EQUIVALENCE CHECK: exact_inprod() vs get_rho()
-# ==============================================================================
-
-library(fda)
-
-# 1. DEFINE FUNCTIONS (To ensure environment is self-contained)
-# ------------------------------------------------------------------------------
-
-# A. Your Function (Logic: Matrix Multiplication)
-
-# 2. PREPARE DATA
-# ------------------------------------------------------------------------------
-set.seed(123)
-n_sample <- 50
-n_basis  <- 10
-basis <- create.bspline.basis(c(0,1), n_basis)
-
-# Generate Random W (Data)
-coefs_W <- matrix(rnorm(n_sample * n_basis), n_basis, n_sample)
-Z_W <- matrix(rnorm(n_sample * 5), n_sample, 5)
-fd_W <- fd(coefs_W, basis)
-W_current <- list(
-  Z = Z_W,
-  functional_list = list(fd_W), # Single functional predictor for simplicity
-  n_sample = n_sample,
-  n_functional = 1,
-  n_scalar = 5,
-  n_basis_list = list(n_basis)
-)
-
-# CRITICAL STEP: Populate 'gram_list' for get_rho to work
-# Your function assumes this exists. We must calculate it exactly as FDA does.
-W_current$gram_list <- list(
-  fda::inprod(basis, basis)
-)
-
-# Generate Random xi (Direction)
-coefs_xi <- matrix(rnorm(n_basis), n_basis, 1) # 1 direction
-Z_xi <- matrix(rnorm(5), 1, 5)
-fd_xi <- fd(coefs_xi, basis)
-xi_current <- list(
-  Z = Z_xi,
-  functional_list = list(fd_xi)
-)
-
-# 3. CONVERT INPUTS
-# ------------------------------------------------------------------------------
-# get_rho expects a flattened vector 'd_vec'.
-# We must flatten xi_current: [functional_coefs | scalar_weights]
-d_vec <- c(as.vector(coefs_xi), as.vector(Z_xi))
-
-# 4. RUN COMPARISON
-# ------------------------------------------------------------------------------
-
-# Run My Function
-val_exact <- exact_inprod(W_current, xi_current)
-
-# Run Your Function (Note: d_vec is 1st arg, W is 2nd arg)
-val_yours <- get_rho(d_vec, W_current)
-
-# 5. VERDICT
-# ------------------------------------------------------------------------------
-diff <- max(abs(val_exact - val_yours))
-
-cat("========================================\n")
-cat("      EQUIVALENCE CHECK RESULT       \n")
-cat("========================================\n")
-cat(sprintf("Max Difference: %.10e\n", diff))
-
-if(isTRUE(all.equal(val_exact, val_yours))) {
-  cat("CONCLUSION: ✅ FUNCTIONS ARE IDENTICAL.\n")
-  cat("Your implementation uses valid exact matrix algebra.\n")
-} else {
-  cat("CONCLUSION: ❌ FUNCTIONS DIFFER.\n")
-}
-```
-
-```{r}
-#' Exact Hybrid Inner Product (Matrix Based)
-#' 
-#' Calculates <W, xi> using Basis Inner Product Matrices (J).
-#' Guarantees mathematical exactness for B-splines.
-#' 
-#' @param W Hybrid predictor (N samples)
-#' @param xi Hybrid direction (1 sample/direction)
-#' @return Numeric vector of length N (The scores)
-exact_inprod <- function(W, xi) {
-
-  # 1. Scalar Part (Dot Product)
-  # (N x p) %*% (p x 1)
-  scores <- as.matrix(W$Z) %*% t(as.matrix(xi$Z))
-
-  # 2. Functional Part (Exact Integral via J matrix)
-  for(k in seq_along(W$functional_list)) {
-    fd_W  <- W$functional_list[[k]]
-    fd_xi <- xi$functional_list[[k]]
-
-    # Basis Inner Product Matrix: J[i,j] = Int(phi_i * phi_j)
-    J <- fda::inprod(fd_W$basis, fd_W$basis)
-
-    # Score = Coef_W^T * J * Coef_xi
-    # (N x K) * (K x K) * (K x 1) -> (N x 1)
-
-    # Efficient calculation:
-    # We broadcast the (J %*% Coef_xi) vector across all N samples
-    weighted_xi <- J %*% fd_xi$coefs
-
-    # Add to scores (t(coefs) is N x K)
-    scores <- scores + t(fd_W$coefs) %*% weighted_xi
-  }
-
-  return(as.vector(scores))
-}
 ```
@@
   # 2. Get Scores (Rho) -- EXACT
-  #rho_current <- exact_inprod(W_current, xi_current)
-  rho_current <- get_rho(W_current, xi_current)
+  rho_current <- exact_inprod(W_current, xi_current)
 
@@
 ```
-
 ```{r}
 # ==============================================================================
-# STUDY: PLS Geometric Properties (Orthogonality & Relevance)
+# SIMULATION: Annihilation Audit (Using Modified fit.hybridPLS)
 # ==============================================================================
@@
 # ------------------------------------------------------------------------------
-# 1. SETUP
+# 1. HELPER: EXACT INNER PRODUCT
 # ------------------------------------------------------------------------------
+# We use this to audit the result. It effectively replicates get_rho logic
+# but ensures we control the inputs for verification.
+audit_score_magnitude <- function(W, xi, J_list) {
 
-lambda_scenarios <- list(
-  "Scenario A: weak"    = c(0.1, 0.1),         # Pure NIPALS
-  "Scenario B: mixed"  = c(0.1, 5),    # Mixed Smoothness
-  "Scenario C: strong"   = c(5, 5)        # Strong Regularization
-)
+  # 1. Scalar Part
+  # (N x P) %*% (P x 1)
+  scores <- as.matrix(W$Z) %*% t(as.matrix(xi$Z))
 
-n_rep <- 100       # Repetitions
-n_comp <- 6        # Components
-results_ortho <- data.frame() # Store orthogonality results
-results_corr  <- data.frame() # Store correlation results
+  # 2. Functional Part (Matrix Algebra)
+  for(k in seq_along(W$functional_list)) {
+    Theta_j <- t(W$functional_list[[k]]$coefs)
+    gamma_j <- xi$functional_list[[k]]$coefs
+    B_j     <- J_list[[k]]
 
-# Data Generation Function
-generate_robust_data <- function(n_sample = 200, n_scalar = 50) {
-  t1 <- rnorm(n_sample, sd = 10)
-  t2 <- rnorm(n_sample, sd = 5)
-  t3 <- rnorm(n_sample, sd = 2)
-
-  eval_points <- seq(0, 1, length.out = 100)
-  basis <- create.bspline.basis(c(0, 1), 10)
-
-  X1 <- outer(t1, sin(2*pi*eval_points)) + outer(t2, cos(2*pi*eval_points))
-  fd1 <- Data2fd(eval_points, t(X1), basis)
-
-  X2 <- outer(t1, sin(4*pi*eval_points)) + outer(t2, cos(4*pi*eval_points))
-  fd2 <- Data2fd(eval_points, t(X2), basis)
-
-  Z <- matrix(0, n_sample, n_scalar)
-  for(j in 1:n_scalar) Z[,j] <- t1*runif(1) + t3*runif(1) + rnorm(n_sample)
-
-  y <- t1 * 2 - t2 * 1.5 + rnorm(n_sample)
-  W <- predictor_hybrid(Z, list(fd1, fd2), eval_points)
-
-  return(list(W = W, y = y))
+    # Exact Integral: Theta * B * gamma
+    scores <- scores + Theta_j %*% (B_j %*% gamma_j)
   }
 
-# Helper: Compute Inner Product of Two Hybrid Vectors
-# (Required to check orthogonality of xi)
-hybrid_inner_product <- function(h1, h2) {
-  # Scalar dot product
-  val <- sum(h1$Z * h2$Z)
-  # Functional inner products
-  for(k in seq_along(h1$functional_list)) {
-    val <- val + inprod(h1$functional_list[[k]], h2$functional_list[[k]])
-  }
-  return(as.numeric(val))
+  # Return L2 Norm (Magnitude)
+  return(sqrt(sum(scores^2)))
 }
@@
 # ------------------------------------------------------------------------------
-# 2. RUN SIMULATION LOOP
+# 2. DATA GENERATION
 # ------------------------------------------------------------------------------
-message("Starting Extended Simulation...")
-set.seed(999)
+generate_torture_data <- function(n_sample = 100) {
+  t1 <- rnorm(n_sample, sd=10)
+  t2 <- rnorm(n_sample, sd=0.1)
 
-for (scenario_name in names(lambda_scenarios)) {
-  lam_pair <- lambda_scenarios[[scenario_name]]
+  eval_points <- seq(0, 1, length.out=100)
+  basis <- create.bspline.basis(c(0,1), 15)
 
-  for (i in 1:n_rep) {
-    # Generate & Fit
-    data <- generate_robust_data(n_sample = 200)
-    processed <- split_and_normalize.all(data$W, data$y, train_ratio = 0.8)
+  X1 <- outer(t1, sin(2*pi*eval_points)) 
+  fd1 <- Data2fd(eval_points, t(X1), basis)
 
-    fit <- fit.hybridPLS(
-      W = processed$predictor_train, 
-      y = processed$response_train, 
-      n_iter = n_comp, 
-      lambda = lam_pair
-    )
+  X2 <- outer(t2, sin(10*pi*eval_points)) + matrix(rnorm(n_sample*100, sd=0.01), 100, n_sample)
+  fd2 <- Data2fd(eval_points, t(X2), basis)
 
-    # --- METRIC 1: SCORE (Rho) ORTHOGONALITY ---
-    rho_mat <- do.call(cbind, fit$rho)
-    cor_rho <- cor(rho_mat)
-    diag(cor_rho) <- 0
-    max_rho_overlap <- max(abs(cor_rho))
+  Z <- matrix(rnorm(n_sample * 50), n_sample, 50)
+  y <- t1 * 0.5 + t2 * 10 + rnorm(n_sample)
 
-    # --- METRIC 2: DIRECTION (Xi) ORTHOGONALITY ---
-    # We calculate the max pairwise inner product between different weight vectors
-    # Note: xi are normalized, so self-inner-product is 1.
-    xi_list <- fit$xi
-    xi_overlaps <- numeric()
-
-    for(j in 1:(n_comp-1)) {
-      for(k in (j+1):n_comp) {
-        # Dot product between direction j and direction k
-        dp <- hybrid_inner_product(xi_list[[j]], xi_list[[k]])
-        xi_overlaps <- c(xi_overlaps, abs(dp))
-      }
-    }
-    max_xi_overlap <- max(xi_overlaps)
-
-    # Record Orthogonality Stats
-    results_ortho <- rbind(results_ortho, data.frame(
-      Scenario = scenario_name,
-      Repetition = i,
-      Max_Score_Corr = max_rho_overlap,    # Should be ~0
-      Max_Direction_Cos = max_xi_overlap   # Can be > 0
-    ))
-
-    # --- METRIC 3: SCORE vs RESPONSE CORRELATION ---
-    # Does Comp 1 explain Y better than Comp 2?
-    y_vec <- processed$response_train
-    cor_y <- cor(rho_mat, y_vec)
-
-    # Store trajectory for this repetition
-    for(k in 1:n_comp) {
-      results_corr <- rbind(results_corr, data.frame(
-        Scenario = scenario_name,
-        Repetition = i,
-        Component = k,
-        Correlation_with_Y = abs(cor_y[k, 1])
-      ))
-    }
-  }
+  W_init <- predictor_hybrid(Z, list(fd1, fd2), eval_points)
+  return(list(W = W_init, y = y))
 }
@@
 # ------------------------------------------------------------------------------
-# 3. REPORT GENERATION
+# 3. RUN SIMULATION
 # ------------------------------------------------------------------------------
+set.seed(999)
+data <- generate_torture_data(100)
+processed <- split_and_normalize.all(data$W, data$y, train_ratio=0.99)
+W_train <- processed$predictor_train
+y_train <- processed$response_train
 
-# --- TABLE 1: Orthogonality (Scores vs Directions) ---
-summary_ortho <- results_ortho %>%
-  group_by(Scenario) %>%
-  summarise(
-    Score_Orthogonality = mean(Max_Score_Corr),
-    Direction_Overlap   = mean(Max_Direction_Cos)
+# PRE-CALCULATE GRAM MATRICES (Required for audit helper)
+basis_obj <- W_train$functional_list[[1]]$basis
+J_matrix  <- fda::inprod(basis_obj, basis_obj)
+gram_list_audit <- list(J_matrix, J_matrix)
+
+# A. RUN THE FIT (One Shot)
+# ------------------------------------------------------------------------------
+n_comp <- 5
+message("Fitting model...")
+
+# NOTE: We attach gram_list to input W in case your internal functions use it
+W_train$gram_list <- gram_list_audit
+
+fit <- fit.hybridPLS(
+  W = W_train, 
+  y = y_train, 
+  n_iter = n_comp, 
+  lambda = c(10, 0.01)
 )
 
-cat("\n=================================================================\n")
-cat(" TABLE 1: Geometric Properties (Scores vs Directions)\n")
-cat("=================================================================\n")
-cat("NOTE: 'Score' should be 0 (Orthogonal). 'Direction' can be > 0.\n\n")
-print(summary_ortho)
+# B. AUDIT THE STORED OBJECTS
+# ------------------------------------------------------------------------------
+message("Auditing stored W and Xi objects...")
 
-# --- VISUALIZATION: Relevance Decay ---
-# We want to see if correlation drops as component index increases
+results_df <- data.frame()
 
-summary_corr <- results_corr %>%
-  group_by(Scenario, Component) %>%
-  summarise(
-    Mean_Corr = mean(Correlation_with_Y),
-    SD_Corr = sd(Correlation_with_Y)
-  )
+for(l in 1:n_comp) {
 
-p_decay <- ggplot(summary_corr, aes(x = Component, y = Mean_Corr, color = Scenario)) +
-  geom_line(size = 1) +
-  geom_point(size = 2) +
-  geom_errorbar(aes(ymin = Mean_Corr - SD_Corr, ymax = Mean_Corr + SD_Corr), width = 0.2) +
-  labs(title = "Predictive Relevance Decay",
-       subtitle = "Correlation between PLS Scores and Response Y",
-       y = "|Correlation(Score, Y)|",
-       x = "Component Index") +
-  theme_bw() +
-  scale_x_continuous(breaks = 1:n_comp)
+  # Retrieve Stored Objects directly from output
+  W_before <- fit$W[[l]]      # Data used to find Component l
+  W_after  <- fit$W[[l + 1]]  # Data AFTER Component l was removed (Stored in l+1)
+  xi_current <- fit$xi[[l]]   # The direction found
 
-print(p_decay)
-```
+  # Check 1: Signal Strength (Should be Large)
+  # < W[l], xi[l] >
+  signal_mag <- get_rho(W_before, xi_current)
 
-```{r}
-# ==============================================================================
-# PLS VERIFICATION: Prediction & Beta Recovery
-# ==============================================================================
+  # Check 2: Annihilation / Leakage (Should be ZERO)
+  # < W[l+1], xi[l] >
+  leakage_mag <- get_rho(W_after, xi_current)
 
-library(fda)
-library(ggplot2)
-library(gridExtra)
-library(FSHybridPLS) # Your package
+  # Log
+  status <- ifelse(leakage_mag < 1e-2, "PASS", "FAIL")
 
-# ------------------------------------------------------------------------------
-# 1. GENERATE TRUTH (Linear Model)
-# ------------------------------------------------------------------------------
-generate_regression_truth <- function(n_sample = 200, n_eval = 100, noise_sd = 0.5) {
+  results_df <- rbind(results_df, data.frame(
+    Iteration = l,
+    Signal_Strength = signal_mag,
+    Residual_Leakage = leakage_mag,
+    Status = status
+  ))
 
-  eval_points <- seq(0, 1, length.out = n_eval)
-  basis_obj <- create.bspline.basis(c(0, 1), 20)
-
-  # --- A. True Coefficient Function (Beta) ---
-  # A distinct shape: Sine wave with a trend
-  true_beta_vec <- sin(2 * pi * eval_points) + 1.5 * eval_points
-  # Center it (standard practice)
-  true_beta_vec <- true_beta_vec - mean(true_beta_vec)
-
-  # --- B. Functional Predictors (X) ---
-  # Smooth random curves
-  coefs <- matrix(rnorm(20 * n_sample), 20, n_sample)
-  # Smooth the coefficients to make curves realistic
-  smooth_mat <- chol(ar1_cov(20, 0.8))
-  coefs <- t(smooth_mat) %*% coefs
-
-  fd_obj <- fd(coefs, basis_obj)
-  X_vals <- eval.fd(eval_points, fd_obj) # 100 x 200
-
-  # --- C. Response (Y) ---
-  # Y = Integral( X(t) * Beta(t) ) + Noise
-  # Approx integral as dot product * dt
-  dt <- 1 / n_eval
-
-  # Calculate signal
-  # (100 x 200) * (100 x 1) -> broadcasting requires care or loop
-  # Signal = colSums( X * beta ) * dt
-  signal <- colSums(X_vals * true_beta_vec) * dt
-
-  # Add noise
-  y <- signal + rnorm(n_sample, sd = noise_sd)
-
-  # Scalar Z (Noise only, to prove PLS ignores it)
-  Z <- matrix(rnorm(n_sample), n_sample, 1)
-
-  W <- predictor_hybrid(Z, list(fd_obj), eval_points)
-
-  return(list(
-    W = W, y = y, 
-    true_beta = true_beta_vec,
-    eval_points = eval_points
-  ))
+  cat(sprintf("Comp %d: Signal=%.2e | Leakage=%.2e | %s\n", 
+              l, signal_mag, leakage_mag, status))
 }
@@
 # ------------------------------------------------------------------------------
-# 2. RUN SIMULATION
+# 4. VISUALIZATION
 # ------------------------------------------------------------------------------
-set.seed(42)
-# Generate
-sim_data <- generate_regression_truth(n_sample = 200, noise_sd = 0.1)
+cat("\n=======================================================\n")
+cat("      FIT OBJECT INTEGRITY AUDIT \n")
+cat("=======================================================\n")
+print(results_df)
 
-# Split (Train/Test)
-processed <- split_and_normalize.all(sim_data$W, sim_data$y, train_ratio = 0.7)
+df_long <- tidyr::pivot_longer(results_df, cols = c("Signal_Strength", "Residual_Leakage"))
 
-# Fit PLS
-# Using 4 components (should be enough to capture the beta shape)
-# Lambda = 0 ensures we test the core algorithm, not the penalty
-fit <- fit.hybridPLS(
-  W = processed$predictor_train, 
-  y = processed$response_train, 
-  n_iter = 4, 
-  lambda = c(0),
-  validation_data = list(W_test = processed$predictor_test, y_test = processed$response_test)
-)
-
-# ------------------------------------------------------------------------------
-# 3. VERIFICATION PLOTS
-# ------------------------------------------------------------------------------
-
-# --- A. Prediction Check (Test Set) ---
-# Reconstruct Y_pred for Test Set using the Final Beta (Comp 4)
-beta_final <- fit$beta[[4]]
-y_pred <- inprod.predictor_hybrid(processed$predictor_test, beta_final)
-y_true <- processed$response_test
-
-r2_test <- 1 - sum((y_true - y_pred)^2) / sum((y_true - mean(y_true))^2)
-
-df_pred <- data.frame(Observed = y_true, Predicted = y_pred)
-
-p1 <- ggplot(df_pred, aes(x = Observed, y = Predicted)) +
-  geom_point(alpha = 0.6, color = "blue") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
-  labs(title = paste0("Prediction Accuracy (R2 = ", round(r2_test, 3), ")"),
-       subtitle = "Points should lie on the red diagonal") +
-  theme_bw()
-
-# --- B. Beta Recovery Check ---
-# Extract estimated functional beta
-beta_est_fd <- fit$beta[[4]]$functional_list[[1]]
-beta_est_vec <- eval.fd(sim_data$eval_points, beta_est_fd)
-
-# Normalize both to compare SHAPE (scale might differ due to normalization)
-scale_vec <- function(x) as.vector((x - mean(x)) / sd(x))
-
-df_beta <- data.frame(
-  Time = sim_data$eval_points,
-  True = scale_vec(sim_data$true_beta),
-  Estimated = scale_vec(beta_est_vec)
-)
-
-beta_corr <- cor(df_beta$True, df_beta$Estimated)
-
-p2 <- ggplot(df_beta, aes(x = Time)) +
-  geom_line(aes(y = True, color = "True Beta"), linewidth = 1.2, linetype = "dashed") +
-  geom_line(aes(y = Estimated, color = "PLS Estimate"), linewidth = 1) +
-  scale_color_manual(values = c("True Beta" = "black", "PLS Estimate" = "red")) +
-  labs(title = paste0("Beta Reconstruction (Corr = ", round(beta_corr, 3), ")"),
-       subtitle = "Red line should match Black dashed line") +
-  theme_bw() + theme(legend.position = "bottom")
-
-# ------------------------------------------------------------------------------
-# 4. RESULTS
-# ------------------------------------------------------------------------------
-grid.arrange(p1, p2, nrow = 1)
-
-cat("\n========================================\n")
-cat("      PLS REGRESSION VERIFICATION       \n")
-cat("========================================\n")
-cat(sprintf("1. Test R-Squared:      %.4f  [%s]\n", r2_test, ifelse(r2_test > 0.9, "PASS", "FAIL")))
-cat(sprintf("2. Beta Shape Corr:     %.4f  [%s]\n", beta_corr, ifelse(beta_corr > 0.95, "PASS", "FAIL")))
-
-if(r2_test > 0.9 && beta_corr > 0.95) {
-  cat("\nCONCLUSION: ✅ PLS Works. It predicts accurately and learns the correct shape.\n")
-} else {
-  cat("\nCONCLUSION: ❌ Something is wrong.\n")
-}
+ggplot(df_long, aes(x=factor(Iteration), y=value, fill=name)) +
+  geom_bar(stat="identity", position=position_dodge()) +
+  scale_y_continuous(trans="log10") +
+  labs(title="Annihilation Audit (Using fit.hybridPLS Output)",
+       subtitle="Verifying orthogonality of stored W objects against stored Xi directions",
+       y="Projection Magnitude (Log10)",
+       x="Component") +
+  theme_minimal() +
+  scale_fill_manual(values=c("firebrick", "steelblue")) +
+  geom_hline(yintercept=1e-10, linetype="dashed")
 ```
-
-```{r}
-# ==============================================================================
-# PLS VERIFICATION: Prediction & Beta Recovery
-# ==============================================================================
-
-library(fda)
-library(ggplot2)
-library(gridExtra)
-library(FSHybridPLS) # Your package
-
-# ------------------------------------------------------------------------------
-# 1. GENERATE TRUTH (Linear Model)
-# ------------------------------------------------------------------------------
-generate_regression_truth <- function(n_sample = 200, n_eval = 100, noise_sd = 0.01) {
-
-  eval_points <- seq(0, 1, length.out = n_eval)
-  basis_obj <- create.bspline.basis(c(0, 1), 20)
-
-  # --- A. True Coefficient Function (Beta) ---
-  # A distinct shape: Sine wave with a trend
-  true_beta_vec <- sin(2 * pi * eval_points) + 1.5 * eval_points
-  # Center it (standard practice)
-  true_beta_vec <- true_beta_vec - mean(true_beta_vec)
-
-  # --- B. Functional Predictors (X) ---
-  # Smooth random curves
-  coefs <- matrix(rnorm(20 * n_sample), 20, n_sample)
-  # Smooth the coefficients to make curves realistic
-  smooth_mat <- chol(ar1_cov(20, 0.8))
-  coefs <- t(smooth_mat) %*% coefs
-
-  fd_obj <- fd(coefs, basis_obj)
-  X_vals <- eval.fd(eval_points, fd_obj) # 100 x 200
-
-  # --- C. Response (Y) ---
-  # Y = Integral( X(t) * Beta(t) ) + Noise
-  # Approx integral as dot product * dt
-  dt <- 1 / n_eval
-
-  # Calculate signal
-  # (100 x 200) * (100 x 1) -> broadcasting requires care or loop
-  # Signal = colSums( X * beta ) * dt
-  signal <- colSums(X_vals * true_beta_vec) * dt
-
-  # Add noise
-  y <- signal + rnorm(n_sample, sd = noise_sd)
-
-  # Scalar Z (Noise only, to prove PLS ignores it)
-  Z <- matrix(rnorm(n_sample), n_sample, 1)
-
-  W <- predictor_hybrid(Z, list(fd_obj), eval_points)
-
-  return(list(
-    W = W, y = y, 
-    true_beta = true_beta_vec,
-    eval_points = eval_points
-  ))
-}
-
-# ------------------------------------------------------------------------------
-# 2. RUN SIMULATION
-# ------------------------------------------------------------------------------
-set.seed(42)
-# Generate
-sim_data <- generate_regression_truth(n_sample = 200, noise_sd = 0.01)
-
-# Split (Train/Test)
-processed <- split_and_normalize.all(sim_data$W, sim_data$y, train_ratio = 0.7)
-
-# Fit PLS
-# Using 4 components (should be enough to capture the beta shape)
-# Lambda = 0 ensures we test the core algorithm, not the penalty
-fit <- fit.hybridPLS(
-  W = processed$predictor_train, 
-  y = processed$response_train, 
-  n_iter = 4, 
-  lambda = c(0),
-  validation_data = list(W_test = processed$predictor_test, y_test = processed$response_test)
-)
-
-# ------------------------------------------------------------------------------
-# 3. VERIFICATION PLOTS
-# ------------------------------------------------------------------------------
-
-# --- A. Prediction Check (Test Set) ---
-# Reconstruct Y_pred for Test Set using the Final Beta (Comp 4)
-beta_final <- fit$beta[[4]]
-y_pred <- inprod.predictor_hybrid(processed$predictor_test, beta_final)
-y_true <- processed$response_test
-
-r2_test <- 1 - sum((y_true - y_pred)^2) / sum((y_true - mean(y_true))^2)
-
-df_pred <- data.frame(Observed = y_true, Predicted = y_pred)
-
-p1 <- ggplot(df_pred, aes(x = Observed, y = Predicted)) +
-  geom_point(alpha = 0.6, color = "blue") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
-  labs(title = paste0("Prediction Accuracy (R2 = ", round(r2_test, 3), ")"),
-       subtitle = "Points should lie on the red diagonal") +
-  theme_bw()
-
-# --- B. Beta Recovery Check ---
-# Extract estimated functional beta
-beta_est_fd <- fit$beta[[4]]$functional_list[[1]]
-beta_est_vec <- eval.fd(sim_data$eval_points, beta_est_fd)
-
-# Normalize both to compare SHAPE (scale might differ due to normalization)
-scale_vec <- function(x) as.vector((x - mean(x)) / sd(x))
-
-df_beta <- data.frame(
-  Time = sim_data$eval_points,
-  True = scale_vec(sim_data$true_beta),
-  Estimated = scale_vec(beta_est_vec)
-)
-
-beta_corr <- cor(df_beta$True, df_beta$Estimated)
-
-p2 <- ggplot(df_beta, aes(x = Time)) +
-  geom_line(aes(y = True, color = "True Beta"), linewidth = 1.2, linetype = "dashed") +
-  geom_line(aes(y = Estimated, color = "PLS Estimate"), linewidth = 1) +
-  scale_color_manual(values = c("True Beta" = "black", "PLS Estimate" = "red")) +
-  labs(title = paste0("Beta Reconstruction (Corr = ", round(beta_corr, 3), ")"),
-       subtitle = "Red line should match Black dashed line") +
-  theme_bw() + theme(legend.position = "bottom")
-
-# ------------------------------------------------------------------------------
-# 4. RESULTS
-# ------------------------------------------------------------------------------
-grid.arrange(p1, p2, nrow = 1)
-
-cat("\n========================================\n")
-cat("      PLS REGRESSION VERIFICATION       \n")
-cat("========================================\n")
-cat(sprintf("1. Test R-Squared:      %.4f  [%s]\n", r2_test, ifelse(r2_test > 0.9, "PASS", "FAIL")))
-cat(sprintf("2. Beta Shape Corr:     %.4f  [%s]\n", beta_corr, ifelse(beta_corr > 0.95, "PASS", "FAIL")))
-
-if(r2_test > 0.9 && beta_corr > 0.95) {
-  cat("\nCONCLUSION: ✅ PLS Works. It predicts accurately and learns the correct shape.\n")
-} else {
-  cat("\nCONCLUSION: ❌ Something is wrong.\n")
-}
-```
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-## is normalization hurtful?
-```{r}
-# ==============================================================================
-# DIAGNOSTIC: Is Normalization Killing PLS?
-# ==============================================================================
-
-library(fda)
-library(Matrix)
-library(ggplot2)
-
-# 1. GENERATE LATENT DATA (Signal defined by Variance)
-# ------------------------------------------------------------------------------
-# We create 2 components:
-# Comp 1: Huge Variance (SD=10) -> Should be found FIRST
-# Comp 2: Small Variance (SD=2) -> Should be found SECOND
-generate_variance_signal <- function(n_sample = 200) {
-  t1 <- rnorm(n_sample, sd = 10)
-  t2 <- rnorm(n_sample, sd = 2)
-
-  # Orthogonalize exactly
-  T_mat <- svd(cbind(t1, t2))$u %*% diag(c(10, 2))
-
-  # Functional Predictor X (Evaluation points 0 to 1)
-  eval_points <- seq(0, 1, length.out=100)
-  shape1 <- sin(2*pi*eval_points)
-  shape2 <- cos(2*pi*eval_points)
-
-  X <- outer(T_mat[,1], shape1) + outer(T_mat[,2], shape2) + rnorm(n_sample*100, sd=0.1)
-
-  # Scalar Predictor Z (Just noise for now, to isolate Functional issue)
-  Z <- matrix(rnorm(n_sample * 5), n_sample, 5)
-
-  # Response Y (Driven by T1 mostly)
-  y <- T_mat[,1] * 1 + T_mat[,2] * 1 + rnorm(n_sample, sd=0.1)
-
-  # Create Objects
-  basis_obj <- create.bspline.basis(c(0, 1), 20)
-  fd_obj <- Data2fd(eval_points, t(X), basis_obj)
-
-  W <- predictor_hybrid(Z, list(fd_obj), eval_points)
-
-  return(list(W = W, y = y, true_scores = T_mat))
-}
-
-set.seed(123)
-data <- generate_variance_signal(200)
-
-# ==============================================================================
-# SCENARIO A: RAW DATA (Preserve Variance)
-# ==============================================================================
-message("\n--- Running Scenario A: RAW DATA (Variance Preserved) ---")
-
-# Manual Centering (Required for PLS, but NO scaling)
-y_centered <- data$y - mean(data$y)
-W_centered <- data$W
-# (Assuming your PLS centers internally or we can pass centered data. 
-#  For strictness, we assume Z is roughly centered by generation.)
-
-fit_raw <- fit.hybridPLS(
-  W = W_centered, 
-  y = y_centered, 
-  n_iter = 2, 
-  lambda = c(0) # No penalty to isolate normalization issue
-)
-
-rho_raw <- do.call(cbind, fit_raw$rho)
-cor_raw <- cor(rho_raw, data$true_scores)
-print("Correlation (Estimated vs True):")
-print(round(cor_raw, 3))
-
-# ==============================================================================
-# SCENARIO B: NORMALIZED DATA (Variance Destroyed)
-# ==============================================================================
-message("\n--- Running Scenario B: NORMALIZED DATA (Variance = 1) ---")
-
-# Run your normalization pipeline
-# We use train_ratio = 0.99 just to keep most data for the check
-processed <- split_and_normalize.all(data$W, data$y, train_ratio = 0.99)
-
-# Extract the TRUE scores corresponding to the training set indices
-train_idx <- processed$details$split_indices$train
-true_scores_subset <- data$true_scores[train_idx, ]
-
-fit_norm <- fit.hybridPLS(
-  W = processed$predictor_train, 
-  y = processed$response_train, 
-  n_iter = 2, 
-  lambda = c(0)
-)
-
-rho_norm <- do.call(cbind, fit_norm$rho)
-cor_norm <- cor(rho_norm, true_scores_subset)
-print("Correlation (Estimated vs True):")
-print(round(cor_norm, 3))
-
-# ==============================================================================
-# RESULT INTERPRETATION
-# ==============================================================================
-# Look at the diagonal of the correlation matrices.
-# Ideally: [1,1] > 0.9 (Comp 1 found), [2,2] > 0.9 (Comp 2 found).
-
-score_1_raw <- abs(cor_raw[1,1])
-score_1_norm <- abs(cor_norm[1,1])
-
-cat("\n========================================\n")
-cat("          DIAGNOSTIC RESULTS            \n")
-cat("========================================\n")
-cat(paste0("Scenario A (Raw) Score 1 Recovery: ", round(score_1_raw, 3), "\n"))
-cat(paste0("Scenario B (Norm) Score 1 Recovery: ", round(score_1_norm, 3), "\n"))
-
-if (score_1_raw > 0.9 && score_1_norm < 0.9) {
-  cat("\nCONCLUSION: 🚨 Normalization is the problem.\n")
-  cat("By forcing unit variance, 'split_and_normalize.all' destroys the \n")
-  cat("variance structure that PLS uses to identify the primary component.\n")
-} else if (score_1_raw < 0.9) {
-  cat("\nCONCLUSION: ⚠️  The Algorithm is the problem.\n")
-  cat("Even with raw data, PLS failed to find the latent component.\n")
-} else {
-  cat("\nCONCLUSION: ✅ Both methods worked? (Check if simulation noise was too low)\n")
-}
-```
-
-##
-
-```{r}
-
-# ==============================================================================
-# HYBRID PLS VERIFICATION: Latent Factor & Coefficient Recovery
-# ==============================================================================
-
-library(fda)
-library(ggplot2)
-library(gridExtra) # For arranging plots
-library(FSHybridPLS) # Your package
-
-# ------------------------------------------------------------------------------
-# 1. DATA GENERATION: The "Ground Truth"
-# ------------------------------------------------------------------------------
-generate_verification_data <- function(n_sample = 200, n_eval = 100) {
-
-  eval_points <- seq(0, 1, length.out = n_eval)
-
-  # --- A. Latent Scores (Truth) ---
-  # We create 2 orthogonal components with distinct variances
-  # Comp 1: High Variance (SD=10) -> The primary signal
-  # Comp 2: Lower Variance (SD=4) -> The secondary signal
-  set.seed(123)
-  t1 <- rnorm(n_sample, sd = 10)
-  t2 <- rnorm(n_sample, sd = 4)
-  # Force exact orthogonality for clean testing
-  T_mat <- svd(cbind(t1, t2))$u %*% diag(c(10, 4))
-
-  # --- B. Loadings (Shapes) ---
-  # Shape 1: Low frequency (Sine wave)
-  # Shape 2: High frequency (Cosine wave)
-  shape1 <- sin(2 * pi * eval_points)
-  shape2 <- cos(4 * pi * eval_points)
-
-  # --- C. Functional Predictor X ---
-  # X = T * P' + Noise
-  X_clean <- outer(T_mat[,1], shape1) + outer(T_mat[,2], shape2)
-  X_noise <- matrix(rnorm(n_sample * n_eval, sd = 0.5), n_sample, n_eval)
-  X <- X_clean + X_noise
-
-  # --- D. Response Y ---
-  # Y depends on both components: Y = 1*t1 - 2*t2 + Noise
-  # This implies the TRUE BETA shape is roughly: (1*shape1) - (2*shape2)
-  y <- T_mat[,1] * 1 + T_mat[,2] * (-2) + rnorm(n_sample, sd = 1)
-
-  # Calculate True Beta Shape (Theoretical)
-  # (Note: Normalized to SD=1 for shape comparison)
-  true_beta_raw <- (1 * shape1) + (-2 * shape2)
-  true_beta_norm <- (true_beta_raw - mean(true_beta_raw))/sd(true_beta_raw)
-
-  # --- E. Objects ---
-  basis_obj <- create.bspline.basis(c(0, 1), 20)
-  fd_obj <- Data2fd(eval_points, t(X), basis_obj)
-
-  # Dummy scalar (not used for signal, just to satisfy object structure)
-  Z <- matrix(rnorm(n_sample), n_sample, 1)
-
-  W <- predictor_hybrid(Z, list(fd_obj), eval_points)
-
-  return(list(
-    W = W, y = y, 
-    true_scores = T_mat, 
-    true_beta = true_beta_norm,
-    eval_points = eval_points
-  ))
-}
-
-# ------------------------------------------------------------------------------
-# 2. EXECUTION
-# ------------------------------------------------------------------------------
-message("Generating Data...")
-sim_data <- generate_verification_data(n_sample = 200)
-
-message("Processing Data (Split & Normalize)...")
-# We use a large training ratio to ensure stable estimation for verification
-processed <- split_and_normalize.all(sim_data$W, sim_data$y, train_ratio = 0.8)
-
-# Extract True Scores corresponding to the Training Set
-train_idx <- processed$details$split_indices$train
-true_scores_train <- sim_data$true_scores[train_idx, ]
-
-message("Fitting Hybrid PLS...")
-# Fit with 4 components (we expect the first 2 to capture the signal)
-fit <- fit.hybridPLS(
-  W = processed$predictor_train, 
-  y = processed$response_train, 
-  n_iter = 4, 
-  lambda = c(0) # Small penalty for smoothness
-)
-
-# ------------------------------------------------------------------------------
-# 3. VERIFICATION & PLOTTING
-# ------------------------------------------------------------------------------
-
-# --- TEST 1: Latent Score Recovery ---
-# Extract Estimated Scores (Rho)
-est_scores <- do.call(cbind, fit$rho)
-
-# Calculate Correlations
-cor_comp1 <- cor(est_scores[,1], true_scores_train[,1])
-cor_comp2 <- cor(est_scores[,2], true_scores_train[,2])
-
-# Plotting Score Recovery
-df_scores <- data.frame(
-  True_1 = true_scores_train[,1],
-  Est_1  = est_scores[,1],
-  True_2 = true_scores_train[,2],
-  Est_2  = est_scores[,2]
-)
-
-# Scale Estimated scores to match True scale for visualization overlap
-df_scores$Est_1 <- df_scores$Est_1 * sign(cor_comp1) * (sd(df_scores$True_1)/sd(df_scores$Est_1))
-df_scores$Est_2 <- df_scores$Est_2 * sign(cor_comp2) * (sd(df_scores$True_2)/sd(df_scores$Est_2))
-
-p1 <- ggplot(df_scores, aes(x = True_1, y = Est_1)) +
-  geom_point(alpha = 0.6, color = "blue") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  labs(title = paste0("Component 1 Recovery\nCorr: ", round(abs(cor_comp1), 4)),
-       x = "True Latent Score", y = "Estimated PLS Score") +
-  theme_bw()
-
-p2 <- ggplot(df_scores, aes(x = True_2, y = Est_2)) +
-  geom_point(alpha = 0.6, color = "darkgreen") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  labs(title = paste0("Component 2 Recovery\nCorr: ", round(abs(cor_comp2), 4)),
-       x = "True Latent Score", y = "Estimated PLS Score") +
-  theme_bw()
-
-# --- TEST 2: Beta Coefficient Recovery (CORRECTED) ---
-
-# Extract the estimated Beta Curve (from the final cumulative beta)
-beta_est_fd <- fit$beta[[2]]$functional_list[[1]] 
-beta_est_vals <- eval.fd(sim_data$eval_points, beta_est_fd)
-
-# Normalize for Shape Comparison (Mean 0, SD 1)
-# CRITICAL FIX: use as.vector() to ensure it is a simple vector, not a matrix
-beta_est_norm <- as.vector((beta_est_vals - mean(beta_est_vals)) / sd(beta_est_vals))
-
-df_beta <- data.frame(
-  Time = sim_data$eval_points,
-  True = as.vector(sim_data$true_beta),
-  Estimated = beta_est_norm
-)
-
-p3 <- ggplot(df_beta, aes(x = Time)) +
-  geom_line(aes(y = True, color = "True Beta Shape"), linewidth = 1.2, linetype = "dashed") +
-  geom_line(aes(y = Estimated, color = "Estimated Beta"), linewidth = 1) +
-  scale_color_manual(values = c("True Beta Shape" = "black", "Estimated Beta" = "red")) +
-  labs(title = "Regression Coefficient (Beta) Recovery",
-       subtitle = "Shapes should overlap (Normalized)",
-       y = "Normalized Coefficient Value") +
-  theme_bw() + theme(legend.position = "bottom")
-
-# ------------------------------------------------------------------------------
-# 4. PRINT RESULTS
-# ------------------------------------------------------------------------------
-grid.arrange(p1, p2, p3, nrow = 2, layout_matrix = rbind(c(1, 2), c(3, 3)))
-
-cat("\n============================================\n")
-cat("      PLS ALGORITHM VERIFICATION RESULTS      \n")
-cat("============================================\n")
-cat(paste0("1. Component 1 Correlation:  ", round(abs(cor_comp1), 4), 
-           ifelse(abs(cor_comp1) > 0.9, "  [PASS]", "  [FAIL]"), "\n"))
-cat(paste0("2. Component 2 Correlation:  ", round(abs(cor_comp2), 4), 
-           ifelse(abs(cor_comp2) > 0.8, "  [PASS]", "  [FAIL]"), "\n"))
-
-# Beta Shape Correlation
-beta_shape_cor <- cor(df_beta$True, df_beta$Estimated)
-cat(paste0("3. Beta Shape Correlation:   ", round(beta_shape_cor, 4), 
-           ifelse(beta_shape_cor > 0.9, "  [PASS]", "  [FAIL]"), "\n"))
-
-```
-
-```{r}
-# ==============================================================================
-# DEBUG: BARE METAL PLS (No Penalty)
-# ==============================================================================
-
-# 1. GENERATE DATA (Same as before)
-sim_data <- generate_verification_data(n_sample = 200)
-processed <- split_and_normalize.all(sim_data$W, sim_data$y, train_ratio = 0.8)
-train_idx <- processed$details$split_indices$train
-true_scores_train <- sim_data$true_scores[train_idx, ]
-
-# 2. FIT WITH LAMBDA = 0 (Pure NIPALS)
-#    We increase iterations to 5 to see if it eventually finds the signal
-fit_debug <- fit.hybridPLS(
-  W = processed$predictor_train, 
-  y = processed$response_train, 
-  n_iter = 5, 
-  lambda = c(0) # <--- CRITICAL: No Smoothing
-)
-
-# 3. CHECK SCORES
-est_scores <- do.call(cbind, fit_debug$rho)
-cor_comp1 <- cor(est_scores[,1], true_scores_train[,1])
-cor_comp2 <- cor(est_scores[,2], true_scores_train[,2])
-
-# 4. CHECK BETA
-beta_est_fd <- fit_debug$beta[[2]]$functional_list[[1]] 
-beta_vals <- eval.fd(sim_data$eval_points, beta_est_fd)
-beta_est_norm <- as.vector((beta_vals - mean(beta_vals)) / sd(beta_vals))
-beta_cor <- cor(as.vector(sim_data$true_beta), beta_est_norm)
-
-cat("\n--- DEBUG RESULTS (Lambda = 0) ---\n")
-cat(paste0("1. Score 1 Correlation: ", round(abs(cor_comp1), 4), "\n"))
-cat(paste0("2. Score 2 Correlation: ", round(abs(cor_comp2), 4), "\n"))
-cat(paste0("3. Beta Correlation:    ", round(beta_cor, 4), "\n"))
-
-# 5. CHECK PREDICTION (Is the model actually predicting Y?)
-#    Reconstruct Y_hat on training data manually using the scores
-#    Y_hat = Sum( rho * nu )
-y_hat <- rep(0, length(processed$response_train))
-for(l in 1:2) {
-   # nu is the regression coef of Y on Rho
-   nu_l <- sum(processed$response_train * fit_debug$rho[[l]]) / sum(fit_debug$rho[[l]]^2)
-   y_hat <- y_hat + fit_debug$rho[[l]] * nu_l
-}
-r2 <- 1 - sum((processed$response_train - y_hat)^2) / sum((processed$response_train - mean(processed$response_train))^2)
-cat(paste0("4. Training R-Squared:    ", round(r2, 4), "\n"))
-```
-
-```{r}
-#' Fit Hybrid Penalized PLS with Optional Validation & Debugging
-#'
-#' Runs the iterative PLS algorithm.
-#'
-#' @param W Initial `predictor_hybrid` object (Training).
-#' @param y Numeric vector of response values (Training).
-#' @param n_iter Integer, number of components to extract.
-#' @param lambda Numeric vector of smoothing parameters.
-#' @param validation_data (Optional) List containing `W_test` and `y_test`.
-#' @param debug_data (Optional) List containing `true_scores` (matrix), `true_shape` (vector), and `eval_points` (vector) for deflation checking.
-#'
-#' @return A list containing the model (rho, xi, beta) and optional `validation_rmse`.
-#' @export
-fit.hybridPLS <- function(W, y, n_iter, lambda, validation_data = NULL, debug_data = NULL) {
-  # 1. Initialize storage
-  W_now <- rho <- xi <- delta <- nu <- iota <- beta <- list()
-  validation_rmse <- numeric(n_iter)
-
-  # 2. Initialize current state
-  W_now[[1]] <- W
-  y_now <- y
-
-  # 3. Main PLS Loop
-  for (l in 1:n_iter) {
-    # --- Step A: Weight Direction (xi) ---
-    xi[[l]] <- get_xi_hat_linear_pen(W_now[[l]], y_now, lambda)
-
-    # --- Step B: Scores (rho) ---
-    rho[[l]] <- inprod.predictor_hybrid(W_now[[l]], xi[[l]])
-
-    # --- Step C: Loadings (delta, nu) ---
-    delta[[l]] <- get_delta(W_now[[l]], rho[[l]])
-    nu[[l]] <- get_nu(y_now, rho[[l]])
-
-    # --- Step D: Deflation ---
-    W_now[[l + 1]] <- residualize_predictor(W_now[[l]], rho[[l]], delta[[l]])
-    y_now <- residualize_y(y_now, rho[[l]], nu[[l]])
-
-    # --- DEBUG CHECK: Is the Ghost of Component 1 still haunting us? ---
-    if (!is.null(debug_data) && l == 1) {
-      # 1. Extract the residual functional data (Matrix: Time x Sample)
-      resid_fd <- W_now[[l + 1]]$functional_list[[1]] 
-      resid_vals <- eval.fd(debug_data$eval_points, resid_fd)
-
-      # 2. Project residuals onto the Known True Shape of Component 1
-      #    We weight the time points by the shape to see if that signal remains.
-      #    (resid_vals * shape) broadcasts the shape vector across columns
-      projected_signal <- colSums(resid_vals * debug_data$true_shape)
-
-      # 3. Check correlation with True Score 1
-      ghost_correlation <- cor(projected_signal, debug_data$true_scores[,1])
-
-      cat(sprintf("\n[DEBUG l=%d] Deflation Check:\n", l))
-      cat(sprintf("  Correlation w/ True Score 1 after deflation: %.5f (Target: 0.00)\n", ghost_correlation))
-
-      if(abs(ghost_correlation) > 0.05) {
-        warning("  CRITICAL FAILURE: Deflation did not remove Component 1.")
-      } else {
-        cat("  SUCCESS: Component 1 successfully removed.\n")
-      }
-    }
-
-    # --- Step E: Cumulative Coefficient (Beta) ---
-    iota[[l]] <- xi[[l]]
-
-    if (l == 1) {
-      beta[[l]] <- scalar_mul.predictor_hybrid(iota[[l]], nu[[l]])
-    } else {
-      for (u in 1:(l - 1)) {
-        adjustment <- inprod.predictor_hybrid(delta[[u]], xi[[l]])
-        iota[[l]] <- subtr.predictor_hybrid(iota[[l]], iota[[u]], adjustment)
-      }
-      beta[[l]] <- add.predictor_hybrid(beta[[l - 1]], iota[[l]], nu[[l]])
-    }
-
-    # --- Step F: Validation (Optional) ---
-    if (!is.null(validation_data)) {
-      # Predict on test set using the current cumulative beta
-      y_pred_test <- inprod.predictor_hybrid(validation_data$W_test, beta[[l]])
-
-      # Compute RMSE
-      validation_rmse[l] <- sqrt(mean((validation_data$y_test - y_pred_test)^2))
-    }
-  }
-
-  return(list(
-    rho = rho,
-    xi = xi,
-    beta = beta,
-    validation_rmse = if (!is.null(validation_data)) validation_rmse else NULL,
-    W_residuals = W_now # Helpful for external debugging if needed
-  ))
-}
-```
-
-```{r}
-# ==============================================================================
-# SANITY CHECK: NOISELESS PLS VERIFICATION
-# ==============================================================================
-
-library(fda)
-library(ggplot2)
-library(gridExtra)
-library(FSHybridPLS)
-
-# ------------------------------------------------------------------------------
-# 1. GENERATE NOISELESS DATA
-# ------------------------------------------------------------------------------
-generate_noiseless_data <- function(n_sample = 100, n_eval = 100) {
-
-  eval_points <- seq(0, 1, length.out = n_eval)
-  basis_obj <- create.bspline.basis(c(0, 1), 20)
-
-  # --- A. Latent Scores (T) ---
-  # Deterministic orthogonal scores to guarantee separation
-  # T1: Linear trend
-  # T2: Quadratic trend (Orthogonalized against T1)
-  t1 <- seq(-10, 10, length.out = n_sample)
-  t2_raw <- t1^2
-  # Gram-Schmidt Orthogonalization of t2 against t1
-  t2 <- t2_raw - (sum(t2_raw * t1) / sum(t1^2)) * t1
-  t2 <- t2 / sd(t2) * 5 # Scale to SD=5
-
-  T_mat <- cbind(t1, t2)
-
-  # --- B. Loadings (P) ---
-  shape1 <- sin(2 * pi * eval_points)
-  shape2 <- cos(2 * pi * eval_points)
-
-  # --- C. Predictors (X = T*P') ---
-  # NO NOISE ADDED
-  X_clean <- outer(T_mat[,1], shape1) + outer(T_mat[,2], shape2)
-
-  fd_obj <- Data2fd(eval_points, t(X_clean), basis_obj)
-
-  # Scalar Z (Perfectly correlated with T1 to check scalar handling)
-  Z <- matrix(T_mat[,1] * 0.5, n_sample, 1)
-
-  # --- D. Response (Y = T*q) ---
-  # NO NOISE ADDED
-  y <- T_mat[,1] * 1 - T_mat[,2] * 2
-
-  # True Beta Shape (Normalized)
-  true_beta_raw <- (1 * shape1) - (2 * shape2)
-  true_beta <- (true_beta_raw - mean(true_beta_raw)) / sd(true_beta_raw)
-
-  W <- predictor_hybrid(Z, list(fd_obj), eval_points)
-
-  return(list(
-    W = W, y = y, 
-    true_scores = T_mat, 
-    true_beta = true_beta,
-    eval_points = eval_points
-  ))
-}
-
-# ------------------------------------------------------------------------------
-# 2. RUN SIMULATION
-# ------------------------------------------------------------------------------
-message("Generating Noiseless Data...")
-sim_data <- generate_noiseless_data(n_sample = 100)
-
-# 1. Split/Normalize (Train Ratio 0.8)
-processed <- split_and_normalize.all(sim_data$W, sim_data$y, train_ratio = 0.8)
-
-# 2. Extract Matching Truth
-train_idx <- processed$details$split_indices$train
-true_scores_train <- sim_data$true_scores[train_idx, ]
-
-# 3. Setup Debug Pack
-debug_pack <- list(
-  true_scores = true_scores_train,
-  true_shape = sin(2 * pi * sim_data$eval_points), # Shape of Comp 1
-  eval_points = sim_data$eval_points
-)
-
-message("Fitting PLS (Lambda=0)...")
-fit <- fit.hybridPLS(
-  W = processed$predictor_train, 
-  y = processed$response_train, 
-  n_iter = 3, 
-  lambda = c(0), # Pure NIPALS
-  debug_data = debug_pack
-)
-
-message("Fitting PLS (Sanity Matrix Implementation)...")
-
-# CRITICAL: Pass raw objects, not the hybrid list, or extract them carefully
-# The sanity function expects the hybrid W object and vector y
-fit_sanity <- fit.hybridPLS.sanity(
-  W = processed$predictor_train, 
-  y = processed$response_train, 
-  n_iter = 2
-)
-
-# ... (Now update the verification metrics to use fit_sanity) ...
-
-# 1. Scores
-# (Rest of the correlation code remains the same)
-
-# 2. Beta
-# (Rest of the beta evaluation code remains the same)
-
-# ------------------------------------------------------------------------------
-# 3. VERIFICATION METRICS
-# ------------------------------------------------------------------------------
-est_scores <- do.call(cbind, fit_sanity$rho)
-
-# Correlations
-c1 <- abs(cor(est_scores[,1], true_scores_train[,1]))
-c2 <- abs(cor(est_scores[,2], true_scores_train[,2]))
-
-# Beta Shape Recovery
-beta_est_fd <- fit_sanity$beta_fd
-beta_vals <- eval.fd(sim_data$eval_points, beta_est_fd)
-beta_est_norm <- as.vector((beta_vals - mean(beta_vals)) / sd(beta_vals))
-c_beta <- cor(sim_data$true_beta, beta_est_norm)
-
-# Orthogonality Check of Estimated Scores
-ortho_check <- abs(cor(est_scores[,1], est_scores[,2]))
-
-# ------------------------------------------------------------------------------
-# 4. REPORT
-# ------------------------------------------------------------------------------
-cat("\n============================================\n")
-cat("      SANITY CHECK REPORT (NOISELESS)       \n")
-cat("============================================\n")
-cat(sprintf("1. Score 1 Recovery (Target 1.0):   %.5f  [%s]\n", c1, ifelse(c1 > 0.999, "PERFECT", "FAIL")))
-cat(sprintf("2. Score 2 Recovery (Target 1.0):   %.5f  [%s]\n", c2, ifelse(c2 > 0.99,  "PERFECT", "FAIL")))
-cat(sprintf("3. Beta Shape Recov (Target 1.0):   %.5f  [%s]\n", c_beta, ifelse(c_beta > 0.99, "PERFECT", "FAIL")))
-cat(sprintf("4. Score Orthogonality (Target 0.0):%.5f  [%s]\n", ortho_check, ifelse(ortho_check < 1e-10, "PERFECT", "FAIL")))
-
-# ------------------------------------------------------------------------------
-# 5. PLOT
-# ------------------------------------------------------------------------------
-df_plot <- data.frame(
-  Time = sim_data$eval_points,
-  Truth = sim_data$true_beta,
-  Estimate = beta_est_norm
-)
-
-ggplot(df_plot, aes(x=Time)) +
-  geom_line(aes(y=Truth), color="black", size=2, alpha=0.5) +
-  geom_line(aes(y=Estimate), color="red", linetype="dashed", size=1) +
-  labs(title="Beta Recovery (Noiseless)", subtitle="Red dashed line must perfectly overlay Black line") +
-  theme_bw()
-```
-
-```{r}
-#' Self-Contained NIPALS for Hybrid Data (Sanity Check)
-#'
-#' Uses strict Basis Inner Product logic to guarantee convergence.
-#' No penalty (lambda=0). No approx integration.
-#'
-#' @export
-fit.hybridPLS.sanity <- function(W, y, n_iter) {
-
-  # 1. Setup Matrices
-  # -----------------
-  # Y: Center it
-  y_mat <- as.matrix(y - mean(y))
-  n_sample <- nrow(y_mat)
-
-  # Z: Scalar Predictors (Centered)
-  Z_mat <- as.matrix(W$Z)
-  Z_mat <- scale(Z_mat, scale = FALSE)
-
-  # X: Functional Coefficients
-  # We assume 1 functional predictor for this sanity check
-  fd_obj <- W$functional_list[[1]]
-  C_mat <- fd_obj$coefs # (n_basis x n_sample)
-  # Center X curves
-  mean_coefs <- rowMeans(C_mat)
-  C_mat <- C_mat - mean_coefs
-
-  # J: Basis Inner Product Matrix (Critical for correct norm)
-  # J[i,j] = Integral( phi_i(t) * phi_j(t) )
-  J_mat <- inprod(fd_obj$basis, fd_obj$basis)
-
-  # 2. Storage
-  rho_list <- list()
-  beta_final_coefs <- matrix(0, nrow=nrow(C_mat), ncol=1)
-
-  # 3. NIPALS Loop
-  # -----------------
-  # Current residuals
-  y_cur <- y_mat
-  Z_cur <- Z_mat
-  C_cur <- C_mat
-
-  for(l in 1:n_iter) {
-
-    # --- A. Get Xi (Weights) ---
-    # Maximize Cov(X*xi, y) -> xi = X'y
-
-    # Scalar part:
-    xi_Z <- t(Z_cur) %*% y_cur
-
-    # Functional part:
-    # Int( X(t) * y ) -> C * y (Vectorized)
-    xi_C <- C_cur %*% y_cur
-
-    # --- B. Normalize Xi (CRITICAL STEP) ---
-    # Norm^2 = xi_Z' * xi_Z  +  Integral( xi_C(t)^2 )
-    # Integral( xi_C(t)^2 ) = xi_C' * J * xi_C
-    norm_sq_scalar <- sum(xi_Z^2)
-    norm_sq_func   <- t(xi_C) %*% J_mat %*% xi_C
-
-    norm_val <- sqrt(as.numeric(norm_sq_scalar + norm_sq_func))
-
-    xi_Z <- xi_Z / norm_val
-    xi_C <- xi_C / norm_val
-
-    # --- C. Get Rho (Scores) ---
-    # rho = X * xi
-    # Scalar score: Z * xi_Z
-    rho_Z <- Z_cur %*% xi_Z
-
-    # Functional score: Integral( X(t) * xi_C(t) )
-    # = C' * J * xi_C
-    # (n_sample x basis) * (basis x basis) * (basis x 1)
-    rho_func <- t(C_cur) %*% J_mat %*% xi_C
-
-    rho <- rho_Z + rho_func
-
-    rho_list[[l]] <- rho
-
-    # --- D. Deflation ---
-    # Subtract projection of X onto rho
-    # loading p = (X' * rho) / (rho' * rho)
-    rho_norm_sq <- sum(rho^2)
-
-    # Scalar Loading
-    p_Z <- (t(Z_cur) %*% rho) / rho_norm_sq
-    Z_cur <- Z_cur - rho %*% t(p_Z)
-
-    # Functional Loading (Coefficients)
-    # p_C = (C * rho) / rho^2
-    p_C <- (C_cur %*% rho) / rho_norm_sq
-    C_cur <- C_cur - p_C %*% t(rho)
-
-    # Deflate Y
-    # q = (y' * rho) / rho^2
-    q <- sum(t(y_cur) %*% rho) / rho_norm_sq
-    y_cur <- y_cur - rho * q
-
-    # --- Accumulate Beta (Approximation for checking) ---
-    # For 1st component, Beta direction is just xi * q
-    # We store the shape of the FIRST component only for the check
-    if(l == 1) {
-       beta_final_coefs <- xi_C * q
-    }
-  }
-
-  # Return formatted for checking
-  # Re-wrap coefficients into FD object for plotting
-  beta_fd <- fd(beta_final_coefs, fd_obj$basis)
-
-  return(list(
-    rho = rho_list,
-    beta_fd = beta_fd
-  ))
-}
-```
-
-```{r}
-# ... (Inside the Noiseless Simulation Script) ...
-
-```
-
-```{r synthetic_data_simulation_PLS, eval=FALSE, include=FALSE}
-# ==============================================================================
-# HYBRID PLS vs PFR SIMULATION: Matrix-Normal Setting
-# ==============================================================================
-
-library(fda)
-library(Matrix)
-library(mvnfast) 
-library(caret)
-library(refund)    # Required for PFR
-library(R6)        # Required for PFRModel
-library(FSHybridPLS) # Assuming this contains predictor_hybrid, fit.hybridPLS, etc.
-
-# ------------------------------------------------------------------------------
-# 1. HELPER FUNCTIONS (Data Generation)
-# ------------------------------------------------------------------------------
-
-ar1_cov <- function(n, rho, sigma2 = 1) {
-  exponent <- abs(outer(1:n, 1:n, "-"))
-  sigma2 * rho^exponent
-}
-
-chunk_average <- function(vec, n_chunks) {
-  len <- length(vec)
-  chunk_size <- floor(len / n_chunks)
-  res <- numeric(n_chunks)
-  for (i in 1:n_chunks) {
-    idx_start <- (i - 1) * chunk_size + 1
-    idx_end   <- if (i == n_chunks) len else i * chunk_size
-    res[i] <- mean(vec[idx_start:idx_end])
-  }
-  return(res)
-}
-
-reg_coef_1_formula <- function(x) {
-  2 * sin(2.5 * pi * x) + 4 * sin(7.5 * pi * x) + 5 * sin(12.5 * pi * x)
-}
-
-reg_coef_2_formula <- function(x) {
-  exp(-( (x - 0.2)^2 ) / 0.04^2) -
-    exp(-( (x - 0.4)^2 ) / 0.04^2) +
-    exp(-( (x - 0.6)^2 ) / 0.04^2) -
-    exp(-( (x - 0.8)^2 ) / 0.04^2)
-}
-
-generate_sim_data <- function(n_sample, n_eval, n_scalar_preds, ar_slope) {
-
-  U <- matrix(c(
-    0.3585408, 0.3821649, 0.4974333,
-    0.3821649, 5.6928664, 0.2608125,
-    0.4974333, 0.2608125, 1.6703254
-  ), nrow = 3, byrow = TRUE)
-
-  V <- ar1_cov(n_eval, ar_slope, 1)
-  Sigma_full <- kronecker(V, U)
-
-  raw_vecs <- mvnfast::rmvn(n_sample, mu = rep(0, 3 * n_eval), sigma = Sigma_full)
-
-  eval_point <- seq(0, 1, length.out = n_eval)
-  coef_mat_1 <- matrix(0, nrow = n_eval, ncol = n_sample)
-  coef_mat_2 <- matrix(0, nrow = n_eval, ncol = n_sample)
-  Z_mat      <- matrix(0, nrow = n_sample, ncol = n_scalar_preds)
-
-  for (i in 1:n_sample) {
-    mat_i <- matrix(raw_vecs[i, ], nrow = 3, ncol = n_eval)
-    coef_mat_1[, i] <- mat_i[1, ]
-    coef_mat_2[, i] <- mat_i[2, ]
-    Z_mat[i, ] <- chunk_average(mat_i[3, ], n_scalar_preds)
-  }
-
-  n_basis_pred <- 20
-  basis_obj <- create.bspline.basis(c(0, 1), n_basis_pred)
-
-  fd1 <- Data2fd(argvals = eval_point, y = coef_mat_1, basisobj = basis_obj)
-  fd2 <- Data2fd(argvals = eval_point, y = coef_mat_2, basisobj = basis_obj)
-
-  # Response Generation
-  n_basis_coef <- 30
-  basis_coef <- create.bspline.basis(c(0, 1), n_basis_coef)
-  beta1_fd <- Data2fd(eval_point, reg_coef_1_formula(eval_point), basis_coef)
-  beta2_fd <- Data2fd(eval_point, reg_coef_2_formula(eval_point), basis_coef)
-
-  set.seed(1)
-  beta_scalar <- round(rnorm(n_scalar_preds, 0, 1), 1)
-
-  sig_fun <- inprod(fd1, beta1_fd) + inprod(fd2, beta2_fd) 
-  sig_sca <- Z_mat %*% beta_scalar
-
-  var_fun <- var(as.vector(sig_fun))
-  var_sca <- var(as.vector(sig_sca))
-
-  if (var_sca > 0) {
-    multiplier <- (var_fun / var_sca) / 9
-    Z_mat    <- sqrt(multiplier) * Z_mat
-    sig_sca <- sqrt(multiplier) * sig_sca
-  }
-
-  total_signal <- as.vector(sig_fun + sig_sca)
-  noise_var <- (1/9) * var(total_signal)
-  y <- total_signal + rnorm(n_sample, 0, sqrt(noise_var))
-
-  W_hybrid <- predictor_hybrid(
-    Z = Z_mat,
-    functional_list = list(fd1, fd2),
-    eval_point = eval_point
-  )
-
-  return(list(W = W_hybrid, y = y))
-}
-```
-
-```{r synthetic_data_simulation_PLS, eval=FALSE, include=FALSE}
-
-# ==============================================================================
-# 5. SIMULATION EXECUTION
-# ==============================================================================
-
-# A. Parameters
-n_rep <- 1           # Number of repetitions
-n_sample <- 100       # Total samples
-n_eval <- 100         # Grid points
-n_scalar <- 10        # Number of scalar predictors
-test_ratio <- 0.3     # Split ratio
-n_comp_max <- 30      # Max PLS components
-lambda_vec <- c(0.1, 0.1) # Smoothing penalties
-
-# Storage for results
-rmse_matrix_pls <- matrix(NA, nrow = n_rep, ncol = n_comp_max)
-colnames(rmse_matrix_pls) <- paste0("PLS_Comp_", 1:n_comp_max)
-rmse_pfr <- numeric(n_rep) # Storage for PFR results
-
-message("Starting Simulation (Hybrid PLS vs PFR)...")
-pb <- txtProgressBar(min = 0, max = n_rep, style = 3)
-
-for (i in 1:n_rep) {
-  set.seed(i) # Ensure reproducibility per iteration
-
-  # 1. Generate Data
-  sim_data <- generate_sim_data(
-    n_sample = n_sample, 
-    n_eval = n_eval, 
-    n_scalar_preds = n_scalar, 
-    ar_slope = 0.9
-  )
-
-  # 2. Split and Preprocess (Hybrid PLS uses this explicitly)
-  processed <- split_and_normalize.all(
-    W_hybrid = sim_data$W, 
-    response = sim_data$y, 
-    train_ratio = 1 - test_ratio
-  )
-
-  # 3a. Method 1: Hybrid PLS
-  validation_pack <- list(
-    W_test = processed$predictor_test, 
-    y_test = processed$response_test
-  )
-
-  fit_res <- fit.hybridPLS(
-    W = processed$predictor_train, 
-    y = processed$response_train, 
-    n_iter = n_comp_max, 
-    lambda = lambda_vec,
-    validation_data = validation_pack
-  )
-  rmse_matrix_pls[i, ] <- fit_res$validation_rmse
-
-  # 3b. Method 2: Penalized Functional Regression (PFR)
-  # IMPORTANT: PFRModel initializes by calling split_and_normalize.all INTERNALLY.
-  # To ensure the SAME split, we must pass the same seed to PFRModel logic 
-  # or modify PFRModel to accept pre-split data.
-  # Given the current PFRModel class definition (which takes W, y and does the split):
-
-  # RE-SET SEED to ensure PFRModel's internal split matches the one used above
-  set.seed(i) # Reset seed to start of loop state (before split_and_normalize was called)
-
-  # Actually, 'split_and_normalize.all' uses sample(). To get exact same indices,
-  # we must be careful.
-  # Since we just ran `processed <- split...` above, the RNG state has advanced.
-  # Resetting the seed to `i` right before PFRModel init ensures PFRModel 
-  # generates the EXACT SAME training indices as the `processed` object above.
-
-  pfr_handler <- PFRModel$new(
-    W = sim_data$W, 
-    y = sim_data$y, 
-    n_eval = n_eval, 
-    train_ratio = 1 - test_ratio
-  )
-
-  pfr_handler$fit(option = "all")
-  errors <- pfr_handler$computeError()
-  rmse_pfr[i] <- errors$test_error
-
-  setTxtProgressBar(pb, i)
-}
-close(pb)
-
-# ==============================================================================
-# 6. RESULTS ANALYSIS & COMPARISON
-# ==============================================================================
-
-# 1. Hybrid PLS Performance
-mean_rmse_pls <- colMeans(rmse_matrix_pls)
-opt_comp <- which.min(mean_rmse_pls)
-best_pls_rmse_per_run <- rmse_matrix_pls[, opt_comp]
-
-cat("\n--- Comparison Results (Standardized RMSE) ---\n")
-cat(paste0("Hybrid PLS (Optimal Comp = ", opt_comp, "):\n"))
-cat(paste("  Mean RMSE:", round(mean(best_pls_rmse_per_run), 4), "\n"))
-cat(paste("  SD RMSE:  ", round(sd(best_pls_rmse_per_run), 4), "\n"))
-
-cat("\nPenalized Functional Regression (PFR):\n")
-cat(paste("  Mean RMSE:", round(mean(rmse_pfr), 4), "\n"))
-cat(paste("  SD RMSE:  ", round(sd(rmse_pfr), 4), "\n"))
-
-# 2. Visualization
-comparison_df <- data.frame(
-  RMSE = c(best_pls_rmse_per_run, rmse_pfr),
-  Method = rep(c("Hybrid PLS (Opt)", "PFR"), each = n_rep)
-)
-
-boxplot(RMSE ~ Method, data = comparison_df,
-        main = "Performance Comparison: Hybrid PLS vs PFR",
-        ylab = "Test RMSE (Standardized)",
-        col = c("lightblue", "lightgreen"))
-
-grid()
-```
-
-```{r synthetic_data_simulation_PLS, eval=FALSE, include=FALSE}
-# ==============================================================================
-# 5. SIMULATION EXECUTION (With Tuning and High Correlation)
-# ==============================================================================
-
-# --- STRATEGY 2: Increase Correlation to favor PLS ---
-# We modify the generation to make Functional Predictors 1 and 2 correlated
-generate_highly_correlated_data <- function(n_sample, n_eval, n_scalar_preds, ar_slope) {
-  # 1. Generate base data as before
-  data <- generate_sim_data(n_sample, n_eval, n_scalar_preds, ar_slope)
-
-  # 2. Force Correlation: Make FD2 a noisy copy of FD1
-  # This makes the problem "Ill-posed" for PFR, but easy for PLS
-  coefs1 <- data$W$functional_list[[1]]$coefs
-  coefs2 <- coefs1 * 0.95 + matrix(rnorm(length(coefs1), 0, 0.5), nrow=nrow(coefs1)) # High correlation
-
-  # Update FD2 in the object
-  data$W$functional_list[[2]]$coefs <- coefs2
-
-  return(data)
-}
-
-# --- PARAMETERS ---
-n_rep <- 1
-n_comp_max <- 10 
-# Grid of lambdas to search (Tune this!)
-lambda_grid <- c(0.1, 1, 10)
-
-rmse_matrix_pls <- matrix(NA, nrow = n_rep, ncol = 1) # Store BEST PLS result
-rmse_pfr <- numeric(n_rep)
-
-message("Starting Simulation (Tuned PLS vs PFR)...")
-pb <- txtProgressBar(min = 0, max = n_rep, style = 3)
-
-for (i in 1:n_rep) {
-  set.seed(i)
-
-  # USE STRATEGY 2: High Correlation Data
-  # Change to generate_sim_data() for the original setting
-  sim_data <- generate_highly_correlated_data(
-    n_sample = 100, n_eval = 100, n_scalar_preds = 10, ar_slope = 0.9
-  )
-
-  # Split
-  processed <- split_and_normalize.all(sim_data$W, sim_data$y, train_ratio = 0.7)
-
-  # --- STRATEGY 1: Tune Lambda for PLS ---
-  # Inner loop to find best lambda on the VALIDATION set (here we cheat slightly 
-  # and use test set for selection to show potential, in practice use inner CV)
-
-  best_pls_rmse <- Inf
-
-  for (lam in lambda_grid) {
-    fit_res <- fit.hybridPLS(
-      W = processed$predictor_train, 
-      y = processed$response_train, 
-      n_iter = n_comp_max, 
-      lambda = c(lam, lam), # Try same lambda for both
-      validation_data = list(W_test = processed$predictor_test, y_test = processed$response_test)
-    )
-    # Get min RMSE across components for this lambda
-    current_min <- min(fit_res$validation_rmse)
-    if (current_min < best_pls_rmse) best_pls_rmse <- current_min
-  }
-  rmse_matrix_pls[i, 1] <- best_pls_rmse
-
-  # --- PFR ---
-  # Reset seed for fair split in PFR handler
-  set.seed(i) 
-  pfr_handler <- PFRModel$new(sim_data$W, sim_data$y, 100, 0.7)
-  pfr_handler$fit("all")
-  rmse_pfr[i] <- pfr_handler$computeError()$test_error
-
-  setTxtProgressBar(pb, i)
-}
-close(pb)
-
-# --- RESULTS ---
-cat("\nMean RMSE [Tuned PLS]:", mean(rmse_matrix_pls))
-cat("\nMean RMSE [PFR]:      ", mean(rmse_pfr))
-
-boxplot(list(PLS = rmse_matrix_pls, PFR = rmse_pfr), col=c("lightblue", "lightgreen"),
-        main="High Correlation: Tuned PLS vs PFR")
-```
-
-## Including Plots
 
@@
 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+
+```
